### 2017-09-26 Slides/OneBit_Allerton_slides.tex
Add files via upload

\documentclass[mathserif]{beamer}
%\usepackage{beamerthemesplit}

\usepackage{bm}
\usepackage{tikz}

\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{pstool}

\usepackage[miktex]{gnuplottex}

\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
\tikzstyle{ssum}=[circle, fill=red!10,draw=black,line width=1pt,minimum size = 0.05cm]
\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.5cm,thick ]
\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
\tikzstyle{Est}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1cm,thick ]

\usetikzlibrary{arrows, positioning}
%\usetikzlibrary{shapes.geometric, ,positioning}
\tikzstyle{box}=[draw, fill=blue!20, scale= 0.8, minimum size=2em]
\tikzstyle{circ}=[draw, circle, fill=red!20, scale= 0.8, minimum size=2em]
\tikzstyle{circ_blue}=[draw, circle, fill=blue!20, scale= 0.8, minimum size=2em]
\tikzstyle{box_red}=[draw, fill=red!20, minimum size=2em, scale= 0.8]

\newcommand{\mmse}{\mathsf{mmse}}
\newcommand{\thetac}{{\color{red} \theta}}
\newcommand{\enc}{\mathsf{enc}}
\newcommand{\qnt}{\mathsf{qnt}}
\newcommand{\sgn}{\mathsf{sign}}
\newcommand{\unif}{\mathsf{unif}}

\newtheorem{prop}{Proposition}
\newtheorem{lem}{Lemma}

\newcommand{\ex}[1]{\ensuremath{\mathbb{E}\left[ #1\right]}}

% bold charactors
\newcommand{\bA}{\bm{A}}
\newcommand{\bB}{\bm{B}}
\newcommand{\bC}{\bm{C}}
\newcommand{\bD}{\bm{D}}
\newcommand{\bE}{\bm{E}}
\newcommand{\bF}{\bm{F}}
\newcommand{\bG}{\bm{G}}
\newcommand{\bH}{\bm{H}}
\newcommand{\bI}{\bm{I}}
\newcommand{\bJ}{\bm{J}}
\newcommand{\bK}{\bm{K}}
\newcommand{\bL}{\bm{L}}
\newcommand{\bM}{\bm{M}}
\newcommand{\bN}{\bm{N}}
\newcommand{\bO}{\bm{O}}
\newcommand{\bP}{\bm{P}}
\newcommand{\bQ}{\bm{Q}}
\newcommand{\bR}{\bm{R}}
\newcommand{\bS}{\bm{S}}
\newcommand{\bT}{\bm{T}}
\newcommand{\bU}{\bm{U}}
\newcommand{\bV}{\bm{V}}
\newcommand{\bW}{\bm{W}}
\newcommand{\bX}{\bm{X}}
\newcommand{\bY}{\bm{Y}}
\newcommand{\bZ}{\bm{Z}}

\newcommand{\ba}{\bm{a}}
\newcommand{\bb}{\bm{b}}
\newcommand{\bc}{\bm{c}}
\newcommand{\bd}{\bm{d}}
\newcommand{\be}{\bm{e}}
%\newcommand{\bf}{\bm{f}}
\newcommand{\bg}{\bm{g}}
\newcommand{\bh}{\bm{h}}
\newcommand{\bi}{\bm{i}}
\newcommand{\bj}{\bm{j}}
\newcommand{\bk}{\bm{k}}
\newcommand{\bl}{\bm{l}}
%\newcommand{\bm}{\bm{m}}
\newcommand{\bn}{\bm{n}}
\newcommand{\bo}{\bm{o}}
\newcommand{\bp}{\bm{p}}
\newcommand{\bq}{\bm{q}}
\newcommand{\br}{\bm{r}}
\newcommand{\bs}{\bm{s}}
\newcommand{\bt}{\bm{t}}
\newcommand{\bu}{\bm{u}}
\newcommand{\bv}{\bm{v}}
\newcommand{\bw}{\bm{w}}
\newcommand{\bx}{\bm{x}}
\newcommand{\by}{\bm{y}}
\newcommand{\bz}{\bm{z}}

\newcommand{\reals}{\mathbb{R}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\snr}{\mathsf{snr}}
\newcommand{\normal}{\mathcal{N}}
\newcommand{\gmid}{\! \mid \!}

%%% Use any fonts you like.
%\usepackage{helvet}

\title{Mean Estimation from One-bit Measurements}
%\subtitle{ISIT 2017}
\author{
\textbf{Alon Kipnis} (Stanford) \\
John Duchi (Stanford)\\ 
}
\date[Allerton 2017]{Allerton \\ October 2017}

\setbeamertemplate{navigation symbols}{}
\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}
}

%\setbeamerfont{page number in head/foot}{size=\large}
\graphicspath{{../Figs}}

\setbeamertemplate{footline}[frame number]

\begin{document}
\graphicspath{{../Figs/}}

\frame[plain]{\titlepage}

\section{Introduction}

\subsection{Motivation}
\begin{frame}
\frametitle{Motivation}
\framesubtitle{}
Point estimation under communication constraints:\\
\begin{center}
\begin{tikzpicture}[>= latex', node distance = 2cm]
\node at (0,0) (p_th) {$p_{\thetac}(x)$};
\node[right of = p_th] (sample) {$X_1,\ldots,X_n$};
\node[box, right = .75cm of sample, align = left](pm) {limited bits \\ per sample
};
\node[right = .75 cm of pm](th_hat) {$\widehat{\thetac}$};
%\node[below = .1cm of  Xhat]{\textcolor{blue}{reconstruction}};
\draw[->, thick] (p_th) -- (sample);
\draw[->, thick] (sample) -- (pm);
\draw[->, thick] (pm) -- (th_hat);
\end{tikzpicture}
\end{center}
Estimation error is due to:
\begin{itemize}
\item[(i)] limited data 
\item[(ii)] limited bits
\end{itemize}
\bigskip

Relevant scenarios:
\begin{itemize}
\item big data
\item low-power sensors 
\item distributed computing / optimization (bottleneck is due to communication between processing units)

\end{itemize}

\end{frame}

\begin{frame}
\frametitle{This talk: }
\framesubtitle{}
Estimating the mean $\thetac$ of a normal distribution $\mathcal N(\thetac,\sigma^2)$ from one-bit per sample ($\sigma$ is known)
\bigskip

\end{frame}
%

\begin{frame}
\frametitle{Three Encoding Scenarios}

\begin{center}
\begin{tikzpicture}[node distance=2cm,auto,>=latex]
  \node at (0,0) (source) {$X_1$} ;
  \node[int1, right of = source, node distance = 2cm, scale = 0.75] (enc1) {Enc 1};  
\draw[->,line width = 2pt] (source) -- (enc1);

 \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
\node[int1, right of = source2, node distance = 2cm, scale = 0.75] (enc2) {Enc 2};  
\draw[->,line width = 2pt] (source2) -- (enc2);

\node[below of = source2, node distance = 2.5cm] (source3) {$X_n$};
\node[int1, right of = source3, node distance = 2cm, scale = 0.75] (enc3) {Enc n};  
\draw[->,line width = 2pt] (source3) -- (enc3);

%\node[above of = source, node distance = 1cm] (dist) {${\mathcal N} \left(\theta, \sigma^2 \right)$};

\node[Est, right of = enc2, node distance = 5cm] (est) {Est};
\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -2.5cm] (mes1) {$M_1 \in \left\{-1,1\right\}$} (est);   
\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M_2 \in \left\{-1,1\right\}$} (est);   
\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -2.5cm]  {$M_n \in \left\{-1,1\right\}$} (est);   
\node[right of = est, node distance = 2.5cm] (dest) {$\widehat{\theta}(M^n)$};
\draw[->, line width=2pt] (est) -- (dest);

\node[below of = source2, node distance = 0.5cm] {$\vdots$};
\node[below of = enc2, node distance = 0.5cm] {$\vdots$};
\node[below of = mes2, node distance = 0.7cm] {$\vdots$};

\visible<2>{
\draw[<->,line width = 2pt, color = red] (enc1) -- (enc2);   
\draw[<->,line width = 2pt, color = red] (enc2) -- (enc3);
\draw[dashed,line width = 2pt, color = white] (enc2)+(0,-0.5) -- +(0,-1.5);}

\visible<3->{
\draw[->,line width = 2pt, color = blue] (enc1) -- (enc2);   
\draw[->,line width = 2pt, color = blue] (enc2) -- (enc3);
\draw[dashed,line width = 2pt, color = white] (enc2)+(0,-0.7) -- +(0,-1.7);}

\end{tikzpicture}
\end{center}

\begin{itemize}
\item Distributed: $M_i = f_i(X_i)$
\visible<2->{
\item {\color{red} Centralized}: $M^n = (M_1,\ldots,M_n) = f(X_1,\ldots,X_n)$ }
\visible<3->{
\item {\color{blue} Adaptive / Sequential}: $M_i = f_i(X_i,M^{i-1})$ }
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Related Work}
\begin{itemize} 
\item Estimation via compressed information [Han '87], [Zhang \& Berger '88]
\item Distributed hypothesis testing under quantization [Tsitsiklis '88]
\item Estimation from multiple machines subject to a bit constraint [Zhang, Duchi, Jordan, Wainwright '13]
\item Remote multiterminal source coding (CEO) [Berger, Zhang, Wiswanathan '96], [Oohama '97]
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Consistency}
Q: in what setting consistent estimation is possible? \\
\bigskip
\pause
A: all !
\[
M_i = \mathbf 1(X_i>0),\quad i=1,\ldots,n
\]
(as in the distributed setting)
\[
\frac{1}{n}\sum_{i=1}^n M_i \rightarrow \Prob\left(X<0 \right) = \Phi\left(X/\sigma<\thetac\right)
\]
\end{frame}

\subsection{Preliminary}

\begin{frame}
\frametitle{Efficiency}
\textbf{Definition:} \emph{asymptotic relative efficiency (ARE)} of an estimator:
\[
\mathrm{ARE}(\widehat{\theta}) \triangleq \lim_{n\rightarrow \infty} \frac{\mathbb E \left[ \left(\widehat{\theta}-\theta \right)^2 \right]}{\sigma^2 / n}
\]
($\sigma^2/n$ is the minimax risk without communication constraints)
%MSE of sample mean $\bar{\theta}$: 
%\[
%\mathbb E \left[ \left(\bar{\theta}-\theta \right)^2 \right] = \frac{\sigma^2}{n}
%\]
%(minimax estimator without communication constraint)

\bigskip
\pause
Q: in what scenarios the ARE is finite? \\
\bigskip
\pause
This talk: all three scenarios

\end{frame}

\begin{frame}
\frametitle{ARE under Centralized Encoding}

\begin{prop} If the parameter space $\Theta$ is bounded, then the ARE under centralized encoding is $1$
\end{prop}
\textbf{Proof:}
\[
\mathbb E \left( \theta- \widehat{\theta} \right)^2 = \overbrace{\mathbb E \left( \theta- \bar{\theta} \right)^2}^{\sigma^2/n} + \mathbb E \left( \bar{\theta}- \widehat{\theta} \right)^2 
\]
\begin{itemize}
\item Encoder is required to describe $\bar{\theta}$ using $n$ bits
\begin{itemize}
\item divide parameter space $\Theta$ into $2^n$ regions of equal size
\item send region index where $\bar{\theta}$ falls
\end{itemize}
\item MSE in estimating $\bar{\theta}$ decreases exponentially in $n$ 
\end{itemize}
\bigskip
Note: globally optimal strategy for a finite $n$ is hard to derive since mean of $\bar{\theta}$ is unknown 
\end{frame}

\begin{frame}
\frametitle{Relation to CEO}

\begin{center}
\begin{tikzpicture}[node distance=2cm,auto,>=latex]
  \node at (0,0) (source) {$\thetac$} ;
  \node[ssum, right of = source, scale = 0.75] (sum1) {+};
  \node[above of = sum1, node distance = 1.2cm] (z1) {$Z_1$};
  \node[int1, right of = sum1, node distance = 2cm, scale = 0.75] (enc1) {Enc 1};  
\draw[->,line width = 2pt] (source) -- (sum1); 
\draw[->,line width = 2pt] (sum1) -- node[above] {$X_1$} (enc1); 
\draw[->,line width = 2pt] (z1) -- (sum1);

\node[below of = sum1, node distance = 0.5cm] (vdts) {$\vdots$};
\node[below of = enc1, node distance = 0.5cm] (vdts2) {$\vdots$};

 \node[coordinate,below of = source, node distance = 2.5cm] (source2) {};
 \node[ssum, right of = source2, scale = 0.75] (sum2) {+};
  \node[above of = sum2, node distance = 1.2cm] (z2) {$Z_n$};
\node[int1, right of = sum2, node distance = 2cm, scale = 0.75] (enc2) {Enc n};

\node[Est, right of = enc2, node distance = 5cm, yshift = 1cm] (est) {Est};

\draw[->,line width = 2pt] (source) -- (sum2); 
%\draw[->,line width = 1pt, dashed] (source) -- (vdts);
%\draw[->,line width = 1pt, dashed] (vdts)--(vdts2);
%\draw[->,line width = 1pt, dashed] (vdts2) -- (est);

\draw[->,line width = 2pt] (sum2) -- node[above] {$X_n$} (enc2); 
\draw[->,line width = 2pt] (z2) -- (sum2);

%\draw[fill=blue!10] (enc1)+(5,0.5) rectangle (enc2)+(2,-0.5);

%\node[int1, right of = enc2, node distance = 6cm, scale = 0.75] (est) {Est};
\draw[->,line width = 2pt] (enc1) -- node[above, xshift = 0cm] (mes1) {$R_1$} (est);   
\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$R_n$} (est);   
\node[right of = est, node distance = 2cm] (dest) {$\widehat{\theta}$};
\draw[->, line width=2pt] (est) -- (dest);
\end{tikzpicture}
\end{center}

Assume:
\begin{itemize}
\item $\theta \sim \mathcal N(0,\sigma_\theta^2)$, ~~~ 
\item $Z_1,\ldots,Z_n \overset{\mathrm{i.i.d}}{\sim}\mathcal N(0,\sigma^2)$
\end{itemize}
Encode $k$ instances:
\begin{itemize}
\item $R_1 = \ldots = R_n =1 $
\item $D_{CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left(\theta_j-\widehat{\theta}_j \right)^2$
\end{itemize}
\end{frame}

\begin{frame}

From [K., Rini, Goldsmith '17]: 
\[
D_{CEO} \leq \frac{4}{3} \frac{\sigma^2}{n} + o(1)
\]
%\begin{itemize}
%\item[] CEO distortion satisfies [Chen, Zhang, Berger, Wicker '04]:
%\[ D^\star = \frac{4}{3} %\frac{\sigma^2}{n} + o(n^{-1}) \]
%\end{itemize}
ARE of $4/3$ can be attained in a fully distributed encoding (with encoding over blocks of multiple problem instances)
\bigskip
\begin{alertblock}{Conclusion}
Distributed encoding is almost not a limiting factor 
(although inability to exploit concentration of measure in high dimension -- might!)
\end{alertblock}
\end{frame}

\section{Adaptive Encoding}

\begin{frame}
\frametitle{Main Results (adaptive encoding)}

\begin{theorem}[converse]
No estimator have ARE lower than $\pi/2$
\end{theorem}

\begin{theorem}[achievability]
Assume that $\Theta$ is a bounded interval. There exists an estimator with ARE equals to $\pi/2$
\end{theorem}

\begin{theorem}[one-step optimal strategy]
The next step one-bit message that minimizes the MSE is of the form $M = \sgn (X-\tau)$ where $\tau$ satisfies the fixed-point equation 
\[
\tau = \frac{1}{2} \left( \frac{ \int_{-\infty}^\tau \theta \pi(d\theta) }{\int_{-\infty}^\tau \pi(d\theta)}  + \frac{ \int_{\tau}^\infty \theta \pi(d\theta)}{\int_{\tau}^\infty \pi(d\theta)} \right)
\]
\end{theorem}
\end{frame}

\begin{frame}
\frametitle{Proof}
\framesubtitle{converse (ARE $\geq \pi/2$)}
Assume a prior $\pi(d\theta)$ on $\Theta$ with location Fisher information $I_\pi$. \\

The van-Trees inequality (e.g. [Tsybakov '08]) implies
\[
\mathbb E \left(\theta - \widehat{\theta} \right)^2 \geq \frac{1}{\mathbb E I_\theta(M^n) + I_\pi} \geq \frac{1}{\sum_{i=1}^n I_\theta(M_i|M^{i-1}) + I_\pi} 
\]
\begin{lem}
\[
I_\theta(M_i|M^{i-1}) \leq 2/(\pi\sigma^2)
\]
\end{lem}
(proof by induction over a finite set of intervals approximating $M_i^{-1}(1)$ given $M^{i-1}$)
\end{frame}

\begin{frame}
\frametitle{Proof}
\framesubtitle{achievability (existence of an estimator with ARE $= \pi/2$)}
[Polyak \& Juditsky '92]: \\
\[
\begin{cases}
\theta_i = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_i)& i=1,\ldots,n\\
\widehat{\theta} = \frac{1}{n} \sum_{i=1}^n \theta_i &
\end{cases}
\]
where:
\begin{itemize}
\item[(i)] $\gamma_n \rightarrow 0^+$ ``not too slow'' 
\item[(ii)] $\psi(x) = \mathbb E \varphi(x+Z)$ 
\item [(iii)] $\chi(x) = \mathbb E \varphi^2(x+Z)$ 
\item[(iv)] some regularity  conditions on $\varphi$, $\chi$, $\psi$
\end{itemize}
Then 
\[
\sqrt{n}(\theta- \widehat{\theta}) \rightarrow \mathcal N\left(0,V\right)
\]
where $V = \chi(0)/\psi'^2(0)$.  \\
\medskip
\pause
Proof of theorem: take $\varphi(x) = \sgn(x)$
\end{frame}

\begin{frame}
\frametitle{One-step optimality}
%Upon observing $M^{i-1}$, what is the optimal detection region $M_i^{-1}(1)$ that minimizes the MSE ? \\
\begin{theorem}
Let $\pi(\theta)$ be an absolutely continuous log-concave distribution. For $X\sim \mathcal N(\theta,\sigma^2)$ let
\[
M = \sgn(X-\tau)
\]
where $\tau$ is the unique solution to
\[
\tau = \frac{1}{2} \left( \frac{ \int_{-\infty}^\tau \theta \pi(d\theta) }{\int_{-\infty}^\tau \pi(d\theta)}  + \frac{ \int_{\tau}^\infty \theta \pi(d\theta)}{\int_{\tau}^\infty \pi(d\theta)} \right)
\]
Then for any $M'(X) \in \{-1,1\}$ and $\widehat{\theta}(M')$:
\[
\mathbb E \left(\theta- \widehat{\theta}(M') \right)^2 \geq \mathbb E \left(\theta - \mathbb E[\theta|M] \right)^2
\]
\end{theorem}
\vspace{-20pt}
\begin{alertblock}{Interpertation:}
The optimal one-bit message is a threshold detector. The threshold is the fixed-point that balances conditional center of masses given the message
\end{alertblock}

\end{frame}

\begin{frame}
\frametitle{One-step Optimal Scheme}
Initialization: $P_0(t) = \pi(\theta)$ \\
Repeat for $n \geq 1$:
\begin{itemize}
\item[(i)] $P_n(t) = \Prob(\theta = t|M^n) = \alpha_n P_{n-1}(t) \Phi \left(M_n \frac{t-\tau_{n-1}}{\sigma} \right)$ 
\item[(ii)] $\widehat{\theta} = \mathbb E[\theta | M^n] = \int t P_n(t)dt $ 
\item[(iii)] Find $\tau_n$ from 
\[
\tau_n = \frac{1}{2} \left( \frac{ \int_{-\infty}^\tau t P_n(t)dt }{\int_{-\infty}^\tau P_n(t)dt}  + \frac{ \int_{\tau}^\infty t P_n(t)dt}{\int_{\tau}^\infty P_n(t)dt} \right)
\]
\item[(iv)] $M_{n+1} = \sgn(X_{n+1}-\tau_n)$
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Numerical Example}
\begin{center}
Normalized empirical risk versus number of samples $n$ \\
(500 Monte Carlo experiments)
\begin{tikzpicture}
\node at (0,0) {\includegraphics[scale=0.5]{one_bit_adpative}};
%\node[color = blue,  minimum width=1cm, align = left] at (1.5,1.5) {assymptotically optimal \eqref{eq:sgd_est}};
%\node[color = red, minimum width=1cm, align = left] at (1.5,0.55) {one-step optimal \eqref{eq:message_update}} ;
\node[rotate = 90, scale = 1] at (-5,0) {$n \mathbb E \left(\widehat{\theta}_n - \theta \right)^2$};
\node[scale = 1] at (0,-3) {$n$};
%\draw[dashed] (-3.5,1.18) node[left, scale = 0.7] {$\frac{\pi}{2}$}-- (-3,1.18);
\end{tikzpicture}
$\theta \sim \unif(-3,3)$
\end{center}
\end{frame}

\section{Distributed Encoding}

\begin{frame}
\frametitle{Distributed Encoding}
\framesubtitle{Threshold Detection}
We consider only messages of the form
\[
M_i = \sgn(X_i - t_i),\quad i=1,\ldots,n
\]
\begin{center}
\begin{tikzpicture}
\node[coordinate] at(0,0) (ti) {};
\draw[color = red, line width = 1.5pt] (ti)+(0,0.2) -- node[above, yshift = 0.07cm] {\color{black} $t_i$} +(0,-0.2);
\draw[<-,line width = 1pt] (-3,0) -- node[above] {$M_i=-1$} (ti);
\draw[->,line width = 1pt] (ti) -- node[above] {$M_i=1$} (6,0);
\end{tikzpicture}
\end{center}
Assume:
\[
\lambda_n([a,b]) = \frac{1}{n} \left| [a,b] \cap \left\{t_i \right\}\right|
\]
converges weakly to a probability distribution $\lambda$
\\
\bigskip
\pause
\textbf{Example:} $t_1,\ldots,t_n$ are drawn independently from a probability distribution $\lambda$ on $\mathbb R$

\end{frame}

\begin{frame}
\frametitle{Main Results (distributed encoding)}

\begin{theorem}
\begin{itemize}
\item[(i)] For any estimator $\widehat{\theta}$:
\[
\liminf_{c\rightarrow \infty}\, \liminf_{n\rightarrow \infty} \sup_{\tau\,:\,| \tau - \theta| \leq \frac{c}{\sqrt{n}} }  n \mathbb E \left(\widehat{\theta} - \tau \right)^2 \geq \sigma^2/K(\theta),
\]
where:
\begin{align*}
K(\theta) & = \int_{\mathbb R} \eta\left( \frac{t-\theta}{\sigma}\right) \lambda(dt) \\
\eta(x) & = \frac{\phi^2(x)}{\Phi(x)\Phi(-x)}
\end{align*}
\item[(ii)] The Maximum likelihood estimator $\widehat{\theta}_{ML}$  satisfies
\[
\sqrt{n}(\theta - \widehat{\theta}_{ML}) \rightarrow \mathcal N\left(0,\sigma^2/K(\theta) \right)
\]
\end{itemize}
\end{theorem}
%{\color{blue} Proof:} $P(M^n|\theta)$ is LAN
\end{frame}

\begin{frame}
\frametitle{Interpretations}
\begin{itemize}
\item ML estimator is local asymptotically minimax 
\item ARE of ML is $1/K(\theta)$ --  depends only in the asymptotic threshold density $\lambda$
\end{itemize}

\begin{itemize}
\item \[
1/K(\theta) = \frac{1}{\int \eta \left( \frac{t-\theta}{\sigma}\right) \lambda(dt)}
\geq \frac{1}{\int \eta \left(0\right) \lambda(dt)} = \pi / 2
\]
(attained by $\lambda(dt) = \delta_{\theta}$)
\item Minimax $\lambda$ for $\theta \in (-b\sigma,b\sigma)$:
\begin{align*}
\mathrm{maximize} \quad &  \inf_{\tau \in (-b,b)} \int \eta(t-\tau) \lambda(dt)
\\ \nonumber
\mathrm{subject~to} 
\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
\end{align*}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Minimax $\lambda$}
\begin{center}
support of optimal threshold density $\lambda^\star$
\vspace{10pt}
\hspace{-27pt}
\begin{tikzpicture}
\node[int] (b1) at (0,0)  {\includegraphics[scale=0.23]{minimax_b_only1}};
\node[int] (b2) at (3.9,0)  {\includegraphics[scale=0.23]{minimax_b_only2}};
\node[int] (b3) at (7.8,0)  {\includegraphics[scale=0.23]{minimax_b_only5}};
\node[int] (b4) at (0,-3)  {\includegraphics[scale=0.23]{minimax_b_only10}};
\node[int] (b5) at (3.9,-3)  {\includegraphics[scale=0.23]{minimax_b_only50}}; 
\node[int] (b6) at (7.8,-3)  {\includegraphics[scale=0.23]{minimax_b_only100}}; 
\end{tikzpicture}
\end{center}
\[
K^\star = \inf_{\theta} K^\star(\theta) = \inf_\theta \int \eta(t-\theta) \lambda^\star(dt)
\]
\end{frame}

\begin{frame}
\frametitle{Minimax $\lambda$}
\begin{center}
Minimax ARE vs size of parameter space %$\Theta= (-\sigma b, \sigma,b)$

\begin{tikzpicture}
\node at (-6,0)  {\includegraphics[scale=0.35]{k_vs_b2}};
\node at (0,-2) {$2b$};
\node[rotate = 90] at (-8.5,0) {$1/K^\star$};
\node at (-6,-2) {$2b$};

\node at (0,0)  {\includegraphics[scale=0.35]{K_vs_b}};
\node at (0,-2) {$2b$};
\node[rotate = 90] at (-2.7,0) {$\frac{1}{2b} \times 1/K^\star$};
\end{tikzpicture}
\end{center}
\begin{itemize}
\item ARE increases with size of parameter space
\end{itemize}

\end{frame}

\section{Summary}

\begin{frame}
\frametitle{Summary}
\begin{itemize}
\item Asymptotic relative efficiency in adaptive setting is $\pi/2$ regardless of size of parameter space -- only $\sim 1.57$ more samples are required due to 1-bit constraints
\item One-step optimal one-bit message is a threshold detector
\item ARE in distributed setting is finite
\item 
ML estimator is local asymptotically optimal for threshold detection
\item ARE of ML is characterized by asymptotic density of threshold values
\item Minimax ARE of ML depends on size of parameter space
\end{itemize}

\bigskip
\begin{alertblock}{Open question}
Is there a distributed encoding scheme with ARE that is both finite and independent of size of parameter space ?
\end{alertblock}

\end{frame}

\end{document}

### 2017-09-26 Slides/example.tex
Add files via upload

\documentclass{beamer}
\usetheme{Singapore}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{tikz}
\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.5cm,thick ]
\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]

\newcommand{\mmse}{\mathsf{mmse}}
\newcommand{\Xc}{{\color{black} X}}

\newcommand{\rhoc}{{\color{orange} \rho}}
\newcommand{\pc}{{\color{orange} p}}
\newcommand{\Rc}{{\color{orange} R}}
\newcommand{\gammac}{{\color{orange} \gamma}}
\newcommand{\deltac}{{\color{orange} \delta}}
\newcommand{\enc}{\mathsf{enc}}
\newcommand{\qnt}{\mathsf{qnt}}

%% Use any fonts you like.
\usepackage{helvet}

\title{Compressed-Sensing under \\ Optimal Quantization}
%\subtitle{ISIT 2017}
\author{Alon Kipnis (Stanford) \\
{Galen Reeves} (Duke)\\
Yonina Eldar (Technion) \\
Andrea Goldsmith (Stanford) }
%\institute{$*$Stanford ~~~~$+$Duke ~~~~~$\dagger$Technion}
\date{ISIT \\
\vspace{20pt}
\today 
} 
%\institute{\url{miesparza@hotmail.com}}

\beamertemplatenavigationsymbolsempty

\begin{document}

\begin{frame}[plain,t]
\titlepage
\end{frame}

\section{Introduction}

\subsection{Motivation}
\begin{frame}
\frametitle{Motivation}
\begin{center}
\begin{tikzpicture}
\node [yshift = -2cm] (source) at (0,0) {\includegraphics[scale = 0.25]
{sparse_vector}};
\node[left of = source, node distance = 2cm] (mat)  {\includegraphics[scale = 0.25]{Dense_matrix}};
\node[right of = source, node distance = 1.1cm] (noise) {\includegraphics[scale = 0.25]
{Dense_vector1}};
\node[right of = noise, node distance = 1.5cm] (observations) {\includegraphics[scale = 0.25]
{Dense_vector2}};
\node[right of = observations, node distance = 4cm] (recon1) {\includegraphics[scale = 0.25]
{sparse_reconstruction}};

\node[above of = source, yshift = 1.2cm, align = center, scale = 0.5] { sparse \\source};
\node[above of = recon1, yshift = 1.2cm, align = center, scale = 0.5] {source \\ estimate};
\node[above of = observations, yshift = 0.5cm,align = center, scale = 0.5] { observed \\signal};
\node[above of = noise, yshift = 0.5cm,align = center, scale = 0.5] {noise};
\node[above of = mat, yshift = 0.5cm, align = center, scale = 0.5] {sampling matrix};

\node[right of = source, node distance = 0.5cm] {$+$};
\node[right of = noise, node distance = 0.75cm] {$=$};

%\draw[->, line width = 3pt] (observations) -- (recon1);
\node[right of = observations, node distance = 2cm] (code) {$\left\{1,\ldots,2^{n \Rc} \right\}$};
\draw[->, line width = 3pt] (observations) -- (code);
\draw[->, line width = 3pt] (code) -- (recon1);

\end{tikzpicture}
\end{center}
Questions:
\begin{itemize}
\item In what sense observed signal is a {\color{red} compressed} representation of the sparse source?
\item What is the optimal tradeoff between reconstruction error / noise / sparsity / no. of samples and  {no. of \color{red}bits} ?
\end{itemize}
\end{frame}

\subsection{Problem Formulation}
\begin{frame}
\frametitle{Quantized Compressed-Sensing}
\begin{itemize}
\item Standard compressed sensing (CS):
\[
\Xc^n \longrightarrow \mathbf H {\Xc^n} + N^m = {Y^m}  \overset{\mathsf{est}}{\longrightarrow} {\widehat{X}^n}
\]
\item Quantized CS -- measurements vector $Y^m$ is quantized
\[
Y^m \longrightarrow Qnt(Y^m) \overset{\mathsf{est}}{\longrightarrow} {\widehat{X}^n}
\]

Previous works:
\begin{itemize} 
\item Scaler quantization -- [Goyal,\,Fletcher,\,Rangan\,'08]
\item Lasso recovery --  [Sue\,\&\,Goyal '09]
\item Optimal high-bit asymptotic -- [Wu\,\&\,Verdu\,'12]
[Dai\,\&\,Milenkovic\,'11] ({\color{red} scalar quantization with wrong proofs})
\item 1-bit quantization -- [Boufounos\,\&\,Baraniuk '08],  [Plan\,\&\,Vershynin '13]
%more precisely -- threshold detections
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{alertblock}{This work:} 
\[
Y^m \overset{\enc}{\longrightarrow} i \in \left\{1,\ldots, 2^{n\Rc}\right\} \overset{\mathsf{est/dec}}{\longrightarrow} {\widehat{X}^n}
\]
Minimal MSE distortion as a function of $\Rc$ (bits), noise, sparsity, and sampling ratio $m/n$ 
\end{alertblock}

\begin{alertblock}{Goal:}
Distortion lower bound under {\color{red}{any}} rate-$\Rc$ quantization and reconstruction techniques
\end{alertblock}
\end{frame}

\begin{frame}
\renewcommand{\Xc}{{\color{red} X}}
\frametitle{Setting}
\[
\sqrt{\gammac} \mathbf H {\Xc^n} + N^m = { Y^m} \overset{\enc}{\longrightarrow} \left\{1,\ldots,2^{n \Rc}  \right\} \overset{\mathsf{est}}{\longrightarrow} \widehat{X}^n
\]
\begin{itemize}
\item Bernoulli-Gauss source with $\pc$ nonzeros: 
\[
{\color{red}X}_i \sim (1-\pc)\delta_0+ \pc \mathcal N(0,1)
\]
\item Random sampling i.i.d matrix: $H_{i,j} \sim N\left(0,1/\sqrt{n} \right)$ 
\item White Gaussian noise: $N^m \sim N\left(0,\mathbf I_m \right)$ 
%\item $\color{orange} R$ bits per source symbol: $g: \mathbb R^m \rightarrow \left\{1,\ldots,2^{n {\color{orange} R}} \right\}$
\end{itemize}
\begin{alertblock}{Goal:}
Characterize MSE distortion in the large system limit:
\[
D\left(\pc, \deltac, \gammac, \Rc \right) =  \lim_{m/n \overset{\infty}{\longrightarrow} \deltac}  \mathbb E \left\| {\Xc^n} - \widehat{X}^n\left(\enc({Y^m}),\mathbf H)\right) \right\|^2
\]
\end{alertblock}
\end{frame}

\subsection{Background}
\begin{frame}
\renewcommand{\Xc}{{\color{black} X}}
\frametitle{Properties of Posterior $P_{X^n|Y^m}$ in the Large System Limit}
\[
{Y^m} = \sqrt{ \gammac} \mathbf H {\Xc^n} + N^m
\]
Assumptions:
\begin{itemize}
\item[(A1)] Single-letter posterior:
\[
P_{ {\Xc}_i| Y^m } \rightarrow P_{\Xc|\sqrt{\gammac {\color{red} \eta} }{\Xc}+N}
\]
\begin{tikzpicture}

\end{tikzpicture}
${\color{red} \eta}$ satisfies the fixed-point replica equation 
\[
\frac{ \deltac}{\color{red} \eta} = 1 + { \gammac} \mathsf{mmse}\left(\Xc | \sqrt{ \gammac {\color{red} \eta}} \Xc+N \right)
\]
\item[(A2)] Decoupling:
\[
P_{\Xc^L| { Y^m} } \rightarrow  \prod_{i=1}^L P_{ \Xc_i|Y^m} 
%\rightarrow  \prod_{i=1}^L P_{{\color{red}X_i}|\sqrt{{\color{orange} \gamma} \eta}{\color{red}X_i}+N_i }
\]
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Assumptions - Discussion}
\begin{itemize}
\item {\color{red} Hold for $\mathbf H$ with Gaussian entries }?
\item Predicted by the replica method [Guo\,\&\,Verdu'05] for a general i.i.d. $\mathbf H$
\item (A1) implies
\[
\lim_{n,m\rightarrow \infty} \mathsf{mmse}\left(\Xc^n | {Y^m} \right) = \mathsf{mmse}\left(\Xc|\sqrt{\gammac \eta} \Xc+N \right)
\]
Holds for a Gaussian $\mathbf H$ [Reeves\,\&\,Pfister '16]
\end{itemize}
\begin{alertblock}{Observation:}
Characterizing the MSE under quantization requires asymptotic posterior and not just its second moment
\end{alertblock}
\end{frame}

\section{Main Results}
\subsection{Blocks}
\begin{frame}
\frametitle{Result I: Achievability}

\begin{definition}
\[
D_{\Xc|\sqrt{\gammac \eta} \Xc +N }(\Rc) \triangleq  \min_{I\left(\widehat{X} ; \sqrt{ \gammac \eta} \Xc+N \right) \leq R } \mathbb E \left(\Xc - \widehat{X} \right)^2
\]
(indirect distortion-rate of $X$ given $\sqrt{ \gammac \eta} \Xc+N$)
\end{definition}

\begin{theorem} 
For every $\epsilon>0$, there exists $n$ large enough and an encoder $\enc : \mathbb R^m \rightarrow \left\{1,\ldots,2^{\lfloor n R \rfloor} \right\}$ such that
\[
\mathbb E \left\| \Xc^n - \widehat{X}^n \left( \enc(Y^m,\mathbf H) ,\mathbf H \right) \right\|^2 < D_{X| \sqrt{ \gammac \eta}\Xc+N} (\Rc) +\epsilon
\]
\end{theorem}
\end{frame}

\begin{frame}
\frametitle{Result II: Converse(ish)}
\begin{theorem}
Fix $L \in \mathbb R$ and $\epsilon>0$. There exists $n_0$ large enough such that for any $n\geq n_0$ and any encoder $g : \mathbb R^m \rightarrow \left\{1,\ldots,2^{\lfloor L R \rfloor} \right\}$, 
\[
\inf_{\widehat{X}^L(g(Y^m),\mathbf H)} \mathbb E \left\|X^L - \widehat{X}^L\right\|^2 > D_{\Xc |\sqrt{\gammac \eta}\Xc+N }(\Rc) - \epsilon,
\]
\end{theorem}
\begin{center}
\begin{tikzpicture}
\node [yshift = -2cm] (source) at (0,0) {\includegraphics[scale = 0.2]
{sparse_vector}};
\node[right of = source, node distance = 2cm] (observations) {\includegraphics[scale = 0.2]
{Dense_vector2}};
\node[right of = observations, node distance = 2cm] (code) {$\left\{1,\ldots,2^{ {\color{red} L}\Rc} \right\}$};
 \node[right of = code, node distance = 2cm] (recon) {\includegraphics[scale = 0.2]
{sparse_reconstruction}};

\node[above of = source, yshift = 0.9cm, align = center] { $X^n$};
\node[above of = observations, yshift = 0.25cm,align = center] { $Y^m$};
\node[above of = recon, yshift = 0.9cm,align = center] { $\widehat{X}^n$};

\draw[dashed] (source)+(-0.15,0.7) -- node[left] {$X^{\color{red} L}$} +(-0.15,-1.25) -- +(0.15,-1.25) --+(0.15,0.7);
\draw[dashed] (recon)+(-0.15,0.7) -- node[right,xshift = 0.3cm] {$\widehat{X}^{\color{red} L}$} +(-0.15,-1.25) -- +(0.15,-1.25) --+(0.15,0.7);

\draw[->, line width = 3pt] (observations) -- (code);
\draw[->, line width = 3pt] (code) -- (recon);
\draw[->, line width = 3pt] (source) -- (observations);
\end{tikzpicture}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Discussion}
%\includegraphics{} figure D(R).
\begin{itemize}
\item Is $D_{\Xc |\sqrt{\gammac \eta}\Xc+N }(\Rc) $ optimal? 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Encoding with unknown Sampling Matrix}
\begin{itemize}

\item Assume that $\mathbf H$ is unknown at the encoder
\item Encoder compresses (dense) observations vector $Y^m$ to minimize $\mathbb E\left\|Y^m - \widehat{Y}^m \right\|^2$
\[
Y^m \overset{\enc}{\longrightarrow} I \in \left\{1,\ldots,2^{{\color{red} n}\Rc} \right\} \overset{\mathsf{dec}}{\longrightarrow} \widehat{Y}^m
\]
\item Sparse source $X^n$ is estimated from the output of this encoder 
\[
D_{CE}(R) = \lim_{n,m\rightarrow \infty} \inf_{\widehat{X}} \mathbb E \left\|X^n - \widehat{X}^n \left(I,\mathbf H\right) \right\|^2
\]
\item Leads to the {\color{red} compress-and-estimate} source coding setting [Kipnis, Rini, Goldsmith '16]

\end{itemize}

\begin{exampleblock}{Remark:}
Previous scheme can be seen as \emph{estimate-and-compress} 
\end{exampleblock}
\end{frame}

\begin{frame}
\frametitle{Result III: Compress-and-estimate Distortion-Rate}
\begin{center}
\begin{tikzpicture}
\node at (0,0) (source) {$X^n \rightarrow \sqrt{\gammac} \mathbf H X^n + N^m = Y^m$};
\node[right of = source, node distance = 4cm] (code) { $\left\{1,\ldots,2^{n\Rc} \right\}$};
\node[right of = code, node distance = 2.5cm] (dest1) { $\widehat{Y}^m$};
\node[below of = code, node distance = 1.5cm] (dest2) { $\widehat{X}^n$};
\draw[->] (source) -- node[above]{\scriptsize $\enc$} (code);
\draw[->,dashed] (code) -- node[above]{\scriptsize $\mathsf{dec}$} (dest1);
\draw[->] (code) -- node[right]{\scriptsize $\mathsf{est}$} (dest2);
\end{tikzpicture}
\end{center}
\begin{theorem}
\[
D_{CE}(\Rc) = \mmse\left(\Xc | \sqrt{\color{red} \gamma' {\color{red} \eta'}}\Xc + N \right)
\]
where
\[
{\color{red}\gamma'} \triangleq \gammac \frac{1- 2^{-2{ \Rc / \rhoc} } }{1 + \gammac \pc 2^{-2 \Rc / \rhoc} },
\]
and ${\color{red} \eta'}$ is determined by replica fixed point equation with SNR ${\color{red}\gamma'}$
\end{theorem}
\end{frame}

\begin{frame}
\frametitle{Example I: distortion vs code rate}
\framesubtitle{(high sampling rate)}
\vspace{-30pt}
\begin{center}
\begin{tikzpicture}
\node[coordinate] (figure) at (0,0) {};
\node (title) [above of = figure, node distance = 2.7cm, scale = 0.5]{($\deltac = 0.5$, $\pc=0.3$, $\gammac = 100$)};
\node (xlabel) [below of = figure, node distance = 3.3cm] {$\Rc$ };
\node (ylabel) [left of = figure, node distance = 3.5cm] {$D/\pc$};
\node at (0,0) (img1) {\includegraphics[scale = 0.2]{DR_wo_p0_3_rho0_5_gm100}};
\node (mmse) [left of = figure, node distance = 2.1cm, yshift = -1.1cm, scale = 0.7] {$\mmse$};
\node (Dx) [below of = figure, node distance = 2cm, yshift = 0cm, rotate = -20, scale = 0.7] {$D_X$};
\pause
\node at (0,0) (img2) {\includegraphics[scale = 0.2]{DR_w1_p0_3_rho0_5_gm100}};
\node (Dxz) [right of = figure, node distance = -0.5cm, yshift = -0.4cm, rotate = -25] {$D_{X|\sqrt{\eta \gammac}X+N}$};
\pause
\node at (0,0) (img3) {\includegraphics[scale = 0.2]{DR_p0_3_rho0_5_gm100}};
\node (Dce) [right of = figure, node distance = -0.6cm, yshift = 0.5cm, rotate = -25] {$D_{CE}$};
\pause

%With 
\node at (0,0) (img3) {\includegraphics[scale = 0.2]{DR_p0_3_G_rho0_5_gm100}};
\node (Dg) [right of = figure, node distance = 0cm, yshift = 1.5cm, rotate = -12] {$D_{\mathsf{Gauss}}$};
\end{tikzpicture}
\end{center}
\vspace{-20pt}
\begin{itemize}
\item Both schemes are optimal as $R\rightarrow \infty$
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Example II: distortion vs code rate}
\framesubtitle{(low sampling rate)}
\vspace{-30pt}
\begin{center}
\begin{tikzpicture}
\node[coordinate] (figure) at (0,0) {};
\node (title) [above of = figure, node distance = 2.7cm, scale = 0.5]{($\deltac = {\color{red} 0.3}$, $\pc= {\color{red} 0.5}$, $\gammac = 100$)};
\node (xlabel) [below of = figure, node distance = 3.3cm] {$\Rc$ };
\node (ylabel) [left of = figure, node distance = 3.5cm] {$D/\pc$};
\node at (0,0) (img1) {\includegraphics[scale = 0.2]{DR_p0_5_rho0_3_gm100_2}};
\node (mmse) [left of = figure, node distance = 1.6cm, yshift = -0.4cm, scale = 0.7] {$\mmse$};
\node (Dx) [left of = figure, node distance = 1.7cm, yshift = -1.5cm, rotate = -60, scale = 0.7] {$D_X$};
\node (Dxz) [right of = figure, node distance = -0.5cm, yshift = 0.9cm, rotate = -25] {$D_{X|\sqrt{\eta \gammac}X+N}$};
\node (Dce) [right of = figure, node distance = -0.6cm, yshift = 0cm, rotate = -20] {$D_{CE}$};
\end{tikzpicture}
\end{center}
\vspace{-20pt}
\begin{itemize}
\item Asymptotic posterior distortion-rate is sub-optimal !
\end{itemize}
\end{frame}
% \begin{frame}
% \frametitle{Example: distortion vs code rate}
% \begin{center}
% \begin{tikzpicture}
% \node at (0,0) (figure) {\includegraphics[scale = 0.5]{DR_p0_3_gm100_rho0_5}};
% \node (title) [above of = figure, node distance = 3cm, scale = 0.5]{($\deltac = 0.5$, $\pc=0.3$, $\gammac = 100$)};
% \node (xlabel) [below of = figure, node distance = 3cm] {$\Rc$ };
% \node (ylabel) [left of = figure, node distance = 3cm] {$D/\pc$};
% \node (Dce) [right of = figure, node distance = -0.6cm, yshift = 0.7cm] {$D_{CE}$};
% \node (Dxz) [right of = figure, node distance = -0.5cm, yshift = -0.4cm, rotate = -25] {$D_{X|\sqrt{\eta \gammac}X+N}$};
% \node (mmse) [left of = figure, node distance = 1.8cm, yshift = -0.9cm, scale = 0.7] {$\mmse$};
% \node (Dx) [left of = figure, node distance = 1.8cm, yshift = 0cm, rotate = -60, scale = 0.7] {$D_X$};
% \end{tikzpicture}
% \end{center}
% \begin{itemize}
% \item Both schemes are optimal as $R\rightarrow \infty$
% \end{itemize}
% \end{frame}

\begin{frame}
\frametitle{Example III: distortion vs sampling rate}
\begin{center}
\begin{tikzpicture}
\node[coordinate] at (0,0) (figure) {};
\node (title) [above of = figure, node distance = 2.8cm, scale = 0.5]{($\Rc=2p$, $\pc=0.2$, $\gammac = 100$)};
\node (xlabel) [below of = figure, node distance = 3.4cm] {$\deltac$ };
\node (ylabel) [left of = figure, node distance = 3.5cm] {$D/\pc$};
\node at (0,0) (figure) {\includegraphics[scale = 0.2]{D_vs_delta_wo_R0_4_p0_2_gm100}};
\node (mmse) [left of = figure, node distance = 1.6cm, yshift = 0cm, rotate = -60, scale = 0.7] {$\mmse$};
\node (Dx) [left of = figure, node distance = 1.7cm, yshift = -1.1cm, scale = 0.7] {$D_X$};
\pause
\node at (0,0) (figure) {\includegraphics[scale = 0.2]{D_vs_delta_R0_4_p0_2_gm100}};
\node (Dce) [right of = figure, node distance = 0.3cm, yshift = 0.7cm] {$D_{CE}$};
\node (Dxz) [right of = figure, node distance = 0.6cm, yshift = -0.8cm, rotate = -10] {$D_{X|\sqrt{\eta \gammac}X+N}$};
\end{tikzpicture}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Example IV: distortion vs SNR}
\begin{center}
\vspace{-25pt}
\begin{tikzpicture}
\node[coordinate] (figure) at (0,0) {};
\node (title) [above of = figure, node distance = 2.7cm, scale = 0.5]{($\deltac = 0.5$, $\pc=0.2$, $\Rc = 2\pc$)};
\node (xlabel) [below of = figure, node distance = 3.3cm] {$\gammac$ };
\node (ylabel) [left of = figure, node distance = 3.5cm] {$D/\pc$};
\node at (0,0) (img1) {\includegraphics[scale = 0.2]{D_vs_gm_wo_rho0_5_p0_2_R2}};
\node (mmse) [left of = figure, node distance = 2cm, yshift = 0.3cm, rotate = -45, scale = 0.7] {$\mmse$};
\node [left of = figure, node distance = 1.5cm, yshift = -1.1cm, scale = 0.7] (Dx)  {$D_X$};
\pause
\node at (0,0) (img2) {\includegraphics[scale = 0.2]{D_vs_gm_w1_rho0_5_p0_2_R2}};
\node (Dxz) [right of = figure, node distance = -0.5cm, yshift = 0cm, rotate = -35] {$D_{X|\sqrt{\eta \gammac}X+N}$};
\pause
\node at (0,0) (img3) {\includegraphics[scale = 0.2]{D_vs_gm_w2_rho0_5_p0_2_R2}};
\node (Dce) [right of = figure, node distance = -0.6cm, yshift = 1.1cm, rotate = -20] {$D_{CE}$};
\end{tikzpicture}
\end{center}
\vspace{-20pt}
\begin{itemize}
\item Compress-and-estimate suffers an ``SNR floor''
%\[
%\gamma' \overset{\gammac \rightarrow \infty}{\longrightarrow} \tilde{\gamma} \triangleq 2^{2\Rc / \deltac} / \pc
%\]
\end{itemize}
\end{frame}

\section{Summary}

\begin{frame}
\frametitle{Summary}
\begin{itemize}
\item Quantized compressed sensing -- optimal tradeoff between MMSE, sparsity, sampling rate, noise intensity and bitrate in the linear measurements model
\item Characterization using the replica posterior: 
\begin{itemize}
\item Single-letter replica distortion-rate function is achievable
\item Not optimal when source is dense since it ignores correlation
\end{itemize}
\item Compress-and-estimate is used when sampling matrix is not available at the encoder 
\end{itemize}

\end{frame}

\end{document}

### 2017-09-26 Writeups/onebit_adpative_Allerton.tex
Add files via upload

%\documentclass[letterpaper]{IEEEtran}
\documentclass[letterpaper, conference]{IEEEtran}      % Use this line for a4 paper
%\IEEEoverridecommandlockouts                              %

%\usepackage{mathcomSTEP}

%\overrideIEEEmargins 
%\IEEEoverridecommandlockouts                              % This command is only needed if 
% you want to use the \thanks command

%\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\usepackage{mathptmx} 
\usepackage{times} 
\usepackage{amsmath} 
\usepackage{amsbsy} 
\usepackage{amssymb}
%\usepackage{newtxtext, newtxmath}
\usepackage{mathrsfs}
\usepackage{comment}
\usepackage[export]{adjustbox}
\usepackage{tikz}
\usetikzlibrary{external,positioning,decorations.pathreplacing,shapes,arrows,patterns}

%\tikzexternalize[mode=list and make]
\usepackage{algorithmicx}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{pstool}
\usepackage[latin1]{inputenc}
\usetikzlibrary{arrows,shapes}
\usepackage{xifthen}
\usepackage{epic}
\usepackage{caption}
\usepackage{epstopdf}

\newtheorem{thm}{\bf{Theorem}}
\newtheorem{cor}[thm]{\bf {Corollary}}
\newtheorem{lem}[thm]{\bf {Lemma}}
\newtheorem{prop}[thm]{\bf {Proposition}}
\newtheorem{example}{\bf {Example}}
\newtheorem{definition}{\bf {Definition}}
\newtheorem{rem}{\bf {Remark}}

\newcommand{\mmse}{\mathsf{mmse}}
\newcommand{\supp}{\mathrm{supp} }
\renewcommand\vec[1]{\ensuremath\boldsymbol{#1}}
\newenvironment{proof}{\paragraph*{Proof}}{\hfill$\square$ \newline}
\newcommand{\sgn}{\mathrm{sgn} }
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand*{\QEDA}{\hfill\ensuremath{\square}}

\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
\tikzstyle{sint}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.8cm,thick ]
\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=1cm,thick ]
\tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]

\title{\LARGE \bf Mean Estimation from Adaptive Single-bit Measurements}
%
\author{
\IEEEauthorblockN{Alon Kipnis}
\IEEEauthorblockA{Department of Electrical Engineering \\
Stanford University\\
Stanford, CA\\}
\and
\IEEEauthorblockN{John C. Duchi}
\IEEEauthorblockA{Department of Electrical Engineering \\
and Department of Statistics \\
Stanford University\\
Stanford, CA\\}
}

\begin{document}
\graphicspath{{../Figures/}}
\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We consider the problem of estimating the mean of a normal distribution under the constraint: that the estimator can access only a single bit per sample from this distribution. We study the squared error in this estimation as a function of the number $n$ of samples and single-bit measurements in an adaptive setting. We show that if at each stage $n$, this single bit is a function of both the new sample and the previous $n-1$ acquired bits, then no estimator can attain asymptotic squared error smaller than $\pi/(2n)$ times the variance. Therefore, we conclude that a strict bit limitation increases the number of samples required for a prescribed accuracy by a factor of at least  $\pi/2$ compared to the unrestricted case. In addition, we provide an explicit estimator that attains this asymptotic error, showing that, rather surprisingly, only $\pi/2$ times more samples are required in order to attain performance equivalent to the unrestricted case. 
\end{abstract}

%{\color{red}  The $\mu$-sum problem (Kim-ElGamal Ch. 21) gives a lower bound. Can be reduced to the CEO.}

%{\color{red}  See LASSO results in http://arxiv.org/abs/1506.02181v1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:Intro}

Processing and estimating information from data collected at multiple physical location may be subject to communication constraints. 
%For example, emerging sensor network technologies in medicine and ``smart cities" use many low-cost sensors to collect large amounts of data and transmit it to remote locations. These sensors must operate under severe power restrictions, hence they are limited by their communication bandwidth. 
For example, consider large-scale sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit. In this scenario, the ability to estimate a particular parameter from data collected by the sensors is dictated not only by quality of observations and their numbers, but also by the constraint on the communication rates between the sensors. The question that we ask is to what extend a parametric estimation task is affected by such communication constraint, and what are the fundamental performance of estimation subject to these restrictions. \\

In this paper we provide an answer to this question in a particular simple setting: the estimation of the mean $\theta$ of a normal distribution with a known variance $\sigma^2$, under the constraint that given the $n$th sample $X_n$, only a single bit can be communicated to the estimator. 
Specifically, the $n$th encoder observes $X_n$ and the $n-1$ previous single bit messages $M_1,\ldots,M_{n-1}$, and delivers a single bit message $M_n$ to the estimator. The estimator provides an estimate $\widehat{\theta}_n$ based on $M^n = (M_1,\ldots,M_n)$.

 \item[(iii)] \emph{Distributed} encoding: the output of the $n$th encoder is a single bit that is only a function of $X_n$.
 \end{itemize}
Clearly, as far as information sharing is concerned, settings (iii) is a more restrictive version of (ii) which is more restrictive than (i). We measure the estimation performance by the mean squared error (MSE) risk. Since without bit constraint this risk is known to be $\sigma^2/n$, we are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting, defined as the ratio between their MSE to $\sigma^2/n$ as $n$ goes to infinity.
%\par
%Maybe explain here why the problem is interesting ? 
%setting (i), setting (ii) + SDM, setting (iii) + CEO.
%The turn to 1) main results and 2) other previous works. 
%
\par
Classical works on statistical estimation under communication constraint in information theory \cite{720540, zhang2013information, zhang1988estimation} implies that the ARE in setting (i) is $1$. Namely, asymptotically, there is no loss in performance in this setting due to the communication constraint. Indeed, under setting (i) the sample mean can be described by an encoder with an exponentially decaying error, leading to MSE of $\sigma^2/n + o(2^{-n})$. In this work we show that a similar result does not hold even in setting (ii): the relative efficiency of any adaptive estimator is at least $\pi/2$. Namely, the single-bit per sample constraint incurs a minimal penalty of at least $\approx 1.57$ compared to an unconstrained estimator or to the optimal estimator in setting (i). In addition to this negative statement, we provide an estimator that almost surely attains this minimal relative efficiency. In other words, we show that the lower bound of $\pi/2$ on the asymptotic relative efficiency is tight, and that it is attained regardless of the particular realization of $\theta$ or the size of the parameter space from which it is taken. Clearly, the minimal penalty on the efficiency of $\pi/2$ also holds under setting (iii), although the question whether such efficiency is achievable (or otherwise, what is the minimal efficiency) remains open. \\

\subsection{Relate Works}
The parametric estimation problem we consider is closely related to many works in statistics and information theory. Statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation} includes as a special case the problem of estimating a single vector of parameters from multiple data-rate constrained observations. These inference problems were studied in the asymptotic limit as the number of observations goes to infinity. In this asymptotic setting the unconstrained inference performance is always attained when all samples are taken from the same distribution \cite[Sec. III]{720540}. Indeed, in an i.i.d setting the \emph{type} of the sample is a sufficient statistics for any estimation task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples. For this reason in \cite{han1987hypothesis} and \cite{zhang1988estimation} attention is given to inference problems involving multiple distributions observed at different locations. Setting (i) above can be seen as a special case of the above works where the communication is limited to a single-bit per terminal. In fact, with a full access to the sample prior to encoding, the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample \cite{gray1998quantization}.
%On the other hand, setting (iii) arises as the number of terminals grow with $n$ and their communication rates are limited to a single bit.

This last situation is also obtained by the multiterminal source coding setting, a.k.a. the CEO problem \cite{berger1996ceo} can be seen as a generalization of our setting (iii), where multiple draws of $\theta$ and rounds of $n$ bit communication is permitted. In particular, the minimal CEO distortion with $1$ bit per terminal provides a lower bound on the MSE risk.

In fact, with a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample \cite{gray1998quantization}. The sigma-delta modulatior (SDM) \cite{1092194} uses a single bit quantizer with a feedback loop, and therefore falls under setting (ii). The SDM with a constant input $\theta$ corrupted by a Gaussian noise was considered in \cite{53738}, where it was shown that the output of the modulator converges to the true constant input. Therefore, the SDM provides a consistent estimator for setting (ii). The rate of this convergence, however, was not analyzed and cannot be derived directly from the results of \cite{53738}. In fact, the results of this paper implies that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations. \par

%
Estimation problem subject to the one-bit quantization constraint were also considered in compressed sensing \cite{boufounos20081,baraniuk2017exponential} and in MIMO detection in wireless communication \cite{singh2009limits}.

The rest of this paper is organized as follows: the main problem and notation are defined in Section~\ref{sec:problem}. In Section~\ref{sec:sequential} we present a lower bound on estimation from one-bit samples in the adaptive scheme, as well as an achievable scheme that attains this bound. Concluding remarks are given in Section~\ref{sec:conclusions}.

\section{Motivation and Related Works}
Standard considerations implies that the optimal encoding in setting (i) is reduced to an optimal $n$ bits description of the  sample mean. The standard technique to encode an unknown random quantity using $n$ bits is attained by an optimal scalar quantizer. However, the design of this quantizer depends on the distribution of its input \cite{gray1998quantization}, which is the goal of the estimation. Therefore, although the ARE in this setting is shown to be one \cite[Sec. III]{720540}, we see that a non-trivial challenge arise even in this case. 
In setting (ii), the above challenge of optimal quantizer design with imprecise input distribution occurs upon the the arrival of each new sample $X_n$.

%sigma delta modulator

%implies the existence of a consistent estimator in this case

% our result provides a lower bound for the accuracy of a sigma-delta modulator

Setting (ii) and (iii) were considered in 
\cite{zhang2013information} under the more general assumption of $m$ machines each has access to $n/m$ independent samples. The main result of \cite{zhang2013information} are lower bounds on the estimation error as a function of the total number of bits $R$ with which each machine can communicate. Our settings corresponds to the case $m=n$ and $R=1$, and our result is a fundamental lower bound and a matching achievable scheme under this simplified setting.

 We also note that the counterpart of setting (iii) in the case of hypothesis testing was considered in \cite{52470}.

 The optimal design  requires the distribution of the input, which is the goal of estimation and is known appriori.

 standard technique to encode an unknown random quantity using $n$ bits is attained by an optimal scalar quantizer,  by designing a scaler quantizer Unlike standard quantization task of encoding an unn

%Note that when multiple realization of $\theta$ are involved, the prior distribution $P_\theta$ plays a significant role in the overall MSE, whereas in our case we expect the final distortion to be independent of the actual prior distribution as in the two schemes in the sequential case. \\

\subsection{Intuition from Remote Multiterminal Source Coding}
A first clue for this rather surprising result can be seen drawing the connection between our parametric estimation problem to the remote multiterminal source coding problem of \cite{berger1996ceo}, also known as the CEO problem. The CEO setting considers $n$ encoders, each has access to a corrupted version of a source signal. The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator. Therefore, assuming that $\theta$ is drawn randomly from a prior $\pi(\theta)$, the distributed estimation setting (iii) corresponds to the CEO setting with $k=1$, where the $i$th agent observes 
\begin{equation}
\label{eq:Gaussian_channel}
X_i = \theta + Z_i,
\end{equation}
and has $R_i=1$ bits to transmit this observation. As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise of variance $\sigma^2$ provides a lower bound on the MSE distortion in estimating $\theta$. In fact, the difference between this lower bound and the actual MSE in our setting indicates the importance of coding over blocks consisting of $k$ independent realizations of $\theta$ versus $k=1$ in our setting. \par
A closed-form expression for CEO under quadratic distortion is known only for the case where the sequence to described by the encoders is sampled from a Gaussian distribution \cite{prabhakaran2004rate}. By using the characterization of the minimal CEO distortion as the number of terminals goes to infinity, we conclude the following:
\begin{prop} \label{prop:ceo_lower_bound}
Assume that $\pi(\theta)$ is the normal distribution. Then any estimator $\widehat{\theta}_n$ of $\theta$ in the distributed setting satisfies
\[
 n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + o(1).
\]
\end{prop}

\begin{proof}
We consider the expression \cite[Eq. 10]{chen2004upper} that provides the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots R_L$:
\begin{equation} \label{eq:ceo_optimal_sumrate}
R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
\end{equation}
Assuming $R_\Sigma = n$ and $L=n$ we get
\begin{equation} \label{eq:ceo_optimal_sumrate}
n = \frac{1}{2} \log \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
\end{equation}
The value of $D^\star$ that satisfies the equation above describes the MSE in the quadratic Gaussian CEO setting under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders. Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting. By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$ we conclude that 
\[
D^\star = \frac{ \frac{4\sigma^2}{3} }{n + \frac{4 \sigma^2}{3 \sigma_\theta^2} } + O(e^{-n}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
\]
\end{proof}
We note that although the CEO lower bound was derived by the MSE attainable assuming optimal allocation a total of $n$ bits among the encoders, the same expression is from the upper bound to the CEO derived in \cite[Prop. 5.2]{KipnisRini2017}, that assumes $R_1=\ldots,R_n = 1$ rather than optimal allocation of $n$ bits among all encoders. %\[
%D_{CEO} / \sigma_\theta^2 \leq \left( 1 + \sum_{i=1}^n \frac{\sigma_\theta^2}{\sigma^2} \frac{1 - 2^{-2R_i}} {1+ \frac{\sigma_\theta^2}{\sigma^2}  2^{-2 R_i}  } \right)^{-1}
%\]
%where $\sigma_\theta^2$ is the variance of the distribution $\pi(\theta)$. Using $R_1=\ldots=R_n=1$ we get
%\[
%D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + o(n^{-1}). 
%\]

Statistical inference problems under communication constraints in the nature of our setting were considered in information theory in 
\cite{han1987hypothesis, zhang1988estimation, 720540}. These works consider a multi-terminal source coding setting in which the $i$th terminal observes $n$ samples from the distribution and is allotted $nR_i$ bits to communicate its estimate. The main focus of these works is the difference between inference with communication constraint and the unconstrained vanilla statistical estimation setting, as the number of samples $n$ goes to infinity subject to a total finite rate constraint. Our setting (i) can be seen as a special case of this setting where with a single terminal and $R_1 = 1$.% whereas our case (iii) is obtained from this setting by taking $n=1$, $R_i=1$, and number of terminals grow with $n$. 
However, as explained in \cite[Sec. III]{720540}, a single terminal in this setting always lead to the unconstrained inference performance. Indeed, when all samples are taken from the same distribution, the \emph{type} of the sample \cite{csiszar1998method} is a sufficient statistics for any inference task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples. For this reason, attention is given in these works to inference problems involving multiple distributions observed at different locations and hence the results there do not apply to our setting. In fact, with a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample. Finally, we note that setting (ii) includes as a special case the sigma-delta modulation (SDM) analog-to-digital conversion scheme with a constant input $\theta$ corrupted by Gaussian noise $Z_i$, as was considered in \cite{53738}. While it was shown there that the output of the modulator converges to the true constant input, the rate of this convergence was not analyzed and cannot be derived directly from the results of \cite{53738}. In fact, a corollary from the results in this paper we conclude that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations. Finally, the multiterminal source coding setting denoted as the CEO problem \cite{berger1996ceo} can be seen as a generalization of our setting (iii), where multiple draws of $\theta$ and rounds of $n$ bit communication is permitted. In particular, the minimal CEO distortion with $1$ bit per terminal provides a lower bound on the MSE risk.  \par

%Why it is surprising that the estimator is independent of $\theta$, $\Theta$ or $\pi(\theta)$.

\subsection{Related Works}
\subsubsection*{Statistical inference under communication constraints}
The problem of statistical inference under communication constraint has a long and rich history in statistics and information theory. Statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation} includes as a special case the problem of estimating a single vector of parameters from multiple data-rate constrained observations. These inference problems were studied in the asymptotic limit as the number of observations goes to infinity. The main question asked there is the difference between inference with communication constraint and the unconstrained vanilla statistical estimation setting. In this asymptotic setting the unconstrained inference performance is always attained when all samples are taken from the same distribution \cite[Sec. III]{720540}. Indeed, in an i.i.d setting the \emph{type} of the sample is a sufficient statistics for any estimation task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples. For this reason in \cite{han1987hypothesis} and \cite{zhang1988estimation} attention is given to inference problems involving multiple distributions observed at different locations. Setting (i) above can be seen as a special case of \cite{han1987hypothesis, zhang1988estimation, 720540} where the communication is limited to a single-bit per terminal.

%\subsubsection{Estimation from 1-bit measurements}
%Single-bit or binary detectors are the basis for digital technology, and works considers the estimation of parameters from the results of such detectors have been around from the early days of digital computing. The burst of works in compressed sensing in the previous decade also gave raise to multiple 1-bit results \cite{rice_university}. Due to the popularization of MIMO technology and the expected break of mm-wave in wireless communication there have been many works 1-bit detection at the A/D in the receiver \cite{2016arXiv160204193Z}.

\subsubsection*{Relation to channel coding}
The problem we consider is the estimation of the parameter $\theta$ by observing 
\begin{equation}
\label{eq:channel}
X_i = \theta + Z_i, \quad i=1,\ldots,n,
\end{equation}
where the $Z_i$s are independent, centered normal with variance $\sigma^2$. The problem of estimating $\theta$ from the $X_i$s can be seen as the attempt to transmit a real number $\theta$ over an additive white Gaussian noise (AWGN) channel. In particular, setting (ii) can be seen as the feedback version of this transmission, which is closely related to \cite{horstein1963sequential, 1053879}. However, in our setting $\theta$ is either fixed or drawn once from a prior distribution, so the communication in \eqref{eq:channel} is limited to a repetition code. Moreover, in setting (ii) we have the additional constraint that the message is a causal function of the previous messages, where in case (iii) it is completely memoryless. Works in information theory which consider such setting includes AWGN channel with 1-bit ADC at the receiver \cite{DBLP:journals/corr/VarastehSG16}. \par

\subsubsection*{Relation to source coding}
With a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample. Setting (ii) includes as a special case the sigma-delta modulation (SDM) analog-to-digital conversion scheme with a constant input $\theta$ corrupted by Gaussian noise $Z_i$, as was considered in \cite{53738}. While it was shown there that the output of the modulator converges to the true constant input, the rate of this convergence was not analyzed and cannot be derived directly from the results of \cite{53738}. As a corollary from the results in this paper we conclude that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations. Finally, the remote multiterminal source coding setting of \cite{berger1996ceo} corresponds to the case of $n$ rate-constrained encoders, each observing a noisy version of an information source. The difference between this setting and ours is that in ours the parameter of interest is not an information source. By assuming a prior distribution on this parameter, the CEO provides a lower bound on the estimation error in the fully distributed setting (iii). This lower bound can be attained if we were to consider the average error in multiple independent realizations of our problem rather than a single realization as we do here. \\

%As opposed to the aforementioned line of works, we focus on estimation of samples taken from a single distribution in the finite blocklength performance. We are interested in particular in addition restrictions on the communication and information sharing between the encoders. For example, our main focus is the case where the observer must communicate a single bit upon drawing from the distribution. This is in contrast to the asymptotic setting where the observer can encode the outcome of $n$ draws at once using a single $n$ bit message. Alternately, such setting can be seen as having $n$ different observers, each is capable of observing a single realization and transmit a single bit.

%{\color{red} The Van Trees inequality was extended to the estimation of multiple parameters in \cite{bobrovsky1987}. It is closely related with the }

\begin{comment}
\subsection{Sigma-Delta Encoding}

and covariance function \cite[Eq. 25]{53738}
\[
R(k) = \mathbb E M_{n+k} M_n = \theta^2 + O \left( \frac{1}{\sigma \sqrt{ k} } \right). 
\]
{\color{red} This is not enough to deduce convergence. Need to go over the paper and check if rate of convergence can be deduced. Also do simulations BEFORE that. \\

What is the error in estimating the mean of stationary ergodic process ? 
}
Since the SDM is a special case of the sequential scheme, we conclude that the MSE of any SDM with a noisy DC signal is bounded from below by $n^{-1} \sigma^2 \pi/2 $.
\end{comment}

The rest of this paper is organized as follows: the main problem and notation are defined in Section~\ref{sec:problem}. Our main results are presented and discussed in Section~\ref{sec:sequential}. Concluding remarks are given in Section~\ref{sec:conclusions}.

%Even with such arguably simple setting, we will see that the performance limit in the estimating task based on single bit observations provides an interesting setting for discussion that bridges classical works in statistics, coding theory, information theory and optimization.

\section{Problem Formulation \label{sec:problem}}

\begin{figure}
\begin{center}
\begin{tikzpicture}[node distance=2cm,auto,>=latex]
  \node at (0,0) (source) {$X_1$} ;
  \node[int1, right of = source, node distance = 1.5cm] (enc1) {Enc 1};  
\draw[->,line width = 2pt] (source) -- (enc1);

 \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
\node[int1, right of = source2, node distance = 1.5cm] (enc2) {Enc 2};  
\draw[->,line width = 2pt] (source2) -- (enc2);

\node[below of = source2, node distance = 2.5cm] (source3) {$X_n$};
\node[int1, right of = source3, node distance = 1.5cm] (enc3) {Enc n};  
\draw[->,line width = 2pt] (source3) -- (enc3);

\node[above of = source, node distance = 1cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
\node[below of = source2, node distance = 0.5cm] {$\vdots$};

\node[int1, right of = enc2, node distance = 4cm ] (est) {Est};
\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -2cm] (mes1) {$M_1 \in \left\{-1,1\right\}$} (est);   
\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M_2 \in \left\{-1,1\right\}$} (est);   
\draw[->] (mes1) -- +(0,-0.7) -| (enc2);

\draw[dashed,->] (mes2) -- +(0,-0.7) -| +(-2,-1.2);
\draw[->,line width = 2pt] (enc3) -| (est);

\node[below of = mes2, node distance = 1.5cm] (mes3) {$M_1,\ldots,M_{n-1} $};

\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -2cm]  {$M_n \in \left\{-1,1\right\}$} (est);

\draw[->] (mes3) -- +(0,-0.5) -| (enc3);

\node[right of = est, node distance = 1.5cm] (dest) {$\widehat{\theta}_n$};
%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
%\draw[->,line width=2pt] (dec) -- (dest);
\draw[->, line width=2pt] (est) -- (dest);
\end{tikzpicture}
\end{center}
\caption{\label{fig:sequential} Adaptive single-bit encoding: the $i$th encoder delivers a single bit message which is a function of its private sample $X_i$ and the previous messages $M_1,\ldots,M_{i-1}$.}
\end{figure}

Let $X_i$, $i=1,\ldots,n$, be $n$ independent samples from the normal distribution $\mathcal N(\theta,\sigma^2)$ with mean $\theta$ and variance $\sigma^2$. We assume that the mean $\theta$ is drawn once from a prior distribution $\pi(\theta)$ on the parameter space $\Theta$, which is a closed interval of the real line. We moreover assume that $\pi(\theta)$ is absolutely continuous with respect to the Lebesgue measure with density $\pi(d\theta)$. The problem we consider is the estimation of the parameter $\theta$ under the following constraints on the communication between the samples $X_1,\ldots,X_n$ and a centralized estimator: 
\begin{itemize}
\item[(i)] The estimator at time $n$ is only a function of the $n$ messages $M^n = \left(M_1,\ldots,M_n \right)$.
\item[(ii)] For each $i=1,\ldots,n$, the $i$th message $M_i$ is a function of the sample $X_i$ and the $i-1$ previous messages $M^{i-1}$.
\item[(iii)] The $i$th message $M_i$ takes only two possible values, say $1$ and $-1$. 
\end{itemize}
In other words,  the $n$ messages $M^n$ are the only information on the sample $X^n = \left(X_1,\ldots,X_n\right)$ available to the estimator. The $i$th message is defined by a function from the real line to $\{-1,1\}$, measurable with respect to the sigma algebra generated by $M^{i-1}$ and $X_i$.  The estimator, upon observing $M^n$, produces an estimate $\widehat{\theta}_n(M^n)$ of $\theta$. A system describing the above scheme is illustrated in Fig.~\ref{fig:sequential}. \\

In this work we are concerned with the mean squared error (MSE) risk:
\begin{equation}
\label{eq:error_def}
\epsilon_n \triangleq \mathbb E\left(\widehat{\theta}_n - \theta \right)^2,
\end{equation}
where the expectation is taken with respect to the distribution of $X^n$ and the prior distribution $\pi(\theta)$. \\
%It is well known that minmax estimation error 
%\begin{equation}
%E_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left(\widehat{\theta}_n - \theta \right)^2 | \theta \right],
%\end{equation}
%can be obtained from $\epsilon_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}.

The main problem we consider is the minimal value that can be attain in \eqref{eq:error_def} as a function of $n$. Note that this minimization is the combination of the following two procedures: (1) selecting the $i$th message $M_i$ based on past messages and current observation $X_i$, and (2) estimating $\theta$ given messages $M^n$. We are interested in particular in the asymptotic relative efficiency of estimators $\widehat{\theta}_n$ for $\theta$ compared to the sample mean $\bar{X}_n = \frac{1}{n} \sum_{i=1}^n X_i$. Since the MSE attained by the latter is $\sigma^2/n$, this relative efficiency is defined as
\begin{equation}
\rho \triangleq \lim_{n \rightarrow \infty} \frac{n}{\sigma^2}  \epsilon_n. 
\label{eq:relative_efficiency}
\end{equation}
{\color{red}
Since the conditional expectation of $\theta$ with respect to $\bar{X}_n$ (and not $\bar{X}_n$) minimizes \eqref{eq:error_def}, we need to justify the fact that we use the sample mean as the reference estimator.
}

In addition to the notations defined above, we denote by $\phi(x)$ the standard normal density and by $\Phi(x)$ the standard normal cumulative distribution function. Prime denote derivative with respect to $\theta$.

% Lower Bound on the assymptotic minimal effeciency.
% Scheme that attains the assymptotic minimal effeciency. 
% Bayesian scheme that is one step optimal. We leave open the question whether this scheme attains the asymptotic minimal effeciency

\section{Results \label{sec:sequential}}
The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the asymptotic relative efficiency of and adaptive estimator cannot get below $\pi/2$. Next, we provide a particular adaptive estimation scheme and show in Theorem~\ref{thm:sgd} that its efficiency is $\pi/2$. Finally, in Theorem~\ref{thm:opt_one_step} we provide an adaptive estimation scheme that is optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen. While it is not clear whether the efficiency of this last scheme is $\pi/2$, numerical simulations suggests that the MSE of this scheme time s $n$ converges as well to $\pi/2$, but in a faster rate than the first scheme.

%While we provide expressions for the optimal message, evaluating the asymptotic efficiency of this estimation scheme turns out to be a challenging task. We therefore leave open the question whether this scheme attains the lower bound with equality, and only provide numerical result that support this conjecture.  \\

%\begin{figure}
%\begin{center}
%\begin{tikzpicture}[node distance=2cm,auto,>=latex]
%  \node at (0,0) (theta) {$\theta$} ;
%  \node at (2,0) (x1) {$X_1$};
%  \node[below of = x1, node distance = 1cm] (x2) {$X_2$};
%    \node[below of = x2, node distance = 1cm] (dots) {$\vdots$};
%  \node[below of = dots, node distance = 1cm] (xn) {$X_n$};
%  
%   \node[right of = x1, node distance = 2cm] (m1) {$M_1$};
%  \node[right of = x2, node distance = 2cm] (m2) {$M_2$};
%    \node[right of = xn, node distance = 2cm] (mn) {$M_n$};
%
%\draw[->] (theta) -- (x1);
%\draw[->] (theta) -- (x2);
%\draw[->] (theta) -- (xn);
%
%\draw[->] (x1)--(m1);
%\draw[->] (x2)--(m2);
%\draw[->] (xn)--(mn);
%
%\draw[->] (m1)--(m2);
%\draw[->, dashed] (m2)--(mn); 
%  
%\end{tikzpicture}
%\end{center}
%\caption{\label{fig:sequencial_graphical} Graphical model notation of the sequential setting.}
%\end{figure}

%\subsection{Properties of an Optimal Scheme}
%The sequential nature of the encoding and the estimation is best explain by the notions of actions and rewards taken from dynamic programming. The \emph{action} taken by the $i$th encoder is the design of a detection region $M_i^{-1}(1)$ that would lead to $M_i = 1$ assuming when $X_i \in M_i^{-1}(1)$ or $M_i=-1$ otherwise. The \emph{reward} (or penalty) is only evaluated at the end of the time horizon $n$.
%% Dynamic program. State = $M^n$. 
%% Reward is collected at the end
%%

\subsection{A Lower Bound on Adaptive Single-Bit Schemes}
Our first results asserts that the relative efficiency \eqref{eq:relative_efficiency} of any adaptive estimation scheme is bounded from below by $\pi/2$, as follows from the following theorem:
\begin{thm}[minimal relative effeciency] \label{thm:adpative_lower_bound}
Let $\widehat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Fig.~\ref{fig:sequential}.
% Let $\pi(\theta)$ be an absolutely continuous prior distribution on $\Theta$ with density function converges to zero at the endpoints of the interval $\Theta$. 
Assumes that $P(d\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
\[
\mathbb E (\theta-\theta_n)^2 \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\pi}{2n}\sigma^2+o(n^{-1}),
\]
where 
\[
I_0 = \mathbb E \left( \frac{d}{d\theta} \log P_\theta(\theta) \right)^2
\]
is the Fisher information with respect to a location model in $\theta$. 
\end{thm}

\subsubsection*{Sketch of Proof}
The main idea in the proof is to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$. Once this bound is achieved, the result follows by using the Van-Trees inequality \cite{gill1995applications} which bounds from below the MSE of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$. The details are given in the Appendix.\\

Next, we present an adaptive estimation scheme which attains the minimal asymptotic efficiency $\pi/2$. 
%Theorem~\ref{thm:adpative_lower_bound}. This estimation scheme can be seen as a gradient descent

\subsection{Asymptotically Optimal Estimator}
Consider the following estimator $\widehat{\theta}_n$ for $\theta$:  set 
\begin{equation}
\label{eq:sgd_alg}
\theta_n = \theta_{n-1} +  \gamma_n \sgn (X_n - \theta_n), \quad n = 1,2,\ldots,
\end{equation}
where $\left\{\gamma_n \right\}_{n=1}^\infty$ is any strictly positive sequence satisfying 
\begin{enumerate}
\item[(i)] $\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n)$ \\
\item[(ii)] $\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty$ 
for some $0< \lambda \leq 1$.
\end{enumerate}
(e.g. $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). The $n$th step estimation is defined by 
\begin{equation} \label{eq:sgd_est}
\widehat{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
\end{equation}

As the following theorem shows, the estimator $\widehat{\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the minimal asymptotic efficiency as established by Theorem~\ref{thm:adpative_lower_bound}.
\begin{thm} \label{thm:sgd}
The sequence $\widehat{\theta}_n$ of \eqref{eq:sgd_alg} satisfies
\[
\sqrt{n} \left( \widehat{\theta}_n - \theta \right) \overset{d}{\rightarrow} \mathcal N \left(0,  \pi \sigma^2 /2 \right).
\]
\end{thm}

\subsubsection*{Proof}
The asymptotic behavior of \eqref{eq:sgd_est} is a special case of  \cite[Thm. 4]{polyak1992acceleration}. The details are provided in the Appendix.\\

Note that $\theta_0$ is not explicitly defined in 
in equation \eqref{eq:sgd_est}. Arguably, a reasonable initialization is $\theta_0 = \mathbb E [\theta]$. However, Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator, is indifferent to this initialization. Thus, the optimal efficiency is attained without using the prior distribution on $\theta$. Nevertheless, the bound in Theorem~\ref{thm:adpative_lower_bound} suggests that the estimation error can be greatly reduced whenever the prior of $\theta$ provides a lot of information $I_0$ on its location. In order to incorporate this information in a more meaningful way, we present a Bayesian estimation scheme that is conjectured to attain the optimal asymptotic efficiency.

\subsection{One-step Optimal Estimation}
In this subsection we present an estimation scheme that posses the property of \emph{one-step optimality}. That is, at each step $i$, the $i$th encoder designs the detection region $M_i^{-1}(1)$ such that the MSE given $M^i$ is minimal. In other word, this scheme designs the messages in a greedy manner, such that the MSE at step $i$ is minimal given the current state of the estimation described by $M^{i-1}$. \\

The structure of the message that minimizes the next step MSE is given by the following theorem:
\begin{thm}[optimal one-step estimation] \label{thm:opt_one_step}
Let $\pi(\theta)$ be an absolutely continuous log-concave probability distribution. Given a sample $X$ from the distribution $\mathcal N(\theta, \sigma^2)$, define 
\begin{equation}
\label{eq:adaptive_main_message}
M = \sgn(X - \tau),
\end{equation}
where $\tau$ satisfies the equation
\begin{equation}
 \label{eq:fixed_point}
 \tau = \frac{m^-(\tau) + m^+(\tau)}{2},
\end{equation}
with
\begin{align*}
m^-(\tau)  & = \frac{\int_{-\infty}^{\tau} \theta P(d\theta) }{\int_{-\infty}^{\tau} P(d\theta)} ,\\
m^+(\tau) & = \frac{\int_{\tau}^\infty \theta P(d\theta) }{\int_{\tau}^\infty P(d\theta)} .
\end{align*}
Then for any estimator $\widehat{\theta}$ which is a function of $M'(X) \in \{-1,1\}$, we have
\begin{equation}
\label{eq:opt_cond}
\mathbb E \left(\theta-\widehat{\theta}(M')\right)^2 \geq  \mathbb E \left(\theta- \mathbb E[\theta|M]\right)^2,
\end{equation}
\end{thm}

\begin{proof}
The proof is completed by the following two lemmas, proofs of which can be found in the Appendix:
\begin{lem} \label{lem:unique}
Let $f(x)$ be a log-concave probability density function. Then the equation 
\begin{equation}
\label{eq:lem_fixed_point}
2x = \frac{\int_x^\infty uf(u)du}{\int_x^\infty f(u)du} + \frac{\int_{-\infty}^x uf(u)du}{\int_{-\infty}^x f(u)du} 
\end{equation}
has a unique solution.
\end{lem}
\end{proof}

\begin{lem} \label{lem:adaptive}
Let $U$ be an absolutely continuous random variable with
pdf $P(du)$. Then the one-bit message $M^\star$ that minimizes
\[
\int \left( u - \mathbb E[U|M(u)]  \right)^2 P(du)
\]
is given by
\[
M^\star  =  \sgn(U - \tau),
\]
where $\tau$ is the unique solution to the equation
 \[
2 \tau = \frac{\int_{\tau}^\infty u P(du)} {\int_{\tau}^\infty P(du)} + \frac{\int_{-\infty}^{\tau} u P(du)}{\int_{-\infty}^{\tau} P(du)}.
\]
\end{lem}

Theorem~\ref{thm:opt_one_step} suggests the following Bayesian estimation scheme: set $P_0(t) = \pi(\theta)$, and for $n\geq 1$ update the prior as
\begin{align}
P_n(t) = & P(\theta=t |M^n) = \frac{ P\left( \theta=t | M^{n-1} \right) P(M_n | \theta = t , M^{n-1})  } { P(M_n | M^{n-1} )} \nonumber \\ 
& = \alpha_n  P_{n-1}(t) \Phi\left(M_n \frac{ t - \tau_{n-1} }{\sigma} \right), \label{eq:density_update}
\end{align}
where $\alpha_n$ is a normalization coefficient that equals to
\[
\alpha_n = \left(\int_{\mathbb R} P_{n-1}(t) \Phi\left(M_n \frac{t- \tau_{n-1} }{\sigma} \right)  dt \right)^{-1}. 
\]
The $n$th estimate for $\theta$ is the conditional expectation of $\theta$ given $M^n$, namely
\begin{equation}
\theta_n = \mathbb E \left[ \theta| M^n\right] = \int_{-\infty}^\infty t P_n(t) dt. \label{eq:estimator_update}
\end{equation}
Next, solve equation \eqref{eq:fixed_point} with the updated prior $P_n(t)$ instead of $P(\theta)$. Note that since the standard normal cdf $\Phi(x)$ is log-concave, the updated prior $P_n(t)$ remains log-concave and thus a unique solution to \eqref{eq:fixed_point} is guaranteed by Lemma~\ref{lem:unique}. Finally, update the $n+1$th message as
\begin{equation}\label{eq:message_update}
M_{n+1} = \sgn(X_{n+1}-\tau_n).
\end{equation}

Since the equation \eqref{eq:fixed_point} has no analytic solution in general, it is hard to derive the asymptotic behavior of the Bayes estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}. We conjecture, however, that it attains the asymptotic relative efficiency of $\sigma^2\pi/2$, as can be observed from the numerical simulation illustrated in Fig.~\ref{fig:adaptive_error}. Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the sample mean for the same sample realization.

 % In fact, the numerical simulation in Fig.~\ref{fig:simulation} shows that this scheme outperform the estimator of \eqref{eq:sgd_est} even when the prior on $\Theta$ is least favorable for Bayes estimation \cite{Bickel1981}.

\begin{figure}
\begin{center}
\begin{tikzpicture}
\node at (0,0) {\includegraphics[scale=0.4]{error}};
\end{tikzpicture}
\caption{Normalized empirical risk $n\left(\widehat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $100$ Monte Carlo trials. In each trial, $\theta$ is chosen uniformly in the interval $(-5,5)$. \label{fig:adaptive_error}  }
\end{center}
\end{figure}

\begin{comment}
\subsection{Relation to Sigma-Delta Modulation \label{subsec:sdm}}
The SDM is a device that converts continuous-time analog signals to a discrete-time sequence of binary digits. The basic operation of a SDM can be described as follows: the modulator takes as input a sequence of continuous amplitude samples $X_n$, which are typically represents samples of a continuous-time signal taken uniformly at sampling rate $f_s$ much higher than the Nyquist rate of the signal \cite{1095151}. The output of the modulator is a sequence $M_n$ of binary values, obtained according to the following rule: 
\begin{align}
\begin{cases} V_{n+1} & =  V_n - \alpha q(V_n) + X_n, \\
M_n & = \sgn(V_n)  \end{cases}, \quad n=1,2,\ldots, \label{eq:sdm}
\end{align}
where $\alpha > 0$ is a parameter of the modulator that is determined by the maximal value of the input sequence $X^n$. The SDM of the form \eqref{eq:sdm} was studied in \cite{53738} under the assumption that the input process $X_n$ is an i.i.d Gaussian process. The main results from \cite{53738} shows that regardless of the initial state $V_0$, the process $M_n$ is a stationary ergodic process with mean $\theta$. It follows that a consistent estimation of $\theta$ is obtained by taking the mean of the sequence $\{M_n\}$. However, the results from \cite{53738} does not provide a closed form for the second order statistics of $\{M_n\}$, so that convergence rate cannot be derived from \cite{53738}.  
\end{comment}

\section{Conclusions \label{sec:conclusions}}
We considered the relative efficiency in estimating the mean of a normal distribution from single-bit measurements in an adaptive setting. We have shown that this minimal relative efficiency is $\pi/2$, namely there is a penalty factor of at least $\pi/2$ on the asymptotic MSE in estimating the mean compared to an estimator that has full access to the sample. We also showed that this lower bound is tight by presenting an estimation procedure that attains it.
%but ignores the prior distribution on the parameter space.
In addition, we characterized the single-bit message that minimizes the next step MSE, and described an estimation procedure that is based on a sequence of one-step optimal messages. We leave open the questions whether this estimator attains the minimal efficiency and whether it leads to an estimation scheme which is globally optimal. \\

%Something about how to interpret the results

% Sigma-Delta
% Relation to CEO
% Open questions
% Extenstion to fully distributed setting

\section*{ACKNOWLEDGMENT}
This research is supported in parts by...
%Tsachy Weissman, Stefano Rini, Robert Gray.

\onecolumn

\appendix

\section{Proofs}
In this appendix we provide detailed proofs of our main results as described in Section~\ref{sec:sequential}.

\subsection*{Proof of Theorem~\ref{thm:adpative_lower_bound}}

We first prove the following two lemmas:
\begin{lem} \label{lem:bound_intervals}
For any $x_1 \geq \ldots \geq x_n \in \mathbb R$, we have 
\begin{equation}
\frac{ \left(  \sum_{k=1}^n (-1)^{k+1}\phi(x_k) \right)^2} 
{\left( \sum_{k=1}^n (-1)^{k+1} \Phi(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} \Phi(x_k) \right)  } \leq \frac{2} {\pi}. \label{eq:bound_intervals}
\end{equation}
\end{lem}
\begin{lem} \label{lem:fisher_bound}
Let $X\sim \mathcal N(\theta,\sigma^2)$ and assume that 
\[
M(X) = \begin{cases} 1,& X \in A, \\
-1, & X \notin A.
\end{cases}
\]
Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $2/(\pi \sigma^2)$.
\end{lem}

\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals}}
We use induction on $n \in \mathbb N$. For the base case $n=1$ we have 
\begin{equation} \label{eq:induction_base}
\frac{  \phi^2(x)} 
{\Phi(x) \left(1 - \Phi(x) \right) } 
\end{equation}. 
Taking the logarithm of \eqref{eq:induction_base} and differentiating, we conclude that any point $x$ that maximizes \eqref{eq:induction_base} satisfies
\[
x = \phi(x) \left( \Phi(x) -\frac{1}{2} \right).
\]
However, since $x > \phi(x) \left( \Phi(x) -\frac{1}{2} \right)$ for all $x > 0$, the only point that satisfies the last condition is $x=0$. At this point \eqref{eq:induction_base} equals $2/\pi$. \par
Assume now that \eqref{eq:bound_intervals} holds for all integers up to some $n = N-1$ and consider the case $n = N$. The maximal value of \eqref{eq:bound_intervals} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
\begin{align*}
& g(x_1,\ldots, x_N) \triangleq 2 \log \left(  \sum_{k=1}^{N} (-1)^{k+1} \phi(x_k) \right) - \log
\left( \sum_{k=1}^N (-1)^{k+1} \Phi(x_k) \right)
-\log \left(1 -  \sum_{k=1}^N (-1)^{k+1} \Phi(x_k) \right) \\
& = 2 \log \delta_N - \log \Delta_N - \log \left(1 - \Delta_N  \right),
\end{align*}
where we denoted $\delta_N \triangleq \sum_{k=1}^{N} (-1)^{k+1} \phi(x_k)$ and $\Delta_N =  \sum_{k=1}^N (-1)^{k+1} \Phi(x_k)$. The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
\[
\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} \phi'(x_k)}{\delta_N} -\frac{(-1)^{k+1} \phi(x_k)}{\Delta_N } + \frac{(-1)^{k+1} \phi(x_k)}{1-\Delta_N }.
\]
Using the fact that $\phi'(x) = -x \phi(x)$, we conclude that the gradient of $g$ vanishes only if
\[
x_k = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
\]
In particular, the condition above implies $x_1 = \ldots = x_N$. If $N$ is odd then for $x_1=\ldots =x_N$ we have that \eqref{eq:bound_intervals} equals
\[
\frac{\phi(x_1)^2}{ \Phi(x_1) (1 - \Phi(x_1))},
\]
which was shown to be smaller than $\pi/2$. If $N$ is even, then for any constant $c$ the limit of \eqref{eq:bound_intervals} exits as $(x_1,\ldots,x_N)\rightarrow (c,\ldots,c)$ and equals zero. Therefore, the maximum of \eqref{eq:bound_intervals} is not attained at this line. We now consider the possibility that \eqref{eq:bound_intervals} is maximized at the borders, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches plus or minus infinity. For simplicity we only consider the cases where $x_N$ goes to minus infinity or $x_1$ goes to plus infinity (the general case where the first $m$ coordinates goes to infinity or the last $m$ to minus infinity is obtained using similar arguments). Assume first $x_N \rightarrow -\infty$. Then  \eqref{eq:bound_intervals} equals
\begin{align*}
\frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}\phi(x_k) \right)^2} 
{\left( \sum_{k=1}^{N-1} (-1)^{k+1} \Phi(x_k) \right)\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} \Phi(x_k)  \right) } ,
\end{align*}
which is smaller than $2/\pi$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
\eqref{eq:bound_intervals} equals
\begin{align*}
& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}\phi(x_k) \right)^2} 
{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} \Phi(x_k) \right)\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} \Phi(x_k)  \right) }  \\
& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}\phi(x'_m) \right)^2} 
{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} \Phi(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} \Phi(x'_{m})  \right) },
\end{align*}
where $x'_{m} = x_{m+1}$. The last expression is also smaller than $2/\pi$ by the induction hypothesis. This proves Lemma~\ref{lem:bound_intervals}. \\

\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
The Fisher information of $M$ with respect to $\theta$ is given by
\begin{align}
I_\theta & =  \mathbb E \left[ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta \right] \nonumber \\
& = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
& \overset{(a)}{=} \frac{ \left( - \int_A \phi' \left( \frac{x-\theta}{\sigma} \right)dx \right)^2} {\sigma^2 P(M=1| \theta) } + \frac{ \left( \int_A \phi' \left( \frac{x-\theta}{\sigma} \right)dx \right)^2} { \sigma^2P(M=-1| \theta) } \nonumber \\ 
& = \frac{\left( \int_A \phi'\left( \frac{x-\theta}{\sigma} \right) dx \right)^2 }{  \sigma^2 P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
& = \frac{\left( \int_A \phi'\left( \frac{x-\theta}{\sigma} \right) dx \right) \left( \int_A \phi'\left( \frac{x-\theta}{\sigma} \right) dx \right)}{  \sigma^2 \left( \int_A \phi \left( \frac{x-\theta}{\sigma} \right) dx \right)  \left(1- \int_A \phi \left( \frac{x-\theta}{\sigma} \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
\end{align}
where differentiation under the integral sign in $(a)$ is possible since $\phi(x)$ is differentiable with absolutely integrable derivative $\phi'(x) = -x\phi(x)$. Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that 
\[
\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon \sigma^2,
\]
which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$. It is therefore enough to proceed in the proof assuming that $A$ is of the form
\[
A = \cup_{j=1}^k (a_j,b_j),
\]
with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
\begin{align*}
\mathbb P(M_n=1) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
& = \sum_{j=1}^k \left( \Phi \left(\frac{b_j-\theta}{\sigma} \right) -  \Phi \left(\frac{a_j-\theta}{\sigma} \right)  \right),
\end{align*}
so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
\begin{align}
& =   \frac { \left( \sum_{j=1}^{k} \phi \left(\frac{a_j-\theta}{\sigma} \right) - \phi \left( \frac{b_j-\theta} {\sigma} \right)  \right)^2 } 
{\sigma^2 \left( \sum_{j=1}^k \Phi \left( \frac{b_j-\theta }{\sigma}\right) - \Phi \left( \frac{a_j-\theta }{\sigma}\right)  \right) }  \nonumber \\
& \times \frac {1} 
{1- \left( \sum_{j=1}^k \Phi \left( \frac{b_j-\theta }{\sigma}\right) - \Phi \left( \frac{a_j-\theta }{\sigma}\right)  \right) } 
\label{eq:lemma_J}
\end{align}
The proof of Lemma~\ref{lem:fisher_bound} is completed since it follows from~\ref{lem:bound_intervals} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $2/(\sigma^2 \pi)$. \\

We now consider the proof of Thm.~\ref{thm:adpative_lower_bound}. In order to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$, we first note that without loss of generality, each message $M_i$ can be written in the form
\begin{equation}
\label{eq:general_messages}
M_i = \begin{cases}
X_i \in A_i & 1, \\
X_i \notin A_i & -1,
\end{cases} 
\end{equation}
where $A_i \subset \mathbb R$ is a Lebesgue measurable set. Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = M^{-1}(1)$. Consider the conditional distribution $P({M^n|\theta})$ of $M^n$ given $\theta$. We have 
\begin{align}
P\left( M^n | \theta \right) & =  \prod_{i=1}^n P\left(M_i | \theta, M^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
\end{align}
where $P\left(M_i =1 | \theta, M^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$. We now prove the following Lemma:

Going back to \eqref{eq:adpt_lower_bound_proof:1}, it follows that the Fisher information of $M^n$ with respect to $\theta$ is given by 
\begin{align}
I_\theta(M^n) = \sum_{i=1}^n I_\theta (M_i|M^{i-1}),
\label{eq:fisher_information}
\end{align}
where $I_\theta (M_i|M^{i-1})$ is the Fisher information of the distribution of $M_i$ given $M^{i-1}$. From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (M_i|M^{i-1}) \leq 2/(\pi \sigma^2)$. The Van Trees inequality \cite{van2004detection, gill1995applications} now implies 
\begin{align*}
\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(M^n) + I_0} \\
& = \frac{1}{ \sum_{i=1}^n I_\theta (M_i | M^{i-1} ) + I_0} \\
& \geq \frac{1}{ 2n/(\pi \sigma^2) + I_0}.
\end{align*}

\QEDA

\subsection*{Proof of Theorem~\ref{thm:sgd}}
The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration}. In particular, Theorem~\ref{thm:sgd} is follows directly from the following simplified version of \cite[Thm. 4]{polyak1992acceleration}:
\begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
Let 
\[
X_i = \theta + Z_i,\quad i=1,\ldots,n.
\]
Define 
\begin{align*}
\theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
\widehat{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i,
\end{align*}
where the $Z_i$s are $\mathcal N(0,\sigma^2)$ and independent of each other, the sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions (i) and (ii) in Theorem~\ref{thm:sgd}, and $\left| \varphi(x) \right| \leq K_1(1+x)$ for some $K_1$. Define $\psi(x) = \mathbb E \varphi(x+Z_1)$, $\chi(x) = \mathbb E \varphi^2(x+Z_1)$ and assume that $\psi(0)=0$, $x\psi(x) >0$ for all $x\neq 0$, $\chi(x)$ is continuous at zero, and that $\psi(x)$ is differentiable at zero with $\psi'(0)>0$. Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
\[
\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\gamma}.
\]
Then $\widehat{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}(\widehat{\theta}_n - \theta)$ converges in distribution to $\mathcal N(0,V)$, where
\[
V = \frac{ \chi(0)} {\psi'^2(0)}. 
\]
\end{thm}

Using the notation in Theorem~\ref{thm:polyak_juditsky}, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have: 
\[
\chi(x) = \mathbb E \varphi^2(x+Z_1),
\]
so $\chi(0) = 1$. In addition,
\begin{align*}
\psi(x) & = \mathbb E \sgn(x+ Z_1) = \int_{-\infty}^\infty \sgn(x+z) \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{\sigma^2}} dz \\
& = \int_{-x}^\infty \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{\sigma^2}} dz -\int_{-\infty}^{-x} \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{\sigma^2}} dz.
\end{align*}
This leads to 
\begin{align*}
\psi'(x) & = \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{x^2}{\sigma^2}} dz +\frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{\sigma^2}} dz,
\end{align*}
so $\psi'(0) = \frac{2}{\sqrt{2\pi}\sigma}$. It is now easy to verify that the rest of the conditions in Theorem~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$. Since 
\[
\frac{\chi(0)}{\psi'^2(0)} = \frac{\pi \sigma^2}{2},
\]
Theorem~\ref{thm:sgd} follows from Theorem~\ref{thm:polyak_juditsky}. \QEDA

\subsection*{Proof of Theorem~\ref{thm:opt_one_step}}
In this subsection we prove lemmas \ref{lem:adaptive} and \ref{lem:unique} which lead to Theorem~\ref{thm:opt_one_step}.

\subsubsection*{Proof of Lemma \ref{lem:adaptive}}
Since any single-bit message $M(u) \in \{0,1\}$ is characterized by two decision region $A_1 = M^{-1}(1)$ and $A_{-1} = M^{-1}(-1)$, it follows that $\mathbb E \left[ U | M(U) \right]$ assumes only two values: $\mu_1 = \mathbb E \left[ U | M(U) = 1 \right]$ and $\mu_{-1} = \mathbb E \left[ U | M(U) = -1 \right]$. We claim that a necessary condition for $M(u)$ to be optimal is that the sets $A_1$ and $A_{-1}$ are, modulo a set of measure $P(du)$ zero, the Voronoi sets on $\mathbb R$ corresponding to the points $\mu_1$ and $\mu_{-1}$, respectively. Indeed, assume by contradiction that for such an optimal partition there exists a set $B \subset A_{1}$ with $\mathbb P (U \in B) >0$ such that $\left( b-\mu_{1} \right)^2 > \left( b- \mu_{-1} \right)^2$. The expected square error in this partition satisfies:
\begin{align*}
& \int_{\mathbb R} \left( u - \mathbb E[U|M(u)]  \right)^2 P(du) = \int_{A_1} (u- \mu_1)^2 P(du) + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
& = \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_1)^2 P(du) + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
& > \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_2)^2 P(du) + \int_{A_{-1}} (u- \mu_{-1})^2 P(du),
\end{align*}
so clearly, the partition $A_1' = A_1 \setminus B$, $A_{-1}' = A_{-1} \cup B$ attains lower error variance which contradicts the optimality assumption and proves our claim. It is evident that Voronoi partition of the real line corresponding to $\mu_1$ and $\mu_{-1}$ is of the form $A_{-1} = (-\infty,\tau)$, $A_{1} = (\tau, \infty)$ where the point $\tau$ is of equal distance from $\mu_1$ and $\mu_{-1}$, namely $\tau = \frac{\mu_1 + \mu_{-1}}{2}$. From these two conditions (which are a special case of the conditions derived in \cite{1056489} for two quantization regions) we conclude that $\tau$ must satisfy the equation
\[
2 \tau = \frac{\int_{\tau}^\infty u P(du)}{\int_{\tau}^\infty P(du)} + \frac{\int_{-\infty}^{\tau} u P(du)}{\int_{-\infty}^{\tau} P(du)}.
\] 
\QEDA

\subsubsection*{Proof of Lemma \ref{lem:unique}} 
Any solution to \eqref{eq:lem_fixed_point} is a solution to $h^+(x) = h^-(x)$ where
\[
h^+(x) = \frac{\int_x^\infty uf(u)du}{\int_x^\infty f(u)du} - x 
\]
and
\[
h^-(x) = x - \frac{\int_{-\infty}^x uf(u)du}{\int_{-\infty}^x f(u)du}.
\]
We now prove that $h^+(x)$ is monotonically decreasing while $h^-(x)$ is increasing, so they meet at most at one point. The derivative of $h^-(x)$ is given by
\begin{equation} 
\label{eq:one_step_proof_derivative}
1 - \frac{ f(\tau) \int_{-\infty}^\tau f(x) (\tau-x)dx } {\left( \int_{-\infty}^\tau f(x) dx \right)^2}.
\end{equation}
Denote $F(x) = \int_{-\infty}^x f(u)du$. Using integration by parts in the numerator and from the fact that $\lim_{\tau \rightarrow -\infty}  \tau \int_{-\infty}^\tau f(x) dx = 0$, the last expression can be written as
\[
1- \frac{ f(\tau) \int_{-\infty}^\tau F(x) dx}
 {\left( F(\tau) \right)^2}.
\]
Log-concavity of $f(x)$ implies log-concavity of $F(x)$, so that we can write $F(x) = e^{g(x)}$ for some concave and differentiable function $g(x)$. Moreover, we have $f(x) = g'(x)e^{g(x)}$ where, by concavity of $g(x)$, the derivative $g'(x)$ of $g(x)$ is non-increasing. With these notation we have
\begin{align*}
\frac{ f(\tau) \int_{-\infty}^\tau F(x) dx}
 {\left( F(\tau) \right)^2} & = \frac{g'(\tau)e^{g(\tau)} \int_{-\infty}^\tau e^{g(x)}dx }{ e^{2g(\tau)} } \\
 & = e^{-g(\tau)} \int_{-\infty}^\tau g'(\tau) e^{g(x)} dx  \\
 & \leq e^{-g(\tau)} \int_{-\infty}^\tau g'(x) e^{g(x)} dx \\
 & = e^{-g(\tau)} F(\tau) = 1.
\end{align*}
(where the second from the last step follows since $g'(x) \leq g'(\tau)$ for any $x\leq \tau$). If follows that \eqref{eq:one_step_proof_derivative} is non-negative and thus $h^-(x)$ is monotonically increasing. Since
\[
h^+(-x) = x - \frac{ \int_{-\infty}^{x} uf(-u)du}{ \int_{-\infty}^x f(-u) du }, 
\]
the fact that $h^+(x)$ is monotonically decreasing follows from similar arguments. Moreover, since the derivatives of $h^+(x)$ and $h^-(x)$ never vanish at the same time over any open interval, their difference cannot be constant over any interval. Finally, since 
\begin{align*}
 \lim_{x\rightarrow -\infty} h^+(x) =  \lim_{x\rightarrow \infty} h^-(x)
\end{align*}
and since non of these functions are constant, monotonicity of $h^+(x)$ and $h^-(x)$ implies that they must meet at some $x\in \mathbb R$. \QEDA

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,/Users/Alon1/LaTex/bibtex/sampling}

\end{document}

### 2017-09-26 Writeups/onebit_adpative_Allerton_V2.tex
Add files via upload

--- 2017-09-26 Writeups/onebit_adpative_Allerton.tex
@@
 
-\title{\LARGE \bf Mean Estimation from Adaptive Single-bit Measurements}
+\title{\LARGE \bf Mean Estimation from Adaptive One-bit Measurements}
 %
@@
 \begin{document}
-\graphicspath{{../Figures/}}
+\graphicspath{{../Figs/}}
 \maketitle
@@
 \begin{abstract}
-We consider the problem of estimating the mean of a normal distribution under the constraint: that the estimator can access only a single bit per sample from this distribution.
-We study the squared error in this estimation as a function of the number $n$ of samples and single-bit measurements in an adaptive setting.
-We show that if at each stage $n$, this single bit is a function of both the new sample and the previous $n-1$ acquired bits, then no estimator can attain asymptotic squared error smaller than $\pi/(2n)$ times the variance.
-Therefore, we conclude that a strict bit limitation increases the number of samples required for a prescribed accuracy by a factor of at least  $\pi/2$ compared to the unrestricted case.
-In addition, we provide an explicit estimator that attains this asymptotic error, showing that, rather surprisingly, only $\pi/2$ times more samples are required in order to attain performance equivalent to the unrestricted case.
+We consider the problem of estimating the mean of a normal distribution under the following constraint: the estimator can access only a single bit of each sample from this distribution.
+We study the squared error risk in this estimation as a function of the number of samples and one-bit measurements $n$.
+We show that, if at step $n$ the single bit is a function of both the new sample and the previous $n-1$ acquired bits, no estimator can attain asymptotic mean squared error smaller than $\pi/(2n)$ times the variance.
+In other words, one-bit restriction increases the number of samples required for a prescribed accuracy of estimation by a factor of at least $\pi/2$ compared to the unrestricted case.
+In addition, we provide an explicit estimator that attains this asymptotic error, showing that, rather surprisingly, only $\pi/2<1.571$ times more samples are required in order to attain estimation performance equivalent to the unrestricted case.
 \end{abstract}
@@
 
-Processing and estimating information from data collected at multiple physical location may be subject to communication constraints. 
+Processing and estimating information from data collected at multiple sensors and physical locations is subject to communication constraints. 
 %For example, emerging sensor network technologies in medicine and ``smart cities" use many low-cost sensors to collect large amounts of data and transmit it to remote locations.
@@
 For example, consider large-scale sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit.
-In this scenario, the ability to estimate a particular parameter from data collected by the sensors is dictated not only by quality of observations and their numbers, but also by the constraint on the communication rates between the sensors.
-The question that we ask is to what extend a parametric estimation task is affected by such communication constraint, and what are the fundamental performance of estimation subject to these restrictions.
-\\
-
-In this paper we provide an answer to this question in a particular simple setting: the estimation of the mean $\theta$ of a normal distribution with a known variance $\sigma^2$, under the constraint that given the $n$th sample $X_n$, only a single bit can be communicated to the estimator.
-Specifically, the $n$th encoder observes $X_n$ and the $n-1$ previous single bit messages $M_1,\ldots,M_{n-1}$, and delivers a single bit message $M_n$ to the estimator.
-The estimator provides an estimate $\widehat{\theta}_n$ based on $M^n = (M_1,\ldots,M_n)$.
-
+In this scenario, the ability to estimate a particular parameter from data collected by the sensors is dictated not only by quality of observations and their numbers, but also by limited communication rates between the sensors and the central estimator.
+The question that we ask is to what extend a parametric estimation task is affected by communication constraints, and what are the fundamental performance limits in estimating a parameter subject to these restrictions.
+In this paper we answer this question in a particular simple setting: the estimation of the mean $\theta$ of a normal distribution with a known variance $\sigma^2$, under the constraint that only a single bit can be communicated on each sample $X_n$ from this distribution.
+As it turns out, the ability to share information among different samples before sending each single-bit message dramatically affects the performance in estimating $\theta$.
+We distinguish in particular among three different settings:
+ \begin{itemize}
+ \item[(i)] \emph{Centralized} encoding: all $n$ encoders confer and produce a single $n$ bit message which is a function of $X_1,\ldots,X_n$. 
+ \item[(ii)] \emph{Adaptive} or \emph{sequential} encoding: the $n$th encoder observes $X_n$ and the $n-1$ previous single bit messages.
  \item[(iii)] \emph{Distributed} encoding: the output of the $n$th encoder is a single bit that is only a function of $X_n$.
@@
 We measure the estimation performance by the mean squared error (MSE) risk.
-Since without bit constraint this risk is known to be $\sigma^2/n$, we are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting, defined as the ratio between their MSE to $\sigma^2/n$ as $n$ goes to infinity.
-%\par
-%Maybe explain here why the problem is interesting ? 
-%setting (i), setting (ii) + SDM, setting (iii) + CEO.
-%The turn to 1) main results and 2) other previous works. 
-%
-\par
-Classical works on statistical estimation under communication constraint in information theory \cite{720540, zhang2013information, zhang1988estimation} implies that the ARE in setting (i) is $1$.
-Namely, asymptotically, there is no loss in performance in this setting due to the communication constraint.
-Indeed, under setting (i) the sample mean can be described by an encoder with an exponentially decaying error, leading to MSE of $\sigma^2/n + o(2^{-n})$.
-In this work we show that a similar result does not hold even in setting (ii): the relative efficiency of any adaptive estimator is at least $\pi/2$.
-Namely, the single-bit per sample constraint incurs a minimal penalty of at least $\approx 1.57$ compared to an unconstrained estimator or to the optimal estimator in setting (i).
-In addition to this negative statement, we provide an estimator that almost surely attains this minimal relative efficiency.
-In other words, we show that the lower bound of $\pi/2$ on the asymptotic relative efficiency is tight, and that it is attained regardless of the particular realization of $\theta$ or the size of the parameter space from which it is taken.
-Clearly, the minimal penalty on the efficiency of $\pi/2$ also holds under setting (iii), although the question whether such efficiency is achievable (or otherwise, what is the minimal efficiency) remains open.
+Since without bit constraint this risk is equals $\sigma^2/n$, we are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting, defined by the ratio between their MSE to $\sigma^2/n$ as $n$ goes to infinity.
 \\
 
-\subsection{Relate Works}
-The parametric estimation problem we consider is closely related to many works in statistics and information theory.
-Statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation} includes as a special case the problem of estimating a single vector of parameters from multiple data-rate constrained observations.
-These inference problems were studied in the asymptotic limit as the number of observations goes to infinity.
-In this asymptotic setting the unconstrained inference performance is always attained when all samples are taken from the same distribution \cite[Sec.
-III]{720540}.
-Indeed, in an i.i.d setting the \emph{type} of the sample is a sufficient statistics for any estimation task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples.
-For this reason in \cite{han1987hypothesis} and \cite{zhang1988estimation} attention is given to inference problems involving multiple distributions observed at different locations.
-Setting (i) above can be seen as a special case of the above works where the communication is limited to a single-bit per terminal.
-In fact, with a full access to the sample prior to encoding, the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample \cite{gray1998quantization}.
-%On the other hand, setting (iii) arises as the number of terminals grow with $n$ and their communication rates are limited to a single bit.
+In setting (i) the estimator can evaluate the sample mean and then communicate it using $n$ bits.
+This strategy leads to MSE behavior of $\sigma^2/n + o(2^{-n})$.
+Therefore, the ARE in this setting is $1$.
+Namely, asymptotically, there is no loss in performance due to the communication constraint under centralized encoding.
+In this work we show that a similar result does not hold even in setting (ii): the ARE of any adaptive estimation scheme is at least $\pi/2$.
+Namely, the single-bit per sample constraint incurs a minimal penalty of at least $1.57$ compared to an unconstrained estimator or to the optimal estimator in setting (i).
+In addition to this negative statement, we provide an estimator that almost surely attains this ARE.
+In other words, we show that the lower bound of $\pi/2$ on the asymptotic relative efficiency is tight, and that it is attained regardless of the particular realization of $\theta$ or the size of the parameter space from which it is taken.
+Clearly, the minimal penalty on the efficiency of $\pi/2$ also holds under setting (iii), although the question whether such efficiency is achievable (or otherwise, what is the minimal ARE) remains open.
+\\
 
-This last situation is also obtained by the multiterminal source coding setting, a.k.a.
-the CEO problem \cite{berger1996ceo} can be seen as a generalization of our setting (iii), where multiple draws of $\theta$ and rounds of $n$ bit communication is permitted.
-In particular, the minimal CEO distortion with $1$ bit per terminal provides a lower bound on the MSE risk.
+As the variance $\sigma^2$ goes to zero, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is easily solved by a bisection style method over the parameter space.
+Therefore, the general case of non-zero variance is a reminiscent of the noisy binary search problem with possibly infinite number of unreliable tests \cite{cicalese2002least, Karp:2007:NBS:1283383.1283478}.
+However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a noisy signal.
+For example, sigma-delta modulator (SDM) analog-to-digital conversion \cite{1092194} uses one-bit threshold detector combined with a feedback loop to update an accumulated error state, and therefore falls under setting (ii).
+A SDM with a constant input $\theta$ corrupted by a Gaussian noise was studied in \cite{53738}, where it was shown that the output of the modulator converges to the true constant input almost surely.
+In other words, the SDM provides a consistent estimator for setting (ii).
+The rate of this convergence, however, was not analyzed and cannot be derived from the results of \cite{53738}.
+Our results imply that the rate of convergence of a SDM to a constant input is at most $\sigma^2\pi/2$ over the number of feedback iterations.
+\\
 
-In fact, with a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample \cite{gray1998quantization}.
-The sigma-delta modulatior (SDM) \cite{1092194} uses a single bit quantizer with a feedback loop, and therefore falls under setting (ii).
-The SDM with a constant input $\theta$ corrupted by a Gaussian noise was considered in \cite{53738}, where it was shown that the output of the modulator converges to the true constant input.
-Therefore, the SDM provides a consistent estimator for setting (ii).
-The rate of this convergence, however, was not analyzed and cannot be derived directly from the results of \cite{53738}.
-In fact, the results of this paper implies that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-\par
+We note that even the centralized encoding of setting (i) poses a non-trivial challenge for the design and analysis of optimal encoding and estimation scheme.
+Indeed, the standard technique to encode an unknown random quantity using $n$ bits is attained by a scalar quantizer.
+However, the optimal design of this quantizer depends on the distribution of its input \cite{gray1998quantization}, which is the goal of our estimation task.
+Therefore a non-trivial exploration exploitation tradeoff arises.
+In our setting, the only missing parameter is the mean, which, under setting (i), is known to the encode with uncertainty interval proportional to $\sigma/\sqrt{n}$.
+Therefore, while it is clear that uncertainty due to quantization decreases exponentially in the number of bits, an exact expression for the MSE in this setting is not easy to derive.
+The situation is even more involved in the adaptive encoding of setting (ii): an encoding and estimation strategy that is globally optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$, may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
+Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $2^{n-1}$ messages, is not guaranteed to be globally optimal.
+Therefore, the main contribution of this paper is a lower bound on the MSE risk of any globally optimal strategy.
+This lower bound is obtained by showing that the Fisher information of any $n$ steps strategy is not larger than $2n/(\pi \sigma^2)$.
+The desired bound of $\pi \sigma^2/(2n)$ on the MSE follows from the van Trees version of the information inequality \cite{gill1995applications}.
+Finally, we show that an estimator that attains asymptotic MSE of $\sigma^2\pi/(2n)$ is obtained as a special case of \cite[Thm.
+4]{polyak1992acceleration}.
+In addition to these two results, we also derive the one-step optimal strategy and demonstrates numerically that  the MSE under this strategy converge to $\pi \sigma^2/(2n)$.
+A proof for this converges remains elusive.
+\\
 
-%
-Estimation problem subject to the one-bit quantization constraint were also considered in compressed sensing \cite{boufounos20081,baraniuk2017exponential} and in MIMO detection in wireless communication \cite{singh2009limits}.
-
-The rest of this paper is organized as follows: the main problem and notation are defined in Section~\ref{sec:problem}.
-In Section~\ref{sec:sequential} we present a lower bound on estimation from one-bit samples in the adaptive scheme, as well as an achievable scheme that attains this bound.
-Concluding remarks are given in Section~\ref{sec:conclusions}.
-
-\section{Motivation and Related Works}
-Standard considerations implies that the optimal encoding in setting (i) is reduced to an optimal $n$ bits description of the  sample mean.
-The standard technique to encode an unknown random quantity using $n$ bits is attained by an optimal scalar quantizer.
-However, the design of this quantizer depends on the distribution of its input \cite{gray1998quantization}, which is the goal of the estimation.
-Therefore, although the ARE in this setting is shown to be one \cite[Sec.
-III]{720540}, we see that a non-trivial challenge arise even in this case.
-In setting (ii), the above challenge of optimal quantizer design with imprecise input distribution occurs upon the the arrival of each new sample $X_n$.
-
-%sigma delta modulator
-
-%implies the existence of a consistent estimator in this case
-
-% our result provides a lower bound for the accuracy of a sigma-delta modulator
+Our results imply that even under coarse quantization constraints, it is possible to achieve MSE in parametric estimation within only a relatively small penalty compared to the unconstrained estimator.
+A possible clue for this non-intuitive result is obtained from drawing the connection between our setting and the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}.
+This connection, explained in details in Section~\ref{sec:ceo}, immediately leads to a lower bound of $4/3$ on the ARE in the distributed encoding of setting (iii).
+While this lower bound provides no new information compared to the lower bound of $\pi /2$ we derive here for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimal even under one-bit quantization of each sample.
+\\
 
@@
 \cite{zhang2013information} under the more general assumption of $m$ machines each has access to $n/m$ independent samples.
-The main result of \cite{zhang2013information} are lower bounds on the estimation error as a function of the total number of bits $R$ with which each machine can communicate.
-Our settings corresponds to the case $m=n$ and $R=1$, and our result is a fundamental lower bound and a matching achievable scheme under this simplified setting.
-
- We also note that the counterpart of setting (iii) in the case of hypothesis testing was considered in \cite{52470}.
-
- The optimal design  requires the distribution of the input, which is the goal of estimation and is known appriori.
-
- standard technique to encode an unknown random quantity using $n$ bits is attained by an optimal scalar quantizer,  by designing a scaler quantizer Unlike standard quantization task of encoding an unn
-
-%Note that when multiple realization of $\theta$ are involved, the prior distribution $P_\theta$ plays a significant role in the overall MSE, whereas in our case we expect the final distortion to be independent of the actual prior distribution as in the two schemes in the sequential case.
+The main result of \cite{zhang2013information} are bounds on the estimation error as a function of the number of bits $R$ with which each machine can communicate.
+Specializing their result to our setting, by taking $m=n$ and $R=1$, leads to looser bounds then $\sigma^2\pi/(2n)$ for case (ii) and (iii).
+Other related works include statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation}, although their results apply only to setting (i).
+The counterpart of setting (iii) in the case of hypothesis testing was considered in \cite{52470}.
+%
+Estimation problem subject to the one-bit quantization constraint were also considered recently in compressed sensing \cite{boufounos20081,baraniuk2017exponential} and in MIMO detection in wireless communication \cite{singh2009limits}.
 \\
 
-\subsection{Intuition from Remote Multiterminal Source Coding}
-A first clue for this rather surprising result can be seen drawing the connection between our parametric estimation problem to the remote multiterminal source coding problem of \cite{berger1996ceo}, also known as the CEO problem.
-The CEO setting considers $n$ encoders, each has access to a corrupted version of a source signal.
-The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator.
-Therefore, assuming that $\theta$ is drawn randomly from a prior $\pi(\theta)$, the distributed estimation setting (iii) corresponds to the CEO setting with $k=1$, where the $i$th agent observes
-\begin{equation}
-\label{eq:Gaussian_channel}
-X_i = \theta + Z_i,
-\end{equation}
-and has $R_i=1$ bits to transmit this observation.
-As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise of variance $\sigma^2$ provides a lower bound on the MSE distortion in estimating $\theta$.
-In fact, the difference between this lower bound and the actual MSE in our setting indicates the importance of coding over blocks consisting of $k$ independent realizations of $\theta$ versus $k=1$ in our setting.
-\par
-A closed-form expression for CEO under quadratic distortion is known only for the case where the sequence to described by the encoders is sampled from a Gaussian distribution \cite{prabhakaran2004rate}.
-By using the characterization of the minimal CEO distortion as the number of terminals goes to infinity, we conclude the following:
-\begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\pi(\theta)$ is the normal distribution. Then any estimator $\widehat{\theta}_n$ of $\theta$ in the distributed setting satisfies
-\[
- n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + o(1).
-\]
-\end{prop}
-
-\begin{proof}
-We consider the expression \cite[Eq. 10]{chen2004upper} that provides the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots R_L$:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-Assuming $R_\Sigma = n$ and $L=n$ we get
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-n = \frac{1}{2} \log \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-The value of $D^\star$ that satisfies the equation above describes the MSE in the quadratic Gaussian CEO setting under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$ we conclude that
-\[
-D^\star = \frac{ \frac{4\sigma^2}{3} }{n + \frac{4 \sigma^2}{3 \sigma_\theta^2} } + O(e^{-n}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-\end{proof}
-We note that although the CEO lower bound was derived by the MSE attainable assuming optimal allocation a total of $n$ bits among the encoders, the same expression is from the upper bound to the CEO derived in \cite[Prop.
-5.2]{KipnisRini2017}, that assumes $R_1=\ldots,R_n = 1$ rather than optimal allocation of $n$ bits among all encoders.
-%\[
-%D_{CEO} / \sigma_\theta^2 \leq \left( 1 + \sum_{i=1}^n \frac{\sigma_\theta^2}{\sigma^2} \frac{1 - 2^{-2R_i}} {1+ \frac{\sigma_\theta^2}{\sigma^2}  2^{-2 R_i}  } \right)^{-1}
-%\]
-%where $\sigma_\theta^2$ is the variance of the distribution $\pi(\theta)$. Using $R_1=\ldots=R_n=1$ we get
-%\[
-%D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + o(n^{-1}). 
-%\]
-
-Statistical inference problems under communication constraints in the nature of our setting were considered in information theory in 
-\cite{han1987hypothesis, zhang1988estimation, 720540}.
-These works consider a multi-terminal source coding setting in which the $i$th terminal observes $n$ samples from the distribution and is allotted $nR_i$ bits to communicate its estimate.
-The main focus of these works is the difference between inference with communication constraint and the unconstrained vanilla statistical estimation setting, as the number of samples $n$ goes to infinity subject to a total finite rate constraint.
-Our setting (i) can be seen as a special case of this setting where with a single terminal and $R_1 = 1$.% whereas our case (iii) is obtained from this setting by taking $n=1$, $R_i=1$, and number of terminals grow with $n$.
-However, as explained in \cite[Sec.
-III]{720540}, a single terminal in this setting always lead to the unconstrained inference performance.
-Indeed, when all samples are taken from the same distribution, the \emph{type} of the sample \cite{csiszar1998method} is a sufficient statistics for any inference task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples.
-For this reason, attention is given in these works to inference problems involving multiple distributions observed at different locations and hence the results there do not apply to our setting.
-In fact, with a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample.
-Finally, we note that setting (ii) includes as a special case the sigma-delta modulation (SDM) analog-to-digital conversion scheme with a constant input $\theta$ corrupted by Gaussian noise $Z_i$, as was considered in \cite{53738}.
-While it was shown there that the output of the modulator converges to the true constant input, the rate of this convergence was not analyzed and cannot be derived directly from the results of \cite{53738}.
-In fact, a corollary from the results in this paper we conclude that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-Finally, the multiterminal source coding setting denoted as the CEO problem \cite{berger1996ceo} can be seen as a generalization of our setting (iii), where multiple draws of $\theta$ and rounds of $n$ bit communication is permitted.
-In particular, the minimal CEO distortion with $1$ bit per terminal provides a lower bound on the MSE risk.
-\par
-
-%Why it is surprising that the estimator is independent of $\theta$, $\Theta$ or $\pi(\theta)$.
-
-\subsection{Related Works}
-\subsubsection*{Statistical inference under communication constraints}
-The problem of statistical inference under communication constraint has a long and rich history in statistics and information theory.
-Statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation} includes as a special case the problem of estimating a single vector of parameters from multiple data-rate constrained observations.
-These inference problems were studied in the asymptotic limit as the number of observations goes to infinity.
-The main question asked there is the difference between inference with communication constraint and the unconstrained vanilla statistical estimation setting.
-In this asymptotic setting the unconstrained inference performance is always attained when all samples are taken from the same distribution \cite[Sec.
-III]{720540}.
-Indeed, in an i.i.d setting the \emph{type} of the sample is a sufficient statistics for any estimation task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples.
-For this reason in \cite{han1987hypothesis} and \cite{zhang1988estimation} attention is given to inference problems involving multiple distributions observed at different locations.
-Setting (i) above can be seen as a special case of \cite{han1987hypothesis, zhang1988estimation, 720540} where the communication is limited to a single-bit per terminal.
-
-%\subsubsection{Estimation from 1-bit measurements}
-%Single-bit or binary detectors are the basis for digital technology, and works considers the estimation of parameters from the results of such detectors have been around from the early days of digital computing.
-The burst of works in compressed sensing in the previous decade also gave raise to multiple 1-bit results \cite{rice_university}.
-Due to the popularization of MIMO technology and the expected break of mm-wave in wireless communication there have been many works 1-bit detection at the A/D in the receiver \cite{2016arXiv160204193Z}.
-
-\subsubsection*{Relation to channel coding}
-The problem we consider is the estimation of the parameter $\theta$ by observing 
-\begin{equation}
-\label{eq:channel}
-X_i = \theta + Z_i, \quad i=1,\ldots,n,
-\end{equation}
-where the $Z_i$s are independent, centered normal with variance $\sigma^2$.
-The problem of estimating $\theta$ from the $X_i$s can be seen as the attempt to transmit a real number $\theta$ over an additive white Gaussian noise (AWGN) channel.
-In particular, setting (ii) can be seen as the feedback version of this transmission, which is closely related to \cite{horstein1963sequential, 1053879}.
-However, in our setting $\theta$ is either fixed or drawn once from a prior distribution, so the communication in \eqref{eq:channel} is limited to a repetition code.
-Moreover, in setting (ii) we have the additional constraint that the message is a causal function of the previous messages, where in case (iii) it is completely memoryless.
-Works in information theory which consider such setting includes AWGN channel with 1-bit ADC at the receiver \cite{DBLP:journals/corr/VarastehSG16}.
-\par
-
-\subsubsection*{Relation to source coding}
-With a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample.
-Setting (ii) includes as a special case the sigma-delta modulation (SDM) analog-to-digital conversion scheme with a constant input $\theta$ corrupted by Gaussian noise $Z_i$, as was considered in \cite{53738}.
-While it was shown there that the output of the modulator converges to the true constant input, the rate of this convergence was not analyzed and cannot be derived directly from the results of \cite{53738}.
-As a corollary from the results in this paper we conclude that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-Finally, the remote multiterminal source coding setting of \cite{berger1996ceo} corresponds to the case of $n$ rate-constrained encoders, each observing a noisy version of an information source.
-The difference between this setting and ours is that in ours the parameter of interest is not an information source.
-By assuming a prior distribution on this parameter, the CEO provides a lower bound on the estimation error in the fully distributed setting (iii).
-This lower bound can be attained if we were to consider the average error in multiple independent realizations of our problem rather than a single realization as we do here.
-\\
-
-%As opposed to the aforementioned line of works, we focus on estimation of samples taken from a single distribution in the finite blocklength performance.
-We are interested in particular in addition restrictions on the communication and information sharing between the encoders.
-For example, our main focus is the case where the observer must communicate a single bit upon drawing from the distribution.
-This is in contrast to the asymptotic setting where the observer can encode the outcome of $n$ draws at once using a single $n$ bit message.
-Alternately, such setting can be seen as having $n$ different observers, each is capable of observing a single realization and transmit a single bit.
-
-%{\color{red} The Van Trees inequality was extended to the estimation of multiple parameters in \cite{bobrovsky1987}. It is closely related with the }
-
-\begin{comment}
-\subsection{Sigma-Delta Encoding}
-
-and covariance function \cite[Eq. 25]{53738}
-\[
-R(k) = \mathbb E M_{n+k} M_n = \theta^2 + O \left( \frac{1}{\sigma \sqrt{ k} } \right). 
-\]
-{\color{red} This is not enough to deduce convergence. Need to go over the paper and check if rate of convergence can be deduced. Also do simulations BEFORE that. \\
-
-What is the error in estimating the mean of stationary ergodic process ? 
-}
-Since the SDM is a special case of the sequential scheme, we conclude that the MSE of any SDM with a noisy DC signal is bounded from below by $n^{-1} \sigma^2 \pi/2 $.
-\end{comment}
-
 The rest of this paper is organized as follows: the main problem and notation are defined in Section~\ref{sec:problem}.
-Our main results are presented and discussed in Section~\ref{sec:sequential}.
+In Section~\ref{sec:ceo} we illustrate a connection between our parametric estimation problem and the remote multiterminal lossy compression problem.
+Our main results are given in  Section~\ref{sec:sequential}, where we present a lower bound on estimation from one-bit samples in the adaptive scheme, as well as an achievable scheme that attains this bound.
 Concluding remarks are given in Section~\ref{sec:conclusions}.
-
-%Even with such arguably simple setting, we will see that the performance limit in the estimating task based on single bit observations provides an interesting setting for discussion that bridges classical works in statistics, coding theory, information theory and optimization.
+For sake of fluency, long proofs are deferred to the Appendix.
 
@@
 \end{center}
-\caption{\label{fig:sequential} Adaptive single-bit encoding: the $i$th encoder delivers a single bit message which is a function of its private sample $X_i$ and the previous messages $M_1,\ldots,M_{i-1}$.}
+\caption{\label{fig:sequential} Adaptive one-bit encoding: the $i$th encoder delivers a single bit message that is a function of its private sample $X_i$ and the previous $i-1$ messages $M_1,\ldots,M_{i-1}$.}
 \end{figure}
 
-Let $X_i$, $i=1,\ldots,n$, be $n$ independent samples from the normal distribution $\mathcal N(\theta,\sigma^2)$ with mean $\theta$ and variance $\sigma^2$.
-We assume that the mean $\theta$ is drawn once from a prior distribution $\pi(\theta)$ on the parameter space $\Theta$, which is a closed interval of the real line.
+Let $X_i$, $i=1,\ldots,n$, be $n$ independent samples from the normal distribution with mean $\theta$ and variance $\sigma^2$.
+We assume that the mean $\theta$ is drawn once from a prior distribution $\pi(\theta)$ on $\Theta$, which is a closed interval of the real line.
 We moreover assume that $\pi(\theta)$ is absolutely continuous with respect to the Lebesgue measure with density $\pi(d\theta)$.
@@
 \end{itemize}
-In other words,  the $n$ messages $M^n$ are the only information on the sample $X^n = \left(X_1,\ldots,X_n\right)$ available to the estimator.
-The $i$th message is defined by a function from the real line to $\{-1,1\}$, measurable with respect to the sigma algebra generated by $M^{i-1}$ and $X_i$.
-The estimator, upon observing $M^n$, produces an estimate $\widehat{\theta}_n(M^n)$ of $\theta$.
+In other words, the $i$th message is defined by a function from the real line to $\{-1,1\}$ that is measurable with respect to the sigma algebra generated by $M^{i-1}$ and $X_i$, and the $n$ messages $M^n$ are the only available to the estimator.
+Upon observing $M^n$, the estimator produces an estimate $\widehat{\theta}_n(M^n)$ of $\theta$.
 A system describing the above scheme is illustrated in Fig.~\ref{fig:sequential}.
@@
 
-In this work we are concerned with the mean squared error (MSE) risk:
+In this work we are concerned with the MSE risk defined as
 \begin{equation}
 \label{eq:error_def}
-\epsilon_n \triangleq \mathbb E\left(\widehat{\theta}_n - \theta \right)^2,
+\mathbb E\left(\widehat{\theta}_n - \theta \right)^2,
 \end{equation}
@@
 
-The main problem we consider is the minimal value that can be attain in \eqref{eq:error_def} as a function of $n$.
-Note that this minimization is the combination of the following two procedures: (1) selecting the $i$th message $M_i$ based on past messages and current observation $X_i$, and (2) estimating $\theta$ given messages $M^n$.
-We are interested in particular in the asymptotic relative efficiency of estimators $\widehat{\theta}_n$ for $\theta$ compared to the sample mean $\bar{X}_n = \frac{1}{n} \sum_{i=1}^n X_i$.
-Since the MSE attained by the latter is $\sigma^2/n$, this relative efficiency is defined as
+The main problem we consider is the minimization of \eqref{eq:error_def} over all encoding and estimation strategies, and the characterization of its minimal value as a function of  $n$.
+This minimization is the combination of the following two procedures: (1) selecting the $i$th message $M_i$ based on past messages and current observation $X_i$, and (2) estimating $\theta$ given messages $M^n$.
+We are interested in particular in the ARE of estimators of $\theta$ compared to the sample mean $\bar{X}_n = \frac{1}{n} \sum_{i=1}^n X_i$.
+Since the MSE attained by the latter is $\sigma^2/n$, this ARE is defined as
 \begin{equation}
-\rho \triangleq \lim_{n \rightarrow \infty} \frac{n}{\sigma^2}  \epsilon_n. 
+ \lim_{n \rightarrow \infty} \frac{n}{\sigma^2}  \mathbb E\left(\widehat{\theta}_n - \theta \right)^2. 
 \label{eq:relative_efficiency}
 \end{equation}
-{\color{red}
-Since the conditional expectation of $\theta$ with respect to $\bar{X}_n$ (and not $\bar{X}_n$) minimizes \eqref{eq:error_def}, we need to justify the fact that we use the sample mean as the reference estimator.
-}
+%{\color{red} Since the conditional expectation of $\theta$ with respect to $\bar{X}_n$ (and not $\bar{X}_n$) minimizes \eqref{eq:error_def}, we need to justify the fact that we use the sample mean as the reference estimator.}
 
 In addition to the notations defined above, we denote by $\phi(x)$ the standard normal density and by $\Phi(x)$ the standard normal cumulative distribution function.
-Prime denote derivative with respect to $\theta$.
+\\%Derivatives with respect to $\theta$ are denoted by prime.\\
 
-% Lower Bound on the assymptotic minimal effeciency.
-% Scheme that attains the assymptotic minimal effeciency. 
-% Bayesian scheme that is one step optimal. We leave open the question whether this scheme attains the asymptotic minimal effeciency
+Before deriving our main results, we comment on the relation between our setting and the remote multiterminal source coding problem.
+
+\section{Relation to Remote Multiterminal Source Coding \label{sec:ceo}}
+In this section we draw a connection between our general problem of mean estimation from one-bit samples, to the remote multiterminal source coding problem \cite{berger1996ceo}, also known as the CEO problem.
+The setting of the CEO includes $n$ encoders, each has access to a noisy version of a random source sequence.
+% $\left\{ U_j,\,j=1,2,\ldots \right\}$. 
+The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator. \par
+Assuming that $\theta$ is drawn randomly once from a prior $\pi(\theta)$, mean estimation from one-bit under distributed encoding (setting (iii) in the Introduction) corresponds to the CEO setting with block length $k=1$, where the $i$th encoder observes
+\begin{equation}
+\label{eq:Gaussian_channel}
+X_i = \theta + \sigma Z_i,
+\end{equation}
+with $Z_1,\ldots,Z_n$ i.i.d.
+standard normal, and uses $R_i=1$ bits to transmit its observation.
+As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise at each estimate of variance $\sigma^2$, provides a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting.
+ \\
+
+A closed-form expression for the MSE distortion in the CEO is known only for the case where the source sequence is sampled independently from the normal distribution \cite{prabhakaran2004rate}.
+By using the characterization of this minimal distortion as the number of terminals goes to infinity, we conclude the following:
+\begin{prop} \label{prop:ceo_lower_bound}
+Assume that $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$. Then any estimator $\widehat{\theta}_n$ of $\theta$ in 
+the distributed setting satisfies
+\begin{equation} \label{eq:ceo_bound}
+ n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + o(1).
+\end{equation}
+\end{prop}
+
+\begin{proof}
+We consider the expression \cite[Eq. 10]{chen2004upper} that provides the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$:
+\begin{equation} \label{eq:ceo_optimal_sumrate}
+R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
+\end{equation}
+Assuming $R_\Sigma = n$ and $L=n$, we get
+\begin{equation} \label{eq:ceo_optimal_sumrate}
+n = \frac{1}{2} \log \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
+\end{equation}
+The value of $D^\star$ that satisfies the equation above describes the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
+Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed encoding setting.
+By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$, we conclude that
+\[
+D^\star = \frac{ \frac{4\sigma^2}{3} }{n + \frac{4 \sigma^2}{3 \sigma_\theta^2} } + O(e^{-n}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
+\]
+\end{proof}
+Since the lower bound \eqref{eq:ceo_bound}  was derived assuming optimal allocation of the $n$ bits among the encoders, it may seem as if a tighter bound can be obtained in our case by considering the CEO distortion with $R_1=\ldots,R_n = 1$.
+However, an upper bound for the CEO distortion under this condition follows from \cite[Prop.
+5.2]{KipnisRini2017}, and leads to
+\[
+D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
+\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + o(n^{-1}),
+\]
+which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small. \par
+We conclude therefore that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed encoding setting, is attributed exclusively to the ability to perform coding over blocks.
+Namely, the ability to consider $k>1$ independent realizations of $\theta$ versus only one in ours.
+In other words, it is the ability to exploit the geometry of a high-dimensional product space, rather than the distributed nature of the problem, that distinguishes between the CEO distortion and the mean estimation from one-bit samples.\par
+In the next section we show that the ARE in adaptive encoding setting does not exceeds $\pi/2$, and thus provides a tighter lower bound for the distributed encoding setting than $4/3$ of  \eqref{eq:ceo_bound}.
 
 \section{Results \label{sec:sequential}}
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the asymptotic relative efficiency of and adaptive estimator cannot get below $\pi/2$.
-Next, we provide a particular adaptive estimation scheme and show in Theorem~\ref{thm:sgd} that its efficiency is $\pi/2$.
-Finally, in Theorem~\ref{thm:opt_one_step} we provide an adaptive estimation scheme that is optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen.
-While it is not clear whether the efficiency of this last scheme is $\pi/2$, numerical simulations suggests that the MSE of this scheme time s $n$ converges as well to $\pi/2$, but in a faster rate than the first scheme.
-
-%While we provide expressions for the optimal message, evaluating the asymptotic efficiency of this estimation scheme turns out to be a challenging task.
-We therefore leave open the question whether this scheme attains the lower bound with equality, and only provide numerical result that support this conjecture.
-\\
+The first main results of this paper, as described in Thm.~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be lower than $\pi/2$.
+Next, we provide a particular adaptive estimation scheme and show in Thm.~\ref{thm:sgd} that its efficiency is $\pi/2$.
+Finally, in Thm.~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen.
+While it is not clear whether the efficiency of this last scheme is $\pi/2$, numerical simulations suggests that the MSE of this scheme times $n$ also converges to $\pi/2$.
 
@@
 
-\subsection{A Lower Bound on Adaptive Single-Bit Schemes}
-Our first results asserts that the relative efficiency \eqref{eq:relative_efficiency} of any adaptive estimation scheme is bounded from below by $\pi/2$, as follows from the following theorem:
+\subsection{A lower bound on adaptive one-bit schemes}
+Our first results asserts that the ARE \eqref{eq:relative_efficiency} of any adaptive estimation scheme is bounded from below by $\pi/2$, as follows from the following theorem:
 \begin{thm}[minimal relative effeciency] \label{thm:adpative_lower_bound}
@@
 % Let $\pi(\theta)$ be an absolutely continuous prior distribution on $\Theta$ with density function converges to zero at the endpoints of the interval $\Theta$. 
-Assumes that $P(d\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
+Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
 \[
-\mathbb E (\theta-\theta_n)^2 \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\pi}{2n}\sigma^2+o(n^{-1}),
+\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\pi}{2n}\sigma^2+o(n^{-1}),
 \]
@@
 \[
-I_0 = \mathbb E \left( \frac{d}{d\theta} \log P_\theta(\theta) \right)^2
+I_0 = \mathbb E \left( \frac{d}{d\theta} \log \pi (\theta) \right)^2
 \]
@@
 The main idea in the proof is to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$.
-Once this bound is achieved, the result follows by using the Van-Trees inequality \cite{gill1995applications} which bounds from below the MSE of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
+Once this bound is achieved, the result follows by using the van-Trees inequality \cite[Thm.
+2.13]{tsybakov2008introduction},\cite{gill1995applications} which bounds from below the MSE of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
 The details are given in the Appendix.\\
 
-Next, we present an adaptive estimation scheme which attains the minimal asymptotic efficiency $\pi/2$. 
-%Theorem~\ref{thm:adpative_lower_bound}. This estimation scheme can be seen as a gradient descent
-
-\subsection{Asymptotically Optimal Estimator}
+Next, we present an adaptive estimation scheme which attains ARE of $\pi/2$. 
+\subsection{Asymptotically optimal estimator}
 Consider the following estimator $\widehat{\theta}_n$ for $\theta$:  set 
@@
 
-As the following theorem shows, the estimator $\widehat{\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the minimal asymptotic efficiency as established by Theorem~\ref{thm:adpative_lower_bound}.
+For the estimator defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} 
+we have the following results:
 \begin{thm} \label{thm:sgd}
-The sequence $\widehat{\theta}_n$ of \eqref{eq:sgd_alg} satisfies
+The sequence $\widehat{\theta}_n$ of \eqref{eq:sgd_est} satisfies
 \[
@@
 
-Note that $\theta_0$ is not explicitly defined in 
+In other words, Thm.~\ref{thm:sgd} implies that the estimator $\widehat{\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the minimal asymptotic efficiency as established by Thm.~\ref{thm:adpative_lower_bound}.\par
+Note that $\theta_0$ is not explicitly defined 
 in equation \eqref{eq:sgd_est}.
-Arguably, a reasonable initialization is $\theta_0 = \mathbb E [\theta]$.
-However, Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator, is indifferent to this initialization.
-Thus, the optimal efficiency is attained without using the prior distribution on $\theta$.
-Nevertheless, the bound in Theorem~\ref{thm:adpative_lower_bound} suggests that the estimation error can be greatly reduced whenever the prior of $\theta$ provides a lot of information $I_0$ on its location.
-In order to incorporate this information in a more meaningful way, we present a Bayesian estimation scheme that is conjectured to attain the optimal asymptotic efficiency.
+While a reasonable initialization is $\theta_0 = \mathbb E [\theta]$,  Thm.~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
+Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the size of the parameter space $\Theta$.
+Nevertheless, the bound in Thm.~\ref{thm:adpative_lower_bound} suggests that the non-asymptotic estimation error can be greatly reduced whenever the location information $I_0$ is large.
+In contrast, the one-step optimal scheme presented in the following subsection exploits the prior information on $\theta$ provided by $\pi(\theta)$.
 
-\subsection{One-step Optimal Estimation}
-In this subsection we present an estimation scheme that posses the property of \emph{one-step optimality}.
-That is, at each step $i$, the $i$th encoder designs the detection region $M_i^{-1}(1)$ such that the MSE given $M^i$ is minimal.
+\subsection{One-step optimal estimation}
+We now consider an estimation scheme that posses the property of \emph{one-step optimality}: at each step $i$, the $i$th encoder designs the detection region $M_i^{-1}(1)$ such that the MSE given $M^i$ is minimal.
 In other word, this scheme designs the messages in a greedy manner, such that the MSE at step $i$ is minimal given the current state of the estimation described by $M^{i-1}$.
@@
 
-The structure of the message that minimizes the next step MSE is given by the following theorem:
+The following theorem determine the structure of the message that minimizes the next step MSE:
 \begin{thm}[optimal one-step estimation] \label{thm:opt_one_step}
@@
 \begin{align*}
-m^-(\tau)  & = \frac{\int_{-\infty}^{\tau} \theta P(d\theta) }{\int_{-\infty}^{\tau} P(d\theta)} ,\\
-m^+(\tau) & = \frac{\int_{\tau}^\infty \theta P(d\theta) }{\int_{\tau}^\infty P(d\theta)} .
+m^-(\tau)  & = \frac{\int_{-\infty}^{\tau} \theta \pi(d\theta) }{\int_{-\infty}^{\tau} \pi(d\theta)} ,\\
+m^+(\tau) & = \frac{\int_{\tau}^\infty \theta \pi(d\theta) }{\int_{\tau}^\infty \pi(d\theta)} .
 \end{align*}
@@
 \end{lem}
-\end{proof}
-
 \begin{lem} \label{lem:adaptive}
 Let $U$ be an absolutely continuous random variable with
-pdf $P(du)$. Then the one-bit message $M^\star$ that minimizes
+pdf $P(du)$. Then the one-bit message $M^\star\in \{-1,1\}$ that minimizes
 \[
@@
 \]
-where $\tau$ is the unique solution to the equation
+where $\tau$ is the unique solution to
  \[
@@
 \end{lem}
+\end{proof}
 
-Theorem~\ref{thm:opt_one_step} suggests the following Bayesian estimation scheme: set $P_0(t) = \pi(\theta)$, and for $n\geq 1$ update the prior as
+Thm.~\ref{thm:opt_one_step} suggests the following adaptive encoding and estimation scheme: 
+\begin{itemize}
+\item Initialization: set $P_0(t) = \pi(\theta)$.
+\item For $n\geq 1$:
+\begin{enumerate}
+\item Update the prior as
 \begin{align}
-P_n(t) = & P(\theta=t |M^n) = \frac{ P\left( \theta=t | M^{n-1} \right) P(M_n | \theta = t , M^{n-1})  } { P(M_n | M^{n-1} )} \nonumber \\ 
+P_n(t) = & P(\theta=t |M^n) \\
+& = \frac{ P\left( \theta=t | M^{n-1} \right) P(M_n | \theta = t , M^{n-1})  } { P(M_n | M^{n-1} )} \nonumber \\ 
 & = \alpha_n  P_{n-1}(t) \Phi\left(M_n \frac{ t - \tau_{n-1} }{\sigma} \right), \label{eq:density_update}
@@
 \]
-The $n$th estimate for $\theta$ is the conditional expectation of $\theta$ given $M^n$, namely
+\item The $n$th estimate for $\theta$ is the conditional expectation of $\theta$ given $M^n$, namely
 \begin{equation}
@@
 \end{equation}
-Next, solve equation \eqref{eq:fixed_point} with the updated prior $P_n(t)$ instead of $P(\theta)$.
-Note that since the standard normal cdf $\Phi(x)$ is log-concave, the updated prior $P_n(t)$ remains log-concave and thus a unique solution to \eqref{eq:fixed_point} is guaranteed by Lemma~\ref{lem:unique}.
-Finally, update the $n+1$th message as
+\item Solve equation \eqref{eq:fixed_point} with the updated prior $P_n(t)$ instead of $P(d\theta)$.
+Note that since the standard normal cdf $\Phi(x)$ is log-concave, the updated prior $P_n(t)$ remains log-concave and thus a unique solution to \eqref{eq:fixed_point} is guaranteed by Lem.~\ref{lem:unique}.
+\item Update the $(n+1)$th message as
 \begin{equation}\label{eq:message_update}
-M_{n+1} = \sgn(X_{n+1}-\tau_n).
+M_{n+1} = \sgn(X_{n+1}-\tau_n)
 \end{equation}
-
-Since the equation \eqref{eq:fixed_point} has no analytic solution in general, it is hard to derive the asymptotic behavior of the Bayes estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}.
+\end{enumerate}
+\end{itemize}
+Since equation \eqref{eq:fixed_point} has no analytic solution in general, it is hard to derive the asymptotic behavior of the estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}.
 We conjecture, however, that it attains the asymptotic relative efficiency of $\sigma^2\pi/2$, as can be observed from the numerical simulation illustrated in Fig.~\ref{fig:adaptive_error}.
-Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the sample mean for the same sample realization.
-
- % In fact, the numerical simulation in Fig.~\ref{fig:simulation} shows that this scheme outperform the estimator of \eqref{eq:sgd_est} even when the prior on $\Theta$ is least favorable for Bayes estimation \cite{Bickel1981}.
+Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the asymptotically optimal estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the sample mean for the same sample realization.
 
@@
 \begin{tikzpicture}
-\node at (0,0) {\includegraphics[scale=0.4]{error}};
+\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
+%\node[color = blue,  minimum width=1cm, align = left] at (1.5,1.5) {assymptotically optimal \eqref{eq:sgd_est}};
+%\node[color = red, minimum width=1cm, align = left] at (1.5,0.55) {one-step optimal \eqref{eq:message_update}} ;
+\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left(\widehat{\theta}_n - \theta \right)^2$};
+\node[scale = 0.7] at (0,-2.4) {$n$};
+%\draw[dashed] (-3.5,1.18) node[left, scale = 0.7] {$\frac{\pi}{2}$}-- (-3,1.18);
 \end{tikzpicture}
-\caption{Normalized empirical risk $n\left(\widehat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $100$ Monte Carlo trials.
-In each trial, $\theta$ is chosen uniformly in the interval $(-5,5)$.
+\caption{Normalized empirical risk $n\left(\widehat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $500$ Monte Carlo trials.
+In each trial, $\theta$ is chosen uniformly in the interval $(-3,3)$.
 \label{fig:adaptive_error}  }
@@
 
-\begin{comment}
-\subsection{Relation to Sigma-Delta Modulation \label{subsec:sdm}}
-The SDM is a device that converts continuous-time analog signals to a discrete-time sequence of binary digits.
-The basic operation of a SDM can be described as follows: the modulator takes as input a sequence of continuous amplitude samples $X_n$, which are typically represents samples of a continuous-time signal taken uniformly at sampling rate $f_s$ much higher than the Nyquist rate of the signal \cite{1095151}.
-The output of the modulator is a sequence $M_n$ of binary values, obtained according to the following rule:
-\begin{align}
-\begin{cases} V_{n+1} & =  V_n - \alpha q(V_n) + X_n, \\
-M_n & = \sgn(V_n)  \end{cases}, \quad n=1,2,\ldots, \label{eq:sdm}
-\end{align}
-where $\alpha > 0$ is a parameter of the modulator that is determined by the maximal value of the input sequence $X^n$.
-The SDM of the form \eqref{eq:sdm} was studied in \cite{53738} under the assumption that the input process $X_n$ is an i.i.d Gaussian process.
-The main results from \cite{53738} shows that regardless of the initial state $V_0$, the process $M_n$ is a stationary ergodic process with mean $\theta$.
-It follows that a consistent estimation of $\theta$ is obtained by taking the mean of the sequence $\{M_n\}$.
-However, the results from \cite{53738} does not provide a closed form for the second order statistics of $\{M_n\}$, so that convergence rate cannot be derived from \cite{53738}.
-\end{comment}
-
 \section{Conclusions \label{sec:conclusions}}
-We considered the relative efficiency in estimating the mean of a normal distribution from single-bit measurements in an adaptive setting.
-We have shown that this minimal relative efficiency is $\pi/2$, namely there is a penalty factor of at least $\pi/2$ on the asymptotic MSE in estimating the mean compared to an estimator that has full access to the sample.
-We also showed that this lower bound is tight by presenting an estimation procedure that attains it.
+We considered the MSE risk and asymptotic relative efficiency in estimating the mean of a normal distribution from a single-bit encoding of each sample from this distribution.
+In the adaptive scenario where each one-bit message is a function of the previously seen messages and current sample, we showed that the minimal relative efficiency is $\pi/2$.
+Namely, there is a penalty factor of at least $\pi/2$ on the asymptotic MSE risk in estimating the mean compared to an estimator that has full access to the sample.
+We also showed that this lower bound is tight by presenting an adaptive estimation procedure that attains it.
 %but ignores the prior distribution on the parameter space.
 In addition, we characterized the single-bit message that minimizes the next step MSE, and described an estimation procedure that is based on a sequence of one-step optimal messages.
-We leave open the questions whether this estimator attains the minimal efficiency and whether it leads to an estimation scheme which is globally optimal.
-\\
+We leave open the questions whether this estimator attains the minimal efficiency and whether it leads to an estimation scheme which is globally optimal in the adaptive setting.
+Another open question that follows from our setting is the asymptotic MSE and relative efficiency of a fully distributed one-bit scheme.
 
-%Something about how to interpret the results
-
-% Sigma-Delta
-% Relation to CEO
-% Open questions
-% Extenstion to fully distributed setting
-
-\section*{ACKNOWLEDGMENT}
-This research is supported in parts by...
+%\section*{ACKNOWLEDGMENT}
+%This research is supported in parts by...
 %Tsachy Weissman, Stefano Rini, Robert Gray.
-
-\onecolumn
 
@@
 
-\subsection*{Proof of Theorem~\ref{thm:adpative_lower_bound}}
+\subsection*{Proof of Thm.~\ref{thm:adpative_lower_bound}}
 
@@
 
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals}}
+\subsubsection*{Proof of Lem.~\ref{lem:bound_intervals}}
 We use induction on $n \in \mathbb N$. For the base case $n=1$ we have 
@@
 \frac{  \phi^2(x)} 
-{\Phi(x) \left(1 - \Phi(x) \right) } 
-\end{equation}. 
-Taking the logarithm of \eqref{eq:induction_base} and differentiating, we conclude that any point $x$ that maximizes \eqref{eq:induction_base} satisfies
+{\Phi(x) \left(1 - \Phi(x) \right) }. 
+\end{equation}
+Taking the logarithm of \eqref{eq:induction_base} and differentiating, we conclude that any point $x$ that maximizes \eqref{eq:induction_base} also satisfies
 \[
@@
 \]
-However, since $x > \phi(x) \left( \Phi(x) -\frac{1}{2} \right)$ for all $x > 0$, the only point that satisfies the last condition is $x=0$.
-At this point \eqref{eq:induction_base} equals $2/\pi$.
-\par
+However, since $x > \phi(x) \left( \Phi(x) -\frac{1}{2} \right)$ for all $x > 0$, the only point that satisfies the last condition is $x=0$, in which \eqref{eq:induction_base} equals $2/\pi$. \par
 Assume now that \eqref{eq:bound_intervals} holds for all integers up to some $n = N-1$ and consider the case $n = N$.
@@
 \begin{align*}
-& g(x_1,\ldots, x_N) \triangleq 2 \log \left(  \sum_{k=1}^{N} (-1)^{k+1} \phi(x_k) \right) - \log
+& g(x_1,\ldots, x_N) \triangleq 2 \log \left(  \sum_{k=1}^{N} (-1)^{k+1} \phi(x_k) \right) - \\
+&  \log
 \left( \sum_{k=1}^N (-1)^{k+1} \Phi(x_k) \right)
@@
 \]
-In particular, the condition above implies $x_1 = \ldots = x_N$. If $N$ is odd then for $x_1=\ldots =x_N$ we have that \eqref{eq:bound_intervals} equals
+In particular, the condition above implies $x_1 = \ldots = x_N$. If $N$ is odd then for $x_1=\ldots =x_N$ we have that the LHS of \eqref{eq:bound_intervals} equals
 \[
@@
 which was shown to be smaller than $\pi/2$.
-If $N$ is even, then for any constant $c$ the limit of \eqref{eq:bound_intervals} exits as $(x_1,\ldots,x_N)\rightarrow (c,\ldots,c)$ and equals zero.
-Therefore, the maximum of \eqref{eq:bound_intervals} is not attained at this line.
-We now consider the possibility that \eqref{eq:bound_intervals} is maximized at the borders, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches plus or minus infinity.
+If $N$ is even, then for any constant $c$ the limit of the LHS of \eqref{eq:bound_intervals} exits as $(x_1,\ldots,x_N)\rightarrow (c,\ldots,c)$ and equals zero.
+Therefore, the maximum of the LHS of \eqref{eq:bound_intervals} is not attained at this line.
+We now consider the possibility that the LHS of \eqref{eq:bound_intervals} is maximized at the borders, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches plus or minus infinity.
 For simplicity we only consider the cases where $x_N$ goes to minus infinity or $x_1$ goes to plus infinity (the general case where the first $m$ coordinates goes to infinity or the last $m$ to minus infinity is obtained using similar arguments).
 Assume first $x_N \rightarrow -\infty$.
-Then  \eqref{eq:bound_intervals} equals
+Then the LHS of \eqref{eq:bound_intervals} equals
 \begin{align*}
@@
 \end{align*}
-which is smaller than $2/\pi$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
+which is smaller than $2/\pi$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then the LHS of
 \eqref{eq:bound_intervals} equals
@@
 \end{align*}
-where $x'_{m} = x_{m+1}$. The last expression is also smaller than $2/\pi$ by the induction hypothesis. This proves Lemma~\ref{lem:bound_intervals}. \\
+where $x'_{m} = x_{m+1}$. The last expression is also smaller than $2/\pi$ by the induction hypothesis. This proves Lem.~\ref{lem:bound_intervals}. \\
 
-\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
+\subsubsection*{Proof of Lem.~\ref{lem:fisher_bound}}
 The Fisher information of $M$ with respect to $\theta$ is given by
@@
 \end{align}
-The proof of Lemma~\ref{lem:fisher_bound} is completed since it follows from~\ref{lem:bound_intervals} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $2/(\sigma^2 \pi)$.
+The proof of Lem.~\ref{lem:fisher_bound} is completed since it follows from~\ref{lem:bound_intervals} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $2/(\sigma^2 \pi)$.
 \\
@@
 We now consider the proof of Thm.~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$, we first note that without loss of generality, each message $M_i$ can be written in the form
+In order to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$, we first note that, without loss of generality, each message $M_i$ can be written in the form
 \begin{equation}
@@
 \end{align}
-where $P\left(M_i =1 | \theta, M^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$. We now prove the following Lemma:
-
-Going back to \eqref{eq:adpt_lower_bound_proof:1}, it follows that the Fisher information of $M^n$ with respect to $\theta$ is given by 
+where $P\left(M_i =1 | \theta, M^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$. The Fisher information of $M^n$ with respect to $\theta$ is given by 
 \begin{align}
@@
 \end{align}
-where $I_\theta (M_i|M^{i-1})$ is the Fisher information of the distribution of $M_i$ given $M^{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (M_i|M^{i-1}) \leq 2/(\pi \sigma^2)$.
-The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
+where $I_\theta (M_i|M^{i-1})$ is the Fisher information of the distribution of $M_i$ given $M^{i-1}$, where it follows from Lem.~\ref{lem:fisher_bound} that $I_\theta (M_i|M^{i-1}) \leq 2/(\pi \sigma^2)$.
+We now use the following theorem from \cite[Thm.
+2.13]{tsybakov2008introduction} (see also \cite{van2004detection, gill1995applications}):
+
+\begin{thm}[The van Trees inequality \cite{tsybakov2008introduction}] \label{thm:vanTrees}  Denote by $p(\cdot,\theta)$ the density of $P_\theta$ with respect to the Lenesgue measure.
+Assume that: (i) the density $p(x,\theta)$ is measureable in $(x,\theta)$ and absolutely continuous in $t$ for almost all $x$ with respect to the Lebesgue measure.
+(ii) The Fisher information
+\[
+I(\theta) = \int \left( \frac{p'(x,\theta)}{p(x,\theta)} \right)^2 p(x,\theta) dx,
+\]
+where $p'(x,t)$ denotes the derivative of $p(x,\theta)$ in $t$, is finite and integrable on $\Theta$.
+(iii) The prior density $\pi(\theta)$ is absolutely continuous on its support $\Theta$ with zero mass at the boundries of $\Theta$, and has a finite Fisher information
+\[
+I_0 = \int_{\Theta} \frac{\left( \pi'(\theta) \right)^2} {\pi(\theta)} d\theta.
+\]
+Then, for any estimator $\widehat{t}(\mathbf X)$, the Bayes risk is bounded as follows:
+\[
+\int_{\theta} \mathbb E \left[ \left( \widehat{t}(\mathbf X) - \theta\right)^2 \right] \pi(d\theta) \geq \frac{1}{ \int I(\theta) \pi(d \theta) + I_0 }.
+\]
+\end{thm}
+Theorem~\ref{thm:vanTrees} applied to our problem with $p(x,\theta) = P(M^n|\theta)$ implies
 \begin{align*}
-\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(M^n) + I_0} \\
+\mathbb E \left(\widehat{\theta}_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(M^n) + I_0} \\
 & = \frac{1}{ \sum_{i=1}^n I_\theta (M_i | M^{i-1} ) + I_0} \\
@@
 
-\subsection*{Proof of Theorem~\ref{thm:sgd}}
+\subsection*{Proof of Thm.~\ref{thm:sgd}}
 The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration}.
-In particular, Theorem~\ref{thm:sgd} is follows directly from the following simplified version of \cite[Thm.
+In particular, Thm.~\ref{thm:sgd} is follows directly from the following simplified version of \cite[Thm.
 4]{polyak1992acceleration}:
@@
 \[
-X_i = \theta + Z_i,\quad i=1,\ldots,n.
+X_i = \theta + Z_i,\quad i=1,\ldots,n,
 \]
-Define 
+where the $Z_i$s are i.i.d. from $\mathcal N(0,\sigma^2)$ and independent of each other. Define 
 \begin{align*}
@@
 \end{align*}
-where the $Z_i$s are $\mathcal N(0,\sigma^2)$ and independent of each other, the sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions (i) and (ii) in Theorem~\ref{thm:sgd}, and $\left| \varphi(x) \right| \leq K_1(1+x)$ for some $K_1$.
+where the sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions (i) and (ii) in Thm.~\ref{thm:sgd}, and $\left| \varphi(x) \right| \leq K_1(1+x)$ for some $K_1$.
 Define $\psi(x) = \mathbb E \varphi(x+Z_1)$, $\chi(x) = \mathbb E \varphi^2(x+Z_1)$ and assume that $\psi(0)=0$, $x\psi(x) >0$ for all $x\neq 0$, $\chi(x)$ is continuous at zero, and that $\psi(x)$ is differentiable at zero with $\psi'(0)>0$.
@@
 
-Using the notation in Theorem~\ref{thm:polyak_juditsky}, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have: 
+Using the notation in Thm.~\ref{thm:polyak_juditsky}, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have: 
 \[
@@
 \end{align*}
-so $\psi'(0) = \frac{2}{\sqrt{2\pi}\sigma}$. It is now easy to verify that the rest of the conditions in Theorem~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$. Since 
+so $\psi'(0) = \frac{2}{\sqrt{2\pi}\sigma}$. It is now easy to verify that the rest of the conditions in Thm.~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$. Since 
 \[
@@
 \]
-Theorem~\ref{thm:sgd} follows from Theorem~\ref{thm:polyak_juditsky}. \QEDA
+Thm.~\ref{thm:sgd} follows from Thm.~\ref{thm:polyak_juditsky}. \QEDA
 
-\subsection*{Proof of Theorem~\ref{thm:opt_one_step}}
-In this subsection we prove lemmas \ref{lem:adaptive} and \ref{lem:unique} which lead to Theorem~\ref{thm:opt_one_step}.
+\subsection*{Proof of Thm.~\ref{thm:opt_one_step}}
+In this subsection we prove Lemmas \ref{lem:adaptive} and \ref{lem:unique} that lead to Thm.~\ref{thm:opt_one_step}.
 
-\subsubsection*{Proof of Lemma \ref{lem:adaptive}}
-Since any single-bit message $M(u) \in \{0,1\}$ is characterized by two decision region $A_1 = M^{-1}(1)$ and $A_{-1} = M^{-1}(-1)$, it follows that $\mathbb E \left[ U | M(U) \right]$ assumes only two values: $\mu_1 = \mathbb E \left[ U | M(U) = 1 \right]$ and $\mu_{-1} = \mathbb E \left[ U | M(U) = -1 \right]$.
+\subsubsection*{Proof of Lem. \ref{lem:adaptive}}
+Since any single-bit message $M(u) \in \{-1,1\}$ is characterized by two decision region $A_1 = M^{-1}(1)$ and $A_{-1} = M^{-1}(-1)$, it follows that $\mathbb E \left[ U | M(U) \right]$ assumes only two values: $\mu_1 = \mathbb E \left[ U | M(U) = 1 \right]$ and $\mu_{-1} = \mathbb E \left[ U | M(U) = -1 \right]$.
 We claim that a necessary condition for $M(u)$ to be optimal is that the sets $A_1$ and $A_{-1}$ are, modulo a set of measure $P(du)$ zero, the Voronoi sets on $\mathbb R$ corresponding to the points $\mu_1$ and $\mu_{-1}$, respectively.
@@
 \begin{align*}
-& \int_{\mathbb R} \left( u - \mathbb E[U|M(u)]  \right)^2 P(du) = \int_{A_1} (u- \mu_1)^2 P(du) + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
-& = \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_1)^2 P(du) + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
-& > \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_2)^2 P(du) + \int_{A_{-1}} (u- \mu_{-1})^2 P(du),
+& \int_{\mathbb R} \left( u - \mathbb E[U|M(u)]  \right)^2 P(du) \\
+& = \int_{A_1} (u- \mu_1)^2 P(du) + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
+& = \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_1)^2 P(du) \\
+&\quad \quad + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
+& > \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_2)^2 P(du) \\
+& + \quad \quad  \int_{A_{-1}} (u- \mu_{-1})^2 P(du),
 \end{align*}
-so clearly, the partition $A_1' = A_1 \setminus B$, $A_{-1}' = A_{-1} \cup B$ attains lower error variance which contradicts the optimality assumption and proves our claim.
+so clearly, the partition $A_1' = A_1 \setminus B$, $A_{-1}' = A_{-1} \cup B$ attains lower error variance, what contradicts the optimality assumption and proves our claim.
 It is evident that Voronoi partition of the real line corresponding to $\mu_1$ and $\mu_{-1}$ is of the form $A_{-1} = (-\infty,\tau)$, $A_{1} = (\tau, \infty)$ where the point $\tau$ is of equal distance from $\mu_1$ and $\mu_{-1}$, namely $\tau = \frac{\mu_1 + \mu_{-1}}{2}$.
@@
 
-\subsubsection*{Proof of Lemma \ref{lem:unique}} 
+\subsubsection*{Proof of Lem. \ref{lem:unique}} 
 Any solution to \eqref{eq:lem_fixed_point} is a solution to $h^+(x) = h^-(x)$ where
@@
 \end{align*}
-and since non of these functions are constant, monotonicity of $h^+(x)$ and $h^-(x)$ implies that they must meet at some $x\in \mathbb R$. \QEDA
+and since non of these functions are constant, monotonicity of $h^+(x)$ and $h^-(x)$ implies that they must meet at a single point in $\mathbb R$. \QEDA
+
+\section{Acknowledgments}
+The work of A. Kipnis is partially supported by NSF Center for Science of Information (CSoI) under grant CCF-0939370 and NSF-BSF under grant 1609695.
 

### 2017-09-26 Writeups/onebit_distributed.tex
Add files via upload

%\documentclass[letterpaper]{IEEEtran}
\documentclass[letterpaper, conference]{IEEEtran}      % Use this line for a4 paper
%\IEEEoverridecommandlockouts                              %

%\usepackage{mathcomSTEP}

%\overrideIEEEmargins 
%\IEEEoverridecommandlockouts                              % This command is only needed if 
% you want to use the \thanks command

%\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\onecolumn

\usepackage{mathptmx} 
\usepackage{times} 
\usepackage{amsmath} 
\usepackage{amsbsy} 
\usepackage{amssymb}
%\usepackage{newtxtext, newtxmath}
\usepackage{mathrsfs}
\usepackage{comment}
\usepackage[export]{adjustbox}
\usepackage{tikz}
\usetikzlibrary{external,positioning,decorations.pathreplacing,shapes,arrows,patterns}

%\tikzexternalize[mode=list and make]
\usepackage{algorithmicx}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{pstool}
\usepackage[latin1]{inputenc}
\usetikzlibrary{arrows,shapes}
\usepackage{xifthen}
\usepackage{epic}
\usepackage{caption}
\usepackage{epstopdf}

\newtheorem{thm}{\bf{Theorem}}
\newtheorem{cor}[thm]{\bf {Corollary}}
\newtheorem{lem}[thm]{\bf {Lemma}}
\newtheorem{prop}[thm]{\bf {Proposition}}
\newtheorem{example}{\bf {Example}}
\newtheorem{definition}{\bf {Definition}}
\newtheorem{rem}{\bf {Remark}}

\newcommand{\mmse}{\mathsf{mmse}}
\newcommand{\supp}{\mathrm{supp} }
\renewcommand\vec[1]{\ensuremath\boldsymbol{#1}}
\newenvironment{proof}{\paragraph*{Proof}}{\hfill$\square$ \newline}
\newcommand{\sgn}{\mathrm{sgn} }
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand*{\QEDA}{\hfill\ensuremath{\square}}

\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
\tikzstyle{sint}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.8cm,thick ]
\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=1cm,thick ]
\tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]

\title{\LARGE \bf Mean Estimation from Single-bit Measurements}
%
%\author{
%\IEEEauthorblockN{Alon Kipnis}
%\IEEEauthorblockA{Department of Electrical Engineering \\
%Stanford University\\
%Stanford, CA\\}
%\and
%\IEEEauthorblockN{John C. Duchi}
%\IEEEauthorblockA{Department of Statistics \\
%and Department of Electrical Engineering \\
%Stanford University\\
%Stanford, CA\\}
%\and
%\IEEEauthorblockN{Andrea J. Goldsmith}
%\IEEEauthorblockA{Department of Electrical Engineering \\
%Stanford University\\
%Stanford, CA\\}
%}

\begin{document}
\graphicspath{{../Figures/}}
\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\section{Distributed Estimation \label{sec:distributed}}

In this setting each observer must transmit a single bit to the estimator and it cannot observe the messages obtained from other observers. As a result, each encoder can be seen as a binary detector whose output depends only on its private sample from the distribution. If we assume that each encoder is deterministic, then it is fully characterized by its \emph{detection region}, which is the subset of the real line on which the sample leads the encoder to output one. \\

The design of the distributed encoding scheme is closely related to that of a multiple description scalar quantizer \cite{vaishampayan1993design}, since each encoder applies a scalar mapping. \\

In this section we consider two possible forms of this detection region. In the first one, each detection region is half of the line, where the halving points varies among the different encoders. In the second setting the detection regions are chosen to minimize the correlation between the various samples.

\subsection{Lower Bound from Remote Multiterminal Source Coding}

The remote multi-terminal lossy source coding problem (a.k.a the CEO problem) \cite{berger1996ceo}, $n$ encoders (agents), each has access to a corrupted version of a source signal, transmit at rates $R_1,\ldots,R_n$ to a central estimation unit. The distributed estimation scheme corresponds to a single round of communication in the CEO setting, where the $i$th agent observes 
\begin{equation}
\label{eq:Gaussian_channel}
X_i = \theta + Z_i,
\end{equation}
and has $R_i=1$ bits to transmit this observation. Note, however, that in the CEO setting each encoder observes multiple number, say $k$, of independent samples $\theta \sim \pi(\theta)$ through the channel \eqref{eq:Gaussian_channel}, and not just one sample as in our setting. In general, in the CEO setting each encoder is allowed $kR_i$ bits to represent its $k$ samples. One possible strategy of the encoder is to send $k$ single bit messages, each of which is only a function of its $k$th observation.  
%the minimal MSE distortion of the CEO provides a lower bound for the MSE in the distributed encoding scheme. 
As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise of variance $\sigma^2$ provides a lower bound on the MSE distortion in estimating $\theta$. Moreover, the difference between this lower bound and the actual MSE in our setting would indicate the importance of coding over blocks consisting of multiple independent realizations of  in our joint estimation and communication problem. \par
%Note that when multiple realization of $\theta$ are involved, the prior distribution $P_\theta$ plays a significant role in the overall MSE, whereas in our case we expect the final distortion to be independent of the actual prior distribution as in the two schemes in the sequential case. \\
A closed-form expression for CEO under quadratic distortion is known only for the case where the source sequence is taken from a Gaussian i.i.d distribution \cite{prabhakaran2004rate}. By using the characterization of the minimal CEO distortion as the number of terminals goes to infinity, we conclude the following result:
\begin{prop} \label{prop:ceo_lower_bound}
Assume that $\pi(\theta)$ is the normal distribution. Then any estimator $\widehat{\theta}_n$ of $\theta$ in the distributed setting satisfies
\[
 n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3n} + o(1/n).
\]
\end{prop}
\begin{proof}
We consider the expression \cite[Eq. 10]{chen2004upper} that provides the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots R_L$:
\begin{equation} \label{eq:ceo_optimal_sumrate1}
R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
\end{equation}
Assuming $R_\Sigma = n$ and $L=n$ we get
\begin{equation} \label{eq:ceo_optimal_sumrate2}
n = \frac{1}{2} \log \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
\end{equation}
The value of $D^\star$ that satisfies the equation above describes the MSE in the quadratic Gaussian CEO setting under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders. Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting. By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$ we conclude that 
\[
D^\star = \frac{ \frac{4\sigma^2}{3} }{n + \frac{4 \sigma^2}{3 \sigma_\theta^2} } + O(e^{-n}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
\]
\end{proof}
Note that although the expression \eqref{eq:ceo_optimal_sumrate1} in the proof above assumes an optimal allocation of $n$ bits among the encoders, rather than a single bit to each one. Nevertheless, the same expression is obtained by considering an upper bound to the CEO distortion derived in \cite[Prop. 5.2]{KipnisRini2017}, in which $R_1=\ldots,R_n = 1$. %\[
%D_{CEO} / \sigma_\theta^2 \leq \left( 1 + \sum_{i=1}^n \frac{\sigma_\theta^2}{\sigma^2} \frac{1 - 2^{-2R_i}} {1+ \frac{\sigma_\theta^2}{\sigma^2}  2^{-2 R_i}  } \right)^{-1}
%\]
%where $\sigma_\theta^2$ is the variance of the distribution $\pi(\theta)$. Using $R_1=\ldots=R_n=1$ we get
%\[
%D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + o(n^{-1}). 
%\]

The bound provided by the CEO in Prop.~\ref{prop:ceo_lower_bound} implies that the relative efficiency in the distributed scheme is at most $4/3$. Since this number is smaller than the relative efficiency of the adaptive scheme, this proposition does not provide new information on the relative efficiency. It does, however, provides the intuition that the limiting factor in estimating $\theta$ is the strict bit-constraint and or the lack of concentration of probability distributions over blocks, rather than distributed estimation. \\

%Comnet on appearance of $\sigma_\theta^2$ as a second order term.

\subsection{Estimation from Threshold Detection}
In this setting we assume that the one-bit message reported by the $i$th encoder is given by 
\[
M_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
-1 & X_i > t_i,
\end{cases}  
\]
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th detector.  In order to characterize the asymptotic behavior of estimation in from these sequence of messages, we consider the \emph{density} of $n$ threshold values defined as:
\[
\lambda_n([a,b]) = \frac{1}{n} \left| \mathcal T \cap [a,b] \right|.
\]
We assume that $\lambda_n$ converges (weakly) to a probability measure $\lambda(t)$ on $\mathbb R$. We first prove a lower bound for estimation in this setting.
\begin{thm} \label{thm:LAN}
For any estimator $\widehat{\theta}_n$ of $\theta_0$ which is a function of $M^n$ we have
\[
\liminf_{c\rightarrow \infty}\, \liminf_{n\rightarrow \infty} \sup_{\tau\,:\,| \tau - \theta| \leq \frac{c}{\sqrt{n}} }  n \mathbb E \left(\widehat{\theta}_n - \tau \right)^2 \geq 1/K(\theta),
\]
where 
\[
K(\theta) \triangleq  \frac{1}{\sigma^2}\int \frac{ \phi^2\left( \frac{t - \theta }{\sigma} \right)}{ \Phi\left(\frac{t- \theta}{\sigma}\right) \left(1-\Phi\left( \frac{t-\theta}{\sigma} \right) \right)} \lambda(dt).
\]
\end{thm}

\begin{proof}
We will prove that the distribution of $M^n$ defines a local asymptotic normal (LAN) family of probability distributions with \emph{precision} parameter $K(\theta)$. The statement in the theorem then follows from the local asymptotic minimax theorem of LAN families \cite{van2000asymptotic}. \\

The likelihood function of $\theta$ with respect to $M^n$ is given by
\[
P_\theta(M^n) =  \prod_{i=1}^n  \Phi \left( M_i \frac{t_i - \theta}{\sigma} \right). 
\]
Consider the log-likelihood ratio under a sequence of local alternatives $\theta' = \theta + h/\sqrt{n}$ for some $h\in \mathbb R$:
\begin{align}
\log \frac{ P_{\theta + \frac{h}{\sqrt{n}}}(M^n)} { P_\theta (M^n) }& =  \sum_{i=1}^n \log \left(  \Phi \left( \frac{M_i}{\sigma} (t_i - \theta - h/\sqrt{n} ) \right)\right)  - \sum_{i=1}^n \log \left( \Phi \left( M_i \frac{t_i - \theta}{\sigma} \right) \right). \label{eq:LAN_proof1}
\end{align}
Using the Taylor expansion of $\log \Phi(x)$, \eqref{eq:LAN_proof1} can be written as
\[
- h \sum_{i=1}^n  \frac{M_i}{\sqrt{n} \sigma }  \frac{ \phi \left(M_i\frac{t_i-\theta}{\sigma} \right)} {\Phi \left( M_i \frac{t_i-\theta}{\sigma} \right) }  - \frac{h^2}{2 \sigma^2 n} \sum_{i=1}^n   \left( \frac{\phi' \left(M_i \frac{t_i-\theta}{\sigma} \right) }{\Phi\left(M_i \frac{t_i-\theta}{\sigma}\right) }- \frac{ \phi^2\left(M_i \frac{t_i-\theta}{\sigma} \right)}{\Phi^2\left(M_i \frac{t_i-\theta}{\sigma} \right)}   \right) + o(1)
\] 
\end{proof}
The proof is completed by proving the following two lemmas:
\begin{lem} \label{lem:LAN1}
For $i=1,\ldots,n$ denote 
\[
U_i = -M_i \frac{ \phi \left( M_i \frac{t_i - \theta}{\sigma} \right)}{ \sigma \Phi \left( M_i \frac{t_i - \theta}{\sigma}\right) }. 
\]
Then 
\[
\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0, K(\theta) \right). 
\]
\end{lem}
\begin{lem} \label{lem:LAN2}
For $i=1,\ldots,n$ denote
\[
V_i = \frac{1}{\sigma^2} \left[ \frac{\phi' \left(M_i \frac{t_i-\theta}{\sigma} \right) }{\Phi\left(M_i \frac{t_i-\theta}{\sigma}\right) }- \frac{ \phi^2\left(M_i \frac{t_i-\theta}{\sigma} \right)}{\Phi^2\left(M_i \frac{t_i-\theta}{\sigma} \right)} \right] .
\]
Then 
\[
\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} K(\theta). 
\]
\end{lem}

\subsubsection*{Proof of Lemma~\ref{lem:LAN1}} 
We have that $\mathbb E  U_i= 0$. In addition,
\[
\mathbb E U_i^2 = \frac{ \phi^2 \left( \frac{t_i-\theta}{\sigma} \right) } { \Phi \left( \frac{t_i-\theta}{\sigma} \right) \left(1- \Phi \left( \frac{t_i-\theta}{\sigma} \right) \right)},
\]
and therefore
\[
\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 \rightarrow K(\theta).
\]

We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition: for any $\delta>0$ we have that 
\[
\mathbb E \left| U_i \right|^{2+\delta} = \phi^{2+\delta} \left(\frac{t_i-\theta} {\sigma } \right)   \left( \frac{1}{\Phi^{2+\delta} \left(\frac{t_i-\theta}{\sigma }\right)} + \frac{1}{1-\Phi^{2+\delta} \left(\frac{t_i-\theta}{\sigma }\right)} \right),
\]
and
\begin{equation}
\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} }{ \left( \sqrt{\sum_{i=1}^n \mathbb E U_i^2 } \right)^{2+\delta}} = 
\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E U_i^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right) \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
\label{eq:Lyaponov}
\end{equation}
As $n$ goes to infinity, we have
\[
\frac{1}{n}\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta}  \rightarrow \int \phi^{2+\delta} \left(\frac{t-\theta}{\sigma }\right) \left( \frac{1}{\Phi^{2+\delta}\left(\frac{t-\theta}{\sigma }\right)} + \frac{1}{1-\Phi^{2+\delta} \left(\frac{t-\theta}{\sigma }\right)} \right) \lambda(dt),
\]
so the numerator in \eqref{eq:Lyaponov} goes to zero. Since the denumerator in \eqref{eq:Lyaponov} goes to $(K(\theta))^{1+\delta})$, the entire expression goes to zero and hence Lyaponov's condition is satisfied. From Lyaponov's central limit theorem we conclude that 
\[
\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0,K(\theta) \right). 
\]
\QEDA

\subsubsection*{Proof of Lemma~\ref{lem:LAN2}}

Since $\phi'(x) = -x \phi(x)$, we have that
\[
\mathbb E V_i =  \frac{\phi^2 \left(\frac{ t_i-\theta}{\sigma} \right) } { \Phi \left(\frac{ t_i-\theta}{\sigma} \right)  \left(1-\Phi \left(\frac{ t_i-\theta}{\sigma} \right)  \right)},
\]
and thus
\[
\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =  \frac{1}{n} \sum_{i=1}^n  \frac{\phi^2\left( \frac{t_i-\theta}{\sigma} \right)} {\sigma^2 \Phi \left( \frac{t_i - \theta}{\sigma} \right)\left(1-\Phi \left( \frac{t_i - \theta}{\sigma} \right) \right)} \rightarrow K(\theta).  
\]
It follows from Kolmogorov's law of large numbers (e.g. \cite[Thm. 10.2.3]{sen1994large}) that
\[
\frac{1}{n} \sum_{i=1}^n \mathbb E V_i \overset{a.s.}{\rightarrow} K(\theta). 
\]
\QEDA

Next, we show that the maximum likelihood estimator of $\theta$ given $M^n$ attains the minmax local asymptotic lower bound of Thm.~\ref{thm:LAN}. The log-likelihood function of $\theta$ is given by
\[
l(M^n  |\theta ) =  \sum_{i=1}^n \log\left[ \Phi \left( M_i \frac{t_i - \theta}{\sigma} \right) \right]
\]
Since $\Phi(x)$ is a log concave function, the log-likelihood function has a unique maximizer $\theta_n$, and we use this maximizer as our $n$th estimate of $\theta$. The asymptotic distribution of $\theta_n$ is given by the following theorem:
\begin{thm} \label{thm:dist_thresholds}
Let $\theta_n$ be the maximizer of $l(M^n|\theta)$. Then 
\[
\sqrt{n}(\theta_n - \theta) \overset{D}{\rightarrow} \mathcal N\left(0,1/K(\theta) \right).
\]
\end{thm}

\begin{proof}
Since all the derivatives of $l(M^n|\theta)$ with respect to $\theta$ exist, we can expand $l'(M^n|\theta_n) = l'(\theta_n)$ about $\theta$ as follows:
\[
l'(\theta_n) = l'(\theta) + \left( \theta_n - \theta \right) l''(\theta) + \frac{1}{2} \left( \theta_n - \theta\right)^2 l'''(\theta_n^*),
\]
where $\theta_n^*$ lies between $\theta$ and $\theta_n$. Since $\theta_n$ is the root of $l'(\theta)$, we have
\begin{equation}
\sqrt{n}(\theta_n - \theta) = \frac{(1/\sqrt{n}) l'(\theta)}{ -(1/n)l''(\theta) - (1/2n)(\theta_n - \theta)l'''(\theta_n^*)}.
\label{eq:ML_expansion}
\end{equation}
%(remember that $l'(\theta)$ and $l''(\theta)$ are function of $M^n$.)
Denote
\[
l_i(\theta) = \log( \mathbb P(M_i | \theta) ) = \log\left( \Phi \left(M_i \frac {t_i -  \theta} {\sigma}\right) \right).
\]
We have
\[
l'_i(\theta) = -M_i \frac{\phi \left(M_i\left( \frac{t_i - \theta}{\sigma} \right) \right)}{\sigma \Phi \left(M_i \left( \frac{t_i - \theta}{\sigma} \right) \right)} = U_i. 
\]
From Lemma~\ref{lem:LAN1} we conclude that the numerator in \eqref{eq:ML_expansion} converges in distribution to $\mathcal N\left(0,K(\theta) \right)$. \\

Next, we consider the term
\[
\frac{1}{n} l''(\theta) = \frac{1}{n} \sum_{i=1}^n l_i''(\theta) = \frac{1}{n} \sum_{i=1}^n \left(\frac{ -\phi' \left(M_i \frac{t_i-\theta}{\sigma } \right) }{\sigma^2 \Phi \left( M_i \frac{t_i-\theta}{\sigma } \right)} + \frac{\phi^2\left(M_i \frac{t-\theta}{\sigma } \right)} {\sigma^2 \Phi^2 \left(M_i \frac{t_i-\theta}{\sigma } \right)}  \right).
\]
We see that $l_i''(\theta) = -V_i$ in Lemma~\ref{lem:LAN2}, and therefore
\[
-\frac{1}{n} l''(\theta) \rightarrow K(\theta). 
\]
Finally, since the third derivative of $l(\theta)$ is bounded in $\theta$, the dominated convergence theorem implies that the last term in \eqref{eq:ML_expansion} goes to zero as $n$ goes to infinity.
\end{proof}

Theorem~\ref{thm:dist_thresholds} shows that the maximum likelihood estimator of $\theta$ given the $n$ single-bit messages is asymptotically normal and attains the local asymptotic minimax variance $1/K(\theta)$. Since the thresholds density integrates to $1$ and from the bound on $K(\theta)$ obtained in the proof of Lemma~\ref{lem:bound_intervals}, it follows that
\[
K(\theta) \leq  \sup_{t\in \mathbb R}  \frac{1}{\sigma^2} \frac{\phi^2\left( \frac{t-\theta}{\sigma} \right)} {\Phi \left( \frac{t - \theta}{\sigma} \right)\left(1-\Phi \left(\frac{ t - \theta}{\sigma }\right) \right) }  \int  \lambda(dt)  \leq \frac{2}{\pi \sigma^2}.
\]
This upper bound implies that the relative efficiency of any distributed estimator is at least $\pi/2$, a fact that agrees with our in the adaptive estimation setting. Unfortunately, this upper bound on $K(\theta)$ is attained whenever the density $\lambda$ is the mass distribution at $\theta$, which is unknown. Therefore, we turn to choose the density $\lambda$ such that the average MSE over the distribution $\pi(\theta)$, namely, such that 
\begin{equation} \label{eq:to_minimize}
\mathbb E \frac{1}{K(\theta)} = \int \frac{ \pi(d\theta) }{ \int \frac{ \phi^2 \left(\frac{t-\theta}{\sigma}\right)  } { \sigma^2 \Phi \left(\frac{t-\theta}{\sigma}\right) \left(1 - \Phi \left(\frac{t-\theta}{\sigma}\right) \right)} \lambda(dt) },
\end{equation}
is minimal.

\subsubsection{An upper bound} 
Since the function $x\rightarrow 1/x$ is convex for $x>0$, Jensen's inequality applied to the denominator in \eqref{eq:to_minimize} leads to
\[
\mathbb E \frac{1}{K(\theta)} \leq  \sigma^2 \int \int  \frac{ { \Phi \left(\frac{t-\theta}{\sigma}\right) \left(1 - \Phi \left(\frac{t-\theta}{\sigma}\right) \right)}  }{  \phi^2 \left(\frac{t-\theta}{\sigma}\right) }  \pi(d\theta) \lambda(dt). 
\]

\begin{example}
Taking $\lambda$ to be the mass distribution at $\theta_0 = \mathbb E[\theta]$ in the expression above implies to following upper bound for the average distortion: 
\begin{equation} \label{eq:dist_upper bound}
\mathbb E \frac{1}{K(\theta)} \leq \sigma^2 \int   \frac{ { \Phi \left(\frac{\theta_0-\theta}{\sigma}\right) \left(1 - \Phi \left(\frac{\theta_0-\theta}{\sigma}\right) \right)}  }{  \phi^2 \left(\frac{\theta_0-\theta}{\sigma}\right) }  \pi(d\theta). 
\end{equation}
For example, with a prior $\phi$ standard normal and $\sigma=1$, the above expression is evaluated to $3.8328$. For large $\sigma$ it converges to $\sigma^2 \pi/2$. For small $\sigma$ the expression above can be very large, but, as explained below, in this case the bound is not tight. 
\end{example}

\subsubsection{Optimal thresholds density}
We now consider the exact minimization of \eqref{eq:to_minimize} over asymptotic density $\lambda$ of the threshold values. The expression on the RHS of \eqref{eq:to_minimize} is convex in $\lambda$ (sum of compositions of linear and one over inverse positive), and we minimize it subject to the constraints: $\int \lambda(dt) = 1$ and $\lambda(dt)\geq0$. \\

The finite dimensional approximation of the problem above can be written as
\begin{align}
\mathrm{minimize}\, & f(\lambda) = \sum_{i=1}^k \frac{1}{ \sum_{j=1}^n g_{i,j} \lambda_j }  \label{eq:cvx_problem}\\
\mathrm{subject to:} & \sum_{j=1}^n {\lambda_j} =1   \nonumber 
\\ & \lambda_j \geq 0, \nonumber 
\end{align}
where $\lambda_j = \lambda(t_j)$ and
\[
g_{i,j} = \frac {\phi^2( \frac{t_j - \theta_i}{\sigma}) \phi(\theta_i)} { \sigma^2 \Phi( \frac{t_j - \theta_i}{\sigma} ) \left( 1-\Phi( \frac{t_j - \theta_i}{\sigma}) \right)}.
\]
The solution to \eqref{eq:cvx_problem} is sparse: when $\sigma$ is large, $\lambda^\star$ is the mass distribution at $0$, and the upper bound \eqref{eq:dist_upper bound} is tight. When $\sigma$ is small, a few other non-zero values of $\lambda^\star$ exists. This behavior of $\lambda^\star$ is pleasing since for small $\sigma$ it is too risky to use all threshold detector at a single value.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,/Users/Alon1/LaTex/bibtex/sampling}

\end{document}

### 2017-09-26 Writeups/onebit_distributed_V2.tex
Add files via upload

--- 2017-09-26 Writeups/onebit_adpative_Allerton.tex
@@
 \documentclass[letterpaper, conference]{IEEEtran}      % Use this line for a4 paper
+
+%LatexiDiff ignore tikz:
+% $: latexdiff -c "PICTUREENV=(?:picture|tikzpicture|DIFnomarkup)[\w\d*@]*" old.tex new.tex > diff.tex
+
 %\IEEEoverridecommandlockouts                              %
@@
 % on the last page of the document
+
+\onecolumn
 
@@
 
-\title{\LARGE \bf Mean Estimation from Adaptive Single-bit Measurements}
+\title{\LARGE \bf Mean Estimation from Single-bit Measurements}
 %
-\author{
-\IEEEauthorblockN{Alon Kipnis}
-\IEEEauthorblockA{Department of Electrical Engineering \\
-Stanford University\\
-Stanford, CA\\}
-\and
-\IEEEauthorblockN{John C. Duchi}
-\IEEEauthorblockA{Department of Electrical Engineering \\
-and Department of Statistics \\
-Stanford University\\
-Stanford, CA\\}
-}
+%\author{
+%\IEEEauthorblockN{Alon Kipnis}
+%\IEEEauthorblockA{Department of Electrical Engineering \\
+%Stanford University\\
+%Stanford, CA\\}
+%\and
+%\IEEEauthorblockN{John C. Duchi}
+%\IEEEauthorblockA{Department of Statistics \\
+%and Department of Electrical Engineering \\
+%Stanford University\\
+%Stanford, CA\\}
+%\and
+%\IEEEauthorblockN{Andrea J. Goldsmith}
+%\IEEEauthorblockA{Department of Electrical Engineering \\
+%Stanford University\\
+%Stanford, CA\\}
+%}
 
@@
 \begin{abstract}
-We consider the problem of estimating the mean of a normal distribution under the constraint: that the estimator can access only a single bit per sample from this distribution.
-We study the squared error in this estimation as a function of the number $n$ of samples and single-bit measurements in an adaptive setting.
-We show that if at each stage $n$, this single bit is a function of both the new sample and the previous $n-1$ acquired bits, then no estimator can attain asymptotic squared error smaller than $\pi/(2n)$ times the variance.
-Therefore, we conclude that a strict bit limitation increases the number of samples required for a prescribed accuracy by a factor of at least  $\pi/2$ compared to the unrestricted case.
-In addition, we provide an explicit estimator that attains this asymptotic error, showing that, rather surprisingly, only $\pi/2$ times more samples are required in order to attain performance equivalent to the unrestricted case.
+We consider the problem of estimating the mean of a normal distribution under the constraint that only a single bit per sample from this distribution is available to the estimator.
+We study the mean squared error risk in this estimation as a function of the number of samples, and hence number of bits, from this distribution.
+We consider an adaptive scheme in which each bit is a function of the current sample and the previously observed bits, as well as a fully distributed setting in which each bit is only a function of the current sample.
+For the adaptive scheme, we show that the optimal relative efficiency, compared to the standard mean estimator without bit limitation, is $\pi/2$.
+Namely, the number of samples required to attain the mean to a prescribed accuracy is only $\pi/2$ times larger due to the bit constraint.
+For the distributed scheme we consider the setting where each bit is obtained by comparing the current sample to a prescribed value.
+For this setting, we show that the expected asymptotic efficiency converges to $\pi/2$ provided that the variance of the distribution is high compared to the apriori uncertainty about the mean.
+Our results indicate that, rather surprisingly, parametric estimation from the coarsest form of quantization without significant penalty in the number of measurements is possible.
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section{Background}
 \label{sec:Intro}
-
-Processing and estimating information from data collected at multiple physical location may be subject to communication constraints. 
+Processing information on multiple physical locations may impose communication constraints on the amount of information that can be shared among different units of the system. 
 %For example, emerging sensor network technologies in medicine and ``smart cities" use many low-cost sensors to collect large amounts of data and transmit it to remote locations.
 These sensors must operate under severe power restrictions, hence they are limited by their communication bandwidth.
-For example, consider large-scale sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit.
-In this scenario, the ability to estimate a particular parameter from data collected by the sensors is dictated not only by quality of observations and their numbers, but also by the constraint on the communication rates between the sensors.
-The question that we ask is to what extend a parametric estimation task is affected by such communication constraint, and what are the fundamental performance of estimation subject to these restrictions.
+%For example, this constraint occurs in large-scale sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit. 
+In this situation, the ability to estimate a particular parameter is dictated not only by quality of observations but also by the constraint on the communication rate of the sensor, which may be severely restricted due to power, bandwidth, or size of data.
+The question that we ask is to what extent a parametric estimation task is affected by such communication constraints, and what are the fundamental performance of estimation subject to these restrictions.
 \\
 
-In this paper we provide an answer to this question in a particular simple setting: the estimation of the mean $\theta$ of a normal distribution with a known variance $\sigma^2$, under the constraint that given the $n$th sample $X_n$, only a single bit can be communicated to the estimator.
-Specifically, the $n$th encoder observes $X_n$ and the $n-1$ previous single bit messages $M_1,\ldots,M_{n-1}$, and delivers a single bit message $M_n$ to the estimator.
-The estimator provides an estimate $\widehat{\theta}_n$ based on $M^n = (M_1,\ldots,M_n)$.
-
- \item[(iii)] \emph{Distributed} encoding: the output of the $n$th encoder is a single bit that is only a function of $X_n$.
+In this paper we provide a precise answer to this question in a limited setting: the estimation of the mean $\theta$ of a normal distribution with a known variance $\sigma^2$, under the constraint that only a single bit can be communicated to the estimator on each sample from this distribution.
+As it turns out, the ability to share information before communicating it dramatically affects the performance in recovering $\theta$.
+We distinguish in particular among three different settings:
+ \begin{itemize}
+ \item[(i)] \emph{Centralized} encoding: all the $n$ encoders confer and produce a single $n$ bit message. 
+ \item[(ii)] \emph{Adaptive} or \emph{sequential} encoding: the $i$th encoder observes the $i$th sample and the $i-1$ previously encoded observations.
+ \item[(iii)] \emph{Distributed} encoding: the output of the $i$th encoder is only a function of the $i$th observation.
  \end{itemize}
-Clearly, as far as information sharing is concerned, settings (iii) is a more restrictive version of (ii) which is more restrictive than (i).
-We measure the estimation performance by the mean squared error (MSE) risk.
-Since without bit constraint this risk is known to be $\sigma^2/n$, we are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting, defined as the ratio between their MSE to $\sigma^2/n$ as $n$ goes to infinity.
-%\par
-%Maybe explain here why the problem is interesting ? 
-%setting (i), setting (ii) + SDM, setting (iii) + CEO.
-%The turn to 1) main results and 2) other previous works. 
+As far as information sharing is concerned, it is evident that settings (iii) is a more restrictive version of (ii) which is more restrictive than (i).
+We are concerned with the mean squared error (MSE) risk in estimating $\theta$ as the number of observations $n$ goes to infinity.
+In particular, we are interested in the \emph{relative efficiency} of estimators in settings (i)-(iii), defined as the ratio between their MSE to $\sigma^2/n$.
+The latter is the MSE attained by the sample mean, which is the minimal risk estimator when no constraints on the communication are imposed.
+\par
 %
+It is well known that the relative efficiency in setting (i) is $1$ \cite{720540, zhang2013information, zhang1988estimation}, i.e., asymptotically, there is no loss in performance due to the communication constraint in this setting.
+Indeed, under setting (i) the sample mean can be described with an error exponentially decaying in $n$, leading to MSE of $\sigma^2/n + o(n)$.
+In this work we show that a similar result does not hold even in setting (ii): the relative efficiency of any adaptive estimator is at least $\pi/2$.
+Namely, a single bit per sample communication constraint in the adaptive setting incurs a minimal penalty of at least $\pi/2 \approx 1.57$ compared to an unconstrained estimator, or to the optimal estimator in setting (i).
+In addition to this negative statement, we provide an estimator which asymptotically attains this minimal relative efficiency, i.e., we show that this lower bound is tight.
+Moreover, we show that even in the distributed setting (iii), a relative efficiency of $\pi/2$ is possible as long as $\sigma^2$ is large compared to the variance of the prior distribution on $\theta$.
+These results are quite surprising since they show that, even under the coarsest form of quantization, an estimator based on $ \approx 1.59 n$ measurements achieves accuracy in MSE or confidence interval comparable to an estimator that uses $n$ samples with infinite bit-precision.
 \par
-Classical works on statistical estimation under communication constraint in information theory \cite{720540, zhang2013information, zhang1988estimation} implies that the ARE in setting (i) is $1$.
-Namely, asymptotically, there is no loss in performance in this setting due to the communication constraint.
-Indeed, under setting (i) the sample mean can be described by an encoder with an exponentially decaying error, leading to MSE of $\sigma^2/n + o(2^{-n})$.
-In this work we show that a similar result does not hold even in setting (ii): the relative efficiency of any adaptive estimator is at least $\pi/2$.
-Namely, the single-bit per sample constraint incurs a minimal penalty of at least $\approx 1.57$ compared to an unconstrained estimator or to the optimal estimator in setting (i).
-In addition to this negative statement, we provide an estimator that almost surely attains this minimal relative efficiency.
-In other words, we show that the lower bound of $\pi/2$ on the asymptotic relative efficiency is tight, and that it is attained regardless of the particular realization of $\theta$ or the size of the parameter space from which it is taken.
-Clearly, the minimal penalty on the efficiency of $\pi/2$ also holds under setting (iii), although the question whether such efficiency is achievable (or otherwise, what is the minimal efficiency) remains open.
-\\
-
-\subsection{Relate Works}
-The parametric estimation problem we consider is closely related to many works in statistics and information theory.
-Statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation} includes as a special case the problem of estimating a single vector of parameters from multiple data-rate constrained observations.
-These inference problems were studied in the asymptotic limit as the number of observations goes to infinity.
-In this asymptotic setting the unconstrained inference performance is always attained when all samples are taken from the same distribution \cite[Sec.
-III]{720540}.
-Indeed, in an i.i.d setting the \emph{type} of the sample is a sufficient statistics for any estimation task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples.
-For this reason in \cite{han1987hypothesis} and \cite{zhang1988estimation} attention is given to inference problems involving multiple distributions observed at different locations.
-Setting (i) above can be seen as a special case of the above works where the communication is limited to a single-bit per terminal.
-In fact, with a full access to the sample prior to encoding, the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample \cite{gray1998quantization}.
-%On the other hand, setting (iii) arises as the number of terminals grow with $n$ and their communication rates are limited to a single bit.
-
-This last situation is also obtained by the multiterminal source coding setting, a.k.a.
-the CEO problem \cite{berger1996ceo} can be seen as a generalization of our setting (iii), where multiple draws of $\theta$ and rounds of $n$ bit communication is permitted.
-In particular, the minimal CEO distortion with $1$ bit per terminal provides a lower bound on the MSE risk.
-
-In fact, with a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample \cite{gray1998quantization}.
-The sigma-delta modulatior (SDM) \cite{1092194} uses a single bit quantizer with a feedback loop, and therefore falls under setting (ii).
-The SDM with a constant input $\theta$ corrupted by a Gaussian noise was considered in \cite{53738}, where it was shown that the output of the modulator converges to the true constant input.
-Therefore, the SDM provides a consistent estimator for setting (ii).
-The rate of this convergence, however, was not analyzed and cannot be derived directly from the results of \cite{53738}.
-In fact, the results of this paper implies that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-\par
-
 %
-Estimation problem subject to the one-bit quantization constraint were also considered in compressed sensing \cite{boufounos20081,baraniuk2017exponential} and in MIMO detection in wireless communication \cite{singh2009limits}.
-
-The rest of this paper is organized as follows: the main problem and notation are defined in Section~\ref{sec:problem}.
-In Section~\ref{sec:sequential} we present a lower bound on estimation from one-bit samples in the adaptive scheme, as well as an achievable scheme that attains this bound.
-Concluding remarks are given in Section~\ref{sec:conclusions}.
-
-\section{Motivation and Related Works}
-Standard considerations implies that the optimal encoding in setting (i) is reduced to an optimal $n$ bits description of the  sample mean.
-The standard technique to encode an unknown random quantity using $n$ bits is attained by an optimal scalar quantizer.
-However, the design of this quantizer depends on the distribution of its input \cite{gray1998quantization}, which is the goal of the estimation.
-Therefore, although the ARE in this setting is shown to be one \cite[Sec.
-III]{720540}, we see that a non-trivial challenge arise even in this case.
-In setting (ii), the above challenge of optimal quantizer design with imprecise input distribution occurs upon the the arrival of each new sample $X_n$.
-
-%sigma delta modulator
-
-%implies the existence of a consistent estimator in this case
-
-% our result provides a lower bound for the accuracy of a sigma-delta modulator
-
-Setting (ii) and (iii) were considered in 
-\cite{zhang2013information} under the more general assumption of $m$ machines each has access to $n/m$ independent samples.
-The main result of \cite{zhang2013information} are lower bounds on the estimation error as a function of the total number of bits $R$ with which each machine can communicate.
-Our settings corresponds to the case $m=n$ and $R=1$, and our result is a fundamental lower bound and a matching achievable scheme under this simplified setting.
-
- We also note that the counterpart of setting (iii) in the case of hypothesis testing was considered in \cite{52470}.
-
- The optimal design  requires the distribution of the input, which is the goal of estimation and is known appriori.
-
- standard technique to encode an unknown random quantity using $n$ bits is attained by an optimal scalar quantizer,  by designing a scaler quantizer Unlike standard quantization task of encoding an unn
-
-%Note that when multiple realization of $\theta$ are involved, the prior distribution $P_\theta$ plays a significant role in the overall MSE, whereas in our case we expect the final distortion to be independent of the actual prior distribution as in the two schemes in the sequential case.
-\\
-
-\subsection{Intuition from Remote Multiterminal Source Coding}
-A first clue for this rather surprising result can be seen drawing the connection between our parametric estimation problem to the remote multiterminal source coding problem of \cite{berger1996ceo}, also known as the CEO problem.
-The CEO setting considers $n$ encoders, each has access to a corrupted version of a source signal.
-The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator.
-Therefore, assuming that $\theta$ is drawn randomly from a prior $\pi(\theta)$, the distributed estimation setting (iii) corresponds to the CEO setting with $k=1$, where the $i$th agent observes
-\begin{equation}
-\label{eq:Gaussian_channel}
-X_i = \theta + Z_i,
-\end{equation}
-and has $R_i=1$ bits to transmit this observation.
-As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise of variance $\sigma^2$ provides a lower bound on the MSE distortion in estimating $\theta$.
-In fact, the difference between this lower bound and the actual MSE in our setting indicates the importance of coding over blocks consisting of $k$ independent realizations of $\theta$ versus $k=1$ in our setting.
-\par
-A closed-form expression for CEO under quadratic distortion is known only for the case where the sequence to described by the encoders is sampled from a Gaussian distribution \cite{prabhakaran2004rate}.
-By using the characterization of the minimal CEO distortion as the number of terminals goes to infinity, we conclude the following:
-\begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\pi(\theta)$ is the normal distribution. Then any estimator $\widehat{\theta}_n$ of $\theta$ in the distributed setting satisfies
-\[
- n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + o(1).
-\]
-\end{prop}
-
-\begin{proof}
-We consider the expression \cite[Eq. 10]{chen2004upper} that provides the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots R_L$:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-Assuming $R_\Sigma = n$ and $L=n$ we get
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-n = \frac{1}{2} \log \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-The value of $D^\star$ that satisfies the equation above describes the MSE in the quadratic Gaussian CEO setting under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$ we conclude that
-\[
-D^\star = \frac{ \frac{4\sigma^2}{3} }{n + \frac{4 \sigma^2}{3 \sigma_\theta^2} } + O(e^{-n}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-\end{proof}
-We note that although the CEO lower bound was derived by the MSE attainable assuming optimal allocation a total of $n$ bits among the encoders, the same expression is from the upper bound to the CEO derived in \cite[Prop.
-5.2]{KipnisRini2017}, that assumes $R_1=\ldots,R_n = 1$ rather than optimal allocation of $n$ bits among all encoders.
-%\[
-%D_{CEO} / \sigma_\theta^2 \leq \left( 1 + \sum_{i=1}^n \frac{\sigma_\theta^2}{\sigma^2} \frac{1 - 2^{-2R_i}} {1+ \frac{\sigma_\theta^2}{\sigma^2}  2^{-2 R_i}  } \right)^{-1}
-%\]
-%where $\sigma_\theta^2$ is the variance of the distribution $\pi(\theta)$. Using $R_1=\ldots=R_n=1$ we get
-%\[
-%D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + o(n^{-1}). 
-%\]
-
-Statistical inference problems under communication constraints in the nature of our setting were considered in information theory in 
+%One clue for this surprising results is given in a famous problem in information theory denoted as the CEO problem, first presented by Berger et.
+al.
+in \cite{berger1996ceo}.
+In this problem, a firms CEO is required to estimate a signal  from information sent to it by multiple agents, where the $i$th agents is given a noisy observation of this signal and has a limited number of bits, say $R_i$, to describe its observation to the CEO.
+
+\subsection*{Related Works}
+%\subsubsection*{Statistical inference under communication constraints}
+Statistical inference problems under communication constraints were considered in information theory in 
 \cite{han1987hypothesis, zhang1988estimation, 720540}.
@@
 \par
-
-%Why it is surprising that the estimator is independent of $\theta$, $\Theta$ or $\pi(\theta)$.
-
-\subsection{Related Works}
-\subsubsection*{Statistical inference under communication constraints}
-The problem of statistical inference under communication constraint has a long and rich history in statistics and information theory.
-Statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation} includes as a special case the problem of estimating a single vector of parameters from multiple data-rate constrained observations.
-These inference problems were studied in the asymptotic limit as the number of observations goes to infinity.
-The main question asked there is the difference between inference with communication constraint and the unconstrained vanilla statistical estimation setting.
-In this asymptotic setting the unconstrained inference performance is always attained when all samples are taken from the same distribution \cite[Sec.
-III]{720540}.
-Indeed, in an i.i.d setting the \emph{type} of the sample is a sufficient statistics for any estimation task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples.
-For this reason in \cite{han1987hypothesis} and \cite{zhang1988estimation} attention is given to inference problems involving multiple distributions observed at different locations.
-Setting (i) above can be seen as a special case of \cite{han1987hypothesis, zhang1988estimation, 720540} where the communication is limited to a single-bit per terminal.
+%The difference between this setting and ours is that in ours the parameter of interest is not an information source.
+By assuming a prior distribution on this parameter, the CEO provides a lower bound on the estimation error in the fully distributed setting (iii).
+This lower bound can be attained if we were to consider the average error in multiple independent realizations of our problem rather than a single realization as we do here.
+\\
+%
+%While our focus in this paper is on setting (ii), we note that unlike the above works, we are also interested in the optimal estimation performance for a finite number of observations and not only in their asymptotic behavior.
+%\subsubsection*{Relation to channel coding}
+More related to our setting is the work \cite{zhang2013information} that considers the minimax MSE risk in estimating a vector of parameters from $m$ machines, where each machine has access to $n/m$ samples a limited number of bits to describe these samples.
+The main results of this work are lower bounds on the estimation error as a function of the total number of bits can be sent by each machine.
+In the terminology of \cite{zhang2013information}, our settings (ii) and (iii) fall under the category of \emph{interactive}, and  \emph{independent} communication protocols, respectively.
+%In both cases we use $m=n$ (single sample per machine) and communication constraint of a single bit per machine.
+However, unlike in \cite{zhang2013information}, we focus on achievable schemes and tight bounds in $n$ for the asymptotic MSE risk, rather than its scaling rate. \\
+
+The rest of this paper is organized as follows: the main problem is defined in Section~\ref{sec:problem}.
+Our main results are presented and discussed in Sections~ \ref{sec:sequential} and \ref{sec:distributed}.
+Concluding remarks are given in Section~\ref{sec:conclusions}.
+
+%We also note that the counterpart of setting (iii) in the case of hypothesis testing was considered in \cite{52470}.
 
@@
 
-\subsubsection*{Relation to channel coding}
-The problem we consider is the estimation of the parameter $\theta$ by observing 
-\begin{equation}
-\label{eq:channel}
-X_i = \theta + Z_i, \quad i=1,\ldots,n,
-\end{equation}
-where the $Z_i$s are independent, centered normal with variance $\sigma^2$.
-The problem of estimating $\theta$ from the $X_i$s can be seen as the attempt to transmit a real number $\theta$ over an additive white Gaussian noise (AWGN) channel.
-In particular, setting (ii) can be seen as the feedback version of this transmission, which is closely related to \cite{horstein1963sequential, 1053879}.
-However, in our setting $\theta$ is either fixed or drawn once from a prior distribution, so the communication in \eqref{eq:channel} is limited to a repetition code.
-Moreover, in setting (ii) we have the additional constraint that the message is a causal function of the previous messages, where in case (iii) it is completely memoryless.
-Works in information theory which consider such setting includes AWGN channel with 1-bit ADC at the receiver \cite{DBLP:journals/corr/VarastehSG16}.
-\par
-
-\subsubsection*{Relation to source coding}
-With a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample.
-Setting (ii) includes as a special case the sigma-delta modulation (SDM) analog-to-digital conversion scheme with a constant input $\theta$ corrupted by Gaussian noise $Z_i$, as was considered in \cite{53738}.
-While it was shown there that the output of the modulator converges to the true constant input, the rate of this convergence was not analyzed and cannot be derived directly from the results of \cite{53738}.
-As a corollary from the results in this paper we conclude that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-Finally, the remote multiterminal source coding setting of \cite{berger1996ceo} corresponds to the case of $n$ rate-constrained encoders, each observing a noisy version of an information source.
-The difference between this setting and ours is that in ours the parameter of interest is not an information source.
-By assuming a prior distribution on this parameter, the CEO provides a lower bound on the estimation error in the fully distributed setting (iii).
-This lower bound can be attained if we were to consider the average error in multiple independent realizations of our problem rather than a single realization as we do here.
-\\
-
-%As opposed to the aforementioned line of works, we focus on estimation of samples taken from a single distribution in the finite blocklength performance.
-We are interested in particular in addition restrictions on the communication and information sharing between the encoders.
-For example, our main focus is the case where the observer must communicate a single bit upon drawing from the distribution.
-This is in contrast to the asymptotic setting where the observer can encode the outcome of $n$ draws at once using a single $n$ bit message.
-Alternately, such setting can be seen as having $n$ different observers, each is capable of observing a single realization and transmit a single bit.
-
-%{\color{red} The Van Trees inequality was extended to the estimation of multiple parameters in \cite{bobrovsky1987}. It is closely related with the }
-
-\begin{comment}
-\subsection{Sigma-Delta Encoding}
-
-and covariance function \cite[Eq. 25]{53738}
-\[
-R(k) = \mathbb E M_{n+k} M_n = \theta^2 + O \left( \frac{1}{\sigma \sqrt{ k} } \right). 
-\]
-{\color{red} This is not enough to deduce convergence. Need to go over the paper and check if rate of convergence can be deduced. Also do simulations BEFORE that. \\
-
-What is the error in estimating the mean of stationary ergodic process ? 
-}
-Since the SDM is a special case of the sequential scheme, we conclude that the MSE of any SDM with a noisy DC signal is bounded from below by $n^{-1} \sigma^2 \pi/2 $.
-\end{comment}
-
-The rest of this paper is organized as follows: the main problem and notation are defined in Section~\ref{sec:problem}.
-Our main results are presented and discussed in Section~\ref{sec:sequential}.
-Concluding remarks are given in Section~\ref{sec:conclusions}.
-
-%Even with such arguably simple setting, we will see that the performance limit in the estimating task based on single bit observations provides an interesting setting for discussion that bridges classical works in statistics, coding theory, information theory and optimization.
-
 \section{Problem Formulation \label{sec:problem}}
+
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}[node distance=2cm,auto,>=latex]
+
+\node[node distance = 1.5cm] at (0,0) (source2) {$X_1,\ldots,X_n$};
+\node[int1, right of = source2, node distance = 2cm] (enc2) {Enc};  
+\draw[->,line width = 2pt] (source2) -- (enc2);
+
+\node[above of = source2, node distance = 1cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
+
+\node[int1, right of = enc2, node distance = 4cm ] (est) {Est};
+
+\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M \in \left\{-1,1\right\}^n$} (est);
+
+\node[right of = est, node distance = 1.5cm] (dest) {$\widehat{\theta}_n$};
+%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
+%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
+%\draw[->,line width=2pt] (dec) -- (dest);
+\draw[->, line width=2pt] (est) -- (dest);
+\end{tikzpicture}
+\end{center}
+\caption{\label{fig:centralized} Centralized encoding using one bit per sample on average.}
+\end{figure}
 
@@
 
-\node[above of = source, node distance = 1cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
 \node[below of = source2, node distance = 0.5cm] {$\vdots$};
+\node[above of = source3, node distance = 0.6cm] {$\vdots$};
+\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
 
@@
 
-Let $X_i$, $i=1,\ldots,n$, be $n$ independent samples from the normal distribution $\mathcal N(\theta,\sigma^2)$ with mean $\theta$ and variance $\sigma^2$.
-We assume that the mean $\theta$ is drawn once from a prior distribution $\pi(\theta)$ on the parameter space $\Theta$, which is a closed interval of the real line.
-We moreover assume that $\pi(\theta)$ is absolutely continuous with respect to the Lebesgue measure with density $\pi(d\theta)$.
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}[node distance=2cm,auto,>=latex]
+  \node at (0,0) (source) {$X_1$} ;
+  \node[int1, right of = source, node distance = 1.5cm] (enc1) {Enc 1};  
+\draw[->,line width = 2pt] (source) -- (enc1);
+
+ \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
+\node[int1, right of = source2, node distance = 1.5cm] (enc2) {Enc 2};  
+\draw[->,line width = 2pt] (source2) -- (enc2);
+
+\node[below of = source2, node distance = 2.5cm] (source3) {$X_n$};
+\node[int1, right of = source3, node distance = 1.5cm] (enc3) {Enc n};  
+\draw[->,line width = 2pt] (source3) -- (enc3);
+
+\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
+\node[below of = source2, node distance = 0.5cm] {$\vdots$};
+\node[above of = source3, node distance = 0.6cm] {$\vdots$};
+
+\node[int1, right of = enc2, node distance = 4cm ] (est) {Est};
+\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -2cm] (mes1) {$M_1 \in \left\{-1,1\right\}$} (est);
+
+\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M_2 \in \left\{-1,1\right\}$} (est);
+
+\draw[->,line width = 2pt] (enc3) -| (est);
+
+\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -2cm]  {$M_n \in \left\{-1,1\right\}$} (est);
+
+\node[right of = est, node distance = 1.5cm] (dest) {$\widehat{\theta}_n$};
+%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
+%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
+%\draw[->,line width=2pt] (dec) -- (dest);
+\draw[->, line width=2pt] (est) -- (dest);
+\end{tikzpicture}
+\end{center}
+\caption{\label{fig:distributed} Distributed single-bit encoding: the single-bit message produced by each encoder is only a function of its private sample $X_i$.}
+\end{figure}
+
+Let $X_i$, $i=1,\ldots,n$, be $n$ independent samples from the normal distribution $P(X) = \mathcal N(\theta,\sigma^2)$ with mean $\theta$ and variance $\sigma^2$.
+We also assume that the mean $\theta$ is drawn once from a prior distribution $\pi(\theta)$ on the parameter space $\Theta$, which is a closed interval of the real line.
+We moreover assume that $\pi(\theta)$ is absolutely continuous with respect to the Lebesgue measure with a bounded second moment.
+We denote the variance of $\theta$ with respect to $\pi(\theta)$ by $\sigma_\theta^2$.
 The problem we consider is the estimation of the parameter $\theta$ under the following constraints on the communication between the samples $X_1,\ldots,X_n$ and a centralized estimator:
 \begin{itemize}
-\item[(i)] The estimator at time $n$ is only a function of the $n$ messages $M^n = \left(M_1,\ldots,M_n \right)$.
-\item[(ii)] For each $i=1,\ldots,n$, the $i$th message $M_i$ is a function of the sample $X_i$ and the $i-1$ previous messages $M^{i-1}$.
-\item[(iii)] The $i$th message $M_i$ takes only two possible values, say $1$ and $-1$. 
+\item[(i)] The estimator at time $n$ is only a function of the $n$ messages $M^n = \left(M_1,\ldots,M_n \right)$ (Fig.~\ref{fig:centralized}).
+\item[(ii)] For each $i=1,\ldots,n$, the $i$th message $M_i$ is a function of the sample $X_i$ and the $i-1$ previous messages $M^{i-1}$ (Fig.~\ref{fig:sequential}).
+\item[(iii)] The $i$th message $M_i$ takes only two possible values, say $1$ and $-1$ (Fig.~\ref{fig:distributed}).
 \end{itemize}
-In other words,  the $n$ messages $M^n$ are the only information on the sample $X^n = \left(X_1,\ldots,X_n\right)$ available to the estimator.
-The $i$th message is defined by a function from the real line to $\{-1,1\}$, measurable with respect to the sigma algebra generated by $M^{i-1}$ and $X_i$.
+In other words, the only information on the sample $X^n \left(X_1,\ldots,X_n\right)$ available to the estimator is the messages $M^n$.
+In addition, each message $M_i$ is a function from the real line into the set $\{-1,1\}$ which is measurable with respect to the sigma algebra generated by $M^{i-1}$ and $X_i$.
 The estimator, upon observing $M^n$, produces an estimate $\widehat{\theta}_n(M^n)$ of $\theta$.
@@
 
-In this work we are concerned with the mean squared error (MSE) risk:
+The performance of this estimation is measured by the mean squared error (MSE) risk function:
 \begin{equation}
 \label{eq:error_def}
-\epsilon_n \triangleq \mathbb E\left(\widehat{\theta}_n - \theta \right)^2,
+R_n \triangleq \mathbb E\left(\widehat{\theta}_n - \theta \right)^2,
 \end{equation}
@@
 %\begin{equation}
-%E_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left(\widehat{\theta}_n - \theta \right)^2 | \theta \right],
+%R_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left(\widehat{\theta}_n - \theta \right)^2 | \theta \right],
 %\end{equation}
-%can be obtained from $\epsilon_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}.
+%can be obtained from $R_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}.
 
 The main problem we consider is the minimal value that can be attain in \eqref{eq:error_def} as a function of $n$.
-Note that this minimization is the combination of the following two procedures: (1) selecting the $i$th message $M_i$ based on past messages and current observation $X_i$, and (2) estimating $\theta$ given messages $M^n$.
+Note that this minimization is the combination of the following two processes: (1) selecting the $i$th message $M_i$ based on past messages and current observation $X_i$, and (2) estimating $\theta$ given messages $M^n$.
 We are interested in particular in the asymptotic relative efficiency of estimators $\widehat{\theta}_n$ for $\theta$ compared to the sample mean $\bar{X}_n = \frac{1}{n} \sum_{i=1}^n X_i$.
@@
 \begin{equation}
-\rho \triangleq \lim_{n \rightarrow \infty} \frac{n}{\sigma^2}  \epsilon_n. 
+ \lim_{n \rightarrow \infty} \frac{n}{\sigma^2}  R_n. 
 \label{eq:relative_efficiency}
 \end{equation}
-{\color{red}
-Since the conditional expectation of $\theta$ with respect to $\bar{X}_n$ (and not $\bar{X}_n$) minimizes \eqref{eq:error_def}, we need to justify the fact that we use the sample mean as the reference estimator.
-}
+%{\color{red} Since the conditional expectation of $\theta$ with respect to $\bar{X}_n$ (and not $\bar{X}_n$) minimizes \eqref{eq:error_def}, we need to justify the fact that we use the sample mean as the reference estimator.}
 
@@
 
-\section{Results \label{sec:sequential}}
+\section{Adaptive Estimation \label{sec:sequential}}
+
 The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the asymptotic relative efficiency of and adaptive estimator cannot get below $\pi/2$.
-Next, we provide a particular adaptive estimation scheme and show in Theorem~\ref{thm:sgd} that its efficiency is $\pi/2$.
+Next, we provide a particular adaptive estimation scheme and show in Theorem~\ref{thm:sgd} that asymptotically attains this efficiency with equality.
 Finally, in Theorem~\ref{thm:opt_one_step} we provide an adaptive estimation scheme that is optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen.
-While it is not clear whether the efficiency of this last scheme is $\pi/2$, numerical simulations suggests that the MSE of this scheme time s $n$ converges as well to $\pi/2$, but in a faster rate than the first scheme.
-
 %While we provide expressions for the optimal message, evaluating the asymptotic efficiency of this estimation scheme turns out to be a challenging task.
@@
 \end{tikzpicture}
-\caption{Normalized empirical risk $n\left(\widehat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $100$ Monte Carlo trials.
-In each trial, $\theta$ is chosen uniformly in the interval $(-5,5)$.
+\caption{Normalized empirical risk $n\left(\widehat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $100$ Monte Carlo trials, where $\theta$ is chosen uniformly in the interval $(-5,5)$.
 \label{fig:adaptive_error}  }
@@
 
+\section{Distributed Estimation \label{sec:distributed}}
+We now consider the case where a single bit message is available on each sample from the distribution, and this message is independent of the other messages.
+Moreover, we assume that each message is characterized by a threshold value, and that ``$1$'' is sent by the $i$th encoder whenever $x_i$ is above this value.
+
+\subsection{Threshold Detection}
+We assume that each message is of the form
+\[
+M_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
+-1 & X_i > t_i,
+\end{cases}  
+\]
+where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th detector applied by the encoder on it sample $X_i$.
+In order to characterize the asymptotic behavior of estimation from these sequence of messages, we consider the \emph{density} of $n$ threshold values defined as:
+\[
+\lambda_n([a,b]) = \frac{1}{n} \left| \mathcal T \cap [a,b] \right|,
+\]
+where $\mathcal T  = \left\{t_n, n \in \mathbb N \right\}$ is the collection of all threshold values.
+We further assume that $\lambda_n$ converges (weakly) to a probability measure $\lambda(t)$ on $\mathbb R$.
+\par
+In order to estimate $\theta$ from the messages $M^n$, we consider the maximum likelihood (ML) estimator. The log-likelihood function of $\theta$ is given by
+\[
+l(M^n  |\theta ) =  \sum_{i=1}^n \log \left( \Phi \left( M_i \frac{t_i - \theta}{\sigma} \right) \right). 
+\]
+Since $\Phi(x)$ is a log concave function, the log-likelihood function has a unique maximizer $\widehat{\theta}_n$ which is the ML estimator.  \\
+
+Next, we show that under the assumptions above, the sequence of messages $M^n$ defines a local asymptotic normal (LAN) family of probability distributions.
+Therefore, the MSE in estimating $\theta$ from the messages $M^n$ satisfies a local asymptotic minimax property with respect to the \emph{precision} parameter of this LAN family \cite{van2000asymptotic}.
+Moreover, we conclude the ML estimator is locally asymptotic minimax.
+
+\begin{thm} \label{thm:LAN}
+Consider the sequence of threshold detectors $M^n$ with threshold density converges to a probability measure $\lambda$. The the following two statements hold:
+\begin{itemize}
+\item[(i)] Any estimator ${\theta}_n$ of $\theta$ which is a function of $M^n$ satisfies
+\[
+\liminf_{c\rightarrow \infty}\, \liminf_{n\rightarrow \infty} \sup_{\tau\,:\,| \tau - \theta| \leq \frac{c}{\sqrt{n}} }  n \mathbb E \left({\theta}_n - \tau \right)^2 \geq \sigma^2/K(\theta),
+\]
+where 
+\[
+K(\theta) \triangleq \int \eta\left(\frac{t-\theta}{\sigma} \right) \lambda(dt),
+\]
+and 
+\[
+ \eta(x) = \frac{ \phi^2\left( x \right)}{ \Phi\left( x \right) \left(1-\Phi\left(x\right) \right)}. 
+\]
+\item[(ii)] The asymptotic distribution of the ML estimator $\widehat{\theta}_n$ is given by
+\[
+\sqrt{n}(\widehat{\theta}_n - \theta) \overset{D}{\rightarrow} \mathcal N\left(0,\sigma^2/K(\theta) \right).
+\]
+\end{itemize}
+\end{thm}
+
+\subsubsection*{Sketch of Proof}
+The proof shows that the probability distribution of the vector of messages $M^n$ define a local asymptotic normal (LAN) family of probability distributions with precision parameter $K(\theta)/\sigma^2$.
+The statements in the theorem then follows from the local asymptotic minimax theorem of LAN families \cite{van2000asymptotic}.
+The details are given in the Appendix.\\
+
+%Theorem~\ref{thm:dist_thresholds} shows that the maximum likelihood estimator of $\theta$ given the $n$ single-bit messages $M^n$ is asymptotically normal and attains the local asymptotic minimax error $\sigma^2/K(\theta)$.
+
+It follows from Thm.~\ref{thm:LAN} that the asymptotic risk of the ML estimator is $\sigma^2/K(\theta)$, and that this risk is asymptotically minimal over all local alternative estimators for $\theta$.
+Moreover, the relative efficiency of the ML in the threshold detection scheme equals $1/K(\theta)$.
+Since the thresholds density $\lambda(t)$ integrates to $1$, and from the bound on the function $\eta(x)$ obtained in the proof of Lemma~\ref{lem:bound_intervals}, it follows that
+\[
+K(\theta) \leq \sup_{t\in \mathbb R} \eta \left( \frac{t-\theta}{\sigma} \right) \int  \lambda(dt)  \leq \frac{2}{\pi}.
+\]
+This upper bound on $K(\theta)$ implies that the relative efficiency of any distributed estimator is at least $\pi/2$, a fact that agrees with the lower bound under adaptive estimation derived in Thm.~\ref{thm:adpative_lower_bound}.
+Unfortunately, this upper bound on $K(\theta)$ is attained whenever the density $\lambda$ is the mass distribution at $\theta$, which is unknown apriori.
+Therefore, in the section below we consider the asymptotic threshold density function $\lambda$ that minimize the expected asymptotic risk $\mathbb E\left [\sigma^2/K(\theta) \right]$.
+
+\subsubsection{Worst case $\theta$} in order to bound the local asymptotic minimax risk it is required to consider the density $\lambda$ that minimizes the worst case $\theta$ in the parameter space $\Theta$.
+We assume that $\Theta = [-b,b]$ for some $b>0$, and consider
+\begin{equation} \label{eq:variational}
+\sup_{\lambda} \inf_{\theta \in [-b,b]}  {K(\theta)} = \int \eta\left( \frac{t-\theta}{\sigma} \right) \lambda (dt),
+\end{equation}
+where the suprimum is over all probability measure $\lambda$ on $\mathbb R$. Since \eqref{eq:variational} is concave in $\lambda$, this optimization problem can be solved using a convex program. 
+As illustrated in Fig.~\ref{fig:cvx}, the threshold density that maximizes \eqref{eq:variational} is supported over a discrete set in the interval $[-b,b]$.
+Fig.~\ref{fig:cvx2} illustrates the asymptotic ML risk as a function of the length $2b$ of the parameter space $\theta$.
+
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}
+\node[int] at (0,0)  {\includegraphics[scale=0.2]{support_b20}};
+\node[int] at (4.1,0)  {\includegraphics[scale=0.2]{support_b10}};
+\node[int] at (0,3.2)  {\includegraphics[scale=0.2]{support_b5}};
+\node[int] at (4.1,3.2)  {\includegraphics[scale=0.2]{support_b1}};
+\end{tikzpicture}
+\caption{\label{fig:cvx}
+Support of the optimal density $\lambda$ that minimizes the asymptotic ML risk for the worst choice of $\theta \in [-\sigma b, \sigma b]$ (blue), for $b=1,5,10,20$ (clockwise).
+The red curve is the value of $K(\theta)$ under this density.
+}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}
+\node at (0,0)  {\includegraphics[scale=0.25]{K_vs_b}};
+\end{tikzpicture}
+\caption{\label{fig:cvx2}
+Asymptotic risk of the ML estimator under an optimal choice of the threshold density $\lambda$ versus the support of the parameter space $\Theta$.
+}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}
+\node[int] at (0,0)  {\includegraphics[scale=0.2]{opt_density_sig025}};
+\node[int] at (4,0)  {\includegraphics[scale=0.2]{opt_density_sig1}};
+\node[int] at (8,0)  {\includegraphics[scale=0.2]{opt_density_sig2}};
+\end{tikzpicture}
+\caption{\label{fig:opt_density}
+The optimal asymptotic threshold density $\lambda$ that minimizes the expected asymptotic ML risk \eqref{eq:cvx_average} for a Gaussian prior for
+ $\sigma/\sigma_\theta=0.25,1,2$ (left to right), where $\sigma_\theta^2$ is the variance of the prior. 
+}
+\end{center}
+\end{figure}
+
+\subsection{Average Asymptotic Risk}
+Consider problem of minimizing the expected asymptotic risk $\mathbb E[ \sigma^2/K(\theta)]$ over all probability measures $\lambda(dt)$. This optimization problem can be written as follows:
+\begin{align}
+\label{eq:cvx_average}
+\mathrm{minimize} \quad &  \sigma^2 \int \frac{\pi(d\theta)}{K(\theta)} =  \sigma^2 \int \frac{\pi(d\theta)}{ \int \eta \left( \frac{t-\theta}{\sigma}\right) \lambda(dt)}. \\ \nonumber
+\mathrm{subject~to} \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) =1. 
+\end{align}
+Since the function $x \rightarrow 1/x$ is convex for positive values, \eqref{eq:cvx_average} defines a convex optimization problem in $\lambda$ whose solution depends on the the prior $\pi(\theta)$.
+The optimal asymptotic threshold density obtained as the solution to \eqref{eq:cvx_average} for a normal prior is illustrated in Fig.~\ref{fig:opt_density}, whereas Fig.~\ref{fig:dist_bound_Gaussian} illustrates the corresponding expected risk.
+The expected asymptotic risk for the uniform distribution is illustrated in Fig.~\ref{fig:dist_bound_uniform}.
+\par
+%
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}
+\node at (0,0) {\includegraphics[scale=0.5]{dist_bound_Gauss_prior}};
+\node at (0,-2.5) {$\sigma/\sigma_\theta$};
+\node[rotate = 90] at (-3.5,0) {(expected asymptotic risk)$/\sigma^2$};
+\node at (1,0) {$\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$ };
+%\node at (-2,-1.05) {$\frac{\pi}{2}$};
+%\node[rotate = -45] at (-1.8,1.2) {\color{red} true };
+%\node[rotate = -70] at (-0.5,0) {\color{blue} bound };
+\end{tikzpicture}
+\caption{Expected asymptotic risk $\mathbb E (1/K(\theta))$ in estimation from threshold detectors versus $\sigma/\sigma_\theta$ for a Gaussian prior with variance $\sigma_\theta^2$.
+The optimal asymptotic threshold density $\lambda$ (red) is obtained by solving \eqref{eq:cvx_average}.
+The bound (blue) is obtained using \eqref{eq:upper_bound}.
+\label{fig:dist_bound_Gaussian}  }
+\end{center}
+\end{figure}
+%
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}
+\node at (0,0) {\includegraphics[scale=0.5]{dist_bound_uniform_prior}};
+\node at (0,-2.5) {$\sigma/\sigma_\theta$};
+\node[rotate = 90] at (-3.5,0) {(expected asymptotic risk)$/\sigma^2$};
+\node at (1,0) {$\pi(\theta)$ = Unif$(- \sqrt{3}\sigma_\theta, \sqrt{3}\sigma_\theta)$ };
+%\node at (-2,-1.05) {$\frac{\pi}{2}$};
+%\node[rotate = -45] at (-1.8,1.2) {\color{red} true };
+%\node[rotate = -70] at (-0.5,0) {\color{blue} bound };
+\end{tikzpicture}
+\caption{Expected asymptotic risk $\mathbb E (1/K(\theta))$ in estimation from threshold detectors versus $\sigma/\sigma_\theta$ for a uniform prior with variance $\sigma_\theta^2$.
+The optimal asymptotic threshold density $\lambda$ (red) is obtained by solving \eqref{eq:cvx_average}.
+The bound (blue) is obtained using \eqref{eq:upper_bound}.
+\label{fig:dist_bound_uniform}  }
+\end{center}
+\end{figure}
+
+As can be seen from Fig.~\ref{fig:opt_density}, for a normal prior with a small variance compared to the variance of the samples $\sigma^2$, the optimal density $\lambda$ is a mass distribution.
+As it turns out from the following proposition, the choice of  $\lambda$ to be a mass distribution leads to a general upper bound on the expected asymptotic risk, and not only on the minimal value of \eqref{eq:cvx_average}.
+\begin{prop}\label{prop:upper_bound}
+Let $\theta_0 = \mathbb E \theta$. Then
+\begin{equation}
+\label{eq:upper_bound}
+\mathbb E \frac{\sigma^2}{K(\theta)}  \leq \sigma^2 \int \frac{\pi(d\theta)}{\eta \left( \frac{\theta_0 - \theta}{\sigma} \right)}, 
+\end{equation}
+\end{prop}
+\begin{proof}
+Since the function $x \rightarrow 1/x$ is convex for positive values, Jensen's inequality applied to the RHS of \eqref{eq:cvx_average} leads to
+\[
+ \frac{\sigma^2}{K(\theta)} \leq \sigma^2 \int  \frac{ \lambda(dt)}{ \eta \left( \frac{t-\theta}{\sigma} \right)  }. 
+\]
+Therefore, the expected value of $\sigma^2/K(\theta)$ satisfies
+\begin{align}
+\mathbb E  \frac{\sigma^2}{K(\theta)}  \leq \sigma^2  \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( \frac{t - \theta}{\sigma} \right)}. \label{eq:upper_bound_proof}
+\end{align}
+The bound \eqref{eq:upper_bound} follows by using $\lambda = \delta_{\theta_0}$. 
+\end{proof}
+We note that since the function $1/\eta(x)$ is quasi-convex and symmetric, taking $\lambda = \lambda_{\theta_0}$ minimizes the RHS of \eqref{eq:upper_bound_proof} and leading to the tightest bound among the family bounds obtained after using Jensen's inequality.
+\par
+The bound \eqref{eq:upper_bound} is not trivial as long as the tail of the prior $\pi(\theta)$ is small enough such that the integral in the RHS of \eqref{eq:upper_bound} is finite.
+In general, this bound is tight whenever the support of the optimal distribution is a mass distribution at the origin.
+The following proposition implies that this bound is always tight as $\sigma / \sigma_\theta$ goes to infinity.
+\begin{prop} \label{prop:asymp}
+ For any prior $\pi(\theta)$ for which
+\[
+\int \frac{\pi(d\theta)}{\eta \left(\theta \right)} < \infty,
+\]
+we have 
+\begin{align}
+\label{eq:asymp}
+\mathbb E [1/K(\theta)] = \frac{\pi}{2} + \left( \frac{\pi}{2} - 1\right) \left(\frac{\sigma_\theta}{\sigma} \right)^2 + o \left(\frac{1}{\sigma} \right)^3. 
+\end{align}
+as $\sigma_\theta / \sigma \rightarrow 0$. 
+\end{prop}
+\begin{proof}
+It is enough to prove that  \eqref{eq:asymp} holds for the upper bound \eqref{eq:upper_bound}.
+First note that the condition in the proposition implies that all the moments of $\pi(\theta)$ exists, and in particular its second and third.
+The results follows by expanding the function $1/\eta(x)$ in a power series as
+\[
+1/\eta(x) = \frac{\pi}{2} + \left(\frac{\pi}{2}-1 \right) x^2 + o(x^3).
+\]
+\end{proof}
+
+\subsection{Discussion}
+It follows from Prop.~\ref{prop:asymp} that the asymptotic expected risk converges to $\pi/2$ when the ratio between the variance of the distribution of $X_i$ to the variance of the prior tends to infinity.
+Therefore, we conclude that the minimal risk in the adaptive setting can be attained even in the distributed setting, as long as this ratio is large enough.
+Prop.~\ref{prop:asymp} also bounds the convergence rate of the expected risk to its optimal value, where we note that higher order terms in \eqref{eq:asymp} can be obtained by considering a higher order power series expansion of $1/\eta(x)$.
+\par
+When the ratio $\sigma^2/ \sigma_\theta^2$ is large, the bound \eqref{eq:upper_bound} is tight and the probability measure $\lambda$ that minimizes the expected risk converges to a mass distribution at the expected value of $\theta$ according to its prior $\pi(\theta)$.
+Namely, all the encoders in this case report "$1$" whenever $X_i$ is larger than this expected value and ''$-1$'' otherwise.
+Intuitively, an accurate estimation of $\theta$ in this case is possible only if a sufficient mix of ''$1$''s and ''$-1$''s is obtained from the sample.
+When $\sigma_\theta^2$ is high, so is the probability of having a realization of $\theta$ away from its mean $\theta_0$.
+In this case, a threshold detector located at $\theta_0$ may have a strong bias toward one of ''$1$'' or ''$-1$'', unless the variance of the samples $\sigma^2$ is also relatively large.
+Indeed, as illustrated in Figs~\ref{fig:opt_density} and \ref{fig:dist_bound_Gaussian}, when $\sigma^2$ is small compared to $\sigma_\theta^2$, the bound in Prop.~\ref{prop:upper_bound} is not tight and the optimal asymptotic threshold density $\lambda$ is supported by multiple points.
+As illustrated in Figs~\ref{fig:dist_bound_Gaussian} and Figs~\ref{fig:dist_bound_uniform}, when the ratio $\sigma/\sigma_\theta$ is small the expected asymptotic risk, and therefore the relative efficiency of any asymptotic local minimax optimal estimator, is higher than $\pi/2$ and cannot be uniformly bounded in this ratio regardless of the threshold distribution $\lambda$.
+For example, if the prior information on $\theta$ indicates that it lays in the interval $[-1,1]$ with a uniform probability and the variance of the observations is $\sigma^2 = 0.02$, then the asymptotic expected relative efficiency is $~\approx 8.25$.
+This number goes down to $~\approx 3.02$ for $\sigma^2 = 0.2$.
+\\
+
+To summarize, we conclude that when the prior information on $\theta$ provides a reasonable localization of its value compared to the variance of the measurements, then the relative efficiency \eqref{eq:relative_efficiency} of the ML estimator is $\pi/2$.
+On the other hand, the relative efficiency of any local asymptotic minimax estimator can be very high if the variance of the measurements is very small compared to the apriori uncertainty in $\theta$, even under the optimal threshold distribution $\lambda$.
+
+%For example, when $\pi(\theta)$ is a zero mean normal with variance $\sigma_\theta^2$ and $\sigma / \sigma_\theta=1$, the upper bound in \eqref{eq:upper_bound} equals $3.563$.
+With $\sigma/\sigma_\theta=2$ it equals $1.748$.
+The behavior of this bound is illustrated in Fig.~\ref{fig:dist_bound_Gaussian}.
+For large $\sigma/\sigma_\theta$ it converges to $\sigma^2 \pi/2$.
+For small $\sigma$ the expression above can be very large, but, as explained below, in this case the bound is not tight.
+
 \section{Conclusions \label{sec:conclusions}}
-We considered the relative efficiency in estimating the mean of a normal distribution from single-bit measurements in an adaptive setting.
-We have shown that this minimal relative efficiency is $\pi/2$, namely there is a penalty factor of at least $\pi/2$ on the asymptotic MSE in estimating the mean compared to an estimator that has full access to the sample.
-We also showed that this lower bound is tight by presenting an estimation procedure that attains it.
+We considered the relative efficiency in estimating the mean of a normal distribution from a single-bit encoding of each sample from this distribution.
+For the adaptive setting, we have shown that this minimal relative efficiency is $\pi/2$, namely there is a penalty factor of at least $\pi/2$ on the asymptotic mean square error risk in estimating the mean compared to an estimator that has full access to the sample.
+We also showed that this lower bound is tight by presenting an adaptive estimation procedure that attains it.
 %but ignores the prior distribution on the parameter space.
 In addition, we characterized the single-bit message that minimizes the next step MSE, and described an estimation procedure that is based on a sequence of one-step optimal messages.
-We leave open the questions whether this estimator attains the minimal efficiency and whether it leads to an estimation scheme which is globally optimal.
-\\
-
-%Something about how to interpret the results
-
-% Sigma-Delta
-% Relation to CEO
-% Open questions
-% Extenstion to fully distributed setting
-
-\section*{ACKNOWLEDGMENT}
-This research is supported in parts by...
+We leave open the questions whether this estimator attains the minimal efficiency and whether it leads to an estimation scheme which is globally optimal in the adaptive setting.
+\par
+For the distributed setting, we considered the estimation from threshold detection under the assumption that density of the threshold values converges to a probability distribution.
+For this setting, we characterized the risk attained by the maximum likelihood estimator, and showed that this estimator is local asymptotic minimax.
+In addition, we showed that when the variance of the underlying normal distribution is high compared to the size of the variance of the prior on the unknown mean, the asymptotic relative efficiency in this setting converges to $\pi/2$.
+Namely, under this conditions, there is no loss in efficiency compared to the adaptive case.
+Nevertheless, this relative efficiency can be very high whenever the variance of the underlying distribution is very small compared to the apriori uncertainty in $\theta$.
+We leave open the question whether there exists a distributed one-bit estimation scheme that achieves relative efficiency close to $\pi/2$ even when the apriori uncertainty in $\theta$ is high compared to the variance of the underlying normal distribution.
+
+%\section*{ACKNOWLEDGMENT}
+%This research is supported in parts by...
 %Tsachy Weissman, Stefano Rini, Robert Gray.
-
-\onecolumn
 
@@
 \begin{equation} \label{eq:induction_base}
-\frac{  \phi^2(x)} 
-{\Phi(x) \left(1 - \Phi(x) \right) } 
-\end{equation}. 
+\eta(x) \triangleq \frac{  \phi^2(x)} 
+{\Phi(x) \left(1 - \Phi(x) \right) }. 
+\end{equation}
 Taking the logarithm of \eqref{eq:induction_base} and differentiating, we conclude that any point $x$ that maximizes \eqref{eq:induction_base} satisfies
@@
 \]
-In particular, the condition above implies $x_1 = \ldots = x_N$. If $N$ is odd then for $x_1=\ldots =x_N$ we have that \eqref{eq:bound_intervals} equals
-\[
-\frac{\phi(x_1)^2}{ \Phi(x_1) (1 - \Phi(x_1))},
-\]
-which was shown to be smaller than $\pi/2$.
+In particular, the condition above implies $x_1 = \ldots = x_N$.
+If $N$ is odd then for $x_1=\ldots =x_N$ we have that \eqref{eq:bound_intervals} equals $\eta(x_1)$, which was previously shown to be smaller than $\pi/2$.
 If $N$ is even, then for any constant $c$ the limit of \eqref{eq:bound_intervals} exits as $(x_1,\ldots,x_N)\rightarrow (c,\ldots,c)$ and equals zero.
@@
 
+\subsection*{Proof of Theorem~\ref{thm:LAN}}
+We will prove that the distribution of $M^n$ defines a local asymptotic normal (LAN) family of probability distributions with \emph{precision} parameter $K(\theta)/\sigma^2$.
+The statements in the theorem then follows from the local asymptotic minimax theorem of LAN families \cite{van2000asymptotic}.
+\\
+
+The probability mass distribution of $M^n$ is given by
+\[
+P_\theta(m^n) =  \prod_{i=1}^n  \Phi \left( m_i \frac{t_i - \theta}{\sigma} \right). 
+\]
+Consider the log-likelihood ratio under a sequence of local alternatives $\theta' = \theta + h/\sqrt{n}$ for some $h\in \mathbb R$:
+\begin{align}
+\log \frac{ P_{\theta + \frac{h}{\sqrt{n}}}(M^n)} { P_\theta (M^n) }& =  \sum_{i=1}^n \log \left(  \Phi \left( \frac{M_i}{\sigma} (t_i - \theta - h/\sqrt{n} ) \right)\right)  - \sum_{i=1}^n \log \left( \Phi \left( M_i \frac{t_i - \theta}{\sigma} \right) \right).
+\label{eq:LAN_proof1}
+\end{align}
+Using the Taylor expansion of $\log \Phi(x)$, \eqref{eq:LAN_proof1} can be written as
+\[
+- h \sum_{i=1}^n  \frac{M_i}{\sqrt{n} \sigma }  \frac{ \phi \left(M_i\frac{t_i-\theta}{\sigma} \right)} {\Phi \left( M_i \frac{t_i-\theta}{\sigma} \right) }  - \frac{h^2}{2 \sigma^2 n} \sum_{i=1}^n   \left( \frac{\phi' \left(M_i \frac{t_i-\theta}{\sigma} \right) }{\Phi\left(M_i \frac{t_i-\theta}{\sigma}\right) }- \frac{ \phi^2\left(M_i \frac{t_i-\theta}{\sigma} \right)}{\Phi^2\left(M_i \frac{t_i-\theta}{\sigma} \right)}   \right) + o(1)
+\]
+
+The proof is completed by proving the following two lemmas:
+\begin{lem} \label{lem:LAN1}
+For $i=1,\ldots,n$ denote 
+\[
+U_i = -M_i \frac{ \phi \left( M_i \frac{t_i - \theta}{\sigma} \right)}{ \Phi \left( M_i \frac{t_i - \theta}{\sigma}\right) }. 
+\]
+Then 
+\[
+\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0, K(\theta) \right). 
+\]
+\end{lem}
+\begin{lem} \label{lem:LAN2}
+For $i=1,\ldots,n$ denote
+\[
+V_i =  \left[ \frac{\phi' \left(M_i \frac{t_i-\theta}{\sigma} \right) }{\Phi\left(M_i \frac{t_i-\theta}{\sigma}\right) }- \frac{ \phi^2\left(M_i \frac{t_i-\theta}{\sigma} \right)}{\Phi^2\left(M_i \frac{t_i-\theta}{\sigma} \right)} \right] .
+\]
+Then 
+\[
+\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} K(\theta). 
+\]
+\end{lem}
+
+\subsubsection*{Proof of Lemma~\ref{lem:LAN1}} 
+We have that $\mathbb E  U_i= 0$. In addition,
+\[
+\mathbb E U_i^2 = \frac{ \phi^2 \left( \frac{t_i-\theta}{\sigma} \right) } { \Phi \left( \frac{t_i-\theta}{\sigma} \right) \left(1- \Phi \left( \frac{t_i-\theta}{\sigma} \right) \right)},
+\]
+and therefore
+\[
+\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 \rightarrow K(\theta).
+\]
+
+We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition: for any $\delta>0$ we have that 
+\[
+\mathbb E \left| U_i \right|^{2+\delta} = \phi^{2+\delta} \left(\frac{t_i-\theta} {\sigma } \right)   \left( \frac{1}{\Phi^{2+\delta} \left(\frac{t_i-\theta}{\sigma }\right)} + \frac{1}{1-\Phi^{2+\delta} \left(\frac{t_i-\theta}{\sigma }\right)} \right),
+\]
+and
+\begin{equation}
+\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} }{ \left( \sqrt{\sum_{i=1}^n \mathbb E U_i^2 } \right)^{2+\delta}} = 
+\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E U_i^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right) \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
+\label{eq:Lyaponov}
+\end{equation}
+As $n$ goes to infinity, we have
+\[
+\frac{1}{n}\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta}  \rightarrow  \int \phi^{2+\delta} \left(\frac{t-\theta}{\sigma }\right) \left( \frac{1}{\Phi^{2+\delta}\left(\frac{t-\theta}{\sigma }\right)} + \frac{1}{1-\Phi^{2+\delta} \left(\frac{t-\theta}{\sigma }\right)} \right) \lambda(dt),
+\]
+so the numerator in \eqref{eq:Lyaponov} goes to zero.
+Since the denumerator in \eqref{eq:Lyaponov} goes to $(K(\theta))^{1+\delta})$, the entire expression goes to zero and hence Lyaponov's condition is satisfied.
+From Lyaponov's central limit theorem we conclude that
+\[
+\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0,K(\theta) \right). 
+\]
+\QEDA
+
+\subsubsection*{Proof of Lemma~\ref{lem:LAN2}}
+
+Since $\phi'(x) = -x \phi(x)$, we have that
+\[
+\mathbb E V_i =  \frac{\phi^2 \left(\frac{ t_i-\theta}{\sigma} \right) } { \Phi \left(\frac{ t_i-\theta}{\sigma} \right)  \left(1-\Phi \left(\frac{ t_i-\theta}{\sigma} \right)  \right)},
+\]
+and thus
+\[
+\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =  \frac{1}{n} \sum_{i=1}^n  \frac{\phi^2\left( \frac{t_i-\theta}{\sigma} \right)} { \Phi \left( \frac{t_i - \theta}{\sigma} \right)\left(1-\Phi \left( \frac{t_i - \theta}{\sigma} \right) \right)} \rightarrow K(\theta).
+\]
+It follows from Kolmogorov's law of large numbers (e.g. \cite[Thm. 10.2.3]{sen1994large}) that
+\[
+\frac{1}{n} \sum_{i=1}^n \mathbb E V_i \overset{a.s.}{\rightarrow} K(\theta). 
+\]
+\QEDA
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\section{Related Results in Source Coding}
+The estimation problem we consider can be seen as the quantization, compression or encoding of the samples, and the  decoding of the parameter $\theta$ from the encoded version of the sample.
+Therefore, this problem is closely related to various setting in coding and information theory.
+The goal of this section is to illustrates this connection and review related results that are relevant in our case.
+
+%As opposed to the aforementioned line of works, we focus on estimation of samples taken from a single distribution in the finite blocklength performance.
+We are interested in particular in addition restrictions on the communication and information sharing between the encoders.
+For example, our main focus is the case where the observer must communicate a single bit upon drawing from the distribution.
+This is in contrast to the asymptotic setting where the observer can encode the outcome of $n$ draws at once using a single $n$ bit message.
+Alternately, such setting can be seen as having $n$ different observers, each is capable of observing a single realization and transmit a single bit.
+
+%{\color{red} The Van Trees inequality was extended to the estimation of multiple parameters in \cite{bobrovsky1987}. It is closely related with the }
+
+\subsection{Statistical Inference under Communication Constraints}
+The works \cite{han1987hypothesis, zhang1988estimation, 720540} consider various problems of statistical inference under multiterminal lossy compression.
+In the setting of \cite{han1987hypothesis, zhang1988estimation, 720540}, each terminal $I$ observes $n$ samples from the distribution and is allotted $nR_i$ bits to communicate its estimate.% Consequently, our case (iii) is obtained from this setting by taking $n=1$, $R_i=1$, and number of terminals grow with $n$.
+The main focus of these works is the difference between inference with communication constraint and the unconstrained vanilla statistical estimation setting, as the number of samples $n$ goes to infinity subject to a total finite rate constraint.
+Our case (i) can be seen as a special case of this setting where with a single terminal and $R_1 = 1$.
+However, as explained in \cite[Sec.
+III]{720540}, in this setting the unconstrained inference performance is always attained when all samples are taken from the same distribution.
+Indeed, in an i.i.d setting the \emph{type} of the sample \cite{csiszar1998method} is a sufficient statistics for any estimation task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples.
+For this reason, attention is given in these works to inference problems involving multiple distributions observed at different locations, hence the name \emph{multiterminal}.
+
+\subsection{Sigma-Delta Encoding}
+
+and covariance function \cite[Eq. 25]{53738}
+\[
+R(k) = \mathbb E M_{n+k} M_n = \theta^2 + O \left( \frac{1}{\sigma \sqrt{ k} } \right). 
+\]
+{\color{red} This is not enough to deduce convergence. Need to go over the paper and check if rate of convergence can be deduced. Also do simulations BEFORE that. \\
+
+What is the error in estimating the mean of stationary ergodic process ? 
+}
+Since the SDM is a special case of the sequential scheme, we conclude that the MSE of any SDM with a noisy DC signal is bounded from below by $n^{-1} \sigma^2 \pi/2 $.
+
+%Even with such arguably simple setting, we will see that the performance limit in the estimating task based on single bit observations provides an interesting setting for discussion that bridges classical works in statistics, coding theory, information theory and optimization.
+
+\subsection*{Source coding}
+With a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample.
+Setting (ii) includes as a special case the sigma-delta modulation (SDM) analog-to-digital conversion scheme with a constant input $\theta$ corrupted by Gaussian noise $Z_i$, as was considered in \cite{53738}.
+While it was shown there that the output of the modulator converges to the true constant input, the rate of this convergence was not analyzed and cannot be derived directly from the results of \cite{53738}.
+As a corollary from the results in this paper we conclude that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations.
+Finally, the remote multiterminal source coding setting of \cite{berger1996ceo} corresponds to the case of $n$ rate-constrained encoders, each observing a noisy version of an information source.
+The difference between this setting and ours is that in ours the parameter of interest is not an information source.
+By assuming a prior distribution on this parameter, the CEO provides a lower bound on the estimation error in the fully distributed setting (iii).
+This lower bound can be attained if we were to consider the average error in multiple independent realizations of our problem rather than a single realization as we do here.
+\\
+
+\subsection*{Relation to channel coding}
+The problem we consider is the estimation of the parameter $\theta$ by observing 
+\begin{equation}
+\label{eq:channel}
+X_i = \theta + Z_i, \quad i=1,\ldots,n,
+\end{equation}
+where the $Z_i$s are independent, centered normal with variance $\sigma^2$.
+The problem of estimating $\theta$ from the $X_i$s can be seen as the attempt to transmit a real number $\theta$ over an additive white Gaussian noise (AWGN) channel.
+In particular, setting (ii) can be seen as the feedback version of this transmission, which is closely related to \cite{horstein1963sequential, 1053879}.
+Using the joint source and channel coding theorem, the number of channel uses required to attain MSE of $\delta$ in estimating $\theta$ is given by
+\begin{equation} \label{eq:rdf_bound}
+n \geq \frac{R_\theta(\delta)}{ \frac{1}{2} \log\left( 1+ \sigma_\theta^2/\sigma^2 \right)},
+\end{equation}
+where $R_\theta(\delta)$ is the rate-distortion function of the prior $\pi(\theta)$, and the variance of this distribution is $\sigma_\theta^2$.
+From \eqref{eq:rdf_bound} we obtain the following lower bound on the asymptotic minimal MSE:
+\begin{equation} \label{eq:drf_bound}
+\delta \geq D_\theta \left(\frac{n}{2} \log \left( 1+ \sigma_\theta^2 / \sigma^2 \right)  \right),
+\end{equation}
+where $D_\theta(R)$ is the inverse of $R_\theta(D)$.
+On the other hand, even if $\sigma^2 \ll \sigma_\theta^2$ than distortion of at least $D_\theta(n)$ is expected.
+So that the lower bound is the maximum between \eqref{eq:drf_bound} and $D_\theta(n)$.
+For example, when $\pi(\theta)$ is Gaussian, we have
+\[
+\mathbb E \left(\theta - \widehat{\theta}\right)^2 \geq \max \left\{  \sigma_\theta^2 \left(1+\frac{\sigma_\theta^2}{\sigma^2} \right)^{-n} , \sigma_\theta^2 2^{-2n} \right\}. 
+\]
+
+Unfortunately, the bound in \eqref{eq:drf_bound} is strict and cannot be attained unless in trivial cases.
+The reason is our setting $\theta$ is drawn once from a prior distribution, so the communication in \eqref{eq:channel} is limited to a repetition code.
+Moreover, in setting (ii) we have the additional constraint that the message is a causal function of the previous messages, where in case (iii) it is completely memoryless.
+Works in information theory which consider such setting includes AWGN channel with 1-bit ADC at the receiver \cite{DBLP:journals/corr/VarastehSG16}.
+\par
+
 \end{document}
+
+\begin{comment}
+\subsection{Remote Multiterminal Source Coding}
+The remote multi-terminal lossy source coding problem (a.k.a the CEO problem) \cite{berger1996ceo}, considers $n$ encoders (agents), each has access to a corrupted version of a source signal, transmit at rates $R_1,\ldots,R_n$ to a central estimation unit.
+The distributed estimation setting (iii) corresponds to a single round of communication in the CEO setting, where the $i$th agent observes
+\begin{equation}
+\label{eq:Gaussian_channel}
+X_i = \theta + Z_i,
+\end{equation}
+and has $R_i=1$ bits to transmit this observation.
+Note, however, that in the CEO setting each encoder observes multiple number, say $k$, of independent samples $\theta \sim \pi(\theta)$ through the channel \eqref{eq:Gaussian_channel}, and not just one sample as in our setting.
+In general, in the CEO setting each encoder is allowed $kR_i$ bits to represent its $k$ samples.
+One possible strategy of the encoder is to send $k$ single bit messages, each of which is only a function of its $k$th observation.
+%the minimal MSE distortion of the CEO provides a lower bound for the MSE in the distributed encoding scheme. 
+As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise of variance $\sigma^2$ provides a lower bound on the MSE distortion in estimating $\theta$.
+Moreover, the difference between this lower bound and the actual MSE in our setting would indicate the importance of coding over blocks consisting of multiple independent realizations of  in our joint estimation and communication problem.
+\par
+%Note that when multiple realization of $\theta$ are involved, the prior distribution $P_\theta$ plays a significant role in the overall MSE, whereas in our case we expect the final distortion to be independent of the actual prior distribution as in the two schemes in the sequential case.
+\\
+A closed-form expression for CEO under quadratic distortion is known only for the case where the sequence to described by the encoders is sampled from a Gaussian distribution \cite{prabhakaran2004rate}.
+By using the characterization of the minimal CEO distortion as the number of terminals goes to infinity, we conclude the following result:
+\begin{prop} \label{prop:ceo_lower_bound}
+Assume that $\pi(\theta)$ is the normal distribution. Then any estimator $\widehat{\theta}_n$ of $\theta$ in the distributed setting satisfies
+\[
+\lim_{n\rightarrow \infty}  n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3n}.
+\]
+\end{prop}
+\begin{proof}
+We consider the expression \cite[Eq. 10]{chen2004upper} that provides the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots R_L$:
+\begin{equation} \label{eq:ceo_optimal_sumrate}
+R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
+\end{equation}
+Assuming $R_\Sigma = n$ and $L=n$ we get
+\begin{equation} \label{eq:ceo_optimal_sumrate}
+n = \frac{1}{2} \log \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
+\end{equation}
+The value of $D^\star$ that satisfies the equation above describes the MSE in the quadratic Gaussian CEO setting under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
+Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
+By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$ we conclude that
+\[
+D^\star = \frac{ \frac{4\sigma^2}{3} }{n + \frac{4 \sigma^2}{3 \sigma_\theta^2} } + O(e^{-n}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
+\]
+\end{proof}
+We note that although the CEO lower bound was derived by the MSE attainable assuming optimal allocation a total of $n$ bits among the encoders, the same expression is from the upper bound to the CEO derived in \cite[Prop.
+5.2]{KipnisRini2017}, that assumes $R_1=\ldots,R_n = 1$ rather than optimal allocation of $n$ bits among all encoders.
+%\[
+%D_{CEO} / \sigma_\theta^2 \leq \left( 1 + \sum_{i=1}^n \frac{\sigma_\theta^2}{\sigma^2} \frac{1 - 2^{-2R_i}} {1+ \frac{\sigma_\theta^2}{\sigma^2}  2^{-2 R_i}  } \right)^{-1}
+%\]
+%where $\sigma_\theta^2$ is the variance of the distribution $\pi(\theta)$. Using $R_1=\ldots=R_n=1$ we get
+%\[
+%D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
+%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + o(n^{-1}). 
+%\]
+
+The bound provided by the CEO in Prop.~\ref{prop:ceo_lower_bound} implies that the relative efficiency in the distributed scheme is at most $4/3$.
+Since this number is smaller than the relative efficiency of the adaptive scheme, this proposition does not provide new information on the relative efficiency.
+It does, however, provides the intuition that the limiting factor in estimating $\theta$ is the strict bit-constraint and or the lack of concentration of probability distributions over blocks, rather than distributed estimation.
+\\
+
+We note that the same first order expression for the CEO distortion is achieved by a particular encoding scheme derived in \cite{KipnisRini2017}, assuming rate of $1$ bits per source symbol at each encoder, i.e.,  $R_1=\ldots = R_n = 1$, rather than a total of $n$ bits on average allocated among the $n$ encoders used in the proof.
+Indeed, the it follows from \cite[Eq.
+?]{KipnisRini2017} that the following distortion is achievable for the CEO
+\[
+\sigma_\theta^2 \left( 1 + \sigma_\theta^2 n \frac{3}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   = \frac{4\sigma^2+\sigma_\theta^2}{3n} + O(n^{-2} \sigma_\theta^4)). 
+\]
+As a result, we conclude that the above lower bound cannot be strengthen if we consider the exact distortion of the CEO with equal rate-allocation using the expression from \cite{prabhakaran2004rate}.
+\\
+
+%Comnet on appearance of $\sigma_\theta^2$ as a second order term.
+
+\end{document}
+
+\end{comment}

### 2017-09-26 Writeups/onebit_distributed_V3.tex
Add files via upload

--- 2017-09-26 Writeups/onebit_distributed_V2.tex
@@
 
-% Lower Bound on the assymptotic minimal effeciency.
-% Scheme that attains the assymptotic minimal effeciency. 
-% Bayesian scheme that is one step optimal. We leave open the question whether this scheme attains the asymptotic minimal effeciency
-
-\section{Adaptive Estimation \label{sec:sequential}}
-
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the asymptotic relative efficiency of and adaptive estimator cannot get below $\pi/2$.
-Next, we provide a particular adaptive estimation scheme and show in Theorem~\ref{thm:sgd} that asymptotically attains this efficiency with equality.
-Finally, in Theorem~\ref{thm:opt_one_step} we provide an adaptive estimation scheme that is optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen.
-%While we provide expressions for the optimal message, evaluating the asymptotic efficiency of this estimation scheme turns out to be a challenging task.
-We therefore leave open the question whether this scheme attains the lower bound with equality, and only provide numerical result that support this conjecture.
-\\
-
-%\begin{figure}
-%\begin{center}
-%\begin{tikzpicture}[node distance=2cm,auto,>=latex]
-%  \node at (0,0) (theta) {$\theta$} ;
-%  \node at (2,0) (x1) {$X_1$};
-%  \node[below of = x1, node distance = 1cm] (x2) {$X_2$};
-%    \node[below of = x2, node distance = 1cm] (dots) {$\vdots$};
-%  \node[below of = dots, node distance = 1cm] (xn) {$X_n$};
-%  
-%   \node[right of = x1, node distance = 2cm] (m1) {$M_1$};
-%  \node[right of = x2, node distance = 2cm] (m2) {$M_2$};
-%    \node[right of = xn, node distance = 2cm] (mn) {$M_n$};
-%
-%\draw[->] (theta) -- (x1);
-%\draw[->] (theta) -- (x2);
-%\draw[->] (theta) -- (xn);
-%
-%\draw[->] (x1)--(m1);
-%\draw[->] (x2)--(m2);
-%\draw[->] (xn)--(mn);
-%
-%\draw[->] (m1)--(m2);
-%\draw[->, dashed] (m2)--(mn); 
-%  
-%\end{tikzpicture}
-%\end{center}
-%\caption{\label{fig:sequencial_graphical} Graphical model notation of the sequential setting.}
-%\end{figure}
-
-%\subsection{Properties of an Optimal Scheme}
-%The sequential nature of the encoding and the estimation is best explain by the notions of actions and rewards taken from dynamic programming.
-The \emph{action} taken by the $i$th encoder is the design of a detection region $M_i^{-1}(1)$ that would lead to $M_i = 1$ assuming when $X_i \in M_i^{-1}(1)$ or $M_i=-1$ otherwise.
-The \emph{reward} (or penalty) is only evaluated at the end of the time horizon $n$.
-%% Dynamic program. State = $M^n$. 
-%% Reward is collected at the end
-%%
-
-\subsection{A Lower Bound on Adaptive Single-Bit Schemes}
-Our first results asserts that the relative efficiency \eqref{eq:relative_efficiency} of any adaptive estimation scheme is bounded from below by $\pi/2$, as follows from the following theorem:
-\begin{thm}[minimal relative effeciency] \label{thm:adpative_lower_bound}
-Let $\widehat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Fig.~\ref{fig:sequential}.
-% Let $\pi(\theta)$ be an absolutely continuous prior distribution on $\Theta$ with density function converges to zero at the endpoints of the interval $\Theta$. 
-Assumes that $P(d\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-\mathbb E (\theta-\theta_n)^2 \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\pi}{2n}\sigma^2+o(n^{-1}),
-\]
-where 
-\[
-I_0 = \mathbb E \left( \frac{d}{d\theta} \log P_\theta(\theta) \right)^2
-\]
-is the Fisher information with respect to a location model in $\theta$. 
-\end{thm}
-
-\subsubsection*{Sketch of Proof}
-The main idea in the proof is to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$.
-Once this bound is achieved, the result follows by using the Van-Trees inequality \cite{gill1995applications} which bounds from below the MSE of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are given in the Appendix.\\
-
-Next, we present an adaptive estimation scheme which attains the minimal asymptotic efficiency $\pi/2$. 
-%Theorem~\ref{thm:adpative_lower_bound}. This estimation scheme can be seen as a gradient descent
-
-\subsection{Asymptotically Optimal Estimator}
-Consider the following estimator $\widehat{\theta}_n$ for $\theta$:  set 
-\begin{equation}
-\label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n \sgn (X_n - \theta_n), \quad n = 1,2,\ldots,
-\end{equation}
-where $\left\{\gamma_n \right\}_{n=1}^\infty$ is any strictly positive sequence satisfying 
-\begin{enumerate}
-\item[(i)] $\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n)$ \\
-\item[(ii)] $\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty$ 
-for some $0< \lambda \leq 1$.
-\end{enumerate}
-(e.g. $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). The $n$th step estimation is defined by 
-\begin{equation} \label{eq:sgd_est}
-\widehat{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
-\end{equation}
-
-As the following theorem shows, the estimator $\widehat{\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the minimal asymptotic efficiency as established by Theorem~\ref{thm:adpative_lower_bound}.
-\begin{thm} \label{thm:sgd}
-The sequence $\widehat{\theta}_n$ of \eqref{eq:sgd_alg} satisfies
-\[
-\sqrt{n} \left( \widehat{\theta}_n - \theta \right) \overset{d}{\rightarrow} \mathcal N \left(0,  \pi \sigma^2 /2 \right).
-\]
-\end{thm}
-
-\subsubsection*{Proof}
-The asymptotic behavior of \eqref{eq:sgd_est} is a special case of  \cite[Thm. 4]{polyak1992acceleration}. The details are provided in the Appendix.\\
-
-Note that $\theta_0$ is not explicitly defined in 
-in equation \eqref{eq:sgd_est}.
-Arguably, a reasonable initialization is $\theta_0 = \mathbb E [\theta]$.
-However, Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator, is indifferent to this initialization.
-Thus, the optimal efficiency is attained without using the prior distribution on $\theta$.
-Nevertheless, the bound in Theorem~\ref{thm:adpative_lower_bound} suggests that the estimation error can be greatly reduced whenever the prior of $\theta$ provides a lot of information $I_0$ on its location.
-In order to incorporate this information in a more meaningful way, we present a Bayesian estimation scheme that is conjectured to attain the optimal asymptotic efficiency.
-
-\subsection{One-step Optimal Estimation}
-In this subsection we present an estimation scheme that posses the property of \emph{one-step optimality}.
-That is, at each step $i$, the $i$th encoder designs the detection region $M_i^{-1}(1)$ such that the MSE given $M^i$ is minimal.
-In other word, this scheme designs the messages in a greedy manner, such that the MSE at step $i$ is minimal given the current state of the estimation described by $M^{i-1}$.
-\\
-
-The structure of the message that minimizes the next step MSE is given by the following theorem:
-\begin{thm}[optimal one-step estimation] \label{thm:opt_one_step}
-Let $\pi(\theta)$ be an absolutely continuous log-concave probability distribution. Given a sample $X$ from the distribution $\mathcal N(\theta, \sigma^2)$, define 
-\begin{equation}
-\label{eq:adaptive_main_message}
-M = \sgn(X - \tau),
-\end{equation}
-where $\tau$ satisfies the equation
-\begin{equation}
- \label{eq:fixed_point}
- \tau = \frac{m^-(\tau) + m^+(\tau)}{2},
-\end{equation}
-with
-\begin{align*}
-m^-(\tau)  & = \frac{\int_{-\infty}^{\tau} \theta P(d\theta) }{\int_{-\infty}^{\tau} P(d\theta)} ,\\
-m^+(\tau) & = \frac{\int_{\tau}^\infty \theta P(d\theta) }{\int_{\tau}^\infty P(d\theta)} .
-\end{align*}
-Then for any estimator $\widehat{\theta}$ which is a function of $M'(X) \in \{-1,1\}$, we have
-\begin{equation}
-\label{eq:opt_cond}
-\mathbb E \left(\theta-\widehat{\theta}(M')\right)^2 \geq  \mathbb E \left(\theta- \mathbb E[\theta|M]\right)^2,
-\end{equation}
-\end{thm}
-
-\begin{proof}
-The proof is completed by the following two lemmas, proofs of which can be found in the Appendix:
-\begin{lem} \label{lem:unique}
-Let $f(x)$ be a log-concave probability density function. Then the equation 
-\begin{equation}
-\label{eq:lem_fixed_point}
-2x = \frac{\int_x^\infty uf(u)du}{\int_x^\infty f(u)du} + \frac{\int_{-\infty}^x uf(u)du}{\int_{-\infty}^x f(u)du} 
-\end{equation}
-has a unique solution.
-\end{lem}
-\end{proof}
-
-\begin{lem} \label{lem:adaptive}
-Let $U$ be an absolutely continuous random variable with
-pdf $P(du)$. Then the one-bit message $M^\star$ that minimizes
-\[
-\int \left( u - \mathbb E[U|M(u)]  \right)^2 P(du)
-\]
-is given by
-\[
-M^\star  =  \sgn(U - \tau),
-\]
-where $\tau$ is the unique solution to the equation
- \[
-2 \tau = \frac{\int_{\tau}^\infty u P(du)} {\int_{\tau}^\infty P(du)} + \frac{\int_{-\infty}^{\tau} u P(du)}{\int_{-\infty}^{\tau} P(du)}.
-\]
-\end{lem}
-
-Theorem~\ref{thm:opt_one_step} suggests the following Bayesian estimation scheme: set $P_0(t) = \pi(\theta)$, and for $n\geq 1$ update the prior as
-\begin{align}
-P_n(t) = & P(\theta=t |M^n) = \frac{ P\left( \theta=t | M^{n-1} \right) P(M_n | \theta = t , M^{n-1})  } { P(M_n | M^{n-1} )} \nonumber \\ 
-& = \alpha_n  P_{n-1}(t) \Phi\left(M_n \frac{ t - \tau_{n-1} }{\sigma} \right), \label{eq:density_update}
-\end{align}
-where $\alpha_n$ is a normalization coefficient that equals to
-\[
-\alpha_n = \left(\int_{\mathbb R} P_{n-1}(t) \Phi\left(M_n \frac{t- \tau_{n-1} }{\sigma} \right)  dt \right)^{-1}. 
-\]
-The $n$th estimate for $\theta$ is the conditional expectation of $\theta$ given $M^n$, namely
-\begin{equation}
-\theta_n = \mathbb E \left[ \theta| M^n\right] = \int_{-\infty}^\infty t P_n(t) dt. \label{eq:estimator_update}
-\end{equation}
-Next, solve equation \eqref{eq:fixed_point} with the updated prior $P_n(t)$ instead of $P(\theta)$.
-Note that since the standard normal cdf $\Phi(x)$ is log-concave, the updated prior $P_n(t)$ remains log-concave and thus a unique solution to \eqref{eq:fixed_point} is guaranteed by Lemma~\ref{lem:unique}.
-Finally, update the $n+1$th message as
-\begin{equation}\label{eq:message_update}
-M_{n+1} = \sgn(X_{n+1}-\tau_n).
-\end{equation}
-
-Since the equation \eqref{eq:fixed_point} has no analytic solution in general, it is hard to derive the asymptotic behavior of the Bayes estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}.
-We conjecture, however, that it attains the asymptotic relative efficiency of $\sigma^2\pi/2$, as can be observed from the numerical simulation illustrated in Fig.~\ref{fig:adaptive_error}.
-Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the sample mean for the same sample realization.
-
- % In fact, the numerical simulation in Fig.~\ref{fig:simulation} shows that this scheme outperform the estimator of \eqref{eq:sgd_est} even when the prior on $\Theta$ is least favorable for Bayes estimation \cite{Bickel1981}.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}
-\node at (0,0) {\includegraphics[scale=0.4]{error}};
-\end{tikzpicture}
-\caption{Normalized empirical risk $n\left(\widehat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $100$ Monte Carlo trials, where $\theta$ is chosen uniformly in the interval $(-5,5)$.
-\label{fig:adaptive_error}  }
-\end{center}
-\end{figure}
-
-\begin{comment}
-\subsection{Relation to Sigma-Delta Modulation \label{subsec:sdm}}
-The SDM is a device that converts continuous-time analog signals to a discrete-time sequence of binary digits.
-The basic operation of a SDM can be described as follows: the modulator takes as input a sequence of continuous amplitude samples $X_n$, which are typically represents samples of a continuous-time signal taken uniformly at sampling rate $f_s$ much higher than the Nyquist rate of the signal \cite{1095151}.
-The output of the modulator is a sequence $M_n$ of binary values, obtained according to the following rule:
-\begin{align}
-\begin{cases} V_{n+1} & =  V_n - \alpha q(V_n) + X_n, \\
-M_n & = \sgn(V_n)  \end{cases}, \quad n=1,2,\ldots, \label{eq:sdm}
-\end{align}
-where $\alpha > 0$ is a parameter of the modulator that is determined by the maximal value of the input sequence $X^n$.
-The SDM of the form \eqref{eq:sdm} was studied in \cite{53738} under the assumption that the input process $X_n$ is an i.i.d Gaussian process.
-The main results from \cite{53738} shows that regardless of the initial state $V_0$, the process $M_n$ is a stationary ergodic process with mean $\theta$.
-It follows that a consistent estimation of $\theta$ is obtained by taking the mean of the sequence $\{M_n\}$.
-However, the results from \cite{53738} does not provide a closed form for the second order statistics of $\{M_n\}$, so that convergence rate cannot be derived from \cite{53738}.
-\end{comment}
-
 \section{Distributed Estimation \label{sec:distributed}}
@@
 \[
-l(M^n  |\theta ) =  \sum_{i=1}^n \log \left( \Phi \left( M_i \frac{t_i - \theta}{\sigma} \right) \right). 
+l(M^n  |\theta ) = \sigma  \sum_{i=1}^n \log \left( \Phi \left( M_i \frac{t_i - \theta}{\sigma} \right) \right). 
 \]
@@
 
-\subsubsection{Worst case $\theta$} in order to bound the local asymptotic minimax risk it is required to consider the density $\lambda$ that minimizes the worst case $\theta$ in the parameter space $\Theta$.
+{\bf Worst case $\theta$}: in order to bound the local asymptotic minimax risk it is required to consider the desnity $\lambda$ that minimizes the worst case $\theta$ in the parameter space $\Theta$.
 We assume that $\Theta = [-b,b]$ for some $b>0$, and consider
@@
 First note that the condition in the proposition implies that all the moments of $\pi(\theta)$ exists, and in particular its second and third.
-The results follows by expanding the function $1/\eta(x)$ in a power series as
+The results follows by expanding the function $1/\eta(x)$ in a power series around zero as
 \[
@@
 \end{align}
-where $P\left(M_i =1 | \theta, M^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$. We now prove the following Lemma:
-
+where $P\left(M_i =1 | \theta, M^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$.
 Going back to \eqref{eq:adpt_lower_bound_proof:1}, it follows that the Fisher information of $M^n$ with respect to $\theta$ is given by

### 2017-09-26 Writeups/onebit_full_V1.tex
Add files via upload

--- 2017-09-26 Writeups/onebit_distributed_V2.tex
@@
 \usepackage{times}
+
 \usepackage{amsmath} 
@@
 \newcommand{\mmse}{\mathsf{mmse}}
+\newcommand{\unif}{\mathsf{unif}}
 \newcommand{\supp}{\mathrm{supp} }
@@
 %\subsubsection*{Statistical inference under communication constraints}
+{\color{red} Shamir \cite{Shamir} showed that in hide-and-seek hypothesis testing problem, bitrate constraint may lead to a significant reduction in detection performance compared to the unrestricted case.
+This result is then applied to online learning, stochastic optimization and sparse PCA.
+Shamir's results shows that the penalty is in the dimension ($d/R$ instead of $lod(d)$).
+In our setting the dimension is $1$.} \\
+
 Statistical inference problems under communication constraints were considered in information theory in 
@@
 
+\section{Relation to Remote Multiterminal Source Coding \label{sec:ceo}}
+In this section we draw a connection between our general problem of mean estimation from one-bit samples, to the remote multiterminal source coding problem \cite{berger1996ceo}, also known as the CEO problem.
+The setting of the CEO includes $n$ encoders, each has access to a noisy version of a random source sequence.
+% $\left\{ U_j,\,j=1,2,\ldots \right\}$. 
+The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator. \par
+Assuming that $\theta$ is drawn randomly once from a prior $\pi(\theta)$, mean estimation from one-bit under distributed encoding (setting (iii) in the Introduction) corresponds to the CEO setting with block length $k=1$, where the $i$th encoder observes
+\begin{equation}
+\label{eq:Gaussian_channel}
+X_i = \theta + \sigma Z_i,
+\end{equation}
+with $Z_1,\ldots,Z_n$ i.i.d.
+standard normal, and uses $R_i=1$ bits to transmit its observation.
+As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise at each estimate of variance $\sigma^2$, provides a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting.
+ \\
+
+A closed-form expression for the MSE distortion in the CEO is known only for the case where the source sequence is sampled independently from the normal distribution \cite{prabhakaran2004rate}.
+By using the characterization of this minimal distortion as the number of terminals goes to infinity, we conclude the following:
+\begin{prop} \label{prop:ceo_lower_bound}
+Assume that $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$. Then any estimator $\widehat{\theta}_n$ of $\theta$ in 
+the distributed setting satisfies
+\begin{equation} \label{eq:ceo_bound}
+ n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + o(1).
+\end{equation}
+\end{prop}
+
+\begin{proof}
+We consider the expression \cite[Eq. 10]{chen2004upper} that provides the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$:
+\begin{equation} \label{eq:ceo_optimal_sumrate}
+R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
+\end{equation}
+Assuming $R_\Sigma = n$ and $L=n$, we get
+\begin{equation} \label{eq:ceo_optimal_sumrate}
+n = \frac{1}{2} \log \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
+\end{equation}
+The value of $D^\star$ that satisfies the equation above describes the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
+Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed encoding setting.
+By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$, we conclude that
+\[
+D^\star = \frac{ \frac{4\sigma^2}{3} }{n + \frac{4 \sigma^2}{3 \sigma_\theta^2} } + O(e^{-n}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
+\]
+\end{proof}
+Since the lower bound \eqref{eq:ceo_bound}  was derived assuming optimal allocation of the $n$ bits among the encoders, it may seem as if a tighter bound can be obtained in our case by considering the CEO distortion with $R_1=\ldots,R_n = 1$.
+However, an upper bound for the CEO distortion under this condition follows from \cite[Prop.
+5.2]{KipnisRini2017}, and leads to
+\[
+D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
+\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + o(n^{-1}),
+\]
+which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small. \par
+We conclude therefore that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed encoding setting, is attributed exclusively to the ability to perform coding over blocks.
+Namely, the ability to consider $k>1$ independent realizations of $\theta$ versus only one in ours.
+In other words, it is the ability to exploit the geometry of a high-dimensional product space, rather than the distributed nature of the problem, that distinguishes between the CEO distortion and the mean estimation from one-bit samples.\par
+In the next section we show that the ARE in adaptive encoding setting does not exceeds $\pi/2$, and thus provides a tighter lower bound for the distributed encoding setting than $4/3$ of  \eqref{eq:ceo_bound}.
+
+\section{Relation to Decentralized Detection}
+Once the decision rule of each sensor or encoder is fixed, the optimal estimation of $\theta$ is determined using the maximum a posteriori probability rule.
+Hence, the distributed setting is reduced to finding the optimal decision rule of each encoder.
+When the parameter space $\Theta$ is finite, the characterization of the optimal decision rules was considered by Tsitsiklist in \cite{tsitsiklis1988decentralized}.
+It was shown there that if the cardinality of $\Theta$ is at most $M$ and the probability of error criterion is used, than no more than $M(M-1)/2$ different decision rules are necessary in order to attain probability of error decreasing exponentially with the optimal exponent.
+That is, some beyond $M(M-1)/2$ some decision rules can be repeated.
+A version of this problem for the adaptive scenario was also considered in \cite{5751320}, where it was shown that with a specific two-stages feedback, asymptotically there is no gain in feedback compared to the fully distributed setting.
+ \\
+Wei et.
+al.
+\cite{904560} considered the case where a single threshold is applied to all quantizers, and showed how to chose the optimal threshold.
+ARE and minimax ARE of estimation from distributed quantized measurements that is based on Fisher information was considered in \cite{4244748, 6882252, chen2010performance, 5184907}.
+However, the error criterion considered in these works is the Fisher information rather than a risk or ARE criterion.
+Moreover, these works provide optimality conditions only under the assumption the the same quantizer is used at each encoder.
+
 \section{Adaptive Estimation \label{sec:sequential}}
 
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the asymptotic relative efficiency of and adaptive estimator cannot get below $\pi/2$.
-Next, we provide a particular adaptive estimation scheme and show in Theorem~\ref{thm:sgd} that asymptotically attains this efficiency with equality.
-Finally, in Theorem~\ref{thm:opt_one_step} we provide an adaptive estimation scheme that is optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen.
-%While we provide expressions for the optimal message, evaluating the asymptotic efficiency of this estimation scheme turns out to be a challenging task.
-We therefore leave open the question whether this scheme attains the lower bound with equality, and only provide numerical result that support this conjecture.
-\\
+The first main results of this paper, as described in Thm.~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be lower than $\pi/2$.
+Next, we provide a particular adaptive estimation scheme and show in Thm.~\ref{thm:sgd} that its efficiency is $\pi/2$.
+Finally, in Thm.~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen.
+While it is not clear whether the efficiency of this last scheme is $\pi/2$, numerical simulations suggests that the MSE of this scheme times $n$ also converges to $\pi/2$.
 
@@
 % Let $\pi(\theta)$ be an absolutely continuous prior distribution on $\Theta$ with density function converges to zero at the endpoints of the interval $\Theta$. 
-Assumes that $P(d\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-\mathbb E (\theta-\theta_n)^2 \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\pi}{2n}\sigma^2+o(n^{-1}),
+Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
+\[
+\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\pi}{2n}\sigma^2+o(n^{-1}),
 \]
@@
 
-Note that $\theta_0$ is not explicitly defined in 
+In other words, Thm.~\ref{thm:sgd} implies that the estimator $\widehat{\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the minimal asymptotic efficiency as established by Thm.~\ref{thm:adpative_lower_bound}.\par
+Note that $\theta_0$ is not explicitly defined 
 in equation \eqref{eq:sgd_est}.
-Arguably, a reasonable initialization is $\theta_0 = \mathbb E [\theta]$.
-However, Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator, is indifferent to this initialization.
-Thus, the optimal efficiency is attained without using the prior distribution on $\theta$.
-Nevertheless, the bound in Theorem~\ref{thm:adpative_lower_bound} suggests that the estimation error can be greatly reduced whenever the prior of $\theta$ provides a lot of information $I_0$ on its location.
-In order to incorporate this information in a more meaningful way, we present a Bayesian estimation scheme that is conjectured to attain the optimal asymptotic efficiency.
-
-\subsection{One-step Optimal Estimation}
-In this subsection we present an estimation scheme that posses the property of \emph{one-step optimality}.
-That is, at each step $i$, the $i$th encoder designs the detection region $M_i^{-1}(1)$ such that the MSE given $M^i$ is minimal.
+While a reasonable initialization is $\theta_0 = \mathbb E [\theta]$,  Thm.~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
+Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the size of the parameter space $\Theta$.
+Nevertheless, the bound in Thm.~\ref{thm:adpative_lower_bound} suggests that the non-asymptotic estimation error can be greatly reduced whenever the location information $I_0$ is large.
+In contrast, the one-step optimal scheme presented in the following subsection exploits the prior information on $\theta$ provided by $\pi(\theta)$.
+
+\subsection{One-step optimal estimation}
+We now consider an estimation scheme that posses the property of \emph{one-step optimality}: at each step $i$, the $i$th encoder designs the detection region $M_i^{-1}(1)$ such that the MSE given $M^i$ is minimal.
 In other word, this scheme designs the messages in a greedy manner, such that the MSE at step $i$ is minimal given the current state of the estimation described by $M^{i-1}$.
@@
 \end{lem}
-
-Theorem~\ref{thm:opt_one_step} suggests the following Bayesian estimation scheme: set $P_0(t) = \pi(\theta)$, and for $n\geq 1$ update the prior as
+\end{proof}
+
+\begin{rem}
+The value of the optimal threshold as given in Theorem~\ref{thm:opt_one_step} is different than the one given in \cite[Eq.
+5]{1619423} for apparently the same problem.
+Indeed, it seems like Equation 4 there is erroneous.
+\end{rem}
+
+Thm.~\ref{thm:opt_one_step} suggests the following adaptive encoding and estimation scheme: 
+\begin{itemize}
+\item Initialization: set $P_0(t) = \pi(\theta)$.
+\item For $n\geq 1$:
+\begin{enumerate}
+\item Update the prior as
 \begin{align}
-P_n(t) = & P(\theta=t |M^n) = \frac{ P\left( \theta=t | M^{n-1} \right) P(M_n | \theta = t , M^{n-1})  } { P(M_n | M^{n-1} )} \nonumber \\ 
+P_n(t) = & P(\theta=t |M^n) \\
+& = \frac{ P\left( \theta=t | M^{n-1} \right) P(M_n | \theta = t , M^{n-1})  } { P(M_n | M^{n-1} )} \nonumber \\ 
 & = \alpha_n  P_{n-1}(t) \Phi\left(M_n \frac{ t - \tau_{n-1} }{\sigma} \right), \label{eq:density_update}
@@
 \end{equation}
-Next, solve equation \eqref{eq:fixed_point} with the updated prior $P_n(t)$ instead of $P(\theta)$.
-Note that since the standard normal cdf $\Phi(x)$ is log-concave, the updated prior $P_n(t)$ remains log-concave and thus a unique solution to \eqref{eq:fixed_point} is guaranteed by Lemma~\ref{lem:unique}.
-Finally, update the $n+1$th message as
+\item Solve equation \eqref{eq:fixed_point} with the updated prior $P_n(t)$ instead of $P(d\theta)$.
+Note that since the standard normal cdf $\Phi(x)$ is log-concave, the updated prior $P_n(t)$ remains log-concave and thus a unique solution to \eqref{eq:fixed_point} is guaranteed by Lem.~\ref{lem:unique}.
+\item Update the $(n+1)$th message as
 \begin{equation}\label{eq:message_update}
-M_{n+1} = \sgn(X_{n+1}-\tau_n).
-\end{equation}
-
-Since the equation \eqref{eq:fixed_point} has no analytic solution in general, it is hard to derive the asymptotic behavior of the Bayes estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}.
+M_{n+1} = \sgn(X_{n+1}-\tau_n)
+\end{equation}
+\end{enumerate}
+\end{itemize}
+Since equation \eqref{eq:fixed_point} has no analytic solution in general, it is hard to derive the asymptotic behavior of the estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}.
 We conjecture, however, that it attains the asymptotic relative efficiency of $\sigma^2\pi/2$, as can be observed from the numerical simulation illustrated in Fig.~\ref{fig:adaptive_error}.
-Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the sample mean for the same sample realization.
-
- % In fact, the numerical simulation in Fig.~\ref{fig:simulation} shows that this scheme outperform the estimator of \eqref{eq:sgd_est} even when the prior on $\Theta$ is least favorable for Bayes estimation \cite{Bickel1981}.
+Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the asymptotically optimal estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the sample mean for the same sample realization.
 
@@
 \begin{tikzpicture}
-\node at (0,0) {\includegraphics[scale=0.4]{error}};
+\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
+%\node[color = blue,  minimum width=1cm, align = left] at (1.5,1.5) {assymptotically optimal \eqref{eq:sgd_est}};
+%\node[color = red, minimum width=1cm, align = left] at (1.5,0.55) {one-step optimal \eqref{eq:message_update}} ;
+\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left(\widehat{\theta}_n - \theta \right)^2$};
+\node[scale = 0.7] at (0,-2.4) {$n$};
+%\draw[dashed] (-3.5,1.18) node[left, scale = 0.7] {$\frac{\pi}{2}$}-- (-3,1.18);
 \end{tikzpicture}
-\caption{Normalized empirical risk $n\left(\widehat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $100$ Monte Carlo trials, where $\theta$ is chosen uniformly in the interval $(-5,5)$.
+\caption{Normalized empirical risk $n\left(\widehat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $500$ Monte Carlo trials.
+In each trial, $\theta$ is chosen uniformly in the interval $(-3,3)$.
 \label{fig:adaptive_error}  }
@@
 \[
-l(M^n  |\theta ) =  \sum_{i=1}^n \log \left( \Phi \left( M_i \frac{t_i - \theta}{\sigma} \right) \right). 
-\]
-Since $\Phi(x)$ is a log concave function, the log-likelihood function has a unique maximizer $\widehat{\theta}_n$ which is the ML estimator.  \\
-
-Next, we show that under the assumptions above, the sequence of messages $M^n$ defines a local asymptotic normal (LAN) family of probability distributions.
+l(M^n  |\theta ) = \sigma  \sum_{i=1}^n \log \left( \Phi \left( M_i \frac{t_i - \theta}{\sigma} \right) \right). 
+\]
+Since $\Phi(x)$ is a log concave function, the log-likelihood function has a unique maximizer $\widehat{\theta}_n$ which is the ML estimator.
+Specifically, the ML estimator $\widehat{\theta}_{ML}$ is the unique root of
+\[
+\sum_{i=1}^n M_i \frac{\phi \left( \frac{t_i-\theta}{\sigma}\right) }{\Phi \left(M_ii \frac{t_i-\theta}{\sigma}\right) }
+\]
+
+Next, we show that under the assumptions above the sequence of messages $M^n$ defines a local asymptotic normal (LAN) family of probability distributions.
 Therefore, the MSE in estimating $\theta$ from the messages $M^n$ satisfies a local asymptotic minimax property with respect to the \emph{precision} parameter of this LAN family \cite{van2000asymptotic}.
@@
 
+\begin{rem}
+The condition that $\lambda_n$ converges weakly to $\lambda$ can be relaxed to the condition
+\[
+\frac{1}{n} \sum_{i=1}^n  \eta \left( \frac{t_i-\theta}{\sigma} \right)  \overset{n \rightarrow \infty}\longrightarrow \int \eta \left( \frac{t-\theta}{\sigma} \right) \lambda(dt)
+\]
+(pointwise for any $\theta \in \Theta$). 
+\end{rem}
+
 \subsubsection*{Sketch of Proof}
@@
 
-\subsubsection{Worst case $\theta$} in order to bound the local asymptotic minimax risk it is required to consider the density $\lambda$ that minimizes the worst case $\theta$ in the parameter space $\Theta$.
-We assume that $\Theta = [-b,b]$ for some $b>0$, and consider
+\subsection{Worst case $\theta$}
+Next, we consider the threshold density $\lambda$ that minimizes the asymptotic risk over the worst choice of $\theta$ in the parameter space $\Theta$, namely
 \begin{equation} \label{eq:variational}
-\sup_{\lambda} \inf_{\theta \in [-b,b]}  {K(\theta)} = \int \eta\left( \frac{t-\theta}{\sigma} \right) \lambda (dt),
-\end{equation}
-where the suprimum is over all probability measure $\lambda$ on $\mathbb R$. Since \eqref{eq:variational} is concave in $\lambda$, this optimization problem can be solved using a convex program. 
-As illustrated in Fig.~\ref{fig:cvx}, the threshold density that maximizes \eqref{eq:variational} is supported over a discrete set in the interval $[-b,b]$.
-Fig.~\ref{fig:cvx2} illustrates the asymptotic ML risk as a function of the length $2b$ of the parameter space $\theta$.
+\sup_{\lambda} \inf_{\theta \in \Theta}  {K(\theta)} = \int \eta\left( \frac{t-\theta}{\sigma} \right) \lambda (dt),
+\end{equation}
+where the supremum is over all probability measure $\lambda$ on $\mathbb R$.
+By setting $\Theta = (-b \sigma, b \sigma)$ for some $b >0$, the supremum in \eqref{eq:variational} is independent of $\sigma$ and we can write
+\begin{equation} \label{eq:variational2}
+K^\star(b) = \sup_{\lambda} \inf_{\tau \in (-b,b)}  \int \eta\left( t-\tau \right) \lambda (dt).
+\end{equation}
+In order to evaluate $K^\star(b)$, we consider the following variational optimization problem:
+\begin{align}
+\label{eq:var_cvx_minimax}
+\mathrm{maximize} \quad &  \inf_{\tau \in (-b,b)} \int \eta(t-\tau) \lambda(dt)
+\\ \nonumber
+\mathrm{subject~to} 
+\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
+\end{align}
+Since the objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda$, this problem can be solved using a convex program.
+In fact, by discretizing the interval $(-b,b)$ using $N_\tau$ values $\tau_1,\ldots,\tau_{N_\tau}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
+\begin{align}
+\label{eq:cvx_minimax}
+\mathrm{maximize} \quad &  K 
+\\ \nonumber
+\mathrm{subject~to} 
+\quad &  K \leq \mathbf H\lambda \\
+& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
+\end{align}
+where $H_{i,j} = \eta(t_i - \tau_j)$. 
+\begin{rem}
+The number of variables in problem \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\tau$.
+Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\tau}$ points.
+\end{rem}
+
+The solution $\lambda^\star$ to \eqref{eq:cvx_minimax} and the function $\mathbf H \lambda^\star$ are illustrated in Fig.~\ref{fig:minimax_support}, for various values of the support size of the parameters space $b$.
+The minimal asymptotic ML risk as a function of $b$ is illustrated in Fig.~\ref{fig:minimax_optval}.
 
@@
 \begin{tikzpicture}
-\node[int] at (0,0)  {\includegraphics[scale=0.2]{support_b20}};
-\node[int] at (4.1,0)  {\includegraphics[scale=0.2]{support_b10}};
-\node[int] at (0,3.2)  {\includegraphics[scale=0.2]{support_b5}};
-\node[int] at (4.1,3.2)  {\includegraphics[scale=0.2]{support_b1}};
+\node[int] (b1) at (0,0)  {\includegraphics[scale=0.25]{minimax_b1}};
+\node[int] (b2) at (4.1,0)  {\includegraphics[scale=0.25]{minimax_b2}};
+\node[int] (b3) at (0,-3)  {\includegraphics[scale=0.25]{minimax_b5}};
+\node[int] (b4) at (4.1,-3)  {\includegraphics[scale=0.25]{minimax_b10}};
+\node[int] (b5) at (0,-6)  {\includegraphics[scale=0.25]{minimax_b50}}; 
+\node[int] (b6) at (4.1,-6)  {\includegraphics[scale=0.25]{minimax_b100}}; 
 \end{tikzpicture}
-\caption{\label{fig:cvx}
-Support of the optimal density $\lambda$ that minimizes the asymptotic ML risk for the worst choice of $\theta \in [-\sigma b, \sigma b]$ (blue), for $b=1,5,10,20$ (clockwise).
-The red curve is the value of $K(\theta)$ under this density.
+\caption{\label{fig:minimax_support}
+Support of the optimal density $\lambda^\star$ that minimizes the asymptotic ML risk for the worst choice of $\theta \in (-\sigma b, \sigma b)$ where the parameter space is the interval $(-b,b)$, for $b=1,2,5,10,50,100$.
+The continuous curve represents the inverse of the asymptotic risk under the optimal density and the dashed curves corresponds the inverse of the asymptotic risk under a uniform distribution over $(-a,a)$ with $a = b+2$.
 }
@@
 \begin{tikzpicture}
-\node at (0,0)  {\includegraphics[scale=0.25]{K_vs_b}};
+\node at (0,0)  {\includegraphics[scale=0.35]{K_vs_b}};
+\node at (0,-2) {$2b$};
+\node[rotate = 90] at (-2.5,0) {$2b/K^\star$};
 \end{tikzpicture}
-\caption{\label{fig:cvx2}
-Asymptotic risk of the ML estimator under an optimal choice of the threshold density $\lambda$ versus the support of the parameter space $\Theta$.
+\caption{\label{fig:minimax_optval}
+Asymptotic risk of the ML estimator under an optimal choice of the threshold density $\lambda$ versus the support of the parameter space $\Theta = (-b,b)$.
 }
@@
 
-\subsection{Average Asymptotic Risk}
+\subsection{Uniform Threshold Distribution}
+We now consider the case where the threshold distribution $\lambda$ is uniform over the range $(-a,a)$ for some $a>0$, namely
+$\lambda(dt) = dt/(2b\sigma)$. The asymptotic ML risk in this case is $\sigma^2$ times the inverse of
+\begin{equation}
+K_{\unif} = \inf_{\theta \in (-b\sigma,b\sigma)} \frac{1}{2b\sigma}\int_{-b\sigma}^{b\sigma} \eta\left(\frac{t-\theta}{\sigma}\right) dt =  \frac{1}{2b}\int_{-b}^{b} \eta(t-b) dt = \frac{1}{4b}\int_{-b}^b \eta(t) dt.
+\label{eq:uniform_risk}
+\end{equation}
+The value of $K_{\unif} / (2b)$ is illustrated in Fig.~\ref{fig:minimax_optval}.
+
+\subsection{Asymptotic Bayes Risk}
 Consider problem of minimizing the expected asymptotic risk $\mathbb E[ \sigma^2/K(\theta)]$ over all probability measures $\lambda(dt)$. This optimization problem can be written as follows:

### 2017-09-26 Writeups/sketch_distributed_scaling.tex
Add files via upload

--- 2017-09-26 Writeups/onebit_adpative_Allerton.tex
@@
 %
-\author{
-\IEEEauthorblockN{Alon Kipnis}
-\IEEEauthorblockA{Department of Electrical Engineering \\
-Stanford University\\
-Stanford, CA\\}
-\and
-\IEEEauthorblockN{John C. Duchi}
-\IEEEauthorblockA{Department of Electrical Engineering \\
-and Department of Statistics \\
-Stanford University\\
-Stanford, CA\\}
-}
+%\author{
+%\IEEEauthorblockN{Alon Kipnis}
+%\IEEEauthorblockA{Department of Electrical Engineering \\
+%Stanford University\\
+%Stanford, CA\\}
+%\and
+%\IEEEauthorblockN{John C. Duchi}
+%\IEEEauthorblockA{Department of Statistics \\
+%and Department of Electrical Engineering \\
+%Stanford University\\
+%Stanford, CA\\}
+%\and
+%\IEEEauthorblockN{Andrea J. Goldsmith}
+%\IEEEauthorblockA{Department of Electrical Engineering \\
+%Stanford University\\
+%Stanford, CA\\}
+%}
 
@@
 \pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-We consider the problem of estimating the mean of a normal distribution under the constraint: that the estimator can access only a single bit per sample from this distribution.
-We study the squared error in this estimation as a function of the number $n$ of samples and single-bit measurements in an adaptive setting.
-We show that if at each stage $n$, this single bit is a function of both the new sample and the previous $n-1$ acquired bits, then no estimator can attain asymptotic squared error smaller than $\pi/(2n)$ times the variance.
-Therefore, we conclude that a strict bit limitation increases the number of samples required for a prescribed accuracy by a factor of at least  $\pi/2$ compared to the unrestricted case.
-In addition, we provide an explicit estimator that attains this asymptotic error, showing that, rather surprisingly, only $\pi/2$ times more samples are required in order to attain performance equivalent to the unrestricted case.
-\end{abstract}
-
-%{\color{red}  The $\mu$-sum problem (Kim-ElGamal Ch. 21) gives a lower bound. Can be reduced to the CEO.}
-
-%{\color{red}  See LASSO results in http://arxiv.org/abs/1506.02181v1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{sec:Intro}
-
-Processing and estimating information from data collected at multiple physical location may be subject to communication constraints. 
-%For example, emerging sensor network technologies in medicine and ``smart cities" use many low-cost sensors to collect large amounts of data and transmit it to remote locations.
-These sensors must operate under severe power restrictions, hence they are limited by their communication bandwidth.
-For example, consider large-scale sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit.
-In this scenario, the ability to estimate a particular parameter from data collected by the sensors is dictated not only by quality of observations and their numbers, but also by the constraint on the communication rates between the sensors.
-The question that we ask is to what extend a parametric estimation task is affected by such communication constraint, and what are the fundamental performance of estimation subject to these restrictions.
-\\
-
-In this paper we provide an answer to this question in a particular simple setting: the estimation of the mean $\theta$ of a normal distribution with a known variance $\sigma^2$, under the constraint that given the $n$th sample $X_n$, only a single bit can be communicated to the estimator.
-Specifically, the $n$th encoder observes $X_n$ and the $n-1$ previous single bit messages $M_1,\ldots,M_{n-1}$, and delivers a single bit message $M_n$ to the estimator.
-The estimator provides an estimate $\widehat{\theta}_n$ based on $M^n = (M_1,\ldots,M_n)$.
-
- \item[(iii)] \emph{Distributed} encoding: the output of the $n$th encoder is a single bit that is only a function of $X_n$.
- \end{itemize}
-Clearly, as far as information sharing is concerned, settings (iii) is a more restrictive version of (ii) which is more restrictive than (i).
-We measure the estimation performance by the mean squared error (MSE) risk.
-Since without bit constraint this risk is known to be $\sigma^2/n$, we are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting, defined as the ratio between their MSE to $\sigma^2/n$ as $n$ goes to infinity.
-%\par
-%Maybe explain here why the problem is interesting ? 
-%setting (i), setting (ii) + SDM, setting (iii) + CEO.
-%The turn to 1) main results and 2) other previous works. 
-%
-\par
-Classical works on statistical estimation under communication constraint in information theory \cite{720540, zhang2013information, zhang1988estimation} implies that the ARE in setting (i) is $1$.
-Namely, asymptotically, there is no loss in performance in this setting due to the communication constraint.
-Indeed, under setting (i) the sample mean can be described by an encoder with an exponentially decaying error, leading to MSE of $\sigma^2/n + o(2^{-n})$.
-In this work we show that a similar result does not hold even in setting (ii): the relative efficiency of any adaptive estimator is at least $\pi/2$.
-Namely, the single-bit per sample constraint incurs a minimal penalty of at least $\approx 1.57$ compared to an unconstrained estimator or to the optimal estimator in setting (i).
-In addition to this negative statement, we provide an estimator that almost surely attains this minimal relative efficiency.
-In other words, we show that the lower bound of $\pi/2$ on the asymptotic relative efficiency is tight, and that it is attained regardless of the particular realization of $\theta$ or the size of the parameter space from which it is taken.
-Clearly, the minimal penalty on the efficiency of $\pi/2$ also holds under setting (iii), although the question whether such efficiency is achievable (or otherwise, what is the minimal efficiency) remains open.
-\\
-
-\subsection{Relate Works}
-The parametric estimation problem we consider is closely related to many works in statistics and information theory.
-Statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation} includes as a special case the problem of estimating a single vector of parameters from multiple data-rate constrained observations.
-These inference problems were studied in the asymptotic limit as the number of observations goes to infinity.
-In this asymptotic setting the unconstrained inference performance is always attained when all samples are taken from the same distribution \cite[Sec.
-III]{720540}.
-Indeed, in an i.i.d setting the \emph{type} of the sample is a sufficient statistics for any estimation task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples.
-For this reason in \cite{han1987hypothesis} and \cite{zhang1988estimation} attention is given to inference problems involving multiple distributions observed at different locations.
-Setting (i) above can be seen as a special case of the above works where the communication is limited to a single-bit per terminal.
-In fact, with a full access to the sample prior to encoding, the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample \cite{gray1998quantization}.
-%On the other hand, setting (iii) arises as the number of terminals grow with $n$ and their communication rates are limited to a single bit.
-
-This last situation is also obtained by the multiterminal source coding setting, a.k.a.
-the CEO problem \cite{berger1996ceo} can be seen as a generalization of our setting (iii), where multiple draws of $\theta$ and rounds of $n$ bit communication is permitted.
-In particular, the minimal CEO distortion with $1$ bit per terminal provides a lower bound on the MSE risk.
-
-In fact, with a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample \cite{gray1998quantization}.
-The sigma-delta modulatior (SDM) \cite{1092194} uses a single bit quantizer with a feedback loop, and therefore falls under setting (ii).
-The SDM with a constant input $\theta$ corrupted by a Gaussian noise was considered in \cite{53738}, where it was shown that the output of the modulator converges to the true constant input.
-Therefore, the SDM provides a consistent estimator for setting (ii).
-The rate of this convergence, however, was not analyzed and cannot be derived directly from the results of \cite{53738}.
-In fact, the results of this paper implies that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-\par
-
-%
-Estimation problem subject to the one-bit quantization constraint were also considered in compressed sensing \cite{boufounos20081,baraniuk2017exponential} and in MIMO detection in wireless communication \cite{singh2009limits}.
-
-The rest of this paper is organized as follows: the main problem and notation are defined in Section~\ref{sec:problem}.
-In Section~\ref{sec:sequential} we present a lower bound on estimation from one-bit samples in the adaptive scheme, as well as an achievable scheme that attains this bound.
-Concluding remarks are given in Section~\ref{sec:conclusions}.
-
-\section{Motivation and Related Works}
-Standard considerations implies that the optimal encoding in setting (i) is reduced to an optimal $n$ bits description of the  sample mean.
-The standard technique to encode an unknown random quantity using $n$ bits is attained by an optimal scalar quantizer.
-However, the design of this quantizer depends on the distribution of its input \cite{gray1998quantization}, which is the goal of the estimation.
-Therefore, although the ARE in this setting is shown to be one \cite[Sec.
-III]{720540}, we see that a non-trivial challenge arise even in this case.
-In setting (ii), the above challenge of optimal quantizer design with imprecise input distribution occurs upon the the arrival of each new sample $X_n$.
-
-%sigma delta modulator
-
-%implies the existence of a consistent estimator in this case
-
-% our result provides a lower bound for the accuracy of a sigma-delta modulator
-
-Setting (ii) and (iii) were considered in 
-\cite{zhang2013information} under the more general assumption of $m$ machines each has access to $n/m$ independent samples.
-The main result of \cite{zhang2013information} are lower bounds on the estimation error as a function of the total number of bits $R$ with which each machine can communicate.
-Our settings corresponds to the case $m=n$ and $R=1$, and our result is a fundamental lower bound and a matching achievable scheme under this simplified setting.
-
- We also note that the counterpart of setting (iii) in the case of hypothesis testing was considered in \cite{52470}.
-
- The optimal design  requires the distribution of the input, which is the goal of estimation and is known appriori.
-
- standard technique to encode an unknown random quantity using $n$ bits is attained by an optimal scalar quantizer,  by designing a scaler quantizer Unlike standard quantization task of encoding an unn
-
-%Note that when multiple realization of $\theta$ are involved, the prior distribution $P_\theta$ plays a significant role in the overall MSE, whereas in our case we expect the final distortion to be independent of the actual prior distribution as in the two schemes in the sequential case.
-\\
-
-\subsection{Intuition from Remote Multiterminal Source Coding}
-A first clue for this rather surprising result can be seen drawing the connection between our parametric estimation problem to the remote multiterminal source coding problem of \cite{berger1996ceo}, also known as the CEO problem.
-The CEO setting considers $n$ encoders, each has access to a corrupted version of a source signal.
-The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator.
-Therefore, assuming that $\theta$ is drawn randomly from a prior $\pi(\theta)$, the distributed estimation setting (iii) corresponds to the CEO setting with $k=1$, where the $i$th agent observes
-\begin{equation}
-\label{eq:Gaussian_channel}
-X_i = \theta + Z_i,
-\end{equation}
-and has $R_i=1$ bits to transmit this observation.
-As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise of variance $\sigma^2$ provides a lower bound on the MSE distortion in estimating $\theta$.
-In fact, the difference between this lower bound and the actual MSE in our setting indicates the importance of coding over blocks consisting of $k$ independent realizations of $\theta$ versus $k=1$ in our setting.
-\par
-A closed-form expression for CEO under quadratic distortion is known only for the case where the sequence to described by the encoders is sampled from a Gaussian distribution \cite{prabhakaran2004rate}.
-By using the characterization of the minimal CEO distortion as the number of terminals goes to infinity, we conclude the following:
-\begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\pi(\theta)$ is the normal distribution. Then any estimator $\widehat{\theta}_n$ of $\theta$ in the distributed setting satisfies
-\[
- n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + o(1).
-\]
-\end{prop}
-
-\begin{proof}
-We consider the expression \cite[Eq. 10]{chen2004upper} that provides the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots R_L$:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-Assuming $R_\Sigma = n$ and $L=n$ we get
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-n = \frac{1}{2} \log \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-The value of $D^\star$ that satisfies the equation above describes the MSE in the quadratic Gaussian CEO setting under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$ we conclude that
-\[
-D^\star = \frac{ \frac{4\sigma^2}{3} }{n + \frac{4 \sigma^2}{3 \sigma_\theta^2} } + O(e^{-n}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-\end{proof}
-We note that although the CEO lower bound was derived by the MSE attainable assuming optimal allocation a total of $n$ bits among the encoders, the same expression is from the upper bound to the CEO derived in \cite[Prop.
-5.2]{KipnisRini2017}, that assumes $R_1=\ldots,R_n = 1$ rather than optimal allocation of $n$ bits among all encoders.
-%\[
-%D_{CEO} / \sigma_\theta^2 \leq \left( 1 + \sum_{i=1}^n \frac{\sigma_\theta^2}{\sigma^2} \frac{1 - 2^{-2R_i}} {1+ \frac{\sigma_\theta^2}{\sigma^2}  2^{-2 R_i}  } \right)^{-1}
-%\]
-%where $\sigma_\theta^2$ is the variance of the distribution $\pi(\theta)$. Using $R_1=\ldots=R_n=1$ we get
-%\[
-%D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + o(n^{-1}). 
-%\]
-
-Statistical inference problems under communication constraints in the nature of our setting were considered in information theory in 
-\cite{han1987hypothesis, zhang1988estimation, 720540}.
-These works consider a multi-terminal source coding setting in which the $i$th terminal observes $n$ samples from the distribution and is allotted $nR_i$ bits to communicate its estimate.
-The main focus of these works is the difference between inference with communication constraint and the unconstrained vanilla statistical estimation setting, as the number of samples $n$ goes to infinity subject to a total finite rate constraint.
-Our setting (i) can be seen as a special case of this setting where with a single terminal and $R_1 = 1$.% whereas our case (iii) is obtained from this setting by taking $n=1$, $R_i=1$, and number of terminals grow with $n$.
-However, as explained in \cite[Sec.
-III]{720540}, a single terminal in this setting always lead to the unconstrained inference performance.
-Indeed, when all samples are taken from the same distribution, the \emph{type} of the sample \cite{csiszar1998method} is a sufficient statistics for any inference task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples.
-For this reason, attention is given in these works to inference problems involving multiple distributions observed at different locations and hence the results there do not apply to our setting.
-In fact, with a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample.
-Finally, we note that setting (ii) includes as a special case the sigma-delta modulation (SDM) analog-to-digital conversion scheme with a constant input $\theta$ corrupted by Gaussian noise $Z_i$, as was considered in \cite{53738}.
-While it was shown there that the output of the modulator converges to the true constant input, the rate of this convergence was not analyzed and cannot be derived directly from the results of \cite{53738}.
-In fact, a corollary from the results in this paper we conclude that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-Finally, the multiterminal source coding setting denoted as the CEO problem \cite{berger1996ceo} can be seen as a generalization of our setting (iii), where multiple draws of $\theta$ and rounds of $n$ bit communication is permitted.
-In particular, the minimal CEO distortion with $1$ bit per terminal provides a lower bound on the MSE risk.
-\par
-
-%Why it is surprising that the estimator is independent of $\theta$, $\Theta$ or $\pi(\theta)$.
-
-\subsection{Related Works}
-\subsubsection*{Statistical inference under communication constraints}
-The problem of statistical inference under communication constraint has a long and rich history in statistics and information theory.
-Statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation} includes as a special case the problem of estimating a single vector of parameters from multiple data-rate constrained observations.
-These inference problems were studied in the asymptotic limit as the number of observations goes to infinity.
-The main question asked there is the difference between inference with communication constraint and the unconstrained vanilla statistical estimation setting.
-In this asymptotic setting the unconstrained inference performance is always attained when all samples are taken from the same distribution \cite[Sec.
-III]{720540}.
-Indeed, in an i.i.d setting the \emph{type} of the sample is a sufficient statistics for any estimation task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples.
-For this reason in \cite{han1987hypothesis} and \cite{zhang1988estimation} attention is given to inference problems involving multiple distributions observed at different locations.
-Setting (i) above can be seen as a special case of \cite{han1987hypothesis, zhang1988estimation, 720540} where the communication is limited to a single-bit per terminal.
-
-%\subsubsection{Estimation from 1-bit measurements}
-%Single-bit or binary detectors are the basis for digital technology, and works considers the estimation of parameters from the results of such detectors have been around from the early days of digital computing.
-The burst of works in compressed sensing in the previous decade also gave raise to multiple 1-bit results \cite{rice_university}.
-Due to the popularization of MIMO technology and the expected break of mm-wave in wireless communication there have been many works 1-bit detection at the A/D in the receiver \cite{2016arXiv160204193Z}.
-
-\subsubsection*{Relation to channel coding}
-The problem we consider is the estimation of the parameter $\theta$ by observing 
-\begin{equation}
-\label{eq:channel}
-X_i = \theta + Z_i, \quad i=1,\ldots,n,
-\end{equation}
-where the $Z_i$s are independent, centered normal with variance $\sigma^2$.
-The problem of estimating $\theta$ from the $X_i$s can be seen as the attempt to transmit a real number $\theta$ over an additive white Gaussian noise (AWGN) channel.
-In particular, setting (ii) can be seen as the feedback version of this transmission, which is closely related to \cite{horstein1963sequential, 1053879}.
-However, in our setting $\theta$ is either fixed or drawn once from a prior distribution, so the communication in \eqref{eq:channel} is limited to a repetition code.
-Moreover, in setting (ii) we have the additional constraint that the message is a causal function of the previous messages, where in case (iii) it is completely memoryless.
-Works in information theory which consider such setting includes AWGN channel with 1-bit ADC at the receiver \cite{DBLP:journals/corr/VarastehSG16}.
-\par
-
-\subsubsection*{Relation to source coding}
-With a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample.
-Setting (ii) includes as a special case the sigma-delta modulation (SDM) analog-to-digital conversion scheme with a constant input $\theta$ corrupted by Gaussian noise $Z_i$, as was considered in \cite{53738}.
-While it was shown there that the output of the modulator converges to the true constant input, the rate of this convergence was not analyzed and cannot be derived directly from the results of \cite{53738}.
-As a corollary from the results in this paper we conclude that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-Finally, the remote multiterminal source coding setting of \cite{berger1996ceo} corresponds to the case of $n$ rate-constrained encoders, each observing a noisy version of an information source.
-The difference between this setting and ours is that in ours the parameter of interest is not an information source.
-By assuming a prior distribution on this parameter, the CEO provides a lower bound on the estimation error in the fully distributed setting (iii).
-This lower bound can be attained if we were to consider the average error in multiple independent realizations of our problem rather than a single realization as we do here.
-\\
-
-%As opposed to the aforementioned line of works, we focus on estimation of samples taken from a single distribution in the finite blocklength performance.
-We are interested in particular in addition restrictions on the communication and information sharing between the encoders.
-For example, our main focus is the case where the observer must communicate a single bit upon drawing from the distribution.
-This is in contrast to the asymptotic setting where the observer can encode the outcome of $n$ draws at once using a single $n$ bit message.
-Alternately, such setting can be seen as having $n$ different observers, each is capable of observing a single realization and transmit a single bit.
-
-%{\color{red} The Van Trees inequality was extended to the estimation of multiple parameters in \cite{bobrovsky1987}. It is closely related with the }
-
-\begin{comment}
-\subsection{Sigma-Delta Encoding}
-
-and covariance function \cite[Eq. 25]{53738}
-\[
-R(k) = \mathbb E M_{n+k} M_n = \theta^2 + O \left( \frac{1}{\sigma \sqrt{ k} } \right). 
-\]
-{\color{red} This is not enough to deduce convergence. Need to go over the paper and check if rate of convergence can be deduced. Also do simulations BEFORE that. \\
-
-What is the error in estimating the mean of stationary ergodic process ? 
-}
-Since the SDM is a special case of the sequential scheme, we conclude that the MSE of any SDM with a noisy DC signal is bounded from below by $n^{-1} \sigma^2 \pi/2 $.
-\end{comment}
-
-The rest of this paper is organized as follows: the main problem and notation are defined in Section~\ref{sec:problem}.
-Our main results are presented and discussed in Section~\ref{sec:sequential}.
-Concluding remarks are given in Section~\ref{sec:conclusions}.
-
-%Even with such arguably simple setting, we will see that the performance limit in the estimating task based on single bit observations provides an interesting setting for discussion that bridges classical works in statistics, coding theory, information theory and optimization.
-
-\section{Problem Formulation \label{sec:problem}}
 
@@
 \draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M_2 \in \left\{-1,1\right\}$} (est);
-\draw[->] (mes1) -- +(0,-0.7) -| (enc2);
 
-\draw[dashed,->] (mes2) -- +(0,-0.7) -| +(-2,-1.2);
 \draw[->,line width = 2pt] (enc3) -| (est);
 
-\node[below of = mes2, node distance = 1.5cm] (mes3) {$M_1,\ldots,M_{n-1} $};
-
 \draw[->,line width = 2pt] (enc3) -| node[above, xshift = -2cm]  {$M_n \in \left\{-1,1\right\}$} (est);
-
-\draw[->] (mes3) -- +(0,-0.5) -| (enc3);
 
@@
 \end{center}
-\caption{\label{fig:sequential} Adaptive single-bit encoding: the $i$th encoder delivers a single bit message which is a function of its private sample $X_i$ and the previous messages $M_1,\ldots,M_{i-1}$.}
+\caption{\label{fig:sequential} Distributed single-bit encoding.}
 \end{figure}
 
-Let $X_i$, $i=1,\ldots,n$, be $n$ independent samples from the normal distribution $\mathcal N(\theta,\sigma^2)$ with mean $\theta$ and variance $\sigma^2$.
-We assume that the mean $\theta$ is drawn once from a prior distribution $\pi(\theta)$ on the parameter space $\Theta$, which is a closed interval of the real line.
-We moreover assume that $\pi(\theta)$ is absolutely continuous with respect to the Lebesgue measure with density $\pi(d\theta)$.
-The problem we consider is the estimation of the parameter $\theta$ under the following constraints on the communication between the samples $X_1,\ldots,X_n$ and a centralized estimator:
-\begin{itemize}
-\item[(i)] The estimator at time $n$ is only a function of the $n$ messages $M^n = \left(M_1,\ldots,M_n \right)$.
-\item[(ii)] For each $i=1,\ldots,n$, the $i$th message $M_i$ is a function of the sample $X_i$ and the $i-1$ previous messages $M^{i-1}$.
-\item[(iii)] The $i$th message $M_i$ takes only two possible values, say $1$ and $-1$. 
-\end{itemize}
-In other words,  the $n$ messages $M^n$ are the only information on the sample $X^n = \left(X_1,\ldots,X_n\right)$ available to the estimator.
-The $i$th message is defined by a function from the real line to $\{-1,1\}$, measurable with respect to the sigma algebra generated by $M^{i-1}$ and $X_i$.
-The estimator, upon observing $M^n$, produces an estimate $\widehat{\theta}_n(M^n)$ of $\theta$.
-A system describing the above scheme is illustrated in Fig.~\ref{fig:sequential}.
-\\
+Consider the distributed 1-bit estimation setting of Fig.~\ref{fig:sequential} where $X_n = Z_n + \theta$ with $Z_n$ zero mean and variance $\sigma^2$.
+Upon observing the $n$th sample $X_n$, the estimator is observing $M_n(X_n) \in \{0,1\}$, where the mapping $M_n : \mathbb R \rightarrow \{0,1\}$ are determined offline in a manner that will be explained below.
+Denote $A_n = M_n^{-1}(1)$ and set
+\[
+U_n = \begin{cases} 1, & \theta \in A_n \\
+-1, & \theta \notin A_n. 
+\end{cases}
+\]
+So the $U_n$s are binary random variables that depends only on the initial draw of $\theta$ and the \emph{detection intervals} $A_1,\ldots,A_n$.
+We define an \emph{error} event $\mathcal E_n$ at the $n$th observation if $U_n \neq M_n(X_n)$, i.e., an error occurs if $\theta \in A_n$ but $\theta + Z_n \notin A_n$ or $\theta \notin A_n$ but $\theta +Z_n \in A_n$.
+With this notation, the $n$ observation can be seen as the result of noisy transmission of  $U_n$ through a binary channel with bit flip probability of $\mathbb P( \mathcal E_n)$.
+We now choose the detection regions $A_n$ as follows: we divide the real line into $m = \lfloor   \sqrt{n} /  (\sigma \alpha_n) \rfloor$ equiprobable disjoint intervals $I_1,\ldots,I_m$.
+For $j=1,\ldots,m$, include $I_j$ in $A_n$ with probability $1/2$.
+As a result, we can think of the index of the interval where $\theta$ falls as the \emph{message} (one of possible $m$) that is communicated by $n$ uses of the channel from $U_n$ to $M_n(X_n)$.
+The width of each interval is $\sigma \alpha_n/ \sqrt{n}$, so if this messages is communicated with zero error, we attain an estimate $\widehat{\theta}$ of accuracy
+\[
+\left| \theta - \widehat{\theta} \right|  <  \sigma \frac{\alpha_n}{\sqrt{n}}. 
+\]
 
-In this work we are concerned with the mean squared error (MSE) risk:
-\begin{equation}
-\label{eq:error_def}
-\epsilon_n \triangleq \mathbb E\left(\widehat{\theta}_n - \theta \right)^2,
-\end{equation}
-where the expectation is taken with respect to the distribution of $X^n$ and the prior distribution $\pi(\theta)$. \\
-%It is well known that minmax estimation error 
-%\begin{equation}
-%E_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left(\widehat{\theta}_n - \theta \right)^2 | \theta \right],
-%\end{equation}
-%can be obtained from $\epsilon_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}.
+We now derive conditions of $\alpha_n$ such that communication with vanishing probability of error is possible. Note that by the codeword construction we have
+\[
+\mathbb P(M_n(X_n)=1) = 1/2,
+\]
+and, assuming $n$ is large enough,
+\[
+\mathbb P(\mathcal E_n) = \sum_{j=1}^m \mathbb P(\theta \in I_j)  \mathbb P(X_n \notin I_j) /2 \approx 0.5 \mathbb P( |Z_n|> \sigma \alpha_n/\sqrt{n}) \approx 0.5 -  \frac{1}{\sqrt{2\pi}} \frac{\alpha_n}{\sqrt{n}}+O(1/n).
+\]
+If $\alpha_n / n \rightarrow 0$, then the probability of bitflip goes to $0.5$ as $n$ increases.
+By the channel coding theorem we know that communication with vanishing probability is possible provided the communication rate
+\[
+R = \log_2(m) = \log_2(\sqrt{n} / (\sigma \alpha_n)) 
+\]
+does not exceeds the capacity:
+\[
+ C = n(1-h( \mathbb P(\mathcal E))) \approx \frac{n}{2\pi \ln 2} \frac{\alpha_n^2}{n} .
+\]
+The last condition is satisfied provided 
+\[
+\alpha_n > \sqrt{2 \pi \ln 2 \log_2(\sqrt{n}/\sigma)}.
+\]
 
-The main problem we consider is the minimal value that can be attain in \eqref{eq:error_def} as a function of $n$.
-Note that this minimization is the combination of the following two procedures: (1) selecting the $i$th message $M_i$ based on past messages and current observation $X_i$, and (2) estimating $\theta$ given messages $M^n$.
-We are interested in particular in the asymptotic relative efficiency of estimators $\widehat{\theta}_n$ for $\theta$ compared to the sample mean $\bar{X}_n = \frac{1}{n} \sum_{i=1}^n X_i$.
-Since the MSE attained by the latter is $\sigma^2/n$, this relative efficiency is defined as
-\begin{equation}
-\rho \triangleq \lim_{n \rightarrow \infty} \frac{n}{\sigma^2}  \epsilon_n. 
-\label{eq:relative_efficiency}
-\end{equation}
 {\color{red}
-Since the conditional expectation of $\theta$ with respect to $\bar{X}_n$ (and not $\bar{X}_n$) minimizes \eqref{eq:error_def}, we need to justify the fact that we use the sample mean as the reference estimator.
+Use Fano's inequality to prove a necessary condition on $\alphan_n$ and therefore on asymptotic relative efficiency.
 }
 
-In addition to the notations defined above, we denote by $\phi(x)$ the standard normal density and by $\Phi(x)$ the standard normal cumulative distribution function.
-Prime denote derivative with respect to $\theta$.
-
-% Lower Bound on the assymptotic minimal effeciency.
-% Scheme that attains the assymptotic minimal effeciency. 
-% Bayesian scheme that is one step optimal. We leave open the question whether this scheme attains the asymptotic minimal effeciency
-
-\section{Results \label{sec:sequential}}
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the asymptotic relative efficiency of and adaptive estimator cannot get below $\pi/2$.
-Next, we provide a particular adaptive estimation scheme and show in Theorem~\ref{thm:sgd} that its efficiency is $\pi/2$.
-Finally, in Theorem~\ref{thm:opt_one_step} we provide an adaptive estimation scheme that is optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen.
-While it is not clear whether the efficiency of this last scheme is $\pi/2$, numerical simulations suggests that the MSE of this scheme time s $n$ converges as well to $\pi/2$, but in a faster rate than the first scheme.
-
-%While we provide expressions for the optimal message, evaluating the asymptotic efficiency of this estimation scheme turns out to be a challenging task.
-We therefore leave open the question whether this scheme attains the lower bound with equality, and only provide numerical result that support this conjecture.
-\\
-
-%\begin{figure}
-%\begin{center}
-%\begin{tikzpicture}[node distance=2cm,auto,>=latex]
-%  \node at (0,0) (theta) {$\theta$} ;
-%  \node at (2,0) (x1) {$X_1$};
-%  \node[below of = x1, node distance = 1cm] (x2) {$X_2$};
-%    \node[below of = x2, node distance = 1cm] (dots) {$\vdots$};
-%  \node[below of = dots, node distance = 1cm] (xn) {$X_n$};
-%  
-%   \node[right of = x1, node distance = 2cm] (m1) {$M_1$};
-%  \node[right of = x2, node distance = 2cm] (m2) {$M_2$};
-%    \node[right of = xn, node distance = 2cm] (mn) {$M_n$};
-%
-%\draw[->] (theta) -- (x1);
-%\draw[->] (theta) -- (x2);
-%\draw[->] (theta) -- (xn);
-%
-%\draw[->] (x1)--(m1);
-%\draw[->] (x2)--(m2);
-%\draw[->] (xn)--(mn);
-%
-%\draw[->] (m1)--(m2);
-%\draw[->, dashed] (m2)--(mn); 
-%  
-%\end{tikzpicture}
-%\end{center}
-%\caption{\label{fig:sequencial_graphical} Graphical model notation of the sequential setting.}
-%\end{figure}
-
-%\subsection{Properties of an Optimal Scheme}
-%The sequential nature of the encoding and the estimation is best explain by the notions of actions and rewards taken from dynamic programming.
-The \emph{action} taken by the $i$th encoder is the design of a detection region $M_i^{-1}(1)$ that would lead to $M_i = 1$ assuming when $X_i \in M_i^{-1}(1)$ or $M_i=-1$ otherwise.
-The \emph{reward} (or penalty) is only evaluated at the end of the time horizon $n$.
-%% Dynamic program. State = $M^n$. 
-%% Reward is collected at the end
-%%
-
-\subsection{A Lower Bound on Adaptive Single-Bit Schemes}
-Our first results asserts that the relative efficiency \eqref{eq:relative_efficiency} of any adaptive estimation scheme is bounded from below by $\pi/2$, as follows from the following theorem:
-\begin{thm}[minimal relative effeciency] \label{thm:adpative_lower_bound}
-Let $\widehat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Fig.~\ref{fig:sequential}.
-% Let $\pi(\theta)$ be an absolutely continuous prior distribution on $\Theta$ with density function converges to zero at the endpoints of the interval $\Theta$. 
-Assumes that $P(d\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-\mathbb E (\theta-\theta_n)^2 \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\pi}{2n}\sigma^2+o(n^{-1}),
-\]
-where 
-\[
-I_0 = \mathbb E \left( \frac{d}{d\theta} \log P_\theta(\theta) \right)^2
-\]
-is the Fisher information with respect to a location model in $\theta$. 
-\end{thm}
-
-\subsubsection*{Sketch of Proof}
-The main idea in the proof is to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$.
-Once this bound is achieved, the result follows by using the Van-Trees inequality \cite{gill1995applications} which bounds from below the MSE of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are given in the Appendix.\\
-
-Next, we present an adaptive estimation scheme which attains the minimal asymptotic efficiency $\pi/2$. 
-%Theorem~\ref{thm:adpative_lower_bound}. This estimation scheme can be seen as a gradient descent
-
-\subsection{Asymptotically Optimal Estimator}
-Consider the following estimator $\widehat{\theta}_n$ for $\theta$:  set 
-\begin{equation}
-\label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n \sgn (X_n - \theta_n), \quad n = 1,2,\ldots,
-\end{equation}
-where $\left\{\gamma_n \right\}_{n=1}^\infty$ is any strictly positive sequence satisfying 
-\begin{enumerate}
-\item[(i)] $\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n)$ \\
-\item[(ii)] $\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty$ 
-for some $0< \lambda \leq 1$.
-\end{enumerate}
-(e.g. $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). The $n$th step estimation is defined by 
-\begin{equation} \label{eq:sgd_est}
-\widehat{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
-\end{equation}
-
-As the following theorem shows, the estimator $\widehat{\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the minimal asymptotic efficiency as established by Theorem~\ref{thm:adpative_lower_bound}.
-\begin{thm} \label{thm:sgd}
-The sequence $\widehat{\theta}_n$ of \eqref{eq:sgd_alg} satisfies
-\[
-\sqrt{n} \left( \widehat{\theta}_n - \theta \right) \overset{d}{\rightarrow} \mathcal N \left(0,  \pi \sigma^2 /2 \right).
-\]
-\end{thm}
-
-\subsubsection*{Proof}
-The asymptotic behavior of \eqref{eq:sgd_est} is a special case of  \cite[Thm. 4]{polyak1992acceleration}. The details are provided in the Appendix.\\
-
-Note that $\theta_0$ is not explicitly defined in 
-in equation \eqref{eq:sgd_est}.
-Arguably, a reasonable initialization is $\theta_0 = \mathbb E [\theta]$.
-However, Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator, is indifferent to this initialization.
-Thus, the optimal efficiency is attained without using the prior distribution on $\theta$.
-Nevertheless, the bound in Theorem~\ref{thm:adpative_lower_bound} suggests that the estimation error can be greatly reduced whenever the prior of $\theta$ provides a lot of information $I_0$ on its location.
-In order to incorporate this information in a more meaningful way, we present a Bayesian estimation scheme that is conjectured to attain the optimal asymptotic efficiency.
-
-\subsection{One-step Optimal Estimation}
-In this subsection we present an estimation scheme that posses the property of \emph{one-step optimality}.
-That is, at each step $i$, the $i$th encoder designs the detection region $M_i^{-1}(1)$ such that the MSE given $M^i$ is minimal.
-In other word, this scheme designs the messages in a greedy manner, such that the MSE at step $i$ is minimal given the current state of the estimation described by $M^{i-1}$.
-\\
-
-The structure of the message that minimizes the next step MSE is given by the following theorem:
-\begin{thm}[optimal one-step estimation] \label{thm:opt_one_step}
-Let $\pi(\theta)$ be an absolutely continuous log-concave probability distribution. Given a sample $X$ from the distribution $\mathcal N(\theta, \sigma^2)$, define 
-\begin{equation}
-\label{eq:adaptive_main_message}
-M = \sgn(X - \tau),
-\end{equation}
-where $\tau$ satisfies the equation
-\begin{equation}
- \label{eq:fixed_point}
- \tau = \frac{m^-(\tau) + m^+(\tau)}{2},
-\end{equation}
-with
-\begin{align*}
-m^-(\tau)  & = \frac{\int_{-\infty}^{\tau} \theta P(d\theta) }{\int_{-\infty}^{\tau} P(d\theta)} ,\\
-m^+(\tau) & = \frac{\int_{\tau}^\infty \theta P(d\theta) }{\int_{\tau}^\infty P(d\theta)} .
-\end{align*}
-Then for any estimator $\widehat{\theta}$ which is a function of $M'(X) \in \{-1,1\}$, we have
-\begin{equation}
-\label{eq:opt_cond}
-\mathbb E \left(\theta-\widehat{\theta}(M')\right)^2 \geq  \mathbb E \left(\theta- \mathbb E[\theta|M]\right)^2,
-\end{equation}
-\end{thm}
-
-\begin{proof}
-The proof is completed by the following two lemmas, proofs of which can be found in the Appendix:
-\begin{lem} \label{lem:unique}
-Let $f(x)$ be a log-concave probability density function. Then the equation 
-\begin{equation}
-\label{eq:lem_fixed_point}
-2x = \frac{\int_x^\infty uf(u)du}{\int_x^\infty f(u)du} + \frac{\int_{-\infty}^x uf(u)du}{\int_{-\infty}^x f(u)du} 
-\end{equation}
-has a unique solution.
-\end{lem}
-\end{proof}
-
-\begin{lem} \label{lem:adaptive}
-Let $U$ be an absolutely continuous random variable with
-pdf $P(du)$. Then the one-bit message $M^\star$ that minimizes
-\[
-\int \left( u - \mathbb E[U|M(u)]  \right)^2 P(du)
-\]
-is given by
-\[
-M^\star  =  \sgn(U - \tau),
-\]
-where $\tau$ is the unique solution to the equation
- \[
-2 \tau = \frac{\int_{\tau}^\infty u P(du)} {\int_{\tau}^\infty P(du)} + \frac{\int_{-\infty}^{\tau} u P(du)}{\int_{-\infty}^{\tau} P(du)}.
-\]
-\end{lem}
-
-Theorem~\ref{thm:opt_one_step} suggests the following Bayesian estimation scheme: set $P_0(t) = \pi(\theta)$, and for $n\geq 1$ update the prior as
-\begin{align}
-P_n(t) = & P(\theta=t |M^n) = \frac{ P\left( \theta=t | M^{n-1} \right) P(M_n | \theta = t , M^{n-1})  } { P(M_n | M^{n-1} )} \nonumber \\ 
-& = \alpha_n  P_{n-1}(t) \Phi\left(M_n \frac{ t - \tau_{n-1} }{\sigma} \right), \label{eq:density_update}
-\end{align}
-where $\alpha_n$ is a normalization coefficient that equals to
-\[
-\alpha_n = \left(\int_{\mathbb R} P_{n-1}(t) \Phi\left(M_n \frac{t- \tau_{n-1} }{\sigma} \right)  dt \right)^{-1}. 
-\]
-The $n$th estimate for $\theta$ is the conditional expectation of $\theta$ given $M^n$, namely
-\begin{equation}
-\theta_n = \mathbb E \left[ \theta| M^n\right] = \int_{-\infty}^\infty t P_n(t) dt. \label{eq:estimator_update}
-\end{equation}
-Next, solve equation \eqref{eq:fixed_point} with the updated prior $P_n(t)$ instead of $P(\theta)$.
-Note that since the standard normal cdf $\Phi(x)$ is log-concave, the updated prior $P_n(t)$ remains log-concave and thus a unique solution to \eqref{eq:fixed_point} is guaranteed by Lemma~\ref{lem:unique}.
-Finally, update the $n+1$th message as
-\begin{equation}\label{eq:message_update}
-M_{n+1} = \sgn(X_{n+1}-\tau_n).
-\end{equation}
-
-Since the equation \eqref{eq:fixed_point} has no analytic solution in general, it is hard to derive the asymptotic behavior of the Bayes estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}.
-We conjecture, however, that it attains the asymptotic relative efficiency of $\sigma^2\pi/2$, as can be observed from the numerical simulation illustrated in Fig.~\ref{fig:adaptive_error}.
-Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the sample mean for the same sample realization.
-
- % In fact, the numerical simulation in Fig.~\ref{fig:simulation} shows that this scheme outperform the estimator of \eqref{eq:sgd_est} even when the prior on $\Theta$ is least favorable for Bayes estimation \cite{Bickel1981}.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}
-\node at (0,0) {\includegraphics[scale=0.4]{error}};
-\end{tikzpicture}
-\caption{Normalized empirical risk $n\left(\widehat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $100$ Monte Carlo trials.
-In each trial, $\theta$ is chosen uniformly in the interval $(-5,5)$.
-\label{fig:adaptive_error}  }
-\end{center}
-\end{figure}
-
-\begin{comment}
-\subsection{Relation to Sigma-Delta Modulation \label{subsec:sdm}}
-The SDM is a device that converts continuous-time analog signals to a discrete-time sequence of binary digits.
-The basic operation of a SDM can be described as follows: the modulator takes as input a sequence of continuous amplitude samples $X_n$, which are typically represents samples of a continuous-time signal taken uniformly at sampling rate $f_s$ much higher than the Nyquist rate of the signal \cite{1095151}.
-The output of the modulator is a sequence $M_n$ of binary values, obtained according to the following rule:
-\begin{align}
-\begin{cases} V_{n+1} & =  V_n - \alpha q(V_n) + X_n, \\
-M_n & = \sgn(V_n)  \end{cases}, \quad n=1,2,\ldots, \label{eq:sdm}
-\end{align}
-where $\alpha > 0$ is a parameter of the modulator that is determined by the maximal value of the input sequence $X^n$.
-The SDM of the form \eqref{eq:sdm} was studied in \cite{53738} under the assumption that the input process $X_n$ is an i.i.d Gaussian process.
-The main results from \cite{53738} shows that regardless of the initial state $V_0$, the process $M_n$ is a stationary ergodic process with mean $\theta$.
-It follows that a consistent estimation of $\theta$ is obtained by taking the mean of the sequence $\{M_n\}$.
-However, the results from \cite{53738} does not provide a closed form for the second order statistics of $\{M_n\}$, so that convergence rate cannot be derived from \cite{53738}.
-\end{comment}
-
-\section{Conclusions \label{sec:conclusions}}
-We considered the relative efficiency in estimating the mean of a normal distribution from single-bit measurements in an adaptive setting.
-We have shown that this minimal relative efficiency is $\pi/2$, namely there is a penalty factor of at least $\pi/2$ on the asymptotic MSE in estimating the mean compared to an estimator that has full access to the sample.
-We also showed that this lower bound is tight by presenting an estimation procedure that attains it.
-%but ignores the prior distribution on the parameter space.
-In addition, we characterized the single-bit message that minimizes the next step MSE, and described an estimation procedure that is based on a sequence of one-step optimal messages.
-We leave open the questions whether this estimator attains the minimal efficiency and whether it leads to an estimation scheme which is globally optimal.
-\\
-
-%Something about how to interpret the results
-
-% Sigma-Delta
-% Relation to CEO
-% Open questions
-% Extenstion to fully distributed setting
-
-\section*{ACKNOWLEDGMENT}
-This research is supported in parts by...
-%Tsachy Weissman, Stefano Rini, Robert Gray.
-
-\onecolumn
-
-\appendix
-
-\section{Proofs}
-In this appendix we provide detailed proofs of our main results as described in Section~\ref{sec:sequential}.
-
-\subsection*{Proof of Theorem~\ref{thm:adpative_lower_bound}}
-
-We first prove the following two lemmas:
-\begin{lem} \label{lem:bound_intervals}
-For any $x_1 \geq \ldots \geq x_n \in \mathbb R$, we have 
-\begin{equation}
-\frac{ \left(  \sum_{k=1}^n (-1)^{k+1}\phi(x_k) \right)^2} 
-{\left( \sum_{k=1}^n (-1)^{k+1} \Phi(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} \Phi(x_k) \right)  } \leq \frac{2} {\pi}. \label{eq:bound_intervals}
-\end{equation}
-\end{lem}
-\begin{lem} \label{lem:fisher_bound}
-Let $X\sim \mathcal N(\theta,\sigma^2)$ and assume that 
-\[
-M(X) = \begin{cases} 1,& X \in A, \\
--1, & X \notin A.
-\end{cases}
-\]
-Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $2/(\pi \sigma^2)$.
-\end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals}}
-We use induction on $n \in \mathbb N$. For the base case $n=1$ we have 
-\begin{equation} \label{eq:induction_base}
-\frac{  \phi^2(x)} 
-{\Phi(x) \left(1 - \Phi(x) \right) } 
-\end{equation}. 
-Taking the logarithm of \eqref{eq:induction_base} and differentiating, we conclude that any point $x$ that maximizes \eqref{eq:induction_base} satisfies
-\[
-x = \phi(x) \left( \Phi(x) -\frac{1}{2} \right).
-\]
-However, since $x > \phi(x) \left( \Phi(x) -\frac{1}{2} \right)$ for all $x > 0$, the only point that satisfies the last condition is $x=0$.
-At this point \eqref{eq:induction_base} equals $2/\pi$.
-\par
-Assume now that \eqref{eq:bound_intervals} holds for all integers up to some $n = N-1$ and consider the case $n = N$.
-The maximal value of \eqref{eq:bound_intervals} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq 2 \log \left(  \sum_{k=1}^{N} (-1)^{k+1} \phi(x_k) \right) - \log
-\left( \sum_{k=1}^N (-1)^{k+1} \Phi(x_k) \right)
--\log \left(1 -  \sum_{k=1}^N (-1)^{k+1} \Phi(x_k) \right) \\
-& = 2 \log \delta_N - \log \Delta_N - \log \left(1 - \Delta_N  \right),
-\end{align*}
-where we denoted $\delta_N \triangleq \sum_{k=1}^{N} (-1)^{k+1} \phi(x_k)$ and $\Delta_N =  \sum_{k=1}^N (-1)^{k+1} \Phi(x_k)$. The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} \phi'(x_k)}{\delta_N} -\frac{(-1)^{k+1} \phi(x_k)}{\Delta_N } + \frac{(-1)^{k+1} \phi(x_k)}{1-\Delta_N }.
-\]
-Using the fact that $\phi'(x) = -x \phi(x)$, we conclude that the gradient of $g$ vanishes only if
-\[
-x_k = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\]
-In particular, the condition above implies $x_1 = \ldots = x_N$. If $N$ is odd then for $x_1=\ldots =x_N$ we have that \eqref{eq:bound_intervals} equals
-\[
-\frac{\phi(x_1)^2}{ \Phi(x_1) (1 - \Phi(x_1))},
-\]
-which was shown to be smaller than $\pi/2$.
-If $N$ is even, then for any constant $c$ the limit of \eqref{eq:bound_intervals} exits as $(x_1,\ldots,x_N)\rightarrow (c,\ldots,c)$ and equals zero.
-Therefore, the maximum of \eqref{eq:bound_intervals} is not attained at this line.
-We now consider the possibility that \eqref{eq:bound_intervals} is maximized at the borders, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches plus or minus infinity.
-For simplicity we only consider the cases where $x_N$ goes to minus infinity or $x_1$ goes to plus infinity (the general case where the first $m$ coordinates goes to infinity or the last $m$ to minus infinity is obtained using similar arguments).
-Assume first $x_N \rightarrow -\infty$.
-Then  \eqref{eq:bound_intervals} equals
-\begin{align*}
-\frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}\phi(x_k) \right)^2} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} \Phi(x_k) \right)\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} \Phi(x_k)  \right) } ,
-\end{align*}
-which is smaller than $2/\pi$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
-\eqref{eq:bound_intervals} equals
-\begin{align*}
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}\phi(x_k) \right)^2} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} \Phi(x_k) \right)\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} \Phi(x_k)  \right) }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}\phi(x'_m) \right)^2} 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} \Phi(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} \Phi(x'_{m})  \right) },
-\end{align*}
-where $x'_{m} = x_{m+1}$. The last expression is also smaller than $2/\pi$ by the induction hypothesis. This proves Lemma~\ref{lem:bound_intervals}. \\
-
-\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
-The Fisher information of $M$ with respect to $\theta$ is given by
-\begin{align}
-I_\theta & =  \mathbb E \left[ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta \right] \nonumber \\
-& = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
-& \overset{(a)}{=} \frac{ \left( - \int_A \phi' \left( \frac{x-\theta}{\sigma} \right)dx \right)^2} {\sigma^2 P(M=1| \theta) } + \frac{ \left( \int_A \phi' \left( \frac{x-\theta}{\sigma} \right)dx \right)^2} { \sigma^2P(M=-1| \theta) } \nonumber \\
-& = \frac{\left( \int_A \phi'\left( \frac{x-\theta}{\sigma} \right) dx \right)^2 }{  \sigma^2 P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
-& = \frac{\left( \int_A \phi'\left( \frac{x-\theta}{\sigma} \right) dx \right) \left( \int_A \phi'\left( \frac{x-\theta}{\sigma} \right) dx \right)}{  \sigma^2 \left( \int_A \phi \left( \frac{x-\theta}{\sigma} \right) dx \right)  \left(1- \int_A \phi \left( \frac{x-\theta}{\sigma} \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
-\end{align}
-where differentiation under the integral sign in $(a)$ is possible since $\phi(x)$ is differentiable with absolutely integrable derivative $\phi'(x) = -x\phi(x)$.
-Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
-\[
-\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon \sigma^2,
-\]
-which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$.
-It is therefore enough to proceed in the proof assuming that $A$ is of the form
-\[
-A = \cup_{j=1}^k (a_j,b_j),
-\]
-with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
-\begin{align*}
-\mathbb P(M_n=1) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
-& = \sum_{j=1}^k \left( \Phi \left(\frac{b_j-\theta}{\sigma} \right) -  \Phi \left(\frac{a_j-\theta}{\sigma} \right)  \right),
-\end{align*}
-so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
-\begin{align}
-& =   \frac { \left( \sum_{j=1}^{k} \phi \left(\frac{a_j-\theta}{\sigma} \right) - \phi \left( \frac{b_j-\theta} {\sigma} \right)  \right)^2 } 
-{\sigma^2 \left( \sum_{j=1}^k \Phi \left( \frac{b_j-\theta }{\sigma}\right) - \Phi \left( \frac{a_j-\theta }{\sigma}\right)  \right) }  \nonumber \\
-& \times \frac {1} 
-{1- \left( \sum_{j=1}^k \Phi \left( \frac{b_j-\theta }{\sigma}\right) - \Phi \left( \frac{a_j-\theta }{\sigma}\right)  \right) } 
-\label{eq:lemma_J}
-\end{align}
-The proof of Lemma~\ref{lem:fisher_bound} is completed since it follows from~\ref{lem:bound_intervals} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $2/(\sigma^2 \pi)$.
-\\
-
-We now consider the proof of Thm.~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$, we first note that without loss of generality, each message $M_i$ can be written in the form
-\begin{equation}
-\label{eq:general_messages}
-M_i = \begin{cases}
-X_i \in A_i & 1, \\
-X_i \notin A_i & -1,
-\end{cases} 
-\end{equation}
-where $A_i \subset \mathbb R$ is a Lebesgue measurable set.
-Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = M^{-1}(1)$.
-Consider the conditional distribution $P({M^n|\theta})$ of $M^n$ given $\theta$.
-We have
-\begin{align}
-P\left( M^n | \theta \right) & =  \prod_{i=1}^n P\left(M_i | \theta, M^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
-\end{align}
-where $P\left(M_i =1 | \theta, M^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$. We now prove the following Lemma:
-
-Going back to \eqref{eq:adpt_lower_bound_proof:1}, it follows that the Fisher information of $M^n$ with respect to $\theta$ is given by 
-\begin{align}
-I_\theta(M^n) = \sum_{i=1}^n I_\theta (M_i|M^{i-1}),
-\label{eq:fisher_information}
-\end{align}
-where $I_\theta (M_i|M^{i-1})$ is the Fisher information of the distribution of $M_i$ given $M^{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (M_i|M^{i-1}) \leq 2/(\pi \sigma^2)$.
-The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
-\begin{align*}
-\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(M^n) + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (M_i | M^{i-1} ) + I_0} \\
-& \geq \frac{1}{ 2n/(\pi \sigma^2) + I_0}.
-\end{align*}
-
-\QEDA
-
-\subsection*{Proof of Theorem~\ref{thm:sgd}}
-The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration}.
-In particular, Theorem~\ref{thm:sgd} is follows directly from the following simplified version of \cite[Thm.
-4]{polyak1992acceleration}:
-\begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
-Let 
-\[
-X_i = \theta + Z_i,\quad i=1,\ldots,n.
-\]
-Define 
-\begin{align*}
-\theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
-\widehat{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i,
-\end{align*}
-where the $Z_i$s are $\mathcal N(0,\sigma^2)$ and independent of each other, the sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions (i) and (ii) in Theorem~\ref{thm:sgd}, and $\left| \varphi(x) \right| \leq K_1(1+x)$ for some $K_1$.
-Define $\psi(x) = \mathbb E \varphi(x+Z_1)$, $\chi(x) = \mathbb E \varphi^2(x+Z_1)$ and assume that $\psi(0)=0$, $x\psi(x) >0$ for all $x\neq 0$, $\chi(x)$ is continuous at zero, and that $\psi(x)$ is differentiable at zero with $\psi'(0)>0$.
-Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
-\[
-\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\gamma}.
-\]
-Then $\widehat{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}(\widehat{\theta}_n - \theta)$ converges in distribution to $\mathcal N(0,V)$, where
-\[
-V = \frac{ \chi(0)} {\psi'^2(0)}. 
-\]
-\end{thm}
-
-Using the notation in Theorem~\ref{thm:polyak_juditsky}, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have: 
-\[
-\chi(x) = \mathbb E \varphi^2(x+Z_1),
-\]
-so $\chi(0) = 1$. In addition,
-\begin{align*}
-\psi(x) & = \mathbb E \sgn(x+ Z_1) = \int_{-\infty}^\infty \sgn(x+z) \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{\sigma^2}} dz \\
-& = \int_{-x}^\infty \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{\sigma^2}} dz -\int_{-\infty}^{-x} \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{\sigma^2}} dz.
-\end{align*}
-This leads to 
-\begin{align*}
-\psi'(x) & = \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{x^2}{\sigma^2}} dz +\frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{\sigma^2}} dz,
-\end{align*}
-so $\psi'(0) = \frac{2}{\sqrt{2\pi}\sigma}$. It is now easy to verify that the rest of the conditions in Theorem~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$. Since 
-\[
-\frac{\chi(0)}{\psi'^2(0)} = \frac{\pi \sigma^2}{2},
-\]
-Theorem~\ref{thm:sgd} follows from Theorem~\ref{thm:polyak_juditsky}. \QEDA
-
-\subsection*{Proof of Theorem~\ref{thm:opt_one_step}}
-In this subsection we prove lemmas \ref{lem:adaptive} and \ref{lem:unique} which lead to Theorem~\ref{thm:opt_one_step}.
-
-\subsubsection*{Proof of Lemma \ref{lem:adaptive}}
-Since any single-bit message $M(u) \in \{0,1\}$ is characterized by two decision region $A_1 = M^{-1}(1)$ and $A_{-1} = M^{-1}(-1)$, it follows that $\mathbb E \left[ U | M(U) \right]$ assumes only two values: $\mu_1 = \mathbb E \left[ U | M(U) = 1 \right]$ and $\mu_{-1} = \mathbb E \left[ U | M(U) = -1 \right]$.
-We claim that a necessary condition for $M(u)$ to be optimal is that the sets $A_1$ and $A_{-1}$ are, modulo a set of measure $P(du)$ zero, the Voronoi sets on $\mathbb R$ corresponding to the points $\mu_1$ and $\mu_{-1}$, respectively.
-Indeed, assume by contradiction that for such an optimal partition there exists a set $B \subset A_{1}$ with $\mathbb P (U \in B) >0$ such that $\left( b-\mu_{1} \right)^2 > \left( b- \mu_{-1} \right)^2$.
-The expected square error in this partition satisfies:
-\begin{align*}
-& \int_{\mathbb R} \left( u - \mathbb E[U|M(u)]  \right)^2 P(du) = \int_{A_1} (u- \mu_1)^2 P(du) + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
-& = \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_1)^2 P(du) + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
-& > \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_2)^2 P(du) + \int_{A_{-1}} (u- \mu_{-1})^2 P(du),
-\end{align*}
-so clearly, the partition $A_1' = A_1 \setminus B$, $A_{-1}' = A_{-1} \cup B$ attains lower error variance which contradicts the optimality assumption and proves our claim.
-It is evident that Voronoi partition of the real line corresponding to $\mu_1$ and $\mu_{-1}$ is of the form $A_{-1} = (-\infty,\tau)$, $A_{1} = (\tau, \infty)$ where the point $\tau$ is of equal distance from $\mu_1$ and $\mu_{-1}$, namely $\tau = \frac{\mu_1 + \mu_{-1}}{2}$.
-From these two conditions (which are a special case of the conditions derived in \cite{1056489} for two quantization regions) we conclude that $\tau$ must satisfy the equation
-\[
-2 \tau = \frac{\int_{\tau}^\infty u P(du)}{\int_{\tau}^\infty P(du)} + \frac{\int_{-\infty}^{\tau} u P(du)}{\int_{-\infty}^{\tau} P(du)}.
-\] 
-\QEDA
-
-\subsubsection*{Proof of Lemma \ref{lem:unique}} 
-Any solution to \eqref{eq:lem_fixed_point} is a solution to $h^+(x) = h^-(x)$ where
-\[
-h^+(x) = \frac{\int_x^\infty uf(u)du}{\int_x^\infty f(u)du} - x 
-\]
-and
-\[
-h^-(x) = x - \frac{\int_{-\infty}^x uf(u)du}{\int_{-\infty}^x f(u)du}.
-\]
-We now prove that $h^+(x)$ is monotonically decreasing while $h^-(x)$ is increasing, so they meet at most at one point. The derivative of $h^-(x)$ is given by
-\begin{equation} 
-\label{eq:one_step_proof_derivative}
-1 - \frac{ f(\tau) \int_{-\infty}^\tau f(x) (\tau-x)dx } {\left( \int_{-\infty}^\tau f(x) dx \right)^2}.
-\end{equation}
-Denote $F(x) = \int_{-\infty}^x f(u)du$.
-Using integration by parts in the numerator and from the fact that $\lim_{\tau \rightarrow -\infty}  \tau \int_{-\infty}^\tau f(x) dx = 0$, the last expression can be written as
-\[
-1- \frac{ f(\tau) \int_{-\infty}^\tau F(x) dx}
- {\left( F(\tau) \right)^2}.
-\]
-Log-concavity of $f(x)$ implies log-concavity of $F(x)$, so that we can write $F(x) = e^{g(x)}$ for some concave and differentiable function $g(x)$.
-Moreover, we have $f(x) = g'(x)e^{g(x)}$ where, by concavity of $g(x)$, the derivative $g'(x)$ of $g(x)$ is non-increasing.
-With these notation we have
-\begin{align*}
-\frac{ f(\tau) \int_{-\infty}^\tau F(x) dx}
- {\left( F(\tau) \right)^2} & = \frac{g'(\tau)e^{g(\tau)} \int_{-\infty}^\tau e^{g(x)}dx }{ e^{2g(\tau)} } \\
- & = e^{-g(\tau)} \int_{-\infty}^\tau g'(\tau) e^{g(x)} dx  \\
- & \leq e^{-g(\tau)} \int_{-\infty}^\tau g'(x) e^{g(x)} dx \\
- & = e^{-g(\tau)} F(\tau) = 1.
-\end{align*}
-(where the second from the last step follows since $g'(x) \leq g'(\tau)$ for any $x\leq \tau$).
-If follows that \eqref{eq:one_step_proof_derivative} is non-negative and thus $h^-(x)$ is monotonically increasing.
-Since
-\[
-h^+(-x) = x - \frac{ \int_{-\infty}^{x} uf(-u)du}{ \int_{-\infty}^x f(-u) du }, 
-\]
-the fact that $h^+(x)$ is monotonically decreasing follows from similar arguments.
-Moreover, since the derivatives of $h^+(x)$ and $h^-(x)$ never vanish at the same time over any open interval, their difference cannot be constant over any interval.
-Finally, since
-\begin{align*}
- \lim_{x\rightarrow -\infty} h^+(x) =  \lim_{x\rightarrow \infty} h^-(x)
-\end{align*}
-and since non of these functions are constant, monotonicity of $h^+(x)$ and $h^-(x)$ implies that they must meet at some $x\in \mathbb R$. \QEDA
+%We use
+%\[
+%\Phi(x) = 0.5  + \frac{1}{\sqrt{2 \pi} }e^{-x^2/2} \left[x+\frac{x^3}{3}+... \right] 
+%\]
+%\[
+%h(0.5 - x) = 1- \frac{1}{2 \ln 2} \sum_{n=1}^\infty  \frac{2^{2n} x^{2n}} {n(2n-1)}
+%\]
 

### 2017-09-26 Code/log_concavity.m
Add files via upload

@@ -1,0 +1,49 @@
+g1 = @(x) -(5*abs(x).*(x<0)+(x-2).^1.5.*(x>2))
+shift = 8;
+g = @(x) g1(x-shift);
+xmax = 7+shift;
+xmin = -7+shift;
+f_un = @(x) (exp(g(x)) ).*(x>xmin).*(x<xmax) + exp(-abs(x));
+al = integral(f_un,xmin,xmax);
+
+f = @(x) f_un(x)/al;
+
+xx = xmin:0.05:xmax;
+figure(2)
+plot(xx,g(xx))
+
+mean = integral(@(x) x.*f(x),xmin,xmax);
+m_p = @(t) integral(@(x) x.*f(x),t,xmax)/integral(f,t,xmax);
+m_m = @(t) integral(@(x) x.*f(x),xmin,t)/integral(f,xmin,t);
+
+obj1 = 0;
+obj2 = 0;
+dobj1 = 0
+den = 0;
+den2 = 0;
+h = 0;
+fx = 0;
+for i = 1:length(xx)
+    tau = xx(i);
+    obj1(i) = m_p(tau)-tau;
+    obj2(i) = tau-m_m(tau);
+    dobj1(i) = 1 - integral(@(x) (tau-x).*f(x).*f(tau),xmin,tau)/integral(f,xmin,tau)^2;
+    h(i) = integral(@(x) (x-tau).*f(x),xmin,tau);
+    den(i) = integral(@(x) f(x),xmin,tau);
+    den2(i) = sum(den)*(xx(2)-xx(1));
+    fx(i) = 1 - f(tau)*den2(i)/(den(i)*den(i));
+end
+
+figure(1)
+clf
+hold on
+%plot(xx,obj1,'b')
+plot(xx,obj2,'r')
+plot(xx,dobj1,'-ob')
+%plot(xx,h,'-.k')
+plot(xx,f(xx),'--k')
+plot(xx,fx,'-xg')
+%plot(xx,den,'--g')
+%plot(xx,(obj1-obj2)/2,'g')
+
+

### 2017-09-26 Writeups/onebit_adaptive_Allerton_V2.tex
minor changes

--- 2017-09-26 Writeups/onebit_adpative_Allerton_V2.tex
@@
 \end{align}
-The proof of Lem.~\ref{lem:fisher_bound} is completed since it follows from~\ref{lem:bound_intervals} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $2/(\sigma^2 \pi)$.
+It follows from Lem.~\ref{lem:bound_intervals} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $2/(\sigma^2 \pi)$.
+Therefore, the proof of  Lem.~\ref{lem:fisher_bound} is now completed.
  \\

### 2017-09-28 Writeups/onebit_adaptive_Allerton_V2.tex
changes to onebit_Allerton_V2.tex

@@
 \[
-x = \phi(x) \left( \Phi(x) -\frac{1}{2} \right).
+x = \phi(x) \frac{\Phi(x) -\frac{1}{2}}{\Phi(x)(1-\Phi(x))} .
 \]
-However, since $x > \phi(x) \left( \Phi(x) -\frac{1}{2} \right)$ for all $x > 0$, the only point that satisfies the last condition is $x=0$, in which \eqref{eq:induction_base} equals $2/\pi$. \par
+However, since 
+\[
+x > \phi(x) \frac{\Phi(x) -\frac{1}{2}}{\Phi(x)(1-\Phi(x))}
+\]
+for all $x > 0$, the only point that satisfies the last condition is $x=0$, in which \eqref{eq:induction_base} equals $2/\pi$. \par
 Assume now that \eqref{eq:bound_intervals} holds for all integers up to some $n = N-1$ and consider the case $n = N$.
@@
 \]
-where the $Z_i$s are i.i.d. from $\mathcal N(0,\sigma^2)$ and independent of each other. Define 
+where the $Z_i$s are i.i.d. with zero mean. Define 
 \begin{align*}
@@
 \begin{align*}
-\psi(x) & = \mathbb E \sgn(x+ Z_1) = \int_{-\infty}^\infty \sgn(x+z) \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{\sigma^2}} dz \\
-& = \int_{-x}^\infty \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{\sigma^2}} dz -\int_{-\infty}^{-x} \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{\sigma^2}} dz.
+\psi(x) & = \mathbb E \sgn(x+ Z_1) = \int_{-\infty}^\infty \sgn(x+z) \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{2\sigma^2}} dz \\
+& = \int_{-x}^\infty \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{2\sigma^2}} dz -\int_{-\infty}^{-x} \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{2\sigma^2}} dz.
 \end{align*}
@@
 \begin{align*}
-\psi'(x) & = \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{x^2}{\sigma^2}} dz +\frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{\sigma^2}} dz,
+\psi'(x) & = \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{x^2}{2\sigma^2}} dz +\frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{2\sigma^2}} dz,
 \end{align*}

### 2017-09-30 Writeups/onebit_adaptive_Allerton_V2.tex
addressed John's comments in V3, including an extention of Thm. 3 to MSE convergance

@@
 We study the squared error risk in this estimation as a function of the number of samples and one-bit measurements $n$.
-We show that, if at step $n$ the single bit is a function of both the new sample and the previous $n-1$ acquired bits, no estimator can attain asymptotic mean squared error smaller than $\pi/(2n)$ times the variance.
+We consider an adaptive estimation setting where the single-bit sent at step $n$ is a function of both the new sample and the previous $n-1$ acquired bits.
+For this setting, we show that no estimator can attain asymptotic mean squared error smaller than $\pi/(2n)$ times the variance.
+%
 In other words, one-bit restriction increases the number of samples required for a prescribed accuracy of estimation by a factor of at least $\pi/2$ compared to the unrestricted case.
+{\color{red} This fundamental restriction on estimation in the adaptive setting implies a lower bound any distributed estimation setting from one-bit samples. }
+%
 In addition, we provide an explicit estimator that attains this asymptotic error, showing that, rather surprisingly, only $\pi/2<1.571$ times more samples are required in order to attain estimation performance equivalent to the unrestricted case.
@@
 
-Processing and estimating information from data collected at multiple sensors and physical locations is subject to communication constraints. 
+Processing and estimating information from data collected at multiple physical locations is subject to communication constraints. 
 %For example, emerging sensor network technologies in medicine and ``smart cities" use many low-cost sensors to collect large amounts of data and transmit it to remote locations.
 These sensors must operate under severe power restrictions, hence they are limited by their communication bandwidth.
-For example, consider large-scale sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit.
-In this scenario, the ability to estimate a particular parameter from data collected by the sensors is dictated not only by quality of observations and their numbers, but also by limited communication rates between the sensors and the central estimator.
+For example, consider large-scale sensor arrays where information is collected through multiple sensors and transmitted to a central estimation unit.
+In this scenario, the ability to estimate a particular parameter from data collected by the sensors is dictated not only by quality of observations and their numbers, but also by the available communication rate between the sensors and the central estimator.
 The question that we ask is to what extend a parametric estimation task is affected by communication constraints, and what are the fundamental performance limits in estimating a parameter subject to these restrictions.
@@
 
-\node[below of = source2, node distance = 2.5cm] (source3) {$X_n$};
+\node[below of = source2, node distance = 3cm] (source3) {$X_n$};
 \node[int1, right of = source3, node distance = 1.5cm] (enc3) {Enc n};  
@@
 \node[int1, right of = enc2, node distance = 4cm ] (est) {Est};
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -2cm] (mes1) {$M_1 \in \left\{-1,1\right\}$} (est);   
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M_2 \in \left\{-1,1\right\}$} (est);   
+\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1.5cm] (mes1) { $M_1 \in \left\{-1,1\right\}$} (est);   
+\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0.5cm] (mes2) { $M_2 \in \left\{-1,1\right\}$} (est);   
 \draw[->] (mes1) -- +(0,-0.7) -| (enc2);
 
-\draw[dashed,->] (mes2) -- +(0,-0.7) -| +(-2,-1.2);
+\draw[->] (mes2) -- +(0,-0.7) -| +(-2.5,-1.2);
+\draw[->] (mes2)+(-1.5,0.8) -- +(-1.5,-0.7);
 \draw[->,line width = 2pt] (enc3) -| (est);
 
-\node[below of = mes2, node distance = 1.5cm] (mes3) {$M_1,\ldots,M_{n-1} $};
+\node[below of = mes2, node distance = 2cm] (mes3) {$M_1,\ldots,M_{n-1} $};
 
@@
 We are interested in particular in the ARE of estimators of $\theta$ compared to the sample mean $\bar{X}_n = \frac{1}{n} \sum_{i=1}^n X_i$.
-Since the MSE attained by the latter is $\sigma^2/n$, this ARE is defined as
+Since $\sqrt{n}(\bar{X}_n-\theta)$ converges to $\mathcal N(0,\sigma^2)$, this ARE is defined as
 \begin{equation}
- \lim_{n \rightarrow \infty} \frac{n}{\sigma^2}  \mathbb E\left(\widehat{\theta}_n - \theta \right)^2. 
+{\sigma^2}  \mathbb E\left(\widehat{\theta}_n - \theta \right)^2. 
 \label{eq:relative_efficiency}
@@
 \section{Results \label{sec:sequential}}
-The first main results of this paper, as described in Thm.~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be lower than $\pi/2$.
+The first main result of this paper, as described in Thm.~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be lower than $\pi/2$.
 Next, we provide a particular adaptive estimation scheme and show in Thm.~\ref{thm:sgd} that its efficiency is $\pi/2$.
@@
 
-Next, we present an adaptive estimation scheme which attains ARE of $\pi/2$. 
+Next, we present an adaptive estimation scheme that attains ARE of $\pi/2$. 
 \subsection{Asymptotically optimal estimator}
@@
 which was shown to be smaller than $\pi/2$.
-If $N$ is even, then for any constant $c$ the limit of the LHS of \eqref{eq:bound_intervals} exits as $(x_1,\ldots,x_N)\rightarrow (c,\ldots,c)$ and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:bound_intervals} is not attained at this line.
+If $N$ is even, then for any constant $c$ the limit of the LHS of \eqref{eq:bound_intervals} as $(x_1,\ldots,x_N)\rightarrow (c,\ldots,c)$ exists and equals zero.
+Therefore, the maximum of the LHS of \eqref{eq:bound_intervals} is not attained at the line $x_1=\ldots=x_N)$.
 We now consider the possibility that the LHS of \eqref{eq:bound_intervals} is maximized at the borders, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches plus or minus infinity.
@@
 & = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
-& \overset{(a)}{=} \frac{ \left( - \int_A \phi' \left( \frac{x-\theta}{\sigma} \right)dx \right)^2} {\sigma^2 P(M=1| \theta) } + \frac{ \left( \int_A \phi' \left( \frac{x-\theta}{\sigma} \right)dx \right)^2} { \sigma^2P(M=-1| \theta) } \nonumber \\
+& =  \frac{ \left( \frac{d}{d\theta} \int_A \phi \left( \frac{x-\theta}{\sigma} \right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A \phi \left( \frac{x-\theta}{\sigma} \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\
+& \overset{(a)}{=} \frac{ \left( - \int_A \phi' \left( \frac{x-\theta}{\sigma} \right)dx \right)^2} {\sigma^2 P(M=1| \theta) } + \frac{ \left(- \int_A \phi' \left( \frac{x-\theta}{\sigma} \right)dx \right)^2} { \sigma^2P(M=-1| \theta) } \nonumber \\
 & = \frac{\left( \int_A \phi'\left( \frac{x-\theta}{\sigma} \right) dx \right)^2 }{  \sigma^2 P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
@@
 \begin{align*}
-\mathbb P(M_n=1) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
+\mathbb P(M_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
 & = \sum_{j=1}^k \left( \Phi \left(\frac{b_j-\theta}{\sigma} \right) -  \Phi \left(\frac{a_j-\theta}{\sigma} \right)  \right),

### 2017-09-30 Writeups/onebit_adaptive_Allerton_V3.tex
addressed John's comments in V3, including an extention of Thm. 3 to MSE convergance

--- 2017-09-30 Writeups/onebit_adaptive_Allerton_V2.tex
@@
 In other words, one-bit restriction increases the number of samples required for a prescribed accuracy of estimation by a factor of at least $\pi/2$ compared to the unrestricted case.
-{\color{red} This fundamental restriction on estimation in the adaptive setting implies a lower bound any distributed estimation setting from one-bit samples. }
+%{\color{red} This fundamental restriction on estimation in the adaptive setting implies a lower bound any distributed estimation setting from one-bit samples. }
 %
@@
 \subsection{Asymptotically optimal estimator}
-Consider the following estimator $\widehat{\theta}_n$ for $\theta$:  set 
+
+Let $\left\{\gamma_n \right\}_{n=1}^\infty$ be a strictly positive sequence satisfying:
+\begin{equation} \label{eq:conditions}
+\begin{cases}
+\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
+\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
+\mathrm{for~some~}0< \lambda \leq 1
+\end{cases}
+\end{equation}
+(e.g. $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Consider the following estimator $\widehat{\theta}_n$ for $\theta$:  
 \begin{equation}
 \label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n \sgn (X_n - \theta_n), \quad n = 1,2,\ldots,
+\theta_n = \theta_{n-1} +  \gamma_n \sgn (X_n - \theta_{n-1}), \quad n = 1,2,\ldots,
 \end{equation}
-where $\left\{\gamma_n \right\}_{n=1}^\infty$ is any strictly positive sequence satisfying 
-\begin{enumerate}
-\item[(i)] $\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n)$ \\
-\item[(ii)] $\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty$ 
-for some $0< \lambda \leq 1$.
-\end{enumerate}
-(e.g. $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). The $n$th step estimation is defined by 
+and set the $n$th step estimation as
 \begin{equation} \label{eq:sgd_est}
@@
 
-For the estimator defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} 
-we have the following results:
+%For the estimator defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} we have the following results:
 \begin{thm} \label{thm:sgd}
 The sequence $\widehat{\theta}_n$ of \eqref{eq:sgd_est} satisfies
+\begin{enumerate}
+\item[(i)]
 \[
@@
 \]
+\item[(ii)] Assume moreover that $\gamma_n = o(n^{-2/3})$ and $\sum_{n=1}^\infty \gamma_n = \infty$. Then
+\[
+\lim_{n\rightarrow \infty} n\mathbb E \left[ \left(\theta-\widehat{\theta}_n \right)^2 \right] = \sigma^2 \frac{\pi}{2}. 
+\]
+\end{enumerate}
+
 \end{thm}
@@
 \subsubsection*{Proof}
-The asymptotic behavior of \eqref{eq:sgd_est} is a special case of  \cite[Thm. 4]{polyak1992acceleration}. The details are provided in the Appendix.\\
+The asymptotic behavior of \eqref{eq:sgd_est} is a special case of \cite[Thm. 4]{polyak1992acceleration} and \cite[Thm. 2]{polyak1990new}. The details are provided in the Appendix.\\
 
@@
 \subsection*{Proof of Thm.~\ref{thm:sgd}}
-The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration}.
-In particular, Thm.~\ref{thm:sgd} is follows directly from the following simplified version of \cite[Thm.
+The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.
+Specifically, (i) in Thm.~\ref{thm:sgd} follows directly from the following simplified version of \cite[Thm.
 4]{polyak1992acceleration}:
@@
 \]
-where the $Z_i$s are i.i.d. with zero mean. Define 
+where the $Z_i$s are i.i.d. with zero means and finite variances. Define
 \begin{align*}
@@
 \end{align*}
-where the sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions (i) and (ii) in Thm.~\ref{thm:sgd}, and $\left| \varphi(x) \right| \leq K_1(1+x)$ for some $K_1$.
-Define $\psi(x) = \mathbb E \varphi(x+Z_1)$, $\chi(x) = \mathbb E \varphi^2(x+Z_1)$ and assume that $\psi(0)=0$, $x\psi(x) >0$ for all $x\neq 0$, $\chi(x)$ is continuous at zero, and that $\psi(x)$ is differentiable at zero with $\psi'(0)>0$.
+where in addition, assume the following: 
+\begin{enumerate}
+\item[(i)] There exits $K_1$ such that $\left| \varphi(x) \right| \leq K_1(1+|x|)$ for all $x\in \in \mathbb R$.
+\item[(ii)] The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions \eqref{eq:conditions}.
+\item[(iii)] The function $\psi(x) \triangleq \mathbb E \varphi(x+Z_1)$ is differentiable at zero with $\psi'(0)>0$, and satisfies $\psi(0)=0$ and $x\psi(x) >0$ for all $x\neq 0$.
 Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
-\[
-\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\gamma}.
-\]
+\begin{equation}
+\label{eq:Polyak_Juditsky_cond3}
+\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
+\end{equation}
+\item[(iv)] The function 
+$\chi(x) \triangleq \mathbb E \varphi^2(x+Z_1)$ is continuous at zero. 
+\end{enumerate}
 Then $\widehat{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}(\widehat{\theta}_n - \theta)$ converges in distribution to $\mathcal N(0,V)$, where
@@
 
-Using the notation in Thm.~\ref{thm:polyak_juditsky}, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have: 
-\[
-\chi(x) = \mathbb E \varphi^2(x+Z_1),
-\]
-so $\chi(0) = 1$. In addition,
+Using the notation above, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have that $\chi(x) = \mathbb E \sgn^2(x+Z_1) = 1$, so $\chi(0) = 1$. In addition,
 \begin{align*}
@@
 \]
-Thm.~\ref{thm:sgd} follows from Thm.~\ref{thm:polyak_juditsky}. \QEDA
+Thm.~\ref{thm:sgd}-(i) follows from Thm.~\ref{thm:polyak_juditsky}.  \\
+In order to prove Thm.~\ref{thm:sgd}-(ii), we consider:
+\begin{thm}{ \cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
+Let
+\begin{align} \label{eq:polyak_new_measurements}
+\begin{cases}
+U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = f'(U_{n-1})+Z_n \\
+\bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
+\end{cases}
+\end{align}
+Assume that the function $f(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative.
+In particular, $f(x)$ is convex with a unique minimizer $x^\star \in \mathbb R$.
+Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution for which the Fisher information exits.
+Let $\psi(x)$ and $\chi(x)$ be defined as in  Thm.~\ref{thm:polyak_juditsky}-(iii) and satisfies the conditions there.
+Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$,
+and there exits $K_3$ such that 
+\[
+\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] \leq K_3(1+|x|^4). 
+\]
+Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions \eqref{eq:conditions} and the additional conditions in Thm.~\ref{thm:sgd}-(ii). Then
+\[
+V_n \triangleq \mathbb E \left[ \left(\bar{U}_n-x^\star \right)^2 \right] = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (f''(x^\star))^2 } + o(n^{-1}).
+\]
+\end{thm}
+
+We now use Thm.~\ref{thm:polyak_new} with $f(x) = 0.5(\theta-x)^2$, $\varphi(x) = -\sgn(-x)$, $Z_n = -Z_n$ and $U_n = \theta_n$. From \eqref{eq:polyak_new_measurements} we have
+\begin{align*} 
+\theta_n & = \theta_{n-1} + \gamma_n \sgn(\theta-\theta_{n-1} - Z_n )  \\
+& = \theta_{n-1} + \gamma_n \sgn(X_n-\theta_{n-1} ),
+\end{align*}
+so the estimator $\widehat{\theta}_n$ defined by $\widehat{\theta}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
+\[
+\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] = 1 \leq K_3(1+|x|^4)
+\]
+for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
+the conditions in Thm.~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
+In particular, $\psi'(0) = \sqrt{2}/ (\sqrt{\pi}/\sigma)$.
+Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $f''(x) = 1$.
+Thm.~\ref{thm:polyak_new} implies
+\[
+n V_n = \mathbb E \left[ \left(\widehat{\theta}_n-\theta \right)^2 \right]  = \frac{\pi}{2}  + o(1).
+\]
+
+ \QEDA
 

### 2017-09-30 Writeups/proof of Lemma 7 for log-concave distributions.tex
addressed John's comments in V3, including an extention of Thm. 3 to MSE convergance

--- 2017-09-30 Writeups/onebit_adaptive_Allerton_V2.tex
@@
 \begin{document}
-\graphicspath{{../Figs/}}
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-We consider the problem of estimating the mean of a normal distribution under the following constraint: the estimator can access only a single bit of each sample from this distribution.
-We study the squared error risk in this estimation as a function of the number of samples and one-bit measurements $n$.
-We consider an adaptive estimation setting where the single-bit sent at step $n$ is a function of both the new sample and the previous $n-1$ acquired bits.
-For this setting, we show that no estimator can attain asymptotic mean squared error smaller than $\pi/(2n)$ times the variance.
-%
-In other words, one-bit restriction increases the number of samples required for a prescribed accuracy of estimation by a factor of at least $\pi/2$ compared to the unrestricted case.
-{\color{red} This fundamental restriction on estimation in the adaptive setting implies a lower bound any distributed estimation setting from one-bit samples. }
-%
-In addition, we provide an explicit estimator that attains this asymptotic error, showing that, rather surprisingly, only $\pi/2<1.571$ times more samples are required in order to attain estimation performance equivalent to the unrestricted case.
-\end{abstract}
-
-%{\color{red}  The $\mu$-sum problem (Kim-ElGamal Ch. 21) gives a lower bound. Can be reduced to the CEO.}
-
-%{\color{red}  See LASSO results in http://arxiv.org/abs/1506.02181v1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{sec:Intro}
-
-Processing and estimating information from data collected at multiple physical locations is subject to communication constraints. 
-%For example, emerging sensor network technologies in medicine and ``smart cities" use many low-cost sensors to collect large amounts of data and transmit it to remote locations.
-These sensors must operate under severe power restrictions, hence they are limited by their communication bandwidth.
-For example, consider large-scale sensor arrays where information is collected through multiple sensors and transmitted to a central estimation unit.
-In this scenario, the ability to estimate a particular parameter from data collected by the sensors is dictated not only by quality of observations and their numbers, but also by the available communication rate between the sensors and the central estimator.
-The question that we ask is to what extend a parametric estimation task is affected by communication constraints, and what are the fundamental performance limits in estimating a parameter subject to these restrictions.
-In this paper we answer this question in a particular simple setting: the estimation of the mean $\theta$ of a normal distribution with a known variance $\sigma^2$, under the constraint that only a single bit can be communicated on each sample $X_n$ from this distribution.
-As it turns out, the ability to share information among different samples before sending each single-bit message dramatically affects the performance in estimating $\theta$.
-We distinguish in particular among three different settings:
- \begin{itemize}
- \item[(i)] \emph{Centralized} encoding: all $n$ encoders confer and produce a single $n$ bit message which is a function of $X_1,\ldots,X_n$. 
- \item[(ii)] \emph{Adaptive} or \emph{sequential} encoding: the $n$th encoder observes $X_n$ and the $n-1$ previous single bit messages.
- \item[(iii)] \emph{Distributed} encoding: the output of the $n$th encoder is a single bit that is only a function of $X_n$.
- \end{itemize}
-Clearly, as far as information sharing is concerned, settings (iii) is a more restrictive version of (ii) which is more restrictive than (i).
-We measure the estimation performance by the mean squared error (MSE) risk.
-Since without bit constraint this risk is equals $\sigma^2/n$, we are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting, defined by the ratio between their MSE to $\sigma^2/n$ as $n$ goes to infinity.
-\\
-
-In setting (i) the estimator can evaluate the sample mean and then communicate it using $n$ bits.
-This strategy leads to MSE behavior of $\sigma^2/n + o(2^{-n})$.
-Therefore, the ARE in this setting is $1$.
-Namely, asymptotically, there is no loss in performance due to the communication constraint under centralized encoding.
-In this work we show that a similar result does not hold even in setting (ii): the ARE of any adaptive estimation scheme is at least $\pi/2$.
-Namely, the single-bit per sample constraint incurs a minimal penalty of at least $1.57$ compared to an unconstrained estimator or to the optimal estimator in setting (i).
-In addition to this negative statement, we provide an estimator that almost surely attains this ARE.
-In other words, we show that the lower bound of $\pi/2$ on the asymptotic relative efficiency is tight, and that it is attained regardless of the particular realization of $\theta$ or the size of the parameter space from which it is taken.
-Clearly, the minimal penalty on the efficiency of $\pi/2$ also holds under setting (iii), although the question whether such efficiency is achievable (or otherwise, what is the minimal ARE) remains open.
-\\
-
-As the variance $\sigma^2$ goes to zero, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is easily solved by a bisection style method over the parameter space.
-Therefore, the general case of non-zero variance is a reminiscent of the noisy binary search problem with possibly infinite number of unreliable tests \cite{cicalese2002least, Karp:2007:NBS:1283383.1283478}.
-However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a noisy signal.
-For example, sigma-delta modulator (SDM) analog-to-digital conversion \cite{1092194} uses one-bit threshold detector combined with a feedback loop to update an accumulated error state, and therefore falls under setting (ii).
-A SDM with a constant input $\theta$ corrupted by a Gaussian noise was studied in \cite{53738}, where it was shown that the output of the modulator converges to the true constant input almost surely.
-In other words, the SDM provides a consistent estimator for setting (ii).
-The rate of this convergence, however, was not analyzed and cannot be derived from the results of \cite{53738}.
-Our results imply that the rate of convergence of a SDM to a constant input is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-\\
-
-We note that even the centralized encoding of setting (i) poses a non-trivial challenge for the design and analysis of optimal encoding and estimation scheme.
-Indeed, the standard technique to encode an unknown random quantity using $n$ bits is attained by a scalar quantizer.
-However, the optimal design of this quantizer depends on the distribution of its input \cite{gray1998quantization}, which is the goal of our estimation task.
-Therefore a non-trivial exploration exploitation tradeoff arises.
-In our setting, the only missing parameter is the mean, which, under setting (i), is known to the encode with uncertainty interval proportional to $\sigma/\sqrt{n}$.
-Therefore, while it is clear that uncertainty due to quantization decreases exponentially in the number of bits, an exact expression for the MSE in this setting is not easy to derive.
-The situation is even more involved in the adaptive encoding of setting (ii): an encoding and estimation strategy that is globally optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$, may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
-Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $2^{n-1}$ messages, is not guaranteed to be globally optimal.
-Therefore, the main contribution of this paper is a lower bound on the MSE risk of any globally optimal strategy.
-This lower bound is obtained by showing that the Fisher information of any $n$ steps strategy is not larger than $2n/(\pi \sigma^2)$.
-The desired bound of $\pi \sigma^2/(2n)$ on the MSE follows from the van Trees version of the information inequality \cite{gill1995applications}.
-Finally, we show that an estimator that attains asymptotic MSE of $\sigma^2\pi/(2n)$ is obtained as a special case of \cite[Thm.
-4]{polyak1992acceleration}.
-In addition to these two results, we also derive the one-step optimal strategy and demonstrates numerically that  the MSE under this strategy converge to $\pi \sigma^2/(2n)$.
-A proof for this converges remains elusive.
-\\
-
-Our results imply that even under coarse quantization constraints, it is possible to achieve MSE in parametric estimation within only a relatively small penalty compared to the unconstrained estimator.
-A possible clue for this non-intuitive result is obtained from drawing the connection between our setting and the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}.
-This connection, explained in details in Section~\ref{sec:ceo}, immediately leads to a lower bound of $4/3$ on the ARE in the distributed encoding of setting (iii).
-While this lower bound provides no new information compared to the lower bound of $\pi /2$ we derive here for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimal even under one-bit quantization of each sample.
-\\
-
-Setting (ii) and (iii) were considered in 
-\cite{zhang2013information} under the more general assumption of $m$ machines each has access to $n/m$ independent samples.
-The main result of \cite{zhang2013information} are bounds on the estimation error as a function of the number of bits $R$ with which each machine can communicate.
-Specializing their result to our setting, by taking $m=n$ and $R=1$, leads to looser bounds then $\sigma^2\pi/(2n)$ for case (ii) and (iii).
-Other related works include statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation}, although their results apply only to setting (i).
-The counterpart of setting (iii) in the case of hypothesis testing was considered in \cite{52470}.
-%
-Estimation problem subject to the one-bit quantization constraint were also considered recently in compressed sensing \cite{boufounos20081,baraniuk2017exponential} and in MIMO detection in wireless communication \cite{singh2009limits}.
-\\
-
-The rest of this paper is organized as follows: the main problem and notation are defined in Section~\ref{sec:problem}.
-In Section~\ref{sec:ceo} we illustrate a connection between our parametric estimation problem and the remote multiterminal lossy compression problem.
-Our main results are given in  Section~\ref{sec:sequential}, where we present a lower bound on estimation from one-bit samples in the adaptive scheme, as well as an achievable scheme that attains this bound.
-Concluding remarks are given in Section~\ref{sec:conclusions}.
-For sake of fluency, long proofs are deferred to the Appendix.
-
-\section{Problem Formulation \label{sec:problem}}
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto,>=latex]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.5cm] (enc1) {Enc 1};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
- \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
-\node[int1, right of = source2, node distance = 1.5cm] (enc2) {Enc 2};  
-\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source2, node distance = 3cm] (source3) {$X_n$};
-\node[int1, right of = source3, node distance = 1.5cm] (enc3) {Enc n};  
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[above of = source, node distance = 1cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-
-\node[int1, right of = enc2, node distance = 4cm ] (est) {Est};
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1.5cm] (mes1) { $M_1 \in \left\{-1,1\right\}$} (est);   
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0.5cm] (mes2) { $M_2 \in \left\{-1,1\right\}$} (est);   
-\draw[->] (mes1) -- +(0,-0.7) -| (enc2);
-
-\draw[->] (mes2) -- +(0,-0.7) -| +(-2.5,-1.2);
-\draw[->] (mes2)+(-1.5,0.8) -- +(-1.5,-0.7);
-\draw[->,line width = 2pt] (enc3) -| (est);
-
-\node[below of = mes2, node distance = 2cm] (mes3) {$M_1,\ldots,M_{n-1} $};
-
-\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -2cm]  {$M_n \in \left\{-1,1\right\}$} (est);
-
-\draw[->] (mes3) -- +(0,-0.5) -| (enc3);
-
-\node[right of = est, node distance = 1.5cm] (dest) {$\widehat{\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=2pt] (est) -- (dest);
-\end{tikzpicture}
-\end{center}
-\caption{\label{fig:sequential} Adaptive one-bit encoding: the $i$th encoder delivers a single bit message that is a function of its private sample $X_i$ and the previous $i-1$ messages $M_1,\ldots,M_{i-1}$.}
-\end{figure}
-
-Let $X_i$, $i=1,\ldots,n$, be $n$ independent samples from the normal distribution with mean $\theta$ and variance $\sigma^2$.
-We assume that the mean $\theta$ is drawn once from a prior distribution $\pi(\theta)$ on $\Theta$, which is a closed interval of the real line.
-We moreover assume that $\pi(\theta)$ is absolutely continuous with respect to the Lebesgue measure with density $\pi(d\theta)$.
-The problem we consider is the estimation of the parameter $\theta$ under the following constraints on the communication between the samples $X_1,\ldots,X_n$ and a centralized estimator:
-\begin{itemize}
-\item[(i)] The estimator at time $n$ is only a function of the $n$ messages $M^n = \left(M_1,\ldots,M_n \right)$.
-\item[(ii)] For each $i=1,\ldots,n$, the $i$th message $M_i$ is a function of the sample $X_i$ and the $i-1$ previous messages $M^{i-1}$.
-\item[(iii)] The $i$th message $M_i$ takes only two possible values, say $1$ and $-1$. 
-\end{itemize}
-In other words, the $i$th message is defined by a function from the real line to $\{-1,1\}$ that is measurable with respect to the sigma algebra generated by $M^{i-1}$ and $X_i$, and the $n$ messages $M^n$ are the only available to the estimator.
-Upon observing $M^n$, the estimator produces an estimate $\widehat{\theta}_n(M^n)$ of $\theta$.
-A system describing the above scheme is illustrated in Fig.~\ref{fig:sequential}.
-\\
-
-In this work we are concerned with the MSE risk defined as
+\begin{lem} \label{lem:bound_intervals}
+Assume that $X_1,\ldots,X_n$ are distributed with CDF $F(x)$ and PDF $f(x)$ such that $F(-x) = 1-F(x)$ (and $f(-x)=f(x)$). Assume moreover that 
+$ f(x) = e^{g(x}}$ where $g(x)$ is concave and twice differentiable such that $g''(x)<0$. Then for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, we have 
 \begin{equation}
-\label{eq:error_def}
-\mathbb E\left(\widehat{\theta}_n - \theta \right)^2,
-\end{equation}
-where the expectation is taken with respect to the distribution of $X^n$ and the prior distribution $\pi(\theta)$. \\
-%It is well known that minmax estimation error 
-%\begin{equation}
-%E_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left(\widehat{\theta}_n - \theta \right)^2 | \theta \right],
-%\end{equation}
-%can be obtained from $\epsilon_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}.
-
-The main problem we consider is the minimization of \eqref{eq:error_def} over all encoding and estimation strategies, and the characterization of its minimal value as a function of  $n$.
-This minimization is the combination of the following two procedures: (1) selecting the $i$th message $M_i$ based on past messages and current observation $X_i$, and (2) estimating $\theta$ given messages $M^n$.
-We are interested in particular in the ARE of estimators of $\theta$ compared to the sample mean $\bar{X}_n = \frac{1}{n} \sum_{i=1}^n X_i$.
-Since $\sqrt{n}(\bar{X}_n-\theta)$ converges to $\mathcal N(0,\sigma^2)$, this ARE is defined as
-\begin{equation}
-{\sigma^2}  \mathbb E\left(\widehat{\theta}_n - \theta \right)^2. 
-\label{eq:relative_efficiency}
-\end{equation}
-%{\color{red} Since the conditional expectation of $\theta$ with respect to $\bar{X}_n$ (and not $\bar{X}_n$) minimizes \eqref{eq:error_def}, we need to justify the fact that we use the sample mean as the reference estimator.}
-
-In addition to the notations defined above, we denote by $\phi(x)$ the standard normal density and by $\Phi(x)$ the standard normal cumulative distribution function.
-\\%Derivatives with respect to $\theta$ are denoted by prime.\\
-
-Before deriving our main results, we comment on the relation between our setting and the remote multiterminal source coding problem.
-
-\section{Relation to Remote Multiterminal Source Coding \label{sec:ceo}}
-In this section we draw a connection between our general problem of mean estimation from one-bit samples, to the remote multiterminal source coding problem \cite{berger1996ceo}, also known as the CEO problem.
-The setting of the CEO includes $n$ encoders, each has access to a noisy version of a random source sequence.
-% $\left\{ U_j,\,j=1,2,\ldots \right\}$. 
-The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator. \par
-Assuming that $\theta$ is drawn randomly once from a prior $\pi(\theta)$, mean estimation from one-bit under distributed encoding (setting (iii) in the Introduction) corresponds to the CEO setting with block length $k=1$, where the $i$th encoder observes
-\begin{equation}
-\label{eq:Gaussian_channel}
-X_i = \theta + \sigma Z_i,
-\end{equation}
-with $Z_1,\ldots,Z_n$ i.i.d.
-standard normal, and uses $R_i=1$ bits to transmit its observation.
-As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise at each estimate of variance $\sigma^2$, provides a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting.
- \\
-
-A closed-form expression for the MSE distortion in the CEO is known only for the case where the source sequence is sampled independently from the normal distribution \cite{prabhakaran2004rate}.
-By using the characterization of this minimal distortion as the number of terminals goes to infinity, we conclude the following:
-\begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$. Then any estimator $\widehat{\theta}_n$ of $\theta$ in 
-the distributed setting satisfies
-\begin{equation} \label{eq:ceo_bound}
- n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + o(1).
-\end{equation}
-\end{prop}
-
-\begin{proof}
-We consider the expression \cite[Eq. 10]{chen2004upper} that provides the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-Assuming $R_\Sigma = n$ and $L=n$, we get
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-n = \frac{1}{2} \log \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-The value of $D^\star$ that satisfies the equation above describes the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed encoding setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$, we conclude that
-\[
-D^\star = \frac{ \frac{4\sigma^2}{3} }{n + \frac{4 \sigma^2}{3 \sigma_\theta^2} } + O(e^{-n}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-\end{proof}
-Since the lower bound \eqref{eq:ceo_bound}  was derived assuming optimal allocation of the $n$ bits among the encoders, it may seem as if a tighter bound can be obtained in our case by considering the CEO distortion with $R_1=\ldots,R_n = 1$.
-However, an upper bound for the CEO distortion under this condition follows from \cite[Prop.
-5.2]{KipnisRini2017}, and leads to
-\[
-D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + o(n^{-1}),
-\]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small. \par
-We conclude therefore that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed encoding setting, is attributed exclusively to the ability to perform coding over blocks.
-Namely, the ability to consider $k>1$ independent realizations of $\theta$ versus only one in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product space, rather than the distributed nature of the problem, that distinguishes between the CEO distortion and the mean estimation from one-bit samples.\par
-In the next section we show that the ARE in adaptive encoding setting does not exceeds $\pi/2$, and thus provides a tighter lower bound for the distributed encoding setting than $4/3$ of  \eqref{eq:ceo_bound}.
-
-\section{Results \label{sec:sequential}}
-The first main result of this paper, as described in Thm.~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be lower than $\pi/2$.
-Next, we provide a particular adaptive estimation scheme and show in Thm.~\ref{thm:sgd} that its efficiency is $\pi/2$.
-Finally, in Thm.~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen.
-While it is not clear whether the efficiency of this last scheme is $\pi/2$, numerical simulations suggests that the MSE of this scheme times $n$ also converges to $\pi/2$.
-
-%\begin{figure}
-%\begin{center}
-%\begin{tikzpicture}[node distance=2cm,auto,>=latex]
-%  \node at (0,0) (theta) {$\theta$} ;
-%  \node at (2,0) (x1) {$X_1$};
-%  \node[below of = x1, node distance = 1cm] (x2) {$X_2$};
-%    \node[below of = x2, node distance = 1cm] (dots) {$\vdots$};
-%  \node[below of = dots, node distance = 1cm] (xn) {$X_n$};
-%  
-%   \node[right of = x1, node distance = 2cm] (m1) {$M_1$};
-%  \node[right of = x2, node distance = 2cm] (m2) {$M_2$};
-%    \node[right of = xn, node distance = 2cm] (mn) {$M_n$};
-%
-%\draw[->] (theta) -- (x1);
-%\draw[->] (theta) -- (x2);
-%\draw[->] (theta) -- (xn);
-%
-%\draw[->] (x1)--(m1);
-%\draw[->] (x2)--(m2);
-%\draw[->] (xn)--(mn);
-%
-%\draw[->] (m1)--(m2);
-%\draw[->, dashed] (m2)--(mn); 
-%  
-%\end{tikzpicture}
-%\end{center}
-%\caption{\label{fig:sequencial_graphical} Graphical model notation of the sequential setting.}
-%\end{figure}
-
-%\subsection{Properties of an Optimal Scheme}
-%The sequential nature of the encoding and the estimation is best explain by the notions of actions and rewards taken from dynamic programming.
-The \emph{action} taken by the $i$th encoder is the design of a detection region $M_i^{-1}(1)$ that would lead to $M_i = 1$ assuming when $X_i \in M_i^{-1}(1)$ or $M_i=-1$ otherwise.
-The \emph{reward} (or penalty) is only evaluated at the end of the time horizon $n$.
-%% Dynamic program. State = $M^n$. 
-%% Reward is collected at the end
-%%
-
-\subsection{A lower bound on adaptive one-bit schemes}
-Our first results asserts that the ARE \eqref{eq:relative_efficiency} of any adaptive estimation scheme is bounded from below by $\pi/2$, as follows from the following theorem:
-\begin{thm}[minimal relative effeciency] \label{thm:adpative_lower_bound}
-Let $\widehat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Fig.~\ref{fig:sequential}.
-% Let $\pi(\theta)$ be an absolutely continuous prior distribution on $\Theta$ with density function converges to zero at the endpoints of the interval $\Theta$. 
-Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\pi}{2n}\sigma^2+o(n^{-1}),
-\]
-where 
-\[
-I_0 = \mathbb E \left( \frac{d}{d\theta} \log \pi (\theta) \right)^2
-\]
-is the Fisher information with respect to a location model in $\theta$. 
-\end{thm}
-
-\subsubsection*{Sketch of Proof}
-The main idea in the proof is to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$.
-Once this bound is achieved, the result follows by using the van-Trees inequality \cite[Thm.
-2.13]{tsybakov2008introduction},\cite{gill1995applications} which bounds from below the MSE of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are given in the Appendix.\\
-
-Next, we present an adaptive estimation scheme that attains ARE of $\pi/2$. 
-\subsection{Asymptotically optimal estimator}
-Consider the following estimator $\widehat{\theta}_n$ for $\theta$:  set 
-\begin{equation}
-\label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n \sgn (X_n - \theta_n), \quad n = 1,2,\ldots,
-\end{equation}
-where $\left\{\gamma_n \right\}_{n=1}^\infty$ is any strictly positive sequence satisfying 
-\begin{enumerate}
-\item[(i)] $\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n)$ \\
-\item[(ii)] $\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty$ 
-for some $0< \lambda \leq 1$.
-\end{enumerate}
-(e.g. $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). The $n$th step estimation is defined by 
-\begin{equation} \label{eq:sgd_est}
-\widehat{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
-\end{equation}
-
-For the estimator defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} 
-we have the following results:
-\begin{thm} \label{thm:sgd}
-The sequence $\widehat{\theta}_n$ of \eqref{eq:sgd_est} satisfies
-\[
-\sqrt{n} \left( \widehat{\theta}_n - \theta \right) \overset{d}{\rightarrow} \mathcal N \left(0,  \pi \sigma^2 /2 \right).
-\]
-\end{thm}
-
-\subsubsection*{Proof}
-The asymptotic behavior of \eqref{eq:sgd_est} is a special case of  \cite[Thm. 4]{polyak1992acceleration}. The details are provided in the Appendix.\\
-
-In other words, Thm.~\ref{thm:sgd} implies that the estimator $\widehat{\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the minimal asymptotic efficiency as established by Thm.~\ref{thm:adpative_lower_bound}.\par
-Note that $\theta_0$ is not explicitly defined 
-in equation \eqref{eq:sgd_est}.
-While a reasonable initialization is $\theta_0 = \mathbb E [\theta]$,  Thm.~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
-Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the size of the parameter space $\Theta$.
-Nevertheless, the bound in Thm.~\ref{thm:adpative_lower_bound} suggests that the non-asymptotic estimation error can be greatly reduced whenever the location information $I_0$ is large.
-In contrast, the one-step optimal scheme presented in the following subsection exploits the prior information on $\theta$ provided by $\pi(\theta)$.
-
-\subsection{One-step optimal estimation}
-We now consider an estimation scheme that posses the property of \emph{one-step optimality}: at each step $i$, the $i$th encoder designs the detection region $M_i^{-1}(1)$ such that the MSE given $M^i$ is minimal.
-In other word, this scheme designs the messages in a greedy manner, such that the MSE at step $i$ is minimal given the current state of the estimation described by $M^{i-1}$.
-\\
-
-The following theorem determine the structure of the message that minimizes the next step MSE:
-\begin{thm}[optimal one-step estimation] \label{thm:opt_one_step}
-Let $\pi(\theta)$ be an absolutely continuous log-concave probability distribution. Given a sample $X$ from the distribution $\mathcal N(\theta, \sigma^2)$, define 
-\begin{equation}
-\label{eq:adaptive_main_message}
-M = \sgn(X - \tau),
-\end{equation}
-where $\tau$ satisfies the equation
-\begin{equation}
- \label{eq:fixed_point}
- \tau = \frac{m^-(\tau) + m^+(\tau)}{2},
-\end{equation}
-with
-\begin{align*}
-m^-(\tau)  & = \frac{\int_{-\infty}^{\tau} \theta \pi(d\theta) }{\int_{-\infty}^{\tau} \pi(d\theta)} ,\\
-m^+(\tau) & = \frac{\int_{\tau}^\infty \theta \pi(d\theta) }{\int_{\tau}^\infty \pi(d\theta)} .
-\end{align*}
-Then for any estimator $\widehat{\theta}$ which is a function of $M'(X) \in \{-1,1\}$, we have
-\begin{equation}
-\label{eq:opt_cond}
-\mathbb E \left(\theta-\widehat{\theta}(M')\right)^2 \geq  \mathbb E \left(\theta- \mathbb E[\theta|M]\right)^2,
-\end{equation}
-\end{thm}
-
-\begin{proof}
-The proof is completed by the following two lemmas, proofs of which can be found in the Appendix:
-\begin{lem} \label{lem:unique}
-Let $f(x)$ be a log-concave probability density function. Then the equation 
-\begin{equation}
-\label{eq:lem_fixed_point}
-2x = \frac{\int_x^\infty uf(u)du}{\int_x^\infty f(u)du} + \frac{\int_{-\infty}^x uf(u)du}{\int_{-\infty}^x f(u)du} 
-\end{equation}
-has a unique solution.
-\end{lem}
-\begin{lem} \label{lem:adaptive}
-Let $U$ be an absolutely continuous random variable with
-pdf $P(du)$. Then the one-bit message $M^\star\in \{-1,1\}$ that minimizes
-\[
-\int \left( u - \mathbb E[U|M(u)]  \right)^2 P(du)
-\]
-is given by
-\[
-M^\star  =  \sgn(U - \tau),
-\]
-where $\tau$ is the unique solution to
- \[
-2 \tau = \frac{\int_{\tau}^\infty u P(du)} {\int_{\tau}^\infty P(du)} + \frac{\int_{-\infty}^{\tau} u P(du)}{\int_{-\infty}^{\tau} P(du)}.
-\]
-\end{lem}
-\end{proof}
-
-Thm.~\ref{thm:opt_one_step} suggests the following adaptive encoding and estimation scheme: 
-\begin{itemize}
-\item Initialization: set $P_0(t) = \pi(\theta)$.
-\item For $n\geq 1$:
-\begin{enumerate}
-\item Update the prior as
-\begin{align}
-P_n(t) = & P(\theta=t |M^n) \\
-& = \frac{ P\left( \theta=t | M^{n-1} \right) P(M_n | \theta = t , M^{n-1})  } { P(M_n | M^{n-1} )} \nonumber \\ 
-& = \alpha_n  P_{n-1}(t) \Phi\left(M_n \frac{ t - \tau_{n-1} }{\sigma} \right), \label{eq:density_update}
-\end{align}
-where $\alpha_n$ is a normalization coefficient that equals to
-\[
-\alpha_n = \left(\int_{\mathbb R} P_{n-1}(t) \Phi\left(M_n \frac{t- \tau_{n-1} }{\sigma} \right)  dt \right)^{-1}. 
-\]
-\item The $n$th estimate for $\theta$ is the conditional expectation of $\theta$ given $M^n$, namely
-\begin{equation}
-\theta_n = \mathbb E \left[ \theta| M^n\right] = \int_{-\infty}^\infty t P_n(t) dt. \label{eq:estimator_update}
-\end{equation}
-\item Solve equation \eqref{eq:fixed_point} with the updated prior $P_n(t)$ instead of $P(d\theta)$.
-Note that since the standard normal cdf $\Phi(x)$ is log-concave, the updated prior $P_n(t)$ remains log-concave and thus a unique solution to \eqref{eq:fixed_point} is guaranteed by Lem.~\ref{lem:unique}.
-\item Update the $(n+1)$th message as
-\begin{equation}\label{eq:message_update}
-M_{n+1} = \sgn(X_{n+1}-\tau_n)
-\end{equation}
-\end{enumerate}
-\end{itemize}
-Since equation \eqref{eq:fixed_point} has no analytic solution in general, it is hard to derive the asymptotic behavior of the estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}.
-We conjecture, however, that it attains the asymptotic relative efficiency of $\sigma^2\pi/2$, as can be observed from the numerical simulation illustrated in Fig.~\ref{fig:adaptive_error}.
-Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the asymptotically optimal estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the sample mean for the same sample realization.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}
-\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
-%\node[color = blue,  minimum width=1cm, align = left] at (1.5,1.5) {assymptotically optimal \eqref{eq:sgd_est}};
-%\node[color = red, minimum width=1cm, align = left] at (1.5,0.55) {one-step optimal \eqref{eq:message_update}} ;
-\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left(\widehat{\theta}_n - \theta \right)^2$};
-\node[scale = 0.7] at (0,-2.4) {$n$};
-%\draw[dashed] (-3.5,1.18) node[left, scale = 0.7] {$\frac{\pi}{2}$}-- (-3,1.18);
-\end{tikzpicture}
-\caption{Normalized empirical risk $n\left(\widehat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $500$ Monte Carlo trials.
-In each trial, $\theta$ is chosen uniformly in the interval $(-3,3)$.
-\label{fig:adaptive_error}  }
-\end{center}
-\end{figure}
-
-\section{Conclusions \label{sec:conclusions}}
-We considered the MSE risk and asymptotic relative efficiency in estimating the mean of a normal distribution from a single-bit encoding of each sample from this distribution.
-In the adaptive scenario where each one-bit message is a function of the previously seen messages and current sample, we showed that the minimal relative efficiency is $\pi/2$.
-Namely, there is a penalty factor of at least $\pi/2$ on the asymptotic MSE risk in estimating the mean compared to an estimator that has full access to the sample.
-We also showed that this lower bound is tight by presenting an adaptive estimation procedure that attains it.
-%but ignores the prior distribution on the parameter space.
-In addition, we characterized the single-bit message that minimizes the next step MSE, and described an estimation procedure that is based on a sequence of one-step optimal messages.
-We leave open the questions whether this estimator attains the minimal efficiency and whether it leads to an estimation scheme which is globally optimal in the adaptive setting.
-Another open question that follows from our setting is the asymptotic MSE and relative efficiency of a fully distributed one-bit scheme.
-
-%\section*{ACKNOWLEDGMENT}
-%This research is supported in parts by...
-%Tsachy Weissman, Stefano Rini, Robert Gray.
-
-\appendix
-
-\section{Proofs}
-In this appendix we provide detailed proofs of our main results as described in Section~\ref{sec:sequential}.
-
-\subsection*{Proof of Thm.~\ref{thm:adpative_lower_bound}}
-
-We first prove the following two lemmas:
-\begin{lem} \label{lem:bound_intervals}
-For any $x_1 \geq \ldots \geq x_n \in \mathbb R$, we have 
-\begin{equation}
-\frac{ \left(  \sum_{k=1}^n (-1)^{k+1}\phi(x_k) \right)^2} 
-{\left( \sum_{k=1}^n (-1)^{k+1} \Phi(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} \Phi(x_k) \right)  } \leq \frac{2} {\pi}. \label{eq:bound_intervals}
+\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
+{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)  } \leq \frac{2} {\pi}. \label{eq:bound_intervals}
 \end{equation}
 \end{lem}
-\begin{lem} \label{lem:fisher_bound}
-Let $X\sim \mathcal N(\theta,\sigma^2)$ and assume that 
-\[
-M(X) = \begin{cases} 1,& X \in A, \\
--1, & X \notin A.
-\end{cases}
-\]
-Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $2/(\pi \sigma^2)$.
-\end{lem}
 
-\subsubsection*{Proof of Lem.~\ref{lem:bound_intervals}}
-We use induction on $n \in \mathbb N$. For the base case $n=1$ we have 
+\subsubsection*{Proof of Lem.~\ref{lem:bound_intervals}}We use induction on $n \in \mathbb N$. For the base case $n=1$ we have 
 \begin{equation} \label{eq:induction_base}
-\frac{  \phi^2(x)} 
-{\Phi(x) \left(1 - \Phi(x) \right) }. 
+\frac{  f^2(x)} 
+{F(x) \left(1 - F(x) \right) }.
 \end{equation}
-Taking the logarithm of \eqref{eq:induction_base} and differentiating, we conclude that any point $x$ that maximizes \eqref{eq:induction_base} also satisfies
-\[
-x = \phi(x) \frac{\Phi(x) -\frac{1}{2}}{\Phi(x)(1-\Phi(x))} .
-\]
-However, since 
-\[
-x > \phi(x) \frac{\Phi(x) -\frac{1}{2}}{\Phi(x)(1-\Phi(x))}
-\]
-for all $x > 0$, the only point that satisfies the last condition is $x=0$, in which \eqref{eq:induction_base} equals $2/\pi$. \par
+Since $f(x)$ is log-concave, so does $F(x)$.
+We now write $F(x) = e^{h(x)}$ with $h(x)$ concave.
+Note that $f(x) = h'(x) e^{h(x)}$, $h'(x)\geq 0$, $f(x) = f(-x) = h'(-x)e^{h(-x)} $, and $h''(x)\leq 0$ ($h(x)$ is twice differentiable since $F(x)$ is twice differentiable).
+Taking the logarithm of \eqref{eq:induction_base} leads to 
+\begin{align*}
+& 2 \log f(x) - \log F(x) + \log F(-x) \\
+& = 2 \log h'(x) + h(x) + h(-x).
+\end{align*}
+Since $h'(x)$ is non-increasing, the maximal value of \eqref{eq:induction_base} is obtained as 
+{HERE!! \color{red} finish proof by showing that \eqref{eq:induction_base} is smaller than $4f(0)$.\\
+}
+\\
 Assume now that \eqref{eq:bound_intervals} holds for all integers up to some $n = N-1$ and consider the case $n = N$.
@@
 \begin{align*}
-& g(x_1,\ldots, x_N) \triangleq 2 \log \left(  \sum_{k=1}^{N} (-1)^{k+1} \phi(x_k) \right) - \\
+& g(x_1,\ldots, x_N) \triangleq 2 \log \left(  \sum_{k=1}^{N} (-1)^{k+1} f(x_k) \right) - \\
 &  \log
-\left( \sum_{k=1}^N (-1)^{k+1} \Phi(x_k) \right)
--\log \left(1 -  \sum_{k=1}^N (-1)^{k+1} \Phi(x_k) \right) \\
+\left( \sum_{k=1}^N (-1)^{k+1} F(x_k) \right)
+-\log \left(1 -  \sum_{k=1}^N (-1)^{k+1} F(x_k) \right) \\
 & = 2 \log \delta_N - \log \Delta_N - \log \left(1 - \Delta_N  \right),
 \end{align*}
-where we denoted $\delta_N \triangleq \sum_{k=1}^{N} (-1)^{k+1} \phi(x_k)$ and $\Delta_N =  \sum_{k=1}^N (-1)^{k+1} \Phi(x_k)$. The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
+where we denoted $\delta_N \triangleq \sum_{k=1}^{N} (-1)^{k+1} f(x_k)$ and $\Delta_N =  \sum_{k=1}^N (-1)^{k+1} F(x_k)$. The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
 \[
-\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} \phi'(x_k)}{\delta_N} -\frac{(-1)^{k+1} \phi(x_k)}{\Delta_N } + \frac{(-1)^{k+1} \phi(x_k)}{1-\Delta_N }.
+\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(-1)^{k+1} \phi(x_k)}{1-\Delta_N }.
 \]
-Using the fact that $\phi'(x) = -x \phi(x)$, we conclude that the gradient of $g$ vanishes only if
+We conclude that the gradient of $g$ vanishes only if
 \[
-x_k = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
+\frac{f'(x_k)}{f(x_k)} = g'(x_k) = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
 \]
-In particular, the condition above implies $x_1 = \ldots = x_N$. If $N$ is odd then for $x_1=\ldots =x_N$ we have that the LHS of \eqref{eq:bound_intervals} equals
+Due to our assumption that $g''(x) < 0$, the function $g'(x)$ is strictly decreasing.
+As a result, $g'(x)$ is one to one and the condition above implies $x_1 = \ldots = x_N$.
+If $N$ is odd then for $x_1=\ldots =x_N$ we have that the LHS of \eqref{eq:bound_intervals} equals
 \[
-\frac{\phi(x_1)^2}{ \Phi(x_1) (1 - \Phi(x_1))},
+\frac{f(x_1)^2}{ F(x_1) (1 - F(x_1))},
 \]
-which was shown to be smaller than $\pi/2$.
+which was shown to be smaller than $4f^2(0)$.
 If $N$ is even, then for any constant $c$ the limit of the LHS of \eqref{eq:bound_intervals} as $(x_1,\ldots,x_N)\rightarrow (c,\ldots,c)$ exists and equals zero.
@@
 \begin{align*}
-\frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}\phi(x_k) \right)^2} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} \Phi(x_k) \right)\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} \Phi(x_k)  \right) } ,
+\frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^2} 
+{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right) } ,
 \end{align*}
@@
 \begin{align*}
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}\phi(x_k) \right)^2} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} \Phi(x_k) \right)\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} \Phi(x_k)  \right) }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}\phi(x'_m) \right)^2} 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} \Phi(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} \Phi(x'_{m})  \right) },
+& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^2} 
+{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right) }  \\
+& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^2} 
+{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right) },
 \end{align*}
-where $x'_{m} = x_{m+1}$. The last expression is also smaller than $2/\pi$ by the induction hypothesis. This proves Lem.~\ref{lem:bound_intervals}. \\
+where $x'_{m} = x_{m+1}$. The last expression is also smaller than $4f(0)$ by the induction hypothesis. This proves Lem.~\ref{lem:bound_intervals}. \\
 
@@
 Therefore, the proof of  Lem.~\ref{lem:fisher_bound} is now completed.
- \\
-
-We now consider the proof of Thm.~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$, we first note that, without loss of generality, each message $M_i$ can be written in the form
-\begin{equation}
-\label{eq:general_messages}
-M_i = \begin{cases}
-X_i \in A_i & 1, \\
-X_i \notin A_i & -1,
-\end{cases} 
-\end{equation}
-where $A_i \subset \mathbb R$ is a Lebesgue measurable set.
-Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = M^{-1}(1)$.
-Consider the conditional distribution $P({M^n|\theta})$ of $M^n$ given $\theta$.
-We have
-\begin{align}
-P\left( M^n | \theta \right) & =  \prod_{i=1}^n P\left(M_i | \theta, M^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
-\end{align}
-where $P\left(M_i =1 | \theta, M^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$. The Fisher information of $M^n$ with respect to $\theta$ is given by 
-\begin{align}
-I_\theta(M^n) = \sum_{i=1}^n I_\theta (M_i|M^{i-1}),
-\label{eq:fisher_information}
-\end{align}
-where $I_\theta (M_i|M^{i-1})$ is the Fisher information of the distribution of $M_i$ given $M^{i-1}$, where it follows from Lem.~\ref{lem:fisher_bound} that $I_\theta (M_i|M^{i-1}) \leq 2/(\pi \sigma^2)$.
-We now use the following theorem from \cite[Thm.
-2.13]{tsybakov2008introduction} (see also \cite{van2004detection, gill1995applications}):
-
-\begin{thm}[The van Trees inequality \cite{tsybakov2008introduction}] \label{thm:vanTrees}  Denote by $p(\cdot,\theta)$ the density of $P_\theta$ with respect to the Lenesgue measure.
-Assume that: (i) the density $p(x,\theta)$ is measureable in $(x,\theta)$ and absolutely continuous in $t$ for almost all $x$ with respect to the Lebesgue measure.
-(ii) The Fisher information
-\[
-I(\theta) = \int \left( \frac{p'(x,\theta)}{p(x,\theta)} \right)^2 p(x,\theta) dx,
-\]
-where $p'(x,t)$ denotes the derivative of $p(x,\theta)$ in $t$, is finite and integrable on $\Theta$.
-(iii) The prior density $\pi(\theta)$ is absolutely continuous on its support $\Theta$ with zero mass at the boundries of $\Theta$, and has a finite Fisher information
-\[
-I_0 = \int_{\Theta} \frac{\left( \pi'(\theta) \right)^2} {\pi(\theta)} d\theta.
-\]
-Then, for any estimator $\widehat{t}(\mathbf X)$, the Bayes risk is bounded as follows:
-\[
-\int_{\theta} \mathbb E \left[ \left( \widehat{t}(\mathbf X) - \theta\right)^2 \right] \pi(d\theta) \geq \frac{1}{ \int I(\theta) \pi(d \theta) + I_0 }.
-\]
-\end{thm}
-Theorem~\ref{thm:vanTrees} applied to our problem with $p(x,\theta) = P(M^n|\theta)$ implies
-\begin{align*}
-\mathbb E \left(\widehat{\theta}_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(M^n) + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (M_i | M^{i-1} ) + I_0} \\
-& \geq \frac{1}{ 2n/(\pi \sigma^2) + I_0}.
-\end{align*}
-
-\QEDA
-
-\subsection*{Proof of Thm.~\ref{thm:sgd}}
-The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration}.
-In particular, Thm.~\ref{thm:sgd} is follows directly from the following simplified version of \cite[Thm.
-4]{polyak1992acceleration}:
-\begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
-Let 
-\[
-X_i = \theta + Z_i,\quad i=1,\ldots,n,
-\]
-where the $Z_i$s are i.i.d. with zero mean. Define 
-\begin{align*}
-\theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
-\widehat{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i,
-\end{align*}
-where the sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions (i) and (ii) in Thm.~\ref{thm:sgd}, and $\left| \varphi(x) \right| \leq K_1(1+x)$ for some $K_1$.
-Define $\psi(x) = \mathbb E \varphi(x+Z_1)$, $\chi(x) = \mathbb E \varphi^2(x+Z_1)$ and assume that $\psi(0)=0$, $x\psi(x) >0$ for all $x\neq 0$, $\chi(x)$ is continuous at zero, and that $\psi(x)$ is differentiable at zero with $\psi'(0)>0$.
-Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
-\[
-\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\gamma}.
-\]
-Then $\widehat{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}(\widehat{\theta}_n - \theta)$ converges in distribution to $\mathcal N(0,V)$, where
-\[
-V = \frac{ \chi(0)} {\psi'^2(0)}. 
-\]
-\end{thm}
-
-Using the notation in Thm.~\ref{thm:polyak_juditsky}, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have: 
-\[
-\chi(x) = \mathbb E \varphi^2(x+Z_1),
-\]
-so $\chi(0) = 1$. In addition,
-\begin{align*}
-\psi(x) & = \mathbb E \sgn(x+ Z_1) = \int_{-\infty}^\infty \sgn(x+z) \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{2\sigma^2}} dz \\
-& = \int_{-x}^\infty \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{2\sigma^2}} dz -\int_{-\infty}^{-x} \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{2\sigma^2}} dz.
-\end{align*}
-This leads to 
-\begin{align*}
-\psi'(x) & = \frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{x^2}{2\sigma^2}} dz +\frac{1}{\sqrt{2\pi}\sigma} e^{-\frac{z^2}{2\sigma^2}} dz,
-\end{align*}
-so $\psi'(0) = \frac{2}{\sqrt{2\pi}\sigma}$. It is now easy to verify that the rest of the conditions in Thm.~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$. Since 
-\[
-\frac{\chi(0)}{\psi'^2(0)} = \frac{\pi \sigma^2}{2},
-\]
-Thm.~\ref{thm:sgd} follows from Thm.~\ref{thm:polyak_juditsky}. \QEDA
-
-\subsection*{Proof of Thm.~\ref{thm:opt_one_step}}
-In this subsection we prove Lemmas \ref{lem:adaptive} and \ref{lem:unique} that lead to Thm.~\ref{thm:opt_one_step}.
-
-\subsubsection*{Proof of Lem. \ref{lem:adaptive}}
-Since any single-bit message $M(u) \in \{-1,1\}$ is characterized by two decision region $A_1 = M^{-1}(1)$ and $A_{-1} = M^{-1}(-1)$, it follows that $\mathbb E \left[ U | M(U) \right]$ assumes only two values: $\mu_1 = \mathbb E \left[ U | M(U) = 1 \right]$ and $\mu_{-1} = \mathbb E \left[ U | M(U) = -1 \right]$.
-We claim that a necessary condition for $M(u)$ to be optimal is that the sets $A_1$ and $A_{-1}$ are, modulo a set of measure $P(du)$ zero, the Voronoi sets on $\mathbb R$ corresponding to the points $\mu_1$ and $\mu_{-1}$, respectively.
-Indeed, assume by contradiction that for such an optimal partition there exists a set $B \subset A_{1}$ with $\mathbb P (U \in B) >0$ such that $\left( b-\mu_{1} \right)^2 > \left( b- \mu_{-1} \right)^2$.
-The expected square error in this partition satisfies:
-\begin{align*}
-& \int_{\mathbb R} \left( u - \mathbb E[U|M(u)]  \right)^2 P(du) \\
-& = \int_{A_1} (u- \mu_1)^2 P(du) + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
-& = \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_1)^2 P(du) \\
-&\quad \quad + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
-& > \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_2)^2 P(du) \\
-& + \quad \quad  \int_{A_{-1}} (u- \mu_{-1})^2 P(du),
-\end{align*}
-so clearly, the partition $A_1' = A_1 \setminus B$, $A_{-1}' = A_{-1} \cup B$ attains lower error variance, what contradicts the optimality assumption and proves our claim.
-It is evident that Voronoi partition of the real line corresponding to $\mu_1$ and $\mu_{-1}$ is of the form $A_{-1} = (-\infty,\tau)$, $A_{1} = (\tau, \infty)$ where the point $\tau$ is of equal distance from $\mu_1$ and $\mu_{-1}$, namely $\tau = \frac{\mu_1 + \mu_{-1}}{2}$.
-From these two conditions (which are a special case of the conditions derived in \cite{1056489} for two quantization regions) we conclude that $\tau$ must satisfy the equation
-\[
-2 \tau = \frac{\int_{\tau}^\infty u P(du)}{\int_{\tau}^\infty P(du)} + \frac{\int_{-\infty}^{\tau} u P(du)}{\int_{-\infty}^{\tau} P(du)}.
-\] 
-\QEDA
-
-\subsubsection*{Proof of Lem. \ref{lem:unique}} 
-Any solution to \eqref{eq:lem_fixed_point} is a solution to $h^+(x) = h^-(x)$ where
-\[
-h^+(x) = \frac{\int_x^\infty uf(u)du}{\int_x^\infty f(u)du} - x 
-\]
-and
-\[
-h^-(x) = x - \frac{\int_{-\infty}^x uf(u)du}{\int_{-\infty}^x f(u)du}.
-\]
-We now prove that $h^+(x)$ is monotonically decreasing while $h^-(x)$ is increasing, so they meet at most at one point. The derivative of $h^-(x)$ is given by
-\begin{equation} 
-\label{eq:one_step_proof_derivative}
-1 - \frac{ f(\tau) \int_{-\infty}^\tau f(x) (\tau-x)dx } {\left( \int_{-\infty}^\tau f(x) dx \right)^2}.
-\end{equation}
-Denote $F(x) = \int_{-\infty}^x f(u)du$.
-Using integration by parts in the numerator and from the fact that $\lim_{\tau \rightarrow -\infty}  \tau \int_{-\infty}^\tau f(x) dx = 0$, the last expression can be written as
-\[
-1- \frac{ f(\tau) \int_{-\infty}^\tau F(x) dx}
- {\left( F(\tau) \right)^2}.
-\]
-Log-concavity of $f(x)$ implies log-concavity of $F(x)$, so that we can write $F(x) = e^{g(x)}$ for some concave and differentiable function $g(x)$.
-Moreover, we have $f(x) = g'(x)e^{g(x)}$ where, by concavity of $g(x)$, the derivative $g'(x)$ of $g(x)$ is non-increasing.
-With these notation we have
-\begin{align*}
-\frac{ f(\tau) \int_{-\infty}^\tau F(x) dx}
- {\left( F(\tau) \right)^2} & = \frac{g'(\tau)e^{g(\tau)} \int_{-\infty}^\tau e^{g(x)}dx }{ e^{2g(\tau)} } \\
- & = e^{-g(\tau)} \int_{-\infty}^\tau g'(\tau) e^{g(x)} dx  \\
- & \leq e^{-g(\tau)} \int_{-\infty}^\tau g'(x) e^{g(x)} dx \\
- & = e^{-g(\tau)} F(\tau) = 1.
-\end{align*}
-(where the second from the last step follows since $g'(x) \leq g'(\tau)$ for any $x\leq \tau$).
-If follows that \eqref{eq:one_step_proof_derivative} is non-negative and thus $h^-(x)$ is monotonically increasing.
-Since
-\[
-h^+(-x) = x - \frac{ \int_{-\infty}^{x} uf(-u)du}{ \int_{-\infty}^x f(-u) du }, 
-\]
-the fact that $h^+(x)$ is monotonically decreasing follows from similar arguments.
-Moreover, since the derivatives of $h^+(x)$ and $h^-(x)$ never vanish at the same time over any open interval, their difference cannot be constant over any interval.
-Finally, since
-\begin{align*}
- \lim_{x\rightarrow -\infty} h^+(x) =  \lim_{x\rightarrow \infty} h^-(x)
-\end{align*}
-and since non of these functions are constant, monotonicity of $h^+(x)$ and $h^-(x)$ implies that they must meet at a single point in $\mathbb R$. \QEDA
-
-\section{Acknowledgments}
-The work of A. Kipnis is partially supported by NSF Center for Science of Information (CSoI) under grant CCF-0939370 and NSF-BSF under grant 1609695.
 

### 2017-10-01 Writeups/onebit_adaptive_Allerton_V3.tex
after addressing John's comments

@@
 We consider an adaptive estimation setting where the single-bit sent at step $n$ is a function of both the new sample and the previous $n-1$ acquired bits.
-For this setting, we show that no estimator can attain asymptotic mean squared error smaller than $\pi/(2n)$ times the variance.
+For this setting, we show that no estimator can attain asymptotic mean squared error smaller than $\pi/(2n)+o(n^{-1})$ times the variance.
 %
@@
 %
-In addition, we provide an explicit estimator that attains this asymptotic error, showing that, rather surprisingly, only $\pi/2<1.571$ times more samples are required in order to attain estimation performance equivalent to the unrestricted case.
+In addition, we provide an explicit estimator that attains this asymptotic error, showing that, rather surprisingly, only $\pi/2$ times more samples are required in order to attain estimation performance equivalent to the unrestricted case.
 \end{abstract}
@@
 In this scenario, the ability to estimate a particular parameter from data collected by the sensors is dictated not only by quality of observations and their numbers, but also by the available communication rate between the sensors and the central estimator.
-The question that we ask is to what extend a parametric estimation task is affected by communication constraints, and what are the fundamental performance limits in estimating a parameter subject to these restrictions.
-In this paper we answer this question in a particular simple setting: the estimation of the mean $\theta$ of a normal distribution with a known variance $\sigma^2$, under the constraint that only a single bit can be communicated on each sample $X_n$ from this distribution.
+The question that we ask is to what extent a parametric estimation task is affected by communication constraints, and what are the fundamental performance limits in estimating a parameter subject to these restrictions.
+In this paper we answer this question in a particular simple setting: the estimation of the mean $\theta$ of a normal distribution with variance $\sigma^2$ under the constraint that only a single bit can be communicated on each sample $X_n$ from this distribution.
 As it turns out, the ability to share information among different samples before sending each single-bit message dramatically affects the performance in estimating $\theta$.
@@
 We measure the estimation performance by the mean squared error (MSE) risk.
-Since without bit constraint this risk is equals $\sigma^2/n$, we are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting, defined by the ratio between their MSE to $\sigma^2/n$ as $n$ goes to infinity.
-\\
+Since without bit constraint this risk is equals $\sigma^2/n$, we are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting, defined by the ratio between their MSE to $\sigma^2/n$ as $n$ goes to infinity when this MSE has a limit.
+The results in this paper focus on setting (ii), which corresponds to an estimation scenario with feedback or with multiple rounds of communication between a sensor and an estimation unit.
+\\% Evidently, the lower bound on the ARE we derive for setting (ii) also applies to setting (iii).
 
 In setting (i) the estimator can evaluate the sample mean and then communicate it using $n$ bits.
-This strategy leads to MSE behavior of $\sigma^2/n + o(2^{-n})$.
+This strategy leads to MSE behavior of $\sigma^2/n + O(2^{-n})$.
 Therefore, the ARE in this setting is $1$.
@@
 In this work we show that a similar result does not hold even in setting (ii): the ARE of any adaptive estimation scheme is at least $\pi/2$.
-Namely, the single-bit per sample constraint incurs a minimal penalty of at least $1.57$ compared to an unconstrained estimator or to the optimal estimator in setting (i).
-In addition to this negative statement, we provide an estimator that almost surely attains this ARE.
+Namely, the single-bit per sample constraint incurs a minimal penalty of at least $1.57$ in the number of samples compared to an unconstrained estimator or to the optimal estimator in setting (i).
+In addition to this negative statement, we provide an estimator that attains this ARE.
 In other words, we show that the lower bound of $\pi/2$ on the asymptotic relative efficiency is tight, and that it is attained regardless of the particular realization of $\theta$ or the size of the parameter space from which it is taken.
@@
 However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a noisy signal.
-For example, sigma-delta modulator (SDM) analog-to-digital conversion \cite{1092194} uses one-bit threshold detector combined with a feedback loop to update an accumulated error state, and therefore falls under setting (ii).
+For example, the sigma-delta modulator (SDM) analog-to-digital conversion \cite{1092194} uses one-bit threshold detector combined with a feedback loop to update an accumulated error state, and therefore falls under setting (ii).
 A SDM with a constant input $\theta$ corrupted by a Gaussian noise was studied in \cite{53738}, where it was shown that the output of the modulator converges to the true constant input almost surely.
@@
 
-We note that even the centralized encoding of setting (i) poses a non-trivial challenge for the design and analysis of optimal encoding and estimation scheme.
-Indeed, the standard technique to encode an unknown random quantity using $n$ bits is attained by a scalar quantizer.
-However, the optimal design of this quantizer depends on the distribution of its input \cite{gray1998quantization}, which is the goal of our estimation task.
-Therefore a non-trivial exploration exploitation tradeoff arises.
+We note that even through its ARE is $1$, the centralized encoding setting (i) already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation scheme.
+Indeed, the standard technique to encode an unknown random quantity using $n$ bits is equivalent to the design of a scalar quantizer \cite{gray1998quantization}.
+However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation task.
+Therefore, a non-trivial exploration exploitation tradeoff arise in this case.
 In our setting, the only missing parameter is the mean, which, under setting (i), is known to the encode with uncertainty interval proportional to $\sigma/\sqrt{n}$.
-Therefore, while it is clear that uncertainty due to quantization decreases exponentially in the number of bits, an exact expression for the MSE in this setting is not easy to derive.
+Therefore, while it is clear that uncertainty due to quantization decreases exponentially in the number of bits $n$, an exact expression for the MSE in this setting is not easy to derive.
 The situation is even more involved in the adaptive encoding of setting (ii): an encoding and estimation strategy that is globally optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$, may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
@@
 This connection, explained in details in Section~\ref{sec:ceo}, immediately leads to a lower bound of $4/3$ on the ARE in the distributed encoding of setting (iii).
-While this lower bound provides no new information compared to the lower bound of $\pi /2$ we derive here for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimal even under one-bit quantization of each sample.
+While this lower bound provides no new information compared to the lower bound of $\pi /2$ we derive later for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimal even under one-bit quantization of each sample.
 \\
@@
 
-The rest of this paper is organized as follows: the main problem and notation are defined in Section~\ref{sec:problem}.
+The rest of this paper is organized as follows: in Section~\ref{sec:problem} we define 
+the main problem and notation.
 In Section~\ref{sec:ceo} we illustrate a connection between our parametric estimation problem and the remote multiterminal lossy compression problem.
-Our main results are given in  Section~\ref{sec:sequential}, where we present a lower bound on estimation from one-bit samples in the adaptive scheme, as well as an achievable scheme that attains this bound.
+In Section~\ref{sec:sequential} we present our main results, deferring long proofs and technical results to the appendix.
 Concluding remarks are given in Section~\ref{sec:conclusions}.
-For sake of fluency, long proofs are deferred to the Appendix.
 
@@
 Let $X_i$, $i=1,\ldots,n$, be $n$ independent samples from the normal distribution with mean $\theta$ and variance $\sigma^2$. 
-We assume that the mean $\theta$ is drawn once from a prior distribution $\pi(\theta)$ on $\Theta$, which is a closed interval of the real line.
+%We assume that the mean $\theta$ belongs to $\Theta$, which is a closed interval of the real line.  
+We assume that the mean $\theta$ is drawn once from a prior distribution $\pi(\theta)$ on $\Theta$, which is a closed subset of the real line.
 We moreover assume that $\pi(\theta)$ is absolutely continuous with respect to the Lebesgue measure with density $\pi(d\theta)$.
-The problem we consider is the estimation of the parameter $\theta$ under the following constraints on the communication between the samples $X_1,\ldots,X_n$ and a centralized estimator:
+The problem we consider is the estimation of the parameter $\theta$ under the following constraints on the communication between the samples $X^n = (X_1,\ldots,X_n)$ and a centralized estimator:
 \begin{itemize}
@@
 where the expectation is taken with respect to the distribution of $X^n$ and the prior distribution $\pi(\theta)$. \\
-%It is well known that minmax estimation error 
-%\begin{equation}
-%E_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left(\widehat{\theta}_n - \theta \right)^2 | \theta \right],
-%\end{equation}
-%can be obtained from $\epsilon_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}.
 
@@
 This minimization is the combination of the following two procedures: (1) selecting the $i$th message $M_i$ based on past messages and current observation $X_i$, and (2) estimating $\theta$ given messages $M^n$.
-We are interested in particular in the ARE of estimators of $\theta$ compared to the sample mean $\bar{X}_n = \frac{1}{n} \sum_{i=1}^n X_i$.
-Since $\sqrt{n}(\bar{X}_n-\theta)$ converges to $\mathcal N(0,\sigma^2)$, this ARE is defined as
+%
+We are interested in particular on the increase in sample complexity compared to the vanilla mean estimation without one-bit constraint. For this reason, we consider the limit
 \begin{equation}
-{\sigma^2}  \mathbb E\left(\widehat{\theta}_n - \theta \right)^2. 
+{\sigma^2} n \mathbb E\left(\widehat{\theta}_n - \theta \right)^2,
 \label{eq:relative_efficiency}
 \end{equation}
+which is the ratio between the MSE of the sample mean and the MSE of the estimator $\widehat{\theta}_n$.
+Note that if the limit $\mathbb E\left(\widehat{\theta}_{n} - \theta \right)^2$ exists and finite, than \eqref{eq:relative_efficiency} is the ARE of $\widehat{\theta}_n$.
+
+%ARE of estimators of $\theta$ compared to the sample mean $\bar{X}_n = \frac{1}{n} \sum_{i=1}^n X_i$. Since $\sqrt{n}(\bar{X}_n-\theta)$ converges to $\mathcal N(0,\sigma^2)$, this ARE is defined as
+%\begin{equation}
+%{\sigma^2}  \mathbb E\left(\widehat{\theta}_n - \theta \right)^2. 
+%\label{eq:relative_efficiency}
+%\end{equation}
 %{\color{red} Since the conditional expectation of $\theta$ with respect to $\bar{X}_n$ (and not $\bar{X}_n$) minimizes \eqref{eq:error_def}, we need to justify the fact that we use the sample mean as the reference estimator.}
@@
 \section{Relation to Remote Multiterminal Source Coding \label{sec:ceo}}
-In this section we draw a connection between our general problem of mean estimation from one-bit samples, to the remote multiterminal source coding problem \cite{berger1996ceo}, also known as the CEO problem.
+In this section we draw a connection between our general problem of mean estimation from one-bit samples and the remote multiterminal source coding problem \cite{berger1996ceo}, also known as the CEO problem.
 The setting of the CEO includes $n$ encoders, each has access to a noisy version of a random source sequence.
@@
 The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator. \par
-Assuming that $\theta$ is drawn randomly once from a prior $\pi(\theta)$, mean estimation from one-bit under distributed encoding (setting (iii) in the Introduction) corresponds to the CEO setting with block length $k=1$, where the $i$th encoder observes
+Assuming that $\theta$ is drawn once from the prior $\pi(\theta)$, mean estimation from one-bit under distributed encoding (setting (iii) in the Introduction) corresponds to the Gaussian CEO setting with block length $k=1$, where the $i$th encoder observes
 \begin{equation}
@@
 As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise at each estimate of variance $\sigma^2$, provides a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting.
+Note that the difference between the Gaussian CEO and our setting is in the fact that each encoder may use an arbitrarily large blocklength $k$, thus describing $k$ realizations of $\theta$ using $k$ bits, whereas our setting only allows $k=1$.
  \\
 
-A closed-form expression for the MSE distortion in the CEO is known only for the case where the source sequence is sampled independently from the normal distribution \cite{prabhakaran2004rate}.
-By using the characterization of this minimal distortion as the number of terminals goes to infinity, we conclude the following:
+By using an expression for the minimal MSE in the Gaussian CEO as the number of terminals goes to infinity, we conclude the following:
 \begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$. Then any estimator $\widehat{\theta}_n$ of $\theta$ in 
-the distributed setting satisfies
+Assume that $\Theta = \mathbb R$ and that $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$. Then any estimator $\widehat{\theta}_n$ of $\theta$ in the distributed setting satisfies
 \begin{equation} \label{eq:ceo_bound}
- n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + o(1).
+ n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + O(n^{-1}),
 \end{equation}
+where the expectation is with respect to $\theta$ and $X^n$.
 \end{prop}
@@
 \begin{equation} \label{eq:ceo_optimal_sumrate}
-n = \frac{1}{2} \log \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
+n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
 \end{equation}
@@
 Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed encoding setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$, we conclude that
+By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$, we see that
 \[
-D^\star = \frac{ \frac{4\sigma^2}{3} }{n + \frac{4 \sigma^2}{3 \sigma_\theta^2} } + O(e^{-n}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
+D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
 \]
 \end{proof}
-Since the lower bound \eqref{eq:ceo_bound}  was derived assuming optimal allocation of the $n$ bits among the encoders, it may seem as if a tighter bound can be obtained in our case by considering the CEO distortion with $R_1=\ldots,R_n = 1$.
+Since the lower bound \eqref{eq:ceo_bound}  was derived assuming optimal allocation of the $n$ bits among the encoders, it may seem as if a tighter bound can be obtained in our case by considering the CEO distortion with $R_1=\ldots = R_n = 1$.
 However, an upper bound for the CEO distortion under this condition follows from \cite[Prop.
@@
 D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + o(n^{-1}),
+\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
 \]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small. \par
+which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ goes to zero. \par
 We conclude therefore that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed encoding setting, is attributed exclusively to the ability to perform coding over blocks.
-Namely, the ability to consider $k>1$ independent realizations of $\theta$ versus only one in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product space, rather than the distributed nature of the problem, that distinguishes between the CEO distortion and the mean estimation from one-bit samples.\par
+Namely, the freedom to consider an arbitrary number $k$ of independent realizations of the problem, versus only one in ours.
+In other words, it is the ability to exploit the geometry of a high-dimensional product space, rather than the distributed nature of the problem, that distinguishes between the CEO distortion and our problem of mean estimation from one-bit samples.\par
 In the next section we show that the ARE in adaptive encoding setting does not exceeds $\pi/2$, and thus provides a tighter lower bound for the distributed encoding setting than $4/3$ of  \eqref{eq:ceo_bound}.
@@
 Finally, in Thm.~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen.
-While it is not clear whether the efficiency of this last scheme is $\pi/2$, numerical simulations suggests that the MSE of this scheme times $n$ also converges to $\pi/2$.
+While it is not clear whether the efficiency of this last scheme is $\pi/2$, numerical simulations suggests that the MSE of this scheme times $n$ also converges to $\pi/2$ faster than the first scheme.
 
@@
 Let $\widehat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Fig.~\ref{fig:sequential}.
-% Let $\pi(\theta)$ be an absolutely continuous prior distribution on $\Theta$ with density function converges to zero at the endpoints of the interval $\Theta$. 
-Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
+Assume that $\Theta$ is an interval and that the density of the prior $\pi(\theta)$ converges to zero at the endpoints of $\Theta$.
+Then
 \[
-\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\pi}{2n}\sigma^2+o(n^{-1}),
+\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\pi}{2n}\sigma^2+O(n^{-2}),
 \]
@@
 2.13]{tsybakov2008introduction},\cite{gill1995applications} which bounds from below the MSE of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are given in the Appendix.\\
+The details are in the Appendix.\\
 
 Next, we present an adaptive estimation scheme that attains ARE of $\pi/2$. 
+%>> to do: relation to robust statistics
 \subsection{Asymptotically optimal estimator}
-
 Let $\left\{\gamma_n \right\}_{n=1}^\infty$ be a strictly positive sequence satisfying:
@@
 \end{equation}
-(e.g. $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Consider the following estimator $\widehat{\theta}_n$ for $\theta$:  
+(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Consider the following estimator $\widehat{\theta}_n$ for $\theta$:  
 \begin{equation}
@@
 
-%For the estimator defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} we have the following results:
+For the estimator defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} we have the following results:
 \begin{thm} \label{thm:sgd}
@@
 \]
-\item[(ii)] Assume moreover that $\gamma_n = o(n^{-2/3})$ and $\sum_{n=1}^\infty \gamma_n = \infty$. Then
+\item[(ii)] In addition to the conditions above, assume that $\gamma_n = o(n^{-2/3})$ and $\sum_{n=1}^\infty \gamma_n = \infty$ (e.g., $\gamma_n = n^{-\beta}$ with $2/3<\beta<1$). Then
 \[
-\lim_{n\rightarrow \infty} n\mathbb E \left[ \left(\theta-\widehat{\theta}_n \right)^2 \right] = \sigma^2 \frac{\pi}{2}. 
+\lim_{n\rightarrow \infty} n\mathbb E \left[ \left(\theta-\widehat{\theta}_n \right)^2 \right] = \frac{\pi}{2} \sigma^2 . 
 \]
@@
 \subsubsection*{Proof}
-The asymptotic behavior of \eqref{eq:sgd_est} is a special case of \cite[Thm. 4]{polyak1992acceleration} and \cite[Thm. 2]{polyak1990new}. The details are provided in the Appendix.\\
+The asymptotic behavior of \eqref{eq:sgd_est} is a special case of \cite[Thm. 4]{polyak1992acceleration} and \cite[Thm. 2]{polyak1990new}. The details are in the Appendix.\\
 
-In other words, Thm.~\ref{thm:sgd} implies that the estimator $\widehat{\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the minimal asymptotic efficiency as established by Thm.~\ref{thm:adpative_lower_bound}.\par
+Thm.~\ref{thm:sgd} implies that the estimator $\widehat{\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the minimal ARE as established by Thm.~\ref{thm:adpative_lower_bound}.
+\par
 Note that $\theta_0$ is not explicitly defined 
@@
 Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the size of the parameter space $\Theta$.
-Nevertheless, the bound in Thm.~\ref{thm:adpative_lower_bound} suggests that the non-asymptotic estimation error can be greatly reduced whenever the location information $I_0$ is large.
-In contrast, the one-step optimal scheme presented in the following subsection exploits the prior information on $\theta$ provided by $\pi(\theta)$.
+Nevertheless, the bound in Thm.~\ref{thm:adpative_lower_bound} suggests that the non-asymptotic estimation error can be significantly reduced whenever the location information $I_0$ is large.
+In contrast, the one-step optimal scheme presented in the following subsection updates the prior distribution on $\theta$ given all information gathered until step $n-1$ to provide the step $n$ estimate and prior.
+In particular, the this scheme exploit the prior information on $\theta$ provided by $\pi(\theta)$.
 
@@
 We considered the MSE risk and asymptotic relative efficiency in estimating the mean of a normal distribution from a single-bit encoding of each sample from this distribution.
-In the adaptive scenario where each one-bit message is a function of the previously seen messages and current sample, we showed that the minimal relative efficiency is $\pi/2$.
+In the adaptive scenario where each one-bit message is a function of the previously seen messages and current sample, we showed that the minimal ARE is $\pi/2$.
 Namely, there is a penalty factor of at least $\pi/2$ on the asymptotic MSE risk in estimating the mean compared to an estimator that has full access to the sample.
 We also showed that this lower bound is tight by presenting an adaptive estimation procedure that attains it.
+The lower bound of $\pi/2$ on the ARE also holds in the fully distributed case where each single-bit message is only a function of a single independent sample, although the question whether this ARE is achievable remains still open.
 %but ignores the prior distribution on the parameter space.
-In addition, we characterized the single-bit message that minimizes the next step MSE, and described an estimation procedure that is based on a sequence of one-step optimal messages.
-We leave open the questions whether this estimator attains the minimal efficiency and whether it leads to an estimation scheme which is globally optimal in the adaptive setting.
-Another open question that follows from our setting is the asymptotic MSE and relative efficiency of a fully distributed one-bit scheme.
+%In addition, we characterized the single-bit message that minimizes the next step MSE, and described an estimation procedure that is based on a sequence of one-step optimal messages.  \\
+%We leave open the questions whether this estimator attains the minimal efficiency and whether it leads to an estimation scheme that is globally optimal in the adaptive setting.
+%In the fully distributed case where each single-bit message is only a function of a single independent sample, the minimal ARE is still an open question, although it is at least $\pi/2$. 
+%For this setting, we showed that with a Gaussian prior on the mean and assuming multiple independent realizations, ARE of $4/3 < \pi/2$ can be attained.
+Therefore, we conclude that the reduction in efficiency in the distributed setting compared to the adaptive one, if exists, is not to the distributed nature of the problem.
+
+%Another open question that follows from our setting is the asymptotic MSE and relative efficiency of a fully distributed one-bit scheme.
 
@@
 \frac{  \phi^2(x)} 
-{\Phi(x) \left(1 - \Phi(x) \right) }. 
+{\Phi(x) \left(1 - \Phi(x) \right) },
 \end{equation}
-Taking the logarithm of \eqref{eq:induction_base} and differentiating, we conclude that any point $x$ that maximizes \eqref{eq:induction_base} also satisfies
-\[
-x = \phi(x) \frac{\Phi(x) -\frac{1}{2}}{\Phi(x)(1-\Phi(x))} .
-\]
-However, since 
-\[
-x > \phi(x) \frac{\Phi(x) -\frac{1}{2}}{\Phi(x)(1-\Phi(x))}
-\]
-for all $x > 0$, the only point that satisfies the last condition is $x=0$, in which \eqref{eq:induction_base} equals $2/\pi$. \par
+which is the weight function in the probit analysis and is known to be a strictly decreasing function of $|x|$ \cite{Samford1953}.
+In particular, the maximum of \eqref{eq:induction_base} is obtained at $x=0$ where it equals $2/\pi$.
+\par
 Assume now that \eqref{eq:bound_intervals} holds for all integers up to some $n = N-1$ and consider the case $n = N$.
@@
 \begin{align}
-I_\theta(M^n) = \sum_{i=1}^n I_\theta (M_i|M^{i-1}),
+I_\theta(M^n) = -\mathbb E \left[ \frac{d^2}{d\theta^2} \log P(M^n | \theta) \right] = \sum_{i=1}^n I_\theta (M_i|M^{i-1}),
 \label{eq:fisher_information}
 \end{align}
-where $I_\theta (M_i|M^{i-1})$ is the Fisher information of the distribution of $M_i$ given $M^{i-1}$, where it follows from Lem.~\ref{lem:fisher_bound} that $I_\theta (M_i|M^{i-1}) \leq 2/(\pi \sigma^2)$.
+where 
+\[
+I_\theta (M_i|M^{i-1}) = \mathbb E \left( \frac{d}{d\theta} \log P(M_i | \theta, M^{i-1}) \right)^2
+\]
+ is the Fisher information of the distribution of $M_i$ given $M^{i-1}$, where it follows from Lem.~\ref{lem:fisher_bound} that $I_\theta (M_i|M^{i-1}) \leq 2/(\pi \sigma^2)$.
 We now use the following theorem from \cite[Thm.
@@
 
-We now use Thm.~\ref{thm:polyak_new} with $f(x) = 0.5(\theta-x)^2$, $\varphi(x) = -\sgn(-x)$, $Z_n = -Z_n$ and $U_n = \theta_n$. From \eqref{eq:polyak_new_measurements} we have
+We now use Thm.~\ref{thm:polyak_new} with $f(x) = 0.5(x-\theta)^2$, $\varphi(x) = -\sgn(-x)$, $Z_n = \theta-X_n$ and $U_n = \theta_n$. From \eqref{eq:polyak_new_measurements} we have
 \begin{align*} 

### 2017-10-01 Writeups/onebit_adaptive_Allerton_V3.tex
another minor edit to Section III

@@
 \IEEEauthorblockN{Alon Kipnis}
-\IEEEauthorblockA{Department of Electrical Engineering \\
+\IEEEauthorblockA{Department of Statistics \\
 Stanford University\\
@@
 The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator. \par
-Assuming that $\theta$ is drawn once from the prior $\pi(\theta)$, mean estimation from one-bit under distributed encoding (setting (iii) in the Introduction) corresponds to the Gaussian CEO setting with block length $k=1$, where the $i$th encoder observes
-\begin{equation}
-\label{eq:Gaussian_channel}
-X_i = \theta + \sigma Z_i,
-\end{equation}
-with $Z_1,\ldots,Z_n$ i.i.d.
-standard normal, and uses $R_i=1$ bits to transmit its observation.
-As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise at each estimate of variance $\sigma^2$, provides a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting.
-Note that the difference between the Gaussian CEO and our setting is in the fact that each encoder may use an arbitrarily large blocklength $k$, thus describing $k$ realizations of $\theta$ using $k$ bits, whereas our setting only allows $k=1$.
+Assuming that $\theta$ is drawn once from the prior $\pi(\theta)$, our mean estimation problem from one-bit samples under distributed encoding (setting (iii) in the Introduction) corresponds to the Gaussian CEO setting with $k=1$ source realization: the $i$th encoder uses $R_i=1$ bits to transmit a message that is a function of $X_i = \theta + \sigma Z_i$, where $Z_i$ is standard normal.
+As a result, the MSE in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$, a Gaussian observation noise at each estimate of variance $\sigma^2$, and an arbitrary number of $k$ independent draws of $\theta$, provides a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting.
+Note that the difference between the CEO and ours is in the fact encoders in the CEO describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realization, whereas our setting only allows $k=1$.
  \\

### 2017-10-02 Writeups/onebit_adaptive_Allerton_V3.tex
minor edit

@@
 \end{equation}
-\item Solve equation \eqref{eq:fixed_point} with the updated prior $P_n(t)$ instead of $P(d\theta)$.
+\item Solve equation \eqref{eq:fixed_point} with the updated prior $P_n(t)$ instead of $\pi(d\theta)$.
 Note that since the standard normal cdf $\Phi(x)$ is log-concave, the updated prior $P_n(t)$ remains log-concave and thus a unique solution to \eqref{eq:fixed_point} is guaranteed by Lem.~\ref{lem:unique}.
@@
 \end{itemize}
-Since equation \eqref{eq:fixed_point} has no analytic solution in general, it is hard to derive the asymptotic behavior of the estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}.
-We conjecture, however, that it attains the asymptotic relative efficiency of $\sigma^2\pi/2$, as can be observed from the numerical simulation illustrated in Fig.~\ref{fig:adaptive_error}.
+Since equation \eqref{eq:fixed_point} has no analytic solution, it is hard to derive the asymptotic behavior of the estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}.
+We conjecture that it attains the asymptotic relative efficiency of $\sigma^2\pi/2$ as can be observed from the numerical simulation illustrated in Fig.~\ref{fig:adaptive_error}.
 Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the asymptotically optimal estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the sample mean for the same sample realization.
@@
 \begin{tikzpicture}
-\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
+\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adaptive}};
 %\node[color = blue,  minimum width=1cm, align = left] at (1.5,1.5) {assymptotically optimal \eqref{eq:sgd_est}};
@@
 \]
-which was shown to be smaller than $\pi/2$.
+which was shown to be not larger than $2/pi$.
 If $N$ is even, then for any constant $c$ the limit of the LHS of \eqref{eq:bound_intervals} as $(x_1,\ldots,x_N)\rightarrow (c,\ldots,c)$ exists and equals zero.

### 2017-10-05 Slides/OneBit_Allerton_slides.tex
new version of presentation

@@
 \usepackage{pstool}
+%\usepackage{beamerthemesplit}
+\usepackage{stmaryrd}
 
@@
 \newcommand{\unif}{\mathsf{unif}}
+\newcommand{\iid}{\mathrm{i.i.d.}}
 
@@
 \end{center}
+\pause
 Estimation error is due to:
@@
 \bigskip
-
+\pause
 Relevant scenarios:
 \begin{itemize}
+\pause
 \item big data
+\pause
 \item low-power sensors 
-\item distributed computing / optimization (bottleneck is due to communication between processing units)
+\pause
+\item distributed computing / optimization % (bottleneck is due to communication between processing units)
 
@@
 
-\node[below of = source2, node distance = 2.5cm] (source3) {$X_n$};
+\node[below of = source2, node distance = 2cm] (source3) {$X_n$};
 \node[int1, right of = source3, node distance = 2cm, scale = 0.75] (enc3) {Enc n};  
@@
 
-%\node[above of = source, node distance = 1cm] (dist) {${\mathcal N} \left(\theta, \sigma^2 \right)$};
+\node[above of = source, node distance = 0.75cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
 
-\node[Est, right of = enc2, node distance = 5cm] (est) {Est};
+\node[Est, right of = enc2, node distance = 4.5cm] (est) {Est};
 \draw[->,line width = 2pt] (enc1) -| node[above, xshift = -2.5cm] (mes1) {$M_1 \in \left\{-1,1\right\}$} (est);   
@@
 \draw[->,line width = 2pt] (enc3) -| node[above, xshift = -2.5cm]  {$M_n \in \left\{-1,1\right\}$} (est);   
-\node[right of = est, node distance = 2.5cm] (dest) {$\widehat{\theta}(M^n)$};
+\node[right of = est, node distance = 2cm] (dest) {$\widehat{\theta}(M^n)$};
 \draw[->, line width=2pt] (est) -- (dest);
@@
 \visible<2>{
-\draw[<->,line width = 2pt, color = red] (enc1) -- (enc2);   
-\draw[<->,line width = 2pt, color = red] (enc2) -- (enc3);
+\draw[<->,line width = 2pt, color = blue] (enc1) -- (enc2);   
+\draw[<->,line width = 2pt, color = blue] (enc2) -- (enc3);
 \draw[dashed,line width = 2pt, color = white] (enc2)+(0,-0.5) -- +(0,-1.5);}
@@
 \visible<3->{
-\draw[->,line width = 2pt, color = blue] (enc1) -- (enc2);   
-\draw[->,line width = 2pt, color = blue] (enc2) -- (enc3);
-\draw[dashed,line width = 2pt, color = white] (enc2)+(0,-0.7) -- +(0,-1.7);}
+\draw[->,line width = 2pt, color = red] (enc1)+(1,0) -- (enc2);   
+\draw[->,line width = 2pt, color = red] (enc2)+(1,0) -- (enc3);
+\draw[line width = 2pt, color = red] (enc1)+(1,0) -- +(1,-1.5);
+
+\draw[dashed,line width = 2pt, color = white] (enc2)+(0.66,-0.7) -- +(0.25,-1.5);}
 
@@
 \visible<2->{
-\item {\color{red} Centralized}: $M^n = (M_1,\ldots,M_n) = f(X_1,\ldots,X_n)$ }
+\item {\color{blue} Centralized}: $M^n = (M_1,\ldots,M_n) = f(X_1,\ldots,X_n)$ }
 \visible<3->{
-\item {\color{blue} Adaptive / Sequential}: $M_i = f_i(X_i,M^{i-1})$ }
+\item {\color{red} Adaptive / Sequential}: $M_i = f_i(X_i,M^{i-1})$ }
 \end{itemize}
@@
 \begin{itemize} 
-\item Estimation via compressed information [Han '87], [Zhang \& Berger '88]
-\item Distributed hypothesis testing under quantization [Tsitsiklis '88]
-\item Estimation from multiple machines subject to a bit constraint [Zhang, Duchi, Jordan, Wainwright '13]
-\item Remote multiterminal source coding (CEO) [Berger, Zhang, Wiswanathan '96], [Oohama '97]
+\pause
+\item Estimation via compressed information [Han '87], [Zhang \& Berger '88] (centralized)
+\pause
+\item Estimation from multiple machines subject to a bit constraint [Zhang, Duchi, Jordan, Wainwright '13] (distributed / adaptive)
+\pause
+\item Distributed hypothesis testing under quantization [Tsitsiklis '88] (distributed)
+\pause
+\item Remote multiterminal source coding (CEO) [Berger, Zhang, Wiswanathan '96], [Oohama '97] (distributed)
 \end{itemize}
@@
 A: all ! 
+\pause
+\bigskip
+\textbf{Proof:}
 \[
@@
 \]
-(as in the distributed setting)
+(distributed setting)
+\pause
 \[
-\frac{1}{n}\sum_{i=1}^n M_i \rightarrow \Prob\left(X<0 \right) = \Phi\left(X/\sigma<\thetac\right)
+\frac{1}{n}\sum_{i=1}^n M_i \rightarrow \Prob\left(X>0 \right) = \Phi\left(\thetac / \sigma \right)
 \]
 \end{frame}
+
+%SAY: supper slow, of course. Can we do better? what is the best possible?
 
@@
 \frametitle{Efficiency}
-\textbf{Definition:} \emph{asymptotic relative efficiency (ARE)} of an estimator:
+\textbf{Definition:} \emph{asymptotic relative efficiency (ARE)}:
 \[
-\mathrm{ARE}(\widehat{\theta}) \triangleq \lim_{n\rightarrow \infty} \frac{\mathbb E \left[ \left(\widehat{\theta}-\theta \right)^2 \right]}{\sigma^2 / n}
+\mathrm{ARE}(\widehat{\theta}_n) \triangleq \lim_{n\rightarrow \infty} \mathbb E \left[ \left(\widehat{\theta}_n-\theta \right)^2 \right] / \left(\sigma^2 / n \right)
 \]
-($\sigma^2/n$ is the minimax risk without communication constraints)
-%MSE of sample mean $\bar{\theta}$: 
-%\[
-%\mathbb E \left[ \left(\bar{\theta}-\theta \right)^2 \right] = \frac{\sigma^2}{n}
-%\]
-%(minimax estimator without communication constraint)
+(relative to minimax risk without bit constraint)
 
-\bigskip
-\pause
-Q: in what scenarios the ARE is finite? \\
-\bigskip
-\pause
-This talk: all three scenarios
+%SAY: many definitions for ARE are possible, we use this one becasue our results apply to all of them
 
@@
 
-\begin{prop} If the parameter space $\Theta$ is bounded, then the ARE under centralized encoding is $1$
+\begin{prop} ARE under centralized encoding is $1$
 \end{prop}
+\pause
+
 \textbf{Proof:}
 \[
-\mathbb E \left( \theta- \widehat{\theta} \right)^2 = \overbrace{\mathbb E \left( \theta- \bar{\theta} \right)^2}^{\sigma^2/n} + \mathbb E \left( \bar{\theta}- \widehat{\theta} \right)^2 
+\mathbb E \left( \theta- \widehat{\theta} \right)^2 = \overbrace{\mathbb E \left( \theta- \bar{\theta} \right)^2}^{\sigma^2/n} + \underbrace{\mathbb E \left( \bar{\theta}- \widehat{\theta} \right)^2}_{O(2^{-2n})}
 \]
+\pause
 \begin{itemize}
@@
 \end{itemize}
-\item MSE in estimating $\bar{\theta}$ decreases exponentially in $n$ 
 \end{itemize}
 \bigskip
-Note: globally optimal strategy for a finite $n$ is hard to derive since mean of $\bar{\theta}$ is unknown 
+\pause
+Note: mean of $\bar{\theta}$ is unknown -- hard to derive a globally optimal strategy
+%SAY: exploration -- exploitation even in this simple setting
 \end{frame}
@@
 \begin{center}
+\vspace{-20pt}
 \begin{tikzpicture}[node distance=2cm,auto,>=latex]
-  \node at (0,0) (source) {$\thetac$} ;
+  \node at (0,0) (source) {$\thetac_j$} ;
   \node[ssum, right of = source, scale = 0.75] (sum1) {+};
-  \node[above of = sum1, node distance = 1.2cm] (z1) {$Z_1$};
+  \node[above of = sum1, node distance = 1cm] (z1) {$Z_{1}$};
   \node[int1, right of = sum1, node distance = 2cm, scale = 0.75] (enc1) {Enc 1};  
 \draw[->,line width = 2pt] (source) -- (sum1); 
-\draw[->,line width = 2pt] (sum1) -- node[above] {$X_1$} (enc1); 
+\draw[->,line width = 2pt] (sum1) -- node[above] {$X_{1}$} (enc1); 
 \draw[->,line width = 2pt] (z1) -- (sum1);
@@
  \node[ssum, right of = source2, scale = 0.75] (sum2) {+};
-  \node[above of = sum2, node distance = 1.2cm] (z2) {$Z_n$};
+  \node[above of = sum2, node distance = 1.2cm] (z2) {$Z_{n}$};
 \node[int1, right of = sum2, node distance = 2cm, scale = 0.75] (enc2) {Enc n};
@@
 
-\draw[->,line width = 2pt] (sum2) -- node[above] {$X_n$} (enc2); 
+\draw[->,line width = 2pt] (sum2) -- node[above] {$X_{n}$} (enc2); 
 \draw[->,line width = 2pt] (z2) -- (sum2);
@@
 %\node[int1, right of = enc2, node distance = 6cm, scale = 0.75] (est) {Est};
-\draw[->,line width = 2pt] (enc1) -- node[above, xshift = 0cm] (mes1) {$R_1$} (est);   
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$R_n$} (est);   
-\node[right of = est, node distance = 2cm] (dest) {$\widehat{\theta}$};
+\draw[->,line width = 2pt] (enc1) -- node[above, xshift = 0cm, rotate = -15] (mes1) {one bit} (est);   
+\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm, rotate = 12] (mes2) {one bit} (est);   
+\node[right of = est, node distance = 1.5cm] (dest) {$\widehat{\thetac}_j$};
 \draw[->, line width=2pt] (est) -- (dest);
@@
 \end{center}
-
+\pause
 Assume:
 \begin{itemize}
-\item $\theta \sim \mathcal N(0,\sigma_\theta^2)$, ~~~ 
-\item $Z_1,\ldots,Z_n \overset{\mathrm{i.i.d}}{\sim}\mathcal N(0,\sigma^2)$
+\item $Z_{1},\ldots,Z_{n} \overset{\mathrm{i.i.d}}{\sim}\mathcal N(0,\sigma^2)$
+\pause
+\item Replicate $k$ times: $\thetac_1,\ldots,\thetac_k \overset{\iid}{\sim} \mathcal N(0,\sigma_0^2)$ 
+\pause
+\item Block encode $X_{j,1},\ldots,X_{j,n}$ using $k$ bits, $j=1,\ldots,k$
+\pause
+\item $D_{CEO} = \inf_{k,\widehat{\theta}} \frac{1}{k} \sum_{j=1}^k \mathbb E \left( \theta_j - \widehat{\theta}_j\right)^2$
 \end{itemize}
-Encode $k$ instances:
-\begin{itemize}
-\item $R_1 = \ldots = R_n =1 $
-\item $D_{CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left(\theta_j-\widehat{\theta}_j \right)^2$
-\end{itemize}
+%SAY: lower bound to our setting
 \end{frame}
@@
 \begin{frame}
-
-From [K., Rini, Goldsmith '17]: 
+Quadratic Gaussian CEO under optimal rate allocation [Chen, Zhang, Berger, Wicker '04] :
 \[
-D_{CEO} \leq \frac{4}{3} \frac{\sigma^2}{n} + o(1)
+ D_{CEO}  \geq \frac{4}{3} \frac{\sigma^2}{n} + o(1/n) 
 \]
@@
 %\end{itemize}
-ARE of $4/3$ can be attained in a fully distributed encoding (with encoding over blocks of multiple problem instances)
+\pause
+\begin{alertblock}{Conclusion}
+Distributed encoding will hurt you (even if you can repeat experiment and encode over blocks)
+\end{alertblock}
 \bigskip
-\begin{alertblock}{Conclusion}
-Distributed encoding is almost not a limiting factor 
-(although inability to exploit concentration of measure in high dimension -- might!)
-\end{alertblock}
+\pause
+\begin{itemize}
+\item In fact [K., Rini, Goldsmith '17]:
+\end{itemize} 
+\[
+ D_{CEO} \leq \frac{4}{3} \frac{\sigma^2}{n} + \frac{\sigma_0^2}{3n} + o(1/n) 
+\]
+(ARE of $4/3$ is achievable with coding over blocks)
+%SAY: depending on how large our bound from $k=1$, it tells us that distributed setting is not the limitng factor
 \end{frame}
@@
 \begin{frame}
+\frametitle{Three Encoding Scenarios}
+
+\begin{center}
+\begin{tikzpicture}[node distance=2cm,auto,>=latex]
+  \node at (0,0) (source) {$X_1$} ;
+  \node[int1, right of = source, node distance = 2cm, scale = 0.75] (enc1) {Enc 1};  
+\draw[->,line width = 2pt] (source) -- (enc1);
+
+ \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
+\node[int1, right of = source2, node distance = 2cm, scale = 0.75] (enc2) {Enc 2};  
+\draw[->,line width = 2pt] (source2) -- (enc2);
+
+\node[below of = source2, node distance = 2cm] (source3) {$X_n$};
+\node[int1, right of = source3, node distance = 2cm, scale = 0.75] (enc3) {Enc n};  
+\draw[->,line width = 2pt] (source3) -- (enc3);
+
+%\node[above of = source3, node distance = 1cm, xshift = -0.5cm] (source3) {$X_i \sim \mathcal N(\theta,\sigma^2)$};
+
+\node[above of = source, node distance = 0.75cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
+
+\node[Est, right of = enc2, node distance = 4.5cm] (est) {Est};
+\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -2.5cm] (mes1) {$M_1 \in \left\{-1,1\right\}$} (est);   
+\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M_2 \in \left\{-1,1\right\}$} (est);   
+\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -2.5cm]  {$M_n \in \left\{-1,1\right\}$} (est);   
+\node[right of = est, node distance = 2cm] (dest) {$\widehat{\theta}(M^n)$};
+\draw[->, line width=2pt] (est) -- (dest);
+
+\node[below of = source2, node distance = 0.5cm] {$\vdots$};
+\node[below of = enc2, node distance = 0.5cm] {$\vdots$};
+\node[below of = mes2, node distance = 0.7cm] {$\vdots$};
+
+\visible<2>{
+\draw[<->,line width = 2pt] (enc1) -- (enc2);   
+\draw[<->,line width = 2pt] (enc2) -- (enc3);
+\draw[dashed,line width = 2pt, color = white] (enc2)+(0,-0.5) -- +(0,-1.5);}
+
+\visible<3->{
+\draw[->,line width = 2pt, color = red] (enc1)+(1,0) -- (enc2);   
+\draw[->,line width = 2pt, color = red] (enc2)+(1,0) -- (enc3);
+\draw[line width = 2pt, color = red] (enc1)+(1,0) -- +(1,-1.5);
+
+\draw[dashed,line width = 2pt, color = white] (enc2)+(0.66,-0.7) -- +(0.25,-1.5);}
+
+\end{tikzpicture}
+\end{center}
+
+\begin{itemize}
+\item Distributed: $M_i = f_i(X_i)$  \hfill{ARE $\geq 4/3$}
+\visible<2->{
+\item {Centralized}: $M^n = f(X_1,\ldots,X_n)$ \hfill{ARE $=1$} }
+\visible<3->{
+\item {\color{red} Adaptive / Sequential: $M_i = f_i(X_i,M^{i-1})$ \hfill{ARE$=\pi/2$} }  }
+\end{itemize}
+\end{frame}
+
+\begin{frame}
 \frametitle{Main Results (adaptive encoding)}
+
+\begin{theorem}[achievability]
+There exists an estimator with ARE $\pi/2$
+\end{theorem}
 
@@
 
-\begin{theorem}[achievability]
-Assume that $\Theta$ is a bounded interval. There exists an estimator with ARE equals to $\pi/2$
-\end{theorem}
-
-\begin{theorem}[one-step optimal strategy]
-The next step one-bit message that minimizes the MSE is of the form $M = \sgn (X-\tau)$ where $\tau$ satisfies the fixed-point equation 
-\[
-\tau = \frac{1}{2} \left( \frac{ \int_{-\infty}^\tau \theta \pi(d\theta) }{\int_{-\infty}^\tau \pi(d\theta)}  + \frac{ \int_{\tau}^\infty \theta \pi(d\theta)}{\int_{\tau}^\infty \pi(d\theta)} \right)
-\]
-\end{theorem}
+%\begin{theorem}[one-step optimal strategy]
+%The next step one-bit message that minimizes the MSE is of the form $M = \sgn (X-\tau)$ where $\tau$ satisfies the fixed-point equation 
+%\[
+%\tau = \frac{1}{2} \left( \frac{ \int_{-\infty}^\tau \theta \pi(d\theta) }{\int_{-\infty}^\tau \pi(d\theta)}  + \frac{ \int_{\tau}^\infty \theta \pi(d\theta)}{\int_{\tau}^\infty \pi(d\theta)} \right)
+%\]
+%\end{theorem}
 \end{frame}
@@
 \begin{frame}
-\frametitle{Proof}
-\framesubtitle{converse (ARE $\geq \pi/2$)}
-Assume a prior $\pi(d\theta)$ on $\Theta$ with location Fisher information $I_\pi$. \\
+\frametitle{Achievability}
+\framesubtitle{existence of an estimator with ARE $= \pi/2$}
 
+\begin{itemize}
+\item[(i)] For $X \sim \mathcal{N}(\theta,\sigma^2)$, $\mathsf{med}(X) = \theta$ 
+\pause
+\item[(ii)] $\mathsf{med}(X) = \underset{m}{ \mathrm{argmin~}} \mathbb E \left|X-m \right|$
+\pause
+\item[(iii)] Stochastic gradient descent on $\mathbb E \left| X-\theta \right|$:
+\[
+\theta_n = \theta_{n-1} + \gamma_n \sgn(X_n - \theta_n)
+\]
+\[
+\widehat{\theta}_n = \frac{1}{n} \sum_{i=1}^n \theta_i 
+\]
+\end{itemize}
+\bigskip
+\pause
+From [Polyak \& Juditsky '92] (under conditions on $(\gamma_n)$): 
+\[
+\sqrt{n}(\theta- \widehat{\theta}_n) \rightarrow \mathcal N\left(0, \sigma^2 \pi /2 \right)
+\]
+\end{frame}
+%picture
+
+%\begin{frame}
+%\frametitle{Achievability} 
+%
+%[Polyak \& Juditsky '92]: \\
+%
+%
+%where:
+%\begin{itemize}
+%\item[(i)] $\gamma_n \rightarrow 0^+$ ``not too slow'' 
+%\item[(ii)] $\psi(x) = \mathbb E \varphi(x+Z)$ 
+%\item [(iii)] $\chi(x) = \mathbb E \varphi^2(x+Z)$ 
+%\item[(iv)] some regularity  conditions on $\varphi$, $\chi$, $\psi$
+%\end{itemize}
+%Then 
+%\[
+%\sqrt{n}(\theta- \widehat{\theta}) \rightarrow \mathcal N\left(0,V\right)
+%\]
+%where $V = \chi(0)/\psi'^2(0)$.  \\
+%\medskip
+%\pause
+%Proof of theorem: take $\varphi(x) = \sgn(x)$
+%\end{frame}
+
+\begin{frame}
+\frametitle{Converse}
+\framesubtitle{ARE $\geq \pi/2$}
 The van-Trees inequality (e.g. [Tsybakov '08]) implies
@@
 \]
-\begin{lem}
+$I_\pi$ is the location Fisher information with w.r.t. some prior $\pi(d\theta)$ on $\Theta$\\
+
+\begin{lem}[K. \& Duchi '17]
 \[
-I_\theta(M_i|M^{i-1}) \leq 2/(\pi\sigma^2)
+I_\theta(M_i|M^{i-1}) \leq \frac{2}{\pi\sigma^2}
 \]
 \end{lem}
-(proof by induction over a finite set of intervals approximating $M_i^{-1}(1)$ given $M^{i-1}$)
+\textbf{Proof}: \\
+Stein identity implies that portion maximizing the information is a threshold: $M_i^{-1}(1) = (\theta,\infty)$  \\
+The rest follows by induction over number of portions
+%SAY: the rest follows by induction over number 
 \end{frame}
 
-\begin{frame}
-\frametitle{Proof}
-\framesubtitle{achievability (existence of an estimator with ARE $= \pi/2$)}
-[Polyak \& Juditsky '92]: \\
-\[
-\begin{cases}
-\theta_i = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_i)& i=1,\ldots,n\\
-\widehat{\theta} = \frac{1}{n} \sum_{i=1}^n \theta_i &
-\end{cases}
-\]
-where:
-\begin{itemize}
-\item[(i)] $\gamma_n \rightarrow 0^+$ ``not too slow'' 
-\item[(ii)] $\psi(x) = \mathbb E \varphi(x+Z)$ 
-\item [(iii)] $\chi(x) = \mathbb E \varphi^2(x+Z)$ 
-\item[(iv)] some regularity  conditions on $\varphi$, $\chi$, $\psi$
-\end{itemize}
-Then 
-\[
-\sqrt{n}(\theta- \widehat{\theta}) \rightarrow \mathcal N\left(0,V\right)
-\]
-where $V = \chi(0)/\psi'^2(0)$.  \\
-\medskip
-\pause
-Proof of theorem: take $\varphi(x) = \sgn(x)$
-\end{frame}
+%\begin{frame}
+%\frametitle{One-step Optimal Bit}
+%% SAY: previously we bound the inforamtion under any scheme. In addition, it is interesting to understand what is the one-step optimal scheme
+%%Q: upon observing $M^{n-1}$, what is the optimal detection region $M_n^{-1}(1)$ that minimizes the MSE ? \\ \pause
+%\begin{theorem}
+%Let $\pi(\theta)$ be an absolutely continuous log-concave distribution. For $X\sim \mathcal N(\theta,\sigma^2)$ let
+%\[
+%M = \sgn(X-\tau)
+%\]
+%where $\tau$ is the unique solution to
+%\[
+%\tau = \frac{1}{2} \left( \frac{ \int_{-\infty}^\tau \theta \pi(d\theta) }{\int_{-\infty}^\tau \pi(d\theta)}  + \frac{ \int_{\tau}^\infty \theta \pi(d\theta)}{\int_{\tau}^\infty \pi(d\theta)} \right)
+%\]
+%Then for any $M'(X) \in \{-1,1\}$ and $\widehat{\theta}(M')$:
+%\[
+%\mathbb E \left(\theta- \widehat{\theta}(M') \right)^2 \geq \mathbb E \left(\theta - \mathbb E[\theta|M] \right)^2
+%\]
+%\end{theorem}
+%\vspace{-20pt}
+%\pause
+%\begin{alertblock}{Interpertation:}
+%\begin{itemize}
+%\item One-bit message that minimizes MSE is a threshold detector
+%\pause
+%\item Leads to a Bayes procedure $\mathbb E \left[\theta | M\right]$
+%\end{itemize}
+%\end{alertblock}
+%
+%%SAY: we don't know if this procedure is optimal, what we conjecture that it is
+%\end{frame}
 
-\begin{frame}
-\frametitle{One-step optimality}
-%Upon observing $M^{i-1}$, what is the optimal detection region $M_i^{-1}(1)$ that minimizes the MSE ? \\
-\begin{theorem}
-Let $\pi(\theta)$ be an absolutely continuous log-concave distribution. For $X\sim \mathcal N(\theta,\sigma^2)$ let
-\[
-M = \sgn(X-\tau)
-\]
-where $\tau$ is the unique solution to
-\[
-\tau = \frac{1}{2} \left( \frac{ \int_{-\infty}^\tau \theta \pi(d\theta) }{\int_{-\infty}^\tau \pi(d\theta)}  + \frac{ \int_{\tau}^\infty \theta \pi(d\theta)}{\int_{\tau}^\infty \pi(d\theta)} \right)
-\]
-Then for any $M'(X) \in \{-1,1\}$ and $\widehat{\theta}(M')$:
-\[
-\mathbb E \left(\theta- \widehat{\theta}(M') \right)^2 \geq \mathbb E \left(\theta - \mathbb E[\theta|M] \right)^2
-\]
-\end{theorem}
-\vspace{-20pt}
-\begin{alertblock}{Interpertation:}
-The optimal one-bit message is a threshold detector. The threshold is the fixed-point that balances conditional center of masses given the message
-\end{alertblock}
+%\begin{frame}
+%\frametitle{One-step Optimal Scheme}
+%Initialization: $P_0(t) = \pi(\theta)$ \\
+%Repeat for $n \geq 1$:
+%\begin{itemize}
+%\item[(i)] $P_n(t) = \Prob(\theta = t|M^n) = \alpha_n P_{n-1}(t) \Phi \left(M_n \frac{t-\tau_{n-1}}{\sigma} \right)$ 
+%\item[(ii)] $\widehat{\theta} = \mathbb E[\theta | M^n] = \int t P_n(t)dt $ 
+%\item[(iii)] Find $\tau_n$ from 
+%\[
+%\tau_n = \frac{1}{2} \left( \frac{ \int_{-\infty}^\tau t P_n(t)dt }{\int_{-\infty}^\tau P_n(t)dt}  + \frac{ \int_{\tau}^\infty t P_n(t)dt}{\int_{\tau}^\infty P_n(t)dt} \right)
+%\]
+%\item[(iv)] $M_{n+1} = \sgn(X_{n+1}-\tau_n)$
+%\end{itemize}
+%\end{frame}
 
-\end{frame}
-
-\begin{frame}
-\frametitle{One-step Optimal Scheme}
-Initialization: $P_0(t) = \pi(\theta)$ \\
-Repeat for $n \geq 1$:
-\begin{itemize}
-\item[(i)] $P_n(t) = \Prob(\theta = t|M^n) = \alpha_n P_{n-1}(t) \Phi \left(M_n \frac{t-\tau_{n-1}}{\sigma} \right)$ 
-\item[(ii)] $\widehat{\theta} = \mathbb E[\theta | M^n] = \int t P_n(t)dt $ 
-\item[(iii)] Find $\tau_n$ from 
-\[
-\tau_n = \frac{1}{2} \left( \frac{ \int_{-\infty}^\tau t P_n(t)dt }{\int_{-\infty}^\tau P_n(t)dt}  + \frac{ \int_{\tau}^\infty t P_n(t)dt}{\int_{\tau}^\infty P_n(t)dt} \right)
-\]
-\item[(iv)] $M_{n+1} = \sgn(X_{n+1}-\tau_n)$
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Numerical Example}
-\begin{center}
-Normalized empirical risk versus number of samples $n$ \\
-(500 Monte Carlo experiments)
-\begin{tikzpicture}
-\node at (0,0) {\includegraphics[scale=0.5]{one_bit_adpative}};
-%\node[color = blue,  minimum width=1cm, align = left] at (1.5,1.5) {assymptotically optimal \eqref{eq:sgd_est}};
-%\node[color = red, minimum width=1cm, align = left] at (1.5,0.55) {one-step optimal \eqref{eq:message_update}} ;
-\node[rotate = 90, scale = 1] at (-5,0) {$n \mathbb E \left(\widehat{\theta}_n - \theta \right)^2$};
-\node[scale = 1] at (0,-3) {$n$};
-%\draw[dashed] (-3.5,1.18) node[left, scale = 0.7] {$\frac{\pi}{2}$}-- (-3,1.18);
-\end{tikzpicture}
-$\theta \sim \unif(-3,3)$
-\end{center}
-\end{frame}
+%\begin{frame}
+%\frametitle{Numerical Example}
+%\begin{center}
+%Normalized empirical risk versus number of samples $n$ \\
+%(1000 Monte Carlo experiments)
+%\begin{tikzpicture}
+%\node at (0,0) {\includegraphics[scale=0.5]{one_bit_adaptive}};
+%%\node[color = blue,  minimum width=1cm, align = left] at (1.5,1.5) {assymptotically optimal \eqref{eq:sgd_est}};
+%%\node[color = red, minimum width=1cm, align = left] at (1.5,0.55) {one-step optimal \eqref{eq:message_update}} ;
+%\node[rotate = 90, scale = 1] at (-5,0) {$n \mathbb E \left(\widehat{\theta}_n - \theta \right)^2$};
+%\node[scale = 1] at (0,-3) {$n$};
+%%\draw[dashed] (-3.5,1.18) node[left, scale = 0.7] {$\frac{\pi}{2}$}-- (-3,1.18);
+%\end{tikzpicture}
+%$\theta \sim \unif(-3,3)$
+%\end{center}
+%\end{frame}
 
@@
 \begin{center}
+\pause
 \begin{tikzpicture}
@@
 \[
-\lambda_n([a,b]) = \frac{1}{n} \left| [a,b] \cap \left\{t_i \right\}\right|
+\lambda_n([a,b]) = \frac{1}{n} \mathsf{card}\left( [a,b]  \cap \left\{t_i \right\} \right)
 \]
@@
 \pause
-\textbf{Example:} $t_1,\ldots,t_n$ are drawn independently from a probability distribution $\lambda$ on $\mathbb R$
+\textbf{Example:} $t_1,\ldots,t_n$ drawn i.i.d. from a distribution $\lambda$ on $\mathbb R$
 
@@
 \begin{itemize}
-\item[(i)] For any estimator $\widehat{\theta}$:
+\item[(i)] The Maximum likelihood estimator $\widehat{\theta}_{ML}$  satisfies
 \[
-\liminf_{c\rightarrow \infty}\, \liminf_{n\rightarrow \infty} \sup_{\tau\,:\,| \tau - \theta| \leq \frac{c}{\sqrt{n}} }  n \mathbb E \left(\widehat{\theta} - \tau \right)^2 \geq \sigma^2/K(\theta),
+\sqrt{n}(\theta - \widehat{\theta}_{ML}) \rightarrow \mathcal N\left(0,\sigma^2/K_\lambda(\theta) \right)
 \]
@@
 \begin{align*}
-K(\theta) & = \int_{\mathbb R} \eta\left( \frac{t-\theta}{\sigma}\right) \lambda(dt) \\
+K_\lambda(\theta) & = \int_{\mathbb R} \eta\left( \frac{t-\theta}{\sigma}\right) \lambda(dt) \\
 \eta(x) & = \frac{\phi^2(x)}{\Phi(x)\Phi(-x)}
 \end{align*}
-\item[(ii)] The Maximum likelihood estimator $\widehat{\theta}_{ML}$  satisfies
+% The weight function in the probit analysis
+\pause
+\item[(ii)] For any estimator $\widehat{\theta}(M_1,\ldots,M_n)$:
 \[
-\sqrt{n}(\theta - \widehat{\theta}_{ML}) \rightarrow \mathcal N\left(0,\sigma^2/K(\theta) \right)
+\liminf_{c\rightarrow \infty}\, \liminf_{n\rightarrow \infty} \sup_{\tau\,:\,| \tau - \theta| \leq \frac{c}{\sqrt{n}} }  n \mathbb E \left(\widehat{\theta} - \tau \right)^2 \geq \sigma^2/K_\lambda(\theta),
 \]
+
 \end{itemize}
@@
 \begin{itemize}
+\pause
 \item ML estimator is local asymptotically minimax 
-\item ARE of ML is $1/K(\theta)$ --  depends only in the asymptotic threshold density $\lambda$
+\pause
+\item ARE of ML is $1/K_{\lambda}(\theta)$ -- 
+only depends on asymptotic threshold density $\lambda$
+\pause
+\item  
+\[
+\mathrm{ARE} = \frac{1}{K_{\lambda}(\theta)}  = \frac{\sigma^2}{\int \eta \left( \frac{t-\theta}{\sigma}\right) \lambda(dt)}
+> \pi / 2
+\]
+(equality iff $\lambda = \delta_{\theta}$)
+%SAY: cannot be as good as sequential thresholds
+%\item Threshold density $\lambda$ that maximizes
+\pause
+\item Minimax $\lambda$ can be found using a convex program -- minimax ARE  depends on radius of $\Theta$
+%ARE depends on size of parameter space $\Theta$ 
+%\begin{center}
+%\begin{tikzpicture}
+%\node at (0,0)  {\includegraphics[scale=0.3]{k_vs_b2}};
+%\node at (0,-1.7) {$r$};
+%\node[rotate = 90] at (-2.3,0) {$1/K_{\lambda^\star}$};
+%\end{tikzpicture}
+%
+%Minimax ARE vs radius $r$ of parameter space
+%\end{center}
+
 \end{itemize}
 
+\end{frame}
+
+\section{Summary}
+
+\begin{frame}
+\frametitle{Summary}
 \begin{itemize}
-\item \[
-1/K(\theta) = \frac{1}{\int \eta \left( \frac{t-\theta}{\sigma}\right) \lambda(dt)}
-\geq \frac{1}{\int \eta \left(0\right) \lambda(dt)} = \pi / 2
-\]
-(attained by $\lambda(dt) = \delta_{\theta}$)
-\item Minimax $\lambda$ for $\theta \in (-b\sigma,b\sigma)$:
+\pause
+\item Centralized encoding: ARE$=1$
+\pause
+\item Adaptive:
+\begin{itemize}
+\item ARE is $\pi/2$ (regardless of radius of $\Theta$)
+\pause
+\item $\sim 1.57$ more samples are required due to 1-bit constraints
+\end{itemize}
+\pause
+%\pause
+%\item One-step optimal one-bit message is a threshold detector
+\bigskip
+\item Distributed threshold detection:
+\begin{itemize}
+\item ARE of MLE characterized by density of threshold values 
+\item MLE is local asymptotically optimal 
+\item minimax ARE depends on radius of $\Theta$
+\end{itemize}
+%\item Minimax ARE of MLE depends on size of parameter space
+\end{itemize}
+
+\bigskip
+\pause
+\begin{alertblock}{Open question}
+Is there a distributed encoding scheme with ARE that is both finite and independent of radius of $\Theta$ ?
+\end{alertblock}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Minimax threshold density}
+
+Minimax $\lambda$ for $\theta \in (-b\sigma,b\sigma)$:
 \begin{align*}
@@
 \end{align*}
-\end{itemize}
 
@@
 
-\section{Summary}
-
-\begin{frame}
-\frametitle{Summary}
-\begin{itemize}
-\item Asymptotic relative efficiency in adaptive setting is $\pi/2$ regardless of size of parameter space -- only $\sim 1.57$ more samples are required due to 1-bit constraints
-\item One-step optimal one-bit message is a threshold detector
-\item ARE in distributed setting is finite
-\item 
-ML estimator is local asymptotically optimal for threshold detection
-\item ARE of ML is characterized by asymptotic density of threshold values
-\item Minimax ARE of ML depends on size of parameter space
-\end{itemize}
-
-\bigskip
-\begin{alertblock}{Open question}
-Is there a distributed encoding scheme with ARE that is both finite and independent of size of parameter space ?
-\end{alertblock}
-
-\end{frame}
-
 \end{document}

### 2017-10-05 Slides/OneBit_Allerton_slides_V2.tex
new version of presentation

--- 2017-10-05 Slides/OneBit_Allerton_slides.tex
@@
 (relative to minimax risk without bit constraint)
+%SAY: many definitions for ARE are possible, we use this one becasue our results apply to all of them
+\bigskip
 
-%SAY: many definitions for ARE are possible, we use this one becasue our results apply to all of them
-
-\end{frame}
-
-\begin{frame}
-\frametitle{ARE under Centralized Encoding}
-
+\pause
 \begin{prop} ARE under centralized encoding is $1$
@@
 \pause
-
 \textbf{Proof:}
@@
 \]
-\pause
-\begin{itemize}
-\item Encoder is required to describe $\bar{\theta}$ using $n$ bits
-\begin{itemize}
-\item divide parameter space $\Theta$ into $2^n$ regions of equal size
-\item send region index where $\bar{\theta}$ falls
-\end{itemize}
-\end{itemize}
-\bigskip
-\pause
-Note: mean of $\bar{\theta}$ is unknown -- hard to derive a globally optimal strategy
-%SAY: exploration -- exploitation even in this simple setting
+
 \end{frame}
+
+%\begin{frame}
+%\frametitle{ARE under Centralized Encoding}
+%
+%\begin{prop} ARE under centralized encoding is $1$
+%\end{prop}
+%\pause
+%
+%\textbf{Proof:}
+%\[
+%\mathbb E \left( \theta- \widehat{\theta} \right)^2 = \overbrace{\mathbb E \left( \theta- \bar{\theta} \right)^2}^{\sigma^2/n} + \underbrace{\mathbb E \left( \bar{\theta}- \widehat{\theta} \right)^2}_{O(2^{-2n})}
+%\]
+%\pause
+%\begin{itemize}
+%\item Encoder is required to describe $\bar{\theta}$ using $n$ bits
+%\begin{itemize}
+%\item divide parameter space $\Theta$ into $2^n$ regions of equal size
+%\item send region index where $\bar{\theta}$ falls
+%\end{itemize}
+%\end{itemize}
+%\bigskip
+%\pause
+%Note: mean of $\bar{\theta}$ is unknown -- hard to derive a globally optimal strategy
+%%SAY: exploration -- exploitation even in this simple setting
+%\end{frame}
 
@@
   \node[above of = sum1, node distance = 1cm] (z1) {$Z_{1}$};
+  \node[right of  = z1, node distance = 4cm]  {
+ $Z_i  \overset{\mathrm{i.i.d}}{\sim}\mathcal N(0,\sigma^2)$ };
   \node[int1, right of = sum1, node distance = 2cm, scale = 0.75] (enc1) {Enc 1};  
@@
 \end{center}
-\pause
-Assume:
 \begin{itemize}
-\item $Z_{1},\ldots,Z_{n} \overset{\mathrm{i.i.d}}{\sim}\mathcal N(0,\sigma^2)$
+\item $X_{1},\ldots,X_{n} \overset{\mathrm{i.i.d}}{\sim}\mathcal N(\theta,\sigma^2)$
 \pause
@@
 \pause
-\item $D_{CEO} = \inf_{k,\widehat{\theta}} \frac{1}{k} \sum_{j=1}^k \mathbb E \left( \theta_j - \widehat{\theta}_j\right)^2$
+\item $D_{CEO} = \underset{k,\widehat{\theta}}{\inf} \frac{1}{k} \sum_{j=1}^k \mathbb E \left( \theta_j - \widehat{\theta}_j\right)^2$
 \end{itemize}
@@
 \bigskip
-\pause
-\begin{itemize}
-\item In fact [K., Rini, Goldsmith '17]:
-\end{itemize} 
-\[
- D_{CEO} \leq \frac{4}{3} \frac{\sigma^2}{n} + \frac{\sigma_0^2}{3n} + o(1/n) 
-\]
-(ARE of $4/3$ is achievable with coding over blocks)
+%\pause
+%\begin{itemize}
+%\item In fact [K., Rini, Goldsmith '17]:
+%\end{itemize} 
+%\[
+% D_{CEO} \leq \frac{4}{3} \frac{\sigma^2}{n} + %\frac{\sigma_0^2}{3n} + o(1/n) 
+%\]
+%(ARE of $4/3$ is achievable with coding over blocks)
 %SAY: depending on how large our bound from $k=1$, it tells us that distributed setting is not the limitng factor
@@
 \section{Adaptive Encoding} 
-
 \begin{frame}
@@
 \visible<3->{
-\item {\color{red} Adaptive / Sequential: $M_i = f_i(X_i,M^{i-1})$ \hfill{ARE$=\pi/2$} }  }
+\item Next: {\color{red} adaptive / sequential: $M_i = f_i(X_i,M^{i-1})$ \hfill{ARE$=\pi/2$} }  }
 \end{itemize}
@@
 \]
+(MSE convergence follows from [Polyak '90]) 
 \end{frame}
@@
 \framesubtitle{ARE $\geq \pi/2$}
-The van-Trees inequality (e.g. [Tsybakov '08]) implies
+Let $\pi(\theta)$ be a prior on $\Theta$. The van-Trees inequality (e.g. [Tsybakov '08]) implies
 \[
@@
 \]
-$I_\pi$ is the location Fisher information with w.r.t. some prior $\pi(d\theta)$ on $\Theta$\\
+$I_\pi$ is the location Fisher information with w.r.t. $\pi(\theta)$ \\
 
@@
 \node[coordinate] at(0,0) (ti) {};
-\draw[color = red, line width = 1.5pt] (ti)+(0,0.2) -- node[above, yshift = 0.07cm] {\color{black} $t_i$} +(0,-0.2);
+\draw[color = red, line width = 1.5pt] (ti)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_i$} +(0,-0.2);
 \draw[<-,line width = 1pt] (-3,0) -- node[above] {$M_i=-1$} (ti);
-\draw[->,line width = 1pt] (ti) -- node[above] {$M_i=1$} (6,0);
+\draw[->,line width = 2pt] (ti) -- node[above] {$M_i=1$} (6,0);
 \end{tikzpicture}
@@
 \pause
-\item ML estimator is local asymptotically minimax 
+\item MLE is local asymptotically minimax 
 \pause
-\item ARE of ML is $1/K_{\lambda}(\theta)$ -- 
+\item ARE of MLE is $1/K_{\lambda}(\theta)$ -- 
 only depends on asymptotic threshold density $\lambda$
@@
 \item ARE of MLE characterized by density of threshold values 
+\pause
 \item MLE is local asymptotically optimal 
+\pause
 \item minimax ARE depends on radius of $\Theta$
@@
 
+\begin{frame}
+\frametitle{One-step Optimal Scheme}
+Initialization: $P_0(t) = \pi(\theta)$ \\
+Repeat for $n \geq 1$:
+\begin{itemize}
+\item[(i)] $P_n(t) = \Prob(\theta = t|M^n) = \alpha_n P_{n-1}(t) \Phi \left(M_n \frac{t-\tau_{n-1}}{\sigma} \right)$ 
+\item[(ii)] $\widehat{\theta} = \mathbb E[\theta | M^n] = \int t P_n(t)dt $ 
+\item[(iii)] Find $\tau_n$ from 
+\[
+\tau_n = \frac{1}{2} \left( \frac{ \int_{-\infty}^\tau t P_n(t)dt }{\int_{-\infty}^\tau P_n(t)dt}  + \frac{ \int_{\tau}^\infty t P_n(t)dt}{\int_{\tau}^\infty P_n(t)dt} \right)
+\]
+\item[(iv)] $M_{n+1} = \sgn(X_{n+1}-\tau_n)$
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Numerical Example}
+\begin{center}
+Normalized empirical risk versus number of samples $n$ \\
+(1000 Monte Carlo experiments)
+\begin{tikzpicture}
+\node at (0,0) {\includegraphics[scale=0.5]{one_bit_adaptive}};
+%\node[color = blue,  minimum width=1cm, align = left] at (1.5,1.5) {assymptotically optimal \eqref{eq:sgd_est}};
+%\node[color = red, minimum width=1cm, align = left] at (1.5,0.55) {one-step optimal \eqref{eq:message_update}} ;
+\node[rotate = 90, scale = 1] at (-5,0) {$n \mathbb E \left(\widehat{\theta}_n - \theta \right)^2$};
+\node[scale = 1] at (0,-3) {$n$};
+%\draw[dashed] (-3.5,1.18) node[left, scale = 0.7] {$\frac{\pi}{2}$}-- (-3,1.18);
+\end{tikzpicture}
+$\theta \sim \unif(-3,3)$
+\end{center}
+\end{frame}
+
 \end{document}

### 2017-10-05 Writeups/proof of Lemma 7 for log-concave distributions.tex
new version of presentation

@@
 \begin{lem} \label{lem:bound_intervals}
-Assume that $X_1,\ldots,X_n$ are distributed with CDF $F(x)$ and PDF $f(x)$ such that $F(-x) = 1-F(x)$ (and $f(-x)=f(x)$). Assume moreover that 
-$ f(x) = e^{g(x}}$ where $g(x)$ is concave and twice differentiable such that $g''(x)<0$. Then for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, we have 
+Let $f(x)$ be a log-concave, symmetric, and twice differentiable pdf. Denote by $F(x)$ the corresponding CDF. Then for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, we have 
 \begin{equation}
@@
 \begin{equation} \label{eq:induction_base}
-\frac{  f^2(x)} 
+\eta(x) \triangleq \frac{  f^2(x)} 
 {F(x) \left(1 - F(x) \right) }.
 \end{equation}
-Since $f(x)$ is log-concave, so does $F(x)$.
-We now write $F(x) = e^{h(x)}$ with $h(x)$ concave.
-Note that $f(x) = h'(x) e^{h(x)}$, $h'(x)\geq 0$, $f(x) = f(-x) = h'(-x)e^{h(-x)} $, and $h''(x)\leq 0$ ($h(x)$ is twice differentiable since $F(x)$ is twice differentiable).
+Since $f(x)$ is log-concave, positive, and twice differentiable, we may write $f(x) = e^{g(x)}$ with $g(x)$ concave and twice differentiable.
+Moreover, since symmetry of $f(x)$ implies symmetry of $g(x)$, and, since the latter is concave, it attains a single maximum at the symmetry point $x=0$.
+Therefore, $x=0$ is the only point for which $g'(x)=0$.
+We now show that $x=0$ is the point where $\eta(x)$ attains its maximum value.
+Since $\eta(x)$ is positive and  goes to zero as $x\rightarrow \pm \infty$, the maximum of $\eta(x)$ cannot be attained as $x\rightarrow \pm \infty$.
+We therefore consider the derivative of $\eta(x)$, given as
+\[
+\eta'(x) = 2 \eta(x) e^{g(x)} \left(\frac{F(x)-1/2}{F(x)(1-F(x))} + g'(x) \right). 
+\]
+Since $f(x)$ is symmetric and integrates to $1$, we 
+have that $F(0)=0.5$ and hence $\eta'(0) = 0$.  It is left to verify that $\eta'(x)\neq 0$ for $x \neq 0$.
+
 Taking the logarithm of \eqref{eq:induction_base} leads to 
 \begin{align*}
-& 2 \log f(x) - \log F(x) + \log F(-x) \\
-& = 2 \log h'(x) + h(x) + h(-x).
+& 2 \log f(x) - \log F(x) - \log F(-x) \\
+& = 2 \log h'(x) + h(x) - h(-x).
 \end{align*}
-Since $h'(x)$ is non-increasing, the maximal value of \eqref{eq:induction_base} is obtained as 
+Note that since $F(x)$ is non-decreasing, so is $h(x)$. In addition, $h'(x)$ is non-increasing since $h(x)$ 
+, the maximal value of \eqref{eq:induction_base} is obtained as 
 {HERE!! \color{red} finish proof by showing that \eqref{eq:induction_base} is smaller than $4f(0)$.\\

### 2017-10-06 Slides/OneBit_Allerton_slides_V2.tex
final version of presentation

@@
 \pause
-\item Distributed hypothesis testing under quantization [Tsitsiklis '88] (distributed)
-\pause
 \item Remote multiterminal source coding (CEO) [Berger, Zhang, Wiswanathan '96], [Oohama '97] (distributed)
@@
 \]
+\pause
+\[
+\sigma \Phi^{-1}\left( \frac{1}{n}\sum_{i=1}^n M_i  \right) \rightarrow \thetac
+\]
 \end{frame}
@@
 
-\subsection{Preliminary}
+\subsection{Preliminaries}
 
@@
 \[
-\mathrm{ARE}(\widehat{\theta}_n) \triangleq \lim_{n\rightarrow \infty} \mathbb E \left[ \left(\widehat{\theta}_n-\theta \right)^2 \right] / \left(\sigma^2 / n \right)
+\mathrm{ARE}(\widehat{\theta}_n) \triangleq \lim_{n\rightarrow \infty} \mathbb E \left[ \left(\widehat{\theta}_n-\thetac \right)^2 \right] / \left(\sigma^2 / n \right)
 \]
-(relative to minimax risk without bit constraint)
+(relative to sample mean $\bar{\theta}$)
 %SAY: many definitions for ARE are possible, we use this one becasue our results apply to all of them
@@
 \[
+\mathbb E \left( \thetac- \widehat{\theta} \right)^2 = \overbrace{\mathbb E \left( \thetac- \bar{\theta} \right)^2}^{\sigma^2/n} + \mathbb E \left( \bar{\theta}- \widehat{\theta} \right)^2
+\]
+\end{frame}
+
+\begin{frame}
+\frametitle{Efficiency}
+\textbf{Definition:} \emph{asymptotic relative efficiency (ARE)}:
+\[
+\mathrm{ARE}(\widehat{\theta}_n) \triangleq \lim_{n\rightarrow \infty} \mathbb E \left[ \left(\widehat{\theta}_n-\theta \right)^2 \right] / \left(\sigma^2 / n \right)
+\]
+(relative to sample mean $\bar{\theta}$)
+%SAY: many definitions for ARE are possible, we use this one becasue our results apply to all of them
+\bigskip
+
+\begin{prop} ARE under centralized encoding is $1$
+\end{prop}
+\textbf{Proof:}
+\[
 \mathbb E \left( \theta- \widehat{\theta} \right)^2 = \overbrace{\mathbb E \left( \theta- \bar{\theta} \right)^2}^{\sigma^2/n} + \underbrace{\mathbb E \left( \bar{\theta}- \widehat{\theta} \right)^2}_{O(2^{-2n})}
 \]
-
 \end{frame}
@@
 \begin{itemize}
-\item $X_{1},\ldots,X_{n} \overset{\mathrm{i.i.d}}{\sim}\mathcal N(\theta,\sigma^2)$
+\item $X_{1},\ldots,X_{n} \overset{\mathrm{i.i.d}}{\sim}\mathcal N(\thetac,\sigma^2)$
 \pause
-\item Replicate $k$ times: $\thetac_1,\ldots,\thetac_k \overset{\iid}{\sim} \mathcal N(0,\sigma_0^2)$ 
+\item Replicate $k$ times: 
+\begin{itemize}
+\item  $\thetac_1,\ldots,\thetac_k \overset{\iid}{\sim} \mathcal N(0,\sigma_0^2)$ 
+\item $\thetac_j \rightarrow X_{j,1},\ldots,X_{j,n}$
+\end{itemize}
 \pause
-\item Block encode $X_{j,1},\ldots,X_{j,n}$ using $k$ bits, $j=1,\ldots,k$
+\item Encoder $i$ block encodes $X_{1,i},\ldots,X_{k,i}$ using $k$ bits
 \pause
-\item $D_{CEO} = \underset{k,\widehat{\theta}}{\inf} \frac{1}{k} \sum_{j=1}^k \mathbb E \left( \theta_j - \widehat{\theta}_j\right)^2$
+\item $D_{CEO} = \underset{k}{\inf} \frac{1}{k} \sum_{j=1}^k \mathbb E \left( \theta_j - \widehat{\theta}_j\right)^2$
 \end{itemize}
@@
 \section{Adaptive Encoding}
+
 \begin{frame}
@@
 \visible<3->{
-\item Next: {\color{red} adaptive / sequential: $M_i = f_i(X_i,M^{i-1})$ \hfill{ARE$=\pi/2$} }  }
+\item Next: {\color{red} adaptive: $M_i = f_i(X_i,M^{i-1})$ \hfill{ARE$=\pi/2$} }  }
 \end{itemize}
 \end{frame}
+
+\subsection{Main Results}
 
@@
 \framesubtitle{existence of an estimator with ARE $= \pi/2$}
-
+\pause
 \begin{itemize}
@@
 \item[(iii)] Stochastic gradient descent on $\mathbb E \left| X-\theta \right|$:
+\pause
+\begin{flushright}
+\begin{tikzpicture}
+\node[coordinate] at(0,0) (ti) {};
+\draw[color = red, line width = 1.5pt] (ti)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $\theta$} +(0,-0.2);
+\draw[<-,line width = 2pt] (-1.5,0) -- node[above] {$-1$} (ti);
+\draw[->,line width = 2pt] (ti) -- node[above] {$1$} (1.5,0);
+\draw (-1.3,1.5) -- (ti) -- (1.3,1.5);
+\end{tikzpicture}
+\end{flushright}
 \[
@@
 \]
-(MSE convergence follows from [Polyak '90]) 
 \end{frame}
@@
 \framesubtitle{ARE $\geq \pi/2$}
-Let $\pi(\theta)$ be a prior on $\Theta$. The van-Trees inequality (e.g. [Tsybakov '08]) implies
+The van-Trees inequality (e.g. [Tsybakov '08]) implies
 \[
-\mathbb E \left(\theta - \widehat{\theta} \right)^2 \geq \frac{1}{\mathbb E I_\theta(M^n) + I_\pi} \geq \frac{1}{\sum_{i=1}^n I_\theta(M_i|M^{i-1}) + I_\pi} 
+\mathbb E \left(\theta - \widehat{\theta} \right)^2 \geq \frac{1}{ I_\theta(M^n) + c} = \frac{1}{\sum_{i=1}^n I_\theta(M_i|M^{i-1}) + c} 
 \]
-$I_\pi$ is the location Fisher information with w.r.t. $\pi(\theta)$ \\
-
+\pause
 \begin{lem}[K. \& Duchi '17]
@@
 \end{lem}
+\pause
 \textbf{Proof}: \\
-Stein identity implies that portion maximizing the information is a threshold: $M_i^{-1}(1) = (\theta,\infty)$  \\
-The rest follows by induction over number of portions
+Stein's identity implies that detection region maximizing the information is a threshold: $M_i^{-1}(1) = (\theta,\infty)$ 
 %SAY: the rest follows by induction over number 
@@
 
+\subsection{Threshold Detection}
+
+\begin{frame}
+\frametitle{Distributed Encoding}
+\framesubtitle{Threshold Detection}
+We consider only messages of the form
+\[
+M_i = \sgn(X_i - t_i),\quad i=1,\ldots,n
+\]
+\pause
+\begin{center}
+\begin{tikzpicture}
+\draw[<->,line width = 1pt] (-3,0) node[left] {$\cdots$} -- (3,0) node[right] {$\cdots$};
+\node[coordinate] at(0,0) (ti) {};
+%\draw[<-,line width = 1pt] (-3,0) -- node[above] (ti);
+%\draw[->,line width = 1pt] (ti) -- node[above]  (6,0);
+\draw[color = red, line width = 1.5pt] (ti)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_1$} +(0,-0.2);
+\pause
+\node[coordinate] at(2,0) (tj) {};
+\draw[color = blue, line width = 1.5pt] (tj)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_2$} +(0,-0.2);
+\pause
+\node[coordinate] at(-1,0) (tk) {};
+\draw[color = green, line width = 1.5pt] (tk)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_3$} +(0,-0.2);
+\end{tikzpicture}
+\end{center}
+%Assume:
+%\[
+%\lambda_n([a,b]) = \frac{1}{n} \mathsf{card}\left( [a,b]  \cap \left\{t_i \right\} \right)
+%\]
+%converges weakly to a probability distribution $\lambda$
+%\\
+%\bigskip
+%\pause
+%\textbf{Example:} $t_1,\ldots,t_n$ drawn i.i.d. from a distribution $\lambda$ on $\mathbb R$ 
+\end{frame}
+
 \begin{frame}
@@
 \begin{center}
-\pause
 \begin{tikzpicture}
+\draw[<->,line width = 1pt] (-3,0) node[left] {$\cdots$} -- (3,0) node[right] {$\cdots$};
 \node[coordinate] at(0,0) (ti) {};
-\draw[color = red, line width = 1.5pt] (ti)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_i$} +(0,-0.2);
-\draw[<-,line width = 1pt] (-3,0) -- node[above] {$M_i=-1$} (ti);
-\draw[->,line width = 2pt] (ti) -- node[above] {$M_i=1$} (6,0);
+%\draw[<-,line width = 1pt] (-3,0) -- node[above] (ti);
+%\draw[->,line width = 1pt] (ti) -- node[above]  (6,0);
+\draw[color = red, line width = 1.5pt] (ti)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_1$} +(0,-0.2);
+\node[coordinate] at(2,0) (tj) {};
+\draw[color = blue, line width = 1.5pt] (tj)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_2$} +(0,-0.2);
+\node[coordinate] at(-1,0) (tk) {};
+\draw[color = green, line width = 1.5pt] (tk)+(0,0.2) -- node[above, yshift = 0.08cm] {\color{black} $t_3$} +(0,-0.2);
 \end{tikzpicture}
@@
 \frametitle{Main Results (distributed encoding)}
-
+\pause
 \begin{theorem}
@@
 (equality iff $\lambda = \delta_{\theta}$)
+
 %SAY: cannot be as good as sequential thresholds
 %\item Threshold density $\lambda$ that maximizes
-\pause
-\item Minimax $\lambda$ can be found using a convex program -- minimax ARE  depends on radius of $\Theta$
+%\pause
+%\item Minimax $\lambda$ can be found using a convex program -- minimax ARE  depends on radius of $\Theta$
 %ARE depends on size of parameter space $\Theta$ 
@@
 \begin{itemize}
-\item ARE is $\pi/2$ (regardless of radius of $\Theta$)
+\item ARE is $\pi/2$ % (regardless of radius of $\Theta$)
 \pause
@@
 \pause
-\item minimax ARE depends on radius of $\Theta$
+%\item minimax ARE depends on radius of $\Theta$
 \end{itemize}
@@
 
-\begin{frame}
+\begin{frame}[noframenumbering]
 \frametitle{Minimax threshold density}
@@
 
-\begin{frame}
+\begin{frame}[noframenumbering]
 \frametitle{Minimax $\lambda$}
@@
 \end{itemize}
-
 \end{frame}
 
-\begin{frame}
+\begin{frame}[noframenumbering]
 \frametitle{One-step Optimal Scheme}
@@
 
-\begin{frame}
+\begin{frame}[noframenumbering]
 \frametitle{Numerical Example}
@@
 %\node[color = red, minimum width=1cm, align = left] at (1.5,0.55) {one-step optimal \eqref{eq:message_update}} ;
-\node[rotate = 90, scale = 1] at (-5,0) {$n \mathbb E \left(\widehat{\theta}_n - \theta \right)^2$};
+\node[rotate = 90, scale = 1] at (-5,0) {$n \ mathbb E \left(\widehat{\theta}_n - \theta \right)^2$};
 \node[scale = 1] at (0,-3) {$n$};

### 2017-10-09 Writeups/onebit_adaptive_Allerton_V3.tex
small changes to final manuscript

@@
 %\documentclass[letterpaper]{IEEEtran}
-\documentclass[letterpaper, conference]{IEEEtran}      % Use this line for a4 paper
+\documentclass[letterpaper, conference,9pt]{IEEEtran}      % Use this line for a4 paper
 %\IEEEoverridecommandlockouts                              %
@@
 \begin{abstract}
-We consider the problem of estimating the mean of a normal distribution under the following constraint: the estimator can access only a single bit of each sample from this distribution.
+We consider the problem of estimating the mean of a normal distribution under the following constraint: the estimator can access only a single bit from each sample from this distribution.
 We study the squared error risk in this estimation as a function of the number of samples and one-bit measurements $n$.
 We consider an adaptive estimation setting where the single-bit sent at step $n$ is a function of both the new sample and the previous $n-1$ acquired bits.
-For this setting, we show that no estimator can attain asymptotic mean squared error smaller than $\pi/(2n)+o(n^{-1})$ times the variance.
+For this setting, we show that no estimator can attain asymptotic mean squared error smaller than $\pi/(2n)+O(n^{-2})$ times the variance.
 %
@@
 
-Processing and estimating information from data collected at multiple physical locations is subject to communication constraints. 
+Estimation performance of information from data collected and processed by multiple units may be limited due to communication constraints between these units. 
 %For example, emerging sensor network technologies in medicine and ``smart cities" use many low-cost sensors to collect large amounts of data and transmit it to remote locations.
@@
 For example, consider large-scale sensor arrays where information is collected through multiple sensors and transmitted to a central estimation unit.
-In this scenario, the ability to estimate a particular parameter from data collected by the sensors is dictated not only by quality of observations and their numbers, but also by the available communication rate between the sensors and the central estimator.
+In this scenario, the ability to estimate a particular parameter from the data is dictated not only by the quality of observations and their number, but also by available rate of communication between the sensors and the central estimator.
 The question that we ask is to what extent a parametric estimation task is affected by communication constraints, and what are the fundamental performance limits in estimating a parameter subject to these restrictions.
-In this paper we answer this question in a particular simple setting: the estimation of the mean $\theta$ of a normal distribution with variance $\sigma^2$ under the constraint that only a single bit can be communicated on each sample $X_n$ from this distribution.
-As it turns out, the ability to share information among different samples before sending each single-bit message dramatically affects the performance in estimating $\theta$.
-We distinguish in particular among three different settings:
+In this paper we answer this question in a particular setting: the estimation of the mean $\theta$ of a normal distribution with variance $\sigma^2$ under the constraint that only a single bit can be communicated on each sample $X_n$ from this distribution.
+As it turns out, the ability to share information among different samples before committing on each single-bit message dramatically affects the performance in estimating $\theta$.
+We therefore distinguish in among three settings:
  \begin{itemize}
@@
 We measure the estimation performance by the mean squared error (MSE) risk.
-Since without bit constraint this risk is equals $\sigma^2/n$, we are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting, defined by the ratio between their MSE to $\sigma^2/n$ as $n$ goes to infinity when this MSE has a limit.
-The results in this paper focus on setting (ii), which corresponds to an estimation scenario with feedback or with multiple rounds of communication between a sensor and an estimation unit.
-\\% Evidently, the lower bound on the ARE we derive for setting (ii) also applies to setting (iii).
+We are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting relative to the MSE attained by the sample mean, which is the minimax estimator in estimating without one-bit constraint and its MSE decreases as $\sigma^2/n+O(n^{-2})$.
+\\
 
@@
 In addition to this negative statement, we provide an estimator that attains this ARE.
-In other words, we show that the lower bound of $\pi/2$ on the asymptotic relative efficiency is tight, and that it is attained regardless of the particular realization of $\theta$ or the size of the parameter space from which it is taken.
-Clearly, the minimal penalty on the efficiency of $\pi/2$ also holds under setting (iii), although the question whether such efficiency is achievable (or otherwise, what is the minimal ARE) remains open.
+In other words, we show that the lower bound of $\pi/2$ on the ARE is tight, and that it is attained regardless of the particular realization of $\theta$ or the radius of the parameter space from which it is taken.
+Clearly, the minimal penalty on the efficiency of $\pi/2$ also holds under setting (iii), although the question whether this efficiency is achievable (or otherwise, what is the minimal ARE) remains open.
 \\
+
+The lower bound of $\pi/2$ on the ARE, i.e., a lower bound of $\sigma^2\pi/(2n) +O(n^{-2})$ on the MSE, is obtained by showing that the Fisher information of any $n$ adaptive messages is not larger than $2n/(\pi \sigma^2)$.
+From here, the desired bound on the MSE follows from the van Trees version of the information inequality \cite{gill1995applications}.
+Finally, we show that an estimator that attains asymptotic MSE of $\sigma^2\pi/(2n)$ is obtained as a special case of \cite[Thm.
+4]{polyak1992acceleration}.
+In addition to these two results, we also derive the one-step optimal strategy in which the message sent at step $i$th is designed to minimize the MSE given this message and the previous $i-1$ messages.
+Furthermore, we demonstrates numerically that the MSE under this strategy converge to $\pi \sigma^2/(2n)$.
+%A proof for this converges remains elusive.
+\\
+
+\subsection*{Background and Related Works}
 
@@
 
-We note that even through its ARE is $1$, the centralized encoding setting (i) already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation scheme.
+We note that even though its ARE is $1$, the centralized encoding setting (i) already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation scheme.
 Indeed, the standard technique to encode an unknown random quantity using $n$ bits is equivalent to the design of a scalar quantizer \cite{gray1998quantization}.
-However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation task.
-Therefore, a non-trivial exploration exploitation tradeoff arise in this case.
-In our setting, the only missing parameter is the mean, which, under setting (i), is known to the encode with uncertainty interval proportional to $\sigma/\sqrt{n}$.
-Therefore, while it is clear that uncertainty due to quantization decreases exponentially in the number of bits $n$, an exact expression for the MSE in this setting is not easy to derive.
-The situation is even more involved in the adaptive encoding of setting (ii): an encoding and estimation strategy that is globally optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$, may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
+However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation problem and hence its exact value is unknown.
+As a result, a non-trivial exploration exploitation tradeoff arises in this case.
+In our setting, the only missing parameter is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$.
+Therefore, while it is clear that uncertainty due to quantization decreases exponentially in the number of bits $n$ leading to ARE $1$, an exact expression for the MSE in this setting is not easy to derive.
+The situation is even more involved in the adaptive encoding of setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$, may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
 Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $2^{n-1}$ messages, is not guaranteed to be globally optimal.
 Therefore, the main contribution of this paper is a lower bound on the MSE risk of any globally optimal strategy.
-This lower bound is obtained by showing that the Fisher information of any $n$ steps strategy is not larger than $2n/(\pi \sigma^2)$.
-The desired bound of $\pi \sigma^2/(2n)$ on the MSE follows from the van Trees version of the information inequality \cite{gill1995applications}.
-Finally, we show that an estimator that attains asymptotic MSE of $\sigma^2\pi/(2n)$ is obtained as a special case of \cite[Thm.
-4]{polyak1992acceleration}.
-In addition to these two results, we also derive the one-step optimal strategy and demonstrates numerically that  the MSE under this strategy converge to $\pi \sigma^2/(2n)$.
-A proof for this converges remains elusive.
 \\
 
-Our results imply that even under coarse quantization constraints, it is possible to achieve MSE in parametric estimation within only a relatively small penalty compared to the unconstrained estimator.
+Our result of ARE of $\pi/2$ in the adaptive setting implies that even under coarse quantization constraints it is possible to achieve MSE in parametric estimation within only a relatively small penalty compared to the unconstrained estimator.
 A possible clue for this non-intuitive result is obtained from drawing the connection between our setting and the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}.
-This connection, explained in details in Section~\ref{sec:ceo}, immediately leads to a lower bound of $4/3$ on the ARE in the distributed encoding of setting (iii).
-While this lower bound provides no new information compared to the lower bound of $\pi /2$ we derive later for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimal even under one-bit quantization of each sample.
-\\
+This connection, which is explained in details in Section~\ref{sec:ceo}, immediately leads to a lower bound of $4/3$ on the ARE in the distributed encoding of setting (iii).
+While this lower bound provides no new information compared to the lower bound of $\pi /2$ we derive later for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimal even under one-bit quantization of each sample.\\
 
-Setting (ii) and (iii) were considered in 
-\cite{zhang2013information} under the more general assumption of $m$ machines each has access to $n/m$ independent samples.
-The main result of \cite{zhang2013information} are bounds on the estimation error as a function of the number of bits $R$ with which each machine can communicate.
-Specializing their result to our setting, by taking $m=n$ and $R=1$, leads to looser bounds then $\sigma^2\pi/(2n)$ for case (ii) and (iii).
+We also note that our settings (ii) and (iii) are special cases of 
+\cite{zhang2013information} that consider adaptive and distributed estimation protocols for $m$ machines, each has access to $n/m$ independent samples.
+The main result of \cite{zhang2013information} are bounds on the estimation error as a function of the number of bits $R$ each machine uses for communication.
+The specialization of their result to our setting by, taking $m=n$ and $R=1$, leads to looser bounds then $\sigma^2\pi/(2n)$ for cases (ii) and (iii).
 Other related works include statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation}, although their results apply only to setting (i).
@@
 \\
+
+\subsection*{Paper Organization}
 
@@
 which is the weight function in the probit analysis and is known to be a strictly decreasing function of $|x|$ \cite{Samford1953}. 
-In particular, the maximum of \eqref{eq:induction_base} is obtained at $x=0$ where it equals $2/\pi$.
-\par
+%The weight function describes the variance of the MLE in the probit model 
+In particular, the maximum of \eqref{eq:induction_base} is obtained at $x=0$ where it equals $2/\pi$. \par
 Assume now that \eqref{eq:bound_intervals} holds for all integers up to some $n = N-1$ and consider the case $n = N$.
@@
 
-\section{Acknowledgments}
-The work of A. Kipnis is partially supported by NSF Center for Science of Information (CSoI) under grant CCF-0939370 and NSF-BSF under grant 1609695.
+%\section{Acknowledgments}
+%The work of A. Kipnis is partially supported by NSF Center for Science of Information (CSoI) under grant CCF-0939370 and NSF-BSF under grant 1609695.
 

### 2017-10-09 Writeups/onebit_adaptive_Allerton_V3.tex
small changes to final version

@@
 
-Estimation performance of information from data collected and processed by multiple units may be limited due to communication constraints between these units. 
+The performance in estimating information from data collected and processed by multiple units may be limited due to communication constraints between these units. 
 %For example, emerging sensor network technologies in medicine and ``smart cities" use many low-cost sensors to collect large amounts of data and transmit it to remote locations.
 These sensors must operate under severe power restrictions, hence they are limited by their communication bandwidth.
-For example, consider large-scale sensor arrays where information is collected through multiple sensors and transmitted to a central estimation unit.
-In this scenario, the ability to estimate a particular parameter from the data is dictated not only by the quality of observations and their number, but also by available rate of communication between the sensors and the central estimator.
-The question that we ask is to what extent a parametric estimation task is affected by communication constraints, and what are the fundamental performance limits in estimating a parameter subject to these restrictions.
+For example, consider large-scale sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit.
+In this scenario, the ability to estimate a particular parameter from the data is dictated not only by the quality of observations and their number, but also by the available rate for communication between the sensors and the central estimator.
+The question that we ask is to what extent a parametric estimation task is affected by these communication constraints, and what are the fundamental performance limits in estimating a parameter subject to these restrictions.
 In this paper we answer this question in a particular setting: the estimation of the mean $\theta$ of a normal distribution with variance $\sigma^2$ under the constraint that only a single bit can be communicated on each sample $X_n$ from this distribution.
 As it turns out, the ability to share information among different samples before committing on each single-bit message dramatically affects the performance in estimating $\theta$.
-We therefore distinguish in among three settings:
+We therefore distinguish among three settings:
  \begin{itemize}
@@
 We measure the estimation performance by the mean squared error (MSE) risk.
-We are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting relative to the MSE attained by the sample mean, which is the minimax estimator in estimating without one-bit constraint and its MSE decreases as $\sigma^2/n+O(n^{-2})$.
+We are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting relative to the MSE attained by the empirical mean of the samples, which is the minimax estimator in estimating without one-bit constraint and its MSE decreases as $\sigma^2/n+O(n^{-2})$.
 \\
 
-In setting (i) the estimator can evaluate the sample mean and then communicate it using $n$ bits.
+In setting (i) the estimator can evaluate the empirical mean of the samples and then communicate it using $n$ bits.
 This strategy leads to MSE behavior of $\sigma^2/n + O(2^{-n})$.
@@
 The main result of \cite{zhang2013information} are bounds on the estimation error as a function of the number of bits $R$ each machine uses for communication.
-The specialization of their result to our setting by, taking $m=n$ and $R=1$, leads to looser bounds then $\sigma^2\pi/(2n)$ for cases (ii) and (iii).
-Other related works include statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation}, although their results apply only to setting (i).
-The counterpart of setting (iii) in the case of hypothesis testing was considered in \cite{52470}.
-%
-Estimation problem subject to the one-bit quantization constraint were also considered recently in compressed sensing \cite{boufounos20081,baraniuk2017exponential} and in MIMO detection in wireless communication \cite{singh2009limits}.
+The specialization of their result to our setting, by taking $m=n$ and $R=1$, leads to looser lower bounds then $\sigma^2\pi/(2n)$ for cases (ii) and (iii).
+The counterpart of our setting (iii) in the case of hypothesis testing was considered in \cite{52470}, although the results there cannot be extended to parametric estimation.
+Other related works include statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation}, and one-bit quantization constraints in compressed sensing  \cite{baraniuk2017exponential} and in MIMO detection in wireless communication \cite{singh2009limits}.
 \\
@@
 
-In this work we are concerned with the MSE risk defined as
+In this work we are concerned with the Bayes MSE risk defined as
 \begin{equation}
@@
 
-The main problem we consider is the minimization of \eqref{eq:error_def} over all encoding and estimation strategies, and the characterization of its minimal value as a function of $n$.
+The main problem we consider is the minimization of \eqref{eq:error_def} over all encoding and estimation strategies and the characterization of its minimal value as a function of $n$.
 This minimization is the combination of the following two procedures: (1) selecting the $i$th message $M_i$ based on past messages and current observation $X_i$, and (2) estimating $\theta$ given messages $M^n$.
 %
-We are interested in particular on the increase in sample complexity compared to the vanilla mean estimation without one-bit constraint. For this reason, we consider the limit
+We are interested in particular on the increase in sample complexity compared to the vanilla mean estimation without one-bit constraint. For this reason, we consider 
 \begin{equation}
-{\sigma^2} n \mathbb E\left(\widehat{\theta}_n - \theta \right)^2,
+{\sigma^2} n \mathbb E\left(\widehat{\theta}_n - \theta \right)^2
 \label{eq:relative_efficiency}
 \end{equation}
-which is the ratio between the MSE of the sample mean and the MSE of the estimator $\widehat{\theta}_n$.
-Note that if the limit $\mathbb E\left(\widehat{\theta}_{n} - \theta \right)^2$ exists and finite, than \eqref{eq:relative_efficiency} is the ARE of $\widehat{\theta}_n$.
+in the limit as $n$ goes to infinity.
+Equation \eqref{eq:relative_efficiency} is the ratio between the MSE attained by the empirical mean of the samples and the MSE attained by the estimator $\widehat{\theta}_n$.
+Note that if the limit $\mathbb E\left(\widehat{\theta}_{n} - \theta \right)^2$ exists and finite, than \eqref{eq:relative_efficiency} is the ARE of $\widehat{\theta}_n$ \cite[Def.
+6.6]{lehmann2006theory}.
 
@@
 
-Before deriving our main results, we comment on the relation between our setting and the remote multiterminal source coding problem.
+Before deriving our main results, we comment on the relation between our setting and the remote multiterminal source coding problem, also known as the CEO problem.
 
 \section{Relation to Remote Multiterminal Source Coding \label{sec:ceo}}
-In this section we draw a connection between our general problem of mean estimation from one-bit samples and the remote multiterminal source coding problem \cite{berger1996ceo}, also known as the CEO problem.
-The setting of the CEO includes $n$ encoders, each has access to a noisy version of a random source sequence.
+%In this section we draw a connection between our general problem of mean estimation from one-bit samples and the remote multiterminal source coding problem \cite{berger1996ceo}, also known as the CEO problem.
+The setting of the CEO includes $n$ encoders, each has access to a noisy version of a random source sequence \cite{berger1996ceo}. 
 % $\left\{ U_j,\,j=1,2,\ldots \right\}$. 
@@
 Assuming that $\theta$ is drawn once from the prior $\pi(\theta)$, our mean estimation problem from one-bit samples under distributed encoding (setting (iii) in the Introduction) corresponds to the Gaussian CEO setting with $k=1$ source realization: the $i$th encoder uses $R_i=1$ bits to transmit a message that is a function of $X_i = \theta + \sigma Z_i$, where $Z_i$ is standard normal.
-As a result, the MSE in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$, a Gaussian observation noise at each estimate of variance $\sigma^2$, and an arbitrary number of $k$ independent draws of $\theta$, provides a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting.
-Note that the difference between the CEO and ours is in the fact encoders in the CEO describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realization, whereas our setting only allows $k=1$.
+As a result, a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting is given by the MSE in the optimal source coding scheme for the CEO with: $n$ terminals of codes rates $R_1 = \ldots = R_n = 1$, a Gaussian observation noise at each terminal of variance $\sigma^2$, and an arbitrary number of $k$ independent draws of $\theta$.
+Note that the difference between the CEO and ours lays in the privilege of each of the CEO encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realization, whereas our setting only allows $k=1$.
  \\
@@
 \begin{proof}
-We consider the expression \cite[Eq. 10]{chen2004upper} that provides the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$:
+We consider the expression \cite[Eq. 10]{chen2004upper} that gives the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$:
 \begin{equation} \label{eq:ceo_optimal_sumrate}
@@
 \end{proof}
-Since the lower bound \eqref{eq:ceo_bound}  was derived assuming optimal allocation of the $n$ bits among the encoders, it may seem as if a tighter bound can be obtained in our case by considering the CEO distortion with $R_1=\ldots = R_n = 1$.
-However, an upper bound for the CEO distortion under this condition follows from \cite[Prop.
-5.2]{KipnisRini2017}, and leads to
+
+Prop.~\ref{prop:ceo_lower_bound} implies that, unlike in the centralized setting, there is a loss in efficiency in estimating $\theta$ due to one-bit measurements in this setting.
+In the next section we show that the ARE in adaptive encoding setting does not exceeds $\pi/2$, and thus provides a tighter lower bound for the distributed encoding setting than $4/3$ of  \eqref{eq:ceo_bound}.
+\\
+
+We note although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO distortion while enforcing the condition $R_1=\ldots = R_n = 1$.
+Indeed, an upper bound for the CEO distortion under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
 \[
@@
 \]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ goes to zero. \par
-We conclude therefore that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed encoding setting, is attributed exclusively to the ability to perform coding over blocks.
+which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ goes to zero. 
+%Recall that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed encoding setting is attributed exclusively to the ability to perform coding over blocks.
 Namely, the freedom to consider an arbitrary number $k$ of independent realizations of the problem, versus only one in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product space, rather than the distributed nature of the problem, that distinguishes between the CEO distortion and our problem of mean estimation from one-bit samples.\par
-In the next section we show that the ARE in adaptive encoding setting does not exceeds $\pi/2$, and thus provides a tighter lower bound for the distributed encoding setting than $4/3$ of  \eqref{eq:ceo_bound}.
+Therefore, since
+%In other words, it is the ability to exploit the geometry of a high-dimensional product space, rather than the distributed nature of the problem, that distinguishes between the CEO distortion and our problem of mean estimation from one-bit samples.\par
 
@@
 Next, we provide a particular adaptive estimation scheme and show in Thm.~\ref{thm:sgd} that its efficiency is $\pi/2$.
-Finally, in Thm.~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen.
+Finally, in Thm.~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the encoder send the message $M_i^\star$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages.
 While it is not clear whether the efficiency of this last scheme is $\pi/2$, numerical simulations suggests that the MSE of this scheme times $n$ also converges to $\pi/2$ faster than the first scheme.
@@
 Let $\widehat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Fig.~\ref{fig:sequential}.
-Assume that $\Theta$ is an interval and that the density of the prior $\pi(\theta)$ converges to zero at the endpoints of $\Theta$.
+Assume that the density of the prior $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$.
 Then
@@
 
-For the estimator defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} we have the following results:
+For the estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} we have the following results:
 \begin{thm} \label{thm:sgd}
@@
 While a reasonable initialization is $\theta_0 = \mathbb E [\theta]$, Thm.~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
-Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the size of the parameter space $\Theta$.
+Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$.
 Nevertheless, the bound in Thm.~\ref{thm:adpative_lower_bound} suggests that the non-asymptotic estimation error can be significantly reduced whenever the location information $I_0$ is large.
@@
 We now consider an estimation scheme that posses the property of \emph{one-step optimality}: at each step $i$, the $i$th encoder designs the detection region $M_i^{-1}(1)$ such that the MSE given $M^i$ is minimal.
-In other word, this scheme designs the messages in a greedy manner, such that the MSE at step $i$ is minimal given the current state of the estimation described by $M^{i-1}$.
+In other word, this scheme designs the messages $M^n$ in a greedy manner, such that the MSE at step $i$ is minimal given the current state of the estimation described by $M^{i-1}$.
 \\
@@
 \begin{lem} \label{lem:adaptive}
-Let $U$ be an absolutely continuous random variable with
-pdf $P(du)$. Then the one-bit message $M^\star\in \{-1,1\}$ that minimizes
+Let $U$ be a random variable with probability density function  $P(du)$. Then the one-bit message $M^\star\in \{-1,1\}$ that minimizes
 \[
@@
 \end{align}
-where $\alpha_n$ is a normalization coefficient that equals to
+where $\alpha_n$ is a normalization coefficient that equals
 \[
@@
 We conjecture that it attains the asymptotic relative efficiency of $\sigma^2\pi/2$ as can be observed from the numerical simulation illustrated in Fig.~\ref{fig:adaptive_error}.
-Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the asymptotically optimal estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the sample mean for the same sample realization.
+Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the asymptotically optimal estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the empirical mean of the samples for the same sample realization.
 
@@
 \end{thm}
-Theorem~\ref{thm:vanTrees} applied to our problem with $p(x,\theta) = P(M^n|\theta)$ implies
+Thm.~\ref{thm:vanTrees} applied to our problem with $p(x,\theta) = P(M^n|\theta)$ implies
 \begin{align*}
@@
 \subsection*{Proof of Thm.~\ref{thm:opt_one_step}}
-In this subsection we prove Lemmas \ref{lem:adaptive} and \ref{lem:unique} that lead to Thm.~\ref{thm:opt_one_step}.
+In this subsection we prove Lem. \ref{lem:adaptive} and \ref{lem:unique} that lead to Thm.~\ref{thm:opt_one_step}.
 

### 2017-10-09 Writeups/onebit_adaptive_Allerton_V3.tex
small changes to final version

@@
 
-In setting (i) the estimator can evaluate the empirical mean of the samples and then communicate it using $n$ bits.
+In setting (i), the estimator can evaluate the empirical mean of the samples and then communicate it using $n$ bits.
 This strategy leads to MSE behavior of $\sigma^2/n + O(2^{-n})$.
@@
 
-The lower bound of $\pi/2$ on the ARE, i.e., a lower bound of $\sigma^2\pi/(2n) +O(n^{-2})$ on the MSE, is obtained by showing that the Fisher information of any $n$ adaptive messages is not larger than $2n/(\pi \sigma^2)$.
+The lower bound of $\pi/2$ on the ARE, i.e., a lower bound of $\sigma^2\pi/(2n) +O(n^{-2})$ on the MSE, is obtained by showing that the Fisher information of any $n$ adaptive messages is not greater than $2n/(\pi \sigma^2)$.
 From here, the desired bound on the MSE follows from the van Trees version of the information inequality \cite{gill1995applications}.
@@
 In addition to these two results, we also derive the one-step optimal strategy in which the message sent at step $i$th is designed to minimize the MSE given this message and the previous $i-1$ messages.
-Furthermore, we demonstrates numerically that the MSE under this strategy converge to $\pi \sigma^2/(2n)$.
-%A proof for this converges remains elusive.
-\\
+Furthermore, we demonstrates numerically that the MSE under this strategy converge to $\pi \sigma^2/(2n)$.\\
 
-\subsection*{Background and Related Works}
+We note that even though its ARE is $1$, the centralized encoding setting (i) already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation scheme.
+Indeed, the standard technique to encode an unknown random quantity using $n$ bits is equivalent to the design of a scalar quantizer \cite{gray1998quantization}.
+However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation problem and hence its exact value is unknown.
+As a result, a non-trivial exploration exploitation tradeoff arises in this case.
+Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$.
+Therefore, while it is clear that uncertainty due to quantization decreases exponentially in the number of bits $n$ leading to ARE $1$, an exact expression for the MSE in this setting seems to be difficult to derive.
+The situation is even more involved in the adaptive encoding of setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$, may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
+Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $2^{n-1}$ messages, is not guaranteed to be globally optimal.
+Our results imply that the ARE of any globally optimal strategy is $\pi/2$.
+
+\subsection*{Related Works}
 
@@
 The rate of this convergence, however, was not analyzed and cannot be derived from the results of \cite{53738}.
-Our results imply that the rate of convergence of a SDM to a constant input is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-\\
-
-We note that even though its ARE is $1$, the centralized encoding setting (i) already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation scheme.
-Indeed, the standard technique to encode an unknown random quantity using $n$ bits is equivalent to the design of a scalar quantizer \cite{gray1998quantization}.
-However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation problem and hence its exact value is unknown.
-As a result, a non-trivial exploration exploitation tradeoff arises in this case.
-In our setting, the only missing parameter is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$.
-Therefore, while it is clear that uncertainty due to quantization decreases exponentially in the number of bits $n$ leading to ARE $1$, an exact expression for the MSE in this setting is not easy to derive.
-The situation is even more involved in the adaptive encoding of setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$, may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
-Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $2^{n-1}$ messages, is not guaranteed to be globally optimal.
-Therefore, the main contribution of this paper is a lower bound on the MSE risk of any globally optimal strategy.
+Our results imply that the rate of convergence of the MSE in SDM to a constant input is at most $\sigma^2\pi/2$ over the number of feedback iterations.
 \\

### 2017-10-28 Writeups/onebit_adaptive_Allerton_V3.tex
update

@@
 %\documentclass[letterpaper]{IEEEtran}
-\documentclass[letterpaper, conference,9pt]{IEEEtran}      % Use this line for a4 paper
+\documentclass[letterpaper, conference,11pt]{IEEEtran}      % Use this line for a4 paper
 %\IEEEoverridecommandlockouts                              %
@@
 In other words, one-bit restriction increases the number of samples required for a prescribed accuracy of estimation by a factor of at least $\pi/2$ compared to the unrestricted case.
-%{\color{red} This fundamental restriction on estimation in the adaptive setting implies a lower bound any distributed estimation setting from one-bit samples. }
 %
@@
 In addition to these two results, we also derive the one-step optimal strategy in which the message sent at step $i$th is designed to minimize the MSE given this message and the previous $i-1$ messages.
-Furthermore, we demonstrates numerically that the MSE under this strategy converge to $\pi \sigma^2/(2n)$.\\
+Furthermore, we demonstrates numerically that the MSE under this strategy converges to $\pi \sigma^2/(2n)$.\\
 
@@
 Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$.
-Therefore, while it is clear that uncertainty due to quantization decreases exponentially in the number of bits $n$ leading to ARE $1$, an exact expression for the MSE in this setting seems to be difficult to derive.
+Therefore, while it is clear that uncertainty due to quantization decreases exponentially in the number of bits $n$ leading to ARE $1$, an exact expression for the MSE in this setting is difficult to derive.
 The situation is even more involved in the adaptive encoding of setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$, may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
@@
 \[
-D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
+D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
 \frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
@@
 %The weight function describes the variance of the MLE in the probit model 
+% Since we consider a general log-concave symmetric density, the above is only true for the normal density. 
 In particular, the maximum of \eqref{eq:induction_base} is obtained at $x=0$ where it equals $2/\pi$. \par

### 2017-10-28 Writeups/proof of Lemma 7 for log-concave distributions.tex
update

@@
 \end{equation}
-Since $f(x)$ is log-concave, positive, and twice differentiable, we may write $f(x) = e^{g(x)}$ with $g(x)$ concave and twice differentiable.
-Moreover, since symmetry of $f(x)$ implies symmetry of $g(x)$, and, since the latter is concave, it attains a single maximum at the symmetry point $x=0$.
-Therefore, $x=0$ is the only point for which $g'(x)=0$.
-We now show that $x=0$ is the point where $\eta(x)$ attains its maximum value.
-Since $\eta(x)$ is positive and  goes to zero as $x\rightarrow \pm \infty$, the maximum of $\eta(x)$ cannot be attained as $x\rightarrow \pm \infty$.
-We therefore consider the derivative of $\eta(x)$, given as
+Since $\eta(x)$ is symmetric about the origin, it is enough to show that $\eta'(x) \leq$ for all $x>0$, and hence $x=0$ is a global maximum of $\eta(x)$.
+Since $F(x)$ is log-concave and twice differentiable, we may write $F(x) = e^{h(x)}$ with $h(x)$ concave and twice differentiable.
+Moreover, note that $h'(x)\geq 0$ because $e^{h(x)}$ is non-decreasing, $h''(x) \leq 0$ because $h(x)$ is concave, and $e^{h(-x)} = 1- e^{h(x)}$ because $f(x)$ is symmetric around $0$.
+Moreover, since $f(x)$ is unimodal, for $x>0$ we have
 \[
-\eta'(x) = 2 \eta(x) e^{g(x)} \left(\frac{F(x)-1/2}{F(x)(1-F(x))} + g'(x) \right). 
+0 \geq f'(x) = e^{h(x)} \left(h''(x) + (h'(x))^2 \right),
 \]
-Since $f(x)$ is symmetric and integrates to $1$, we 
-have that $F(0)=0.5$ and hence $\eta'(0) = 0$.  It is left to verify that $\eta'(x)\neq 0$ for $x \neq 0$.
+and hence 
+\[
+0 \geq h''(x) + (h'(x))^2, \quad x\geq 0.
+\]
+Similarly, 
+\[
+0 \leq h''(-x) + (h'(-x))^2, \quad x\geq 0. 
+\]
+Using these facts, we conclude that
+\[
+\eta(x) =  \frac{ h'(x) h'(-x) e^{h(x)+h(-x)}} 
+{e^{h(x) + h(-x)}  } = h'(x)h'(-x),
+\]
+thus
+\[
+\eta'(x) = h''(x)h'(-x) - h''(-x) h'(x).
+\]
+For $x>0$ we obtain
+\begin{align*}
+\eta'(x) &\leq -\left(h'(x) \right)^2 h'(-x)  + \left(h'(-x) \right)^2 h'(x) \\
+& = h'(x)h'(-x) \left( h'(-x)-h'(x) \right) \leq 0.
+\end{align*}
+\\
 
-Taking the logarithm of \eqref{eq:induction_base} leads to 
-\begin{align*}
-& 2 \log f(x) - \log F(x) - \log F(-x) \\
-& = 2 \log h'(x) + h(x) - h(-x).
-\end{align*}
-Note that since $F(x)$ is non-decreasing, so is $h(x)$. In addition, $h'(x)$ is non-increasing since $h(x)$ 
-, the maximal value of \eqref{eq:induction_base} is obtained as 
-{HERE!! \color{red} finish proof by showing that \eqref{eq:induction_base} is smaller than $4f(0)$.\\
-}
-\\
 Assume now that \eqref{eq:bound_intervals} holds for all integers up to some $n = N-1$ and consider the case $n = N$.

### 2018-02-07 Writeups/onebit_full_V1.tex
stated working on full version

@@
 
-%{\color{red}  The $\mu$-sum problem (Kim-ElGamal Ch. 21) gives a lower bound. Can be reduced to the CEO.}
+{\color{red} 
+One-bit with constant input is important, since estimating when the parameter varies with time is always harder.
+Our result implies than the error in any estimation with one-bit per sample is at least $pi/2$ times the MSE with an unlimited number of bits per sample.
+ \\
+}
+
+{\color{red} Check connection to the $\mu$-sum problem (Kim-ElGamal Ch. 21) that (maybe ?) gives a lower bound, and can be reduced to the CEO.
+}
 
@@
 Shamir's results shows that the penalty is in the dimension ($d/R$ instead of $lod(d)$).
-In our setting the dimension is $1$.} \\
+In our setting the dimension is $1$.
+\\
+Baranuik et. al. \cite{baraniuk2017exponential} showed that adaptive one-bit measurements leads to exponential decay of MSE, but they did not consider noise!! \\
+Masry and Ishwar 
+\cite{masry2009field} considered the estimation of 
+he case of threshold measurements of random threshold values, and provided exact expression for the mean and variance of the
+error attained under two random sampling techniques and linear estimation. \\
+As we explain below, our problem can also be seen as a special case of communicating a function, namely the sample mean, as in \cite{1413468}, and ($\mu$-sum).
+Difference between one-bit quantization and threshold detection / quantization. 
+}
 

### 2018-02-23 Writeups/onebit_full_V2.tex
finished first complete draft of full version (onebit_full_V2.tex)

%\documentclass[letterpaper]{IEEEtran}
\documentclass[letterpaper, conference, 11pt]{IEEEtran}      % Use this line for a4 paper

%LatexiDiff ignore tikz:
% $: latexdiff -c "PICTUREENV=(?:picture|tikzpicture|DIFnomarkup)[\w\d*@]*" old.tex new.tex > diff.tex

%\IEEEoverridecommandlockouts                              %

%\usepackage{mathcomSTEP}

%\overrideIEEEmargins 
%\IEEEoverridecommandlockouts                              % This command is only needed if 
% you want to use the \thanks command

%\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

%\onecolumn

\usepackage{mathptmx} 
\usepackage{times}

\usepackage{amsmath} 
\usepackage{amsbsy} 
\usepackage{amssymb}
%\usepackage{newtxtext, newtxmath}
\usepackage{mathrsfs}
\usepackage{comment}
\usepackage[export]{adjustbox}
\usepackage{tikz}
\usetikzlibrary{external,positioning,decorations.pathreplacing,shapes,arrows,patterns}

%\tikzexternalize[mode=list and make]
\usepackage{algorithmicx}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{pstool}
\usepackage[latin1]{inputenc}
\usetikzlibrary{arrows,shapes}
\usepackage{xifthen}
\usepackage{epic}
\usepackage{caption}
\usepackage{epstopdf}

\newtheorem{thm}{\bf{Theorem}}
\newtheorem{cor}[thm]{\bf {Corollary}}
\newtheorem{lem}[thm]{\bf {Lemma}}
\newtheorem{prop}[thm]{\bf {Proposition}}
\newtheorem{example}{\bf {Example}}
\newtheorem{definition}{\bf {Definition}}
\newtheorem{rem}{\bf {Remark}}

\newcommand{\mmse}{\mathsf{mmse}}
\newcommand{\unif}{\mathsf{unif}}
\newcommand{\card}{\mathrm{card}}
\newcommand{\ARE}{\mathsf{ARE}}
\newcommand{\supp}{\mathrm{supp} }
\renewcommand\vec[1]{\ensuremath\boldsymbol{#1}}
\newenvironment{proof}{\paragraph*{Proof}}{\hfill$\square$ \newline}
\newcommand{\sgn}{\mathrm{sgn} }
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand*{\QEDA}{\hfill\ensuremath{\square}}

\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
\tikzstyle{sint}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.8cm,thick ]
\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=1cm,thick ]
\tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]

\title{\LARGE \bf Mean Estimation from Single-Bit Measurements}
%
%\author{
%\IEEEauthorblockN{Alon Kipnis}
%\IEEEauthorblockA{Department of Electrical Engineering \\
%Stanford University\\
%Stanford, CA\\}
%\and
%\IEEEauthorblockN{John C. Duchi}
%\IEEEauthorblockA{Department of Statistics \\
%and Department of Electrical Engineering \\
%Stanford University\\
%Stanford, CA\\}
%\and
%\IEEEauthorblockN{Andrea J. Goldsmith}
%\IEEEauthorblockA{Department of Electrical Engineering \\
%Stanford University\\
%Stanford, CA\\}
%}

\begin{document}
\graphicspath{{../Figs/}}
\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We consider the problem of estimating the mean of a symmetric log-concave distribution under the constraint that only a single bit per sample from this distribution is available to the estimator. We study the mean squared error risk in this estimation as a function of the number of samples, and hence number of bits, from this distribution. Under an adaptive scheme in which each bit is a function of the current sample and the previously observed bits, we show that the optimal relative efficiency, compared to the standard mean estimator without bit limitation, is the efficiency of the median. For the distributed scheme we consider the setting where each bit is obtained by comparing against a prescribed threshold value. We show that the maximum likelihood estimator in this case is asymptotically local minimax, and its asymptotic relative efficiency is finite although strictly larger than that of the sample median. 
% and depends on the size of the parameter space from which the mean is taken. Furthermore, assuming a prior on this space, the efficiency in the distributed case approaches $\sigma^2/4f^2(0)$ provided the variance of the distribution is high compared to the variance of the prior. 
%
%Therefore, our results indicates that, rather surprisingly, parametric estimation from the coarsest form of quantization incurs only a multiplicative penalty factor on the number of measurements. For example, this factor is $\pi/2$ for the normal distribution. 
\end{abstract}

%{\color{red}  See LASSO results in http://arxiv.org/abs/1506.02181v1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:Intro}
Estimating parameters from data collected and processed by multiple units may be limited due to communication constraints between these units. 
%
For example, this scenario arises in sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit. In these situations, the ability to estimate a particular parameter from the data is dictated not only by the quality of observations and their number, but also by the available bandwidth for communicating between the sensors and the central estimator. The question that we ask is to what extent a parametric estimation task is affected by this constraint on communication, and what are the fundamental performance limits in estimating a parameter subject to such restriction. \\

This paper answers this question in a particular setting: the estimation of the mean $\theta$ of a symmetric log-concave distribution $P_X$ with a finite variance, under the constraint that only a single bit can be communicated on each sample from this distribution. As it turns out, the ability to share information before committing on each single-bit message dramatically affects the performance in estimating $\theta$. We therefore distinguish among three settings:
\begin{itemize}
 \item[(i)] \emph{Centralized} encoding: all $n$ encoders confer and produce a single $n$ bit message. 
 \item[(ii)] \emph{Adaptive} or \emph{sequential} encoding: the $i$th encoder observes the $i$th sample and the $i-1$ previous messages.
 \item[(iii)] \emph{Distributed} encoding: the $i$th message is only a function of the $i$th observation.
 \end{itemize}
Evidently, as far as information sharing is concerned, settings (iii) is a more restrictive version of (ii) which is more restrictive than (i). Below are three application example of each of settings (i)-(iii), respectively:
\begin{itemize}
\item[(i)] {\bf Signal acquisition:} a quantity is measured $n$ times at different instances, and the results are averaged in order to reduce measurement noise. The averaged result is then stored using one of $n$ states. 
\item[(ii)] {\bf analog-to-digital conversion via sigma-delta modulation (SDM):} in SDM an analog signal is converted into a sequence of bits by sampling it at a very high rate and then using one-bit threshold detector combined with a feedback loop to update an accumulated error state. Therefore, the MSE in tracking an analog signal using a SDM falls under our setting (ii) when we assume that the signal at the input to the modulator is a constant (direct current) corrupted by, say, thermal noise \cite{53738}. Since the sampling rates in SDM is usually many times more than the bandwidth of its input, analyzing SDM under a constant input provides meaningful lower bound even for non-constant signals.
\item[(iii)] {\bf Differential privacy:} -- a business entity is interested in estimating the average income of its clients. In order to keep this information as confidential as possible, each client answers a single yes/no questions about its individual income. 
\end{itemize}

We measure the performance in estimating $\theta$ by the mean squared error (MSE) risk. We are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting compared to asymptotically normal estimators whose variances decreases as $\sigma^2/n+o(n^{-1})$ where $\sigma^2$. Estimator of this form includes the empirical mean of $X_1,\ldots,X_n$, and under some conditions, optimal Bayes estimations. We note that the performance under estimating a signal that may vary with each noisy measurement is always harder that our setting where the parameter (the mean) remains fixed. Therefore, the excess MSE risk due to the one-bit per measurement constraint we derive in this paper can serve as the most optimistic estimate for the degradation in performance in estimating a signal that vary in time.

% given a prior distribution on the space $\Theta$ where $\theta$ resides. \\

In setting (i), the estimator can evaluate the empirical mean of the samples and then quantize it using $n$ bits. Since the accuracy in describing the empirical mean decreases exponentially in $n$, the error due to quantization is negligible compared to the MSE in estimating the mean. Therefore, the ARE in this setting is $1$. Namely, asymptotically, there is no loss in performance due to the communication constraint under centralized encoding. 
%
In this paper we show that a similar results does not hold even in setting and (ii): the ARE of any adaptive estimation scheme is at least that of the sample median. Specifically, when $P_X$ is normal, this ARE equals $2/\pi \approx 0.637$, showing that the one-bit constraint increases the effective sample size in estimating $\theta$ by at least $2/\pi \approx 1.57$ compared to estimating it without the bit constraint. We also show that this lower bound on the ARE and is tight by providing an estimator that attains it. % This estimator is obtained by averaging the results of a series of comparisons of the samples against certain thresholds. 
%This estimator is can be seen as a stochastic gradient descent procedure for minimizing the absolute error, hence it attains the asymptotic MSE of the sample median. % Interestingly, our estimator attains \eqref{eq:median_MSE} regardless of the particular realization of $\theta$ or the radius of the parameter space from which it is taken.
%
Clearly, the minimal penalty on the MSE in setting (ii) also holds under setting (iii), although the question whether this MSE is achievable (or otherwise, what is the minimal MSE) remains open. Instead, in setting (iii) we restrict ourselves to estimators from messages obtained by comparison against a prescribed value (that may be different for each sample). We show that the maximum likelihood (ML) estimator for $\theta$ from these messages is asymptotically local minimax, and its asymptotic variance is strictly greater than the variance of the median. Thus, at least when limited to threshold detection, the ability to adapt the threshold allows for a more efficient estimation. %This is in contrast to the \\ counterpart of our setting where $\theta$ is taken from a finite space

Even though the ARE in setting (i) is $1$, this scheme already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation procedures. Indeed, the standard technique to encode an unknown random quantity using $n$ bits is equivalent to the design of a scalar quantizer \cite{gray1998quantization}. However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation problem and hence its exact value is unknown. As a result, a non-trivial exploration exploitation trade-off arises in this case. Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$. Therefore, while it is clear that uncertainty due to quantization decreases exponentially in the number of bits $n$ leading to ARE $1$, an exact expression for the MSE in this setting is still difficult to derive. \par
The situation is even more involved in the adaptive encoding setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$, may not lead to a globally optimal strategy upon the recipient of the $n$th sample. Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $n-1$ messages, is not guaranteed to be globally optimal. Therefore, while we characterize the optimal detector given the previous messages, this characterization cannot be use to derive a lower bound on the ARE. Instead, our result on the median efficiency being the minimal ARE is obtained by bounding the Fisher information of any $n$ adaptive messages and using the van Trees version of the information inequality \cite{gill1995applications}.

%Finally, we show that an estimator that attains asymptotic MSE of $\sigma^2\pi/(2n)$ is obtained as a special case of \cite[Thm. 4]{polyak1992acceleration}. In addition to these two results, we also derive the one-step optimal strategy in which the message sent at step $i$th is designed to minimize the MSE given this message and the previous $i-1$ messages. Furthermore, we demonstrates numerically that the MSE under this strategy converges to $\pi \sigma^2/(2n)$.\\

\subsection*{Related Works}
As the variance $\sigma^2$ goes to zero, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is easily solved by a bisection style method over the parameter space. Therefore, the general case of non-zero variance is a reminiscent of the noisy binary search problem with possibly infinite number of unreliable tests \cite{cicalese2002least, Karp:2007:NBS:1283383.1283478}. However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a constant input $\theta$ corrupted by a Gaussian noise. Using a SDM, Wong and Gray \cite{53738} showed that the output of the modulator converges to the true constant input almost surely, so that a SDM provides a consistent estimator for setting (ii). The rate of this convergence, however, was not analyzed and cannot be derived from the results of \cite{53738}. In particular, our results for setting (ii) imply that the asymptotic rate of convergence of the MSE in SDM to a constant input under Gaussian nosie is at most $\sigma^2\pi/2$ over the number of feedback iterations. Baraniuk et. al \cite{baraniuk2017exponential} also considered adaptive one-bit measurements in the context of analog-to-digital conversion, although without noise at the input. Their result of an exponential MSE decaying rate clearly does not hold in the noisy setting (stated otherwise, the MSE can decay exponentially up to the noise level). 
\\

One-bit measurements in the distributed setting (iii) was considered in \cite{904560,4244748, 6882252, chen2010performance, 5184907}, but without optimizing the encoders or their detection rule. % analyzed the estimation from distributed quantized measurements when the same detection rule is applied by all encoders. However, the error criterion considered in these works is the Fisher information rather than the MSE risk or ARE criterion. \par
%Once the decision rule of each encoder is fixed, the optimal estimation of $\theta$ is determined using the maximum a posteriori probability rule. Hence, the distributed setting is reduced to finding the optimal decision rule of each encoder.
The work of \cite{52470} addresses the counterpart of our setting (iii) in the case of hypothesis testing, although the results there cannot be extended to parametric estimation. More generally, when the parameter space $\Theta$ is finite, the characterization of the optimal detection rules was considered by Tsitsiklist in \cite{tsitsiklis1988decentralized}. It was shown there that if the cardinality of $\Theta$ is at most $M$ and the probability of error criterion is used, than no more than $M(M-1)/2$ different detection rules are necessary in order to attain probability of error decreasing exponentially with the optimal exponent. %That is, beyond $M(M-1)/2$ some decision rules can be repeated without lossing optimality.
Furthermore, in a version of this problem for the adaptive sestting \cite{5751320}, it was shown that, with a specific two-stages feedback, there is no gain in feedback compared to the fully distributed setting. Our results implies that the ARE in the distributed setting with threshold detection rules is strictly larger than that in the adaptive setting, suggesting that the case of a finite $\Theta$ is very different than when $\Theta$ is an open set.\par
%
As we explain in details in Section~\ref{sec:preliminary}, the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}, leads to a lower bounds on the MSE in setting (iii). For the case of a Gaussian distribution, this lower bound bounds the ARE to be at most $3/4$. Thus, while this bound on the ARE provides no new information compared to the upper bound of $2/\pi$ we derive for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimal even under one-bit quantization of each sample.\\

Finally, we note that our settings (ii) and (iii) can be obtained as special cases of 
\cite{zhang2013information} that consider adaptive and distributed estimation protocols for $m$ machines, each has access to $n/m$ independent samples. The main result of \cite{zhang2013information} are bounds on the estimation error as a function of the number of bits $R$ each machine uses for communication. The specialization of their result to our setting, by taking $m=n$ and $R=1$, leads to looser lower bounds then we derive here for cases (ii) and (iii). Other related works include statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation}, and one-bit quantization constraints 
%in compressed sensing\cite{baraniuk2017exponential} and 
in MIMO detection in wireless communication \cite{singh2009limits}. \\

\section{Problem Formulation \label{sec:problem}}

\begin{figure}
\begin{center}
\begin{tikzpicture}[node distance=2cm,auto,>=latex]

\node[node distance = 1.5cm] at (0,0) (source2) {$X_1,\ldots,X_n$};
\node[int1, right of = source2, node distance = 2cm] (enc2) {Enc};  
\draw[->,line width = 2pt] (source2) -- (enc2); 
\node[int1, right of = enc2, node distance = 4cm ] (est) {Est};

\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M \in \left\{-1,1\right\}^n$} (est);

\node[right of = est, node distance = 1.5cm] (dest) {$\widehat{\theta}_n$};
%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
%\draw[->,line width=2pt] (dec) -- (dest);
\draw[->, line width=2pt] (est) -- (dest);
\end{tikzpicture}
\end{center}
\caption{\label{fig:centralized} Centralized encoding using one bit per sample on average.}
\end{figure}

\begin{figure}
\begin{center}
\begin{tikzpicture}[node distance=2cm,auto,>=latex]
  \node at (0,0) (source) {$X_1$} ;
  \node[int1, right of = source, node distance = 1.5cm] (enc1) {Enc 1};  
\draw[->,line width = 2pt] (source) -- (enc1);

 \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
\node[int1, right of = source2, node distance = 1.5cm] (enc2) {Enc 2};  
\draw[->,line width = 2pt] (source2) -- (enc2);

\node[below of = source2, node distance = 2.5cm] (source3) {$X_n$};
\node[int1, right of = source3, node distance = 1.5cm] (enc3) {Enc n};  
\draw[->,line width = 2pt] (source3) -- (enc3);

\node[below of = source2, node distance = 0.5cm] {$\vdots$};
\node[above of = source3, node distance = 0.6cm] {$\vdots$};
%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim P_X$};

\node[int1, right of = enc2, node distance = 4cm ] (est) {Est};
\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -2cm] (mes1) {$M_1 \in \left\{-1,1\right\}$} (est);   
\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M_2 \in \left\{-1,1\right\}$} (est);   
\draw[->] (enc1)+(0.7,0) -- +(0.7,-0.7) -| (enc2);

\draw[dashed,->] (enc2)+(0.7,0) -- +(0.7,-0.7) -| +(0,-1.2);
\draw[->,line width = 2pt] (enc3) -| (est);

\node[below of = mes2, node distance = 1.5cm] (mes3) {$M_1,\ldots,M_{n-1} $};

\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -2cm]  {$M_n \in \left\{-1,1\right\}$} (est);

\draw[->] (mes3.west) -- +(0,-0.5) -| (enc3);

\node[right of = est, node distance = 1.5cm] (dest) {$\widehat{\theta}_n$};
%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
%\draw[->,line width=2pt] (dec) -- (dest);
\draw[->, line width=2pt] (est) -- (dest);
\end{tikzpicture}
\end{center}
\caption{\label{fig:sequential} Adaptive single-bit encoding: the $i$th encoder delivers a single bit message which is a function of its private sample $X_i$ and the previous messages $M_1,\ldots,M_{i-1}$.}
\end{figure}

\begin{figure}
\begin{center}
\begin{tikzpicture}[node distance=2cm,auto,>=latex]
  \node at (0,0) (source) {$X_1$} ;
  \node[int1, right of = source, node distance = 1.5cm] (enc1) {Enc 1};  
\draw[->,line width = 2pt] (source) -- (enc1);

 \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
\node[int1, right of = source2, node distance = 1.5cm] (enc2) {Enc 2};  
\draw[->,line width = 2pt] (source2) -- (enc2);

\node[below of = source2, node distance = 2.5cm] (source3) {$X_n$};
\node[int1, right of = source3, node distance = 1.5cm] (enc3) {Enc n};  
\draw[->,line width = 2pt] (source3) -- (enc3);

%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
\node[below of = source2, node distance = 0.5cm] {$\vdots$};
\node[above of = source3, node distance = 0.6cm] {$\vdots$};

\node[int1, right of = enc2, node distance = 4cm ] (est) {Est};
\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -2cm] (mes1) {$M_1 \in \left\{-1,1\right\}$} (est);

\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M_2 \in \left\{-1,1\right\}$} (est);

\draw[->,line width = 2pt] (enc3) -| (est);

\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -2cm]  {$M_n \in \left\{-1,1\right\}$} (est);

\node[right of = est, node distance = 1.5cm] (dest) {$\widehat{\theta}_n$};
%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
%\draw[->,line width=2pt] (dec) -- (dest);
\draw[->, line width=2pt] (est) -- (dest);
\end{tikzpicture}
\end{center}
\caption{\label{fig:distributed} Distributed single-bit encoding: the single-bit message produced by each encoder is only a function of its private sample $X_i$.}
\end{figure}
Let $\Theta$ be a closed interval of the real line. Let $f(x)$ be a symmetric log-concave density function with a finite second moment $\sigma^2$. We denote by $P_X$ the probability distribution with density $f\left( x-\theta \right)$, where $\theta \in \Theta$. Therefore, $P_X$ is an absolutely continuous log-concave distribution with mean $\theta$, variance $\sigma^2$. Moreover, symmetry and log-concavity of $f(x)$ implies that $P_X$ has a single mode at $x =\theta$. \par
In some cases we assume that $\theta$ is drawn once from the prior distribution $\pi$ on the parameter space $\Theta$. In this cases we assume that $\pi$  
is absolutely continuous distribution, and denote its density by $\pi(\theta)$, i.e., $\pi(d\theta) = \pi(\theta)d\theta$.  
\par
The random variables $X_1,\ldots,X_n$ represent $n$ independent samples from $P_X$. 
We are interested in estimating the parameter $\theta$ from a set of $n$ binary messages $M^n = (M_1,\ldots,M_n)$, obtained from $X^n = (X_1,\ldots,X_n)$ under three possible scenarios: 
\begin{itemize}
\item[(i)~~] Centralized $M^n(X^n)$ (Fig.~\ref{fig:centralized}).
\item[(ii)~] Adaptive $M_i(X_i,M^{i-1})$, $i=1,\ldots,n$ (Fig.~\ref{fig:sequential}).
\item[(iii)] Distributed $M_i(X_i)$, $i=1,\ldots,n$ (Fig.~\ref{fig:distributed}).
\end{itemize}

The performance of an estimator $\hat{\theta}_n \triangleq \hat{\theta}_n(M^n)$ in any of these cases is measured according to the mean squared error (MSE) risk:
\begin{equation}
\label{eq:error_def}
R_n \triangleq \mathbb E\left(\hat{\theta}_n - \theta \right)^2,
\end{equation}
where the expectation is taken with respect to the distribution of $X^n$ and the prior distribution $\pi(\theta)$.  
%It is well known that minmax estimation error 
%\begin{equation}
%R_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left(\hat{\theta}_n - \theta \right)^2 | \theta \right],
%\end{equation}
%can be obtained from $R_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}. 
%
The main problem we consider is the minimal value of \eqref{eq:error_def} as a function of $n$, under various choices of the encoding functions in cases (i), (ii), and (iii). \\

Particular interest is given to the ARE of estimators with respect to an asymptotically normal efficient estimator without the one-bit constraint. Specifically,  let $\{a_n,\,n\in \mathbb N\}$ be a sequence such that 
\[
\sqrt{a_n}\left(\hat{\theta}_n - \theta\right) \overset{D}{\longrightarrow} \mathcal N(0, \sigma^2).
\]
Then the ARE of $\hat{\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
\[
\ARE(\hat{\theta}_n) \triangleq
\lim_{n\rightarrow \infty} \frac{a_n}{n}. 
\]
Note that in the special case where there exists $V \in \mathbb R$ such that
\[
a_n \mathbb E \left(\hat{\theta}_n - \theta \right)^2 = V + O(1/n),
\]
then the ARE of $\hat{\theta}_n$ is finite and equals $\sigma^2/V$. 
%sample mean $\bar{X}_n = \frac{1}{n} \sum_{i=1}^n X_i$. Since the MSE attained by the latter is $\sigma^2/n$, this relative efficiency is defined as
%\begin{equation}
% \lim_{n \rightarrow \infty} \frac{n}{\sigma^2}  R_n. 
%\label{eq:relative_efficiency}
%\end{equation}

%In addition to the notations defined above, we denote by $\phi(x)$ the standard normal density and by $\Phi(x)$ the standard normal cumulative distribution function. Prime denote derivative with respect to $\theta$.

\section{Preliminary Results \label{sec:preliminary}}
On a first impression it may not be clear whether consistent estimation of the mean is even possible in the adaptive and centralized settings. On the other hand, one may suspect that estimation in these cases is trivial as in the centralized setting (i), where it is easy to attain ARE 1. In this section we settle this skepticism by showing that (1) a consistent estimator with an asymptotically normal distribution always exists in setting (iii), and (2) the ARE in setting (iii) with $P_X = \mathcal N(\theta, \sigma^2)$ is bounded from below by $3/4$.

\subsection{Consistent Estimation}
Denote by $M_i$ is the indicator of the event $X_i > \theta_0$ for some arbitrary $\theta_0$. Note that
\[
\frac{1}{n} \sum_{i=1}^n M_i \overset{a.s.}{\rightarrow} F(\theta),
\]
where $F(x)$ is the cumulative distribution of $X_1-\theta$ that is assumed to be known. Therefore, 
\begin{equation}
\label{eq:estimator_naive}
\hat{\theta}_n = F^{-1}\left( \frac{1}{n} \sum_{i=1}^n M_i \right)
\end{equation}
is a consistent estimator for $\theta$ under setting (iii). Moreover, it can be verified, as we do in Section~\ref{sec:distributed}, that $\hat{\theta}_n$ is asymptotically normal with variance that is the inverse of
\begin{equation} \label{eq:eta_def}
\eta(\theta-\theta_0) \triangleq \frac{f^2(\theta-\theta_0)} {F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}. 
\end{equation}
In particular, the ARE of $\hat{\theta}_n$ is finite and equals $\sigma^2/\eta(\theta - \theta_0)$. For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that the function $\eta(x)$ is a strictly decreasing function of $|x|$. The following proposition, generalizes this property of $\eta(x)$ to any log-concave distribution.
\begin{prop} \label{prop:eta}
Let $f(x)$ be log-concave, symmetric and differntiable probability density function. Then 
\begin{itemize}
\item[(i)] The function
\[
\eta(x) = \frac{f^2(x)}{F(x) \left(1-F(x) \right)}
\]
is symmetric and strictly decreasing for any $x>0$ in the support of $f(x)$. In particular, $
\eta(x) \leq \eta(0) = 4f^2(0)$. 
\item[(ii)] $\eta(x)$ goes to $0$ as $|x|$ goes to infinity. 
\end{itemize}

\end{prop}
\begin{proof}
See Appendix~\ref{app:proofs}. 
\end{proof}
%
\begin{figure}
\begin{center}
\begin{tikzpicture}[scale = 0.6]
\begin{axis}[
width=8cm, height=6cm,
xmin = -3, xmax=3, 
restrict y to domain = 0:100,
ymin = 0,
samples=10, 
xlabel= $x$,
xtick={-2,-1,0,1,2},
xticklabels={-2,-1,0,1,2},
ytick={0,0.3989423,0.6366198},
yticklabels={0,$\frac{1}{\sqrt{2 \pi}}$,$2/\pi$},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {../Figs/eta.csv};
\addlegendentry{$\eta(x)$};
\addplot[domain = -5:5, samples = 50, color = red, solid, smooth]  {exp(-x^2/2) / sqrt(2*3.14159)};
\addlegendentry{$\phi(x)$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.6]
\begin{axis}[
width=8cm, height=6cm,
xmin = -4, xmax=4, 
restrict y to domain = -10:0,
ymin = -10,
samples=10, 
xlabel= $x$,
xtick={-3,-2,-1,0,1,2,3},
xticklabels={-3,-2,-1,0,1,2,3},
ytick={0,-0.45158,-0.919},
yticklabels={0,,},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {../Figs/eta.csv};
\addlegendentry{$\log \eta(x)$};
\addplot[domain = -5:5, samples = 30, color = red, solid, smooth]  {-(x)^2/2 -0.9189};
\addlegendentry{$\log \phi(x)$};
\end{axis}
\end{tikzpicture}
\caption{
The function $\eta(x) = f^2(x) / F(x)F(-x)$ (blue) for $f(x) = \phi(x)$ the standard normal density (red).
\label{fig:eta}
}
\end{center}
\end{figure}

At $\theta = \theta_0$ the variance of $\hat{\theta}_n$ of \eqref{eq:estimator_naive} equals $1/(4f(0)^2)$ which is the variance of the median. However, since  $\eta(x)$ vanishes as $|x|\rightarrow \infty$ (see illustration in Fig.~\ref{fig:eta} for the normal density),  the variance of $\hat{\theta}_n$ may be very large when $\theta$ is away from $\theta_0$. In this case, the estimator $\hat{\theta}_n$ has little practical value unless $\Theta$ is very small compared to $\sigma^2$. \par
%
In Section~\ref{sec:sequential} we present an asymptotically normal estimator that attains the variance of the median $1/\eta(0)$ regardless of the radius of $\Theta$ or the prior $\pi(\theta)$. We also show in Section~\ref{sec:sequential} that no estimator can attain variance that is smaller than $1/\eta(0)$, so that the ARE of any estimator is at least $\sigma^2\eta(0) = (2f(0)\sigma)^2$.

\subsection{Lower bound from the CEO \label{sec:ceo}}
The CEO setting includes $n$ encoders, each has access to a noisy version of a random source sequence \cite{berger1996ceo}. 
% $\left\{ U_j,\,j=1,2,\ldots \right\}$. 
The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator. \par
Assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding (setting (iii) in the Introduction) corresponds to the Gaussian CEO setting with $k=1$ source realization: the $i$th encoder uses $R_i=1$ bits to transmit a message that is a function of $X_i = \theta + \sigma Z_i$, where $Z_i$ is standard normal. As a result, a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting is given by the MSE in the optimal source coding scheme for the CEO with: $n$ terminals of codes rates $R_1 = \ldots = R_n = 1$, a Gaussian observation noise at each terminal of variance $\sigma^2$, and an arbitrary number of $k$ independent draws of $\theta$. Note that the difference between the CEO and ours lays in the privilege of each of the CEO encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realization, whereas our setting only allows $k=1$. 
 \\

By using an expression for the minimal MSE in the Gaussian CEO as the number of terminals goes to infinity, we conclude the following:
\begin{prop} \label{prop:ceo_lower_bound}
Assume that $\Theta = \mathbb R$ and that $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$. Then any estimator $\hat{\theta}_n$ of $\theta$ in the distributed setting satisfies
\begin{equation} \label{eq:ceo_bound}
 n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + O(n^{-1}),
\end{equation}
where the expectation is with respect to $\theta$ and $X^n$.
\end{prop}

\begin{proof}
We consider the expression \cite[Eq. 10]{chen2004upper} that gives the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$:
\begin{equation} \label{eq:ceo_optimal_sumrate}
R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
\end{equation}
Assuming $R_\Sigma = n$ and $L=n$, we get
\begin{equation} \label{eq:ceo_optimal_sumrate}
n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
\end{equation}
The value of $D^\star$ that satisfies the equation above describes the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders. Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed encoding setting. By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$, we see that 
\[
D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
\]
\end{proof}
We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO distortion while enforcing the condition $R_1=\ldots = R_n = 1$. Indeed, an upper bound for the CEO distortion under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
\[
D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
\]
which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ goes to zero. \par
From the formulation of the CEO problem, it follows that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is exclusively attributed  to the ability to perform coding over blocks. Namely, each CEO encoder may encode an arbitrary number of $k$ independent realizations of $\theta$ using $k$ bits, versus only one realization with one bit in ours. In other words, it is the ability to exploit the geometry of a high-dimensional product probability space that 
distinguishes between the CEO problem with one bit per encoder and the mean estimation problem from one-bit measurements in the distributed setting of Fig.~\ref{fig:distributed}.

\section{Adaptive Estimation \label{sec:sequential}}
The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $(2f(0)\sigma)^2$, which the ARE of the median of $X^n$. Next, we provide a particular adaptive estimation scheme that attains this maximal efficiency. Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen. Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $(2f(0)\sigma)^2$.

\subsection{Maximal efficiency of adaptive one-bit schemes}
Our first results asserts that the ARE of any adaptive estimation scheme is bounded from above by $(2 f(0)\sigma )^2$, as follows from the following theorem:
\begin{thm}[minimal relative effeciency] \label{thm:adpative_lower_bound}
Let $\hat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Fig.~\ref{fig:sequential} and assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
\[
\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\sigma^2}{4f^2(0) n}+o(n^{-1}),
\]
where 
\[
I_0 = \mathbb E \left( \frac{d}{d\theta} \log \pi (\theta) \right)^2
\]
is the Fisher information with respect to a location model in $\theta$. 
\end{thm}

\subsubsection*{Sketch of Proof}
The main idea in the proof is to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$. Once this bound is achieved, the result follows by using the van-Trees inequality \cite[Thm. 2.13]{tsybakov2008introduction},\cite{gill1995applications} which bounds from below the MSE of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$. The details are given in the Appendix.\\

Next, we present an adaptive estimation scheme that attains the maximal ARE of $(2f(0)\sigma)^2$.

\subsection{Asymptotically optimal estimator}
Let $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ be a strictly positive sequence. Consider the following estimator $\hat{\theta}_n$ for $\theta$:  
\begin{equation}
\label{eq:sgd_alg}
\theta_n = \theta_{n-1} +  \gamma_n \sgn (X_n - \theta_{n-1}), \quad n = 1,2,\ldots,
\end{equation}
and set the $n$th step estimation as
\begin{equation} \label{eq:sgd_est}
\hat{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
\end{equation}

For the estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} we have the following results:
\begin{thm} \label{thm:sgd}
Consider the sequence $\left\{\hat{\theta}_n,\, n\in \mathbb N \right\}$ defined by \eqref{eq:sgd_est}. 
\begin{enumerate}
\item[(i)] Assume that $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ satisfies
\begin{equation} \label{eq:conditions1}
\begin{cases}
\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
\mathrm{for~some~}0< \lambda \leq 1
\end{cases}
\end{equation}
(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Then
\[
\sqrt{n} \left( \hat{\theta}_n - \theta \right) \overset{d}{\rightarrow} \mathcal N \left(0,  \left( 2 f(0)\right)^{-2} \right).
\]
\item[(ii)] Assume that in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ satisfies
\begin{equation} \label{eq:conditions2}
\begin{cases}
\gamma_n = o(n^{-2/3}), &  \\
\sum_{n=1}^\infty \gamma_n = \infty.  & \\
\end{cases}
\end{equation}
(e.g., $\gamma_n = n^{-\beta}$ with $2/3<\beta<1$). Then
\[
\lim_{n\rightarrow \infty} n\mathbb E \left[ \left(\theta-\hat{\theta}_n \right)^2 \right] = \left( 2 f(0)\right)^{-2}. 
\]
\end{enumerate}
\end{thm}

\subsubsection*{Proof}
The asymptotic behavior of \eqref{eq:sgd_est} is obtained from \cite[Thm. 4]{polyak1992acceleration} and \cite[Thm. 2]{polyak1990new}. The details are in the Appendix.\\

Theorem~\ref{thm:sgd} implies that the estimator $\hat{\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the maximal ARE as established by Theorem~\ref{thm:adpative_lower_bound}.
\par
Note that $\theta_0$ is not explicitly defined 
in equation \eqref{eq:sgd_est}. A reasonable initialization for $\theta_0$ is $\theta_0 = \mathbb E [\theta]$, although Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization. Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$. Nevertheless, the bound in Theorem~\ref{thm:adpative_lower_bound} suggests that the non-asymptotic MSE can be reduced significantly whenever the location information $I_0$ is large. In what follows, we consider a greedy estimation procedure that uses the optimal decision rule given the prior distribution and the previous messages. In particular, this procedure exploit the prior information on $\theta$ provided by its prior.

\subsection{One-step optimal estimation}
We now consider an estimation scheme that posses the property of \emph{one-step optimality}: at each step $n$, the $n$th encoder designs the detection region $M_n^{-1}(1)$ such that the MSE given $M^n$ is minimal. In other word, this scheme designs the messages in a greedy manner, such that the MSE at step $n$ is minimal given the current state of the estimation described by $M^{n-1}$. \\

The following theorem determine the message, i.e., the decision rule $(M^{n-1},X_n)\rightarrow M_n$, that minimizes the next step MSE:
\begin{thm}[optimal one-step estimation] \label{thm:opt_one_step}
Let $\pi(\theta)$ be an absolutely continuous log-concave probability distribution. Given a sample $X$ from a log-concave distribution with mean $\theta$, define 
\begin{equation}
\label{eq:adaptive_main_message}
M^\star = \sgn(X - \tau),
\end{equation}
where $\tau$ satisfies the equation
\begin{equation}
 \label{eq:fixed_point}
 \tau = \frac{m^-(\tau) + m^+(\tau)}{2},
\end{equation}
with
\begin{align*}
m^-(\tau)  & = \frac{\int_{-\infty}^{\tau} \theta \pi(d\theta) }{\int_{-\infty}^{\tau} \pi(d\theta)} ,\\
m^+(\tau) & = \frac{\int_{\tau}^\infty \theta \pi(d\theta) }{\int_{\tau}^\infty \pi(d\theta)} .
\end{align*}
Then for any estimator $\hat{\theta}$ which is a function of $M(X) \in \{-1,1\}$, we have
\begin{equation}
\label{eq:opt_cond}
\mathbb E \left(\theta-\hat{\theta}(M)\right)^2 \geq  \mathbb E \left(\theta- \mathbb E[\theta|M^\star]\right)^2,
\end{equation}
\end{thm}

\begin{proof}
The proof is completed by the following two lemmas, proofs of which can be found in the Appendix:
\begin{lem} \label{lem:unique}
Let $f(x)$ be a log-concave probability density function. Then the equation 
\begin{equation}
\label{eq:lem_fixed_point}
2x = \frac{\int_x^\infty uf(u)du}{\int_x^\infty f(u)du} + \frac{\int_{-\infty}^x uf(u)du}{\int_{-\infty}^x f(u)du} 
\end{equation}
has a unique solution.
\end{lem}
\begin{lem} \label{lem:adaptive}
Let $U$ be an absolutely continuous random variable with pdf $P(du)$. Then the one-bit message $M^\star\in \{-1,1\}$ that minimizes
\[
\int \left( u - \mathbb E[U|M(u)]  \right)^2 P(du)
\]
is given by
\[
M^\star  =  \sgn(U - \tau),
\]
where $\tau$ is the unique solution to
 \[
2 \tau = \frac{\int_{\tau}^\infty u P(du)} {\int_{\tau}^\infty P(du)} + \frac{\int_{-\infty}^{\tau} u P(du)}{\int_{-\infty}^{\tau} P(du)}.
\]
\end{lem}
\end{proof}

\begin{rem}
The value of the optimal threshold as given in Theorem~\ref{thm:opt_one_step} is different than the one given in \cite[Eq. 5]{1619423} for apparently the same problem. Indeed, it seems like Equation 4 there is erroneous. 
\end{rem}

By applying at each step the optimal one-step decision rule from Theorem~\ref{thm:opt_one_step},  we arrive at the following adaptive encoding and estimation scheme: 
\begin{itemize}
\item Initialization: set $P_0(t) = \pi(t)$ and $\tau_0 = \mathbb E \theta$. 
\item For $n\geq 1$:
\begin{enumerate}
\item[(1)] Update the prior as
\begin{align}
& P_n(t) = P(\theta=t |M^n) \nonumber \\
& \quad = \frac{ P\left( \theta=t | M^{n-1} \right) P(M_n | \theta = t , M^{n-1})  } { P(M_n | M^{n-1} )} \nonumber \\ 
& \quad = \alpha_n  P_{n-1}(t) F\left(M_n (t - \tau_{n-1}) \right), \label{eq:density_update}
\end{align}
where $\alpha_n$ is given by
\[
\alpha_n = \left(\int_{\mathbb R} P_{n-1}(t) F \left(M_n (t- \tau_{n-1}) \right)  dt \right)^{-1}. 
\]
\item[(2)] The $n$th estimate for $\theta$ is the conditional expectation of $\theta$ given $M^n$, namely
\begin{equation}
\theta_n = \mathbb E \left[ \theta| M^n\right] = \int_{-\infty}^\infty t P_n(t) dt. \label{eq:estimator_update}
\end{equation}
\item[(3)] Obtain $\tau_n$ from equation \eqref{eq:fixed_point} with the updated prior $P_n(t)$. Note that $F(x)$ is log-concave so the updated prior $P_n(t)$ remains log-concave and thus a unique solution to \eqref{eq:fixed_point} is guaranteed by Lemma~\ref{lem:unique}. 
\item[(4)] Update the $(n+1)$th message as
\begin{equation}\label{eq:message_update}
M_{n+1} = \sgn(X_{n+1}-\tau_n)
\end{equation}
\end{enumerate}
\end{itemize}
Since equation \eqref{eq:fixed_point} has no analytic solution in general, it is hard to derive the asymptotic behavior of the estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}. We conjecture, however, that it attains the asymptotic relative efficiency of $4f^2(0)$ under the same conditions on $f(x)$ in the problem formulation. 
In Fig.~\ref{fig:adaptive_error} we demonstrate this convergence in the case where $f(x)$ is the standard normal density. Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the asymptotically optimal estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the sample mean for the same sample realization.

\begin{figure}
\begin{center}
\begin{tikzpicture}
\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
%\node[color = blue,  minimum width=1cm, align = left] at (1.5,1.5) {assymptotically optimal \eqref{eq:sgd_est}};
%\node[color = red, minimum width=1cm, align = left] at (1.5,0.55) {one-step optimal \eqref{eq:message_update}} ;
\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left(\hat{\theta}_n - \theta \right)^2$};
\node[scale = 0.7] at (0,-2.4) {$n$};
%\draw[dashed] (-3.5,1.18) node[left, scale = 0.7] {$\frac{\pi}{2}$}-- (-3,1.18);
\end{tikzpicture}
\caption{Normalized empirical risk $n\left(\hat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $500$ Monte Carlo trials. In each trial, $\theta$ is chosen uniformly in the interval $(-3,3)$. \label{fig:adaptive_error}  }
\end{center}
\end{figure}

\begin{comment}
\subsection{Relation to Sigma-Delta Modulation \label{subsec:sdm}}
The SDM is a device that converts continuous-time analog signals to a discrete-time sequence of binary digits. The basic operation of a SDM can be described as follows: the modulator takes as input a sequence of continuous amplitude samples $X_n$, which are typically represents samples of a continuous-time signal taken uniformly at sampling rate $f_s$ much higher than the Nyquist rate of the signal \cite{1095151}. The output of the modulator is a sequence $M_n$ of binary values, obtained according to the following rule: 
\begin{align}
\begin{cases} V_{n+1} & =  V_n - \alpha q(V_n) + X_n, \\
M_n & = \sgn(V_n)  \end{cases}, \quad n=1,2,\ldots, \label{eq:sdm}
\end{align}
where $\alpha > 0$ is a parameter of the modulator that is determined by the maximal value of the input sequence $X^n$. The SDM of the form \eqref{eq:sdm} was studied in \cite{53738} under the assumption that the input process $X_n$ is an i.i.d Gaussian process. The main results from \cite{53738} shows that regardless of the initial state $V_0$, the process $M_n$ is a stationary ergodic process with mean $\theta$. It follows that a consistent estimation of $\theta$ is obtained by taking the mean of the sequence $\{M_n\}$. However, the results from \cite{53738} does not provide a closed form for the second order statistics of $\{M_n\}$, so that convergence rate cannot be derived from \cite{53738}.  
\end{comment}

\section{Distributed Estimation from Threshold Detectors \label{sec:distributed}}
We now consider the distributed encoding setting described in Fig.~\ref{fig:distributed}, in which each single-bit message is independent of the other messages. Instead of searching for the optimal choice of the messages, we only consider messages that are obtained each sample against a prescribed threshold. Namely, each message is of the form
\begin{equation}
\label{eq:threshold_message}
M_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
-1 & X_i > t_i,
\end{cases}  
\end{equation}
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th detector applied by the encoder on it sample $X_i$. The \emph{density} $\lambda_n$ of the set of threshold values $\mathcal T_n  \triangleq \left\{t_1,\ldots,t_n \right\}$ is defined as their empirical distribution, i.e., for an interval $I \subset \mathbb R$, 
\[
\lambda_n(I) = \frac{ \card \left( \mathcal T_n \cap I \right)}{n}.
\]
We further assume that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$. For example, this convergence occurs whenever $t_1,\ldots,t_n$ are drawn independently from the probability distribution $\lambda(dt)$. 
 \\

\subsection{Local Asymptotic Minimax Estimation}

In order to estimate $\theta$ from the messages $M^n$, we consider the maximum likelihood (ML) estimator. The log-likelihood function of $\theta$ is given by
\[
l(M^n  |\theta ) =  \sum_{i=1}^n \log F \left( M_i \left( t_i - \theta \right) \right). 
\]
Since $F(x)$ is a log concave function, the log-likelihood function has a unique maximizer $\hat{\theta}_n$ which is the ML estimator. Specifically, the ML estimator $\hat{\theta}_{ML}$ is the unique root of 
\[
\sum_{i=1}^n M_i \frac{f \left( t_i-\theta\right) }{F \left(M_i  (t_i-\theta)\right) } 
\]

Next, we show that under the assumptions above the sequence of messages $M^n$ defines a local asymptotic normal (LAN) family of probability distributions. As a result, we conclude that the ML estimator in estimating $\theta$ from $M^n$ satisfies a local asymptotic minimax property with respect to the \emph{precision} parameter of this LAN family \cite{van2000asymptotic}. 
\begin{thm} \label{thm:LAN}
Let $f(x)$ be a log-concave, symmetric, and twice differentiable probability density function. Consider the sequence $M^n$ of threshold detectors 
\[
M_i = \sgn(X_i - t_i),\quad i=1,\ldots,n,
\]
with threshold density converges to a probability measure $\lambda$. The the following two statements hold:
\begin{itemize}
\item[(i)] Any estimator ${\theta}_n$ of $\theta$ which is a function of $M^n$ satisfies
\[
\liminf_{c\rightarrow \infty}\, \liminf_{n\rightarrow \infty} \sup_{\tau\,:\,| \tau - \theta| \leq \frac{c}{\sqrt{n}} }  n \mathbb E \left({\theta}_n - \tau \right)^2 \geq 1/K(\theta),
\]
where 
\[
K(\theta) \triangleq \int \eta\left(t-\theta \right) \lambda(dt),
\]
and 
\[
 \eta(x) \triangleq \frac{ f^2\left( x \right)}{ F\left( x \right) \left(1-F(x) \right)}. 
\]
\item[(ii)] The asymptotic distribution of the ML estimator $\hat{\theta}_n$ is given by
\[
\sqrt{n}(\hat{\theta}_n - \theta) \overset{D}{\rightarrow} \mathcal N\left(0,1/K(\theta) \right).
\]
\end{itemize}
\end{thm}

\begin{rem}
The condition that $\lambda_n(dt)$ converges weakly to $\lambda(dt)$ can be relaxed to the condition that for any $\theta \in \Theta$, 
\[
\frac{1}{n} \sum_{i=1}^n  \eta \left( t_i-\theta \right)  
\]
converges to $K(\theta)$.
\end{rem}

\begin{proof}
See Appendix. 
\end{proof}

It follows from Theorem~\ref{thm:LAN} that the asymptotic MSE of the ML estimator is $1/(nK(\theta))$, and that this MSE is asymptotically minimal with respect to all local alternative estimators for $\theta$. In particular, we conclude that the ARE of any estimator based on threshold detection is $K(\theta)\sigma^2$. \par
It follows from Proposition~\ref{prop:eta} that $\eta(x)$ attains its maximum at the origin. Since the thresholds density $\lambda$ integrates to $1$, it follows that
\[
K(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right)  = \eta(0) = 4f^2(0).
\]
This upper bound on $K(\theta)$ implies that the ARE of any distributed estimator is not smaller than $(2f(0)\sigma)^2$, a fact that agrees with the lower bound under adaptive estimation derived in Theorem~\ref{thm:adpative_lower_bound}. Furthermore, 
since this upper bound on $K(\theta)$ is attained whenever the density $\lambda$ is the mass distribution at $\theta$ which is unknown apriori, Theorem~\ref{thm:LAN} implies that estimation in the  distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting. In other words, the ability to adaptively choose the threshold value strictly improves the relative efficiency compared to a non-adaptive threshold selection. \\

In what follow, we consider the asymptotic threshold density $\lambda(dt)$ that minimize the asymptotic MSE under the worst choice of $\theta \in \Theta$, or, what is the same, the expected value of $\mathbb E\left [1/K(\theta) \right]$ under the least favorable prior $\pi(\theta)$. 
%As we shall see, even with an optimal selection of the threshold density, the minimax risk increases linearly in $b$ as in Example~\ref{ex:uniform_density}.

\subsection{Minimax Threshold Density}
%Assume that $\theta = [-b,b]$ and consider
%\begin{equation} \label{eq:variational}
%K^\star(b) = \sup_{\lambda} \min_{\theta \in [-b,b]}  {K(\theta)} = \int \eta\left( t-\theta \right) \lambda (dt), 
%\end{equation}
%where the supremum is over all probability measure $\lambda$ on $\mathbb R$.
The distribution $\lambda(dt)$ that minimizes the asymptotic MSE $K(\theta)$ over the worst choice of $\theta$ in $\Theta = [-b,b]$ is given as the solution to the following optimization problem:
\begin{align}
\label{eq:var_cvx_minimax}
\begin{split}
\mathrm{maximize} \quad &  \min_{\theta \in [-b,b]} \int \eta(t-\theta) \lambda(dt)
\\ 
\mathrm{subject~to} 
\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
\end{split}
\end{align}
Denote the maximal value of the objective in \eqref{eq:var_cvx_minimax} by $K^\star(b)$. Since the objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda$, this problem can be solved using a convex program. By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
\begin{align}
\label{eq:cvx_minimax}
\begin{split}
\mathrm{maximize} \quad &  K \\ 
\mathrm{subject~to} 
\quad &  K \leq \mathbf H\lambda \\
& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
\end{split}
\end{align}
where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
\begin{rem}
The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$. Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points. Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using 
\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
\end{rem}

Figure~\ref{fig:minimax_support} illustrates $\lambda^\star$ obtained as the solution to \eqref{eq:cvx_minimax} and the function $\mathbf H \lambda^\star$ for the case of $f(x)$ the standard  normal density. The minimal asymptotic ML risk $K^\star$ is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $b$. Also illustrated in these Figures is the MSE obtained when the threshold values are uniformly distribution over $\Theta = [-b,b]$, i.e., 
$\lambda(dt) = dt/(2b)$. In this case we have
\begin{align}
& K_{\unif} \triangleq \min_{\theta \in [-b,b]} \frac{1}{2b}\int_{-b}^{b} \eta\left(t-\theta\right) dt \nonumber
 \\
& = 
\frac{1}{2b}\int_{-b}^{b} \eta\left(t\pm b\right) dt
= \frac{1}{2b}\int_{0}^{2b} \eta(t) dt = \frac{1}{4b}\int_{-2b}^{2b} \eta(t) dt, \label{eq:uniform_risk}
\end{align}
so the ARE under a uniform distribution equals $\sigma^2 K_\unif$. \\

\begin{figure}
\begin{center}
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
xticklabels={-$b$, 0, $b$},
title = {$\sigma/b = 1/2$},
ytick={0,0.1,1},
%ylabel = {$\lambda(dt)$},
yticklabels={0,0.1,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/minmax_lmd_b0.5_sig0.5.csv};

\addplot[color = green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.5.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {../Figs/minimax_th_b0.5_sig0.5.csv};

\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 0.6,
samples=10, 
xlabel= {$dt$},
title = {$\sigma/b = 1/5$},
xtick={-0.5,0,0.5},
xticklabels={-$b$, 0, $b$},
ytick={0,0.5},
ylabel = {$\lambda(dt)$},
yticklabels={0,0.5},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/minmax_lmd_b0.5_sig0.2.csv};

\addplot[color = green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.2.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {../Figs/minimax_th_b0.5_sig0.2.csv};

\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 0.3,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
title = {$\sigma / b = 1/10$},
xticklabels={-$b$, 0, $b$},
ytick={0,0.2},
%ylabel = {$\lambda(dt)$},
yticklabels={0,0.2},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/minmax_lmd_b0.5_sig0.1.csv};

\addplot[color = green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.1.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {../Figs/minimax_th_b0.5_sig0.1.csv};

\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 0.15,
samples=10, 
xlabel= {$dt$},
title = {$\sigma / b = 1/20$},
xtick={-0.5,0,0.5},
xticklabels={-$b$, 0, $b$},
ytick={0,0.1},
ylabel = {$\lambda(dt)$},
yticklabels={0,0.1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {../Figs/minmax_lmd_b0.5_sig0.05.csv};

\addplot[color = green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.05.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {../Figs/minimax_th_b0.5_sig0.05.csv};

%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}

\caption{\label{fig:minimax_support}
The optimal density $\lambda^\star$ (blue) that minimizes the maximum asymptotic ML risk for $f(x)$ a standard normal density $\Theta = [-b,b]$, and various values of $\sigma$. %$\lambda^\star$ in these figures is obtained by solving \eqref{eq:cvx_minimax}. 
The continuous curve (red) represents the asymptotic risk for a fixed $\theta \in [-b,b]$ under the optimal density, so its maximal value is minimax risk. The dashed curve is the asymptotic risk a fixed $\theta \in [-b,b]$ under a uniform distribution over $[-b,b]$, so its maximal value is given by \eqref{eq:uniform_risk}. }
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\begin{tikzpicture}[scale = 1]
\begin{axis}[
width=8cm, height=6cm,
xmin = 0, xmax=2, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=1, 
xlabel= {$\sigma/b$},
%xtick={-0.5,0,0.5},
%xticklabels={-$$, 0, $b$},
ytick={0,0.637,1},
yticklabels={0,$2/\pi$,1},
ylabel = {$\ARE$},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = red, smooth] plot table [x = x, y = y, col sep=comma] {../Figs/minmax_ARE_b0.5.csv};
\addlegendentry{$\lambda^\star(dt)$};

\addplot[color = green, smooth, dashed, line width = 0.5pt] plot table [x = x, y = z, col sep=comma] {../Figs/minmax_ARE_b0.5.csv};
\addlegendentry{$dt/(2b)$};
\end{axis}
\end{tikzpicture}
\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/b$ for $P_X = \mathcal N(\theta,\sigma^2)$. The dashed curve represents the minimal ARE under a uniform threshold density given by $\sigma^2/K_{\unif}$, where $K_{\unif}$ is given by \eqref{eq:uniform_risk}. }.
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
xticklabels={-$b$, 0, $b$},
title = {$\sigma/\sigma_{\theta} = 1$},
ytick={0,1},
%ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/unif_Bayes_lmd_b0.5_sig1.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
title = {$\sigma/\sigma_{\theta} = 2$},
xtick={-0.5,0,0.5},
xticklabels={-$b$, 0, $b$},
ytick={0,1},
ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/unif_Bayes_lmd_b0.5_sig2.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
title = {$\sigma/\sigma_{\theta} = 3$},
xticklabels={-$b$, 0, $b$},
ytick={0,1},
%ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/unif_Bayes_lmd_b0.5_sig3.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
title = {$\sigma/\sigma_{\theta} = 4$},
xtick={-0.5,0,0.5},
xticklabels={-$b$, 0, $b$},
ytick={0,1},
ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/unif_Bayes_lmd_b0.5_sig4.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}

\caption{\label{fig:opt_density}
The threshold density $\lambda(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=b^2/3$ is the variance of the prior. 
}
\end{center}
\end{figure}

\subsection{Asymptotic Bayes Risk}
 We consider now the problem of minimizing the asymptotic Bayes risk $
R_{\pi,\lambda} \triangleq \mathbb E  K^{-1}(\theta)$ over all probability measures $\lambda(dt)$ with support in $\mathbb R$. This optimization problem can be written as follows:
\begin{align}
\label{eq:cvx_average}
\begin{split}
\mathrm{minimize} \quad & R_{\pi,\lambda} =  \int \frac{\pi(d\theta)}{ \int \eta \left( t-\theta\right) \lambda(dt)}. \\ 
\mathrm{subject~to} \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) =1. 
\end{split}
\end{align}
We denote by $R^\star_{\pi}$ the minimal value of the objective function in \eqref{eq:cvx_average}. Since the function $x \rightarrow 1/x$ is convex for positive values, \eqref{eq:cvx_average} defines a convex optimization problem in $\lambda$ whose solution depends on the prior $\pi$. The solution to this problem is approximated by considering $\lambda$ and $\pi$ over a discrete set in a similar way that \eqref{eq:cvx_minimax} is obtained from \eqref{eq:var_cvx_minimax}. \par
For the case of a normal distribution ($P_X = \mathcal N(\theta, \sigma^2)$) and a uniform prior ( $\pi(d\theta) =dt/(2b)$), the optimal asymptotic threshold density obtained as the solution to \eqref{eq:cvx_average} is illustrated in Fig.~\ref{fig:opt_density}, whereas Fig.~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk. 
\par
%
%\begin{figure}
%\begin{center}
%\begin{tikzpicture}
%\node at (0,0) {\includegraphics[scale=0.5]{dist_bound_Gauss_prior}};
%\node at (0,-2.5) {$\sigma/\sigma_\theta$};
%\node[rotate = 90] at (-3.5,0) {(expected asymptotic risk)$/\sigma^2$};
%\node at (1,0) {$\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$ };
%%\node at (-2,-1.05) {$\frac{\pi}{2}$};
%%\node[rotate = -45] at (-1.8,1.2) {\color{red} true };
%%\node[rotate = -70] at (-0.5,0) {\color{blue} bound };
%\end{tikzpicture}
%\caption{Expected asymptotic risk $\mathbb E K^{-1}(\theta)$ in estimation from threshold detectors versus $\sigma/\sigma_\theta$ for a Gaussian prior with variance $\sigma_\theta^2$. The optimal asymptotic threshold density $\lambda$ (red) is obtained by solving \eqref{eq:cvx_average}. The bound (blue) is obtained using \eqref{eq:upper_bound}.
%\label{fig:dist_bound_Gaussian}  }
%\end{center}
%\end{figure}
%
\begin{figure}
\begin{center}

\begin{tikzpicture}[scale = 1]
\begin{axis}[
width=8cm, height=6cm,
xmin = 0, xmax=2, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 10,
samples=1, 
xlabel= {$\sigma/\sigma_\theta$},
%xtick={-0.5,0,0.5},
%xticklabels={-$$, 0, $b$},
ytick={0,1.5708,5},
yticklabels={0,$\pi/2$,5},
ylabel = {$R_{\pi}^\star/\sigma^2$},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {../Figs/unif_Bayes_Risk.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {../Figs/unif_Bayes_Risk.csv};
\addplot[color = black, dashed] {3.14159 / 2};
\end{axis}
\end{tikzpicture}
\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \mathcal N(\theta, \sigma^2)$under an optimal threshold distribution $\lambda^\star$ for $\pi$ the uniform distribution over $\Theta = [-0.5,0.5]$. 
%
%versus $\sigma/\sigma_\theta = 2\sqrt{3}\sigma$.
The distribution $\lambda^\star$ is the minimizer of \eqref{eq:cvx_average}. It is illustrated for various cases in Fig.~\ref{fig:opt_density}. The dashed curve represents the upper bound \eqref{eq:upper_bound}. 
\label{fig:dist_bound_uniform}  }
\end{center}
\end{figure}

As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \mathcal N(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution. In this case, the ML estimator reduces to the estimator $\hat{\theta}_n$ of \eqref{eq:estimator_naive}. As the following proposition shows, the Bayes risk for this choice of $\lambda$ is maximal, and thus provides an upper bound on the Bayes risk under any $\lambda$. 
 \eqref{eq:cvx_average}. 
\begin{prop}\label{prop:upper_bound}
For any prior $\pi(d\theta)$ and $\theta_0$ in the support of $\eta(x)$ we have
\begin{equation} 
\label{eq:upper_bound}
R_\pi^\star  \leq 
 \int \frac{\pi(d\theta)}{\eta \left( \theta_0 - \theta \right)},
\end{equation}
Furthermore, assuming that $\theta_0 = \mathbb E \theta$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
\begin{equation}
\label{eq:bound_Taylor}
R^\star_\pi \leq \frac{1}{4 f^2(0)} + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right) \sigma_\theta^2 + O(\sigma_\theta^3).
\end{equation}
\end{prop}
\begin{proof}
The function $x \rightarrow 1/x$ is convex for positive values, hence Jensen's inequality implies
\[
\left( \int \eta \left( t-\theta\right) \lambda(dt) \right)^{-1}  \leq \int  \frac{ \lambda(dt)}{ \eta \left( t-\theta\right)  }. 
\]
Therefore, the expected value of $K^{-1}(\theta)$ satisfies
\begin{align}
\mathbb E  \frac{1}{K(\theta)}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
\end{align}
The bound \eqref{eq:upper_bound} is obtained by taking $\lambda$ to be a mass distribution at any $\theta_0$ in the support of $\eta(x)$. Finally, \eqref{eq:bound_Taylor} is obtained by expanding $1/\eta(x)$ to a third order Taylor series around zero
%\[
%1/\eta(x) = \frac{1}{4f^2(0)}  + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right)  x^2 + O(x^3),
%\]
and taking its expectation with respect to $\pi$ at $x=\theta_0-\theta$. 
\end{proof}
We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so taking $\theta_0 = \mathbb E \theta$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$. The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $K^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.

\begin{example} \label{ex:bound}
Consider the case $P_X = \mathcal N(\theta, \sigma^2)$. The bound in \eqref{eq:bound_Taylor} implies 
\[
\frac{R^\star_\pi}{\sigma^2}  \leq \frac{\pi}{2} + \left( \frac{\pi}{2} -1 \right) \left( \frac{ \sigma_\theta}{\sigma} \right)^2 + O \left(  \frac{\sigma_\theta} { \sigma} \right)^3. 
\]
It follows that the ARE approaches its maximal value of $2/\pi$ whenever $\sigma_\theta/\sigma$ is small. The exact value of \eqref{eq:upper_bound} in this case, as well as the Bayes ARE with the optimal threshold density $\lambda^\star$ for a uniform $\pi$, are illustrated in Fig.~\ref{fig:dist_bound_uniform}. 
%i.e., each encoder simply reports "$1$" or "$-1$" whenever $X_i$ is larger or smaller than $\theta_0$, respectively. Intuitively, an accurate estimation of $\theta$ in this case is possible only if a sufficient mix of ''$1$''s and ''$-1$''s is obtained from the sample. When $\sigma_\theta^2$ is high compared to $\simga^2$, one of the events $"1"$ or "$-1"$ becomes too rare to
\end{example}

% The following proposition implies that this bound is always tight as $\sigma / \sigma_\theta$ goes to infinity.
%\begin{prop} \label{prop:asymp}
% For any prior $\pi(\theta)$ for which
%\[
%\int \frac{\pi(d\theta)}{\eta \left(\theta \right)} < \infty,
%\]
%we have 
%\begin{align}
%\label{eq:asymp}
%\mathbb E [1/K(\theta)] = \frac{\pi}{2} + \left( \frac{\pi}{2} - 1\right) \left(\frac{\sigma_\theta}{\sigma} \right)^2 + o \left(\frac{1}{\sigma} \right)^3. 
%\end{align}
%as $\sigma_\theta / \sigma \rightarrow 0$. 
%\end{prop}
%\begin{proof}
%It is enough to prove that  \eqref{eq:asymp} holds for the upper bound \eqref{eq:upper_bound}. First note that the condition in the proposition implies that all the moments of $\pi(\theta)$ exists, and in particular its second and third. The results follows by expanding the function $1/\eta(x)$ in a power series around zero as
%\[
%1/\eta(x) = \frac{\pi}{2} + \left(\frac{\pi}{2}-1 \right) x^2 + o(x^3).
%\]
%\end{proof}

\section{Conclusions \label{sec:conclusions}}
We considered the MSE risk in estimating the mean of a normal distribution from a sequence of bits obtained by encoding each sample from the distribution using a single bit. Under an adaptive encoding of the samples, we showed that the no estimator can attain asymptotic MSE or relative efficiency larger than that of the median of the samples. We also showed that this lower bound is tight by presenting an adaptive estimation procedure from this bit sequence that is as efficient as the median. We also consider a one-step optimal scheme that minimizes the MSE given any set of previously obtained bits. Numerical simulations shows that the one-step optimal scheme attains the optimal relative efficiency for the normal distribution. 
\par
In the distributed setting, we considered the estimation from threshold detection under the assumption that the empirical distribution of the threshold values converges to a probability distribution. For this setting, we showed that the maximum likelihood estimator is local asymptotically minimax, and that the relative efficiency of this estimator is strictly smaller than that of the sample median.  \\

%Interesting extension of our setting is to the case of estimating a $d$ dimensional vector of parameters rather than a scalar. An interesting questions in this extension is behavior of the MSE as a function of $d$. 
%{\color{red} Shamir \cite{Shamir} showed that in hide-and-seek hypothesis testing problem, bitrate constraint may lead to a significant reduction in detection performance compared to the unrestricted case. This result is then applied to online learning, stochastic optimization and sparse PCA. Shamir's results shows that the penalty is in the dimension ($d/R$ instead of $lod(d)$). In our setting the dimension is $1$. \\}

%\section*{ACKNOWLEDGMENT}
%This research is supported in parts by...
%Tsachy Weissman, Stefano Rini, Robert Gray.

\appendix

\section{Proofs \label{app:proofs}}
This appendix contains the proofs of Proposition~\ref{prop:eta}, Theorems \ref{thm:adpative_lower_bound}, \ref{thm:sgd}, \ref{thm:opt_one_step}, and \ref{thm:LAN}.

\subsection{Proof of Proposition~\ref{prop:eta}}
(i) Since $f(x)$ is log-concave, so does $F(x)$. There exists $h(x)$ that is non-decreasing, concave, twice differntiable, such that $F(x) = e^{h(x)}$. In addition, $f(x) = h'(x)F(x)$ so $h'(x) \geq 0$, and $h'(x)$ is decreasing since $h''(x) \leq 0$ because $h(x)$ is concave. In fact, $h'(x) = f(x)/F(x)$ is non-constant for any $x$ in the support of $f(x)$, so $h'(x)$ is strictly decreasing in this support. It easily verified that
\[
\eta(x) = h'(x) h'(-x).
\]
It follows that $\eta(x)$ is symmetric. We now show that $\eta(x)$ is decreasing for $x>0$. Let $0<x_1 < x_2$. Consider
\begin{align}
& \eta(x_2) - \eta(x_1) = h'(x_2)h'(-x_2) - h'(x_1)h'(-x_1) \nonumber \\
&  =h'(x_2)h'(-x_1) \left(\frac{h'(-x_2)}{h'(-x_1)} - \frac{h'(x_1)}{h'(x_2)}  \right). \label{eq:eta_proof}
\end{align}
Now, because $h'(x)$ is decreasing, we have that $h'(x_1) \geq h'(x_2)$ and $h'(-x_2) \geq  h'(-x_1)$. If follows that the brackets in the RHS of \eqref{eq:eta_proof} are negative, whereas $h'(x_2) h'(-x_1)$ is non-negative since $h'(x)$ is non-negative. Hence $\eta(x_2) \leq \eta(x_1)$. It follows that $\eta(x)$ is a monotone decreasing function for $x>0$. It is left to show that it is strictly decreasing for $x>0$ in the support of $f(x)$. Since $h'(x)$ is strictly decreasing, $\eta(x)$ may be constant only for $x>0$ for which $h'(x)/h'(-x)$ is a constant. But for all such $x$s, $h'(x)$ is strictly increasing, $h'(-x)$ is strictly decreasing, and thus $h'(x)/h'(-x)$ is strictly increasing. \par
(ii) Because $F(x)$ is differentiable, for any $a \in \mathbb R$ there exists $a\leq c \leq x$ such that 
$F(x) = F(a) + f(c) (x-a)$. For $a=0$, and using the fact that $f(x)$ is non-increasing for $x>0$ we have
\[
\frac{f(x)}{F(x)} = \frac{f(x)}{0.5 + f(c) x }  \leq \frac{f(x)}{f(c)} \frac{1}{x} \leq \frac{1}{x}.  
\]
From symmetry of $f(x)$ we get that $f(-x)/F(-x) \leq 1/x$ for $x>0$. Finally, noting that $h(x)\rightarrow 0$ as $x\rightarrow \infty$, we conclude that for $x>0$, 
\[
\eta(x) = h'(-x)h'(x) \leq \frac{h(x)}{x} \leq \frac{1}{x}. 
\]

\subsection*{Proof of Theorem~\ref{thm:adpative_lower_bound}}

We first prove the following two lemmas:
\begin{lem} \label{lem:bound_intervals}
Let $f(x)$ be a log-concave, symmetric, and differentiable pdf. Denote by $F(x)$ the corresponding CDF. Then for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, we have 
\begin{equation}
\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)  } \leq 4f^2(0). \label{eq:bound_intervals}
\end{equation}
\end{lem}

\begin{lem} \label{lem:fisher_bound}
Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$. Assume that for a Borel measurable $A$, 
\[
M(X) = \begin{cases} 1,& X \in A, \\
-1, & X \notin A.
\end{cases}
\]
Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $4f^2(0)$.
\end{lem}

\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals}} 
We now use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:bound_intervals} is bounded from above by $\eta(0)$. \par
The case $n=1$ it follows from Proposition~\ref{prop:eta}. 
Assume now that \eqref{eq:bound_intervals} holds for all integers up to some $n = N-1$ and consider the case $n = N$. The maximal value of the LHS of \eqref{eq:bound_intervals} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
\begin{align*}
& g(x_1,\ldots, x_N) \triangleq 2 \log \left(  \sum_{k=1}^{N} (-1)^{k+1} f(x_k) \right) - \\
&  \log
\left( \sum_{k=1}^N (-1)^{k+1} F(x_k) \right)
-\log \left(1 -  \sum_{k=1}^N (-1)^{k+1} F(x_k) \right) \\
& = 2 \log \delta_N - \log \Delta_N - \log \left(1 - \Delta_N  \right),
\end{align*}
where we denoted $\delta_N \triangleq \sum_{k=1}^{N} (-1)^{k+1} f(x_k)$ and $\Delta_N =  \sum_{k=1}^N (-1)^{k+1} F(x_k)$. The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
\[
\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(-1)^{k+1} f(x_k)}{1-\Delta_N }.
\]
We conclude that the gradient of $g$ vanishes if and only if
\begin{equation}
\label{eq:gradient_zero}
\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
\end{equation}
From the case $n=1$ and for $x$ in the support of $f(x)$, we have
\[
\frac{f'(x)}{f(x)} = h''(x)+\left(h'(x)\right)^2 < 0 . 
\]
As a result, $\frac{f'(x)}{f(x)}$ is one to one and \eqref{eq:gradient_zero} implies $x_1 = \ldots = x_N$. If $N$ is odd then for $x_1=\ldots =x_N$ we have that the LHS of \eqref{eq:bound_intervals} equals $\eta(x_1)$ which was shown to be smaller than $\eta(0)$. If $N$ is even, then for any constant $c$ the limit of the LHS of \eqref{eq:bound_intervals} as $(x_1,\ldots,x_N)\rightarrow (c,\ldots,c)$ exists and equals zero. Therefore, the maximum of the LHS of \eqref{eq:bound_intervals} is not attained at the line $x_1=\ldots=x_N)$. We now consider the possibility that the LHS of \eqref{eq:bound_intervals} is maximized at the borders, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches plus or minus infinity. For simplicity we only consider the cases where $x_N$ goes to minus infinity or $x_1$ goes to plus infinity (the general case where the first $m$ coordinates goes to infinity or the last $m$ to minus infinity is obtained using similar arguments). Assume first $x_N \rightarrow -\infty$. Then the LHS of \eqref{eq:bound_intervals} equals
\begin{align*}
\frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^2} 
{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right) } ,
\end{align*}
which is smaller than $\eta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then the LHS of
\eqref{eq:bound_intervals} equals
\begin{align*}
& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^2} 
{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right) }  \\
& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^2} 
{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right) },
\end{align*}
where $x'_{m} = x_{m+1}$. The last expression is also smaller than $\eta(0)$ by the induction hypothesis. \QEDA \\

\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
The Fisher information of $M$ with respect to $\theta$ is given by
\begin{align}
I_\theta & =  \mathbb E \left[ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta \right] \nonumber \\
& = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\ 
& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\ 
& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
\end{align}
where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$. Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that 
\[
\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
\]
which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$. It is therefore enough to proceed in the proof assuming that $A$ is of the form
\[
A = \cup_{j=1}^k (a_j,b_j),
\]
with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
\begin{align*}
\mathbb P(M_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
\end{align*}
so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
\begin{align}
& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
& \times \frac {1} 
{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
\label{eq:lemma_J}
\end{align}
It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $4f^2(0)$.  \QEDA \\

We now consider the proof of Theorem~\ref{thm:adpative_lower_bound}. In order to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$, we first note that without loss of generality, each message $M_i$ can is of the form
\begin{equation}
\label{eq:general_messages}
M_i = \begin{cases}
X_i \in A_i & 1, \\
X_i \notin A_i & -1,
\end{cases} 
\end{equation}
where $A_i \subset \mathbb R$ is a Borel measurable set. Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = M^{-1}(1)$. Consider the conditional distribution $P({M^n|\theta})$ of $M^n$ given $\theta$. We have 
\begin{align}
P\left( M^n | \theta \right) & =  \prod_{i=1}^n P\left(M_i | \theta, M^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
\end{align}
where $P\left(M_i =1 | \theta, M^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $M^n$ with respect to $\theta$ is given by 
\begin{align}
I_\theta(M^n) = \sum_{i=1}^n I_\theta (M_i|M^{i-1}),
\label{eq:fisher_information}
\end{align}
where $I_\theta (M_i|M^{i-1})$ is the Fisher information of the distribution of $M_i$ given $M^{i-1}$. From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (M_i|M^{i-1}) \leq 4f^2(0)$. The Van Trees inequality \cite{van2004detection, gill1995applications} now implies 
\begin{align*}
\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(M^n) + I_0} \\
& = \frac{1}{ \sum_{i=1}^n I_\theta (M_i | M^{i-1} ) + I_0} \\
& \geq \frac{1}{ 4f^2(0) n + I_0}.
\end{align*}

\QEDA

\subsection*{Proof of Theorem~\ref{thm:sgd}}
The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}. Specifically, (i) in Theorem~\ref{thm:sgd} follows from the following simplified version of \cite[Thm. 4]{polyak1992acceleration}:
\begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
Let 
\[
X_i = \theta + Z_i,\quad i=1,\ldots,n,
\]
where the $Z_i$s are i.i.d. with zero means and finite variances. Define
\begin{align*}
\theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
\hat{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
\end{align*}
where in addition, assume the following: 
\begin{enumerate}
\item[(i)] There exits $K_1$ such that $\left| \varphi(x) \right| \leq K_1(1+|x|)$ for all $x\in \mathbb R$.
\item[(ii)] The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions \eqref{eq:conditions1}.
\item[(iii)] The function $\psi(x) \triangleq \mathbb E \varphi(x+Z_1)$ is differentiable at zero with $\psi'(0)>0$, and satisfies $\psi(0)=0$ and $x\psi(x) >0$ for all $x\neq 0$.
Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
\begin{equation}
\label{eq:Polyak_Juditsky_cond3}
\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
\end{equation}
\item[(iv)] The function 
$\chi(x) \triangleq \mathbb E \varphi^2(x+Z_1)$ is continuous at zero. 
\end{enumerate}
Then $\hat{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}(\hat{\theta}_n - \theta)$ converges in distribution to $\mathcal N(0,V)$, where
\[
V = \frac{ \chi(0)} {\psi'^2(0)}. 
\]
\end{thm}

Using the notation above, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have that $\chi(x) = \mathbb E \sgn^2(x+Z_1) = 1$, so $\chi(0) = 1$. In addition,
\begin{align*}
\psi(x) & = \mathbb E \sgn(x+ Z_1) = \int_{-\infty}^\infty \sgn(x+z) f(z) dz \\
& = \int_{-x}^\infty f(z) dz -\int_{-\infty}^{-x} f(z) dz. 
\end{align*}
Using the symmetry of $f(x)$ around zero, it follows that $\psi'(x) = 2f(x)$ and thus $\psi'(0) = 2f(0)$. It is now easy to verify that the rest of the conditions in Thm.~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$. Since 
\[
\frac{\chi(0)}{\psi'^2(0)} = \frac{1}{4 f^2(0)},
\]
Thm.~\ref{thm:sgd}-(i) follows from Thm.~\ref{thm:polyak_juditsky}.  \\

In order to prove Thm.~\ref{thm:sgd}-(ii), we consider:
\begin{thm}{ \cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
Let
\begin{align} \label{eq:polyak_new_measurements}
\begin{cases}
U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = g'(U_{n-1})+Z_n \\
\bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
\end{cases}
\end{align}
Assume that the function $g(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative. In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \mathbb R$. Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution for which the Fisher information exits. Let $\psi(x)$ and $\chi(x)$ be defined as in Thm.~\ref{thm:polyak_juditsky}-(iii) and satisfies the conditions there. Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$, 
and there exits $K_3$ such that 
\[
\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] \leq K_3(1+|x|^4). 
\]
Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions  \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
\[
V_n \triangleq \mathbb E \left[ \left(\bar{U}_n-x^\star \right)^2 \right] = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
\]
\end{thm}

We now use Thm.~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = -\sgn(-x)$, $Z_n = \theta-X_n$ and $U_n = \theta_n$. From \eqref{eq:polyak_new_measurements} we have
\begin{align*} 
\theta_n & = \theta_{n-1} + \gamma_n \sgn(\theta-\theta_{n-1} - Z_n )  \\
& = \theta_{n-1} + \gamma_n \sgn(X_n-\theta_{n-1} ),
\end{align*}
so the estimator $\hat{\theta}_n$ defined by $\hat{\theta}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
\[
\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] = 1 \leq K_3(1+|x|^4)
\]
for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
the conditions in Thm.~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof. In particular, $\psi'(0) = (2f(0))^{-2}$. Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$. Thm.~\ref{thm:polyak_new} implies 
\[
n V_n = \mathbb E \left[ \left(\hat{\theta}_n-\theta \right)^2 \right]  = \frac{1}{4 f^2(0)} + o(1).
\]
\QEDA

\subsection*{Proof of Theorem~\ref{thm:opt_one_step}}
In this subsection we prove Lemmas~\ref{lem:adaptive} and~\ref{lem:unique} which together implies Theorem~\ref{thm:opt_one_step}.

\subsubsection*{Proof of Lemma \ref{lem:adaptive}}
Any single-bit message $M(u) \in \{0,1\}$ is characterized by two decision region $A_1 = M^{-1}(1)$ and $A_{-1} = M^{-1}(-1)$, so that $\mathbb E \left[ U | M(U) \right]$ assumes only two values: $\mu_1 = \mathbb E \left[ U | M(U) = 1 \right]$ and $\mu_{-1} = \mathbb E \left[ U | M(U) = -1 \right]$. We claim that a necessary condition for $M(u)$ to be optimal is that the sets $A_1$ and $A_{-1}$ are the Voronoi sets on $\mathbb R$ corresponding to the points $\mu_1$ and $\mu_{-1}$, respectively, modulo a set of measure $P(du)$ zero. Indeed, assume by contradiction that for such an optimal partition there exists a set $B \subset A_{1}$ with $\mathbb P (U \in B) >0$ such that $\left( b-\mu_{1} \right)^2 > \left( b- \mu_{-1} \right)^2$. The expected square error in this partition satisfies:
\begin{align*}
& \int_{\mathbb R} \left( u - \mathbb E[U|M(u)]  \right)^2 P(du) =  \\
& \int_{A_1} (u- \mu_1)^2 P(du) + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
& = \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_1)^2 P(du) \\
& \quad + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
& > \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_2)^2 P(du) \\
& \quad + \int_{A_{-1}} (u- \mu_{-1})^2 P(du),
\end{align*}
so the partition $A_1' = A_1 \setminus B$, $A_{-1}' = A_{-1} \cup B$ attains lower error variance which contradicts the optimality assumption and proves our claim. It is evident that Voronoi partition of the real line corresponding to $\mu_1$ and $\mu_{-1}$ is of the form $A_{-1} = (-\infty,\tau)$, $A_{1} = (\tau, \infty)$ where the point $\tau$ is of equal distance from $\mu_1$ and $\mu_{-1}$, namely $\tau = \frac{\mu_1 + \mu_{-1}}{2}$. From these two conditions (which are a special case of the conditions derived in \cite{1056489} for two quantization regions) we conclude that $\tau$ must satisfy the equation
\[
2 \tau = \frac{\int_{\tau}^\infty u P(du)}{\int_{\tau}^\infty P(du)} + \frac{\int_{-\infty}^{\tau} u P(du)}{\int_{-\infty}^{\tau} P(du)}.
\] 
\QEDA

\subsubsection*{Proof of Lemma \ref{lem:unique}} 
Any solution to \eqref{eq:lem_fixed_point} is a solution to $h^+(x) = h^-(x)$ where
\[
h^+(x) = \frac{\int_x^\infty uf(u)du}{\int_x^\infty f(u)du} - x 
\]
and
\[
h^-(x) = x - \frac{\int_{-\infty}^x uf(u)du}{\int_{-\infty}^x f(u)du}.
\]
We now prove that $h^+(x)$ is monotonically decreasing while $h^-(x)$ is increasing, so they meet at most at one point. The derivative of $h^-(x)$ is given by
\begin{equation} 
\label{eq:one_step_proof_derivative}
1 - \frac{ f(\tau) \int_{-\infty}^\tau f(x) (\tau-x)dx } {\left( \int_{-\infty}^\tau f(x) dx \right)^2}.
\end{equation}
Denote $F(x) = \int_{-\infty}^x f(u)du$. Using integration by parts in the numerator and from the fact that $\lim_{\tau \rightarrow -\infty}  \tau \int_{-\infty}^\tau f(x) dx = 0$, the last expression can be written as
\[
1- \frac{ f(\tau) \int_{-\infty}^\tau F(x) dx}
 {\left( F(\tau) \right)^2}.
\]
Log-concavity of $f(x)$ implies log-concavity of $F(x)$, so that we can write $F(x) = e^{g(x)}$ for some concave and differentiable function $g(x)$. Moreover, we have $f(x) = g'(x)e^{g(x)}$ where, by concavity of $g(x)$, the derivative $g'(x)$ of $g(x)$ is non-increasing. With these notation we have
\begin{align*}
\frac{ f(\tau) \int_{-\infty}^\tau F(x) dx}
 {\left( F(\tau) \right)^2} & = \frac{g'(\tau)e^{g(\tau)} \int_{-\infty}^\tau e^{g(x)}dx }{ e^{2g(\tau)} } \\
 & = e^{-g(\tau)} \int_{-\infty}^\tau g'(\tau) e^{g(x)} dx  \\
 & \leq e^{-g(\tau)} \int_{-\infty}^\tau g'(x) e^{g(x)} dx \\
 & = e^{-g(\tau)} F(\tau) = 1.
\end{align*}
(where the second from the last step follows since $g'(x) \leq g'(\tau)$ for any $x\leq \tau$). If follows that \eqref{eq:one_step_proof_derivative} is non-negative and thus $h^-(x)$ is monotonically increasing. Since
\[
h^+(-x) = x - \frac{ \int_{-\infty}^{x} uf(-u)du}{ \int_{-\infty}^x f(-u) du }, 
\]
the fact that $h^+(x)$ is monotonically decreasing follows from similar arguments. Moreover, since the derivatives of $h^+(x)$ and $h^-(x)$ never vanish at the same time over any open interval, their difference cannot be constant over any interval. Finally, since 
\begin{align*}
 \lim_{x\rightarrow -\infty} h^+(x) =  \lim_{x\rightarrow \infty} h^-(x)
\end{align*}
and since non of these functions are constant, monotonicity of $h^+(x)$ and $h^-(x)$ implies that they must meet at some $x\in \mathbb R$. \QEDA

\subsection*{Proof of Theorem~\ref{thm:LAN}}
We will prove that $P_\theta(m_i) = \mathbb P(M_i = m_i)$, $\i=1,\ldots,n$ is a local asymptotic normal (LAN) family  with \emph{precision} parameter $K(\theta)$. The statements in the theorem then follows from the local asymptotic minimax theorem of LAN families \cite{van2000asymptotic}. \\

The probability mass distribution of $M^n$ is given by
\[
P_\theta(m^n) =  \prod_{i=1}^n F \left( m_i (t_i - \theta)\right), \quad m^n \in \{-1,1\}^n.
\]
Consider the log-likelihood ratio under a sequence of local alternatives $\theta' = \theta + h/\sqrt{n}$ for some $h\in \mathbb R$:
\begin{align}
\log \frac{ P_{\theta + \frac{h}{\sqrt{n}}}(m^n)} { P_\theta (m^n) }& =  \sum_{i=1}^n \log \left( F \left( m_i (t_i - \theta - h/\sqrt{n} ) \right)\right)  - \sum_{i=1}^n \log \left( F \left( m_i (t_i - \theta) \right) \right). \label{eq:LAN_proof1}
\end{align}
Since $f(x)$ is differentiable, $\log F(x)$ is twice differentiable and we may write
\[
\log F(x+t) = \log F(x) + \frac{f(x)}{F(x)}h - \frac{t^2}{2}\left( \frac{f'(x)}{F(x)} - \frac{f^2(x)}{F^2(x)} \right) + o(t^2).
\]
Therefore, \eqref{eq:LAN_proof1} can be written as
\[
- h \sum_{i=1}^n  \frac{m_i}{\sqrt{n} }  \frac{ f \left(m_i (t_i-\theta) \right)} {F \left( m_i (t_i-\theta) \right) }  - \frac{h^2}{2 n} \sum_{i=1}^n  \left( \frac{f' \left(m_i (t_i-\theta) \right) }{F\left(m_i (t_i-\theta)\right) }- \frac{ f^2\left(m_i (t_i-\theta) \right)}{F^2\left(m_i (t_i-\theta) \right)}   \right) + o(1/n)
\]

The proof is completed by proving the following two lemmas:
\begin{lem} \label{lem:LAN1}
For $i=1,\ldots,n$ denote 
\[
U_i = -M_i \frac{ f \left( M_i (t_i - \theta) \right)}{ F \left( M_i (t_i - \theta)\right) }. 
\]
Then 
\[
\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0, K(\theta) \right). 
\]
\end{lem}
\begin{lem} \label{lem:LAN2}
For $i=1,\ldots,n$ denote
\[
V_i =  -\left[ \frac{f' \left(M_i (t_i-\theta) \right) }{F\left(M_i (t_i-\theta)\right) }- \frac{ f^2\left(M_i (t_i-\theta) \right)}{F^2\left(M_i (t_i-\theta) \right)} \right] .
\]
Then 
\[
\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} K(\theta). 
\]
\end{lem}

\subsubsection*{Proof of Lemma~\ref{lem:LAN1}} 
First note that 
\begin{align*}
\mathbb E  [U_i] & = \mathbb E\left[ \mathbb E  [U_i|M_i] \right] \\
& =  -\frac{f(t_i-\theta)}{F(t_i-\theta)} \mathbb P (M_i=1) + \frac{f(\theta-t_i)}{F(\theta-t_i)} \mathbb P (M_i=-1) \\
& = -f(t_i-\theta) + f(\theta-t_i) = 0.
\end{align*}
In addition,
\[
\mathbb E U_i^2 = \frac{ f^2 \left( t_i-\theta \right) } { F \left( t_i-\theta \right) \left(1- F \left( t_i-\theta \right) \right)},
\]
and therefore
\[
\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 \rightarrow K(\theta).
\]

We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition for his version of the central limit time: for any $\delta>0$ we have that 
\[
\mathbb E \left| U_i \right|^{2+\delta} = \left( \frac{f^{2+\delta} \left(t_i-\theta \right)  }{F^{2+\delta} \left( t_i-\theta \right)} + \frac{f^{2+\delta} \left(t_i-\theta \right)  }{1-F^{2+\delta} \left(t_i-\theta\right)} \right),
\]
and
\begin{equation}
\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} } { \left( \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta} = 
\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E U_i^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
\label{eq:Lyaponov}
\end{equation}
The functions $\log F(x)$ and $\log (1-F(x)) = \log F(-x)$ are differentiable, so that $f(x)/F(x)$, $f(x)/(1-F(x))$, and hence $\left(f(x)/F(x)\right)^{2+\delta}$ and $\left(f(x)/(1-F(x)) \right)^{2+\delta}$ are integrable. As $n$ goes to infinity, we have
\[
\frac{1}{n}\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta}  \rightarrow  \int \left( \frac{ f^{2+\delta} \left(t-\theta\right)}{F^{2+\delta}\left(t-\theta\right)} + \frac{ f^{2+\delta} \left(t-\theta\right)}{1-F^{2+\delta} \left(t-\theta\right)} \right) \lambda(dt),
\]
from which we conclude that the numerator in \eqref{eq:Lyaponov} goes to zero. Since the denumerator in \eqref{eq:Lyaponov} goes to $K^\delta(\theta)$, the entire expression goes to zero and hence Lyaponov's condition is satisfied. From Lyaponov's central limit theorem we conclude that 
\[
\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0,K(\theta) \right). 
\]
\QEDA

\subsubsection*{Proof of Lemma~\ref{lem:LAN2}}

We have:
\begin{align*}
\mathbb E V_i  & = \left[ \frac{ f^2\left(t_i-\theta \right)}{F\left( t_i-\theta \right)} - f' \left(t_i-\theta \right)  \right] 
+ \left[ \frac{ f^2\left(\theta-t_i \right)}{F\left( \theta - t_i \right)} - f' \left( \theta - t_i \right) \right] \\
& = \frac{f^2(\theta - t_i)}{F(\theta-t_i)F(t_i-\theta)} = \eta(\theta - t_i).
\end{align*}
where above we used the facts  $f'(-x) = -f'(x)$ and $F(x)+F(-x)=1$. We conclude that:
\[
\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =  \frac{1}{n} \sum_{i=1}^n  \frac{f^2\left( t_i-\theta \right)} { F \left( t_i - \theta \right)\left(1-F \left( t_i - \theta \right) \right)} \rightarrow K(\theta).  
\]
Finally, it follows from Kolmogorov's law of large numbers (e.g. \cite[Thm. 10.2.3]{sen1994large}) that
\[
\frac{1}{n} \sum_{i=1}^n \mathbb E V_i \overset{a.s.}{\rightarrow} K(\theta). 
\]
\QEDA

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,/Users/Alon1/LaTex/bibtex/sampling}

\section{Related Results in Source Coding}
The estimation problem we consider can be seen as the quantization, compression or encoding of the samples, and the  decoding of the parameter $\theta$ from the encoded version of the sample. Therefore, this problem is closely related to various setting in coding and information theory. The goal of this section is to illustrates this connection and review related results that are relevant in our case.

%As opposed to the aforementioned line of works, we focus on estimation of samples taken from a single distribution in the finite blocklength performance. We are interested in particular in addition restrictions on the communication and information sharing between the encoders. For example, our main focus is the case where the observer must communicate a single bit upon drawing from the distribution. This is in contrast to the asymptotic setting where the observer can encode the outcome of $n$ draws at once using a single $n$ bit message. Alternately, such setting can be seen as having $n$ different observers, each is capable of observing a single realization and transmit a single bit.

%{\color{red} The Van Trees inequality was extended to the estimation of multiple parameters in \cite{bobrovsky1987}. It is closely related with the }

\subsection{Statistical Inference under Communication Constraints}
The works \cite{han1987hypothesis, zhang1988estimation, 720540} consider various problems of statistical inference under multiterminal lossy compression. In the setting of \cite{han1987hypothesis, zhang1988estimation, 720540}, each terminal $I$ observes $n$ samples from the distribution and is allotted $nR_i$ bits to communicate its estimate.% Consequently, our case (iii) is obtained from this setting by taking $n=1$, $R_i=1$, and number of terminals grow with $n$. 
The main focus of these works is the difference between inference with communication constraint and the unconstrained vanilla statistical estimation setting, as the number of samples $n$ goes to infinity subject to a total finite rate constraint. Our case (i) can be seen as a special case of this setting where with a single terminal and $R_1 = 1$. However, as explained in \cite[Sec. III]{720540}, in this setting the unconstrained inference performance is always attained when all samples are taken from the same distribution. Indeed, in an i.i.d setting the \emph{type} of the sample \cite{csiszar1998method} is a sufficient statistics for any estimation task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples. For this reason, attention is given in these works to inference problems involving multiple distributions observed at different locations, hence the name \emph{multiterminal}.

\subsection{Sigma-Delta Encoding}

and covariance function \cite[Eq. 25]{53738}
\[
R(k) = \mathbb E M_{n+k} M_n = \theta^2 + O \left( \frac{1}{\sigma \sqrt{ k} } \right). 
\]
{\color{red} This is not enough to deduce convergence. Need to go over the paper and check if rate of convergence can be deduced. Also do simulations BEFORE that. \\

What is the error in estimating the mean of stationary ergodic process ? 
}
Since the SDM is a special case of the sequential scheme, we conclude that the MSE of any SDM with a noisy DC signal is bounded from below by $n^{-1} \sigma^2 \pi/2 $.

%Even with such arguably simple setting, we will see that the performance limit in the estimating task based on single bit observations provides an interesting setting for discussion that bridges classical works in statistics, coding theory, information theory and optimization.

\subsection*{Source coding}
With a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample. Setting (ii) includes as a special case the sigma-delta modulation (SDM) analog-to-digital conversion scheme with a constant input $\theta$ corrupted by Gaussian noise $Z_i$, as was considered in \cite{53738}. While it was shown there that the output of the modulator converges to the true constant input, the rate of this convergence was not analyzed and cannot be derived directly from the results of \cite{53738}. As a corollary from the results in this paper we conclude that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations. Finally, the remote multiterminal source coding setting of \cite{berger1996ceo} corresponds to the case of $n$ rate-constrained encoders, each observing a noisy version of an information source. The difference between this setting and ours is that in ours the parameter of interest is not an information source. By assuming a prior distribution on this parameter, the CEO provides a lower bound on the estimation error in the fully distributed setting (iii). This lower bound can be attained if we were to consider the average error in multiple independent realizations of our problem rather than a single realization as we do here. \\

\end{document}

\begin{comment}
\subsection{Remote Multiterminal Source Coding}
The remote multi-terminal lossy source coding problem (a.k.a the CEO problem) \cite{berger1996ceo}, considers $n$ encoders (agents), each has access to a corrupted version of a source signal, transmit at rates $R_1,\ldots,R_n$ to a central estimation unit. The distributed estimation setting (iii) corresponds to a single round of communication in the CEO setting, where the $i$th agent observes 
\begin{equation}
\label{eq:Gaussian_channel}
X_i = \theta + Z_i,
\end{equation}
and has $R_i=1$ bits to transmit this observation. Note, however, that in the CEO setting each encoder observes multiple number, say $k$, of independent samples $\theta \sim \pi(\theta)$ through the channel \eqref{eq:Gaussian_channel}, and not just one sample as in our setting. In general, in the CEO setting each encoder is allowed $kR_i$ bits to represent its $k$ samples. One possible strategy of the encoder is to send $k$ single bit messages, each of which is only a function of its $k$th observation.  
%the minimal MSE distortion of the CEO provides a lower bound for the MSE in the distributed encoding scheme. 
As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise of variance $\sigma^2$ provides a lower bound on the MSE distortion in estimating $\theta$. Moreover, the difference between this lower bound and the actual MSE in our setting would indicate the importance of coding over blocks consisting of multiple independent realizations of  in our joint estimation and communication problem. \par
%Note that when multiple realization of $\theta$ are involved, the prior distribution $P_\theta$ plays a significant role in the overall MSE, whereas in our case we expect the final distortion to be independent of the actual prior distribution as in the two schemes in the sequential case. \\
A closed-form expression for CEO under quadratic distortion is known only for the case where the sequence to described by the encoders is sampled from a Gaussian distribution \cite{prabhakaran2004rate}. By using the characterization of the minimal CEO distortion as the number of terminals goes to infinity, we conclude the following result:
\begin{prop} \label{prop:ceo_lower_bound}
Assume that $\pi(\theta)$ is the normal distribution. Then any estimator $\hat{\theta}_n$ of $\theta$ in the distributed setting satisfies
\[
\lim_{n\rightarrow \infty}  n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3n}.
\]
\end{prop}
\begin{proof}
We consider the following expression from \cite[Eq. 10]{chen2004upper} that provides the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots R_L$:
\begin{equation} \label{eq:ceo_optimal_sumrate}
R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
\end{equation}
Assuming $R_\Sigma = n$ and $L=n$ we get
\begin{equation} \label{eq:ceo_optimal_sumrate}
n = \frac{1}{2} \log \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
\end{equation}
The value of $D^\star$ that satisfies the equation above describes the MSE in the quadratic Gaussian CEO setting under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders. Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting. By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$ we conclude that 
\[
D^\star = \frac{ \frac{4\sigma^2}{3} }{n + \frac{4 \sigma^2}{3 \sigma_\theta^2} } + O(e^{-n}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
\]
\end{proof}
We note that although the CEO lower bound was derived by the MSE attainable assuming optimal allocation a total of $n$ bits among the encoders, the same expression is from the upper bound to the CEO derived in \cite[Prop. 5.2]{KipnisRini2017}, that assumes $R_1=\ldots,R_n = 1$ rather than optimal allocation of $n$ bits among all encoders. %\[
%D_{CEO} / \sigma_\theta^2 \leq \left( 1 + \sum_{i=1}^n \frac{\sigma_\theta^2}{\sigma^2} \frac{1 - 2^{-2R_i}} {1+ \frac{\sigma_\theta^2}{\sigma^2}  2^{-2 R_i}  } \right)^{-1}
%\]
%where $\sigma_\theta^2$ is the variance of the distribution $\pi(\theta)$. Using $R_1=\ldots=R_n=1$ we get
%\[
%D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + o(n^{-1}). 
%\]

The bound provided by the CEO in Prop.~\ref{prop:ceo_lower_bound} implies that the relative efficiency in the distributed scheme is at most $4/3$. Since this number is smaller than the relative efficiency of the adaptive scheme, this proposition does not provide new information on the relative efficiency. It does, however, provides the intuition that the limiting factor in estimating $\theta$ is the strict bit-constraint and or the lack of concentration of probability distributions over blocks, rather than distributed estimation. \\

We note that the same first order expression for the CEO distortion is achieved by a particular encoding scheme derived in \cite{KipnisRini2017}, assuming rate of $1$ bits per source symbol at each encoder, i.e.,  $R_1=\ldots = R_n = 1$, rather than a total of $n$ bits on average allocated among the $n$ encoders used in the proof. Indeed, the it follows from \cite[Eq. ?]{KipnisRini2017} that the following distortion is achievable for the CEO
\[
\sigma_\theta^2 \left( 1 + \sigma_\theta^2 n \frac{3}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   = \frac{4\sigma^2+\sigma_\theta^2}{3n} + O(n^{-2} \sigma_\theta^4)). 
\]
As a result, we conclude that the above lower bound cannot be strengthen if we consider the exact distortion of the CEO with equal rate-allocation using the expression from \cite{prabhakaran2004rate}.  \\

%Comnet on appearance of $\sigma_\theta^2$ as a second order term.

\end{document}

\end{comment}

### 2018-09-06 Code/aux.py
full first draft

@@ -1,0 +1,110 @@
+#gradient descent implementation
+from scipy.special import erf
+from scipy.stats import norm
+import numpy as np
+
+
+def median(prob,x_vals) :
+    return x_vals[prob.cumsum()>=0.5][0]
+
+def sign(x) :
+    return 2*(x>0)-1
+
+def grad_descent(y, th0 = 0, g0 = 0.75) :
+    #must be  2/3 < g0 < 1
+    n = y.shape[0]
+    th_t = th0
+    th_bar = 0
+    th_hat = []
+    th_hat.append(th0)
+    for i in range(n) :
+        th_t = th_t + (i+1)**(-g0)*sign(y[i]-th_t)
+        th_bar = th_bar + (th_t-th_bar) / (i+1)
+        th_hat.append(th_bar)
+    return th_hat
+    
+def Qfunc(x) :
+    return 0.5*(1-erf(x/np.sqrt(2)))
+
+def Phi(x) :
+    return norm.cdf(x)
+
+def inv_Phi(x, sig = 1) :
+    return norm.ppf(x, loc=0, scale = sig)
+
+def phi(x) :
+    return norm.pdf(x)
+
+def bayes_adaptive(y, Amin, Amax, th_prior = None, xx = None, eps = 1e-3) :
+
+    n = y.shape[0]
+    
+    if th_prior == None : 
+        #uniform prior
+        dx = (Amax-Amin)*eps/np.sqrt(n)
+        xx = np.arange(Amin,Amax,dx)
+        th_prior = (xx<Amax)*(xx>Amin)*1.0/(Amax-Amin)*dx
+        #least favorable
+        #th_prior = (np.exp(-(xx-Amax) ** 2 * 10.) + np.exp(-(xx+Amin) ** 2 * 10. ))
+    
+    th_all = []
+    th_prior = th_prior/th_prior.sum()
+    th_hat = (xx*th_prior).sum()
+    th_all.append(th_hat) #zero information estimation
+    for i in range(n) :
+        #th_hat = median(th_prior,xx)
+        
+        M = 2*((y[i]-th_hat)>0)-1
+        th_prior = th_prior * Qfunc(M*(th_hat-xx))
+        th_prior = th_prior/th_prior.sum()
+        th_hat = (xx*th_prior).sum()
+        
+        th_all.append(th_hat)
+    return th_all
+    
+def binary_entropy(x) :
[…]

### 2018-09-06 Code/sim_script.py

@@ -1,0 +1,78 @@
+from aux import *
+import numpy as np
+import pandas as pd
+
+nMonte = 10000
+
+n = 1000
+
+Amax = inv_Phi(0.99)
+Amin = -inv_Phi(0.99)
+
+err_var_split = np.zeros(n+1)
+err_split = np.zeros(n+1)
+err_var_grad = np.zeros(n+1)
+err_grad = np.zeros(n+1)
+err_var_bayes = np.zeros(n+1)
+err_bayes = np.zeros(n+1)
+err_var_sdm = np.zeros(n+1)
+err_sdm = np.zeros(n+1)
+err_var_smp = np.zeros(n)
+err_smp = np.zeros(n)
+
+sig = 1
+
+for i in range(nMonte) :
+    th = Amin + (Amax-Amin)*np.random.rand()# uniform prior over (Amin,Amax)
+    z = sig * np.random.randn(n)
+    y = z + th
+    
+    #Split
+    split_ratio = np.sqrt(n) / n
+    th_hat_split = [split_est(y[:k], split_ratio = split_ratio, th0 = 6*(np.random.rand()-0.5), inv_PDF = inv_Phi) for k in range(n+1)]
+    err_split += th-np.array(th_hat_split)
+    err_var_split += (th-np.array(th_hat_split))**2
+    
+    #SGD
+    th_hat_grad = grad_descent(y, g0 = 0.68)
+    err_grad += th-np.array(th_hat_grad)
+    err_var_grad += (th-np.array(th_hat_grad))**2
+    
+    #Bayes
+    th_hat_bayes = bayes_adaptive(y, Amin, Amax)
+    err_bayes += th-np.array(th_hat_bayes)
+    err_var_bayes += (th-np.array(th_hat_bayes))**2
+    
+    #th_hat_sdm = sigma_delta(y,v0  = 0)
+    #err_sdm += th-np.array(th_hat_sdm)
+    #err_var_sdm += (th-np.array(th_hat_sdm))**2
+    
+    #Sample mean
+    mean_hat = np.cumsum(y) / np.arange(1,n+1)
+    err_smp += th - mean_hat
+    err_var_smp += (th-np.array(mean_hat))**2
+
+
+err_var_split /= nMonte
+err_split /= nMonte
+err_var_grad /= nMonte
+err_grad /= nMonte
+err_var_bayes /= nMonte
+err_bayes /= nMonte    
[…]

### 2018-09-06 Writeups/nonexistence.tex
small change

%\documentclass[letterpaper]{IEEEtran}
\documentclass[letterpaper, 10pt]{IEEEtran}      % Use this line for a4 paper

%LatexiDiff ignore tikz:
% $: latexdiff -c "PICTUREENV=(?:picture|tikzpicture|DIFnomarkup)[\w\d*@]*" old.tex new.tex > diff.tex

%\IEEEoverridecommandlockouts                              %

%\usepackage{mathcomSTEP}

%\overrideIEEEmargins 
%\IEEEoverridecommandlockouts                              % This command is only needed if 
% you want to use the \thanks command

%\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\onecolumn

\usepackage{mathptmx} 
\usepackage{times} 
\usepackage{amsmath} 
\usepackage{amsbsy} 
\usepackage{amssymb}
%\usepackage{newtxtext, newtxmath}
\usepackage{mathrsfs}
\usepackage{comment}
\usepackage[export]{adjustbox}
\usepackage{tikz}
\usetikzlibrary{external,positioning,decorations.pathreplacing,shapes,arrows,patterns}

%\tikzexternalize[mode=list and make]
\usepackage{algorithmicx}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{pstool}
\usepackage[latin1]{inputenc}
\usetikzlibrary{arrows,shapes}
\usepackage{xifthen}
\usepackage{epic}
%\usepackage{caption}
\usepackage{epstopdf}

\newtheorem{thm}{\bf{Theorem}}
\newtheorem{cor}[thm]{\bf {Corollary}}
\newtheorem{lem}[thm]{\bf {Lemma}}
\newtheorem{prop}[thm]{\bf {Proposition}}
\newtheorem{example}{\bf {Example}}
\newtheorem{definition}{\bf {Definition}}
\newtheorem{rem}{\bf {Remark}}

\newcommand{\mmse}{\mathsf{mmse}}
\newcommand{\unif}{\mathsf{unif}}
\newcommand{\card}{\mathrm{card}}
\newcommand{\ARE}{\mathsf{ARE}}
\newcommand{\supp}{\mathrm{supp} }
\renewcommand\vec[1]{\ensuremath\boldsymbol{#1}}
\newenvironment{proof}{\paragraph*{Proof}}{\hfill$\square$ \newline}
\newcommand{\sgn}{\mathrm{sgn} }
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand*{\QEDA}{\hfill\ensuremath{\square}}

\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
\tikzstyle{sint}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.8cm,thick ]
\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=1cm,thick ]
\tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]

\title{\LARGE \bf Non-existence of a Uniformly Optimal Distributed Scheme}

\begin{document}
We consider the distributed encoding setting in which each single-bit message is independent of the other messages.

\subsection*{Definitions}
\begin{equation} \label{eq:eta_def}
\eta(\theta) \triangleq \frac{f^2(\theta)} {F(\theta)\left(1-F(\theta)\right)},
\end{equation}
where $f$ and $F$ are the PDF and CDF of a log-concave distribution, respectively. 
\begin{prop} \label{prop:eta}
Let $f(x)$ be log-concave, symmetric and differntiable PDF. Then 
\begin{itemize}
\item[(i)] The function
\[
\eta(x) = \frac{f^2(x)}{F(x) \left(1-F(x) \right)}
\]
is symmetric and strictly decreasing for any $x>0$ in the support of $f(x)$. In particular, $
\eta(x) \leq \eta(0) = 4f^2(0)$. 
\item[(ii)] $\eta(x)$ goes to $0$ as $|x|$ goes to infinity. 
\end{itemize}
\end{prop}

\subsection*{Local Asymptotic Normality of Messages}
We first provides conditions under which the messages $M_1,M_2,\ldots$ constitute a local asymptotic normal family. 
\begin{thm} \label{thm:LAN1}
Let 
\[
M_n = \begin{cases} 1 & X_n \in A_n, \\
-1 & X_n \notin A_n,
\end{cases} \quad n\in \mathbb N,
\]
where $\{A_n\}_{n=1}^\infty$ is a sequence of Borel sets. Assume that as $n$ goes to infinity, for any $\theta \in \Theta$,
\begin{equation}
\label{eq:precision_general}
\frac{1}{n} \sum_{i=1}^n \frac{ \left(\frac{d}{d \theta} \Pr(X_i \in A_i) \right)^2 }{ \Pr(X_i \in A_i) \Pr(X_i \notin A_i) }
\end{equation}
converges to a positive number $K(\theta)$ denoted as the \emph{precision parameter}. Then for any $\theta \in \Theta$ and $h\in \mathbb R$,
\begin{align*}
& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (M_1,\ldots,M_n) }{
\mathbb P_{\theta} (M_1,\ldots,M_n)} \\
& \overset{D}{\longrightarrow} \mathcal N\left(-\frac{1}{2} h^2 K(\theta), h^2 K(\theta) \right). 
\end{align*}
\end{thm}

\subsection*{Non-existence of Uniformly Optimal Strategy}
We now show that no distributed estimation scheme can attain normalized risk of $1/\eta(0)$ for all $\theta \in \Theta$.

\begin{thm} \label{thm:non_existence}
Let $M_1,M_2,\ldots $ be a sequence satisfying the condition in Theorem~\ref{thm:LAN1}. Let $\Xi \subset \Theta $ be the set of points for which there exists an estimator $\hat{\theta}_n = \hat{\theta}(M_1,\ldots,M_n)$ such that
\[
\lim_{n\to \infty} \mathbb E \left[ n \left(\theta - \hat{\theta}_n \right)^2 \right] = 1/\eta(0). 
\]
Then $\Xi$ has Lebesgue measure zero. 
\end{thm}

\begin{proof}
The proof requires the following lemmas:
\begin{lem} \label{lem:eta_epsilon_bound}
Let $\epsilon>0$ and
$x_1,\ldots,x_m \in \mathbb R$. If $\{x_1,\ldots,x_m\} \cap (-\epsilon,\epsilon) = \emptyset$, then 
\[
\frac{ \left( \sum_{i=1}^m (-1)^{i+1} f(x_i) \right)^2}{ \left(\sum_{i=1}^m (-1)^{i+1} F(x_i) \right) \left( 1- \sum_{i=1}^m (-1)^{i+1} F(x_i) \right)} \leq \eta(\epsilon).
\]
\end{lem}
\subsubsection*{Proof of Lemma~\ref{lem:eta_epsilon_bound}}
By induction on $m$. \\

Theorem~\ref{thm:LAN1} says that $M_1,M_2,\ldots$ defines a LAN family with precision parameter $K(\theta)$. The local asymptotic minimax property of estimators in LAN models implies that for any estimator $\hat{\theta}_n =\hat{\theta}_n(M_1,\ldots,M_n)$ and $\delta>0$, there exists $n$ large enough such that 
\[
\mathbb E \left[n(\theta - \hat{\theta}_n)^2  \right] + \delta \geq \frac{1}{K(\theta)} ,
\] 
where $K(\theta)$ is the precision parameter \eqref{eq:precision_general}. It follows that for all $\theta \in \Xi$ we have $K(\theta)=1/\eta(0)$. 
%
%Let $\theta \in \Xi$ and let $\hat{\theta}_n$ be an estimator such that $n\mathbb E (\hat{\theta}_n-\theta)^2 \to 1/\eta(0)$. 
%
It follows from Proposition~\ref{prop:eta} that if $\epsilon>0$, then $\eta(\epsilon) < \eta(0)$. Since the only defining property of the sequence of messages $\{M_i\}_{i=1}^\infty$ is the precision parameter $K(\theta)$, we may assume without loss of generality that each $A_i$ is a finite union of $M_i$  intervals
\begin{equation}
\label{eq:finite_union}
A_i = \bigcup_{k=1}^{M_i} (b_{i,k}, a_{i,k}),
\end{equation}
where $b_{i,k+1} > a_{i,k+1} > b_{i,k} > a_{i,k}$ for every $i$ and $k$. Indeed, for any sequence of Borel measurable sets $\{A_i\}_{i=1}^\infty$ for which  \eqref{eq:precision_general} converge to $K(\theta)$ for any $\theta \in \Theta$, has a sequence $\{A'_i\}_{i=1}^\infty$ converging to the same limit in which $A'_i$ is of the form \eqref{eq:finite_union}. With this assumption, \eqref{eq:precision_general} is given by
\begin{equation}
\label{eq:precision_general2}
\frac{1}{n}\sum_{i=1}^n \frac{  \left( \sum_{k=1}^{M_i} f(b_{i,k})-f(a_{i,k}) \right)^2}{ \sum_{k=1}^{M_i} \left( F(b_{i,k})-F(a_{i,k}) \right) \left( 1-\sum_{k=1}^{M_i} \left( F(b_{i,k})-F(a_{i,k}) \right)\right)}
\end{equation}
Next, Lemma~\ref{lem:eta_epsilon_bound} implies that for any $\theta$ such that $K(\theta) \to \eta(0)$, any interval of the form $(\theta-\epsilon,\theta+\epsilon)$ contains an infinite number of elements from $\{ a_{i,k},b_{i,k},\, i\in \mathbb N, k = 1,\ldots,M_i \}$ (otherwise, there exists $\rho>0$ such that 
\[
\{ a_{i,k},b_{i,k},\, i\in \mathbb N, k = 1,\ldots,M_i \} \cap (-\rho+\theta,\theta+\rho) = \emptyset,
\]
so that Lemma~\ref{lem:eta_epsilon_bound} implies $K(\theta) \leq \eta(\rho) < \eta(0)$). We conclude that each point in $\Xi$ is a limit points for the set 
\begin{align}
\label{eq:endpoint_set}
& \left\{b_{i,k},a_{i,k},\, k=1,\ldots,M_i,i=1,\ldots, \mathbb N  \right\} = \bigcup_{i\in \mathbb N} \bigcup_{k=1}^{M_i} \{ a_{i,k},b_{i,k}\}. 
\end{align}
However, \eqref{eq:endpoint_set} is a countable union of countable sets, and hence has no interior point (by Baire's Category Theorem). In particular, it Lebesgue measure is zero. 
\end{proof}

\end{document}

### 2018-09-06 Writeups/onebit_full_V2.tex
small change

@@
 %\documentclass[letterpaper]{IEEEtran}
-\documentclass[letterpaper, conference, 11pt]{IEEEtran}      % Use this line for a4 paper
+\documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper
 
@@
 
-%\onecolumn
+\onecolumn
 
@@
 \usepackage{times} 
-
 \usepackage{amsmath} 
@@
 \usepackage{epic}
-\usepackage{caption}
+%\usepackage{caption}
 \usepackage{epstopdf}
@@
 \newtheorem{rem}{\bf {Remark}}
+\newtheorem{assump}{\bf {Assumptions}}
 
@@
 \newcommand{\sgn}{\mathrm{sgn} }
+\newcommand{\Prob}{\mathbb{P} }
 \newcommand{\argmax}{\mathrm{argmax}}
@@
 \begin{abstract}
-We consider the problem of estimating the mean of a symmetric log-concave distribution under the constraint that only a single bit per sample from this distribution is available to the estimator.
-We study the mean squared error risk in this estimation as a function of the number of samples, and hence number of bits, from this distribution.
-Under an adaptive scheme in which each bit is a function of the current sample and the previously observed bits, we show that the optimal relative efficiency, compared to the standard mean estimator without bit limitation, is the efficiency of the median.
-For the distributed scheme we consider the setting where each bit is obtained by comparing against a prescribed threshold value.
-We show that the maximum likelihood estimator in this case is asymptotically local minimax, and its asymptotic relative efficiency is finite although strictly larger than that of the sample median.
-% and depends on the size of the parameter space from which the mean is taken.
-Furthermore, assuming a prior on this space, the efficiency in the distributed case approaches $\sigma^2/4f^2(0)$ provided the variance of the distribution is high compared to the variance of the prior.
+We consider the problem of estimating the mean of a symmetric log-concave distribution under the following constraint: only a single bit per sample from this distribution is available to the estimator.
+We study the mean squared error (MSE) risk in this estimation as a function of the number of samples, and hence number of bits, from this distribution.
+Under an adaptive setting in which each bit is a function of the current sample and the previously observed bits, we show that the optimal relative efficiency compared to the sample mean is the efficiency of the median.
+For example, in estimating the mean of a normal distribution, a constraint of one bit per sample incurs a penalty of $\pi/2$ in sample size compared to the unconstrained case.
+%
+We also consider a distributed setting where each one bit message is only a function of a single sample.
+We derive lower bounds on the MSE in this setting, and show that the optimal efficiency can only be attained at a finite number of points in the parameter space.
+%
+Finally, we analyze a distributed setting where the bits are obtained by comparing each sample against a prescribed threshold, and consider the threshold density that minimizes the maximal MSE. 
+%
+Our results indicates that estimating the mean from one bit measurements is equivalent to estimating the sample median from these measurements.
+In the adaptive case, this estimate can be done with vanishing error for any point in the parameter space.
+In the distributed case, this estimate can be done with vanishing error only for a finite number of possible values for the unknown mean.
 %
@@
 The question that we ask is to what extent a parametric estimation task is affected by this constraint on communication, and what are the fundamental performance limits in estimating a parameter subject to such restriction.
-\\
-
-This paper answers this question in a particular setting: the estimation of the mean $\theta$ of a symmetric log-concave distribution $P_X$ with a finite variance, under the constraint that only a single bit can be communicated on each sample from this distribution.
+\par
+This paper answers this question in a particular setting: the estimation of the mean $\theta$ of a symmetric log-concave distribution with a finite variance, under the constraint that only a single bit can be communicated on each sample from this distribution.
 As it turns out, the ability to share information before committing on each single-bit message dramatically affects the performance in estimating $\theta$.
@@
 \begin{itemize}
- \item[(i)] \emph{Centralized} encoding: all $n$ encoders confer and produce a single $n$ bit message. 
- \item[(ii)] \emph{Adaptive} or \emph{sequential} encoding: the $i$th encoder observes the $i$th sample and the $i-1$ previous messages.
- \item[(iii)] \emph{Distributed} encoding: the $i$th message is only a function of the $i$th observation.
+ \item[(i)\,\,] \emph{Centralized} encoding: all $n$ encoders confer and produce a single $n$ bit message. 
+ \item[(ii)\,] \emph{Adaptive} or \emph{sequential} encoding: the $n$th encoder observes the $n$th sample and the $n-1$ previous messages (bits).
+ \item[(iii)] \emph{Distributed} encoding: the $n$th message is only a function of the $n$th observation.
  \end{itemize}
 Evidently, as far as information sharing is concerned, settings (iii) is a more restrictive version of (ii) which is more restrictive than (i).
-Below are three application example of each of settings (i)-(iii), respectively:
+Below are three application examples for each of settings (i)-(iii) above, respectively:
 \begin{itemize}
-\item[(i)] {\bf Signal acquisition:} a quantity is measured $n$ times at different instances, and the results are averaged in order to reduce measurement noise.
+\item {\bf Signal acquisition:} a quantity is measured $n$ times at different instances, and the results are averaged in order to reduce measurement noise.
 The averaged result is then stored using one of $n$ states.
-\item[(ii)] {\bf analog-to-digital conversion via sigma-delta modulation (SDM):} in SDM an analog signal is converted into a sequence of bits by sampling it at a very high rate and then using one-bit threshold detector combined with a feedback loop to update an accumulated error state.
+\item {\bf Analog-to-digital conversion:} in sigma-delta modulation, an analog signal is converted into a sequence of bits by sampling it at a very high rate and then using one-bit threshold detector combined with a feedback loop to update an accumulated error state.
 Therefore, the MSE in tracking an analog signal using a SDM falls under our setting (ii) when we assume that the signal at the input to the modulator is a constant (direct current) corrupted by, say, thermal noise \cite{53738}.
-Since the sampling rates in SDM is usually many times more than the bandwidth of its input, analyzing SDM under a constant input provides meaningful lower bound even for non-constant signals.
-\item[(iii)] {\bf Differential privacy:} -- a business entity is interested in estimating the average income of its clients.
-In order to keep this information as confidential as possible, each client answers a single yes/no questions about its individual income.
+Since the sampling rates in SDM are usually many times more than the bandwidth of its input, analyzing SDM under a constant input provides meaningful lower bound even for non-constant signals.
+\item {\bf Differential privacy:} -- a business entity is interested in estimating the average income of its clients.
+In order to keep this information as confidential as possible, each client independently provides an answer to a yes/no question related to its income.
 \end{itemize}
-
+%
 We measure the performance in estimating $\theta$ by the mean squared error (MSE) risk.
-We are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting compared to asymptotically normal estimators whose variances decreases as $\sigma^2/n+o(n^{-1})$ where $\sigma^2$.
-Estimator of this form includes the empirical mean of $X_1,\ldots,X_n$, and under some conditions, optimal Bayes estimations.
-We note that the performance under estimating a signal that may vary with each noisy measurement is always harder that our setting where the parameter (the mean) remains fixed.
-Therefore, the excess MSE risk due to the one-bit per measurement constraint we derive in this paper can serve as the most optimistic estimate for the degradation in performance in estimating a signal that vary in time.
+We are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting compared to asymptotically normal estimators whose variances decreases as $\sigma^2/n+o(n^{-1})$.
+Estimators of this form include the empirical mean of the samples, and, under some conditions, the optimal Bayes estimator.
+\par
+%
+In addition to the examples above, the excess risk in estimating a fixed parameter due to a one-bit per measurement constraint is useful in bounding from below the excess risk in estimating a signal from its noisy measurements.
+Namely, the excess MSE or ARE we derive serves as the most optimistic estimate for the risk in estimating a signal that varies in time or space under the one bit per measurement constraint.
+Such situtations are considered in \cite{baraniuk2017exponential, jacques2013robust, plan2013one, li2017channel, choi2016near}.
+\\
 
@@
 
-In setting (i), the estimator can evaluate the empirical mean of the samples and then quantize it using $n$ bits.
+In setting (i), the estimator can evaluate the optimal mean estimator (e.g., the sample mean in the Gaussian case) and then quantize it using $n$ bits.
 Since the accuracy in describing the empirical mean decreases exponentially in $n$, the error due to quantization is negligible compared to the MSE in estimating the mean.
@@
 %
-In this paper we show that a similar results does not hold even in setting and (ii): the ARE of any adaptive estimation scheme is at least that of the sample median.
-Specifically, when $P_X$ is normal, this ARE equals $2/\pi \approx 0.637$, showing that the one-bit constraint increases the effective sample size in estimating $\theta$ by at least $2/\pi \approx 1.57$ compared to estimating it without the bit constraint.
-We also show that this lower bound on the ARE and is tight by providing an estimator that attains it.
+In this paper we show that a similar results does not hold in setting (ii): the ARE of any adaptive estimation scheme is at most the ARE of the sample median.
+Specifically, when the samples are drawn from the normal distribution, this ARE equals $\pi/2$, showing that the one-bit constraint increases the effective sample size in estimating $\theta$ by at least $\pi/2 \approx 1.57$ compared to estimating it without the bit constraint.
+We also show that this lower bound on the ARE is tight by providing an estimator that attains it.
 % This estimator is obtained by averaging the results of a series of comparisons of the samples against certain thresholds.
@@
 %
-Clearly, the minimal penalty on the MSE in setting (ii) also holds under setting (iii), although the question whether this MSE is achievable (or otherwise, what is the minimal MSE) remains open.
-Instead, in setting (iii) we restrict ourselves to estimators from messages obtained by comparison against a prescribed value (that may be different for each sample).
+Clearly, the penalty on the sample size in setting (iii) is at least as large as that in setting (ii). 
+Unlike in setting (ii), we show that there is no distributed estimation scheme that is uniformly optimal in the sense that it attains the ARE of the sample median for all $\theta$ in the parameter space.
+% Instead, in setting (iii) we restrict ourselves to estimators from messages obtained by comparison against a prescribed value (that may be different for each sample).
 We show that the maximum likelihood (ML) estimator for $\theta$ from these messages is asymptotically local minimax, and its asymptotic variance is strictly greater than the variance of the median.
@@
 
-Even though the ARE in setting (i) is $1$, this scheme already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation procedures.
+We note that although the ARE in setting (i) is $1$, this scheme already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation procedures.
 Indeed, the standard technique to encode an unknown random quantity using $n$ bits is equivalent to the design of a scalar quantizer \cite{gray1998quantization}.
@@
 As a result, a non-trivial exploration exploitation trade-off arises in this case.
-Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$.
-Therefore, while it is clear that uncertainty due to quantization decreases exponentially in the number of bits $n$ leading to ARE $1$, an exact expression for the MSE in this setting is still difficult to derive.
+%Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$. 
+Therefore, while uncertainty due to quantization decreases exponentially in the number of bits $n$, hence the ARE is $1$, an exact expression for the MSE in this setting is still difficult to derive.
 \par
-The situation is even more involved in the adaptive encoding setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$, may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
+%
+The situation is even more involved in the adaptive encoding setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$ may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
 Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $n-1$ messages, is not guaranteed to be globally optimal.
-Therefore, while we characterize the optimal detector given the previous messages, this characterization cannot be use to derive a lower bound on the ARE.
-Instead, our result on the median efficiency being the minimal ARE is obtained by bounding the Fisher information of any $n$ adaptive messages and using the van Trees version of the information inequality \cite{gill1995applications}.
+Therefore, while we characterize the optimal one-bit message given the previous messages, this characterization does not necessarily  leads to an upper bound on the ARE.
+Instead, our result on the maximal ARE is obtained by bounding the Fisher information of any $n$ adaptive messages and using an appropriate information inequality.
+\par
+In addition to encoding and estimation schemes that leads to optimal results, we also consider two additional ``natural'' schemes.
+Specifically, in setting (ii) we consider the one-bit optimal scheme, i.e., the case of a greedy encoder that given the $n$th sample and the previous $n-1$ bits, provides a bit that minimizes the $n$-step MSE.
+In setting (iii) we also consider the case where the messages are obtained by comparing each sample against a prescribed threshold.
+This threshold may be different across samples and is assumed deterministic (independent of the data).
 
@@
 \subsection*{Related Works}
-As the variance $\sigma^2$ goes to zero, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is easily solved by a bisection style method over the parameter space.
+As the variance $\sigma^2$ goes to zero, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is solved by a bisection style method over the parameter space.
 Therefore, the general case of non-zero variance is a reminiscent of the noisy binary search problem with possibly infinite number of unreliable tests \cite{cicalese2002least, Karp:2007:NBS:1283383.1283478}.
-However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a constant input $\theta$ corrupted by a Gaussian noise.
+However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a constant input corrupted by a Gaussian noise.
 Using a SDM, Wong and Gray \cite{53738} showed that the output of the modulator converges to the true constant input almost surely, so that a SDM provides a consistent estimator for setting (ii).
 The rate of this convergence, however, was not analyzed and cannot be derived from the results of \cite{53738}.
-In particular, our results for setting (ii) imply that the asymptotic rate of convergence of the MSE in SDM to a constant input under Gaussian nosie is at most $\sigma^2\pi/2$ over the number of feedback iterations.
+In particular, our results for setting (ii) imply that the asymptotic rate of convergence of the MSE in SDM to a constant input under an additive white Gaussian nosie is at most $\sigma^2\pi/2$ over the number of feedback iterations.
 Baraniuk et.
 al \cite{baraniuk2017exponential} also considered adaptive one-bit measurements in the context of analog-to-digital conversion, although without noise at the input.
-Their result of an exponential MSE decaying rate clearly does not hold in the noisy setting (stated otherwise, the MSE can decay exponentially up to the noise level).
-\\
-
-One-bit measurements in the distributed setting (iii) was considered in \cite{904560,4244748, 6882252, chen2010performance, 5184907}, but without optimizing the encoders or their detection rule.
+By establishing the lower bound of $\sigma^2\pi/2n$ on the MSE, we show that the main results of \cite{baraniuk2017exponential}, an exponential MSE decaying rate, does not hold in the noisy setting.
+Stated otherwise, the MSE in the setting of \cite{baraniuk2017exponential} may decay exponentially up to the noise level, after which it decays at most as $\sigma^2\pi/2n$.
+\par
+%
+One-bit measurements in the distributed setting (iii) was considered in \cite{904560,4244748, 6882252, chen2010performance, 5184907}, but without optimizing the encoders and their detection rules.
+Consequently, the performance derived in these works are not optimal.
  % analyzed the estimation from distributed quantized measurements when the same detection rule is applied by all encoders.
@@
 The work of \cite{52470} addresses the counterpart of our setting (iii) in the case of hypothesis testing, although the results there cannot be extended to parametric estimation.
-More generally, when the parameter space $\Theta$ is finite, the characterization of the optimal detection rules was considered by Tsitsiklist in \cite{tsitsiklis1988decentralized}.
-It was shown there that if the cardinality of $\Theta$ is at most $M$ and the probability of error criterion is used, than no more than $M(M-1)/2$ different detection rules are necessary in order to attain probability of error decreasing exponentially with the optimal exponent.
+When the parameter space $\Theta$ is finite, Tsitsiklist \cite{tsitsiklis1988decentralized} showed that when the cardinality of $\Theta$ is at most $M$ and the probability of error criterion is used, then no more than $M(M-1)/2$ different detection rules are necessary in order to attain probability of error decreasing exponentially with the optimal exponent.
 %That is, beyond $M(M-1)/2$ some decision rules can be repeated without lossing optimality.
 Furthermore, in a version of this problem for the adaptive sestting \cite{5751320}, it was shown that, with a specific two-stages feedback, there is no gain in feedback compared to the fully distributed setting.
-Our results implies that the ARE in the distributed setting with threshold detection rules is strictly larger than that in the adaptive setting, suggesting that the case of a finite $\Theta$ is very different than when $\Theta$ is an open set.\par
-%
-As we explain in details in Section~\ref{sec:preliminary}, the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}, leads to a lower bounds on the MSE in setting (iii).
+Our results implies that the ARE in the distributed setting with threshold detection rules is strictly larger than that in the adaptive setting, suggesting that the case of a finite $\Theta$ is very different than the case where $\Theta$ is an open set.\par
+%
+As we explain in detail in Section~ \ref{sec:preliminary}, the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}, leads to a lower bounds on the MSE in setting (iii).
 For the case of a Gaussian distribution, this lower bound bounds the ARE to be at most $3/4$.
-Thus, while this bound on the ARE provides no new information compared to the upper bound of $2/\pi$ we derive for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimal even under one-bit quantization of each sample.\\
-
+Thus, while this bound on the ARE provides no new information compared to the upper bound of $2/\pi$ we derive for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimal even under the one bit per sample constraint.
+ \par
+% 
 Finally, we note that our settings (ii) and (iii) can be obtained as special cases of 
-\cite{zhang2013information} that consider adaptive and distributed estimation protocols for $m$ machines, each has access to $n/m$ independent samples.
+\cite{zhang2013information} 
+that consider adaptive and distributed estimation protocols for $m$ machines, each has access to $n/m$ independent samples.
 The main result of \cite{zhang2013information} are bounds on the estimation error as a function of the number of bits $R$ each machine uses for communication.
 The specialization of their result to our setting, by taking $m=n$ and $R=1$, leads to looser lower bounds then we derive here for cases (ii) and (iii).
-Other related works include statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation}, and one-bit quantization constraints
-%in compressed sensing\cite{baraniuk2017exponential} and 
-in MIMO detection in wireless communication \cite{singh2009limits}. \\
+Looser bounds can also be obtained from \cite{zhang1988estimation, han2018distributed} that considered inference and distributed estimation under data compression constraint \cite{DBLP:journals/corr/abs-1802-08417, zhang1988estimation, han2018distributed}.
+\\
+%in MIMO detection in wireless communication \cite{singh2009limits}. \\
+
+The remainder of this paper is organized as follows.
+In Section~\ref{sec:problem} we describe the problem and useful notation.
+In Section~\ref{sec:preliminary} we provide two simple bounds on the efficiency and MSE.
+Our main results for the adaptive and distributed cases are given in Sections~\ref{sec:sequential} and \ref{sec:distributed}, respectively.
+In Section~\ref{sec:conclusions} we provide concluding remarks.
 
@@
 \draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M_2 \in \left\{-1,1\right\}$} (est);
+
 \draw[->] (enc1)+(0.7,0) -- +(0.7,-0.7) -| (enc2);
@@
 
-\node[right of = est, node distance = 1.5cm] (dest) {$\widehat{\theta}_n$};
+\node[right of = est, node distance = 1.5cm] (dest) {$\hat{\theta}_n$};
 %         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
@@
 \end{center}
-\caption{\label{fig:sequential} Adaptive single-bit encoding: the $i$th encoder delivers a single bit message which is a function of its private sample $X_i$ and the previous messages $M_1,\ldots,M_{i-1}$.}
+\caption{\label{fig:sequential} Adaptive single-bit encoding: the $n$th encoder delivers a single bit message which is a function of its private sample $X_n$ and the previous messages $M_1,\ldots,M_{n-1}$.}
 \end{figure}
@@
 \end{figure}
-Let $\Theta$ be a closed interval of the real line.
-Let $f(x)$ be a symmetric log-concave density function with a finite second moment $\sigma^2$.
-We denote by $P_X$ the probability distribution with density $f\left( x-\theta \right)$, where $\theta \in \Theta$.
-Therefore, $P_X$ is an absolutely continuous log-concave distribution with mean $\theta$, variance $\sigma^2$.
-Moreover, symmetry and log-concavity of $f(x)$ implies that $P_X$ has a single mode at $x =\theta$.
+Let $f(x)$ be a symmetric and log-concave density function with a finite second moment $\sigma^2$.
+For $\theta \in \Theta$, denote by $P_X$ the probability distribution with density $f\left( x-\theta \right)$.
+Therefore, $P_X$ is an absolutely continuous log-concave distribution with mean $\theta$ and variance $\sigma^2$.
+Symmetry and log-concavity of $f(x)$ imply that $P_X$ is strongly unimodal with its mode at $x =\theta$ \cite{ibragimov1956composition}.
+We further assume that the \emph{parameter space} $\Theta$ is a closed interval of the real line.
 \par
-In some cases we assume that $\theta$ is drawn once from the prior distribution $\pi$ on the parameter space $\Theta$. In this cases we assume that $\pi$  
-is absolutely continuous distribution, and denote its density by $\pi(\theta)$, i.e., $\pi(d\theta) = \pi(\theta)d\theta$.  
+In some situations it is useful to assume that $\theta$ is drawn once from the prior distribution $\pi$ on $\Theta$.
+In this case we assume that $\pi$ is an absolutely continuous distribution, and denote its density by $\pi(\theta)$, i.e., $\pi(d\theta) = \pi(\theta)d\theta$.
 \par
 The random variables $X_1,\ldots,X_n$ represent $n$ independent samples from $P_X$. 
-We are interested in estimating the parameter $\theta$ from a set of $n$ binary messages $M^n = (M_1,\ldots,M_n)$, obtained from $X^n = (X_1,\ldots,X_n)$ under three possible scenarios: 
+We are interested in estimating $\theta$ from a set of $n$ binary messages $M_1,\ldots,M_n$, obtained from $X_1,\ldots,X_n$ under three possible scenarios: 
 \begin{itemize}
-\item[(i)~~] Centralized $M^n(X^n)$ (Fig.~\ref{fig:centralized}).
-\item[(ii)~] Adaptive $M_i(X_i,M^{i-1})$, $i=1,\ldots,n$ (Fig.~\ref{fig:sequential}).
+\item[(i)~~] Centralized $M_i(X_1,\ldots,X_n)$, $i=1,\ldots,n$ (Fig.~\ref{fig:centralized}).
+\item[(ii)~] Adaptive $M_i(X_i,M_1,\ldots,M_{i-1})$, $i=2,\ldots,n$ (Fig.~\ref{fig:sequential}).
 \item[(iii)] Distributed $M_i(X_i)$, $i=1,\ldots,n$ (Fig.~\ref{fig:distributed}).
@@
 \end{equation}
-where the expectation is taken with respect to the distribution of $X^n$ and the prior distribution $\pi(\theta)$.  
+where the expectation is taken with respect to the distribution of $X^n$ and, whenever available, a prior distribution $\pi(\theta)$ over $\Theta$.  
 %It is well known that minmax estimation error 
@@
 %
-The main problem we consider is the minimal value of \eqref{eq:error_def} as a function of $n$, under various choices of the encoding functions in cases (i), (ii), and (iii). \\
-
-Particular interest is given to the ARE of estimators with respect to an asymptotically normal efficient estimator without the one-bit constraint.
+The main problem we consider is the minimal value of \eqref{eq:error_def} as a function of $n$ under different choices of the encoding functions in cases (i), (ii), and (iii). \\
+
+We give particular attention to the ARE of estimators with respect to an asymptotically normal efficient estimator that is not subject to the bit constraint.
 Specifically, let $\{a_n,\,n\in \mathbb N\}$ be a sequence such that
@@
 \[
-a_n \mathbb E \left(\hat{\theta}_n - \theta \right)^2 = V + O(1/n),
-\]
-then the ARE of $\hat{\theta}_n$ is finite and equals $\sigma^2/V$. 
-%sample mean $\bar{X}_n = \frac{1}{n} \sum_{i=1}^n X_i$. Since the MSE attained by the latter is $\sigma^2/n$, this relative efficiency is defined as
-%\begin{equation}
-% \lim_{n \rightarrow \infty} \frac{n}{\sigma^2}  R_n. 
-%\label{eq:relative_efficiency}
-%\end{equation}
-
-%In addition to the notations defined above, we denote by $\phi(x)$ the standard normal density and by $\Phi(x)$ the standard normal cumulative distribution function.
-Prime denote derivative with respect to $\theta$.
-
-\section{Preliminary Results \label{sec:preliminary}}
-On a first impression it may not be clear whether consistent estimation of the mean is even possible in the adaptive and centralized settings.
-On the other hand, one may suspect that estimation in these cases is trivial as in the centralized setting (i), where it is easy to attain ARE 1.
-In this section we settle this skepticism by showing that (1) a consistent estimator with an asymptotically normal distribution always exists in setting (iii), and (2) the ARE in setting (iii) with $P_X = \mathcal N(\theta, \sigma^2)$ is bounded from below by $3/4$.
-
-\subsection{Consistent Estimation}
-Denote by $M_i$ is the indicator of the event $X_i > \theta_0$ for some arbitrary $\theta_0$. Note that
-\[
-\frac{1}{n} \sum_{i=1}^n M_i \overset{a.s.}{\rightarrow} F(\theta),
-\]
-where $F(x)$ is the cumulative distribution of $X_1-\theta$ that is assumed to be known. Therefore, 
-\begin{equation}
-\label{eq:estimator_naive}
-\hat{\theta}_n = F^{-1}\left( \frac{1}{n} \sum_{i=1}^n M_i \right)
-\end{equation}
-is a consistent estimator for $\theta$ under setting (iii).
-Moreover, it can be verified, as we do in Section~\ref{sec:distributed}, that $\hat{\theta}_n$ is asymptotically normal with variance that is the inverse of
+a_n \mathbb E \left(\hat{\theta}_n - \theta \right)^2 = V + o(1),
+\]
+with $o(1)\to 0$ as $n\to \infty$, then the ARE of $\hat{\theta}_n$ is finite and equals $\sigma^2/V$. \\
+
+In addition to the notation above, we also denote by $F(x)$ the cumulative distribution function of $X_i$, and define
 \begin{equation} \label{eq:eta_def}
-\eta(\theta-\theta_0) \triangleq \frac{f^2(\theta-\theta_0)} {F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}. 
-\end{equation}
-In particular, the ARE of $\hat{\theta}_n$ is finite and equals $\sigma^2/\eta(\theta - \theta_0)$.
-For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that the function $\eta(x)$ is a strictly decreasing function of $|x|$.
-The following proposition, generalizes this property of $\eta(x)$ to any log-concave distribution.
-\begin{prop} \label{prop:eta}
-Let $f(x)$ be log-concave, symmetric and differntiable probability density function. Then 
-\begin{itemize}
-\item[(i)] The function
-\[
-\eta(x) = \frac{f^2(x)}{F(x) \left(1-F(x) \right)}
-\]
-is symmetric and strictly decreasing for any $x>0$ in the support of $f(x)$. In particular, $
-\eta(x) \leq \eta(0) = 4f^2(0)$. 
-\item[(ii)] $\eta(x)$ goes to $0$ as $|x|$ goes to infinity. 
-\end{itemize}
-
-\end{prop}
-\begin{proof}
-See Appendix~\ref{app:proofs}. 
-\end{proof}
-%
+\eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))} =  \frac{f(x)f(-x)}{F(x)F(-x)}, 
+\end{equation}
+where the last equality is due to symmetry of $f(x)$. We note that 
+\begin{equation}
+\label{eq:eta_h}
+\eta(x) = h(x)h(-x) = f(x) \left( h(x) + h(-x) \right), 
+\end{equation}
+where 
+\[
+h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
+\]
+is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function of since $f(x)$ is log-concave \cite{bagnoli2005log}. 
+%
+For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as shown in Fig.~\ref{fig:eta}. 
+%
+In this paper we only consider the normal distribution and other log-concave symmetric distributions for which this property of $\eta(x)$ holds. Specifically, we require the following:
+\begin{assump} \label{assump:failure_rate}
+ $\eta(x)$ is strongly unimodal. 
+\end{assump}
+%That is, Assumption~\ref{assump:failure_rate} says that $\eta'(x) < 0 $ for all $x>0$. 
+Under this assumption we have, 
+\[
+4f^2(x) \leq \eta(x) \leq \eta(0),
+\] 
+%
+where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median.
+Combined with log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that $\eta(x)$ vanishes as $|x|\rightarrow \infty$.
+\par
+%
+Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions).
+Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.
+\\
+
 \begin{figure}
@@
 ymin = 0,
+ymax = 0.9,
 samples=10, 
@@
 \addlegendentry{$\phi(x)$};
+\addplot[domain = -5:5, samples = 50, color = black, solid, dashed]  {4*exp(-x^2) / (2*3.14159)};
+\addlegendentry{$4\phi^2(x)$};
+
 \end{axis}
@@
 \caption{
-The function $\eta(x) = f^2(x) / F(x)F(-x)$ (blue) for $f(x) = \phi(x)$ the standard normal density (red).
+The function $\eta(x) = f^2(x) / F(x)F(-x)$ for $f(x) = \phi(x)$ the standard normal density.
 \label{fig:eta}
@@
 
-At $\theta = \theta_0$ the variance of $\hat{\theta}_n$ of \eqref{eq:estimator_naive} equals $1/(4f(0)^2)$ which is the variance of the median.
-However, since  $\eta(x)$ vanishes as $|x|\rightarrow \infty$ (see illustration in Fig.~\ref{fig:eta} for the normal density),  the variance of $\hat{\theta}_n$ may be very large when $\theta$ is away from $\theta_0$.
-In this case, the estimator $\hat{\theta}_n$ has little practical value unless $\Theta$ is very small compared to $\sigma^2$.
+\section{Simple Bounds \label{sec:preliminary}}
+On a first impression it may not be clear whether consistent estimation of the mean is even possible in the adaptive and centralized settings.
+On the other hand, it may seem as if estimation in these cases is trivial as in the centralized setting (i).
+%
+In this section we settle such skepticism by providing simple lower and upper bounds to the relative efficiency under setting (iii). We show that:
+\begin{itemize}
+\item[I.] A consistent estimator with an asymptotically normal distribution always exists in setting (iii), and hence in setting (ii). 
+\item[II.] For the normal distribution, the ARE in setting (iii) is at most $3/4$. Namely, all estimators in this case are strictly inferior compared to the sample mean. 
+\end{itemize}
+
+\subsection{Consistent Estimation}
+Fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
+\[
+M_i = \mathbf 1_{X_i>\theta_0}, 
+\]
+where $\mathbf 1_A$ is the indicator of the event $A$. We have
+\[
+p_n \triangleq\frac{1}{n} \sum_{i=1}^n M_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
+\]
+so that 
+\begin{equation}
+\label{eq:estimator_naive}
+\hat{\theta}_n = \theta_0 + F^{-1}\left( p_n \right)
+\end{equation}
+is a consistent estimator for $\theta$ in the distributed setting of Fig.~\ref{fig:distributed}, where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set.
+Furthermore, the variance of $p_n$ is $F(\theta-\theta_0)F(\theta_0-\theta)$, and hence the delta method implies that $\hat{\theta}_n$ is asymptotically normal with variance
+\begin{equation} 
+\frac{1}{
+\eta(\theta-\theta_0)} = \frac{F(\theta-\theta_0)F(\theta_0-\theta)}{f^2(\theta-\theta_0)}. 
+\end{equation}
+In particular, the ARE of $\hat{\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
+In other words, for a prescribed accuracy, $\hat{\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
 \par
 %
-In Section~\ref{sec:sequential} we present an asymptotically normal estimator that attains the variance of the median $1/\eta(0)$ regardless of the radius of $\Theta$ or the prior $\pi(\theta)$.
-We also show in Section~\ref{sec:sequential} that no estimator can attain variance that is smaller than $1/\eta(0)$, so that the ARE of any estimator is at least $\sigma^2\eta(0) = (2f(0)\sigma)^2$.
-
-\subsection{Lower bound from the CEO \label{sec:ceo}}
-The CEO setting includes $n$ encoders, each has access to a noisy version of a random source sequence \cite{berger1996ceo}. 
+%
+Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of $\hat{\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
+This ARE is attained only when $\theta_0 = \theta$, although $\theta$ is unknown apriori.
+Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of $\hat{\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
+As an example, when $f(x)$ is a normal density, the ARE of $\hat{\theta}_n$ is $\approx 0.07$ when $\theta_0$ is $2.33$ standard deviations from $\theta$.
+Therefore, the estimator $\hat{\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
+\par
+It is suggested that lower variance can be obtained by an estimator of the form \eqref{eq:estimator_naive} if, after observing a batch of the single bit messages, one can update the threshold value $\theta_0$.
+Such a scheme falls within the adaptive setting of Fig.~\ref{fig:sequential} which we consider in Section~\ref{sec:sequential}.
+\\
+% variance equals to $1/\eta(0)n + o(1)$.
+We also show in Section~\ref{sec:sequential} that no estimator can attain variance that is asymptotically smaller than $1/\eta(0)n$, so that the ARE of any estimator in settings (ii) and (iii) is at least $\eta(0) \sigma^2$.
+
+\subsection{Multiterminal Source Coding \label{sec:ceo}}
+The CEO setting includes $n$ encoders, each has access to a noisy version of a random sequence \cite{berger1996ceo}. 
 % $\left\{ U_j,\,j=1,2,\ldots \right\}$. 
-The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator. \par
-Assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding (setting (iii) in the Introduction) corresponds to the Gaussian CEO setting with $k=1$ source realization: the $i$th encoder uses $R_i=1$ bits to transmit a message that is a function of $X_i = \theta + \sigma Z_i$, where $Z_i$ is standard normal.
-As a result, a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting is given by the MSE in the optimal source coding scheme for the CEO with: $n$ terminals of codes rates $R_1 = \ldots = R_n = 1$, a Gaussian observation noise at each terminal of variance $\sigma^2$, and an arbitrary number of $k$ independent draws of $\theta$.
-Note that the difference between the CEO and ours lays in the privilege of each of the CEO encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realization, whereas our setting only allows $k=1$.
- \\
-
-By using an expression for the minimal MSE in the Gaussian CEO as the number of terminals goes to infinity, we conclude the following:
+The $i$th encoder observes $k$ noisy samples and transmit $R_i k$ bits to a central estimator. \par
+Assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding (setting (iii) in the Introduction) corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
+As a result, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the MSE in the optimal coding scheme for the CEO.
+Note that the difference between the CEO setting and ours lays in the privilege of each of the encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realization, rather than a single realization using a single bit in ours.
+ \par
+An optimal scheme for the CEO and its corresponding MSE is known only for the case where the prior on $\theta$, as well as the noise corrupting it at each location, are Gaussian.
+Namely, the Gaussian CEO is obtained from our setting when the $i$th encoder uses $R_i=1$ bits to transmit a message that is a function of $X_i = \theta + \sigma Z_i$, where $Z_i$ is standard normal.
+Consequently, a lower bound the MSE in our distributed setting is obtained by considering the minimal MSE in the Gaussian CEO as the number of terminals goes to infinity.
+This leads to the following proposition:
 \begin{prop} \label{prop:ceo_lower_bound}
@@
 Assuming $R_\Sigma = n$ and $L=n$, we get
-\begin{equation} \label{eq:ceo_optimal_sumrate}
+\begin{equation} \label{eq:ceo_optimal_sumrate2}
 n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
@@
 Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed encoding setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$, we see that
+By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
 \[
@@
 \]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ goes to zero. \par
+which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small. \par
 From the formulation of the CEO problem, it follows that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is exclusively attributed  to the ability to perform coding over blocks.
@@
 \section{Adaptive Estimation \label{sec:sequential}}
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $(2f(0)\sigma)^2$, which the ARE of the median of $X^n$.
+The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $\eta(0)\sigma^2$, which is the ARE of the median of the sample $X_1,\ldots,X_n$.
 Next, we provide a particular adaptive estimation scheme that attains this maximal efficiency.
-Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen.
-Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $(2f(0)\sigma)^2$.
-
-\subsection{Maximal efficiency of adaptive one-bit schemes}
-Our first results asserts that the ARE of any adaptive estimation scheme is bounded from above by $(2 f(0)\sigma )^2$, as follows from the following theorem:
-\begin{thm}[minimal relative effeciency] \label{thm:adpative_lower_bound}
-Let $\hat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Fig.~\ref{fig:sequential} and assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\sigma^2}{4f^2(0) n}+o(n^{-1}),
+Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $i-1$ messages is chosen.
+%Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $\eta(0)\sigma^2$.
+
+\subsection{Maximal efficiency in adaptive setting}
+Our first result asserts that the ARE of any adaptive encoding and estimation scheme is bounded from above by $\eta(0)\sigma^2$. %This result follows from the following theorem:
+\begin{thm}[maximal relative effeciency] \label{thm:adpative_lower_bound}
+Let $\hat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Fig.~\ref{fig:sequential}. Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
+\[
+n\mathbb E\left[ (\theta-\hat{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0},
 \]
@@
 2.13]{tsybakov2008introduction},\cite{gill1995applications} which bounds from below the MSE of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are given in the Appendix.\\
-
-Next, we present an adaptive estimation scheme that attains the maximal ARE of $(2f(0)\sigma)^2$.
+The details are in the Appendix.\\
+
+Theorem~\ref{thm:adpative_lower_bound} implies that any estimator $\hat{\theta}_n$ from any adaptive encoding scheme satisfies
+\[
+n\mathbb E\left[ (\theta-\theta_n)^2 \right] \leq  \frac{1}{4f^2(0)}+O(n^{-1}),
+\]
+and 
+\[
+\ARE(\hat{\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
+\]
+
+Next, we present an adaptive encoding and estimation scheme that attains the maximal ARE of $\eta(0)\sigma^2$.
 
@@
 \label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n \sgn (X_n - \theta_{n-1}), \quad n = 1,2,\ldots,
-\end{equation}
-and set the $n$th step estimation as
+\theta_n = \theta_{n-1} +  \gamma_n M_n, \quad n = 1,2,\ldots,
+\end{equation}
+where 
+\begin{equation}
+M_n = M_n (X_n,\theta_{n-1}) =\sgn (X_n - \theta_{n-1}).
+\end{equation}
+Define the $n$th step estimation as
 \begin{equation} \label{eq:sgd_est}
@@
 
-For the estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} we have the following results:
+We have the following results:
 \begin{thm} \label{thm:sgd}
@@
 \[
-\sqrt{n} \left( \hat{\theta}_n - \theta \right) \overset{d}{\rightarrow} \mathcal N \left(0,  \left( 2 f(0)\right)^{-2} \right).
+\sqrt{n} \left( \hat{\theta}_n - \theta \right) \overset{d}{\rightarrow} \mathcal N \left(0,  1/\eta(0) \right).
 \]
@@
 \[
-\lim_{n\rightarrow \infty} n\mathbb E \left[ \left(\theta-\hat{\theta}_n \right)^2 \right] = \left( 2 f(0)\right)^{-2}. 
+\lim_{n\rightarrow \infty} n\mathbb E \left[ \left(\theta-\hat{\theta}_n \right)^2 \right] = \frac{1}{\eta(0)}. 
 \]
@@
 \subsubsection*{Proof}
-The asymptotic behavior of \eqref{eq:sgd_est} is obtained from \cite[Thm. 4]{polyak1992acceleration} and \cite[Thm. 2]{polyak1990new}. The details are in the Appendix.\\
+The asymptotic behavior of \eqref{eq:sgd_est} follows from \cite[Thm. 4]{polyak1992acceleration} and \cite[Thm. 2]{polyak1990new}. The details are in the Appendix. \\
 
 Theorem~\ref{thm:sgd} implies that the estimator $\hat{\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the maximal ARE as established by Theorem~\ref{thm:adpative_lower_bound}.
+The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$.
+Consequently, the procedure above is known as averaged stochastic gradient descent for minimizing $x \to |x|$ given the data $X_1,\ldots,X_n$.
+The minimal value of this optimization is the sample median, and Theorem~\ref{thm:sgd} provides conditions for the sequence of gradient steps so that the algorithm converges to this minimum.
  \par
-Note that $\theta_0$ is not explicitly defined 
-in equation \eqref{eq:sgd_est}.
+%Note that $\theta_0$ is not explicitly defined in equation \eqref{eq:sgd_est}.
 A reasonable initialization for $\theta_0$ is $\theta_0 = \mathbb E [\theta]$, although Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
 Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$.
-Nevertheless, the bound in Theorem~\ref{thm:adpative_lower_bound} suggests that the non-asymptotic MSE can be reduced significantly whenever the location information $I_0$ is large.
-In what follows, we consider a greedy estimation procedure that uses the optimal decision rule given the prior distribution and the previous messages.
-In particular, this procedure exploit the prior information on $\theta$ provided by its prior.
+\\
+In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $M_n$ is a function of the current gradient descent estimate $\theta_{n-1}$ and its private sample.
+As we explain next, it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ using only a single ``access'' to such state.
+
+\subsection{Optimality using a Single Interaction}
+In Section~\ref{sec:preliminary} we considered an estimator that is based on messages of the form 
+\[
+M_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
+\]
+and showed that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
+%
+We now show that a similar encoding leads to an asymptotically normal estimator with the minimal variance $1/\eta(0)$, provided we may update once the threshold value $\theta_0$.
+In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
+We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate $\hat{\theta}_{n_1}$ based on $M_1,\ldots,M_{n_1}$, and then use $\hat{\theta}_{n_1}$ as the new threshold value to obtain messages $M_{n_1+1}, \ldots, M_n$.
+The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
+\begin{thm}
+For $i=1,\ldots,n$ set
+\[
+M_i = \begin{cases}
+ \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
+ \mathbf 1_{X_i \geq \hat{\theta}_{n_1} }& i={n_1+1,\ldots,n},
+\end{cases}
+\]
+where $n = n_1+ n_2$ and 
+\[
+\hat{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
+\frac{1}{n_1} \sum_{i=1}^{n_1} M_i 
+ \right).
+\] 
+Let 
+\[
+\hat{\theta}_{n_2}  = \hat{\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} M_i \right)
+\]
+and assume that $n_1(n) \rightarrow \infty$ and $n_1(n)/n \rightarrow 0$. Then:
+\begin{align*}
+ \sqrt{n} \left( \hat{\theta}_{n_2} - \theta  \right)^2  \overset{D}{\longrightarrow}  \mathcal N\left( 0, 1/\eta(0) \right).
+\end{align*}
+\end{thm}
+%
+%
+\begin{proof}
+For $t\in \mathbb R$, set
+\[
+p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
+\]
+From the central limit theorem
+\begin{align*}
+& \sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)  = \sqrt{\frac{n}{n_2}} \sqrt{n_2} \left(  p_{n_2}(t) - F(\theta - t) \right) \\
+& \overset{D}{\rightarrow} \mathcal N\left( 0, V(t) \right),
+\end{align*}
+where
+\[
+V(t) \triangleq F(\theta - t) F \left( t - \theta\right). 
+\]
+Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ we obtain
+\begin{align*}
+& \sqrt{n} \left( t + F^{-1}(\hat{p}_{n_2}(t)) - \theta \right) \\
+&= \sqrt{n} \left( g(\hat{p}_{n_2}(t)) - g \left(F(\theta-t) \right)  \right) \\
+& \overset{D}{\to} \mathcal N\left(0, 
+1/\eta(\theta-t) \right).
+\end{align*}
+%where this convergence is uniform in $t$ since all moments of $F^{-1}(\hat{p}_{n_2})$ exists. 
+By the law of large numbers we also have
+\[
+p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} M_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
+\]
+so that $\hat{\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity, and thus 
+\[
+\eta( \hat{\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
+\]
+By Slutsky's theorem we get
+\begin{align*}
+& \sqrt{n}\left(\hat{\theta}_{n_2} - \theta\right) \\
+& = \sqrt{n} \left( \hat{\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}(\hat{\theta}_{n_1})) - \theta \right)  \\
+& \overset{D}{\to} \mathcal N\left( 0, 
+1/\eta(0) \right). 
+\end{align*}
+\end{proof}
+%
+
+To conclude the adaptive estimation setting, we now consider estimation from one bit messages obtained via an encoding scheme that is one-step optimal.
+%Namely, each message obtained by employing the optimal the decision rule given the prior distribution and the previous messages.
 
@@
 \end{align*}
-Then for any estimator $\hat{\theta}$ which is a function of $M(X) \in \{-1,1\}$, we have
+For any estimator $\hat{\theta}$ which is a function of $M(X) \in \{-1,1\}$,
 \begin{equation}
 \label{eq:opt_cond}
-\mathbb E \left(\theta-\hat{\theta}(M)\right)^2 \geq  \mathbb E \left(\theta- \mathbb E[\theta|M^\star]\right)^2,
+\mathbb E \left(\theta-\hat{\theta}(M)\right)^2 \geq  \mathbb E \left(\theta- \mathbb E[\theta|M^\star]\right)^2.
 \end{equation}
@@
 \begin{proof}
-The proof is completed by the following two lemmas, proofs of which can be found in the Appendix:
+The proof is the result of the following two lemmas, proofs of which can be found in the Appendix:
 \begin{lem} \label{lem:unique}
-Let $f(x)$ be a log-concave probability density function. Then the equation 
+Let $f(x)$ be a log-concave density function. Then the equation 
 \begin{equation}
@@
 \begin{lem} \label{lem:adaptive}
-Let $U$ be an absolutely continuous random variable with pdf $P(du)$. Then the one-bit message $M^\star\in \{-1,1\}$ that minimizes
-\[
-\int \left( u - \mathbb E[U|M(u)]  \right)^2 P(du)
-\]
-is given by
-\[
-M^\star  =  \sgn(U - \tau),
+Let $U$ be an absolutely continuous random variable with PDF $P(du)$. Set 
+\[
+M^\star(u)  =  \sgn(u - \tau),
 \]
@@
 2 \tau = \frac{\int_{\tau}^\infty u P(du)} {\int_{\tau}^\infty P(du)} + \frac{\int_{-\infty}^{\tau} u P(du)}{\int_{-\infty}^{\tau} P(du)}.
+\]
+Then for any measurable $M: \mathbb R\to \{-1,1\}$,
+\[
+\int \left( u - \mathbb E[U|M^\star (u)]  \right)^2 P(du) \leq \int \left( u - \mathbb E[U|M(u)]  \right)^2 P(du). 
 \]
@@
 \begin{rem}
-The value of the optimal threshold as given in Theorem~\ref{thm:opt_one_step} is different than the one given in \cite[Eq.
-5]{1619423} for apparently the same problem.
-Indeed, it seems like Equation 4 there is erroneous.
+The optimal threshold given in Theorem~\ref{thm:opt_one_step} is different than the one given in \cite[Eq. 5]{1619423} for apparently the same problem. Indeed, it seems like Equation 4 in 
+\cite{1619423} is erroneous. 
 \end{rem}
 
-By applying at each step the optimal one-step decision rule from Theorem~\ref{thm:opt_one_step},  we arrive at the following adaptive encoding and estimation scheme: 
+By applying the optimal one-step decision rule from Theorem~\ref{thm:opt_one_step} at each step, we arrive at the following adaptive encoding and estimation scheme: 
 \begin{itemize}
@@
 \item[(3)] Obtain $\tau_n$ from equation \eqref{eq:fixed_point} with the updated prior $P_n(t)$.
-Note that $F(x)$ is log-concave so the updated prior $P_n(t)$ remains log-concave and thus a unique solution to \eqref{eq:fixed_point} is guaranteed by Lemma~\ref{lem:unique}.
+Note that if $P_{n-1}(t)$ and $F(x)$ are log-concave, so does $P_n(t)$.
+Therefore, $P_n(t)$ is log-concave by induction and a unique solution to \eqref{eq:fixed_point} is guaranteed by Lemma~\ref{lem:unique}.
 \item[(4)] Update the $(n+1)$th message as
@@
 \end{itemize}
-Since equation \eqref{eq:fixed_point} has no analytic solution in general, it is hard to derive the asymptotic behavior of the estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}.
+%Since Equation \eqref{eq:fixed_point} has no analytic solution in general, it is hard to derive the asymptotic behavior of the estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}.
 We conjecture, however, that it attains the asymptotic relative efficiency of $4f^2(0)$ under the same conditions on $f(x)$ in the problem formulation.
-In Fig.~\ref{fig:adaptive_error} we demonstrate this convergence in the case where $f(x)$ is the standard normal density.
+The normalized MSE of the estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update} is illustrated in Fig.~\ref{fig:adaptive_error} in the case where $f(x)$ is the standard normal density.
 Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the asymptotically optimal estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the sample mean for the same sample realization.
@@
 \begin{center}
-\begin{tikzpicture}
-\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
-%\node[color = blue,  minimum width=1cm, align = left] at (1.5,1.5) {assymptotically optimal \eqref{eq:sgd_est}};
-%\node[color = red, minimum width=1cm, align = left] at (1.5,0.55) {one-step optimal \eqref{eq:message_update}} ;
-\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left(\hat{\theta}_n - \theta \right)^2$};
-\node[scale = 0.7] at (0,-2.4) {$n$};
-%\draw[dashed] (-3.5,1.18) node[left, scale = 0.7] {$\frac{\pi}{2}$}-- (-3,1.18);
+\begin{tikzpicture}[scale = 0.6]
+\begin{axis}[
+width=10cm, height=6cm,
+xmin = 0, xmax=1000, 
+restrict y to domain = 0:3,
+ymin = 0,
+ymax = 3.4,
+samples=10, 
+xlabel= $n$,
+%ylabel = $n\mathbb E \left[\left(\theta - \hat{\theta}_n \right)^2 \right]$,
+%xtick={-3,-2,-1,0,1,2,3},
+%xticklabels={-3,-2,-1,0,1,2,3},
+ytick={0,1,1.57},
+yticklabels={0,1,$\pi/2$},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+
+\addplot[color = blue, solid, smooth] plot table [x = n, y = SGD, col sep=comma] {../SimRes/sim_res.csv};
+\addlegendentry{asymptotically optimal};
+
+\addplot[color = red, solid, smooth] plot table [x = n, y = Bayes, col sep=comma] {../SimRes/sim_res.csv};
+\addlegendentry{one step optimal};
+
+\addplot[color = green!30!black, solid, smooth] plot table [x = n, y = split, col sep=comma] {../SimRes/sim_res.csv};
+\addlegendentry{single interaction};
+
+\end{axis}
 \end{tikzpicture}
-\caption{Normalized empirical risk $n\left(\hat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $500$ Monte Carlo trials.
-In each trial, $\theta$ is chosen uniformly in the interval $(-3,3)$.
+%\begin{tikzpicture}
+%\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
+%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left(\hat{\theta}_n - \theta \right)^2$};
+%\node[scale = 0.7] at (0,-2.4) {$n$};
+%\end{tikzpicture}
+\caption{Normalized empirical risk $n\left(\hat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.
+In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$.
+The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage.
 \label{fig:adaptive_error}  }
@@
 
-\section{Distributed Estimation from Threshold Detectors \label{sec:distributed}}
-We now consider the distributed encoding setting described in Fig.~\ref{fig:distributed}, in which each single-bit message is independent of the other messages.
-Instead of searching for the optimal choice of the messages, we only consider messages that are obtained each sample against a prescribed threshold.
-Namely, each message is of the form
+\section{Distributed Estimation \label{sec:distributed}}
+We now consider the distributed encoding setting described in Fig.~\ref{fig:distributed} (Setting (iii) in the Introduction).
+In this setting each single-bit message $M_i$ is only a function of its private sample $X_i$, and hence $M_i$ characterized by its \emph{detection region}, defined as
+\[
+A_i = \left\{ x \in \mathbb R \,:\, M_i(x) = 1 \right\}.
+\]
+Consequently, $M_i$ is of the form
+\[
+M_i = \begin{cases} 1 & X_i \in A_i, \\
+-1 & X_i \notin A_i,
+\end{cases} \quad i\in \mathbb N,
+\]
+where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\\
+
+As a first step, we provide conditions under which the messages $M_1,M_2,\ldots$ define a local asymptotic normal family.
+
+\begin{thm} \label{thm:LAN1}
+For $n \in \mathbb N$ and $A_n \subset \mathbb R$,  define
+\begin{equation}
+\label{eq:precision_general}
+L_n(A_1,\ldots,A_n;\theta) \triangleq \frac{1}{n} \sum_{i=1}^n \frac{ \left(\frac{d}{d \theta} \Prob(X_i \in A_i) \right)^2 }{ \Prob(X_i \in A_i)\left(1- \Prob(X_i \in A_i) \right) }. 
+\end{equation}
+Consider the following conditions:
+\begin{itemize}
+\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is a log-concave, differentiable and symmetric density function such that $\eta(x)$ is unimodal.
+\item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
+\item[(iii)] The limit 
+\begin{equation}
+\label{eq:LAN_lim}
+\kappa(\theta) \triangleq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
+\end{equation}
+exists. 
+\end{itemize}
+For $i=1,\ldots,n$ set
+\[
+M_n = \begin{cases} 1 & X_n \in A_n, \\
+-1 & X_n \notin A_n. 
+\end{cases} 
+\]
+For any $\theta$, $f(x)$ and a sequence of sets $A_1,A_2,\ldots$ such that (i)-(iii) hold, and any $h\in \mathbb R$, we have
+\begin{align*}
+& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (M_1,\ldots,M_n) }{
+\mathbb P_{\theta} (M_1,\ldots,M_n)} \\
+& \overset{D}{\longrightarrow} \mathcal N\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
+\end{align*} 
+\end{thm}
+Theorem~\ref{thm:LAN1} provides conditions under which $M_1,\ldots,M_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}.
+An important conclusion of this theorem follows from the local asymptotic minimax property of estimators in LAN models (e.g.
+\cite{van2000asymptotic}):
+\begin{cor} \label{cor:LA_minimax}
+Let $\hat{\theta}_n$ be an estimator of $\theta \in \Theta$ from $M_1,\ldots,M_n$ with detection regions $A_1,\ldots,A_n$.
+Assume that as $n$ goes to infinity, conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
+Then for any bounded, symmetric, and quasi-convex function $L$,
+\[
+\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\hat{\theta}_{n} - \tau) \right) \right] \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
+\]
+where $Z \sim \mathcal N(0,1)$. In particular, for $L(x) = x^2$, 
+\[
+\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( \hat{\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
+\]
+\end{cor}
+%
+Corollary~\ref{cor:LA_minimax} says that when the messages define a LAN model, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model at $\theta$.
+This fact poses the upper bound of $\kappa(\theta)\sigma^2$ for the ARE of estimators in such models.
+\\
+
+Next, we show that under LAN no estimator can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly for all $\theta \in \Theta$.
+
+\subsection{Non-existence of a Uniformly Optimal Strategy}
+We now show that under LAN models, the optimal minimal risk $1/\eta(0)$ can only be attained at a finite number of points within $\Theta$.
+This fact implies in particular that, unlike in the adaptive setting, no distributed estimation scheme has ARE of $\eta(0)\sigma^2$ for all $\theta \in \Theta$.
+
+\begin{thm} \label{thm:non_existence}
+Under conditions (i)-(iii) in Theorem~\ref{thm:LAN1}, assume that each $A_i$ is a union of at most $K$ intervals.
+The number of points $\theta \in \Theta$ satisfying $\kappa(\theta) = \eta(0)$ is at most $2K$.
+\end{thm}
+
+\begin{proof}
+See Appendix. 
+\end{proof}
+%Theorem ~\ref{thm:non_existence} implies that for any distributed encoding scheme with messages defining a LAN family, and whose number of connected components is uniformly bounded, the set of point with MSe
+
+We next consider the case where each detection region is a half open interval, i.e., the $i$th message is obtained by comparing $X_i$ against a single threshold.
+As we explain, in this case, existence of a density for the sequence of threshold is enough to establish local asymptotic normality and leads to a closed form expression for the precision parameter and the ARE.
+
+%In the adaptive setting, it follows from Theorem~\ref{thm:sgd} that messages of this kind with appropriately chosen thresholds leads to an estimator with the optimal ARE of $\eta(0)sigma^2$.
+However, Theorem~\ref{thm:non_existence} implies that such ARE can only be attained for a negligible subset of the parameter space.
+As we shall see next, messages obtained by comparison against a sequence of thresholds cannot attain the optimal efficiency of expect perhaps on a single point of $\Theta$.
+
+\subsection{Threshold Detection}
+Assume now that each $M_i$ is of the form
 \begin{equation}
@@
 \end{equation}
-where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th detector applied by the encoder on it sample $X_i$.
-The \emph{density} $\lambda_n$ of the set of threshold values $\mathcal T_n  \triangleq \left\{t_1,\ldots,t_n \right\}$ is defined as their empirical distribution, i.e., for an interval $I \subset \mathbb R$,
-\[
-\lambda_n(I) = \frac{ \card \left( \mathcal T_n \cap I \right)}{n}.
-\]
-We further assume that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$.
-For example, this convergence occurs whenever $t_1,\ldots,t_n$ are drawn independently from the probability distribution $\lambda(dt)$.
+where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder.
+In other words, the detection region of $M_i$ is $A_i = (t_i,\infty)$ and $\mathbb P(X_i \in A_i) = F \left( M_i(t_i-\theta) \right)$.
+It follows that
+\begin{equation}
+L_n(A_1,\ldots,A_n;\theta) = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
+\label{eq:Ln_threshold}
+\end{equation}
+A natural condition for the existence of the limit \eqref{eq:Ln_threshold} as $n\to \infty$ is that the empirical distribution of the threshold values converges to a probability measure.
+Specifically, for an interval $I \subset \mathbb R$ define
+\[
+\lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
+\]
+Theorem~\ref{thm:LAN1} implies:
+\begin{cor} \label{cor:LAN_thresh}
+Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$.
+Then $\left\{ M_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a LAN family with precision parameter
+\[
+\kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
+\]
+\end{cor}
+
+Due to local asymptotic normality of $\{M_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $M_1,\ldots,M_n$, denoted here by 
+$\hat{\theta}^{ML}_n$, is local asymptotic minimax in the sense that 
+\[
+\sqrt{n} \left( \hat{\theta}^{ML}_n - \theta \right) \overset{D}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
+\]
+It follows that when the density of the threshold values converges to a probability measure, the ARE of the ML estimator is $\kappa(\theta)\sigma^2$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
+We note that $\hat{\theta}^{ML}_n$ is given by the root of
+\begin{equation}
+\label{eq:ML}
+\sum_{i=1}^n M_i \frac{f \left( t_i-\theta\right) }{F \left(M_i  (t_i-\theta)\right) },  
+\end{equation}
+which is the derivative of the log-likelihood function.
+This root is unique since the log-likelihood function is concave.
+Furthermore, for any $n \in \mathbb R$, we have that $\hat{\theta}^{ML}_n  \in [t_{(1)}, t_{(n)}]$ where $t_{(i)}$ denotes the $i$th element of $\{t_1,t_2\ldots\}$.
+Therefore, if $\{t_1,t_2\ldots\}$ is bounded (for example $\{t_1,t_2\ldots\} \subset \Theta$), then
+\[
+\lim_{n\to \infty} n\left(\hat{\theta}^{ML}_n - \theta \right)  = 1/\kappa(\theta), 
+\] 
+so that the ML estimator attains the local asymptotic MSE of Corollary~\ref{cor:LA_minimax}. \par
+%
+Since $\eta(x)$ attains its maximum at the origin, we conclude that
+\[
+\kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
+\]
+This upper bound on $\kappa(\theta)$ implies that the ARE of any distributed estimator based on a sequence of threshold detectors does not exceed $\eta(0)\sigma^2$, a fact that agrees with the lower bound under adaptive estimation derived in Theorem~\ref{thm:adpative_lower_bound}.
+%
+This upper bound on $\kappa(\theta)$ is attained only when $\lambda$ is the mass distribution at $\theta$.
+Since $\theta$ is apriori unknown, we conclude that estimation in the distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting.
+In other words, the ability to choose the threshold values in an adaptive manner based on previous messages strictly improves relative efficiency compared to a non-adaptive threshold selection.
 \\
 
-\subsection{Local Asymptotic Minimax Estimation}
-
-In order to estimate $\theta$ from the messages $M^n$, we consider the maximum likelihood (ML) estimator. The log-likelihood function of $\theta$ is given by
-\[
-l(M^n  |\theta ) =  \sum_{i=1}^n \log F \left( M_i \left( t_i - \theta \right) \right). 
-\]
-Since $F(x)$ is a log concave function, the log-likelihood function has a unique maximizer $\hat{\theta}_n$ which is the ML estimator.
-Specifically, the ML estimator $\hat{\theta}_{ML}$ is the unique root of
-\[
-\sum_{i=1}^n M_i \frac{f \left( t_i-\theta\right) }{F \left(M_i  (t_i-\theta)\right) } 
-\]
-
-Next, we show that under the assumptions above the sequence of messages $M^n$ defines a local asymptotic normal (LAN) family of probability distributions.
-As a result, we conclude that the ML estimator in estimating $\theta$ from $M^n$ satisfies a local asymptotic minimax property with respect to the \emph{precision} parameter of this LAN family \cite{van2000asymptotic}.
-\begin{thm} \label{thm:LAN}
-Let $f(x)$ be a log-concave, symmetric, and twice differentiable probability density function. Consider the sequence $M^n$ of threshold detectors 
-\[
-M_i = \sgn(X_i - t_i),\quad i=1,\ldots,n,
-\]
-with threshold density converges to a probability measure $\lambda$. The the following two statements hold:
-\begin{itemize}
-\item[(i)] Any estimator ${\theta}_n$ of $\theta$ which is a function of $M^n$ satisfies
-\[
-\liminf_{c\rightarrow \infty}\, \liminf_{n\rightarrow \infty} \sup_{\tau\,:\,| \tau - \theta| \leq \frac{c}{\sqrt{n}} }  n \mathbb E \left({\theta}_n - \tau \right)^2 \geq 1/K(\theta),
-\]
-where 
-\[
-K(\theta) \triangleq \int \eta\left(t-\theta \right) \lambda(dt),
-\]
-and 
-\[
- \eta(x) \triangleq \frac{ f^2\left( x \right)}{ F\left( x \right) \left(1-F(x) \right)}. 
-\]
-\item[(ii)] The asymptotic distribution of the ML estimator $\hat{\theta}_n$ is given by
-\[
-\sqrt{n}(\hat{\theta}_n - \theta) \overset{D}{\rightarrow} \mathcal N\left(0,1/K(\theta) \right).
-\]
-\end{itemize}
-\end{thm}
-
-\begin{rem}
-The condition that $\lambda_n(dt)$ converges weakly to $\lambda(dt)$ can be relaxed to the condition that for any $\theta \in \Theta$, 
-\[
-\frac{1}{n} \sum_{i=1}^n  \eta \left( t_i-\theta \right)  
-\]
-converges to $K(\theta)$.
-\end{rem}
-
-\begin{proof}
-See Appendix. 
-\end{proof}
-
-It follows from Theorem~\ref{thm:LAN} that the asymptotic MSE of the ML estimator is $1/(nK(\theta))$, and that this MSE is asymptotically minimal with respect to all local alternative estimators for $\theta$.
-In particular, we conclude that the ARE of any estimator based on threshold detection is $K(\theta)\sigma^2$.
-\par
-It follows from Proposition~\ref{prop:eta} that $\eta(x)$ attains its maximum at the origin. Since the thresholds density $\lambda$ integrates to $1$, it follows that
-\[
-K(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right)  = \eta(0) = 4f^2(0).
-\]
-This upper bound on $K(\theta)$ implies that the ARE of any distributed estimator is not smaller than $(2f(0)\sigma)^2$, a fact that agrees with the lower bound under adaptive estimation derived in Theorem~\ref{thm:adpative_lower_bound}.
-Furthermore,
-since this upper bound on $K(\theta)$ is attained whenever the density $\lambda$ is the mass distribution at $\theta$ which is unknown apriori, Theorem~\ref{thm:LAN} implies that estimation in the  distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting.
-In other words, the ability to adaptively choose the threshold value strictly improves the relative efficiency compared to a non-adaptive threshold selection.
-\\
-
-In what follow, we consider the asymptotic threshold density $\lambda(dt)$ that minimize the asymptotic MSE under the worst choice of $\theta \in \Theta$, or, what is the same, the expected value of $\mathbb E\left [1/K(\theta) \right]$ under the least favorable prior $\pi(\theta)$.
-%As we shall see, even with an optimal selection of the threshold density, the minimax risk increases linearly in $b$ as in Example~\ref{ex:uniform_density}.
+%We conclude that when the density of the threshold values converges to a probability measure, the ARE of the ML is $\kappa(\theta)$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
+
+%
+We conclude this section by considering the density of the threshold values that maximizes the ARE $\kappa(\theta)$ under the worst choice of $\theta \in \Theta$.
 
 \subsection{Minimax Threshold Density}
-%Assume that $\theta = [-b,b]$ and consider
-%\begin{equation} \label{eq:variational}
-%K^\star(b) = \sup_{\lambda} \min_{\theta \in [-b,b]}  {K(\theta)} = \int \eta\left( t-\theta \right) \lambda (dt), 
-%\end{equation}
-%where the supremum is over all probability measure $\lambda$ on $\mathbb R$.
-The distribution $\lambda(dt)$ that minimizes the asymptotic MSE $K(\theta)$ over the worst choice of $\theta$ in $\Theta = [-b,b]$ is given as the solution to the following optimization problem:
+The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta = (-T,T)$ is given as the solution to the following optimization problem:
 \begin{align}
@@
 \begin{split}
-\mathrm{maximize} \quad &  \min_{\theta \in [-b,b]} \int \eta(t-\theta) \lambda(dt)
+\mathrm{maximize} \quad &  \inf_{\theta \in (-T,T)} \int \eta(t-\theta) \lambda(dt)
 \\ 
@@
 \end{align}
-Denote the maximal value of the objective in \eqref{eq:var_cvx_minimax} by $K^\star(b)$.
-Since the objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda$, this problem can be solved using a convex program.
-By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
-\begin{align}
-\label{eq:cvx_minimax}
-\begin{split}
-\mathrm{maximize} \quad &  K \\ 
-\mathrm{subject~to} 
-\quad &  K \leq \mathbf H\lambda \\
-& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
-\end{split}
-\end{align}
-where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
-\begin{rem}
-The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$.
+The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program.
+We denote by $\kappa^\star(T)$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum.
+%
+%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
+%\begin{align}
+%\label{eq:cvx_minimax}
+%\begin{split}
+%\mathrm{maximize} \quad &  K \\ 
+%\mathrm{subject~to} 
+%\quad &  K \leq \mathbf H\lambda \\
+%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
+%\end{split}
+%\end{align}
+%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
+%\begin{rem}
+%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$.
 Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points.
 Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using
-\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
-\end{rem}
-
-Figure~\ref{fig:minimax_support} illustrates $\lambda^\star$ obtained as the solution to \eqref{eq:cvx_minimax} and the function $\mathbf H \lambda^\star$ for the case of $f(x)$ the standard  normal density.
-The minimal asymptotic ML risk $K^\star$ is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $b$.
-Also illustrated in these Figures is the MSE obtained when the threshold values are uniformly distribution over $\Theta = [-b,b]$, i.e.,
-$\lambda(dt) = dt/(2b)$. In this case we have
+%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
+%\end{rem}
+
+Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$.
+The minimal asymptotic risk $\kappa^\star(\theta)$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $T$.
+Also illustrated in these Figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = (-T,T)$, namely
 \begin{align}
-& K_{\unif} \triangleq \min_{\theta \in [-b,b]} \frac{1}{2b}\int_{-b}^{b} \eta\left(t-\theta\right) dt \nonumber
+& \kappa_{\unif} \triangleq \min_{\theta \in (-T,T)} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
  \\
 & = 
-\frac{1}{2b}\int_{-b}^{b} \eta\left(t\pm b\right) dt
-= \frac{1}{2b}\int_{0}^{2b} \eta(t) dt = \frac{1}{4b}\int_{-2b}^{2b} \eta(t) dt, \label{eq:uniform_risk}
+\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
+= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
 \end{align}
-so the ARE under a uniform distribution equals $\sigma^2 K_\unif$. \\
+From Corollary~\ref{cor:LAN_thresh}, we conclude that the ARE under a uniform distribution is $\kappa_\unif \sigma^2$. \\
 
@@
 xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-title = {$\sigma/b = 1/2$},
+xticklabels={-$T$, 0, $T$},
+title = {$\sigma/T = 1/2$},
 ytick={0,0.1,1},
@@
 
-\addplot[color = green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.5.csv};
+\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.5.csv};
 
@@
 xlabel= {$dt$},
-title = {$\sigma/b = 1/5$},
+title = {$\sigma/T = 1/5$},
 xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
+xticklabels={-$T$, 0, $T$},
 ytick={0,0.5},
@@
 
-\addplot[color = green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.2.csv};
+\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.2.csv};
 
@@
 xtick={-0.5,0,0.5},
-title = {$\sigma / b = 1/10$},
-xticklabels={-$b$, 0, $b$},
+title = {$\sigma / T = 1/10$},
+xticklabels={-$T$, 0, $T$},
 ytick={0,0.2},
@@
 
-\addplot[color = green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.1.csv};
+\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.1.csv};
 
@@
 xlabel= {$dt$},
-title = {$\sigma / b = 1/20$},
+title = {$\sigma / T = 1/20$},
 xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
+xticklabels={-$T$, 0, $T$},
 ytick={0,0.1},
@@
 
-\addplot[color = green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.05.csv};
+\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.05.csv};
 
@@
 \caption{\label{fig:minimax_support}
-The optimal density $\lambda^\star$ (blue) that minimizes the maximum asymptotic ML risk for $f(x)$ a standard normal density $\Theta = [-b,b]$, and various values of $\sigma$.
+Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x)$ the normal density with variance $\sigma^2$. 
+%Here the parameter space is $\Theta = (-T,T)$.  
 %$\lambda^\star$ in these figures is obtained by solving \eqref{eq:cvx_minimax}. 
-The continuous curve (red) represents the asymptotic risk for a fixed $\theta \in [-b,b]$ under the optimal density, so its maximal value is minimax risk.
-The dashed curve is the asymptotic risk a fixed $\theta \in [-b,b]$ under a uniform distribution over $[-b,b]$, so its maximal value is given by \eqref{eq:uniform_risk}.
+The continuous curve (red) represents the reciprocal of the asymptotic risk for at a fixed $\theta \in [-T,T]$ under the optimal density, so the minimax risk is the inverse of its minimal value.
+The dashed curve (green) is the reciprocal of the asymptotic risk for a fixed $\theta$ under a uniform distribution over $\Theta$ and its minimal value the inverse of \eqref{eq:uniform_risk}.
 }
@@
 width=8cm, height=6cm,
-xmin = 0, xmax=2, 
+xmin = 0, xmax=2.5, 
+xmode = log,
 restrict y to domain = 0:100,
@@
 samples=1, 
-xlabel= {$\sigma/b$},
+xlabel= {$\sigma/T$},
 %xtick={-0.5,0,0.5},
@@
 ]
-\addplot[color = red, smooth] plot table [x = x, y = y, col sep=comma] {../Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{$\lambda^\star(dt)$};
-
-\addplot[color = green, smooth, dashed, line width = 0.5pt] plot table [x = x, y = z, col sep=comma] {../Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{$dt/(2b)$};
+\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {../Figs/minmax_ARE_b0.5.csv};
+\addlegendentry{optimal threshold density};
+
+\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {../Figs/minmax_ARE_b0.5.csv};
+\addlegendentry{uniform threshold desnity};
 \end{axis}
 \end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/b$ for $P_X = \mathcal N(\theta,\sigma^2)$.
-The dashed curve represents the minimal ARE under a uniform threshold density given by $\sigma^2/K_{\unif}$, where $K_{\unif}$ is given by \eqref{eq:uniform_risk}.
+\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x)$ the centered normal density with variance $\sigma^2$ and $\Theta = (-T,T)$.
+The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
 }.
@@
 
+%We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
+Next, we prove that with any set of messages obtained via a distributed strategy, there exits at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
+
+\begin{comment}
+\subsection{Asymptotic Bayes Risk}
 \begin{figure}
@@
 \caption{\label{fig:opt_density}
-The threshold density $\lambda(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=b^2/3$ is the variance of the prior.
+Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=b^2/3$ is the variance of the prior.
 }
@@
 
-\subsection{Asymptotic Bayes Risk}
  We consider now the problem of minimizing the asymptotic Bayes risk $
@@
 \par
-%
-%\begin{figure}
-%\begin{center}
-%\begin{tikzpicture}
-%\node at (0,0) {\includegraphics[scale=0.5]{dist_bound_Gauss_prior}};
-%\node at (0,-2.5) {$\sigma/\sigma_\theta$};
-%\node[rotate = 90] at (-3.5,0) {(expected asymptotic risk)$/\sigma^2$};
-%\node at (1,0) {$\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$ };
-%%\node at (-2,-1.05) {$\frac{\pi}{2}$};
-%%\node[rotate = -45] at (-1.8,1.2) {\color{red} true };
-%%\node[rotate = -70] at (-0.5,0) {\color{blue} bound };
-%\end{tikzpicture}
-%\caption{Expected asymptotic risk $\mathbb E K^{-1}(\theta)$ in estimation from threshold detectors versus $\sigma/\sigma_\theta$ for a Gaussian prior with variance $\sigma_\theta^2$.
-The optimal asymptotic threshold density $\lambda$ (red) is obtained by solving \eqref{eq:cvx_average}.
-The bound (blue) is obtained using \eqref{eq:upper_bound}.
-%\label{fig:dist_bound_Gaussian}  }
-%\end{center}
-%\end{figure}
-%
 \begin{figure}
@@
 \]
-Therefore, the expected value of $K^{-1}(\theta)$ satisfies
+Therefore, the expected value of $\kappa^{-1}(\theta)$ satisfies
 \begin{align}
-\mathbb E  \frac{1}{K(\theta)}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
+\mathbb E  \frac{1}{\kappa(\theta)}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
 \end{align}
@@
 The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$.
-The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $K^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.
+The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $\kappa^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.
 
 \begin{example} \label{ex:bound}
-Consider the case $P_X = \mathcal N(\theta, \sigma^2)$. The bound in \eqref{eq:bound_Taylor} implies 
+In the normal case $P_X = \mathcal N(\theta, \sigma^2)$, the bound in \eqref{eq:bound_Taylor} implies 
 \[
@@
 %\label{eq:asymp}
-%\mathbb E [1/K(\theta)] = \frac{\pi}{2} + \left( \frac{\pi}{2} - 1\right) \left(\frac{\sigma_\theta}{\sigma} \right)^2 + o \left(\frac{1}{\sigma} \right)^3. 
+%\mathbb E [1/\kappa(\theta)] = \frac{\pi}{2} + \left( \frac{\pi}{2} - 1\right) \left(\frac{\sigma_\theta}{\sigma} \right)^2 + o \left(\frac{1}{\sigma} \right)^3. 
 %\end{align}
@@
 %\end{proof}
+\end{comment}
 
 \section{Conclusions \label{sec:conclusions}}
-We considered the MSE risk in estimating the mean of a normal distribution from a sequence of bits obtained by encoding each sample from the distribution using a single bit.
-Under an adaptive encoding of the samples, we showed that the no estimator can attain asymptotic MSE or relative efficiency larger than that of the median of the samples.
-We also showed that this lower bound is tight by presenting an adaptive estimation procedure from this bit sequence that is as efficient as the median.
-We also consider a one-step optimal scheme that minimizes the MSE given any set of previously obtained bits.
-Numerical simulations shows that the one-step optimal scheme attains the optimal relative efficiency for the normal distribution.
+We considered the MSE risk in estimating the mean of a symmetric and log-concave distributions from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
+%
+In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency (ARE) larger than that of the median of the samples.
+We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median.
+%We further showed that the optimal MSE and ARE can be attained using only a single adaptation. Namely, a single round of communication between {\color{red} the estimator and the encoder} . 
+We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the MSE given any set of previously obtained bits.
+%Numerical simulations shows that the one-step optimal scheme attains the optimal relative efficiency for the normal distribution.
 \par
-In the distributed setting, we considered the estimation from threshold detection under the assumption that the empirical distribution of the threshold values converges to a probability distribution.
-For this setting, we showed that the maximum likelihood estimator is local asymptotically minimax, and that the relative efficiency of this estimator is strictly smaller than that of the sample median.
+In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, and thus provided a local asymptotic minimax bound on the MSE and ARE under such conditions.
+We concluded that in this case, the optimal performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in the distributed setting.
+We further considered the special case of messages encoded using threshold detection rules.
+We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax error.
  \\
@@
 
-\appendix
+\onecolumn
+
+\appendices
 
 \section{Proofs \label{app:proofs}}
-This appendix contains the proofs of Proposition~\ref{prop:eta}, Theorems \ref{thm:adpative_lower_bound}, \ref{thm:sgd}, \ref{thm:opt_one_step}, and \ref{thm:LAN}.
-
-\subsection{Proof of Proposition~\ref{prop:eta}}
-(i) Since $f(x)$ is log-concave, so does $F(x)$.
-There exists $h(x)$ that is non-decreasing, concave, twice differntiable, such that $F(x) = e^{h(x)}$.
-In addition, $f(x) = h'(x)F(x)$ so $h'(x) \geq 0$, and $h'(x)$ is decreasing since $h''(x) \leq 0$ because $h(x)$ is concave.
-In fact, $h'(x) = f(x)/F(x)$ is non-constant for any $x$ in the support of $f(x)$, so $h'(x)$ is strictly decreasing in this support.
-It easily verified that
-\[
-\eta(x) = h'(x) h'(-x).
-\]
-It follows that $\eta(x)$ is symmetric. We now show that $\eta(x)$ is decreasing for $x>0$. Let $0<x_1 < x_2$. Consider
-\begin{align}
-& \eta(x_2) - \eta(x_1) = h'(x_2)h'(-x_2) - h'(x_1)h'(-x_1) \nonumber \\
-&  =h'(x_2)h'(-x_1) \left(\frac{h'(-x_2)}{h'(-x_1)} - \frac{h'(x_1)}{h'(x_2)}  \right). \label{eq:eta_proof}
-\end{align}
-Now, because $h'(x)$ is decreasing, we have that $h'(x_1) \geq h'(x_2)$ and $h'(-x_2) \geq  h'(-x_1)$.
-If follows that the brackets in the RHS of \eqref{eq:eta_proof} are negative, whereas $h'(x_2) h'(-x_1)$ is non-negative since $h'(x)$ is non-negative.
-Hence $\eta(x_2) \leq \eta(x_1)$.
-It follows that $\eta(x)$ is a monotone decreasing function for $x>0$.
-It is left to show that it is strictly decreasing for $x>0$ in the support of $f(x)$.
-Since $h'(x)$ is strictly decreasing, $\eta(x)$ may be constant only for $x>0$ for which $h'(x)/h'(-x)$ is a constant.
-But for all such $x$s, $h'(x)$ is strictly increasing, $h'(-x)$ is strictly decreasing, and thus $h'(x)/h'(-x)$ is strictly increasing.
-\par
-(ii) Because $F(x)$ is differentiable, for any $a \in \mathbb R$ there exists $a\leq c \leq x$ such that 
-$F(x) = F(a) + f(c) (x-a)$. For $a=0$, and using the fact that $f(x)$ is non-increasing for $x>0$ we have
-\[
-\frac{f(x)}{F(x)} = \frac{f(x)}{0.5 + f(c) x }  \leq \frac{f(x)}{f(c)} \frac{1}{x} \leq \frac{1}{x}.  
-\]
-From symmetry of $f(x)$ we get that $f(-x)/F(-x) \leq 1/x$ for $x>0$. Finally, noting that $h(x)\rightarrow 0$ as $x\rightarrow \infty$, we conclude that for $x>0$, 
-\[
-\eta(x) = h'(-x)h'(x) \leq \frac{h(x)}{x} \leq \frac{1}{x}. 
-\]
+
+\begin{lem} \label{lem:bound_intervals}
+Let $f(x)$ be a log-concave, symmetric, and differentiable density such that $\eta(x)$ is strongly unimodal. For any $x_1 > \ldots > x_n \in \mathbb R$, 
+\begin{equation}
+\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
+{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
+\leq \max_i \eta(x_i). \label{eq:lem_bound_intervals}
+\end{equation}
+In particular, if $|x_i|>\epsilon > 0$ for all $i=1,\ldots,n$, then 
+\[
+\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
+{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
+\leq \eta(\epsilon) < 0. 
+\]
+\end{lem}
+
+\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals}} 
+Denote 
+\[
+\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
+\]
+\[
+\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
+\]
+so 
+\[
+\eta(x) =  \frac{  \left(\delta_1(x) \right)^2}{\Delta_1(x)
+(1-\Delta_1(x))}
+= \frac{  \left( f (x) \right)^2}{ F(x)\left(1-F(x)\right)^2}. 
+\]
+We use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:lem_bound_intervals} is bounded from above by $\max_i \eta(x_i)$. The case $n=1$ is trivial. Assume that 
+\begin{equation}
+\frac{ \left( \delta_n \right)^2} 
+{\Delta_n \left(1- \Delta_n \right) } \leq \max_i \eta(x_i)
+\label{eq:lem_bound_intervals_proof}
+\end{equation}
+for all integers up to $n = N-1$ and consider the case $n = N$. 
+%
+The maximal value of the LHS of \eqref{eq:lem_bound_intervals_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
+\begin{align*}
+& g(x_1,\ldots, x_N) \triangleq  2 \log \delta_N -  \log \Delta_N -  \log \left(1 - \Delta_N  \right),
+\end{align*}
+ The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
+\[
+\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(-1)^{k+1} f(x_k)}{1-\Delta_N },
+\]
+and we conclude that the gradient of $g$ vanishes if and only if
+\begin{equation}
+\label{eq:gradient_zero}
+\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
+\end{equation}
+%
+Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable. We have 
+\[
+\frac{f'(x)}{f(x)} = c'(x), \quad x\in \mathbb R,
+\]
+which is anti-symmetric, non-negative for $x<0$,  non-positive for $x>0$, and non-increasing since $c(x)$ is concave.
+Therefore, if $c'(x_i) = c'(x_{i+1})$ for some $i =1,\ldots,N-1$, then either (1) $x_i = x_{i+1}$ or (2) $c'(x)$ is the zero function.
+Since (2) violates the assumption that $f(x)$ is a density function, we conclude that $c'(x)$ is an injection.
+%
+As a result, \eqref{eq:gradient_zero} is satisfied if and only if $x_1 = \ldots = x_N$.
+For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_proof} equals $\eta(x_1) = \max_i \eta(x_i)$ hence the statement holds.
+For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
+Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_proof} is not attained at the line $x_1=\ldots=x_N)$.
+We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_proof} is maximized at the borders.
+That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
+As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_proof} is zero and thus this case reduces to the case $n= N-2$.
+A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$, or  $x_i, x_{i+1}$ for some $i$.
+It is left to consider the cases:
+\begin{itemize}
+\item[(1)]  $x_N \to -\infty$.
+\item[(2)] $x_1 \to \infty$.
+\end{itemize}
+Under case (1) we have
+\begin{align*}
+\lim_{x_N \to -\infty} \frac{  \delta_N^2} 
+{\Delta_N \left(1- \Delta_N \right) }
+ = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^2} 
+{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)} ,
+\end{align*}
+which is smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis. Under case (2) we have
+\begin{align*}
+&  \lim_{x_1 \to \infty}
+\frac{ \delta_N} 
+{\Delta_N\left(1- \Delta_N \right) } \\
+=
+& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)} 
+{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right) \left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right) }  \\
+& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^2 } 
+{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right) },
+\end{align*}
+where $x'_{m} = x_{m+1}$. The last expression is also smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis.  \QEDA \\
 
@@
 
-We first prove the following two lemmas:
-\begin{lem} \label{lem:bound_intervals}
-Let $f(x)$ be a log-concave, symmetric, and differentiable pdf. Denote by $F(x)$ the corresponding CDF. Then for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, we have 
-\begin{equation}
-\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)  } \leq 4f^2(0). \label{eq:bound_intervals}
-\end{equation}
-\end{lem}
-
+We first prove the following lemma:
 \begin{lem} \label{lem:fisher_bound}
-Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$. Assume that for a Borel measurable $A$, 
+Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that $\eta(x)$ is unimodal. For a Borel measurable $A$ set, 
 \[
@@
 \]
-Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $4f^2(0)$.
+Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $\eta(0)$.
 \end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals}} 
-We now use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:bound_intervals} is bounded from above by $\eta(0)$. \par
-The case $n=1$ it follows from Proposition~\ref{prop:eta}. 
-Assume now that \eqref{eq:bound_intervals} holds for all integers up to some $n = N-1$ and consider the case $n = N$.
-The maximal value of the LHS of \eqref{eq:bound_intervals} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq 2 \log \left(  \sum_{k=1}^{N} (-1)^{k+1} f(x_k) \right) - \\
-&  \log
-\left( \sum_{k=1}^N (-1)^{k+1} F(x_k) \right)
--\log \left(1 -  \sum_{k=1}^N (-1)^{k+1} F(x_k) \right) \\
-& = 2 \log \delta_N - \log \Delta_N - \log \left(1 - \Delta_N  \right),
-\end{align*}
-where we denoted $\delta_N \triangleq \sum_{k=1}^{N} (-1)^{k+1} f(x_k)$ and $\Delta_N =  \sum_{k=1}^N (-1)^{k+1} F(x_k)$. The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(-1)^{k+1} f(x_k)}{1-\Delta_N }.
-\]
-We conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-From the case $n=1$ and for $x$ in the support of $f(x)$, we have
-\[
-\frac{f'(x)}{f(x)} = h''(x)+\left(h'(x)\right)^2 < 0 . 
-\]
-As a result, $\frac{f'(x)}{f(x)}$ is one to one and \eqref{eq:gradient_zero} implies $x_1 = \ldots = x_N$.
-If $N$ is odd then for $x_1=\ldots =x_N$ we have that the LHS of \eqref{eq:bound_intervals} equals $\eta(x_1)$ which was shown to be smaller than $\eta(0)$.
-If $N$ is even, then for any constant $c$ the limit of the LHS of \eqref{eq:bound_intervals} as $(x_1,\ldots,x_N)\rightarrow (c,\ldots,c)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:bound_intervals} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:bound_intervals} is maximized at the borders, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches plus or minus infinity.
-For simplicity we only consider the cases where $x_N$ goes to minus infinity or $x_1$ goes to plus infinity (the general case where the first $m$ coordinates goes to infinity or the last $m$ to minus infinity is obtained using similar arguments).
-Assume first $x_N \rightarrow -\infty$.
-Then the LHS of \eqref{eq:bound_intervals} equals
-\begin{align*}
-\frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^2} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right) } ,
-\end{align*}
-which is smaller than $\eta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then the LHS of
-\eqref{eq:bound_intervals} equals
-\begin{align*}
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^2} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right) }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^2} 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right) },
-\end{align*}
-where $x'_{m} = x_{m+1}$. The last expression is also smaller than $\eta(0)$ by the induction hypothesis. \QEDA \\
 
@@
 
-We now consider the proof of Theorem~\ref{thm:adpative_lower_bound}.
+We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
 In order to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$, we first note that without loss of generality, each message $M_i$ can is of the form
@@
 where $A_i \subset \mathbb R$ is a Borel measurable set. 
-Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = M^{-1}(1)$.
-Consider the conditional distribution $P({M^n|\theta})$ of $M^n$ given $\theta$.
-We have
+%Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = M^{-1}(1)$.
+Consider the conditional distribution $P({M^n|\theta})$ of $M^n$ given $\theta$. We have 
 \begin{align}
@@
 Using the symmetry of $f(x)$ around zero, it follows that $\psi'(x) = 2f(x)$ and thus $\psi'(0) = 2f(0)$.
-It is now easy to verify that the rest of the conditions in Thm.~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$.
+It is now easy to verify that the rest of the conditions in Theorem~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$.
 Since
@@
 \]
-Thm.~\ref{thm:sgd}-(i) follows from Thm.~\ref{thm:polyak_juditsky}.  \\
-
-In order to prove Thm.~\ref{thm:sgd}-(ii), we consider:
+Theorem~\ref{thm:sgd}-(i) follows from Theorem~\ref{thm:polyak_juditsky}.  \\
+
+In order to prove part (ii) of Theorem~\ref{thm:sgd} we use the following result from \cite{polyak1990new}:
 \begin{thm}{ \cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
@@
 Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution for which the Fisher information exits.
-Let $\psi(x)$ and $\chi(x)$ be defined as in Thm.~\ref{thm:polyak_juditsky}-(iii) and satisfies the conditions there.
+Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{thm:polyak_juditsky}-(iii) and satisfies the conditions there.
 Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$,
@@
 
-We now use Thm.~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = -\sgn(-x)$, $Z_n = \theta-X_n$ and $U_n = \theta_n$. From \eqref{eq:polyak_new_measurements} we have
+We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = -\sgn(-x)$, $Z_n = \theta-X_n$ and $U_n = \theta_n$. From \eqref{eq:polyak_new_measurements} we have
 \begin{align*} 
@@
 for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
-the conditions in Thm.~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
+the conditions in Theorem~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
 In particular, $\psi'(0) = (2f(0))^{-2}$.
 Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$.
-Thm.~\ref{thm:polyak_new} implies
+Theorem~\ref{thm:polyak_new} implies
 \[
@@
 
-\subsection*{Proof of Theorem~\ref{thm:LAN}}
-We will prove that $P_\theta(m_i) = \mathbb P(M_i = m_i)$, $\i=1,\ldots,n$ is a local asymptotic normal (LAN) family  with \emph{precision} parameter $K(\theta)$.
-The statements in the theorem then follows from the local asymptotic minimax theorem of LAN families \cite{van2000asymptotic}.
-\\
-
-The probability mass distribution of $M^n$ is given by
-\[
-P_\theta(m^n) =  \prod_{i=1}^n F \left( m_i (t_i - \theta)\right), \quad m^n \in \{-1,1\}^n.
-\]
-Consider the log-likelihood ratio under a sequence of local alternatives $\theta' = \theta + h/\sqrt{n}$ for some $h\in \mathbb R$:
+\subsection*{Proof of Theorem~\ref{thm:LAN1}}
+The log probability mass distribution of $M^n=(M_1,\ldots,M_n)$ is given by
+\begin{align*}
+& \log \Prob_\theta(m^n) = \sum_{i=1}^n \left( \frac{m_i+1}{2} \log  \Prob(X_i\in A_i) + 
+\frac{1-m_i}{2} \log \Prob(X_i\in A_i) \right), \quad m^n \in \{-1,1\}^n. 
+\end{align*}
+Consequently, 
 \begin{align}
-\log \frac{ P_{\theta + \frac{h}{\sqrt{n}}}(m^n)} { P_\theta (m^n) }& =  \sum_{i=1}^n \log \left( F \left( m_i (t_i - \theta - h/\sqrt{n} ) \right)\right)  - \sum_{i=1}^n \log \left( F \left( m_i (t_i - \theta) \right) \right).
+& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(m^n)} { \Prob_\theta (m^n) } = \sum_{i=1}^n    \frac{m_i+1}{2} 
+\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} + 
+\sum_{i=1}^n  \frac{1-m_i}{2} 
+\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}. 
 \label{eq:LAN_proof1}
 \end{align}
-Since $f(x)$ is differentiable, $\log F(x)$ is twice differentiable and we may write
-\[
-\log F(x+t) = \log F(x) + \frac{f(x)}{F(x)}h - \frac{t^2}{2}\left( \frac{f'(x)}{F(x)} - \frac{f^2(x)}{F^2(x)} \right) + o(t^2).
-\]
-Therefore, \eqref{eq:LAN_proof1} can be written as
-\[
-- h \sum_{i=1}^n  \frac{m_i}{\sqrt{n} }  \frac{ f \left(m_i (t_i-\theta) \right)} {F \left( m_i (t_i-\theta) \right) }  - \frac{h^2}{2 n} \sum_{i=1}^n  \left( \frac{f' \left(m_i (t_i-\theta) \right) }{F\left(m_i (t_i-\theta)\right) }- \frac{ f^2\left(m_i (t_i-\theta) \right)}{F^2\left(m_i (t_i-\theta) \right)}   \right) + o(1/n)
-\]
-
-The proof is completed by proving the following two lemmas:
-\begin{lem} \label{lem:LAN1}
+For each $i=1,\ldots,n$, write 
+\[
+A_i = \bigcup_{k=1}^{K_i} \left(t_{i,k},t_{i,k+1} \right),
+\]
+where $t_{i,1}<\ldots<t_{i,K_i}$ and, with a slight abuse of notation, $t_{i,1}$ and $t_{i,K_i}$ may also be $-\infty$ or $+\infty$, respectively. Thus
+\[
+\Prob_{\theta}(X_i \in A_i) = \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta).
+\]
+In particular, since $f$ is differentible, $\Prob_{\theta}(X_i \in A_i)$ is twice differentiable, and we may write
+\begin{align*}
+\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)  = \Prob_{\theta} (X_i \in A_i) + \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \frac{h}{\sqrt{n}} + o(h), 
+\end{align*}
+and thus
+\begin{align*}
+& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} = \log \left(1 + \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} + o(h) \right) \\
+& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2 + o(h^2).
+\end{align*}
+Similarly, we have
+\begin{align*}
+& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} \\
+& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 + o(h^2).
+\end{align*}
+From \eqref{eq:LAN_proof1} we obtain
+\begin{align*}
+& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(m^n)} { \Prob_\theta (m^n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
+\left( 
+\frac{m_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
+ \frac{1-m_i}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}   \right) \\
+ & - \frac{h^2}{2n} 
+ \sum_{i=1}^n 
+\left( 
+ \frac{m_i+1}{2} 
+\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
++ 
+ \frac{1-m_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 \right) + o(h^2) \\
+\end{align*}
+%
+Noting that 
+\[
+\frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} = \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)},
+\]
+the proof is completed by proving the following two claims:
+\begin{itemize}
+\item[I.] 
 For $i=1,\ldots,n$ denote 
 \[
-U_i = -M_i \frac{ f \left( M_i (t_i - \theta) \right)}{ F \left( M_i (t_i - \theta)\right) }. 
+U_i = \frac{M_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
+ \frac{1-M_i}{2}  \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}. 
 \]
@@
 \[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0, K(\theta) \right). 
-\]
+\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0, \kappa(\theta) \right). 
+\]
+\item[II.]
+For $i=1,\ldots,n$ denote 
+\[
+V_i =  \frac{M_i-1}{2} 
+\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
++ 
+ \frac{1-M_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2.
+\]
+Then 
+\[
+\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} \kappa(\theta). 
+\]
+\end{itemize}
+\subsubsection*{Proof of Claim I}
+First note that 
+\begin{align*}
+\mathbb E  [U_i] & = 
+ \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}   \Prob (M_i=1)   + 
+ \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}   \Prob (M_i=-1)  = 0. 
+\end{align*}
+In addition,
+\begin{align*}
+& \mathbb E U_i^2 = 
+\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2  \Prob (M_i=1)   + 
+\left( \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2 \Prob (M_i=-1) \\
+& =
+ \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)} +  
+  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)} \\
+ & =  
+  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left(1-\Prob_{\theta}(X_i \in A_i) \right)} 
+\end{align*}
+Therefore
+\[
+\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 = L_n(A_1,\ldots,A_n) \overset{a.s.}{\longrightarrow} \kappa(\theta)
+\]
+for any $\theta \in \Theta$ such that the limit above exists.
+We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition for his version of the central limit time: for any $\delta>0$ we have that
+\begin{align*}
+& \mathbb E \left| U_i \right|^{2+\delta} =
+ \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
+  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} 
+\end{align*}
+and
+\begin{equation}
+\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} } { \left( \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta} = 
+\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
+\label{eq:Lyaponov}
+\end{equation}
+Next, we claim that there exits $\delta>0$ and $K>0$, that are independent of $n$, such that
+\begin{align}
+\frac{1}{n} \sum_{i=1}^n \mathbb E  |U_i|^{2+\delta}  < M \label{eq:Lyaponov_num}
+\end{align} 
+for all $n$ large enough. To see this, note that
+\begin{align*}
+& \mathbb E |U_i|^{2+\delta} = 
+ \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
+  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}  \\
+  &  = \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
+  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} } 
+  \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \\
+  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
+  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}, 
+\end{align*}
+where the last transition is because 
+\[
+ \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \leq 1. 
+\]
+We now use the fact that each $A_i$ is a finite union of interval and consider the following lemma, proof of which is given in the appendix:
+\begin{lem} \label{lem:bound_intervals_delta}
+Let $f(x)$ be a log-concave, symmetric, and differentiable PDF such that $\eta(x)$ is unimodal.  There exists $\delta>0$ such that for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, 
+\begin{equation}
+\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^{2+\delta} }
+{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} } 
+\leq  2^\delta f^{2+\delta}(0). 
+\label{eq:lem_bound_intervals_delta}
+\end{equation}
 \end{lem}
-\begin{lem} \label{lem:LAN2}
-For $i=1,\ldots,n$ denote
-\[
-V_i =  -\left[ \frac{f' \left(M_i (t_i-\theta) \right) }{F\left(M_i (t_i-\theta)\right) }- \frac{ f^2\left(M_i (t_i-\theta) \right)}{F^2\left(M_i (t_i-\theta) \right)} \right] .
-\]
-Then 
-\[
-\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} K(\theta). 
-\]
-\end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:LAN1}} 
-First note that 
-\begin{align*}
-\mathbb E  [U_i] & = \mathbb E\left[ \mathbb E  [U_i|M_i] \right] \\
-& =  -\frac{f(t_i-\theta)}{F(t_i-\theta)} \mathbb P (M_i=1) + \frac{f(\theta-t_i)}{F(\theta-t_i)} \mathbb P (M_i=-1) \\
-& = -f(t_i-\theta) + f(\theta-t_i) = 0.
-\end{align*}
-In addition,
-\[
-\mathbb E U_i^2 = \frac{ f^2 \left( t_i-\theta \right) } { F \left( t_i-\theta \right) \left(1- F \left( t_i-\theta \right) \right)},
-\]
-and therefore
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 \rightarrow K(\theta).
-\]
-
-We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition for his version of the central limit time: for any $\delta>0$ we have that 
-\[
-\mathbb E \left| U_i \right|^{2+\delta} = \left( \frac{f^{2+\delta} \left(t_i-\theta \right)  }{F^{2+\delta} \left( t_i-\theta \right)} + \frac{f^{2+\delta} \left(t_i-\theta \right)  }{1-F^{2+\delta} \left(t_i-\theta\right)} \right),
+
+Lemma~\ref{lem:bound_intervals_delta} implies 
+\begin{align*}
+  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
+  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} = \frac{\left| \sum_{k=1}^{K_i} (-1)^k f(x_{i,k}-\theta) \right|^{2+\delta} }
+  { \left( \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta} \left( 1 - \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta}} \\
+  & \leq 2^\delta f^{2+\delta}(0). 
+\end{align*}
+In particular, we conclude that 
+\[
+\frac{1}{n} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} \leq 2^\delta f^{2+\delta}(0), 
+\]
+and thus for any $\delta>0$ the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we conclude that 
+\[
+\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0,\kappa(\theta) \right). 
+\]
+
+\subsubsection*{Proof of Claim II} 
+We have:
+\begin{align*}
+\mathbb E V_i  & = 
+ \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)}  
++ 
+ \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)}  \\
+ & = 
+  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left( 1-\Prob_{\theta}(X_i \in A_i) \right)}  
+\end{align*}
+ We conclude that:
+\begin{equation} \label{eq:LAN_limit_cond}
+\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =   L_n(A_1,\ldots,A_n)  \to \kappa(\theta)
+\end{equation}
+Since the $V_i$s are independent of each other, Kolmogorov's law of large numbers implies
+%(e.g. \cite[Theorem 10.2.3]{sen1994large}) 
+\[
+\frac{1}{n} \sum_{i=1}^n  V_i \overset{a.s.}{\longrightarrow} \kappa(\theta)
+\]
+for any $\theta \in \Theta$ for which the limit \eqref{eq:LAN_limit_cond} exists.
+
+\QEDA
+
+\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals_delta}} 
+Denote 
+\[
+\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
+\]
+\[
+\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
 \]
 and 
-\begin{equation}
-\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} } { \left( \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta} = 
-\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E U_i^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
-\label{eq:Lyaponov}
-\end{equation}
-The functions $\log F(x)$ and $\log (1-F(x)) = \log F(-x)$ are differentiable, so that $f(x)/F(x)$, $f(x)/(1-F(x))$, and hence $\left(f(x)/F(x)\right)^{2+\delta}$ and $\left(f(x)/(1-F(x)) \right)^{2+\delta}$ are integrable.
-As $n$ goes to infinity, we have
-\[
-\frac{1}{n}\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta}  \rightarrow  \int \left( \frac{ f^{2+\delta} \left(t-\theta\right)}{F^{2+\delta}\left(t-\theta\right)} + \frac{ f^{2+\delta} \left(t-\theta\right)}{1-F^{2+\delta} \left(t-\theta\right)} \right) \lambda(dt),
-\]
-from which we conclude that the numerator in \eqref{eq:Lyaponov} goes to zero.
-Since the denumerator in \eqref{eq:Lyaponov} goes to $K^\delta(\theta)$, the entire expression goes to zero and hence Lyaponov's condition is satisfied.
-From Lyaponov's central limit theorem we conclude that
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0,K(\theta) \right). 
-\]
-\QEDA
-
-\subsubsection*{Proof of Lemma~\ref{lem:LAN2}}
-
-We have:
-\begin{align*}
-\mathbb E V_i  & = \left[ \frac{ f^2\left(t_i-\theta \right)}{F\left( t_i-\theta \right)} - f' \left(t_i-\theta \right)  \right] 
-+ \left[ \frac{ f^2\left(\theta-t_i \right)}{F\left( \theta - t_i \right)} - f' \left( \theta - t_i \right) \right] \\
-& = \frac{f^2(\theta - t_i)}{F(\theta-t_i)F(t_i-\theta)} = \eta(\theta - t_i).
-\end{align*}
-where above we used the facts  $f'(-x) = -f'(x)$ and $F(x)+F(-x)=1$. We conclude that:
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =  \frac{1}{n} \sum_{i=1}^n  \frac{f^2\left( t_i-\theta \right)} { F \left( t_i - \theta \right)\left(1-F \left( t_i - \theta \right) \right)} \rightarrow K(\theta).
-\]
-Finally, it follows from Kolmogorov's law of large numbers (e.g. \cite[Thm. 10.2.3]{sen1994large}) that
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E V_i \overset{a.s.}{\rightarrow} K(\theta). 
-\]
-\QEDA
+\[
+\eta_\delta(x) \triangleq  \frac{  \left(\delta_1(x) \right)^{2+\delta}}{  \left(\Delta_1(x)  \right)^{1+\delta}
+(1-\Delta_1(x))^{1+\delta}}
+= \frac{  \left( f (x) \right)^{2+\delta}}{ \left(F(x) \right)^{1+\delta}(1-F(x))^{1+\delta}}. 
+\]
+The proof is by induction on $n$.
+For the case $n=1$ the LHS of \eqref{eq:lem_bound_intervals_delta} equals $\eta_\delta(x)$.
+Note that $\eta_\delta(0) = 2^\delta f^{2+\delta}(0)$, so it is enough to prove that $\eta_\delta(0)$ attains it maximum at $x=0$.
+We have $\eta_\delta(x) = \eta^{1+\delta}(x)/f^\delta(x)$, and thus
+\[
+\log \eta_\delta'(x) = (1+\delta) \frac{\eta'(x)}{\eta(x)} - \delta \frac{f'(x)}{f(x)}. 
+\]
+By Assumption~\ref{assump:failure_rate} both terms above are negative for $x>0$, so that $\log \eta_\delta'(x) \leq 0$ if and only if
+\begin{equation} \label{eq:delta_proof_cond}
+(1+\delta) \left| \frac{\eta'(x)}{\eta(x)} \right| \geq \delta \left| \frac{f'(x)}{f(x)} \right|, \qquad x>0.
+\end{equation}
+Also by Assumption~\ref{assump:failure_rate}, for $x>0$ we have
+\[
+0 > (\log \eta(x))' = \frac{h'(x)}{h(x)}-\frac{h'(-x)}{h(-x)},
+\]
+so that \eqref{eq:delta_proof_cond} is satisfies for $\delta>0$ small enough.
+
+Next, assume that 
+\begin{equation}
+\frac{ \left( \delta_n \right)^{2+\delta}} 
+{\left(\Delta_n \right)^{1+\delta}\left(1- \Delta_n \right)^{1+\delta} } \leq \eta_\delta(0) = 2^\delta f^{2+\delta}(0) . 
+\label{eq:lem_bound_intervals_delta_proof}
+\end{equation}
+for all integers up to $n = N-1$ and consider the case $n = N$. 
+%If $x_{i+1} = x_i$ for some $i=1,\ldots,N-1$, then then the indices $i$ and $i+1$ may  be removed from all sums in \eqref{eq:lem_bound_intervals}, what brings us to the case $n = N-2$.
+Therefore, we may assume that $x_1 < \ldots < x_n$.
+%
+The maximal value of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
+\begin{align*}
+& g(x_1,\ldots, x_N) \triangleq  (2+\delta) \log \delta_N - (1+\delta) \log \Delta_N - (1+\delta) \log \left(1 - \Delta_N  \right),
+\end{align*}
+ The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
+\[
+\frac{\partial  g}{\partial x_k} = \frac{(2+\delta) (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(1+\delta)(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(1+\delta)(-1)^{k+1} f(x_k)}{1-\Delta_N }.
+\]
+We conclude that the gradient of $g$ vanishes if and only if
+\begin{equation}
+\label{eq:gradient_zero_delta}
+\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N(1+\delta)}{2+\delta} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
+\end{equation}
+From the same reason as in the proof of Lemma~\ref{lem:bound_intervals}, \eqref{eq:gradient_zero_delta} is satisfied if and only if $x_1 = \ldots = x_N$.
+For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_delta_proof} equals $\eta_\delta(x_1)$ which was shown to be smaller than $\eta_\delta(\epsilon)$.
+For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
+Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is not attained at the line $x_1=\ldots=x_N)$.
+We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is maximized at the borders.
+That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
+As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_delta_proof} is zero and thus this case reduces to the case $n= N-2$.
+A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$,  $x_i, x_{i+1} = -\epsilon$ for some $i$, or $x_i, x_{i+1} = \epsilon$ for some $i$.
+It is therefore enough to consider the cases:
+\begin{itemize}
+\item[(1)]  $x_N \to -\infty$.
+\item[(2)] $x_1 \to \infty$.
+\end{itemize}
+Assume first $x_N \rightarrow -\infty$. Then 
+\begin{align*}
+\frac{ \left( \delta_N \right)^{2+\delta}} 
+{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  }
+ = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
+{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)^{1+\delta} } ,
+\end{align*}
+which is smaller than $\eta_\delta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
+\begin{align*}
+& \frac{ \left( \delta_N \right)^{2+\delta}} 
+{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  } \\
+=
+& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
+{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right)^{1+\delta} }  \\
+& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^{2+\delta}} 
+{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)^{1+\delta}\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right)^{1+\delta} },
+\end{align*}
+where $x'_{m} = x_{m+1}$ for $m=1,\ldots, N-1$. The last expression is smaller than $\eta_{\delta}(0)$ by the induction hypothesis.  \QEDA \\
+
+\subsection*{Proof of Theorem~\ref{thm:non_existence}}
+
+Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta) = \eta(0)$. 
+%
+Since $M_1,M_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, for $\theta \in \Xi$ if and only if
+\begin{equation}
+\label{eq:non_existence_proof}
+\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0). 
+\end{equation}
+By assumption, we have $M_i^{-1} = A_i$ where $A_i$ can be expressed as
+\[
+A_i = \cup_{i=1}^K (a_{i,k},b_{i,k}), 
+\]
+where $a_{i,1} \leq b_{i,1} \leq \ldots \leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values $-\infty$ and $\infty$, respectively. Denote
+\[
+\mathcal B_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\}.
+\]
+For any $\theta$ and $\epsilon>0$, denote 
+\[
+S_n(\theta, \epsilon) \triangleq \left\{ i\leq n \,:\, (\theta-\epsilon,\theta+\epsilon) \cap \mathcal B_i \neq \emptyset \right\}
+\]
+In words, $S_n$ contains all integers smaller than $n$ in which an $\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals consisting $A_i$. 
+%
+We now claim that 
+if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. Indeed, for such $\theta$ we have
+\begin{align}
+& L_n(A_1,\ldots,A_n; \theta) \nonumber \\
+& = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
+\frac{ \left(\sum_{k=1}^{K}  f(\theta - b_{i,k})- f(\theta - a_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
+& 
++ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(b_{i,k}-\theta) - f(a_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
+& \overset{(a)}{\leq}
+\frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
+ \label{eq:non_existence_proof1}
+\end{align}
+where $(a)$ follows from Lemma~\ref{lem:bound_intervals} and the fact that for $i \in S_n(\theta, \epsilon)$, 
+\[
+\max\left\{ \max_k \eta(b_{i,k}-\theta) , \max_k \eta(a_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
+\]
+Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, \eqref{eq:non_existence_proof1}, and thus $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.
+\par
+For $k\in \mathbb N$, assume by contradiction that there exists $N \geq 2K + 1$ distinct elements
+$\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$ consists of at most $K$ intervals, we have that 
+\begin{equation}
+\label{eq:few_optimality_points_proof}
+\card (\cup_{i=1}^n \mathcal B_i) \leq 2 n K. 
+\end{equation}
+Fix $\epsilon>0$ such that 
+\[
+\epsilon < \frac{1}{2}\min_{i\neq j} |\theta_i - \theta_j|. 
+\]
+Since for each $\theta \in \Theta$ we have $S_n(\theta, \epsilon) \to 1$, there exists $n$ large enough such that 
+\[
+\card \left(S_n(\theta_i, \epsilon) \right) \geq n \left(1-\frac{1}{2N} \right)
+\]
+for all $i=1,\ldots,N$.
+However, $S_n(\theta_1,\epsilon), \ldots S_n(\theta_N,\epsilon)$ are disjoint, so the cardinallity of their union is at least $n\left(1-\frac{1}{2N} \right)N$ which is grater than $2nK + n/2$ in contradiction to \eqref{eq:few_optimality_points_proof}.
 
@@
 \bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,/Users/Alon1/LaTex/bibtex/sampling}
-
-\section{Related Results in Source Coding}
-The estimation problem we consider can be seen as the quantization, compression or encoding of the samples, and the  decoding of the parameter $\theta$ from the encoded version of the sample.
-Therefore, this problem is closely related to various setting in coding and information theory.
-The goal of this section is to illustrates this connection and review related results that are relevant in our case.
-
-%As opposed to the aforementioned line of works, we focus on estimation of samples taken from a single distribution in the finite blocklength performance.
-We are interested in particular in addition restrictions on the communication and information sharing between the encoders.
-For example, our main focus is the case where the observer must communicate a single bit upon drawing from the distribution.
-This is in contrast to the asymptotic setting where the observer can encode the outcome of $n$ draws at once using a single $n$ bit message.
-Alternately, such setting can be seen as having $n$ different observers, each is capable of observing a single realization and transmit a single bit.
-
-%{\color{red} The Van Trees inequality was extended to the estimation of multiple parameters in \cite{bobrovsky1987}. It is closely related with the }
-
-\subsection{Statistical Inference under Communication Constraints}
-The works \cite{han1987hypothesis, zhang1988estimation, 720540} consider various problems of statistical inference under multiterminal lossy compression.
-In the setting of \cite{han1987hypothesis, zhang1988estimation, 720540}, each terminal $I$ observes $n$ samples from the distribution and is allotted $nR_i$ bits to communicate its estimate.% Consequently, our case (iii) is obtained from this setting by taking $n=1$, $R_i=1$, and number of terminals grow with $n$.
-The main focus of these works is the difference between inference with communication constraint and the unconstrained vanilla statistical estimation setting, as the number of samples $n$ goes to infinity subject to a total finite rate constraint.
-Our case (i) can be seen as a special case of this setting where with a single terminal and $R_1 = 1$.
-However, as explained in \cite[Sec.
-III]{720540}, in this setting the unconstrained inference performance is always attained when all samples are taken from the same distribution.
-Indeed, in an i.i.d setting the \emph{type} of the sample \cite{csiszar1998method} is a sufficient statistics for any estimation task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples.
-For this reason, attention is given in these works to inference problems involving multiple distributions observed at different locations, hence the name \emph{multiterminal}.
-
-\subsection{Sigma-Delta Encoding}
-
-and covariance function \cite[Eq. 25]{53738}
-\[
-R(k) = \mathbb E M_{n+k} M_n = \theta^2 + O \left( \frac{1}{\sigma \sqrt{ k} } \right). 
-\]
-{\color{red} This is not enough to deduce convergence. Need to go over the paper and check if rate of convergence can be deduced. Also do simulations BEFORE that. \\
-
-What is the error in estimating the mean of stationary ergodic process ? 
-}
-Since the SDM is a special case of the sequential scheme, we conclude that the MSE of any SDM with a noisy DC signal is bounded from below by $n^{-1} \sigma^2 \pi/2 $.
-
-%Even with such arguably simple setting, we will see that the performance limit in the estimating task based on single bit observations provides an interesting setting for discussion that bridges classical works in statistics, coding theory, information theory and optimization.
-
-\subsection*{Source coding}
-With a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample.
-Setting (ii) includes as a special case the sigma-delta modulation (SDM) analog-to-digital conversion scheme with a constant input $\theta$ corrupted by Gaussian noise $Z_i$, as was considered in \cite{53738}.
-While it was shown there that the output of the modulator converges to the true constant input, the rate of this convergence was not analyzed and cannot be derived directly from the results of \cite{53738}.
-As a corollary from the results in this paper we conclude that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-Finally, the remote multiterminal source coding setting of \cite{berger1996ceo} corresponds to the case of $n$ rate-constrained encoders, each observing a noisy version of an information source.
-The difference between this setting and ours is that in ours the parameter of interest is not an information source.
-By assuming a prior distribution on this parameter, the CEO provides a lower bound on the estimation error in the fully distributed setting (iii).
-This lower bound can be attained if we were to consider the average error in multiple independent realizations of our problem rather than a single realization as we do here.
-\\
+\bibliography{/Users/kipnisal/LaTex/bibtex/IEEEfull,/Users/kipnisal/LaTex/bibtex/sampling}
 
@@
 Indeed, the it follows from \cite[Eq.
-?]{KipnisRini2017} that the following distortion is achievable for the CEO
+?]{KipnisRini2017} that the following distortion is achievable in the CEO problem:
 \[

### 2018-09-06 SimRes/reproduce_sim_script.py

@@ -1,0 +1,83 @@
+
+# CJ has its own randState upon calling
+# to reproduce results one needs to set
+# the internal State of the global stream
+# to the one saved when ruuning the code for
+# the fist time;
+import os,sys,pickle,numpy,random;
+CJsavedState = pickle.load(open('CJrandState.pickle','rb'));
+numpy.random.set_state(CJsavedState['numpy_CJsavedState']);
+random.setstate(CJsavedState['CJsavedState']);
+    
+sys.path.append('.');
+from aux import *
+import numpy as np
+
+nMonte = 10000
+
+n = 1000
+
+Amax = inv_Phi(0.95)
+Amin = -inv_Phi(0.95)
+
+err_var_split = np.zeros(n+1)
+err_split = np.zeros(n+1)
+err_var_grad = np.zeros(n+1)
+err_grad = np.zeros(n+1)
+err_var_bayes = np.zeros(n+1)
+err_bayes = np.zeros(n+1)
+err_var_sdm = np.zeros(n+1)
+err_sdm = np.zeros(n+1)
+err_var_smp = np.zeros(n)
+err_smp = np.zeros(n)
+
+sig = 1
+
+for i in range(nMonte) :
+    th = Amin + (Amax-Amin)*np.random.rand()# uniform prior over (Amin,Amax)
+    z = sig * np.random.randn(n)
+    y = z + th
+    
+    #Split
+    split_ratio = np.sqrt(n) / n
+    th_hat_split = [split_est(y[:k], split_ratio = split_ratio, th0 = 6*(np.random.rand()-0.5), inv_PDF = inv_Phi) for k in range(n+1)]
+    err_split += th-np.array(th_hat_split)
+    err_var_split += (th-np.array(th_hat_split))**2
+    
+    #SGD
+    th_hat_grad = grad_descent(y, g0 = 0.68)
+    err_grad += th-np.array(th_hat_grad)
+    err_var_grad += (th-np.array(th_hat_grad))**2
+    
+    #Bayes
+    th_hat_bayes = bayes_adaptive(y, Amin, Amax)
+    err_bayes += th-np.array(th_hat_bayes)
+    err_var_bayes += (th-np.array(th_hat_bayes))**2
+    
+    #th_hat_sdm = sigma_delta(y,v0  = 0)
+    #err_sdm += th-np.array(th_hat_sdm)
[…]

### 2019-01-07 Writeups/onebit_full_V2.tex
changed title, fixed grammer

@@
 
-\title{\LARGE \bf Mean Estimation from Single-Bit Measurements}
-%
-%\author{
-%\IEEEauthorblockN{Alon Kipnis}
-%\IEEEauthorblockA{Department of Electrical Engineering \\
-%Stanford University\\
-%Stanford, CA\\}
-%\and
-%\IEEEauthorblockN{John C. Duchi}
-%\IEEEauthorblockA{Department of Statistics \\
-%and Department of Electrical Engineering \\
-%Stanford University\\
-%Stanford, CA\\}
-%\and
-%\IEEEauthorblockN{Andrea J. Goldsmith}
-%\IEEEauthorblockA{Department of Electrical Engineering \\
-%Stanford University\\
-%Stanford, CA\\}
-%}
+\author{
+    \IEEEauthorblockN{John C. Duchi\IEEEauthorrefmark{1}\IEEEauthorrefmark{2} and
+Alon Kipnis\IEEEauthorrefmark{1} \\}
+    \IEEEauthorblockA{\IEEEauthorrefmark{1}Stanford University, Department of Statistics \\}
+    \IEEEauthorblockA{\IEEEauthorrefmark{2}Stanford University, Department of Electrical Engineering. }
+}
+
+\title{\LARGE \bf Mean Estimation from One-Bit Measurements}
 
@@
 We consider the problem of estimating the mean of a symmetric log-concave distribution under the following constraint: only a single bit per sample from this distribution is available to the estimator.
-We study the mean squared error (MSE) risk in this estimation as a function of the number of samples, and hence number of bits, from this distribution.
+We study the mean squared error (MSE) risk in this estimation as a function of the number of samples, and hence the number of bits, from this distribution.
 Under an adaptive setting in which each bit is a function of the current sample and the previously observed bits, we show that the optimal relative efficiency compared to the sample mean is the efficiency of the median.
@@
 %
-We also consider a distributed setting where each one bit message is only a function of a single sample.
+We also consider a distributed setting where each one-bit message is only a function of a single sample.
 We derive lower bounds on the MSE in this setting, and show that the optimal efficiency can only be attained at a finite number of points in the parameter space.
 %
-Finally, we analyze a distributed setting where the bits are obtained by comparing each sample against a prescribed threshold, and consider the threshold density that minimizes the maximal MSE. 
-%
-Our results indicates that estimating the mean from one bit measurements is equivalent to estimating the sample median from these measurements.
+Finally, we analyze a distributed setting where the bits are obtained by comparing each sample against a prescribed threshold.
+Consequently, we consider the threshold density that minimizes the maximal MSE.
+%
+Our results indicate that estimating the mean from one-bit measurements is equivalent to estimating the sample median from these measurements.
 In the adaptive case, this estimate can be done with vanishing error for any point in the parameter space.
@@
 %
-%Therefore, our results indicates that, rather surprisingly, parametric estimation from the coarsest form of quantization incurs only a multiplicative penalty factor on the number of measurements.
+%Therefore, our results indicate that, rather surprisingly, parametric estimation from the coarsest form of quantization incurs only a multiplicative penalty factor on the number of measurements.
 For example, this factor is $\pi/2$ for the normal distribution.
@@
 For example, this scenario arises in sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit.
-In these situations, the ability to estimate a particular parameter from the data is dictated not only by the quality of observations and their number, but also by the available bandwidth for communicating between the sensors and the central estimator.
+In these situations, the ability to estimate a particular parameter from the data is dictated not only by the quality of observations and their number but also by the available bandwidth for communicating between the sensors and the central estimator.
 The question that we ask is to what extent a parametric estimation task is affected by this constraint on communication, and what are the fundamental performance limits in estimating a parameter subject to such restriction.
 \par
-This paper answers this question in a particular setting: the estimation of the mean $\theta$ of a symmetric log-concave distribution with a finite variance, under the constraint that only a single bit can be communicated on each sample from this distribution.
-As it turns out, the ability to share information before committing on each single-bit message dramatically affects the performance in estimating $\theta$.
-We therefore distinguish among three settings:
+This paper answers this question in a particular setting: the estimation of the mean $\theta$ of a symmetric log-concave distribution with finite variance, under the constraint that only a single bit can be communicated on each sample from this distribution.
+As it turns out, the ability to share information before committing on each one-bit message dramatically affects the performance in estimating $\theta$.
+We, therefore, distinguish among three settings:
 \begin{itemize}
- \item[(i)\,\,] \emph{Centralized} encoding: all $n$ encoders confer and produce a single $n$ bit message. 
- \item[(ii)\,] \emph{Adaptive} or \emph{sequential} encoding: the $n$th encoder observes the $n$th sample and the $n-1$ previous messages (bits).
- \item[(iii)] \emph{Distributed} encoding: the $n$th message is only a function of the $n$th observation.
+ \item[(i)\,\,] \emph{Centralized} encoding (Fig.~\ref{fig:centralized}): all $n$ encoders confer and produce a single $n$ bit message. 
+ \item[(ii)\,] \emph{Adaptive} or \emph{sequential} encoding (Fig.~\ref{fig:sequential}): the $n$th encoder observes the $n$th sample and the $n-1$ previous messages (bits).
+ \item[(iii)] \emph{Distributed} encoding (Fig.~\ref{fig:distributed}): the $n$th message is only a function of the $n$th observation.
  \end{itemize}
@@
 Namely, the excess MSE or ARE we derive serves as the most optimistic estimate for the risk in estimating a signal that varies in time or space under the one bit per measurement constraint.
-Such situtations are considered in \cite{baraniuk2017exponential, jacques2013robust, plan2013one, li2017channel, choi2016near}.
+Such situations are considered in \cite{baraniuk2017exponential, jacques2013robust, plan2013one, li2017channel, choi2016near}.
 \\
@@
 %
-In this paper we show that a similar results does not hold in setting (ii): the ARE of any adaptive estimation scheme is at most the ARE of the sample median.
+In this paper we show that a similar result does not hold in setting (ii): the ARE of any adaptive estimation scheme is at most the ARE of the sample median.
 Specifically, when the samples are drawn from the normal distribution, this ARE equals $\pi/2$, showing that the one-bit constraint increases the effective sample size in estimating $\theta$ by at least $\pi/2 \approx 1.57$ compared to estimating it without the bit constraint.
@@
 However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation problem and hence its exact value is unknown.
-As a result, a non-trivial exploration exploitation trade-off arises in this case.
+As a result, a non-trivial exploration-exploitation trade-off arises in this case.
 %Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$. 
@@
 Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $n-1$ messages, is not guaranteed to be globally optimal.
-Therefore, while we characterize the optimal one-bit message given the previous messages, this characterization does not necessarily  leads to an upper bound on the ARE.
+Therefore, while we characterize the optimal one-bit message given the previous messages, this characterization does not necessarily lead to an upper bound on the ARE.
 Instead, our result on the maximal ARE is obtained by bounding the Fisher information of any $n$ adaptive messages and using an appropriate information inequality.
 \par
-In addition to encoding and estimation schemes that leads to optimal results, we also consider two additional ``natural'' schemes.
+In addition to encoding and estimation schemes that lead to optimal results, we also consider two additional ``natural'' schemes.
 Specifically, in setting (ii) we consider the one-bit optimal scheme, i.e., the case of a greedy encoder that given the $n$th sample and the previous $n-1$ bits, provides a bit that minimizes the $n$-step MSE.
@@
 In addition to these two results, we also derive the one-step optimal strategy in which the message sent at step $i$th is designed to minimize the MSE given this message and the previous $i-1$ messages.
-Furthermore, we demonstrates numerically that the MSE under this strategy converges to $\pi \sigma^2/(2n)$.\\
+Furthermore, we demonstrate numerically that the MSE under this strategy converges to $\pi \sigma^2/(2n)$.\\
 
@@
 As the variance $\sigma^2$ goes to zero, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is solved by a bisection style method over the parameter space.
-Therefore, the general case of non-zero variance is a reminiscent of the noisy binary search problem with possibly infinite number of unreliable tests \cite{cicalese2002least, Karp:2007:NBS:1283383.1283478}.
-However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a constant input corrupted by a Gaussian noise.
-Using a SDM, Wong and Gray \cite{53738} showed that the output of the modulator converges to the true constant input almost surely, so that a SDM provides a consistent estimator for setting (ii).
+Therefore, the general case of non-zero variance is reminiscent of the noisy binary search problem with a possibly infinite number of unreliable tests \cite{cicalese2002least, Karp:2007:NBS:1283383.1283478}.
+However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a constant input corrupted by Gaussian noise.
+Using an SDM, Wong and Gray \cite{53738} showed that the output of the modulator converges to the true constant input almost surely, so that an SDM provides a consistent estimator for setting (ii).
 The rate of this convergence, however, was not analyzed and cannot be derived from the results of \cite{53738}.
-In particular, our results for setting (ii) imply that the asymptotic rate of convergence of the MSE in SDM to a constant input under an additive white Gaussian nosie is at most $\sigma^2\pi/2$ over the number of feedback iterations.
+In particular, our results for setting (ii) imply that the asymptotic rate of convergence of the MSE in SDM to a constant input under an additive white Gaussian noise is at most $\sigma^2\pi/2$ over the number of feedback iterations.
 Baraniuk et.
@@
 When the parameter space $\Theta$ is finite, Tsitsiklist \cite{tsitsiklis1988decentralized} showed that when the cardinality of $\Theta$ is at most $M$ and the probability of error criterion is used, then no more than $M(M-1)/2$ different detection rules are necessary in order to attain probability of error decreasing exponentially with the optimal exponent.
-%That is, beyond $M(M-1)/2$ some decision rules can be repeated without lossing optimality.
-Furthermore, in a version of this problem for the adaptive sestting \cite{5751320}, it was shown that, with a specific two-stages feedback, there is no gain in feedback compared to the fully distributed setting.
-Our results implies that the ARE in the distributed setting with threshold detection rules is strictly larger than that in the adaptive setting, suggesting that the case of a finite $\Theta$ is very different than the case where $\Theta$ is an open set.\par
-%
-As we explain in detail in Section~ \ref{sec:preliminary}, the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}, leads to a lower bounds on the MSE in setting (iii).
+%That is, beyond $M(M-1)/2$ some decision rules can be repeated without losing optimality.
+Furthermore, in a version of this problem for the adaptive setting \cite{5751320}, it was shown that, with specific two-stage feedback, there is no gain in feedback compared to the fully distributed setting.
+Our results imply that they ARE in the distributed setting with threshold detection rules is strictly larger than that in the adaptive setting, suggesting that the case of a finite $\Theta$ is very different from the case where $\Theta$ is an open set.\par
+%
+As we explain in detail in Section~ \ref{sec:preliminary}, the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}, leads to lower bounds on the MSE in setting (iii).
 For the case of a Gaussian distribution, this lower bound bounds the ARE to be at most $3/4$.
@@
 The specialization of their result to our setting, by taking $m=n$ and $R=1$, leads to looser lower bounds then we derive here for cases (ii) and (iii).
-Looser bounds can also be obtained from \cite{zhang1988estimation, han2018distributed} that considered inference and distributed estimation under data compression constraint \cite{DBLP:journals/corr/abs-1802-08417, zhang1988estimation, han2018distributed}.
+Looser bounds can also be obtained from \cite{zhang1988estimation, han2018distributed, } that considered inference and distributed estimation under data compression constraint \cite{DBLP:journals/corr/abs-1802-08417, zhang1988estimation, han2018distributed, xu2017information}.
 \\
@@
 \end{center}
-\caption{\label{fig:centralized} Centralized encoding using one bit per sample on average.}
+\caption{\label{fig:centralized} Centralized one-bit encoding: encoder sends $n$ bits after observing $n$ samples.}
 \end{figure}
@@
 \end{center}
-\caption{\label{fig:sequential} Adaptive single-bit encoding: the $n$th encoder delivers a single bit message which is a function of its private sample $X_n$ and the previous messages $M_1,\ldots,M_{n-1}$.}
+\caption{\label{fig:sequential} Adaptive one-bit encoding: the $n$th encoder delivers a single bit message which is a function of its private sample $X_n$ and the previous messages $M_1,\ldots,M_{n-1}$.}
 \end{figure}
@@
 \end{center}
-\caption{\label{fig:distributed} Distributed single-bit encoding: the single-bit message produced by each encoder is only a function of its private sample $X_i$.}
+\caption{\label{fig:distributed} Distributed one-bit encoding: the one-bit message produced by each encoder is only a function of its private sample $X_i$.}
 \end{figure}
@@
 %
-The main problem we consider is the minimal value of \eqref{eq:error_def} as a function of $n$ under different choices of the encoding functions in cases (i), (ii), and (iii). \\
+The main problems we consider in this paper are the minimal value of \eqref{eq:error_def}, as a function of $n$ and $f(x)$, under different choices of the encoding functions in cases (i), (ii), and (iii).
+\\
 
@@
 \]
-is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function of since $f(x)$ is log-concave \cite{bagnoli2005log}. 
-%
-For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as shown in Fig.~\ref{fig:eta}. 
+is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function since $f(x)$ is log-concave \cite{bagnoli2005log}. 
+%
+For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as illustrated in Fig.~\ref{fig:eta}. 
 %
@@
 
-\section{Simple Bounds \label{sec:preliminary}}
-On a first impression it may not be clear whether consistent estimation of the mean is even possible in the adaptive and centralized settings.
+\section{ Consisten Estimation and Of-the-shelf Bounds \label{sec:preliminary}}
+On a first impression, it may not be clear whether consistent estimation of the mean is even possible in the adaptive and centralized settings.
 On the other hand, it may seem as if estimation in these cases is trivial as in the centralized setting (i).
 %
-In this section we settle such skepticism by providing simple lower and upper bounds to the relative efficiency under setting (iii). We show that:
+We next settle such skepticism by deriving lower and upper bounds to the relative efficiency under setting (iii). We show that:
 \begin{itemize}
 \item[I.] A consistent estimator with an asymptotically normal distribution always exists in setting (iii), and hence in setting (ii). 
-\item[II.] For the normal distribution, the ARE in setting (iii) is at most $3/4$. Namely, all estimators in this case are strictly inferior compared to the sample mean. 
+\item[II.] For the normal distribution, the ARE in setting (iii) is at most $3/4$. Namely, under setting (iii), all estimators are strictly inferior compared to the sample mean. 
 \end{itemize}
@@
 \subsection{Multiterminal Source Coding \label{sec:ceo}}
-The CEO setting includes $n$ encoders, each has access to a noisy version of a random sequence \cite{berger1996ceo}. 
-% $\left\{ U_j,\,j=1,2,\ldots \right\}$. 
-The $i$th encoder observes $k$ noisy samples and transmit $R_i k$ bits to a central estimator. \par
-Assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding (setting (iii) in the Introduction) corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
-As a result, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the MSE in the optimal coding scheme for the CEO.
-Note that the difference between the CEO setting and ours lays in the privilege of each of the encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realization, rather than a single realization using a single bit in ours.
+The CEO setting considers the estimation of a sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_i$ is available at $n$ terminals.
+At each terminal $i$, an encoder observes the $k$ noisy samples
+\[
+X_{i,j} = \theta_j + Z_{i,j},\qquad j=1,\ldots,k, \qquad i = 1,\ldots,n,
+\]
+and transmits $R_i k$ bits to a central estimator  \cite{berger1996ceo}.  \par
+%
+Assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding in Fig.~\ref{fig:distributed} corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
+As a result, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the minimal MSE in the CEO setting as $k \to \infty$.
+Note that the difference between the CEO setting and ours lays in the privilege of each of the encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realizations, rather than a single realization using a single bit in ours.
  \par
@@
 Namely, the Gaussian CEO is obtained from our setting when the $i$th encoder uses $R_i=1$ bits to transmit a message that is a function of $X_i = \theta + \sigma Z_i$, where $Z_i$ is standard normal.
-Consequently, a lower bound the MSE in our distributed setting is obtained by considering the minimal MSE in the Gaussian CEO as the number of terminals goes to infinity.
+Consequently, a lower bound on the MSE in our distributed setting is obtained by considering the minimal MSE in the Gaussian CEO as the number of encoders $n$ goes to infinity.
 This leads to the following proposition:
 \begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\Theta = \mathbb R$ and that $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$. Then any estimator $\hat{\theta}_n$ of $\theta$ in the distributed setting satisfies
+Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$. Then any estimator $\hat{\theta}_n$ of $\theta$ in the distributed setting satisfies
 \begin{equation} \label{eq:ceo_bound}
@@
 \begin{proof}
-We consider the expression \cite[Eq. 10]{chen2004upper} that gives the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$:
+We consider the minimal distortion $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
+from \cite[Eq. 10]{chen2004upper}:
 \begin{equation} \label{eq:ceo_optimal_sumrate}
@@
 \end{equation}
-Assuming $R_\Sigma = n$ and $L=n$, we get
+For the special case of $R_\Sigma = n$ and $L=n$, we get
 \begin{equation} \label{eq:ceo_optimal_sumrate2}
@@
 \end{equation}
-The value of $D^\star$ that satisfies the equation above describes the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed encoding setting.
+$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
+Therefore, this $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting of Fig.~\ref{fig:distributed}.
 By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
@@
 Next, we provide a particular adaptive estimation scheme that attains this maximal efficiency.
-Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $i-1$ messages is chosen.
+Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $M_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages.
 %Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $\eta(0)\sigma^2$.
@@
 \subsubsection*{Sketch of Proof}
-The main idea in the proof is to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$.
+The main idea in the proof is to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
 Once this bound is achieved, the result follows by using the van-Trees inequality \cite[Thm.
@@
 
-To conclude the adaptive estimation setting, we now consider estimation from one bit messages obtained via an encoding scheme that is one-step optimal.
+To conclude the adaptive estimation setting, we now consider estimation from one-bit messages obtained via an encoding scheme that is one-step optimal.
 %Namely, each message obtained by employing the optimal the decision rule given the prior distribution and the previous messages.
@@
 We now consider an estimation scheme that posses the property of \emph{one-step optimality}: at each step $n$, the $n$th encoder designs the detection region $M_n^{-1}(1)$ such that the MSE given $M^n$ is minimal.
-In other word, this scheme designs the messages in a greedy manner, such that the MSE at step $n$ is minimal given the current state of the estimation described by $M^{n-1}$.
+In other words, this scheme designs the messages in a greedy manner, such that the MSE at step $n$ is minimal given the current state of the estimation described by $M^{n-1}$.
 \\
@@
 width=10cm, height=6cm,
-xmin = 0, xmax=1000, 
+xmin = 0, xmax=800, 
 restrict y to domain = 0:3,
@@
 xlabel= $n$,
-%ylabel = $n\mathbb E \left[\left(\theta - \hat{\theta}_n \right)^2 \right]$,
+ylabel = {$n\mathbb E \left[\left(\theta - \hat{\theta}_n \right)^2 \right]$},
 %xtick={-3,-2,-1,0,1,2,3},
@@
 
-\addplot[color = blue, solid, smooth] plot table [x = n, y = SGD, col sep=comma] {../SimRes/sim_res.csv};
+\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {../SimRes/sim_res_nMonte5000.csv};
 \addlegendentry{asymptotically optimal};
 
-\addplot[color = red, solid, smooth] plot table [x = n, y = Bayes, col sep=comma] {../SimRes/sim_res.csv};
+\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {../SimRes/sim_res_nMonte5000.csv};
 \addlegendentry{one step optimal};
 
-\addplot[color = green!30!black, solid, smooth] plot table [x = n, y = split, col sep=comma] {../SimRes/sim_res.csv};
+\addplot[color = green!30!black, solid, smooth] plot table [x = itr, y = split, col sep=comma] {../SimRes/sim_res_nMonte5000.csv};
 \addlegendentry{single interaction};
@@
 %\end{tikzpicture}
-\caption{Normalized empirical risk $n\left(\hat{\theta}_n-\theta\right)^2$ versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.
+\caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.
 In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$.
@@
 We now consider the distributed encoding setting described in Fig.~\ref{fig:distributed} (Setting (iii) in the Introduction).
-In this setting each single-bit message $M_i$ is only a function of its private sample $X_i$, and hence $M_i$ characterized by its \emph{detection region}, defined as
+In this setting each one-bit message $M_i$ is only a function of its private sample $X_i$, and hence $M_i$ characterized by its \emph{detection region}, defined as
 \[
@@
 \end{proof}
-%Theorem ~\ref{thm:non_existence} implies that for any distributed encoding scheme with messages defining a LAN family, and whose number of connected components is uniformly bounded, the set of point with MSe
-
-We next consider the case where each detection region is a half open interval, i.e., the $i$th message is obtained by comparing $X_i$ against a single threshold.
-As we explain, in this case, existence of a density for the sequence of threshold is enough to establish local asymptotic normality and leads to a closed form expression for the precision parameter and the ARE.
-
-%In the adaptive setting, it follows from Theorem~\ref{thm:sgd} that messages of this kind with appropriately chosen thresholds leads to an estimator with the optimal ARE of $\eta(0)sigma^2$.
+
+We next consider the case where each detection region is a half-open interval, i.e., the $i$th message is obtained by comparing $X_i$ against a single threshold.
+As we explain next, the existence of a density for the sequence of thresholds is enough to establish local asymptotic normality and leads to a closed form expression for the precision parameter and the ARE.
+
+%In the adaptive setting, it follows from Theorem~\ref{thm:sgd} that messages of this kind with appropriately chosen thresholds lead to an estimator with the optimal ARE of $\eta(0)sigma^2$.
 However, Theorem~\ref{thm:non_existence} implies that such ARE can only be attained for a negligible subset of the parameter space.
-As we shall see next, messages obtained by comparison against a sequence of thresholds cannot attain the optimal efficiency of expect perhaps on a single point of $\Theta$.
+As we shall see next, messages obtained via a comparison against a sequence of thresholds cannot attain the optimal efficiency one more than a single point of $\Theta$.
 
@@
 \subsection{Minimax Threshold Density}
-The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta = (-T,T)$ is given as the solution to the following optimization problem:
+The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta = [-T,T]$ is given as the solution to the following optimization problem:
 \begin{align}
@@
 \begin{split}
-\mathrm{maximize} \quad &  \inf_{\theta \in (-T,T)} \int \eta(t-\theta) \lambda(dt)
+\mathrm{maximize} \quad &  \inf_{\theta \in [-T,T]} \int \eta(t-\theta) \lambda(dt)
 \\ 
@@
 The minimal asymptotic risk $\kappa^\star(\theta)$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $T$.
-Also illustrated in these Figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = (-T,T)$, namely
+Also illustrated in these Figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
 \begin{align}
-& \kappa_{\unif} \triangleq \min_{\theta \in (-T,T)} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
+& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
  \\
@@
 \caption{\label{fig:minimax_support}
-Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x)$ the normal density with variance $\sigma^2$. 
-%Here the parameter space is $\Theta = (-T,T)$.  
-%$\lambda^\star$ in these figures is obtained by solving \eqref{eq:cvx_minimax}. 
-The continuous curve (red) represents the reciprocal of the asymptotic risk for at a fixed $\theta \in [-T,T]$ under the optimal density, so the minimax risk is the inverse of its minimal value.
-The dashed curve (green) is the reciprocal of the asymptotic risk for a fixed $\theta$ under a uniform distribution over $\Theta$ and its minimal value the inverse of \eqref{eq:uniform_risk}.
+Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \mathcal N(\theta,\sigma^2)$ and $\theta \in \Theta = [-T,T]$.
+%
+The continuous curve (red) represents the reciprocal of the asymptotic risk for at a fixed $\theta \in \Theta$ under the optimal density, so the minimax risk is the inverse of its minimal value.
+The dashed curve (green) is the reciprocal of the asymptotic risk for a fixed $\theta$ under a uniform distribution of threshold values over $\Theta$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
 }
@@
 \end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x)$ the centered normal density with variance $\sigma^2$ and $\Theta = (-T,T)$.
+\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \mathcal N(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
 The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
@@
 %We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
-Next, we prove that with any set of messages obtained via a distributed strategy, there exits at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
+Next, we prove that with any set of messages obtained via a distributed strategy, there exists at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
 
@@
 \section{Conclusions \label{sec:conclusions}}
-We considered the MSE risk in estimating the mean of a symmetric and log-concave distributions from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
+We considered the MSE risk in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
 %
@@
 %We further showed that the optimal MSE and ARE can be attained using only a single adaptation. Namely, a single round of communication between {\color{red} the estimator and the encoder} . 
-We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the MSE given any set of previously obtained bits.
-%Numerical simulations shows that the one-step optimal scheme attains the optimal relative efficiency for the normal distribution.
+We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
+%Numerical simulations show that the one-step optimal scheme attains the optimal relative efficiency for the normal distribution.
 \par
-In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, and thus provided a local asymptotic minimax bound on the MSE and ARE under such conditions.
-We concluded that in this case, the optimal performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in the distributed setting.
-We further considered the special case of messages encoded using threshold detection rules.
-We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax error.
+In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and ARE. 
+%
+We conclude that under such conditions, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in the distributed setting.
+%
+We further considered the special case of messages obtained by comparing against a prescribed sequence of thresholds.
+We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.
  \\
-
-%Interesting extension of our setting is to the case of estimating a $d$ dimensional vector of parameters rather than a scalar.
-An interesting questions in this extension is behavior of the MSE as a function of $d$.
-%{\color{red} Shamir \cite{Shamir} showed that in hide-and-seek hypothesis testing problem, bitrate constraint may lead to a significant reduction in detection performance compared to the unrestricted case.
-This result is then applied to online learning, stochastic optimization and sparse PCA.
-Shamir's results shows that the penalty is in the dimension ($d/R$ instead of $lod(d)$).
-In our setting the dimension is $1$.
-\\}
 
@@
 We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ single-bit messages with respect to $\theta$, we first note that without loss of generality, each message $M_i$ can is of the form
+In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $M_i$ can is of the form
 \begin{equation}
@@
 \subsubsection*{Proof of Lemma \ref{lem:adaptive}}
-Any single-bit message $M(u) \in \{0,1\}$ is characterized by two decision region $A_1 = M^{-1}(1)$ and $A_{-1} = M^{-1}(-1)$, so that $\mathbb E \left[ U | M(U) \right]$ assumes only two values: $\mu_1 = \mathbb E \left[ U | M(U) = 1 \right]$ and $\mu_{-1} = \mathbb E \left[ U | M(U) = -1 \right]$.
+Any one-bit message $M(u) \in \{0,1\}$ is characterized by two decision region $A_1 = M^{-1}(1)$ and $A_{-1} = M^{-1}(-1)$, so that $\mathbb E \left[ U | M(U) \right]$ assumes only two values: $\mu_1 = \mathbb E \left[ U | M(U) = 1 \right]$ and $\mu_{-1} = \mathbb E \left[ U | M(U) = -1 \right]$.
 We claim that a necessary condition for $M(u)$ to be optimal is that the sets $A_1$ and $A_{-1}$ are the Voronoi sets on $\mathbb R$ corresponding to the points $\mu_1$ and $\mu_{-1}$, respectively, modulo a set of measure $P(du)$ zero.
@@
 
+\end{comment}
 \end{document}
-
-\end{comment}

### 2019-01-07 Code/sim_script.py
removed files

@@ -34,7 +34,7 @@ for i in range(nMonte) :
     err_var_split += (th-np.array(th_hat_split))**2
     
     #SGD
-    th_hat_grad = grad_descent(y, g0 = 0.68)
+    th_hat_grad = grad_descent(y, g0 = 0.75)
     err_grad += th-np.array(th_hat_grad)
     err_var_grad += (th-np.array(th_hat_grad))**2
     

### 2019-01-09 old writeups/onebit_full_V1.tex
renamed directory

--- 2018-02-07 Writeups/onebit_full_V1.tex
@@
 \label{sec:Intro}
-Processing information on multiple physical locations may impose communication constraints on the amount of information that can be shared among different units of the system. 
+The performance in estimating information from data collected and processed by multiple units may be limited due to communication constraints between these units. 
 %For example, emerging sensor network technologies in medicine and ``smart cities" use many low-cost sensors to collect large amounts of data and transmit it to remote locations.
 These sensors must operate under severe power restrictions, hence they are limited by their communication bandwidth.
-%For example, this constraint occurs in large-scale sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit. 
-In this situation, the ability to estimate a particular parameter is dictated not only by quality of observations but also by the constraint on the communication rate of the sensor, which may be severely restricted due to power, bandwidth, or size of data.
-The question that we ask is to what extent a parametric estimation task is affected by such communication constraints, and what are the fundamental performance of estimation subject to these restrictions.
-\\
-
-In this paper we provide a precise answer to this question in a limited setting: the estimation of the mean $\theta$ of a normal distribution with a known variance $\sigma^2$, under the constraint that only a single bit can be communicated to the estimator on each sample from this distribution.
-As it turns out, the ability to share information before communicating it dramatically affects the performance in recovering $\theta$.
-We distinguish in particular among three different settings:
+For example, consider large-scale sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit.
+In this scenario, the ability to estimate a particular parameter from the data is dictated not only by the quality of observations and their number, but also by the available rate for communication between the sensors and the central estimator.
+The question that we ask is to what extent a parametric estimation task is affected by these communication constraints, and what are the fundamental performance limits in estimating a parameter subject to these restrictions.
+\\
+In this paper we answer this question in a particular setting: the estimation of the mean $\theta$ of a symmetric log-concave distribution with a known variance $\sigma^2$, under the constraint that only a single bit can be communicated on each sample $X_n$ from this distribution.
+As it turns out, the ability to share information among different samples before committing on each single-bit message dramatically affects the performance in estimating $\theta$.
+We therefore distinguish among three settings:
 \begin{itemize}
@@
  \end{itemize}
-As far as information sharing is concerned, it is evident that settings (iii) is a more restrictive version of (ii) which is more restrictive than (i).
-We are concerned with the mean squared error (MSE) risk in estimating $\theta$ as the number of observations $n$ goes to infinity.
-In particular, we are interested in the \emph{relative efficiency} of estimators in settings (i)-(iii), defined as the ratio between their MSE to $\sigma^2/n$.
-The latter is the MSE attained by the sample mean, which is the minimal risk estimator when no constraints on the communication are imposed.
+Evidently, as far as information sharing is concerned, settings (iii) is a more restrictive version of (ii) which is more restrictive than (i).
+We measure the estimation performance by the mean squared error (MSE) risk.
+We are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting relative to the MSE attained by the empirical mean of the samples, which is the minimax estimator in estimating without one-bit constraint and its MSE decreases as $\sigma^2/n+O(n^{-2})$.
+\\
+
+In setting (i), the estimator can evaluate the empirical mean of the samples and then communicate it using $n$ bits.
+This strategy leads to MSE behavior of $\sigma^2/n + O(2^{-n})$.
+Therefore, the ARE in this setting is $1$.
+Namely, asymptotically, there is no loss in performance due to the communication constraint under centralized encoding.
+In this work we show that a similar result does not hold even in setting (ii): the ARE of any adaptive estimation scheme is at least $\pi/2$.
+Namely, the single-bit per sample constraint incurs a minimal penalty of at least $1.57$ in the number of samples compared to an unconstrained estimator or to the optimal estimator in setting (i).
+In addition to this negative statement, we provide an estimator that attains this ARE.
+In other words, we show that the lower bound of $\pi/2$ on the ARE is tight, and that it is attained regardless of the particular realization of $\theta$ or the radius of the parameter space from which it is taken.
+Clearly, the minimal penalty on the efficiency of $\pi/2$ also holds under setting (iii), although the question whether this efficiency is achievable (or otherwise, what is the minimal ARE) remains open.
+\\
+
+The lower bound of $\pi/2$ on the ARE, i.e., a lower bound of $\sigma^2\pi/(2n) +O(n^{-2})$ on the MSE, is obtained by showing that the Fisher information of any $n$ adaptive messages is not greater than $2n/(\pi \sigma^2)$.
+From here, the desired bound on the MSE follows from the van Trees version of the information inequality \cite{gill1995applications}.
+Finally, we show that an estimator that attains asymptotic MSE of $\sigma^2\pi/(2n)$ is obtained as a special case of \cite[Thm.
+4]{polyak1992acceleration}.
+In addition to these two results, we also derive the one-step optimal strategy in which the message sent at step $i$th is designed to minimize the MSE given this message and the previous $i-1$ messages.
+Furthermore, we demonstrates numerically that the MSE under this strategy converges to $\pi \sigma^2/(2n)$.\\
+
+We note that even though its ARE is $1$, the centralized encoding setting (i) already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation scheme.
+Indeed, the standard technique to encode an unknown random quantity using $n$ bits is equivalent to the design of a scalar quantizer \cite{gray1998quantization}.
+However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation problem and hence its exact value is unknown.
+As a result, a non-trivial exploration exploitation tradeoff arises in this case.
+Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$.
+Therefore, while it is clear that uncertainty due to quantization decreases exponentially in the number of bits $n$ leading to ARE $1$, an exact expression for the MSE in this setting is still difficult to derive.
 \par
-%
-It is well known that the relative efficiency in setting (i) is $1$ \cite{720540, zhang2013information, zhang1988estimation}, i.e., asymptotically, there is no loss in performance due to the communication constraint in this setting.
-Indeed, under setting (i) the sample mean can be described with an error exponentially decaying in $n$, leading to MSE of $\sigma^2/n + o(n)$.
-In this work we show that a similar result does not hold even in setting (ii): the relative efficiency of any adaptive estimator is at least $\pi/2$.
-Namely, a single bit per sample communication constraint in the adaptive setting incurs a minimal penalty of at least $\pi/2 \approx 1.57$ compared to an unconstrained estimator, or to the optimal estimator in setting (i).
-In addition to this negative statement, we provide an estimator which asymptotically attains this minimal relative efficiency, i.e., we show that this lower bound is tight.
-Moreover, we show that even in the distributed setting (iii), a relative efficiency of $\pi/2$ is possible as long as $\sigma^2$ is large compared to the variance of the prior distribution on $\theta$.
-These results are quite surprising since they show that, even under the coarsest form of quantization, an estimator based on $ \approx 1.59 n$ measurements achieves accuracy in MSE or confidence interval comparable to an estimator that uses $n$ samples with infinite bit-precision.
+The situation is even more involved in the adaptive encoding of setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$, may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
+Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $n-1$ messages, is not guaranteed to be globally optimal.
+Our results imply that the ARE of any globally optimal strategy is $\pi/2$.
+We moreover show that this ARE is attained  even if $\sigma^2$ nor the radius of the parameter space $\Theta$ are unknown.
 \par
-%
-%One clue for this surprising results is given in a famous problem in information theory denoted as the CEO problem, first presented by Berger et.
-al.
-in \cite{berger1996ceo}.
-In this problem, a firms CEO is required to estimate a signal  from information sent to it by multiple agents, where the $i$th agents is given a noisy observation of this signal and has a limited number of bits, say $R_i$, to describe its observation to the CEO.
+For setting (iii) our results are more limited, and focus only on one-bit messages that are obtained by a threshold detection, i.e., are of the form $f_i = \sgn(X_i - t_i)$, for a sequence of threshold values $t_i$.
 
 \subsection*{Related Works}
-%\subsubsection*{Statistical inference under communication constraints}
 {\color{red} Shamir \cite{Shamir} showed that in hide-and-seek hypothesis testing problem, bitrate constraint may lead to a significant reduction in detection performance compared to the unrestricted case.
@@
 
-Statistical inference problems under communication constraints were considered in information theory in 
-\cite{han1987hypothesis, zhang1988estimation, 720540}.
-These works consider a multi-terminal source coding setting in which the $i$th terminal observes $n$ samples from the distribution and is allotted $nR_i$ bits to communicate its estimate.
-The main focus of these works is the difference between inference with communication constraint and the unconstrained vanilla statistical estimation setting, as the number of samples $n$ goes to infinity subject to a total finite rate constraint.
-Our setting (i) can be seen as a special case of this setting where with a single terminal and $R_1 = 1$.% whereas our case (iii) is obtained from this setting by taking $n=1$, $R_i=1$, and number of terminals grow with $n$.
-However, as explained in \cite[Sec.
-III]{720540}, a single terminal in this setting always lead to the unconstrained inference performance.
-Indeed, when all samples are taken from the same distribution, the \emph{type} of the sample \cite{csiszar1998method} is a sufficient statistics for any inference task, and the latter can be described using a number of codewords polynomial in $n$ regardless of the distribution of the samples.
-For this reason, attention is given in these works to inference problems involving multiple distributions observed at different locations and hence the results there do not apply to our setting.
-In fact, with a full access to the sample as in setting (i), the problem of encoding and estimating $\theta$ is reduced to the MSE attained by a scalar quantizer adjusted to the sufficient statistics of the sample.
-Finally, we note that setting (ii) includes as a special case the sigma-delta modulation (SDM) analog-to-digital conversion scheme with a constant input $\theta$ corrupted by Gaussian noise $Z_i$, as was considered in \cite{53738}.
-While it was shown there that the output of the modulator converges to the true constant input, the rate of this convergence was not analyzed and cannot be derived directly from the results of \cite{53738}.
-In fact, a corollary from the results in this paper we conclude that the rate of convergence of a SDM to a constant input signal is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-Finally, the multiterminal source coding setting denoted as the CEO problem \cite{berger1996ceo} can be seen as a generalization of our setting (iii), where multiple draws of $\theta$ and rounds of $n$ bit communication is permitted.
-In particular, the minimal CEO distortion with $1$ bit per terminal provides a lower bound on the MSE risk.
-\par
-%The difference between this setting and ours is that in ours the parameter of interest is not an information source.
-By assuming a prior distribution on this parameter, the CEO provides a lower bound on the estimation error in the fully distributed setting (iii).
-This lower bound can be attained if we were to consider the average error in multiple independent realizations of our problem rather than a single realization as we do here.
-\\
-%
-%While our focus in this paper is on setting (ii), we note that unlike the above works, we are also interested in the optimal estimation performance for a finite number of observations and not only in their asymptotic behavior.
-%\subsubsection*{Relation to channel coding}
-More related to our setting is the work \cite{zhang2013information} that considers the minimax MSE risk in estimating a vector of parameters from $m$ machines, where each machine has access to $n/m$ samples a limited number of bits to describe these samples.
-The main results of this work are lower bounds on the estimation error as a function of the total number of bits can be sent by each machine.
-In the terminology of \cite{zhang2013information}, our settings (ii) and (iii) fall under the category of \emph{interactive}, and  \emph{independent} communication protocols, respectively.
-%In both cases we use $m=n$ (single sample per machine) and communication constraint of a single bit per machine.
-However, unlike in \cite{zhang2013information}, we focus on achievable schemes and tight bounds in $n$ for the asymptotic MSE risk, rather than its scaling rate. \\
-
-The rest of this paper is organized as follows: the main problem is defined in Section~\ref{sec:problem}.
-Our main results are presented and discussed in Sections~ \ref{sec:sequential} and \ref{sec:distributed}.
-Concluding remarks are given in Section~\ref{sec:conclusions}.
-
-%We also note that the counterpart of setting (iii) in the case of hypothesis testing was considered in \cite{52470}.
-
-%\subsubsection{Estimation from 1-bit measurements}
-%Single-bit or binary detectors are the basis for digital technology, and works considers the estimation of parameters from the results of such detectors have been around from the early days of digital computing.
-The burst of works in compressed sensing in the previous decade also gave raise to multiple 1-bit results \cite{rice_university}.
-Due to the popularization of MIMO technology and the expected break of mm-wave in wireless communication there have been many works 1-bit detection at the A/D in the receiver \cite{2016arXiv160204193Z}.
-
-\section{Problem Formulation \label{sec:problem}}
+As the variance $\sigma^2$ goes to zero, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is easily solved by a bisection style method over the parameter space.
+Therefore, the general case of non-zero variance is a reminiscent of the noisy binary search problem with possibly infinite number of unreliable tests \cite{cicalese2002least, Karp:2007:NBS:1283383.1283478}.
+However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a noisy signal.
+For example, the sigma-delta modulator (SDM) analog-to-digital conversion \cite{1092194} uses one-bit threshold detector combined with a feedback loop to update an accumulated error state, and therefore falls under setting (ii).
+A SDM with a constant input $\theta$ corrupted by a Gaussian noise was studied in \cite{53738}, where it was shown that the output of the modulator converges to the true constant input almost surely.
+In other words, the SDM provides a consistent estimator for setting (ii).
+The rate of this convergence, however, was not analyzed and cannot be derived from the results of \cite{53738}.
+In particular, our results for setting (ii) imply that the asymptotic rate of convergence of the MSE in SDM to a constant input is at most $\sigma^2\pi/2$ over the number of feedback iterations.
+\\
+
+Our result of ARE of $\pi/2$ in the adaptive setting implies that even under coarse quantization constraints it is possible to achieve MSE in parametric estimation within only a relatively small penalty compared to the unconstrained estimator.
+A possible clue for this non-intuitive result is obtained from drawing the connection between our setting and the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}.
+This connection, which is explained in details in Section~\ref{sec:ceo}, immediately leads to a lower bound of $4/3$ on the ARE in the distributed encoding of setting (iii).
+While this lower bound provides no new information compared to the lower bound of $\pi /2$ we derive later for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimal even under one-bit quantization of each sample.\\
+
+We also note that our settings (ii) and (iii) are special cases of 
+\cite{zhang2013information} that consider adaptive and distributed estimation protocols for $m$ machines, each has access to $n/m$ independent samples.
+The main result of \cite{zhang2013information} are bounds on the estimation error as a function of the number of bits $R$ each machine uses for communication.
+The specialization of their result to our setting, by taking $m=n$ and $R=1$, leads to looser lower bounds then $\sigma^2\pi/(2n)$ for cases (ii) and (iii).
+The counterpart of our setting (iii) in the case of hypothesis testing was considered in \cite{52470}, although the results there cannot be extended to parametric estimation.
+Other related works include statistical inference under multiterminal data compression \cite{han1987hypothesis, zhang1988estimation}, and one-bit quantization constraints in compressed sensing  \cite{baraniuk2017exponential} and in MIMO detection in wireless communication \cite{singh2009limits}.
+\\
+
+\section{Problem Description \label{sec:problem}}
 
@@
 
-Let $X_i$, $i=1,\ldots,n$, be $n$ independent samples from the normal distribution $P(X) = \mathcal N(\theta,\sigma^2)$ with mean $\theta$ and variance $\sigma^2$.
-We also assume that the mean $\theta$ is drawn once from a prior distribution $\pi(\theta)$ on the parameter space $\Theta$, which is a closed interval of the real line.
+Let $\phi(x)$ be a symmetric log-concave density function with a unit second moment. We denote by $P_X$ the probability distribution with density
+\[
+\phi\left( \frac{x-\theta}{\sigma} \right).
+\]
+That is, $P_X$ is log-concave with mean $\theta$ and variance $\sigma^2$.
+Let $X_1,\ldots,X_n$ represent $n$ independent samples from $P_X$.
+We assume that $\sigma^2$ is known, and that $\theta$ is drawn once from a prior distribution $\pi(\theta)$ on the parameter space $\Theta$, which is a closed interval of the real line.
 We moreover assume that $\pi(\theta)$ is absolutely continuous with respect to the Lebesgue measure with a bounded second moment.
 We denote the variance of $\theta$ with respect to $\pi(\theta)$ by $\sigma_\theta^2$.
-The problem we consider is the estimation of the parameter $\theta$ under the following constraints on the communication between the samples $X_1,\ldots,X_n$ and a centralized estimator:
+We are interested in estimating the parameter $\theta$ from a set of $n$ binary messages $M^n = (M_1,\ldots,M_n)$, obtained from $X^n = (X_1,\ldots,X_n)$ under three possible scenarios:
 \begin{itemize}
-\item[(i)] The estimator at time $n$ is only a function of the $n$ messages $M^n = \left(M_1,\ldots,M_n \right)$ (Fig.~\ref{fig:centralized}).
-\item[(ii)] For each $i=1,\ldots,n$, the $i$th message $M_i$ is a function of the sample $X_i$ and the $i-1$ previous messages $M^{i-1}$ (Fig.~\ref{fig:sequential}).
-\item[(iii)] The $i$th message $M_i$ takes only two possible values, say $1$ and $-1$ (Fig.~\ref{fig:distributed}).
+\item[(i)] {\bf centralized:} $M^n = f_n(X^n)$ (Fig.~\ref{fig:centralized}).
+\item[(ii)] {\bf sequential:} $M_i = f_i(X_i,M^{i-1})$, $i=1,\ldots,n$ (Fig.~\ref{fig:sequential}).
+\item[(iii)] {\bf distributed:} $M_i = f_i(X_i)$, $i=1,\ldots,n$ (Fig.~\ref{fig:distributed}).
 \end{itemize}
-In other words, the only information on the sample $X^n \left(X_1,\ldots,X_n\right)$ available to the estimator is the messages $M^n$.
-In addition, each message $M_i$ is a function from the real line into the set $\{-1,1\}$ which is measurable with respect to the sigma algebra generated by $M^{i-1}$ and $X_i$.
-The estimator, upon observing $M^n$, produces an estimate $\widehat{\theta}_n(M^n)$ of $\theta$.
-A system describing the above scheme is illustrated in Fig.~\ref{fig:sequential}.
-\\
-
-The performance of this estimation is measured by the mean squared error (MSE) risk function:
+
+The performance of an estimator $\widehat{\theta}_n \triangleq \widehat{\theta}_n(M^n)$ in any of these cases is measured according to the mean squared error (MSE) risk:
 \begin{equation}
@@
 \end{equation}
-where the expectation is taken with respect to the distribution of $X^n$ and the prior distribution $\pi(\theta)$.  \\
+where the expectation is taken with respect to the distribution of $X^n$ and the prior distribution $\pi(\theta)$.  
 %It is well known that minmax estimation error 
@@
 %can be obtained from $R_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}. 
-
-The main problem we consider is the minimal value that can be attain in \eqref{eq:error_def} as a function of $n$.
-Note that this minimization is the combination of the following two processes: (1) selecting the $i$th message $M_i$ based on past messages and current observation $X_i$, and (2) estimating $\theta$ given messages $M^n$.
-We are interested in particular in the asymptotic relative efficiency of estimators $\widehat{\theta}_n$ for $\theta$ compared to the sample mean $\bar{X}_n = \frac{1}{n} \sum_{i=1}^n X_i$.
+%
+The main problem we consider is the minimal value of \eqref{eq:error_def} as a function of $n$, under all possible choices of the encoding functions in cases (i), (ii), and (iii).
+
+Particular interest is given to the asymptotic relative efficiency of estimators compared to the sample mean $\bar{X}_n = \frac{1}{n} \sum_{i=1}^n X_i$.
 Since the MSE attained by the latter is $\sigma^2/n$, this relative efficiency is defined as
@@
 
-\section{Relation to Remote Multiterminal Source Coding \label{sec:ceo}}
-In this section we draw a connection between our general problem of mean estimation from one-bit samples, to the remote multiterminal source coding problem \cite{berger1996ceo}, also known as the CEO problem.
-The setting of the CEO includes $n$ encoders, each has access to a noisy version of a random source sequence.
+\section{Lower bound from remote multiterminal source coding \label{sec:ceo}}
+In this section we draw a connection between our general problem of mean estimation from one-bit samples and the remote multiterminal source coding problem \cite{berger1996ceo}, also known as the CEO problem.
+The CEO setting includes $n$ encoders, each has access to a noisy version of a random source sequence \cite{berger1996ceo}.
 % $\left\{ U_j,\,j=1,2,\ldots \right\}$. 
 The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator. \par
-Assuming that $\theta$ is drawn randomly once from a prior $\pi(\theta)$, mean estimation from one-bit under distributed encoding (setting (iii) in the Introduction) corresponds to the CEO setting with block length $k=1$, where the $i$th encoder observes
-\begin{equation}
-\label{eq:Gaussian_channel}
-X_i = \theta + \sigma Z_i,
-\end{equation}
-with $Z_1,\ldots,Z_n$ i.i.d.
-standard normal, and uses $R_i=1$ bits to transmit its observation.
-As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise at each estimate of variance $\sigma^2$, provides a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting.
- \\
-
-A closed-form expression for the MSE distortion in the CEO is known only for the case where the source sequence is sampled independently from the normal distribution \cite{prabhakaran2004rate}.
-By using the characterization of this minimal distortion as the number of terminals goes to infinity, we conclude the following:
+Assuming that $\theta$ is drawn once from the prior $\pi(\theta)$, our mean estimation problem from one-bit samples under distributed encoding (setting (iii) in the Introduction) corresponds to the Gaussian CEO setting with $k=1$ source realization: the $i$th encoder uses $R_i=1$ bits to transmit a message that is a function of $X_i = \theta + \sigma Z_i$, where $Z_i$ is standard normal.
+As a result, a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting is given by the MSE in the optimal source coding scheme for the CEO with: $n$ terminals of codes rates $R_1 = \ldots = R_n = 1$, a Gaussian observation noise at each terminal of variance $\sigma^2$, and an arbitrary number of $k$ independent draws of $\theta$.
+Note that the difference between the CEO and ours lays in the privilege of each of the CEO encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realization, whereas our setting only allows $k=1$.
+ \\
+
+By using an expression for the minimal MSE in the Gaussian CEO as the number of terminals goes to infinity, we conclude the following:
 \begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$. Then any estimator $\widehat{\theta}_n$ of $\theta$ in 
-the distributed setting satisfies
+Assume that $\Theta = \mathbb R$ and that $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$. Then any estimator $\widehat{\theta}_n$ of $\theta$ in the distributed setting satisfies
 \begin{equation} \label{eq:ceo_bound}
- n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + o(1).
-\end{equation}
+ n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + O(n^{-1}),
+\end{equation}
+where the expectation is with respect to $\theta$ and $X^n$.
 \end{prop}
@@
 Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed encoding setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$, we conclude that
-\[
-D^\star = \frac{ \frac{4\sigma^2}{3} }{n + \frac{4 \sigma^2}{3 \sigma_\theta^2} } + O(e^{-n}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
+By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$, we see that
+\[
+D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
 \]
 \end{proof}
-Since the lower bound \eqref{eq:ceo_bound}  was derived assuming optimal allocation of the $n$ bits among the encoders, it may seem as if a tighter bound can be obtained in our case by considering the CEO distortion with $R_1=\ldots,R_n = 1$.
-However, an upper bound for the CEO distortion under this condition follows from \cite[Prop.
-5.2]{KipnisRini2017}, and leads to
-\[
-D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + o(n^{-1}),
-\]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small. \par
-We conclude therefore that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed encoding setting, is attributed exclusively to the ability to perform coding over blocks.
-Namely, the ability to consider $k>1$ independent realizations of $\theta$ versus only one in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product space, rather than the distributed nature of the problem, that distinguishes between the CEO distortion and the mean estimation from one-bit samples.\par
+
+Prop.~\ref{prop:ceo_lower_bound} implies that, unlike in the centralized setting, there is a loss in efficiency in estimating $\theta$ due to one-bit measurements in this setting.
 In the next section we show that the ARE in adaptive encoding setting does not exceeds $\pi/2$, and thus provides a tighter lower bound for the distributed encoding setting than $4/3$ of  \eqref{eq:ceo_bound}.
+\\
+
+We note although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO distortion while enforcing the condition $R_1=\ldots = R_n = 1$.
+Indeed, an upper bound for the CEO distortion under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
+\[
+D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
+\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
+\]
+which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ goes to zero. \\
+
+We note that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is only due to the ability to perform coding over blocks.
+Namely, the freedom to consider an arbitrary number $k$ of independent realizations of the problem, versus only one in ours.
+In other words, it is the ability to exploit the geometry of a high-dimensional product probability space, rather than the distributed nature of the problem, that distinguishes between the CEO distortion and our problem of mean estimation from one-bit samples.
 
@@
 
-The first main results of this paper, as described in Thm.~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be lower than $\pi/2$.
-Next, we provide a particular adaptive estimation scheme and show in Thm.~\ref{thm:sgd} that its efficiency is $\pi/2$.
+The first main results of this paper, as described in Thm.~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be lower than $1/(4f^2(0))$.
+Next, we provide a particular adaptive estimation scheme that attains this efficiency.
 Finally, in Thm.~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the message $M_i$ that minimizes the MSE given $X_i$ and the previous $M^{i-1}$ messages is chosen.
-While it is not clear whether the efficiency of this last scheme is $\pi/2$, numerical simulations suggests that the MSE of this scheme times $n$ also converges to $\pi/2$.
+While it is not clear whether the efficiency of this last scheme is $1/(4f^2(0))$, numerical simulations suggests that the MSE of this scheme times $n$ also converges to $1/(4f^2(0))$.
 
@@
 \subsection{A lower bound on adaptive one-bit schemes}
-Our first results asserts that the ARE \eqref{eq:relative_efficiency} of any adaptive estimation scheme is bounded from below by $\pi/2$, as follows from the following theorem:
+Our first results asserts that the ARE \eqref{eq:relative_efficiency} of any adaptive estimation scheme is bounded from below by $1/(4f^2(0))$, as follows from the following theorem:
 \begin{thm}[minimal relative effeciency] \label{thm:adpative_lower_bound}
@@
 \[
-\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\pi}{2n}\sigma^2+o(n^{-1}),
+\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{\pi \sigma^2 }{2n +\pi \sigma^2  I_0}  =  \frac{\sigma^2}{4f^2(0) n}+o(n^{-1}),
 \]
@@
 
-Next, we present an adaptive estimation scheme which attains ARE of $\pi/2$. 
+Next, we present an adaptive estimation scheme which attains ARE of $1/(4f^2(0))$. 
 \subsection{Asymptotically optimal estimator}
@@
 \[
-\sqrt{n} \left( \widehat{\theta}_n - \theta \right) \overset{d}{\rightarrow} \mathcal N \left(0,  \pi \sigma^2 /2 \right).
+\sqrt{n} \left( \widehat{\theta}_n - \theta \right) \overset{d}{\rightarrow} \mathcal N \left(0,  \frac{\sigma^2}{4f^2(0)}  \right).
 \]
@@
 \begin{lem} \label{lem:bound_intervals}
-For any $x_1 \geq \ldots \geq x_n \in \mathbb R$, we have 
-\begin{equation}
-\frac{ \left(  \sum_{k=1}^n (-1)^{k+1}\phi(x_k) \right)^2} 
-{\left( \sum_{k=1}^n (-1)^{k+1} \Phi(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} \Phi(x_k) \right)  } \leq \frac{2} {\pi}. \label{eq:bound_intervals}
+Assume that $f(x)$ is log-concave and symmetric. Then for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, we have 
+\begin{equation}
+\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
+{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)  } \leq \frac{2} {\pi}. \label{eq:bound_intervals}
 \end{equation}
@@
 \begin{lem} \label{lem:fisher_bound}
-Let $X\sim \mathcal N(\theta,\sigma^2)$ and assume that 
+Let $X$ be a random variable with a symmetric and log-concave density function $f(x)$. Assume that, for a Borel measurable $A$, 
 \[
@@
 \]
-Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $2/(\pi \sigma^2)$.
+Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $4f^2(0)/ \sigma^2$.
 \end{lem}
@@
 \subsubsection*{Proof of Lemma~\ref{lem:bound_intervals}}
-We use induction on $n \in \mathbb N$. For the base case $n=1$ we have 
+The proof is by induction on $n \in \mathbb N$. For the base case $n=1$ we have 
 \begin{equation} \label{eq:induction_base}

### 2019-01-09 onebit_full_V2.tex
renamed directory

--- 2019-01-07 Writeups/onebit_full_V2.tex
@@
 \begin{document}
-\graphicspath{{../Figs/}}
+\graphicspath{{./Figs/}}
 \maketitle
@@
 The averaged result is then stored using one of $n$ states.
-\item {\bf Analog-to-digital conversion:} in sigma-delta modulation, an analog signal is converted into a sequence of bits by sampling it at a very high rate and then using one-bit threshold detector combined with a feedback loop to update an accumulated error state.
+\item {\bf Analog-to-digital conversion:} A sigma-delta modulator (SDM) converts an analog signal into a sequence of bits by sampling the signal at a very high rate and then using one-bit threshold detector combined with a feedback loop to update an accumulated error state \cite{1092194}.
 Therefore, the MSE in tracking an analog signal using a SDM falls under our setting (ii) when we assume that the signal at the input to the modulator is a constant (direct current) corrupted by, say, thermal noise \cite{53738}.
@@
 In addition to the examples above, the excess risk in estimating a fixed parameter due to a one-bit per measurement constraint is useful in bounding from below the excess risk in estimating a signal from its noisy measurements.
-Namely, the excess MSE or ARE we derive serves as the most optimistic estimate for the risk in estimating a signal that varies in time or space under the one bit per measurement constraint.
-Such situations are considered in \cite{baraniuk2017exponential, jacques2013robust, plan2013one, li2017channel, choi2016near}.
+Namely, the excess MSE or ARE we derive serves as the most optimistic estimate for the risk in estimating under the one-bit per measurement constraint a signal changing over time or space.
+Such estimation settings are considered in \cite{baraniuk2017exponential, jacques2013robust, plan2013one, li2017channel, choi2016near}.
 \\
@@
 Clearly, the penalty on the sample size in setting (iii) is at least as large as that in setting (ii).
-Unlike in setting (ii), we show that there is no distributed estimation scheme that is uniformly optimal in the sense that it attains the ARE of the sample median for all $\theta$ in the parameter space.
+Furthermore, we show that, unlike in setting (ii), there is no distributed estimation scheme that is uniformly optimal in the sense that it attains the ARE of the sample median for all $\theta$ in the parameter space.
 % Instead, in setting (iii) we restrict ourselves to estimators from messages obtained by comparison against a prescribed value (that may be different for each sample).
@@
 The main result of \cite{zhang2013information} are bounds on the estimation error as a function of the number of bits $R$ each machine uses for communication.
-The specialization of their result to our setting, by taking $m=n$ and $R=1$, leads to looser lower bounds then we derive here for cases (ii) and (iii).
-Looser bounds can also be obtained from \cite{zhang1988estimation, han2018distributed, } that considered inference and distributed estimation under data compression constraint \cite{DBLP:journals/corr/abs-1802-08417, zhang1988estimation, han2018distributed, xu2017information}.
+The specialization of their result to our setting, by taking $m=n$ and $R=1$, leads to looser lower bounds then the ones we derive in this paper for cases (ii) and (iii).
+Looser bounds can also be obtained from works considering general inference and distributed estimation problems under data compression constraint \cite{DBLP:journals/corr/abs-1802-08417, zhang1988estimation, han2018distributed, xu2017information}.
 \\
@@
 ]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {../Figs/eta.csv};
+\addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {./Figs/eta.csv};
 \addlegendentry{$\eta(x)$};
@@
 ]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {../Figs/eta.csv};
+\addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {./Figs/eta.csv};
 \addlegendentry{$\log \eta(x)$};
@@
 
-\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {../SimRes/sim_res_nMonte5000.csv};
+\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
 \addlegendentry{asymptotically optimal};
 
-\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {../SimRes/sim_res_nMonte5000.csv};
+\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
 \addlegendentry{one step optimal};
 
-\addplot[color = green!30!black, solid, smooth] plot table [x = itr, y = split, col sep=comma] {../SimRes/sim_res_nMonte5000.csv};
+\addplot[color = green!30!black, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
 \addlegendentry{single interaction};
@@
 ]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/minmax_lmd_b0.5_sig0.5.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.5.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {../Figs/minimax_th_b0.5_sig0.5.csv};
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
+
+\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
+
+\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
 
@@
 ]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/minmax_lmd_b0.5_sig0.2.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.2.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {../Figs/minimax_th_b0.5_sig0.2.csv};
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
+
+\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
+
+\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
 
@@
 ]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/minmax_lmd_b0.5_sig0.1.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.1.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {../Figs/minimax_th_b0.5_sig0.1.csv};
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
+
+\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
+
+\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
 
@@
 ]
-\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {../Figs/minmax_lmd_b0.5_sig0.05.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {../Figs/minimax_th_b0.5_sig0.05.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {../Figs/minimax_th_b0.5_sig0.05.csv};
+\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
+
+\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
+
+\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
 
@@
 ]
-\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {../Figs/minmax_ARE_b0.5.csv};
+\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
 \addlegendentry{optimal threshold density};
 
-\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {../Figs/minmax_ARE_b0.5.csv};
+\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
 \addlegendentry{uniform threshold desnity};
@@
 ]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/unif_Bayes_lmd_b0.5_sig1.csv};
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
 %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
@@
 ]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/unif_Bayes_lmd_b0.5_sig2.csv};
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
 %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
@@
 ]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/unif_Bayes_lmd_b0.5_sig3.csv};
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
 %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
@@
 ]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {../Figs/unif_Bayes_lmd_b0.5_sig4.csv};
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
 %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
@@
 ]
-\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {../Figs/unif_Bayes_Risk.csv};
+\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
 %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {../Figs/unif_Bayes_Risk.csv};
+\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
 \addplot[color = black, dashed] {3.14159 / 2};

### 2019-02-21 onebit_full_V2.tex
Updating main manuscript ('one_bit_V2.tex') after joint meeting

@@
 \newcommand*{\QEDA}{\hfill\ensuremath{\square}}
+\newcommand{\CEO}{\mathsf{CEO}}
 
@@
 \tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
-\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=1cm,thick ]
+\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.7cm,thick ]
 \tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
@@
 \author{
-    \IEEEauthorblockN{John C. Duchi\IEEEauthorrefmark{1}\IEEEauthorrefmark{2} and
-Alon Kipnis\IEEEauthorrefmark{1} \\}
+    \IEEEauthorblockN{
+Alon Kipnis\IEEEauthorrefmark{1} and   
+    John C. Duchi\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}  \\}
     \IEEEauthorblockA{\IEEEauthorrefmark{1}Stanford University, Department of Statistics \\}
@@
 We consider the problem of estimating the mean of a symmetric log-concave distribution under the following constraint: only a single bit per sample from this distribution is available to the estimator.
-We study the mean squared error (MSE) risk in this estimation as a function of the number of samples, and hence the number of bits, from this distribution.
-Under an adaptive setting in which each bit is a function of the current sample and the previously observed bits, we show that the optimal relative efficiency compared to the sample mean is the efficiency of the median.
-For example, in estimating the mean of a normal distribution, a constraint of one bit per sample incurs a penalty of $\pi/2$ in sample size compared to the unconstrained case.
-%
-We also consider a distributed setting where each one-bit message is only a function of a single sample.
-We derive lower bounds on the MSE in this setting, and show that the optimal efficiency can only be attained at a finite number of points in the parameter space.
-%
-Finally, we analyze a distributed setting where the bits are obtained by comparing each sample against a prescribed threshold.
+We study the mean squared error risk in this estimation as a function of the number of samples, and hence the number of bits, from this distribution.
+%
+Under an adaptive setting in which each bit is a function of the current sample and previously recorded bits, we show that the optimal relative efficiency compared to the sample mean is the efficiency of the median.
+%For example, in estimating the mean of a normal distribution, a constraint of one bit per sample incurs a penalty of $\pi/2$ in sample size compared to the unconstrained case.
+%
+We also consider a distributed setting where each bit is only a function of a single sample.
+We show that the optimal efficiency of the adaptive setting can be attained by splitting the sample into two parts and allowing only a single adaptation.
+Otherwise, we show that no one sample estimation procedure can attain the optimal efficiency uniformly over all points in the parameter space.
+%
+%Finally, we analyze a distributed setting where the bits are obtained by comparing each sample against a prescribed threshold.
 Consequently, we consider the threshold density that minimizes the maximal MSE.
@@
 In the distributed case, this estimate can be done with vanishing error only for a finite number of possible values for the unknown mean.
-%
-%Therefore, our results indicate that, rather surprisingly, parametric estimation from the coarsest form of quantization incurs only a multiplicative penalty factor on the number of measurements.
-For example, this factor is $\pi/2$ for the normal distribution.
 \end{abstract}
@@
 \par
+%%
+\begin{figure*}
+\begin{center}
+\begin{tikzpicture}[node distance=2cm,auto]
+
+  \node at (0,0) (source) {$X_1$} ;
+ \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
+\node[below of = source2, node distance = 2.1cm] (source3) {$X_n$};
+
+\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};
+
+\draw[->,line width = 2pt] (source2) -- (enc2); 
+\draw[->,line width = 2pt] (source) -| (enc2); 
+\draw[->,line width = 2pt] (source3) -| (enc2);
+
+\node[below of = source2, node distance = 0.5cm] {$\vdots$};
+
+\draw[->,line width = 2pt] (source2) -- (enc2); 
+\node[int1, right of = enc2, node distance = 2.7cm ] (est) {Est};
+
+\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {\small $B_1,\ldots,B_n$} (est);
+
+\node[right of = est, node distance = 1.2cm] (dest) {\small $\hat{\theta}_n$};
+%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
+%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
+%\draw[->,line width=2pt] (dec) -- (dest);
+\draw[->, line width=2pt] (est) -- (dest);
+\node at (2,-4.5) {(i) Centralized};
+\end{tikzpicture}
+%
+\begin{tikzpicture}[node distance=2cm,auto]
+  \node at (0,0) (source) {\small $X_1$} ;
+  \node[int1, right of = source, node distance = 1.2cm] (enc1) {Enc 1};  
+\draw[->,line width = 2pt] (source) -- (enc1);
+
+ \node[below of = source, node distance = 1.5cm] (source2) {\small $X_2$};
+\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc 2};  
+\draw[->,line width = 2pt] (source2) -- (enc2);
+
+\node[below of = source2, node distance = 2.1cm] (source3) {\small $X_n$};
+\node[int1, right of = source3, node distance = 1.2cm] (enc3) {Enc n};  
+\draw[->,line width = 2pt] (source3) -- (enc3);
+
+\node[below of = source2, node distance = 0.5cm] {$\vdots$};
+%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim P_X$};
+
+\node[int1, right of = enc2, node distance = 3cm ] (est) {Est};
+\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);   
+\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$B_2$} (est);
+
+\draw[->] (enc1)+(0.7,0) -- +(0.7,-0.7) -| (enc2);
+
+%\draw[dashed,->] (enc2)+(0.7,0) -- +(0.7,-0.7) -| +(0,-1.2);
+\draw[->,line width = 2pt] (enc3) -| (est);
+
+%\node[below of = mes2, node distance = 1.5cm] (mes3) {$B_1,\ldots,B_{n-1} $};
+
+\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -1cm]  {$B_n$} (est);
+
+%\draw[->] (mes3.west) -- +(0,-0.5) -| (enc3);
+
+\node[below right = 2.3cm and 0.7cm of 
+enc1.center, yshift = 0.cm] (end) {$B_1,\ldots,B_{n-1}$};
+
+\draw[->] (enc1)+(0.7,0) -- (end.west) -| (enc3);
+
+\node[right of = est, node distance = 1.2cm] (dest) {$\hat{\theta}_n$};
+%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
+%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
+%\draw[->,line width=2pt] (dec) -- (dest);
+\draw[->, line width=2pt] (est) -- (dest);
+\node at (2,-4.5) {(ii) Adaptive};
+\end{tikzpicture}
+%
+\begin{tikzpicture}[node distance=2cm,auto]
+  \node at (0,0) (source) {$X_1$} ;
+  \node[int1, right of = source, node distance = 1.2cm] (enc1) {Enc 1};  
+\draw[->,line width = 2pt] (source) -- (enc1);
+
+ \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
+\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc 2};  
+\draw[->,line width = 2pt] (source2) -- (enc2);
+
+\node[below of = source2, node distance = 2.1cm] (source3) {$X_n$};
+\node[int1, right of = source3, node distance = 1.2cm] (enc3) {Enc n};  
+\draw[->,line width = 2pt] (source3) -- (enc3);
+
+%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
+\node[below of = source2, node distance = 0.5cm] {$\vdots$};
+
+\node[int1, right of = enc2, node distance = 2.1cm ] (est) {Est};
+\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
+
+\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$B_2$} (est);
+
+\draw[->,line width = 2pt] (enc3) -| (est);
+
+\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -1cm]  {$B_n$} (est);
+
+\node[right of = est, node distance = 1.2cm] (dest) {$\hat{\theta}_n$};
+%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
+%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
+%\draw[->,line width=2pt] (dec) -- (dest);
+\draw[->, line width=2pt] (est) -- (dest);
+\node at (2,-4.5) {(iii) Distributed};
+\end{tikzpicture}
+\end{center}
+\caption{\label{fig:setup} 
+Three encoding settings: (i) Centralized  -- an encoder sends $n$ bits after observing $n$ samples.
+(ii) Adaptive (sequential) --  each encoder sends a bit $B_n$ depending on its private sample $X_n$ and previous bits $B_1,\ldots,B_{n-1}$.
+(iii) Distributed  -- each encoder sends a single bit $B_i$ only based on its private sample $X_i$.}
+\end{figure*}
+%%
+
 This paper answers this question in a particular setting: the estimation of the mean $\theta$ of a symmetric log-concave distribution with finite variance, under the constraint that only a single bit can be communicated on each sample from this distribution.
 As it turns out, the ability to share information before committing on each one-bit message dramatically affects the performance in estimating $\theta$.
-We, therefore, distinguish among three settings:
+We, therefore, distinguish among the three settings illustrated in Figure~\ref{fig:setup}
 \begin{itemize}
- \item[(i)\,\,] \emph{Centralized} encoding (Fig.~\ref{fig:centralized}): all $n$ encoders confer and produce a single $n$ bit message. 
- \item[(ii)\,] \emph{Adaptive} or \emph{sequential} encoding (Fig.~\ref{fig:sequential}): the $n$th encoder observes the $n$th sample and the $n-1$ previous messages (bits).
- \item[(iii)] \emph{Distributed} encoding (Fig.~\ref{fig:distributed}): the $n$th message is only a function of the $n$th observation.
+ \item[(i)\,\,] \emph{Centralized} encoding: all $n$ encoders confer and produce a single message consists of $n$ bits.
+ \item[(ii)\,] \emph{Adaptive} or \emph{sequential} encoding: The $n$th encoder observes the $n$th sample and the $n-1$ previous bits.
+ \item[(iii)] \emph{Distributed} encoding: The $n$th message is only a function of the $n$th sample.
  \end{itemize}
 Evidently, as far as information sharing is concerned, settings (iii) is a more restrictive version of (ii) which is more restrictive than (i).
-Below are three application examples for each of settings (i)-(iii) above, respectively:
+Below are three application examples for each of the settings (i)-(iii) above, respectively:
 \begin{itemize}
-\item {\bf Signal acquisition:} a quantity is measured $n$ times at different instances, and the results are averaged in order to reduce measurement noise.
-The averaged result is then stored using one of $n$ states.
+\item {\bf Signal acquisition:} A quantity is measured $n$ times at different instances.
+The results are averaged in order to reduce measurement noise and the averaged result is then stored or communicated using $n$ bits.
 \item {\bf Analog-to-digital conversion:} A sigma-delta modulator (SDM) converts an analog signal into a sequence of bits by sampling the signal at a very high rate and then using one-bit threshold detector combined with a feedback loop to update an accumulated error state \cite{1092194}.
-Therefore, the MSE in tracking an analog signal using a SDM falls under our setting (ii) when we assume that the signal at the input to the modulator is a constant (direct current) corrupted by, say, thermal noise \cite{53738}.
+Therefore, the MSE in tracking an analog signal using an SDM falls under our setting (ii) when we assume that the signal at the input to the modulator is a constant (direct current) corrupted by, say, thermal noise \cite{53738}.
 Since the sampling rates in SDM are usually many times more than the bandwidth of its input, analyzing SDM under a constant input provides meaningful lower bound even for non-constant signals.
-\item {\bf Differential privacy:} -- a business entity is interested in estimating the average income of its clients.
+\item {\bf Privacy:} A business entity is interested in estimating the average income of its clients.
 In order to keep this information as confidential as possible, each client independently provides an answer to a yes/no question related to its income.
@@
 We measure the performance in estimating $\theta$ by the mean squared error (MSE) risk.
-We are interested in particular in the \emph{asymptotic relative efficiency} (ARE) of estimators in the constrained setting compared to asymptotically normal estimators whose variances decreases as $\sigma^2/n+o(n^{-1})$.
+For an asymptotically normal estimator with a finite MSE risk $R_n$, we are interested in particular in the limit
+\[
+\lim_{n\to \infty} \frac{\sigma^2}{n R_n},
+\]
+describing the 
+ \emph{asymptotic relative efficiency} (ARE) of the estimator compared to asymptotically normal estimators whose variances decreases as $\sigma^2/n+o(n^{-1})$.
 Estimators of this form include the empirical mean of the samples, and, under some conditions, the optimal Bayes estimator.
@@
 In this paper we show that a similar result does not hold in setting (ii): the ARE of any adaptive estimation scheme is at most the ARE of the sample median.
-Specifically, when the samples are drawn from the normal distribution, this ARE equals $\pi/2$, showing that the one-bit constraint increases the effective sample size in estimating $\theta$ by at least $\pi/2 \approx 1.57$ compared to estimating it without the bit constraint.
+Specifically, when the samples are drawn from the normal distribution, this ARE equals $2/\pi$, showing that the one-bit constraint increases the effective sample size in estimating $\theta$ by at least $\pi/2$ compared to estimating it without the bit constraint.
 We also show that this lower bound on the ARE is tight by providing an estimator that attains it.
-% This estimator is obtained by averaging the results of a series of comparisons of the samples against certain thresholds.
-%This estimator is can be seen as a stochastic gradient descent procedure for minimizing the absolute error, hence it attains the asymptotic MSE of the sample median.
-% Interestingly, our estimator attains \eqref{eq:median_MSE} regardless of the particular realization of $\theta$ or the radius of the parameter space from which it is taken.
+In fact, we show that only one adaptiveness, as illustrated in Figure~\ref{fig:one_round} is enough to achieve the optimal ARE.
 %
 Clearly, the penalty on the sample size in setting (iii) is at least as large as that in setting (ii).
-Furthermore, we show that, unlike in setting (ii), there is no distributed estimation scheme that is uniformly optimal in the sense that it attains the ARE of the sample median for all $\theta$ in the parameter space.
+We show, however, that unlike in setting (ii), there is no distributed estimation scheme that is uniformly optimal in the sense that it attains the ARE of the sample median for all $\theta$ in the parameter space.
+This result is obtained by establishing local asymptotic normality of regularly enough encoding procedures for setting (iii), resulting in an exact characterization of the ARE of such procedures.
+To summarize our contributions, we establish that the optimal ARE in settings (i) is $1$, the optimal ARE in setting (ii) is ARE of the sample median, and no uniformly optimal procedure exists in setting (iii).
+
 % Instead, in setting (iii) we restrict ourselves to estimators from messages obtained by comparison against a prescribed value (that may be different for each sample).
@@
 
-We note that although the ARE in setting (i) is $1$, this scheme already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation procedures.
-Indeed, the standard technique to encode an unknown random quantity using $n$ bits is equivalent to the design of a scalar quantizer \cite{gray1998quantization}.
+It is important to note that although the ARE in setting (i) is one, this scheme already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation procedures.
+Indeed, the task of representing an unknown random quantity using $n$ bits is equivalent to designing a $2^n$ levels scalar quantizer \cite{gray1998quantization}.
 However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation problem and hence its exact value is unknown.
-As a result, a non-trivial exploration-exploitation trade-off arises in this case.
+As a result, a non-trivial exploration-exploitation trade-off arises even in this case.
 %Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$. 
 Therefore, while uncertainty due to quantization decreases exponentially in the number of bits $n$, hence the ARE is $1$, an exact expression for the MSE in this setting is still difficult to derive. 
-\par
 %
@@
 \par
-In addition to encoding and estimation schemes that lead to optimal results, we also consider two additional ``natural'' schemes.
+%
+%In addition to encoding and estimation schemes that lead to optimal results, we also consider two additional ``natural'' schemes.
 Specifically, in setting (ii) we consider the one-bit optimal scheme, i.e., the case of a greedy encoder that given the $n$th sample and the previous $n-1$ bits, provides a bit that minimizes the $n$-step MSE.
@@
 
-%Finally, we show that an estimator that attains asymptotic MSE of $\sigma^2\pi/(2n)$ is obtained as a special case of \cite[Thm.
-4]{polyak1992acceleration}.
-In addition to these two results, we also derive the one-step optimal strategy in which the message sent at step $i$th is designed to minimize the MSE given this message and the previous $i-1$ messages.
-Furthermore, we demonstrate numerically that the MSE under this strategy converges to $\pi \sigma^2/(2n)$.\\
-
 \subsection*{Related Works}
-As the variance $\sigma^2$ goes to zero, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is solved by a bisection style method over the parameter space.
+When the variance $\sigma^2$ is negligible compared the to desired accuracy, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is solved by a bisection style method over the parameter space.
 Therefore, the general case of non-zero variance is reminiscent of the noisy binary search problem with a possibly infinite number of unreliable tests \cite{cicalese2002least, Karp:2007:NBS:1283383.1283478}.
@@
 Furthermore, in a version of this problem for the adaptive setting \cite{5751320}, it was shown that, with specific two-stage feedback, there is no gain in feedback compared to the fully distributed setting.
-Our results imply that they ARE in the distributed setting with threshold detection rules is strictly larger than that in the adaptive setting, suggesting that the case of a finite $\Theta$ is very different from the case where $\Theta$ is an open set.\par
+Our results imply that the ARE in the distributed setting with threshold detection rules is strictly larger than that in the adaptive setting for almost all points in $\Theta$, suggesting that the case where the cardinality of $\Theta$ is finite is different from the case where $\Theta$ is an open set.\par
 %
@@
 For the case of a Gaussian distribution, this lower bound bounds the ARE to be at most $3/4$.
-Thus, while this bound on the ARE provides no new information compared to the upper bound of $2/\pi$ we derive for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimal even under the one bit per sample constraint.
+Thus, while this bound on the ARE provides no new information compared to the upper bound of $2/\pi$ we derive for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimum even under the one bit per sample constraint.
  \par
 % 
-Finally, we note that our settings (ii) and (iii) can be obtained as special cases of 
-\cite{zhang2013information} 
-that consider adaptive and distributed estimation protocols for $m$ machines, each has access to $n/m$ independent samples.
-The main result of \cite{zhang2013information} are bounds on the estimation error as a function of the number of bits $R$ each machine uses for communication.
-The specialization of their result to our setting, by taking $m=n$ and $R=1$, leads to looser lower bounds then the ones we derive in this paper for cases (ii) and (iii).
-Looser bounds can also be obtained from works considering general inference and distributed estimation problems under data compression constraint \cite{DBLP:journals/corr/abs-1802-08417, zhang1988estimation, han2018distributed, xu2017information}.
+Finally, we note that minimax estimation under limited communication with an arbitrary number of bits per node was considered in 
+\cite{zhang2013information, duchi2014optimality}.
+The specialization of the results in \cite{zhang2013information, duchi2014optimality} to our settings (ii) and (iii) leads to looser lower bounds then the ones we derive in this paper.
+Looser bounds can also be obtained from works considering general inference and distributed estimation problems under data compression constraint \cite{DBLP:journals/corr/abs-1802-08417, zhang1988estimation, han2018distributed, xu2017information, Barnes2018}.
+In particular, the subsequent work of \cite{Barnes2018} uses an approach similar to ours to derive lower bound on the error in various parametric estimation problems from quantized measurements.
 \\
-%in MIMO detection in wireless communication \cite{singh2009limits}. \\
 
@@
 
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto,>=latex]
-
-\node[node distance = 1.5cm] at (0,0) (source2) {$X_1,\ldots,X_n$};
-\node[int1, right of = source2, node distance = 2cm] (enc2) {Enc};  
-\draw[->,line width = 2pt] (source2) -- (enc2); 
-\node[int1, right of = enc2, node distance = 4cm ] (est) {Est};
-
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M \in \left\{-1,1\right\}^n$} (est);
-
-\node[right of = est, node distance = 1.5cm] (dest) {$\widehat{\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=2pt] (est) -- (dest);
-\end{tikzpicture}
-\end{center}
-\caption{\label{fig:centralized} Centralized one-bit encoding: encoder sends $n$ bits after observing $n$ samples.}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto,>=latex]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.5cm] (enc1) {Enc 1};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
- \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
-\node[int1, right of = source2, node distance = 1.5cm] (enc2) {Enc 2};  
-\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source2, node distance = 2.5cm] (source3) {$X_n$};
-\node[int1, right of = source3, node distance = 1.5cm] (enc3) {Enc n};  
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-\node[above of = source3, node distance = 0.6cm] {$\vdots$};
-%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim P_X$};
-
-\node[int1, right of = enc2, node distance = 4cm ] (est) {Est};
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -2cm] (mes1) {$M_1 \in \left\{-1,1\right\}$} (est);   
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M_2 \in \left\{-1,1\right\}$} (est);
-
-\draw[->] (enc1)+(0.7,0) -- +(0.7,-0.7) -| (enc2);
-
-\draw[dashed,->] (enc2)+(0.7,0) -- +(0.7,-0.7) -| +(0,-1.2);
-\draw[->,line width = 2pt] (enc3) -| (est);
-
-\node[below of = mes2, node distance = 1.5cm] (mes3) {$M_1,\ldots,M_{n-1} $};
-
-\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -2cm]  {$M_n \in \left\{-1,1\right\}$} (est);
-
-\draw[->] (mes3.west) -- +(0,-0.5) -| (enc3);
-
-\node[right of = est, node distance = 1.5cm] (dest) {$\hat{\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=2pt] (est) -- (dest);
-\end{tikzpicture}
-\end{center}
-\caption{\label{fig:sequential} Adaptive one-bit encoding: the $n$th encoder delivers a single bit message which is a function of its private sample $X_n$ and the previous messages $M_1,\ldots,M_{n-1}$.}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto,>=latex]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.5cm] (enc1) {Enc 1};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
- \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
-\node[int1, right of = source2, node distance = 1.5cm] (enc2) {Enc 2};  
-\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source2, node distance = 2.5cm] (source3) {$X_n$};
-\node[int1, right of = source3, node distance = 1.5cm] (enc3) {Enc n};  
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-\node[above of = source3, node distance = 0.6cm] {$\vdots$};
-
-\node[int1, right of = enc2, node distance = 4cm ] (est) {Est};
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -2cm] (mes1) {$M_1 \in \left\{-1,1\right\}$} (est);
-
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$M_2 \in \left\{-1,1\right\}$} (est);
-
-\draw[->,line width = 2pt] (enc3) -| (est);
-
-\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -2cm]  {$M_n \in \left\{-1,1\right\}$} (est);
-
-\node[right of = est, node distance = 1.5cm] (dest) {$\hat{\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=2pt] (est) -- (dest);
-\end{tikzpicture}
-\end{center}
-\caption{\label{fig:distributed} Distributed one-bit encoding: the one-bit message produced by each encoder is only a function of its private sample $X_i$.}
-\end{figure}
 Let $f(x)$ be a symmetric and log-concave density function with a finite second moment $\sigma^2$.
@@
 Therefore, $P_X$ is an absolutely continuous log-concave distribution with mean $\theta$ and variance $\sigma^2$.
-Symmetry and log-concavity of $f(x)$ imply that $P_X$ is strongly unimodal with its mode at $x =\theta$ \cite{ibragimov1956composition}.
+Symmetry and log-concavity of $f(x)$ imply that $P_X$ is strongly unimodal (has a unique local maxima) with its mode at $x =\theta$ \cite{ibragimov1956composition}.
 We further assume that the \emph{parameter space} $\Theta$ is a closed interval of the real line.
@@
 The random variables $X_1,\ldots,X_n$ represent $n$ independent samples from $P_X$. 
-We are interested in estimating $\theta$ from a set of $n$ binary messages $M_1,\ldots,M_n$, obtained from $X_1,\ldots,X_n$ under three possible scenarios: 
+We are interested in estimating $\theta$ from a set of $n$ binary messages $B_1,\ldots,B_n$, obtained from $X_1,\ldots,X_n$ under three possible scenarios illustrated in Figure~\ref{fig:setup}: 
 \begin{itemize}
-\item[(i)~~] Centralized $M_i(X_1,\ldots,X_n)$, $i=1,\ldots,n$ (Fig.~\ref{fig:centralized}).
-\item[(ii)~] Adaptive $M_i(X_i,M_1,\ldots,M_{i-1})$, $i=2,\ldots,n$ (Fig.~\ref{fig:sequential}).
-\item[(iii)] Distributed $M_i(X_i)$, $i=1,\ldots,n$ (Fig.~\ref{fig:distributed}).
+\item[(i)~~] Centralized $B_i(X_1,\ldots,X_n)$, $i=1,\ldots,n$.
+\item[(ii)~] Adaptive $B_i(X_i,B_1,\ldots,B_{i-1})$, $i=2,\ldots,n$.
+\item[(iii)] Distributed $B_i(X_i)$, $i=1,\ldots,n$.
 \end{itemize}
 
-The performance of an estimator $\hat{\theta}_n \triangleq \hat{\theta}_n(M^n)$ in any of these cases is measured according to the mean squared error (MSE) risk:
+The performance of an estimator $\hat{\theta}_n \triangleq \hat{\theta}_n(B^n)$ in any of these cases is measured according to the mean squared error (MSE) risk:
 \begin{equation}
@@
 \end{equation}
-where the expectation is taken with respect to the distribution of $X^n$ and, whenever available, a prior distribution $\pi(\theta)$ over $\Theta$.  
+where the expectation is taken with respect to the distribution of $X_1,\ldots,X_n$ and, whenever available, a prior distribution $\pi(\theta)$ over $\Theta$.  
 %It is well known that minmax estimation error 
@@
 \begin{assump} \label{assump:failure_rate}
- $\eta(x)$ is strongly unimodal. 
+ $\eta(x)$ has a unique maximum (at the origin) and is a non-increasing function of $|x|$. 
 \end{assump}
@@
 
-\section{ Consisten Estimation and Of-the-shelf Bounds \label{sec:preliminary}}
-On a first impression, it may not be clear whether consistent estimation of the mean is even possible in the adaptive and centralized settings.
+\section{Consisten Estimation and Existing Bounds \label{sec:preliminary}}
+%On a first impression, it may not be clear whether consistent estimation of the mean is even possible in the adaptive and centralized settings.
 On the other hand, it may seem as if estimation in these cases is trivial as in the centralized setting (i).
 %
-We next settle such skepticism by deriving lower and upper bounds to the relative efficiency under setting (iii). We show that:
+We next settle such skepticism by deriving lower and upper bounds to the relative efficiency under setting (iii).
+
+In this section, we derive lower and upper bounds on the relative efficiency under setting (iii) using known results. These bounds establish the following facts:
 \begin{itemize}
@@
 \[
-M_i = \mathbf 1_{X_i>\theta_0}, 
+B_i = \mathbf 1_{X_i>\theta_0}, 
 \]
@@
 \[
-p_n \triangleq\frac{1}{n} \sum_{i=1}^n M_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
+p_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
 \]
@@
 \end{equation}
-is a consistent estimator for $\theta$ in the distributed setting of Fig.~\ref{fig:distributed}, where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set.
+is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set.
 Furthermore, the variance of $p_n$ is $F(\theta-\theta_0)F(\theta_0-\theta)$, and hence the delta method implies that $\hat{\theta}_n$ is asymptotically normal with variance
@@
 It is suggested that lower variance can be obtained by an estimator of the form \eqref{eq:estimator_naive} if, after observing a batch of the single bit messages, one can update the threshold value $\theta_0$.
-Such a scheme falls within the adaptive setting of Fig.~\ref{fig:sequential} which we consider in Section~\ref{sec:sequential}.
+Such a scheme falls within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
 \\
@@
 \]
-and transmits $R_i k$ bits to a central estimator  \cite{berger1996ceo}.  \par
-%
-Assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding in Fig.~\ref{fig:distributed} corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
-As a result, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the minimal MSE in the CEO setting as $k \to \infty$.
+and transmits $R_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates $\hat{\theta}_1,\ldots,\hat{\theta}_k$ with the goal of minimizing the average MSE:
+\[
+D_{CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - \hat{\theta}_j \right)^2 \right]. 
+\]
+Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $R_1=\ldots=R_n = 1$.
+It follows that, assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
+%
+Consequently, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the minimal MSE in the CEO setting as $k \to \infty$.
 Note that the difference between the CEO setting and ours lays in the privilege of each of the encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realizations, rather than a single realization using a single bit in ours.
  \par
-An optimal scheme for the CEO and its corresponding MSE is known only for the case where the prior on $\theta$, as well as the noise corrupting it at each location, are Gaussian.
-Namely, the Gaussian CEO is obtained from our setting when the $i$th encoder uses $R_i=1$ bits to transmit a message that is a function of $X_i = \theta + \sigma Z_i$, where $Z_i$ is standard normal.
-Consequently, a lower bound on the MSE in our distributed setting is obtained by considering the minimal MSE in the Gaussian CEO as the number of encoders $n$ goes to infinity.
-This leads to the following proposition:
+When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k\to \infty$ were fully characterized in \cite{prabhakaran2004rate}.
+Furthermore, the work of \cite{chen2004upper} provided an expression for MSE attained in the CEO setting under Gaussian priors.
+Adapting to our setting, this expression provides the following proposition:
 \begin{prop} \label{prop:ceo_lower_bound}
@@
 \begin{proof}
-We consider the minimal distortion $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
-from \cite[Eq. 10]{chen2004upper}:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-For the special case of $R_\Sigma = n$ and $L=n$, we get
-\begin{equation} \label{eq:ceo_optimal_sumrate2}
-n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, this $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting of Fig.~\ref{fig:distributed}.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
-\[
-D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
+See Appendix. 
 \end{proof}
-We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO distortion while enforcing the condition $R_1=\ldots = R_n = 1$.
-Indeed, an upper bound for the CEO distortion under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
-\[
-D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
-\]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small. \par
-From the formulation of the CEO problem, it follows that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is exclusively attributed  to the ability to perform coding over blocks.
-Namely, each CEO encoder may encode an arbitrary number of $k$ independent realizations of $\theta$ using $k$ bits, versus only one realization with one bit in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product probability space that
-distinguishes between the CEO problem with one bit per encoder and the mean estimation problem from one-bit measurements in the distributed setting of Fig.~\ref{fig:distributed}.
+
+From the formulation of the CEO problem, it follows that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is attributed to the ability to perform coding over blocks.
+Namely, each encoder in the CEO setting may encode an arbitrary number of $k$ independent realizations of $\theta$ using $k$ bits, versus only one realization with one bit in ours.
+In other words, it is the ability to exploit the geometry of a high-dimensional product probability space that distinguishes between the CEO problem with one bit per encoder on average and the mean estimation problem from one-bit measurements in the distributed setting.
 
@@
 The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $\eta(0)\sigma^2$, which is the ARE of the median of the sample $X_1,\ldots,X_n$.
-Next, we provide a particular adaptive estimation scheme that attains this maximal efficiency.
-Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $M_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages.
+We also provide a particular adaptive estimation scheme that attains this maximal efficiency.
+%Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $B_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages.
 %Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $\eta(0)\sigma^2$.
 
-\subsection{Maximal efficiency in adaptive setting}
+\subsection{Limited efficiency in the adaptive setting}
 Our first result asserts that the ARE of any adaptive encoding and estimation scheme is bounded from above by $\eta(0)\sigma^2$. %This result follows from the following theorem:
 \begin{thm}[maximal relative effeciency] \label{thm:adpative_lower_bound}
-Let $\hat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Fig.~\ref{fig:sequential}. Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
+Let $\hat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Figure~\ref{fig:setup}-(ii). Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
 \[
@@
 The main idea in the proof is to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
-Once this bound is achieved, the result follows by using the van-Trees inequality \cite[Thm.
-2.13]{tsybakov2008introduction},\cite{gill1995applications} which bounds from below the MSE of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
+Once this bound is achieved, the result follows by using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
 The details are in the Appendix.\\
@@
 \label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n M_n, \quad n = 1,2,\ldots,
+\theta_n = \theta_{n-1} +  \gamma_n B_n, \quad n = 1,2,\ldots,
 \end{equation}
@@
 \begin{equation}
-M_n = M_n (X_n,\theta_{n-1}) =\sgn (X_n - \theta_{n-1}).
+B_n = B_n (X_n,\theta_{n-1}) =\sgn (X_n - \theta_{n-1}).
 \end{equation}
@@
 \\
-In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $M_n$ is a function of the current gradient descent estimate $\theta_{n-1}$ and its private sample.
-As we explain next, it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ using only a single ``access'' to such state.
+In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $B_n$ depends on its private sample as well as the current gradient descent estimate $\theta_{n-1}$.
+In this sense, each encoder in this algorithm interacts with previous one by using the current estimate.
+%
+As we explain next, 
+it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ with only one round of interactions among the encoders.
+
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}[node distance=2cm,auto]
+  \node at (0,0) (source) {$X_1$} ;
+  \node[int1, right of = source, node distance = 1.2cm] (enc1) {Enc};  
+\draw[->,line width = 2pt] (source) -- (enc1);
+
+% \node[below of = source, node distance = 1cm] (source2) {$X_2$};
+%\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};  
+%\draw[->,line width = 2pt] (source2) -- (enc2);
+
+\node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
+\node[int1, right of = source3, node distance = 1.2cm] (enc3) {Enc};
+
+\draw[->,line width = 2pt] (source3) -- (enc3);
+
+\node[below of = source, node distance = 0.5cm] {$\vdots$};
+
+\node[int1, right of = enc3, node distance = 2.1cm ] (est) {Est 1};
+
+\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
+
+%\draw[->,line width = 2pt] (enc2) -| node[above, xshift = -1cm] (mes2) {$B_2$} (est);
+
+\draw[->,line width = 2pt] (enc3) -- node[above, xshift = 0cm]  {$B_{n_1}$} (est);
+
+\node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
+\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {Enc$(\hat{\theta}_1)$};  
+\draw[->,line width = 2pt] (sourceB) -- (enc1B);
+
+\node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
+\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {Enc$(\hat{\theta}_1)$};  
+\draw[->,line width = 2pt] (source3B) -- (enc3B); 
+\node[below of = sourceB, node distance = 0.4cm] {$\vdots$};
+
+\node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {Est 2};
+
+\draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.8cm] {$B_{n_1+1}$} (estB);
+\draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);
+
+\draw[->,line width = 0.5pt] (est.east) node[above, xshift  =0.5cm] {$\hat{\theta}_{n_1}$} -| (enc1B.north);
+
+\draw[->,line width = 0.5pt] (enc1B) -- (enc3B);
+
+%\draw[->,line width = 1pt] (enc1B)  -- node[right] {$\hat{\theta}_{n_1}$} (enc3B);
+
+\draw[->,line width = 2pt] (estB) -- +(0.8,0) node[right] {$\hat{\theta}_n$};
+\end{tikzpicture}
+\end{center}
+\caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
+\label{fig:one_round}
+}
+\end{figure}
 
@@
 \[
-M_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
+B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
 \]
@@
 %
-We now show that a similar encoding leads to an asymptotically normal estimator with the minimal variance $1/\eta(0)$, provided we may update once the threshold value $\theta_0$.
+We now show that a similar encoding leads to an asymptotically normal estimator with the minimal variance $1/\eta(0)$, provided we allow at least once to update the threshold value $\theta_0$. 
+%
 In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
-We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate $\hat{\theta}_{n_1}$ based on $M_1,\ldots,M_{n_1}$, and then use $\hat{\theta}_{n_1}$ as the new threshold value to obtain messages $M_{n_1+1}, \ldots, M_n$.
+We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate $\hat{\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use $\hat{\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$.
+Figure~\ref{fig:one_round} illustrates a diagram of this procedure.
+%
 The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
@@
 \[
-M_i = \begin{cases}
+B_i = \begin{cases}
  \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
@@
 \hat{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
-\frac{1}{n_1} \sum_{i=1}^{n_1} M_i 
+\frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
  \right).
@@
 \[
-\hat{\theta}_{n_2}  = \hat{\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} M_i \right)
+\hat{\theta}_{n_2}  = \hat{\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
 \]
@@
 \[
-p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} M_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
+p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
 \]
@@
 %
-
-To conclude the adaptive estimation setting, we now consider estimation from one-bit messages obtained via an encoding scheme that is one-step optimal.
-%Namely, each message obtained by employing the optimal the decision rule given the prior distribution and the previous messages.
-
-\subsection{One-step optimal estimation}
-We now consider an estimation scheme that posses the property of \emph{one-step optimality}: at each step $n$, the $n$th encoder designs the detection region $M_n^{-1}(1)$ such that the MSE given $M^n$ is minimal.
-In other words, this scheme designs the messages in a greedy manner, such that the MSE at step $n$ is minimal given the current state of the estimation described by $M^{n-1}$.
-\\
-
-The following theorem determine the message, i.e., the decision rule $(M^{n-1},X_n)\rightarrow M_n$, that minimizes the next step MSE:
-\begin{thm}[optimal one-step estimation] \label{thm:opt_one_step}
-Let $\pi(\theta)$ be an absolutely continuous log-concave probability distribution. Given a sample $X$ from a log-concave distribution with mean $\theta$, define 
-\begin{equation}
-\label{eq:adaptive_main_message}
-M^\star = \sgn(X - \tau),
-\end{equation}
-where $\tau$ satisfies the equation
-\begin{equation}
- \label{eq:fixed_point}
- \tau = \frac{m^-(\tau) + m^+(\tau)}{2},
-\end{equation}
-with
-\begin{align*}
-m^-(\tau)  & = \frac{\int_{-\infty}^{\tau} \theta \pi(d\theta) }{\int_{-\infty}^{\tau} \pi(d\theta)} ,\\
-m^+(\tau) & = \frac{\int_{\tau}^\infty \theta \pi(d\theta) }{\int_{\tau}^\infty \pi(d\theta)} .
-\end{align*}
-For any estimator $\hat{\theta}$ which is a function of $M(X) \in \{-1,1\}$,
-\begin{equation}
-\label{eq:opt_cond}
-\mathbb E \left(\theta-\hat{\theta}(M)\right)^2 \geq  \mathbb E \left(\theta- \mathbb E[\theta|M^\star]\right)^2.
-\end{equation}
-\end{thm}
-
-\begin{proof}
-The proof is the result of the following two lemmas, proofs of which can be found in the Appendix:
-\begin{lem} \label{lem:unique}
-Let $f(x)$ be a log-concave density function. Then the equation 
-\begin{equation}
-\label{eq:lem_fixed_point}
-2x = \frac{\int_x^\infty uf(u)du}{\int_x^\infty f(u)du} + \frac{\int_{-\infty}^x uf(u)du}{\int_{-\infty}^x f(u)du} 
-\end{equation}
-has a unique solution.
-\end{lem}
-\begin{lem} \label{lem:adaptive}
-Let $U$ be an absolutely continuous random variable with PDF $P(du)$. Set 
-\[
-M^\star(u)  =  \sgn(u - \tau),
-\]
-where $\tau$ is the unique solution to
- \[
-2 \tau = \frac{\int_{\tau}^\infty u P(du)} {\int_{\tau}^\infty P(du)} + \frac{\int_{-\infty}^{\tau} u P(du)}{\int_{-\infty}^{\tau} P(du)}.
-\]
-Then for any measurable $M: \mathbb R\to \{-1,1\}$,
-\[
-\int \left( u - \mathbb E[U|M^\star (u)]  \right)^2 P(du) \leq \int \left( u - \mathbb E[U|M(u)]  \right)^2 P(du). 
-\]
-\end{lem}
-\end{proof}
-
-\begin{rem}
-The optimal threshold given in Theorem~\ref{thm:opt_one_step} is different than the one given in \cite[Eq. 5]{1619423} for apparently the same problem. Indeed, it seems like Equation 4 in 
-\cite{1619423} is erroneous. 
-\end{rem}
-
-By applying the optimal one-step decision rule from Theorem~\ref{thm:opt_one_step} at each step, we arrive at the following adaptive encoding and estimation scheme: 
-\begin{itemize}
-\item Initialization: set $P_0(t) = \pi(t)$ and $\tau_0 = \mathbb E \theta$. 
-\item For $n\geq 1$:
-\begin{enumerate}
-\item[(1)] Update the prior as
-\begin{align}
-& P_n(t) = P(\theta=t |M^n) \nonumber \\
-& \quad = \frac{ P\left( \theta=t | M^{n-1} \right) P(M_n | \theta = t , M^{n-1})  } { P(M_n | M^{n-1} )} \nonumber \\ 
-& \quad = \alpha_n  P_{n-1}(t) F\left(M_n (t - \tau_{n-1}) \right), \label{eq:density_update}
-\end{align}
-where $\alpha_n$ is given by
-\[
-\alpha_n = \left(\int_{\mathbb R} P_{n-1}(t) F \left(M_n (t- \tau_{n-1}) \right)  dt \right)^{-1}. 
-\]
-\item[(2)] The $n$th estimate for $\theta$ is the conditional expectation of $\theta$ given $M^n$, namely
-\begin{equation}
-\theta_n = \mathbb E \left[ \theta| M^n\right] = \int_{-\infty}^\infty t P_n(t) dt. \label{eq:estimator_update}
-\end{equation}
-\item[(3)] Obtain $\tau_n$ from equation \eqref{eq:fixed_point} with the updated prior $P_n(t)$.
-Note that if $P_{n-1}(t)$ and $F(x)$ are log-concave, so does $P_n(t)$.
-Therefore, $P_n(t)$ is log-concave by induction and a unique solution to \eqref{eq:fixed_point} is guaranteed by Lemma~\ref{lem:unique}.
-\item[(4)] Update the $(n+1)$th message as
-\begin{equation}\label{eq:message_update}
-M_{n+1} = \sgn(X_{n+1}-\tau_n)
-\end{equation}
-\end{enumerate}
-\end{itemize}
-%Since Equation \eqref{eq:fixed_point} has no analytic solution in general, it is hard to derive the asymptotic behavior of the estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update}.
-We conjecture, however, that it attains the asymptotic relative efficiency of $4f^2(0)$ under the same conditions on $f(x)$ in the problem formulation.
-The normalized MSE of the estimator defined by \eqref{eq:estimator_update} and \eqref{eq:message_update} is illustrated in Fig.~\ref{fig:adaptive_error} in the case where $f(x)$ is the standard normal density.
-Also shown in Fig.~\ref{fig:adaptive_error} are the normalized MSE of the asymptotically optimal estimator defined by \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, as well as the MSE achieved by the sample mean for the same sample realization.
 
@@
 
-\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{one step optimal};
-
-\addplot[color = green!30!black, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
+%\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
+
+\addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
 \addlegendentry{single interaction};
@@
 
-\begin{comment}
-\subsection{Relation to Sigma-Delta Modulation \label{subsec:sdm}}
-The SDM is a device that converts continuous-time analog signals to a discrete-time sequence of binary digits.
-The basic operation of a SDM can be described as follows: the modulator takes as input a sequence of continuous amplitude samples $X_n$, which are typically represents samples of a continuous-time signal taken uniformly at sampling rate $f_s$ much higher than the Nyquist rate of the signal \cite{1095151}.
-The output of the modulator is a sequence $M_n$ of binary values, obtained according to the following rule:
-\begin{align}
-\begin{cases} V_{n+1} & =  V_n - \alpha q(V_n) + X_n, \\
-M_n & = \sgn(V_n)  \end{cases}, \quad n=1,2,\ldots, \label{eq:sdm}
-\end{align}
-where $\alpha > 0$ is a parameter of the modulator that is determined by the maximal value of the input sequence $X^n$.
-The SDM of the form \eqref{eq:sdm} was studied in \cite{53738} under the assumption that the input process $X_n$ is an i.i.d Gaussian process.
-The main results from \cite{53738} shows that regardless of the initial state $V_0$, the process $M_n$ is a stationary ergodic process with mean $\theta$.
-It follows that a consistent estimation of $\theta$ is obtained by taking the mean of the sequence $\{M_n\}$.
-However, the results from \cite{53738} does not provide a closed form for the second order statistics of $\{M_n\}$, so that convergence rate cannot be derived from \cite{53738}.
-\end{comment}
-
 \section{Distributed Estimation \label{sec:distributed}}
-We now consider the distributed encoding setting described in Fig.~\ref{fig:distributed} (Setting (iii) in the Introduction).
-In this setting each one-bit message $M_i$ is only a function of its private sample $X_i$, and hence $M_i$ characterized by its \emph{detection region}, defined as
-\[
-A_i = \left\{ x \in \mathbb R \,:\, M_i(x) = 1 \right\}.
-\]
-Consequently, $M_i$ is of the form
-\[
-M_i = \begin{cases} 1 & X_i \in A_i, \\
+We now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii).
+In this setting each one-bit message $B_i$ is only a function of its private sample $X_i$, and hence $B_i$ characterized by its \emph{detection region}, defined as
+\[
+A_i = \left\{ x \in \mathbb R \,:\, B_i(x) = 1 \right\}.
+\]
+Consequently, $B_i$ is of the form
+\[
+B_i = \begin{cases} 1 & X_i \in A_i, \\
 -1 & X_i \notin A_i,
@@
 
-As a first step, we provide conditions under which the messages $M_1,M_2,\ldots$ define a local asymptotic normal family.
+As a first step, we provide conditions under which the messages $B_1,B_2,\ldots$ define a local asymptotic normal family.
 
@@
 \[
-M_n = \begin{cases} 1 & X_n \in A_n, \\
+B_n = \begin{cases} 1 & X_n \in A_n, \\
 -1 & X_n \notin A_n. 
@@
 \begin{align*}
-& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (M_1,\ldots,M_n) }{
-\mathbb P_{\theta} (M_1,\ldots,M_n)} \\
+& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (B_1,\ldots,B_n) }{
+\mathbb P_{\theta} (B_1,\ldots,B_n)} \\
 & \overset{D}{\longrightarrow} \mathcal N\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
@@
 \end{thm}
-Theorem~\ref{thm:LAN1} provides conditions under which $M_1,\ldots,M_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}.
-An important conclusion of this theorem follows from the local asymptotic minimax property of estimators in LAN models (e.g.
-\cite{van2000asymptotic}):
+Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}. 
+%
+Among these conditions, (iii) is arguably the strongest and hardest to verify.
+As we show in Section~\ref{subsec:threshold} below, this condition is satisfied, for example, when $A_1, \ldots,A_n$ are half lines whose starting points are drawn independently from some probability measure on $\mathbb R$.
+Similar ideas imply that condition (iii) holds whenever we choose the intervals consisting each $A_i$ according to some pre-specified distribution.
+\par
+%
+An important conclusion of  Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models (e.g. \cite{van2000asymptotic}):
 \begin{cor} \label{cor:LA_minimax}
-Let $\hat{\theta}_n$ be an estimator of $\theta \in \Theta$ from $M_1,\ldots,M_n$ with detection regions $A_1,\ldots,A_n$.
-Assume that as $n$ goes to infinity, conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
+Let $\hat{\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
 Then for any bounded, symmetric, and quasi-convex function $L$,
-\[
-\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\hat{\theta}_{n} - \tau) \right) \right] \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
-\]
+\begin{align*}
+& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\hat{\theta}_{n} - \tau) \right) \right]
+\\
+& \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
+\end{align*}
 where $Z \sim \mathcal N(0,1)$. In particular, for $L(x) = x^2$, 
-\[
+\begin{align*}
 \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( \hat{\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
-\]
+\end{align*}
 \end{cor}
@@
 
-\subsection{Threshold Detection}
-Assume now that each $M_i$ is of the form
+\subsection{Threshold Detection \label{subsec:threshold}}
+Assume now that each $B_i$ is of the form
 \begin{equation}
 \label{eq:threshold_message}
-M_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
+B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
 -1 & X_i > t_i,
@@
 where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder.
-In other words, the detection region of $M_i$ is $A_i = (t_i,\infty)$ and $\mathbb P(X_i \in A_i) = F \left( M_i(t_i-\theta) \right)$.
+In other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and $\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$.
 It follows that
@@
 Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$.
-Then $\left\{ M_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a LAN family with precision parameter
+Then $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a LAN family with precision parameter
 \[
@@
 \end{cor}
-
-Due to local asymptotic normality of $\{M_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $M_1,\ldots,M_n$, denoted here by 
+The condition that $\lambda_n$ converges to a probability measure is satisfies, for example, whenever the $t_1,\ldots,t_n$s are drawn independently from a probability distribution $\lambda(dt)$ on $\mathbb R$.
+\par
+Due to local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by 
 $\hat{\theta}^{ML}_n$, is local asymptotic minimax in the sense that 
@@
 \label{eq:ML}
-\sum_{i=1}^n M_i \frac{f \left( t_i-\theta\right) }{F \left(M_i  (t_i-\theta)\right) },  
+\sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) },  
 \end{equation}
@@
 width=8cm, height=6cm,
-xmin = 0, xmax=2.5, 
+xmax=2.5, 
 xmode = log,
@@
 
-\begin{comment}
-\subsection{Asymptotic Bayes Risk}
 \begin{figure}
@@
 Since the function $x \rightarrow 1/x$ is convex for positive values, \eqref{eq:cvx_average} defines a convex optimization problem in $\lambda$ whose solution depends on the prior $\pi$.
-The solution to this problem is approximated by considering $\lambda$ and $\pi$ over a discrete set in a similar way that \eqref{eq:cvx_minimax} is obtained from \eqref{eq:var_cvx_minimax}.
-\par
-For the case of a normal distribution ($P_X = \mathcal N(\theta, \sigma^2)$) and a uniform prior ( $\pi(d\theta) =dt/(2b)$), the optimal asymptotic threshold density obtained as the solution to \eqref{eq:cvx_average} is illustrated in Fig.~\ref{fig:opt_density}, whereas Fig.~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
+The solution to this problem is approximated by considering $\lambda$ and $\pi$ over a discrete set.
+On Figure~\ref{fig:opt_density} we illustrate the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distributon ($P_X = \mathcal N(\theta, \sigma^2)$) and the prior on $\theta$ is uniform over $\Theta = [-b,b]$.
+Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
 \par
@@
 
-% The following proposition implies that this bound is always tight as $\sigma / \sigma_\theta$ goes to infinity.
-%\begin{prop} \label{prop:asymp}
-% For any prior $\pi(\theta)$ for which
-%\[
-%\int \frac{\pi(d\theta)}{\eta \left(\theta \right)} < \infty,
-%\]
-%we have 
-%\begin{align}
-%\label{eq:asymp}
-%\mathbb E [1/\kappa(\theta)] = \frac{\pi}{2} + \left( \frac{\pi}{2} - 1\right) \left(\frac{\sigma_\theta}{\sigma} \right)^2 + o \left(\frac{1}{\sigma} \right)^3. 
-%\end{align}
-%as $\sigma_\theta / \sigma \rightarrow 0$. 
-%\end{prop}
-%\begin{proof}
-%It is enough to prove that  \eqref{eq:asymp} holds for the upper bound \eqref{eq:upper_bound}.
-First note that the condition in the proposition implies that all the moments of $\pi(\theta)$ exists, and in particular its second and third.
-The results follows by expanding the function $1/\eta(x)$ in a power series around zero as
-%\[
-%1/\eta(x) = \frac{\pi}{2} + \left(\frac{\pi}{2}-1 \right) x^2 + o(x^3).
-%\]
-%\end{proof}
-\end{comment}
-
 \section{Conclusions \label{sec:conclusions}}
@@
 We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median.
-%We further showed that the optimal MSE and ARE can be attained using only a single adaptation. Namely, a single round of communication between {\color{red} the estimator and the encoder} . 
-We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
-%Numerical simulations show that the one-step optimal scheme attains the optimal relative efficiency for the normal distribution.
+%We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
 \par
@@
 \section{Proofs \label{app:proofs}}
+
+\subsection{Proof of Proposition~\ref{prop:ceo_lower_bound}}
+
+First, we note that when $f(x) = \mathcal N(0,\sigma^2)$ and $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$, our distributed setting reduces to the Gaussian CEO problem with $R_1=\ldots = R_n =1$ and $k=1$.
+Therefore, any MSE attained in our distributed setting is also attained by the CEO and thus the optimal CEO strategy (with arbitrary $k$) provides a lower bound to the MSE in our setting.
+\\
+
+Consider the minimal distortion $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
+from \cite[Eq. 10]{chen2004upper}:
+\begin{equation} \label{eq:ceo_optimal_sumrate}
+R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
+\end{equation}
+For the special case of $R_\Sigma = n$ and $L=n$, we get
+\begin{equation} \label{eq:ceo_optimal_sumrate2}
+n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
+\end{equation}
+$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
+Therefore, this $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
+By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
+\[
+D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
+\]
+We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO distortion while enforcing the condition $R_1=\ldots = R_n = 1$.
+Indeed, an upper bound for the CEO distortion under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
+\[
+D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
+\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
+\]
+which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.
 
@@
 \subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
+When $f(x)$ is the normal density function, this lemma follows from \cite[Thm.
+3]{Barnes2018}.
+The proof below is based on a different techique than in \cite{Barnes2018}, and is valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}.
+\\
+
 The Fisher information of $M$ with respect to $\theta$ is given by
@@
 \begin{align*}
-\mathbb P(M_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
+\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
 & = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
@@
 We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $M_i$ can is of the form
+In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
 \begin{equation}
 \label{eq:general_messages}
-M_i = \begin{cases}
+B_i = \begin{cases}
 X_i \in A_i & 1, \\
@@
 where $A_i \subset \mathbb R$ is a Borel measurable set. 
-%Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = M^{-1}(1)$.
-Consider the conditional distribution $P({M^n|\theta})$ of $M^n$ given $\theta$. We have 
+%Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
+Consider the conditional distribution $P({B^n|\theta})$ of $B^n$ given $\theta$. We have 
 \begin{align}
-P\left( M^n | \theta \right) & =  \prod_{i=1}^n P\left(M_i | \theta, M^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
+P\left( B^n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
 \end{align}
-where $P\left(M_i =1 | \theta, M^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $M^n$ with respect to $\theta$ is given by 
+where $P\left(B_i =1 | \theta, B^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B^n$ with respect to $\theta$ is given by 
 \begin{align}
-I_\theta(M^n) = \sum_{i=1}^n I_\theta (M_i|M^{i-1}),
+I_\theta(B^n) = \sum_{i=1}^n I_\theta (B_i|B^{i-1}),
 \label{eq:fisher_information}
 \end{align}
-where $I_\theta (M_i|M^{i-1})$ is the Fisher information of the distribution of $M_i$ given $M^{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (M_i|M^{i-1}) \leq 4f^2(0)$.
+where $I_\theta (B_i|B^{i-1})$ is the Fisher information of the distribution of $B_i$ given $B^{i-1}$.
+From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B^{i-1}) \leq 4f^2(0)$.
 The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
 \begin{align*}
-\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(M^n) + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (M_i | M^{i-1} ) + I_0} \\
+\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(B^n) + I_0} \\
+& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
 & \geq \frac{1}{ 4f^2(0) n + I_0}.
@@
 
-\subsection*{Proof of Theorem~\ref{thm:opt_one_step}}
-In this subsection we prove Lemmas~\ref{lem:adaptive} and~\ref{lem:unique} which together implies Theorem~\ref{thm:opt_one_step}.
-
-\subsubsection*{Proof of Lemma \ref{lem:adaptive}}
-Any one-bit message $M(u) \in \{0,1\}$ is characterized by two decision region $A_1 = M^{-1}(1)$ and $A_{-1} = M^{-1}(-1)$, so that $\mathbb E \left[ U | M(U) \right]$ assumes only two values: $\mu_1 = \mathbb E \left[ U | M(U) = 1 \right]$ and $\mu_{-1} = \mathbb E \left[ U | M(U) = -1 \right]$.
-We claim that a necessary condition for $M(u)$ to be optimal is that the sets $A_1$ and $A_{-1}$ are the Voronoi sets on $\mathbb R$ corresponding to the points $\mu_1$ and $\mu_{-1}$, respectively, modulo a set of measure $P(du)$ zero.
-Indeed, assume by contradiction that for such an optimal partition there exists a set $B \subset A_{1}$ with $\mathbb P (U \in B) >0$ such that $\left( b-\mu_{1} \right)^2 > \left( b- \mu_{-1} \right)^2$.
-The expected square error in this partition satisfies:
-\begin{align*}
-& \int_{\mathbb R} \left( u - \mathbb E[U|M(u)]  \right)^2 P(du) =  \\
-& \int_{A_1} (u- \mu_1)^2 P(du) + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
-& = \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_1)^2 P(du) \\
-& \quad + \int_{A_{-1}} (u- \mu_{-1})^2 P(du) \\
-& > \int_{A_1\setminus B} (u- \mu_1)^2 P(du) +  \int_{B} (u- \mu_2)^2 P(du) \\
-& \quad + \int_{A_{-1}} (u- \mu_{-1})^2 P(du),
-\end{align*}
-so the partition $A_1' = A_1 \setminus B$, $A_{-1}' = A_{-1} \cup B$ attains lower error variance which contradicts the optimality assumption and proves our claim.
-It is evident that Voronoi partition of the real line corresponding to $\mu_1$ and $\mu_{-1}$ is of the form $A_{-1} = (-\infty,\tau)$, $A_{1} = (\tau, \infty)$ where the point $\tau$ is of equal distance from $\mu_1$ and $\mu_{-1}$, namely $\tau = \frac{\mu_1 + \mu_{-1}}{2}$.
-From these two conditions (which are a special case of the conditions derived in \cite{1056489} for two quantization regions) we conclude that $\tau$ must satisfy the equation
-\[
-2 \tau = \frac{\int_{\tau}^\infty u P(du)}{\int_{\tau}^\infty P(du)} + \frac{\int_{-\infty}^{\tau} u P(du)}{\int_{-\infty}^{\tau} P(du)}.
-\] 
-\QEDA
-
-\subsubsection*{Proof of Lemma \ref{lem:unique}} 
-Any solution to \eqref{eq:lem_fixed_point} is a solution to $h^+(x) = h^-(x)$ where
-\[
-h^+(x) = \frac{\int_x^\infty uf(u)du}{\int_x^\infty f(u)du} - x 
-\]
-and
-\[
-h^-(x) = x - \frac{\int_{-\infty}^x uf(u)du}{\int_{-\infty}^x f(u)du}.
-\]
-We now prove that $h^+(x)$ is monotonically decreasing while $h^-(x)$ is increasing, so they meet at most at one point. The derivative of $h^-(x)$ is given by
-\begin{equation} 
-\label{eq:one_step_proof_derivative}
-1 - \frac{ f(\tau) \int_{-\infty}^\tau f(x) (\tau-x)dx } {\left( \int_{-\infty}^\tau f(x) dx \right)^2}.
-\end{equation}
-Denote $F(x) = \int_{-\infty}^x f(u)du$.
-Using integration by parts in the numerator and from the fact that $\lim_{\tau \rightarrow -\infty}  \tau \int_{-\infty}^\tau f(x) dx = 0$, the last expression can be written as
-\[
-1- \frac{ f(\tau) \int_{-\infty}^\tau F(x) dx}
- {\left( F(\tau) \right)^2}.
-\]
-Log-concavity of $f(x)$ implies log-concavity of $F(x)$, so that we can write $F(x) = e^{g(x)}$ for some concave and differentiable function $g(x)$.
-Moreover, we have $f(x) = g'(x)e^{g(x)}$ where, by concavity of $g(x)$, the derivative $g'(x)$ of $g(x)$ is non-increasing.
-With these notation we have
-\begin{align*}
-\frac{ f(\tau) \int_{-\infty}^\tau F(x) dx}
- {\left( F(\tau) \right)^2} & = \frac{g'(\tau)e^{g(\tau)} \int_{-\infty}^\tau e^{g(x)}dx }{ e^{2g(\tau)} } \\
- & = e^{-g(\tau)} \int_{-\infty}^\tau g'(\tau) e^{g(x)} dx  \\
- & \leq e^{-g(\tau)} \int_{-\infty}^\tau g'(x) e^{g(x)} dx \\
- & = e^{-g(\tau)} F(\tau) = 1.
-\end{align*}
-(where the second from the last step follows since $g'(x) \leq g'(\tau)$ for any $x\leq \tau$).
-If follows that \eqref{eq:one_step_proof_derivative} is non-negative and thus $h^-(x)$ is monotonically increasing.
-Since
-\[
-h^+(-x) = x - \frac{ \int_{-\infty}^{x} uf(-u)du}{ \int_{-\infty}^x f(-u) du }, 
-\]
-the fact that $h^+(x)$ is monotonically decreasing follows from similar arguments.
-Moreover, since the derivatives of $h^+(x)$ and $h^-(x)$ never vanish at the same time over any open interval, their difference cannot be constant over any interval.
-Finally, since
-\begin{align*}
- \lim_{x\rightarrow -\infty} h^+(x) =  \lim_{x\rightarrow \infty} h^-(x)
-\end{align*}
-and since non of these functions are constant, monotonicity of $h^+(x)$ and $h^-(x)$ implies that they must meet at some $x\in \mathbb R$. \QEDA
-
 \subsection*{Proof of Theorem~\ref{thm:LAN1}}
-The log probability mass distribution of $M^n=(M_1,\ldots,M_n)$ is given by
-\begin{align*}
-& \log \Prob_\theta(m^n) = \sum_{i=1}^n \left( \frac{m_i+1}{2} \log  \Prob(X_i\in A_i) + 
-\frac{1-m_i}{2} \log \Prob(X_i\in A_i) \right), \quad m^n \in \{-1,1\}^n. 
+The log probability mass distribution of $B^n=(B_1,\ldots,B_n)$ is given by
+\begin{align*}
+& \log \Prob_\theta(b^n) = \sum_{i=1}^n \left( \frac{b_i+1}{2} \log  \Prob(X_i\in A_i) + 
+\frac{1-b_i}{2} \log \Prob(X_i\in A_i) \right), \quad b^n \in \{-1,1\}^n. 
 \end{align*}
@@
 \begin{align}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(m^n)} { \Prob_\theta (m^n) } = \sum_{i=1}^n    \frac{m_i+1}{2} 
+& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) } = \sum_{i=1}^n    \frac{b_i+1}{2} 
 \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} + 
-\sum_{i=1}^n  \frac{1-m_i}{2} 
+\sum_{i=1}^n  \frac{1-b_i}{2} 
 \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}. 
@@
 \begin{align*}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(m^n)} { \Prob_\theta (m^n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
+& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
 \left( 
-\frac{m_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-m_i}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}   \right) \\
+\frac{b_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
+ \frac{1-b_i}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}   \right) \\
  & - \frac{h^2}{2n} 
@@
 \left( 
- \frac{m_i+1}{2} 
+ \frac{b_i+1}{2} 
 \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
 + 
- \frac{1-m_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 \right) + o(h^2) \\
+ \frac{1-b_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 \right) + o(h^2) \\
 \end{align*}
@@
 \[
-U_i = \frac{M_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-M_i}{2}  \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}. 
+U_i = \frac{B_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
+ \frac{1-B_i}{2}  \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}. 
 \]
@@
 \[
-V_i =  \frac{M_i-1}{2} 
+V_i =  \frac{B_i-1}{2} 
 \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
 + 
- \frac{1-M_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2.
+ \frac{1-B_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2.
 \]
@@
 \mathbb E  [U_i] & = 
- \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}   \Prob (M_i=1)   + 
- \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}   \Prob (M_i=-1)  = 0. 
+ \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=1)   + 
+ \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=-1)  = 0. 
 \end{align*}
@@
 & \mathbb E U_i^2 = 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2  \Prob (M_i=1)   + 
-\left( \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2 \Prob (M_i=-1) \\
+\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2  \Prob (B_i=1)   + 
+\left( \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2 \Prob (B_i=-1) \\
 & =
@@
 %
-Since $M_1,M_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, for $\theta \in \Xi$ if and only if
+Since $B_1,B_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, for $\theta \in \Xi$ if and only if
 \begin{equation}
@@
 \end{equation}
-By assumption, we have $M_i^{-1} = A_i$ where $A_i$ can be expressed as
+By assumption, we have $B_i^{-1} = A_i$ where $A_i$ can be expressed as
 \[
@@
 \bibliographystyle{IEEEtran}
-\bibliography{/Users/kipnisal/LaTex/bibtex/IEEEfull,/Users/kipnisal/LaTex/bibtex/sampling}
+\bibliography{IEEEfull,onebit}
 
 \end{document}
-
-\begin{comment}
-\subsection{Remote Multiterminal Source Coding}
-The remote multi-terminal lossy source coding problem (a.k.a the CEO problem) \cite{berger1996ceo}, considers $n$ encoders (agents), each has access to a corrupted version of a source signal, transmit at rates $R_1,\ldots,R_n$ to a central estimation unit.
-The distributed estimation setting (iii) corresponds to a single round of communication in the CEO setting, where the $i$th agent observes
-\begin{equation}
-\label{eq:Gaussian_channel}
-X_i = \theta + Z_i,
-\end{equation}
-and has $R_i=1$ bits to transmit this observation.
-Note, however, that in the CEO setting each encoder observes multiple number, say $k$, of independent samples $\theta \sim \pi(\theta)$ through the channel \eqref{eq:Gaussian_channel}, and not just one sample as in our setting.
-In general, in the CEO setting each encoder is allowed $kR_i$ bits to represent its $k$ samples.
-One possible strategy of the encoder is to send $k$ single bit messages, each of which is only a function of its $k$th observation.
-%the minimal MSE distortion of the CEO provides a lower bound for the MSE in the distributed encoding scheme. 
-As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise of variance $\sigma^2$ provides a lower bound on the MSE distortion in estimating $\theta$.
-Moreover, the difference between this lower bound and the actual MSE in our setting would indicate the importance of coding over blocks consisting of multiple independent realizations of  in our joint estimation and communication problem.
-\par
-%Note that when multiple realization of $\theta$ are involved, the prior distribution $P_\theta$ plays a significant role in the overall MSE, whereas in our case we expect the final distortion to be independent of the actual prior distribution as in the two schemes in the sequential case.
-\\
-A closed-form expression for CEO under quadratic distortion is known only for the case where the sequence to described by the encoders is sampled from a Gaussian distribution \cite{prabhakaran2004rate}.
-By using the characterization of the minimal CEO distortion as the number of terminals goes to infinity, we conclude the following result:
-\begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\pi(\theta)$ is the normal distribution. Then any estimator $\hat{\theta}_n$ of $\theta$ in the distributed setting satisfies
-\[
-\lim_{n\rightarrow \infty}  n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3n}.
-\]
-\end{prop}
-\begin{proof}
-We consider the following expression from \cite[Eq.
-10]{chen2004upper} that provides the minimal distortion $D^\star$ in the CEO with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots R_L$:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-Assuming $R_\Sigma = n$ and $L=n$ we get
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-n = \frac{1}{2} \log \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-The value of $D^\star$ that satisfies the equation above describes the MSE in the quadratic Gaussian CEO setting under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate} as $n\rightarrow \infty$ we conclude that
-\[
-D^\star = \frac{ \frac{4\sigma^2}{3} }{n + \frac{4 \sigma^2}{3 \sigma_\theta^2} } + O(e^{-n}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-\end{proof}
-We note that although the CEO lower bound was derived by the MSE attainable assuming optimal allocation a total of $n$ bits among the encoders, the same expression is from the upper bound to the CEO derived in \cite[Prop.
-5.2]{KipnisRini2017}, that assumes $R_1=\ldots,R_n = 1$ rather than optimal allocation of $n$ bits among all encoders.
-%\[
-%D_{CEO} / \sigma_\theta^2 \leq \left( 1 + \sum_{i=1}^n \frac{\sigma_\theta^2}{\sigma^2} \frac{1 - 2^{-2R_i}} {1+ \frac{\sigma_\theta^2}{\sigma^2}  2^{-2 R_i}  } \right)^{-1}
-%\]
-%where $\sigma_\theta^2$ is the variance of the distribution $\pi(\theta)$. Using $R_1=\ldots=R_n=1$ we get
-%\[
-%D_{CEO} \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + o(n^{-1}). 
-%\]
-
-The bound provided by the CEO in Prop.~\ref{prop:ceo_lower_bound} implies that the relative efficiency in the distributed scheme is at most $4/3$.
-Since this number is smaller than the relative efficiency of the adaptive scheme, this proposition does not provide new information on the relative efficiency.
-It does, however, provides the intuition that the limiting factor in estimating $\theta$ is the strict bit-constraint and or the lack of concentration of probability distributions over blocks, rather than distributed estimation.
-\\
-
-We note that the same first order expression for the CEO distortion is achieved by a particular encoding scheme derived in \cite{KipnisRini2017}, assuming rate of $1$ bits per source symbol at each encoder, i.e.,  $R_1=\ldots = R_n = 1$, rather than a total of $n$ bits on average allocated among the $n$ encoders used in the proof.
-Indeed, the it follows from \cite[Eq.
-?]{KipnisRini2017} that the following distortion is achievable in the CEO problem:
-\[
-\sigma_\theta^2 \left( 1 + \sigma_\theta^2 n \frac{3}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   = \frac{4\sigma^2+\sigma_\theta^2}{3n} + O(n^{-2} \sigma_\theta^4)). 
-\]
-As a result, we conclude that the above lower bound cannot be strengthen if we consider the exact distortion of the CEO with equal rate-allocation using the expression from \cite{prabhakaran2004rate}.
-\\
-
-%Comnet on appearance of $\sigma_\theta^2$ as a second order term.
-
-\end{comment}
-\end{document}

### 2019-06-19 onebit_full_V2.tex
Proof of normal approximation to SGD

@@
-%\documentclass[letterpaper]{IEEEtran}
 \documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper
@@
 
+\usepackage[hidelinks]{hyperref}
 %\tikzexternalize[mode=list and make]
@@
 \newcommand{\mmse}{\mathsf{mmse}}
+\newcommand{\ex}[1]{\ensuremath{\mathbb{E}\left[ #1\right]}}
+
+\newcommand{\Var}[1]{\ensuremath{\mathrm{Var} \left[ #1\right]}}
+
 \newcommand{\unif}{\mathsf{unif}}
@@
 \newcommand{\CEO}{\mathsf{CEO}}
+\newcommand{\Ncal}{\mathcal{N}}
 
@@
 
-%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
+%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim {\Ncal} \left(\theta, \sigma^2 \right)$};
 \node[below of = source2, node distance = 0.5cm] {$\vdots$};
@@
 \[
-\sqrt{a_n}\left(\hat{\theta}_n - \theta\right) \overset{D}{\longrightarrow} \mathcal N(0, \sigma^2).
+\sqrt{a_n}\left(\hat{\theta}_n - \theta\right) \overset{d}{\longrightarrow} \Ncal(0, \sigma^2).
 \]
@@
 
-\section{Consisten Estimation and Existing Bounds \label{sec:preliminary}}
+\section{Consistent Estimation and Off-the-shelf Bounds \label{sec:preliminary}}
 %On a first impression, it may not be clear whether consistent estimation of the mean is even possible in the adaptive and centralized settings.
@@
 \[
-p_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
+P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
 \]
@@
 \label{eq:estimator_naive}
-\hat{\theta}_n = \theta_0 + F^{-1}\left( p_n \right)
-\end{equation}
-is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set.
-Furthermore, the variance of $p_n$ is $F(\theta-\theta_0)F(\theta_0-\theta)$, and hence the delta method implies that $\hat{\theta}_n$ is asymptotically normal with variance
-\begin{equation} 
-\frac{1}{
-\eta(\theta-\theta_0)} = \frac{F(\theta-\theta_0)F(\theta_0-\theta)}{f^2(\theta-\theta_0)}. 
+\hat{\theta}_n = \theta_0 + F^{-1}\left( P_n \right)
+\end{equation}
+is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set due to log-concavity.
+Furthermore, the variance of $P_n$ is $F(\theta-\theta_0)F(\theta_0-\theta)$, and hence the delta method implies that $\hat{\theta}_n$ is asymptotically normal with variance
+\begin{equation} 
+ \frac{F(\theta-\theta_0)F(\theta_0-\theta)}{f^2(\theta-\theta_0)} = \frac{1}{
+\eta(\theta-\theta_0)}.
 \end{equation}
@@
 Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of $\hat{\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
-This ARE is attained only when $\theta_0 = \theta$, although $\theta$ is unknown apriori.
+This ARE is attained only when $\theta_0 = \theta$, whereas $\theta$ is apriori unknown.
 Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of $\hat{\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
-As an example, when $f(x)$ is a normal density, the ARE of $\hat{\theta}_n$ is $\approx 0.07$ when $\theta_0$ is $2.33$ standard deviations from $\theta$.
+As an example, when $f(x)$ is a normal density, the ARE of $\hat{\theta}_n$ is less than $\approx 0.14$ when $\theta_0$ is $2$ standard deviations from $\theta$.
 Therefore, the estimator $\hat{\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
 \par
-It is suggested that lower variance can be obtained by an estimator of the form \eqref{eq:estimator_naive} if, after observing a batch of the single bit messages, one can update the threshold value $\theta_0$.
-Such a scheme falls within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
+It is suggested that we can attain lower variance in estimation by updating the threshold value $\theta_0$ in \eqref{eq:estimator_naive} after observing one or a batch of the single bit messages.
+Schemes with such adaptation fall within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
 \\
-% variance equals to $1/\eta(0)n + o(1)$.
-We also show in Section~\ref{sec:sequential} that no estimator can attain variance that is asymptotically smaller than $1/\eta(0)n$, so that the ARE of any estimator in settings (ii) and (iii) is at least $\eta(0) \sigma^2$.
 
@@
 \[
-D_{CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - \hat{\theta}_j \right)^2 \right]. 
+MSE_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - \hat{\theta}_j \right)^2 \right]. 
 \]
@@
 \begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$. Then any estimator $\hat{\theta}_n$ of $\theta$ in the distributed setting satisfies
+Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$. Then any estimator $\hat{\theta}_n$ of $\theta$ in the distributed setting satisfies
 \begin{equation} \label{eq:ceo_bound}
- n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + O(n^{-1}),
+ n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
 \end{equation}
@@
 \begin{proof}
-See Appendix. 
+See Appendix~\ref{app:proof:prop_ceo_lower_bound}.
 \end{proof}
@@
 Once this bound is achieved, the result follows by using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are in the Appendix.\\
+The details are in Appendix~\ref{proof:thm:adpative_lower_bound}.\\
 
@@
 \begin{equation} \label{eq:sgd_est}
-\hat{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
+\bar{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
 \end{equation}
@@
 \begin{thm} \label{thm:sgd}
-Consider the sequence $\left\{\hat{\theta}_n,\, n\in \mathbb N \right\}$ defined by \eqref{eq:sgd_est}. 
+Consider the sequence $\left\{\bar{\theta}_n,\, n\in \mathbb N \right\}$ defined by \eqref{eq:sgd_est}. 
 \begin{enumerate}
@@
 \[
-\sqrt{n} \left( \hat{\theta}_n - \theta \right) \overset{d}{\rightarrow} \mathcal N \left(0,  1/\eta(0) \right).
-\]
-\item[(ii)] Assume that in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ satisfies
+\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left(0,\frac{1}{\eta(0)}\right).
+\]
+\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with finite Fisher information for location
+\[
+I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)}  \right)^2 f(x) dx < \infty.
+\]
+%(or that $f(x-\theta)$ is differentiable in quadratic mean).  
+For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $P^n_{\theta,h,n}$ be the measure with density $f(x-\theta - h/\sqrt{n})$. Then 
+\begin{align}
+\label{eq:sgd_part2}
+\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
+\end{align}
+under $P^n_{\theta,h,n}$. 
+\item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ satisfies
 \begin{equation} \label{eq:conditions2}
@@
 \end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ with $2/3<\beta<1$). Then
-\[
-\lim_{n\rightarrow \infty} n\mathbb E \left[ \left(\theta-\hat{\theta}_n \right)^2 \right] = \frac{1}{\eta(0)}. 
+(e.g., $\gamma_n = n^{-\beta}$ with $\beta \in (2/3,1)$). Then
+\[
+\lim_{n\to \infty} n \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{\eta(0)}. 
 \]
@@
 \subsubsection*{Proof}
-The asymptotic behavior of \eqref{eq:sgd_est} follows from \cite[Thm. 4]{polyak1992acceleration} and \cite[Thm. 2]{polyak1990new}. The details are in the Appendix. \\
+See Appendix~\ref{proof:thm:sgd}. \\
 
 Theorem~\ref{thm:sgd} implies that the estimator $\hat{\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the maximal ARE as established by Theorem~\ref{thm:adpative_lower_bound}.
+Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$.
+%
 The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$.
@@
 \node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
-\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {Enc$(\hat{\theta}_1)$};  
+\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {Enc$(\hat{\theta}_{n_1})$};  
 \draw[->,line width = 2pt] (sourceB) -- (enc1B);
@@
 \node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
-\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {Enc$(\hat{\theta}_1)$};  
+\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {Enc$(\hat{\theta}_{n_1})$};  
 \draw[->,line width = 2pt] (source3B) -- (enc3B); 
@@
 
-\subsection{Optimality using a Single Interaction}
+\subsection{Optimality using Single Threshold Adaptation}
 In Section~\ref{sec:preliminary} we considered an estimator that is based on messages of the form 
@@
 \begin{align*}
- \sqrt{n} \left( \hat{\theta}_{n_2} - \theta  \right)^2  \overset{D}{\longrightarrow}  \mathcal N\left( 0, 1/\eta(0) \right).
+ \sqrt{n} \left( \hat{\theta}_{n_2} - \theta  \right)^2  \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
 \end{align*}
@@
 & \sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)  = \sqrt{\frac{n}{n_2}} \sqrt{n_2} \left(  p_{n_2}(t) - F(\theta - t) \right) \\
-& \overset{D}{\rightarrow} \mathcal N\left( 0, V(t) \right),
+& \overset{d}{\rightarrow} \Ncal\left( 0, V(t) \right),
 \end{align*}
@@
 &= \sqrt{n} \left( g(\hat{p}_{n_2}(t)) - g \left(F(\theta-t) \right)  \right) \\
-& \overset{D}{\to} \mathcal N\left(0, 
+& \overset{d}{\to} \Ncal\left(0, 
 1/\eta(\theta-t) \right).
@@
 & = \sqrt{n} \left( \hat{\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}(\hat{\theta}_{n_1})) - \theta \right)  \\
-& \overset{D}{\to} \mathcal N\left( 0, 
+& \overset{d}{\to} \Ncal\left( 0, 
 1/\eta(0) \right). 
@@
 \mathbb P_{\theta} (B_1,\ldots,B_n)} \\
-& \overset{D}{\longrightarrow} \mathcal N\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
+& \overset{d}{\longrightarrow} \Ncal\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
 \end{align*} 
 \end{thm}
+
+\begin{proof}
+See Appendix~\ref{proof:thm:LAN1}. 
+\end{proof}
+
 Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}. 
@@
 \end{align*}
-where $Z \sim \mathcal N(0,1)$. In particular, for $L(x) = x^2$, 
+where $Z \sim \Ncal(0,1)$. In particular, for $L(x) = x^2$, 
 \begin{align*}
@@
 \begin{proof}
-See Appendix. 
+See Appendix~\ref{proof:non_existence}
 \end{proof}
@@
 \[
-\sqrt{n} \left( \hat{\theta}^{ML}_n - \theta \right) \overset{D}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
+\sqrt{n} \left( \hat{\theta}^{ML}_n - \theta \right) \overset{d}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
 \]
@@
 \caption{\label{fig:minimax_support}
-Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \mathcal N(\theta,\sigma^2)$ and $\theta \in \Theta = [-T,T]$.
+Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in \Theta = [-T,T]$.
 %
@@
 \end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \mathcal N(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
+\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \Ncal(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
 The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
@@
 The solution to this problem is approximated by considering $\lambda$ and $\pi$ over a discrete set.
-On Figure~\ref{fig:opt_density} we illustrate the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distributon ($P_X = \mathcal N(\theta, \sigma^2)$) and the prior on $\theta$ is uniform over $\Theta = [-b,b]$.
+On Figure~\ref{fig:opt_density} we illustrate the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distributon ($P_X = \Ncal(\theta, \sigma^2)$) and the prior on $\theta$ is uniform over $\Theta = [-b,b]$.
 Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
@@
 \end{tikzpicture}
-\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \mathcal N(\theta, \sigma^2)$under an optimal threshold distribution $\lambda^\star$ for $\pi$ the uniform distribution over $\Theta = [-0.5,0.5]$.
+\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \Ncal(\theta, \sigma^2)$under an optimal threshold distribution $\lambda^\star$ for $\pi$ the uniform distribution over $\Theta = [-0.5,0.5]$.
 %
@@
 
-As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \mathcal N(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution.
+As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \Ncal(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution.
 In this case, the ML estimator reduces to the estimator $\hat{\theta}_n$ of \eqref{eq:estimator_naive}.
@@
 \begin{example} \label{ex:bound}
-In the normal case $P_X = \mathcal N(\theta, \sigma^2)$, the bound in \eqref{eq:bound_Taylor} implies 
+In the normal case $P_X = \Ncal(\theta, \sigma^2)$, the bound in \eqref{eq:bound_Taylor} implies 
 \[
@@
 
-\appendices
-
-\section{Proofs \label{app:proofs}}
-
-\subsection{Proof of Proposition~\ref{prop:ceo_lower_bound}}
-
-First, we note that when $f(x) = \mathcal N(0,\sigma^2)$ and $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$, our distributed setting reduces to the Gaussian CEO problem with $R_1=\ldots = R_n =1$ and $k=1$.
+\appendix
+
+\section{}
+
+\subsection{Proof of Proposition~\ref{prop:ceo_lower_bound}
+\label{app:proof:prop_ceo_lower_bound}}
+
+First, we note that when $f(x) = \Ncal(0,\sigma^2)$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$, our distributed setting reduces to the Gaussian CEO problem with $R_1=\ldots = R_n =1$ and $k=1$.
 Therefore, any MSE attained in our distributed setting is also attained by the CEO and thus the optimal CEO strategy (with arbitrary $k$) provides a lower bound to the MSE in our setting.
@@
 
-Consider the minimal distortion $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
+Consider the minimal MSE $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
 from \cite[Eq. 10]{chen2004upper}:
@@
 $D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, this $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
+Therefore, this $D^\star$ provides a lower bound to the CEO MSE with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
 By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
@@
 \]
-We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO distortion while enforcing the condition $R_1=\ldots = R_n = 1$.
-Indeed, an upper bound for the CEO distortion under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
+We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO MSE while enforcing the condition $R_1=\ldots = R_n = 1$.
+Indeed, an upper bound for the CEO MSE under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
 \[
@@
 
-\begin{lem} \label{lem:bound_intervals}
-Let $f(x)$ be a log-concave, symmetric, and differentiable density such that $\eta(x)$ is strongly unimodal. For any $x_1 > \ldots > x_n \in \mathbb R$, 
-\begin{equation}
-\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-\leq \max_i \eta(x_i). \label{eq:lem_bound_intervals}
-\end{equation}
-In particular, if $|x_i|>\epsilon > 0$ for all $i=1,\ldots,n$, then 
-\[
-\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-\leq \eta(\epsilon) < 0. 
-\]
-\end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals}} 
+\subsection{Proof of Lemma~\ref{lem:bound_intervals_delta} \label{proof:lem:bound_intervals_delta}}
+
+%\begin{lem} \label{lem:bound_intervals}
+%Let $f(x)$ be a log-concave, symmetric, and differentiable density such that $\eta(x)$ is strongly unimodal. For any $x_1 > \ldots > x_n \in \mathbb R$, 
+%\begin{equation}
+%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
+%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
+%\leq \max_i \eta(x_i). \label{eq:lem_bound_intervals}
+%\end{equation}
+%In particular, if $|x_i|>\epsilon > 0$ for all $i=1,\ldots,n$, then 
+%\[
+%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
+%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
+%\leq \eta(\epsilon) < 0. 
+%\]
+%\end{lem}
+
 Denote 
@@
 \]
-We use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:lem_bound_intervals} is bounded from above by $\max_i \eta(x_i)$. The case $n=1$ is trivial. Assume that 
+We use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:lem_bound_intervals_delta} is bounded from above by $\max_i \eta(x_i)$. The case $n=1$ is trivial. Assume that 
 \begin{equation}
@@
 
-\subsection*{Proof of Theorem~\ref{thm:adpative_lower_bound}}
+\subsection{Proof of Theorem~\ref{thm:adpative_lower_bound}
+\label{proof:thm:adpative_lower_bound}
+}
 
@@
 \end{align}
-It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $4f^2(0)$.  \QEDA \\
+It follows from Lemma~\ref{lem:bound_intervals_delta} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $4f^2(0)$.  \QEDA \\
 
@@
 
-\subsection*{Proof of Theorem~\ref{thm:sgd}}
+\subsection{Proof of Theorem~\ref{thm:sgd}
+\label{proof:thm:sgd}
+}
 The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.
-Specifically, (i) in Theorem~\ref{thm:sgd} follows from the following simplified version of \cite[Thm.
-4]{polyak1992acceleration}:
+
+\subsubsection*{Proof of (i)}
+%Specifically, (i) in Theorem~\ref{thm:sgd} 
+Consider the following simplified version of \cite[Thm. 4]{polyak1992acceleration}:
 \begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
@@
 where the $Z_i$s are i.i.d. with zero means and finite variances. Define
-\begin{align*}
+\begin{align}
+\begin{split}
 \theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
-\hat{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
-\end{align*}
+\bar{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
+\end{split}
+\label{eq:Polyak_Juditsky_alg}
+\end{align}
 where in addition, assume the following: 
@@
 \item[(ii)] The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions \eqref{eq:conditions1}.
-\item[(iii)] The function $\psi(x) \triangleq \mathbb E \varphi(x+Z_1)$ is differentiable at zero with $\psi'(0)>0$, and satisfies $\psi(0)=0$ and $x\psi(x) >0$ for all $x\neq 0$.
+\item[(iii)] The function $\psi(x) \triangleq \ex{ \varphi(x+Z_1)}$ is differentiable at zero with $\psi'(0)>0$, and satisfies $\psi(0)=0$ and $x\psi(x) >0$ for all $x\neq 0$.
 Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
@@
 \item[(iv)] The function 
-$\chi(x) \triangleq \mathbb E \varphi^2(x+Z_1)$ is continuous at zero. 
+$\chi(x) \triangleq \ex{\varphi^2(x+Z_1)}$ is continuous at zero. 
 \end{enumerate}
-Then $\hat{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}(\hat{\theta}_n - \theta)$ converges in distribution to $\mathcal N(0,V)$, where
+Then $\bar{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}(\hat{\theta}_n - \theta)$ converges in distribution to $\Ncal(0,V)$, where
 \[
@@
 \begin{align*}
-\psi(x) & = \mathbb E \sgn(x+ Z_1) = \int_{-\infty}^\infty \sgn(x+z) f(z) dz \\
+\psi(x) & = \ex{ \sgn(x+ Z_1) }= \int_{-\infty}^\infty \sgn(x+z) f(z) dz \\
 & = \int_{-x}^\infty f(z) dz -\int_{-\infty}^{-x} f(z) dz. 
@@
 \[
-\frac{\chi(0)}{\psi'^2(0)} = \frac{1}{4 f^2(0)},
-\]
-Theorem~\ref{thm:sgd}-(i) follows from Theorem~\ref{thm:polyak_juditsky}.  \\
-
-In order to prove part (ii) of Theorem~\ref{thm:sgd} we use the following result from \cite{polyak1990new}:
-\begin{thm}{ \cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
+\frac{\chi(0)}{\psi'^2(0)} = \frac{1}{4 f^2(0)} = \frac{1}{\eta(0)},
+\]
+it follows from Theorem~\ref{thm:polyak_juditsky} that
+\[
+\sqrt{n}\left(\hat{\theta}_n-\theta \right) \overset{d}{\to} \Ncal \left(0, 1/ \eta(0)\right). 
+\]
+
+\subsubsection*{Proof of (ii)}
+The proof requires the following refinement of Theorem~\ref{thm:polyak_juditsky}.
+\begin{thm} \label{thm:normal_expansion}
+Let $\Delta_i = \theta_i - \theta$ and $\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \bar{\Delta}_i$. 
+Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{thm:polyak_juditsky}, there exists $K_1$ and $\lambda>0$ such that
+\begin{equation}
+\ex{\left| \varphi(Z_1) - \varphi(x+Z_1)  \right|} \leq K_1 |x|^{1+\lambda}
+\label{eq:PJ_additional_cond}. 
+\end{equation}
+Then:
+\begin{itemize}
+\item[(i)] \begin{equation}
+\sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1). \label{eq:normal_expansion_lem}
+\end{equation}
+where $o_{p,n}(1)$ converges in probability to $0$ as $n\to \infty$.
+\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite location Fisher information 
+\[
+I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)} \right)^2 f(x) dx,
+\]
+then
+\[
+\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{1}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
+\]
+under the local alternative $Z_1,\ldots,Z_n \sim P^n_{h/\sqrt{n}}$ with density $f^n(x-h/\sqrt{n})$.
+\end{itemize}
+\end{thm}
+The proof of Theorem~\ref{thm:normal_expansion} is given in Subsection~\ref{proof:thm:normal_expansion} below. \\
+
+In our setting, the condition \eqref{eq:PJ_additional_cond} holds since
+\begin{align*}
+& %\varphi(Z_1) - \varphi(x+Z_1) = 
+\sgn(Z_1) - \sgn(x + Z_1) \\
+& = \begin{cases}
+2 & Z_1 > 0,\, x+Z_1<0, \\
+-2 & Z_1 <0, \, x+Z_1>0, \\
+0 & \text{otherwise}. 
+\end{cases}
+\end{align*}
+Consequently, 
+\begin{align*}
+\ex{ \left| \varphi(Z_1) - \varphi(x+Z_1) \right| }  \leq \Prob\left( |Z_1| < x  \right) \leq f(0) |x|, 
+\end{align*}
+In addition, by anti symmetry of $f'(x)$ around $x=0$, 
+\[
+\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = 2f(0). 
+\]
+Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}.
+
+\subsubsection*{Proof of (iii)}
+%In order to prove part (ii) of Theorem~\ref{thm:sgd} 
+Consider the following result from \cite{polyak1990new}:
+\begin{thm}{\cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
 Let
@@
 In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \mathbb R$.
-Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution for which the Fisher information exits.
-Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{thm:polyak_juditsky}-(iii) and satisfies the conditions there.
+Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution with a density for which the Fisher information exits.
+Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{thm:polyak_juditsky}-(iii) and satisfy the conditions there.
 Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$,
@@
 
-We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = -\sgn(-x)$, $Z_n = \theta-X_n$ and $U_n = \theta_n$. From \eqref{eq:polyak_new_measurements} we have
-\begin{align*} 
-\theta_n & = \theta_{n-1} + \gamma_n \sgn(\theta-\theta_{n-1} - Z_n )  \\
-& = \theta_{n-1} + \gamma_n \sgn(X_n-\theta_{n-1} ),
-\end{align*}
-so the estimator $\hat{\theta}_n$ defined by $\hat{\theta}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
+We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$. From \eqref{eq:polyak_new_measurements} we have
+\begin{align*} 
+U_n & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
+& = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
+\end{align*}
+so the estimator $\bar{U}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
 \[
@@
 Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$.
-Theorem~\ref{thm:polyak_new} implies
-\[
-n V_n = \mathbb E \left[ \left(\hat{\theta}_n-\theta \right)^2 \right]  = \frac{1}{4 f^2(0)} + o(1).
-\]
+Theorem~\ref{thm:polyak_new} implies that for any $\theta \in \mathbb R$,
+\[
+n V_n = n \mathbb E \left[ \left(\hat{\theta}_n-\theta \right)^2 \right]  = \frac{1}{4 f^2(0)} + o(1).
+\]
+{\color{red}
+
+\subsection{Proof of Theorem~\ref{thm:normal_expansion}
+\label{proof:thm:normal_expansion}
+}
+\subsubsection*{Proof of (i)}
+The proof of part (i) of Theorem~\ref{thm:normal_expansion} requires the following two additional results from \cite{polyak1992acceleration}:
+\begin{lem}{\cite[Lem. 2]{polyak1992acceleration}}
+\label{lem:Polyak_expansion}
+Consider the process $\{\Delta_i^1 \}_{i=0}^\infty$ defined by
+\[
+\Delta^1_i = \Delta^1_{i-1} - \gamma_i (A \Delta_{i-1}+ \xi_i),\qquad \Delta_{0}^1 = c.
+\]
+Assume that $A>0$ and condition (ii) of Theorem~\ref{thm:polyak_juditsky} hold. Then 
+\begin{equation}
+\label{eq:Polyak_expansion}
+\sqrt{n} \bar{\Delta}_n^1 = \frac{1}{\sqrt{n}}\sum_{i=0}^{n-1} \Delta_i^1 = \frac{\alpha_n \Delta_0^1}{\sqrt{n} \gamma_0}  + \frac{1}{\sqrt{n} A} \sum_{i=1}^{n-1} \xi_i + \frac{1}{\sqrt{n}}\sum_{i=1}^{n-1} w_i^n \xi_i,
+\end{equation}
+where $\alpha_n$, and $w_i^n$ are real numbers such that $|\alpha_n| \leq K$ and $|w_i^n|\leq K$ for some $K< \infty$, and 
+\[
+\lim_{n\to \infty} \frac{1}{n} \sum_{i=1}^{n-1} |w_i^n| = 0. 
+\]
+\end{lem}
+
+\begin{lem} \label{lem:PJ_converging_sum}
+Under the conditions of Theorem~\ref{thm:polyak_juditsky},
+\[
+\sum_{i=1}^\infty \frac{|\Delta_{i}|^{1+\lambda}}{\sqrt{i}} < \infty 
+\]
+almost surely. 
+\end{lem}
+Lemma~\ref{lem:PJ_converging_sum} follows from the proof of Theorem 2 in \cite{polyak1992acceleration}.
+
+We separate the proof of part (i) into two steps.
+\subsubsection*{Step I}
+The expansion \eqref{eq:normal_expansion_lem} holds for the process  ${\bar{\Delta}^1_i}$ defined as follows:
+\begin{align} \label{eq:Polyak_expansion_lem1_alg}
+& \Delta_i^1  = \Delta_{i-1}^1 - \gamma_i \psi'(0) \Delta_{i-1}^1 - \gamma_i \varphi(Z_i), \qquad
+ \delta_0^1 = \Delta_0\\
+& \bar{\Delta}^1_i = \frac{1}{n}\sum_{i=0}^{n-1} \Delta^1_i.
+\end{align}
+
+In order to show this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$.
+The first expression on the RHS on \eqref{eq:Polyak_expansion} goes to zero in variance.
+In addition,
+\begin{align*}
+& \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }  = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
+& = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0. 
+\end{align*}
+We obtain
+\begin{equation}
+\sqrt{n} \bar{\Delta}^1_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1), \label{eq:Polyak_expansion_aux_process}
+\end{equation}
+
+\subsubsection*{Step II} $\bar{\Delta}_n$ and $\bar{\Delta}^1_n$ are asymptotically equivalent. \\
+
+From \eqref{eq:Polyak_Juditsky_alg} and \eqref{eq:Polyak_expansion_lem1_alg}, the difference $\delta_i = \Delta_i - \Delta_i^1$ satisfies the recursion
+\[
+\delta_i = \delta_{i-1} - \gamma_i \psi'(0) \delta_{i-1} + \gamma_i \left( \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i) \right),
+\]
+where $\delta_0 = 0$. Use Lemma~\ref{lem:Polyak_expansion} with $\xi_i =  \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i)$ to obtain
+\begin{align}
+& \sqrt{n}\bar{\delta}_n = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \xi_i  \\
+& = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \label{eq:PJ_proof1} \\
+& + 
+\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi(\Delta_{i-1})  + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i)
+\right) \label{eq:PJ_proof2}
+\end{align}
+For the term \eqref{eq:PJ_proof1} and using \eqref{eq:Polyak_Juditsky_cond3}, there exists $K_1$ and $K_2$ such that 
+\begin{align*}
+& \eqref{eq:PJ_proof1}
+\leq K_1 \sum_{i=1}^\infty \frac{1}{\sqrt{i}} \left| \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \right| \\
+& \leq K_2 \sum_{i=1}^\infty \frac{ |\Delta_i|^{1+\lambda}}{\sqrt{i}}. 
+\end{align*}
+
+Lemma~\ref{lem:PJ_converging_sum} shows that 
+\begin{align}
+\sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}}  < \infty \label{eq:PJ_converging_sum},
+\end{align}
+hence the Kronecker lemma implies
+\[
+\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \to 0.
+\]
+For the term \eqref{eq:PJ_proof2}, set 
+\[
+\epsilon_i \triangleq \psi(\Delta_{i-1}) + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i).
+\]
+For $a>0$ and $n \in \mathbb N$, define the event
+\[
+A_{n,a} \triangleq \left\{ \sum_{i=1}^{n-1} \frac{|\epsilon_i|}{\sqrt{i}}  \geq a  \right\}. 
+\]
+By Markov's inequality, we have
+\begin{align}
+\ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } \leq \frac{1}{a} \sum_{i=1}^{n-1} \frac{ \ex{|\epsilon_i| \Delta_{i-1} \mid }}{\sqrt{i}}. \label{eq:PJ_proof_3}
+\end{align}
+Using \eqref{eq:Polyak_Juditsky_cond3} and \eqref{eq:PJ_additional_cond}, there exists $K'$ and $\lambda'>0$ such that
+\begin{align*}
+& \ex{ |\epsilon_i| | \Delta_{i-1}}  \leq |\psi(\Delta_{i-1})| + \left| \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i) \right|  \\
+& \leq K' |\Delta_{i-1}|^{1+\lambda}. 
+\end{align*}
+Plugging this bound in \eqref{eq:PJ_proof_3} and using Lemma~\ref{lem:PJ_converging_sum},we obtain 
+\[
+\Prob(A_{n,a}) = \ex{ \ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } } \leq  \frac{K''}{a}
+\]
+for some constant $K''$. It follows that for any $\epsilon$, we may choose $a$ large enough such that 
+\[
+\sup_{n} \Prob(A_{n,a}) < \epsilon.
+\]
+This implies that for any $\epsilon>0$,
+\[
+\Prob \left( \sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty \right) \geq 1-\epsilon,
+\]
+and hence 
+\[
+\sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty
+\]
+almost surely. The Kronecker lemma now implies 
+\[
+\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left|\epsilon_i\right| \to 0,
+\]
+hence the term \eqref{eq:PJ_proof2} satisfies
+\[
+\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right) \epsilon_i \leq \frac{K'''}{\sqrt{n}} \sum_{i=1}^{n-1} |\epsilon_i| \to 0. 
+\]
+This conclude the proof of part (i).
+
+\subsubsection*{Part (ii)}
+Use \eqref{eq:normal_expansion_lem} to write
+\[
+\sqrt{n} \bar{\Delta}_n = G_n + o_{p,n}(1),
+\]
+where
+\[
+G_n \triangleq -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n} \varphi(Z_i). 
+\]
+From \cite[Exm.
+7.8]{van2000asymptotic}, the location model $f(x-\theta)$ with continuously differentiable $f(x)$ is differentiable in quadratic mean with the score function $-f'(x-\theta)/f(x-\theta)$.
+This fact implies the following expansion \cite[Thm.
+7.2]{van2000asymptotic}:
+\begin{align}
+\label{eq:PJ_LAN}
+& \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} (Z_1,\ldots,Z_n) =  \log \prod_{i=1}^{n} \frac{f(Z_i-h/\sqrt{n})}  {f(X_i-\theta)} = h J_n - \frac{1}{2}h^2 I_{\theta} + o_{p,n}(1),
+\end{align}
+where 
+\[
+J_n \triangleq -\frac{1}{\sqrt{n}} \sum_{i=1}^n \frac{f'(Z_i)}{f(Z_i)} .
+\]
+We have
+\begin{align*}
+& \ex{ G_n J_n} = \frac{1}{\psi'(0)}\frac{1}{n} \sum_{i=1}^n \ex{ \varphi(Z_i) \frac{f'(Z_i)}{f(Z_i)} }  \\
+& = \frac{1}{ \psi'(0)} \ex{ \varphi(Z_1) \frac{f'(Z_1)}{f(Z_1)}} =  \frac{1}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx , 
+\end{align*}
+Since both $\sqrt{n}G_n$ and $\sqrt{n}J_n$ are the sum of $n$ i.i.d. random variables with zero mean and finite variance, we obtain, from the central limit theorem and Slutsky's theorem, that
+\[
+\left(\sqrt{n} \bar{\Delta}_n, \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} \right) \overset{d}{\to} \Ncal \left( \left(0,-\frac{h^2}{2} I_\theta \right),  \begin{pmatrix}
+\frac{\chi(0)}{\psi'^2(0)} & \frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx \\
+\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx & h^2 I_\theta 
+\end{pmatrix}  \right)
+\]
+Le Cam's third lemma \cite[Exm. 6.7]{van2000asymptotic} implies that under $P_{\theta+h/\sqrt{n}}$, 
+\[
+\sqrt{n}\bar{\Delta}_n \overset{d}{\to} \Ncal\left(\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx,  \frac{\chi(0)}{\psi'^2(0)} \right).
+\]
+
 \QEDA
-
-\subsection*{Proof of Theorem~\ref{thm:LAN1}}
+}
+
+\subsection{Proof of Theorem~\ref{thm:LAN1}
+\label{proof:thm:LAN1}
+}
 The log probability mass distribution of $B^n=(B_1,\ldots,B_n)$ is given by
@@
 \[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0, \kappa(\theta) \right). 
+\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0, \kappa(\theta) \right). 
 \]
@@
 \]
-We now use the fact that each $A_i$ is a finite union of interval and consider the following lemma, proof of which is given in the appendix:
+We now use the fact that each $A_i$ is a finite union of interval and consider the following lemma, proof of which is given in Appendix~\ref{proof:lem:bound_intervals_delta}.
 \begin{lem} \label{lem:bound_intervals_delta}
@@
 \[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0,\kappa(\theta) \right). 
+\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0,\kappa(\theta) \right). 
 \]
@@
 \end{equation}
-From the same reason as in the proof of Lemma~\ref{lem:bound_intervals}, \eqref{eq:gradient_zero_delta} is satisfied if and only if $x_1 = \ldots = x_N$.
+From the same reason as in the proof of Lemma~\ref{lem:bound_intervals_delta}, \eqref{eq:gradient_zero_delta} is satisfied if and only if $x_1 = \ldots = x_N$.
 For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_delta_proof} equals $\eta_\delta(x_1)$ which was shown to be smaller than $\eta_\delta(\epsilon)$.
@@
 
-\subsection*{Proof of Theorem~\ref{thm:non_existence}}
+\subsection{Proof of Theorem~\ref{thm:non_existence}
+\label{proof:thm:non_existence}
+}
 
@@
 \end{align}
-where $(a)$ follows from Lemma~\ref{lem:bound_intervals} and the fact that for $i \in S_n(\theta, \epsilon)$, 
+where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} and the fact that for $i \in S_n(\theta, \epsilon)$, 
 \[

### 2019-07-04 onebit_full.tex
added part proof of regularity for SGD estimator

--- 2019-06-19 onebit_full_V2.tex
@@
 \usepackage{amssymb}
+
 %\usepackage{newtxtext, newtxmath}
@@
 
-\newcommand{\mmse}{\mathsf{mmse}}
 \newcommand{\ex}[1]{\ensuremath{\mathbb{E}\left[ #1\right]}}
@@
 
-\node[right of = est, node distance = 1.2cm] (dest) {\small $\hat{\theta}_n$};
+\node[right of = est, node distance = 1.2cm] (dest) {\small ${\theta}_n$};
 %         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
@@
 %\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=2pt] (est) -- (dest);
+\draw[->, line width=1pt] (est) -- (dest);
 \node at (2,-4.5) {(i) Centralized};
@@
 
-\node[right of = est, node distance = 1.2cm] (dest) {$\hat{\theta}_n$};
+\node[right of = est, node distance = 1.2cm] (dest) {${\theta}_n$};
 %         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
@@
 %\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=2pt] (est) -- (dest);
+\draw[->, line width=1pt] (est) -- (dest);
 \node at (2,-4.5) {(ii) Adaptive};
@@
 %\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=2pt] (est) -- (dest);
+\draw[->, line width=1pt] (est) -- (dest);
 \node at (2,-4.5) {(iii) Distributed};
@@
 Three encoding settings: (i) Centralized  -- an encoder sends $n$ bits after observing $n$ samples.
-(ii) Adaptive (sequential) --  each encoder sends a bit $B_n$ depending on its private sample $X_n$ and previous bits $B_1,\ldots,B_{n-1}$.
-(iii) Distributed  -- each encoder sends a single bit $B_i$ only based on its private sample $X_i$.}
+(ii) Adaptive (sequential) --  the $i$th encoder sends the bit $B_i$ depending on its private sample $X_i$ and previous bits $B_1,\ldots,B_{i-1}$.
+(iii) Distributed  -- each encoder send the bit $B_i$ based on its private sample $X_i$ only.}
 \end{figure*}
@@
 \item {\bf Analog-to-digital conversion:} A sigma-delta modulator (SDM) converts an analog signal into a sequence of bits by sampling the signal at a very high rate and then using one-bit threshold detector combined with a feedback loop to update an accumulated error state \cite{1092194}.
-Therefore, the MSE in tracking an analog signal using an SDM falls under our setting (ii) when we assume that the signal at the input to the modulator is a constant (direct current) corrupted by, say, thermal noise \cite{53738}.
+Therefore, the expected error in tracking an analog signal using an SDM falls under our setting (ii) when we assume that the signal at the input to the modulator is a constant (direct current) corrupted by, say, thermal noise \cite{53738}.
 Since the sampling rates in SDM are usually many times more than the bandwidth of its input, analyzing SDM under a constant input provides meaningful lower bound even for non-constant signals.
@@
 %
-We measure the performance in estimating $\theta$ by the mean squared error (MSE) risk.
-For an asymptotically normal estimator with a finite MSE risk $R_n$, we are interested in particular in the limit
-\[
-\lim_{n\to \infty} \frac{\sigma^2}{n R_n},
-\]
-describing the 
- \emph{asymptotic relative efficiency} (ARE) of the estimator compared to asymptotically normal estimators whose variances decreases as $\sigma^2/n+o(n^{-1})$.
+We measure the performance in estimating $\theta$ by the quadratic risk. For an estimator with finite quadratic risk $R_n$, we are interested in particular in the limit
+\begin{equation}
+\label{eq:ARE_def}
+\lim_{n\to \infty} \frac{\sigma^2/n}{R_n},
+\end{equation}
+describing the \emph{asymptotic relative efficiency} (ARE) of this estimator compared to an estimator whose variance decreases as $\sigma^2/n+o(n^{-1})$.
 Estimators of this form include the empirical mean of the samples, and, under some conditions, the optimal Bayes estimator.
@@
 %
-In addition to the examples above, the excess risk in estimating a fixed parameter due to a one-bit per measurement constraint is useful in bounding from below the excess risk in estimating a signal from its noisy measurements.
-Namely, the excess MSE or ARE we derive serves as the most optimistic estimate for the risk in estimating under the one-bit per measurement constraint a signal changing over time or space.
+In addition to the examples above, the excess risk in estimating a fixed parameter due to a one-bit per sample constraint is useful in bounding from below the excess risk in estimating signals from thier noisy one-bit quanitzed noisy measurements.
+Specifically, the excess risk or ARE we derive serve as the most optimistic estimate for the risk in estimating under one-bit per measurement constraint signals changing over time or space.
 Such estimation settings are considered in \cite{baraniuk2017exponential, jacques2013robust, plan2013one, li2017channel, choi2016near}.
-\\
+\par
 
@@
 In setting (i), the estimator can evaluate the optimal mean estimator (e.g., the sample mean in the Gaussian case) and then quantize it using $n$ bits.
-Since the accuracy in describing the empirical mean decreases exponentially in $n$, the error due to quantization is negligible compared to the MSE in estimating the mean.
+Since the accuracy in describing the empirical mean decreases exponentially in $n$, the error due to quantization is negligible compared to the quadratic risk in estimating the mean \cite{720540}.
 Therefore, the ARE in this setting is $1$.
@@
 
-It is important to note that although the ARE in setting (i) is one, this scheme already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation procedures.
-Indeed, the task of representing an unknown random quantity using $n$ bits is equivalent to designing a $2^n$ levels scalar quantizer \cite{gray1998quantization}.
+It is important to note that although the ARE in setting (i) is one, this scheme already poses a non-trivial challenge for the design and analysis of optimal encoding and estimation procedures.
+Indeed, representing an unknown random quantity using $n$ bits is equivalent to designing a $2^n$ levels scalar quantizer \cite{gray1998quantization}.
 However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation problem and hence its exact value is unknown.
-As a result, a non-trivial exploration-exploitation trade-off arises even in this case.
+As a result, a non-trivial exploration-exploitation trade-off arises even in setting (i).
 %Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$. 
-Therefore, while uncertainty due to quantization decreases exponentially in the number of bits $n$, hence the ARE is $1$, an exact expression for the MSE in this setting is still difficult to derive. 
+Therefore, while uncertainty due to quantization decreases exponentially in the number of bits $n$, hence the ARE is $1$, it is still difficult to derive an exact expression for the MSE in this setting.
 %
@@
 In particular, the subsequent work of \cite{Barnes2018} uses an approach similar to ours to derive lower bound on the error in various parametric estimation problems from quantized measurements.
-\\
+\par
 
@@
 
-The performance of an estimator $\hat{\theta}_n \triangleq \hat{\theta}_n(B^n)$ in any of these cases is measured according to the mean squared error (MSE) risk:
+The performance of an estimator ${\theta}_n \triangleq {\theta}_n(B^n)$ in any of these cases is measured according to the quadratic risk:
 \begin{equation}
 \label{eq:error_def}
-R_n \triangleq \mathbb E\left(\hat{\theta}_n - \theta \right)^2,
+R_n \triangleq \mathbb E\left({\theta}_n - \theta \right)^2,
 \end{equation}
@@
 %\begin{equation}
-%R_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left(\hat{\theta}_n - \theta \right)^2 | \theta \right],
+%R_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left({\theta}_n - \theta \right)^2 | \theta \right],
 %\end{equation}
@@
 The main problems we consider in this paper are the minimal value of \eqref{eq:error_def}, as a function of $n$ and $f(x)$, under different choices of the encoding functions in cases (i), (ii), and (iii).
-\\
+\par
 
@@
 \[
-\sqrt{a_n}\left(\hat{\theta}_n - \theta\right) \overset{d}{\longrightarrow} \Ncal(0, \sigma^2).
-\]
-Then the ARE of $\hat{\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
-\[
-\ARE(\hat{\theta}_n) \triangleq
+\sqrt{a_n}\left({\theta}_n - \theta\right) \overset{d}{\longrightarrow} \Ncal(0, \sigma^2).
+\]
+Then the ARE of ${\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
+\[
+\ARE({\theta}_n) \triangleq
 \lim_{n\rightarrow \infty} \frac{a_n}{n}. 
@@
 \[
-a_n \mathbb E \left(\hat{\theta}_n - \theta \right)^2 = V + o(1),
-\]
-with $o(1)\to 0$ as $n\to \infty$, then the ARE of $\hat{\theta}_n$ is finite and equals $\sigma^2/V$. \\
+a_n \mathbb E \left({\theta}_n - \theta \right)^2 = V + o(1),
+\]
+with $o(1)\to 0$ as $n\to \infty$, then the ARE of ${\theta}_n$ is finite and equals $\sigma^2/V$. \par
 
@@
 Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions).
-Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.
-\\
+Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.\par
 
@@
 \section{Consistent Estimation and Off-the-shelf Bounds \label{sec:preliminary}}
-%On a first impression, it may not be clear whether consistent estimation of the mean is even possible in the adaptive and centralized settings.
-On the other hand, it may seem as if estimation in these cases is trivial as in the centralized setting (i).
-%
-We next settle such skepticism by deriving lower and upper bounds to the relative efficiency under setting (iii).
-
-In this section, we derive lower and upper bounds on the relative efficiency under setting (iii) using known results. These bounds establish the following facts:
+%
+In this section we adapt known results to derive lower and upper bounds on the relative efficiency under setting (iii). These bounds establish the following facts:
 \begin{itemize}
@@
 \label{eq:estimator_naive}
-\hat{\theta}_n = \theta_0 + F^{-1}\left( P_n \right)
+{\theta}_n = \theta_0 + F^{-1}\left( P_n \right)
 \end{equation}
 is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set due to log-concavity.
-Furthermore, the variance of $P_n$ is $F(\theta-\theta_0)F(\theta_0-\theta)$, and hence the delta method implies that $\hat{\theta}_n$ is asymptotically normal with variance
-\begin{equation} 
- \frac{F(\theta-\theta_0)F(\theta_0-\theta)}{f^2(\theta-\theta_0)} = \frac{1}{
+Furthermore, the variance of $P_n$ is $F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)$, and hence the delta method implies that ${\theta}_n$ is asymptotically normal with variance
+\begin{equation} 
+ \frac{F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}{f^2(\theta-\theta_0)} = \frac{1}{
 \eta(\theta-\theta_0)}.
 \end{equation}
-In particular, the ARE of $\hat{\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
-In other words, for a prescribed accuracy, $\hat{\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
+In particular, the ARE of ${\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
+In other words, for a prescribed accuracy, ${\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
 \par
@@
 %
-Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of $\hat{\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
+Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of ${\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
 This ARE is attained only when $\theta_0 = \theta$, whereas $\theta$ is apriori unknown.
-Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of $\hat{\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
-As an example, when $f(x)$ is a normal density, the ARE of $\hat{\theta}_n$ is less than $\approx 0.14$ when $\theta_0$ is $2$ standard deviations from $\theta$.
-Therefore, the estimator $\hat{\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
+Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of ${\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
+As an example, when $f(x)$ is a normal density, the ARE of ${\theta}_n$ is less than $\approx 0.14$ when $\theta_0$ is $2$ standard deviations from $\theta$.
+Therefore, the estimator ${\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
 \par
@@
 Schemes with such adaptation fall within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
-\\
+\par
 
@@
 \]
-and transmits $R_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates $\hat{\theta}_1,\ldots,\hat{\theta}_k$ with the goal of minimizing the average MSE:
-\[
-MSE_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - \hat{\theta}_j \right)^2 \right]. 
-\]
-Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $R_1=\ldots=R_n = 1$.
+and transmits $r_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates ${\theta}_1,\ldots,{\theta}_k$ with the goal of minimizing the quadratic risk:
+\[
+R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - {\theta}_j \right)^2 \right]. 
+\]
+Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $r_1=\ldots=r_n = 1$.
 It follows that, assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
@@
  \par
-When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k\to \infty$ were fully characterized in \cite{prabhakaran2004rate}.
-Furthermore, the work of \cite{chen2004upper} provided an expression for MSE attained in the CEO setting under Gaussian priors.
+When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k$ goes to infinity were fully characterized in \cite{prabhakaran2004rate}.
+Furthermore, the work of \cite{chen2004upper} provided an expression for quadratic risk attained in the CEO setting under Gaussian priors.
 Adapting to our setting, this expression provides the following proposition:
 \begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$. Then any estimator $\hat{\theta}_n$ of $\theta$ in the distributed setting satisfies
+Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is arbitrary.
+Then any estimator ${\theta}_n$ of $\theta$ in the distributed setting satisfies
 \begin{equation} \label{eq:ceo_bound}
@@
 \begin{thm}[maximal relative effeciency] \label{thm:adpative_lower_bound}
-Let $\hat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Figure~\ref{fig:setup}-(ii). Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-n\mathbb E\left[ (\theta-\hat{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0},
+Let ${\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Figure~\ref{fig:setup}-(ii). Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
+\[
+n\mathbb E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0},
 \]
@@
 Once this bound is achieved, the result follows by using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are in Appendix~\ref{proof:thm:adpative_lower_bound}.\\
-
-Theorem~\ref{thm:adpative_lower_bound} implies that any estimator $\hat{\theta}_n$ from any adaptive encoding scheme satisfies
+The details are in Appendix~\ref{proof:thm:adpative_lower_bound}.\par
+
+Theorem~\ref{thm:adpative_lower_bound} implies that any estimator ${\theta}_n$ from any adaptive encoding scheme satisfies
 \[
@@
 \[
-\ARE(\hat{\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
+\ARE({\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
 \]
@@
 \subsection{Asymptotically optimal estimator}
-Let $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ be a strictly positive sequence. Consider the following estimator $\hat{\theta}_n$ for $\theta$:  
+Let $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ be a strictly positive sequence. Consider the following estimator ${\theta}_n$ for $\theta$:  
 \begin{equation}
@@
 \]
+%
+%
 \item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with finite Fisher information for location
@@
 %(or that $f(x-\theta)$ is differentiable in quadratic mean).  
-For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $P^n_{\theta,h,n}$ be the measure with density $f(x-\theta - h/\sqrt{n})$. Then 
+Then the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $P^n_{\theta,h,n}$ be the measure with density $f(x-\theta - h/\sqrt{n})$.
+Then
 \begin{align}
@@
 \end{align}
-under $P^n_{\theta,h,n}$. 
+under $P^n_{\theta,h,n}$. Consequently, for any bounded, symmetric, and quasi-convex function $L$, 
+\begin{align*}
+& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right]
+\\
+& \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right],
+\end{align*}
+where $Z \sim \Ncal(0,1)$. 
+%
+%
 \item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ satisfies
@@
 \[
-\lim_{n\to \infty} n \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{\eta(0)}. 
+ \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{n\eta(0)} + o(n^{-1}). 
 \]
@@
 \subsubsection*{Proof}
-See Appendix~\ref{proof:thm:sgd}. \\
-
-Theorem~\ref{thm:sgd} implies that the estimator $\hat{\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the maximal ARE as established by Theorem~\ref{thm:adpative_lower_bound}.
-Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$.
+See Appendix~\ref{proof:thm:sgd}. \par
+
+Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the maximal ARE as established by Theorem~\ref{thm:adpative_lower_bound}.
+%Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$.
 %
@@
 \node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
-\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {Enc$(\hat{\theta}_{n_1})$};  
+\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {Enc$({\theta}_{n_1})$};  
 \draw[->,line width = 2pt] (sourceB) -- (enc1B);
@@
 \node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
-\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {Enc$(\hat{\theta}_{n_1})$};  
+\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {Enc$({\theta}_{n_1})$};  
 \draw[->,line width = 2pt] (source3B) -- (enc3B); 
@@
 
-\draw[->,line width = 0.5pt] (est.east) node[above, xshift  =0.5cm] {$\hat{\theta}_{n_1}$} -| (enc1B.north);
-
-\draw[->,line width = 0.5pt] (enc1B) -- (enc3B);
-
-%\draw[->,line width = 1pt] (enc1B)  -- node[right] {$\hat{\theta}_{n_1}$} (enc3B);
-
-\draw[->,line width = 2pt] (estB) -- +(0.8,0) node[right] {$\hat{\theta}_n$};
+\draw[->,line width = 1pt] (est.east) node[above, xshift  =0.5cm] {${\theta}_{n_1}$} -| (enc1B.north);
+
+%\draw[->,line width = 1pt] (enc1B) -- (enc3B);
+
+\draw[->,line width = 1pt] (est.east) -| +(1,-0.5) -- +(1,-2) -| (enc3B.north);
+
+%\draw[->,line width = 1pt] (enc1B)  -- node[right] {${\theta}_{n_1}$} (enc3B);
+
+\draw[->,line width = 1pt] (estB) -- +(0.8,0) node[right] {${\theta}_n$};
 \end{tikzpicture}
@@
 
-\subsection{Optimality using Single Threshold Adaptation}
-In Section~\ref{sec:preliminary} we considered an estimator that is based on messages of the form 
+\subsection{Optimality using One Round of Threshold Adaptation}
+In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
 \[
@@
 \]
-and showed that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
-%
-We now show that a similar encoding leads to an asymptotically normal estimator with the minimal variance $1/\eta(0)$, provided we allow at least once to update the threshold value $\theta_0$. 
+and deduced that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
+%
+We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ at least once.
 %
 In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
-We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate $\hat{\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use $\hat{\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$.
+We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate ${\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use ${\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$.
 Figure~\ref{fig:one_round} illustrates a diagram of this procedure.
@@
  \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
- \mathbf 1_{X_i \geq \hat{\theta}_{n_1} }& i={n_1+1,\ldots,n},
+ \mathbf 1_{X_i \geq {\theta}_{n_1} }& i={n_1+1,\ldots,n},
 \end{cases}
@@
 \[
-\hat{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
+{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
 \frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
@@
 \[
-\hat{\theta}_{n_2}  = \hat{\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
+{\theta}_{n_2}  = {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
 \]
@@
 \begin{align*}
- \sqrt{n} \left( \hat{\theta}_{n_2} - \theta  \right)^2  \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
+ \sqrt{n} \left( {\theta}_{n_2} - \theta  \right)^2  \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
 \end{align*}
@@
 \]
-so that $\hat{\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity, and thus 
-\[
-\eta( \hat{\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
+so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity, and thus 
+\[
+\eta( {\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
 \]
@@
 \begin{align*}
-& \sqrt{n}\left(\hat{\theta}_{n_2} - \theta\right) \\
-& = \sqrt{n} \left( \hat{\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}(\hat{\theta}_{n_1})) - \theta \right)  \\
+& \sqrt{n}\left({\theta}_{n_2} - \theta\right) \\
+& = \sqrt{n} \left( {\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}({\theta}_{n_1})) - \theta \right)  \\
 & \overset{d}{\to} \Ncal\left( 0, 
@@
 xlabel= $n$,
-ylabel = {$n\mathbb E \left[\left(\theta - \hat{\theta}_n \right)^2 \right]$},
+ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
 %xtick={-3,-2,-1,0,1,2,3},
@@
 %\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
-%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left(\hat{\theta}_n - \theta \right)^2$};
+%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left({\theta}_n - \theta \right)^2$};
 %\node[scale = 0.7] at (0,-2.4) {$n$};
@@
 \begin{cor} \label{cor:LA_minimax}
-Let $\hat{\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
+Let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
 Then for any bounded, symmetric, and quasi-convex function $L$,
 \begin{align*}
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\hat{\theta}_{n} - \tau) \right) \right]
+& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right]
 \\
@@
 \begin{align*}
-\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( \hat{\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
+\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( {\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
 \end{align*}
@@
 This fact poses the upper bound of $\kappa(\theta)\sigma^2$ for the ARE of estimators in such models.
-\\
+\par
 
@@
 \begin{proof}
-See Appendix~\ref{proof:non_existence}
+See Appendix~\ref{proof:thm:non_existence}.
 \end{proof}
@@
 Due to local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by 
-$\hat{\theta}^{ML}_n$, is local asymptotic minimax in the sense that 
-\[
-\sqrt{n} \left( \hat{\theta}^{ML}_n - \theta \right) \overset{d}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
+${\theta}^{ML}_n$, is local asymptotic minimax in the sense that 
+\[
+\sqrt{n} \left( {\theta}^{ML}_n - \theta \right) \overset{d}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
 \]
 It follows that when the density of the threshold values converges to a probability measure, the ARE of the ML estimator is $\kappa(\theta)\sigma^2$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-We note that $\hat{\theta}^{ML}_n$ is given by the root of
+We note that ${\theta}^{ML}_n$ is given by the root of
 \begin{equation}
@@
 This root is unique since the log-likelihood function is concave.
-Furthermore, for any $n \in \mathbb R$, we have that $\hat{\theta}^{ML}_n  \in [t_{(1)}, t_{(n)}]$ where $t_{(i)}$ denotes the $i$th element of $\{t_1,t_2\ldots\}$.
+Furthermore, for any $n \in \mathbb R$, we have that ${\theta}^{ML}_n  \in [t_{(1)}, t_{(n)}]$ where $t_{(i)}$ denotes the $i$th element of $\{t_1,t_2\ldots\}$.
 Therefore, if $\{t_1,t_2\ldots\}$ is bounded (for example $\{t_1,t_2\ldots\} \subset \Theta$), then
 \[
-\lim_{n\to \infty} n\left(\hat{\theta}^{ML}_n - \theta \right)  = 1/\kappa(\theta), 
+\lim_{n\to \infty} n \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
 \] 
@@
 In other words, the ability to choose the threshold values in an adaptive manner based on previous messages strictly improves relative efficiency compared to a non-adaptive threshold selection.
-\\
+\par
 
@@
 As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \Ncal(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution.
-In this case, the ML estimator reduces to the estimator $\hat{\theta}_n$ of \eqref{eq:estimator_naive}.
+In this case, the ML estimator reduces to the estimator ${\theta}_n$ of \eqref{eq:estimator_naive}.
 As the following proposition shows, the Bayes risk for this choice of $\lambda$ is maximal, and thus provides an upper bound on the Bayes risk under any $\lambda$.
@@
 \end{enumerate}
-Then $\bar{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}(\hat{\theta}_n - \theta)$ converges in distribution to $\Ncal(0,V)$, where
+Then $\bar{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}({\theta}_n - \theta)$ converges in distribution to $\Ncal(0,V)$, where
 \[
@@
 \[
-\sqrt{n}\left(\hat{\theta}_n-\theta \right) \overset{d}{\to} \Ncal \left(0, 1/ \eta(0)\right). 
+\sqrt{n}\left({\theta}_n-\theta \right) \overset{d}{\to} \Ncal \left(0, 1/ \eta(0)\right). 
 \]
@@
 \begin{thm} \label{thm:normal_expansion}
-Let $\Delta_i = \theta_i - \theta$ and $\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \bar{\Delta}_i$. 
-Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{thm:polyak_juditsky}, there exists $K_1$ and $\lambda>0$ such that
+Set $\Delta_i = \theta_i - \theta$ and
+$\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \Delta_i$. Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{thm:polyak_juditsky}, there exists $K_1$ and $\lambda>0$ such that
 \begin{equation}
@@
 \[
-\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{1}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
-\]
-under the local alternative $Z_1,\ldots,Z_n \sim P^n_{h/\sqrt{n}}$ with density $f^n(x-h/\sqrt{n})$.
+\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-1}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
+\]
+under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h/\sqrt{n}}$ with density $f^n(x-h/\sqrt{n})$.
 \end{itemize}
@@
 
-In our setting, the condition \eqref{eq:PJ_additional_cond} holds since
+We have, 
 \begin{align*}
@@
 \end{align*}
-Consequently, 
+It follows that
 \begin{align*}
@@
 \end{align*}
-In addition, by anti symmetry of $f'(x)$ around $x=0$, 
-\[
-\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = 2f(0). 
+hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
+\[
+\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = 2f(0) = \psi'(0). 
 \]
@@
 \[
-n V_n = n \mathbb E \left[ \left(\hat{\theta}_n-\theta \right)^2 \right]  = \frac{1}{4 f^2(0)} + o(1).
+V_n = \mathbb E \left[ \left({\theta}_n-\theta \right)^2 \right]  = \frac{1}{4n f^2(0)} + o(n^{-1}).
 \]
@@
 \[
-\Delta^1_i = \Delta^1_{i-1} - \gamma_i (A \Delta_{i-1}+ \xi_i),\qquad \Delta_{0}^1 = c.
+\Delta^1_i = \Delta^1_{i-1} - \gamma_i (A \Delta_{i-1}+ \xi_i),\quad i=1,2\ldots.
 \]
@@
 \]
-Le Cam's third lemma \cite[Exm. 6.7]{van2000asymptotic} implies that under $P_{\theta+h/\sqrt{n}}$, 
+Le Cam's third lemma \cite[Exm. 6.7]{van2000asymptotic} implies that under $\Prob^n_{h/\sqrt{n}}$, 
 \[
@@
 %
-Since $B_1,B_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, for $\theta \in \Xi$ if and only if
+Since $B_1,B_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, $\theta$ is in $\Xi$ if and only if
 \begin{equation}

### 2019-07-26 onebit_full.tex
removed 'bounded' from LAminimax result
corrected citation from Beran

@@
 
+\newcommand{\enc}{\mathsf{enc}}
+\newcommand{\est}{\mathsf{est}}
+
 \tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
@@
 
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};
+\node[int1, right of = source2, node distance = 1.2cm] (enc2) {$\enc$};
 
@@
 \draw[->,line width = 2pt] (source2) -- (enc2); 
-\node[int1, right of = enc2, node distance = 2.7cm ] (est) {Est};
+\node[int1, right of = enc2, node distance = 2.7cm ] (est) {$\est$};
 
@@
   \node at (0,0) (source) {\small $X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {Enc 1};  
+  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
 \draw[->,line width = 2pt] (source) -- (enc1);
@@
  \node[below of = source, node distance = 1.5cm] (source2) {\small $X_2$};
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc 2};  
+\node[int1, right of = source2, node distance = 1.2cm] (enc2) {$\enc$};  
 \draw[->,line width = 2pt] (source2) -- (enc2);
@@
 \node[below of = source2, node distance = 2.1cm] (source3) {\small $X_n$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {Enc n};  
+\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};  
 \draw[->,line width = 2pt] (source3) -- (enc3);
@@
 
-\node[int1, right of = enc2, node distance = 3cm ] (est) {Est};
+\node[int1, right of = enc2, node distance = 3cm ] (est) {$\est$};
 \draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);   
@@
   \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {Enc 1};  
+  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
 \draw[->,line width = 2pt] (source) -- (enc1);
@@
  \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc 2};  
+\node[int1, right of = source2, node distance = 1.2cm] (enc2) {$\enc$};  
 \draw[->,line width = 2pt] (source2) -- (enc2);
@@
 \node[below of = source2, node distance = 2.1cm] (source3) {$X_n$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {Enc n};  
+\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};  
 \draw[->,line width = 2pt] (source3) -- (enc3);
@@
 
-\node[int1, right of = enc2, node distance = 2.1cm ] (est) {Est};
+\node[int1, right of = enc2, node distance = 2.1cm ] (est) {$\est$};
 \draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
@@
 \subsection{Asymptotically optimal estimator}
-Let $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ be a strictly positive sequence. Consider the following estimator ${\theta}_n$ for $\theta$:  
+Let $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ be a strictly positive sequence. Consider the following estimator ${\theta}_n$ for $\theta$:  
 \begin{equation}
@@
 \begin{thm} \label{thm:sgd}
-Consider the sequence $\left\{\bar{\theta}_n,\, n\in \mathbb N \right\}$ defined by \eqref{eq:sgd_est}. 
+Consider the sequence $\left\{\bar{\theta}_n \right\}_{n\in \mathbb N}$ defined by \eqref{eq:sgd_est}. 
 \begin{enumerate}
-\item[(i)] Assume that $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ satisfies
+\item[(i)] Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
 \begin{equation} \label{eq:conditions1}
@@
 %(or that $f(x-\theta)$ is differentiable in quadratic mean).  
-Then the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $P^n_{\theta,h,n}$ be the measure with density $f(x-\theta - h/\sqrt{n})$.
-Then
+Then for any bounded, symmetric, and quasi-convex function $L$, 
 \begin{align} 
-\label{eq:sgd_part2}
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
+& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
+\\
+& \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
 \end{align}
-under $P^n_{\theta,h,n}$. Consequently, for any bounded, symmetric, and quasi-convex function $L$, 
-\begin{align*}
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right]
-\\
-& \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right],
-\end{align*}
 where $Z \sim \Ncal(0,1)$. 
@@
 %
-\item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ satisfies
+\item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
 \begin{equation} \label{eq:conditions2}
@@
 The minimal value of this optimization is the sample median, and Theorem~\ref{thm:sgd} provides conditions for the sequence of gradient steps so that the algorithm converges to this minimum.
+In particular, parts (i) and (ii) of Theorem~\ref{thm:sgd} provides conditions under which $\bar{\theta}$ is asymptotically normal and local asymptotically minimax, in the sense that it attains the local asymptotic minimax bound \cite{van2000asymptotic}.
+Part (iii) provides an additional condition under which $\bar{\theta}$ also converges in its second moment.
  \par
@@
   \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {Enc};  
+  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
 \draw[->,line width = 2pt] (source) -- (enc1);
@@
 \node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {Enc};
+\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};
 
@@
 
-\node[int1, right of = enc3, node distance = 2.1cm ] (est) {Est 1};
+\node[int1, right of = enc3, node distance = 2.1cm ] (est) {$\est_1$};
 
@@
 \node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
-\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {Enc$({\theta}_{n_1})$};  
+\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {$\enc$};  
 \draw[->,line width = 2pt] (sourceB) -- (enc1B);
@@
 \node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
-\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {Enc$({\theta}_{n_1})$};  
+\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {$\enc$};  
 \draw[->,line width = 2pt] (source3B) -- (enc3B); 
@@
 
-\node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {Est 2};
-
-\draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.8cm] {$B_{n_1+1}$} (estB);
+\node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {$\est_2$};
+
+\draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.5cm] {$B_{n_1+1}$} (estB);
 \draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);
@@
 
-\draw[->,line width = 1pt] (est.east) -| +(1,-0.5) -- +(1,-2) -| (enc3B.north);
+\draw[->,line width = 0.5pt] (est.east) -| +(1.3,-0.5) -- +(1.3,-2.5) -| (enc3B.north);
 
@@
 
-\draw[->,line width = 1pt] (estB) -- +(0.8,0) node[right] {${\theta}_n$};
+\draw[->,line width = 0.5pt] (estB) -- +(0.8,0) node[right] {${\theta}_n$};
+\node[below of = enc1B, node distance = 0.5cm] {$\vdots$};
+
 \end{tikzpicture}
@@
 \]
-where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\\
+where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\par
 
@@
 %
-An important conclusion of  Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models (e.g. \cite{van2000asymptotic}):
+An important conclusion of  Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models \cite{van2000asymptotic}):
 \begin{cor} \label{cor:LA_minimax}
 Let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
-Then for any bounded, symmetric, and quasi-convex function $L$,
+Then for any symmetric and quasi-convex function $L$,
 \begin{align*}
@@
 \end{align}
-From Corollary~\ref{cor:LAN_thresh}, we conclude that the ARE under a uniform distribution is $\kappa_\unif \sigma^2$. \\
+From Corollary~\ref{cor:LAN_thresh}, we conclude that the ARE under a uniform distribution is $\kappa_\unif \sigma^2$. \par
 
@@
 We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.
- \\
 
@@
 \subsubsection*{Proof of (ii)}
-The proof requires the following refinement of Theorem~\ref{thm:polyak_juditsky}.
+We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\mathbb R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates.
+Then
+\begin{align}
+\label{eq:sgd_part2}
+\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
+\end{align}
+under $\Prob_{\theta,n}$.
+Under the assumption that $f(x)$ is continuously differentiable with finite Fisher information for location, the model $\{Z_n+ \theta\}_{n \in \mathbb N}$ is differentiable in quadratic mean \cite[Exm.
+7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
+\[
+\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
+\]
+where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$. 
+ The random variable $L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)
+$ is bounded, and hence 
+\[
+\ex{ L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)} \to \ex{L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)}
+\]
+
+Any regular estimators in a LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}, hence the proof of (ii) follows once we establish the regularity of $\bar{\theta}_n$. \\
+
+%Any estimator satisfying \eqref{eq:sgd_part2} also satisfies \eqref{eq:attaining_LAM} \cite[P. 157]{ibragimov2013statistical}.
+
+The proof of the regularity of $\bar{\theta}_n$ requires the following refinement of Theorem~\ref{thm:polyak_juditsky}.
 \begin{thm} \label{thm:normal_expansion}
@@
 \]
+
 {\color{red}

### 2019-08-15 onebit_full.tex
small changes

@@
 
-\subsubsection*{Sketch of Proof}
-The main idea in the proof is to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
-Once this bound is achieved, the result follows by using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are in Appendix~\ref{proof:thm:adpative_lower_bound}.\par
+\subsubsection*{Proof}
+%We first bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
+The result then follows using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
+The details are in
+See Appendix~\ref{proof:thm:adpative_lower_bound}.\par
 
@@
 
-Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the maximal ARE as established by Theorem~\ref{thm:adpative_lower_bound}.
+Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the maximal ARE, as established by Theorem~\ref{thm:adpative_lower_bound}.
 %Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$.
@@
 
-\subsection{Optimality using One Round of Threshold Adaptation}
+\subsection{Maximal Efficiency using One Round of Threshold Adaptation}
 In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
@@
 %
-We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ at least once.
+We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ based on previously observed bits at least once.
 %
@@
 \begin{align*}
- \sqrt{n} \left( {\theta}_{n_2} - \theta  \right)^2  \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
+ \sqrt{n} \left( {\theta}_{n_2} - \theta  \right) \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
 \end{align*}
@@
 \]
-Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ we obtain
+Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ implies
 \begin{align*}
@@
 %where this convergence is uniform in $t$ since all moments of $F^{-1}(\hat{p}_{n_2})$ exists. 
-By the law of large numbers we also have
+On the other hand, by the law of large numbers,
 \[
@@
 \]
-so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity, and thus 
+so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity and thus 
 \[
@@
 \]
-By Slutsky's theorem we get
+Finally,
 \begin{align*}
@@
 & \overset{d}{\to} \Ncal\left( 0, 
-1/\eta(0) \right). 
-\end{align*}
+1/\eta(0) \right) 
+\end{align*}
+by Slutsky's theorem.
 \end{proof}
@@
 \section{Distributed Estimation \label{sec:distributed}}
-We now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii).
-In this setting each one-bit message $B_i$ is only a function of its private sample $X_i$, and hence $B_i$ characterized by its \emph{detection region}, defined as
+In this section, we now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii) where  each one-bit message $B_i$ is only a function of its private sample $X_i$.
+In this case, the $i$th encoder is fully characterized its \emph{detection region}, defined as
 \[
@@
 \end{tikzpicture}
-\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \Ncal(\theta, \sigma^2)$under an optimal threshold distribution $\lambda^\star$ for $\pi$ the uniform distribution over $\Theta = [-0.5,0.5]$.
+\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \Ncal(\theta, \sigma^2)$ under an optimal threshold distribution $\lambda^\star$, when the prior $\pi$ is the uniform distribution over $\Theta = [-0.5,0.5]$.
 %
@@
 \begin{align}
-\mathbb E  \frac{1}{\kappa(\theta)}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
+\ex{  \frac{1}{\kappa(\theta)}}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
 \end{align}
@@
 \end{proof}
-We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so taking $\theta_0 = \mathbb E \theta$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
+We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so the choice $\theta_0 = \ex{ \theta}$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
 The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$.

### 2019-08-16 onebit_full.tex
small changes
changed h to h_n in proof of Thm. 12

@@
 %
-\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with finite Fisher information for location
+\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with a finite location Fisher information, namely
 \[
@@
 under $\Prob_{\theta,n}$.
-Under the assumption that $f(x)$ is continuously differentiable with finite Fisher information for location, the model $\{Z_n+ \theta\}_{n \in \mathbb N}$ is differentiable in quadratic mean \cite[Exm.
+Under the assumption that $f(x)$ is continuously differentiable with a finite location Fisher information, the model $\{Z_n+ \theta\}_{n \in \mathbb N}$ is differentiable in quadratic mean \cite[Exm.
 7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
@@
 \]
-
-Any regular estimators in a LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}, hence the proof of (ii) follows once we establish the regularity of $\bar{\theta}_n$. \\
-
-%Any estimator satisfying \eqref{eq:sgd_part2} also satisfies \eqref{eq:attaining_LAM} \cite[P. 157]{ibragimov2013statistical}.
-
-The proof of the regularity of $\bar{\theta}_n$ requires the following refinement of Theorem~\ref{thm:polyak_juditsky}.
+Any regular estimators in a LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}, hence in order to prove (ii) it is left to show that $\bar{\theta}_n$ is regular. For this purpose, 
+we use the following refinement of Theorem~\ref{thm:polyak_juditsky}, proof of which is given in Subsection~\ref{proof:thm:normal_expansion} below.
+%
 \begin{thm} \label{thm:normal_expansion}
@@
 \]
-then
-\[
-\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-1}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
-\]
-under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h/\sqrt{n}}$ with density $f^n(x-h/\sqrt{n})$.
+then for any converging sequence $h_n \to h$,
+\[
+\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-h}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
+\]
+under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h_n/\sqrt{n}}$ with density $\prod_{i=1}^n f(x_i-h_n/\sqrt{n})$.
 \end{itemize}
 \end{thm}
-The proof of Theorem~\ref{thm:normal_expansion} is given in Subsection~\ref{proof:thm:normal_expansion} below. \\
-
-We have, 
+We now use this theorem to show regularity of $\bar{\theta}_n$. We have, 
 \begin{align*}
@@
 \[
-\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = 2f(0) = \psi'(0). 
+\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = -2f(0) = -\psi'(0). 
 \]
@@
 \]
-Assume that $A>0$ and condition (ii) of Theorem~\ref{thm:polyak_juditsky} hold. Then 
+Assume that $A>0$ and condition (ii) of Theorem~\ref{thm:polyak_juditsky} holds. Then 
 \begin{equation}
@@
 \end{equation}
-where $\alpha_n$, and $w_i^n$ are real numbers such that $|\alpha_n| \leq K$ and $|w_i^n|\leq K$ for some $K< \infty$, and 
+where $\alpha_n$ and $w_i^n$ are real numbers such that $|\alpha_n| \leq K$ and $|w_i^n|\leq K$ for some $K< \infty$, and 
 \[
@@
 \subsubsection*{Step I}
-The expansion \eqref{eq:normal_expansion_lem} holds for the process  ${\bar{\Delta}^1_i}$ defined as follows:
+The expansion \eqref{eq:normal_expansion_lem} holds for the process  $\{\bar{\Delta}^1_i\}_{i=1}^\infty$ defined as follows:
 \begin{align} \label{eq:Polyak_expansion_lem1_alg}
@@
 
-In order to show this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$.
+In order to prove this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$.
 The first expression on the RHS on \eqref{eq:Polyak_expansion} goes to zero in variance.
@@
 \label{eq:PJ_LAN}
-& \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} (Z_1,\ldots,Z_n) =  \log \prod_{i=1}^{n} \frac{f(Z_i-h/\sqrt{n})}  {f(X_i-\theta)} = h J_n - \frac{1}{2}h^2 I_{\theta} + o_{p,n}(1),
+& \log \frac{\Prob^n_{h_n/\sqrt{n}}}{\Prob^n_0} (Z_1,\ldots,Z_n) =  \log \prod_{i=1}^{n} \frac{f(Z_i-h_n/\sqrt{n})}  {f(X_i-\theta)} = h J_n - \frac{1}{2}h^2 I_{\theta} + o_{p,n}(1),
 \end{align}
+for any converging sequence $h_n \to h$, 
 where 

### 2019-08-20 onebit_full.tex
added a note on the extension of Thm. 2 to other loss functions

@@
 \begin{equation} \label{eq:ceo_bound}
- n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
+ n \ex{\left( \theta - \theta_n \right)^2} \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
 \end{equation}
@@
 \[
-n\mathbb E\left[ (\theta-\theta_n)^2 \right] \leq  \frac{1}{4f^2(0)}+O(n^{-1}),
+n\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{1}{4f^2(0)}+O(n^{-1}),
 \]
@@
 \]
-
-Next, we present an adaptive encoding and estimation scheme that attains the maximal ARE of $\eta(0)\sigma^2$.
+It is possible to extend Theorem~\ref{thm:adpative_lower_bound} to any other loss functions using a more subtle version of the Van Tress inequality provided in \cite{efroimovich1980information}.
+See also \cite{DBLP:journals/corr/abs-1902-08582}.
+\par
+%
+Next, we provide an adaptive encoding and estimation scheme that attains the maximal ARE of $\eta(0)\sigma^2$.
 

### 2019-09-19 Figs/encoding-settings.tex
Starting to edit

--- 2019-08-16 onebit_full.tex
@@
-\documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper
-
-%LatexiDiff ignore tikz:
-% $: latexdiff -c "PICTUREENV=(?:picture|tikzpicture|DIFnomarkup)[\w\d*@]*" old.tex new.tex > diff.tex
-
-%\IEEEoverridecommandlockouts                              %
-
-%\usepackage{mathcomSTEP}
-
-%\overrideIEEEmargins 
-%\IEEEoverridecommandlockouts                              % This command is only needed if 
-% you want to use the \thanks command
-
-%\overrideIEEEmargins                                      % Needed to meet printer requirements.
-
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-\onecolumn
-
-\usepackage{mathptmx} 
-\usepackage{times} 
-\usepackage{amsmath} 
-\usepackage{amsbsy} 
-\usepackage{amssymb}
-
-%\usepackage{newtxtext, newtxmath}
-\usepackage{mathrsfs}
-\usepackage{comment}
-\usepackage[export]{adjustbox}
-\usepackage{tikz}
-\usetikzlibrary{external,positioning,decorations.pathreplacing,shapes,arrows,patterns}
-
-\usepackage[hidelinks]{hyperref}
-%\tikzexternalize[mode=list and make]
-\usepackage{algorithmicx}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage{pstool}
-\usepackage[latin1]{inputenc}
-\usetikzlibrary{arrows,shapes}
-\usepackage{xifthen}
-\usepackage{epic}
-%\usepackage{caption}
-\usepackage{epstopdf}
-
-\newtheorem{thm}{\bf{Theorem}}
-\newtheorem{cor}[thm]{\bf {Corollary}}
-\newtheorem{lem}[thm]{\bf {Lemma}}
-\newtheorem{prop}[thm]{\bf {Proposition}}
-\newtheorem{example}{\bf {Example}}
-\newtheorem{definition}{\bf {Definition}}
-\newtheorem{rem}{\bf {Remark}}
-\newtheorem{assump}{\bf {Assumptions}}
-
-\newcommand{\ex}[1]{\ensuremath{\mathbb{E}\left[ #1\right]}}
-
-\newcommand{\Var}[1]{\ensuremath{\mathrm{Var} \left[ #1\right]}}
-
-\newcommand{\unif}{\mathsf{unif}}
-\newcommand{\card}{\mathrm{card}}
-\newcommand{\ARE}{\mathsf{ARE}}
-\newcommand{\supp}{\mathrm{supp} }
-\renewcommand\vec[1]{\ensuremath\boldsymbol{#1}}
-\newenvironment{proof}{\paragraph*{Proof}}{\hfill$\square$ \newline}
-\newcommand{\sgn}{\mathrm{sgn} }
-\newcommand{\Prob}{\mathbb{P} }
-\newcommand{\argmax}{\mathrm{argmax}}
-\newcommand*{\QEDA}{\hfill\ensuremath{\square}}
-\newcommand{\CEO}{\mathsf{CEO}}
-\newcommand{\Ncal}{\mathcal{N}}
-
-\newcommand{\enc}{\mathsf{enc}}
-\newcommand{\est}{\mathsf{est}}
-
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-\tikzstyle{sint}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.8cm,thick ]
-\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
-\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
-\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.7cm,thick ]
-\tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-
-\author{
-    \IEEEauthorblockN{
-Alon Kipnis\IEEEauthorrefmark{1} and   
-    John C. Duchi\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}  \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}Stanford University, Department of Statistics \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Stanford University, Department of Electrical Engineering. }
-}
-
-\title{\LARGE \bf Mean Estimation from One-Bit Measurements}
-
-\begin{document}
-\graphicspath{{./Figs/}}
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-We consider the problem of estimating the mean of a symmetric log-concave distribution under the following constraint: only a single bit per sample from this distribution is available to the estimator.
-We study the mean squared error risk in this estimation as a function of the number of samples, and hence the number of bits, from this distribution.
-%
-Under an adaptive setting in which each bit is a function of the current sample and previously recorded bits, we show that the optimal relative efficiency compared to the sample mean is the efficiency of the median.
-%For example, in estimating the mean of a normal distribution, a constraint of one bit per sample incurs a penalty of $\pi/2$ in sample size compared to the unconstrained case.
-%
-We also consider a distributed setting where each bit is only a function of a single sample.
-We show that the optimal efficiency of the adaptive setting can be attained by splitting the sample into two parts and allowing only a single adaptation.
-Otherwise, we show that no one sample estimation procedure can attain the optimal efficiency uniformly over all points in the parameter space.
-%
-%Finally, we analyze a distributed setting where the bits are obtained by comparing each sample against a prescribed threshold.
-Consequently, we consider the threshold density that minimizes the maximal MSE.
-%
-Our results indicate that estimating the mean from one-bit measurements is equivalent to estimating the sample median from these measurements.
-In the adaptive case, this estimate can be done with vanishing error for any point in the parameter space.
-In the distributed case, this estimate can be done with vanishing error only for a finite number of possible values for the unknown mean.
-\end{abstract}
-
-%{\color{red}  See LASSO results in http://arxiv.org/abs/1506.02181v1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{sec:Intro}
-Estimating parameters from data collected and processed by multiple units may be limited due to communication constraints between these units. 
-%
-For example, this scenario arises in sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit.
-In these situations, the ability to estimate a particular parameter from the data is dictated not only by the quality of observations and their number but also by the available bandwidth for communicating between the sensors and the central estimator.
-The question that we ask is to what extent a parametric estimation task is affected by this constraint on communication, and what are the fundamental performance limits in estimating a parameter subject to such restriction.
-\par
-%%
-\begin{figure*}
 \begin{center}
@@
 \end{center}
-\caption{\label{fig:setup} 
-Three encoding settings: (i) Centralized  -- an encoder sends $n$ bits after observing $n$ samples.
-(ii) Adaptive (sequential) --  the $i$th encoder sends the bit $B_i$ depending on its private sample $X_i$ and previous bits $B_1,\ldots,B_{i-1}$.
-(iii) Distributed  -- each encoder send the bit $B_i$ based on its private sample $X_i$ only.}
-\end{figure*}
-%%
-
-This paper answers this question in a particular setting: the estimation of the mean $\theta$ of a symmetric log-concave distribution with finite variance, under the constraint that only a single bit can be communicated on each sample from this distribution.
-As it turns out, the ability to share information before committing on each one-bit message dramatically affects the performance in estimating $\theta$.
-We, therefore, distinguish among the three settings illustrated in Figure~\ref{fig:setup}
-\begin{itemize}
- \item[(i)\,\,] \emph{Centralized} encoding: all $n$ encoders confer and produce a single message consists of $n$ bits.
- \item[(ii)\,] \emph{Adaptive} or \emph{sequential} encoding: The $n$th encoder observes the $n$th sample and the $n-1$ previous bits.
- \item[(iii)] \emph{Distributed} encoding: The $n$th message is only a function of the $n$th sample.
- \end{itemize}
-Evidently, as far as information sharing is concerned, settings (iii) is a more restrictive version of (ii) which is more restrictive than (i).
-Below are three application examples for each of the settings (i)-(iii) above, respectively:
-\begin{itemize}
-\item {\bf Signal acquisition:} A quantity is measured $n$ times at different instances.
-The results are averaged in order to reduce measurement noise and the averaged result is then stored or communicated using $n$ bits.
-\item {\bf Analog-to-digital conversion:} A sigma-delta modulator (SDM) converts an analog signal into a sequence of bits by sampling the signal at a very high rate and then using one-bit threshold detector combined with a feedback loop to update an accumulated error state \cite{1092194}.
-Therefore, the expected error in tracking an analog signal using an SDM falls under our setting (ii) when we assume that the signal at the input to the modulator is a constant (direct current) corrupted by, say, thermal noise \cite{53738}.
-Since the sampling rates in SDM are usually many times more than the bandwidth of its input, analyzing SDM under a constant input provides meaningful lower bound even for non-constant signals.
-\item {\bf Privacy:} A business entity is interested in estimating the average income of its clients.
-In order to keep this information as confidential as possible, each client independently provides an answer to a yes/no question related to its income.
-\end{itemize}
-%
-We measure the performance in estimating $\theta$ by the quadratic risk. For an estimator with finite quadratic risk $R_n$, we are interested in particular in the limit
-\begin{equation}
-\label{eq:ARE_def}
-\lim_{n\to \infty} \frac{\sigma^2/n}{R_n},
-\end{equation}
-describing the \emph{asymptotic relative efficiency} (ARE) of this estimator compared to an estimator whose variance decreases as $\sigma^2/n+o(n^{-1})$.
-Estimators of this form include the empirical mean of the samples, and, under some conditions, the optimal Bayes estimator.
-\par
-%
-In addition to the examples above, the excess risk in estimating a fixed parameter due to a one-bit per sample constraint is useful in bounding from below the excess risk in estimating signals from thier noisy one-bit quanitzed noisy measurements.
-Specifically, the excess risk or ARE we derive serve as the most optimistic estimate for the risk in estimating under one-bit per measurement constraint signals changing over time or space.
-Such estimation settings are considered in \cite{baraniuk2017exponential, jacques2013robust, plan2013one, li2017channel, choi2016near}.
-\par
-
-% given a prior distribution on the space $\Theta$ where $\theta$ resides. \\
-
-In setting (i), the estimator can evaluate the optimal mean estimator (e.g., the sample mean in the Gaussian case) and then quantize it using $n$ bits.
-Since the accuracy in describing the empirical mean decreases exponentially in $n$, the error due to quantization is negligible compared to the quadratic risk in estimating the mean \cite{720540}.
-Therefore, the ARE in this setting is $1$.
-Namely, asymptotically, there is no loss in performance due to the communication constraint under centralized encoding.
-%
-In this paper we show that a similar result does not hold in setting (ii): the ARE of any adaptive estimation scheme is at most the ARE of the sample median.
-Specifically, when the samples are drawn from the normal distribution, this ARE equals $2/\pi$, showing that the one-bit constraint increases the effective sample size in estimating $\theta$ by at least $\pi/2$ compared to estimating it without the bit constraint.
-We also show that this lower bound on the ARE is tight by providing an estimator that attains it.
-In fact, we show that only one adaptiveness, as illustrated in Figure~\ref{fig:one_round} is enough to achieve the optimal ARE.
-%
-Clearly, the penalty on the sample size in setting (iii) is at least as large as that in setting (ii).
-We show, however, that unlike in setting (ii), there is no distributed estimation scheme that is uniformly optimal in the sense that it attains the ARE of the sample median for all $\theta$ in the parameter space.
-This result is obtained by establishing local asymptotic normality of regularly enough encoding procedures for setting (iii), resulting in an exact characterization of the ARE of such procedures.
-To summarize our contributions, we establish that the optimal ARE in settings (i) is $1$, the optimal ARE in setting (ii) is ARE of the sample median, and no uniformly optimal procedure exists in setting (iii).
-
-% Instead, in setting (iii) we restrict ourselves to estimators from messages obtained by comparison against a prescribed value (that may be different for each sample).
-We show that the maximum likelihood (ML) estimator for $\theta$ from these messages is asymptotically local minimax, and its asymptotic variance is strictly greater than the variance of the median.
-Thus, at least when limited to threshold detection, the ability to adapt the threshold allows for a more efficient estimation.
-%This is in contrast to the \\ counterpart of our setting where $\theta$ is taken from a finite space
-
-It is important to note that although the ARE in setting (i) is one, this scheme already poses a non-trivial challenge for the design and analysis of optimal encoding and estimation procedures.
-Indeed, representing an unknown random quantity using $n$ bits is equivalent to designing a $2^n$ levels scalar quantizer \cite{gray1998quantization}.
-However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation problem and hence its exact value is unknown.
-As a result, a non-trivial exploration-exploitation trade-off arises even in setting (i).
-%Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$. 
-Therefore, while uncertainty due to quantization decreases exponentially in the number of bits $n$, hence the ARE is $1$, it is still difficult to derive an exact expression for the MSE in this setting.
-%
-The situation is even more involved in the adaptive encoding setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$ may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
-Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $n-1$ messages, is not guaranteed to be globally optimal.
-Therefore, while we characterize the optimal one-bit message given the previous messages, this characterization does not necessarily lead to an upper bound on the ARE.
-Instead, our result on the maximal ARE is obtained by bounding the Fisher information of any $n$ adaptive messages and using an appropriate information inequality.
-\par
-%
-%In addition to encoding and estimation schemes that lead to optimal results, we also consider two additional ``natural'' schemes.
-Specifically, in setting (ii) we consider the one-bit optimal scheme, i.e., the case of a greedy encoder that given the $n$th sample and the previous $n-1$ bits, provides a bit that minimizes the $n$-step MSE.
-In setting (iii) we also consider the case where the messages are obtained by comparing each sample against a prescribed threshold.
-This threshold may be different across samples and is assumed deterministic (independent of the data).
-
-\subsection*{Related Works}
-When the variance $\sigma^2$ is negligible compared the to desired accuracy, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is solved by a bisection style method over the parameter space.
-Therefore, the general case of non-zero variance is reminiscent of the noisy binary search problem with a possibly infinite number of unreliable tests \cite{cicalese2002least, Karp:2007:NBS:1283383.1283478}.
-However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a constant input corrupted by Gaussian noise.
-Using an SDM, Wong and Gray \cite{53738} showed that the output of the modulator converges to the true constant input almost surely, so that an SDM provides a consistent estimator for setting (ii).
-The rate of this convergence, however, was not analyzed and cannot be derived from the results of \cite{53738}.
-In particular, our results for setting (ii) imply that the asymptotic rate of convergence of the MSE in SDM to a constant input under an additive white Gaussian noise is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-Baraniuk et.
-al \cite{baraniuk2017exponential} also considered adaptive one-bit measurements in the context of analog-to-digital conversion, although without noise at the input.
-By establishing the lower bound of $\sigma^2\pi/2n$ on the MSE, we show that the main results of \cite{baraniuk2017exponential}, an exponential MSE decaying rate, does not hold in the noisy setting.
-Stated otherwise, the MSE in the setting of \cite{baraniuk2017exponential} may decay exponentially up to the noise level, after which it decays at most as $\sigma^2\pi/2n$.
-\par
-%
-One-bit measurements in the distributed setting (iii) was considered in \cite{904560,4244748, 6882252, chen2010performance, 5184907}, but without optimizing the encoders and their detection rules.
-Consequently, the performance derived in these works are not optimal.
- % analyzed the estimation from distributed quantized measurements when the same detection rule is applied by all encoders.
-However, the error criterion considered in these works is the Fisher information rather than the MSE risk or ARE criterion.
-\par
-%Once the decision rule of each encoder is fixed, the optimal estimation of $\theta$ is determined using the maximum a posteriori probability rule.
-Hence, the distributed setting is reduced to finding the optimal decision rule of each encoder.
-The work of \cite{52470} addresses the counterpart of our setting (iii) in the case of hypothesis testing, although the results there cannot be extended to parametric estimation.
-When the parameter space $\Theta$ is finite, Tsitsiklist \cite{tsitsiklis1988decentralized} showed that when the cardinality of $\Theta$ is at most $M$ and the probability of error criterion is used, then no more than $M(M-1)/2$ different detection rules are necessary in order to attain probability of error decreasing exponentially with the optimal exponent.
-%That is, beyond $M(M-1)/2$ some decision rules can be repeated without losing optimality.
-Furthermore, in a version of this problem for the adaptive setting \cite{5751320}, it was shown that, with specific two-stage feedback, there is no gain in feedback compared to the fully distributed setting.
-Our results imply that the ARE in the distributed setting with threshold detection rules is strictly larger than that in the adaptive setting for almost all points in $\Theta$, suggesting that the case where the cardinality of $\Theta$ is finite is different from the case where $\Theta$ is an open set.\par
-%
-As we explain in detail in Section~ \ref{sec:preliminary}, the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}, leads to lower bounds on the MSE in setting (iii).
-For the case of a Gaussian distribution, this lower bound bounds the ARE to be at most $3/4$.
-Thus, while this bound on the ARE provides no new information compared to the upper bound of $2/\pi$ we derive for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimum even under the one bit per sample constraint.
- \par
-% 
-Finally, we note that minimax estimation under limited communication with an arbitrary number of bits per node was considered in 
-\cite{zhang2013information, duchi2014optimality}.
-The specialization of the results in \cite{zhang2013information, duchi2014optimality} to our settings (ii) and (iii) leads to looser lower bounds then the ones we derive in this paper.
-Looser bounds can also be obtained from works considering general inference and distributed estimation problems under data compression constraint \cite{DBLP:journals/corr/abs-1802-08417, zhang1988estimation, han2018distributed, xu2017information, Barnes2018}.
-In particular, the subsequent work of \cite{Barnes2018} uses an approach similar to ours to derive lower bound on the error in various parametric estimation problems from quantized measurements.
-\par
-
-The remainder of this paper is organized as follows.
-In Section~\ref{sec:problem} we describe the problem and useful notation.
-In Section~\ref{sec:preliminary} we provide two simple bounds on the efficiency and MSE.
-Our main results for the adaptive and distributed cases are given in Sections~\ref{sec:sequential} and \ref{sec:distributed}, respectively.
-In Section~\ref{sec:conclusions} we provide concluding remarks.
-
-\section{Problem Formulation \label{sec:problem}}
-
-Let $f(x)$ be a symmetric and log-concave density function with a finite second moment $\sigma^2$.
-For $\theta \in \Theta$, denote by $P_X$ the probability distribution with density $f\left( x-\theta \right)$.
-Therefore, $P_X$ is an absolutely continuous log-concave distribution with mean $\theta$ and variance $\sigma^2$.
-Symmetry and log-concavity of $f(x)$ imply that $P_X$ is strongly unimodal (has a unique local maxima) with its mode at $x =\theta$ \cite{ibragimov1956composition}.
-We further assume that the \emph{parameter space} $\Theta$ is a closed interval of the real line.
-\par
-In some situations it is useful to assume that $\theta$ is drawn once from the prior distribution $\pi$ on $\Theta$.
-In this case we assume that $\pi$ is an absolutely continuous distribution, and denote its density by $\pi(\theta)$, i.e., $\pi(d\theta) = \pi(\theta)d\theta$.
-\par
-The random variables $X_1,\ldots,X_n$ represent $n$ independent samples from $P_X$. 
-We are interested in estimating $\theta$ from a set of $n$ binary messages $B_1,\ldots,B_n$, obtained from $X_1,\ldots,X_n$ under three possible scenarios illustrated in Figure~\ref{fig:setup}: 
-\begin{itemize}
-\item[(i)~~] Centralized $B_i(X_1,\ldots,X_n)$, $i=1,\ldots,n$.
-\item[(ii)~] Adaptive $B_i(X_i,B_1,\ldots,B_{i-1})$, $i=2,\ldots,n$.
-\item[(iii)] Distributed $B_i(X_i)$, $i=1,\ldots,n$.
-\end{itemize}
-
-The performance of an estimator ${\theta}_n \triangleq {\theta}_n(B^n)$ in any of these cases is measured according to the quadratic risk:
-\begin{equation}
-\label{eq:error_def}
-R_n \triangleq \mathbb E\left({\theta}_n - \theta \right)^2,
-\end{equation}
-where the expectation is taken with respect to the distribution of $X_1,\ldots,X_n$ and, whenever available, a prior distribution $\pi(\theta)$ over $\Theta$.  
-%It is well known that minmax estimation error 
-%\begin{equation}
-%R_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left({\theta}_n - \theta \right)^2 | \theta \right],
-%\end{equation}
-%can be obtained from $R_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}. 
-%
-The main problems we consider in this paper are the minimal value of \eqref{eq:error_def}, as a function of $n$ and $f(x)$, under different choices of the encoding functions in cases (i), (ii), and (iii).
-\par
-
-We give particular attention to the ARE of estimators with respect to an asymptotically normal efficient estimator that is not subject to the bit constraint.
-Specifically, let $\{a_n,\,n\in \mathbb N\}$ be a sequence such that
-\[
-\sqrt{a_n}\left({\theta}_n - \theta\right) \overset{d}{\longrightarrow} \Ncal(0, \sigma^2).
-\]
-Then the ARE of ${\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
-\[
-\ARE({\theta}_n) \triangleq
-\lim_{n\rightarrow \infty} \frac{a_n}{n}. 
-\]
-Note that in the special case where there exists $V \in \mathbb R$ such that
-\[
-a_n \mathbb E \left({\theta}_n - \theta \right)^2 = V + o(1),
-\]
-with $o(1)\to 0$ as $n\to \infty$, then the ARE of ${\theta}_n$ is finite and equals $\sigma^2/V$. \par
-
-In addition to the notation above, we also denote by $F(x)$ the cumulative distribution function of $X_i$, and define
-\begin{equation} \label{eq:eta_def}
-\eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))} =  \frac{f(x)f(-x)}{F(x)F(-x)}, 
-\end{equation}
-where the last equality is due to symmetry of $f(x)$. We note that 
-\begin{equation}
-\label{eq:eta_h}
-\eta(x) = h(x)h(-x) = f(x) \left( h(x) + h(-x) \right), 
-\end{equation}
-where 
-\[
-h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
-\]
-is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function since $f(x)$ is log-concave \cite{bagnoli2005log}. 
-%
-For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as illustrated in Fig.~\ref{fig:eta}. 
-%
-In this paper we only consider the normal distribution and other log-concave symmetric distributions for which this property of $\eta(x)$ holds. Specifically, we require the following:
-\begin{assump} \label{assump:failure_rate}
- $\eta(x)$ has a unique maximum (at the origin) and is a non-increasing function of $|x|$. 
-\end{assump}
-%That is, Assumption~\ref{assump:failure_rate} says that $\eta'(x) < 0 $ for all $x>0$. 
-Under this assumption we have, 
-\[
-4f^2(x) \leq \eta(x) \leq \eta(0),
-\] 
-%
-where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median.
-Combined with log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that $\eta(x)$ vanishes as $|x|\rightarrow \infty$.
-\par
-%
-Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions).
-Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.\par
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -3, xmax=3, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.9,
-samples=10, 
-xlabel= $x$,
-xtick={-2,-1,0,1,2},
-xticklabels={-2,-1,0,1,2},
-ytick={0,0.3989423,0.6366198},
-yticklabels={0,$\frac{1}{\sqrt{2 \pi}}$,$2/\pi$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\eta(x)$};
-\addplot[domain = -5:5, samples = 50, color = red, solid, smooth]  {exp(-x^2/2) / sqrt(2*3.14159)};
-\addlegendentry{$\phi(x)$};
-\addplot[domain = -5:5, samples = 50, color = black, solid, dashed]  {4*exp(-x^2) / (2*3.14159)};
-\addlegendentry{$4\phi^2(x)$};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -4, xmax=4, 
-restrict y to domain = -10:0,
-ymin = -10,
-samples=10, 
-xlabel= $x$,
-xtick={-3,-2,-1,0,1,2,3},
-xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,-0.45158,-0.919},
-yticklabels={0,,},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\log \eta(x)$};
-\addplot[domain = -5:5, samples = 30, color = red, solid, smooth]  {-(x)^2/2 -0.9189};
-\addlegendentry{$\log \phi(x)$};
-\end{axis}
-\end{tikzpicture}
-\caption{
-The function $\eta(x) = f^2(x) / F(x)F(-x)$ for $f(x) = \phi(x)$ the standard normal density.
-\label{fig:eta}
-}
-\end{center}
-\end{figure}
-
-\section{Consistent Estimation and Off-the-shelf Bounds \label{sec:preliminary}}
-%
-In this section we adapt known results to derive lower and upper bounds on the relative efficiency under setting (iii). These bounds establish the following facts:
-\begin{itemize}
-\item[I.] A consistent estimator with an asymptotically normal distribution always exists in setting (iii), and hence in setting (ii). 
-\item[II.] For the normal distribution, the ARE in setting (iii) is at most $3/4$. Namely, under setting (iii), all estimators are strictly inferior compared to the sample mean. 
-\end{itemize}
-
-\subsection{Consistent Estimation}
-Fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
-\[
-B_i = \mathbf 1_{X_i>\theta_0}, 
-\]
-where $\mathbf 1_A$ is the indicator of the event $A$. We have
-\[
-P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
-\]
-so that 
-\begin{equation}
-\label{eq:estimator_naive}
-{\theta}_n = \theta_0 + F^{-1}\left( P_n \right)
-\end{equation}
-is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set due to log-concavity.
-Furthermore, the variance of $P_n$ is $F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)$, and hence the delta method implies that ${\theta}_n$ is asymptotically normal with variance
-\begin{equation} 
- \frac{F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}{f^2(\theta-\theta_0)} = \frac{1}{
-\eta(\theta-\theta_0)}.
-\end{equation}
-In particular, the ARE of ${\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
-In other words, for a prescribed accuracy, ${\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
-\par
-%
-%
-Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of ${\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
-This ARE is attained only when $\theta_0 = \theta$, whereas $\theta$ is apriori unknown.
-Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of ${\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
-As an example, when $f(x)$ is a normal density, the ARE of ${\theta}_n$ is less than $\approx 0.14$ when $\theta_0$ is $2$ standard deviations from $\theta$.
-Therefore, the estimator ${\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
-\par
-It is suggested that we can attain lower variance in estimation by updating the threshold value $\theta_0$ in \eqref{eq:estimator_naive} after observing one or a batch of the single bit messages.
-Schemes with such adaptation fall within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
-\par
-
-\subsection{Multiterminal Source Coding \label{sec:ceo}}
-The CEO setting considers the estimation of a sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_i$ is available at $n$ terminals.
-At each terminal $i$, an encoder observes the $k$ noisy samples
-\[
-X_{i,j} = \theta_j + Z_{i,j},\qquad j=1,\ldots,k, \qquad i = 1,\ldots,n,
-\]
-and transmits $r_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates ${\theta}_1,\ldots,{\theta}_k$ with the goal of minimizing the quadratic risk:
-\[
-R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - {\theta}_j \right)^2 \right]. 
-\]
-Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $r_1=\ldots=r_n = 1$.
-It follows that, assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
-%
-Consequently, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the minimal MSE in the CEO setting as $k \to \infty$.
-Note that the difference between the CEO setting and ours lays in the privilege of each of the encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realizations, rather than a single realization using a single bit in ours.
- \par
-When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k$ goes to infinity were fully characterized in \cite{prabhakaran2004rate}.
-Furthermore, the work of \cite{chen2004upper} provided an expression for quadratic risk attained in the CEO setting under Gaussian priors.
-Adapting to our setting, this expression provides the following proposition:
-\begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is arbitrary.
-Then any estimator ${\theta}_n$ of $\theta$ in the distributed setting satisfies
-\begin{equation} \label{eq:ceo_bound}
- n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
-\end{equation}
-where the expectation is with respect to $\theta$ and $X^n$.
-\end{prop}
-
-\begin{proof}
-See Appendix~\ref{app:proof:prop_ceo_lower_bound}.
-\end{proof}
-
-From the formulation of the CEO problem, it follows that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is attributed to the ability to perform coding over blocks.
-Namely, each encoder in the CEO setting may encode an arbitrary number of $k$ independent realizations of $\theta$ using $k$ bits, versus only one realization with one bit in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product probability space that distinguishes between the CEO problem with one bit per encoder on average and the mean estimation problem from one-bit measurements in the distributed setting.
-
-\section{Adaptive Estimation \label{sec:sequential}}
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $\eta(0)\sigma^2$, which is the ARE of the median of the sample $X_1,\ldots,X_n$.
-We also provide a particular adaptive estimation scheme that attains this maximal efficiency.
-%Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $B_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages.
-%Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $\eta(0)\sigma^2$.
-
-\subsection{Limited efficiency in the adaptive setting}
-Our first result asserts that the ARE of any adaptive encoding and estimation scheme is bounded from above by $\eta(0)\sigma^2$. %This result follows from the following theorem:
-\begin{thm}[maximal relative effeciency] \label{thm:adpative_lower_bound}
-Let ${\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Figure~\ref{fig:setup}-(ii). Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-n\mathbb E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0},
-\]
-where 
-\[
-I_0 = \mathbb E \left( \frac{d}{d\theta} \log \pi (\theta) \right)^2
-\]
-is the Fisher information with respect to a location model in $\theta$. 
-\end{thm}
-
-\subsubsection*{Proof}
-%We first bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
-The result then follows using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are in
-See Appendix~\ref{proof:thm:adpative_lower_bound}.\par
-
-Theorem~\ref{thm:adpative_lower_bound} implies that any estimator ${\theta}_n$ from any adaptive encoding scheme satisfies
-\[
-n\mathbb E\left[ (\theta-\theta_n)^2 \right] \leq  \frac{1}{4f^2(0)}+O(n^{-1}),
-\]
-and 
-\[
-\ARE({\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
-\]
-
-Next, we present an adaptive encoding and estimation scheme that attains the maximal ARE of $\eta(0)\sigma^2$.
-
-\subsection{Asymptotically optimal estimator}
-Let $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ be a strictly positive sequence. Consider the following estimator ${\theta}_n$ for $\theta$:  
-\begin{equation}
-\label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n B_n, \quad n = 1,2,\ldots,
-\end{equation}
-where 
-\begin{equation}
-B_n = B_n (X_n,\theta_{n-1}) =\sgn (X_n - \theta_{n-1}).
-\end{equation}
-Define the $n$th step estimation as
-\begin{equation} \label{eq:sgd_est}
-\bar{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
-\end{equation}
-
-We have the following results:
-\begin{thm} \label{thm:sgd}
-Consider the sequence $\left\{\bar{\theta}_n \right\}_{n\in \mathbb N}$ defined by \eqref{eq:sgd_est}. 
-\begin{enumerate}
-\item[(i)] Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions1}
-\begin{cases}
-\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
-\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
-\mathrm{for~some~}0< \lambda \leq 1
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Then
-\[
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left(0,\frac{1}{\eta(0)}\right).
-\]
-%
-%
-\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with a finite location Fisher information, namely
-\[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)}  \right)^2 f(x) dx < \infty.
-\]
-%(or that $f(x-\theta)$ is differentiable in quadratic mean).  
-Then for any bounded, symmetric, and quasi-convex function $L$, 
-\begin{align} 
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
-\\
-& \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
-\end{align}
-where $Z \sim \Ncal(0,1)$. 
-%
-%
-\item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions2}
-\begin{cases}
-\gamma_n = o(n^{-2/3}), &  \\
-\sum_{n=1}^\infty \gamma_n = \infty.  & \\
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ with $\beta \in (2/3,1)$). Then
-\[
- \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{n\eta(0)} + o(n^{-1}). 
-\]
-\end{enumerate}
-\end{thm}
-
-\subsubsection*{Proof}
-See Appendix~\ref{proof:thm:sgd}. \par
-
-Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the maximal ARE, as established by Theorem~\ref{thm:adpative_lower_bound}.
-%Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$.
-%
-The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$.
-Consequently, the procedure above is known as averaged stochastic gradient descent for minimizing $x \to |x|$ given the data $X_1,\ldots,X_n$.
-The minimal value of this optimization is the sample median, and Theorem~\ref{thm:sgd} provides conditions for the sequence of gradient steps so that the algorithm converges to this minimum.
-In particular, parts (i) and (ii) of Theorem~\ref{thm:sgd} provides conditions under which $\bar{\theta}$ is asymptotically normal and local asymptotically minimax, in the sense that it attains the local asymptotic minimax bound \cite{van2000asymptotic}.
-Part (iii) provides an additional condition under which $\bar{\theta}$ also converges in its second moment.
- \par
-%Note that $\theta_0$ is not explicitly defined in equation \eqref{eq:sgd_est}.
-A reasonable initialization for $\theta_0$ is $\theta_0 = \mathbb E [\theta]$, although Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
-Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$.
-\\
-In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $B_n$ depends on its private sample as well as the current gradient descent estimate $\theta_{n-1}$.
-In this sense, each encoder in this algorithm interacts with previous one by using the current estimate.
-%
-As we explain next, 
-it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ with only one round of interactions among the encoders.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
-% \node[below of = source, node distance = 1cm] (source2) {$X_2$};
-%\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};  
-%\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};
-
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[below of = source, node distance = 0.5cm] {$\vdots$};
-
-\node[int1, right of = enc3, node distance = 2.1cm ] (est) {$\est_1$};
-
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
-
-%\draw[->,line width = 2pt] (enc2) -| node[above, xshift = -1cm] (mes2) {$B_2$} (est);
-
-\draw[->,line width = 2pt] (enc3) -- node[above, xshift = 0cm]  {$B_{n_1}$} (est);
-
-\node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
-\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {$\enc$};  
-\draw[->,line width = 2pt] (sourceB) -- (enc1B);
-
-\node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
-\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {$\enc$};  
-\draw[->,line width = 2pt] (source3B) -- (enc3B); 
-\node[below of = sourceB, node distance = 0.4cm] {$\vdots$};
-
-\node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {$\est_2$};
-
-\draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.5cm] {$B_{n_1+1}$} (estB);
-\draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);
-
-\draw[->,line width = 1pt] (est.east) node[above, xshift  =0.5cm] {${\theta}_{n_1}$} -| (enc1B.north);
-
-%\draw[->,line width = 1pt] (enc1B) -- (enc3B);
-
-\draw[->,line width = 0.5pt] (est.east) -| +(1.3,-0.5) -- +(1.3,-2.5) -| (enc3B.north);
-
-%\draw[->,line width = 1pt] (enc1B)  -- node[right] {${\theta}_{n_1}$} (enc3B);
-
-\draw[->,line width = 0.5pt] (estB) -- +(0.8,0) node[right] {${\theta}_n$};
-\node[below of = enc1B, node distance = 0.5cm] {$\vdots$};
-
-\end{tikzpicture}
-\end{center}
-\caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
-\label{fig:one_round}
-}
-\end{figure}
-
-\subsection{Maximal Efficiency using One Round of Threshold Adaptation}
-In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
-\[
-B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
-\]
-and deduced that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
-%
-We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ based on previously observed bits at least once.
-%
-In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
-We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate ${\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use ${\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$.
-Figure~\ref{fig:one_round} illustrates a diagram of this procedure.
-%
-The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
-\begin{thm}
-For $i=1,\ldots,n$ set
-\[
-B_i = \begin{cases}
- \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
- \mathbf 1_{X_i \geq {\theta}_{n_1} }& i={n_1+1,\ldots,n},
-\end{cases}
-\]
-where $n = n_1+ n_2$ and 
-\[
-{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
-\frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
- \right).
-\] 
-Let 
-\[
-{\theta}_{n_2}  = {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
-\]
-and assume that $n_1(n) \rightarrow \infty$ and $n_1(n)/n \rightarrow 0$. Then:
-\begin{align*}
- \sqrt{n} \left( {\theta}_{n_2} - \theta  \right) \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
-\end{align*}
-\end{thm}
-%
-%
-\begin{proof}
-For $t\in \mathbb R$, set
-\[
-p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
-\]
-From the central limit theorem
-\begin{align*}
-& \sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)  = \sqrt{\frac{n}{n_2}} \sqrt{n_2} \left(  p_{n_2}(t) - F(\theta - t) \right) \\
-& \overset{d}{\rightarrow} \Ncal\left( 0, V(t) \right),
-\end{align*}
-where
-\[
-V(t) \triangleq F(\theta - t) F \left( t - \theta\right). 
-\]
-Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ implies
-\begin{align*}
-& \sqrt{n} \left( t + F^{-1}(\hat{p}_{n_2}(t)) - \theta \right) \\
-&= \sqrt{n} \left( g(\hat{p}_{n_2}(t)) - g \left(F(\theta-t) \right)  \right) \\
-& \overset{d}{\to} \Ncal\left(0, 
-1/\eta(\theta-t) \right).
-\end{align*}
-%where this convergence is uniform in $t$ since all moments of $F^{-1}(\hat{p}_{n_2})$ exists. 
-On the other hand, by the law of large numbers,
-\[
-p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
-\]
-so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity and thus 
-\[
-\eta( {\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
-\]
-Finally,
-\begin{align*}
-& \sqrt{n}\left({\theta}_{n_2} - \theta\right) \\
-& = \sqrt{n} \left( {\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}({\theta}_{n_1})) - \theta \right)  \\
-& \overset{d}{\to} \Ncal\left( 0, 
-1/\eta(0) \right) 
-\end{align*}
-by Slutsky's theorem.
-\end{proof}
-%
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=10cm, height=6cm,
-xmin = 0, xmax=800, 
-restrict y to domain = 0:3,
-ymin = 0,
-ymax = 3.4,
-samples=10, 
-xlabel= $n$,
-ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
-%xtick={-3,-2,-1,0,1,2,3},
-%xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,1,1.57},
-yticklabels={0,1,$\pi/2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-
-\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{asymptotically optimal};
-
-%\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
-
-\addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{single interaction};
-
-\end{axis}
-\end{tikzpicture}
-%\begin{tikzpicture}
-%\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
-%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left({\theta}_n - \theta \right)^2$};
-%\node[scale = 0.7] at (0,-2.4) {$n$};
-%\end{tikzpicture}
-\caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.
-In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$.
-The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage.
-\label{fig:adaptive_error}  }
-\end{center}
-\end{figure}
-
-\section{Distributed Estimation \label{sec:distributed}}
-In this section, we now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii) where  each one-bit message $B_i$ is only a function of its private sample $X_i$.
-In this case, the $i$th encoder is fully characterized its \emph{detection region}, defined as
-\[
-A_i = \left\{ x \in \mathbb R \,:\, B_i(x) = 1 \right\}.
-\]
-Consequently, $B_i$ is of the form
-\[
-B_i = \begin{cases} 1 & X_i \in A_i, \\
--1 & X_i \notin A_i,
-\end{cases} \quad i\in \mathbb N,
-\]
-where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\par
-
-As a first step, we provide conditions under which the messages $B_1,B_2,\ldots$ define a local asymptotic normal family.
-
-\begin{thm} \label{thm:LAN1}
-For $n \in \mathbb N$ and $A_n \subset \mathbb R$,  define
-\begin{equation}
-\label{eq:precision_general}
-L_n(A_1,\ldots,A_n;\theta) \triangleq \frac{1}{n} \sum_{i=1}^n \frac{ \left(\frac{d}{d \theta} \Prob(X_i \in A_i) \right)^2 }{ \Prob(X_i \in A_i)\left(1- \Prob(X_i \in A_i) \right) }. 
-\end{equation}
-Consider the following conditions:
-\begin{itemize}
-\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is a log-concave, differentiable and symmetric density function such that $\eta(x)$ is unimodal.
-\item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
-\item[(iii)] The limit 
-\begin{equation}
-\label{eq:LAN_lim}
-\kappa(\theta) \triangleq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
-\end{equation}
-exists. 
-\end{itemize}
-For $i=1,\ldots,n$ set
-\[
-B_n = \begin{cases} 1 & X_n \in A_n, \\
--1 & X_n \notin A_n. 
-\end{cases} 
-\]
-For any $\theta$, $f(x)$ and a sequence of sets $A_1,A_2,\ldots$ such that (i)-(iii) hold, and any $h\in \mathbb R$, we have
-\begin{align*}
-& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (B_1,\ldots,B_n) }{
-\mathbb P_{\theta} (B_1,\ldots,B_n)} \\
-& \overset{d}{\longrightarrow} \Ncal\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
-\end{align*} 
-\end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:LAN1}. 
-\end{proof}
-
-Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}. 
-%
-Among these conditions, (iii) is arguably the strongest and hardest to verify.
-As we show in Section~\ref{subsec:threshold} below, this condition is satisfied, for example, when $A_1, \ldots,A_n$ are half lines whose starting points are drawn independently from some probability measure on $\mathbb R$.
-Similar ideas imply that condition (iii) holds whenever we choose the intervals consisting each $A_i$ according to some pre-specified distribution.
-\par
-%
-An important conclusion of  Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models \cite{van2000asymptotic}):
-\begin{cor} \label{cor:LA_minimax}
-Let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
-Then for any symmetric and quasi-convex function $L$,
-\begin{align*}
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right]
-\\
-& \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
-\end{align*}
-where $Z \sim \Ncal(0,1)$. In particular, for $L(x) = x^2$,
-\begin{align*}
-\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( {\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
-\end{align*}
-\end{cor}
-%
-Corollary~\ref{cor:LA_minimax} says that when the messages define a LAN model, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model at $\theta$.
-This fact poses the upper bound of $\kappa(\theta)\sigma^2$ for the ARE of estimators in such models.
-\par
-
-Next, we show that under LAN no estimator can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly for all $\theta \in \Theta$.
-
-\subsection{Non-existence of a Uniformly Optimal Strategy}
-We now show that under LAN models, the optimal minimal risk $1/\eta(0)$ can only be attained at a finite number of points within $\Theta$.
-This fact implies in particular that, unlike in the adaptive setting, no distributed estimation scheme has ARE of $\eta(0)\sigma^2$ for all $\theta \in \Theta$.
-
-\begin{thm} \label{thm:non_existence}
-Under conditions (i)-(iii) in Theorem~\ref{thm:LAN1}, assume that each $A_i$ is a union of at most $K$ intervals.
-The number of points $\theta \in \Theta$ satisfying $\kappa(\theta) = \eta(0)$ is at most $2K$.
-\end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:non_existence}.
-\end{proof}
-
-We next consider the case where each detection region is a half-open interval, i.e., the $i$th message is obtained by comparing $X_i$ against a single threshold.
-As we explain next, the existence of a density for the sequence of thresholds is enough to establish local asymptotic normality and leads to a closed form expression for the precision parameter and the ARE.
-
-%In the adaptive setting, it follows from Theorem~\ref{thm:sgd} that messages of this kind with appropriately chosen thresholds lead to an estimator with the optimal ARE of $\eta(0)sigma^2$.
-However, Theorem~\ref{thm:non_existence} implies that such ARE can only be attained for a negligible subset of the parameter space.
-As we shall see next, messages obtained via a comparison against a sequence of thresholds cannot attain the optimal efficiency one more than a single point of $\Theta$.
-
-\subsection{Threshold Detection \label{subsec:threshold}}
-Assume now that each $B_i$ is of the form
-\begin{equation}
-\label{eq:threshold_message}
-B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
--1 & X_i > t_i,
-\end{cases}  
-\end{equation}
-where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder.
-In other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and $\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$.
-It follows that
-\begin{equation}
-L_n(A_1,\ldots,A_n;\theta) = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
-\label{eq:Ln_threshold}
-\end{equation}
-A natural condition for the existence of the limit \eqref{eq:Ln_threshold} as $n\to \infty$ is that the empirical distribution of the threshold values converges to a probability measure.
-Specifically, for an interval $I \subset \mathbb R$ define
-\[
-\lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
-\]
-Theorem~\ref{thm:LAN1} implies:
-\begin{cor} \label{cor:LAN_thresh}
-Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$.
-Then $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a LAN family with precision parameter
-\[
-\kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
-\]
-\end{cor}
-The condition that $\lambda_n$ converges to a probability measure is satisfies, for example, whenever the $t_1,\ldots,t_n$s are drawn independently from a probability distribution $\lambda(dt)$ on $\mathbb R$.
-\par
-Due to local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by 
-${\theta}^{ML}_n$, is local asymptotic minimax in the sense that 
-\[
-\sqrt{n} \left( {\theta}^{ML}_n - \theta \right) \overset{d}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
-\]
-It follows that when the density of the threshold values converges to a probability measure, the ARE of the ML estimator is $\kappa(\theta)\sigma^2$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-We note that ${\theta}^{ML}_n$ is given by the root of
-\begin{equation}
-\label{eq:ML}
-\sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) },  
-\end{equation}
-which is the derivative of the log-likelihood function.
-This root is unique since the log-likelihood function is concave.
-Furthermore, for any $n \in \mathbb R$, we have that ${\theta}^{ML}_n  \in [t_{(1)}, t_{(n)}]$ where $t_{(i)}$ denotes the $i$th element of $\{t_1,t_2\ldots\}$.
-Therefore, if $\{t_1,t_2\ldots\}$ is bounded (for example $\{t_1,t_2\ldots\} \subset \Theta$), then
-\[
-\lim_{n\to \infty} n \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
-\] 
-so that the ML estimator attains the local asymptotic MSE of Corollary~\ref{cor:LA_minimax}. \par
-%
-Since $\eta(x)$ attains its maximum at the origin, we conclude that
-\[
-\kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
-\]
-This upper bound on $\kappa(\theta)$ implies that the ARE of any distributed estimator based on a sequence of threshold detectors does not exceed $\eta(0)\sigma^2$, a fact that agrees with the lower bound under adaptive estimation derived in Theorem~\ref{thm:adpative_lower_bound}.
-%
-This upper bound on $\kappa(\theta)$ is attained only when $\lambda$ is the mass distribution at $\theta$.
-Since $\theta$ is apriori unknown, we conclude that estimation in the distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting.
-In other words, the ability to choose the threshold values in an adaptive manner based on previous messages strictly improves relative efficiency compared to a non-adaptive threshold selection.
-\par
-
-%We conclude that when the density of the threshold values converges to a probability measure, the ARE of the ML is $\kappa(\theta)$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-
-%
-We conclude this section by considering the density of the threshold values that maximizes the ARE $\kappa(\theta)$ under the worst choice of $\theta \in \Theta$.
-
-\subsection{Minimax Threshold Density}
-The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta = [-T,T]$ is given as the solution to the following optimization problem:
-\begin{align}
-\label{eq:var_cvx_minimax}
-\begin{split}
-\mathrm{maximize} \quad &  \inf_{\theta \in [-T,T]} \int \eta(t-\theta) \lambda(dt)
-\\ 
-\mathrm{subject~to} 
-\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
-\end{split}
-\end{align}
-The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program.
-We denote by $\kappa^\star(T)$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum.
-%
-%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
-%\begin{align}
-%\label{eq:cvx_minimax}
-%\begin{split}
-%\mathrm{maximize} \quad &  K \\ 
-%\mathrm{subject~to} 
-%\quad &  K \leq \mathbf H\lambda \\
-%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
-%\end{split}
-%\end{align}
-%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
-%\begin{rem}
-%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$.
-Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points.
-Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using
-%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
-%\end{rem}
-
-Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$.
-The minimal asymptotic risk $\kappa^\star(\theta)$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $T$.
-Also illustrated in these Figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
-\begin{align}
-& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
- \\
-& = 
-\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
-= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
-\end{align}
-From Corollary~\ref{cor:LAN_thresh}, we conclude that the ARE under a uniform distribution is $\kappa_\unif \sigma^2$. \par
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-title = {$\sigma/T = 1/2$},
-ytick={0,0.1,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.6,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/T = 1/5$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.5},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.5},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.3,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma / T = 1/10$},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.2},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.2},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.15,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma / T = 1/20$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:minimax_support}
-Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in \Theta = [-T,T]$.
-%
-The continuous curve (red) represents the reciprocal of the asymptotic risk for at a fixed $\theta \in \Theta$ under the optimal density, so the minimax risk is the inverse of its minimal value.
-The dashed curve (green) is the reciprocal of the asymptotic risk for a fixed $\theta$ under a uniform distribution of threshold values over $\Theta$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
-}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmax=2.5, 
-xmode = log,
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=1, 
-xlabel= {$\sigma/T$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,0.637,1},
-yticklabels={0,$2/\pi$,1},
-ylabel = {$\ARE$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{optimal threshold density};
-
-\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{uniform threshold desnity};
-\end{axis}
-\end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \Ncal(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
-The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
-}.
-\end{center}
-\end{figure}
-
-%We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
-Next, we prove that with any set of messages obtained via a distributed strategy, there exists at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-title = {$\sigma/\sigma_{\theta} = 1$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 2$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma/\sigma_{\theta} = 3$},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 4$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:opt_density}
-Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=b^2/3$ is the variance of the prior.
-}
-\end{center}
-\end{figure}
-
- We consider now the problem of minimizing the asymptotic Bayes risk $
-R_{\pi,\lambda} \triangleq \mathbb E  K^{-1}(\theta)$ over all probability measures $\lambda(dt)$ with support in $\mathbb R$. This optimization problem can be written as follows:
-\begin{align}
-\label{eq:cvx_average}
-\begin{split}
-\mathrm{minimize} \quad & R_{\pi,\lambda} =  \int \frac{\pi(d\theta)}{ \int \eta \left( t-\theta\right) \lambda(dt)}. \\ 
-\mathrm{subject~to} \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) =1. 
-\end{split}
-\end{align}
-We denote by $R^\star_{\pi}$ the minimal value of the objective function in \eqref{eq:cvx_average}.
-Since the function $x \rightarrow 1/x$ is convex for positive values, \eqref{eq:cvx_average} defines a convex optimization problem in $\lambda$ whose solution depends on the prior $\pi$.
-The solution to this problem is approximated by considering $\lambda$ and $\pi$ over a discrete set.
-On Figure~\ref{fig:opt_density} we illustrate the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distributon ($P_X = \Ncal(\theta, \sigma^2)$) and the prior on $\theta$ is uniform over $\Theta = [-b,b]$.
-Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
-\par
-\begin{figure}
-\begin{center}
-
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = 0, xmax=2, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 10,
-samples=1, 
-xlabel= {$\sigma/\sigma_\theta$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,1.5708,5},
-yticklabels={0,$\pi/2$,5},
-ylabel = {$R_{\pi}^\star/\sigma^2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-\addplot[color = black, dashed] {3.14159 / 2};
-\end{axis}
-\end{tikzpicture}
-\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \Ncal(\theta, \sigma^2)$ under an optimal threshold distribution $\lambda^\star$, when the prior $\pi$ is the uniform distribution over $\Theta = [-0.5,0.5]$.
-%
-%versus $\sigma/\sigma_\theta = 2\sqrt{3}\sigma$.
-The distribution $\lambda^\star$ is the minimizer of \eqref{eq:cvx_average}.
-It is illustrated for various cases in Fig.~\ref{fig:opt_density}.
-The dashed curve represents the upper bound \eqref{eq:upper_bound}.
-\label{fig:dist_bound_uniform}  }
-\end{center}
-\end{figure}
-
-As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \Ncal(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution.
-In this case, the ML estimator reduces to the estimator ${\theta}_n$ of \eqref{eq:estimator_naive}.
-As the following proposition shows, the Bayes risk for this choice of $\lambda$ is maximal, and thus provides an upper bound on the Bayes risk under any $\lambda$.
- \eqref{eq:cvx_average}. 
-\begin{prop}\label{prop:upper_bound}
-For any prior $\pi(d\theta)$ and $\theta_0$ in the support of $\eta(x)$ we have
-\begin{equation} 
-\label{eq:upper_bound}
-R_\pi^\star  \leq 
- \int \frac{\pi(d\theta)}{\eta \left( \theta_0 - \theta \right)},
-\end{equation}
-Furthermore, assuming that $\theta_0 = \mathbb E \theta$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
-\begin{equation}
-\label{eq:bound_Taylor}
-R^\star_\pi \leq \frac{1}{4 f^2(0)} + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right) \sigma_\theta^2 + O(\sigma_\theta^3).
-\end{equation}
-\end{prop}
-\begin{proof}
-The function $x \rightarrow 1/x$ is convex for positive values, hence Jensen's inequality implies
-\[
-\left( \int \eta \left( t-\theta\right) \lambda(dt) \right)^{-1}  \leq \int  \frac{ \lambda(dt)}{ \eta \left( t-\theta\right)  }. 
-\]
-Therefore, the expected value of $\kappa^{-1}(\theta)$ satisfies
-\begin{align}
-\ex{  \frac{1}{\kappa(\theta)}}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
-\end{align}
-The bound \eqref{eq:upper_bound} is obtained by taking $\lambda$ to be a mass distribution at any $\theta_0$ in the support of $\eta(x)$.
-Finally, \eqref{eq:bound_Taylor} is obtained by expanding $1/\eta(x)$ to a third order Taylor series around zero
-%\[
-%1/\eta(x) = \frac{1}{4f^2(0)}  + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right)  x^2 + O(x^3),
-%\]
-and taking its expectation with respect to $\pi$ at $x=\theta_0-\theta$. 
-\end{proof}
-We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so the choice $\theta_0 = \ex{ \theta}$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
-The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$.
-The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $\kappa^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.
-
-\begin{example} \label{ex:bound}
-In the normal case $P_X = \Ncal(\theta, \sigma^2)$, the bound in \eqref{eq:bound_Taylor} implies 
-\[
-\frac{R^\star_\pi}{\sigma^2}  \leq \frac{\pi}{2} + \left( \frac{\pi}{2} -1 \right) \left( \frac{ \sigma_\theta}{\sigma} \right)^2 + O \left(  \frac{\sigma_\theta} { \sigma} \right)^3. 
-\]
-It follows that the ARE approaches its maximal value of $2/\pi$ whenever $\sigma_\theta/\sigma$ is small.
-The exact value of \eqref{eq:upper_bound} in this case, as well as the Bayes ARE with the optimal threshold density $\lambda^\star$ for a uniform $\pi$, are illustrated in Fig.~\ref{fig:dist_bound_uniform}.
-%i.e., each encoder simply reports "$1$" or "$-1$" whenever $X_i$ is larger or smaller than $\theta_0$, respectively.
-Intuitively, an accurate estimation of $\theta$ in this case is possible only if a sufficient mix of ''$1$''s and ''$-1$''s is obtained from the sample.
-When $\sigma_\theta^2$ is high compared to $\simga^2$, one of the events $"1"$ or "$-1"$ becomes too rare to
-\end{example}
-
-\section{Conclusions \label{sec:conclusions}}
-We considered the MSE risk in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
-%
-In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency (ARE) larger than that of the median of the samples.
-We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median.
-%We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
-\par
-In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and ARE. 
-%
-We conclude that under such conditions, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in the distributed setting.
-%
-We further considered the special case of messages obtained by comparing against a prescribed sequence of thresholds.
-We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.
-
-%\section*{ACKNOWLEDGMENT}
-%This research is supported in parts by...
-%Tsachy Weissman, Stefano Rini, Robert Gray.
-
-\onecolumn
-
-\appendix
-
-\section{}
-
-\subsection{Proof of Proposition~\ref{prop:ceo_lower_bound}
-\label{app:proof:prop_ceo_lower_bound}}
-
-First, we note that when $f(x) = \Ncal(0,\sigma^2)$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$, our distributed setting reduces to the Gaussian CEO problem with $R_1=\ldots = R_n =1$ and $k=1$.
-Therefore, any MSE attained in our distributed setting is also attained by the CEO and thus the optimal CEO strategy (with arbitrary $k$) provides a lower bound to the MSE in our setting.
-\\
-
-Consider the minimal MSE $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
-from \cite[Eq. 10]{chen2004upper}:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-For the special case of $R_\Sigma = n$ and $L=n$, we get
-\begin{equation} \label{eq:ceo_optimal_sumrate2}
-n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, this $D^\star$ provides a lower bound to the CEO MSE with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
-\[
-D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO MSE while enforcing the condition $R_1=\ldots = R_n = 1$.
-Indeed, an upper bound for the CEO MSE under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
-\[
-D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
-\]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.
-
-\subsection{Proof of Lemma~\ref{lem:bound_intervals_delta} \label{proof:lem:bound_intervals_delta}}
-
-%\begin{lem} \label{lem:bound_intervals}
-%Let $f(x)$ be a log-concave, symmetric, and differentiable density such that $\eta(x)$ is strongly unimodal. For any $x_1 > \ldots > x_n \in \mathbb R$, 
-%\begin{equation}
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \max_i \eta(x_i). \label{eq:lem_bound_intervals}
-%\end{equation}
-%In particular, if $|x_i|>\epsilon > 0$ for all $i=1,\ldots,n$, then 
-%\[
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \eta(\epsilon) < 0. 
-%\]
-%\end{lem}
-
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-so 
-\[
-\eta(x) =  \frac{  \left(\delta_1(x) \right)^2}{\Delta_1(x)
-(1-\Delta_1(x))}
-= \frac{  \left( f (x) \right)^2}{ F(x)\left(1-F(x)\right)^2}. 
-\]
-We use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:lem_bound_intervals_delta} is bounded from above by $\max_i \eta(x_i)$. The case $n=1$ is trivial. Assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^2} 
-{\Delta_n \left(1- \Delta_n \right) } \leq \max_i \eta(x_i)
-\label{eq:lem_bound_intervals_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  2 \log \delta_N -  \log \Delta_N -  \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(-1)^{k+1} f(x_k)}{1-\Delta_N },
-\]
-and we conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-%
-Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable. We have 
-\[
-\frac{f'(x)}{f(x)} = c'(x), \quad x\in \mathbb R,
-\]
-which is anti-symmetric, non-negative for $x<0$,  non-positive for $x>0$, and non-increasing since $c(x)$ is concave.
-Therefore, if $c'(x_i) = c'(x_{i+1})$ for some $i =1,\ldots,N-1$, then either (1) $x_i = x_{i+1}$ or (2) $c'(x)$ is the zero function.
-Since (2) violates the assumption that $f(x)$ is a density function, we conclude that $c'(x)$ is an injection.
-%
-As a result, \eqref{eq:gradient_zero} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_proof} equals $\eta(x_1) = \max_i \eta(x_i)$ hence the statement holds.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$, or  $x_i, x_{i+1}$ for some $i$.
-It is left to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Under case (1) we have
-\begin{align*}
-\lim_{x_N \to -\infty} \frac{  \delta_N^2} 
-{\Delta_N \left(1- \Delta_N \right) }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^2} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)} ,
-\end{align*}
-which is smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis. Under case (2) we have
-\begin{align*}
-&  \lim_{x_1 \to \infty}
-\frac{ \delta_N} 
-{\Delta_N\left(1- \Delta_N \right) } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right) \left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right) }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^2 } 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right) },
-\end{align*}
-where $x'_{m} = x_{m+1}$. The last expression is also smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis.  \QEDA \\
-
-\subsection{Proof of Theorem~\ref{thm:adpative_lower_bound}
-\label{proof:thm:adpative_lower_bound}
-}
-
-We first prove the following lemma:
-\begin{lem} \label{lem:fisher_bound}
-Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that $\eta(x)$ is unimodal. For a Borel measurable $A$ set, 
-\[
-M(X) = \begin{cases} 1,& X \in A, \\
--1, & X \notin A.
-\end{cases}
-\]
-Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $\eta(0)$.
-\end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
-When $f(x)$ is the normal density function, this lemma follows from \cite[Thm.
-3]{Barnes2018}.
-The proof below is based on a different techique than in \cite{Barnes2018}, and is valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}.
-\\
-
-The Fisher information of $M$ with respect to $\theta$ is given by
-\begin{align}
-I_\theta & =  \mathbb E \left[ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta \right] \nonumber \\
-& = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
-& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\
-& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\ 
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
-\end{align}
-where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$.
-Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
-\[
-\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
-\]
-which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$.
-It is therefore enough to proceed in the proof assuming that $A$ is of the form
-\[
-A = \cup_{j=1}^k (a_j,b_j),
-\]
-with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
-\begin{align*}
-\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
-& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
-\end{align*}
-so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
-\begin{align}
-& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
-{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
-& \times \frac {1} 
-{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
-\label{eq:lemma_J}
-\end{align}
-It follows from Lemma~\ref{lem:bound_intervals_delta} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $4f^2(0)$.  \QEDA \\
-
-We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
-\begin{equation}
-\label{eq:general_messages}
-B_i = \begin{cases}
-X_i \in A_i & 1, \\
-X_i \notin A_i & -1,
-\end{cases} 
-\end{equation}
-where $A_i \subset \mathbb R$ is a Borel measurable set. 
-%Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
-Consider the conditional distribution $P({B^n|\theta})$ of $B^n$ given $\theta$. We have 
-\begin{align}
-P\left( B^n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
-\end{align}
-where $P\left(B_i =1 | \theta, B^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B^n$ with respect to $\theta$ is given by 
-\begin{align}
-I_\theta(B^n) = \sum_{i=1}^n I_\theta (B_i|B^{i-1}),
-\label{eq:fisher_information}
-\end{align}
-where $I_\theta (B_i|B^{i-1})$ is the Fisher information of the distribution of $B_i$ given $B^{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B^{i-1}) \leq 4f^2(0)$.
-The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
-\begin{align*}
-\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(B^n) + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
-& \geq \frac{1}{ 4f^2(0) n + I_0}.
-\end{align*}
-
-\QEDA
-
-\subsection{Proof of Theorem~\ref{thm:sgd}
-\label{proof:thm:sgd}
-}
-The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.
-
-\subsubsection*{Proof of (i)}
-%Specifically, (i) in Theorem~\ref{thm:sgd} 
-Consider the following simplified version of \cite[Thm. 4]{polyak1992acceleration}:
-\begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
-Let 
-\[
-X_i = \theta + Z_i,\quad i=1,\ldots,n,
-\]
-where the $Z_i$s are i.i.d. with zero means and finite variances. Define
-\begin{align}
-\begin{split}
-\theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
-\bar{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
-\end{split}
-\label{eq:Polyak_Juditsky_alg}
-\end{align}
-where in addition, assume the following: 
-\begin{enumerate}
-\item[(i)] There exits $K_1$ such that $\left| \varphi(x) \right| \leq K_1(1+|x|)$ for all $x\in \mathbb R$.
-\item[(ii)] The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions \eqref{eq:conditions1}.
-\item[(iii)] The function $\psi(x) \triangleq \ex{ \varphi(x+Z_1)}$ is differentiable at zero with $\psi'(0)>0$, and satisfies $\psi(0)=0$ and $x\psi(x) >0$ for all $x\neq 0$.
-Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
-\begin{equation}
-\label{eq:Polyak_Juditsky_cond3}
-\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
-\end{equation}
-\item[(iv)] The function 
-$\chi(x) \triangleq \ex{\varphi^2(x+Z_1)}$ is continuous at zero. 
-\end{enumerate}
-Then $\bar{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}({\theta}_n - \theta)$ converges in distribution to $\Ncal(0,V)$, where
-\[
-V = \frac{ \chi(0)} {\psi'^2(0)}. 
-\]
-\end{thm}
-
-Using the notation above, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have that $\chi(x) = \mathbb E \sgn^2(x+Z_1) = 1$, so $\chi(0) = 1$. In addition,
-\begin{align*}
-\psi(x) & = \ex{ \sgn(x+ Z_1) }= \int_{-\infty}^\infty \sgn(x+z) f(z) dz \\
-& = \int_{-x}^\infty f(z) dz -\int_{-\infty}^{-x} f(z) dz. 
-\end{align*}
-Using the symmetry of $f(x)$ around zero, it follows that $\psi'(x) = 2f(x)$ and thus $\psi'(0) = 2f(0)$.
-It is now easy to verify that the rest of the conditions in Theorem~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$.
-Since
-\[
-\frac{\chi(0)}{\psi'^2(0)} = \frac{1}{4 f^2(0)} = \frac{1}{\eta(0)},
-\]
-it follows from Theorem~\ref{thm:polyak_juditsky} that
-\[
-\sqrt{n}\left({\theta}_n-\theta \right) \overset{d}{\to} \Ncal \left(0, 1/ \eta(0)\right). 
-\]
-
-\subsubsection*{Proof of (ii)}
-We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\mathbb R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates.
-Then
-\begin{align}
-\label{eq:sgd_part2}
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
-\end{align}
-under $\Prob_{\theta,n}$.
-Under the assumption that $f(x)$ is continuously differentiable with a finite location Fisher information, the model $\{Z_n+ \theta\}_{n \in \mathbb N}$ is differentiable in quadratic mean \cite[Exm.
-7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
-\[
-\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
-\]
-where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$. 
- The random variable $L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)
-$ is bounded, and hence 
-\[
-\ex{ L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)} \to \ex{L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)}
-\]
-Any regular estimators in a LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}, hence in order to prove (ii) it is left to show that $\bar{\theta}_n$ is regular. For this purpose, 
-we use the following refinement of Theorem~\ref{thm:polyak_juditsky}, proof of which is given in Subsection~\ref{proof:thm:normal_expansion} below.
-%
-\begin{thm} \label{thm:normal_expansion}
-Set $\Delta_i = \theta_i - \theta$ and
-$\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \Delta_i$. Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{thm:polyak_juditsky}, there exists $K_1$ and $\lambda>0$ such that
-\begin{equation}
-\ex{\left| \varphi(Z_1) - \varphi(x+Z_1)  \right|} \leq K_1 |x|^{1+\lambda}
-\label{eq:PJ_additional_cond}. 
-\end{equation}
-Then:
-\begin{itemize}
-\item[(i)] \begin{equation}
-\sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1). \label{eq:normal_expansion_lem}
-\end{equation}
-where $o_{p,n}(1)$ converges in probability to $0$ as $n\to \infty$.
-\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite location Fisher information 
-\[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)} \right)^2 f(x) dx,
-\]
-then for any converging sequence $h_n \to h$,
-\[
-\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-h}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
-\]
-under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h_n/\sqrt{n}}$ with density $\prod_{i=1}^n f(x_i-h_n/\sqrt{n})$.
-\end{itemize}
-\end{thm}
-We now use this theorem to show regularity of $\bar{\theta}_n$. We have, 
-\begin{align*}
-& %\varphi(Z_1) - \varphi(x+Z_1) = 
-\sgn(Z_1) - \sgn(x + Z_1) \\
-& = \begin{cases}
-2 & Z_1 > 0,\, x+Z_1<0, \\
--2 & Z_1 <0, \, x+Z_1>0, \\
-0 & \text{otherwise}. 
-\end{cases}
-\end{align*}
-It follows that
-\begin{align*}
-\ex{ \left| \varphi(Z_1) - \varphi(x+Z_1) \right| }  \leq \Prob\left( |Z_1| < x  \right) \leq f(0) |x|, 
-\end{align*}
-hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
-\[
-\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = -2f(0) = -\psi'(0). 
-\]
-Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}.
-
-\subsubsection*{Proof of (iii)}
-%In order to prove part (ii) of Theorem~\ref{thm:sgd} 
-Consider the following result from \cite{polyak1990new}:
-\begin{thm}{\cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
-Let
-\begin{align} \label{eq:polyak_new_measurements}
-\begin{cases}
-U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = g'(U_{n-1})+Z_n \\
-\bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
-\end{cases}
-\end{align}
-Assume that the function $g(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative.
-In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \mathbb R$.
-Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution with a density for which the Fisher information exits.
-Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{thm:polyak_juditsky}-(iii) and satisfy the conditions there.
-Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$,
-and there exits $K_3$ such that 
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] \leq K_3(1+|x|^4). 
-\]
-Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
-\[
-V_n \triangleq \mathbb E \left[ \left(\bar{U}_n-x^\star \right)^2 \right] = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
-\]
-\end{thm}
-
-We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$. From \eqref{eq:polyak_new_measurements} we have
-\begin{align*} 
-U_n & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
-& = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
-\end{align*}
-so the estimator $\bar{U}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] = 1 \leq K_3(1+|x|^4)
-\]
-for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
-the conditions in Theorem~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
-In particular, $\psi'(0) = (2f(0))^{-2}$.
-Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$.
-Theorem~\ref{thm:polyak_new} implies that for any $\theta \in \mathbb R$,
-\[
-V_n = \mathbb E \left[ \left({\theta}_n-\theta \right)^2 \right]  = \frac{1}{4n f^2(0)} + o(n^{-1}).
-\]
-
-{\color{red}
-
-\subsection{Proof of Theorem~\ref{thm:normal_expansion}
-\label{proof:thm:normal_expansion}
-}
-\subsubsection*{Proof of (i)}
-The proof of part (i) of Theorem~\ref{thm:normal_expansion} requires the following two additional results from \cite{polyak1992acceleration}:
-\begin{lem}{\cite[Lem. 2]{polyak1992acceleration}}
-\label{lem:Polyak_expansion}
-Consider the process $\{\Delta_i^1 \}_{i=0}^\infty$ defined by
-\[
-\Delta^1_i = \Delta^1_{i-1} - \gamma_i (A \Delta_{i-1}+ \xi_i),\quad i=1,2\ldots.
-\]
-Assume that $A>0$ and condition (ii) of Theorem~\ref{thm:polyak_juditsky} holds. Then 
-\begin{equation}
-\label{eq:Polyak_expansion}
-\sqrt{n} \bar{\Delta}_n^1 = \frac{1}{\sqrt{n}}\sum_{i=0}^{n-1} \Delta_i^1 = \frac{\alpha_n \Delta_0^1}{\sqrt{n} \gamma_0}  + \frac{1}{\sqrt{n} A} \sum_{i=1}^{n-1} \xi_i + \frac{1}{\sqrt{n}}\sum_{i=1}^{n-1} w_i^n \xi_i,
-\end{equation}
-where $\alpha_n$ and $w_i^n$ are real numbers such that $|\alpha_n| \leq K$ and $|w_i^n|\leq K$ for some $K< \infty$, and 
-\[
-\lim_{n\to \infty} \frac{1}{n} \sum_{i=1}^{n-1} |w_i^n| = 0. 
-\]
-\end{lem}
-
-\begin{lem} \label{lem:PJ_converging_sum}
-Under the conditions of Theorem~\ref{thm:polyak_juditsky},
-\[
-\sum_{i=1}^\infty \frac{|\Delta_{i}|^{1+\lambda}}{\sqrt{i}} < \infty 
-\]
-almost surely. 
-\end{lem}
-Lemma~\ref{lem:PJ_converging_sum} follows from the proof of Theorem 2 in \cite{polyak1992acceleration}.
-
-We separate the proof of part (i) into two steps.
-\subsubsection*{Step I}
-The expansion \eqref{eq:normal_expansion_lem} holds for the process  $\{\bar{\Delta}^1_i\}_{i=1}^\infty$ defined as follows:
-\begin{align} \label{eq:Polyak_expansion_lem1_alg}
-& \Delta_i^1  = \Delta_{i-1}^1 - \gamma_i \psi'(0) \Delta_{i-1}^1 - \gamma_i \varphi(Z_i), \qquad
- \delta_0^1 = \Delta_0\\
-& \bar{\Delta}^1_i = \frac{1}{n}\sum_{i=0}^{n-1} \Delta^1_i.
-\end{align}
-
-In order to prove this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$.
-The first expression on the RHS on \eqref{eq:Polyak_expansion} goes to zero in variance.
-In addition,
-\begin{align*}
-& \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }  = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
-& = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0. 
-\end{align*}
-We obtain
-\begin{equation}
-\sqrt{n} \bar{\Delta}^1_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1), \label{eq:Polyak_expansion_aux_process}
-\end{equation}
-
-\subsubsection*{Step II} $\bar{\Delta}_n$ and $\bar{\Delta}^1_n$ are asymptotically equivalent. \\
-
-From \eqref{eq:Polyak_Juditsky_alg} and \eqref{eq:Polyak_expansion_lem1_alg}, the difference $\delta_i = \Delta_i - \Delta_i^1$ satisfies the recursion
-\[
-\delta_i = \delta_{i-1} - \gamma_i \psi'(0) \delta_{i-1} + \gamma_i \left( \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i) \right),
-\]
-where $\delta_0 = 0$. Use Lemma~\ref{lem:Polyak_expansion} with $\xi_i =  \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i)$ to obtain
-\begin{align}
-& \sqrt{n}\bar{\delta}_n = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \xi_i  \\
-& = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \label{eq:PJ_proof1} \\
-& + 
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi(\Delta_{i-1})  + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i)
-\right) \label{eq:PJ_proof2}
-\end{align}
-For the term \eqref{eq:PJ_proof1} and using \eqref{eq:Polyak_Juditsky_cond3}, there exists $K_1$ and $K_2$ such that 
-\begin{align*}
-& \eqref{eq:PJ_proof1}
-\leq K_1 \sum_{i=1}^\infty \frac{1}{\sqrt{i}} \left| \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \right| \\
-& \leq K_2 \sum_{i=1}^\infty \frac{ |\Delta_i|^{1+\lambda}}{\sqrt{i}}. 
-\end{align*}
-
-Lemma~\ref{lem:PJ_converging_sum} shows that 
-\begin{align}
-\sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}}  < \infty \label{eq:PJ_converging_sum},
-\end{align}
-hence the Kronecker lemma implies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \to 0.
-\]
-For the term \eqref{eq:PJ_proof2}, set 
-\[
-\epsilon_i \triangleq \psi(\Delta_{i-1}) + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i).
-\]
-For $a>0$ and $n \in \mathbb N$, define the event
-\[
-A_{n,a} \triangleq \left\{ \sum_{i=1}^{n-1} \frac{|\epsilon_i|}{\sqrt{i}}  \geq a  \right\}. 
-\]
-By Markov's inequality, we have
-\begin{align}
-\ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } \leq \frac{1}{a} \sum_{i=1}^{n-1} \frac{ \ex{|\epsilon_i| \Delta_{i-1} \mid }}{\sqrt{i}}. \label{eq:PJ_proof_3}
-\end{align}
-Using \eqref{eq:Polyak_Juditsky_cond3} and \eqref{eq:PJ_additional_cond}, there exists $K'$ and $\lambda'>0$ such that
-\begin{align*}
-& \ex{ |\epsilon_i| | \Delta_{i-1}}  \leq |\psi(\Delta_{i-1})| + \left| \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i) \right|  \\
-& \leq K' |\Delta_{i-1}|^{1+\lambda}. 
-\end{align*}
-Plugging this bound in \eqref{eq:PJ_proof_3} and using Lemma~\ref{lem:PJ_converging_sum},we obtain 
-\[
-\Prob(A_{n,a}) = \ex{ \ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } } \leq  \frac{K''}{a}
-\]
-for some constant $K''$. It follows that for any $\epsilon$, we may choose $a$ large enough such that 
-\[
-\sup_{n} \Prob(A_{n,a}) < \epsilon.
-\]
-This implies that for any $\epsilon>0$,
-\[
-\Prob \left( \sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty \right) \geq 1-\epsilon,
-\]
-and hence 
-\[
-\sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty
-\]
-almost surely. The Kronecker lemma now implies 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left|\epsilon_i\right| \to 0,
-\]
-hence the term \eqref{eq:PJ_proof2} satisfies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right) \epsilon_i \leq \frac{K'''}{\sqrt{n}} \sum_{i=1}^{n-1} |\epsilon_i| \to 0. 
-\]
-This conclude the proof of part (i).
-
-\subsubsection*{Part (ii)}
-Use \eqref{eq:normal_expansion_lem} to write
-\[
-\sqrt{n} \bar{\Delta}_n = G_n + o_{p,n}(1),
-\]
-where
-\[
-G_n \triangleq -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n} \varphi(Z_i). 
-\]
-From \cite[Exm.
-7.8]{van2000asymptotic}, the location model $f(x-\theta)$ with continuously differentiable $f(x)$ is differentiable in quadratic mean with the score function $-f'(x-\theta)/f(x-\theta)$.
-This fact implies the following expansion \cite[Thm.
-7.2]{van2000asymptotic}:
-\begin{align}
-\label{eq:PJ_LAN}
-& \log \frac{\Prob^n_{h_n/\sqrt{n}}}{\Prob^n_0} (Z_1,\ldots,Z_n) =  \log \prod_{i=1}^{n} \frac{f(Z_i-h_n/\sqrt{n})}  {f(X_i-\theta)} = h J_n - \frac{1}{2}h^2 I_{\theta} + o_{p,n}(1),
-\end{align}
-for any converging sequence $h_n \to h$, 
-where 
-\[
-J_n \triangleq -\frac{1}{\sqrt{n}} \sum_{i=1}^n \frac{f'(Z_i)}{f(Z_i)} .
-\]
-We have
-\begin{align*}
-& \ex{ G_n J_n} = \frac{1}{\psi'(0)}\frac{1}{n} \sum_{i=1}^n \ex{ \varphi(Z_i) \frac{f'(Z_i)}{f(Z_i)} }  \\
-& = \frac{1}{ \psi'(0)} \ex{ \varphi(Z_1) \frac{f'(Z_1)}{f(Z_1)}} =  \frac{1}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx , 
-\end{align*}
-Since both $\sqrt{n}G_n$ and $\sqrt{n}J_n$ are the sum of $n$ i.i.d. random variables with zero mean and finite variance, we obtain, from the central limit theorem and Slutsky's theorem, that
-\[
-\left(\sqrt{n} \bar{\Delta}_n, \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} \right) \overset{d}{\to} \Ncal \left( \left(0,-\frac{h^2}{2} I_\theta \right),  \begin{pmatrix}
-\frac{\chi(0)}{\psi'^2(0)} & \frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx \\
-\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx & h^2 I_\theta 
-\end{pmatrix}  \right)
-\]
-Le Cam's third lemma \cite[Exm. 6.7]{van2000asymptotic} implies that under $\Prob^n_{h/\sqrt{n}}$, 
-\[
-\sqrt{n}\bar{\Delta}_n \overset{d}{\to} \Ncal\left(\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx,  \frac{\chi(0)}{\psi'^2(0)} \right).
-\]
-
-\QEDA
-}
-
-\subsection{Proof of Theorem~\ref{thm:LAN1}
-\label{proof:thm:LAN1}
-}
-The log probability mass distribution of $B^n=(B_1,\ldots,B_n)$ is given by
-\begin{align*}
-& \log \Prob_\theta(b^n) = \sum_{i=1}^n \left( \frac{b_i+1}{2} \log  \Prob(X_i\in A_i) + 
-\frac{1-b_i}{2} \log \Prob(X_i\in A_i) \right), \quad b^n \in \{-1,1\}^n. 
-\end{align*}
-Consequently, 
-\begin{align}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) } = \sum_{i=1}^n    \frac{b_i+1}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} + 
-\sum_{i=1}^n  \frac{1-b_i}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}. 
-\label{eq:LAN_proof1}
-\end{align}
-For each $i=1,\ldots,n$, write 
-\[
-A_i = \bigcup_{k=1}^{K_i} \left(t_{i,k},t_{i,k+1} \right),
-\]
-where $t_{i,1}<\ldots<t_{i,K_i}$ and, with a slight abuse of notation, $t_{i,1}$ and $t_{i,K_i}$ may also be $-\infty$ or $+\infty$, respectively. Thus
-\[
-\Prob_{\theta}(X_i \in A_i) = \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta).
-\]
-In particular, since $f$ is differentible, $\Prob_{\theta}(X_i \in A_i)$ is twice differentiable, and we may write
-\begin{align*}
-\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)  = \Prob_{\theta} (X_i \in A_i) + \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \frac{h}{\sqrt{n}} + o(h), 
-\end{align*}
-and thus
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} = \log \left(1 + \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} + o(h) \right) \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2 + o(h^2).
-\end{align*}
-Similarly, we have
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 + o(h^2).
-\end{align*}
-From \eqref{eq:LAN_proof1} we obtain
-\begin{align*}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
-\left( 
-\frac{b_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-b_i}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}   \right) \\
- & - \frac{h^2}{2n} 
- \sum_{i=1}^n 
-\left( 
- \frac{b_i+1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-b_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 \right) + o(h^2) \\
-\end{align*}
-%
-Noting that 
-\[
-\frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} = \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)},
-\]
-the proof is completed by proving the following two claims:
-\begin{itemize}
-\item[I.] 
-For $i=1,\ldots,n$ denote 
-\[
-U_i = \frac{B_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-B_i}{2}  \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}. 
-\]
-Then 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0, \kappa(\theta) \right). 
-\]
-\item[II.]
-For $i=1,\ldots,n$ denote 
-\[
-V_i =  \frac{B_i-1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-B_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2.
-\]
-Then 
-\[
-\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} \kappa(\theta). 
-\]
-\end{itemize}
-\subsubsection*{Proof of Claim I}
-First note that 
-\begin{align*}
-\mathbb E  [U_i] & = 
- \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=1)   + 
- \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=-1)  = 0. 
-\end{align*}
-In addition,
-\begin{align*}
-& \mathbb E U_i^2 = 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2  \Prob (B_i=1)   + 
-\left( \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2 \Prob (B_i=-1) \\
-& =
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)} +  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)} \\
- & =  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left(1-\Prob_{\theta}(X_i \in A_i) \right)} 
-\end{align*}
-Therefore
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 = L_n(A_1,\ldots,A_n) \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ such that the limit above exists.
-We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition for his version of the central limit time: for any $\delta>0$ we have that
-\begin{align*}
-& \mathbb E \left| U_i \right|^{2+\delta} =
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} 
-\end{align*}
-and
-\begin{equation}
-\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} } { \left( \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta} = 
-\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
-\label{eq:Lyaponov}
-\end{equation}
-Next, we claim that there exits $\delta>0$ and $K>0$, that are independent of $n$, such that
-\begin{align}
-\frac{1}{n} \sum_{i=1}^n \mathbb E  |U_i|^{2+\delta}  < M \label{eq:Lyaponov_num}
-\end{align} 
-for all $n$ large enough. To see this, note that
-\begin{align*}
-& \mathbb E |U_i|^{2+\delta} = 
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}  \\
-  &  = \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} } 
-  \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \\
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}, 
-\end{align*}
-where the last transition is because 
-\[
- \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \leq 1. 
-\]
-We now use the fact that each $A_i$ is a finite union of interval and consider the following lemma, proof of which is given in Appendix~\ref{proof:lem:bound_intervals_delta}.
-\begin{lem} \label{lem:bound_intervals_delta}
-Let $f(x)$ be a log-concave, symmetric, and differentiable PDF such that $\eta(x)$ is unimodal.  There exists $\delta>0$ such that for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, 
-\begin{equation}
-\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^{2+\delta} }
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} } 
-\leq  2^\delta f^{2+\delta}(0). 
-\label{eq:lem_bound_intervals_delta}
-\end{equation}
-\end{lem}
-
-Lemma~\ref{lem:bound_intervals_delta} implies 
-\begin{align*}
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} = \frac{\left| \sum_{k=1}^{K_i} (-1)^k f(x_{i,k}-\theta) \right|^{2+\delta} }
-  { \left( \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta} \left( 1 - \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta}} \\
-  & \leq 2^\delta f^{2+\delta}(0). 
-\end{align*}
-In particular, we conclude that 
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} \leq 2^\delta f^{2+\delta}(0), 
-\]
-and thus for any $\delta>0$ the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we conclude that 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0,\kappa(\theta) \right). 
-\]
-
-\subsubsection*{Proof of Claim II} 
-We have:
-\begin{align*}
-\mathbb E V_i  & = 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)}  
-+ 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)}  \\
- & = 
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left( 1-\Prob_{\theta}(X_i \in A_i) \right)}  
-\end{align*}
- We conclude that:
-\begin{equation} \label{eq:LAN_limit_cond}
-\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =   L_n(A_1,\ldots,A_n)  \to \kappa(\theta)
-\end{equation}
-Since the $V_i$s are independent of each other, Kolmogorov's law of large numbers implies
-%(e.g. \cite[Theorem 10.2.3]{sen1994large}) 
-\[
-\frac{1}{n} \sum_{i=1}^n  V_i \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ for which the limit \eqref{eq:LAN_limit_cond} exists.
-
-\QEDA
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals_delta}} 
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-and 
-\[
-\eta_\delta(x) \triangleq  \frac{  \left(\delta_1(x) \right)^{2+\delta}}{  \left(\Delta_1(x)  \right)^{1+\delta}
-(1-\Delta_1(x))^{1+\delta}}
-= \frac{  \left( f (x) \right)^{2+\delta}}{ \left(F(x) \right)^{1+\delta}(1-F(x))^{1+\delta}}. 
-\]
-The proof is by induction on $n$.
-For the case $n=1$ the LHS of \eqref{eq:lem_bound_intervals_delta} equals $\eta_\delta(x)$.
-Note that $\eta_\delta(0) = 2^\delta f^{2+\delta}(0)$, so it is enough to prove that $\eta_\delta(0)$ attains it maximum at $x=0$.
-We have $\eta_\delta(x) = \eta^{1+\delta}(x)/f^\delta(x)$, and thus
-\[
-\log \eta_\delta'(x) = (1+\delta) \frac{\eta'(x)}{\eta(x)} - \delta \frac{f'(x)}{f(x)}. 
-\]
-By Assumption~\ref{assump:failure_rate} both terms above are negative for $x>0$, so that $\log \eta_\delta'(x) \leq 0$ if and only if
-\begin{equation} \label{eq:delta_proof_cond}
-(1+\delta) \left| \frac{\eta'(x)}{\eta(x)} \right| \geq \delta \left| \frac{f'(x)}{f(x)} \right|, \qquad x>0.
-\end{equation}
-Also by Assumption~\ref{assump:failure_rate}, for $x>0$ we have
-\[
-0 > (\log \eta(x))' = \frac{h'(x)}{h(x)}-\frac{h'(-x)}{h(-x)},
-\]
-so that \eqref{eq:delta_proof_cond} is satisfies for $\delta>0$ small enough.
-
-Next, assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^{2+\delta}} 
-{\left(\Delta_n \right)^{1+\delta}\left(1- \Delta_n \right)^{1+\delta} } \leq \eta_\delta(0) = 2^\delta f^{2+\delta}(0) . 
-\label{eq:lem_bound_intervals_delta_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%If $x_{i+1} = x_i$ for some $i=1,\ldots,N-1$, then then the indices $i$ and $i+1$ may  be removed from all sums in \eqref{eq:lem_bound_intervals}, what brings us to the case $n = N-2$.
-Therefore, we may assume that $x_1 < \ldots < x_n$.
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  (2+\delta) \log \delta_N - (1+\delta) \log \Delta_N - (1+\delta) \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{(2+\delta) (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(1+\delta)(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(1+\delta)(-1)^{k+1} f(x_k)}{1-\Delta_N }.
-\]
-We conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero_delta}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N(1+\delta)}{2+\delta} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-From the same reason as in the proof of Lemma~\ref{lem:bound_intervals_delta}, \eqref{eq:gradient_zero_delta} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_delta_proof} equals $\eta_\delta(x_1)$ which was shown to be smaller than $\eta_\delta(\epsilon)$.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_delta_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$,  $x_i, x_{i+1} = -\epsilon$ for some $i$, or $x_i, x_{i+1} = \epsilon$ for some $i$.
-It is therefore enough to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Assume first $x_N \rightarrow -\infty$. Then 
-\begin{align*}
-\frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)^{1+\delta} } ,
-\end{align*}
-which is smaller than $\eta_\delta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
-\begin{align*}
-& \frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right)^{1+\delta} }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^{2+\delta}} 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)^{1+\delta}\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right)^{1+\delta} },
-\end{align*}
-where $x'_{m} = x_{m+1}$ for $m=1,\ldots, N-1$. The last expression is smaller than $\eta_{\delta}(0)$ by the induction hypothesis.  \QEDA \\
-
-\subsection{Proof of Theorem~\ref{thm:non_existence}
-\label{proof:thm:non_existence}
-}
-
-Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta) = \eta(0)$. 
-%
-Since $B_1,B_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, $\theta$ is in $\Xi$ if and only if
-\begin{equation}
-\label{eq:non_existence_proof}
-\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0). 
-\end{equation}
-By assumption, we have $B_i^{-1} = A_i$ where $A_i$ can be expressed as
-\[
-A_i = \cup_{i=1}^K (a_{i,k},b_{i,k}), 
-\]
-where $a_{i,1} \leq b_{i,1} \leq \ldots \leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values $-\infty$ and $\infty$, respectively. Denote
-\[
-\mathcal B_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\}.
-\]
-For any $\theta$ and $\epsilon>0$, denote 
-\[
-S_n(\theta, \epsilon) \triangleq \left\{ i\leq n \,:\, (\theta-\epsilon,\theta+\epsilon) \cap \mathcal B_i \neq \emptyset \right\}
-\]
-In words, $S_n$ contains all integers smaller than $n$ in which an $\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals consisting $A_i$. 
-%
-We now claim that 
-if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. Indeed, for such $\theta$ we have
-\begin{align}
-& L_n(A_1,\ldots,A_n; \theta) \nonumber \\
-& = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
-\frac{ \left(\sum_{k=1}^{K}  f(\theta - b_{i,k})- f(\theta - a_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& 
-+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(b_{i,k}-\theta) - f(a_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& \overset{(a)}{\leq}
-\frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
- \label{eq:non_existence_proof1}
-\end{align}
-where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} and the fact that for $i \in S_n(\theta, \epsilon)$, 
-\[
-\max\left\{ \max_k \eta(b_{i,k}-\theta) , \max_k \eta(a_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
-\]
-Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, \eqref{eq:non_existence_proof1}, and thus $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.
-\par
-For $k\in \mathbb N$, assume by contradiction that there exists $N \geq 2K + 1$ distinct elements
-$\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$ consists of at most $K$ intervals, we have that 
-\begin{equation}
-\label{eq:few_optimality_points_proof}
-\card (\cup_{i=1}^n \mathcal B_i) \leq 2 n K. 
-\end{equation}
-Fix $\epsilon>0$ such that 
-\[
-\epsilon < \frac{1}{2}\min_{i\neq j} |\theta_i - \theta_j|. 
-\]
-Since for each $\theta \in \Theta$ we have $S_n(\theta, \epsilon) \to 1$, there exists $n$ large enough such that 
-\[
-\card \left(S_n(\theta_i, \epsilon) \right) \geq n \left(1-\frac{1}{2N} \right)
-\]
-for all $i=1,\ldots,N$.
-However, $S_n(\theta_1,\epsilon), \ldots S_n(\theta_N,\epsilon)$ are disjoint, so the cardinallity of their union is at least $n\left(1-\frac{1}{2N} \right)N$ which is grater than $2nK + n/2$ in contradiction to \eqref{eq:few_optimality_points_proof}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEfull,onebit}
-
-\end{document}

### 2019-09-19 abstract.tex
Starting to edit

% -*- Mode: latex -*- %
\begin{abstract}
  We consider the problem of estimating the mean of a symmetric log-concave
  distribution under constraint that only a single bit per sample
  from this distribution is available to the estimator. We study the mean
  squared error as a function of the
  sample size (and hence number of bits).
  We consider three settings: first, a centralized setting, where
  an encoder may release $n$ bits given a sample of size $n$, and for
  which there is no asymptotic penalty for quantization; second, an adaptive
  setting  in which each bit is a function of the current
  observation and previously recorded bits, where we show that
  the optimal relative
  efficiency compared to the sample mean is precisely
  the efficiency of the median; lastly, we show that in
  a distributed setting where each bit is only a function
  of a local sample, no estimator can achieve optimal efficiency
  uniformly over the parameter space.
  We additionally complement our results in the adaptive setting
  by showing that \emph{one} round of adaptivity is sufficient
  to achieve optimal mean-square error.
  %% single sample. We show that the optimal efficiency of the adaptive
  %% setting can be attained by splitting the sample into two parts and
  %% allowing only a single adaptation. Otherwise, we show that no one sample
  %% estimation procedure can attain the optimal efficiency uniformly over all
  %% points in the parameter space.  Our results indicate that estimating the
  %% mean from one-bit measurements is equivalent to estimating the sample
  %% median from these measurements. In the adaptive case, this estimate can be
  %% done with vanishing error for any point in the parameter space. In the
  %% distributed case, this estimate can be done with vanishing error only for
  %% a finite number of possible values for the unknown mean.
\end{abstract}

### 2019-09-19 introduction.tex
Starting to edit

--- 2019-08-16 onebit_full.tex
@@
-\documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper
+% -*- Mode: latex -*- %
 
-%LatexiDiff ignore tikz:
-% $: latexdiff -c "PICTUREENV=(?:picture|tikzpicture|DIFnomarkup)[\w\d*@]*" old.tex new.tex > diff.tex
-
-%\IEEEoverridecommandlockouts                              %
-
-%\usepackage{mathcomSTEP}
-
-%\overrideIEEEmargins 
-%\IEEEoverridecommandlockouts                              % This command is only needed if 
-% you want to use the \thanks command
-
-%\overrideIEEEmargins                                      % Needed to meet printer requirements.
-
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-\onecolumn
-
-\usepackage{mathptmx} 
-\usepackage{times} 
-\usepackage{amsmath} 
-\usepackage{amsbsy} 
-\usepackage{amssymb}
-
-%\usepackage{newtxtext, newtxmath}
-\usepackage{mathrsfs}
-\usepackage{comment}
-\usepackage[export]{adjustbox}
-\usepackage{tikz}
-\usetikzlibrary{external,positioning,decorations.pathreplacing,shapes,arrows,patterns}
-
-\usepackage[hidelinks]{hyperref}
-%\tikzexternalize[mode=list and make]
-\usepackage{algorithmicx}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage{pstool}
-\usepackage[latin1]{inputenc}
-\usetikzlibrary{arrows,shapes}
-\usepackage{xifthen}
-\usepackage{epic}
-%\usepackage{caption}
-\usepackage{epstopdf}
-
-\newtheorem{thm}{\bf{Theorem}}
-\newtheorem{cor}[thm]{\bf {Corollary}}
-\newtheorem{lem}[thm]{\bf {Lemma}}
-\newtheorem{prop}[thm]{\bf {Proposition}}
-\newtheorem{example}{\bf {Example}}
-\newtheorem{definition}{\bf {Definition}}
-\newtheorem{rem}{\bf {Remark}}
-\newtheorem{assump}{\bf {Assumptions}}
-
-\newcommand{\ex}[1]{\ensuremath{\mathbb{E}\left[ #1\right]}}
-
-\newcommand{\Var}[1]{\ensuremath{\mathrm{Var} \left[ #1\right]}}
-
-\newcommand{\unif}{\mathsf{unif}}
-\newcommand{\card}{\mathrm{card}}
-\newcommand{\ARE}{\mathsf{ARE}}
-\newcommand{\supp}{\mathrm{supp} }
-\renewcommand\vec[1]{\ensuremath\boldsymbol{#1}}
-\newenvironment{proof}{\paragraph*{Proof}}{\hfill$\square$ \newline}
-\newcommand{\sgn}{\mathrm{sgn} }
-\newcommand{\Prob}{\mathbb{P} }
-\newcommand{\argmax}{\mathrm{argmax}}
-\newcommand*{\QEDA}{\hfill\ensuremath{\square}}
-\newcommand{\CEO}{\mathsf{CEO}}
-\newcommand{\Ncal}{\mathcal{N}}
-
-\newcommand{\enc}{\mathsf{enc}}
-\newcommand{\est}{\mathsf{est}}
-
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-\tikzstyle{sint}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.8cm,thick ]
-\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
-\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
-\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.7cm,thick ]
-\tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-
-\author{
-    \IEEEauthorblockN{
-Alon Kipnis\IEEEauthorrefmark{1} and   
-    John C. Duchi\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}  \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}Stanford University, Department of Statistics \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Stanford University, Department of Electrical Engineering. }
-}
-
-\title{\LARGE \bf Mean Estimation from One-Bit Measurements}
-
-\begin{document}
-\graphicspath{{./Figs/}}
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-We consider the problem of estimating the mean of a symmetric log-concave distribution under the following constraint: only a single bit per sample from this distribution is available to the estimator.
-We study the mean squared error risk in this estimation as a function of the number of samples, and hence the number of bits, from this distribution.
-%
-Under an adaptive setting in which each bit is a function of the current sample and previously recorded bits, we show that the optimal relative efficiency compared to the sample mean is the efficiency of the median.
-%For example, in estimating the mean of a normal distribution, a constraint of one bit per sample incurs a penalty of $\pi/2$ in sample size compared to the unconstrained case.
-%
-We also consider a distributed setting where each bit is only a function of a single sample.
-We show that the optimal efficiency of the adaptive setting can be attained by splitting the sample into two parts and allowing only a single adaptation.
-Otherwise, we show that no one sample estimation procedure can attain the optimal efficiency uniformly over all points in the parameter space.
-%
-%Finally, we analyze a distributed setting where the bits are obtained by comparing each sample against a prescribed threshold.
-Consequently, we consider the threshold density that minimizes the maximal MSE.
-%
-Our results indicate that estimating the mean from one-bit measurements is equivalent to estimating the sample median from these measurements.
-In the adaptive case, this estimate can be done with vanishing error for any point in the parameter space.
-In the distributed case, this estimate can be done with vanishing error only for a finite number of possible values for the unknown mean.
-\end{abstract}
-
-%{\color{red}  See LASSO results in http://arxiv.org/abs/1506.02181v1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
 \label{sec:Intro}
-Estimating parameters from data collected and processed by multiple units may be limited due to communication constraints between these units. 
-%
-For example, this scenario arises in sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit.
-In these situations, the ability to estimate a particular parameter from the data is dictated not only by the quality of observations and their number but also by the available bandwidth for communicating between the sensors and the central estimator.
-The question that we ask is to what extent a parametric estimation task is affected by this constraint on communication, and what are the fundamental performance limits in estimating a parameter subject to such restriction.
-\par
+
+We consider estimation of parameters from data collected by multiple units
+under communication constraints between the units.  Such scenarios arise in
+sensor arrays, where sensor motes collect information, which they transmit
+to a central estimation unit~\cite{LesserOrTa03,LiWoHuSa02}. More generally,
+communication is substantially more expensive than computation in modern
+computing infrastructure~\cite{FullerMi11}.  It is thus of interest to
+understand the extent to which communication constraints induce fundamental
+accuracy and efficiency limits in parametric estimation problems.
 %%
 \begin{figure*}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto]
-
-  \node at (0,0) (source) {$X_1$} ;
- \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
-\node[below of = source2, node distance = 2.1cm] (source3) {$X_n$};
-
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {$\enc$};
-
-\draw[->,line width = 2pt] (source2) -- (enc2); 
-\draw[->,line width = 2pt] (source) -| (enc2); 
-\draw[->,line width = 2pt] (source3) -| (enc2);
-
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-
-\draw[->,line width = 2pt] (source2) -- (enc2); 
-\node[int1, right of = enc2, node distance = 2.7cm ] (est) {$\est$};
-
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {\small $B_1,\ldots,B_n$} (est);
-
-\node[right of = est, node distance = 1.2cm] (dest) {\small ${\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=1pt] (est) -- (dest);
-\node at (2,-4.5) {(i) Centralized};
-\end{tikzpicture}
-%
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {\small $X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
- \node[below of = source, node distance = 1.5cm] (source2) {\small $X_2$};
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {$\enc$};  
-\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source2, node distance = 2.1cm] (source3) {\small $X_n$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};  
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim P_X$};
-
-\node[int1, right of = enc2, node distance = 3cm ] (est) {$\est$};
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);   
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$B_2$} (est);
-
-\draw[->] (enc1)+(0.7,0) -- +(0.7,-0.7) -| (enc2);
-
-%\draw[dashed,->] (enc2)+(0.7,0) -- +(0.7,-0.7) -| +(0,-1.2);
-\draw[->,line width = 2pt] (enc3) -| (est);
-
-%\node[below of = mes2, node distance = 1.5cm] (mes3) {$B_1,\ldots,B_{n-1} $};
-
-\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -1cm]  {$B_n$} (est);
-
-%\draw[->] (mes3.west) -- +(0,-0.5) -| (enc3);
-
-\node[below right = 2.3cm and 0.7cm of 
-enc1.center, yshift = 0.cm] (end) {$B_1,\ldots,B_{n-1}$};
-
-\draw[->] (enc1)+(0.7,0) -- (end.west) -| (enc3);
-
-\node[right of = est, node distance = 1.2cm] (dest) {${\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=1pt] (est) -- (dest);
-\node at (2,-4.5) {(ii) Adaptive};
-\end{tikzpicture}
-%
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
- \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {$\enc$};  
-\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source2, node distance = 2.1cm] (source3) {$X_n$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};  
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim {\Ncal} \left(\theta, \sigma^2 \right)$};
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-
-\node[int1, right of = enc2, node distance = 2.1cm ] (est) {$\est$};
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
-
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$B_2$} (est);
-
-\draw[->,line width = 2pt] (enc3) -| (est);
-
-\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -1cm]  {$B_n$} (est);
-
-\node[right of = est, node distance = 1.2cm] (dest) {${\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=1pt] (est) -- (dest);
-\node at (2,-4.5) {(iii) Distributed};
-\end{tikzpicture}
-\end{center}
-\caption{\label{fig:setup} 
-Three encoding settings: (i) Centralized  -- an encoder sends $n$ bits after observing $n$ samples.
-(ii) Adaptive (sequential) --  the $i$th encoder sends the bit $B_i$ depending on its private sample $X_i$ and previous bits $B_1,\ldots,B_{i-1}$.
-(iii) Distributed  -- each encoder send the bit $B_i$ based on its private sample $X_i$ only.}
+  \include{Figs/encoding-settings}
+  \caption{\label{fig:setup} Three encoding settings: (i) Centralized -- an
+    encoder sends $n$ bits after observing $n$ samples. (ii) Adaptive
+    (sequential) -- the $i$th encoder sends the bit $B_i$ depending on its
+    private sample $X_i$ and previous bits $B_1,\ldots,B_{i-1}$. (iii)
+    Distributed -- each encoder send the bit $B_i$ based on its private
+    sample $X_i$ only.}
 \end{figure*}
@@
 
-This paper answers this question in a particular setting: the estimation of the mean $\theta$ of a symmetric log-concave distribution with finite variance, under the constraint that only a single bit can be communicated on each sample from this distribution.
-As it turns out, the ability to share information before committing on each one-bit message dramatically affects the performance in estimating $\theta$.
-We, therefore, distinguish among the three settings illustrated in Figure~\ref{fig:setup}
+We answer this question in a sylized version of this problem: the estimation
+of the mean $\theta$ of a symmetric log-concave distribution under the
+constraint that only a single bit can be communicated about each observation
+from this distribution.
+
+%% JCD: I am here. %%
+
+As it turns out, the ability to share information
+before committing on each one-bit message dramatically affects the
+performance in estimating $\theta$. We, therefore, distinguish among the
+three settings illustrated in Figure~\ref{fig:setup}
 \begin{itemize}
@@
 In Section~\ref{sec:conclusions} we provide concluding remarks.
-
-\section{Problem Formulation \label{sec:problem}}
-
-Let $f(x)$ be a symmetric and log-concave density function with a finite second moment $\sigma^2$.
-For $\theta \in \Theta$, denote by $P_X$ the probability distribution with density $f\left( x-\theta \right)$.
-Therefore, $P_X$ is an absolutely continuous log-concave distribution with mean $\theta$ and variance $\sigma^2$.
-Symmetry and log-concavity of $f(x)$ imply that $P_X$ is strongly unimodal (has a unique local maxima) with its mode at $x =\theta$ \cite{ibragimov1956composition}.
-We further assume that the \emph{parameter space} $\Theta$ is a closed interval of the real line.
-\par
-In some situations it is useful to assume that $\theta$ is drawn once from the prior distribution $\pi$ on $\Theta$.
-In this case we assume that $\pi$ is an absolutely continuous distribution, and denote its density by $\pi(\theta)$, i.e., $\pi(d\theta) = \pi(\theta)d\theta$.
-\par
-The random variables $X_1,\ldots,X_n$ represent $n$ independent samples from $P_X$. 
-We are interested in estimating $\theta$ from a set of $n$ binary messages $B_1,\ldots,B_n$, obtained from $X_1,\ldots,X_n$ under three possible scenarios illustrated in Figure~\ref{fig:setup}: 
-\begin{itemize}
-\item[(i)~~] Centralized $B_i(X_1,\ldots,X_n)$, $i=1,\ldots,n$.
-\item[(ii)~] Adaptive $B_i(X_i,B_1,\ldots,B_{i-1})$, $i=2,\ldots,n$.
-\item[(iii)] Distributed $B_i(X_i)$, $i=1,\ldots,n$.
-\end{itemize}
-
-The performance of an estimator ${\theta}_n \triangleq {\theta}_n(B^n)$ in any of these cases is measured according to the quadratic risk:
-\begin{equation}
-\label{eq:error_def}
-R_n \triangleq \mathbb E\left({\theta}_n - \theta \right)^2,
-\end{equation}
-where the expectation is taken with respect to the distribution of $X_1,\ldots,X_n$ and, whenever available, a prior distribution $\pi(\theta)$ over $\Theta$.  
-%It is well known that minmax estimation error 
-%\begin{equation}
-%R_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left({\theta}_n - \theta \right)^2 | \theta \right],
-%\end{equation}
-%can be obtained from $R_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}. 
-%
-The main problems we consider in this paper are the minimal value of \eqref{eq:error_def}, as a function of $n$ and $f(x)$, under different choices of the encoding functions in cases (i), (ii), and (iii).
-\par
-
-We give particular attention to the ARE of estimators with respect to an asymptotically normal efficient estimator that is not subject to the bit constraint.
-Specifically, let $\{a_n,\,n\in \mathbb N\}$ be a sequence such that
-\[
-\sqrt{a_n}\left({\theta}_n - \theta\right) \overset{d}{\longrightarrow} \Ncal(0, \sigma^2).
-\]
-Then the ARE of ${\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
-\[
-\ARE({\theta}_n) \triangleq
-\lim_{n\rightarrow \infty} \frac{a_n}{n}. 
-\]
-Note that in the special case where there exists $V \in \mathbb R$ such that
-\[
-a_n \mathbb E \left({\theta}_n - \theta \right)^2 = V + o(1),
-\]
-with $o(1)\to 0$ as $n\to \infty$, then the ARE of ${\theta}_n$ is finite and equals $\sigma^2/V$. \par
-
-In addition to the notation above, we also denote by $F(x)$ the cumulative distribution function of $X_i$, and define
-\begin{equation} \label{eq:eta_def}
-\eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))} =  \frac{f(x)f(-x)}{F(x)F(-x)}, 
-\end{equation}
-where the last equality is due to symmetry of $f(x)$. We note that 
-\begin{equation}
-\label{eq:eta_h}
-\eta(x) = h(x)h(-x) = f(x) \left( h(x) + h(-x) \right), 
-\end{equation}
-where 
-\[
-h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
-\]
-is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function since $f(x)$ is log-concave \cite{bagnoli2005log}. 
-%
-For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as illustrated in Fig.~\ref{fig:eta}. 
-%
-In this paper we only consider the normal distribution and other log-concave symmetric distributions for which this property of $\eta(x)$ holds. Specifically, we require the following:
-\begin{assump} \label{assump:failure_rate}
- $\eta(x)$ has a unique maximum (at the origin) and is a non-increasing function of $|x|$. 
-\end{assump}
-%That is, Assumption~\ref{assump:failure_rate} says that $\eta'(x) < 0 $ for all $x>0$. 
-Under this assumption we have, 
-\[
-4f^2(x) \leq \eta(x) \leq \eta(0),
-\] 
-%
-where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median.
-Combined with log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that $\eta(x)$ vanishes as $|x|\rightarrow \infty$.
-\par
-%
-Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions).
-Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.\par
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -3, xmax=3, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.9,
-samples=10, 
-xlabel= $x$,
-xtick={-2,-1,0,1,2},
-xticklabels={-2,-1,0,1,2},
-ytick={0,0.3989423,0.6366198},
-yticklabels={0,$\frac{1}{\sqrt{2 \pi}}$,$2/\pi$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\eta(x)$};
-\addplot[domain = -5:5, samples = 50, color = red, solid, smooth]  {exp(-x^2/2) / sqrt(2*3.14159)};
-\addlegendentry{$\phi(x)$};
-\addplot[domain = -5:5, samples = 50, color = black, solid, dashed]  {4*exp(-x^2) / (2*3.14159)};
-\addlegendentry{$4\phi^2(x)$};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -4, xmax=4, 
-restrict y to domain = -10:0,
-ymin = -10,
-samples=10, 
-xlabel= $x$,
-xtick={-3,-2,-1,0,1,2,3},
-xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,-0.45158,-0.919},
-yticklabels={0,,},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\log \eta(x)$};
-\addplot[domain = -5:5, samples = 30, color = red, solid, smooth]  {-(x)^2/2 -0.9189};
-\addlegendentry{$\log \phi(x)$};
-\end{axis}
-\end{tikzpicture}
-\caption{
-The function $\eta(x) = f^2(x) / F(x)F(-x)$ for $f(x) = \phi(x)$ the standard normal density.
-\label{fig:eta}
-}
-\end{center}
-\end{figure}
-
-\section{Consistent Estimation and Off-the-shelf Bounds \label{sec:preliminary}}
-%
-In this section we adapt known results to derive lower and upper bounds on the relative efficiency under setting (iii). These bounds establish the following facts:
-\begin{itemize}
-\item[I.] A consistent estimator with an asymptotically normal distribution always exists in setting (iii), and hence in setting (ii). 
-\item[II.] For the normal distribution, the ARE in setting (iii) is at most $3/4$. Namely, under setting (iii), all estimators are strictly inferior compared to the sample mean. 
-\end{itemize}
-
-\subsection{Consistent Estimation}
-Fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
-\[
-B_i = \mathbf 1_{X_i>\theta_0}, 
-\]
-where $\mathbf 1_A$ is the indicator of the event $A$. We have
-\[
-P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
-\]
-so that 
-\begin{equation}
-\label{eq:estimator_naive}
-{\theta}_n = \theta_0 + F^{-1}\left( P_n \right)
-\end{equation}
-is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set due to log-concavity.
-Furthermore, the variance of $P_n$ is $F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)$, and hence the delta method implies that ${\theta}_n$ is asymptotically normal with variance
-\begin{equation} 
- \frac{F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}{f^2(\theta-\theta_0)} = \frac{1}{
-\eta(\theta-\theta_0)}.
-\end{equation}
-In particular, the ARE of ${\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
-In other words, for a prescribed accuracy, ${\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
-\par
-%
-%
-Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of ${\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
-This ARE is attained only when $\theta_0 = \theta$, whereas $\theta$ is apriori unknown.
-Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of ${\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
-As an example, when $f(x)$ is a normal density, the ARE of ${\theta}_n$ is less than $\approx 0.14$ when $\theta_0$ is $2$ standard deviations from $\theta$.
-Therefore, the estimator ${\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
-\par
-It is suggested that we can attain lower variance in estimation by updating the threshold value $\theta_0$ in \eqref{eq:estimator_naive} after observing one or a batch of the single bit messages.
-Schemes with such adaptation fall within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
-\par
-
-\subsection{Multiterminal Source Coding \label{sec:ceo}}
-The CEO setting considers the estimation of a sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_i$ is available at $n$ terminals.
-At each terminal $i$, an encoder observes the $k$ noisy samples
-\[
-X_{i,j} = \theta_j + Z_{i,j},\qquad j=1,\ldots,k, \qquad i = 1,\ldots,n,
-\]
-and transmits $r_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates ${\theta}_1,\ldots,{\theta}_k$ with the goal of minimizing the quadratic risk:
-\[
-R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - {\theta}_j \right)^2 \right]. 
-\]
-Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $r_1=\ldots=r_n = 1$.
-It follows that, assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
-%
-Consequently, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the minimal MSE in the CEO setting as $k \to \infty$.
-Note that the difference between the CEO setting and ours lays in the privilege of each of the encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realizations, rather than a single realization using a single bit in ours.
- \par
-When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k$ goes to infinity were fully characterized in \cite{prabhakaran2004rate}.
-Furthermore, the work of \cite{chen2004upper} provided an expression for quadratic risk attained in the CEO setting under Gaussian priors.
-Adapting to our setting, this expression provides the following proposition:
-\begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is arbitrary.
-Then any estimator ${\theta}_n$ of $\theta$ in the distributed setting satisfies
-\begin{equation} \label{eq:ceo_bound}
- n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
-\end{equation}
-where the expectation is with respect to $\theta$ and $X^n$.
-\end{prop}
-
-\begin{proof}
-See Appendix~\ref{app:proof:prop_ceo_lower_bound}.
-\end{proof}
-
-From the formulation of the CEO problem, it follows that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is attributed to the ability to perform coding over blocks.
-Namely, each encoder in the CEO setting may encode an arbitrary number of $k$ independent realizations of $\theta$ using $k$ bits, versus only one realization with one bit in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product probability space that distinguishes between the CEO problem with one bit per encoder on average and the mean estimation problem from one-bit measurements in the distributed setting.
-
-\section{Adaptive Estimation \label{sec:sequential}}
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $\eta(0)\sigma^2$, which is the ARE of the median of the sample $X_1,\ldots,X_n$.
-We also provide a particular adaptive estimation scheme that attains this maximal efficiency.
-%Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $B_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages.
-%Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $\eta(0)\sigma^2$.
-
-\subsection{Limited efficiency in the adaptive setting}
-Our first result asserts that the ARE of any adaptive encoding and estimation scheme is bounded from above by $\eta(0)\sigma^2$. %This result follows from the following theorem:
-\begin{thm}[maximal relative effeciency] \label{thm:adpative_lower_bound}
-Let ${\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Figure~\ref{fig:setup}-(ii). Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-n\mathbb E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0},
-\]
-where 
-\[
-I_0 = \mathbb E \left( \frac{d}{d\theta} \log \pi (\theta) \right)^2
-\]
-is the Fisher information with respect to a location model in $\theta$. 
-\end{thm}
-
-\subsubsection*{Proof}
-%We first bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
-The result then follows using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are in
-See Appendix~\ref{proof:thm:adpative_lower_bound}.\par
-
-Theorem~\ref{thm:adpative_lower_bound} implies that any estimator ${\theta}_n$ from any adaptive encoding scheme satisfies
-\[
-n\mathbb E\left[ (\theta-\theta_n)^2 \right] \leq  \frac{1}{4f^2(0)}+O(n^{-1}),
-\]
-and 
-\[
-\ARE({\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
-\]
-
-Next, we present an adaptive encoding and estimation scheme that attains the maximal ARE of $\eta(0)\sigma^2$.
-
-\subsection{Asymptotically optimal estimator}
-Let $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ be a strictly positive sequence. Consider the following estimator ${\theta}_n$ for $\theta$:  
-\begin{equation}
-\label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n B_n, \quad n = 1,2,\ldots,
-\end{equation}
-where 
-\begin{equation}
-B_n = B_n (X_n,\theta_{n-1}) =\sgn (X_n - \theta_{n-1}).
-\end{equation}
-Define the $n$th step estimation as
-\begin{equation} \label{eq:sgd_est}
-\bar{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
-\end{equation}
-
-We have the following results:
-\begin{thm} \label{thm:sgd}
-Consider the sequence $\left\{\bar{\theta}_n \right\}_{n\in \mathbb N}$ defined by \eqref{eq:sgd_est}. 
-\begin{enumerate}
-\item[(i)] Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions1}
-\begin{cases}
-\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
-\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
-\mathrm{for~some~}0< \lambda \leq 1
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Then
-\[
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left(0,\frac{1}{\eta(0)}\right).
-\]
-%
-%
-\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with a finite location Fisher information, namely
-\[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)}  \right)^2 f(x) dx < \infty.
-\]
-%(or that $f(x-\theta)$ is differentiable in quadratic mean).  
-Then for any bounded, symmetric, and quasi-convex function $L$, 
-\begin{align} 
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
-\\
-& \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
-\end{align}
-where $Z \sim \Ncal(0,1)$. 
-%
-%
-\item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions2}
-\begin{cases}
-\gamma_n = o(n^{-2/3}), &  \\
-\sum_{n=1}^\infty \gamma_n = \infty.  & \\
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ with $\beta \in (2/3,1)$). Then
-\[
- \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{n\eta(0)} + o(n^{-1}). 
-\]
-\end{enumerate}
-\end{thm}
-
-\subsubsection*{Proof}
-See Appendix~\ref{proof:thm:sgd}. \par
-
-Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the maximal ARE, as established by Theorem~\ref{thm:adpative_lower_bound}.
-%Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$.
-%
-The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$.
-Consequently, the procedure above is known as averaged stochastic gradient descent for minimizing $x \to |x|$ given the data $X_1,\ldots,X_n$.
-The minimal value of this optimization is the sample median, and Theorem~\ref{thm:sgd} provides conditions for the sequence of gradient steps so that the algorithm converges to this minimum.
-In particular, parts (i) and (ii) of Theorem~\ref{thm:sgd} provides conditions under which $\bar{\theta}$ is asymptotically normal and local asymptotically minimax, in the sense that it attains the local asymptotic minimax bound \cite{van2000asymptotic}.
-Part (iii) provides an additional condition under which $\bar{\theta}$ also converges in its second moment.
- \par
-%Note that $\theta_0$ is not explicitly defined in equation \eqref{eq:sgd_est}.
-A reasonable initialization for $\theta_0$ is $\theta_0 = \mathbb E [\theta]$, although Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
-Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$.
-\\
-In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $B_n$ depends on its private sample as well as the current gradient descent estimate $\theta_{n-1}$.
-In this sense, each encoder in this algorithm interacts with previous one by using the current estimate.
-%
-As we explain next, 
-it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ with only one round of interactions among the encoders.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
-% \node[below of = source, node distance = 1cm] (source2) {$X_2$};
-%\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};  
-%\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};
-
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[below of = source, node distance = 0.5cm] {$\vdots$};
-
-\node[int1, right of = enc3, node distance = 2.1cm ] (est) {$\est_1$};
-
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
-
-%\draw[->,line width = 2pt] (enc2) -| node[above, xshift = -1cm] (mes2) {$B_2$} (est);
-
-\draw[->,line width = 2pt] (enc3) -- node[above, xshift = 0cm]  {$B_{n_1}$} (est);
-
-\node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
-\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {$\enc$};  
-\draw[->,line width = 2pt] (sourceB) -- (enc1B);
-
-\node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
-\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {$\enc$};  
-\draw[->,line width = 2pt] (source3B) -- (enc3B); 
-\node[below of = sourceB, node distance = 0.4cm] {$\vdots$};
-
-\node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {$\est_2$};
-
-\draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.5cm] {$B_{n_1+1}$} (estB);
-\draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);
-
-\draw[->,line width = 1pt] (est.east) node[above, xshift  =0.5cm] {${\theta}_{n_1}$} -| (enc1B.north);
-
-%\draw[->,line width = 1pt] (enc1B) -- (enc3B);
-
-\draw[->,line width = 0.5pt] (est.east) -| +(1.3,-0.5) -- +(1.3,-2.5) -| (enc3B.north);
-
-%\draw[->,line width = 1pt] (enc1B)  -- node[right] {${\theta}_{n_1}$} (enc3B);
-
-\draw[->,line width = 0.5pt] (estB) -- +(0.8,0) node[right] {${\theta}_n$};
-\node[below of = enc1B, node distance = 0.5cm] {$\vdots$};
-
-\end{tikzpicture}
-\end{center}
-\caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
-\label{fig:one_round}
-}
-\end{figure}
-
-\subsection{Maximal Efficiency using One Round of Threshold Adaptation}
-In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
-\[
-B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
-\]
-and deduced that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
-%
-We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ based on previously observed bits at least once.
-%
-In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
-We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate ${\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use ${\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$.
-Figure~\ref{fig:one_round} illustrates a diagram of this procedure.
-%
-The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
-\begin{thm}
-For $i=1,\ldots,n$ set
-\[
-B_i = \begin{cases}
- \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
- \mathbf 1_{X_i \geq {\theta}_{n_1} }& i={n_1+1,\ldots,n},
-\end{cases}
-\]
-where $n = n_1+ n_2$ and 
-\[
-{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
-\frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
- \right).
-\] 
-Let 
-\[
-{\theta}_{n_2}  = {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
-\]
-and assume that $n_1(n) \rightarrow \infty$ and $n_1(n)/n \rightarrow 0$. Then:
-\begin{align*}
- \sqrt{n} \left( {\theta}_{n_2} - \theta  \right) \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
-\end{align*}
-\end{thm}
-%
-%
-\begin{proof}
-For $t\in \mathbb R$, set
-\[
-p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
-\]
-From the central limit theorem
-\begin{align*}
-& \sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)  = \sqrt{\frac{n}{n_2}} \sqrt{n_2} \left(  p_{n_2}(t) - F(\theta - t) \right) \\
-& \overset{d}{\rightarrow} \Ncal\left( 0, V(t) \right),
-\end{align*}
-where
-\[
-V(t) \triangleq F(\theta - t) F \left( t - \theta\right). 
-\]
-Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ implies
-\begin{align*}
-& \sqrt{n} \left( t + F^{-1}(\hat{p}_{n_2}(t)) - \theta \right) \\
-&= \sqrt{n} \left( g(\hat{p}_{n_2}(t)) - g \left(F(\theta-t) \right)  \right) \\
-& \overset{d}{\to} \Ncal\left(0, 
-1/\eta(\theta-t) \right).
-\end{align*}
-%where this convergence is uniform in $t$ since all moments of $F^{-1}(\hat{p}_{n_2})$ exists. 
-On the other hand, by the law of large numbers,
-\[
-p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
-\]
-so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity and thus 
-\[
-\eta( {\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
-\]
-Finally,
-\begin{align*}
-& \sqrt{n}\left({\theta}_{n_2} - \theta\right) \\
-& = \sqrt{n} \left( {\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}({\theta}_{n_1})) - \theta \right)  \\
-& \overset{d}{\to} \Ncal\left( 0, 
-1/\eta(0) \right) 
-\end{align*}
-by Slutsky's theorem.
-\end{proof}
-%
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=10cm, height=6cm,
-xmin = 0, xmax=800, 
-restrict y to domain = 0:3,
-ymin = 0,
-ymax = 3.4,
-samples=10, 
-xlabel= $n$,
-ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
-%xtick={-3,-2,-1,0,1,2,3},
-%xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,1,1.57},
-yticklabels={0,1,$\pi/2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-
-\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{asymptotically optimal};
-
-%\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
-
-\addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{single interaction};
-
-\end{axis}
-\end{tikzpicture}
-%\begin{tikzpicture}
-%\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
-%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left({\theta}_n - \theta \right)^2$};
-%\node[scale = 0.7] at (0,-2.4) {$n$};
-%\end{tikzpicture}
-\caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.
-In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$.
-The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage.
-\label{fig:adaptive_error}  }
-\end{center}
-\end{figure}
-
-\section{Distributed Estimation \label{sec:distributed}}
-In this section, we now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii) where  each one-bit message $B_i$ is only a function of its private sample $X_i$.
-In this case, the $i$th encoder is fully characterized its \emph{detection region}, defined as
-\[
-A_i = \left\{ x \in \mathbb R \,:\, B_i(x) = 1 \right\}.
-\]
-Consequently, $B_i$ is of the form
-\[
-B_i = \begin{cases} 1 & X_i \in A_i, \\
--1 & X_i \notin A_i,
-\end{cases} \quad i\in \mathbb N,
-\]
-where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\par
-
-As a first step, we provide conditions under which the messages $B_1,B_2,\ldots$ define a local asymptotic normal family.
-
-\begin{thm} \label{thm:LAN1}
-For $n \in \mathbb N$ and $A_n \subset \mathbb R$,  define
-\begin{equation}
-\label{eq:precision_general}
-L_n(A_1,\ldots,A_n;\theta) \triangleq \frac{1}{n} \sum_{i=1}^n \frac{ \left(\frac{d}{d \theta} \Prob(X_i \in A_i) \right)^2 }{ \Prob(X_i \in A_i)\left(1- \Prob(X_i \in A_i) \right) }. 
-\end{equation}
-Consider the following conditions:
-\begin{itemize}
-\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is a log-concave, differentiable and symmetric density function such that $\eta(x)$ is unimodal.
-\item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
-\item[(iii)] The limit 
-\begin{equation}
-\label{eq:LAN_lim}
-\kappa(\theta) \triangleq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
-\end{equation}
-exists. 
-\end{itemize}
-For $i=1,\ldots,n$ set
-\[
-B_n = \begin{cases} 1 & X_n \in A_n, \\
--1 & X_n \notin A_n. 
-\end{cases} 
-\]
-For any $\theta$, $f(x)$ and a sequence of sets $A_1,A_2,\ldots$ such that (i)-(iii) hold, and any $h\in \mathbb R$, we have
-\begin{align*}
-& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (B_1,\ldots,B_n) }{
-\mathbb P_{\theta} (B_1,\ldots,B_n)} \\
-& \overset{d}{\longrightarrow} \Ncal\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
-\end{align*} 
-\end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:LAN1}. 
-\end{proof}
-
-Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}. 
-%
-Among these conditions, (iii) is arguably the strongest and hardest to verify.
-As we show in Section~\ref{subsec:threshold} below, this condition is satisfied, for example, when $A_1, \ldots,A_n$ are half lines whose starting points are drawn independently from some probability measure on $\mathbb R$.
-Similar ideas imply that condition (iii) holds whenever we choose the intervals consisting each $A_i$ according to some pre-specified distribution.
-\par
-%
-An important conclusion of  Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models \cite{van2000asymptotic}):
-\begin{cor} \label{cor:LA_minimax}
-Let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
-Then for any symmetric and quasi-convex function $L$,
-\begin{align*}
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right]
-\\
-& \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
-\end{align*}
-where $Z \sim \Ncal(0,1)$. In particular, for $L(x) = x^2$,
-\begin{align*}
-\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( {\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
-\end{align*}
-\end{cor}
-%
-Corollary~\ref{cor:LA_minimax} says that when the messages define a LAN model, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model at $\theta$.
-This fact poses the upper bound of $\kappa(\theta)\sigma^2$ for the ARE of estimators in such models.
-\par
-
-Next, we show that under LAN no estimator can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly for all $\theta \in \Theta$.
-
-\subsection{Non-existence of a Uniformly Optimal Strategy}
-We now show that under LAN models, the optimal minimal risk $1/\eta(0)$ can only be attained at a finite number of points within $\Theta$.
-This fact implies in particular that, unlike in the adaptive setting, no distributed estimation scheme has ARE of $\eta(0)\sigma^2$ for all $\theta \in \Theta$.
-
-\begin{thm} \label{thm:non_existence}
-Under conditions (i)-(iii) in Theorem~\ref{thm:LAN1}, assume that each $A_i$ is a union of at most $K$ intervals.
-The number of points $\theta \in \Theta$ satisfying $\kappa(\theta) = \eta(0)$ is at most $2K$.
-\end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:non_existence}.
-\end{proof}
-
-We next consider the case where each detection region is a half-open interval, i.e., the $i$th message is obtained by comparing $X_i$ against a single threshold.
-As we explain next, the existence of a density for the sequence of thresholds is enough to establish local asymptotic normality and leads to a closed form expression for the precision parameter and the ARE.
-
-%In the adaptive setting, it follows from Theorem~\ref{thm:sgd} that messages of this kind with appropriately chosen thresholds lead to an estimator with the optimal ARE of $\eta(0)sigma^2$.
-However, Theorem~\ref{thm:non_existence} implies that such ARE can only be attained for a negligible subset of the parameter space.
-As we shall see next, messages obtained via a comparison against a sequence of thresholds cannot attain the optimal efficiency one more than a single point of $\Theta$.
-
-\subsection{Threshold Detection \label{subsec:threshold}}
-Assume now that each $B_i$ is of the form
-\begin{equation}
-\label{eq:threshold_message}
-B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
--1 & X_i > t_i,
-\end{cases}  
-\end{equation}
-where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder.
-In other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and $\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$.
-It follows that
-\begin{equation}
-L_n(A_1,\ldots,A_n;\theta) = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
-\label{eq:Ln_threshold}
-\end{equation}
-A natural condition for the existence of the limit \eqref{eq:Ln_threshold} as $n\to \infty$ is that the empirical distribution of the threshold values converges to a probability measure.
-Specifically, for an interval $I \subset \mathbb R$ define
-\[
-\lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
-\]
-Theorem~\ref{thm:LAN1} implies:
-\begin{cor} \label{cor:LAN_thresh}
-Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$.
-Then $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a LAN family with precision parameter
-\[
-\kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
-\]
-\end{cor}
-The condition that $\lambda_n$ converges to a probability measure is satisfies, for example, whenever the $t_1,\ldots,t_n$s are drawn independently from a probability distribution $\lambda(dt)$ on $\mathbb R$.
-\par
-Due to local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by 
-${\theta}^{ML}_n$, is local asymptotic minimax in the sense that 
-\[
-\sqrt{n} \left( {\theta}^{ML}_n - \theta \right) \overset{d}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
-\]
-It follows that when the density of the threshold values converges to a probability measure, the ARE of the ML estimator is $\kappa(\theta)\sigma^2$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-We note that ${\theta}^{ML}_n$ is given by the root of
-\begin{equation}
-\label{eq:ML}
-\sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) },  
-\end{equation}
-which is the derivative of the log-likelihood function.
-This root is unique since the log-likelihood function is concave.
-Furthermore, for any $n \in \mathbb R$, we have that ${\theta}^{ML}_n  \in [t_{(1)}, t_{(n)}]$ where $t_{(i)}$ denotes the $i$th element of $\{t_1,t_2\ldots\}$.
-Therefore, if $\{t_1,t_2\ldots\}$ is bounded (for example $\{t_1,t_2\ldots\} \subset \Theta$), then
-\[
-\lim_{n\to \infty} n \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
-\] 
-so that the ML estimator attains the local asymptotic MSE of Corollary~\ref{cor:LA_minimax}. \par
-%
-Since $\eta(x)$ attains its maximum at the origin, we conclude that
-\[
-\kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
-\]
-This upper bound on $\kappa(\theta)$ implies that the ARE of any distributed estimator based on a sequence of threshold detectors does not exceed $\eta(0)\sigma^2$, a fact that agrees with the lower bound under adaptive estimation derived in Theorem~\ref{thm:adpative_lower_bound}.
-%
-This upper bound on $\kappa(\theta)$ is attained only when $\lambda$ is the mass distribution at $\theta$.
-Since $\theta$ is apriori unknown, we conclude that estimation in the distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting.
-In other words, the ability to choose the threshold values in an adaptive manner based on previous messages strictly improves relative efficiency compared to a non-adaptive threshold selection.
-\par
-
-%We conclude that when the density of the threshold values converges to a probability measure, the ARE of the ML is $\kappa(\theta)$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-
-%
-We conclude this section by considering the density of the threshold values that maximizes the ARE $\kappa(\theta)$ under the worst choice of $\theta \in \Theta$.
-
-\subsection{Minimax Threshold Density}
-The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta = [-T,T]$ is given as the solution to the following optimization problem:
-\begin{align}
-\label{eq:var_cvx_minimax}
-\begin{split}
-\mathrm{maximize} \quad &  \inf_{\theta \in [-T,T]} \int \eta(t-\theta) \lambda(dt)
-\\ 
-\mathrm{subject~to} 
-\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
-\end{split}
-\end{align}
-The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program.
-We denote by $\kappa^\star(T)$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum.
-%
-%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
-%\begin{align}
-%\label{eq:cvx_minimax}
-%\begin{split}
-%\mathrm{maximize} \quad &  K \\ 
-%\mathrm{subject~to} 
-%\quad &  K \leq \mathbf H\lambda \\
-%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
-%\end{split}
-%\end{align}
-%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
-%\begin{rem}
-%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$.
-Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points.
-Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using
-%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
-%\end{rem}
-
-Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$.
-The minimal asymptotic risk $\kappa^\star(\theta)$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $T$.
-Also illustrated in these Figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
-\begin{align}
-& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
- \\
-& = 
-\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
-= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
-\end{align}
-From Corollary~\ref{cor:LAN_thresh}, we conclude that the ARE under a uniform distribution is $\kappa_\unif \sigma^2$. \par
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-title = {$\sigma/T = 1/2$},
-ytick={0,0.1,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.6,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/T = 1/5$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.5},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.5},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.3,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma / T = 1/10$},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.2},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.2},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.15,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma / T = 1/20$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:minimax_support}
-Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in \Theta = [-T,T]$.
-%
-The continuous curve (red) represents the reciprocal of the asymptotic risk for at a fixed $\theta \in \Theta$ under the optimal density, so the minimax risk is the inverse of its minimal value.
-The dashed curve (green) is the reciprocal of the asymptotic risk for a fixed $\theta$ under a uniform distribution of threshold values over $\Theta$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
-}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmax=2.5, 
-xmode = log,
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=1, 
-xlabel= {$\sigma/T$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,0.637,1},
-yticklabels={0,$2/\pi$,1},
-ylabel = {$\ARE$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{optimal threshold density};
-
-\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{uniform threshold desnity};
-\end{axis}
-\end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \Ncal(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
-The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
-}.
-\end{center}
-\end{figure}
-
-%We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
-Next, we prove that with any set of messages obtained via a distributed strategy, there exists at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-title = {$\sigma/\sigma_{\theta} = 1$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 2$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma/\sigma_{\theta} = 3$},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 4$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:opt_density}
-Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=b^2/3$ is the variance of the prior.
-}
-\end{center}
-\end{figure}
-
- We consider now the problem of minimizing the asymptotic Bayes risk $
-R_{\pi,\lambda} \triangleq \mathbb E  K^{-1}(\theta)$ over all probability measures $\lambda(dt)$ with support in $\mathbb R$. This optimization problem can be written as follows:
-\begin{align}
-\label{eq:cvx_average}
-\begin{split}
-\mathrm{minimize} \quad & R_{\pi,\lambda} =  \int \frac{\pi(d\theta)}{ \int \eta \left( t-\theta\right) \lambda(dt)}. \\ 
-\mathrm{subject~to} \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) =1. 
-\end{split}
-\end{align}
-We denote by $R^\star_{\pi}$ the minimal value of the objective function in \eqref{eq:cvx_average}.
-Since the function $x \rightarrow 1/x$ is convex for positive values, \eqref{eq:cvx_average} defines a convex optimization problem in $\lambda$ whose solution depends on the prior $\pi$.
-The solution to this problem is approximated by considering $\lambda$ and $\pi$ over a discrete set.
-On Figure~\ref{fig:opt_density} we illustrate the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distributon ($P_X = \Ncal(\theta, \sigma^2)$) and the prior on $\theta$ is uniform over $\Theta = [-b,b]$.
-Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
-\par
-\begin{figure}
-\begin{center}
-
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = 0, xmax=2, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 10,
-samples=1, 
-xlabel= {$\sigma/\sigma_\theta$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,1.5708,5},
-yticklabels={0,$\pi/2$,5},
-ylabel = {$R_{\pi}^\star/\sigma^2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-\addplot[color = black, dashed] {3.14159 / 2};
-\end{axis}
-\end{tikzpicture}
-\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \Ncal(\theta, \sigma^2)$ under an optimal threshold distribution $\lambda^\star$, when the prior $\pi$ is the uniform distribution over $\Theta = [-0.5,0.5]$.
-%
-%versus $\sigma/\sigma_\theta = 2\sqrt{3}\sigma$.
-The distribution $\lambda^\star$ is the minimizer of \eqref{eq:cvx_average}.
-It is illustrated for various cases in Fig.~\ref{fig:opt_density}.
-The dashed curve represents the upper bound \eqref{eq:upper_bound}.
-\label{fig:dist_bound_uniform}  }
-\end{center}
-\end{figure}
-
-As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \Ncal(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution.
-In this case, the ML estimator reduces to the estimator ${\theta}_n$ of \eqref{eq:estimator_naive}.
-As the following proposition shows, the Bayes risk for this choice of $\lambda$ is maximal, and thus provides an upper bound on the Bayes risk under any $\lambda$.
- \eqref{eq:cvx_average}. 
-\begin{prop}\label{prop:upper_bound}
-For any prior $\pi(d\theta)$ and $\theta_0$ in the support of $\eta(x)$ we have
-\begin{equation} 
-\label{eq:upper_bound}
-R_\pi^\star  \leq 
- \int \frac{\pi(d\theta)}{\eta \left( \theta_0 - \theta \right)},
-\end{equation}
-Furthermore, assuming that $\theta_0 = \mathbb E \theta$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
-\begin{equation}
-\label{eq:bound_Taylor}
-R^\star_\pi \leq \frac{1}{4 f^2(0)} + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right) \sigma_\theta^2 + O(\sigma_\theta^3).
-\end{equation}
-\end{prop}
-\begin{proof}
-The function $x \rightarrow 1/x$ is convex for positive values, hence Jensen's inequality implies
-\[
-\left( \int \eta \left( t-\theta\right) \lambda(dt) \right)^{-1}  \leq \int  \frac{ \lambda(dt)}{ \eta \left( t-\theta\right)  }. 
-\]
-Therefore, the expected value of $\kappa^{-1}(\theta)$ satisfies
-\begin{align}
-\ex{  \frac{1}{\kappa(\theta)}}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
-\end{align}
-The bound \eqref{eq:upper_bound} is obtained by taking $\lambda$ to be a mass distribution at any $\theta_0$ in the support of $\eta(x)$.
-Finally, \eqref{eq:bound_Taylor} is obtained by expanding $1/\eta(x)$ to a third order Taylor series around zero
-%\[
-%1/\eta(x) = \frac{1}{4f^2(0)}  + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right)  x^2 + O(x^3),
-%\]
-and taking its expectation with respect to $\pi$ at $x=\theta_0-\theta$. 
-\end{proof}
-We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so the choice $\theta_0 = \ex{ \theta}$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
-The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$.
-The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $\kappa^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.
-
-\begin{example} \label{ex:bound}
-In the normal case $P_X = \Ncal(\theta, \sigma^2)$, the bound in \eqref{eq:bound_Taylor} implies 
-\[
-\frac{R^\star_\pi}{\sigma^2}  \leq \frac{\pi}{2} + \left( \frac{\pi}{2} -1 \right) \left( \frac{ \sigma_\theta}{\sigma} \right)^2 + O \left(  \frac{\sigma_\theta} { \sigma} \right)^3. 
-\]
-It follows that the ARE approaches its maximal value of $2/\pi$ whenever $\sigma_\theta/\sigma$ is small.
-The exact value of \eqref{eq:upper_bound} in this case, as well as the Bayes ARE with the optimal threshold density $\lambda^\star$ for a uniform $\pi$, are illustrated in Fig.~\ref{fig:dist_bound_uniform}.
-%i.e., each encoder simply reports "$1$" or "$-1$" whenever $X_i$ is larger or smaller than $\theta_0$, respectively.
-Intuitively, an accurate estimation of $\theta$ in this case is possible only if a sufficient mix of ''$1$''s and ''$-1$''s is obtained from the sample.
-When $\sigma_\theta^2$ is high compared to $\simga^2$, one of the events $"1"$ or "$-1"$ becomes too rare to
-\end{example}
-
-\section{Conclusions \label{sec:conclusions}}
-We considered the MSE risk in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
-%
-In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency (ARE) larger than that of the median of the samples.
-We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median.
-%We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
-\par
-In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and ARE. 
-%
-We conclude that under such conditions, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in the distributed setting.
-%
-We further considered the special case of messages obtained by comparing against a prescribed sequence of thresholds.
-We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.
-
-%\section*{ACKNOWLEDGMENT}
-%This research is supported in parts by...
-%Tsachy Weissman, Stefano Rini, Robert Gray.
-
-\onecolumn
-
-\appendix
-
-\section{}
-
-\subsection{Proof of Proposition~\ref{prop:ceo_lower_bound}
-\label{app:proof:prop_ceo_lower_bound}}
-
-First, we note that when $f(x) = \Ncal(0,\sigma^2)$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$, our distributed setting reduces to the Gaussian CEO problem with $R_1=\ldots = R_n =1$ and $k=1$.
-Therefore, any MSE attained in our distributed setting is also attained by the CEO and thus the optimal CEO strategy (with arbitrary $k$) provides a lower bound to the MSE in our setting.
-\\
-
-Consider the minimal MSE $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
-from \cite[Eq. 10]{chen2004upper}:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-For the special case of $R_\Sigma = n$ and $L=n$, we get
-\begin{equation} \label{eq:ceo_optimal_sumrate2}
-n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, this $D^\star$ provides a lower bound to the CEO MSE with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
-\[
-D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO MSE while enforcing the condition $R_1=\ldots = R_n = 1$.
-Indeed, an upper bound for the CEO MSE under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
-\[
-D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
-\]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.
-
-\subsection{Proof of Lemma~\ref{lem:bound_intervals_delta} \label{proof:lem:bound_intervals_delta}}
-
-%\begin{lem} \label{lem:bound_intervals}
-%Let $f(x)$ be a log-concave, symmetric, and differentiable density such that $\eta(x)$ is strongly unimodal. For any $x_1 > \ldots > x_n \in \mathbb R$, 
-%\begin{equation}
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \max_i \eta(x_i). \label{eq:lem_bound_intervals}
-%\end{equation}
-%In particular, if $|x_i|>\epsilon > 0$ for all $i=1,\ldots,n$, then 
-%\[
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \eta(\epsilon) < 0. 
-%\]
-%\end{lem}
-
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-so 
-\[
-\eta(x) =  \frac{  \left(\delta_1(x) \right)^2}{\Delta_1(x)
-(1-\Delta_1(x))}
-= \frac{  \left( f (x) \right)^2}{ F(x)\left(1-F(x)\right)^2}. 
-\]
-We use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:lem_bound_intervals_delta} is bounded from above by $\max_i \eta(x_i)$. The case $n=1$ is trivial. Assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^2} 
-{\Delta_n \left(1- \Delta_n \right) } \leq \max_i \eta(x_i)
-\label{eq:lem_bound_intervals_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  2 \log \delta_N -  \log \Delta_N -  \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(-1)^{k+1} f(x_k)}{1-\Delta_N },
-\]
-and we conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-%
-Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable. We have 
-\[
-\frac{f'(x)}{f(x)} = c'(x), \quad x\in \mathbb R,
-\]
-which is anti-symmetric, non-negative for $x<0$,  non-positive for $x>0$, and non-increasing since $c(x)$ is concave.
-Therefore, if $c'(x_i) = c'(x_{i+1})$ for some $i =1,\ldots,N-1$, then either (1) $x_i = x_{i+1}$ or (2) $c'(x)$ is the zero function.
-Since (2) violates the assumption that $f(x)$ is a density function, we conclude that $c'(x)$ is an injection.
-%
-As a result, \eqref{eq:gradient_zero} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_proof} equals $\eta(x_1) = \max_i \eta(x_i)$ hence the statement holds.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$, or  $x_i, x_{i+1}$ for some $i$.
-It is left to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Under case (1) we have
-\begin{align*}
-\lim_{x_N \to -\infty} \frac{  \delta_N^2} 
-{\Delta_N \left(1- \Delta_N \right) }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^2} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)} ,
-\end{align*}
-which is smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis. Under case (2) we have
-\begin{align*}
-&  \lim_{x_1 \to \infty}
-\frac{ \delta_N} 
-{\Delta_N\left(1- \Delta_N \right) } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right) \left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right) }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^2 } 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right) },
-\end{align*}
-where $x'_{m} = x_{m+1}$. The last expression is also smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis.  \QEDA \\
-
-\subsection{Proof of Theorem~\ref{thm:adpative_lower_bound}
-\label{proof:thm:adpative_lower_bound}
-}
-
-We first prove the following lemma:
-\begin{lem} \label{lem:fisher_bound}
-Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that $\eta(x)$ is unimodal. For a Borel measurable $A$ set, 
-\[
-M(X) = \begin{cases} 1,& X \in A, \\
--1, & X \notin A.
-\end{cases}
-\]
-Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $\eta(0)$.
-\end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
-When $f(x)$ is the normal density function, this lemma follows from \cite[Thm.
-3]{Barnes2018}.
-The proof below is based on a different techique than in \cite{Barnes2018}, and is valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}.
-\\
-
-The Fisher information of $M$ with respect to $\theta$ is given by
-\begin{align}
-I_\theta & =  \mathbb E \left[ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta \right] \nonumber \\
-& = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
-& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\
-& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\ 
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
-\end{align}
-where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$.
-Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
-\[
-\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
-\]
-which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$.
-It is therefore enough to proceed in the proof assuming that $A$ is of the form
-\[
-A = \cup_{j=1}^k (a_j,b_j),
-\]
-with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
-\begin{align*}
-\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
-& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
-\end{align*}
-so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
-\begin{align}
-& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
-{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
-& \times \frac {1} 
-{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
-\label{eq:lemma_J}
-\end{align}
-It follows from Lemma~\ref{lem:bound_intervals_delta} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $4f^2(0)$.  \QEDA \\
-
-We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
-\begin{equation}
-\label{eq:general_messages}
-B_i = \begin{cases}
-X_i \in A_i & 1, \\
-X_i \notin A_i & -1,
-\end{cases} 
-\end{equation}
-where $A_i \subset \mathbb R$ is a Borel measurable set. 
-%Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
-Consider the conditional distribution $P({B^n|\theta})$ of $B^n$ given $\theta$. We have 
-\begin{align}
-P\left( B^n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
-\end{align}
-where $P\left(B_i =1 | \theta, B^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B^n$ with respect to $\theta$ is given by 
-\begin{align}
-I_\theta(B^n) = \sum_{i=1}^n I_\theta (B_i|B^{i-1}),
-\label{eq:fisher_information}
-\end{align}
-where $I_\theta (B_i|B^{i-1})$ is the Fisher information of the distribution of $B_i$ given $B^{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B^{i-1}) \leq 4f^2(0)$.
-The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
-\begin{align*}
-\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(B^n) + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
-& \geq \frac{1}{ 4f^2(0) n + I_0}.
-\end{align*}
-
-\QEDA
-
-\subsection{Proof of Theorem~\ref{thm:sgd}
-\label{proof:thm:sgd}
-}
-The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.
-
-\subsubsection*{Proof of (i)}
-%Specifically, (i) in Theorem~\ref{thm:sgd} 
-Consider the following simplified version of \cite[Thm. 4]{polyak1992acceleration}:
-\begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
-Let 
-\[
-X_i = \theta + Z_i,\quad i=1,\ldots,n,
-\]
-where the $Z_i$s are i.i.d. with zero means and finite variances. Define
-\begin{align}
-\begin{split}
-\theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
-\bar{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
-\end{split}
-\label{eq:Polyak_Juditsky_alg}
-\end{align}
-where in addition, assume the following: 
-\begin{enumerate}
-\item[(i)] There exits $K_1$ such that $\left| \varphi(x) \right| \leq K_1(1+|x|)$ for all $x\in \mathbb R$.
-\item[(ii)] The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions \eqref{eq:conditions1}.
-\item[(iii)] The function $\psi(x) \triangleq \ex{ \varphi(x+Z_1)}$ is differentiable at zero with $\psi'(0)>0$, and satisfies $\psi(0)=0$ and $x\psi(x) >0$ for all $x\neq 0$.
-Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
-\begin{equation}
-\label{eq:Polyak_Juditsky_cond3}
-\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
-\end{equation}
-\item[(iv)] The function 
-$\chi(x) \triangleq \ex{\varphi^2(x+Z_1)}$ is continuous at zero. 
-\end{enumerate}
-Then $\bar{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}({\theta}_n - \theta)$ converges in distribution to $\Ncal(0,V)$, where
-\[
-V = \frac{ \chi(0)} {\psi'^2(0)}. 
-\]
-\end{thm}
-
-Using the notation above, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have that $\chi(x) = \mathbb E \sgn^2(x+Z_1) = 1$, so $\chi(0) = 1$. In addition,
-\begin{align*}
-\psi(x) & = \ex{ \sgn(x+ Z_1) }= \int_{-\infty}^\infty \sgn(x+z) f(z) dz \\
-& = \int_{-x}^\infty f(z) dz -\int_{-\infty}^{-x} f(z) dz. 
-\end{align*}
-Using the symmetry of $f(x)$ around zero, it follows that $\psi'(x) = 2f(x)$ and thus $\psi'(0) = 2f(0)$.
-It is now easy to verify that the rest of the conditions in Theorem~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$.
-Since
-\[
-\frac{\chi(0)}{\psi'^2(0)} = \frac{1}{4 f^2(0)} = \frac{1}{\eta(0)},
-\]
-it follows from Theorem~\ref{thm:polyak_juditsky} that
-\[
-\sqrt{n}\left({\theta}_n-\theta \right) \overset{d}{\to} \Ncal \left(0, 1/ \eta(0)\right). 
-\]
-
-\subsubsection*{Proof of (ii)}
-We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\mathbb R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates.
-Then
-\begin{align}
-\label{eq:sgd_part2}
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
-\end{align}
-under $\Prob_{\theta,n}$.
-Under the assumption that $f(x)$ is continuously differentiable with a finite location Fisher information, the model $\{Z_n+ \theta\}_{n \in \mathbb N}$ is differentiable in quadratic mean \cite[Exm.
-7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
-\[
-\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
-\]
-where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$. 
- The random variable $L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)
-$ is bounded, and hence 
-\[
-\ex{ L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)} \to \ex{L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)}
-\]
-Any regular estimators in a LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}, hence in order to prove (ii) it is left to show that $\bar{\theta}_n$ is regular. For this purpose, 
-we use the following refinement of Theorem~\ref{thm:polyak_juditsky}, proof of which is given in Subsection~\ref{proof:thm:normal_expansion} below.
-%
-\begin{thm} \label{thm:normal_expansion}
-Set $\Delta_i = \theta_i - \theta$ and
-$\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \Delta_i$. Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{thm:polyak_juditsky}, there exists $K_1$ and $\lambda>0$ such that
-\begin{equation}
-\ex{\left| \varphi(Z_1) - \varphi(x+Z_1)  \right|} \leq K_1 |x|^{1+\lambda}
-\label{eq:PJ_additional_cond}. 
-\end{equation}
-Then:
-\begin{itemize}
-\item[(i)] \begin{equation}
-\sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1). \label{eq:normal_expansion_lem}
-\end{equation}
-where $o_{p,n}(1)$ converges in probability to $0$ as $n\to \infty$.
-\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite location Fisher information 
-\[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)} \right)^2 f(x) dx,
-\]
-then for any converging sequence $h_n \to h$,
-\[
-\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-h}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
-\]
-under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h_n/\sqrt{n}}$ with density $\prod_{i=1}^n f(x_i-h_n/\sqrt{n})$.
-\end{itemize}
-\end{thm}
-We now use this theorem to show regularity of $\bar{\theta}_n$. We have, 
-\begin{align*}
-& %\varphi(Z_1) - \varphi(x+Z_1) = 
-\sgn(Z_1) - \sgn(x + Z_1) \\
-& = \begin{cases}
-2 & Z_1 > 0,\, x+Z_1<0, \\
--2 & Z_1 <0, \, x+Z_1>0, \\
-0 & \text{otherwise}. 
-\end{cases}
-\end{align*}
-It follows that
-\begin{align*}
-\ex{ \left| \varphi(Z_1) - \varphi(x+Z_1) \right| }  \leq \Prob\left( |Z_1| < x  \right) \leq f(0) |x|, 
-\end{align*}
-hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
-\[
-\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = -2f(0) = -\psi'(0). 
-\]
-Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}.
-
-\subsubsection*{Proof of (iii)}
-%In order to prove part (ii) of Theorem~\ref{thm:sgd} 
-Consider the following result from \cite{polyak1990new}:
-\begin{thm}{\cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
-Let
-\begin{align} \label{eq:polyak_new_measurements}
-\begin{cases}
-U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = g'(U_{n-1})+Z_n \\
-\bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
-\end{cases}
-\end{align}
-Assume that the function $g(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative.
-In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \mathbb R$.
-Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution with a density for which the Fisher information exits.
-Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{thm:polyak_juditsky}-(iii) and satisfy the conditions there.
-Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$,
-and there exits $K_3$ such that 
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] \leq K_3(1+|x|^4). 
-\]
-Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
-\[
-V_n \triangleq \mathbb E \left[ \left(\bar{U}_n-x^\star \right)^2 \right] = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
-\]
-\end{thm}
-
-We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$. From \eqref{eq:polyak_new_measurements} we have
-\begin{align*} 
-U_n & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
-& = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
-\end{align*}
-so the estimator $\bar{U}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] = 1 \leq K_3(1+|x|^4)
-\]
-for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
-the conditions in Theorem~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
-In particular, $\psi'(0) = (2f(0))^{-2}$.
-Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$.
-Theorem~\ref{thm:polyak_new} implies that for any $\theta \in \mathbb R$,
-\[
-V_n = \mathbb E \left[ \left({\theta}_n-\theta \right)^2 \right]  = \frac{1}{4n f^2(0)} + o(n^{-1}).
-\]
-
-{\color{red}
-
-\subsection{Proof of Theorem~\ref{thm:normal_expansion}
-\label{proof:thm:normal_expansion}
-}
-\subsubsection*{Proof of (i)}
-The proof of part (i) of Theorem~\ref{thm:normal_expansion} requires the following two additional results from \cite{polyak1992acceleration}:
-\begin{lem}{\cite[Lem. 2]{polyak1992acceleration}}
-\label{lem:Polyak_expansion}
-Consider the process $\{\Delta_i^1 \}_{i=0}^\infty$ defined by
-\[
-\Delta^1_i = \Delta^1_{i-1} - \gamma_i (A \Delta_{i-1}+ \xi_i),\quad i=1,2\ldots.
-\]
-Assume that $A>0$ and condition (ii) of Theorem~\ref{thm:polyak_juditsky} holds. Then 
-\begin{equation}
-\label{eq:Polyak_expansion}
-\sqrt{n} \bar{\Delta}_n^1 = \frac{1}{\sqrt{n}}\sum_{i=0}^{n-1} \Delta_i^1 = \frac{\alpha_n \Delta_0^1}{\sqrt{n} \gamma_0}  + \frac{1}{\sqrt{n} A} \sum_{i=1}^{n-1} \xi_i + \frac{1}{\sqrt{n}}\sum_{i=1}^{n-1} w_i^n \xi_i,
-\end{equation}
-where $\alpha_n$ and $w_i^n$ are real numbers such that $|\alpha_n| \leq K$ and $|w_i^n|\leq K$ for some $K< \infty$, and 
-\[
-\lim_{n\to \infty} \frac{1}{n} \sum_{i=1}^{n-1} |w_i^n| = 0. 
-\]
-\end{lem}
-
-\begin{lem} \label{lem:PJ_converging_sum}
-Under the conditions of Theorem~\ref{thm:polyak_juditsky},
-\[
-\sum_{i=1}^\infty \frac{|\Delta_{i}|^{1+\lambda}}{\sqrt{i}} < \infty 
-\]
-almost surely. 
-\end{lem}
-Lemma~\ref{lem:PJ_converging_sum} follows from the proof of Theorem 2 in \cite{polyak1992acceleration}.
-
-We separate the proof of part (i) into two steps.
-\subsubsection*{Step I}
-The expansion \eqref{eq:normal_expansion_lem} holds for the process  $\{\bar{\Delta}^1_i\}_{i=1}^\infty$ defined as follows:
-\begin{align} \label{eq:Polyak_expansion_lem1_alg}
-& \Delta_i^1  = \Delta_{i-1}^1 - \gamma_i \psi'(0) \Delta_{i-1}^1 - \gamma_i \varphi(Z_i), \qquad
- \delta_0^1 = \Delta_0\\
-& \bar{\Delta}^1_i = \frac{1}{n}\sum_{i=0}^{n-1} \Delta^1_i.
-\end{align}
-
-In order to prove this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$.
-The first expression on the RHS on \eqref{eq:Polyak_expansion} goes to zero in variance.
-In addition,
-\begin{align*}
-& \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }  = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
-& = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0. 
-\end{align*}
-We obtain
-\begin{equation}
-\sqrt{n} \bar{\Delta}^1_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1), \label{eq:Polyak_expansion_aux_process}
-\end{equation}
-
-\subsubsection*{Step II} $\bar{\Delta}_n$ and $\bar{\Delta}^1_n$ are asymptotically equivalent. \\
-
-From \eqref{eq:Polyak_Juditsky_alg} and \eqref{eq:Polyak_expansion_lem1_alg}, the difference $\delta_i = \Delta_i - \Delta_i^1$ satisfies the recursion
-\[
-\delta_i = \delta_{i-1} - \gamma_i \psi'(0) \delta_{i-1} + \gamma_i \left( \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i) \right),
-\]
-where $\delta_0 = 0$. Use Lemma~\ref{lem:Polyak_expansion} with $\xi_i =  \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i)$ to obtain
-\begin{align}
-& \sqrt{n}\bar{\delta}_n = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \xi_i  \\
-& = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \label{eq:PJ_proof1} \\
-& + 
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi(\Delta_{i-1})  + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i)
-\right) \label{eq:PJ_proof2}
-\end{align}
-For the term \eqref{eq:PJ_proof1} and using \eqref{eq:Polyak_Juditsky_cond3}, there exists $K_1$ and $K_2$ such that 
-\begin{align*}
-& \eqref{eq:PJ_proof1}
-\leq K_1 \sum_{i=1}^\infty \frac{1}{\sqrt{i}} \left| \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \right| \\
-& \leq K_2 \sum_{i=1}^\infty \frac{ |\Delta_i|^{1+\lambda}}{\sqrt{i}}. 
-\end{align*}
-
-Lemma~\ref{lem:PJ_converging_sum} shows that 
-\begin{align}
-\sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}}  < \infty \label{eq:PJ_converging_sum},
-\end{align}
-hence the Kronecker lemma implies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \to 0.
-\]
-For the term \eqref{eq:PJ_proof2}, set 
-\[
-\epsilon_i \triangleq \psi(\Delta_{i-1}) + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i).
-\]
-For $a>0$ and $n \in \mathbb N$, define the event
-\[
-A_{n,a} \triangleq \left\{ \sum_{i=1}^{n-1} \frac{|\epsilon_i|}{\sqrt{i}}  \geq a  \right\}. 
-\]
-By Markov's inequality, we have
-\begin{align}
-\ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } \leq \frac{1}{a} \sum_{i=1}^{n-1} \frac{ \ex{|\epsilon_i| \Delta_{i-1} \mid }}{\sqrt{i}}. \label{eq:PJ_proof_3}
-\end{align}
-Using \eqref{eq:Polyak_Juditsky_cond3} and \eqref{eq:PJ_additional_cond}, there exists $K'$ and $\lambda'>0$ such that
-\begin{align*}
-& \ex{ |\epsilon_i| | \Delta_{i-1}}  \leq |\psi(\Delta_{i-1})| + \left| \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i) \right|  \\
-& \leq K' |\Delta_{i-1}|^{1+\lambda}. 
-\end{align*}
-Plugging this bound in \eqref{eq:PJ_proof_3} and using Lemma~\ref{lem:PJ_converging_sum},we obtain 
-\[
-\Prob(A_{n,a}) = \ex{ \ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } } \leq  \frac{K''}{a}
-\]
-for some constant $K''$. It follows that for any $\epsilon$, we may choose $a$ large enough such that 
-\[
-\sup_{n} \Prob(A_{n,a}) < \epsilon.
-\]
-This implies that for any $\epsilon>0$,
-\[
-\Prob \left( \sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty \right) \geq 1-\epsilon,
-\]
-and hence 
-\[
-\sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty
-\]
-almost surely. The Kronecker lemma now implies 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left|\epsilon_i\right| \to 0,
-\]
-hence the term \eqref{eq:PJ_proof2} satisfies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right) \epsilon_i \leq \frac{K'''}{\sqrt{n}} \sum_{i=1}^{n-1} |\epsilon_i| \to 0. 
-\]
-This conclude the proof of part (i).
-
-\subsubsection*{Part (ii)}
-Use \eqref{eq:normal_expansion_lem} to write
-\[
-\sqrt{n} \bar{\Delta}_n = G_n + o_{p,n}(1),
-\]
-where
-\[
-G_n \triangleq -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n} \varphi(Z_i). 
-\]
-From \cite[Exm.
-7.8]{van2000asymptotic}, the location model $f(x-\theta)$ with continuously differentiable $f(x)$ is differentiable in quadratic mean with the score function $-f'(x-\theta)/f(x-\theta)$.
-This fact implies the following expansion \cite[Thm.
-7.2]{van2000asymptotic}:
-\begin{align}
-\label{eq:PJ_LAN}
-& \log \frac{\Prob^n_{h_n/\sqrt{n}}}{\Prob^n_0} (Z_1,\ldots,Z_n) =  \log \prod_{i=1}^{n} \frac{f(Z_i-h_n/\sqrt{n})}  {f(X_i-\theta)} = h J_n - \frac{1}{2}h^2 I_{\theta} + o_{p,n}(1),
-\end{align}
-for any converging sequence $h_n \to h$, 
-where 
-\[
-J_n \triangleq -\frac{1}{\sqrt{n}} \sum_{i=1}^n \frac{f'(Z_i)}{f(Z_i)} .
-\]
-We have
-\begin{align*}
-& \ex{ G_n J_n} = \frac{1}{\psi'(0)}\frac{1}{n} \sum_{i=1}^n \ex{ \varphi(Z_i) \frac{f'(Z_i)}{f(Z_i)} }  \\
-& = \frac{1}{ \psi'(0)} \ex{ \varphi(Z_1) \frac{f'(Z_1)}{f(Z_1)}} =  \frac{1}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx , 
-\end{align*}
-Since both $\sqrt{n}G_n$ and $\sqrt{n}J_n$ are the sum of $n$ i.i.d. random variables with zero mean and finite variance, we obtain, from the central limit theorem and Slutsky's theorem, that
-\[
-\left(\sqrt{n} \bar{\Delta}_n, \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} \right) \overset{d}{\to} \Ncal \left( \left(0,-\frac{h^2}{2} I_\theta \right),  \begin{pmatrix}
-\frac{\chi(0)}{\psi'^2(0)} & \frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx \\
-\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx & h^2 I_\theta 
-\end{pmatrix}  \right)
-\]
-Le Cam's third lemma \cite[Exm. 6.7]{van2000asymptotic} implies that under $\Prob^n_{h/\sqrt{n}}$, 
-\[
-\sqrt{n}\bar{\Delta}_n \overset{d}{\to} \Ncal\left(\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx,  \frac{\chi(0)}{\psi'^2(0)} \right).
-\]
-
-\QEDA
-}
-
-\subsection{Proof of Theorem~\ref{thm:LAN1}
-\label{proof:thm:LAN1}
-}
-The log probability mass distribution of $B^n=(B_1,\ldots,B_n)$ is given by
-\begin{align*}
-& \log \Prob_\theta(b^n) = \sum_{i=1}^n \left( \frac{b_i+1}{2} \log  \Prob(X_i\in A_i) + 
-\frac{1-b_i}{2} \log \Prob(X_i\in A_i) \right), \quad b^n \in \{-1,1\}^n. 
-\end{align*}
-Consequently, 
-\begin{align}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) } = \sum_{i=1}^n    \frac{b_i+1}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} + 
-\sum_{i=1}^n  \frac{1-b_i}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}. 
-\label{eq:LAN_proof1}
-\end{align}
-For each $i=1,\ldots,n$, write 
-\[
-A_i = \bigcup_{k=1}^{K_i} \left(t_{i,k},t_{i,k+1} \right),
-\]
-where $t_{i,1}<\ldots<t_{i,K_i}$ and, with a slight abuse of notation, $t_{i,1}$ and $t_{i,K_i}$ may also be $-\infty$ or $+\infty$, respectively. Thus
-\[
-\Prob_{\theta}(X_i \in A_i) = \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta).
-\]
-In particular, since $f$ is differentible, $\Prob_{\theta}(X_i \in A_i)$ is twice differentiable, and we may write
-\begin{align*}
-\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)  = \Prob_{\theta} (X_i \in A_i) + \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \frac{h}{\sqrt{n}} + o(h), 
-\end{align*}
-and thus
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} = \log \left(1 + \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} + o(h) \right) \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2 + o(h^2).
-\end{align*}
-Similarly, we have
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 + o(h^2).
-\end{align*}
-From \eqref{eq:LAN_proof1} we obtain
-\begin{align*}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
-\left( 
-\frac{b_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-b_i}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}   \right) \\
- & - \frac{h^2}{2n} 
- \sum_{i=1}^n 
-\left( 
- \frac{b_i+1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-b_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 \right) + o(h^2) \\
-\end{align*}
-%
-Noting that 
-\[
-\frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} = \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)},
-\]
-the proof is completed by proving the following two claims:
-\begin{itemize}
-\item[I.] 
-For $i=1,\ldots,n$ denote 
-\[
-U_i = \frac{B_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-B_i}{2}  \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}. 
-\]
-Then 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0, \kappa(\theta) \right). 
-\]
-\item[II.]
-For $i=1,\ldots,n$ denote 
-\[
-V_i =  \frac{B_i-1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-B_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2.
-\]
-Then 
-\[
-\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} \kappa(\theta). 
-\]
-\end{itemize}
-\subsubsection*{Proof of Claim I}
-First note that 
-\begin{align*}
-\mathbb E  [U_i] & = 
- \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=1)   + 
- \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=-1)  = 0. 
-\end{align*}
-In addition,
-\begin{align*}
-& \mathbb E U_i^2 = 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2  \Prob (B_i=1)   + 
-\left( \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2 \Prob (B_i=-1) \\
-& =
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)} +  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)} \\
- & =  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left(1-\Prob_{\theta}(X_i \in A_i) \right)} 
-\end{align*}
-Therefore
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 = L_n(A_1,\ldots,A_n) \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ such that the limit above exists.
-We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition for his version of the central limit time: for any $\delta>0$ we have that
-\begin{align*}
-& \mathbb E \left| U_i \right|^{2+\delta} =
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} 
-\end{align*}
-and
-\begin{equation}
-\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} } { \left( \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta} = 
-\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
-\label{eq:Lyaponov}
-\end{equation}
-Next, we claim that there exits $\delta>0$ and $K>0$, that are independent of $n$, such that
-\begin{align}
-\frac{1}{n} \sum_{i=1}^n \mathbb E  |U_i|^{2+\delta}  < M \label{eq:Lyaponov_num}
-\end{align} 
-for all $n$ large enough. To see this, note that
-\begin{align*}
-& \mathbb E |U_i|^{2+\delta} = 
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}  \\
-  &  = \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} } 
-  \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \\
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}, 
-\end{align*}
-where the last transition is because 
-\[
- \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \leq 1. 
-\]
-We now use the fact that each $A_i$ is a finite union of interval and consider the following lemma, proof of which is given in Appendix~\ref{proof:lem:bound_intervals_delta}.
-\begin{lem} \label{lem:bound_intervals_delta}
-Let $f(x)$ be a log-concave, symmetric, and differentiable PDF such that $\eta(x)$ is unimodal.  There exists $\delta>0$ such that for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, 
-\begin{equation}
-\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^{2+\delta} }
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} } 
-\leq  2^\delta f^{2+\delta}(0). 
-\label{eq:lem_bound_intervals_delta}
-\end{equation}
-\end{lem}
-
-Lemma~\ref{lem:bound_intervals_delta} implies 
-\begin{align*}
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} = \frac{\left| \sum_{k=1}^{K_i} (-1)^k f(x_{i,k}-\theta) \right|^{2+\delta} }
-  { \left( \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta} \left( 1 - \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta}} \\
-  & \leq 2^\delta f^{2+\delta}(0). 
-\end{align*}
-In particular, we conclude that 
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} \leq 2^\delta f^{2+\delta}(0), 
-\]
-and thus for any $\delta>0$ the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we conclude that 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0,\kappa(\theta) \right). 
-\]
-
-\subsubsection*{Proof of Claim II} 
-We have:
-\begin{align*}
-\mathbb E V_i  & = 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)}  
-+ 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)}  \\
- & = 
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left( 1-\Prob_{\theta}(X_i \in A_i) \right)}  
-\end{align*}
- We conclude that:
-\begin{equation} \label{eq:LAN_limit_cond}
-\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =   L_n(A_1,\ldots,A_n)  \to \kappa(\theta)
-\end{equation}
-Since the $V_i$s are independent of each other, Kolmogorov's law of large numbers implies
-%(e.g. \cite[Theorem 10.2.3]{sen1994large}) 
-\[
-\frac{1}{n} \sum_{i=1}^n  V_i \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ for which the limit \eqref{eq:LAN_limit_cond} exists.
-
-\QEDA
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals_delta}} 
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-and 
-\[
-\eta_\delta(x) \triangleq  \frac{  \left(\delta_1(x) \right)^{2+\delta}}{  \left(\Delta_1(x)  \right)^{1+\delta}
-(1-\Delta_1(x))^{1+\delta}}
-= \frac{  \left( f (x) \right)^{2+\delta}}{ \left(F(x) \right)^{1+\delta}(1-F(x))^{1+\delta}}. 
-\]
-The proof is by induction on $n$.
-For the case $n=1$ the LHS of \eqref{eq:lem_bound_intervals_delta} equals $\eta_\delta(x)$.
-Note that $\eta_\delta(0) = 2^\delta f^{2+\delta}(0)$, so it is enough to prove that $\eta_\delta(0)$ attains it maximum at $x=0$.
-We have $\eta_\delta(x) = \eta^{1+\delta}(x)/f^\delta(x)$, and thus
-\[
-\log \eta_\delta'(x) = (1+\delta) \frac{\eta'(x)}{\eta(x)} - \delta \frac{f'(x)}{f(x)}. 
-\]
-By Assumption~\ref{assump:failure_rate} both terms above are negative for $x>0$, so that $\log \eta_\delta'(x) \leq 0$ if and only if
-\begin{equation} \label{eq:delta_proof_cond}
-(1+\delta) \left| \frac{\eta'(x)}{\eta(x)} \right| \geq \delta \left| \frac{f'(x)}{f(x)} \right|, \qquad x>0.
-\end{equation}
-Also by Assumption~\ref{assump:failure_rate}, for $x>0$ we have
-\[
-0 > (\log \eta(x))' = \frac{h'(x)}{h(x)}-\frac{h'(-x)}{h(-x)},
-\]
-so that \eqref{eq:delta_proof_cond} is satisfies for $\delta>0$ small enough.
-
-Next, assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^{2+\delta}} 
-{\left(\Delta_n \right)^{1+\delta}\left(1- \Delta_n \right)^{1+\delta} } \leq \eta_\delta(0) = 2^\delta f^{2+\delta}(0) . 
-\label{eq:lem_bound_intervals_delta_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%If $x_{i+1} = x_i$ for some $i=1,\ldots,N-1$, then then the indices $i$ and $i+1$ may  be removed from all sums in \eqref{eq:lem_bound_intervals}, what brings us to the case $n = N-2$.
-Therefore, we may assume that $x_1 < \ldots < x_n$.
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  (2+\delta) \log \delta_N - (1+\delta) \log \Delta_N - (1+\delta) \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{(2+\delta) (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(1+\delta)(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(1+\delta)(-1)^{k+1} f(x_k)}{1-\Delta_N }.
-\]
-We conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero_delta}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N(1+\delta)}{2+\delta} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-From the same reason as in the proof of Lemma~\ref{lem:bound_intervals_delta}, \eqref{eq:gradient_zero_delta} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_delta_proof} equals $\eta_\delta(x_1)$ which was shown to be smaller than $\eta_\delta(\epsilon)$.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_delta_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$,  $x_i, x_{i+1} = -\epsilon$ for some $i$, or $x_i, x_{i+1} = \epsilon$ for some $i$.
-It is therefore enough to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Assume first $x_N \rightarrow -\infty$. Then 
-\begin{align*}
-\frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)^{1+\delta} } ,
-\end{align*}
-which is smaller than $\eta_\delta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
-\begin{align*}
-& \frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right)^{1+\delta} }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^{2+\delta}} 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)^{1+\delta}\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right)^{1+\delta} },
-\end{align*}
-where $x'_{m} = x_{m+1}$ for $m=1,\ldots, N-1$. The last expression is smaller than $\eta_{\delta}(0)$ by the induction hypothesis.  \QEDA \\
-
-\subsection{Proof of Theorem~\ref{thm:non_existence}
-\label{proof:thm:non_existence}
-}
-
-Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta) = \eta(0)$. 
-%
-Since $B_1,B_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, $\theta$ is in $\Xi$ if and only if
-\begin{equation}
-\label{eq:non_existence_proof}
-\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0). 
-\end{equation}
-By assumption, we have $B_i^{-1} = A_i$ where $A_i$ can be expressed as
-\[
-A_i = \cup_{i=1}^K (a_{i,k},b_{i,k}), 
-\]
-where $a_{i,1} \leq b_{i,1} \leq \ldots \leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values $-\infty$ and $\infty$, respectively. Denote
-\[
-\mathcal B_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\}.
-\]
-For any $\theta$ and $\epsilon>0$, denote 
-\[
-S_n(\theta, \epsilon) \triangleq \left\{ i\leq n \,:\, (\theta-\epsilon,\theta+\epsilon) \cap \mathcal B_i \neq \emptyset \right\}
-\]
-In words, $S_n$ contains all integers smaller than $n$ in which an $\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals consisting $A_i$. 
-%
-We now claim that 
-if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. Indeed, for such $\theta$ we have
-\begin{align}
-& L_n(A_1,\ldots,A_n; \theta) \nonumber \\
-& = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
-\frac{ \left(\sum_{k=1}^{K}  f(\theta - b_{i,k})- f(\theta - a_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& 
-+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(b_{i,k}-\theta) - f(a_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& \overset{(a)}{\leq}
-\frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
- \label{eq:non_existence_proof1}
-\end{align}
-where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} and the fact that for $i \in S_n(\theta, \epsilon)$, 
-\[
-\max\left\{ \max_k \eta(b_{i,k}-\theta) , \max_k \eta(a_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
-\]
-Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, \eqref{eq:non_existence_proof1}, and thus $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.
-\par
-For $k\in \mathbb N$, assume by contradiction that there exists $N \geq 2K + 1$ distinct elements
-$\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$ consists of at most $K$ intervals, we have that 
-\begin{equation}
-\label{eq:few_optimality_points_proof}
-\card (\cup_{i=1}^n \mathcal B_i) \leq 2 n K. 
-\end{equation}
-Fix $\epsilon>0$ such that 
-\[
-\epsilon < \frac{1}{2}\min_{i\neq j} |\theta_i - \theta_j|. 
-\]
-Since for each $\theta \in \Theta$ we have $S_n(\theta, \epsilon) \to 1$, there exists $n$ large enough such that 
-\[
-\card \left(S_n(\theta_i, \epsilon) \right) \geq n \left(1-\frac{1}{2N} \right)
-\]
-for all $i=1,\ldots,N$.
-However, $S_n(\theta_1,\epsilon), \ldots S_n(\theta_N,\epsilon)$ are disjoint, so the cardinallity of their union is at least $n\left(1-\frac{1}{2N} \right)N$ which is grater than $2nK + n/2$ in contradiction to \eqref{eq:few_optimality_points_proof}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEfull,onebit}
-
-\end{document}

### 2019-09-19 onebit_full.tex
Starting to edit

@@
+%% \documentclass[11pt]{article}
 \documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper
@@
 \maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-We consider the problem of estimating the mean of a symmetric log-concave distribution under the following constraint: only a single bit per sample from this distribution is available to the estimator.
-We study the mean squared error risk in this estimation as a function of the number of samples, and hence the number of bits, from this distribution.
-%
-Under an adaptive setting in which each bit is a function of the current sample and previously recorded bits, we show that the optimal relative efficiency compared to the sample mean is the efficiency of the median.
-%For example, in estimating the mean of a normal distribution, a constraint of one bit per sample incurs a penalty of $\pi/2$ in sample size compared to the unconstrained case.
-%
-We also consider a distributed setting where each bit is only a function of a single sample.
-We show that the optimal efficiency of the adaptive setting can be attained by splitting the sample into two parts and allowing only a single adaptation.
-Otherwise, we show that no one sample estimation procedure can attain the optimal efficiency uniformly over all points in the parameter space.
-%
-%Finally, we analyze a distributed setting where the bits are obtained by comparing each sample against a prescribed threshold.
-Consequently, we consider the threshold density that minimizes the maximal MSE.
-%
-Our results indicate that estimating the mean from one-bit measurements is equivalent to estimating the sample median from these measurements.
-In the adaptive case, this estimate can be done with vanishing error for any point in the parameter space.
-In the distributed case, this estimate can be done with vanishing error only for a finite number of possible values for the unknown mean.
-\end{abstract}
+\input{abstract}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{sec:Intro}
-Estimating parameters from data collected and processed by multiple units may be limited due to communication constraints between these units. 
-%
-For example, this scenario arises in sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit.
-In these situations, the ability to estimate a particular parameter from the data is dictated not only by the quality of observations and their number but also by the available bandwidth for communicating between the sensors and the central estimator.
-The question that we ask is to what extent a parametric estimation task is affected by this constraint on communication, and what are the fundamental performance limits in estimating a parameter subject to such restriction.
-\par
-%%
-\begin{figure*}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto]
-
-  \node at (0,0) (source) {$X_1$} ;
- \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
-\node[below of = source2, node distance = 2.1cm] (source3) {$X_n$};
-
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {$\enc$};
-
-\draw[->,line width = 2pt] (source2) -- (enc2); 
-\draw[->,line width = 2pt] (source) -| (enc2); 
-\draw[->,line width = 2pt] (source3) -| (enc2);
-
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-
-\draw[->,line width = 2pt] (source2) -- (enc2); 
-\node[int1, right of = enc2, node distance = 2.7cm ] (est) {$\est$};
-
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {\small $B_1,\ldots,B_n$} (est);
-
-\node[right of = est, node distance = 1.2cm] (dest) {\small ${\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=1pt] (est) -- (dest);
-\node at (2,-4.5) {(i) Centralized};
-\end{tikzpicture}
-%
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {\small $X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
- \node[below of = source, node distance = 1.5cm] (source2) {\small $X_2$};
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {$\enc$};  
-\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source2, node distance = 2.1cm] (source3) {\small $X_n$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};  
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim P_X$};
-
-\node[int1, right of = enc2, node distance = 3cm ] (est) {$\est$};
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);   
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$B_2$} (est);
-
-\draw[->] (enc1)+(0.7,0) -- +(0.7,-0.7) -| (enc2);
-
-%\draw[dashed,->] (enc2)+(0.7,0) -- +(0.7,-0.7) -| +(0,-1.2);
-\draw[->,line width = 2pt] (enc3) -| (est);
-
-%\node[below of = mes2, node distance = 1.5cm] (mes3) {$B_1,\ldots,B_{n-1} $};
-
-\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -1cm]  {$B_n$} (est);
-
-%\draw[->] (mes3.west) -- +(0,-0.5) -| (enc3);
-
-\node[below right = 2.3cm and 0.7cm of 
-enc1.center, yshift = 0.cm] (end) {$B_1,\ldots,B_{n-1}$};
-
-\draw[->] (enc1)+(0.7,0) -- (end.west) -| (enc3);
-
-\node[right of = est, node distance = 1.2cm] (dest) {${\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=1pt] (est) -- (dest);
-\node at (2,-4.5) {(ii) Adaptive};
-\end{tikzpicture}
-%
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
- \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {$\enc$};  
-\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source2, node distance = 2.1cm] (source3) {$X_n$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};  
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim {\Ncal} \left(\theta, \sigma^2 \right)$};
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-
-\node[int1, right of = enc2, node distance = 2.1cm ] (est) {$\est$};
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
-
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$B_2$} (est);
-
-\draw[->,line width = 2pt] (enc3) -| (est);
-
-\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -1cm]  {$B_n$} (est);
-
-\node[right of = est, node distance = 1.2cm] (dest) {${\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=1pt] (est) -- (dest);
-\node at (2,-4.5) {(iii) Distributed};
-\end{tikzpicture}
-\end{center}
-\caption{\label{fig:setup} 
-Three encoding settings: (i) Centralized  -- an encoder sends $n$ bits after observing $n$ samples.
-(ii) Adaptive (sequential) --  the $i$th encoder sends the bit $B_i$ depending on its private sample $X_i$ and previous bits $B_1,\ldots,B_{i-1}$.
-(iii) Distributed  -- each encoder send the bit $B_i$ based on its private sample $X_i$ only.}
-\end{figure*}
-%%
-
-This paper answers this question in a particular setting: the estimation of the mean $\theta$ of a symmetric log-concave distribution with finite variance, under the constraint that only a single bit can be communicated on each sample from this distribution.
-As it turns out, the ability to share information before committing on each one-bit message dramatically affects the performance in estimating $\theta$.
-We, therefore, distinguish among the three settings illustrated in Figure~\ref{fig:setup}
-\begin{itemize}
- \item[(i)\,\,] \emph{Centralized} encoding: all $n$ encoders confer and produce a single message consists of $n$ bits.
- \item[(ii)\,] \emph{Adaptive} or \emph{sequential} encoding: The $n$th encoder observes the $n$th sample and the $n-1$ previous bits.
- \item[(iii)] \emph{Distributed} encoding: The $n$th message is only a function of the $n$th sample.
- \end{itemize}
-Evidently, as far as information sharing is concerned, settings (iii) is a more restrictive version of (ii) which is more restrictive than (i).
-Below are three application examples for each of the settings (i)-(iii) above, respectively:
-\begin{itemize}
-\item {\bf Signal acquisition:} A quantity is measured $n$ times at different instances.
-The results are averaged in order to reduce measurement noise and the averaged result is then stored or communicated using $n$ bits.
-\item {\bf Analog-to-digital conversion:} A sigma-delta modulator (SDM) converts an analog signal into a sequence of bits by sampling the signal at a very high rate and then using one-bit threshold detector combined with a feedback loop to update an accumulated error state \cite{1092194}.
-Therefore, the expected error in tracking an analog signal using an SDM falls under our setting (ii) when we assume that the signal at the input to the modulator is a constant (direct current) corrupted by, say, thermal noise \cite{53738}.
-Since the sampling rates in SDM are usually many times more than the bandwidth of its input, analyzing SDM under a constant input provides meaningful lower bound even for non-constant signals.
-\item {\bf Privacy:} A business entity is interested in estimating the average income of its clients.
-In order to keep this information as confidential as possible, each client independently provides an answer to a yes/no question related to its income.
-\end{itemize}
-%
-We measure the performance in estimating $\theta$ by the quadratic risk. For an estimator with finite quadratic risk $R_n$, we are interested in particular in the limit
-\begin{equation}
-\label{eq:ARE_def}
-\lim_{n\to \infty} \frac{\sigma^2/n}{R_n},
-\end{equation}
-describing the \emph{asymptotic relative efficiency} (ARE) of this estimator compared to an estimator whose variance decreases as $\sigma^2/n+o(n^{-1})$.
-Estimators of this form include the empirical mean of the samples, and, under some conditions, the optimal Bayes estimator.
-\par
-%
-In addition to the examples above, the excess risk in estimating a fixed parameter due to a one-bit per sample constraint is useful in bounding from below the excess risk in estimating signals from thier noisy one-bit quanitzed noisy measurements.
-Specifically, the excess risk or ARE we derive serve as the most optimistic estimate for the risk in estimating under one-bit per measurement constraint signals changing over time or space.
-Such estimation settings are considered in \cite{baraniuk2017exponential, jacques2013robust, plan2013one, li2017channel, choi2016near}.
-\par
-
-% given a prior distribution on the space $\Theta$ where $\theta$ resides. \\
-
-In setting (i), the estimator can evaluate the optimal mean estimator (e.g., the sample mean in the Gaussian case) and then quantize it using $n$ bits.
-Since the accuracy in describing the empirical mean decreases exponentially in $n$, the error due to quantization is negligible compared to the quadratic risk in estimating the mean \cite{720540}.
-Therefore, the ARE in this setting is $1$.
-Namely, asymptotically, there is no loss in performance due to the communication constraint under centralized encoding.
-%
-In this paper we show that a similar result does not hold in setting (ii): the ARE of any adaptive estimation scheme is at most the ARE of the sample median.
-Specifically, when the samples are drawn from the normal distribution, this ARE equals $2/\pi$, showing that the one-bit constraint increases the effective sample size in estimating $\theta$ by at least $\pi/2$ compared to estimating it without the bit constraint.
-We also show that this lower bound on the ARE is tight by providing an estimator that attains it.
-In fact, we show that only one adaptiveness, as illustrated in Figure~\ref{fig:one_round} is enough to achieve the optimal ARE.
-%
-Clearly, the penalty on the sample size in setting (iii) is at least as large as that in setting (ii).
-We show, however, that unlike in setting (ii), there is no distributed estimation scheme that is uniformly optimal in the sense that it attains the ARE of the sample median for all $\theta$ in the parameter space.
-This result is obtained by establishing local asymptotic normality of regularly enough encoding procedures for setting (iii), resulting in an exact characterization of the ARE of such procedures.
-To summarize our contributions, we establish that the optimal ARE in settings (i) is $1$, the optimal ARE in setting (ii) is ARE of the sample median, and no uniformly optimal procedure exists in setting (iii).
-
-% Instead, in setting (iii) we restrict ourselves to estimators from messages obtained by comparison against a prescribed value (that may be different for each sample).
-We show that the maximum likelihood (ML) estimator for $\theta$ from these messages is asymptotically local minimax, and its asymptotic variance is strictly greater than the variance of the median.
-Thus, at least when limited to threshold detection, the ability to adapt the threshold allows for a more efficient estimation.
-%This is in contrast to the \\ counterpart of our setting where $\theta$ is taken from a finite space
-
-It is important to note that although the ARE in setting (i) is one, this scheme already poses a non-trivial challenge for the design and analysis of optimal encoding and estimation procedures.
-Indeed, representing an unknown random quantity using $n$ bits is equivalent to designing a $2^n$ levels scalar quantizer \cite{gray1998quantization}.
-However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation problem and hence its exact value is unknown.
-As a result, a non-trivial exploration-exploitation trade-off arises even in setting (i).
-%Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$. 
-Therefore, while uncertainty due to quantization decreases exponentially in the number of bits $n$, hence the ARE is $1$, it is still difficult to derive an exact expression for the MSE in this setting.
-%
-The situation is even more involved in the adaptive encoding setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$ may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
-Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $n-1$ messages, is not guaranteed to be globally optimal.
-Therefore, while we characterize the optimal one-bit message given the previous messages, this characterization does not necessarily lead to an upper bound on the ARE.
-Instead, our result on the maximal ARE is obtained by bounding the Fisher information of any $n$ adaptive messages and using an appropriate information inequality.
-\par
-%
-%In addition to encoding and estimation schemes that lead to optimal results, we also consider two additional ``natural'' schemes.
-Specifically, in setting (ii) we consider the one-bit optimal scheme, i.e., the case of a greedy encoder that given the $n$th sample and the previous $n-1$ bits, provides a bit that minimizes the $n$-step MSE.
-In setting (iii) we also consider the case where the messages are obtained by comparing each sample against a prescribed threshold.
-This threshold may be different across samples and is assumed deterministic (independent of the data).
-
-\subsection*{Related Works}
-When the variance $\sigma^2$ is negligible compared the to desired accuracy, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is solved by a bisection style method over the parameter space.
-Therefore, the general case of non-zero variance is reminiscent of the noisy binary search problem with a possibly infinite number of unreliable tests \cite{cicalese2002least, Karp:2007:NBS:1283383.1283478}.
-However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a constant input corrupted by Gaussian noise.
-Using an SDM, Wong and Gray \cite{53738} showed that the output of the modulator converges to the true constant input almost surely, so that an SDM provides a consistent estimator for setting (ii).
-The rate of this convergence, however, was not analyzed and cannot be derived from the results of \cite{53738}.
-In particular, our results for setting (ii) imply that the asymptotic rate of convergence of the MSE in SDM to a constant input under an additive white Gaussian noise is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-Baraniuk et.
-al \cite{baraniuk2017exponential} also considered adaptive one-bit measurements in the context of analog-to-digital conversion, although without noise at the input.
-By establishing the lower bound of $\sigma^2\pi/2n$ on the MSE, we show that the main results of \cite{baraniuk2017exponential}, an exponential MSE decaying rate, does not hold in the noisy setting.
-Stated otherwise, the MSE in the setting of \cite{baraniuk2017exponential} may decay exponentially up to the noise level, after which it decays at most as $\sigma^2\pi/2n$.
-\par
-%
-One-bit measurements in the distributed setting (iii) was considered in \cite{904560,4244748, 6882252, chen2010performance, 5184907}, but without optimizing the encoders and their detection rules.
-Consequently, the performance derived in these works are not optimal.
- % analyzed the estimation from distributed quantized measurements when the same detection rule is applied by all encoders.
-However, the error criterion considered in these works is the Fisher information rather than the MSE risk or ARE criterion.
-\par
-%Once the decision rule of each encoder is fixed, the optimal estimation of $\theta$ is determined using the maximum a posteriori probability rule.
-Hence, the distributed setting is reduced to finding the optimal decision rule of each encoder.
-The work of \cite{52470} addresses the counterpart of our setting (iii) in the case of hypothesis testing, although the results there cannot be extended to parametric estimation.
-When the parameter space $\Theta$ is finite, Tsitsiklist \cite{tsitsiklis1988decentralized} showed that when the cardinality of $\Theta$ is at most $M$ and the probability of error criterion is used, then no more than $M(M-1)/2$ different detection rules are necessary in order to attain probability of error decreasing exponentially with the optimal exponent.
-%That is, beyond $M(M-1)/2$ some decision rules can be repeated without losing optimality.
-Furthermore, in a version of this problem for the adaptive setting \cite{5751320}, it was shown that, with specific two-stage feedback, there is no gain in feedback compared to the fully distributed setting.
-Our results imply that the ARE in the distributed setting with threshold detection rules is strictly larger than that in the adaptive setting for almost all points in $\Theta$, suggesting that the case where the cardinality of $\Theta$ is finite is different from the case where $\Theta$ is an open set.\par
-%
-As we explain in detail in Section~ \ref{sec:preliminary}, the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}, leads to lower bounds on the MSE in setting (iii).
-For the case of a Gaussian distribution, this lower bound bounds the ARE to be at most $3/4$.
-Thus, while this bound on the ARE provides no new information compared to the upper bound of $2/\pi$ we derive for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimum even under the one bit per sample constraint.
- \par
-% 
-Finally, we note that minimax estimation under limited communication with an arbitrary number of bits per node was considered in 
-\cite{zhang2013information, duchi2014optimality}.
-The specialization of the results in \cite{zhang2013information, duchi2014optimality} to our settings (ii) and (iii) leads to looser lower bounds then the ones we derive in this paper.
-Looser bounds can also be obtained from works considering general inference and distributed estimation problems under data compression constraint \cite{DBLP:journals/corr/abs-1802-08417, zhang1988estimation, han2018distributed, xu2017information, Barnes2018}.
-In particular, the subsequent work of \cite{Barnes2018} uses an approach similar to ours to derive lower bound on the error in various parametric estimation problems from quantized measurements.
-\par
-
-The remainder of this paper is organized as follows.
-In Section~\ref{sec:problem} we describe the problem and useful notation.
-In Section~\ref{sec:preliminary} we provide two simple bounds on the efficiency and MSE.
-Our main results for the adaptive and distributed cases are given in Sections~\ref{sec:sequential} and \ref{sec:distributed}, respectively.
-In Section~\ref{sec:conclusions} we provide concluding remarks.
+
+\input{introduction}
 

### 2019-09-21 introduction.tex
Temp commit before daycare

@@
 from this distribution.
+Different information sharing schemes strongly affect the
+performance of estimators for $\theta$; we illustrate
+the three main settings we consider in Figure~\ref{fig:setup}.
+\begin{enumerate}[(i)]
+\item \emph{Centralized} encoding: all $n$ encoders confer and produce a
+  single message consists of $n$ bits.
+ \item \emph{Adaptive} or \emph{sequential} encoding: The $n$th encoder
+   observes the $n$th sample and the $n-1$ previous bits.
+ \item \emph{Distributed} encoding: The $n$th message is only a function of
+   the $n$th sample.
+\end{enumerate}
+The distributed setting~(iii) is the most restrictive; as it turns out,
+(ii) is slightly more restrictive than the fully centralized setting~(i),
+and in our setting, a variant of the adaptive setting~(ii)
+in which there is only \emph{one} round of adaptivity---as we make formal
+later---is enough to achieve the same efficiency as the fully sequential
+setting~(ii).
+Each setting has natural applications:
+\begin{itemize}
+\item {\bf Signal acquisition (i):} A quantity is measured $n$ times at
+  different instances. The results are averaged in order to reduce
+  measurement noise and the averaged result is then stored or communicated
+  using $n$ bits.
+\item {\bf Analog-to-digital conversion (ii):} A sigma-delta modulator (SDM)
+  converts an analog signal into a sequence of bits by sampling the signal
+  at a very high rate and then using one-bit threshold detector combined
+  with a feedback loop to update an accumulated error state
+  \cite{1092194}. Therefore, the expected error in tracking an analog signal
+  using an SDM falls under our setting (ii) when we assume that the signal
+  at the input to the modulator is a constant (direct current) corrupted by,
+  say, thermal noise \cite{53738}. Since the sampling rates in SDM are
+  usually many times more than the bandwidth of its input, analyzing SDM
+  under a constant input provides meaningful lower bound even for
+  non-constant signals.
+\item {\bf Privacy (ii)--(iii):} A business entity is interested in
+  estimating the average income of its clients. In order to keep this
+  information as confidential as possible, each client independently
+  provides an answer to a yes/no question related to its
+  income~\cite{DuchiJoWa18}.
+\end{itemize}
 
-%% JCD: I am here. %%
-
-As it turns out, the ability to share information
-before committing on each one-bit message dramatically affects the
-performance in estimating $\theta$. We, therefore, distinguish among the
-three settings illustrated in Figure~\ref{fig:setup}
-\begin{itemize}
- \item[(i)\,\,] \emph{Centralized} encoding: all $n$ encoders confer and produce a single message consists of $n$ bits.
- \item[(ii)\,] \emph{Adaptive} or \emph{sequential} encoding: The $n$th encoder observes the $n$th sample and the $n-1$ previous bits.
- \item[(iii)] \emph{Distributed} encoding: The $n$th message is only a function of the $n$th sample.
- \end{itemize}
-Evidently, as far as information sharing is concerned, settings (iii) is a more restrictive version of (ii) which is more restrictive than (i).
-Below are three application examples for each of the settings (i)-(iii) above, respectively:
-\begin{itemize}
-\item {\bf Signal acquisition:} A quantity is measured $n$ times at different instances.
-The results are averaged in order to reduce measurement noise and the averaged result is then stored or communicated using $n$ bits.
-\item {\bf Analog-to-digital conversion:} A sigma-delta modulator (SDM) converts an analog signal into a sequence of bits by sampling the signal at a very high rate and then using one-bit threshold detector combined with a feedback loop to update an accumulated error state \cite{1092194}.
-Therefore, the expected error in tracking an analog signal using an SDM falls under our setting (ii) when we assume that the signal at the input to the modulator is a constant (direct current) corrupted by, say, thermal noise \cite{53738}.
-Since the sampling rates in SDM are usually many times more than the bandwidth of its input, analyzing SDM under a constant input provides meaningful lower bound even for non-constant signals.
-\item {\bf Privacy:} A business entity is interested in estimating the average income of its clients.
-In order to keep this information as confidential as possible, each client independently provides an answer to a yes/no question related to its income.
-\end{itemize}
-%
-We measure the performance in estimating $\theta$ by the quadratic risk. For an estimator with finite quadratic risk $R_n$, we are interested in particular in the limit
+Let us provide an informal description of our results and setting.  For an
+estimator $\theta_n$ with finite quadratic risk (mean squared error) $R_n =
+\E_\theta[(\theta_n - \theta)^2]$, letting $\sigma^2 = \var(X)$
+we are interested in particular in the
+limit (assuming it exists)
 \begin{equation}
@@
 \end{equation}
-describing the \emph{asymptotic relative efficiency} (ARE) of this estimator compared to an estimator whose variance decreases as $\sigma^2/n+o(n^{-1})$.
-Estimators of this form include the empirical mean of the samples, and, under some conditions, the optimal Bayes estimator.
-\par
-%
+which describes the \emph{asymptotic relative efficiency} (ARE) of this
+estimator compared to an estimator whose variance decreases as
+$\sigma^2/n+o(n^{-1})$. Estimators of this form include the sample mean
+and, under some conditions, the optimal Bayes estimator.
+
+%% JCD: I AM HERE %%
+
 In addition to the examples above, the excess risk in estimating a fixed parameter due to a one-bit per sample constraint is useful in bounding from below the excess risk in estimating signals from thier noisy one-bit quanitzed noisy measurements.

### 2019-09-23 adaptive-estimation.tex
Adding a bib file

--- 2019-09-19 onebit_full.tex
@@
-%% \documentclass[11pt]{article}
-\documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper
-
-%LatexiDiff ignore tikz:
-% $: latexdiff -c "PICTUREENV=(?:picture|tikzpicture|DIFnomarkup)[\w\d*@]*" old.tex new.tex > diff.tex
-
-%\IEEEoverridecommandlockouts                              %
-
-%\usepackage{mathcomSTEP}
-
-%\overrideIEEEmargins 
-%\IEEEoverridecommandlockouts                              % This command is only needed if 
-% you want to use the \thanks command
-
-%\overrideIEEEmargins                                      % Needed to meet printer requirements.
-
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-\onecolumn
-
-\usepackage{mathptmx} 
-\usepackage{times} 
-\usepackage{amsmath} 
-\usepackage{amsbsy} 
-\usepackage{amssymb}
-
-%\usepackage{newtxtext, newtxmath}
-\usepackage{mathrsfs}
-\usepackage{comment}
-\usepackage[export]{adjustbox}
-\usepackage{tikz}
-\usetikzlibrary{external,positioning,decorations.pathreplacing,shapes,arrows,patterns}
-
-\usepackage[hidelinks]{hyperref}
-%\tikzexternalize[mode=list and make]
-\usepackage{algorithmicx}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage{pstool}
-\usepackage[latin1]{inputenc}
-\usetikzlibrary{arrows,shapes}
-\usepackage{xifthen}
-\usepackage{epic}
-%\usepackage{caption}
-\usepackage{epstopdf}
-
-\newtheorem{thm}{\bf{Theorem}}
-\newtheorem{cor}[thm]{\bf {Corollary}}
-\newtheorem{lem}[thm]{\bf {Lemma}}
-\newtheorem{prop}[thm]{\bf {Proposition}}
-\newtheorem{example}{\bf {Example}}
-\newtheorem{definition}{\bf {Definition}}
-\newtheorem{rem}{\bf {Remark}}
-\newtheorem{assump}{\bf {Assumptions}}
-
-\newcommand{\ex}[1]{\ensuremath{\mathbb{E}\left[ #1\right]}}
-
-\newcommand{\Var}[1]{\ensuremath{\mathrm{Var} \left[ #1\right]}}
-
-\newcommand{\unif}{\mathsf{unif}}
-\newcommand{\card}{\mathrm{card}}
-\newcommand{\ARE}{\mathsf{ARE}}
-\newcommand{\supp}{\mathrm{supp} }
-\renewcommand\vec[1]{\ensuremath\boldsymbol{#1}}
-\newenvironment{proof}{\paragraph*{Proof}}{\hfill$\square$ \newline}
-\newcommand{\sgn}{\mathrm{sgn} }
-\newcommand{\Prob}{\mathbb{P} }
-\newcommand{\argmax}{\mathrm{argmax}}
-\newcommand*{\QEDA}{\hfill\ensuremath{\square}}
-\newcommand{\CEO}{\mathsf{CEO}}
-\newcommand{\Ncal}{\mathcal{N}}
-
-\newcommand{\enc}{\mathsf{enc}}
-\newcommand{\est}{\mathsf{est}}
-
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-\tikzstyle{sint}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.8cm,thick ]
-\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
-\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
-\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.7cm,thick ]
-\tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-
-\author{
-    \IEEEauthorblockN{
-Alon Kipnis\IEEEauthorrefmark{1} and   
-    John C. Duchi\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}  \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}Stanford University, Department of Statistics \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Stanford University, Department of Electrical Engineering. }
-}
-
-\title{\LARGE \bf Mean Estimation from One-Bit Measurements}
-
-\begin{document}
-\graphicspath{{./Figs/}}
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{abstract}
-
-%{\color{red}  See LASSO results in http://arxiv.org/abs/1506.02181v1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\input{introduction}
-
-\section{Problem Formulation \label{sec:problem}}
-
-Let $f(x)$ be a symmetric and log-concave density function with a finite second moment $\sigma^2$.
-For $\theta \in \Theta$, denote by $P_X$ the probability distribution with density $f\left( x-\theta \right)$.
-Therefore, $P_X$ is an absolutely continuous log-concave distribution with mean $\theta$ and variance $\sigma^2$.
-Symmetry and log-concavity of $f(x)$ imply that $P_X$ is strongly unimodal (has a unique local maxima) with its mode at $x =\theta$ \cite{ibragimov1956composition}.
-We further assume that the \emph{parameter space} $\Theta$ is a closed interval of the real line.
-\par
-In some situations it is useful to assume that $\theta$ is drawn once from the prior distribution $\pi$ on $\Theta$.
-In this case we assume that $\pi$ is an absolutely continuous distribution, and denote its density by $\pi(\theta)$, i.e., $\pi(d\theta) = \pi(\theta)d\theta$.
-\par
-The random variables $X_1,\ldots,X_n$ represent $n$ independent samples from $P_X$. 
-We are interested in estimating $\theta$ from a set of $n$ binary messages $B_1,\ldots,B_n$, obtained from $X_1,\ldots,X_n$ under three possible scenarios illustrated in Figure~\ref{fig:setup}: 
-\begin{itemize}
-\item[(i)~~] Centralized $B_i(X_1,\ldots,X_n)$, $i=1,\ldots,n$.
-\item[(ii)~] Adaptive $B_i(X_i,B_1,\ldots,B_{i-1})$, $i=2,\ldots,n$.
-\item[(iii)] Distributed $B_i(X_i)$, $i=1,\ldots,n$.
-\end{itemize}
-
-The performance of an estimator ${\theta}_n \triangleq {\theta}_n(B^n)$ in any of these cases is measured according to the quadratic risk:
-\begin{equation}
-\label{eq:error_def}
-R_n \triangleq \mathbb E\left({\theta}_n - \theta \right)^2,
-\end{equation}
-where the expectation is taken with respect to the distribution of $X_1,\ldots,X_n$ and, whenever available, a prior distribution $\pi(\theta)$ over $\Theta$.  
-%It is well known that minmax estimation error 
-%\begin{equation}
-%R_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left({\theta}_n - \theta \right)^2 | \theta \right],
-%\end{equation}
-%can be obtained from $R_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}. 
-%
-The main problems we consider in this paper are the minimal value of \eqref{eq:error_def}, as a function of $n$ and $f(x)$, under different choices of the encoding functions in cases (i), (ii), and (iii).
-\par
-
-We give particular attention to the ARE of estimators with respect to an asymptotically normal efficient estimator that is not subject to the bit constraint.
-Specifically, let $\{a_n,\,n\in \mathbb N\}$ be a sequence such that
-\[
-\sqrt{a_n}\left({\theta}_n - \theta\right) \overset{d}{\longrightarrow} \Ncal(0, \sigma^2).
-\]
-Then the ARE of ${\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
-\[
-\ARE({\theta}_n) \triangleq
-\lim_{n\rightarrow \infty} \frac{a_n}{n}. 
-\]
-Note that in the special case where there exists $V \in \mathbb R$ such that
-\[
-a_n \mathbb E \left({\theta}_n - \theta \right)^2 = V + o(1),
-\]
-with $o(1)\to 0$ as $n\to \infty$, then the ARE of ${\theta}_n$ is finite and equals $\sigma^2/V$. \par
-
-In addition to the notation above, we also denote by $F(x)$ the cumulative distribution function of $X_i$, and define
-\begin{equation} \label{eq:eta_def}
-\eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))} =  \frac{f(x)f(-x)}{F(x)F(-x)}, 
-\end{equation}
-where the last equality is due to symmetry of $f(x)$. We note that 
-\begin{equation}
-\label{eq:eta_h}
-\eta(x) = h(x)h(-x) = f(x) \left( h(x) + h(-x) \right), 
-\end{equation}
-where 
-\[
-h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
-\]
-is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function since $f(x)$ is log-concave \cite{bagnoli2005log}. 
-%
-For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as illustrated in Fig.~\ref{fig:eta}. 
-%
-In this paper we only consider the normal distribution and other log-concave symmetric distributions for which this property of $\eta(x)$ holds. Specifically, we require the following:
-\begin{assump} \label{assump:failure_rate}
- $\eta(x)$ has a unique maximum (at the origin) and is a non-increasing function of $|x|$. 
-\end{assump}
-%That is, Assumption~\ref{assump:failure_rate} says that $\eta'(x) < 0 $ for all $x>0$. 
-Under this assumption we have, 
-\[
-4f^2(x) \leq \eta(x) \leq \eta(0),
-\] 
-%
-where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median.
-Combined with log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that $\eta(x)$ vanishes as $|x|\rightarrow \infty$.
-\par
-%
-Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions).
-Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.\par
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -3, xmax=3, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.9,
-samples=10, 
-xlabel= $x$,
-xtick={-2,-1,0,1,2},
-xticklabels={-2,-1,0,1,2},
-ytick={0,0.3989423,0.6366198},
-yticklabels={0,$\frac{1}{\sqrt{2 \pi}}$,$2/\pi$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\eta(x)$};
-\addplot[domain = -5:5, samples = 50, color = red, solid, smooth]  {exp(-x^2/2) / sqrt(2*3.14159)};
-\addlegendentry{$\phi(x)$};
-\addplot[domain = -5:5, samples = 50, color = black, solid, dashed]  {4*exp(-x^2) / (2*3.14159)};
-\addlegendentry{$4\phi^2(x)$};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -4, xmax=4, 
-restrict y to domain = -10:0,
-ymin = -10,
-samples=10, 
-xlabel= $x$,
-xtick={-3,-2,-1,0,1,2,3},
-xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,-0.45158,-0.919},
-yticklabels={0,,},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\log \eta(x)$};
-\addplot[domain = -5:5, samples = 30, color = red, solid, smooth]  {-(x)^2/2 -0.9189};
-\addlegendentry{$\log \phi(x)$};
-\end{axis}
-\end{tikzpicture}
-\caption{
-The function $\eta(x) = f^2(x) / F(x)F(-x)$ for $f(x) = \phi(x)$ the standard normal density.
-\label{fig:eta}
-}
-\end{center}
-\end{figure}
-
-\section{Consistent Estimation and Off-the-shelf Bounds \label{sec:preliminary}}
-%
-In this section we adapt known results to derive lower and upper bounds on the relative efficiency under setting (iii). These bounds establish the following facts:
-\begin{itemize}
-\item[I.] A consistent estimator with an asymptotically normal distribution always exists in setting (iii), and hence in setting (ii). 
-\item[II.] For the normal distribution, the ARE in setting (iii) is at most $3/4$. Namely, under setting (iii), all estimators are strictly inferior compared to the sample mean. 
-\end{itemize}
-
-\subsection{Consistent Estimation}
-Fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
-\[
-B_i = \mathbf 1_{X_i>\theta_0}, 
-\]
-where $\mathbf 1_A$ is the indicator of the event $A$. We have
-\[
-P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
-\]
-so that 
-\begin{equation}
-\label{eq:estimator_naive}
-{\theta}_n = \theta_0 + F^{-1}\left( P_n \right)
-\end{equation}
-is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set due to log-concavity.
-Furthermore, the variance of $P_n$ is $F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)$, and hence the delta method implies that ${\theta}_n$ is asymptotically normal with variance
-\begin{equation} 
- \frac{F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}{f^2(\theta-\theta_0)} = \frac{1}{
-\eta(\theta-\theta_0)}.
-\end{equation}
-In particular, the ARE of ${\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
-In other words, for a prescribed accuracy, ${\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
-\par
-%
-%
-Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of ${\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
-This ARE is attained only when $\theta_0 = \theta$, whereas $\theta$ is apriori unknown.
-Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of ${\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
-As an example, when $f(x)$ is a normal density, the ARE of ${\theta}_n$ is less than $\approx 0.14$ when $\theta_0$ is $2$ standard deviations from $\theta$.
-Therefore, the estimator ${\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
-\par
-It is suggested that we can attain lower variance in estimation by updating the threshold value $\theta_0$ in \eqref{eq:estimator_naive} after observing one or a batch of the single bit messages.
-Schemes with such adaptation fall within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
-\par
-
-\subsection{Multiterminal Source Coding \label{sec:ceo}}
-The CEO setting considers the estimation of a sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_i$ is available at $n$ terminals.
-At each terminal $i$, an encoder observes the $k$ noisy samples
-\[
-X_{i,j} = \theta_j + Z_{i,j},\qquad j=1,\ldots,k, \qquad i = 1,\ldots,n,
-\]
-and transmits $r_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates ${\theta}_1,\ldots,{\theta}_k$ with the goal of minimizing the quadratic risk:
-\[
-R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - {\theta}_j \right)^2 \right]. 
-\]
-Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $r_1=\ldots=r_n = 1$.
-It follows that, assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
-%
-Consequently, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the minimal MSE in the CEO setting as $k \to \infty$.
-Note that the difference between the CEO setting and ours lays in the privilege of each of the encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realizations, rather than a single realization using a single bit in ours.
- \par
-When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k$ goes to infinity were fully characterized in \cite{prabhakaran2004rate}.
-Furthermore, the work of \cite{chen2004upper} provided an expression for quadratic risk attained in the CEO setting under Gaussian priors.
-Adapting to our setting, this expression provides the following proposition:
-\begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is arbitrary.
-Then any estimator ${\theta}_n$ of $\theta$ in the distributed setting satisfies
-\begin{equation} \label{eq:ceo_bound}
- n \ex{\left( \theta - \theta_n \right)^2} \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
-\end{equation}
-where the expectation is with respect to $\theta$ and $X^n$.
-\end{prop}
-
-\begin{proof}
-See Appendix~\ref{app:proof:prop_ceo_lower_bound}.
-\end{proof}
-
-From the formulation of the CEO problem, it follows that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is attributed to the ability to perform coding over blocks.
-Namely, each encoder in the CEO setting may encode an arbitrary number of $k$ independent realizations of $\theta$ using $k$ bits, versus only one realization with one bit in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product probability space that distinguishes between the CEO problem with one bit per encoder on average and the mean estimation problem from one-bit measurements in the distributed setting.
-
 \section{Adaptive Estimation \label{sec:sequential}}
@@
 \end{figure}
-
-\section{Distributed Estimation \label{sec:distributed}}
-In this section, we now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii) where  each one-bit message $B_i$ is only a function of its private sample $X_i$.
-In this case, the $i$th encoder is fully characterized its \emph{detection region}, defined as
-\[
-A_i = \left\{ x \in \mathbb R \,:\, B_i(x) = 1 \right\}.
-\]
-Consequently, $B_i$ is of the form
-\[
-B_i = \begin{cases} 1 & X_i \in A_i, \\
--1 & X_i \notin A_i,
-\end{cases} \quad i\in \mathbb N,
-\]
-where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\par
-
-As a first step, we provide conditions under which the messages $B_1,B_2,\ldots$ define a local asymptotic normal family.
-
-\begin{thm} \label{thm:LAN1}
-For $n \in \mathbb N$ and $A_n \subset \mathbb R$,  define
-\begin{equation}
-\label{eq:precision_general}
-L_n(A_1,\ldots,A_n;\theta) \triangleq \frac{1}{n} \sum_{i=1}^n \frac{ \left(\frac{d}{d \theta} \Prob(X_i \in A_i) \right)^2 }{ \Prob(X_i \in A_i)\left(1- \Prob(X_i \in A_i) \right) }. 
-\end{equation}
-Consider the following conditions:
-\begin{itemize}
-\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is a log-concave, differentiable and symmetric density function such that $\eta(x)$ is unimodal.
-\item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
-\item[(iii)] The limit 
-\begin{equation}
-\label{eq:LAN_lim}
-\kappa(\theta) \triangleq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
-\end{equation}
-exists. 
-\end{itemize}
-For $i=1,\ldots,n$ set
-\[
-B_n = \begin{cases} 1 & X_n \in A_n, \\
--1 & X_n \notin A_n. 
-\end{cases} 
-\]
-For any $\theta$, $f(x)$ and a sequence of sets $A_1,A_2,\ldots$ such that (i)-(iii) hold, and any $h\in \mathbb R$, we have
-\begin{align*}
-& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (B_1,\ldots,B_n) }{
-\mathbb P_{\theta} (B_1,\ldots,B_n)} \\
-& \overset{d}{\longrightarrow} \Ncal\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
-\end{align*} 
-\end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:LAN1}. 
-\end{proof}
-
-Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}. 
-%
-Among these conditions, (iii) is arguably the strongest and hardest to verify.
-As we show in Section~\ref{subsec:threshold} below, this condition is satisfied, for example, when $A_1, \ldots,A_n$ are half lines whose starting points are drawn independently from some probability measure on $\mathbb R$.
-Similar ideas imply that condition (iii) holds whenever we choose the intervals consisting each $A_i$ according to some pre-specified distribution.
-\par
-%
-An important conclusion of  Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models \cite{van2000asymptotic}):
-\begin{cor} \label{cor:LA_minimax}
-Let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
-Then for any symmetric and quasi-convex function $L$,
-\begin{align*}
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right]
-\\
-& \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
-\end{align*}
-where $Z \sim \Ncal(0,1)$. In particular, for $L(x) = x^2$,
-\begin{align*}
-\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( {\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
-\end{align*}
-\end{cor}
-%
-Corollary~\ref{cor:LA_minimax} says that when the messages define a LAN model, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model at $\theta$.
-This fact poses the upper bound of $\kappa(\theta)\sigma^2$ for the ARE of estimators in such models.
-\par
-
-Next, we show that under LAN no estimator can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly for all $\theta \in \Theta$.
-
-\subsection{Non-existence of a Uniformly Optimal Strategy}
-We now show that under LAN models, the optimal minimal risk $1/\eta(0)$ can only be attained at a finite number of points within $\Theta$.
-This fact implies in particular that, unlike in the adaptive setting, no distributed estimation scheme has ARE of $\eta(0)\sigma^2$ for all $\theta \in \Theta$.
-
-\begin{thm} \label{thm:non_existence}
-Under conditions (i)-(iii) in Theorem~\ref{thm:LAN1}, assume that each $A_i$ is a union of at most $K$ intervals.
-The number of points $\theta \in \Theta$ satisfying $\kappa(\theta) = \eta(0)$ is at most $2K$.
-\end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:non_existence}.
-\end{proof}
-
-We next consider the case where each detection region is a half-open interval, i.e., the $i$th message is obtained by comparing $X_i$ against a single threshold.
-As we explain next, the existence of a density for the sequence of thresholds is enough to establish local asymptotic normality and leads to a closed form expression for the precision parameter and the ARE.
-
-%In the adaptive setting, it follows from Theorem~\ref{thm:sgd} that messages of this kind with appropriately chosen thresholds lead to an estimator with the optimal ARE of $\eta(0)sigma^2$.
-However, Theorem~\ref{thm:non_existence} implies that such ARE can only be attained for a negligible subset of the parameter space.
-As we shall see next, messages obtained via a comparison against a sequence of thresholds cannot attain the optimal efficiency one more than a single point of $\Theta$.
-
-\subsection{Threshold Detection \label{subsec:threshold}}
-Assume now that each $B_i$ is of the form
-\begin{equation}
-\label{eq:threshold_message}
-B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
--1 & X_i > t_i,
-\end{cases}  
-\end{equation}
-where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder.
-In other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and $\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$.
-It follows that
-\begin{equation}
-L_n(A_1,\ldots,A_n;\theta) = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
-\label{eq:Ln_threshold}
-\end{equation}
-A natural condition for the existence of the limit \eqref{eq:Ln_threshold} as $n\to \infty$ is that the empirical distribution of the threshold values converges to a probability measure.
-Specifically, for an interval $I \subset \mathbb R$ define
-\[
-\lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
-\]
-Theorem~\ref{thm:LAN1} implies:
-\begin{cor} \label{cor:LAN_thresh}
-Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$.
-Then $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a LAN family with precision parameter
-\[
-\kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
-\]
-\end{cor}
-The condition that $\lambda_n$ converges to a probability measure is satisfies, for example, whenever the $t_1,\ldots,t_n$s are drawn independently from a probability distribution $\lambda(dt)$ on $\mathbb R$.
-\par
-Due to local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by 
-${\theta}^{ML}_n$, is local asymptotic minimax in the sense that 
-\[
-\sqrt{n} \left( {\theta}^{ML}_n - \theta \right) \overset{d}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
-\]
-It follows that when the density of the threshold values converges to a probability measure, the ARE of the ML estimator is $\kappa(\theta)\sigma^2$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-We note that ${\theta}^{ML}_n$ is given by the root of
-\begin{equation}
-\label{eq:ML}
-\sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) },  
-\end{equation}
-which is the derivative of the log-likelihood function.
-This root is unique since the log-likelihood function is concave.
-Furthermore, for any $n \in \mathbb R$, we have that ${\theta}^{ML}_n  \in [t_{(1)}, t_{(n)}]$ where $t_{(i)}$ denotes the $i$th element of $\{t_1,t_2\ldots\}$.
-Therefore, if $\{t_1,t_2\ldots\}$ is bounded (for example $\{t_1,t_2\ldots\} \subset \Theta$), then
-\[
-\lim_{n\to \infty} n \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
-\] 
-so that the ML estimator attains the local asymptotic MSE of Corollary~\ref{cor:LA_minimax}. \par
-%
-Since $\eta(x)$ attains its maximum at the origin, we conclude that
-\[
-\kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
-\]
-This upper bound on $\kappa(\theta)$ implies that the ARE of any distributed estimator based on a sequence of threshold detectors does not exceed $\eta(0)\sigma^2$, a fact that agrees with the lower bound under adaptive estimation derived in Theorem~\ref{thm:adpative_lower_bound}.
-%
-This upper bound on $\kappa(\theta)$ is attained only when $\lambda$ is the mass distribution at $\theta$.
-Since $\theta$ is apriori unknown, we conclude that estimation in the distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting.
-In other words, the ability to choose the threshold values in an adaptive manner based on previous messages strictly improves relative efficiency compared to a non-adaptive threshold selection.
-\par
-
-%We conclude that when the density of the threshold values converges to a probability measure, the ARE of the ML is $\kappa(\theta)$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-
-%
-We conclude this section by considering the density of the threshold values that maximizes the ARE $\kappa(\theta)$ under the worst choice of $\theta \in \Theta$.
-
-\subsection{Minimax Threshold Density}
-The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta = [-T,T]$ is given as the solution to the following optimization problem:
-\begin{align}
-\label{eq:var_cvx_minimax}
-\begin{split}
-\mathrm{maximize} \quad &  \inf_{\theta \in [-T,T]} \int \eta(t-\theta) \lambda(dt)
-\\ 
-\mathrm{subject~to} 
-\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
-\end{split}
-\end{align}
-The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program.
-We denote by $\kappa^\star(T)$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum.
-%
-%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
-%\begin{align}
-%\label{eq:cvx_minimax}
-%\begin{split}
-%\mathrm{maximize} \quad &  K \\ 
-%\mathrm{subject~to} 
-%\quad &  K \leq \mathbf H\lambda \\
-%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
-%\end{split}
-%\end{align}
-%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
-%\begin{rem}
-%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$.
-Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points.
-Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using
-%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
-%\end{rem}
-
-Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$.
-The minimal asymptotic risk $\kappa^\star(\theta)$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $T$.
-Also illustrated in these Figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
-\begin{align}
-& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
- \\
-& = 
-\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
-= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
-\end{align}
-From Corollary~\ref{cor:LAN_thresh}, we conclude that the ARE under a uniform distribution is $\kappa_\unif \sigma^2$. \par
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-title = {$\sigma/T = 1/2$},
-ytick={0,0.1,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.6,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/T = 1/5$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.5},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.5},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.3,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma / T = 1/10$},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.2},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.2},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.15,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma / T = 1/20$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:minimax_support}
-Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in \Theta = [-T,T]$.
-%
-The continuous curve (red) represents the reciprocal of the asymptotic risk for at a fixed $\theta \in \Theta$ under the optimal density, so the minimax risk is the inverse of its minimal value.
-The dashed curve (green) is the reciprocal of the asymptotic risk for a fixed $\theta$ under a uniform distribution of threshold values over $\Theta$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
-}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmax=2.5, 
-xmode = log,
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=1, 
-xlabel= {$\sigma/T$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,0.637,1},
-yticklabels={0,$2/\pi$,1},
-ylabel = {$\ARE$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{optimal threshold density};
-
-\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{uniform threshold desnity};
-\end{axis}
-\end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \Ncal(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
-The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
-}.
-\end{center}
-\end{figure}
-
-%We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
-Next, we prove that with any set of messages obtained via a distributed strategy, there exists at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-title = {$\sigma/\sigma_{\theta} = 1$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 2$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma/\sigma_{\theta} = 3$},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 4$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:opt_density}
-Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=b^2/3$ is the variance of the prior.
-}
-\end{center}
-\end{figure}
-
- We consider now the problem of minimizing the asymptotic Bayes risk $
-R_{\pi,\lambda} \triangleq \mathbb E  K^{-1}(\theta)$ over all probability measures $\lambda(dt)$ with support in $\mathbb R$. This optimization problem can be written as follows:
-\begin{align}
-\label{eq:cvx_average}
-\begin{split}
-\mathrm{minimize} \quad & R_{\pi,\lambda} =  \int \frac{\pi(d\theta)}{ \int \eta \left( t-\theta\right) \lambda(dt)}. \\ 
-\mathrm{subject~to} \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) =1. 
-\end{split}
-\end{align}
-We denote by $R^\star_{\pi}$ the minimal value of the objective function in \eqref{eq:cvx_average}.
-Since the function $x \rightarrow 1/x$ is convex for positive values, \eqref{eq:cvx_average} defines a convex optimization problem in $\lambda$ whose solution depends on the prior $\pi$.
-The solution to this problem is approximated by considering $\lambda$ and $\pi$ over a discrete set.
-On Figure~\ref{fig:opt_density} we illustrate the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distributon ($P_X = \Ncal(\theta, \sigma^2)$) and the prior on $\theta$ is uniform over $\Theta = [-b,b]$.
-Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
-\par
-\begin{figure}
-\begin{center}
-
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = 0, xmax=2, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 10,
-samples=1, 
-xlabel= {$\sigma/\sigma_\theta$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,1.5708,5},
-yticklabels={0,$\pi/2$,5},
-ylabel = {$R_{\pi}^\star/\sigma^2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-\addplot[color = black, dashed] {3.14159 / 2};
-\end{axis}
-\end{tikzpicture}
-\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \Ncal(\theta, \sigma^2)$ under an optimal threshold distribution $\lambda^\star$, when the prior $\pi$ is the uniform distribution over $\Theta = [-0.5,0.5]$.
-%
-%versus $\sigma/\sigma_\theta = 2\sqrt{3}\sigma$.
-The distribution $\lambda^\star$ is the minimizer of \eqref{eq:cvx_average}.
-It is illustrated for various cases in Fig.~\ref{fig:opt_density}.
-The dashed curve represents the upper bound \eqref{eq:upper_bound}.
-\label{fig:dist_bound_uniform}  }
-\end{center}
-\end{figure}
-
-As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \Ncal(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution.
-In this case, the ML estimator reduces to the estimator ${\theta}_n$ of \eqref{eq:estimator_naive}.
-As the following proposition shows, the Bayes risk for this choice of $\lambda$ is maximal, and thus provides an upper bound on the Bayes risk under any $\lambda$.
- \eqref{eq:cvx_average}. 
-\begin{prop}\label{prop:upper_bound}
-For any prior $\pi(d\theta)$ and $\theta_0$ in the support of $\eta(x)$ we have
-\begin{equation} 
-\label{eq:upper_bound}
-R_\pi^\star  \leq 
- \int \frac{\pi(d\theta)}{\eta \left( \theta_0 - \theta \right)},
-\end{equation}
-Furthermore, assuming that $\theta_0 = \mathbb E \theta$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
-\begin{equation}
-\label{eq:bound_Taylor}
-R^\star_\pi \leq \frac{1}{4 f^2(0)} + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right) \sigma_\theta^2 + O(\sigma_\theta^3).
-\end{equation}
-\end{prop}
-\begin{proof}
-The function $x \rightarrow 1/x$ is convex for positive values, hence Jensen's inequality implies
-\[
-\left( \int \eta \left( t-\theta\right) \lambda(dt) \right)^{-1}  \leq \int  \frac{ \lambda(dt)}{ \eta \left( t-\theta\right)  }. 
-\]
-Therefore, the expected value of $\kappa^{-1}(\theta)$ satisfies
-\begin{align}
-\ex{  \frac{1}{\kappa(\theta)}}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
-\end{align}
-The bound \eqref{eq:upper_bound} is obtained by taking $\lambda$ to be a mass distribution at any $\theta_0$ in the support of $\eta(x)$.
-Finally, \eqref{eq:bound_Taylor} is obtained by expanding $1/\eta(x)$ to a third order Taylor series around zero
-%\[
-%1/\eta(x) = \frac{1}{4f^2(0)}  + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right)  x^2 + O(x^3),
-%\]
-and taking its expectation with respect to $\pi$ at $x=\theta_0-\theta$. 
-\end{proof}
-We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so the choice $\theta_0 = \ex{ \theta}$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
-The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$.
-The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $\kappa^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.
-
-\begin{example} \label{ex:bound}
-In the normal case $P_X = \Ncal(\theta, \sigma^2)$, the bound in \eqref{eq:bound_Taylor} implies 
-\[
-\frac{R^\star_\pi}{\sigma^2}  \leq \frac{\pi}{2} + \left( \frac{\pi}{2} -1 \right) \left( \frac{ \sigma_\theta}{\sigma} \right)^2 + O \left(  \frac{\sigma_\theta} { \sigma} \right)^3. 
-\]
-It follows that the ARE approaches its maximal value of $2/\pi$ whenever $\sigma_\theta/\sigma$ is small.
-The exact value of \eqref{eq:upper_bound} in this case, as well as the Bayes ARE with the optimal threshold density $\lambda^\star$ for a uniform $\pi$, are illustrated in Fig.~\ref{fig:dist_bound_uniform}.
-%i.e., each encoder simply reports "$1$" or "$-1$" whenever $X_i$ is larger or smaller than $\theta_0$, respectively.
-Intuitively, an accurate estimation of $\theta$ in this case is possible only if a sufficient mix of ''$1$''s and ''$-1$''s is obtained from the sample.
-When $\sigma_\theta^2$ is high compared to $\simga^2$, one of the events $"1"$ or "$-1"$ becomes too rare to
-\end{example}
-
-\section{Conclusions \label{sec:conclusions}}
-We considered the MSE risk in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
-%
-In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency (ARE) larger than that of the median of the samples.
-We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median.
-%We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
-\par
-In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and ARE. 
-%
-We conclude that under such conditions, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in the distributed setting.
-%
-We further considered the special case of messages obtained by comparing against a prescribed sequence of thresholds.
-We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.
-
-%\section*{ACKNOWLEDGMENT}
-%This research is supported in parts by...
-%Tsachy Weissman, Stefano Rini, Robert Gray.
-
-\onecolumn
-
-\appendix
-
-\section{}
-
-\subsection{Proof of Proposition~\ref{prop:ceo_lower_bound}
-\label{app:proof:prop_ceo_lower_bound}}
-
-First, we note that when $f(x) = \Ncal(0,\sigma^2)$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$, our distributed setting reduces to the Gaussian CEO problem with $R_1=\ldots = R_n =1$ and $k=1$.
-Therefore, any MSE attained in our distributed setting is also attained by the CEO and thus the optimal CEO strategy (with arbitrary $k$) provides a lower bound to the MSE in our setting.
-\\
-
-Consider the minimal MSE $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
-from \cite[Eq. 10]{chen2004upper}:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-For the special case of $R_\Sigma = n$ and $L=n$, we get
-\begin{equation} \label{eq:ceo_optimal_sumrate2}
-n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, this $D^\star$ provides a lower bound to the CEO MSE with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
-\[
-D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO MSE while enforcing the condition $R_1=\ldots = R_n = 1$.
-Indeed, an upper bound for the CEO MSE under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
-\[
-D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
-\]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.
-
-\subsection{Proof of Lemma~\ref{lem:bound_intervals_delta} \label{proof:lem:bound_intervals_delta}}
-
-%\begin{lem} \label{lem:bound_intervals}
-%Let $f(x)$ be a log-concave, symmetric, and differentiable density such that $\eta(x)$ is strongly unimodal. For any $x_1 > \ldots > x_n \in \mathbb R$, 
-%\begin{equation}
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \max_i \eta(x_i). \label{eq:lem_bound_intervals}
-%\end{equation}
-%In particular, if $|x_i|>\epsilon > 0$ for all $i=1,\ldots,n$, then 
-%\[
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \eta(\epsilon) < 0. 
-%\]
-%\end{lem}
-
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-so 
-\[
-\eta(x) =  \frac{  \left(\delta_1(x) \right)^2}{\Delta_1(x)
-(1-\Delta_1(x))}
-= \frac{  \left( f (x) \right)^2}{ F(x)\left(1-F(x)\right)^2}. 
-\]
-We use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:lem_bound_intervals_delta} is bounded from above by $\max_i \eta(x_i)$. The case $n=1$ is trivial. Assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^2} 
-{\Delta_n \left(1- \Delta_n \right) } \leq \max_i \eta(x_i)
-\label{eq:lem_bound_intervals_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  2 \log \delta_N -  \log \Delta_N -  \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(-1)^{k+1} f(x_k)}{1-\Delta_N },
-\]
-and we conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-%
-Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable. We have 
-\[
-\frac{f'(x)}{f(x)} = c'(x), \quad x\in \mathbb R,
-\]
-which is anti-symmetric, non-negative for $x<0$,  non-positive for $x>0$, and non-increasing since $c(x)$ is concave.
-Therefore, if $c'(x_i) = c'(x_{i+1})$ for some $i =1,\ldots,N-1$, then either (1) $x_i = x_{i+1}$ or (2) $c'(x)$ is the zero function.
-Since (2) violates the assumption that $f(x)$ is a density function, we conclude that $c'(x)$ is an injection.
-%
-As a result, \eqref{eq:gradient_zero} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_proof} equals $\eta(x_1) = \max_i \eta(x_i)$ hence the statement holds.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$, or  $x_i, x_{i+1}$ for some $i$.
-It is left to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Under case (1) we have
-\begin{align*}
-\lim_{x_N \to -\infty} \frac{  \delta_N^2} 
-{\Delta_N \left(1- \Delta_N \right) }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^2} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)} ,
-\end{align*}
-which is smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis. Under case (2) we have
-\begin{align*}
-&  \lim_{x_1 \to \infty}
-\frac{ \delta_N} 
-{\Delta_N\left(1- \Delta_N \right) } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right) \left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right) }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^2 } 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right) },
-\end{align*}
-where $x'_{m} = x_{m+1}$. The last expression is also smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis.  \QEDA \\
-
-\subsection{Proof of Theorem~\ref{thm:adpative_lower_bound}
-\label{proof:thm:adpative_lower_bound}
-}
-
-We first prove the following lemma:
-\begin{lem} \label{lem:fisher_bound}
-Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that $\eta(x)$ is unimodal. For a Borel measurable $A$ set, 
-\[
-M(X) = \begin{cases} 1,& X \in A, \\
--1, & X \notin A.
-\end{cases}
-\]
-Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $\eta(0)$.
-\end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
-When $f(x)$ is the normal density function, this lemma follows from \cite[Thm.
-3]{Barnes2018}.
-The proof below is based on a different techique than in \cite{Barnes2018}, and is valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}.
-\\
-
-The Fisher information of $M$ with respect to $\theta$ is given by
-\begin{align}
-I_\theta & =  \mathbb E \left[ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta \right] \nonumber \\
-& = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
-& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\
-& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\ 
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
-\end{align}
-where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$.
-Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
-\[
-\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
-\]
-which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$.
-It is therefore enough to proceed in the proof assuming that $A$ is of the form
-\[
-A = \cup_{j=1}^k (a_j,b_j),
-\]
-with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
-\begin{align*}
-\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
-& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
-\end{align*}
-so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
-\begin{align}
-& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
-{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
-& \times \frac {1} 
-{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
-\label{eq:lemma_J}
-\end{align}
-It follows from Lemma~\ref{lem:bound_intervals_delta} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $4f^2(0)$.  \QEDA \\
-
-We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
-\begin{equation}
-\label{eq:general_messages}
-B_i = \begin{cases}
-X_i \in A_i & 1, \\
-X_i \notin A_i & -1,
-\end{cases} 
-\end{equation}
-where $A_i \subset \mathbb R$ is a Borel measurable set. 
-%Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
-Consider the conditional distribution $P({B^n|\theta})$ of $B^n$ given $\theta$. We have 
-\begin{align}
-P\left( B^n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
-\end{align}
-where $P\left(B_i =1 | \theta, B^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B^n$ with respect to $\theta$ is given by 
-\begin{align}
-I_\theta(B^n) = \sum_{i=1}^n I_\theta (B_i|B^{i-1}),
-\label{eq:fisher_information}
-\end{align}
-where $I_\theta (B_i|B^{i-1})$ is the Fisher information of the distribution of $B_i$ given $B^{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B^{i-1}) \leq 4f^2(0)$.
-The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
-\begin{align*}
-\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(B^n) + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
-& \geq \frac{1}{ 4f^2(0) n + I_0}.
-\end{align*}
-
-\QEDA
-
-\subsection{Proof of Theorem~\ref{thm:sgd}
-\label{proof:thm:sgd}
-}
-The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.
-
-\subsubsection*{Proof of (i)}
-%Specifically, (i) in Theorem~\ref{thm:sgd} 
-Consider the following simplified version of \cite[Thm. 4]{polyak1992acceleration}:
-\begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
-Let 
-\[
-X_i = \theta + Z_i,\quad i=1,\ldots,n,
-\]
-where the $Z_i$s are i.i.d. with zero means and finite variances. Define
-\begin{align}
-\begin{split}
-\theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
-\bar{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
-\end{split}
-\label{eq:Polyak_Juditsky_alg}
-\end{align}
-where in addition, assume the following: 
-\begin{enumerate}
-\item[(i)] There exits $K_1$ such that $\left| \varphi(x) \right| \leq K_1(1+|x|)$ for all $x\in \mathbb R$.
-\item[(ii)] The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions \eqref{eq:conditions1}.
-\item[(iii)] The function $\psi(x) \triangleq \ex{ \varphi(x+Z_1)}$ is differentiable at zero with $\psi'(0)>0$, and satisfies $\psi(0)=0$ and $x\psi(x) >0$ for all $x\neq 0$.
-Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
-\begin{equation}
-\label{eq:Polyak_Juditsky_cond3}
-\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
-\end{equation}
-\item[(iv)] The function 
-$\chi(x) \triangleq \ex{\varphi^2(x+Z_1)}$ is continuous at zero. 
-\end{enumerate}
-Then $\bar{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}({\theta}_n - \theta)$ converges in distribution to $\Ncal(0,V)$, where
-\[
-V = \frac{ \chi(0)} {\psi'^2(0)}. 
-\]
-\end{thm}
-
-Using the notation above, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have that $\chi(x) = \mathbb E \sgn^2(x+Z_1) = 1$, so $\chi(0) = 1$. In addition,
-\begin{align*}
-\psi(x) & = \ex{ \sgn(x+ Z_1) }= \int_{-\infty}^\infty \sgn(x+z) f(z) dz \\
-& = \int_{-x}^\infty f(z) dz -\int_{-\infty}^{-x} f(z) dz. 
-\end{align*}
-Using the symmetry of $f(x)$ around zero, it follows that $\psi'(x) = 2f(x)$ and thus $\psi'(0) = 2f(0)$.
-It is now easy to verify that the rest of the conditions in Theorem~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$.
-Since
-\[
-\frac{\chi(0)}{\psi'^2(0)} = \frac{1}{4 f^2(0)} = \frac{1}{\eta(0)},
-\]
-it follows from Theorem~\ref{thm:polyak_juditsky} that
-\[
-\sqrt{n}\left({\theta}_n-\theta \right) \overset{d}{\to} \Ncal \left(0, 1/ \eta(0)\right). 
-\]
-
-\subsubsection*{Proof of (ii)}
-We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\mathbb R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates.
-Then
-\begin{align}
-\label{eq:sgd_part2}
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
-\end{align}
-under $\Prob_{\theta,n}$.
-Under the assumption that $f(x)$ is continuously differentiable with a finite location Fisher information, the model $\{Z_n+ \theta\}_{n \in \mathbb N}$ is differentiable in quadratic mean \cite[Exm.
-7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
-\[
-\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
-\]
-where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$. 
- The random variable $L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)
-$ is bounded, and hence 
-\[
-\ex{ L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)} \to \ex{L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)}
-\]
-Any regular estimators in a LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}, hence in order to prove (ii) it is left to show that $\bar{\theta}_n$ is regular. For this purpose, 
-we use the following refinement of Theorem~\ref{thm:polyak_juditsky}, proof of which is given in Subsection~\ref{proof:thm:normal_expansion} below.
-%
-\begin{thm} \label{thm:normal_expansion}
-Set $\Delta_i = \theta_i - \theta$ and
-$\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \Delta_i$. Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{thm:polyak_juditsky}, there exists $K_1$ and $\lambda>0$ such that
-\begin{equation}
-\ex{\left| \varphi(Z_1) - \varphi(x+Z_1)  \right|} \leq K_1 |x|^{1+\lambda}
-\label{eq:PJ_additional_cond}. 
-\end{equation}
-Then:
-\begin{itemize}
-\item[(i)] \begin{equation}
-\sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1). \label{eq:normal_expansion_lem}
-\end{equation}
-where $o_{p,n}(1)$ converges in probability to $0$ as $n\to \infty$.
-\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite location Fisher information 
-\[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)} \right)^2 f(x) dx,
-\]
-then for any converging sequence $h_n \to h$,
-\[
-\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-h}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
-\]
-under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h_n/\sqrt{n}}$ with density $\prod_{i=1}^n f(x_i-h_n/\sqrt{n})$.
-\end{itemize}
-\end{thm}
-We now use this theorem to show regularity of $\bar{\theta}_n$. We have, 
-\begin{align*}
-& %\varphi(Z_1) - \varphi(x+Z_1) = 
-\sgn(Z_1) - \sgn(x + Z_1) \\
-& = \begin{cases}
-2 & Z_1 > 0,\, x+Z_1<0, \\
--2 & Z_1 <0, \, x+Z_1>0, \\
-0 & \text{otherwise}. 
-\end{cases}
-\end{align*}
-It follows that
-\begin{align*}
-\ex{ \left| \varphi(Z_1) - \varphi(x+Z_1) \right| }  \leq \Prob\left( |Z_1| < x  \right) \leq f(0) |x|, 
-\end{align*}
-hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
-\[
-\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = -2f(0) = -\psi'(0). 
-\]
-Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}.
-
-\subsubsection*{Proof of (iii)}
-%In order to prove part (ii) of Theorem~\ref{thm:sgd} 
-Consider the following result from \cite{polyak1990new}:
-\begin{thm}{\cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
-Let
-\begin{align} \label{eq:polyak_new_measurements}
-\begin{cases}
-U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = g'(U_{n-1})+Z_n \\
-\bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
-\end{cases}
-\end{align}
-Assume that the function $g(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative.
-In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \mathbb R$.
-Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution with a density for which the Fisher information exits.
-Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{thm:polyak_juditsky}-(iii) and satisfy the conditions there.
-Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$,
-and there exits $K_3$ such that 
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] \leq K_3(1+|x|^4). 
-\]
-Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
-\[
-V_n \triangleq \mathbb E \left[ \left(\bar{U}_n-x^\star \right)^2 \right] = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
-\]
-\end{thm}
-
-We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$. From \eqref{eq:polyak_new_measurements} we have
-\begin{align*} 
-U_n & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
-& = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
-\end{align*}
-so the estimator $\bar{U}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] = 1 \leq K_3(1+|x|^4)
-\]
-for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
-the conditions in Theorem~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
-In particular, $\psi'(0) = (2f(0))^{-2}$.
-Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$.
-Theorem~\ref{thm:polyak_new} implies that for any $\theta \in \mathbb R$,
-\[
-V_n = \mathbb E \left[ \left({\theta}_n-\theta \right)^2 \right]  = \frac{1}{4n f^2(0)} + o(n^{-1}).
-\]
-
-{\color{red}
-
-\subsection{Proof of Theorem~\ref{thm:normal_expansion}
-\label{proof:thm:normal_expansion}
-}
-\subsubsection*{Proof of (i)}
-The proof of part (i) of Theorem~\ref{thm:normal_expansion} requires the following two additional results from \cite{polyak1992acceleration}:
-\begin{lem}{\cite[Lem. 2]{polyak1992acceleration}}
-\label{lem:Polyak_expansion}
-Consider the process $\{\Delta_i^1 \}_{i=0}^\infty$ defined by
-\[
-\Delta^1_i = \Delta^1_{i-1} - \gamma_i (A \Delta_{i-1}+ \xi_i),\quad i=1,2\ldots.
-\]
-Assume that $A>0$ and condition (ii) of Theorem~\ref{thm:polyak_juditsky} holds. Then 
-\begin{equation}
-\label{eq:Polyak_expansion}
-\sqrt{n} \bar{\Delta}_n^1 = \frac{1}{\sqrt{n}}\sum_{i=0}^{n-1} \Delta_i^1 = \frac{\alpha_n \Delta_0^1}{\sqrt{n} \gamma_0}  + \frac{1}{\sqrt{n} A} \sum_{i=1}^{n-1} \xi_i + \frac{1}{\sqrt{n}}\sum_{i=1}^{n-1} w_i^n \xi_i,
-\end{equation}
-where $\alpha_n$ and $w_i^n$ are real numbers such that $|\alpha_n| \leq K$ and $|w_i^n|\leq K$ for some $K< \infty$, and 
-\[
-\lim_{n\to \infty} \frac{1}{n} \sum_{i=1}^{n-1} |w_i^n| = 0. 
-\]
-\end{lem}
-
-\begin{lem} \label{lem:PJ_converging_sum}
-Under the conditions of Theorem~\ref{thm:polyak_juditsky},
-\[
-\sum_{i=1}^\infty \frac{|\Delta_{i}|^{1+\lambda}}{\sqrt{i}} < \infty 
-\]
-almost surely. 
-\end{lem}
-Lemma~\ref{lem:PJ_converging_sum} follows from the proof of Theorem 2 in \cite{polyak1992acceleration}.
-
-We separate the proof of part (i) into two steps.
-\subsubsection*{Step I}
-The expansion \eqref{eq:normal_expansion_lem} holds for the process  $\{\bar{\Delta}^1_i\}_{i=1}^\infty$ defined as follows:
-\begin{align} \label{eq:Polyak_expansion_lem1_alg}
-& \Delta_i^1  = \Delta_{i-1}^1 - \gamma_i \psi'(0) \Delta_{i-1}^1 - \gamma_i \varphi(Z_i), \qquad
- \delta_0^1 = \Delta_0\\
-& \bar{\Delta}^1_i = \frac{1}{n}\sum_{i=0}^{n-1} \Delta^1_i.
-\end{align}
-
-In order to prove this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$.
-The first expression on the RHS on \eqref{eq:Polyak_expansion} goes to zero in variance.
-In addition,
-\begin{align*}
-& \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }  = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
-& = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0. 
-\end{align*}
-We obtain
-\begin{equation}
-\sqrt{n} \bar{\Delta}^1_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1), \label{eq:Polyak_expansion_aux_process}
-\end{equation}
-
-\subsubsection*{Step II} $\bar{\Delta}_n$ and $\bar{\Delta}^1_n$ are asymptotically equivalent. \\
-
-From \eqref{eq:Polyak_Juditsky_alg} and \eqref{eq:Polyak_expansion_lem1_alg}, the difference $\delta_i = \Delta_i - \Delta_i^1$ satisfies the recursion
-\[
-\delta_i = \delta_{i-1} - \gamma_i \psi'(0) \delta_{i-1} + \gamma_i \left( \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i) \right),
-\]
-where $\delta_0 = 0$. Use Lemma~\ref{lem:Polyak_expansion} with $\xi_i =  \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i)$ to obtain
-\begin{align}
-& \sqrt{n}\bar{\delta}_n = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \xi_i  \\
-& = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \label{eq:PJ_proof1} \\
-& + 
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi(\Delta_{i-1})  + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i)
-\right) \label{eq:PJ_proof2}
-\end{align}
-For the term \eqref{eq:PJ_proof1} and using \eqref{eq:Polyak_Juditsky_cond3}, there exists $K_1$ and $K_2$ such that 
-\begin{align*}
-& \eqref{eq:PJ_proof1}
-\leq K_1 \sum_{i=1}^\infty \frac{1}{\sqrt{i}} \left| \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \right| \\
-& \leq K_2 \sum_{i=1}^\infty \frac{ |\Delta_i|^{1+\lambda}}{\sqrt{i}}. 
-\end{align*}
-
-Lemma~\ref{lem:PJ_converging_sum} shows that 
-\begin{align}
-\sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}}  < \infty \label{eq:PJ_converging_sum},
-\end{align}
-hence the Kronecker lemma implies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \to 0.
-\]
-For the term \eqref{eq:PJ_proof2}, set 
-\[
-\epsilon_i \triangleq \psi(\Delta_{i-1}) + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i).
-\]
-For $a>0$ and $n \in \mathbb N$, define the event
-\[
-A_{n,a} \triangleq \left\{ \sum_{i=1}^{n-1} \frac{|\epsilon_i|}{\sqrt{i}}  \geq a  \right\}. 
-\]
-By Markov's inequality, we have
-\begin{align}
-\ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } \leq \frac{1}{a} \sum_{i=1}^{n-1} \frac{ \ex{|\epsilon_i| \Delta_{i-1} \mid }}{\sqrt{i}}. \label{eq:PJ_proof_3}
-\end{align}
-Using \eqref{eq:Polyak_Juditsky_cond3} and \eqref{eq:PJ_additional_cond}, there exists $K'$ and $\lambda'>0$ such that
-\begin{align*}
-& \ex{ |\epsilon_i| | \Delta_{i-1}}  \leq |\psi(\Delta_{i-1})| + \left| \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i) \right|  \\
-& \leq K' |\Delta_{i-1}|^{1+\lambda}. 
-\end{align*}
-Plugging this bound in \eqref{eq:PJ_proof_3} and using Lemma~\ref{lem:PJ_converging_sum},we obtain 
-\[
-\Prob(A_{n,a}) = \ex{ \ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } } \leq  \frac{K''}{a}
-\]
-for some constant $K''$. It follows that for any $\epsilon$, we may choose $a$ large enough such that 
-\[
-\sup_{n} \Prob(A_{n,a}) < \epsilon.
-\]
-This implies that for any $\epsilon>0$,
-\[
-\Prob \left( \sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty \right) \geq 1-\epsilon,
-\]
-and hence 
-\[
-\sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty
-\]
-almost surely. The Kronecker lemma now implies 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left|\epsilon_i\right| \to 0,
-\]
-hence the term \eqref{eq:PJ_proof2} satisfies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right) \epsilon_i \leq \frac{K'''}{\sqrt{n}} \sum_{i=1}^{n-1} |\epsilon_i| \to 0. 
-\]
-This conclude the proof of part (i).
-
-\subsubsection*{Part (ii)}
-Use \eqref{eq:normal_expansion_lem} to write
-\[
-\sqrt{n} \bar{\Delta}_n = G_n + o_{p,n}(1),
-\]
-where
-\[
-G_n \triangleq -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n} \varphi(Z_i). 
-\]
-From \cite[Exm.
-7.8]{van2000asymptotic}, the location model $f(x-\theta)$ with continuously differentiable $f(x)$ is differentiable in quadratic mean with the score function $-f'(x-\theta)/f(x-\theta)$.
-This fact implies the following expansion \cite[Thm.
-7.2]{van2000asymptotic}:
-\begin{align}
-\label{eq:PJ_LAN}
-& \log \frac{\Prob^n_{h_n/\sqrt{n}}}{\Prob^n_0} (Z_1,\ldots,Z_n) =  \log \prod_{i=1}^{n} \frac{f(Z_i-h_n/\sqrt{n})}  {f(X_i-\theta)} = h J_n - \frac{1}{2}h^2 I_{\theta} + o_{p,n}(1),
-\end{align}
-for any converging sequence $h_n \to h$, 
-where 
-\[
-J_n \triangleq -\frac{1}{\sqrt{n}} \sum_{i=1}^n \frac{f'(Z_i)}{f(Z_i)} .
-\]
-We have
-\begin{align*}
-& \ex{ G_n J_n} = \frac{1}{\psi'(0)}\frac{1}{n} \sum_{i=1}^n \ex{ \varphi(Z_i) \frac{f'(Z_i)}{f(Z_i)} }  \\
-& = \frac{1}{ \psi'(0)} \ex{ \varphi(Z_1) \frac{f'(Z_1)}{f(Z_1)}} =  \frac{1}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx , 
-\end{align*}
-Since both $\sqrt{n}G_n$ and $\sqrt{n}J_n$ are the sum of $n$ i.i.d. random variables with zero mean and finite variance, we obtain, from the central limit theorem and Slutsky's theorem, that
-\[
-\left(\sqrt{n} \bar{\Delta}_n, \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} \right) \overset{d}{\to} \Ncal \left( \left(0,-\frac{h^2}{2} I_\theta \right),  \begin{pmatrix}
-\frac{\chi(0)}{\psi'^2(0)} & \frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx \\
-\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx & h^2 I_\theta 
-\end{pmatrix}  \right)
-\]
-Le Cam's third lemma \cite[Exm. 6.7]{van2000asymptotic} implies that under $\Prob^n_{h/\sqrt{n}}$, 
-\[
-\sqrt{n}\bar{\Delta}_n \overset{d}{\to} \Ncal\left(\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx,  \frac{\chi(0)}{\psi'^2(0)} \right).
-\]
-
-\QEDA
-}
-
-\subsection{Proof of Theorem~\ref{thm:LAN1}
-\label{proof:thm:LAN1}
-}
-The log probability mass distribution of $B^n=(B_1,\ldots,B_n)$ is given by
-\begin{align*}
-& \log \Prob_\theta(b^n) = \sum_{i=1}^n \left( \frac{b_i+1}{2} \log  \Prob(X_i\in A_i) + 
-\frac{1-b_i}{2} \log \Prob(X_i\in A_i) \right), \quad b^n \in \{-1,1\}^n. 
-\end{align*}
-Consequently, 
-\begin{align}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) } = \sum_{i=1}^n    \frac{b_i+1}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} + 
-\sum_{i=1}^n  \frac{1-b_i}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}. 
-\label{eq:LAN_proof1}
-\end{align}
-For each $i=1,\ldots,n$, write 
-\[
-A_i = \bigcup_{k=1}^{K_i} \left(t_{i,k},t_{i,k+1} \right),
-\]
-where $t_{i,1}<\ldots<t_{i,K_i}$ and, with a slight abuse of notation, $t_{i,1}$ and $t_{i,K_i}$ may also be $-\infty$ or $+\infty$, respectively. Thus
-\[
-\Prob_{\theta}(X_i \in A_i) = \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta).
-\]
-In particular, since $f$ is differentible, $\Prob_{\theta}(X_i \in A_i)$ is twice differentiable, and we may write
-\begin{align*}
-\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)  = \Prob_{\theta} (X_i \in A_i) + \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \frac{h}{\sqrt{n}} + o(h), 
-\end{align*}
-and thus
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} = \log \left(1 + \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} + o(h) \right) \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2 + o(h^2).
-\end{align*}
-Similarly, we have
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 + o(h^2).
-\end{align*}
-From \eqref{eq:LAN_proof1} we obtain
-\begin{align*}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
-\left( 
-\frac{b_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-b_i}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}   \right) \\
- & - \frac{h^2}{2n} 
- \sum_{i=1}^n 
-\left( 
- \frac{b_i+1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-b_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 \right) + o(h^2) \\
-\end{align*}
-%
-Noting that 
-\[
-\frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} = \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)},
-\]
-the proof is completed by proving the following two claims:
-\begin{itemize}
-\item[I.] 
-For $i=1,\ldots,n$ denote 
-\[
-U_i = \frac{B_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-B_i}{2}  \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}. 
-\]
-Then 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0, \kappa(\theta) \right). 
-\]
-\item[II.]
-For $i=1,\ldots,n$ denote 
-\[
-V_i =  \frac{B_i-1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-B_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2.
-\]
-Then 
-\[
-\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} \kappa(\theta). 
-\]
-\end{itemize}
-\subsubsection*{Proof of Claim I}
-First note that 
-\begin{align*}
-\mathbb E  [U_i] & = 
- \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=1)   + 
- \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=-1)  = 0. 
-\end{align*}
-In addition,
-\begin{align*}
-& \mathbb E U_i^2 = 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2  \Prob (B_i=1)   + 
-\left( \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2 \Prob (B_i=-1) \\
-& =
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)} +  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)} \\
- & =  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left(1-\Prob_{\theta}(X_i \in A_i) \right)} 
-\end{align*}
-Therefore
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 = L_n(A_1,\ldots,A_n) \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ such that the limit above exists.
-We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition for his version of the central limit time: for any $\delta>0$ we have that
-\begin{align*}
-& \mathbb E \left| U_i \right|^{2+\delta} =
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} 
-\end{align*}
-and
-\begin{equation}
-\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} } { \left( \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta} = 
-\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
-\label{eq:Lyaponov}
-\end{equation}
-Next, we claim that there exits $\delta>0$ and $K>0$, that are independent of $n$, such that
-\begin{align}
-\frac{1}{n} \sum_{i=1}^n \mathbb E  |U_i|^{2+\delta}  < M \label{eq:Lyaponov_num}
-\end{align} 
-for all $n$ large enough. To see this, note that
-\begin{align*}
-& \mathbb E |U_i|^{2+\delta} = 
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}  \\
-  &  = \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} } 
-  \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \\
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}, 
-\end{align*}
-where the last transition is because 
-\[
- \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \leq 1. 
-\]
-We now use the fact that each $A_i$ is a finite union of interval and consider the following lemma, proof of which is given in Appendix~\ref{proof:lem:bound_intervals_delta}.
-\begin{lem} \label{lem:bound_intervals_delta}
-Let $f(x)$ be a log-concave, symmetric, and differentiable PDF such that $\eta(x)$ is unimodal.  There exists $\delta>0$ such that for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, 
-\begin{equation}
-\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^{2+\delta} }
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} } 
-\leq  2^\delta f^{2+\delta}(0). 
-\label{eq:lem_bound_intervals_delta}
-\end{equation}
-\end{lem}
-
-Lemma~\ref{lem:bound_intervals_delta} implies 
-\begin{align*}
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} = \frac{\left| \sum_{k=1}^{K_i} (-1)^k f(x_{i,k}-\theta) \right|^{2+\delta} }
-  { \left( \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta} \left( 1 - \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta}} \\
-  & \leq 2^\delta f^{2+\delta}(0). 
-\end{align*}
-In particular, we conclude that 
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} \leq 2^\delta f^{2+\delta}(0), 
-\]
-and thus for any $\delta>0$ the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we conclude that 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0,\kappa(\theta) \right). 
-\]
-
-\subsubsection*{Proof of Claim II} 
-We have:
-\begin{align*}
-\mathbb E V_i  & = 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)}  
-+ 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)}  \\
- & = 
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left( 1-\Prob_{\theta}(X_i \in A_i) \right)}  
-\end{align*}
- We conclude that:
-\begin{equation} \label{eq:LAN_limit_cond}
-\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =   L_n(A_1,\ldots,A_n)  \to \kappa(\theta)
-\end{equation}
-Since the $V_i$s are independent of each other, Kolmogorov's law of large numbers implies
-%(e.g. \cite[Theorem 10.2.3]{sen1994large}) 
-\[
-\frac{1}{n} \sum_{i=1}^n  V_i \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ for which the limit \eqref{eq:LAN_limit_cond} exists.
-
-\QEDA
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals_delta}} 
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-and 
-\[
-\eta_\delta(x) \triangleq  \frac{  \left(\delta_1(x) \right)^{2+\delta}}{  \left(\Delta_1(x)  \right)^{1+\delta}
-(1-\Delta_1(x))^{1+\delta}}
-= \frac{  \left( f (x) \right)^{2+\delta}}{ \left(F(x) \right)^{1+\delta}(1-F(x))^{1+\delta}}. 
-\]
-The proof is by induction on $n$.
-For the case $n=1$ the LHS of \eqref{eq:lem_bound_intervals_delta} equals $\eta_\delta(x)$.
-Note that $\eta_\delta(0) = 2^\delta f^{2+\delta}(0)$, so it is enough to prove that $\eta_\delta(0)$ attains it maximum at $x=0$.
-We have $\eta_\delta(x) = \eta^{1+\delta}(x)/f^\delta(x)$, and thus
-\[
-\log \eta_\delta'(x) = (1+\delta) \frac{\eta'(x)}{\eta(x)} - \delta \frac{f'(x)}{f(x)}. 
-\]
-By Assumption~\ref{assump:failure_rate} both terms above are negative for $x>0$, so that $\log \eta_\delta'(x) \leq 0$ if and only if
-\begin{equation} \label{eq:delta_proof_cond}
-(1+\delta) \left| \frac{\eta'(x)}{\eta(x)} \right| \geq \delta \left| \frac{f'(x)}{f(x)} \right|, \qquad x>0.
-\end{equation}
-Also by Assumption~\ref{assump:failure_rate}, for $x>0$ we have
-\[
-0 > (\log \eta(x))' = \frac{h'(x)}{h(x)}-\frac{h'(-x)}{h(-x)},
-\]
-so that \eqref{eq:delta_proof_cond} is satisfies for $\delta>0$ small enough.
-
-Next, assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^{2+\delta}} 
-{\left(\Delta_n \right)^{1+\delta}\left(1- \Delta_n \right)^{1+\delta} } \leq \eta_\delta(0) = 2^\delta f^{2+\delta}(0) . 
-\label{eq:lem_bound_intervals_delta_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%If $x_{i+1} = x_i$ for some $i=1,\ldots,N-1$, then then the indices $i$ and $i+1$ may  be removed from all sums in \eqref{eq:lem_bound_intervals}, what brings us to the case $n = N-2$.
-Therefore, we may assume that $x_1 < \ldots < x_n$.
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  (2+\delta) \log \delta_N - (1+\delta) \log \Delta_N - (1+\delta) \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{(2+\delta) (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(1+\delta)(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(1+\delta)(-1)^{k+1} f(x_k)}{1-\Delta_N }.
-\]
-We conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero_delta}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N(1+\delta)}{2+\delta} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-From the same reason as in the proof of Lemma~\ref{lem:bound_intervals_delta}, \eqref{eq:gradient_zero_delta} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_delta_proof} equals $\eta_\delta(x_1)$ which was shown to be smaller than $\eta_\delta(\epsilon)$.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_delta_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$,  $x_i, x_{i+1} = -\epsilon$ for some $i$, or $x_i, x_{i+1} = \epsilon$ for some $i$.
-It is therefore enough to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Assume first $x_N \rightarrow -\infty$. Then 
-\begin{align*}
-\frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)^{1+\delta} } ,
-\end{align*}
-which is smaller than $\eta_\delta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
-\begin{align*}
-& \frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right)^{1+\delta} }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^{2+\delta}} 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)^{1+\delta}\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right)^{1+\delta} },
-\end{align*}
-where $x'_{m} = x_{m+1}$ for $m=1,\ldots, N-1$. The last expression is smaller than $\eta_{\delta}(0)$ by the induction hypothesis.  \QEDA \\
-
-\subsection{Proof of Theorem~\ref{thm:non_existence}
-\label{proof:thm:non_existence}
-}
-
-Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta) = \eta(0)$. 
-%
-Since $B_1,B_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, $\theta$ is in $\Xi$ if and only if
-\begin{equation}
-\label{eq:non_existence_proof}
-\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0). 
-\end{equation}
-By assumption, we have $B_i^{-1} = A_i$ where $A_i$ can be expressed as
-\[
-A_i = \cup_{i=1}^K (a_{i,k},b_{i,k}), 
-\]
-where $a_{i,1} \leq b_{i,1} \leq \ldots \leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values $-\infty$ and $\infty$, respectively. Denote
-\[
-\mathcal B_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\}.
-\]
-For any $\theta$ and $\epsilon>0$, denote 
-\[
-S_n(\theta, \epsilon) \triangleq \left\{ i\leq n \,:\, (\theta-\epsilon,\theta+\epsilon) \cap \mathcal B_i \neq \emptyset \right\}
-\]
-In words, $S_n$ contains all integers smaller than $n$ in which an $\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals consisting $A_i$. 
-%
-We now claim that 
-if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. Indeed, for such $\theta$ we have
-\begin{align}
-& L_n(A_1,\ldots,A_n; \theta) \nonumber \\
-& = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
-\frac{ \left(\sum_{k=1}^{K}  f(\theta - b_{i,k})- f(\theta - a_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& 
-+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(b_{i,k}-\theta) - f(a_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& \overset{(a)}{\leq}
-\frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
- \label{eq:non_existence_proof1}
-\end{align}
-where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} and the fact that for $i \in S_n(\theta, \epsilon)$, 
-\[
-\max\left\{ \max_k \eta(b_{i,k}-\theta) , \max_k \eta(a_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
-\]
-Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, \eqref{eq:non_existence_proof1}, and thus $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.
-\par
-For $k\in \mathbb N$, assume by contradiction that there exists $N \geq 2K + 1$ distinct elements
-$\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$ consists of at most $K$ intervals, we have that 
-\begin{equation}
-\label{eq:few_optimality_points_proof}
-\card (\cup_{i=1}^n \mathcal B_i) \leq 2 n K. 
-\end{equation}
-Fix $\epsilon>0$ such that 
-\[
-\epsilon < \frac{1}{2}\min_{i\neq j} |\theta_i - \theta_j|. 
-\]
-Since for each $\theta \in \Theta$ we have $S_n(\theta, \epsilon) \to 1$, there exists $n$ large enough such that 
-\[
-\card \left(S_n(\theta_i, \epsilon) \right) \geq n \left(1-\frac{1}{2N} \right)
-\]
-for all $i=1,\ldots,N$.
-However, $S_n(\theta_1,\epsilon), \ldots S_n(\theta_N,\epsilon)$ are disjoint, so the cardinallity of their union is at least $n\left(1-\frac{1}{2N} \right)N$ which is grater than $2nK + n/2$ in contradiction to \eqref{eq:few_optimality_points_proof}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEfull,onebit}
-
-\end{document}

### 2019-09-23 appendices.tex
Adding a bib file

--- 2019-09-19 onebit_full.tex
@@
-%% \documentclass[11pt]{article}
-\documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper
-
-%LatexiDiff ignore tikz:
-% $: latexdiff -c "PICTUREENV=(?:picture|tikzpicture|DIFnomarkup)[\w\d*@]*" old.tex new.tex > diff.tex
-
-%\IEEEoverridecommandlockouts                              %
-
-%\usepackage{mathcomSTEP}
-
-%\overrideIEEEmargins 
-%\IEEEoverridecommandlockouts                              % This command is only needed if 
-% you want to use the \thanks command
-
-%\overrideIEEEmargins                                      % Needed to meet printer requirements.
-
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-\onecolumn
-
-\usepackage{mathptmx} 
-\usepackage{times} 
-\usepackage{amsmath} 
-\usepackage{amsbsy} 
-\usepackage{amssymb}
-
-%\usepackage{newtxtext, newtxmath}
-\usepackage{mathrsfs}
-\usepackage{comment}
-\usepackage[export]{adjustbox}
-\usepackage{tikz}
-\usetikzlibrary{external,positioning,decorations.pathreplacing,shapes,arrows,patterns}
-
-\usepackage[hidelinks]{hyperref}
-%\tikzexternalize[mode=list and make]
-\usepackage{algorithmicx}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage{pstool}
-\usepackage[latin1]{inputenc}
-\usetikzlibrary{arrows,shapes}
-\usepackage{xifthen}
-\usepackage{epic}
-%\usepackage{caption}
-\usepackage{epstopdf}
-
-\newtheorem{thm}{\bf{Theorem}}
-\newtheorem{cor}[thm]{\bf {Corollary}}
-\newtheorem{lem}[thm]{\bf {Lemma}}
-\newtheorem{prop}[thm]{\bf {Proposition}}
-\newtheorem{example}{\bf {Example}}
-\newtheorem{definition}{\bf {Definition}}
-\newtheorem{rem}{\bf {Remark}}
-\newtheorem{assump}{\bf {Assumptions}}
-
-\newcommand{\ex}[1]{\ensuremath{\mathbb{E}\left[ #1\right]}}
-
-\newcommand{\Var}[1]{\ensuremath{\mathrm{Var} \left[ #1\right]}}
-
-\newcommand{\unif}{\mathsf{unif}}
-\newcommand{\card}{\mathrm{card}}
-\newcommand{\ARE}{\mathsf{ARE}}
-\newcommand{\supp}{\mathrm{supp} }
-\renewcommand\vec[1]{\ensuremath\boldsymbol{#1}}
-\newenvironment{proof}{\paragraph*{Proof}}{\hfill$\square$ \newline}
-\newcommand{\sgn}{\mathrm{sgn} }
-\newcommand{\Prob}{\mathbb{P} }
-\newcommand{\argmax}{\mathrm{argmax}}
-\newcommand*{\QEDA}{\hfill\ensuremath{\square}}
-\newcommand{\CEO}{\mathsf{CEO}}
-\newcommand{\Ncal}{\mathcal{N}}
-
-\newcommand{\enc}{\mathsf{enc}}
-\newcommand{\est}{\mathsf{est}}
-
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-\tikzstyle{sint}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.8cm,thick ]
-\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
-\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
-\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.7cm,thick ]
-\tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-
-\author{
-    \IEEEauthorblockN{
-Alon Kipnis\IEEEauthorrefmark{1} and   
-    John C. Duchi\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}  \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}Stanford University, Department of Statistics \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Stanford University, Department of Electrical Engineering. }
-}
-
-\title{\LARGE \bf Mean Estimation from One-Bit Measurements}
-
-\begin{document}
-\graphicspath{{./Figs/}}
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{abstract}
-
-%{\color{red}  See LASSO results in http://arxiv.org/abs/1506.02181v1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\input{introduction}
-
-\section{Problem Formulation \label{sec:problem}}
-
-Let $f(x)$ be a symmetric and log-concave density function with a finite second moment $\sigma^2$.
-For $\theta \in \Theta$, denote by $P_X$ the probability distribution with density $f\left( x-\theta \right)$.
-Therefore, $P_X$ is an absolutely continuous log-concave distribution with mean $\theta$ and variance $\sigma^2$.
-Symmetry and log-concavity of $f(x)$ imply that $P_X$ is strongly unimodal (has a unique local maxima) with its mode at $x =\theta$ \cite{ibragimov1956composition}.
-We further assume that the \emph{parameter space} $\Theta$ is a closed interval of the real line.
-\par
-In some situations it is useful to assume that $\theta$ is drawn once from the prior distribution $\pi$ on $\Theta$.
-In this case we assume that $\pi$ is an absolutely continuous distribution, and denote its density by $\pi(\theta)$, i.e., $\pi(d\theta) = \pi(\theta)d\theta$.
-\par
-The random variables $X_1,\ldots,X_n$ represent $n$ independent samples from $P_X$. 
-We are interested in estimating $\theta$ from a set of $n$ binary messages $B_1,\ldots,B_n$, obtained from $X_1,\ldots,X_n$ under three possible scenarios illustrated in Figure~\ref{fig:setup}: 
-\begin{itemize}
-\item[(i)~~] Centralized $B_i(X_1,\ldots,X_n)$, $i=1,\ldots,n$.
-\item[(ii)~] Adaptive $B_i(X_i,B_1,\ldots,B_{i-1})$, $i=2,\ldots,n$.
-\item[(iii)] Distributed $B_i(X_i)$, $i=1,\ldots,n$.
-\end{itemize}
-
-The performance of an estimator ${\theta}_n \triangleq {\theta}_n(B^n)$ in any of these cases is measured according to the quadratic risk:
-\begin{equation}
-\label{eq:error_def}
-R_n \triangleq \mathbb E\left({\theta}_n - \theta \right)^2,
-\end{equation}
-where the expectation is taken with respect to the distribution of $X_1,\ldots,X_n$ and, whenever available, a prior distribution $\pi(\theta)$ over $\Theta$.  
-%It is well known that minmax estimation error 
-%\begin{equation}
-%R_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left({\theta}_n - \theta \right)^2 | \theta \right],
-%\end{equation}
-%can be obtained from $R_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}. 
-%
-The main problems we consider in this paper are the minimal value of \eqref{eq:error_def}, as a function of $n$ and $f(x)$, under different choices of the encoding functions in cases (i), (ii), and (iii).
-\par
-
-We give particular attention to the ARE of estimators with respect to an asymptotically normal efficient estimator that is not subject to the bit constraint.
-Specifically, let $\{a_n,\,n\in \mathbb N\}$ be a sequence such that
-\[
-\sqrt{a_n}\left({\theta}_n - \theta\right) \overset{d}{\longrightarrow} \Ncal(0, \sigma^2).
-\]
-Then the ARE of ${\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
-\[
-\ARE({\theta}_n) \triangleq
-\lim_{n\rightarrow \infty} \frac{a_n}{n}. 
-\]
-Note that in the special case where there exists $V \in \mathbb R$ such that
-\[
-a_n \mathbb E \left({\theta}_n - \theta \right)^2 = V + o(1),
-\]
-with $o(1)\to 0$ as $n\to \infty$, then the ARE of ${\theta}_n$ is finite and equals $\sigma^2/V$. \par
-
-In addition to the notation above, we also denote by $F(x)$ the cumulative distribution function of $X_i$, and define
-\begin{equation} \label{eq:eta_def}
-\eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))} =  \frac{f(x)f(-x)}{F(x)F(-x)}, 
-\end{equation}
-where the last equality is due to symmetry of $f(x)$. We note that 
-\begin{equation}
-\label{eq:eta_h}
-\eta(x) = h(x)h(-x) = f(x) \left( h(x) + h(-x) \right), 
-\end{equation}
-where 
-\[
-h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
-\]
-is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function since $f(x)$ is log-concave \cite{bagnoli2005log}. 
-%
-For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as illustrated in Fig.~\ref{fig:eta}. 
-%
-In this paper we only consider the normal distribution and other log-concave symmetric distributions for which this property of $\eta(x)$ holds. Specifically, we require the following:
-\begin{assump} \label{assump:failure_rate}
- $\eta(x)$ has a unique maximum (at the origin) and is a non-increasing function of $|x|$. 
-\end{assump}
-%That is, Assumption~\ref{assump:failure_rate} says that $\eta'(x) < 0 $ for all $x>0$. 
-Under this assumption we have, 
-\[
-4f^2(x) \leq \eta(x) \leq \eta(0),
-\] 
-%
-where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median.
-Combined with log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that $\eta(x)$ vanishes as $|x|\rightarrow \infty$.
-\par
-%
-Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions).
-Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.\par
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -3, xmax=3, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.9,
-samples=10, 
-xlabel= $x$,
-xtick={-2,-1,0,1,2},
-xticklabels={-2,-1,0,1,2},
-ytick={0,0.3989423,0.6366198},
-yticklabels={0,$\frac{1}{\sqrt{2 \pi}}$,$2/\pi$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\eta(x)$};
-\addplot[domain = -5:5, samples = 50, color = red, solid, smooth]  {exp(-x^2/2) / sqrt(2*3.14159)};
-\addlegendentry{$\phi(x)$};
-\addplot[domain = -5:5, samples = 50, color = black, solid, dashed]  {4*exp(-x^2) / (2*3.14159)};
-\addlegendentry{$4\phi^2(x)$};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -4, xmax=4, 
-restrict y to domain = -10:0,
-ymin = -10,
-samples=10, 
-xlabel= $x$,
-xtick={-3,-2,-1,0,1,2,3},
-xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,-0.45158,-0.919},
-yticklabels={0,,},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\log \eta(x)$};
-\addplot[domain = -5:5, samples = 30, color = red, solid, smooth]  {-(x)^2/2 -0.9189};
-\addlegendentry{$\log \phi(x)$};
-\end{axis}
-\end{tikzpicture}
-\caption{
-The function $\eta(x) = f^2(x) / F(x)F(-x)$ for $f(x) = \phi(x)$ the standard normal density.
-\label{fig:eta}
-}
-\end{center}
-\end{figure}
-
-\section{Consistent Estimation and Off-the-shelf Bounds \label{sec:preliminary}}
-%
-In this section we adapt known results to derive lower and upper bounds on the relative efficiency under setting (iii). These bounds establish the following facts:
-\begin{itemize}
-\item[I.] A consistent estimator with an asymptotically normal distribution always exists in setting (iii), and hence in setting (ii). 
-\item[II.] For the normal distribution, the ARE in setting (iii) is at most $3/4$. Namely, under setting (iii), all estimators are strictly inferior compared to the sample mean. 
-\end{itemize}
-
-\subsection{Consistent Estimation}
-Fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
-\[
-B_i = \mathbf 1_{X_i>\theta_0}, 
-\]
-where $\mathbf 1_A$ is the indicator of the event $A$. We have
-\[
-P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
-\]
-so that 
-\begin{equation}
-\label{eq:estimator_naive}
-{\theta}_n = \theta_0 + F^{-1}\left( P_n \right)
-\end{equation}
-is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set due to log-concavity.
-Furthermore, the variance of $P_n$ is $F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)$, and hence the delta method implies that ${\theta}_n$ is asymptotically normal with variance
-\begin{equation} 
- \frac{F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}{f^2(\theta-\theta_0)} = \frac{1}{
-\eta(\theta-\theta_0)}.
-\end{equation}
-In particular, the ARE of ${\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
-In other words, for a prescribed accuracy, ${\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
-\par
-%
-%
-Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of ${\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
-This ARE is attained only when $\theta_0 = \theta$, whereas $\theta$ is apriori unknown.
-Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of ${\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
-As an example, when $f(x)$ is a normal density, the ARE of ${\theta}_n$ is less than $\approx 0.14$ when $\theta_0$ is $2$ standard deviations from $\theta$.
-Therefore, the estimator ${\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
-\par
-It is suggested that we can attain lower variance in estimation by updating the threshold value $\theta_0$ in \eqref{eq:estimator_naive} after observing one or a batch of the single bit messages.
-Schemes with such adaptation fall within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
-\par
-
-\subsection{Multiterminal Source Coding \label{sec:ceo}}
-The CEO setting considers the estimation of a sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_i$ is available at $n$ terminals.
-At each terminal $i$, an encoder observes the $k$ noisy samples
-\[
-X_{i,j} = \theta_j + Z_{i,j},\qquad j=1,\ldots,k, \qquad i = 1,\ldots,n,
-\]
-and transmits $r_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates ${\theta}_1,\ldots,{\theta}_k$ with the goal of minimizing the quadratic risk:
-\[
-R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - {\theta}_j \right)^2 \right]. 
-\]
-Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $r_1=\ldots=r_n = 1$.
-It follows that, assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
-%
-Consequently, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the minimal MSE in the CEO setting as $k \to \infty$.
-Note that the difference between the CEO setting and ours lays in the privilege of each of the encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realizations, rather than a single realization using a single bit in ours.
- \par
-When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k$ goes to infinity were fully characterized in \cite{prabhakaran2004rate}.
-Furthermore, the work of \cite{chen2004upper} provided an expression for quadratic risk attained in the CEO setting under Gaussian priors.
-Adapting to our setting, this expression provides the following proposition:
-\begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is arbitrary.
-Then any estimator ${\theta}_n$ of $\theta$ in the distributed setting satisfies
-\begin{equation} \label{eq:ceo_bound}
- n \ex{\left( \theta - \theta_n \right)^2} \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
-\end{equation}
-where the expectation is with respect to $\theta$ and $X^n$.
-\end{prop}
-
-\begin{proof}
-See Appendix~\ref{app:proof:prop_ceo_lower_bound}.
-\end{proof}
-
-From the formulation of the CEO problem, it follows that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is attributed to the ability to perform coding over blocks.
-Namely, each encoder in the CEO setting may encode an arbitrary number of $k$ independent realizations of $\theta$ using $k$ bits, versus only one realization with one bit in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product probability space that distinguishes between the CEO problem with one bit per encoder on average and the mean estimation problem from one-bit measurements in the distributed setting.
-
-\section{Adaptive Estimation \label{sec:sequential}}
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $\eta(0)\sigma^2$, which is the ARE of the median of the sample $X_1,\ldots,X_n$.
-We also provide a particular adaptive estimation scheme that attains this maximal efficiency.
-%Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $B_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages.
-%Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $\eta(0)\sigma^2$.
-
-\subsection{Limited efficiency in the adaptive setting}
-Our first result asserts that the ARE of any adaptive encoding and estimation scheme is bounded from above by $\eta(0)\sigma^2$. %This result follows from the following theorem:
-\begin{thm}[maximal relative effeciency] \label{thm:adpative_lower_bound}
-Let ${\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Figure~\ref{fig:setup}-(ii). Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-n\mathbb E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0},
-\]
-where 
-\[
-I_0 = \mathbb E \left( \frac{d}{d\theta} \log \pi (\theta) \right)^2
-\]
-is the Fisher information with respect to a location model in $\theta$. 
-\end{thm}
-
-\subsubsection*{Proof}
-%We first bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
-The result then follows using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are in
-See Appendix~\ref{proof:thm:adpative_lower_bound}.\par
-
-Theorem~\ref{thm:adpative_lower_bound} implies that any estimator ${\theta}_n$ from any adaptive encoding scheme satisfies
-\[
-n\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{1}{4f^2(0)}+O(n^{-1}),
-\]
-and 
-\[
-\ARE({\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
-\]
-It is possible to extend Theorem~\ref{thm:adpative_lower_bound} to any other loss functions using a more subtle version of the Van Tress inequality provided in \cite{efroimovich1980information}.
-See also \cite{DBLP:journals/corr/abs-1902-08582}.
-\par
-%
-Next, we provide an adaptive encoding and estimation scheme that attains the maximal ARE of $\eta(0)\sigma^2$.
-
-\subsection{Asymptotically optimal estimator}
-Let $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ be a strictly positive sequence. Consider the following estimator ${\theta}_n$ for $\theta$:  
-\begin{equation}
-\label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n B_n, \quad n = 1,2,\ldots,
-\end{equation}
-where 
-\begin{equation}
-B_n = B_n (X_n,\theta_{n-1}) =\sgn (X_n - \theta_{n-1}).
-\end{equation}
-Define the $n$th step estimation as
-\begin{equation} \label{eq:sgd_est}
-\bar{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
-\end{equation}
-
-We have the following results:
-\begin{thm} \label{thm:sgd}
-Consider the sequence $\left\{\bar{\theta}_n \right\}_{n\in \mathbb N}$ defined by \eqref{eq:sgd_est}. 
-\begin{enumerate}
-\item[(i)] Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions1}
-\begin{cases}
-\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
-\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
-\mathrm{for~some~}0< \lambda \leq 1
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Then
-\[
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left(0,\frac{1}{\eta(0)}\right).
-\]
-%
-%
-\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with a finite location Fisher information, namely
-\[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)}  \right)^2 f(x) dx < \infty.
-\]
-%(or that $f(x-\theta)$ is differentiable in quadratic mean).  
-Then for any bounded, symmetric, and quasi-convex function $L$, 
-\begin{align} 
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
-\\
-& \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
-\end{align}
-where $Z \sim \Ncal(0,1)$. 
-%
-%
-\item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions2}
-\begin{cases}
-\gamma_n = o(n^{-2/3}), &  \\
-\sum_{n=1}^\infty \gamma_n = \infty.  & \\
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ with $\beta \in (2/3,1)$). Then
-\[
- \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{n\eta(0)} + o(n^{-1}). 
-\]
-\end{enumerate}
-\end{thm}
-
-\subsubsection*{Proof}
-See Appendix~\ref{proof:thm:sgd}. \par
-
-Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the maximal ARE, as established by Theorem~\ref{thm:adpative_lower_bound}.
-%Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$.
-%
-The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$.
-Consequently, the procedure above is known as averaged stochastic gradient descent for minimizing $x \to |x|$ given the data $X_1,\ldots,X_n$.
-The minimal value of this optimization is the sample median, and Theorem~\ref{thm:sgd} provides conditions for the sequence of gradient steps so that the algorithm converges to this minimum.
-In particular, parts (i) and (ii) of Theorem~\ref{thm:sgd} provides conditions under which $\bar{\theta}$ is asymptotically normal and local asymptotically minimax, in the sense that it attains the local asymptotic minimax bound \cite{van2000asymptotic}.
-Part (iii) provides an additional condition under which $\bar{\theta}$ also converges in its second moment.
- \par
-%Note that $\theta_0$ is not explicitly defined in equation \eqref{eq:sgd_est}.
-A reasonable initialization for $\theta_0$ is $\theta_0 = \mathbb E [\theta]$, although Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
-Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$.
-\\
-In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $B_n$ depends on its private sample as well as the current gradient descent estimate $\theta_{n-1}$.
-In this sense, each encoder in this algorithm interacts with previous one by using the current estimate.
-%
-As we explain next, 
-it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ with only one round of interactions among the encoders.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
-% \node[below of = source, node distance = 1cm] (source2) {$X_2$};
-%\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};  
-%\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};
-
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[below of = source, node distance = 0.5cm] {$\vdots$};
-
-\node[int1, right of = enc3, node distance = 2.1cm ] (est) {$\est_1$};
-
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
-
-%\draw[->,line width = 2pt] (enc2) -| node[above, xshift = -1cm] (mes2) {$B_2$} (est);
-
-\draw[->,line width = 2pt] (enc3) -- node[above, xshift = 0cm]  {$B_{n_1}$} (est);
-
-\node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
-\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {$\enc$};  
-\draw[->,line width = 2pt] (sourceB) -- (enc1B);
-
-\node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
-\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {$\enc$};  
-\draw[->,line width = 2pt] (source3B) -- (enc3B); 
-\node[below of = sourceB, node distance = 0.4cm] {$\vdots$};
-
-\node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {$\est_2$};
-
-\draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.5cm] {$B_{n_1+1}$} (estB);
-\draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);
-
-\draw[->,line width = 1pt] (est.east) node[above, xshift  =0.5cm] {${\theta}_{n_1}$} -| (enc1B.north);
-
-%\draw[->,line width = 1pt] (enc1B) -- (enc3B);
-
-\draw[->,line width = 0.5pt] (est.east) -| +(1.3,-0.5) -- +(1.3,-2.5) -| (enc3B.north);
-
-%\draw[->,line width = 1pt] (enc1B)  -- node[right] {${\theta}_{n_1}$} (enc3B);
-
-\draw[->,line width = 0.5pt] (estB) -- +(0.8,0) node[right] {${\theta}_n$};
-\node[below of = enc1B, node distance = 0.5cm] {$\vdots$};
-
-\end{tikzpicture}
-\end{center}
-\caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
-\label{fig:one_round}
-}
-\end{figure}
-
-\subsection{Maximal Efficiency using One Round of Threshold Adaptation}
-In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
-\[
-B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
-\]
-and deduced that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
-%
-We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ based on previously observed bits at least once.
-%
-In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
-We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate ${\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use ${\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$.
-Figure~\ref{fig:one_round} illustrates a diagram of this procedure.
-%
-The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
-\begin{thm}
-For $i=1,\ldots,n$ set
-\[
-B_i = \begin{cases}
- \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
- \mathbf 1_{X_i \geq {\theta}_{n_1} }& i={n_1+1,\ldots,n},
-\end{cases}
-\]
-where $n = n_1+ n_2$ and 
-\[
-{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
-\frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
- \right).
-\] 
-Let 
-\[
-{\theta}_{n_2}  = {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
-\]
-and assume that $n_1(n) \rightarrow \infty$ and $n_1(n)/n \rightarrow 0$. Then:
-\begin{align*}
- \sqrt{n} \left( {\theta}_{n_2} - \theta  \right) \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
-\end{align*}
-\end{thm}
-%
-%
-\begin{proof}
-For $t\in \mathbb R$, set
-\[
-p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
-\]
-From the central limit theorem
-\begin{align*}
-& \sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)  = \sqrt{\frac{n}{n_2}} \sqrt{n_2} \left(  p_{n_2}(t) - F(\theta - t) \right) \\
-& \overset{d}{\rightarrow} \Ncal\left( 0, V(t) \right),
-\end{align*}
-where
-\[
-V(t) \triangleq F(\theta - t) F \left( t - \theta\right). 
-\]
-Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ implies
-\begin{align*}
-& \sqrt{n} \left( t + F^{-1}(\hat{p}_{n_2}(t)) - \theta \right) \\
-&= \sqrt{n} \left( g(\hat{p}_{n_2}(t)) - g \left(F(\theta-t) \right)  \right) \\
-& \overset{d}{\to} \Ncal\left(0, 
-1/\eta(\theta-t) \right).
-\end{align*}
-%where this convergence is uniform in $t$ since all moments of $F^{-1}(\hat{p}_{n_2})$ exists. 
-On the other hand, by the law of large numbers,
-\[
-p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
-\]
-so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity and thus 
-\[
-\eta( {\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
-\]
-Finally,
-\begin{align*}
-& \sqrt{n}\left({\theta}_{n_2} - \theta\right) \\
-& = \sqrt{n} \left( {\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}({\theta}_{n_1})) - \theta \right)  \\
-& \overset{d}{\to} \Ncal\left( 0, 
-1/\eta(0) \right) 
-\end{align*}
-by Slutsky's theorem.
-\end{proof}
-%
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=10cm, height=6cm,
-xmin = 0, xmax=800, 
-restrict y to domain = 0:3,
-ymin = 0,
-ymax = 3.4,
-samples=10, 
-xlabel= $n$,
-ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
-%xtick={-3,-2,-1,0,1,2,3},
-%xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,1,1.57},
-yticklabels={0,1,$\pi/2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-
-\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{asymptotically optimal};
-
-%\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
-
-\addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{single interaction};
-
-\end{axis}
-\end{tikzpicture}
-%\begin{tikzpicture}
-%\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
-%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left({\theta}_n - \theta \right)^2$};
-%\node[scale = 0.7] at (0,-2.4) {$n$};
-%\end{tikzpicture}
-\caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.
-In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$.
-The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage.
-\label{fig:adaptive_error}  }
-\end{center}
-\end{figure}
-
-\section{Distributed Estimation \label{sec:distributed}}
-In this section, we now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii) where  each one-bit message $B_i$ is only a function of its private sample $X_i$.
-In this case, the $i$th encoder is fully characterized its \emph{detection region}, defined as
-\[
-A_i = \left\{ x \in \mathbb R \,:\, B_i(x) = 1 \right\}.
-\]
-Consequently, $B_i$ is of the form
-\[
-B_i = \begin{cases} 1 & X_i \in A_i, \\
--1 & X_i \notin A_i,
-\end{cases} \quad i\in \mathbb N,
-\]
-where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\par
-
-As a first step, we provide conditions under which the messages $B_1,B_2,\ldots$ define a local asymptotic normal family.
-
-\begin{thm} \label{thm:LAN1}
-For $n \in \mathbb N$ and $A_n \subset \mathbb R$,  define
-\begin{equation}
-\label{eq:precision_general}
-L_n(A_1,\ldots,A_n;\theta) \triangleq \frac{1}{n} \sum_{i=1}^n \frac{ \left(\frac{d}{d \theta} \Prob(X_i \in A_i) \right)^2 }{ \Prob(X_i \in A_i)\left(1- \Prob(X_i \in A_i) \right) }. 
-\end{equation}
-Consider the following conditions:
-\begin{itemize}
-\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is a log-concave, differentiable and symmetric density function such that $\eta(x)$ is unimodal.
-\item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
-\item[(iii)] The limit 
-\begin{equation}
-\label{eq:LAN_lim}
-\kappa(\theta) \triangleq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
-\end{equation}
-exists. 
-\end{itemize}
-For $i=1,\ldots,n$ set
-\[
-B_n = \begin{cases} 1 & X_n \in A_n, \\
--1 & X_n \notin A_n. 
-\end{cases} 
-\]
-For any $\theta$, $f(x)$ and a sequence of sets $A_1,A_2,\ldots$ such that (i)-(iii) hold, and any $h\in \mathbb R$, we have
-\begin{align*}
-& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (B_1,\ldots,B_n) }{
-\mathbb P_{\theta} (B_1,\ldots,B_n)} \\
-& \overset{d}{\longrightarrow} \Ncal\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
-\end{align*} 
-\end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:LAN1}. 
-\end{proof}
-
-Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}. 
-%
-Among these conditions, (iii) is arguably the strongest and hardest to verify.
-As we show in Section~\ref{subsec:threshold} below, this condition is satisfied, for example, when $A_1, \ldots,A_n$ are half lines whose starting points are drawn independently from some probability measure on $\mathbb R$.
-Similar ideas imply that condition (iii) holds whenever we choose the intervals consisting each $A_i$ according to some pre-specified distribution.
-\par
-%
-An important conclusion of  Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models \cite{van2000asymptotic}):
-\begin{cor} \label{cor:LA_minimax}
-Let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
-Then for any symmetric and quasi-convex function $L$,
-\begin{align*}
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right]
-\\
-& \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
-\end{align*}
-where $Z \sim \Ncal(0,1)$. In particular, for $L(x) = x^2$,
-\begin{align*}
-\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( {\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
-\end{align*}
-\end{cor}
-%
-Corollary~\ref{cor:LA_minimax} says that when the messages define a LAN model, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model at $\theta$.
-This fact poses the upper bound of $\kappa(\theta)\sigma^2$ for the ARE of estimators in such models.
-\par
-
-Next, we show that under LAN no estimator can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly for all $\theta \in \Theta$.
-
-\subsection{Non-existence of a Uniformly Optimal Strategy}
-We now show that under LAN models, the optimal minimal risk $1/\eta(0)$ can only be attained at a finite number of points within $\Theta$.
-This fact implies in particular that, unlike in the adaptive setting, no distributed estimation scheme has ARE of $\eta(0)\sigma^2$ for all $\theta \in \Theta$.
-
-\begin{thm} \label{thm:non_existence}
-Under conditions (i)-(iii) in Theorem~\ref{thm:LAN1}, assume that each $A_i$ is a union of at most $K$ intervals.
-The number of points $\theta \in \Theta$ satisfying $\kappa(\theta) = \eta(0)$ is at most $2K$.
-\end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:non_existence}.
-\end{proof}
-
-We next consider the case where each detection region is a half-open interval, i.e., the $i$th message is obtained by comparing $X_i$ against a single threshold.
-As we explain next, the existence of a density for the sequence of thresholds is enough to establish local asymptotic normality and leads to a closed form expression for the precision parameter and the ARE.
-
-%In the adaptive setting, it follows from Theorem~\ref{thm:sgd} that messages of this kind with appropriately chosen thresholds lead to an estimator with the optimal ARE of $\eta(0)sigma^2$.
-However, Theorem~\ref{thm:non_existence} implies that such ARE can only be attained for a negligible subset of the parameter space.
-As we shall see next, messages obtained via a comparison against a sequence of thresholds cannot attain the optimal efficiency one more than a single point of $\Theta$.
-
-\subsection{Threshold Detection \label{subsec:threshold}}
-Assume now that each $B_i$ is of the form
-\begin{equation}
-\label{eq:threshold_message}
-B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
--1 & X_i > t_i,
-\end{cases}  
-\end{equation}
-where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder.
-In other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and $\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$.
-It follows that
-\begin{equation}
-L_n(A_1,\ldots,A_n;\theta) = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
-\label{eq:Ln_threshold}
-\end{equation}
-A natural condition for the existence of the limit \eqref{eq:Ln_threshold} as $n\to \infty$ is that the empirical distribution of the threshold values converges to a probability measure.
-Specifically, for an interval $I \subset \mathbb R$ define
-\[
-\lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
-\]
-Theorem~\ref{thm:LAN1} implies:
-\begin{cor} \label{cor:LAN_thresh}
-Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$.
-Then $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a LAN family with precision parameter
-\[
-\kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
-\]
-\end{cor}
-The condition that $\lambda_n$ converges to a probability measure is satisfies, for example, whenever the $t_1,\ldots,t_n$s are drawn independently from a probability distribution $\lambda(dt)$ on $\mathbb R$.
-\par
-Due to local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by 
-${\theta}^{ML}_n$, is local asymptotic minimax in the sense that 
-\[
-\sqrt{n} \left( {\theta}^{ML}_n - \theta \right) \overset{d}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
-\]
-It follows that when the density of the threshold values converges to a probability measure, the ARE of the ML estimator is $\kappa(\theta)\sigma^2$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-We note that ${\theta}^{ML}_n$ is given by the root of
-\begin{equation}
-\label{eq:ML}
-\sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) },  
-\end{equation}
-which is the derivative of the log-likelihood function.
-This root is unique since the log-likelihood function is concave.
-Furthermore, for any $n \in \mathbb R$, we have that ${\theta}^{ML}_n  \in [t_{(1)}, t_{(n)}]$ where $t_{(i)}$ denotes the $i$th element of $\{t_1,t_2\ldots\}$.
-Therefore, if $\{t_1,t_2\ldots\}$ is bounded (for example $\{t_1,t_2\ldots\} \subset \Theta$), then
-\[
-\lim_{n\to \infty} n \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
-\] 
-so that the ML estimator attains the local asymptotic MSE of Corollary~\ref{cor:LA_minimax}. \par
-%
-Since $\eta(x)$ attains its maximum at the origin, we conclude that
-\[
-\kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
-\]
-This upper bound on $\kappa(\theta)$ implies that the ARE of any distributed estimator based on a sequence of threshold detectors does not exceed $\eta(0)\sigma^2$, a fact that agrees with the lower bound under adaptive estimation derived in Theorem~\ref{thm:adpative_lower_bound}.
-%
-This upper bound on $\kappa(\theta)$ is attained only when $\lambda$ is the mass distribution at $\theta$.
-Since $\theta$ is apriori unknown, we conclude that estimation in the distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting.
-In other words, the ability to choose the threshold values in an adaptive manner based on previous messages strictly improves relative efficiency compared to a non-adaptive threshold selection.
-\par
-
-%We conclude that when the density of the threshold values converges to a probability measure, the ARE of the ML is $\kappa(\theta)$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-
-%
-We conclude this section by considering the density of the threshold values that maximizes the ARE $\kappa(\theta)$ under the worst choice of $\theta \in \Theta$.
-
-\subsection{Minimax Threshold Density}
-The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta = [-T,T]$ is given as the solution to the following optimization problem:
-\begin{align}
-\label{eq:var_cvx_minimax}
-\begin{split}
-\mathrm{maximize} \quad &  \inf_{\theta \in [-T,T]} \int \eta(t-\theta) \lambda(dt)
-\\ 
-\mathrm{subject~to} 
-\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
-\end{split}
-\end{align}
-The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program.
-We denote by $\kappa^\star(T)$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum.
-%
-%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
-%\begin{align}
-%\label{eq:cvx_minimax}
-%\begin{split}
-%\mathrm{maximize} \quad &  K \\ 
-%\mathrm{subject~to} 
-%\quad &  K \leq \mathbf H\lambda \\
-%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
-%\end{split}
-%\end{align}
-%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
-%\begin{rem}
-%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$.
-Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points.
-Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using
-%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
-%\end{rem}
-
-Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$.
-The minimal asymptotic risk $\kappa^\star(\theta)$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $T$.
-Also illustrated in these Figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
-\begin{align}
-& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
- \\
-& = 
-\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
-= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
-\end{align}
-From Corollary~\ref{cor:LAN_thresh}, we conclude that the ARE under a uniform distribution is $\kappa_\unif \sigma^2$. \par
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-title = {$\sigma/T = 1/2$},
-ytick={0,0.1,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.6,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/T = 1/5$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.5},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.5},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.3,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma / T = 1/10$},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.2},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.2},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.15,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma / T = 1/20$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:minimax_support}
-Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in \Theta = [-T,T]$.
-%
-The continuous curve (red) represents the reciprocal of the asymptotic risk for at a fixed $\theta \in \Theta$ under the optimal density, so the minimax risk is the inverse of its minimal value.
-The dashed curve (green) is the reciprocal of the asymptotic risk for a fixed $\theta$ under a uniform distribution of threshold values over $\Theta$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
-}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmax=2.5, 
-xmode = log,
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=1, 
-xlabel= {$\sigma/T$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,0.637,1},
-yticklabels={0,$2/\pi$,1},
-ylabel = {$\ARE$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{optimal threshold density};
-
-\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{uniform threshold desnity};
-\end{axis}
-\end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \Ncal(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
-The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
-}.
-\end{center}
-\end{figure}
-
-%We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
-Next, we prove that with any set of messages obtained via a distributed strategy, there exists at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-title = {$\sigma/\sigma_{\theta} = 1$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 2$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma/\sigma_{\theta} = 3$},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 4$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:opt_density}
-Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=b^2/3$ is the variance of the prior.
-}
-\end{center}
-\end{figure}
-
- We consider now the problem of minimizing the asymptotic Bayes risk $
-R_{\pi,\lambda} \triangleq \mathbb E  K^{-1}(\theta)$ over all probability measures $\lambda(dt)$ with support in $\mathbb R$. This optimization problem can be written as follows:
-\begin{align}
-\label{eq:cvx_average}
-\begin{split}
-\mathrm{minimize} \quad & R_{\pi,\lambda} =  \int \frac{\pi(d\theta)}{ \int \eta \left( t-\theta\right) \lambda(dt)}. \\ 
-\mathrm{subject~to} \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) =1. 
-\end{split}
-\end{align}
-We denote by $R^\star_{\pi}$ the minimal value of the objective function in \eqref{eq:cvx_average}.
-Since the function $x \rightarrow 1/x$ is convex for positive values, \eqref{eq:cvx_average} defines a convex optimization problem in $\lambda$ whose solution depends on the prior $\pi$.
-The solution to this problem is approximated by considering $\lambda$ and $\pi$ over a discrete set.
-On Figure~\ref{fig:opt_density} we illustrate the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distributon ($P_X = \Ncal(\theta, \sigma^2)$) and the prior on $\theta$ is uniform over $\Theta = [-b,b]$.
-Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
-\par
-\begin{figure}
-\begin{center}
-
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = 0, xmax=2, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 10,
-samples=1, 
-xlabel= {$\sigma/\sigma_\theta$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,1.5708,5},
-yticklabels={0,$\pi/2$,5},
-ylabel = {$R_{\pi}^\star/\sigma^2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-\addplot[color = black, dashed] {3.14159 / 2};
-\end{axis}
-\end{tikzpicture}
-\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \Ncal(\theta, \sigma^2)$ under an optimal threshold distribution $\lambda^\star$, when the prior $\pi$ is the uniform distribution over $\Theta = [-0.5,0.5]$.
-%
-%versus $\sigma/\sigma_\theta = 2\sqrt{3}\sigma$.
-The distribution $\lambda^\star$ is the minimizer of \eqref{eq:cvx_average}.
-It is illustrated for various cases in Fig.~\ref{fig:opt_density}.
-The dashed curve represents the upper bound \eqref{eq:upper_bound}.
-\label{fig:dist_bound_uniform}  }
-\end{center}
-\end{figure}
-
-As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \Ncal(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution.
-In this case, the ML estimator reduces to the estimator ${\theta}_n$ of \eqref{eq:estimator_naive}.
-As the following proposition shows, the Bayes risk for this choice of $\lambda$ is maximal, and thus provides an upper bound on the Bayes risk under any $\lambda$.
- \eqref{eq:cvx_average}. 
-\begin{prop}\label{prop:upper_bound}
-For any prior $\pi(d\theta)$ and $\theta_0$ in the support of $\eta(x)$ we have
-\begin{equation} 
-\label{eq:upper_bound}
-R_\pi^\star  \leq 
- \int \frac{\pi(d\theta)}{\eta \left( \theta_0 - \theta \right)},
-\end{equation}
-Furthermore, assuming that $\theta_0 = \mathbb E \theta$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
-\begin{equation}
-\label{eq:bound_Taylor}
-R^\star_\pi \leq \frac{1}{4 f^2(0)} + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right) \sigma_\theta^2 + O(\sigma_\theta^3).
-\end{equation}
-\end{prop}
-\begin{proof}
-The function $x \rightarrow 1/x$ is convex for positive values, hence Jensen's inequality implies
-\[
-\left( \int \eta \left( t-\theta\right) \lambda(dt) \right)^{-1}  \leq \int  \frac{ \lambda(dt)}{ \eta \left( t-\theta\right)  }. 
-\]
-Therefore, the expected value of $\kappa^{-1}(\theta)$ satisfies
-\begin{align}
-\ex{  \frac{1}{\kappa(\theta)}}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
-\end{align}
-The bound \eqref{eq:upper_bound} is obtained by taking $\lambda$ to be a mass distribution at any $\theta_0$ in the support of $\eta(x)$.
-Finally, \eqref{eq:bound_Taylor} is obtained by expanding $1/\eta(x)$ to a third order Taylor series around zero
-%\[
-%1/\eta(x) = \frac{1}{4f^2(0)}  + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right)  x^2 + O(x^3),
-%\]
-and taking its expectation with respect to $\pi$ at $x=\theta_0-\theta$. 
-\end{proof}
-We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so the choice $\theta_0 = \ex{ \theta}$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
-The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$.
-The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $\kappa^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.
-
-\begin{example} \label{ex:bound}
-In the normal case $P_X = \Ncal(\theta, \sigma^2)$, the bound in \eqref{eq:bound_Taylor} implies 
-\[
-\frac{R^\star_\pi}{\sigma^2}  \leq \frac{\pi}{2} + \left( \frac{\pi}{2} -1 \right) \left( \frac{ \sigma_\theta}{\sigma} \right)^2 + O \left(  \frac{\sigma_\theta} { \sigma} \right)^3. 
-\]
-It follows that the ARE approaches its maximal value of $2/\pi$ whenever $\sigma_\theta/\sigma$ is small.
-The exact value of \eqref{eq:upper_bound} in this case, as well as the Bayes ARE with the optimal threshold density $\lambda^\star$ for a uniform $\pi$, are illustrated in Fig.~\ref{fig:dist_bound_uniform}.
-%i.e., each encoder simply reports "$1$" or "$-1$" whenever $X_i$ is larger or smaller than $\theta_0$, respectively.
-Intuitively, an accurate estimation of $\theta$ in this case is possible only if a sufficient mix of ''$1$''s and ''$-1$''s is obtained from the sample.
-When $\sigma_\theta^2$ is high compared to $\simga^2$, one of the events $"1"$ or "$-1"$ becomes too rare to
-\end{example}
-
-\section{Conclusions \label{sec:conclusions}}
-We considered the MSE risk in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
-%
-In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency (ARE) larger than that of the median of the samples.
-We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median.
-%We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
-\par
-In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and ARE. 
-%
-We conclude that under such conditions, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in the distributed setting.
-%
-We further considered the special case of messages obtained by comparing against a prescribed sequence of thresholds.
-We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.
-
-%\section*{ACKNOWLEDGMENT}
-%This research is supported in parts by...
-%Tsachy Weissman, Stefano Rini, Robert Gray.
-
-\onecolumn
-
-\appendix
+% -*- Mode: latex -*- %
 
@@
 However, $S_n(\theta_1,\epsilon), \ldots S_n(\theta_N,\epsilon)$ are disjoint, so the cardinallity of their union is at least $n\left(1-\frac{1}{2N} \right)N$ which is grater than $2nK + n/2$ in contradiction to \eqref{eq:few_optimality_points_proof}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEfull,onebit}
-
-\end{document}

### 2019-09-23 conclusions.tex
Adding a bib file

--- 2019-09-19 onebit_full.tex
@@
-%% \documentclass[11pt]{article}
-\documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper
-
-%LatexiDiff ignore tikz:
-% $: latexdiff -c "PICTUREENV=(?:picture|tikzpicture|DIFnomarkup)[\w\d*@]*" old.tex new.tex > diff.tex
-
-%\IEEEoverridecommandlockouts                              %
-
-%\usepackage{mathcomSTEP}
-
-%\overrideIEEEmargins 
-%\IEEEoverridecommandlockouts                              % This command is only needed if 
-% you want to use the \thanks command
-
-%\overrideIEEEmargins                                      % Needed to meet printer requirements.
-
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-\onecolumn
-
-\usepackage{mathptmx} 
-\usepackage{times} 
-\usepackage{amsmath} 
-\usepackage{amsbsy} 
-\usepackage{amssymb}
-
-%\usepackage{newtxtext, newtxmath}
-\usepackage{mathrsfs}
-\usepackage{comment}
-\usepackage[export]{adjustbox}
-\usepackage{tikz}
-\usetikzlibrary{external,positioning,decorations.pathreplacing,shapes,arrows,patterns}
-
-\usepackage[hidelinks]{hyperref}
-%\tikzexternalize[mode=list and make]
-\usepackage{algorithmicx}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage{pstool}
-\usepackage[latin1]{inputenc}
-\usetikzlibrary{arrows,shapes}
-\usepackage{xifthen}
-\usepackage{epic}
-%\usepackage{caption}
-\usepackage{epstopdf}
-
-\newtheorem{thm}{\bf{Theorem}}
-\newtheorem{cor}[thm]{\bf {Corollary}}
-\newtheorem{lem}[thm]{\bf {Lemma}}
-\newtheorem{prop}[thm]{\bf {Proposition}}
-\newtheorem{example}{\bf {Example}}
-\newtheorem{definition}{\bf {Definition}}
-\newtheorem{rem}{\bf {Remark}}
-\newtheorem{assump}{\bf {Assumptions}}
-
-\newcommand{\ex}[1]{\ensuremath{\mathbb{E}\left[ #1\right]}}
-
-\newcommand{\Var}[1]{\ensuremath{\mathrm{Var} \left[ #1\right]}}
-
-\newcommand{\unif}{\mathsf{unif}}
-\newcommand{\card}{\mathrm{card}}
-\newcommand{\ARE}{\mathsf{ARE}}
-\newcommand{\supp}{\mathrm{supp} }
-\renewcommand\vec[1]{\ensuremath\boldsymbol{#1}}
-\newenvironment{proof}{\paragraph*{Proof}}{\hfill$\square$ \newline}
-\newcommand{\sgn}{\mathrm{sgn} }
-\newcommand{\Prob}{\mathbb{P} }
-\newcommand{\argmax}{\mathrm{argmax}}
-\newcommand*{\QEDA}{\hfill\ensuremath{\square}}
-\newcommand{\CEO}{\mathsf{CEO}}
-\newcommand{\Ncal}{\mathcal{N}}
-
-\newcommand{\enc}{\mathsf{enc}}
-\newcommand{\est}{\mathsf{est}}
-
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-\tikzstyle{sint}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.8cm,thick ]
-\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
-\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
-\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.7cm,thick ]
-\tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-
-\author{
-    \IEEEauthorblockN{
-Alon Kipnis\IEEEauthorrefmark{1} and   
-    John C. Duchi\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}  \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}Stanford University, Department of Statistics \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Stanford University, Department of Electrical Engineering. }
-}
-
-\title{\LARGE \bf Mean Estimation from One-Bit Measurements}
-
-\begin{document}
-\graphicspath{{./Figs/}}
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{abstract}
-
-%{\color{red}  See LASSO results in http://arxiv.org/abs/1506.02181v1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\input{introduction}
-
-\section{Problem Formulation \label{sec:problem}}
-
-Let $f(x)$ be a symmetric and log-concave density function with a finite second moment $\sigma^2$.
-For $\theta \in \Theta$, denote by $P_X$ the probability distribution with density $f\left( x-\theta \right)$.
-Therefore, $P_X$ is an absolutely continuous log-concave distribution with mean $\theta$ and variance $\sigma^2$.
-Symmetry and log-concavity of $f(x)$ imply that $P_X$ is strongly unimodal (has a unique local maxima) with its mode at $x =\theta$ \cite{ibragimov1956composition}.
-We further assume that the \emph{parameter space} $\Theta$ is a closed interval of the real line.
-\par
-In some situations it is useful to assume that $\theta$ is drawn once from the prior distribution $\pi$ on $\Theta$.
-In this case we assume that $\pi$ is an absolutely continuous distribution, and denote its density by $\pi(\theta)$, i.e., $\pi(d\theta) = \pi(\theta)d\theta$.
-\par
-The random variables $X_1,\ldots,X_n$ represent $n$ independent samples from $P_X$. 
-We are interested in estimating $\theta$ from a set of $n$ binary messages $B_1,\ldots,B_n$, obtained from $X_1,\ldots,X_n$ under three possible scenarios illustrated in Figure~\ref{fig:setup}: 
-\begin{itemize}
-\item[(i)~~] Centralized $B_i(X_1,\ldots,X_n)$, $i=1,\ldots,n$.
-\item[(ii)~] Adaptive $B_i(X_i,B_1,\ldots,B_{i-1})$, $i=2,\ldots,n$.
-\item[(iii)] Distributed $B_i(X_i)$, $i=1,\ldots,n$.
-\end{itemize}
-
-The performance of an estimator ${\theta}_n \triangleq {\theta}_n(B^n)$ in any of these cases is measured according to the quadratic risk:
-\begin{equation}
-\label{eq:error_def}
-R_n \triangleq \mathbb E\left({\theta}_n - \theta \right)^2,
-\end{equation}
-where the expectation is taken with respect to the distribution of $X_1,\ldots,X_n$ and, whenever available, a prior distribution $\pi(\theta)$ over $\Theta$.  
-%It is well known that minmax estimation error 
-%\begin{equation}
-%R_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left({\theta}_n - \theta \right)^2 | \theta \right],
-%\end{equation}
-%can be obtained from $R_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}. 
-%
-The main problems we consider in this paper are the minimal value of \eqref{eq:error_def}, as a function of $n$ and $f(x)$, under different choices of the encoding functions in cases (i), (ii), and (iii).
-\par
-
-We give particular attention to the ARE of estimators with respect to an asymptotically normal efficient estimator that is not subject to the bit constraint.
-Specifically, let $\{a_n,\,n\in \mathbb N\}$ be a sequence such that
-\[
-\sqrt{a_n}\left({\theta}_n - \theta\right) \overset{d}{\longrightarrow} \Ncal(0, \sigma^2).
-\]
-Then the ARE of ${\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
-\[
-\ARE({\theta}_n) \triangleq
-\lim_{n\rightarrow \infty} \frac{a_n}{n}. 
-\]
-Note that in the special case where there exists $V \in \mathbb R$ such that
-\[
-a_n \mathbb E \left({\theta}_n - \theta \right)^2 = V + o(1),
-\]
-with $o(1)\to 0$ as $n\to \infty$, then the ARE of ${\theta}_n$ is finite and equals $\sigma^2/V$. \par
-
-In addition to the notation above, we also denote by $F(x)$ the cumulative distribution function of $X_i$, and define
-\begin{equation} \label{eq:eta_def}
-\eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))} =  \frac{f(x)f(-x)}{F(x)F(-x)}, 
-\end{equation}
-where the last equality is due to symmetry of $f(x)$. We note that 
-\begin{equation}
-\label{eq:eta_h}
-\eta(x) = h(x)h(-x) = f(x) \left( h(x) + h(-x) \right), 
-\end{equation}
-where 
-\[
-h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
-\]
-is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function since $f(x)$ is log-concave \cite{bagnoli2005log}. 
-%
-For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as illustrated in Fig.~\ref{fig:eta}. 
-%
-In this paper we only consider the normal distribution and other log-concave symmetric distributions for which this property of $\eta(x)$ holds. Specifically, we require the following:
-\begin{assump} \label{assump:failure_rate}
- $\eta(x)$ has a unique maximum (at the origin) and is a non-increasing function of $|x|$. 
-\end{assump}
-%That is, Assumption~\ref{assump:failure_rate} says that $\eta'(x) < 0 $ for all $x>0$. 
-Under this assumption we have, 
-\[
-4f^2(x) \leq \eta(x) \leq \eta(0),
-\] 
-%
-where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median.
-Combined with log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that $\eta(x)$ vanishes as $|x|\rightarrow \infty$.
-\par
-%
-Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions).
-Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.\par
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -3, xmax=3, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.9,
-samples=10, 
-xlabel= $x$,
-xtick={-2,-1,0,1,2},
-xticklabels={-2,-1,0,1,2},
-ytick={0,0.3989423,0.6366198},
-yticklabels={0,$\frac{1}{\sqrt{2 \pi}}$,$2/\pi$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\eta(x)$};
-\addplot[domain = -5:5, samples = 50, color = red, solid, smooth]  {exp(-x^2/2) / sqrt(2*3.14159)};
-\addlegendentry{$\phi(x)$};
-\addplot[domain = -5:5, samples = 50, color = black, solid, dashed]  {4*exp(-x^2) / (2*3.14159)};
-\addlegendentry{$4\phi^2(x)$};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -4, xmax=4, 
-restrict y to domain = -10:0,
-ymin = -10,
-samples=10, 
-xlabel= $x$,
-xtick={-3,-2,-1,0,1,2,3},
-xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,-0.45158,-0.919},
-yticklabels={0,,},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\log \eta(x)$};
-\addplot[domain = -5:5, samples = 30, color = red, solid, smooth]  {-(x)^2/2 -0.9189};
-\addlegendentry{$\log \phi(x)$};
-\end{axis}
-\end{tikzpicture}
-\caption{
-The function $\eta(x) = f^2(x) / F(x)F(-x)$ for $f(x) = \phi(x)$ the standard normal density.
-\label{fig:eta}
-}
-\end{center}
-\end{figure}
-
-\section{Consistent Estimation and Off-the-shelf Bounds \label{sec:preliminary}}
-%
-In this section we adapt known results to derive lower and upper bounds on the relative efficiency under setting (iii). These bounds establish the following facts:
-\begin{itemize}
-\item[I.] A consistent estimator with an asymptotically normal distribution always exists in setting (iii), and hence in setting (ii). 
-\item[II.] For the normal distribution, the ARE in setting (iii) is at most $3/4$. Namely, under setting (iii), all estimators are strictly inferior compared to the sample mean. 
-\end{itemize}
-
-\subsection{Consistent Estimation}
-Fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
-\[
-B_i = \mathbf 1_{X_i>\theta_0}, 
-\]
-where $\mathbf 1_A$ is the indicator of the event $A$. We have
-\[
-P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
-\]
-so that 
-\begin{equation}
-\label{eq:estimator_naive}
-{\theta}_n = \theta_0 + F^{-1}\left( P_n \right)
-\end{equation}
-is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set due to log-concavity.
-Furthermore, the variance of $P_n$ is $F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)$, and hence the delta method implies that ${\theta}_n$ is asymptotically normal with variance
-\begin{equation} 
- \frac{F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}{f^2(\theta-\theta_0)} = \frac{1}{
-\eta(\theta-\theta_0)}.
-\end{equation}
-In particular, the ARE of ${\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
-In other words, for a prescribed accuracy, ${\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
-\par
-%
-%
-Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of ${\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
-This ARE is attained only when $\theta_0 = \theta$, whereas $\theta$ is apriori unknown.
-Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of ${\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
-As an example, when $f(x)$ is a normal density, the ARE of ${\theta}_n$ is less than $\approx 0.14$ when $\theta_0$ is $2$ standard deviations from $\theta$.
-Therefore, the estimator ${\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
-\par
-It is suggested that we can attain lower variance in estimation by updating the threshold value $\theta_0$ in \eqref{eq:estimator_naive} after observing one or a batch of the single bit messages.
-Schemes with such adaptation fall within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
-\par
-
-\subsection{Multiterminal Source Coding \label{sec:ceo}}
-The CEO setting considers the estimation of a sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_i$ is available at $n$ terminals.
-At each terminal $i$, an encoder observes the $k$ noisy samples
-\[
-X_{i,j} = \theta_j + Z_{i,j},\qquad j=1,\ldots,k, \qquad i = 1,\ldots,n,
-\]
-and transmits $r_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates ${\theta}_1,\ldots,{\theta}_k$ with the goal of minimizing the quadratic risk:
-\[
-R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - {\theta}_j \right)^2 \right]. 
-\]
-Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $r_1=\ldots=r_n = 1$.
-It follows that, assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
-%
-Consequently, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the minimal MSE in the CEO setting as $k \to \infty$.
-Note that the difference between the CEO setting and ours lays in the privilege of each of the encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realizations, rather than a single realization using a single bit in ours.
- \par
-When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k$ goes to infinity were fully characterized in \cite{prabhakaran2004rate}.
-Furthermore, the work of \cite{chen2004upper} provided an expression for quadratic risk attained in the CEO setting under Gaussian priors.
-Adapting to our setting, this expression provides the following proposition:
-\begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is arbitrary.
-Then any estimator ${\theta}_n$ of $\theta$ in the distributed setting satisfies
-\begin{equation} \label{eq:ceo_bound}
- n \ex{\left( \theta - \theta_n \right)^2} \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
-\end{equation}
-where the expectation is with respect to $\theta$ and $X^n$.
-\end{prop}
-
-\begin{proof}
-See Appendix~\ref{app:proof:prop_ceo_lower_bound}.
-\end{proof}
-
-From the formulation of the CEO problem, it follows that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is attributed to the ability to perform coding over blocks.
-Namely, each encoder in the CEO setting may encode an arbitrary number of $k$ independent realizations of $\theta$ using $k$ bits, versus only one realization with one bit in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product probability space that distinguishes between the CEO problem with one bit per encoder on average and the mean estimation problem from one-bit measurements in the distributed setting.
-
-\section{Adaptive Estimation \label{sec:sequential}}
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $\eta(0)\sigma^2$, which is the ARE of the median of the sample $X_1,\ldots,X_n$.
-We also provide a particular adaptive estimation scheme that attains this maximal efficiency.
-%Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $B_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages.
-%Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $\eta(0)\sigma^2$.
-
-\subsection{Limited efficiency in the adaptive setting}
-Our first result asserts that the ARE of any adaptive encoding and estimation scheme is bounded from above by $\eta(0)\sigma^2$. %This result follows from the following theorem:
-\begin{thm}[maximal relative effeciency] \label{thm:adpative_lower_bound}
-Let ${\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Figure~\ref{fig:setup}-(ii). Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-n\mathbb E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0},
-\]
-where 
-\[
-I_0 = \mathbb E \left( \frac{d}{d\theta} \log \pi (\theta) \right)^2
-\]
-is the Fisher information with respect to a location model in $\theta$. 
-\end{thm}
-
-\subsubsection*{Proof}
-%We first bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
-The result then follows using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are in
-See Appendix~\ref{proof:thm:adpative_lower_bound}.\par
-
-Theorem~\ref{thm:adpative_lower_bound} implies that any estimator ${\theta}_n$ from any adaptive encoding scheme satisfies
-\[
-n\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{1}{4f^2(0)}+O(n^{-1}),
-\]
-and 
-\[
-\ARE({\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
-\]
-It is possible to extend Theorem~\ref{thm:adpative_lower_bound} to any other loss functions using a more subtle version of the Van Tress inequality provided in \cite{efroimovich1980information}.
-See also \cite{DBLP:journals/corr/abs-1902-08582}.
-\par
-%
-Next, we provide an adaptive encoding and estimation scheme that attains the maximal ARE of $\eta(0)\sigma^2$.
-
-\subsection{Asymptotically optimal estimator}
-Let $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ be a strictly positive sequence. Consider the following estimator ${\theta}_n$ for $\theta$:  
-\begin{equation}
-\label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n B_n, \quad n = 1,2,\ldots,
-\end{equation}
-where 
-\begin{equation}
-B_n = B_n (X_n,\theta_{n-1}) =\sgn (X_n - \theta_{n-1}).
-\end{equation}
-Define the $n$th step estimation as
-\begin{equation} \label{eq:sgd_est}
-\bar{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
-\end{equation}
-
-We have the following results:
-\begin{thm} \label{thm:sgd}
-Consider the sequence $\left\{\bar{\theta}_n \right\}_{n\in \mathbb N}$ defined by \eqref{eq:sgd_est}. 
-\begin{enumerate}
-\item[(i)] Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions1}
-\begin{cases}
-\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
-\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
-\mathrm{for~some~}0< \lambda \leq 1
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Then
-\[
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left(0,\frac{1}{\eta(0)}\right).
-\]
-%
-%
-\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with a finite location Fisher information, namely
-\[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)}  \right)^2 f(x) dx < \infty.
-\]
-%(or that $f(x-\theta)$ is differentiable in quadratic mean).  
-Then for any bounded, symmetric, and quasi-convex function $L$, 
-\begin{align} 
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
-\\
-& \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
-\end{align}
-where $Z \sim \Ncal(0,1)$. 
-%
-%
-\item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions2}
-\begin{cases}
-\gamma_n = o(n^{-2/3}), &  \\
-\sum_{n=1}^\infty \gamma_n = \infty.  & \\
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ with $\beta \in (2/3,1)$). Then
-\[
- \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{n\eta(0)} + o(n^{-1}). 
-\]
-\end{enumerate}
-\end{thm}
-
-\subsubsection*{Proof}
-See Appendix~\ref{proof:thm:sgd}. \par
-
-Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the maximal ARE, as established by Theorem~\ref{thm:adpative_lower_bound}.
-%Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$.
-%
-The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$.
-Consequently, the procedure above is known as averaged stochastic gradient descent for minimizing $x \to |x|$ given the data $X_1,\ldots,X_n$.
-The minimal value of this optimization is the sample median, and Theorem~\ref{thm:sgd} provides conditions for the sequence of gradient steps so that the algorithm converges to this minimum.
-In particular, parts (i) and (ii) of Theorem~\ref{thm:sgd} provides conditions under which $\bar{\theta}$ is asymptotically normal and local asymptotically minimax, in the sense that it attains the local asymptotic minimax bound \cite{van2000asymptotic}.
-Part (iii) provides an additional condition under which $\bar{\theta}$ also converges in its second moment.
- \par
-%Note that $\theta_0$ is not explicitly defined in equation \eqref{eq:sgd_est}.
-A reasonable initialization for $\theta_0$ is $\theta_0 = \mathbb E [\theta]$, although Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
-Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$.
-\\
-In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $B_n$ depends on its private sample as well as the current gradient descent estimate $\theta_{n-1}$.
-In this sense, each encoder in this algorithm interacts with previous one by using the current estimate.
-%
-As we explain next, 
-it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ with only one round of interactions among the encoders.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
-% \node[below of = source, node distance = 1cm] (source2) {$X_2$};
-%\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};  
-%\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};
-
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[below of = source, node distance = 0.5cm] {$\vdots$};
-
-\node[int1, right of = enc3, node distance = 2.1cm ] (est) {$\est_1$};
-
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
-
-%\draw[->,line width = 2pt] (enc2) -| node[above, xshift = -1cm] (mes2) {$B_2$} (est);
-
-\draw[->,line width = 2pt] (enc3) -- node[above, xshift = 0cm]  {$B_{n_1}$} (est);
-
-\node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
-\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {$\enc$};  
-\draw[->,line width = 2pt] (sourceB) -- (enc1B);
-
-\node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
-\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {$\enc$};  
-\draw[->,line width = 2pt] (source3B) -- (enc3B); 
-\node[below of = sourceB, node distance = 0.4cm] {$\vdots$};
-
-\node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {$\est_2$};
-
-\draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.5cm] {$B_{n_1+1}$} (estB);
-\draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);
-
-\draw[->,line width = 1pt] (est.east) node[above, xshift  =0.5cm] {${\theta}_{n_1}$} -| (enc1B.north);
-
-%\draw[->,line width = 1pt] (enc1B) -- (enc3B);
-
-\draw[->,line width = 0.5pt] (est.east) -| +(1.3,-0.5) -- +(1.3,-2.5) -| (enc3B.north);
-
-%\draw[->,line width = 1pt] (enc1B)  -- node[right] {${\theta}_{n_1}$} (enc3B);
-
-\draw[->,line width = 0.5pt] (estB) -- +(0.8,0) node[right] {${\theta}_n$};
-\node[below of = enc1B, node distance = 0.5cm] {$\vdots$};
-
-\end{tikzpicture}
-\end{center}
-\caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
-\label{fig:one_round}
-}
-\end{figure}
-
-\subsection{Maximal Efficiency using One Round of Threshold Adaptation}
-In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
-\[
-B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
-\]
-and deduced that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
-%
-We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ based on previously observed bits at least once.
-%
-In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
-We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate ${\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use ${\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$.
-Figure~\ref{fig:one_round} illustrates a diagram of this procedure.
-%
-The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
-\begin{thm}
-For $i=1,\ldots,n$ set
-\[
-B_i = \begin{cases}
- \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
- \mathbf 1_{X_i \geq {\theta}_{n_1} }& i={n_1+1,\ldots,n},
-\end{cases}
-\]
-where $n = n_1+ n_2$ and 
-\[
-{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
-\frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
- \right).
-\] 
-Let 
-\[
-{\theta}_{n_2}  = {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
-\]
-and assume that $n_1(n) \rightarrow \infty$ and $n_1(n)/n \rightarrow 0$. Then:
-\begin{align*}
- \sqrt{n} \left( {\theta}_{n_2} - \theta  \right) \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
-\end{align*}
-\end{thm}
-%
-%
-\begin{proof}
-For $t\in \mathbb R$, set
-\[
-p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
-\]
-From the central limit theorem
-\begin{align*}
-& \sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)  = \sqrt{\frac{n}{n_2}} \sqrt{n_2} \left(  p_{n_2}(t) - F(\theta - t) \right) \\
-& \overset{d}{\rightarrow} \Ncal\left( 0, V(t) \right),
-\end{align*}
-where
-\[
-V(t) \triangleq F(\theta - t) F \left( t - \theta\right). 
-\]
-Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ implies
-\begin{align*}
-& \sqrt{n} \left( t + F^{-1}(\hat{p}_{n_2}(t)) - \theta \right) \\
-&= \sqrt{n} \left( g(\hat{p}_{n_2}(t)) - g \left(F(\theta-t) \right)  \right) \\
-& \overset{d}{\to} \Ncal\left(0, 
-1/\eta(\theta-t) \right).
-\end{align*}
-%where this convergence is uniform in $t$ since all moments of $F^{-1}(\hat{p}_{n_2})$ exists. 
-On the other hand, by the law of large numbers,
-\[
-p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
-\]
-so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity and thus 
-\[
-\eta( {\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
-\]
-Finally,
-\begin{align*}
-& \sqrt{n}\left({\theta}_{n_2} - \theta\right) \\
-& = \sqrt{n} \left( {\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}({\theta}_{n_1})) - \theta \right)  \\
-& \overset{d}{\to} \Ncal\left( 0, 
-1/\eta(0) \right) 
-\end{align*}
-by Slutsky's theorem.
-\end{proof}
-%
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=10cm, height=6cm,
-xmin = 0, xmax=800, 
-restrict y to domain = 0:3,
-ymin = 0,
-ymax = 3.4,
-samples=10, 
-xlabel= $n$,
-ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
-%xtick={-3,-2,-1,0,1,2,3},
-%xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,1,1.57},
-yticklabels={0,1,$\pi/2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-
-\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{asymptotically optimal};
-
-%\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
-
-\addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{single interaction};
-
-\end{axis}
-\end{tikzpicture}
-%\begin{tikzpicture}
-%\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
-%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left({\theta}_n - \theta \right)^2$};
-%\node[scale = 0.7] at (0,-2.4) {$n$};
-%\end{tikzpicture}
-\caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.
-In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$.
-The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage.
-\label{fig:adaptive_error}  }
-\end{center}
-\end{figure}
-
-\section{Distributed Estimation \label{sec:distributed}}
-In this section, we now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii) where  each one-bit message $B_i$ is only a function of its private sample $X_i$.
-In this case, the $i$th encoder is fully characterized its \emph{detection region}, defined as
-\[
-A_i = \left\{ x \in \mathbb R \,:\, B_i(x) = 1 \right\}.
-\]
-Consequently, $B_i$ is of the form
-\[
-B_i = \begin{cases} 1 & X_i \in A_i, \\
--1 & X_i \notin A_i,
-\end{cases} \quad i\in \mathbb N,
-\]
-where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\par
-
-As a first step, we provide conditions under which the messages $B_1,B_2,\ldots$ define a local asymptotic normal family.
-
-\begin{thm} \label{thm:LAN1}
-For $n \in \mathbb N$ and $A_n \subset \mathbb R$,  define
-\begin{equation}
-\label{eq:precision_general}
-L_n(A_1,\ldots,A_n;\theta) \triangleq \frac{1}{n} \sum_{i=1}^n \frac{ \left(\frac{d}{d \theta} \Prob(X_i \in A_i) \right)^2 }{ \Prob(X_i \in A_i)\left(1- \Prob(X_i \in A_i) \right) }. 
-\end{equation}
-Consider the following conditions:
-\begin{itemize}
-\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is a log-concave, differentiable and symmetric density function such that $\eta(x)$ is unimodal.
-\item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
-\item[(iii)] The limit 
-\begin{equation}
-\label{eq:LAN_lim}
-\kappa(\theta) \triangleq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
-\end{equation}
-exists. 
-\end{itemize}
-For $i=1,\ldots,n$ set
-\[
-B_n = \begin{cases} 1 & X_n \in A_n, \\
--1 & X_n \notin A_n. 
-\end{cases} 
-\]
-For any $\theta$, $f(x)$ and a sequence of sets $A_1,A_2,\ldots$ such that (i)-(iii) hold, and any $h\in \mathbb R$, we have
-\begin{align*}
-& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (B_1,\ldots,B_n) }{
-\mathbb P_{\theta} (B_1,\ldots,B_n)} \\
-& \overset{d}{\longrightarrow} \Ncal\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
-\end{align*} 
-\end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:LAN1}. 
-\end{proof}
-
-Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}. 
-%
-Among these conditions, (iii) is arguably the strongest and hardest to verify.
-As we show in Section~\ref{subsec:threshold} below, this condition is satisfied, for example, when $A_1, \ldots,A_n$ are half lines whose starting points are drawn independently from some probability measure on $\mathbb R$.
-Similar ideas imply that condition (iii) holds whenever we choose the intervals consisting each $A_i$ according to some pre-specified distribution.
-\par
-%
-An important conclusion of  Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models \cite{van2000asymptotic}):
-\begin{cor} \label{cor:LA_minimax}
-Let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
-Then for any symmetric and quasi-convex function $L$,
-\begin{align*}
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right]
-\\
-& \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
-\end{align*}
-where $Z \sim \Ncal(0,1)$. In particular, for $L(x) = x^2$,
-\begin{align*}
-\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( {\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
-\end{align*}
-\end{cor}
-%
-Corollary~\ref{cor:LA_minimax} says that when the messages define a LAN model, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model at $\theta$.
-This fact poses the upper bound of $\kappa(\theta)\sigma^2$ for the ARE of estimators in such models.
-\par
-
-Next, we show that under LAN no estimator can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly for all $\theta \in \Theta$.
-
-\subsection{Non-existence of a Uniformly Optimal Strategy}
-We now show that under LAN models, the optimal minimal risk $1/\eta(0)$ can only be attained at a finite number of points within $\Theta$.
-This fact implies in particular that, unlike in the adaptive setting, no distributed estimation scheme has ARE of $\eta(0)\sigma^2$ for all $\theta \in \Theta$.
-
-\begin{thm} \label{thm:non_existence}
-Under conditions (i)-(iii) in Theorem~\ref{thm:LAN1}, assume that each $A_i$ is a union of at most $K$ intervals.
-The number of points $\theta \in \Theta$ satisfying $\kappa(\theta) = \eta(0)$ is at most $2K$.
-\end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:non_existence}.
-\end{proof}
-
-We next consider the case where each detection region is a half-open interval, i.e., the $i$th message is obtained by comparing $X_i$ against a single threshold.
-As we explain next, the existence of a density for the sequence of thresholds is enough to establish local asymptotic normality and leads to a closed form expression for the precision parameter and the ARE.
-
-%In the adaptive setting, it follows from Theorem~\ref{thm:sgd} that messages of this kind with appropriately chosen thresholds lead to an estimator with the optimal ARE of $\eta(0)sigma^2$.
-However, Theorem~\ref{thm:non_existence} implies that such ARE can only be attained for a negligible subset of the parameter space.
-As we shall see next, messages obtained via a comparison against a sequence of thresholds cannot attain the optimal efficiency one more than a single point of $\Theta$.
-
-\subsection{Threshold Detection \label{subsec:threshold}}
-Assume now that each $B_i$ is of the form
-\begin{equation}
-\label{eq:threshold_message}
-B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
--1 & X_i > t_i,
-\end{cases}  
-\end{equation}
-where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder.
-In other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and $\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$.
-It follows that
-\begin{equation}
-L_n(A_1,\ldots,A_n;\theta) = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
-\label{eq:Ln_threshold}
-\end{equation}
-A natural condition for the existence of the limit \eqref{eq:Ln_threshold} as $n\to \infty$ is that the empirical distribution of the threshold values converges to a probability measure.
-Specifically, for an interval $I \subset \mathbb R$ define
-\[
-\lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
-\]
-Theorem~\ref{thm:LAN1} implies:
-\begin{cor} \label{cor:LAN_thresh}
-Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$.
-Then $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a LAN family with precision parameter
-\[
-\kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
-\]
-\end{cor}
-The condition that $\lambda_n$ converges to a probability measure is satisfies, for example, whenever the $t_1,\ldots,t_n$s are drawn independently from a probability distribution $\lambda(dt)$ on $\mathbb R$.
-\par
-Due to local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by 
-${\theta}^{ML}_n$, is local asymptotic minimax in the sense that 
-\[
-\sqrt{n} \left( {\theta}^{ML}_n - \theta \right) \overset{d}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
-\]
-It follows that when the density of the threshold values converges to a probability measure, the ARE of the ML estimator is $\kappa(\theta)\sigma^2$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-We note that ${\theta}^{ML}_n$ is given by the root of
-\begin{equation}
-\label{eq:ML}
-\sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) },  
-\end{equation}
-which is the derivative of the log-likelihood function.
-This root is unique since the log-likelihood function is concave.
-Furthermore, for any $n \in \mathbb R$, we have that ${\theta}^{ML}_n  \in [t_{(1)}, t_{(n)}]$ where $t_{(i)}$ denotes the $i$th element of $\{t_1,t_2\ldots\}$.
-Therefore, if $\{t_1,t_2\ldots\}$ is bounded (for example $\{t_1,t_2\ldots\} \subset \Theta$), then
-\[
-\lim_{n\to \infty} n \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
-\] 
-so that the ML estimator attains the local asymptotic MSE of Corollary~\ref{cor:LA_minimax}. \par
-%
-Since $\eta(x)$ attains its maximum at the origin, we conclude that
-\[
-\kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
-\]
-This upper bound on $\kappa(\theta)$ implies that the ARE of any distributed estimator based on a sequence of threshold detectors does not exceed $\eta(0)\sigma^2$, a fact that agrees with the lower bound under adaptive estimation derived in Theorem~\ref{thm:adpative_lower_bound}.
-%
-This upper bound on $\kappa(\theta)$ is attained only when $\lambda$ is the mass distribution at $\theta$.
-Since $\theta$ is apriori unknown, we conclude that estimation in the distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting.
-In other words, the ability to choose the threshold values in an adaptive manner based on previous messages strictly improves relative efficiency compared to a non-adaptive threshold selection.
-\par
-
-%We conclude that when the density of the threshold values converges to a probability measure, the ARE of the ML is $\kappa(\theta)$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-
-%
-We conclude this section by considering the density of the threshold values that maximizes the ARE $\kappa(\theta)$ under the worst choice of $\theta \in \Theta$.
-
-\subsection{Minimax Threshold Density}
-The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta = [-T,T]$ is given as the solution to the following optimization problem:
-\begin{align}
-\label{eq:var_cvx_minimax}
-\begin{split}
-\mathrm{maximize} \quad &  \inf_{\theta \in [-T,T]} \int \eta(t-\theta) \lambda(dt)
-\\ 
-\mathrm{subject~to} 
-\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
-\end{split}
-\end{align}
-The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program.
-We denote by $\kappa^\star(T)$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum.
-%
-%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
-%\begin{align}
-%\label{eq:cvx_minimax}
-%\begin{split}
-%\mathrm{maximize} \quad &  K \\ 
-%\mathrm{subject~to} 
-%\quad &  K \leq \mathbf H\lambda \\
-%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
-%\end{split}
-%\end{align}
-%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
-%\begin{rem}
-%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$.
-Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points.
-Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using
-%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
-%\end{rem}
-
-Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$.
-The minimal asymptotic risk $\kappa^\star(\theta)$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $T$.
-Also illustrated in these Figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
-\begin{align}
-& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
- \\
-& = 
-\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
-= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
-\end{align}
-From Corollary~\ref{cor:LAN_thresh}, we conclude that the ARE under a uniform distribution is $\kappa_\unif \sigma^2$. \par
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-title = {$\sigma/T = 1/2$},
-ytick={0,0.1,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.6,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/T = 1/5$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.5},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.5},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.3,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma / T = 1/10$},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.2},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.2},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.15,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma / T = 1/20$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:minimax_support}
-Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in \Theta = [-T,T]$.
-%
-The continuous curve (red) represents the reciprocal of the asymptotic risk for at a fixed $\theta \in \Theta$ under the optimal density, so the minimax risk is the inverse of its minimal value.
-The dashed curve (green) is the reciprocal of the asymptotic risk for a fixed $\theta$ under a uniform distribution of threshold values over $\Theta$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
-}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmax=2.5, 
-xmode = log,
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=1, 
-xlabel= {$\sigma/T$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,0.637,1},
-yticklabels={0,$2/\pi$,1},
-ylabel = {$\ARE$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{optimal threshold density};
-
-\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{uniform threshold desnity};
-\end{axis}
-\end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \Ncal(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
-The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
-}.
-\end{center}
-\end{figure}
-
-%We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
-Next, we prove that with any set of messages obtained via a distributed strategy, there exists at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-title = {$\sigma/\sigma_{\theta} = 1$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 2$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma/\sigma_{\theta} = 3$},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 4$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:opt_density}
-Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=b^2/3$ is the variance of the prior.
-}
-\end{center}
-\end{figure}
-
- We consider now the problem of minimizing the asymptotic Bayes risk $
-R_{\pi,\lambda} \triangleq \mathbb E  K^{-1}(\theta)$ over all probability measures $\lambda(dt)$ with support in $\mathbb R$. This optimization problem can be written as follows:
-\begin{align}
-\label{eq:cvx_average}
-\begin{split}
-\mathrm{minimize} \quad & R_{\pi,\lambda} =  \int \frac{\pi(d\theta)}{ \int \eta \left( t-\theta\right) \lambda(dt)}. \\ 
-\mathrm{subject~to} \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) =1. 
-\end{split}
-\end{align}
-We denote by $R^\star_{\pi}$ the minimal value of the objective function in \eqref{eq:cvx_average}.
-Since the function $x \rightarrow 1/x$ is convex for positive values, \eqref{eq:cvx_average} defines a convex optimization problem in $\lambda$ whose solution depends on the prior $\pi$.
-The solution to this problem is approximated by considering $\lambda$ and $\pi$ over a discrete set.
-On Figure~\ref{fig:opt_density} we illustrate the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distributon ($P_X = \Ncal(\theta, \sigma^2)$) and the prior on $\theta$ is uniform over $\Theta = [-b,b]$.
-Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
-\par
-\begin{figure}
-\begin{center}
-
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = 0, xmax=2, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 10,
-samples=1, 
-xlabel= {$\sigma/\sigma_\theta$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,1.5708,5},
-yticklabels={0,$\pi/2$,5},
-ylabel = {$R_{\pi}^\star/\sigma^2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-\addplot[color = black, dashed] {3.14159 / 2};
-\end{axis}
-\end{tikzpicture}
-\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \Ncal(\theta, \sigma^2)$ under an optimal threshold distribution $\lambda^\star$, when the prior $\pi$ is the uniform distribution over $\Theta = [-0.5,0.5]$.
-%
-%versus $\sigma/\sigma_\theta = 2\sqrt{3}\sigma$.
-The distribution $\lambda^\star$ is the minimizer of \eqref{eq:cvx_average}.
-It is illustrated for various cases in Fig.~\ref{fig:opt_density}.
-The dashed curve represents the upper bound \eqref{eq:upper_bound}.
-\label{fig:dist_bound_uniform}  }
-\end{center}
-\end{figure}
-
-As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \Ncal(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution.
-In this case, the ML estimator reduces to the estimator ${\theta}_n$ of \eqref{eq:estimator_naive}.
-As the following proposition shows, the Bayes risk for this choice of $\lambda$ is maximal, and thus provides an upper bound on the Bayes risk under any $\lambda$.
- \eqref{eq:cvx_average}. 
-\begin{prop}\label{prop:upper_bound}
-For any prior $\pi(d\theta)$ and $\theta_0$ in the support of $\eta(x)$ we have
-\begin{equation} 
-\label{eq:upper_bound}
-R_\pi^\star  \leq 
- \int \frac{\pi(d\theta)}{\eta \left( \theta_0 - \theta \right)},
-\end{equation}
-Furthermore, assuming that $\theta_0 = \mathbb E \theta$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
-\begin{equation}
-\label{eq:bound_Taylor}
-R^\star_\pi \leq \frac{1}{4 f^2(0)} + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right) \sigma_\theta^2 + O(\sigma_\theta^3).
-\end{equation}
-\end{prop}
-\begin{proof}
-The function $x \rightarrow 1/x$ is convex for positive values, hence Jensen's inequality implies
-\[
-\left( \int \eta \left( t-\theta\right) \lambda(dt) \right)^{-1}  \leq \int  \frac{ \lambda(dt)}{ \eta \left( t-\theta\right)  }. 
-\]
-Therefore, the expected value of $\kappa^{-1}(\theta)$ satisfies
-\begin{align}
-\ex{  \frac{1}{\kappa(\theta)}}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
-\end{align}
-The bound \eqref{eq:upper_bound} is obtained by taking $\lambda$ to be a mass distribution at any $\theta_0$ in the support of $\eta(x)$.
-Finally, \eqref{eq:bound_Taylor} is obtained by expanding $1/\eta(x)$ to a third order Taylor series around zero
-%\[
-%1/\eta(x) = \frac{1}{4f^2(0)}  + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right)  x^2 + O(x^3),
-%\]
-and taking its expectation with respect to $\pi$ at $x=\theta_0-\theta$. 
-\end{proof}
-We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so the choice $\theta_0 = \ex{ \theta}$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
-The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$.
-The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $\kappa^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.
-
-\begin{example} \label{ex:bound}
-In the normal case $P_X = \Ncal(\theta, \sigma^2)$, the bound in \eqref{eq:bound_Taylor} implies 
-\[
-\frac{R^\star_\pi}{\sigma^2}  \leq \frac{\pi}{2} + \left( \frac{\pi}{2} -1 \right) \left( \frac{ \sigma_\theta}{\sigma} \right)^2 + O \left(  \frac{\sigma_\theta} { \sigma} \right)^3. 
-\]
-It follows that the ARE approaches its maximal value of $2/\pi$ whenever $\sigma_\theta/\sigma$ is small.
-The exact value of \eqref{eq:upper_bound} in this case, as well as the Bayes ARE with the optimal threshold density $\lambda^\star$ for a uniform $\pi$, are illustrated in Fig.~\ref{fig:dist_bound_uniform}.
-%i.e., each encoder simply reports "$1$" or "$-1$" whenever $X_i$ is larger or smaller than $\theta_0$, respectively.
-Intuitively, an accurate estimation of $\theta$ in this case is possible only if a sufficient mix of ''$1$''s and ''$-1$''s is obtained from the sample.
-When $\sigma_\theta^2$ is high compared to $\simga^2$, one of the events $"1"$ or "$-1"$ becomes too rare to
-\end{example}
-
 \section{Conclusions \label{sec:conclusions}}
@@
 We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.
-
-%\section*{ACKNOWLEDGMENT}
-%This research is supported in parts by...
-%Tsachy Weissman, Stefano Rini, Robert Gray.
-
-\onecolumn
-
-\appendix
-
-\section{}
-
-\subsection{Proof of Proposition~\ref{prop:ceo_lower_bound}
-\label{app:proof:prop_ceo_lower_bound}}
-
-First, we note that when $f(x) = \Ncal(0,\sigma^2)$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$, our distributed setting reduces to the Gaussian CEO problem with $R_1=\ldots = R_n =1$ and $k=1$.
-Therefore, any MSE attained in our distributed setting is also attained by the CEO and thus the optimal CEO strategy (with arbitrary $k$) provides a lower bound to the MSE in our setting.
-\\
-
-Consider the minimal MSE $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
-from \cite[Eq. 10]{chen2004upper}:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-For the special case of $R_\Sigma = n$ and $L=n$, we get
-\begin{equation} \label{eq:ceo_optimal_sumrate2}
-n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, this $D^\star$ provides a lower bound to the CEO MSE with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
-\[
-D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO MSE while enforcing the condition $R_1=\ldots = R_n = 1$.
-Indeed, an upper bound for the CEO MSE under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
-\[
-D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
-\]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.
-
-\subsection{Proof of Lemma~\ref{lem:bound_intervals_delta} \label{proof:lem:bound_intervals_delta}}
-
-%\begin{lem} \label{lem:bound_intervals}
-%Let $f(x)$ be a log-concave, symmetric, and differentiable density such that $\eta(x)$ is strongly unimodal. For any $x_1 > \ldots > x_n \in \mathbb R$, 
-%\begin{equation}
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \max_i \eta(x_i). \label{eq:lem_bound_intervals}
-%\end{equation}
-%In particular, if $|x_i|>\epsilon > 0$ for all $i=1,\ldots,n$, then 
-%\[
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \eta(\epsilon) < 0. 
-%\]
-%\end{lem}
-
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-so 
-\[
-\eta(x) =  \frac{  \left(\delta_1(x) \right)^2}{\Delta_1(x)
-(1-\Delta_1(x))}
-= \frac{  \left( f (x) \right)^2}{ F(x)\left(1-F(x)\right)^2}. 
-\]
-We use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:lem_bound_intervals_delta} is bounded from above by $\max_i \eta(x_i)$. The case $n=1$ is trivial. Assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^2} 
-{\Delta_n \left(1- \Delta_n \right) } \leq \max_i \eta(x_i)
-\label{eq:lem_bound_intervals_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  2 \log \delta_N -  \log \Delta_N -  \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(-1)^{k+1} f(x_k)}{1-\Delta_N },
-\]
-and we conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-%
-Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable. We have 
-\[
-\frac{f'(x)}{f(x)} = c'(x), \quad x\in \mathbb R,
-\]
-which is anti-symmetric, non-negative for $x<0$,  non-positive for $x>0$, and non-increasing since $c(x)$ is concave.
-Therefore, if $c'(x_i) = c'(x_{i+1})$ for some $i =1,\ldots,N-1$, then either (1) $x_i = x_{i+1}$ or (2) $c'(x)$ is the zero function.
-Since (2) violates the assumption that $f(x)$ is a density function, we conclude that $c'(x)$ is an injection.
-%
-As a result, \eqref{eq:gradient_zero} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_proof} equals $\eta(x_1) = \max_i \eta(x_i)$ hence the statement holds.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$, or  $x_i, x_{i+1}$ for some $i$.
-It is left to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Under case (1) we have
-\begin{align*}
-\lim_{x_N \to -\infty} \frac{  \delta_N^2} 
-{\Delta_N \left(1- \Delta_N \right) }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^2} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)} ,
-\end{align*}
-which is smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis. Under case (2) we have
-\begin{align*}
-&  \lim_{x_1 \to \infty}
-\frac{ \delta_N} 
-{\Delta_N\left(1- \Delta_N \right) } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right) \left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right) }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^2 } 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right) },
-\end{align*}
-where $x'_{m} = x_{m+1}$. The last expression is also smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis.  \QEDA \\
-
-\subsection{Proof of Theorem~\ref{thm:adpative_lower_bound}
-\label{proof:thm:adpative_lower_bound}
-}
-
-We first prove the following lemma:
-\begin{lem} \label{lem:fisher_bound}
-Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that $\eta(x)$ is unimodal. For a Borel measurable $A$ set, 
-\[
-M(X) = \begin{cases} 1,& X \in A, \\
--1, & X \notin A.
-\end{cases}
-\]
-Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $\eta(0)$.
-\end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
-When $f(x)$ is the normal density function, this lemma follows from \cite[Thm.
-3]{Barnes2018}.
-The proof below is based on a different techique than in \cite{Barnes2018}, and is valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}.
-\\
-
-The Fisher information of $M$ with respect to $\theta$ is given by
-\begin{align}
-I_\theta & =  \mathbb E \left[ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta \right] \nonumber \\
-& = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
-& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\
-& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\ 
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
-\end{align}
-where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$.
-Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
-\[
-\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
-\]
-which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$.
-It is therefore enough to proceed in the proof assuming that $A$ is of the form
-\[
-A = \cup_{j=1}^k (a_j,b_j),
-\]
-with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
-\begin{align*}
-\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
-& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
-\end{align*}
-so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
-\begin{align}
-& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
-{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
-& \times \frac {1} 
-{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
-\label{eq:lemma_J}
-\end{align}
-It follows from Lemma~\ref{lem:bound_intervals_delta} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $4f^2(0)$.  \QEDA \\
-
-We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
-\begin{equation}
-\label{eq:general_messages}
-B_i = \begin{cases}
-X_i \in A_i & 1, \\
-X_i \notin A_i & -1,
-\end{cases} 
-\end{equation}
-where $A_i \subset \mathbb R$ is a Borel measurable set. 
-%Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
-Consider the conditional distribution $P({B^n|\theta})$ of $B^n$ given $\theta$. We have 
-\begin{align}
-P\left( B^n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
-\end{align}
-where $P\left(B_i =1 | \theta, B^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B^n$ with respect to $\theta$ is given by 
-\begin{align}
-I_\theta(B^n) = \sum_{i=1}^n I_\theta (B_i|B^{i-1}),
-\label{eq:fisher_information}
-\end{align}
-where $I_\theta (B_i|B^{i-1})$ is the Fisher information of the distribution of $B_i$ given $B^{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B^{i-1}) \leq 4f^2(0)$.
-The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
-\begin{align*}
-\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(B^n) + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
-& \geq \frac{1}{ 4f^2(0) n + I_0}.
-\end{align*}
-
-\QEDA
-
-\subsection{Proof of Theorem~\ref{thm:sgd}
-\label{proof:thm:sgd}
-}
-The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.
-
-\subsubsection*{Proof of (i)}
-%Specifically, (i) in Theorem~\ref{thm:sgd} 
-Consider the following simplified version of \cite[Thm. 4]{polyak1992acceleration}:
-\begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
-Let 
-\[
-X_i = \theta + Z_i,\quad i=1,\ldots,n,
-\]
-where the $Z_i$s are i.i.d. with zero means and finite variances. Define
-\begin{align}
-\begin{split}
-\theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
-\bar{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
-\end{split}
-\label{eq:Polyak_Juditsky_alg}
-\end{align}
-where in addition, assume the following: 
-\begin{enumerate}
-\item[(i)] There exits $K_1$ such that $\left| \varphi(x) \right| \leq K_1(1+|x|)$ for all $x\in \mathbb R$.
-\item[(ii)] The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions \eqref{eq:conditions1}.
-\item[(iii)] The function $\psi(x) \triangleq \ex{ \varphi(x+Z_1)}$ is differentiable at zero with $\psi'(0)>0$, and satisfies $\psi(0)=0$ and $x\psi(x) >0$ for all $x\neq 0$.
-Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
-\begin{equation}
-\label{eq:Polyak_Juditsky_cond3}
-\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
-\end{equation}
-\item[(iv)] The function 
-$\chi(x) \triangleq \ex{\varphi^2(x+Z_1)}$ is continuous at zero. 
-\end{enumerate}
-Then $\bar{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}({\theta}_n - \theta)$ converges in distribution to $\Ncal(0,V)$, where
-\[
-V = \frac{ \chi(0)} {\psi'^2(0)}. 
-\]
-\end{thm}
-
-Using the notation above, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have that $\chi(x) = \mathbb E \sgn^2(x+Z_1) = 1$, so $\chi(0) = 1$. In addition,
-\begin{align*}
-\psi(x) & = \ex{ \sgn(x+ Z_1) }= \int_{-\infty}^\infty \sgn(x+z) f(z) dz \\
-& = \int_{-x}^\infty f(z) dz -\int_{-\infty}^{-x} f(z) dz. 
-\end{align*}
-Using the symmetry of $f(x)$ around zero, it follows that $\psi'(x) = 2f(x)$ and thus $\psi'(0) = 2f(0)$.
-It is now easy to verify that the rest of the conditions in Theorem~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$.
-Since
-\[
-\frac{\chi(0)}{\psi'^2(0)} = \frac{1}{4 f^2(0)} = \frac{1}{\eta(0)},
-\]
-it follows from Theorem~\ref{thm:polyak_juditsky} that
-\[
-\sqrt{n}\left({\theta}_n-\theta \right) \overset{d}{\to} \Ncal \left(0, 1/ \eta(0)\right). 
-\]
-
-\subsubsection*{Proof of (ii)}
-We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\mathbb R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates.
-Then
-\begin{align}
-\label{eq:sgd_part2}
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
-\end{align}
-under $\Prob_{\theta,n}$.
-Under the assumption that $f(x)$ is continuously differentiable with a finite location Fisher information, the model $\{Z_n+ \theta\}_{n \in \mathbb N}$ is differentiable in quadratic mean \cite[Exm.
-7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
-\[
-\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
-\]
-where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$. 
- The random variable $L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)
-$ is bounded, and hence 
-\[
-\ex{ L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)} \to \ex{L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)}
-\]
-Any regular estimators in a LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}, hence in order to prove (ii) it is left to show that $\bar{\theta}_n$ is regular. For this purpose, 
-we use the following refinement of Theorem~\ref{thm:polyak_juditsky}, proof of which is given in Subsection~\ref{proof:thm:normal_expansion} below.
-%
-\begin{thm} \label{thm:normal_expansion}
-Set $\Delta_i = \theta_i - \theta$ and
-$\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \Delta_i$. Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{thm:polyak_juditsky}, there exists $K_1$ and $\lambda>0$ such that
-\begin{equation}
-\ex{\left| \varphi(Z_1) - \varphi(x+Z_1)  \right|} \leq K_1 |x|^{1+\lambda}
-\label{eq:PJ_additional_cond}. 
-\end{equation}
-Then:
-\begin{itemize}
-\item[(i)] \begin{equation}
-\sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1). \label{eq:normal_expansion_lem}
-\end{equation}
-where $o_{p,n}(1)$ converges in probability to $0$ as $n\to \infty$.
-\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite location Fisher information 
-\[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)} \right)^2 f(x) dx,
-\]
-then for any converging sequence $h_n \to h$,
-\[
-\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-h}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
-\]
-under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h_n/\sqrt{n}}$ with density $\prod_{i=1}^n f(x_i-h_n/\sqrt{n})$.
-\end{itemize}
-\end{thm}
-We now use this theorem to show regularity of $\bar{\theta}_n$. We have, 
-\begin{align*}
-& %\varphi(Z_1) - \varphi(x+Z_1) = 
-\sgn(Z_1) - \sgn(x + Z_1) \\
-& = \begin{cases}
-2 & Z_1 > 0,\, x+Z_1<0, \\
--2 & Z_1 <0, \, x+Z_1>0, \\
-0 & \text{otherwise}. 
-\end{cases}
-\end{align*}
-It follows that
-\begin{align*}
-\ex{ \left| \varphi(Z_1) - \varphi(x+Z_1) \right| }  \leq \Prob\left( |Z_1| < x  \right) \leq f(0) |x|, 
-\end{align*}
-hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
-\[
-\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = -2f(0) = -\psi'(0). 
-\]
-Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}.
-
-\subsubsection*{Proof of (iii)}
-%In order to prove part (ii) of Theorem~\ref{thm:sgd} 
-Consider the following result from \cite{polyak1990new}:
-\begin{thm}{\cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
-Let
-\begin{align} \label{eq:polyak_new_measurements}
-\begin{cases}
-U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = g'(U_{n-1})+Z_n \\
-\bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
-\end{cases}
-\end{align}
-Assume that the function $g(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative.
-In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \mathbb R$.
-Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution with a density for which the Fisher information exits.
-Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{thm:polyak_juditsky}-(iii) and satisfy the conditions there.
-Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$,
-and there exits $K_3$ such that 
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] \leq K_3(1+|x|^4). 
-\]
-Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
-\[
-V_n \triangleq \mathbb E \left[ \left(\bar{U}_n-x^\star \right)^2 \right] = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
-\]
-\end{thm}
-
-We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$. From \eqref{eq:polyak_new_measurements} we have
-\begin{align*} 
-U_n & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
-& = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
-\end{align*}
-so the estimator $\bar{U}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] = 1 \leq K_3(1+|x|^4)
-\]
-for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
-the conditions in Theorem~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
-In particular, $\psi'(0) = (2f(0))^{-2}$.
-Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$.
-Theorem~\ref{thm:polyak_new} implies that for any $\theta \in \mathbb R$,
-\[
-V_n = \mathbb E \left[ \left({\theta}_n-\theta \right)^2 \right]  = \frac{1}{4n f^2(0)} + o(n^{-1}).
-\]
-
-{\color{red}
-
-\subsection{Proof of Theorem~\ref{thm:normal_expansion}
-\label{proof:thm:normal_expansion}
-}
-\subsubsection*{Proof of (i)}
-The proof of part (i) of Theorem~\ref{thm:normal_expansion} requires the following two additional results from \cite{polyak1992acceleration}:
-\begin{lem}{\cite[Lem. 2]{polyak1992acceleration}}
-\label{lem:Polyak_expansion}
-Consider the process $\{\Delta_i^1 \}_{i=0}^\infty$ defined by
-\[
-\Delta^1_i = \Delta^1_{i-1} - \gamma_i (A \Delta_{i-1}+ \xi_i),\quad i=1,2\ldots.
-\]
-Assume that $A>0$ and condition (ii) of Theorem~\ref{thm:polyak_juditsky} holds. Then 
-\begin{equation}
-\label{eq:Polyak_expansion}
-\sqrt{n} \bar{\Delta}_n^1 = \frac{1}{\sqrt{n}}\sum_{i=0}^{n-1} \Delta_i^1 = \frac{\alpha_n \Delta_0^1}{\sqrt{n} \gamma_0}  + \frac{1}{\sqrt{n} A} \sum_{i=1}^{n-1} \xi_i + \frac{1}{\sqrt{n}}\sum_{i=1}^{n-1} w_i^n \xi_i,
-\end{equation}
-where $\alpha_n$ and $w_i^n$ are real numbers such that $|\alpha_n| \leq K$ and $|w_i^n|\leq K$ for some $K< \infty$, and 
-\[
-\lim_{n\to \infty} \frac{1}{n} \sum_{i=1}^{n-1} |w_i^n| = 0. 
-\]
-\end{lem}
-
-\begin{lem} \label{lem:PJ_converging_sum}
-Under the conditions of Theorem~\ref{thm:polyak_juditsky},
-\[
-\sum_{i=1}^\infty \frac{|\Delta_{i}|^{1+\lambda}}{\sqrt{i}} < \infty 
-\]
-almost surely. 
-\end{lem}
-Lemma~\ref{lem:PJ_converging_sum} follows from the proof of Theorem 2 in \cite{polyak1992acceleration}.
-
-We separate the proof of part (i) into two steps.
-\subsubsection*{Step I}
-The expansion \eqref{eq:normal_expansion_lem} holds for the process  $\{\bar{\Delta}^1_i\}_{i=1}^\infty$ defined as follows:
-\begin{align} \label{eq:Polyak_expansion_lem1_alg}
-& \Delta_i^1  = \Delta_{i-1}^1 - \gamma_i \psi'(0) \Delta_{i-1}^1 - \gamma_i \varphi(Z_i), \qquad
- \delta_0^1 = \Delta_0\\
-& \bar{\Delta}^1_i = \frac{1}{n}\sum_{i=0}^{n-1} \Delta^1_i.
-\end{align}
-
-In order to prove this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$.
-The first expression on the RHS on \eqref{eq:Polyak_expansion} goes to zero in variance.
-In addition,
-\begin{align*}
-& \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }  = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
-& = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0. 
-\end{align*}
-We obtain
-\begin{equation}
-\sqrt{n} \bar{\Delta}^1_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1), \label{eq:Polyak_expansion_aux_process}
-\end{equation}
-
-\subsubsection*{Step II} $\bar{\Delta}_n$ and $\bar{\Delta}^1_n$ are asymptotically equivalent. \\
-
-From \eqref{eq:Polyak_Juditsky_alg} and \eqref{eq:Polyak_expansion_lem1_alg}, the difference $\delta_i = \Delta_i - \Delta_i^1$ satisfies the recursion
-\[
-\delta_i = \delta_{i-1} - \gamma_i \psi'(0) \delta_{i-1} + \gamma_i \left( \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i) \right),
-\]
-where $\delta_0 = 0$. Use Lemma~\ref{lem:Polyak_expansion} with $\xi_i =  \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i)$ to obtain
-\begin{align}
-& \sqrt{n}\bar{\delta}_n = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \xi_i  \\
-& = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \label{eq:PJ_proof1} \\
-& + 
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi(\Delta_{i-1})  + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i)
-\right) \label{eq:PJ_proof2}
-\end{align}
-For the term \eqref{eq:PJ_proof1} and using \eqref{eq:Polyak_Juditsky_cond3}, there exists $K_1$ and $K_2$ such that 
-\begin{align*}
-& \eqref{eq:PJ_proof1}
-\leq K_1 \sum_{i=1}^\infty \frac{1}{\sqrt{i}} \left| \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \right| \\
-& \leq K_2 \sum_{i=1}^\infty \frac{ |\Delta_i|^{1+\lambda}}{\sqrt{i}}. 
-\end{align*}
-
-Lemma~\ref{lem:PJ_converging_sum} shows that 
-\begin{align}
-\sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}}  < \infty \label{eq:PJ_converging_sum},
-\end{align}
-hence the Kronecker lemma implies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \to 0.
-\]
-For the term \eqref{eq:PJ_proof2}, set 
-\[
-\epsilon_i \triangleq \psi(\Delta_{i-1}) + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i).
-\]
-For $a>0$ and $n \in \mathbb N$, define the event
-\[
-A_{n,a} \triangleq \left\{ \sum_{i=1}^{n-1} \frac{|\epsilon_i|}{\sqrt{i}}  \geq a  \right\}. 
-\]
-By Markov's inequality, we have
-\begin{align}
-\ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } \leq \frac{1}{a} \sum_{i=1}^{n-1} \frac{ \ex{|\epsilon_i| \Delta_{i-1} \mid }}{\sqrt{i}}. \label{eq:PJ_proof_3}
-\end{align}
-Using \eqref{eq:Polyak_Juditsky_cond3} and \eqref{eq:PJ_additional_cond}, there exists $K'$ and $\lambda'>0$ such that
-\begin{align*}
-& \ex{ |\epsilon_i| | \Delta_{i-1}}  \leq |\psi(\Delta_{i-1})| + \left| \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i) \right|  \\
-& \leq K' |\Delta_{i-1}|^{1+\lambda}. 
-\end{align*}
-Plugging this bound in \eqref{eq:PJ_proof_3} and using Lemma~\ref{lem:PJ_converging_sum},we obtain 
-\[
-\Prob(A_{n,a}) = \ex{ \ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } } \leq  \frac{K''}{a}
-\]
-for some constant $K''$. It follows that for any $\epsilon$, we may choose $a$ large enough such that 
-\[
-\sup_{n} \Prob(A_{n,a}) < \epsilon.
-\]
-This implies that for any $\epsilon>0$,
-\[
-\Prob \left( \sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty \right) \geq 1-\epsilon,
-\]
-and hence 
-\[
-\sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty
-\]
-almost surely. The Kronecker lemma now implies 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left|\epsilon_i\right| \to 0,
-\]
-hence the term \eqref{eq:PJ_proof2} satisfies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right) \epsilon_i \leq \frac{K'''}{\sqrt{n}} \sum_{i=1}^{n-1} |\epsilon_i| \to 0. 
-\]
-This conclude the proof of part (i).
-
-\subsubsection*{Part (ii)}
-Use \eqref{eq:normal_expansion_lem} to write
-\[
-\sqrt{n} \bar{\Delta}_n = G_n + o_{p,n}(1),
-\]
-where
-\[
-G_n \triangleq -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n} \varphi(Z_i). 
-\]
-From \cite[Exm.
-7.8]{van2000asymptotic}, the location model $f(x-\theta)$ with continuously differentiable $f(x)$ is differentiable in quadratic mean with the score function $-f'(x-\theta)/f(x-\theta)$.
-This fact implies the following expansion \cite[Thm.
-7.2]{van2000asymptotic}:
-\begin{align}
-\label{eq:PJ_LAN}
-& \log \frac{\Prob^n_{h_n/\sqrt{n}}}{\Prob^n_0} (Z_1,\ldots,Z_n) =  \log \prod_{i=1}^{n} \frac{f(Z_i-h_n/\sqrt{n})}  {f(X_i-\theta)} = h J_n - \frac{1}{2}h^2 I_{\theta} + o_{p,n}(1),
-\end{align}
-for any converging sequence $h_n \to h$, 
-where 
-\[
-J_n \triangleq -\frac{1}{\sqrt{n}} \sum_{i=1}^n \frac{f'(Z_i)}{f(Z_i)} .
-\]
-We have
-\begin{align*}
-& \ex{ G_n J_n} = \frac{1}{\psi'(0)}\frac{1}{n} \sum_{i=1}^n \ex{ \varphi(Z_i) \frac{f'(Z_i)}{f(Z_i)} }  \\
-& = \frac{1}{ \psi'(0)} \ex{ \varphi(Z_1) \frac{f'(Z_1)}{f(Z_1)}} =  \frac{1}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx , 
-\end{align*}
-Since both $\sqrt{n}G_n$ and $\sqrt{n}J_n$ are the sum of $n$ i.i.d. random variables with zero mean and finite variance, we obtain, from the central limit theorem and Slutsky's theorem, that
-\[
-\left(\sqrt{n} \bar{\Delta}_n, \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} \right) \overset{d}{\to} \Ncal \left( \left(0,-\frac{h^2}{2} I_\theta \right),  \begin{pmatrix}
-\frac{\chi(0)}{\psi'^2(0)} & \frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx \\
-\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx & h^2 I_\theta 
-\end{pmatrix}  \right)
-\]
-Le Cam's third lemma \cite[Exm. 6.7]{van2000asymptotic} implies that under $\Prob^n_{h/\sqrt{n}}$, 
-\[
-\sqrt{n}\bar{\Delta}_n \overset{d}{\to} \Ncal\left(\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx,  \frac{\chi(0)}{\psi'^2(0)} \right).
-\]
-
-\QEDA
-}
-
-\subsection{Proof of Theorem~\ref{thm:LAN1}
-\label{proof:thm:LAN1}
-}
-The log probability mass distribution of $B^n=(B_1,\ldots,B_n)$ is given by
-\begin{align*}
-& \log \Prob_\theta(b^n) = \sum_{i=1}^n \left( \frac{b_i+1}{2} \log  \Prob(X_i\in A_i) + 
-\frac{1-b_i}{2} \log \Prob(X_i\in A_i) \right), \quad b^n \in \{-1,1\}^n. 
-\end{align*}
-Consequently, 
-\begin{align}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) } = \sum_{i=1}^n    \frac{b_i+1}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} + 
-\sum_{i=1}^n  \frac{1-b_i}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}. 
-\label{eq:LAN_proof1}
-\end{align}
-For each $i=1,\ldots,n$, write 
-\[
-A_i = \bigcup_{k=1}^{K_i} \left(t_{i,k},t_{i,k+1} \right),
-\]
-where $t_{i,1}<\ldots<t_{i,K_i}$ and, with a slight abuse of notation, $t_{i,1}$ and $t_{i,K_i}$ may also be $-\infty$ or $+\infty$, respectively. Thus
-\[
-\Prob_{\theta}(X_i \in A_i) = \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta).
-\]
-In particular, since $f$ is differentible, $\Prob_{\theta}(X_i \in A_i)$ is twice differentiable, and we may write
-\begin{align*}
-\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)  = \Prob_{\theta} (X_i \in A_i) + \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \frac{h}{\sqrt{n}} + o(h), 
-\end{align*}
-and thus
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} = \log \left(1 + \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} + o(h) \right) \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2 + o(h^2).
-\end{align*}
-Similarly, we have
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 + o(h^2).
-\end{align*}
-From \eqref{eq:LAN_proof1} we obtain
-\begin{align*}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
-\left( 
-\frac{b_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-b_i}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}   \right) \\
- & - \frac{h^2}{2n} 
- \sum_{i=1}^n 
-\left( 
- \frac{b_i+1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-b_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 \right) + o(h^2) \\
-\end{align*}
-%
-Noting that 
-\[
-\frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} = \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)},
-\]
-the proof is completed by proving the following two claims:
-\begin{itemize}
-\item[I.] 
-For $i=1,\ldots,n$ denote 
-\[
-U_i = \frac{B_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-B_i}{2}  \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}. 
-\]
-Then 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0, \kappa(\theta) \right). 
-\]
-\item[II.]
-For $i=1,\ldots,n$ denote 
-\[
-V_i =  \frac{B_i-1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-B_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2.
-\]
-Then 
-\[
-\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} \kappa(\theta). 
-\]
-\end{itemize}
-\subsubsection*{Proof of Claim I}
-First note that 
-\begin{align*}
-\mathbb E  [U_i] & = 
- \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=1)   + 
- \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=-1)  = 0. 
-\end{align*}
-In addition,
-\begin{align*}
-& \mathbb E U_i^2 = 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2  \Prob (B_i=1)   + 
-\left( \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2 \Prob (B_i=-1) \\
-& =
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)} +  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)} \\
- & =  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left(1-\Prob_{\theta}(X_i \in A_i) \right)} 
-\end{align*}
-Therefore
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 = L_n(A_1,\ldots,A_n) \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ such that the limit above exists.
-We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition for his version of the central limit time: for any $\delta>0$ we have that
-\begin{align*}
-& \mathbb E \left| U_i \right|^{2+\delta} =
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} 
-\end{align*}
-and
-\begin{equation}
-\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} } { \left( \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta} = 
-\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
-\label{eq:Lyaponov}
-\end{equation}
-Next, we claim that there exits $\delta>0$ and $K>0$, that are independent of $n$, such that
-\begin{align}
-\frac{1}{n} \sum_{i=1}^n \mathbb E  |U_i|^{2+\delta}  < M \label{eq:Lyaponov_num}
-\end{align} 
-for all $n$ large enough. To see this, note that
-\begin{align*}
-& \mathbb E |U_i|^{2+\delta} = 
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}  \\
-  &  = \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} } 
-  \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \\
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}, 
-\end{align*}
-where the last transition is because 
-\[
- \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \leq 1. 
-\]
-We now use the fact that each $A_i$ is a finite union of interval and consider the following lemma, proof of which is given in Appendix~\ref{proof:lem:bound_intervals_delta}.
-\begin{lem} \label{lem:bound_intervals_delta}
-Let $f(x)$ be a log-concave, symmetric, and differentiable PDF such that $\eta(x)$ is unimodal.  There exists $\delta>0$ such that for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, 
-\begin{equation}
-\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^{2+\delta} }
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} } 
-\leq  2^\delta f^{2+\delta}(0). 
-\label{eq:lem_bound_intervals_delta}
-\end{equation}
-\end{lem}
-
-Lemma~\ref{lem:bound_intervals_delta} implies 
-\begin{align*}
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} = \frac{\left| \sum_{k=1}^{K_i} (-1)^k f(x_{i,k}-\theta) \right|^{2+\delta} }
-  { \left( \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta} \left( 1 - \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta}} \\
-  & \leq 2^\delta f^{2+\delta}(0). 
-\end{align*}
-In particular, we conclude that 
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} \leq 2^\delta f^{2+\delta}(0), 
-\]
-and thus for any $\delta>0$ the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we conclude that 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0,\kappa(\theta) \right). 
-\]
-
-\subsubsection*{Proof of Claim II} 
-We have:
-\begin{align*}
-\mathbb E V_i  & = 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)}  
-+ 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)}  \\
- & = 
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left( 1-\Prob_{\theta}(X_i \in A_i) \right)}  
-\end{align*}
- We conclude that:
-\begin{equation} \label{eq:LAN_limit_cond}
-\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =   L_n(A_1,\ldots,A_n)  \to \kappa(\theta)
-\end{equation}
-Since the $V_i$s are independent of each other, Kolmogorov's law of large numbers implies
-%(e.g. \cite[Theorem 10.2.3]{sen1994large}) 
-\[
-\frac{1}{n} \sum_{i=1}^n  V_i \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ for which the limit \eqref{eq:LAN_limit_cond} exists.
-
-\QEDA
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals_delta}} 
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-and 
-\[
-\eta_\delta(x) \triangleq  \frac{  \left(\delta_1(x) \right)^{2+\delta}}{  \left(\Delta_1(x)  \right)^{1+\delta}
-(1-\Delta_1(x))^{1+\delta}}
-= \frac{  \left( f (x) \right)^{2+\delta}}{ \left(F(x) \right)^{1+\delta}(1-F(x))^{1+\delta}}. 
-\]
-The proof is by induction on $n$.
-For the case $n=1$ the LHS of \eqref{eq:lem_bound_intervals_delta} equals $\eta_\delta(x)$.
-Note that $\eta_\delta(0) = 2^\delta f^{2+\delta}(0)$, so it is enough to prove that $\eta_\delta(0)$ attains it maximum at $x=0$.
-We have $\eta_\delta(x) = \eta^{1+\delta}(x)/f^\delta(x)$, and thus
-\[
-\log \eta_\delta'(x) = (1+\delta) \frac{\eta'(x)}{\eta(x)} - \delta \frac{f'(x)}{f(x)}. 
-\]
-By Assumption~\ref{assump:failure_rate} both terms above are negative for $x>0$, so that $\log \eta_\delta'(x) \leq 0$ if and only if
-\begin{equation} \label{eq:delta_proof_cond}
-(1+\delta) \left| \frac{\eta'(x)}{\eta(x)} \right| \geq \delta \left| \frac{f'(x)}{f(x)} \right|, \qquad x>0.
-\end{equation}
-Also by Assumption~\ref{assump:failure_rate}, for $x>0$ we have
-\[
-0 > (\log \eta(x))' = \frac{h'(x)}{h(x)}-\frac{h'(-x)}{h(-x)},
-\]
-so that \eqref{eq:delta_proof_cond} is satisfies for $\delta>0$ small enough.
-
-Next, assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^{2+\delta}} 
-{\left(\Delta_n \right)^{1+\delta}\left(1- \Delta_n \right)^{1+\delta} } \leq \eta_\delta(0) = 2^\delta f^{2+\delta}(0) . 
-\label{eq:lem_bound_intervals_delta_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%If $x_{i+1} = x_i$ for some $i=1,\ldots,N-1$, then then the indices $i$ and $i+1$ may  be removed from all sums in \eqref{eq:lem_bound_intervals}, what brings us to the case $n = N-2$.
-Therefore, we may assume that $x_1 < \ldots < x_n$.
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  (2+\delta) \log \delta_N - (1+\delta) \log \Delta_N - (1+\delta) \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{(2+\delta) (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(1+\delta)(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(1+\delta)(-1)^{k+1} f(x_k)}{1-\Delta_N }.
-\]
-We conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero_delta}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N(1+\delta)}{2+\delta} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-From the same reason as in the proof of Lemma~\ref{lem:bound_intervals_delta}, \eqref{eq:gradient_zero_delta} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_delta_proof} equals $\eta_\delta(x_1)$ which was shown to be smaller than $\eta_\delta(\epsilon)$.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_delta_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$,  $x_i, x_{i+1} = -\epsilon$ for some $i$, or $x_i, x_{i+1} = \epsilon$ for some $i$.
-It is therefore enough to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Assume first $x_N \rightarrow -\infty$. Then 
-\begin{align*}
-\frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)^{1+\delta} } ,
-\end{align*}
-which is smaller than $\eta_\delta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
-\begin{align*}
-& \frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right)^{1+\delta} }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^{2+\delta}} 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)^{1+\delta}\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right)^{1+\delta} },
-\end{align*}
-where $x'_{m} = x_{m+1}$ for $m=1,\ldots, N-1$. The last expression is smaller than $\eta_{\delta}(0)$ by the induction hypothesis.  \QEDA \\
-
-\subsection{Proof of Theorem~\ref{thm:non_existence}
-\label{proof:thm:non_existence}
-}
-
-Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta) = \eta(0)$. 
-%
-Since $B_1,B_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, $\theta$ is in $\Xi$ if and only if
-\begin{equation}
-\label{eq:non_existence_proof}
-\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0). 
-\end{equation}
-By assumption, we have $B_i^{-1} = A_i$ where $A_i$ can be expressed as
-\[
-A_i = \cup_{i=1}^K (a_{i,k},b_{i,k}), 
-\]
-where $a_{i,1} \leq b_{i,1} \leq \ldots \leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values $-\infty$ and $\infty$, respectively. Denote
-\[
-\mathcal B_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\}.
-\]
-For any $\theta$ and $\epsilon>0$, denote 
-\[
-S_n(\theta, \epsilon) \triangleq \left\{ i\leq n \,:\, (\theta-\epsilon,\theta+\epsilon) \cap \mathcal B_i \neq \emptyset \right\}
-\]
-In words, $S_n$ contains all integers smaller than $n$ in which an $\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals consisting $A_i$. 
-%
-We now claim that 
-if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. Indeed, for such $\theta$ we have
-\begin{align}
-& L_n(A_1,\ldots,A_n; \theta) \nonumber \\
-& = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
-\frac{ \left(\sum_{k=1}^{K}  f(\theta - b_{i,k})- f(\theta - a_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& 
-+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(b_{i,k}-\theta) - f(a_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& \overset{(a)}{\leq}
-\frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
- \label{eq:non_existence_proof1}
-\end{align}
-where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} and the fact that for $i \in S_n(\theta, \epsilon)$, 
-\[
-\max\left\{ \max_k \eta(b_{i,k}-\theta) , \max_k \eta(a_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
-\]
-Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, \eqref{eq:non_existence_proof1}, and thus $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.
-\par
-For $k\in \mathbb N$, assume by contradiction that there exists $N \geq 2K + 1$ distinct elements
-$\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$ consists of at most $K$ intervals, we have that 
-\begin{equation}
-\label{eq:few_optimality_points_proof}
-\card (\cup_{i=1}^n \mathcal B_i) \leq 2 n K. 
-\end{equation}
-Fix $\epsilon>0$ such that 
-\[
-\epsilon < \frac{1}{2}\min_{i\neq j} |\theta_i - \theta_j|. 
-\]
-Since for each $\theta \in \Theta$ we have $S_n(\theta, \epsilon) \to 1$, there exists $n$ large enough such that 
-\[
-\card \left(S_n(\theta_i, \epsilon) \right) \geq n \left(1-\frac{1}{2N} \right)
-\]
-for all $i=1,\ldots,N$.
-However, $S_n(\theta_1,\epsilon), \ldots S_n(\theta_N,\epsilon)$ are disjoint, so the cardinallity of their union is at least $n\left(1-\frac{1}{2N} \right)N$ which is grater than $2nK + n/2$ in contradiction to \eqref{eq:few_optimality_points_proof}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEfull,onebit}
-
-\end{document}

### 2019-09-23 distributed-estimation.tex
Adding a bib file

--- 2019-09-19 onebit_full.tex
@@
-%% \documentclass[11pt]{article}
-\documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper
-
-%LatexiDiff ignore tikz:
-% $: latexdiff -c "PICTUREENV=(?:picture|tikzpicture|DIFnomarkup)[\w\d*@]*" old.tex new.tex > diff.tex
-
-%\IEEEoverridecommandlockouts                              %
-
-%\usepackage{mathcomSTEP}
-
-%\overrideIEEEmargins 
-%\IEEEoverridecommandlockouts                              % This command is only needed if 
-% you want to use the \thanks command
-
-%\overrideIEEEmargins                                      % Needed to meet printer requirements.
-
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-\onecolumn
-
-\usepackage{mathptmx} 
-\usepackage{times} 
-\usepackage{amsmath} 
-\usepackage{amsbsy} 
-\usepackage{amssymb}
-
-%\usepackage{newtxtext, newtxmath}
-\usepackage{mathrsfs}
-\usepackage{comment}
-\usepackage[export]{adjustbox}
-\usepackage{tikz}
-\usetikzlibrary{external,positioning,decorations.pathreplacing,shapes,arrows,patterns}
-
-\usepackage[hidelinks]{hyperref}
-%\tikzexternalize[mode=list and make]
-\usepackage{algorithmicx}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage{pstool}
-\usepackage[latin1]{inputenc}
-\usetikzlibrary{arrows,shapes}
-\usepackage{xifthen}
-\usepackage{epic}
-%\usepackage{caption}
-\usepackage{epstopdf}
-
-\newtheorem{thm}{\bf{Theorem}}
-\newtheorem{cor}[thm]{\bf {Corollary}}
-\newtheorem{lem}[thm]{\bf {Lemma}}
-\newtheorem{prop}[thm]{\bf {Proposition}}
-\newtheorem{example}{\bf {Example}}
-\newtheorem{definition}{\bf {Definition}}
-\newtheorem{rem}{\bf {Remark}}
-\newtheorem{assump}{\bf {Assumptions}}
-
-\newcommand{\ex}[1]{\ensuremath{\mathbb{E}\left[ #1\right]}}
-
-\newcommand{\Var}[1]{\ensuremath{\mathrm{Var} \left[ #1\right]}}
-
-\newcommand{\unif}{\mathsf{unif}}
-\newcommand{\card}{\mathrm{card}}
-\newcommand{\ARE}{\mathsf{ARE}}
-\newcommand{\supp}{\mathrm{supp} }
-\renewcommand\vec[1]{\ensuremath\boldsymbol{#1}}
-\newenvironment{proof}{\paragraph*{Proof}}{\hfill$\square$ \newline}
-\newcommand{\sgn}{\mathrm{sgn} }
-\newcommand{\Prob}{\mathbb{P} }
-\newcommand{\argmax}{\mathrm{argmax}}
-\newcommand*{\QEDA}{\hfill\ensuremath{\square}}
-\newcommand{\CEO}{\mathsf{CEO}}
-\newcommand{\Ncal}{\mathcal{N}}
-
-\newcommand{\enc}{\mathsf{enc}}
-\newcommand{\est}{\mathsf{est}}
-
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-\tikzstyle{sint}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.8cm,thick ]
-\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
-\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
-\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.7cm,thick ]
-\tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-
-\author{
-    \IEEEauthorblockN{
-Alon Kipnis\IEEEauthorrefmark{1} and   
-    John C. Duchi\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}  \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}Stanford University, Department of Statistics \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Stanford University, Department of Electrical Engineering. }
-}
-
-\title{\LARGE \bf Mean Estimation from One-Bit Measurements}
-
-\begin{document}
-\graphicspath{{./Figs/}}
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{abstract}
-
-%{\color{red}  See LASSO results in http://arxiv.org/abs/1506.02181v1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\input{introduction}
-
-\section{Problem Formulation \label{sec:problem}}
-
-Let $f(x)$ be a symmetric and log-concave density function with a finite second moment $\sigma^2$.
-For $\theta \in \Theta$, denote by $P_X$ the probability distribution with density $f\left( x-\theta \right)$.
-Therefore, $P_X$ is an absolutely continuous log-concave distribution with mean $\theta$ and variance $\sigma^2$.
-Symmetry and log-concavity of $f(x)$ imply that $P_X$ is strongly unimodal (has a unique local maxima) with its mode at $x =\theta$ \cite{ibragimov1956composition}.
-We further assume that the \emph{parameter space} $\Theta$ is a closed interval of the real line.
-\par
-In some situations it is useful to assume that $\theta$ is drawn once from the prior distribution $\pi$ on $\Theta$.
-In this case we assume that $\pi$ is an absolutely continuous distribution, and denote its density by $\pi(\theta)$, i.e., $\pi(d\theta) = \pi(\theta)d\theta$.
-\par
-The random variables $X_1,\ldots,X_n$ represent $n$ independent samples from $P_X$. 
-We are interested in estimating $\theta$ from a set of $n$ binary messages $B_1,\ldots,B_n$, obtained from $X_1,\ldots,X_n$ under three possible scenarios illustrated in Figure~\ref{fig:setup}: 
-\begin{itemize}
-\item[(i)~~] Centralized $B_i(X_1,\ldots,X_n)$, $i=1,\ldots,n$.
-\item[(ii)~] Adaptive $B_i(X_i,B_1,\ldots,B_{i-1})$, $i=2,\ldots,n$.
-\item[(iii)] Distributed $B_i(X_i)$, $i=1,\ldots,n$.
-\end{itemize}
-
-The performance of an estimator ${\theta}_n \triangleq {\theta}_n(B^n)$ in any of these cases is measured according to the quadratic risk:
-\begin{equation}
-\label{eq:error_def}
-R_n \triangleq \mathbb E\left({\theta}_n - \theta \right)^2,
-\end{equation}
-where the expectation is taken with respect to the distribution of $X_1,\ldots,X_n$ and, whenever available, a prior distribution $\pi(\theta)$ over $\Theta$.  
-%It is well known that minmax estimation error 
-%\begin{equation}
-%R_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left({\theta}_n - \theta \right)^2 | \theta \right],
-%\end{equation}
-%can be obtained from $R_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}. 
-%
-The main problems we consider in this paper are the minimal value of \eqref{eq:error_def}, as a function of $n$ and $f(x)$, under different choices of the encoding functions in cases (i), (ii), and (iii).
-\par
-
-We give particular attention to the ARE of estimators with respect to an asymptotically normal efficient estimator that is not subject to the bit constraint.
-Specifically, let $\{a_n,\,n\in \mathbb N\}$ be a sequence such that
-\[
-\sqrt{a_n}\left({\theta}_n - \theta\right) \overset{d}{\longrightarrow} \Ncal(0, \sigma^2).
-\]
-Then the ARE of ${\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
-\[
-\ARE({\theta}_n) \triangleq
-\lim_{n\rightarrow \infty} \frac{a_n}{n}. 
-\]
-Note that in the special case where there exists $V \in \mathbb R$ such that
-\[
-a_n \mathbb E \left({\theta}_n - \theta \right)^2 = V + o(1),
-\]
-with $o(1)\to 0$ as $n\to \infty$, then the ARE of ${\theta}_n$ is finite and equals $\sigma^2/V$. \par
-
-In addition to the notation above, we also denote by $F(x)$ the cumulative distribution function of $X_i$, and define
-\begin{equation} \label{eq:eta_def}
-\eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))} =  \frac{f(x)f(-x)}{F(x)F(-x)}, 
-\end{equation}
-where the last equality is due to symmetry of $f(x)$. We note that 
-\begin{equation}
-\label{eq:eta_h}
-\eta(x) = h(x)h(-x) = f(x) \left( h(x) + h(-x) \right), 
-\end{equation}
-where 
-\[
-h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
-\]
-is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function since $f(x)$ is log-concave \cite{bagnoli2005log}. 
-%
-For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as illustrated in Fig.~\ref{fig:eta}. 
-%
-In this paper we only consider the normal distribution and other log-concave symmetric distributions for which this property of $\eta(x)$ holds. Specifically, we require the following:
-\begin{assump} \label{assump:failure_rate}
- $\eta(x)$ has a unique maximum (at the origin) and is a non-increasing function of $|x|$. 
-\end{assump}
-%That is, Assumption~\ref{assump:failure_rate} says that $\eta'(x) < 0 $ for all $x>0$. 
-Under this assumption we have, 
-\[
-4f^2(x) \leq \eta(x) \leq \eta(0),
-\] 
-%
-where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median.
-Combined with log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that $\eta(x)$ vanishes as $|x|\rightarrow \infty$.
-\par
-%
-Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions).
-Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.\par
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -3, xmax=3, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.9,
-samples=10, 
-xlabel= $x$,
-xtick={-2,-1,0,1,2},
-xticklabels={-2,-1,0,1,2},
-ytick={0,0.3989423,0.6366198},
-yticklabels={0,$\frac{1}{\sqrt{2 \pi}}$,$2/\pi$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\eta(x)$};
-\addplot[domain = -5:5, samples = 50, color = red, solid, smooth]  {exp(-x^2/2) / sqrt(2*3.14159)};
-\addlegendentry{$\phi(x)$};
-\addplot[domain = -5:5, samples = 50, color = black, solid, dashed]  {4*exp(-x^2) / (2*3.14159)};
-\addlegendentry{$4\phi^2(x)$};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -4, xmax=4, 
-restrict y to domain = -10:0,
-ymin = -10,
-samples=10, 
-xlabel= $x$,
-xtick={-3,-2,-1,0,1,2,3},
-xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,-0.45158,-0.919},
-yticklabels={0,,},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\log \eta(x)$};
-\addplot[domain = -5:5, samples = 30, color = red, solid, smooth]  {-(x)^2/2 -0.9189};
-\addlegendentry{$\log \phi(x)$};
-\end{axis}
-\end{tikzpicture}
-\caption{
-The function $\eta(x) = f^2(x) / F(x)F(-x)$ for $f(x) = \phi(x)$ the standard normal density.
-\label{fig:eta}
-}
-\end{center}
-\end{figure}
-
-\section{Consistent Estimation and Off-the-shelf Bounds \label{sec:preliminary}}
-%
-In this section we adapt known results to derive lower and upper bounds on the relative efficiency under setting (iii). These bounds establish the following facts:
-\begin{itemize}
-\item[I.] A consistent estimator with an asymptotically normal distribution always exists in setting (iii), and hence in setting (ii). 
-\item[II.] For the normal distribution, the ARE in setting (iii) is at most $3/4$. Namely, under setting (iii), all estimators are strictly inferior compared to the sample mean. 
-\end{itemize}
-
-\subsection{Consistent Estimation}
-Fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
-\[
-B_i = \mathbf 1_{X_i>\theta_0}, 
-\]
-where $\mathbf 1_A$ is the indicator of the event $A$. We have
-\[
-P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
-\]
-so that 
-\begin{equation}
-\label{eq:estimator_naive}
-{\theta}_n = \theta_0 + F^{-1}\left( P_n \right)
-\end{equation}
-is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set due to log-concavity.
-Furthermore, the variance of $P_n$ is $F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)$, and hence the delta method implies that ${\theta}_n$ is asymptotically normal with variance
-\begin{equation} 
- \frac{F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}{f^2(\theta-\theta_0)} = \frac{1}{
-\eta(\theta-\theta_0)}.
-\end{equation}
-In particular, the ARE of ${\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
-In other words, for a prescribed accuracy, ${\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
-\par
-%
-%
-Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of ${\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
-This ARE is attained only when $\theta_0 = \theta$, whereas $\theta$ is apriori unknown.
-Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of ${\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
-As an example, when $f(x)$ is a normal density, the ARE of ${\theta}_n$ is less than $\approx 0.14$ when $\theta_0$ is $2$ standard deviations from $\theta$.
-Therefore, the estimator ${\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
-\par
-It is suggested that we can attain lower variance in estimation by updating the threshold value $\theta_0$ in \eqref{eq:estimator_naive} after observing one or a batch of the single bit messages.
-Schemes with such adaptation fall within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
-\par
-
-\subsection{Multiterminal Source Coding \label{sec:ceo}}
-The CEO setting considers the estimation of a sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_i$ is available at $n$ terminals.
-At each terminal $i$, an encoder observes the $k$ noisy samples
-\[
-X_{i,j} = \theta_j + Z_{i,j},\qquad j=1,\ldots,k, \qquad i = 1,\ldots,n,
-\]
-and transmits $r_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates ${\theta}_1,\ldots,{\theta}_k$ with the goal of minimizing the quadratic risk:
-\[
-R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - {\theta}_j \right)^2 \right]. 
-\]
-Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $r_1=\ldots=r_n = 1$.
-It follows that, assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
-%
-Consequently, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the minimal MSE in the CEO setting as $k \to \infty$.
-Note that the difference between the CEO setting and ours lays in the privilege of each of the encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realizations, rather than a single realization using a single bit in ours.
- \par
-When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k$ goes to infinity were fully characterized in \cite{prabhakaran2004rate}.
-Furthermore, the work of \cite{chen2004upper} provided an expression for quadratic risk attained in the CEO setting under Gaussian priors.
-Adapting to our setting, this expression provides the following proposition:
-\begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is arbitrary.
-Then any estimator ${\theta}_n$ of $\theta$ in the distributed setting satisfies
-\begin{equation} \label{eq:ceo_bound}
- n \ex{\left( \theta - \theta_n \right)^2} \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
-\end{equation}
-where the expectation is with respect to $\theta$ and $X^n$.
-\end{prop}
-
-\begin{proof}
-See Appendix~\ref{app:proof:prop_ceo_lower_bound}.
-\end{proof}
-
-From the formulation of the CEO problem, it follows that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is attributed to the ability to perform coding over blocks.
-Namely, each encoder in the CEO setting may encode an arbitrary number of $k$ independent realizations of $\theta$ using $k$ bits, versus only one realization with one bit in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product probability space that distinguishes between the CEO problem with one bit per encoder on average and the mean estimation problem from one-bit measurements in the distributed setting.
-
-\section{Adaptive Estimation \label{sec:sequential}}
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $\eta(0)\sigma^2$, which is the ARE of the median of the sample $X_1,\ldots,X_n$.
-We also provide a particular adaptive estimation scheme that attains this maximal efficiency.
-%Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $B_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages.
-%Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $\eta(0)\sigma^2$.
-
-\subsection{Limited efficiency in the adaptive setting}
-Our first result asserts that the ARE of any adaptive encoding and estimation scheme is bounded from above by $\eta(0)\sigma^2$. %This result follows from the following theorem:
-\begin{thm}[maximal relative effeciency] \label{thm:adpative_lower_bound}
-Let ${\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Figure~\ref{fig:setup}-(ii). Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-n\mathbb E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0},
-\]
-where 
-\[
-I_0 = \mathbb E \left( \frac{d}{d\theta} \log \pi (\theta) \right)^2
-\]
-is the Fisher information with respect to a location model in $\theta$. 
-\end{thm}
-
-\subsubsection*{Proof}
-%We first bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
-The result then follows using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are in
-See Appendix~\ref{proof:thm:adpative_lower_bound}.\par
-
-Theorem~\ref{thm:adpative_lower_bound} implies that any estimator ${\theta}_n$ from any adaptive encoding scheme satisfies
-\[
-n\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{1}{4f^2(0)}+O(n^{-1}),
-\]
-and 
-\[
-\ARE({\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
-\]
-It is possible to extend Theorem~\ref{thm:adpative_lower_bound} to any other loss functions using a more subtle version of the Van Tress inequality provided in \cite{efroimovich1980information}.
-See also \cite{DBLP:journals/corr/abs-1902-08582}.
-\par
-%
-Next, we provide an adaptive encoding and estimation scheme that attains the maximal ARE of $\eta(0)\sigma^2$.
-
-\subsection{Asymptotically optimal estimator}
-Let $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ be a strictly positive sequence. Consider the following estimator ${\theta}_n$ for $\theta$:  
-\begin{equation}
-\label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n B_n, \quad n = 1,2,\ldots,
-\end{equation}
-where 
-\begin{equation}
-B_n = B_n (X_n,\theta_{n-1}) =\sgn (X_n - \theta_{n-1}).
-\end{equation}
-Define the $n$th step estimation as
-\begin{equation} \label{eq:sgd_est}
-\bar{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
-\end{equation}
-
-We have the following results:
-\begin{thm} \label{thm:sgd}
-Consider the sequence $\left\{\bar{\theta}_n \right\}_{n\in \mathbb N}$ defined by \eqref{eq:sgd_est}. 
-\begin{enumerate}
-\item[(i)] Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions1}
-\begin{cases}
-\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
-\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
-\mathrm{for~some~}0< \lambda \leq 1
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Then
-\[
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left(0,\frac{1}{\eta(0)}\right).
-\]
-%
-%
-\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with a finite location Fisher information, namely
-\[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)}  \right)^2 f(x) dx < \infty.
-\]
-%(or that $f(x-\theta)$ is differentiable in quadratic mean).  
-Then for any bounded, symmetric, and quasi-convex function $L$, 
-\begin{align} 
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
-\\
-& \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
-\end{align}
-where $Z \sim \Ncal(0,1)$. 
-%
-%
-\item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions2}
-\begin{cases}
-\gamma_n = o(n^{-2/3}), &  \\
-\sum_{n=1}^\infty \gamma_n = \infty.  & \\
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ with $\beta \in (2/3,1)$). Then
-\[
- \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{n\eta(0)} + o(n^{-1}). 
-\]
-\end{enumerate}
-\end{thm}
-
-\subsubsection*{Proof}
-See Appendix~\ref{proof:thm:sgd}. \par
-
-Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the maximal ARE, as established by Theorem~\ref{thm:adpative_lower_bound}.
-%Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$.
-%
-The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$.
-Consequently, the procedure above is known as averaged stochastic gradient descent for minimizing $x \to |x|$ given the data $X_1,\ldots,X_n$.
-The minimal value of this optimization is the sample median, and Theorem~\ref{thm:sgd} provides conditions for the sequence of gradient steps so that the algorithm converges to this minimum.
-In particular, parts (i) and (ii) of Theorem~\ref{thm:sgd} provides conditions under which $\bar{\theta}$ is asymptotically normal and local asymptotically minimax, in the sense that it attains the local asymptotic minimax bound \cite{van2000asymptotic}.
-Part (iii) provides an additional condition under which $\bar{\theta}$ also converges in its second moment.
- \par
-%Note that $\theta_0$ is not explicitly defined in equation \eqref{eq:sgd_est}.
-A reasonable initialization for $\theta_0$ is $\theta_0 = \mathbb E [\theta]$, although Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
-Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$.
-\\
-In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $B_n$ depends on its private sample as well as the current gradient descent estimate $\theta_{n-1}$.
-In this sense, each encoder in this algorithm interacts with previous one by using the current estimate.
-%
-As we explain next, 
-it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ with only one round of interactions among the encoders.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
-% \node[below of = source, node distance = 1cm] (source2) {$X_2$};
-%\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};  
-%\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};
-
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[below of = source, node distance = 0.5cm] {$\vdots$};
-
-\node[int1, right of = enc3, node distance = 2.1cm ] (est) {$\est_1$};
-
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
-
-%\draw[->,line width = 2pt] (enc2) -| node[above, xshift = -1cm] (mes2) {$B_2$} (est);
-
-\draw[->,line width = 2pt] (enc3) -- node[above, xshift = 0cm]  {$B_{n_1}$} (est);
-
-\node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
-\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {$\enc$};  
-\draw[->,line width = 2pt] (sourceB) -- (enc1B);
-
-\node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
-\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {$\enc$};  
-\draw[->,line width = 2pt] (source3B) -- (enc3B); 
-\node[below of = sourceB, node distance = 0.4cm] {$\vdots$};
-
-\node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {$\est_2$};
-
-\draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.5cm] {$B_{n_1+1}$} (estB);
-\draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);
-
-\draw[->,line width = 1pt] (est.east) node[above, xshift  =0.5cm] {${\theta}_{n_1}$} -| (enc1B.north);
-
-%\draw[->,line width = 1pt] (enc1B) -- (enc3B);
-
-\draw[->,line width = 0.5pt] (est.east) -| +(1.3,-0.5) -- +(1.3,-2.5) -| (enc3B.north);
-
-%\draw[->,line width = 1pt] (enc1B)  -- node[right] {${\theta}_{n_1}$} (enc3B);
-
-\draw[->,line width = 0.5pt] (estB) -- +(0.8,0) node[right] {${\theta}_n$};
-\node[below of = enc1B, node distance = 0.5cm] {$\vdots$};
-
-\end{tikzpicture}
-\end{center}
-\caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
-\label{fig:one_round}
-}
-\end{figure}
-
-\subsection{Maximal Efficiency using One Round of Threshold Adaptation}
-In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
-\[
-B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
-\]
-and deduced that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
-%
-We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ based on previously observed bits at least once.
-%
-In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
-We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate ${\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use ${\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$.
-Figure~\ref{fig:one_round} illustrates a diagram of this procedure.
-%
-The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
-\begin{thm}
-For $i=1,\ldots,n$ set
-\[
-B_i = \begin{cases}
- \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
- \mathbf 1_{X_i \geq {\theta}_{n_1} }& i={n_1+1,\ldots,n},
-\end{cases}
-\]
-where $n = n_1+ n_2$ and 
-\[
-{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
-\frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
- \right).
-\] 
-Let 
-\[
-{\theta}_{n_2}  = {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
-\]
-and assume that $n_1(n) \rightarrow \infty$ and $n_1(n)/n \rightarrow 0$. Then:
-\begin{align*}
- \sqrt{n} \left( {\theta}_{n_2} - \theta  \right) \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
-\end{align*}
-\end{thm}
-%
-%
-\begin{proof}
-For $t\in \mathbb R$, set
-\[
-p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
-\]
-From the central limit theorem
-\begin{align*}
-& \sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)  = \sqrt{\frac{n}{n_2}} \sqrt{n_2} \left(  p_{n_2}(t) - F(\theta - t) \right) \\
-& \overset{d}{\rightarrow} \Ncal\left( 0, V(t) \right),
-\end{align*}
-where
-\[
-V(t) \triangleq F(\theta - t) F \left( t - \theta\right). 
-\]
-Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ implies
-\begin{align*}
-& \sqrt{n} \left( t + F^{-1}(\hat{p}_{n_2}(t)) - \theta \right) \\
-&= \sqrt{n} \left( g(\hat{p}_{n_2}(t)) - g \left(F(\theta-t) \right)  \right) \\
-& \overset{d}{\to} \Ncal\left(0, 
-1/\eta(\theta-t) \right).
-\end{align*}
-%where this convergence is uniform in $t$ since all moments of $F^{-1}(\hat{p}_{n_2})$ exists. 
-On the other hand, by the law of large numbers,
-\[
-p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
-\]
-so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity and thus 
-\[
-\eta( {\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
-\]
-Finally,
-\begin{align*}
-& \sqrt{n}\left({\theta}_{n_2} - \theta\right) \\
-& = \sqrt{n} \left( {\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}({\theta}_{n_1})) - \theta \right)  \\
-& \overset{d}{\to} \Ncal\left( 0, 
-1/\eta(0) \right) 
-\end{align*}
-by Slutsky's theorem.
-\end{proof}
-%
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=10cm, height=6cm,
-xmin = 0, xmax=800, 
-restrict y to domain = 0:3,
-ymin = 0,
-ymax = 3.4,
-samples=10, 
-xlabel= $n$,
-ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
-%xtick={-3,-2,-1,0,1,2,3},
-%xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,1,1.57},
-yticklabels={0,1,$\pi/2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-
-\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{asymptotically optimal};
-
-%\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
-
-\addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{single interaction};
-
-\end{axis}
-\end{tikzpicture}
-%\begin{tikzpicture}
-%\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
-%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left({\theta}_n - \theta \right)^2$};
-%\node[scale = 0.7] at (0,-2.4) {$n$};
-%\end{tikzpicture}
-\caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.
-In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$.
-The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage.
-\label{fig:adaptive_error}  }
-\end{center}
-\end{figure}
-
 \section{Distributed Estimation \label{sec:distributed}}
@@
 \end{example}
-
-\section{Conclusions \label{sec:conclusions}}
-We considered the MSE risk in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
-%
-In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency (ARE) larger than that of the median of the samples.
-We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median.
-%We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
-\par
-In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and ARE. 
-%
-We conclude that under such conditions, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in the distributed setting.
-%
-We further considered the special case of messages obtained by comparing against a prescribed sequence of thresholds.
-We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.
-
-%\section*{ACKNOWLEDGMENT}
-%This research is supported in parts by...
-%Tsachy Weissman, Stefano Rini, Robert Gray.
-
-\onecolumn
-
-\appendix
-
-\section{}
-
-\subsection{Proof of Proposition~\ref{prop:ceo_lower_bound}
-\label{app:proof:prop_ceo_lower_bound}}
-
-First, we note that when $f(x) = \Ncal(0,\sigma^2)$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$, our distributed setting reduces to the Gaussian CEO problem with $R_1=\ldots = R_n =1$ and $k=1$.
-Therefore, any MSE attained in our distributed setting is also attained by the CEO and thus the optimal CEO strategy (with arbitrary $k$) provides a lower bound to the MSE in our setting.
-\\
-
-Consider the minimal MSE $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
-from \cite[Eq. 10]{chen2004upper}:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-For the special case of $R_\Sigma = n$ and $L=n$, we get
-\begin{equation} \label{eq:ceo_optimal_sumrate2}
-n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, this $D^\star$ provides a lower bound to the CEO MSE with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
-\[
-D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO MSE while enforcing the condition $R_1=\ldots = R_n = 1$.
-Indeed, an upper bound for the CEO MSE under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
-\[
-D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
-\]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.
-
-\subsection{Proof of Lemma~\ref{lem:bound_intervals_delta} \label{proof:lem:bound_intervals_delta}}
-
-%\begin{lem} \label{lem:bound_intervals}
-%Let $f(x)$ be a log-concave, symmetric, and differentiable density such that $\eta(x)$ is strongly unimodal. For any $x_1 > \ldots > x_n \in \mathbb R$, 
-%\begin{equation}
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \max_i \eta(x_i). \label{eq:lem_bound_intervals}
-%\end{equation}
-%In particular, if $|x_i|>\epsilon > 0$ for all $i=1,\ldots,n$, then 
-%\[
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \eta(\epsilon) < 0. 
-%\]
-%\end{lem}
-
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-so 
-\[
-\eta(x) =  \frac{  \left(\delta_1(x) \right)^2}{\Delta_1(x)
-(1-\Delta_1(x))}
-= \frac{  \left( f (x) \right)^2}{ F(x)\left(1-F(x)\right)^2}. 
-\]
-We use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:lem_bound_intervals_delta} is bounded from above by $\max_i \eta(x_i)$. The case $n=1$ is trivial. Assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^2} 
-{\Delta_n \left(1- \Delta_n \right) } \leq \max_i \eta(x_i)
-\label{eq:lem_bound_intervals_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  2 \log \delta_N -  \log \Delta_N -  \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(-1)^{k+1} f(x_k)}{1-\Delta_N },
-\]
-and we conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-%
-Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable. We have 
-\[
-\frac{f'(x)}{f(x)} = c'(x), \quad x\in \mathbb R,
-\]
-which is anti-symmetric, non-negative for $x<0$,  non-positive for $x>0$, and non-increasing since $c(x)$ is concave.
-Therefore, if $c'(x_i) = c'(x_{i+1})$ for some $i =1,\ldots,N-1$, then either (1) $x_i = x_{i+1}$ or (2) $c'(x)$ is the zero function.
-Since (2) violates the assumption that $f(x)$ is a density function, we conclude that $c'(x)$ is an injection.
-%
-As a result, \eqref{eq:gradient_zero} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_proof} equals $\eta(x_1) = \max_i \eta(x_i)$ hence the statement holds.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$, or  $x_i, x_{i+1}$ for some $i$.
-It is left to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Under case (1) we have
-\begin{align*}
-\lim_{x_N \to -\infty} \frac{  \delta_N^2} 
-{\Delta_N \left(1- \Delta_N \right) }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^2} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)} ,
-\end{align*}
-which is smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis. Under case (2) we have
-\begin{align*}
-&  \lim_{x_1 \to \infty}
-\frac{ \delta_N} 
-{\Delta_N\left(1- \Delta_N \right) } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right) \left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right) }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^2 } 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right) },
-\end{align*}
-where $x'_{m} = x_{m+1}$. The last expression is also smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis.  \QEDA \\
-
-\subsection{Proof of Theorem~\ref{thm:adpative_lower_bound}
-\label{proof:thm:adpative_lower_bound}
-}
-
-We first prove the following lemma:
-\begin{lem} \label{lem:fisher_bound}
-Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that $\eta(x)$ is unimodal. For a Borel measurable $A$ set, 
-\[
-M(X) = \begin{cases} 1,& X \in A, \\
--1, & X \notin A.
-\end{cases}
-\]
-Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $\eta(0)$.
-\end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
-When $f(x)$ is the normal density function, this lemma follows from \cite[Thm.
-3]{Barnes2018}.
-The proof below is based on a different techique than in \cite{Barnes2018}, and is valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}.
-\\
-
-The Fisher information of $M$ with respect to $\theta$ is given by
-\begin{align}
-I_\theta & =  \mathbb E \left[ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta \right] \nonumber \\
-& = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
-& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\
-& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\ 
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
-\end{align}
-where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$.
-Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
-\[
-\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
-\]
-which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$.
-It is therefore enough to proceed in the proof assuming that $A$ is of the form
-\[
-A = \cup_{j=1}^k (a_j,b_j),
-\]
-with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
-\begin{align*}
-\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
-& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
-\end{align*}
-so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
-\begin{align}
-& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
-{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
-& \times \frac {1} 
-{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
-\label{eq:lemma_J}
-\end{align}
-It follows from Lemma~\ref{lem:bound_intervals_delta} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $4f^2(0)$.  \QEDA \\
-
-We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
-\begin{equation}
-\label{eq:general_messages}
-B_i = \begin{cases}
-X_i \in A_i & 1, \\
-X_i \notin A_i & -1,
-\end{cases} 
-\end{equation}
-where $A_i \subset \mathbb R$ is a Borel measurable set. 
-%Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
-Consider the conditional distribution $P({B^n|\theta})$ of $B^n$ given $\theta$. We have 
-\begin{align}
-P\left( B^n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
-\end{align}
-where $P\left(B_i =1 | \theta, B^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B^n$ with respect to $\theta$ is given by 
-\begin{align}
-I_\theta(B^n) = \sum_{i=1}^n I_\theta (B_i|B^{i-1}),
-\label{eq:fisher_information}
-\end{align}
-where $I_\theta (B_i|B^{i-1})$ is the Fisher information of the distribution of $B_i$ given $B^{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B^{i-1}) \leq 4f^2(0)$.
-The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
-\begin{align*}
-\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(B^n) + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
-& \geq \frac{1}{ 4f^2(0) n + I_0}.
-\end{align*}
-
-\QEDA
-
-\subsection{Proof of Theorem~\ref{thm:sgd}
-\label{proof:thm:sgd}
-}
-The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.
-
-\subsubsection*{Proof of (i)}
-%Specifically, (i) in Theorem~\ref{thm:sgd} 
-Consider the following simplified version of \cite[Thm. 4]{polyak1992acceleration}:
-\begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
-Let 
-\[
-X_i = \theta + Z_i,\quad i=1,\ldots,n,
-\]
-where the $Z_i$s are i.i.d. with zero means and finite variances. Define
-\begin{align}
-\begin{split}
-\theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
-\bar{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
-\end{split}
-\label{eq:Polyak_Juditsky_alg}
-\end{align}
-where in addition, assume the following: 
-\begin{enumerate}
-\item[(i)] There exits $K_1$ such that $\left| \varphi(x) \right| \leq K_1(1+|x|)$ for all $x\in \mathbb R$.
-\item[(ii)] The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions \eqref{eq:conditions1}.
-\item[(iii)] The function $\psi(x) \triangleq \ex{ \varphi(x+Z_1)}$ is differentiable at zero with $\psi'(0)>0$, and satisfies $\psi(0)=0$ and $x\psi(x) >0$ for all $x\neq 0$.
-Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
-\begin{equation}
-\label{eq:Polyak_Juditsky_cond3}
-\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
-\end{equation}
-\item[(iv)] The function 
-$\chi(x) \triangleq \ex{\varphi^2(x+Z_1)}$ is continuous at zero. 
-\end{enumerate}
-Then $\bar{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}({\theta}_n - \theta)$ converges in distribution to $\Ncal(0,V)$, where
-\[
-V = \frac{ \chi(0)} {\psi'^2(0)}. 
-\]
-\end{thm}
-
-Using the notation above, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have that $\chi(x) = \mathbb E \sgn^2(x+Z_1) = 1$, so $\chi(0) = 1$. In addition,
-\begin{align*}
-\psi(x) & = \ex{ \sgn(x+ Z_1) }= \int_{-\infty}^\infty \sgn(x+z) f(z) dz \\
-& = \int_{-x}^\infty f(z) dz -\int_{-\infty}^{-x} f(z) dz. 
-\end{align*}
-Using the symmetry of $f(x)$ around zero, it follows that $\psi'(x) = 2f(x)$ and thus $\psi'(0) = 2f(0)$.
-It is now easy to verify that the rest of the conditions in Theorem~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$.
-Since
-\[
-\frac{\chi(0)}{\psi'^2(0)} = \frac{1}{4 f^2(0)} = \frac{1}{\eta(0)},
-\]
-it follows from Theorem~\ref{thm:polyak_juditsky} that
-\[
-\sqrt{n}\left({\theta}_n-\theta \right) \overset{d}{\to} \Ncal \left(0, 1/ \eta(0)\right). 
-\]
-
-\subsubsection*{Proof of (ii)}
-We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\mathbb R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates.
-Then
-\begin{align}
-\label{eq:sgd_part2}
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
-\end{align}
-under $\Prob_{\theta,n}$.
-Under the assumption that $f(x)$ is continuously differentiable with a finite location Fisher information, the model $\{Z_n+ \theta\}_{n \in \mathbb N}$ is differentiable in quadratic mean \cite[Exm.
-7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
-\[
-\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
-\]
-where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$. 
- The random variable $L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)
-$ is bounded, and hence 
-\[
-\ex{ L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)} \to \ex{L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)}
-\]
-Any regular estimators in a LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}, hence in order to prove (ii) it is left to show that $\bar{\theta}_n$ is regular. For this purpose, 
-we use the following refinement of Theorem~\ref{thm:polyak_juditsky}, proof of which is given in Subsection~\ref{proof:thm:normal_expansion} below.
-%
-\begin{thm} \label{thm:normal_expansion}
-Set $\Delta_i = \theta_i - \theta$ and
-$\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \Delta_i$. Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{thm:polyak_juditsky}, there exists $K_1$ and $\lambda>0$ such that
-\begin{equation}
-\ex{\left| \varphi(Z_1) - \varphi(x+Z_1)  \right|} \leq K_1 |x|^{1+\lambda}
-\label{eq:PJ_additional_cond}. 
-\end{equation}
-Then:
-\begin{itemize}
-\item[(i)] \begin{equation}
-\sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1). \label{eq:normal_expansion_lem}
-\end{equation}
-where $o_{p,n}(1)$ converges in probability to $0$ as $n\to \infty$.
-\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite location Fisher information 
-\[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)} \right)^2 f(x) dx,
-\]
-then for any converging sequence $h_n \to h$,
-\[
-\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-h}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
-\]
-under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h_n/\sqrt{n}}$ with density $\prod_{i=1}^n f(x_i-h_n/\sqrt{n})$.
-\end{itemize}
-\end{thm}
-We now use this theorem to show regularity of $\bar{\theta}_n$. We have, 
-\begin{align*}
-& %\varphi(Z_1) - \varphi(x+Z_1) = 
-\sgn(Z_1) - \sgn(x + Z_1) \\
-& = \begin{cases}
-2 & Z_1 > 0,\, x+Z_1<0, \\
--2 & Z_1 <0, \, x+Z_1>0, \\
-0 & \text{otherwise}. 
-\end{cases}
-\end{align*}
-It follows that
-\begin{align*}
-\ex{ \left| \varphi(Z_1) - \varphi(x+Z_1) \right| }  \leq \Prob\left( |Z_1| < x  \right) \leq f(0) |x|, 
-\end{align*}
-hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
-\[
-\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = -2f(0) = -\psi'(0). 
-\]
-Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}.
-
-\subsubsection*{Proof of (iii)}
-%In order to prove part (ii) of Theorem~\ref{thm:sgd} 
-Consider the following result from \cite{polyak1990new}:
-\begin{thm}{\cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
-Let
-\begin{align} \label{eq:polyak_new_measurements}
-\begin{cases}
-U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = g'(U_{n-1})+Z_n \\
-\bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
-\end{cases}
-\end{align}
-Assume that the function $g(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative.
-In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \mathbb R$.
-Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution with a density for which the Fisher information exits.
-Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{thm:polyak_juditsky}-(iii) and satisfy the conditions there.
-Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$,
-and there exits $K_3$ such that 
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] \leq K_3(1+|x|^4). 
-\]
-Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
-\[
-V_n \triangleq \mathbb E \left[ \left(\bar{U}_n-x^\star \right)^2 \right] = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
-\]
-\end{thm}
-
-We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$. From \eqref{eq:polyak_new_measurements} we have
-\begin{align*} 
-U_n & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
-& = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
-\end{align*}
-so the estimator $\bar{U}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] = 1 \leq K_3(1+|x|^4)
-\]
-for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
-the conditions in Theorem~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
-In particular, $\psi'(0) = (2f(0))^{-2}$.
-Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$.
-Theorem~\ref{thm:polyak_new} implies that for any $\theta \in \mathbb R$,
-\[
-V_n = \mathbb E \left[ \left({\theta}_n-\theta \right)^2 \right]  = \frac{1}{4n f^2(0)} + o(n^{-1}).
-\]
-
-{\color{red}
-
-\subsection{Proof of Theorem~\ref{thm:normal_expansion}
-\label{proof:thm:normal_expansion}
-}
-\subsubsection*{Proof of (i)}
-The proof of part (i) of Theorem~\ref{thm:normal_expansion} requires the following two additional results from \cite{polyak1992acceleration}:
-\begin{lem}{\cite[Lem. 2]{polyak1992acceleration}}
-\label{lem:Polyak_expansion}
-Consider the process $\{\Delta_i^1 \}_{i=0}^\infty$ defined by
-\[
-\Delta^1_i = \Delta^1_{i-1} - \gamma_i (A \Delta_{i-1}+ \xi_i),\quad i=1,2\ldots.
-\]
-Assume that $A>0$ and condition (ii) of Theorem~\ref{thm:polyak_juditsky} holds. Then 
-\begin{equation}
-\label{eq:Polyak_expansion}
-\sqrt{n} \bar{\Delta}_n^1 = \frac{1}{\sqrt{n}}\sum_{i=0}^{n-1} \Delta_i^1 = \frac{\alpha_n \Delta_0^1}{\sqrt{n} \gamma_0}  + \frac{1}{\sqrt{n} A} \sum_{i=1}^{n-1} \xi_i + \frac{1}{\sqrt{n}}\sum_{i=1}^{n-1} w_i^n \xi_i,
-\end{equation}
-where $\alpha_n$ and $w_i^n$ are real numbers such that $|\alpha_n| \leq K$ and $|w_i^n|\leq K$ for some $K< \infty$, and 
-\[
-\lim_{n\to \infty} \frac{1}{n} \sum_{i=1}^{n-1} |w_i^n| = 0. 
-\]
-\end{lem}
-
-\begin{lem} \label{lem:PJ_converging_sum}
-Under the conditions of Theorem~\ref{thm:polyak_juditsky},
-\[
-\sum_{i=1}^\infty \frac{|\Delta_{i}|^{1+\lambda}}{\sqrt{i}} < \infty 
-\]
-almost surely. 
-\end{lem}
-Lemma~\ref{lem:PJ_converging_sum} follows from the proof of Theorem 2 in \cite{polyak1992acceleration}.
-
-We separate the proof of part (i) into two steps.
-\subsubsection*{Step I}
-The expansion \eqref{eq:normal_expansion_lem} holds for the process  $\{\bar{\Delta}^1_i\}_{i=1}^\infty$ defined as follows:
-\begin{align} \label{eq:Polyak_expansion_lem1_alg}
-& \Delta_i^1  = \Delta_{i-1}^1 - \gamma_i \psi'(0) \Delta_{i-1}^1 - \gamma_i \varphi(Z_i), \qquad
- \delta_0^1 = \Delta_0\\
-& \bar{\Delta}^1_i = \frac{1}{n}\sum_{i=0}^{n-1} \Delta^1_i.
-\end{align}
-
-In order to prove this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$.
-The first expression on the RHS on \eqref{eq:Polyak_expansion} goes to zero in variance.
-In addition,
-\begin{align*}
-& \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }  = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
-& = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0. 
-\end{align*}
-We obtain
-\begin{equation}
-\sqrt{n} \bar{\Delta}^1_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1), \label{eq:Polyak_expansion_aux_process}
-\end{equation}
-
-\subsubsection*{Step II} $\bar{\Delta}_n$ and $\bar{\Delta}^1_n$ are asymptotically equivalent. \\
-
-From \eqref{eq:Polyak_Juditsky_alg} and \eqref{eq:Polyak_expansion_lem1_alg}, the difference $\delta_i = \Delta_i - \Delta_i^1$ satisfies the recursion
-\[
-\delta_i = \delta_{i-1} - \gamma_i \psi'(0) \delta_{i-1} + \gamma_i \left( \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i) \right),
-\]
-where $\delta_0 = 0$. Use Lemma~\ref{lem:Polyak_expansion} with $\xi_i =  \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i)$ to obtain
-\begin{align}
-& \sqrt{n}\bar{\delta}_n = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \xi_i  \\
-& = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \label{eq:PJ_proof1} \\
-& + 
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi(\Delta_{i-1})  + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i)
-\right) \label{eq:PJ_proof2}
-\end{align}
-For the term \eqref{eq:PJ_proof1} and using \eqref{eq:Polyak_Juditsky_cond3}, there exists $K_1$ and $K_2$ such that 
-\begin{align*}
-& \eqref{eq:PJ_proof1}
-\leq K_1 \sum_{i=1}^\infty \frac{1}{\sqrt{i}} \left| \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \right| \\
-& \leq K_2 \sum_{i=1}^\infty \frac{ |\Delta_i|^{1+\lambda}}{\sqrt{i}}. 
-\end{align*}
-
-Lemma~\ref{lem:PJ_converging_sum} shows that 
-\begin{align}
-\sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}}  < \infty \label{eq:PJ_converging_sum},
-\end{align}
-hence the Kronecker lemma implies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \to 0.
-\]
-For the term \eqref{eq:PJ_proof2}, set 
-\[
-\epsilon_i \triangleq \psi(\Delta_{i-1}) + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i).
-\]
-For $a>0$ and $n \in \mathbb N$, define the event
-\[
-A_{n,a} \triangleq \left\{ \sum_{i=1}^{n-1} \frac{|\epsilon_i|}{\sqrt{i}}  \geq a  \right\}. 
-\]
-By Markov's inequality, we have
-\begin{align}
-\ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } \leq \frac{1}{a} \sum_{i=1}^{n-1} \frac{ \ex{|\epsilon_i| \Delta_{i-1} \mid }}{\sqrt{i}}. \label{eq:PJ_proof_3}
-\end{align}
-Using \eqref{eq:Polyak_Juditsky_cond3} and \eqref{eq:PJ_additional_cond}, there exists $K'$ and $\lambda'>0$ such that
-\begin{align*}
-& \ex{ |\epsilon_i| | \Delta_{i-1}}  \leq |\psi(\Delta_{i-1})| + \left| \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i) \right|  \\
-& \leq K' |\Delta_{i-1}|^{1+\lambda}. 
-\end{align*}
-Plugging this bound in \eqref{eq:PJ_proof_3} and using Lemma~\ref{lem:PJ_converging_sum},we obtain 
-\[
-\Prob(A_{n,a}) = \ex{ \ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } } \leq  \frac{K''}{a}
-\]
-for some constant $K''$. It follows that for any $\epsilon$, we may choose $a$ large enough such that 
-\[
-\sup_{n} \Prob(A_{n,a}) < \epsilon.
-\]
-This implies that for any $\epsilon>0$,
-\[
-\Prob \left( \sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty \right) \geq 1-\epsilon,
-\]
-and hence 
-\[
-\sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty
-\]
-almost surely. The Kronecker lemma now implies 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left|\epsilon_i\right| \to 0,
-\]
-hence the term \eqref{eq:PJ_proof2} satisfies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right) \epsilon_i \leq \frac{K'''}{\sqrt{n}} \sum_{i=1}^{n-1} |\epsilon_i| \to 0. 
-\]
-This conclude the proof of part (i).
-
-\subsubsection*{Part (ii)}
-Use \eqref{eq:normal_expansion_lem} to write
-\[
-\sqrt{n} \bar{\Delta}_n = G_n + o_{p,n}(1),
-\]
-where
-\[
-G_n \triangleq -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n} \varphi(Z_i). 
-\]
-From \cite[Exm.
-7.8]{van2000asymptotic}, the location model $f(x-\theta)$ with continuously differentiable $f(x)$ is differentiable in quadratic mean with the score function $-f'(x-\theta)/f(x-\theta)$.
-This fact implies the following expansion \cite[Thm.
-7.2]{van2000asymptotic}:
-\begin{align}
-\label{eq:PJ_LAN}
-& \log \frac{\Prob^n_{h_n/\sqrt{n}}}{\Prob^n_0} (Z_1,\ldots,Z_n) =  \log \prod_{i=1}^{n} \frac{f(Z_i-h_n/\sqrt{n})}  {f(X_i-\theta)} = h J_n - \frac{1}{2}h^2 I_{\theta} + o_{p,n}(1),
-\end{align}
-for any converging sequence $h_n \to h$, 
-where 
-\[
-J_n \triangleq -\frac{1}{\sqrt{n}} \sum_{i=1}^n \frac{f'(Z_i)}{f(Z_i)} .
-\]
-We have
-\begin{align*}
-& \ex{ G_n J_n} = \frac{1}{\psi'(0)}\frac{1}{n} \sum_{i=1}^n \ex{ \varphi(Z_i) \frac{f'(Z_i)}{f(Z_i)} }  \\
-& = \frac{1}{ \psi'(0)} \ex{ \varphi(Z_1) \frac{f'(Z_1)}{f(Z_1)}} =  \frac{1}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx , 
-\end{align*}
-Since both $\sqrt{n}G_n$ and $\sqrt{n}J_n$ are the sum of $n$ i.i.d. random variables with zero mean and finite variance, we obtain, from the central limit theorem and Slutsky's theorem, that
-\[
-\left(\sqrt{n} \bar{\Delta}_n, \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} \right) \overset{d}{\to} \Ncal \left( \left(0,-\frac{h^2}{2} I_\theta \right),  \begin{pmatrix}
-\frac{\chi(0)}{\psi'^2(0)} & \frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx \\
-\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx & h^2 I_\theta 
-\end{pmatrix}  \right)
-\]
-Le Cam's third lemma \cite[Exm. 6.7]{van2000asymptotic} implies that under $\Prob^n_{h/\sqrt{n}}$, 
-\[
-\sqrt{n}\bar{\Delta}_n \overset{d}{\to} \Ncal\left(\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx,  \frac{\chi(0)}{\psi'^2(0)} \right).
-\]
-
-\QEDA
-}
-
-\subsection{Proof of Theorem~\ref{thm:LAN1}
-\label{proof:thm:LAN1}
-}
-The log probability mass distribution of $B^n=(B_1,\ldots,B_n)$ is given by
-\begin{align*}
-& \log \Prob_\theta(b^n) = \sum_{i=1}^n \left( \frac{b_i+1}{2} \log  \Prob(X_i\in A_i) + 
-\frac{1-b_i}{2} \log \Prob(X_i\in A_i) \right), \quad b^n \in \{-1,1\}^n. 
-\end{align*}
-Consequently, 
-\begin{align}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) } = \sum_{i=1}^n    \frac{b_i+1}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} + 
-\sum_{i=1}^n  \frac{1-b_i}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}. 
-\label{eq:LAN_proof1}
-\end{align}
-For each $i=1,\ldots,n$, write 
-\[
-A_i = \bigcup_{k=1}^{K_i} \left(t_{i,k},t_{i,k+1} \right),
-\]
-where $t_{i,1}<\ldots<t_{i,K_i}$ and, with a slight abuse of notation, $t_{i,1}$ and $t_{i,K_i}$ may also be $-\infty$ or $+\infty$, respectively. Thus
-\[
-\Prob_{\theta}(X_i \in A_i) = \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta).
-\]
-In particular, since $f$ is differentible, $\Prob_{\theta}(X_i \in A_i)$ is twice differentiable, and we may write
-\begin{align*}
-\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)  = \Prob_{\theta} (X_i \in A_i) + \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \frac{h}{\sqrt{n}} + o(h), 
-\end{align*}
-and thus
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} = \log \left(1 + \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} + o(h) \right) \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2 + o(h^2).
-\end{align*}
-Similarly, we have
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 + o(h^2).
-\end{align*}
-From \eqref{eq:LAN_proof1} we obtain
-\begin{align*}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
-\left( 
-\frac{b_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-b_i}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}   \right) \\
- & - \frac{h^2}{2n} 
- \sum_{i=1}^n 
-\left( 
- \frac{b_i+1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-b_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 \right) + o(h^2) \\
-\end{align*}
-%
-Noting that 
-\[
-\frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} = \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)},
-\]
-the proof is completed by proving the following two claims:
-\begin{itemize}
-\item[I.] 
-For $i=1,\ldots,n$ denote 
-\[
-U_i = \frac{B_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-B_i}{2}  \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}. 
-\]
-Then 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0, \kappa(\theta) \right). 
-\]
-\item[II.]
-For $i=1,\ldots,n$ denote 
-\[
-V_i =  \frac{B_i-1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-B_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2.
-\]
-Then 
-\[
-\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} \kappa(\theta). 
-\]
-\end{itemize}
-\subsubsection*{Proof of Claim I}
-First note that 
-\begin{align*}
-\mathbb E  [U_i] & = 
- \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=1)   + 
- \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=-1)  = 0. 
-\end{align*}
-In addition,
-\begin{align*}
-& \mathbb E U_i^2 = 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2  \Prob (B_i=1)   + 
-\left( \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2 \Prob (B_i=-1) \\
-& =
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)} +  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)} \\
- & =  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left(1-\Prob_{\theta}(X_i \in A_i) \right)} 
-\end{align*}
-Therefore
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 = L_n(A_1,\ldots,A_n) \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ such that the limit above exists.
-We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition for his version of the central limit time: for any $\delta>0$ we have that
-\begin{align*}
-& \mathbb E \left| U_i \right|^{2+\delta} =
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} 
-\end{align*}
-and
-\begin{equation}
-\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} } { \left( \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta} = 
-\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
-\label{eq:Lyaponov}
-\end{equation}
-Next, we claim that there exits $\delta>0$ and $K>0$, that are independent of $n$, such that
-\begin{align}
-\frac{1}{n} \sum_{i=1}^n \mathbb E  |U_i|^{2+\delta}  < M \label{eq:Lyaponov_num}
-\end{align} 
-for all $n$ large enough. To see this, note that
-\begin{align*}
-& \mathbb E |U_i|^{2+\delta} = 
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}  \\
-  &  = \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} } 
-  \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \\
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}, 
-\end{align*}
-where the last transition is because 
-\[
- \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \leq 1. 
-\]
-We now use the fact that each $A_i$ is a finite union of interval and consider the following lemma, proof of which is given in Appendix~\ref{proof:lem:bound_intervals_delta}.
-\begin{lem} \label{lem:bound_intervals_delta}
-Let $f(x)$ be a log-concave, symmetric, and differentiable PDF such that $\eta(x)$ is unimodal.  There exists $\delta>0$ such that for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, 
-\begin{equation}
-\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^{2+\delta} }
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} } 
-\leq  2^\delta f^{2+\delta}(0). 
-\label{eq:lem_bound_intervals_delta}
-\end{equation}
-\end{lem}
-
-Lemma~\ref{lem:bound_intervals_delta} implies 
-\begin{align*}
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} = \frac{\left| \sum_{k=1}^{K_i} (-1)^k f(x_{i,k}-\theta) \right|^{2+\delta} }
-  { \left( \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta} \left( 1 - \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta}} \\
-  & \leq 2^\delta f^{2+\delta}(0). 
-\end{align*}
-In particular, we conclude that 
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} \leq 2^\delta f^{2+\delta}(0), 
-\]
-and thus for any $\delta>0$ the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we conclude that 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0,\kappa(\theta) \right). 
-\]
-
-\subsubsection*{Proof of Claim II} 
-We have:
-\begin{align*}
-\mathbb E V_i  & = 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)}  
-+ 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)}  \\
- & = 
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left( 1-\Prob_{\theta}(X_i \in A_i) \right)}  
-\end{align*}
- We conclude that:
-\begin{equation} \label{eq:LAN_limit_cond}
-\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =   L_n(A_1,\ldots,A_n)  \to \kappa(\theta)
-\end{equation}
-Since the $V_i$s are independent of each other, Kolmogorov's law of large numbers implies
-%(e.g. \cite[Theorem 10.2.3]{sen1994large}) 
-\[
-\frac{1}{n} \sum_{i=1}^n  V_i \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ for which the limit \eqref{eq:LAN_limit_cond} exists.
-
-\QEDA
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals_delta}} 
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-and 
-\[
-\eta_\delta(x) \triangleq  \frac{  \left(\delta_1(x) \right)^{2+\delta}}{  \left(\Delta_1(x)  \right)^{1+\delta}
-(1-\Delta_1(x))^{1+\delta}}
-= \frac{  \left( f (x) \right)^{2+\delta}}{ \left(F(x) \right)^{1+\delta}(1-F(x))^{1+\delta}}. 
-\]
-The proof is by induction on $n$.
-For the case $n=1$ the LHS of \eqref{eq:lem_bound_intervals_delta} equals $\eta_\delta(x)$.
-Note that $\eta_\delta(0) = 2^\delta f^{2+\delta}(0)$, so it is enough to prove that $\eta_\delta(0)$ attains it maximum at $x=0$.
-We have $\eta_\delta(x) = \eta^{1+\delta}(x)/f^\delta(x)$, and thus
-\[
-\log \eta_\delta'(x) = (1+\delta) \frac{\eta'(x)}{\eta(x)} - \delta \frac{f'(x)}{f(x)}. 
-\]
-By Assumption~\ref{assump:failure_rate} both terms above are negative for $x>0$, so that $\log \eta_\delta'(x) \leq 0$ if and only if
-\begin{equation} \label{eq:delta_proof_cond}
-(1+\delta) \left| \frac{\eta'(x)}{\eta(x)} \right| \geq \delta \left| \frac{f'(x)}{f(x)} \right|, \qquad x>0.
-\end{equation}
-Also by Assumption~\ref{assump:failure_rate}, for $x>0$ we have
-\[
-0 > (\log \eta(x))' = \frac{h'(x)}{h(x)}-\frac{h'(-x)}{h(-x)},
-\]
-so that \eqref{eq:delta_proof_cond} is satisfies for $\delta>0$ small enough.
-
-Next, assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^{2+\delta}} 
-{\left(\Delta_n \right)^{1+\delta}\left(1- \Delta_n \right)^{1+\delta} } \leq \eta_\delta(0) = 2^\delta f^{2+\delta}(0) . 
-\label{eq:lem_bound_intervals_delta_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%If $x_{i+1} = x_i$ for some $i=1,\ldots,N-1$, then then the indices $i$ and $i+1$ may  be removed from all sums in \eqref{eq:lem_bound_intervals}, what brings us to the case $n = N-2$.
-Therefore, we may assume that $x_1 < \ldots < x_n$.
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  (2+\delta) \log \delta_N - (1+\delta) \log \Delta_N - (1+\delta) \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{(2+\delta) (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(1+\delta)(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(1+\delta)(-1)^{k+1} f(x_k)}{1-\Delta_N }.
-\]
-We conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero_delta}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N(1+\delta)}{2+\delta} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-From the same reason as in the proof of Lemma~\ref{lem:bound_intervals_delta}, \eqref{eq:gradient_zero_delta} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_delta_proof} equals $\eta_\delta(x_1)$ which was shown to be smaller than $\eta_\delta(\epsilon)$.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_delta_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$,  $x_i, x_{i+1} = -\epsilon$ for some $i$, or $x_i, x_{i+1} = \epsilon$ for some $i$.
-It is therefore enough to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Assume first $x_N \rightarrow -\infty$. Then 
-\begin{align*}
-\frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)^{1+\delta} } ,
-\end{align*}
-which is smaller than $\eta_\delta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
-\begin{align*}
-& \frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right)^{1+\delta} }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^{2+\delta}} 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)^{1+\delta}\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right)^{1+\delta} },
-\end{align*}
-where $x'_{m} = x_{m+1}$ for $m=1,\ldots, N-1$. The last expression is smaller than $\eta_{\delta}(0)$ by the induction hypothesis.  \QEDA \\
-
-\subsection{Proof of Theorem~\ref{thm:non_existence}
-\label{proof:thm:non_existence}
-}
-
-Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta) = \eta(0)$. 
-%
-Since $B_1,B_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, $\theta$ is in $\Xi$ if and only if
-\begin{equation}
-\label{eq:non_existence_proof}
-\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0). 
-\end{equation}
-By assumption, we have $B_i^{-1} = A_i$ where $A_i$ can be expressed as
-\[
-A_i = \cup_{i=1}^K (a_{i,k},b_{i,k}), 
-\]
-where $a_{i,1} \leq b_{i,1} \leq \ldots \leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values $-\infty$ and $\infty$, respectively. Denote
-\[
-\mathcal B_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\}.
-\]
-For any $\theta$ and $\epsilon>0$, denote 
-\[
-S_n(\theta, \epsilon) \triangleq \left\{ i\leq n \,:\, (\theta-\epsilon,\theta+\epsilon) \cap \mathcal B_i \neq \emptyset \right\}
-\]
-In words, $S_n$ contains all integers smaller than $n$ in which an $\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals consisting $A_i$. 
-%
-We now claim that 
-if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. Indeed, for such $\theta$ we have
-\begin{align}
-& L_n(A_1,\ldots,A_n; \theta) \nonumber \\
-& = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
-\frac{ \left(\sum_{k=1}^{K}  f(\theta - b_{i,k})- f(\theta - a_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& 
-+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(b_{i,k}-\theta) - f(a_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& \overset{(a)}{\leq}
-\frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
- \label{eq:non_existence_proof1}
-\end{align}
-where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} and the fact that for $i \in S_n(\theta, \epsilon)$, 
-\[
-\max\left\{ \max_k \eta(b_{i,k}-\theta) , \max_k \eta(a_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
-\]
-Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, \eqref{eq:non_existence_proof1}, and thus $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.
-\par
-For $k\in \mathbb N$, assume by contradiction that there exists $N \geq 2K + 1$ distinct elements
-$\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$ consists of at most $K$ intervals, we have that 
-\begin{equation}
-\label{eq:few_optimality_points_proof}
-\card (\cup_{i=1}^n \mathcal B_i) \leq 2 n K. 
-\end{equation}
-Fix $\epsilon>0$ such that 
-\[
-\epsilon < \frac{1}{2}\min_{i\neq j} |\theta_i - \theta_j|. 
-\]
-Since for each $\theta \in \Theta$ we have $S_n(\theta, \epsilon) \to 1$, there exists $n$ large enough such that 
-\[
-\card \left(S_n(\theta_i, \epsilon) \right) \geq n \left(1-\frac{1}{2N} \right)
-\]
-for all $i=1,\ldots,N$.
-However, $S_n(\theta_1,\epsilon), \ldots S_n(\theta_N,\epsilon)$ are disjoint, so the cardinallity of their union is at least $n\left(1-\frac{1}{2N} \right)N$ which is grater than $2nK + n/2$ in contradiction to \eqref{eq:few_optimality_points_proof}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEfull,onebit}
-
-\end{document}

### 2019-09-23 introduction.tex
Adding a bib file

@@
 estimator $\theta_n$ with finite quadratic risk (mean squared error) $R_n =
-\E_\theta[(\theta_n - \theta)^2]$, letting $\sigma^2 = \var(X)$
-we are interested in particular in the
-limit (assuming it exists)
+\E_\theta[(\theta_n - \theta)^2]$, we study the limit
 \begin{equation}
   \label{eq:ARE_def}
-  \lim_{n\to \infty} \frac{\sigma^2/n}{R_n},
+  \limsup_{n\to \infty} n R_n.
 \end{equation}
-which describes the \emph{asymptotic relative efficiency} (ARE) of this
-estimator compared to an estimator whose variance decreases as
-$\sigma^2/n+o(n^{-1})$. Estimators of this form include the sample mean
-and, under some conditions, the optimal Bayes estimator.
-
-%% JCD: I AM HERE %%
-
-In addition to the examples above, the excess risk in estimating a fixed parameter due to a one-bit per sample constraint is useful in bounding from below the excess risk in estimating signals from thier noisy one-bit quanitzed noisy measurements.
-Specifically, the excess risk or ARE we derive serve as the most optimistic estimate for the risk in estimating under one-bit per measurement constraint signals changing over time or space.
-Such estimation settings are considered in \cite{baraniuk2017exponential, jacques2013robust, plan2013one, li2017channel, choi2016near}.
-\par
+By comparing this quantity to achievable rates of convergence without
+communication constraints, we can evaluate the efficiency
+losses---asymptotic relative efficiency---of the estimator to appropriately
+optimal (unconstrained) estimators. (We shall be more formal in the sequel.)
+By lower bounding the quantity~\eqref{eq:ARE_def}, we also provide limits on
+estimation of single-bit-per-measurement constrained signals in more general
+settings~\cite{baraniuk2017exponential, jacques2013robust, plan2013one,
+  li2017channel, choi2016near}.
 
@@
 
-In setting (i), the estimator can evaluate the optimal mean estimator (e.g., the sample mean in the Gaussian case) and then quantize it using $n$ bits.
-Since the accuracy in describing the empirical mean decreases exponentially in $n$, the error due to quantization is negligible compared to the quadratic risk in estimating the mean \cite{720540}.
-Therefore, the ARE in this setting is $1$.
-Namely, asymptotically, there is no loss in performance due to the communication constraint under centralized encoding.
+In setting (i), the estimator can evaluate any optimal estimator of location
+(e.g., the sample mean if the data is Gaussian), then quantize it using
+$n$ bits. As the accuracy in describing the empirical mean decreases
+exponentially in $n$, the quantization error is negligible compared
+to the statistical error in mean estimation~\cite{720540}. That is,
+centralized encoding induces no asymptotic efficiency loss.
 %
-In this paper we show that a similar result does not hold in setting (ii): the ARE of any adaptive estimation scheme is at most the ARE of the sample median.
-Specifically, when the samples are drawn from the normal distribution, this ARE equals $2/\pi$, showing that the one-bit constraint increases the effective sample size in estimating $\theta$ by at least $\pi/2$ compared to estimating it without the bit constraint.
-We also show that this lower bound on the ARE is tight by providing an estimator that attains it.
-In fact, we show that only one adaptiveness, as illustrated in Figure~\ref{fig:one_round} is enough to achieve the optimal ARE.
+The story is different in settings (ii) and (iii). Precisely, we show that
+in the adaptive setting~(ii), the optimal efficiency of a one-bit scheme is
+(asypmtotically) precisely that of the sample median, and that this
+efficiency is achievable. As a concrete example, when $X_i$ are
+i.i.d.\ Gaussian, we necessarily lose a factor of $\pi/2 \approx 1.57$ in
+the asymptotic risk; the one-bit constraint decreases the effective sample
+size by a factor of $\pi/2$ compared to estimating it without the bit
+constraint. It turns out that, in the settings we consider,
+only a \emph{single round} of adaptivity (see Fig.~\ref{fig:one_round} for
+an illustration) is sufficient to achieve optimal convergence rates.
 %
-Clearly, the penalty on the sample size in setting (iii) is at least as large as that in setting (ii).
-We show, however, that unlike in setting (ii), there is no distributed estimation scheme that is uniformly optimal in the sense that it attains the ARE of the sample median for all $\theta$ in the parameter space.
-This result is obtained by establishing local asymptotic normality of regularly enough encoding procedures for setting (iii), resulting in an exact characterization of the ARE of such procedures.
-To summarize our contributions, we establish that the optimal ARE in settings (i) is $1$, the optimal ARE in setting (ii) is ARE of the sample median, and no uniformly optimal procedure exists in setting (iii).
+In distinction from setting (ii), in setting (iii) when the messages must be
+independent, there is no distributed estimation scheme that achieves the
+efficiency of the sample median uniformly over $\theta$.  We establish this
+result via Le Cam's local asyptotic normality theory, allowing us
+to provide exact characterizations of the asymptotic efficiency
+of suitably regular encoding schemes.
+%% To summarize our
+%% contributions, we establish that the optimal ARE in settings (i) is $1$, the
+%% optimal ARE in setting (ii) is ARE of the sample median, and no uniformly
+%% optimal procedure exists in setting (iii).
 
@@
 
-It is important to note that although the ARE in setting (i) is one, this scheme already poses a non-trivial challenge for the design and analysis of optimal encoding and estimation procedures.
-Indeed, representing an unknown random quantity using $n$ bits is equivalent to designing a $2^n$ levels scalar quantizer \cite{gray1998quantization}.
-However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation problem and hence its exact value is unknown.
-As a result, a non-trivial exploration-exploitation trade-off arises even in setting (i).
-%Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$. 
-Therefore, while uncertainty due to quantization decreases exponentially in the number of bits $n$, hence the ARE is $1$, it is still difficult to derive an exact expression for the MSE in this setting.
+Our asymptotic setting is important in that it allows us to elide
+difficulties present in finite sample settings. For example, in setting~(i),
+developing an optimal quantizer at finite $n$ requires choosing a $2^n$
+level scalar quantizer, which is non-trivial~\cite{gray1998quantization}.
+In interactive and sequential settings (e.g.~(ii)), the situation is more
+challenging, as it is unclear whether any type of compositionality applies,
+in that an $n-1$-step optimal estimator may be only vaguely related to the
+$n$-step optimal estimator. Thus, to provide our lower bounds, we rely on
+stronger information-based inequalities, including the Van Trees
+inequality~\cite{Tsybakov09} and Le Cam's local asymptotic normality
+theory~\cite{LeCam86,LeCamYa00,VanDerVaart98}.
+
+%% It is important to note that although the ARE in setting (i) is one, this
+%% scheme already poses a non-trivial challenge for the design and analysis of
+%% optimal encoding and estimation procedures. Indeed, representing an unknown
+%% random quantity using $n$ bits is equivalent to designing a $2^n$ levels
+%% scalar quantizer \cite{gray1998quantization}. However, the optimal design of
+%% this quantizer depends on the distribution of its input, which is the goal
+%% of our estimation problem and hence its exact value is unknown. As a result,
+%% a non-trivial exploration-exploitation trade-off arises even in setting (i).
+%% %Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$. 
+%% Therefore, while uncertainty due to quantization decreases exponentially in
+%% the number of bits $n$, hence the ARE is $1$, it is still difficult to
+%% derive an exact expression for the MSE in this setting.
 %
-The situation is even more involved in the adaptive encoding setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$ may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
+%% The situation is even more involved in the adaptive encoding setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$ may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
 Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $n-1$ messages, is not guaranteed to be globally optimal.
@@
 \subsection*{Related Works}
-When the variance $\sigma^2$ is negligible compared the to desired accuracy, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is solved by a bisection style method over the parameter space.
-Therefore, the general case of non-zero variance is reminiscent of the noisy binary search problem with a possibly infinite number of unreliable tests \cite{cicalese2002least, Karp:2007:NBS:1283383.1283478}.
-However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a constant input corrupted by Gaussian noise.
-Using an SDM, Wong and Gray \cite{53738} showed that the output of the modulator converges to the true constant input almost surely, so that an SDM provides a consistent estimator for setting (ii).
-The rate of this convergence, however, was not analyzed and cannot be derived from the results of \cite{53738}.
-In particular, our results for setting (ii) imply that the asymptotic rate of convergence of the MSE in SDM to a constant input under an additive white Gaussian noise is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-Baraniuk et.
-al \cite{baraniuk2017exponential} also considered adaptive one-bit measurements in the context of analog-to-digital conversion, although without noise at the input.
-By establishing the lower bound of $\sigma^2\pi/2n$ on the MSE, we show that the main results of \cite{baraniuk2017exponential}, an exponential MSE decaying rate, does not hold in the noisy setting.
-Stated otherwise, the MSE in the setting of \cite{baraniuk2017exponential} may decay exponentially up to the noise level, after which it decays at most as $\sigma^2\pi/2n$.
-\par
+
+When the variance $\sigma^2$ is negligible compared the to desired accuracy,
+the task of finding $\theta$ using one-bit queries in the adaptive setting
+(ii) is solved by a bisection style method over the parameter
+space. Therefore, the general case of non-zero variance is reminiscent of
+the noisy binary search problem with a possibly infinite number of
+unreliable tests \cite{cicalese2002least,
+  Karp:2007:NBS:1283383.1283478}. However, since we assume a continuous
+parameter space, a more closely related problem is that of one-bit
+analog-to-digital conversion of a constant input corrupted by Gaussian
+noise. Using an SDM, Wong and Gray \cite{53738} showed that the output of
+the modulator converges to the true constant input almost surely, so that an
+SDM provides a consistent estimator for setting (ii). The rate of this
+convergence, however, was not analyzed and cannot be derived from the
+results of \cite{53738}. In particular, our results for setting (ii) imply
+that the asymptotic rate of convergence of the MSE in SDM to a constant
+input under an additive white Gaussian noise is at most $\sigma^2\pi/2$ over
+the number of feedback iterations. Baraniuk et. al
+\cite{baraniuk2017exponential} also considered adaptive one-bit measurements
+in the context of analog-to-digital conversion, although without noise at
+the input. By establishing the lower bound of $\sigma^2\pi/2n$ on the MSE,
+we show that the main results of \cite{baraniuk2017exponential}, an
+exponential MSE decaying rate, does not hold in the noisy setting. Stated
+otherwise, the MSE in the setting of \cite{baraniuk2017exponential} may
+decay exponentially up to the noise level, after which it decays at most as
+$\sigma^2\pi/2n$. \par
 %

### 2019-09-23 onebit_full.tex
Adding a bib file

@@
 
-\usepackage{mathptmx} 
-\usepackage{times} 
-\usepackage{amsmath} 
-\usepackage{amsbsy} 
-\usepackage{amssymb}
-
-%\usepackage{newtxtext, newtxmath}
-\usepackage{mathrsfs}
-\usepackage{comment}
-\usepackage[export]{adjustbox}
-\usepackage{tikz}
-\usetikzlibrary{external,positioning,decorations.pathreplacing,shapes,arrows,patterns}
-
-\usepackage[hidelinks]{hyperref}
-%\tikzexternalize[mode=list and make]
-\usepackage{algorithmicx}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage{pstool}
-\usepackage[latin1]{inputenc}
-\usetikzlibrary{arrows,shapes}
-\usepackage{xifthen}
-\usepackage{epic}
-%\usepackage{caption}
-\usepackage{epstopdf}
-
-\newtheorem{thm}{\bf{Theorem}}
-\newtheorem{cor}[thm]{\bf {Corollary}}
-\newtheorem{lem}[thm]{\bf {Lemma}}
-\newtheorem{prop}[thm]{\bf {Proposition}}
-\newtheorem{example}{\bf {Example}}
-\newtheorem{definition}{\bf {Definition}}
-\newtheorem{rem}{\bf {Remark}}
-\newtheorem{assump}{\bf {Assumptions}}
-
-\newcommand{\ex}[1]{\ensuremath{\mathbb{E}\left[ #1\right]}}
-
-\newcommand{\Var}[1]{\ensuremath{\mathrm{Var} \left[ #1\right]}}
-
-\newcommand{\unif}{\mathsf{unif}}
-\newcommand{\card}{\mathrm{card}}
-\newcommand{\ARE}{\mathsf{ARE}}
-\newcommand{\supp}{\mathrm{supp} }
-\renewcommand\vec[1]{\ensuremath\boldsymbol{#1}}
-\newenvironment{proof}{\paragraph*{Proof}}{\hfill$\square$ \newline}
-\newcommand{\sgn}{\mathrm{sgn} }
-\newcommand{\Prob}{\mathbb{P} }
-\newcommand{\argmax}{\mathrm{argmax}}
-\newcommand*{\QEDA}{\hfill\ensuremath{\square}}
-\newcommand{\CEO}{\mathsf{CEO}}
-\newcommand{\Ncal}{\mathcal{N}}
-
-\newcommand{\enc}{\mathsf{enc}}
-\newcommand{\est}{\mathsf{est}}
-
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-\tikzstyle{sint}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.8cm,thick ]
-\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
-\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
-\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.7cm,thick ]
-\tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
+\usepackage{macros}
 
@@
 
-\section{Problem Formulation \label{sec:problem}}
+\input{problem-formulation}
 
-Let $f(x)$ be a symmetric and log-concave density function with a finite second moment $\sigma^2$.
-For $\theta \in \Theta$, denote by $P_X$ the probability distribution with density $f\left( x-\theta \right)$.
-Therefore, $P_X$ is an absolutely continuous log-concave distribution with mean $\theta$ and variance $\sigma^2$.
-Symmetry and log-concavity of $f(x)$ imply that $P_X$ is strongly unimodal (has a unique local maxima) with its mode at $x =\theta$ \cite{ibragimov1956composition}.
-We further assume that the \emph{parameter space} $\Theta$ is a closed interval of the real line.
-\par
-In some situations it is useful to assume that $\theta$ is drawn once from the prior distribution $\pi$ on $\Theta$.
-In this case we assume that $\pi$ is an absolutely continuous distribution, and denote its density by $\pi(\theta)$, i.e., $\pi(d\theta) = \pi(\theta)d\theta$.
-\par
-The random variables $X_1,\ldots,X_n$ represent $n$ independent samples from $P_X$. 
-We are interested in estimating $\theta$ from a set of $n$ binary messages $B_1,\ldots,B_n$, obtained from $X_1,\ldots,X_n$ under three possible scenarios illustrated in Figure~\ref{fig:setup}: 
-\begin{itemize}
-\item[(i)~~] Centralized $B_i(X_1,\ldots,X_n)$, $i=1,\ldots,n$.
-\item[(ii)~] Adaptive $B_i(X_i,B_1,\ldots,B_{i-1})$, $i=2,\ldots,n$.
-\item[(iii)] Distributed $B_i(X_i)$, $i=1,\ldots,n$.
-\end{itemize}
+\input{preliminaries}
 
-The performance of an estimator ${\theta}_n \triangleq {\theta}_n(B^n)$ in any of these cases is measured according to the quadratic risk:
-\begin{equation}
-\label{eq:error_def}
-R_n \triangleq \mathbb E\left({\theta}_n - \theta \right)^2,
-\end{equation}
-where the expectation is taken with respect to the distribution of $X_1,\ldots,X_n$ and, whenever available, a prior distribution $\pi(\theta)$ over $\Theta$.  
-%It is well known that minmax estimation error 
-%\begin{equation}
-%R_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left({\theta}_n - \theta \right)^2 | \theta \right],
-%\end{equation}
-%can be obtained from $R_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}. 
-%
-The main problems we consider in this paper are the minimal value of \eqref{eq:error_def}, as a function of $n$ and $f(x)$, under different choices of the encoding functions in cases (i), (ii), and (iii).
-\par
+%% \input{adaptive-estimation}
 
-We give particular attention to the ARE of estimators with respect to an asymptotically normal efficient estimator that is not subject to the bit constraint.
-Specifically, let $\{a_n,\,n\in \mathbb N\}$ be a sequence such that
-\[
-\sqrt{a_n}\left({\theta}_n - \theta\right) \overset{d}{\longrightarrow} \Ncal(0, \sigma^2).
-\]
-Then the ARE of ${\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
-\[
-\ARE({\theta}_n) \triangleq
-\lim_{n\rightarrow \infty} \frac{a_n}{n}. 
-\]
-Note that in the special case where there exists $V \in \mathbb R$ such that
-\[
-a_n \mathbb E \left({\theta}_n - \theta \right)^2 = V + o(1),
-\]
-with $o(1)\to 0$ as $n\to \infty$, then the ARE of ${\theta}_n$ is finite and equals $\sigma^2/V$. \par
+%% \input{distributed-estimation}
 
-In addition to the notation above, we also denote by $F(x)$ the cumulative distribution function of $X_i$, and define
-\begin{equation} \label{eq:eta_def}
-\eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))} =  \frac{f(x)f(-x)}{F(x)F(-x)}, 
-\end{equation}
-where the last equality is due to symmetry of $f(x)$. We note that 
-\begin{equation}
-\label{eq:eta_h}
-\eta(x) = h(x)h(-x) = f(x) \left( h(x) + h(-x) \right), 
-\end{equation}
-where 
-\[
-h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
-\]
-is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function since $f(x)$ is log-concave \cite{bagnoli2005log}. 
-%
-For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as illustrated in Fig.~\ref{fig:eta}. 
-%
-In this paper we only consider the normal distribution and other log-concave symmetric distributions for which this property of $\eta(x)$ holds. Specifically, we require the following:
-\begin{assump} \label{assump:failure_rate}
- $\eta(x)$ has a unique maximum (at the origin) and is a non-increasing function of $|x|$. 
-\end{assump}
-%That is, Assumption~\ref{assump:failure_rate} says that $\eta'(x) < 0 $ for all $x>0$. 
-Under this assumption we have, 
-\[
-4f^2(x) \leq \eta(x) \leq \eta(0),
-\] 
-%
-where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median.
-Combined with log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that $\eta(x)$ vanishes as $|x|\rightarrow \infty$.
-\par
-%
-Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions).
-Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.\par
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -3, xmax=3, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.9,
-samples=10, 
-xlabel= $x$,
-xtick={-2,-1,0,1,2},
-xticklabels={-2,-1,0,1,2},
-ytick={0,0.3989423,0.6366198},
-yticklabels={0,$\frac{1}{\sqrt{2 \pi}}$,$2/\pi$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\eta(x)$};
-\addplot[domain = -5:5, samples = 50, color = red, solid, smooth]  {exp(-x^2/2) / sqrt(2*3.14159)};
-\addlegendentry{$\phi(x)$};
-\addplot[domain = -5:5, samples = 50, color = black, solid, dashed]  {4*exp(-x^2) / (2*3.14159)};
-\addlegendentry{$4\phi^2(x)$};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -4, xmax=4, 
-restrict y to domain = -10:0,
-ymin = -10,
-samples=10, 
-xlabel= $x$,
-xtick={-3,-2,-1,0,1,2,3},
-xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,-0.45158,-0.919},
-yticklabels={0,,},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\log \eta(x)$};
-\addplot[domain = -5:5, samples = 30, color = red, solid, smooth]  {-(x)^2/2 -0.9189};
-\addlegendentry{$\log \phi(x)$};
-\end{axis}
-\end{tikzpicture}
-\caption{
-The function $\eta(x) = f^2(x) / F(x)F(-x)$ for $f(x) = \phi(x)$ the standard normal density.
-\label{fig:eta}
-}
-\end{center}
-\end{figure}
-
-\section{Consistent Estimation and Off-the-shelf Bounds \label{sec:preliminary}}
-%
-In this section we adapt known results to derive lower and upper bounds on the relative efficiency under setting (iii). These bounds establish the following facts:
-\begin{itemize}
-\item[I.] A consistent estimator with an asymptotically normal distribution always exists in setting (iii), and hence in setting (ii). 
-\item[II.] For the normal distribution, the ARE in setting (iii) is at most $3/4$. Namely, under setting (iii), all estimators are strictly inferior compared to the sample mean. 
-\end{itemize}
-
-\subsection{Consistent Estimation}
-Fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
-\[
-B_i = \mathbf 1_{X_i>\theta_0}, 
-\]
-where $\mathbf 1_A$ is the indicator of the event $A$. We have
-\[
-P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
-\]
-so that 
-\begin{equation}
-\label{eq:estimator_naive}
-{\theta}_n = \theta_0 + F^{-1}\left( P_n \right)
-\end{equation}
-is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set due to log-concavity.
-Furthermore, the variance of $P_n$ is $F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)$, and hence the delta method implies that ${\theta}_n$ is asymptotically normal with variance
-\begin{equation} 
- \frac{F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}{f^2(\theta-\theta_0)} = \frac{1}{
-\eta(\theta-\theta_0)}.
-\end{equation}
-In particular, the ARE of ${\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
-In other words, for a prescribed accuracy, ${\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
-\par
-%
-%
-Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of ${\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
-This ARE is attained only when $\theta_0 = \theta$, whereas $\theta$ is apriori unknown.
-Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of ${\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
-As an example, when $f(x)$ is a normal density, the ARE of ${\theta}_n$ is less than $\approx 0.14$ when $\theta_0$ is $2$ standard deviations from $\theta$.
-Therefore, the estimator ${\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
-\par
-It is suggested that we can attain lower variance in estimation by updating the threshold value $\theta_0$ in \eqref{eq:estimator_naive} after observing one or a batch of the single bit messages.
-Schemes with such adaptation fall within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
-\par
-
-\subsection{Multiterminal Source Coding \label{sec:ceo}}
-The CEO setting considers the estimation of a sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_i$ is available at $n$ terminals.
-At each terminal $i$, an encoder observes the $k$ noisy samples
-\[
-X_{i,j} = \theta_j + Z_{i,j},\qquad j=1,\ldots,k, \qquad i = 1,\ldots,n,
-\]
-and transmits $r_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates ${\theta}_1,\ldots,{\theta}_k$ with the goal of minimizing the quadratic risk:
-\[
-R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - {\theta}_j \right)^2 \right]. 
-\]
-Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $r_1=\ldots=r_n = 1$.
-It follows that, assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
-%
-Consequently, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the minimal MSE in the CEO setting as $k \to \infty$.
-Note that the difference between the CEO setting and ours lays in the privilege of each of the encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realizations, rather than a single realization using a single bit in ours.
- \par
-When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k$ goes to infinity were fully characterized in \cite{prabhakaran2004rate}.
-Furthermore, the work of \cite{chen2004upper} provided an expression for quadratic risk attained in the CEO setting under Gaussian priors.
-Adapting to our setting, this expression provides the following proposition:
-\begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is arbitrary.
-Then any estimator ${\theta}_n$ of $\theta$ in the distributed setting satisfies
-\begin{equation} \label{eq:ceo_bound}
- n \ex{\left( \theta - \theta_n \right)^2} \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
-\end{equation}
-where the expectation is with respect to $\theta$ and $X^n$.
-\end{prop}
-
-\begin{proof}
-See Appendix~\ref{app:proof:prop_ceo_lower_bound}.
-\end{proof}
-
-From the formulation of the CEO problem, it follows that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is attributed to the ability to perform coding over blocks.
-Namely, each encoder in the CEO setting may encode an arbitrary number of $k$ independent realizations of $\theta$ using $k$ bits, versus only one realization with one bit in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product probability space that distinguishes between the CEO problem with one bit per encoder on average and the mean estimation problem from one-bit measurements in the distributed setting.
-
-\section{Adaptive Estimation \label{sec:sequential}}
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $\eta(0)\sigma^2$, which is the ARE of the median of the sample $X_1,\ldots,X_n$.
-We also provide a particular adaptive estimation scheme that attains this maximal efficiency.
-%Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $B_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages.
-%Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $\eta(0)\sigma^2$.
-
-\subsection{Limited efficiency in the adaptive setting}
-Our first result asserts that the ARE of any adaptive encoding and estimation scheme is bounded from above by $\eta(0)\sigma^2$. %This result follows from the following theorem:
-\begin{thm}[maximal relative effeciency] \label{thm:adpative_lower_bound}
-Let ${\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Figure~\ref{fig:setup}-(ii). Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-n\mathbb E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0},
-\]
-where 
-\[
-I_0 = \mathbb E \left( \frac{d}{d\theta} \log \pi (\theta) \right)^2
-\]
-is the Fisher information with respect to a location model in $\theta$. 
-\end{thm}
-
-\subsubsection*{Proof}
-%We first bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
-The result then follows using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are in
-See Appendix~\ref{proof:thm:adpative_lower_bound}.\par
-
-Theorem~\ref{thm:adpative_lower_bound} implies that any estimator ${\theta}_n$ from any adaptive encoding scheme satisfies
-\[
-n\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{1}{4f^2(0)}+O(n^{-1}),
-\]
-and 
-\[
-\ARE({\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
-\]
-It is possible to extend Theorem~\ref{thm:adpative_lower_bound} to any other loss functions using a more subtle version of the Van Tress inequality provided in \cite{efroimovich1980information}.
-See also \cite{DBLP:journals/corr/abs-1902-08582}.
-\par
-%
-Next, we provide an adaptive encoding and estimation scheme that attains the maximal ARE of $\eta(0)\sigma^2$.
-
-\subsection{Asymptotically optimal estimator}
-Let $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ be a strictly positive sequence. Consider the following estimator ${\theta}_n$ for $\theta$:  
-\begin{equation}
-\label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n B_n, \quad n = 1,2,\ldots,
-\end{equation}
-where 
-\begin{equation}
-B_n = B_n (X_n,\theta_{n-1}) =\sgn (X_n - \theta_{n-1}).
-\end{equation}
-Define the $n$th step estimation as
-\begin{equation} \label{eq:sgd_est}
-\bar{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
-\end{equation}
-
-We have the following results:
-\begin{thm} \label{thm:sgd}
-Consider the sequence $\left\{\bar{\theta}_n \right\}_{n\in \mathbb N}$ defined by \eqref{eq:sgd_est}. 
-\begin{enumerate}
-\item[(i)] Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions1}
-\begin{cases}
-\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
-\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
-\mathrm{for~some~}0< \lambda \leq 1
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Then
-\[
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left(0,\frac{1}{\eta(0)}\right).
-\]
-%
-%
-\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with a finite location Fisher information, namely
-\[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)}  \right)^2 f(x) dx < \infty.
-\]
-%(or that $f(x-\theta)$ is differentiable in quadratic mean).  
-Then for any bounded, symmetric, and quasi-convex function $L$, 
-\begin{align} 
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
-\\
-& \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
-\end{align}
-where $Z \sim \Ncal(0,1)$. 
-%
-%
-\item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions2}
-\begin{cases}
-\gamma_n = o(n^{-2/3}), &  \\
-\sum_{n=1}^\infty \gamma_n = \infty.  & \\
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ with $\beta \in (2/3,1)$). Then
-\[
- \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{n\eta(0)} + o(n^{-1}). 
-\]
-\end{enumerate}
-\end{thm}
-
-\subsubsection*{Proof}
-See Appendix~\ref{proof:thm:sgd}. \par
-
-Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the maximal ARE, as established by Theorem~\ref{thm:adpative_lower_bound}.
-%Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$.
-%
-The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$.
-Consequently, the procedure above is known as averaged stochastic gradient descent for minimizing $x \to |x|$ given the data $X_1,\ldots,X_n$.
-The minimal value of this optimization is the sample median, and Theorem~\ref{thm:sgd} provides conditions for the sequence of gradient steps so that the algorithm converges to this minimum.
-In particular, parts (i) and (ii) of Theorem~\ref{thm:sgd} provides conditions under which $\bar{\theta}$ is asymptotically normal and local asymptotically minimax, in the sense that it attains the local asymptotic minimax bound \cite{van2000asymptotic}.
-Part (iii) provides an additional condition under which $\bar{\theta}$ also converges in its second moment.
- \par
-%Note that $\theta_0$ is not explicitly defined in equation \eqref{eq:sgd_est}.
-A reasonable initialization for $\theta_0$ is $\theta_0 = \mathbb E [\theta]$, although Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
-Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$.
-\\
-In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $B_n$ depends on its private sample as well as the current gradient descent estimate $\theta_{n-1}$.
-In this sense, each encoder in this algorithm interacts with previous one by using the current estimate.
-%
-As we explain next, 
-it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ with only one round of interactions among the encoders.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
-% \node[below of = source, node distance = 1cm] (source2) {$X_2$};
-%\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};  
-%\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};
-
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[below of = source, node distance = 0.5cm] {$\vdots$};
-
-\node[int1, right of = enc3, node distance = 2.1cm ] (est) {$\est_1$};
-
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
-
-%\draw[->,line width = 2pt] (enc2) -| node[above, xshift = -1cm] (mes2) {$B_2$} (est);
-
-\draw[->,line width = 2pt] (enc3) -- node[above, xshift = 0cm]  {$B_{n_1}$} (est);
-
-\node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
-\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {$\enc$};  
-\draw[->,line width = 2pt] (sourceB) -- (enc1B);
-
-\node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
-\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {$\enc$};  
-\draw[->,line width = 2pt] (source3B) -- (enc3B); 
-\node[below of = sourceB, node distance = 0.4cm] {$\vdots$};
-
-\node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {$\est_2$};
-
-\draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.5cm] {$B_{n_1+1}$} (estB);
-\draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);
-
-\draw[->,line width = 1pt] (est.east) node[above, xshift  =0.5cm] {${\theta}_{n_1}$} -| (enc1B.north);
-
-%\draw[->,line width = 1pt] (enc1B) -- (enc3B);
-
-\draw[->,line width = 0.5pt] (est.east) -| +(1.3,-0.5) -- +(1.3,-2.5) -| (enc3B.north);
-
-%\draw[->,line width = 1pt] (enc1B)  -- node[right] {${\theta}_{n_1}$} (enc3B);
-
-\draw[->,line width = 0.5pt] (estB) -- +(0.8,0) node[right] {${\theta}_n$};
-\node[below of = enc1B, node distance = 0.5cm] {$\vdots$};
-
-\end{tikzpicture}
-\end{center}
-\caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
-\label{fig:one_round}
-}
-\end{figure}
-
-\subsection{Maximal Efficiency using One Round of Threshold Adaptation}
-In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
-\[
-B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
-\]
-and deduced that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
-%
-We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ based on previously observed bits at least once.
-%
-In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
-We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate ${\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use ${\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$.
-Figure~\ref{fig:one_round} illustrates a diagram of this procedure.
-%
-The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
-\begin{thm}
-For $i=1,\ldots,n$ set
-\[
-B_i = \begin{cases}
- \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
- \mathbf 1_{X_i \geq {\theta}_{n_1} }& i={n_1+1,\ldots,n},
-\end{cases}
-\]
-where $n = n_1+ n_2$ and 
-\[
-{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
-\frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
- \right).
-\] 
-Let 
-\[
-{\theta}_{n_2}  = {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
-\]
-and assume that $n_1(n) \rightarrow \infty$ and $n_1(n)/n \rightarrow 0$. Then:
-\begin{align*}
- \sqrt{n} \left( {\theta}_{n_2} - \theta  \right) \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
-\end{align*}
-\end{thm}
-%
-%
-\begin{proof}
-For $t\in \mathbb R$, set
-\[
-p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
-\]
-From the central limit theorem
-\begin{align*}
-& \sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)  = \sqrt{\frac{n}{n_2}} \sqrt{n_2} \left(  p_{n_2}(t) - F(\theta - t) \right) \\
-& \overset{d}{\rightarrow} \Ncal\left( 0, V(t) \right),
-\end{align*}
-where
-\[
-V(t) \triangleq F(\theta - t) F \left( t - \theta\right). 
-\]
-Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ implies
-\begin{align*}
-& \sqrt{n} \left( t + F^{-1}(\hat{p}_{n_2}(t)) - \theta \right) \\
-&= \sqrt{n} \left( g(\hat{p}_{n_2}(t)) - g \left(F(\theta-t) \right)  \right) \\
-& \overset{d}{\to} \Ncal\left(0, 
-1/\eta(\theta-t) \right).
-\end{align*}
-%where this convergence is uniform in $t$ since all moments of $F^{-1}(\hat{p}_{n_2})$ exists. 
-On the other hand, by the law of large numbers,
-\[
-p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
-\]
-so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity and thus 
-\[
-\eta( {\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
-\]
-Finally,
-\begin{align*}
-& \sqrt{n}\left({\theta}_{n_2} - \theta\right) \\
-& = \sqrt{n} \left( {\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}({\theta}_{n_1})) - \theta \right)  \\
-& \overset{d}{\to} \Ncal\left( 0, 
-1/\eta(0) \right) 
-\end{align*}
-by Slutsky's theorem.
-\end{proof}
-%
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=10cm, height=6cm,
-xmin = 0, xmax=800, 
-restrict y to domain = 0:3,
-ymin = 0,
-ymax = 3.4,
-samples=10, 
-xlabel= $n$,
-ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
-%xtick={-3,-2,-1,0,1,2,3},
-%xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,1,1.57},
-yticklabels={0,1,$\pi/2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-
-\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{asymptotically optimal};
-
-%\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
-
-\addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{single interaction};
-
-\end{axis}
-\end{tikzpicture}
-%\begin{tikzpicture}
-%\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
-%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left({\theta}_n - \theta \right)^2$};
-%\node[scale = 0.7] at (0,-2.4) {$n$};
-%\end{tikzpicture}
-\caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.
-In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$.
-The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage.
-\label{fig:adaptive_error}  }
-\end{center}
-\end{figure}
-
-\section{Distributed Estimation \label{sec:distributed}}
-In this section, we now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii) where  each one-bit message $B_i$ is only a function of its private sample $X_i$.
-In this case, the $i$th encoder is fully characterized its \emph{detection region}, defined as
-\[
-A_i = \left\{ x \in \mathbb R \,:\, B_i(x) = 1 \right\}.
-\]
-Consequently, $B_i$ is of the form
-\[
-B_i = \begin{cases} 1 & X_i \in A_i, \\
--1 & X_i \notin A_i,
-\end{cases} \quad i\in \mathbb N,
-\]
-where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\par
-
-As a first step, we provide conditions under which the messages $B_1,B_2,\ldots$ define a local asymptotic normal family.
-
-\begin{thm} \label{thm:LAN1}
-For $n \in \mathbb N$ and $A_n \subset \mathbb R$,  define
-\begin{equation}
-\label{eq:precision_general}
-L_n(A_1,\ldots,A_n;\theta) \triangleq \frac{1}{n} \sum_{i=1}^n \frac{ \left(\frac{d}{d \theta} \Prob(X_i \in A_i) \right)^2 }{ \Prob(X_i \in A_i)\left(1- \Prob(X_i \in A_i) \right) }. 
-\end{equation}
-Consider the following conditions:
-\begin{itemize}
-\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is a log-concave, differentiable and symmetric density function such that $\eta(x)$ is unimodal.
-\item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
-\item[(iii)] The limit 
-\begin{equation}
-\label{eq:LAN_lim}
-\kappa(\theta) \triangleq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
-\end{equation}
-exists. 
-\end{itemize}
-For $i=1,\ldots,n$ set
-\[
-B_n = \begin{cases} 1 & X_n \in A_n, \\
--1 & X_n \notin A_n. 
-\end{cases} 
-\]
-For any $\theta$, $f(x)$ and a sequence of sets $A_1,A_2,\ldots$ such that (i)-(iii) hold, and any $h\in \mathbb R$, we have
-\begin{align*}
-& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (B_1,\ldots,B_n) }{
-\mathbb P_{\theta} (B_1,\ldots,B_n)} \\
-& \overset{d}{\longrightarrow} \Ncal\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
-\end{align*} 
-\end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:LAN1}. 
-\end{proof}
-
-Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}. 
-%
-Among these conditions, (iii) is arguably the strongest and hardest to verify.
-As we show in Section~\ref{subsec:threshold} below, this condition is satisfied, for example, when $A_1, \ldots,A_n$ are half lines whose starting points are drawn independently from some probability measure on $\mathbb R$.
-Similar ideas imply that condition (iii) holds whenever we choose the intervals consisting each $A_i$ according to some pre-specified distribution.
-\par
-%
-An important conclusion of  Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models \cite{van2000asymptotic}):
-\begin{cor} \label{cor:LA_minimax}
-Let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
-Then for any symmetric and quasi-convex function $L$,
-\begin{align*}
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right]
-\\
-& \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
-\end{align*}
-where $Z \sim \Ncal(0,1)$. In particular, for $L(x) = x^2$,
-\begin{align*}
-\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( {\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
-\end{align*}
-\end{cor}
-%
-Corollary~\ref{cor:LA_minimax} says that when the messages define a LAN model, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model at $\theta$.
-This fact poses the upper bound of $\kappa(\theta)\sigma^2$ for the ARE of estimators in such models.
-\par
-
-Next, we show that under LAN no estimator can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly for all $\theta \in \Theta$.
-
-\subsection{Non-existence of a Uniformly Optimal Strategy}
-We now show that under LAN models, the optimal minimal risk $1/\eta(0)$ can only be attained at a finite number of points within $\Theta$.
-This fact implies in particular that, unlike in the adaptive setting, no distributed estimation scheme has ARE of $\eta(0)\sigma^2$ for all $\theta \in \Theta$.
-
-\begin{thm} \label{thm:non_existence}
-Under conditions (i)-(iii) in Theorem~\ref{thm:LAN1}, assume that each $A_i$ is a union of at most $K$ intervals.
-The number of points $\theta \in \Theta$ satisfying $\kappa(\theta) = \eta(0)$ is at most $2K$.
-\end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:non_existence}.
-\end{proof}
-
-We next consider the case where each detection region is a half-open interval, i.e., the $i$th message is obtained by comparing $X_i$ against a single threshold.
-As we explain next, the existence of a density for the sequence of thresholds is enough to establish local asymptotic normality and leads to a closed form expression for the precision parameter and the ARE.
-
-%In the adaptive setting, it follows from Theorem~\ref{thm:sgd} that messages of this kind with appropriately chosen thresholds lead to an estimator with the optimal ARE of $\eta(0)sigma^2$.
-However, Theorem~\ref{thm:non_existence} implies that such ARE can only be attained for a negligible subset of the parameter space.
-As we shall see next, messages obtained via a comparison against a sequence of thresholds cannot attain the optimal efficiency one more than a single point of $\Theta$.
-
-\subsection{Threshold Detection \label{subsec:threshold}}
-Assume now that each $B_i$ is of the form
-\begin{equation}
-\label{eq:threshold_message}
-B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
--1 & X_i > t_i,
-\end{cases}  
-\end{equation}
-where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder.
-In other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and $\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$.
-It follows that
-\begin{equation}
-L_n(A_1,\ldots,A_n;\theta) = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
-\label{eq:Ln_threshold}
-\end{equation}
-A natural condition for the existence of the limit \eqref{eq:Ln_threshold} as $n\to \infty$ is that the empirical distribution of the threshold values converges to a probability measure.
-Specifically, for an interval $I \subset \mathbb R$ define
-\[
-\lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
-\]
-Theorem~\ref{thm:LAN1} implies:
-\begin{cor} \label{cor:LAN_thresh}
-Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$.
-Then $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a LAN family with precision parameter
-\[
-\kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
-\]
-\end{cor}
-The condition that $\lambda_n$ converges to a probability measure is satisfies, for example, whenever the $t_1,\ldots,t_n$s are drawn independently from a probability distribution $\lambda(dt)$ on $\mathbb R$.
-\par
-Due to local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by 
-${\theta}^{ML}_n$, is local asymptotic minimax in the sense that 
-\[
-\sqrt{n} \left( {\theta}^{ML}_n - \theta \right) \overset{d}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
-\]
-It follows that when the density of the threshold values converges to a probability measure, the ARE of the ML estimator is $\kappa(\theta)\sigma^2$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-We note that ${\theta}^{ML}_n$ is given by the root of
-\begin{equation}
-\label{eq:ML}
-\sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) },  
-\end{equation}
-which is the derivative of the log-likelihood function.
-This root is unique since the log-likelihood function is concave.
-Furthermore, for any $n \in \mathbb R$, we have that ${\theta}^{ML}_n  \in [t_{(1)}, t_{(n)}]$ where $t_{(i)}$ denotes the $i$th element of $\{t_1,t_2\ldots\}$.
-Therefore, if $\{t_1,t_2\ldots\}$ is bounded (for example $\{t_1,t_2\ldots\} \subset \Theta$), then
-\[
-\lim_{n\to \infty} n \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
-\] 
-so that the ML estimator attains the local asymptotic MSE of Corollary~\ref{cor:LA_minimax}. \par
-%
-Since $\eta(x)$ attains its maximum at the origin, we conclude that
-\[
-\kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
-\]
-This upper bound on $\kappa(\theta)$ implies that the ARE of any distributed estimator based on a sequence of threshold detectors does not exceed $\eta(0)\sigma^2$, a fact that agrees with the lower bound under adaptive estimation derived in Theorem~\ref{thm:adpative_lower_bound}.
-%
-This upper bound on $\kappa(\theta)$ is attained only when $\lambda$ is the mass distribution at $\theta$.
-Since $\theta$ is apriori unknown, we conclude that estimation in the distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting.
-In other words, the ability to choose the threshold values in an adaptive manner based on previous messages strictly improves relative efficiency compared to a non-adaptive threshold selection.
-\par
-
-%We conclude that when the density of the threshold values converges to a probability measure, the ARE of the ML is $\kappa(\theta)$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-
-%
-We conclude this section by considering the density of the threshold values that maximizes the ARE $\kappa(\theta)$ under the worst choice of $\theta \in \Theta$.
-
-\subsection{Minimax Threshold Density}
-The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta = [-T,T]$ is given as the solution to the following optimization problem:
-\begin{align}
-\label{eq:var_cvx_minimax}
-\begin{split}
-\mathrm{maximize} \quad &  \inf_{\theta \in [-T,T]} \int \eta(t-\theta) \lambda(dt)
-\\ 
-\mathrm{subject~to} 
-\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
-\end{split}
-\end{align}
-The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program.
-We denote by $\kappa^\star(T)$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum.
-%
-%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
-%\begin{align}
-%\label{eq:cvx_minimax}
-%\begin{split}
-%\mathrm{maximize} \quad &  K \\ 
-%\mathrm{subject~to} 
-%\quad &  K \leq \mathbf H\lambda \\
-%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
-%\end{split}
-%\end{align}
-%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
-%\begin{rem}
-%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$.
-Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points.
-Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using
-%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
-%\end{rem}
-
-Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$.
-The minimal asymptotic risk $\kappa^\star(\theta)$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $T$.
-Also illustrated in these Figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
-\begin{align}
-& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
- \\
-& = 
-\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
-= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
-\end{align}
-From Corollary~\ref{cor:LAN_thresh}, we conclude that the ARE under a uniform distribution is $\kappa_\unif \sigma^2$. \par
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-title = {$\sigma/T = 1/2$},
-ytick={0,0.1,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.6,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/T = 1/5$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.5},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.5},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.3,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma / T = 1/10$},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.2},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.2},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.15,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma / T = 1/20$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:minimax_support}
-Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in \Theta = [-T,T]$.
-%
-The continuous curve (red) represents the reciprocal of the asymptotic risk for at a fixed $\theta \in \Theta$ under the optimal density, so the minimax risk is the inverse of its minimal value.
-The dashed curve (green) is the reciprocal of the asymptotic risk for a fixed $\theta$ under a uniform distribution of threshold values over $\Theta$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
-}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmax=2.5, 
-xmode = log,
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=1, 
-xlabel= {$\sigma/T$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,0.637,1},
-yticklabels={0,$2/\pi$,1},
-ylabel = {$\ARE$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{optimal threshold density};
-
-\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{uniform threshold desnity};
-\end{axis}
-\end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \Ncal(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
-The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
-}.
-\end{center}
-\end{figure}
-
-%We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
-Next, we prove that with any set of messages obtained via a distributed strategy, there exists at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-title = {$\sigma/\sigma_{\theta} = 1$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 2$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma/\sigma_{\theta} = 3$},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 4$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:opt_density}
-Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=b^2/3$ is the variance of the prior.
-}
-\end{center}
-\end{figure}
-
- We consider now the problem of minimizing the asymptotic Bayes risk $
-R_{\pi,\lambda} \triangleq \mathbb E  K^{-1}(\theta)$ over all probability measures $\lambda(dt)$ with support in $\mathbb R$. This optimization problem can be written as follows:
-\begin{align}
-\label{eq:cvx_average}
-\begin{split}
-\mathrm{minimize} \quad & R_{\pi,\lambda} =  \int \frac{\pi(d\theta)}{ \int \eta \left( t-\theta\right) \lambda(dt)}. \\ 
-\mathrm{subject~to} \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) =1. 
-\end{split}
-\end{align}
-We denote by $R^\star_{\pi}$ the minimal value of the objective function in \eqref{eq:cvx_average}.
-Since the function $x \rightarrow 1/x$ is convex for positive values, \eqref{eq:cvx_average} defines a convex optimization problem in $\lambda$ whose solution depends on the prior $\pi$.
-The solution to this problem is approximated by considering $\lambda$ and $\pi$ over a discrete set.
-On Figure~\ref{fig:opt_density} we illustrate the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distributon ($P_X = \Ncal(\theta, \sigma^2)$) and the prior on $\theta$ is uniform over $\Theta = [-b,b]$.
-Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
-\par
-\begin{figure}
-\begin{center}
-
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = 0, xmax=2, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 10,
-samples=1, 
-xlabel= {$\sigma/\sigma_\theta$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,1.5708,5},
-yticklabels={0,$\pi/2$,5},
-ylabel = {$R_{\pi}^\star/\sigma^2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-\addplot[color = black, dashed] {3.14159 / 2};
-\end{axis}
-\end{tikzpicture}
-\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \Ncal(\theta, \sigma^2)$ under an optimal threshold distribution $\lambda^\star$, when the prior $\pi$ is the uniform distribution over $\Theta = [-0.5,0.5]$.
-%
-%versus $\sigma/\sigma_\theta = 2\sqrt{3}\sigma$.
-The distribution $\lambda^\star$ is the minimizer of \eqref{eq:cvx_average}.
-It is illustrated for various cases in Fig.~\ref{fig:opt_density}.
-The dashed curve represents the upper bound \eqref{eq:upper_bound}.
-\label{fig:dist_bound_uniform}  }
-\end{center}
-\end{figure}
-
-As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \Ncal(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution.
-In this case, the ML estimator reduces to the estimator ${\theta}_n$ of \eqref{eq:estimator_naive}.
-As the following proposition shows, the Bayes risk for this choice of $\lambda$ is maximal, and thus provides an upper bound on the Bayes risk under any $\lambda$.
- \eqref{eq:cvx_average}. 
-\begin{prop}\label{prop:upper_bound}
-For any prior $\pi(d\theta)$ and $\theta_0$ in the support of $\eta(x)$ we have
-\begin{equation} 
-\label{eq:upper_bound}
-R_\pi^\star  \leq 
- \int \frac{\pi(d\theta)}{\eta \left( \theta_0 - \theta \right)},
-\end{equation}
-Furthermore, assuming that $\theta_0 = \mathbb E \theta$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
-\begin{equation}
-\label{eq:bound_Taylor}
-R^\star_\pi \leq \frac{1}{4 f^2(0)} + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right) \sigma_\theta^2 + O(\sigma_\theta^3).
-\end{equation}
-\end{prop}
-\begin{proof}
-The function $x \rightarrow 1/x$ is convex for positive values, hence Jensen's inequality implies
-\[
-\left( \int \eta \left( t-\theta\right) \lambda(dt) \right)^{-1}  \leq \int  \frac{ \lambda(dt)}{ \eta \left( t-\theta\right)  }. 
-\]
-Therefore, the expected value of $\kappa^{-1}(\theta)$ satisfies
-\begin{align}
-\ex{  \frac{1}{\kappa(\theta)}}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
-\end{align}
-The bound \eqref{eq:upper_bound} is obtained by taking $\lambda$ to be a mass distribution at any $\theta_0$ in the support of $\eta(x)$.
-Finally, \eqref{eq:bound_Taylor} is obtained by expanding $1/\eta(x)$ to a third order Taylor series around zero
-%\[
-%1/\eta(x) = \frac{1}{4f^2(0)}  + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right)  x^2 + O(x^3),
-%\]
-and taking its expectation with respect to $\pi$ at $x=\theta_0-\theta$. 
-\end{proof}
-We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so the choice $\theta_0 = \ex{ \theta}$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
-The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$.
-The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $\kappa^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.
-
-\begin{example} \label{ex:bound}
-In the normal case $P_X = \Ncal(\theta, \sigma^2)$, the bound in \eqref{eq:bound_Taylor} implies 
-\[
-\frac{R^\star_\pi}{\sigma^2}  \leq \frac{\pi}{2} + \left( \frac{\pi}{2} -1 \right) \left( \frac{ \sigma_\theta}{\sigma} \right)^2 + O \left(  \frac{\sigma_\theta} { \sigma} \right)^3. 
-\]
-It follows that the ARE approaches its maximal value of $2/\pi$ whenever $\sigma_\theta/\sigma$ is small.
-The exact value of \eqref{eq:upper_bound} in this case, as well as the Bayes ARE with the optimal threshold density $\lambda^\star$ for a uniform $\pi$, are illustrated in Fig.~\ref{fig:dist_bound_uniform}.
-%i.e., each encoder simply reports "$1$" or "$-1$" whenever $X_i$ is larger or smaller than $\theta_0$, respectively.
-Intuitively, an accurate estimation of $\theta$ in this case is possible only if a sufficient mix of ''$1$''s and ''$-1$''s is obtained from the sample.
-When $\sigma_\theta^2$ is high compared to $\simga^2$, one of the events $"1"$ or "$-1"$ becomes too rare to
-\end{example}
-
-\section{Conclusions \label{sec:conclusions}}
-We considered the MSE risk in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
-%
-In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency (ARE) larger than that of the median of the samples.
-We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median.
-%We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
-\par
-In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and ARE. 
-%
-We conclude that under such conditions, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in the distributed setting.
-%
-We further considered the special case of messages obtained by comparing against a prescribed sequence of thresholds.
-We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.
+%% \input{conclusions}
 
@@
 
-\section{}
-
-\subsection{Proof of Proposition~\ref{prop:ceo_lower_bound}
-\label{app:proof:prop_ceo_lower_bound}}
-
-First, we note that when $f(x) = \Ncal(0,\sigma^2)$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$, our distributed setting reduces to the Gaussian CEO problem with $R_1=\ldots = R_n =1$ and $k=1$.
-Therefore, any MSE attained in our distributed setting is also attained by the CEO and thus the optimal CEO strategy (with arbitrary $k$) provides a lower bound to the MSE in our setting.
-\\
-
-Consider the minimal MSE $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
-from \cite[Eq. 10]{chen2004upper}:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-For the special case of $R_\Sigma = n$ and $L=n$, we get
-\begin{equation} \label{eq:ceo_optimal_sumrate2}
-n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, this $D^\star$ provides a lower bound to the CEO MSE with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
-\[
-D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO MSE while enforcing the condition $R_1=\ldots = R_n = 1$.
-Indeed, an upper bound for the CEO MSE under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
-\[
-D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
-\]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.
-
-\subsection{Proof of Lemma~\ref{lem:bound_intervals_delta} \label{proof:lem:bound_intervals_delta}}
-
-%\begin{lem} \label{lem:bound_intervals}
-%Let $f(x)$ be a log-concave, symmetric, and differentiable density such that $\eta(x)$ is strongly unimodal. For any $x_1 > \ldots > x_n \in \mathbb R$, 
-%\begin{equation}
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \max_i \eta(x_i). \label{eq:lem_bound_intervals}
-%\end{equation}
-%In particular, if $|x_i|>\epsilon > 0$ for all $i=1,\ldots,n$, then 
-%\[
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \eta(\epsilon) < 0. 
-%\]
-%\end{lem}
-
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-so 
-\[
-\eta(x) =  \frac{  \left(\delta_1(x) \right)^2}{\Delta_1(x)
-(1-\Delta_1(x))}
-= \frac{  \left( f (x) \right)^2}{ F(x)\left(1-F(x)\right)^2}. 
-\]
-We use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:lem_bound_intervals_delta} is bounded from above by $\max_i \eta(x_i)$. The case $n=1$ is trivial. Assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^2} 
-{\Delta_n \left(1- \Delta_n \right) } \leq \max_i \eta(x_i)
-\label{eq:lem_bound_intervals_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  2 \log \delta_N -  \log \Delta_N -  \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(-1)^{k+1} f(x_k)}{1-\Delta_N },
-\]
-and we conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-%
-Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable. We have 
-\[
-\frac{f'(x)}{f(x)} = c'(x), \quad x\in \mathbb R,
-\]
-which is anti-symmetric, non-negative for $x<0$,  non-positive for $x>0$, and non-increasing since $c(x)$ is concave.
-Therefore, if $c'(x_i) = c'(x_{i+1})$ for some $i =1,\ldots,N-1$, then either (1) $x_i = x_{i+1}$ or (2) $c'(x)$ is the zero function.
-Since (2) violates the assumption that $f(x)$ is a density function, we conclude that $c'(x)$ is an injection.
-%
-As a result, \eqref{eq:gradient_zero} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_proof} equals $\eta(x_1) = \max_i \eta(x_i)$ hence the statement holds.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$, or  $x_i, x_{i+1}$ for some $i$.
-It is left to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Under case (1) we have
-\begin{align*}
-\lim_{x_N \to -\infty} \frac{  \delta_N^2} 
-{\Delta_N \left(1- \Delta_N \right) }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^2} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)} ,
-\end{align*}
-which is smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis. Under case (2) we have
-\begin{align*}
-&  \lim_{x_1 \to \infty}
-\frac{ \delta_N} 
-{\Delta_N\left(1- \Delta_N \right) } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right) \left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right) }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^2 } 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right) },
-\end{align*}
-where $x'_{m} = x_{m+1}$. The last expression is also smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis.  \QEDA \\
-
-\subsection{Proof of Theorem~\ref{thm:adpative_lower_bound}
-\label{proof:thm:adpative_lower_bound}
-}
-
-We first prove the following lemma:
-\begin{lem} \label{lem:fisher_bound}
-Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that $\eta(x)$ is unimodal. For a Borel measurable $A$ set, 
-\[
-M(X) = \begin{cases} 1,& X \in A, \\
--1, & X \notin A.
-\end{cases}
-\]
-Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $\eta(0)$.
-\end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
-When $f(x)$ is the normal density function, this lemma follows from \cite[Thm.
-3]{Barnes2018}.
-The proof below is based on a different techique than in \cite{Barnes2018}, and is valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}.
-\\
-
-The Fisher information of $M$ with respect to $\theta$ is given by
-\begin{align}
-I_\theta & =  \mathbb E \left[ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta \right] \nonumber \\
-& = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
-& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\
-& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\ 
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
-\end{align}
-where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$.
-Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
-\[
-\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
-\]
-which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$.
-It is therefore enough to proceed in the proof assuming that $A$ is of the form
-\[
-A = \cup_{j=1}^k (a_j,b_j),
-\]
-with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
-\begin{align*}
-\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
-& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
-\end{align*}
-so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
-\begin{align}
-& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
-{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
-& \times \frac {1} 
-{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
-\label{eq:lemma_J}
-\end{align}
-It follows from Lemma~\ref{lem:bound_intervals_delta} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $4f^2(0)$.  \QEDA \\
-
-We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
-\begin{equation}
-\label{eq:general_messages}
-B_i = \begin{cases}
-X_i \in A_i & 1, \\
-X_i \notin A_i & -1,
-\end{cases} 
-\end{equation}
-where $A_i \subset \mathbb R$ is a Borel measurable set. 
-%Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
-Consider the conditional distribution $P({B^n|\theta})$ of $B^n$ given $\theta$. We have 
-\begin{align}
-P\left( B^n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
-\end{align}
-where $P\left(B_i =1 | \theta, B^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B^n$ with respect to $\theta$ is given by 
-\begin{align}
-I_\theta(B^n) = \sum_{i=1}^n I_\theta (B_i|B^{i-1}),
-\label{eq:fisher_information}
-\end{align}
-where $I_\theta (B_i|B^{i-1})$ is the Fisher information of the distribution of $B_i$ given $B^{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B^{i-1}) \leq 4f^2(0)$.
-The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
-\begin{align*}
-\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(B^n) + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
-& \geq \frac{1}{ 4f^2(0) n + I_0}.
-\end{align*}
-
-\QEDA
-
-\subsection{Proof of Theorem~\ref{thm:sgd}
-\label{proof:thm:sgd}
-}
-The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.
-
-\subsubsection*{Proof of (i)}
-%Specifically, (i) in Theorem~\ref{thm:sgd} 
-Consider the following simplified version of \cite[Thm. 4]{polyak1992acceleration}:
-\begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
-Let 
-\[
-X_i = \theta + Z_i,\quad i=1,\ldots,n,
-\]
-where the $Z_i$s are i.i.d. with zero means and finite variances. Define
-\begin{align}
-\begin{split}
-\theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
-\bar{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
-\end{split}
-\label{eq:Polyak_Juditsky_alg}
-\end{align}
-where in addition, assume the following: 
-\begin{enumerate}
-\item[(i)] There exits $K_1$ such that $\left| \varphi(x) \right| \leq K_1(1+|x|)$ for all $x\in \mathbb R$.
-\item[(ii)] The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions \eqref{eq:conditions1}.
-\item[(iii)] The function $\psi(x) \triangleq \ex{ \varphi(x+Z_1)}$ is differentiable at zero with $\psi'(0)>0$, and satisfies $\psi(0)=0$ and $x\psi(x) >0$ for all $x\neq 0$.
-Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
-\begin{equation}
-\label{eq:Polyak_Juditsky_cond3}
-\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
-\end{equation}
-\item[(iv)] The function 
-$\chi(x) \triangleq \ex{\varphi^2(x+Z_1)}$ is continuous at zero. 
-\end{enumerate}
-Then $\bar{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}({\theta}_n - \theta)$ converges in distribution to $\Ncal(0,V)$, where
-\[
-V = \frac{ \chi(0)} {\psi'^2(0)}. 
-\]
-\end{thm}
-
-Using the notation above, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have that $\chi(x) = \mathbb E \sgn^2(x+Z_1) = 1$, so $\chi(0) = 1$. In addition,
-\begin{align*}
-\psi(x) & = \ex{ \sgn(x+ Z_1) }= \int_{-\infty}^\infty \sgn(x+z) f(z) dz \\
-& = \int_{-x}^\infty f(z) dz -\int_{-\infty}^{-x} f(z) dz. 
-\end{align*}
-Using the symmetry of $f(x)$ around zero, it follows that $\psi'(x) = 2f(x)$ and thus $\psi'(0) = 2f(0)$.
-It is now easy to verify that the rest of the conditions in Theorem~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$.
-Since
-\[
-\frac{\chi(0)}{\psi'^2(0)} = \frac{1}{4 f^2(0)} = \frac{1}{\eta(0)},
-\]
-it follows from Theorem~\ref{thm:polyak_juditsky} that
-\[
-\sqrt{n}\left({\theta}_n-\theta \right) \overset{d}{\to} \Ncal \left(0, 1/ \eta(0)\right). 
-\]
-
-\subsubsection*{Proof of (ii)}
-We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\mathbb R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates.
-Then
-\begin{align}
-\label{eq:sgd_part2}
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
-\end{align}
-under $\Prob_{\theta,n}$.
-Under the assumption that $f(x)$ is continuously differentiable with a finite location Fisher information, the model $\{Z_n+ \theta\}_{n \in \mathbb N}$ is differentiable in quadratic mean \cite[Exm.
-7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
-\[
-\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
-\]
-where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$. 
- The random variable $L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)
-$ is bounded, and hence 
-\[
-\ex{ L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)} \to \ex{L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)}
-\]
-Any regular estimators in a LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}, hence in order to prove (ii) it is left to show that $\bar{\theta}_n$ is regular. For this purpose, 
-we use the following refinement of Theorem~\ref{thm:polyak_juditsky}, proof of which is given in Subsection~\ref{proof:thm:normal_expansion} below.
-%
-\begin{thm} \label{thm:normal_expansion}
-Set $\Delta_i = \theta_i - \theta$ and
-$\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \Delta_i$. Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{thm:polyak_juditsky}, there exists $K_1$ and $\lambda>0$ such that
-\begin{equation}
-\ex{\left| \varphi(Z_1) - \varphi(x+Z_1)  \right|} \leq K_1 |x|^{1+\lambda}
-\label{eq:PJ_additional_cond}. 
-\end{equation}
-Then:
-\begin{itemize}
-\item[(i)] \begin{equation}
-\sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1). \label{eq:normal_expansion_lem}
-\end{equation}
-where $o_{p,n}(1)$ converges in probability to $0$ as $n\to \infty$.
-\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite location Fisher information 
-\[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)} \right)^2 f(x) dx,
-\]
-then for any converging sequence $h_n \to h$,
-\[
-\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-h}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
-\]
-under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h_n/\sqrt{n}}$ with density $\prod_{i=1}^n f(x_i-h_n/\sqrt{n})$.
-\end{itemize}
-\end{thm}
-We now use this theorem to show regularity of $\bar{\theta}_n$. We have, 
-\begin{align*}
-& %\varphi(Z_1) - \varphi(x+Z_1) = 
-\sgn(Z_1) - \sgn(x + Z_1) \\
-& = \begin{cases}
-2 & Z_1 > 0,\, x+Z_1<0, \\
--2 & Z_1 <0, \, x+Z_1>0, \\
-0 & \text{otherwise}. 
-\end{cases}
-\end{align*}
-It follows that
-\begin{align*}
-\ex{ \left| \varphi(Z_1) - \varphi(x+Z_1) \right| }  \leq \Prob\left( |Z_1| < x  \right) \leq f(0) |x|, 
-\end{align*}
-hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
-\[
-\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = -2f(0) = -\psi'(0). 
-\]
-Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}.
-
-\subsubsection*{Proof of (iii)}
-%In order to prove part (ii) of Theorem~\ref{thm:sgd} 
-Consider the following result from \cite{polyak1990new}:
-\begin{thm}{\cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
-Let
-\begin{align} \label{eq:polyak_new_measurements}
-\begin{cases}
-U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = g'(U_{n-1})+Z_n \\
-\bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
-\end{cases}
-\end{align}
-Assume that the function $g(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative.
-In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \mathbb R$.
-Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution with a density for which the Fisher information exits.
-Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{thm:polyak_juditsky}-(iii) and satisfy the conditions there.
-Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$,
-and there exits $K_3$ such that 
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] \leq K_3(1+|x|^4). 
-\]
-Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
-\[
-V_n \triangleq \mathbb E \left[ \left(\bar{U}_n-x^\star \right)^2 \right] = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
-\]
-\end{thm}
-
-We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$. From \eqref{eq:polyak_new_measurements} we have
-\begin{align*} 
-U_n & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
-& = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
-\end{align*}
-so the estimator $\bar{U}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] = 1 \leq K_3(1+|x|^4)
-\]
-for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
-the conditions in Theorem~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
-In particular, $\psi'(0) = (2f(0))^{-2}$.
-Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$.
-Theorem~\ref{thm:polyak_new} implies that for any $\theta \in \mathbb R$,
-\[
-V_n = \mathbb E \left[ \left({\theta}_n-\theta \right)^2 \right]  = \frac{1}{4n f^2(0)} + o(n^{-1}).
-\]
-
-{\color{red}
-
-\subsection{Proof of Theorem~\ref{thm:normal_expansion}
-\label{proof:thm:normal_expansion}
-}
-\subsubsection*{Proof of (i)}
-The proof of part (i) of Theorem~\ref{thm:normal_expansion} requires the following two additional results from \cite{polyak1992acceleration}:
-\begin{lem}{\cite[Lem. 2]{polyak1992acceleration}}
-\label{lem:Polyak_expansion}
-Consider the process $\{\Delta_i^1 \}_{i=0}^\infty$ defined by
-\[
-\Delta^1_i = \Delta^1_{i-1} - \gamma_i (A \Delta_{i-1}+ \xi_i),\quad i=1,2\ldots.
-\]
-Assume that $A>0$ and condition (ii) of Theorem~\ref{thm:polyak_juditsky} holds. Then 
-\begin{equation}
-\label{eq:Polyak_expansion}
-\sqrt{n} \bar{\Delta}_n^1 = \frac{1}{\sqrt{n}}\sum_{i=0}^{n-1} \Delta_i^1 = \frac{\alpha_n \Delta_0^1}{\sqrt{n} \gamma_0}  + \frac{1}{\sqrt{n} A} \sum_{i=1}^{n-1} \xi_i + \frac{1}{\sqrt{n}}\sum_{i=1}^{n-1} w_i^n \xi_i,
-\end{equation}
-where $\alpha_n$ and $w_i^n$ are real numbers such that $|\alpha_n| \leq K$ and $|w_i^n|\leq K$ for some $K< \infty$, and 
-\[
-\lim_{n\to \infty} \frac{1}{n} \sum_{i=1}^{n-1} |w_i^n| = 0. 
-\]
-\end{lem}
-
-\begin{lem} \label{lem:PJ_converging_sum}
-Under the conditions of Theorem~\ref{thm:polyak_juditsky},
-\[
-\sum_{i=1}^\infty \frac{|\Delta_{i}|^{1+\lambda}}{\sqrt{i}} < \infty 
-\]
-almost surely. 
-\end{lem}
-Lemma~\ref{lem:PJ_converging_sum} follows from the proof of Theorem 2 in \cite{polyak1992acceleration}.
-
-We separate the proof of part (i) into two steps.
-\subsubsection*{Step I}
-The expansion \eqref{eq:normal_expansion_lem} holds for the process  $\{\bar{\Delta}^1_i\}_{i=1}^\infty$ defined as follows:
-\begin{align} \label{eq:Polyak_expansion_lem1_alg}
-& \Delta_i^1  = \Delta_{i-1}^1 - \gamma_i \psi'(0) \Delta_{i-1}^1 - \gamma_i \varphi(Z_i), \qquad
- \delta_0^1 = \Delta_0\\
-& \bar{\Delta}^1_i = \frac{1}{n}\sum_{i=0}^{n-1} \Delta^1_i.
-\end{align}
-
-In order to prove this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$.
-The first expression on the RHS on \eqref{eq:Polyak_expansion} goes to zero in variance.
-In addition,
-\begin{align*}
-& \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }  = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
-& = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0. 
-\end{align*}
-We obtain
-\begin{equation}
-\sqrt{n} \bar{\Delta}^1_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1), \label{eq:Polyak_expansion_aux_process}
-\end{equation}
-
-\subsubsection*{Step II} $\bar{\Delta}_n$ and $\bar{\Delta}^1_n$ are asymptotically equivalent. \\
-
-From \eqref{eq:Polyak_Juditsky_alg} and \eqref{eq:Polyak_expansion_lem1_alg}, the difference $\delta_i = \Delta_i - \Delta_i^1$ satisfies the recursion
-\[
-\delta_i = \delta_{i-1} - \gamma_i \psi'(0) \delta_{i-1} + \gamma_i \left( \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i) \right),
-\]
-where $\delta_0 = 0$. Use Lemma~\ref{lem:Polyak_expansion} with $\xi_i =  \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i)$ to obtain
-\begin{align}
-& \sqrt{n}\bar{\delta}_n = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \xi_i  \\
-& = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \label{eq:PJ_proof1} \\
-& + 
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi(\Delta_{i-1})  + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i)
-\right) \label{eq:PJ_proof2}
-\end{align}
-For the term \eqref{eq:PJ_proof1} and using \eqref{eq:Polyak_Juditsky_cond3}, there exists $K_1$ and $K_2$ such that 
-\begin{align*}
-& \eqref{eq:PJ_proof1}
-\leq K_1 \sum_{i=1}^\infty \frac{1}{\sqrt{i}} \left| \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \right| \\
-& \leq K_2 \sum_{i=1}^\infty \frac{ |\Delta_i|^{1+\lambda}}{\sqrt{i}}. 
-\end{align*}
-
-Lemma~\ref{lem:PJ_converging_sum} shows that 
-\begin{align}
-\sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}}  < \infty \label{eq:PJ_converging_sum},
-\end{align}
-hence the Kronecker lemma implies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \to 0.
-\]
-For the term \eqref{eq:PJ_proof2}, set 
-\[
-\epsilon_i \triangleq \psi(\Delta_{i-1}) + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i).
-\]
-For $a>0$ and $n \in \mathbb N$, define the event
-\[
-A_{n,a} \triangleq \left\{ \sum_{i=1}^{n-1} \frac{|\epsilon_i|}{\sqrt{i}}  \geq a  \right\}. 
-\]
-By Markov's inequality, we have
-\begin{align}
-\ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } \leq \frac{1}{a} \sum_{i=1}^{n-1} \frac{ \ex{|\epsilon_i| \Delta_{i-1} \mid }}{\sqrt{i}}. \label{eq:PJ_proof_3}
-\end{align}
-Using \eqref{eq:Polyak_Juditsky_cond3} and \eqref{eq:PJ_additional_cond}, there exists $K'$ and $\lambda'>0$ such that
-\begin{align*}
-& \ex{ |\epsilon_i| | \Delta_{i-1}}  \leq |\psi(\Delta_{i-1})| + \left| \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i) \right|  \\
-& \leq K' |\Delta_{i-1}|^{1+\lambda}. 
-\end{align*}
-Plugging this bound in \eqref{eq:PJ_proof_3} and using Lemma~\ref{lem:PJ_converging_sum},we obtain 
-\[
-\Prob(A_{n,a}) = \ex{ \ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } } \leq  \frac{K''}{a}
-\]
-for some constant $K''$. It follows that for any $\epsilon$, we may choose $a$ large enough such that 
-\[
-\sup_{n} \Prob(A_{n,a}) < \epsilon.
-\]
-This implies that for any $\epsilon>0$,
-\[
-\Prob \left( \sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty \right) \geq 1-\epsilon,
-\]
-and hence 
-\[
-\sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty
-\]
-almost surely. The Kronecker lemma now implies 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left|\epsilon_i\right| \to 0,
-\]
-hence the term \eqref{eq:PJ_proof2} satisfies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right) \epsilon_i \leq \frac{K'''}{\sqrt{n}} \sum_{i=1}^{n-1} |\epsilon_i| \to 0. 
-\]
-This conclude the proof of part (i).
-
-\subsubsection*{Part (ii)}
-Use \eqref{eq:normal_expansion_lem} to write
-\[
-\sqrt{n} \bar{\Delta}_n = G_n + o_{p,n}(1),
-\]
-where
-\[
-G_n \triangleq -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n} \varphi(Z_i). 
-\]
-From \cite[Exm.
-7.8]{van2000asymptotic}, the location model $f(x-\theta)$ with continuously differentiable $f(x)$ is differentiable in quadratic mean with the score function $-f'(x-\theta)/f(x-\theta)$.
-This fact implies the following expansion \cite[Thm.
-7.2]{van2000asymptotic}:
-\begin{align}
-\label{eq:PJ_LAN}
-& \log \frac{\Prob^n_{h_n/\sqrt{n}}}{\Prob^n_0} (Z_1,\ldots,Z_n) =  \log \prod_{i=1}^{n} \frac{f(Z_i-h_n/\sqrt{n})}  {f(X_i-\theta)} = h J_n - \frac{1}{2}h^2 I_{\theta} + o_{p,n}(1),
-\end{align}
-for any converging sequence $h_n \to h$, 
-where 
-\[
-J_n \triangleq -\frac{1}{\sqrt{n}} \sum_{i=1}^n \frac{f'(Z_i)}{f(Z_i)} .
-\]
-We have
-\begin{align*}
-& \ex{ G_n J_n} = \frac{1}{\psi'(0)}\frac{1}{n} \sum_{i=1}^n \ex{ \varphi(Z_i) \frac{f'(Z_i)}{f(Z_i)} }  \\
-& = \frac{1}{ \psi'(0)} \ex{ \varphi(Z_1) \frac{f'(Z_1)}{f(Z_1)}} =  \frac{1}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx , 
-\end{align*}
-Since both $\sqrt{n}G_n$ and $\sqrt{n}J_n$ are the sum of $n$ i.i.d. random variables with zero mean and finite variance, we obtain, from the central limit theorem and Slutsky's theorem, that
-\[
-\left(\sqrt{n} \bar{\Delta}_n, \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} \right) \overset{d}{\to} \Ncal \left( \left(0,-\frac{h^2}{2} I_\theta \right),  \begin{pmatrix}
-\frac{\chi(0)}{\psi'^2(0)} & \frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx \\
-\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx & h^2 I_\theta 
-\end{pmatrix}  \right)
-\]
-Le Cam's third lemma \cite[Exm. 6.7]{van2000asymptotic} implies that under $\Prob^n_{h/\sqrt{n}}$, 
-\[
-\sqrt{n}\bar{\Delta}_n \overset{d}{\to} \Ncal\left(\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx,  \frac{\chi(0)}{\psi'^2(0)} \right).
-\]
-
-\QEDA
-}
-
-\subsection{Proof of Theorem~\ref{thm:LAN1}
-\label{proof:thm:LAN1}
-}
-The log probability mass distribution of $B^n=(B_1,\ldots,B_n)$ is given by
-\begin{align*}
-& \log \Prob_\theta(b^n) = \sum_{i=1}^n \left( \frac{b_i+1}{2} \log  \Prob(X_i\in A_i) + 
-\frac{1-b_i}{2} \log \Prob(X_i\in A_i) \right), \quad b^n \in \{-1,1\}^n. 
-\end{align*}
-Consequently, 
-\begin{align}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) } = \sum_{i=1}^n    \frac{b_i+1}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} + 
-\sum_{i=1}^n  \frac{1-b_i}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}. 
-\label{eq:LAN_proof1}
-\end{align}
-For each $i=1,\ldots,n$, write 
-\[
-A_i = \bigcup_{k=1}^{K_i} \left(t_{i,k},t_{i,k+1} \right),
-\]
-where $t_{i,1}<\ldots<t_{i,K_i}$ and, with a slight abuse of notation, $t_{i,1}$ and $t_{i,K_i}$ may also be $-\infty$ or $+\infty$, respectively. Thus
-\[
-\Prob_{\theta}(X_i \in A_i) = \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta).
-\]
-In particular, since $f$ is differentible, $\Prob_{\theta}(X_i \in A_i)$ is twice differentiable, and we may write
-\begin{align*}
-\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)  = \Prob_{\theta} (X_i \in A_i) + \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \frac{h}{\sqrt{n}} + o(h), 
-\end{align*}
-and thus
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} = \log \left(1 + \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} + o(h) \right) \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2 + o(h^2).
-\end{align*}
-Similarly, we have
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 + o(h^2).
-\end{align*}
-From \eqref{eq:LAN_proof1} we obtain
-\begin{align*}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
-\left( 
-\frac{b_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-b_i}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}   \right) \\
- & - \frac{h^2}{2n} 
- \sum_{i=1}^n 
-\left( 
- \frac{b_i+1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-b_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 \right) + o(h^2) \\
-\end{align*}
-%
-Noting that 
-\[
-\frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} = \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)},
-\]
-the proof is completed by proving the following two claims:
-\begin{itemize}
-\item[I.] 
-For $i=1,\ldots,n$ denote 
-\[
-U_i = \frac{B_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-B_i}{2}  \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}. 
-\]
-Then 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0, \kappa(\theta) \right). 
-\]
-\item[II.]
-For $i=1,\ldots,n$ denote 
-\[
-V_i =  \frac{B_i-1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-B_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2.
-\]
-Then 
-\[
-\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} \kappa(\theta). 
-\]
-\end{itemize}
-\subsubsection*{Proof of Claim I}
-First note that 
-\begin{align*}
-\mathbb E  [U_i] & = 
- \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=1)   + 
- \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=-1)  = 0. 
-\end{align*}
-In addition,
-\begin{align*}
-& \mathbb E U_i^2 = 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2  \Prob (B_i=1)   + 
-\left( \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2 \Prob (B_i=-1) \\
-& =
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)} +  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)} \\
- & =  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left(1-\Prob_{\theta}(X_i \in A_i) \right)} 
-\end{align*}
-Therefore
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 = L_n(A_1,\ldots,A_n) \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ such that the limit above exists.
-We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition for his version of the central limit time: for any $\delta>0$ we have that
-\begin{align*}
-& \mathbb E \left| U_i \right|^{2+\delta} =
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} 
-\end{align*}
-and
-\begin{equation}
-\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} } { \left( \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta} = 
-\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
-\label{eq:Lyaponov}
-\end{equation}
-Next, we claim that there exits $\delta>0$ and $K>0$, that are independent of $n$, such that
-\begin{align}
-\frac{1}{n} \sum_{i=1}^n \mathbb E  |U_i|^{2+\delta}  < M \label{eq:Lyaponov_num}
-\end{align} 
-for all $n$ large enough. To see this, note that
-\begin{align*}
-& \mathbb E |U_i|^{2+\delta} = 
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}  \\
-  &  = \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} } 
-  \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \\
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}, 
-\end{align*}
-where the last transition is because 
-\[
- \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \leq 1. 
-\]
-We now use the fact that each $A_i$ is a finite union of interval and consider the following lemma, proof of which is given in Appendix~\ref{proof:lem:bound_intervals_delta}.
-\begin{lem} \label{lem:bound_intervals_delta}
-Let $f(x)$ be a log-concave, symmetric, and differentiable PDF such that $\eta(x)$ is unimodal.  There exists $\delta>0$ such that for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, 
-\begin{equation}
-\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^{2+\delta} }
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} } 
-\leq  2^\delta f^{2+\delta}(0). 
-\label{eq:lem_bound_intervals_delta}
-\end{equation}
-\end{lem}
-
-Lemma~\ref{lem:bound_intervals_delta} implies 
-\begin{align*}
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} = \frac{\left| \sum_{k=1}^{K_i} (-1)^k f(x_{i,k}-\theta) \right|^{2+\delta} }
-  { \left( \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta} \left( 1 - \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta}} \\
-  & \leq 2^\delta f^{2+\delta}(0). 
-\end{align*}
-In particular, we conclude that 
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} \leq 2^\delta f^{2+\delta}(0), 
-\]
-and thus for any $\delta>0$ the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we conclude that 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0,\kappa(\theta) \right). 
-\]
-
-\subsubsection*{Proof of Claim II} 
-We have:
-\begin{align*}
-\mathbb E V_i  & = 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)}  
-+ 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)}  \\
- & = 
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left( 1-\Prob_{\theta}(X_i \in A_i) \right)}  
-\end{align*}
- We conclude that:
-\begin{equation} \label{eq:LAN_limit_cond}
-\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =   L_n(A_1,\ldots,A_n)  \to \kappa(\theta)
-\end{equation}
-Since the $V_i$s are independent of each other, Kolmogorov's law of large numbers implies
-%(e.g. \cite[Theorem 10.2.3]{sen1994large}) 
-\[
-\frac{1}{n} \sum_{i=1}^n  V_i \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ for which the limit \eqref{eq:LAN_limit_cond} exists.
-
-\QEDA
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals_delta}} 
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-and 
-\[
-\eta_\delta(x) \triangleq  \frac{  \left(\delta_1(x) \right)^{2+\delta}}{  \left(\Delta_1(x)  \right)^{1+\delta}
-(1-\Delta_1(x))^{1+\delta}}
-= \frac{  \left( f (x) \right)^{2+\delta}}{ \left(F(x) \right)^{1+\delta}(1-F(x))^{1+\delta}}. 
-\]
-The proof is by induction on $n$.
-For the case $n=1$ the LHS of \eqref{eq:lem_bound_intervals_delta} equals $\eta_\delta(x)$.
-Note that $\eta_\delta(0) = 2^\delta f^{2+\delta}(0)$, so it is enough to prove that $\eta_\delta(0)$ attains it maximum at $x=0$.
-We have $\eta_\delta(x) = \eta^{1+\delta}(x)/f^\delta(x)$, and thus
-\[
-\log \eta_\delta'(x) = (1+\delta) \frac{\eta'(x)}{\eta(x)} - \delta \frac{f'(x)}{f(x)}. 
-\]
-By Assumption~\ref{assump:failure_rate} both terms above are negative for $x>0$, so that $\log \eta_\delta'(x) \leq 0$ if and only if
-\begin{equation} \label{eq:delta_proof_cond}
-(1+\delta) \left| \frac{\eta'(x)}{\eta(x)} \right| \geq \delta \left| \frac{f'(x)}{f(x)} \right|, \qquad x>0.
-\end{equation}
-Also by Assumption~\ref{assump:failure_rate}, for $x>0$ we have
-\[
-0 > (\log \eta(x))' = \frac{h'(x)}{h(x)}-\frac{h'(-x)}{h(-x)},
-\]
-so that \eqref{eq:delta_proof_cond} is satisfies for $\delta>0$ small enough.
-
-Next, assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^{2+\delta}} 
-{\left(\Delta_n \right)^{1+\delta}\left(1- \Delta_n \right)^{1+\delta} } \leq \eta_\delta(0) = 2^\delta f^{2+\delta}(0) . 
-\label{eq:lem_bound_intervals_delta_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%If $x_{i+1} = x_i$ for some $i=1,\ldots,N-1$, then then the indices $i$ and $i+1$ may  be removed from all sums in \eqref{eq:lem_bound_intervals}, what brings us to the case $n = N-2$.
-Therefore, we may assume that $x_1 < \ldots < x_n$.
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  (2+\delta) \log \delta_N - (1+\delta) \log \Delta_N - (1+\delta) \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{(2+\delta) (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(1+\delta)(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(1+\delta)(-1)^{k+1} f(x_k)}{1-\Delta_N }.
-\]
-We conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero_delta}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N(1+\delta)}{2+\delta} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-From the same reason as in the proof of Lemma~\ref{lem:bound_intervals_delta}, \eqref{eq:gradient_zero_delta} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_delta_proof} equals $\eta_\delta(x_1)$ which was shown to be smaller than $\eta_\delta(\epsilon)$.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_delta_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$,  $x_i, x_{i+1} = -\epsilon$ for some $i$, or $x_i, x_{i+1} = \epsilon$ for some $i$.
-It is therefore enough to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Assume first $x_N \rightarrow -\infty$. Then 
-\begin{align*}
-\frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)^{1+\delta} } ,
-\end{align*}
-which is smaller than $\eta_\delta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
-\begin{align*}
-& \frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right)^{1+\delta} }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^{2+\delta}} 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)^{1+\delta}\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right)^{1+\delta} },
-\end{align*}
-where $x'_{m} = x_{m+1}$ for $m=1,\ldots, N-1$. The last expression is smaller than $\eta_{\delta}(0)$ by the induction hypothesis.  \QEDA \\
-
-\subsection{Proof of Theorem~\ref{thm:non_existence}
-\label{proof:thm:non_existence}
-}
-
-Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta) = \eta(0)$. 
-%
-Since $B_1,B_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, $\theta$ is in $\Xi$ if and only if
-\begin{equation}
-\label{eq:non_existence_proof}
-\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0). 
-\end{equation}
-By assumption, we have $B_i^{-1} = A_i$ where $A_i$ can be expressed as
-\[
-A_i = \cup_{i=1}^K (a_{i,k},b_{i,k}), 
-\]
-where $a_{i,1} \leq b_{i,1} \leq \ldots \leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values $-\infty$ and $\infty$, respectively. Denote
-\[
-\mathcal B_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\}.
-\]
-For any $\theta$ and $\epsilon>0$, denote 
-\[
-S_n(\theta, \epsilon) \triangleq \left\{ i\leq n \,:\, (\theta-\epsilon,\theta+\epsilon) \cap \mathcal B_i \neq \emptyset \right\}
-\]
-In words, $S_n$ contains all integers smaller than $n$ in which an $\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals consisting $A_i$. 
-%
-We now claim that 
-if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. Indeed, for such $\theta$ we have
-\begin{align}
-& L_n(A_1,\ldots,A_n; \theta) \nonumber \\
-& = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
-\frac{ \left(\sum_{k=1}^{K}  f(\theta - b_{i,k})- f(\theta - a_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& 
-+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(b_{i,k}-\theta) - f(a_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& \overset{(a)}{\leq}
-\frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
- \label{eq:non_existence_proof1}
-\end{align}
-where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} and the fact that for $i \in S_n(\theta, \epsilon)$, 
-\[
-\max\left\{ \max_k \eta(b_{i,k}-\theta) , \max_k \eta(a_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
-\]
-Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, \eqref{eq:non_existence_proof1}, and thus $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.
-\par
-For $k\in \mathbb N$, assume by contradiction that there exists $N \geq 2K + 1$ distinct elements
-$\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$ consists of at most $K$ intervals, we have that 
-\begin{equation}
-\label{eq:few_optimality_points_proof}
-\card (\cup_{i=1}^n \mathcal B_i) \leq 2 n K. 
-\end{equation}
-Fix $\epsilon>0$ such that 
-\[
-\epsilon < \frac{1}{2}\min_{i\neq j} |\theta_i - \theta_j|. 
-\]
-Since for each $\theta \in \Theta$ we have $S_n(\theta, \epsilon) \to 1$, there exists $n$ large enough such that 
-\[
-\card \left(S_n(\theta_i, \epsilon) \right) \geq n \left(1-\frac{1}{2N} \right)
-\]
-for all $i=1,\ldots,N$.
-However, $S_n(\theta_1,\epsilon), \ldots S_n(\theta_N,\epsilon)$ are disjoint, so the cardinallity of their union is at least $n\left(1-\frac{1}{2N} \right)N$ which is grater than $2nK + n/2$ in contradiction to \eqref{eq:few_optimality_points_proof}.
+%% \input{appendices}
 

### 2019-09-23 preliminaries.tex
Adding a bib file

--- 2019-02-21 onebit_full_V2.tex
@@
-%\documentclass[letterpaper]{IEEEtran}
-\documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper
-
-%LatexiDiff ignore tikz:
-% $: latexdiff -c "PICTUREENV=(?:picture|tikzpicture|DIFnomarkup)[\w\d*@]*" old.tex new.tex > diff.tex
-
-%\IEEEoverridecommandlockouts                              %
-
-%\usepackage{mathcomSTEP}
-
-%\overrideIEEEmargins 
-%\IEEEoverridecommandlockouts                              % This command is only needed if 
-% you want to use the \thanks command
-
-%\overrideIEEEmargins                                      % Needed to meet printer requirements.
-
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-\onecolumn
-
-\usepackage{mathptmx} 
-\usepackage{times} 
-\usepackage{amsmath} 
-\usepackage{amsbsy} 
-\usepackage{amssymb}
-%\usepackage{newtxtext, newtxmath}
-\usepackage{mathrsfs}
-\usepackage{comment}
-\usepackage[export]{adjustbox}
-\usepackage{tikz}
-\usetikzlibrary{external,positioning,decorations.pathreplacing,shapes,arrows,patterns}
-
-%\tikzexternalize[mode=list and make]
-\usepackage{algorithmicx}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage{pstool}
-\usepackage[latin1]{inputenc}
-\usetikzlibrary{arrows,shapes}
-\usepackage{xifthen}
-\usepackage{epic}
-%\usepackage{caption}
-\usepackage{epstopdf}
-
-\newtheorem{thm}{\bf{Theorem}}
-\newtheorem{cor}[thm]{\bf {Corollary}}
-\newtheorem{lem}[thm]{\bf {Lemma}}
-\newtheorem{prop}[thm]{\bf {Proposition}}
-\newtheorem{example}{\bf {Example}}
-\newtheorem{definition}{\bf {Definition}}
-\newtheorem{rem}{\bf {Remark}}
-\newtheorem{assump}{\bf {Assumptions}}
-
-\newcommand{\mmse}{\mathsf{mmse}}
-\newcommand{\unif}{\mathsf{unif}}
-\newcommand{\card}{\mathrm{card}}
-\newcommand{\ARE}{\mathsf{ARE}}
-\newcommand{\supp}{\mathrm{supp} }
-\renewcommand\vec[1]{\ensuremath\boldsymbol{#1}}
-\newenvironment{proof}{\paragraph*{Proof}}{\hfill$\square$ \newline}
-\newcommand{\sgn}{\mathrm{sgn} }
-\newcommand{\Prob}{\mathbb{P} }
-\newcommand{\argmax}{\mathrm{argmax}}
-\newcommand*{\QEDA}{\hfill\ensuremath{\square}}
-\newcommand{\CEO}{\mathsf{CEO}}
-
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-\tikzstyle{sint}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.8cm,thick ]
-\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
-\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
-\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.7cm,thick ]
-\tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-
-\author{
-    \IEEEauthorblockN{
-Alon Kipnis\IEEEauthorrefmark{1} and   
-    John C. Duchi\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}  \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}Stanford University, Department of Statistics \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Stanford University, Department of Electrical Engineering. }
-}
-
-\title{\LARGE \bf Mean Estimation from One-Bit Measurements}
-
-\begin{document}
-\graphicspath{{./Figs/}}
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-We consider the problem of estimating the mean of a symmetric log-concave distribution under the following constraint: only a single bit per sample from this distribution is available to the estimator.
-We study the mean squared error risk in this estimation as a function of the number of samples, and hence the number of bits, from this distribution.
+\section{Consistent Estimation and Off-the-shelf Bounds \label{sec:preliminary}}
 %
-Under an adaptive setting in which each bit is a function of the current sample and previously recorded bits, we show that the optimal relative efficiency compared to the sample mean is the efficiency of the median.
-%For example, in estimating the mean of a normal distribution, a constraint of one bit per sample incurs a penalty of $\pi/2$ in sample size compared to the unconstrained case.
-%
-We also consider a distributed setting where each bit is only a function of a single sample.
-We show that the optimal efficiency of the adaptive setting can be attained by splitting the sample into two parts and allowing only a single adaptation.
-Otherwise, we show that no one sample estimation procedure can attain the optimal efficiency uniformly over all points in the parameter space.
-%
-%Finally, we analyze a distributed setting where the bits are obtained by comparing each sample against a prescribed threshold.
-Consequently, we consider the threshold density that minimizes the maximal MSE.
-%
-Our results indicate that estimating the mean from one-bit measurements is equivalent to estimating the sample median from these measurements.
-In the adaptive case, this estimate can be done with vanishing error for any point in the parameter space.
-In the distributed case, this estimate can be done with vanishing error only for a finite number of possible values for the unknown mean.
-\end{abstract}
-
-%{\color{red}  See LASSO results in http://arxiv.org/abs/1506.02181v1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{sec:Intro}
-Estimating parameters from data collected and processed by multiple units may be limited due to communication constraints between these units. 
-%
-For example, this scenario arises in sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit.
-In these situations, the ability to estimate a particular parameter from the data is dictated not only by the quality of observations and their number but also by the available bandwidth for communicating between the sensors and the central estimator.
-The question that we ask is to what extent a parametric estimation task is affected by this constraint on communication, and what are the fundamental performance limits in estimating a parameter subject to such restriction.
-\par
-%%
-\begin{figure*}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto]
-
-  \node at (0,0) (source) {$X_1$} ;
- \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
-\node[below of = source2, node distance = 2.1cm] (source3) {$X_n$};
-
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};
-
-\draw[->,line width = 2pt] (source2) -- (enc2); 
-\draw[->,line width = 2pt] (source) -| (enc2); 
-\draw[->,line width = 2pt] (source3) -| (enc2);
-
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-
-\draw[->,line width = 2pt] (source2) -- (enc2); 
-\node[int1, right of = enc2, node distance = 2.7cm ] (est) {Est};
-
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {\small $B_1,\ldots,B_n$} (est);
-
-\node[right of = est, node distance = 1.2cm] (dest) {\small $\hat{\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=2pt] (est) -- (dest);
-\node at (2,-4.5) {(i) Centralized};
-\end{tikzpicture}
-%
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {\small $X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {Enc 1};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
- \node[below of = source, node distance = 1.5cm] (source2) {\small $X_2$};
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc 2};  
-\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source2, node distance = 2.1cm] (source3) {\small $X_n$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {Enc n};  
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim P_X$};
-
-\node[int1, right of = enc2, node distance = 3cm ] (est) {Est};
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);   
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$B_2$} (est);
-
-\draw[->] (enc1)+(0.7,0) -- +(0.7,-0.7) -| (enc2);
-
-%\draw[dashed,->] (enc2)+(0.7,0) -- +(0.7,-0.7) -| +(0,-1.2);
-\draw[->,line width = 2pt] (enc3) -| (est);
-
-%\node[below of = mes2, node distance = 1.5cm] (mes3) {$B_1,\ldots,B_{n-1} $};
-
-\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -1cm]  {$B_n$} (est);
-
-%\draw[->] (mes3.west) -- +(0,-0.5) -| (enc3);
-
-\node[below right = 2.3cm and 0.7cm of 
-enc1.center, yshift = 0.cm] (end) {$B_1,\ldots,B_{n-1}$};
-
-\draw[->] (enc1)+(0.7,0) -- (end.west) -| (enc3);
-
-\node[right of = est, node distance = 1.2cm] (dest) {$\hat{\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=2pt] (est) -- (dest);
-\node at (2,-4.5) {(ii) Adaptive};
-\end{tikzpicture}
-%
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {Enc 1};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
- \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc 2};  
-\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source2, node distance = 2.1cm] (source3) {$X_n$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {Enc n};  
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-
-\node[int1, right of = enc2, node distance = 2.1cm ] (est) {Est};
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
-
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$B_2$} (est);
-
-\draw[->,line width = 2pt] (enc3) -| (est);
-
-\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -1cm]  {$B_n$} (est);
-
-\node[right of = est, node distance = 1.2cm] (dest) {$\hat{\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=2pt] (est) -- (dest);
-\node at (2,-4.5) {(iii) Distributed};
-\end{tikzpicture}
-\end{center}
-\caption{\label{fig:setup} 
-Three encoding settings: (i) Centralized  -- an encoder sends $n$ bits after observing $n$ samples.
-(ii) Adaptive (sequential) --  each encoder sends a bit $B_n$ depending on its private sample $X_n$ and previous bits $B_1,\ldots,B_{n-1}$.
-(iii) Distributed  -- each encoder sends a single bit $B_i$ only based on its private sample $X_i$.}
-\end{figure*}
-%%
-
-This paper answers this question in a particular setting: the estimation of the mean $\theta$ of a symmetric log-concave distribution with finite variance, under the constraint that only a single bit can be communicated on each sample from this distribution.
-As it turns out, the ability to share information before committing on each one-bit message dramatically affects the performance in estimating $\theta$.
-We, therefore, distinguish among the three settings illustrated in Figure~\ref{fig:setup}
-\begin{itemize}
- \item[(i)\,\,] \emph{Centralized} encoding: all $n$ encoders confer and produce a single message consists of $n$ bits.
- \item[(ii)\,] \emph{Adaptive} or \emph{sequential} encoding: The $n$th encoder observes the $n$th sample and the $n-1$ previous bits.
- \item[(iii)] \emph{Distributed} encoding: The $n$th message is only a function of the $n$th sample.
- \end{itemize}
-Evidently, as far as information sharing is concerned, settings (iii) is a more restrictive version of (ii) which is more restrictive than (i).
-Below are three application examples for each of the settings (i)-(iii) above, respectively:
-\begin{itemize}
-\item {\bf Signal acquisition:} A quantity is measured $n$ times at different instances.
-The results are averaged in order to reduce measurement noise and the averaged result is then stored or communicated using $n$ bits.
-\item {\bf Analog-to-digital conversion:} A sigma-delta modulator (SDM) converts an analog signal into a sequence of bits by sampling the signal at a very high rate and then using one-bit threshold detector combined with a feedback loop to update an accumulated error state \cite{1092194}.
-Therefore, the MSE in tracking an analog signal using an SDM falls under our setting (ii) when we assume that the signal at the input to the modulator is a constant (direct current) corrupted by, say, thermal noise \cite{53738}.
-Since the sampling rates in SDM are usually many times more than the bandwidth of its input, analyzing SDM under a constant input provides meaningful lower bound even for non-constant signals.
-\item {\bf Privacy:} A business entity is interested in estimating the average income of its clients.
-In order to keep this information as confidential as possible, each client independently provides an answer to a yes/no question related to its income.
-\end{itemize}
-%
-We measure the performance in estimating $\theta$ by the mean squared error (MSE) risk.
-For an asymptotically normal estimator with a finite MSE risk $R_n$, we are interested in particular in the limit
-\[
-\lim_{n\to \infty} \frac{\sigma^2}{n R_n},
-\]
-describing the 
- \emph{asymptotic relative efficiency} (ARE) of the estimator compared to asymptotically normal estimators whose variances decreases as $\sigma^2/n+o(n^{-1})$.
-Estimators of this form include the empirical mean of the samples, and, under some conditions, the optimal Bayes estimator.
-\par
-%
-In addition to the examples above, the excess risk in estimating a fixed parameter due to a one-bit per measurement constraint is useful in bounding from below the excess risk in estimating a signal from its noisy measurements.
-Namely, the excess MSE or ARE we derive serves as the most optimistic estimate for the risk in estimating under the one-bit per measurement constraint a signal changing over time or space.
-Such estimation settings are considered in \cite{baraniuk2017exponential, jacques2013robust, plan2013one, li2017channel, choi2016near}.
-\\
-
-% given a prior distribution on the space $\Theta$ where $\theta$ resides. \\
-
-In setting (i), the estimator can evaluate the optimal mean estimator (e.g., the sample mean in the Gaussian case) and then quantize it using $n$ bits.
-Since the accuracy in describing the empirical mean decreases exponentially in $n$, the error due to quantization is negligible compared to the MSE in estimating the mean.
-Therefore, the ARE in this setting is $1$.
-Namely, asymptotically, there is no loss in performance due to the communication constraint under centralized encoding.
-%
-In this paper we show that a similar result does not hold in setting (ii): the ARE of any adaptive estimation scheme is at most the ARE of the sample median.
-Specifically, when the samples are drawn from the normal distribution, this ARE equals $2/\pi$, showing that the one-bit constraint increases the effective sample size in estimating $\theta$ by at least $\pi/2$ compared to estimating it without the bit constraint.
-We also show that this lower bound on the ARE is tight by providing an estimator that attains it.
-In fact, we show that only one adaptiveness, as illustrated in Figure~\ref{fig:one_round} is enough to achieve the optimal ARE.
-%
-Clearly, the penalty on the sample size in setting (iii) is at least as large as that in setting (ii).
-We show, however, that unlike in setting (ii), there is no distributed estimation scheme that is uniformly optimal in the sense that it attains the ARE of the sample median for all $\theta$ in the parameter space.
-This result is obtained by establishing local asymptotic normality of regularly enough encoding procedures for setting (iii), resulting in an exact characterization of the ARE of such procedures.
-To summarize our contributions, we establish that the optimal ARE in settings (i) is $1$, the optimal ARE in setting (ii) is ARE of the sample median, and no uniformly optimal procedure exists in setting (iii).
-
-% Instead, in setting (iii) we restrict ourselves to estimators from messages obtained by comparison against a prescribed value (that may be different for each sample).
-We show that the maximum likelihood (ML) estimator for $\theta$ from these messages is asymptotically local minimax, and its asymptotic variance is strictly greater than the variance of the median.
-Thus, at least when limited to threshold detection, the ability to adapt the threshold allows for a more efficient estimation.
-%This is in contrast to the \\ counterpart of our setting where $\theta$ is taken from a finite space
-
-It is important to note that although the ARE in setting (i) is one, this scheme already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation procedures.
-Indeed, the task of representing an unknown random quantity using $n$ bits is equivalent to designing a $2^n$ levels scalar quantizer \cite{gray1998quantization}.
-However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation problem and hence its exact value is unknown.
-As a result, a non-trivial exploration-exploitation trade-off arises even in this case.
-%Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$. 
-Therefore, while uncertainty due to quantization decreases exponentially in the number of bits $n$, hence the ARE is $1$, an exact expression for the MSE in this setting is still difficult to derive. 
-%
-The situation is even more involved in the adaptive encoding setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$ may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
-Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $n-1$ messages, is not guaranteed to be globally optimal.
-Therefore, while we characterize the optimal one-bit message given the previous messages, this characterization does not necessarily lead to an upper bound on the ARE.
-Instead, our result on the maximal ARE is obtained by bounding the Fisher information of any $n$ adaptive messages and using an appropriate information inequality.
-\par
-%
-%In addition to encoding and estimation schemes that lead to optimal results, we also consider two additional ``natural'' schemes.
-Specifically, in setting (ii) we consider the one-bit optimal scheme, i.e., the case of a greedy encoder that given the $n$th sample and the previous $n-1$ bits, provides a bit that minimizes the $n$-step MSE.
-In setting (iii) we also consider the case where the messages are obtained by comparing each sample against a prescribed threshold.
-This threshold may be different across samples and is assumed deterministic (independent of the data).
-
-\subsection*{Related Works}
-When the variance $\sigma^2$ is negligible compared the to desired accuracy, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is solved by a bisection style method over the parameter space.
-Therefore, the general case of non-zero variance is reminiscent of the noisy binary search problem with a possibly infinite number of unreliable tests \cite{cicalese2002least, Karp:2007:NBS:1283383.1283478}.
-However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a constant input corrupted by Gaussian noise.
-Using an SDM, Wong and Gray \cite{53738} showed that the output of the modulator converges to the true constant input almost surely, so that an SDM provides a consistent estimator for setting (ii).
-The rate of this convergence, however, was not analyzed and cannot be derived from the results of \cite{53738}.
-In particular, our results for setting (ii) imply that the asymptotic rate of convergence of the MSE in SDM to a constant input under an additive white Gaussian noise is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-Baraniuk et.
-al \cite{baraniuk2017exponential} also considered adaptive one-bit measurements in the context of analog-to-digital conversion, although without noise at the input.
-By establishing the lower bound of $\sigma^2\pi/2n$ on the MSE, we show that the main results of \cite{baraniuk2017exponential}, an exponential MSE decaying rate, does not hold in the noisy setting.
-Stated otherwise, the MSE in the setting of \cite{baraniuk2017exponential} may decay exponentially up to the noise level, after which it decays at most as $\sigma^2\pi/2n$.
-\par
-%
-One-bit measurements in the distributed setting (iii) was considered in \cite{904560,4244748, 6882252, chen2010performance, 5184907}, but without optimizing the encoders and their detection rules.
-Consequently, the performance derived in these works are not optimal.
- % analyzed the estimation from distributed quantized measurements when the same detection rule is applied by all encoders.
-However, the error criterion considered in these works is the Fisher information rather than the MSE risk or ARE criterion.
-\par
-%Once the decision rule of each encoder is fixed, the optimal estimation of $\theta$ is determined using the maximum a posteriori probability rule.
-Hence, the distributed setting is reduced to finding the optimal decision rule of each encoder.
-The work of \cite{52470} addresses the counterpart of our setting (iii) in the case of hypothesis testing, although the results there cannot be extended to parametric estimation.
-When the parameter space $\Theta$ is finite, Tsitsiklist \cite{tsitsiklis1988decentralized} showed that when the cardinality of $\Theta$ is at most $M$ and the probability of error criterion is used, then no more than $M(M-1)/2$ different detection rules are necessary in order to attain probability of error decreasing exponentially with the optimal exponent.
-%That is, beyond $M(M-1)/2$ some decision rules can be repeated without losing optimality.
-Furthermore, in a version of this problem for the adaptive setting \cite{5751320}, it was shown that, with specific two-stage feedback, there is no gain in feedback compared to the fully distributed setting.
-Our results imply that the ARE in the distributed setting with threshold detection rules is strictly larger than that in the adaptive setting for almost all points in $\Theta$, suggesting that the case where the cardinality of $\Theta$ is finite is different from the case where $\Theta$ is an open set.\par
-%
-As we explain in detail in Section~ \ref{sec:preliminary}, the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}, leads to lower bounds on the MSE in setting (iii).
-For the case of a Gaussian distribution, this lower bound bounds the ARE to be at most $3/4$.
-Thus, while this bound on the ARE provides no new information compared to the upper bound of $2/\pi$ we derive for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimum even under the one bit per sample constraint.
- \par
-% 
-Finally, we note that minimax estimation under limited communication with an arbitrary number of bits per node was considered in 
-\cite{zhang2013information, duchi2014optimality}.
-The specialization of the results in \cite{zhang2013information, duchi2014optimality} to our settings (ii) and (iii) leads to looser lower bounds then the ones we derive in this paper.
-Looser bounds can also be obtained from works considering general inference and distributed estimation problems under data compression constraint \cite{DBLP:journals/corr/abs-1802-08417, zhang1988estimation, han2018distributed, xu2017information, Barnes2018}.
-In particular, the subsequent work of \cite{Barnes2018} uses an approach similar to ours to derive lower bound on the error in various parametric estimation problems from quantized measurements.
-\\
-
-The remainder of this paper is organized as follows.
-In Section~\ref{sec:problem} we describe the problem and useful notation.
-In Section~\ref{sec:preliminary} we provide two simple bounds on the efficiency and MSE.
-Our main results for the adaptive and distributed cases are given in Sections~\ref{sec:sequential} and \ref{sec:distributed}, respectively.
-In Section~\ref{sec:conclusions} we provide concluding remarks.
-
-\section{Problem Formulation \label{sec:problem}}
-
-Let $f(x)$ be a symmetric and log-concave density function with a finite second moment $\sigma^2$.
-For $\theta \in \Theta$, denote by $P_X$ the probability distribution with density $f\left( x-\theta \right)$.
-Therefore, $P_X$ is an absolutely continuous log-concave distribution with mean $\theta$ and variance $\sigma^2$.
-Symmetry and log-concavity of $f(x)$ imply that $P_X$ is strongly unimodal (has a unique local maxima) with its mode at $x =\theta$ \cite{ibragimov1956composition}.
-We further assume that the \emph{parameter space} $\Theta$ is a closed interval of the real line.
-\par
-In some situations it is useful to assume that $\theta$ is drawn once from the prior distribution $\pi$ on $\Theta$.
-In this case we assume that $\pi$ is an absolutely continuous distribution, and denote its density by $\pi(\theta)$, i.e., $\pi(d\theta) = \pi(\theta)d\theta$.
-\par
-The random variables $X_1,\ldots,X_n$ represent $n$ independent samples from $P_X$. 
-We are interested in estimating $\theta$ from a set of $n$ binary messages $B_1,\ldots,B_n$, obtained from $X_1,\ldots,X_n$ under three possible scenarios illustrated in Figure~\ref{fig:setup}: 
-\begin{itemize}
-\item[(i)~~] Centralized $B_i(X_1,\ldots,X_n)$, $i=1,\ldots,n$.
-\item[(ii)~] Adaptive $B_i(X_i,B_1,\ldots,B_{i-1})$, $i=2,\ldots,n$.
-\item[(iii)] Distributed $B_i(X_i)$, $i=1,\ldots,n$.
-\end{itemize}
-
-The performance of an estimator $\hat{\theta}_n \triangleq \hat{\theta}_n(B^n)$ in any of these cases is measured according to the mean squared error (MSE) risk:
-\begin{equation}
-\label{eq:error_def}
-R_n \triangleq \mathbb E\left(\hat{\theta}_n - \theta \right)^2,
-\end{equation}
-where the expectation is taken with respect to the distribution of $X_1,\ldots,X_n$ and, whenever available, a prior distribution $\pi(\theta)$ over $\Theta$.  
-%It is well known that minmax estimation error 
-%\begin{equation}
-%R_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left(\hat{\theta}_n - \theta \right)^2 | \theta \right],
-%\end{equation}
-%can be obtained from $R_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}. 
-%
-The main problems we consider in this paper are the minimal value of \eqref{eq:error_def}, as a function of $n$ and $f(x)$, under different choices of the encoding functions in cases (i), (ii), and (iii).
-\\
-
-We give particular attention to the ARE of estimators with respect to an asymptotically normal efficient estimator that is not subject to the bit constraint.
-Specifically, let $\{a_n,\,n\in \mathbb N\}$ be a sequence such that
-\[
-\sqrt{a_n}\left(\hat{\theta}_n - \theta\right) \overset{D}{\longrightarrow} \mathcal N(0, \sigma^2).
-\]
-Then the ARE of $\hat{\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
-\[
-\ARE(\hat{\theta}_n) \triangleq
-\lim_{n\rightarrow \infty} \frac{a_n}{n}. 
-\]
-Note that in the special case where there exists $V \in \mathbb R$ such that
-\[
-a_n \mathbb E \left(\hat{\theta}_n - \theta \right)^2 = V + o(1),
-\]
-with $o(1)\to 0$ as $n\to \infty$, then the ARE of $\hat{\theta}_n$ is finite and equals $\sigma^2/V$. \\
-
-In addition to the notation above, we also denote by $F(x)$ the cumulative distribution function of $X_i$, and define
-\begin{equation} \label{eq:eta_def}
-\eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))} =  \frac{f(x)f(-x)}{F(x)F(-x)}, 
-\end{equation}
-where the last equality is due to symmetry of $f(x)$. We note that 
-\begin{equation}
-\label{eq:eta_h}
-\eta(x) = h(x)h(-x) = f(x) \left( h(x) + h(-x) \right), 
-\end{equation}
-where 
-\[
-h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
-\]
-is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function since $f(x)$ is log-concave \cite{bagnoli2005log}. 
-%
-For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as illustrated in Fig.~\ref{fig:eta}. 
-%
-In this paper we only consider the normal distribution and other log-concave symmetric distributions for which this property of $\eta(x)$ holds. Specifically, we require the following:
-\begin{assump} \label{assump:failure_rate}
- $\eta(x)$ has a unique maximum (at the origin) and is a non-increasing function of $|x|$. 
-\end{assump}
-%That is, Assumption~\ref{assump:failure_rate} says that $\eta'(x) < 0 $ for all $x>0$. 
-Under this assumption we have, 
-\[
-4f^2(x) \leq \eta(x) \leq \eta(0),
-\] 
-%
-where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median.
-Combined with log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that $\eta(x)$ vanishes as $|x|\rightarrow \infty$.
-\par
-%
-Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions).
-Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.
-\\
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -3, xmax=3, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.9,
-samples=10, 
-xlabel= $x$,
-xtick={-2,-1,0,1,2},
-xticklabels={-2,-1,0,1,2},
-ytick={0,0.3989423,0.6366198},
-yticklabels={0,$\frac{1}{\sqrt{2 \pi}}$,$2/\pi$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\eta(x)$};
-\addplot[domain = -5:5, samples = 50, color = red, solid, smooth]  {exp(-x^2/2) / sqrt(2*3.14159)};
-\addlegendentry{$\phi(x)$};
-\addplot[domain = -5:5, samples = 50, color = black, solid, dashed]  {4*exp(-x^2) / (2*3.14159)};
-\addlegendentry{$4\phi^2(x)$};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -4, xmax=4, 
-restrict y to domain = -10:0,
-ymin = -10,
-samples=10, 
-xlabel= $x$,
-xtick={-3,-2,-1,0,1,2,3},
-xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,-0.45158,-0.919},
-yticklabels={0,,},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\log \eta(x)$};
-\addplot[domain = -5:5, samples = 30, color = red, solid, smooth]  {-(x)^2/2 -0.9189};
-\addlegendentry{$\log \phi(x)$};
-\end{axis}
-\end{tikzpicture}
-\caption{
-The function $\eta(x) = f^2(x) / F(x)F(-x)$ for $f(x) = \phi(x)$ the standard normal density.
-\label{fig:eta}
-}
-\end{center}
-\end{figure}
-
-\section{Consisten Estimation and Existing Bounds \label{sec:preliminary}}
-%On a first impression, it may not be clear whether consistent estimation of the mean is even possible in the adaptive and centralized settings.
-On the other hand, it may seem as if estimation in these cases is trivial as in the centralized setting (i).
-%
-We next settle such skepticism by deriving lower and upper bounds to the relative efficiency under setting (iii).
-
-In this section, we derive lower and upper bounds on the relative efficiency under setting (iii) using known results. These bounds establish the following facts:
+In this section we adapt known results to derive lower and upper bounds on the relative efficiency under setting (iii). These bounds establish the following facts:
 \begin{itemize}
@@
 \label{eq:estimator_naive}
-\hat{\theta}_n = \theta_0 + F^{-1}\left( p_n \right)
+{\theta}_n = \theta_0 + F^{-1}\left( P_n \right)
 \end{equation}
-is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set.
-Furthermore, the variance of $p_n$ is $F(\theta-\theta_0)F(\theta_0-\theta)$, and hence the delta method implies that $\hat{\theta}_n$ is asymptotically normal with variance
+is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set due to log-concavity.
+Furthermore, the variance of $P_n$ is $F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)$, and hence the delta method implies that ${\theta}_n$ is asymptotically normal with variance
 \begin{equation} 
-\frac{1}{
-\eta(\theta-\theta_0)} = \frac{F(\theta-\theta_0)F(\theta_0-\theta)}{f^2(\theta-\theta_0)}. 
+ \frac{F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}{f^2(\theta-\theta_0)} = \frac{1}{
+\eta(\theta-\theta_0)}.
 \end{equation}
-In particular, the ARE of $\hat{\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
-In other words, for a prescribed accuracy, $\hat{\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
+In particular, the ARE of ${\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
+In other words, for a prescribed accuracy, ${\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
 \par
@@
 %
-Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of $\hat{\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
-This ARE is attained only when $\theta_0 = \theta$, although $\theta$ is unknown apriori.
-Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of $\hat{\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
-As an example, when $f(x)$ is a normal density, the ARE of $\hat{\theta}_n$ is $\approx 0.07$ when $\theta_0$ is $2.33$ standard deviations from $\theta$.
-Therefore, the estimator $\hat{\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
+Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of ${\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
+This ARE is attained only when $\theta_0 = \theta$, whereas $\theta$ is apriori unknown.
+Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of ${\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
+As an example, when $f(x)$ is a normal density, the ARE of ${\theta}_n$ is less than $\approx 0.14$ when $\theta_0$ is $2$ standard deviations from $\theta$.
+Therefore, the estimator ${\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
 \par
-It is suggested that lower variance can be obtained by an estimator of the form \eqref{eq:estimator_naive} if, after observing a batch of the single bit messages, one can update the threshold value $\theta_0$.
-Such a scheme falls within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
-\\
-% variance equals to $1/\eta(0)n + o(1)$.
-We also show in Section~\ref{sec:sequential} that no estimator can attain variance that is asymptotically smaller than $1/\eta(0)n$, so that the ARE of any estimator in settings (ii) and (iii) is at least $\eta(0) \sigma^2$.
+It is suggested that we can attain lower variance in estimation by updating the threshold value $\theta_0$ in \eqref{eq:estimator_naive} after observing one or a batch of the single bit messages.
+Schemes with such adaptation fall within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
+\par
 
@@
 \]
-and transmits $R_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates $\hat{\theta}_1,\ldots,\hat{\theta}_k$ with the goal of minimizing the average MSE:
+and transmits $r_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates ${\theta}_1,\ldots,{\theta}_k$ with the goal of minimizing the quadratic risk:
 \[
-D_{CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - \hat{\theta}_j \right)^2 \right]. 
+R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - {\theta}_j \right)^2 \right]. 
 \]
-Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $R_1=\ldots=R_n = 1$.
+Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $r_1=\ldots=r_n = 1$.
 It follows that, assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
@@
  \par
-When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k\to \infty$ were fully characterized in \cite{prabhakaran2004rate}.
-Furthermore, the work of \cite{chen2004upper} provided an expression for MSE attained in the CEO setting under Gaussian priors.
+When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k$ goes to infinity were fully characterized in \cite{prabhakaran2004rate}.
+Furthermore, the work of \cite{chen2004upper} provided an expression for quadratic risk attained in the CEO setting under Gaussian priors.
 Adapting to our setting, this expression provides the following proposition:
 \begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$. Then any estimator $\hat{\theta}_n$ of $\theta$ in the distributed setting satisfies
+Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is arbitrary.
+Then any estimator ${\theta}_n$ of $\theta$ in the distributed setting satisfies
 \begin{equation} \label{eq:ceo_bound}
- n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + O(n^{-1}),
+ n \ex{\left( \theta - \theta_n \right)^2} \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
 \end{equation}
@@
 In other words, it is the ability to exploit the geometry of a high-dimensional product probability space that distinguishes between the CEO problem with one bit per encoder on average and the mean estimation problem from one-bit measurements in the distributed setting.
-
-\section{Adaptive Estimation \label{sec:sequential}}
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $\eta(0)\sigma^2$, which is the ARE of the median of the sample $X_1,\ldots,X_n$.
-We also provide a particular adaptive estimation scheme that attains this maximal efficiency.
-%Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $B_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages.
-%Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $\eta(0)\sigma^2$.
-
-\subsection{Limited efficiency in the adaptive setting}
-Our first result asserts that the ARE of any adaptive encoding and estimation scheme is bounded from above by $\eta(0)\sigma^2$. %This result follows from the following theorem:
-\begin{thm}[maximal relative effeciency] \label{thm:adpative_lower_bound}
-Let $\hat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Figure~\ref{fig:setup}-(ii). Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-n\mathbb E\left[ (\theta-\hat{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0},
-\]
-where 
-\[
-I_0 = \mathbb E \left( \frac{d}{d\theta} \log \pi (\theta) \right)^2
-\]
-is the Fisher information with respect to a location model in $\theta$. 
-\end{thm}
-
-\subsubsection*{Sketch of Proof}
-The main idea in the proof is to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
-Once this bound is achieved, the result follows by using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are in the Appendix.\\
-
-Theorem~\ref{thm:adpative_lower_bound} implies that any estimator $\hat{\theta}_n$ from any adaptive encoding scheme satisfies
-\[
-n\mathbb E\left[ (\theta-\theta_n)^2 \right] \leq  \frac{1}{4f^2(0)}+O(n^{-1}),
-\]
-and 
-\[
-\ARE(\hat{\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
-\]
-
-Next, we present an adaptive encoding and estimation scheme that attains the maximal ARE of $\eta(0)\sigma^2$.
-
-\subsection{Asymptotically optimal estimator}
-Let $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ be a strictly positive sequence. Consider the following estimator $\hat{\theta}_n$ for $\theta$:  
-\begin{equation}
-\label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n B_n, \quad n = 1,2,\ldots,
-\end{equation}
-where 
-\begin{equation}
-B_n = B_n (X_n,\theta_{n-1}) =\sgn (X_n - \theta_{n-1}).
-\end{equation}
-Define the $n$th step estimation as
-\begin{equation} \label{eq:sgd_est}
-\hat{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
-\end{equation}
-
-We have the following results:
-\begin{thm} \label{thm:sgd}
-Consider the sequence $\left\{\hat{\theta}_n,\, n\in \mathbb N \right\}$ defined by \eqref{eq:sgd_est}. 
-\begin{enumerate}
-\item[(i)] Assume that $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ satisfies
-\begin{equation} \label{eq:conditions1}
-\begin{cases}
-\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
-\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
-\mathrm{for~some~}0< \lambda \leq 1
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Then
-\[
-\sqrt{n} \left( \hat{\theta}_n - \theta \right) \overset{d}{\rightarrow} \mathcal N \left(0,  1/\eta(0) \right).
-\]
-\item[(ii)] Assume that in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ satisfies
-\begin{equation} \label{eq:conditions2}
-\begin{cases}
-\gamma_n = o(n^{-2/3}), &  \\
-\sum_{n=1}^\infty \gamma_n = \infty.  & \\
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ with $2/3<\beta<1$). Then
-\[
-\lim_{n\rightarrow \infty} n\mathbb E \left[ \left(\theta-\hat{\theta}_n \right)^2 \right] = \frac{1}{\eta(0)}. 
-\]
-\end{enumerate}
-\end{thm}
-
-\subsubsection*{Proof}
-The asymptotic behavior of \eqref{eq:sgd_est} follows from \cite[Thm. 4]{polyak1992acceleration} and \cite[Thm. 2]{polyak1990new}. The details are in the Appendix. \\
-
-Theorem~\ref{thm:sgd} implies that the estimator $\hat{\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the maximal ARE as established by Theorem~\ref{thm:adpative_lower_bound}.
-The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$.
-Consequently, the procedure above is known as averaged stochastic gradient descent for minimizing $x \to |x|$ given the data $X_1,\ldots,X_n$.
-The minimal value of this optimization is the sample median, and Theorem~\ref{thm:sgd} provides conditions for the sequence of gradient steps so that the algorithm converges to this minimum.
- \par
-%Note that $\theta_0$ is not explicitly defined in equation \eqref{eq:sgd_est}.
-A reasonable initialization for $\theta_0$ is $\theta_0 = \mathbb E [\theta]$, although Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
-Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$.
-\\
-In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $B_n$ depends on its private sample as well as the current gradient descent estimate $\theta_{n-1}$.
-In this sense, each encoder in this algorithm interacts with previous one by using the current estimate.
-%
-As we explain next, 
-it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ with only one round of interactions among the encoders.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {Enc};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
-% \node[below of = source, node distance = 1cm] (source2) {$X_2$};
-%\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};  
-%\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {Enc};
-
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[below of = source, node distance = 0.5cm] {$\vdots$};
-
-\node[int1, right of = enc3, node distance = 2.1cm ] (est) {Est 1};
-
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
-
-%\draw[->,line width = 2pt] (enc2) -| node[above, xshift = -1cm] (mes2) {$B_2$} (est);
-
-\draw[->,line width = 2pt] (enc3) -- node[above, xshift = 0cm]  {$B_{n_1}$} (est);
-
-\node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
-\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {Enc$(\hat{\theta}_1)$};  
-\draw[->,line width = 2pt] (sourceB) -- (enc1B);
-
-\node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
-\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {Enc$(\hat{\theta}_1)$};  
-\draw[->,line width = 2pt] (source3B) -- (enc3B); 
-\node[below of = sourceB, node distance = 0.4cm] {$\vdots$};
-
-\node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {Est 2};
-
-\draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.8cm] {$B_{n_1+1}$} (estB);
-\draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);
-
-\draw[->,line width = 0.5pt] (est.east) node[above, xshift  =0.5cm] {$\hat{\theta}_{n_1}$} -| (enc1B.north);
-
-\draw[->,line width = 0.5pt] (enc1B) -- (enc3B);
-
-%\draw[->,line width = 1pt] (enc1B)  -- node[right] {$\hat{\theta}_{n_1}$} (enc3B);
-
-\draw[->,line width = 2pt] (estB) -- +(0.8,0) node[right] {$\hat{\theta}_n$};
-\end{tikzpicture}
-\end{center}
-\caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
-\label{fig:one_round}
-}
-\end{figure}
-
-\subsection{Optimality using a Single Interaction}
-In Section~\ref{sec:preliminary} we considered an estimator that is based on messages of the form 
-\[
-B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
-\]
-and showed that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
-%
-We now show that a similar encoding leads to an asymptotically normal estimator with the minimal variance $1/\eta(0)$, provided we allow at least once to update the threshold value $\theta_0$. 
-%
-In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
-We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate $\hat{\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use $\hat{\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$.
-Figure~\ref{fig:one_round} illustrates a diagram of this procedure.
-%
-The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
-\begin{thm}
-For $i=1,\ldots,n$ set
-\[
-B_i = \begin{cases}
- \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
- \mathbf 1_{X_i \geq \hat{\theta}_{n_1} }& i={n_1+1,\ldots,n},
-\end{cases}
-\]
-where $n = n_1+ n_2$ and 
-\[
-\hat{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
-\frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
- \right).
-\] 
-Let 
-\[
-\hat{\theta}_{n_2}  = \hat{\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
-\]
-and assume that $n_1(n) \rightarrow \infty$ and $n_1(n)/n \rightarrow 0$. Then:
-\begin{align*}
- \sqrt{n} \left( \hat{\theta}_{n_2} - \theta  \right)^2  \overset{D}{\longrightarrow}  \mathcal N\left( 0, 1/\eta(0) \right).
-\end{align*}
-\end{thm}
-%
-%
-\begin{proof}
-For $t\in \mathbb R$, set
-\[
-p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
-\]
-From the central limit theorem
-\begin{align*}
-& \sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)  = \sqrt{\frac{n}{n_2}} \sqrt{n_2} \left(  p_{n_2}(t) - F(\theta - t) \right) \\
-& \overset{D}{\rightarrow} \mathcal N\left( 0, V(t) \right),
-\end{align*}
-where
-\[
-V(t) \triangleq F(\theta - t) F \left( t - \theta\right). 
-\]
-Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ we obtain
-\begin{align*}
-& \sqrt{n} \left( t + F^{-1}(\hat{p}_{n_2}(t)) - \theta \right) \\
-&= \sqrt{n} \left( g(\hat{p}_{n_2}(t)) - g \left(F(\theta-t) \right)  \right) \\
-& \overset{D}{\to} \mathcal N\left(0, 
-1/\eta(\theta-t) \right).
-\end{align*}
-%where this convergence is uniform in $t$ since all moments of $F^{-1}(\hat{p}_{n_2})$ exists. 
-By the law of large numbers we also have
-\[
-p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
-\]
-so that $\hat{\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity, and thus 
-\[
-\eta( \hat{\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
-\]
-By Slutsky's theorem we get
-\begin{align*}
-& \sqrt{n}\left(\hat{\theta}_{n_2} - \theta\right) \\
-& = \sqrt{n} \left( \hat{\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}(\hat{\theta}_{n_1})) - \theta \right)  \\
-& \overset{D}{\to} \mathcal N\left( 0, 
-1/\eta(0) \right). 
-\end{align*}
-\end{proof}
-%
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=10cm, height=6cm,
-xmin = 0, xmax=800, 
-restrict y to domain = 0:3,
-ymin = 0,
-ymax = 3.4,
-samples=10, 
-xlabel= $n$,
-ylabel = {$n\mathbb E \left[\left(\theta - \hat{\theta}_n \right)^2 \right]$},
-%xtick={-3,-2,-1,0,1,2,3},
-%xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,1,1.57},
-yticklabels={0,1,$\pi/2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-
-\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{asymptotically optimal};
-
-%\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
-
-\addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{single interaction};
-
-\end{axis}
-\end{tikzpicture}
-%\begin{tikzpicture}
-%\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
-%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left(\hat{\theta}_n - \theta \right)^2$};
-%\node[scale = 0.7] at (0,-2.4) {$n$};
-%\end{tikzpicture}
-\caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.
-In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$.
-The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage.
-\label{fig:adaptive_error}  }
-\end{center}
-\end{figure}
-
-\section{Distributed Estimation \label{sec:distributed}}
-We now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii).
-In this setting each one-bit message $B_i$ is only a function of its private sample $X_i$, and hence $B_i$ characterized by its \emph{detection region}, defined as
-\[
-A_i = \left\{ x \in \mathbb R \,:\, B_i(x) = 1 \right\}.
-\]
-Consequently, $B_i$ is of the form
-\[
-B_i = \begin{cases} 1 & X_i \in A_i, \\
--1 & X_i \notin A_i,
-\end{cases} \quad i\in \mathbb N,
-\]
-where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\\
-
-As a first step, we provide conditions under which the messages $B_1,B_2,\ldots$ define a local asymptotic normal family.
-
-\begin{thm} \label{thm:LAN1}
-For $n \in \mathbb N$ and $A_n \subset \mathbb R$,  define
-\begin{equation}
-\label{eq:precision_general}
-L_n(A_1,\ldots,A_n;\theta) \triangleq \frac{1}{n} \sum_{i=1}^n \frac{ \left(\frac{d}{d \theta} \Prob(X_i \in A_i) \right)^2 }{ \Prob(X_i \in A_i)\left(1- \Prob(X_i \in A_i) \right) }. 
-\end{equation}
-Consider the following conditions:
-\begin{itemize}
-\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is a log-concave, differentiable and symmetric density function such that $\eta(x)$ is unimodal.
-\item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
-\item[(iii)] The limit 
-\begin{equation}
-\label{eq:LAN_lim}
-\kappa(\theta) \triangleq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
-\end{equation}
-exists. 
-\end{itemize}
-For $i=1,\ldots,n$ set
-\[
-B_n = \begin{cases} 1 & X_n \in A_n, \\
--1 & X_n \notin A_n. 
-\end{cases} 
-\]
-For any $\theta$, $f(x)$ and a sequence of sets $A_1,A_2,\ldots$ such that (i)-(iii) hold, and any $h\in \mathbb R$, we have
-\begin{align*}
-& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (B_1,\ldots,B_n) }{
-\mathbb P_{\theta} (B_1,\ldots,B_n)} \\
-& \overset{D}{\longrightarrow} \mathcal N\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
-\end{align*} 
-\end{thm}
-Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}. 
-%
-Among these conditions, (iii) is arguably the strongest and hardest to verify.
-As we show in Section~\ref{subsec:threshold} below, this condition is satisfied, for example, when $A_1, \ldots,A_n$ are half lines whose starting points are drawn independently from some probability measure on $\mathbb R$.
-Similar ideas imply that condition (iii) holds whenever we choose the intervals consisting each $A_i$ according to some pre-specified distribution.
-\par
-%
-An important conclusion of  Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models (e.g. \cite{van2000asymptotic}):
-\begin{cor} \label{cor:LA_minimax}
-Let $\hat{\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
-Then for any bounded, symmetric, and quasi-convex function $L$,
-\begin{align*}
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\hat{\theta}_{n} - \tau) \right) \right]
-\\
-& \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
-\end{align*}
-where $Z \sim \mathcal N(0,1)$. In particular, for $L(x) = x^2$, 
-\begin{align*}
-\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( \hat{\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
-\end{align*}
-\end{cor}
-%
-Corollary~\ref{cor:LA_minimax} says that when the messages define a LAN model, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model at $\theta$.
-This fact poses the upper bound of $\kappa(\theta)\sigma^2$ for the ARE of estimators in such models.
-\\
-
-Next, we show that under LAN no estimator can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly for all $\theta \in \Theta$.
-
-\subsection{Non-existence of a Uniformly Optimal Strategy}
-We now show that under LAN models, the optimal minimal risk $1/\eta(0)$ can only be attained at a finite number of points within $\Theta$.
-This fact implies in particular that, unlike in the adaptive setting, no distributed estimation scheme has ARE of $\eta(0)\sigma^2$ for all $\theta \in \Theta$.
-
-\begin{thm} \label{thm:non_existence}
-Under conditions (i)-(iii) in Theorem~\ref{thm:LAN1}, assume that each $A_i$ is a union of at most $K$ intervals.
-The number of points $\theta \in \Theta$ satisfying $\kappa(\theta) = \eta(0)$ is at most $2K$.
-\end{thm}
-
-\begin{proof}
-See Appendix. 
-\end{proof}
-
-We next consider the case where each detection region is a half-open interval, i.e., the $i$th message is obtained by comparing $X_i$ against a single threshold.
-As we explain next, the existence of a density for the sequence of thresholds is enough to establish local asymptotic normality and leads to a closed form expression for the precision parameter and the ARE.
-
-%In the adaptive setting, it follows from Theorem~\ref{thm:sgd} that messages of this kind with appropriately chosen thresholds lead to an estimator with the optimal ARE of $\eta(0)sigma^2$.
-However, Theorem~\ref{thm:non_existence} implies that such ARE can only be attained for a negligible subset of the parameter space.
-As we shall see next, messages obtained via a comparison against a sequence of thresholds cannot attain the optimal efficiency one more than a single point of $\Theta$.
-
-\subsection{Threshold Detection \label{subsec:threshold}}
-Assume now that each $B_i$ is of the form
-\begin{equation}
-\label{eq:threshold_message}
-B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
--1 & X_i > t_i,
-\end{cases}  
-\end{equation}
-where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder.
-In other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and $\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$.
-It follows that
-\begin{equation}
-L_n(A_1,\ldots,A_n;\theta) = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
-\label{eq:Ln_threshold}
-\end{equation}
-A natural condition for the existence of the limit \eqref{eq:Ln_threshold} as $n\to \infty$ is that the empirical distribution of the threshold values converges to a probability measure.
-Specifically, for an interval $I \subset \mathbb R$ define
-\[
-\lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
-\]
-Theorem~\ref{thm:LAN1} implies:
-\begin{cor} \label{cor:LAN_thresh}
-Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$.
-Then $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a LAN family with precision parameter
-\[
-\kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
-\]
-\end{cor}
-The condition that $\lambda_n$ converges to a probability measure is satisfies, for example, whenever the $t_1,\ldots,t_n$s are drawn independently from a probability distribution $\lambda(dt)$ on $\mathbb R$.
-\par
-Due to local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by 
-$\hat{\theta}^{ML}_n$, is local asymptotic minimax in the sense that 
-\[
-\sqrt{n} \left( \hat{\theta}^{ML}_n - \theta \right) \overset{D}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
-\]
-It follows that when the density of the threshold values converges to a probability measure, the ARE of the ML estimator is $\kappa(\theta)\sigma^2$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-We note that $\hat{\theta}^{ML}_n$ is given by the root of
-\begin{equation}
-\label{eq:ML}
-\sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) },  
-\end{equation}
-which is the derivative of the log-likelihood function.
-This root is unique since the log-likelihood function is concave.
-Furthermore, for any $n \in \mathbb R$, we have that $\hat{\theta}^{ML}_n  \in [t_{(1)}, t_{(n)}]$ where $t_{(i)}$ denotes the $i$th element of $\{t_1,t_2\ldots\}$.
-Therefore, if $\{t_1,t_2\ldots\}$ is bounded (for example $\{t_1,t_2\ldots\} \subset \Theta$), then
-\[
-\lim_{n\to \infty} n\left(\hat{\theta}^{ML}_n - \theta \right)  = 1/\kappa(\theta), 
-\] 
-so that the ML estimator attains the local asymptotic MSE of Corollary~\ref{cor:LA_minimax}. \par
-%
-Since $\eta(x)$ attains its maximum at the origin, we conclude that
-\[
-\kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
-\]
-This upper bound on $\kappa(\theta)$ implies that the ARE of any distributed estimator based on a sequence of threshold detectors does not exceed $\eta(0)\sigma^2$, a fact that agrees with the lower bound under adaptive estimation derived in Theorem~\ref{thm:adpative_lower_bound}.
-%
-This upper bound on $\kappa(\theta)$ is attained only when $\lambda$ is the mass distribution at $\theta$.
-Since $\theta$ is apriori unknown, we conclude that estimation in the distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting.
-In other words, the ability to choose the threshold values in an adaptive manner based on previous messages strictly improves relative efficiency compared to a non-adaptive threshold selection.
-\\
-
-%We conclude that when the density of the threshold values converges to a probability measure, the ARE of the ML is $\kappa(\theta)$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-
-%
-We conclude this section by considering the density of the threshold values that maximizes the ARE $\kappa(\theta)$ under the worst choice of $\theta \in \Theta$.
-
-\subsection{Minimax Threshold Density}
-The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta = [-T,T]$ is given as the solution to the following optimization problem:
-\begin{align}
-\label{eq:var_cvx_minimax}
-\begin{split}
-\mathrm{maximize} \quad &  \inf_{\theta \in [-T,T]} \int \eta(t-\theta) \lambda(dt)
-\\ 
-\mathrm{subject~to} 
-\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
-\end{split}
-\end{align}
-The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program.
-We denote by $\kappa^\star(T)$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum.
-%
-%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
-%\begin{align}
-%\label{eq:cvx_minimax}
-%\begin{split}
-%\mathrm{maximize} \quad &  K \\ 
-%\mathrm{subject~to} 
-%\quad &  K \leq \mathbf H\lambda \\
-%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
-%\end{split}
-%\end{align}
-%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
-%\begin{rem}
-%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$.
-Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points.
-Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using
-%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
-%\end{rem}
-
-Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$.
-The minimal asymptotic risk $\kappa^\star(\theta)$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $T$.
-Also illustrated in these Figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
-\begin{align}
-& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
- \\
-& = 
-\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
-= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
-\end{align}
-From Corollary~\ref{cor:LAN_thresh}, we conclude that the ARE under a uniform distribution is $\kappa_\unif \sigma^2$. \\
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-title = {$\sigma/T = 1/2$},
-ytick={0,0.1,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.6,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/T = 1/5$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.5},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.5},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.3,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma / T = 1/10$},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.2},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.2},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.15,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma / T = 1/20$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:minimax_support}
-Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \mathcal N(\theta,\sigma^2)$ and $\theta \in \Theta = [-T,T]$.
-%
-The continuous curve (red) represents the reciprocal of the asymptotic risk for at a fixed $\theta \in \Theta$ under the optimal density, so the minimax risk is the inverse of its minimal value.
-The dashed curve (green) is the reciprocal of the asymptotic risk for a fixed $\theta$ under a uniform distribution of threshold values over $\Theta$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
-}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmax=2.5, 
-xmode = log,
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=1, 
-xlabel= {$\sigma/T$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,0.637,1},
-yticklabels={0,$2/\pi$,1},
-ylabel = {$\ARE$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{optimal threshold density};
-
-\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{uniform threshold desnity};
-\end{axis}
-\end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \mathcal N(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
-The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
-}.
-\end{center}
-\end{figure}
-
-%We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
-Next, we prove that with any set of messages obtained via a distributed strategy, there exists at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-title = {$\sigma/\sigma_{\theta} = 1$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 2$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma/\sigma_{\theta} = 3$},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 4$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:opt_density}
-Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=b^2/3$ is the variance of the prior.
-}
-\end{center}
-\end{figure}
-
- We consider now the problem of minimizing the asymptotic Bayes risk $
-R_{\pi,\lambda} \triangleq \mathbb E  K^{-1}(\theta)$ over all probability measures $\lambda(dt)$ with support in $\mathbb R$. This optimization problem can be written as follows:
-\begin{align}
-\label{eq:cvx_average}
-\begin{split}
-\mathrm{minimize} \quad & R_{\pi,\lambda} =  \int \frac{\pi(d\theta)}{ \int \eta \left( t-\theta\right) \lambda(dt)}. \\ 
-\mathrm{subject~to} \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) =1. 
-\end{split}
-\end{align}
-We denote by $R^\star_{\pi}$ the minimal value of the objective function in \eqref{eq:cvx_average}.
-Since the function $x \rightarrow 1/x$ is convex for positive values, \eqref{eq:cvx_average} defines a convex optimization problem in $\lambda$ whose solution depends on the prior $\pi$.
-The solution to this problem is approximated by considering $\lambda$ and $\pi$ over a discrete set.
-On Figure~\ref{fig:opt_density} we illustrate the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distributon ($P_X = \mathcal N(\theta, \sigma^2)$) and the prior on $\theta$ is uniform over $\Theta = [-b,b]$.
-Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
-\par
-\begin{figure}
-\begin{center}
-
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = 0, xmax=2, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 10,
-samples=1, 
-xlabel= {$\sigma/\sigma_\theta$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,1.5708,5},
-yticklabels={0,$\pi/2$,5},
-ylabel = {$R_{\pi}^\star/\sigma^2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-\addplot[color = black, dashed] {3.14159 / 2};
-\end{axis}
-\end{tikzpicture}
-\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \mathcal N(\theta, \sigma^2)$under an optimal threshold distribution $\lambda^\star$ for $\pi$ the uniform distribution over $\Theta = [-0.5,0.5]$.
-%
-%versus $\sigma/\sigma_\theta = 2\sqrt{3}\sigma$.
-The distribution $\lambda^\star$ is the minimizer of \eqref{eq:cvx_average}.
-It is illustrated for various cases in Fig.~\ref{fig:opt_density}.
-The dashed curve represents the upper bound \eqref{eq:upper_bound}.
-\label{fig:dist_bound_uniform}  }
-\end{center}
-\end{figure}
-
-As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \mathcal N(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution.
-In this case, the ML estimator reduces to the estimator $\hat{\theta}_n$ of \eqref{eq:estimator_naive}.
-As the following proposition shows, the Bayes risk for this choice of $\lambda$ is maximal, and thus provides an upper bound on the Bayes risk under any $\lambda$.
- \eqref{eq:cvx_average}. 
-\begin{prop}\label{prop:upper_bound}
-For any prior $\pi(d\theta)$ and $\theta_0$ in the support of $\eta(x)$ we have
-\begin{equation} 
-\label{eq:upper_bound}
-R_\pi^\star  \leq 
- \int \frac{\pi(d\theta)}{\eta \left( \theta_0 - \theta \right)},
-\end{equation}
-Furthermore, assuming that $\theta_0 = \mathbb E \theta$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
-\begin{equation}
-\label{eq:bound_Taylor}
-R^\star_\pi \leq \frac{1}{4 f^2(0)} + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right) \sigma_\theta^2 + O(\sigma_\theta^3).
-\end{equation}
-\end{prop}
-\begin{proof}
-The function $x \rightarrow 1/x$ is convex for positive values, hence Jensen's inequality implies
-\[
-\left( \int \eta \left( t-\theta\right) \lambda(dt) \right)^{-1}  \leq \int  \frac{ \lambda(dt)}{ \eta \left( t-\theta\right)  }. 
-\]
-Therefore, the expected value of $\kappa^{-1}(\theta)$ satisfies
-\begin{align}
-\mathbb E  \frac{1}{\kappa(\theta)}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
-\end{align}
-The bound \eqref{eq:upper_bound} is obtained by taking $\lambda$ to be a mass distribution at any $\theta_0$ in the support of $\eta(x)$.
-Finally, \eqref{eq:bound_Taylor} is obtained by expanding $1/\eta(x)$ to a third order Taylor series around zero
-%\[
-%1/\eta(x) = \frac{1}{4f^2(0)}  + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right)  x^2 + O(x^3),
-%\]
-and taking its expectation with respect to $\pi$ at $x=\theta_0-\theta$. 
-\end{proof}
-We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so taking $\theta_0 = \mathbb E \theta$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
-The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$.
-The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $\kappa^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.
-
-\begin{example} \label{ex:bound}
-In the normal case $P_X = \mathcal N(\theta, \sigma^2)$, the bound in \eqref{eq:bound_Taylor} implies 
-\[
-\frac{R^\star_\pi}{\sigma^2}  \leq \frac{\pi}{2} + \left( \frac{\pi}{2} -1 \right) \left( \frac{ \sigma_\theta}{\sigma} \right)^2 + O \left(  \frac{\sigma_\theta} { \sigma} \right)^3. 
-\]
-It follows that the ARE approaches its maximal value of $2/\pi$ whenever $\sigma_\theta/\sigma$ is small.
-The exact value of \eqref{eq:upper_bound} in this case, as well as the Bayes ARE with the optimal threshold density $\lambda^\star$ for a uniform $\pi$, are illustrated in Fig.~\ref{fig:dist_bound_uniform}.
-%i.e., each encoder simply reports "$1$" or "$-1$" whenever $X_i$ is larger or smaller than $\theta_0$, respectively.
-Intuitively, an accurate estimation of $\theta$ in this case is possible only if a sufficient mix of ''$1$''s and ''$-1$''s is obtained from the sample.
-When $\sigma_\theta^2$ is high compared to $\simga^2$, one of the events $"1"$ or "$-1"$ becomes too rare to
-\end{example}
-
-\section{Conclusions \label{sec:conclusions}}
-We considered the MSE risk in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
-%
-In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency (ARE) larger than that of the median of the samples.
-We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median.
-%We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
-\par
-In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and ARE. 
-%
-We conclude that under such conditions, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in the distributed setting.
-%
-We further considered the special case of messages obtained by comparing against a prescribed sequence of thresholds.
-We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.
- \\
-
-%\section*{ACKNOWLEDGMENT}
-%This research is supported in parts by...
-%Tsachy Weissman, Stefano Rini, Robert Gray.
-
-\onecolumn
-
-\appendices
-
-\section{Proofs \label{app:proofs}}
-
-\subsection{Proof of Proposition~\ref{prop:ceo_lower_bound}}
-
-First, we note that when $f(x) = \mathcal N(0,\sigma^2)$ and $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$, our distributed setting reduces to the Gaussian CEO problem with $R_1=\ldots = R_n =1$ and $k=1$.
-Therefore, any MSE attained in our distributed setting is also attained by the CEO and thus the optimal CEO strategy (with arbitrary $k$) provides a lower bound to the MSE in our setting.
-\\
-
-Consider the minimal distortion $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
-from \cite[Eq. 10]{chen2004upper}:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-For the special case of $R_\Sigma = n$ and $L=n$, we get
-\begin{equation} \label{eq:ceo_optimal_sumrate2}
-n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, this $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
-\[
-D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO distortion while enforcing the condition $R_1=\ldots = R_n = 1$.
-Indeed, an upper bound for the CEO distortion under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
-\[
-D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
-\]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.
-
-\begin{lem} \label{lem:bound_intervals}
-Let $f(x)$ be a log-concave, symmetric, and differentiable density such that $\eta(x)$ is strongly unimodal. For any $x_1 > \ldots > x_n \in \mathbb R$, 
-\begin{equation}
-\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-\leq \max_i \eta(x_i). \label{eq:lem_bound_intervals}
-\end{equation}
-In particular, if $|x_i|>\epsilon > 0$ for all $i=1,\ldots,n$, then 
-\[
-\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-\leq \eta(\epsilon) < 0. 
-\]
-\end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals}} 
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-so 
-\[
-\eta(x) =  \frac{  \left(\delta_1(x) \right)^2}{\Delta_1(x)
-(1-\Delta_1(x))}
-= \frac{  \left( f (x) \right)^2}{ F(x)\left(1-F(x)\right)^2}. 
-\]
-We use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:lem_bound_intervals} is bounded from above by $\max_i \eta(x_i)$. The case $n=1$ is trivial. Assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^2} 
-{\Delta_n \left(1- \Delta_n \right) } \leq \max_i \eta(x_i)
-\label{eq:lem_bound_intervals_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  2 \log \delta_N -  \log \Delta_N -  \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(-1)^{k+1} f(x_k)}{1-\Delta_N },
-\]
-and we conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-%
-Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable. We have 
-\[
-\frac{f'(x)}{f(x)} = c'(x), \quad x\in \mathbb R,
-\]
-which is anti-symmetric, non-negative for $x<0$,  non-positive for $x>0$, and non-increasing since $c(x)$ is concave.
-Therefore, if $c'(x_i) = c'(x_{i+1})$ for some $i =1,\ldots,N-1$, then either (1) $x_i = x_{i+1}$ or (2) $c'(x)$ is the zero function.
-Since (2) violates the assumption that $f(x)$ is a density function, we conclude that $c'(x)$ is an injection.
-%
-As a result, \eqref{eq:gradient_zero} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_proof} equals $\eta(x_1) = \max_i \eta(x_i)$ hence the statement holds.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$, or  $x_i, x_{i+1}$ for some $i$.
-It is left to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Under case (1) we have
-\begin{align*}
-\lim_{x_N \to -\infty} \frac{  \delta_N^2} 
-{\Delta_N \left(1- \Delta_N \right) }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^2} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)} ,
-\end{align*}
-which is smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis. Under case (2) we have
-\begin{align*}
-&  \lim_{x_1 \to \infty}
-\frac{ \delta_N} 
-{\Delta_N\left(1- \Delta_N \right) } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right) \left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right) }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^2 } 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right) },
-\end{align*}
-where $x'_{m} = x_{m+1}$. The last expression is also smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis.  \QEDA \\
-
-\subsection*{Proof of Theorem~\ref{thm:adpative_lower_bound}}
-
-We first prove the following lemma:
-\begin{lem} \label{lem:fisher_bound}
-Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that $\eta(x)$ is unimodal. For a Borel measurable $A$ set, 
-\[
-M(X) = \begin{cases} 1,& X \in A, \\
--1, & X \notin A.
-\end{cases}
-\]
-Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $\eta(0)$.
-\end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
-When $f(x)$ is the normal density function, this lemma follows from \cite[Thm.
-3]{Barnes2018}.
-The proof below is based on a different techique than in \cite{Barnes2018}, and is valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}.
-\\
-
-The Fisher information of $M$ with respect to $\theta$ is given by
-\begin{align}
-I_\theta & =  \mathbb E \left[ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta \right] \nonumber \\
-& = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
-& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\
-& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\ 
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
-\end{align}
-where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$.
-Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
-\[
-\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
-\]
-which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$.
-It is therefore enough to proceed in the proof assuming that $A$ is of the form
-\[
-A = \cup_{j=1}^k (a_j,b_j),
-\]
-with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
-\begin{align*}
-\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
-& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
-\end{align*}
-so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
-\begin{align}
-& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
-{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
-& \times \frac {1} 
-{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
-\label{eq:lemma_J}
-\end{align}
-It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $4f^2(0)$.  \QEDA \\
-
-We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
-\begin{equation}
-\label{eq:general_messages}
-B_i = \begin{cases}
-X_i \in A_i & 1, \\
-X_i \notin A_i & -1,
-\end{cases} 
-\end{equation}
-where $A_i \subset \mathbb R$ is a Borel measurable set. 
-%Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
-Consider the conditional distribution $P({B^n|\theta})$ of $B^n$ given $\theta$. We have 
-\begin{align}
-P\left( B^n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
-\end{align}
-where $P\left(B_i =1 | \theta, B^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B^n$ with respect to $\theta$ is given by 
-\begin{align}
-I_\theta(B^n) = \sum_{i=1}^n I_\theta (B_i|B^{i-1}),
-\label{eq:fisher_information}
-\end{align}
-where $I_\theta (B_i|B^{i-1})$ is the Fisher information of the distribution of $B_i$ given $B^{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B^{i-1}) \leq 4f^2(0)$.
-The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
-\begin{align*}
-\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(B^n) + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
-& \geq \frac{1}{ 4f^2(0) n + I_0}.
-\end{align*}
-
-\QEDA
-
-\subsection*{Proof of Theorem~\ref{thm:sgd}}
-The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.
-Specifically, (i) in Theorem~\ref{thm:sgd} follows from the following simplified version of \cite[Thm.
-4]{polyak1992acceleration}:
-\begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
-Let 
-\[
-X_i = \theta + Z_i,\quad i=1,\ldots,n,
-\]
-where the $Z_i$s are i.i.d. with zero means and finite variances. Define
-\begin{align*}
-\theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
-\hat{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
-\end{align*}
-where in addition, assume the following: 
-\begin{enumerate}
-\item[(i)] There exits $K_1$ such that $\left| \varphi(x) \right| \leq K_1(1+|x|)$ for all $x\in \mathbb R$.
-\item[(ii)] The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions \eqref{eq:conditions1}.
-\item[(iii)] The function $\psi(x) \triangleq \mathbb E \varphi(x+Z_1)$ is differentiable at zero with $\psi'(0)>0$, and satisfies $\psi(0)=0$ and $x\psi(x) >0$ for all $x\neq 0$.
-Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
-\begin{equation}
-\label{eq:Polyak_Juditsky_cond3}
-\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
-\end{equation}
-\item[(iv)] The function 
-$\chi(x) \triangleq \mathbb E \varphi^2(x+Z_1)$ is continuous at zero. 
-\end{enumerate}
-Then $\hat{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}(\hat{\theta}_n - \theta)$ converges in distribution to $\mathcal N(0,V)$, where
-\[
-V = \frac{ \chi(0)} {\psi'^2(0)}. 
-\]
-\end{thm}
-
-Using the notation above, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have that $\chi(x) = \mathbb E \sgn^2(x+Z_1) = 1$, so $\chi(0) = 1$. In addition,
-\begin{align*}
-\psi(x) & = \mathbb E \sgn(x+ Z_1) = \int_{-\infty}^\infty \sgn(x+z) f(z) dz \\
-& = \int_{-x}^\infty f(z) dz -\int_{-\infty}^{-x} f(z) dz. 
-\end{align*}
-Using the symmetry of $f(x)$ around zero, it follows that $\psi'(x) = 2f(x)$ and thus $\psi'(0) = 2f(0)$.
-It is now easy to verify that the rest of the conditions in Theorem~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$.
-Since
-\[
-\frac{\chi(0)}{\psi'^2(0)} = \frac{1}{4 f^2(0)},
-\]
-Theorem~\ref{thm:sgd}-(i) follows from Theorem~\ref{thm:polyak_juditsky}.  \\
-
-In order to prove part (ii) of Theorem~\ref{thm:sgd} we use the following result from \cite{polyak1990new}:
-\begin{thm}{ \cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
-Let
-\begin{align} \label{eq:polyak_new_measurements}
-\begin{cases}
-U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = g'(U_{n-1})+Z_n \\
-\bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
-\end{cases}
-\end{align}
-Assume that the function $g(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative.
-In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \mathbb R$.
-Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution for which the Fisher information exits.
-Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{thm:polyak_juditsky}-(iii) and satisfies the conditions there.
-Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$,
-and there exits $K_3$ such that 
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] \leq K_3(1+|x|^4). 
-\]
-Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions  \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
-\[
-V_n \triangleq \mathbb E \left[ \left(\bar{U}_n-x^\star \right)^2 \right] = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
-\]
-\end{thm}
-
-We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = -\sgn(-x)$, $Z_n = \theta-X_n$ and $U_n = \theta_n$. From \eqref{eq:polyak_new_measurements} we have
-\begin{align*} 
-\theta_n & = \theta_{n-1} + \gamma_n \sgn(\theta-\theta_{n-1} - Z_n )  \\
-& = \theta_{n-1} + \gamma_n \sgn(X_n-\theta_{n-1} ),
-\end{align*}
-so the estimator $\hat{\theta}_n$ defined by $\hat{\theta}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] = 1 \leq K_3(1+|x|^4)
-\]
-for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
-the conditions in Theorem~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
-In particular, $\psi'(0) = (2f(0))^{-2}$.
-Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$.
-Theorem~\ref{thm:polyak_new} implies
-\[
-n V_n = \mathbb E \left[ \left(\hat{\theta}_n-\theta \right)^2 \right]  = \frac{1}{4 f^2(0)} + o(1).
-\]
-\QEDA
-
-\subsection*{Proof of Theorem~\ref{thm:LAN1}}
-The log probability mass distribution of $B^n=(B_1,\ldots,B_n)$ is given by
-\begin{align*}
-& \log \Prob_\theta(b^n) = \sum_{i=1}^n \left( \frac{b_i+1}{2} \log  \Prob(X_i\in A_i) + 
-\frac{1-b_i}{2} \log \Prob(X_i\in A_i) \right), \quad b^n \in \{-1,1\}^n. 
-\end{align*}
-Consequently, 
-\begin{align}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) } = \sum_{i=1}^n    \frac{b_i+1}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} + 
-\sum_{i=1}^n  \frac{1-b_i}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}. 
-\label{eq:LAN_proof1}
-\end{align}
-For each $i=1,\ldots,n$, write 
-\[
-A_i = \bigcup_{k=1}^{K_i} \left(t_{i,k},t_{i,k+1} \right),
-\]
-where $t_{i,1}<\ldots<t_{i,K_i}$ and, with a slight abuse of notation, $t_{i,1}$ and $t_{i,K_i}$ may also be $-\infty$ or $+\infty$, respectively. Thus
-\[
-\Prob_{\theta}(X_i \in A_i) = \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta).
-\]
-In particular, since $f$ is differentible, $\Prob_{\theta}(X_i \in A_i)$ is twice differentiable, and we may write
-\begin{align*}
-\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)  = \Prob_{\theta} (X_i \in A_i) + \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \frac{h}{\sqrt{n}} + o(h), 
-\end{align*}
-and thus
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} = \log \left(1 + \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} + o(h) \right) \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2 + o(h^2).
-\end{align*}
-Similarly, we have
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 + o(h^2).
-\end{align*}
-From \eqref{eq:LAN_proof1} we obtain
-\begin{align*}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
-\left( 
-\frac{b_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-b_i}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}   \right) \\
- & - \frac{h^2}{2n} 
- \sum_{i=1}^n 
-\left( 
- \frac{b_i+1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-b_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 \right) + o(h^2) \\
-\end{align*}
-%
-Noting that 
-\[
-\frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} = \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)},
-\]
-the proof is completed by proving the following two claims:
-\begin{itemize}
-\item[I.] 
-For $i=1,\ldots,n$ denote 
-\[
-U_i = \frac{B_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-B_i}{2}  \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}. 
-\]
-Then 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0, \kappa(\theta) \right). 
-\]
-\item[II.]
-For $i=1,\ldots,n$ denote 
-\[
-V_i =  \frac{B_i-1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-B_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2.
-\]
-Then 
-\[
-\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} \kappa(\theta). 
-\]
-\end{itemize}
-\subsubsection*{Proof of Claim I}
-First note that 
-\begin{align*}
-\mathbb E  [U_i] & = 
- \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=1)   + 
- \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=-1)  = 0. 
-\end{align*}
-In addition,
-\begin{align*}
-& \mathbb E U_i^2 = 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2  \Prob (B_i=1)   + 
-\left( \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2 \Prob (B_i=-1) \\
-& =
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)} +  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)} \\
- & =  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left(1-\Prob_{\theta}(X_i \in A_i) \right)} 
-\end{align*}
-Therefore
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 = L_n(A_1,\ldots,A_n) \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ such that the limit above exists.
-We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition for his version of the central limit time: for any $\delta>0$ we have that
-\begin{align*}
-& \mathbb E \left| U_i \right|^{2+\delta} =
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} 
-\end{align*}
-and
-\begin{equation}
-\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} } { \left( \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta} = 
-\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
-\label{eq:Lyaponov}
-\end{equation}
-Next, we claim that there exits $\delta>0$ and $K>0$, that are independent of $n$, such that
-\begin{align}
-\frac{1}{n} \sum_{i=1}^n \mathbb E  |U_i|^{2+\delta}  < M \label{eq:Lyaponov_num}
-\end{align} 
-for all $n$ large enough. To see this, note that
-\begin{align*}
-& \mathbb E |U_i|^{2+\delta} = 
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}  \\
-  &  = \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} } 
-  \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \\
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}, 
-\end{align*}
-where the last transition is because 
-\[
- \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \leq 1. 
-\]
-We now use the fact that each $A_i$ is a finite union of interval and consider the following lemma, proof of which is given in the appendix:
-\begin{lem} \label{lem:bound_intervals_delta}
-Let $f(x)$ be a log-concave, symmetric, and differentiable PDF such that $\eta(x)$ is unimodal.  There exists $\delta>0$ such that for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, 
-\begin{equation}
-\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^{2+\delta} }
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} } 
-\leq  2^\delta f^{2+\delta}(0). 
-\label{eq:lem_bound_intervals_delta}
-\end{equation}
-\end{lem}
-
-Lemma~\ref{lem:bound_intervals_delta} implies 
-\begin{align*}
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} = \frac{\left| \sum_{k=1}^{K_i} (-1)^k f(x_{i,k}-\theta) \right|^{2+\delta} }
-  { \left( \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta} \left( 1 - \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta}} \\
-  & \leq 2^\delta f^{2+\delta}(0). 
-\end{align*}
-In particular, we conclude that 
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} \leq 2^\delta f^{2+\delta}(0), 
-\]
-and thus for any $\delta>0$ the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we conclude that 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0,\kappa(\theta) \right). 
-\]
-
-\subsubsection*{Proof of Claim II} 
-We have:
-\begin{align*}
-\mathbb E V_i  & = 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)}  
-+ 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)}  \\
- & = 
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left( 1-\Prob_{\theta}(X_i \in A_i) \right)}  
-\end{align*}
- We conclude that:
-\begin{equation} \label{eq:LAN_limit_cond}
-\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =   L_n(A_1,\ldots,A_n)  \to \kappa(\theta)
-\end{equation}
-Since the $V_i$s are independent of each other, Kolmogorov's law of large numbers implies
-%(e.g. \cite[Theorem 10.2.3]{sen1994large}) 
-\[
-\frac{1}{n} \sum_{i=1}^n  V_i \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ for which the limit \eqref{eq:LAN_limit_cond} exists.
-
-\QEDA
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals_delta}} 
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-and 
-\[
-\eta_\delta(x) \triangleq  \frac{  \left(\delta_1(x) \right)^{2+\delta}}{  \left(\Delta_1(x)  \right)^{1+\delta}
-(1-\Delta_1(x))^{1+\delta}}
-= \frac{  \left( f (x) \right)^{2+\delta}}{ \left(F(x) \right)^{1+\delta}(1-F(x))^{1+\delta}}. 
-\]
-The proof is by induction on $n$.
-For the case $n=1$ the LHS of \eqref{eq:lem_bound_intervals_delta} equals $\eta_\delta(x)$.
-Note that $\eta_\delta(0) = 2^\delta f^{2+\delta}(0)$, so it is enough to prove that $\eta_\delta(0)$ attains it maximum at $x=0$.
-We have $\eta_\delta(x) = \eta^{1+\delta}(x)/f^\delta(x)$, and thus
-\[
-\log \eta_\delta'(x) = (1+\delta) \frac{\eta'(x)}{\eta(x)} - \delta \frac{f'(x)}{f(x)}. 
-\]
-By Assumption~\ref{assump:failure_rate} both terms above are negative for $x>0$, so that $\log \eta_\delta'(x) \leq 0$ if and only if
-\begin{equation} \label{eq:delta_proof_cond}
-(1+\delta) \left| \frac{\eta'(x)}{\eta(x)} \right| \geq \delta \left| \frac{f'(x)}{f(x)} \right|, \qquad x>0.
-\end{equation}
-Also by Assumption~\ref{assump:failure_rate}, for $x>0$ we have
-\[
-0 > (\log \eta(x))' = \frac{h'(x)}{h(x)}-\frac{h'(-x)}{h(-x)},
-\]
-so that \eqref{eq:delta_proof_cond} is satisfies for $\delta>0$ small enough.
-
-Next, assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^{2+\delta}} 
-{\left(\Delta_n \right)^{1+\delta}\left(1- \Delta_n \right)^{1+\delta} } \leq \eta_\delta(0) = 2^\delta f^{2+\delta}(0) . 
-\label{eq:lem_bound_intervals_delta_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%If $x_{i+1} = x_i$ for some $i=1,\ldots,N-1$, then then the indices $i$ and $i+1$ may  be removed from all sums in \eqref{eq:lem_bound_intervals}, what brings us to the case $n = N-2$.
-Therefore, we may assume that $x_1 < \ldots < x_n$.
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  (2+\delta) \log \delta_N - (1+\delta) \log \Delta_N - (1+\delta) \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{(2+\delta) (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(1+\delta)(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(1+\delta)(-1)^{k+1} f(x_k)}{1-\Delta_N }.
-\]
-We conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero_delta}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N(1+\delta)}{2+\delta} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-From the same reason as in the proof of Lemma~\ref{lem:bound_intervals}, \eqref{eq:gradient_zero_delta} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_delta_proof} equals $\eta_\delta(x_1)$ which was shown to be smaller than $\eta_\delta(\epsilon)$.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_delta_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$,  $x_i, x_{i+1} = -\epsilon$ for some $i$, or $x_i, x_{i+1} = \epsilon$ for some $i$.
-It is therefore enough to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Assume first $x_N \rightarrow -\infty$. Then 
-\begin{align*}
-\frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)^{1+\delta} } ,
-\end{align*}
-which is smaller than $\eta_\delta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
-\begin{align*}
-& \frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right)^{1+\delta} }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^{2+\delta}} 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)^{1+\delta}\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right)^{1+\delta} },
-\end{align*}
-where $x'_{m} = x_{m+1}$ for $m=1,\ldots, N-1$. The last expression is smaller than $\eta_{\delta}(0)$ by the induction hypothesis.  \QEDA \\
-
-\subsection*{Proof of Theorem~\ref{thm:non_existence}}
-
-Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta) = \eta(0)$. 
-%
-Since $B_1,B_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, for $\theta \in \Xi$ if and only if
-\begin{equation}
-\label{eq:non_existence_proof}
-\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0). 
-\end{equation}
-By assumption, we have $B_i^{-1} = A_i$ where $A_i$ can be expressed as
-\[
-A_i = \cup_{i=1}^K (a_{i,k},b_{i,k}), 
-\]
-where $a_{i,1} \leq b_{i,1} \leq \ldots \leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values $-\infty$ and $\infty$, respectively. Denote
-\[
-\mathcal B_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\}.
-\]
-For any $\theta$ and $\epsilon>0$, denote 
-\[
-S_n(\theta, \epsilon) \triangleq \left\{ i\leq n \,:\, (\theta-\epsilon,\theta+\epsilon) \cap \mathcal B_i \neq \emptyset \right\}
-\]
-In words, $S_n$ contains all integers smaller than $n$ in which an $\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals consisting $A_i$. 
-%
-We now claim that 
-if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. Indeed, for such $\theta$ we have
-\begin{align}
-& L_n(A_1,\ldots,A_n; \theta) \nonumber \\
-& = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
-\frac{ \left(\sum_{k=1}^{K}  f(\theta - b_{i,k})- f(\theta - a_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& 
-+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(b_{i,k}-\theta) - f(a_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& \overset{(a)}{\leq}
-\frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
- \label{eq:non_existence_proof1}
-\end{align}
-where $(a)$ follows from Lemma~\ref{lem:bound_intervals} and the fact that for $i \in S_n(\theta, \epsilon)$, 
-\[
-\max\left\{ \max_k \eta(b_{i,k}-\theta) , \max_k \eta(a_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
-\]
-Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, \eqref{eq:non_existence_proof1}, and thus $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.
-\par
-For $k\in \mathbb N$, assume by contradiction that there exists $N \geq 2K + 1$ distinct elements
-$\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$ consists of at most $K$ intervals, we have that 
-\begin{equation}
-\label{eq:few_optimality_points_proof}
-\card (\cup_{i=1}^n \mathcal B_i) \leq 2 n K. 
-\end{equation}
-Fix $\epsilon>0$ such that 
-\[
-\epsilon < \frac{1}{2}\min_{i\neq j} |\theta_i - \theta_j|. 
-\]
-Since for each $\theta \in \Theta$ we have $S_n(\theta, \epsilon) \to 1$, there exists $n$ large enough such that 
-\[
-\card \left(S_n(\theta_i, \epsilon) \right) \geq n \left(1-\frac{1}{2N} \right)
-\]
-for all $i=1,\ldots,N$.
-However, $S_n(\theta_1,\epsilon), \ldots S_n(\theta_N,\epsilon)$ are disjoint, so the cardinallity of their union is at least $n\left(1-\frac{1}{2N} \right)N$ which is grater than $2nK + n/2$ in contradiction to \eqref{eq:few_optimality_points_proof}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEfull,onebit}
-
-\end{document}

### 2019-09-23 problem-formulation.tex
Adding a bib file

--- 2019-02-21 onebit_full_V2.tex
@@
-%\documentclass[letterpaper]{IEEEtran}
-\documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper
-
-%LatexiDiff ignore tikz:
-% $: latexdiff -c "PICTUREENV=(?:picture|tikzpicture|DIFnomarkup)[\w\d*@]*" old.tex new.tex > diff.tex
-
-%\IEEEoverridecommandlockouts                              %
-
-%\usepackage{mathcomSTEP}
-
-%\overrideIEEEmargins 
-%\IEEEoverridecommandlockouts                              % This command is only needed if 
-% you want to use the \thanks command
-
-%\overrideIEEEmargins                                      % Needed to meet printer requirements.
-
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-\onecolumn
-
-\usepackage{mathptmx} 
-\usepackage{times} 
-\usepackage{amsmath} 
-\usepackage{amsbsy} 
-\usepackage{amssymb}
-%\usepackage{newtxtext, newtxmath}
-\usepackage{mathrsfs}
-\usepackage{comment}
-\usepackage[export]{adjustbox}
-\usepackage{tikz}
-\usetikzlibrary{external,positioning,decorations.pathreplacing,shapes,arrows,patterns}
-
-%\tikzexternalize[mode=list and make]
-\usepackage{algorithmicx}
-\usepackage{pgfplots}
-\usepackage{graphicx}
-\usepackage{pstool}
-\usepackage[latin1]{inputenc}
-\usetikzlibrary{arrows,shapes}
-\usepackage{xifthen}
-\usepackage{epic}
-%\usepackage{caption}
-\usepackage{epstopdf}
-
-\newtheorem{thm}{\bf{Theorem}}
-\newtheorem{cor}[thm]{\bf {Corollary}}
-\newtheorem{lem}[thm]{\bf {Lemma}}
-\newtheorem{prop}[thm]{\bf {Proposition}}
-\newtheorem{example}{\bf {Example}}
-\newtheorem{definition}{\bf {Definition}}
-\newtheorem{rem}{\bf {Remark}}
-\newtheorem{assump}{\bf {Assumptions}}
-
-\newcommand{\mmse}{\mathsf{mmse}}
-\newcommand{\unif}{\mathsf{unif}}
-\newcommand{\card}{\mathrm{card}}
-\newcommand{\ARE}{\mathsf{ARE}}
-\newcommand{\supp}{\mathrm{supp} }
-\renewcommand\vec[1]{\ensuremath\boldsymbol{#1}}
-\newenvironment{proof}{\paragraph*{Proof}}{\hfill$\square$ \newline}
-\newcommand{\sgn}{\mathrm{sgn} }
-\newcommand{\Prob}{\mathbb{P} }
-\newcommand{\argmax}{\mathrm{argmax}}
-\newcommand*{\QEDA}{\hfill\ensuremath{\square}}
-\newcommand{\CEO}{\mathsf{CEO}}
-
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-\tikzstyle{sint}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.8cm,thick ]
-\tikzstyle{sum}=[circle, fill=blue!10, draw=black,line width=1pt,minimum size = 0.5cm, thick ]
-\tikzstyle{ssum}=[circle, fill=blue!10,draw=black,line width=1pt,minimum size = 0.1cm]
-\tikzstyle{int1}=[draw, fill=blue!10, minimum height = 0.5cm, minimum width=0.7cm,thick ]
-\tikzstyle{enc}=[draw, fill=blue!10, minimum height = 2.7cm, minimum width=1cm,thick ]
-\tikzstyle{int}=[draw, fill=blue!10, minimum height = 1cm, minimum width=1.5cm,thick ]
-
-\author{
-    \IEEEauthorblockN{
-Alon Kipnis\IEEEauthorrefmark{1} and   
-    John C. Duchi\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}  \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}Stanford University, Department of Statistics \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Stanford University, Department of Electrical Engineering. }
-}
-
-\title{\LARGE \bf Mean Estimation from One-Bit Measurements}
-
-\begin{document}
-\graphicspath{{./Figs/}}
-\maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-We consider the problem of estimating the mean of a symmetric log-concave distribution under the following constraint: only a single bit per sample from this distribution is available to the estimator.
-We study the mean squared error risk in this estimation as a function of the number of samples, and hence the number of bits, from this distribution.
-%
-Under an adaptive setting in which each bit is a function of the current sample and previously recorded bits, we show that the optimal relative efficiency compared to the sample mean is the efficiency of the median.
-%For example, in estimating the mean of a normal distribution, a constraint of one bit per sample incurs a penalty of $\pi/2$ in sample size compared to the unconstrained case.
-%
-We also consider a distributed setting where each bit is only a function of a single sample.
-We show that the optimal efficiency of the adaptive setting can be attained by splitting the sample into two parts and allowing only a single adaptation.
-Otherwise, we show that no one sample estimation procedure can attain the optimal efficiency uniformly over all points in the parameter space.
-%
-%Finally, we analyze a distributed setting where the bits are obtained by comparing each sample against a prescribed threshold.
-Consequently, we consider the threshold density that minimizes the maximal MSE.
-%
-Our results indicate that estimating the mean from one-bit measurements is equivalent to estimating the sample median from these measurements.
-In the adaptive case, this estimate can be done with vanishing error for any point in the parameter space.
-In the distributed case, this estimate can be done with vanishing error only for a finite number of possible values for the unknown mean.
-\end{abstract}
-
-%{\color{red}  See LASSO results in http://arxiv.org/abs/1506.02181v1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{sec:Intro}
-Estimating parameters from data collected and processed by multiple units may be limited due to communication constraints between these units. 
-%
-For example, this scenario arises in sensor arrays where information is collected at multiple physical locations and transmitted to a central estimation unit.
-In these situations, the ability to estimate a particular parameter from the data is dictated not only by the quality of observations and their number but also by the available bandwidth for communicating between the sensors and the central estimator.
-The question that we ask is to what extent a parametric estimation task is affected by this constraint on communication, and what are the fundamental performance limits in estimating a parameter subject to such restriction.
-\par
-%%
-\begin{figure*}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto]
-
-  \node at (0,0) (source) {$X_1$} ;
- \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
-\node[below of = source2, node distance = 2.1cm] (source3) {$X_n$};
-
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};
-
-\draw[->,line width = 2pt] (source2) -- (enc2); 
-\draw[->,line width = 2pt] (source) -| (enc2); 
-\draw[->,line width = 2pt] (source3) -| (enc2);
-
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-
-\draw[->,line width = 2pt] (source2) -- (enc2); 
-\node[int1, right of = enc2, node distance = 2.7cm ] (est) {Est};
-
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {\small $B_1,\ldots,B_n$} (est);
-
-\node[right of = est, node distance = 1.2cm] (dest) {\small $\hat{\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=2pt] (est) -- (dest);
-\node at (2,-4.5) {(i) Centralized};
-\end{tikzpicture}
-%
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {\small $X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {Enc 1};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
- \node[below of = source, node distance = 1.5cm] (source2) {\small $X_2$};
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc 2};  
-\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source2, node distance = 2.1cm] (source3) {\small $X_n$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {Enc n};  
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim P_X$};
-
-\node[int1, right of = enc2, node distance = 3cm ] (est) {Est};
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);   
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$B_2$} (est);
-
-\draw[->] (enc1)+(0.7,0) -- +(0.7,-0.7) -| (enc2);
-
-%\draw[dashed,->] (enc2)+(0.7,0) -- +(0.7,-0.7) -| +(0,-1.2);
-\draw[->,line width = 2pt] (enc3) -| (est);
-
-%\node[below of = mes2, node distance = 1.5cm] (mes3) {$B_1,\ldots,B_{n-1} $};
-
-\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -1cm]  {$B_n$} (est);
-
-%\draw[->] (mes3.west) -- +(0,-0.5) -| (enc3);
-
-\node[below right = 2.3cm and 0.7cm of 
-enc1.center, yshift = 0.cm] (end) {$B_1,\ldots,B_{n-1}$};
-
-\draw[->] (enc1)+(0.7,0) -- (end.west) -| (enc3);
-
-\node[right of = est, node distance = 1.2cm] (dest) {$\hat{\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=2pt] (est) -- (dest);
-\node at (2,-4.5) {(ii) Adaptive};
-\end{tikzpicture}
-%
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {Enc 1};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
- \node[below of = source, node distance = 1.5cm] (source2) {$X_2$};
-\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc 2};  
-\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source2, node distance = 2.1cm] (source3) {$X_n$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {Enc n};  
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-%\node[above of = source3, node distance = 1cm] (dist) {$X_i \sim {\mathcal N} \left(\theta, \sigma^2 \right)$};
-\node[below of = source2, node distance = 0.5cm] {$\vdots$};
-
-\node[int1, right of = enc2, node distance = 2.1cm ] (est) {Est};
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
-
-\draw[->,line width = 2pt] (enc2) -- node[above, xshift = 0cm] (mes2) {$B_2$} (est);
-
-\draw[->,line width = 2pt] (enc3) -| (est);
-
-\draw[->,line width = 2pt] (enc3) -| node[above, xshift = -1cm]  {$B_n$} (est);
-
-\node[right of = est, node distance = 1.2cm] (dest) {$\hat{\theta}_n$};
-%         \node [int1] (dec) [right of=dest, node distance = 1.5cm,  align=center] {\small Dec };
-%\node [int1] (enc) [right of = dec, node distance = 3cm]{Enc}; 
-%\draw[->,line width=2pt] (dec) -- (dest);
-\draw[->, line width=2pt] (est) -- (dest);
-\node at (2,-4.5) {(iii) Distributed};
-\end{tikzpicture}
-\end{center}
-\caption{\label{fig:setup} 
-Three encoding settings: (i) Centralized  -- an encoder sends $n$ bits after observing $n$ samples.
-(ii) Adaptive (sequential) --  each encoder sends a bit $B_n$ depending on its private sample $X_n$ and previous bits $B_1,\ldots,B_{n-1}$.
-(iii) Distributed  -- each encoder sends a single bit $B_i$ only based on its private sample $X_i$.}
-\end{figure*}
-%%
-
-This paper answers this question in a particular setting: the estimation of the mean $\theta$ of a symmetric log-concave distribution with finite variance, under the constraint that only a single bit can be communicated on each sample from this distribution.
-As it turns out, the ability to share information before committing on each one-bit message dramatically affects the performance in estimating $\theta$.
-We, therefore, distinguish among the three settings illustrated in Figure~\ref{fig:setup}
-\begin{itemize}
- \item[(i)\,\,] \emph{Centralized} encoding: all $n$ encoders confer and produce a single message consists of $n$ bits.
- \item[(ii)\,] \emph{Adaptive} or \emph{sequential} encoding: The $n$th encoder observes the $n$th sample and the $n-1$ previous bits.
- \item[(iii)] \emph{Distributed} encoding: The $n$th message is only a function of the $n$th sample.
- \end{itemize}
-Evidently, as far as information sharing is concerned, settings (iii) is a more restrictive version of (ii) which is more restrictive than (i).
-Below are three application examples for each of the settings (i)-(iii) above, respectively:
-\begin{itemize}
-\item {\bf Signal acquisition:} A quantity is measured $n$ times at different instances.
-The results are averaged in order to reduce measurement noise and the averaged result is then stored or communicated using $n$ bits.
-\item {\bf Analog-to-digital conversion:} A sigma-delta modulator (SDM) converts an analog signal into a sequence of bits by sampling the signal at a very high rate and then using one-bit threshold detector combined with a feedback loop to update an accumulated error state \cite{1092194}.
-Therefore, the MSE in tracking an analog signal using an SDM falls under our setting (ii) when we assume that the signal at the input to the modulator is a constant (direct current) corrupted by, say, thermal noise \cite{53738}.
-Since the sampling rates in SDM are usually many times more than the bandwidth of its input, analyzing SDM under a constant input provides meaningful lower bound even for non-constant signals.
-\item {\bf Privacy:} A business entity is interested in estimating the average income of its clients.
-In order to keep this information as confidential as possible, each client independently provides an answer to a yes/no question related to its income.
-\end{itemize}
-%
-We measure the performance in estimating $\theta$ by the mean squared error (MSE) risk.
-For an asymptotically normal estimator with a finite MSE risk $R_n$, we are interested in particular in the limit
-\[
-\lim_{n\to \infty} \frac{\sigma^2}{n R_n},
-\]
-describing the 
- \emph{asymptotic relative efficiency} (ARE) of the estimator compared to asymptotically normal estimators whose variances decreases as $\sigma^2/n+o(n^{-1})$.
-Estimators of this form include the empirical mean of the samples, and, under some conditions, the optimal Bayes estimator.
-\par
-%
-In addition to the examples above, the excess risk in estimating a fixed parameter due to a one-bit per measurement constraint is useful in bounding from below the excess risk in estimating a signal from its noisy measurements.
-Namely, the excess MSE or ARE we derive serves as the most optimistic estimate for the risk in estimating under the one-bit per measurement constraint a signal changing over time or space.
-Such estimation settings are considered in \cite{baraniuk2017exponential, jacques2013robust, plan2013one, li2017channel, choi2016near}.
-\\
-
-% given a prior distribution on the space $\Theta$ where $\theta$ resides. \\
-
-In setting (i), the estimator can evaluate the optimal mean estimator (e.g., the sample mean in the Gaussian case) and then quantize it using $n$ bits.
-Since the accuracy in describing the empirical mean decreases exponentially in $n$, the error due to quantization is negligible compared to the MSE in estimating the mean.
-Therefore, the ARE in this setting is $1$.
-Namely, asymptotically, there is no loss in performance due to the communication constraint under centralized encoding.
-%
-In this paper we show that a similar result does not hold in setting (ii): the ARE of any adaptive estimation scheme is at most the ARE of the sample median.
-Specifically, when the samples are drawn from the normal distribution, this ARE equals $2/\pi$, showing that the one-bit constraint increases the effective sample size in estimating $\theta$ by at least $\pi/2$ compared to estimating it without the bit constraint.
-We also show that this lower bound on the ARE is tight by providing an estimator that attains it.
-In fact, we show that only one adaptiveness, as illustrated in Figure~\ref{fig:one_round} is enough to achieve the optimal ARE.
-%
-Clearly, the penalty on the sample size in setting (iii) is at least as large as that in setting (ii).
-We show, however, that unlike in setting (ii), there is no distributed estimation scheme that is uniformly optimal in the sense that it attains the ARE of the sample median for all $\theta$ in the parameter space.
-This result is obtained by establishing local asymptotic normality of regularly enough encoding procedures for setting (iii), resulting in an exact characterization of the ARE of such procedures.
-To summarize our contributions, we establish that the optimal ARE in settings (i) is $1$, the optimal ARE in setting (ii) is ARE of the sample median, and no uniformly optimal procedure exists in setting (iii).
-
-% Instead, in setting (iii) we restrict ourselves to estimators from messages obtained by comparison against a prescribed value (that may be different for each sample).
-We show that the maximum likelihood (ML) estimator for $\theta$ from these messages is asymptotically local minimax, and its asymptotic variance is strictly greater than the variance of the median.
-Thus, at least when limited to threshold detection, the ability to adapt the threshold allows for a more efficient estimation.
-%This is in contrast to the \\ counterpart of our setting where $\theta$ is taken from a finite space
-
-It is important to note that although the ARE in setting (i) is one, this scheme already poses a non-trivial challenge for the design and analysis of an optimal encoding and estimation procedures.
-Indeed, the task of representing an unknown random quantity using $n$ bits is equivalent to designing a $2^n$ levels scalar quantizer \cite{gray1998quantization}.
-However, the optimal design of this quantizer depends on the distribution of its input, which is the goal of our estimation problem and hence its exact value is unknown.
-As a result, a non-trivial exploration-exploitation trade-off arises even in this case.
-%Note that the only missing parameter in our setting is the mean, which, under setting (i), is known to the encoder with uncertainty interval proportional to $\sigma/\sqrt{n}$. 
-Therefore, while uncertainty due to quantization decreases exponentially in the number of bits $n$, hence the ARE is $1$, an exact expression for the MSE in this setting is still difficult to derive. 
-%
-The situation is even more involved in the adaptive encoding setting (ii): an encoding and estimation strategy that is optimal for $n-1$ adaptive one-bit messages of a sample of size $n-1$ may not lead to a globally optimal strategy upon the recipient of the $n$th sample.
-Conversely, any one-step optimal strategy, in the sense that it finds the best one-bit message as a function of the current sample and the previous $n-1$ messages, is not guaranteed to be globally optimal.
-Therefore, while we characterize the optimal one-bit message given the previous messages, this characterization does not necessarily lead to an upper bound on the ARE.
-Instead, our result on the maximal ARE is obtained by bounding the Fisher information of any $n$ adaptive messages and using an appropriate information inequality.
-\par
-%
-%In addition to encoding and estimation schemes that lead to optimal results, we also consider two additional ``natural'' schemes.
-Specifically, in setting (ii) we consider the one-bit optimal scheme, i.e., the case of a greedy encoder that given the $n$th sample and the previous $n-1$ bits, provides a bit that minimizes the $n$-step MSE.
-In setting (iii) we also consider the case where the messages are obtained by comparing each sample against a prescribed threshold.
-This threshold may be different across samples and is assumed deterministic (independent of the data).
-
-\subsection*{Related Works}
-When the variance $\sigma^2$ is negligible compared the to desired accuracy, the task of finding $\theta$ using one-bit queries in the adaptive setting (ii) is solved by a bisection style method over the parameter space.
-Therefore, the general case of non-zero variance is reminiscent of the noisy binary search problem with a possibly infinite number of unreliable tests \cite{cicalese2002least, Karp:2007:NBS:1283383.1283478}.
-However, since we assume a continuous parameter space, a more closely related problem is that of one-bit analog-to-digital conversion of a constant input corrupted by Gaussian noise.
-Using an SDM, Wong and Gray \cite{53738} showed that the output of the modulator converges to the true constant input almost surely, so that an SDM provides a consistent estimator for setting (ii).
-The rate of this convergence, however, was not analyzed and cannot be derived from the results of \cite{53738}.
-In particular, our results for setting (ii) imply that the asymptotic rate of convergence of the MSE in SDM to a constant input under an additive white Gaussian noise is at most $\sigma^2\pi/2$ over the number of feedback iterations.
-Baraniuk et.
-al \cite{baraniuk2017exponential} also considered adaptive one-bit measurements in the context of analog-to-digital conversion, although without noise at the input.
-By establishing the lower bound of $\sigma^2\pi/2n$ on the MSE, we show that the main results of \cite{baraniuk2017exponential}, an exponential MSE decaying rate, does not hold in the noisy setting.
-Stated otherwise, the MSE in the setting of \cite{baraniuk2017exponential} may decay exponentially up to the noise level, after which it decays at most as $\sigma^2\pi/2n$.
-\par
-%
-One-bit measurements in the distributed setting (iii) was considered in \cite{904560,4244748, 6882252, chen2010performance, 5184907}, but without optimizing the encoders and their detection rules.
-Consequently, the performance derived in these works are not optimal.
- % analyzed the estimation from distributed quantized measurements when the same detection rule is applied by all encoders.
-However, the error criterion considered in these works is the Fisher information rather than the MSE risk or ARE criterion.
-\par
-%Once the decision rule of each encoder is fixed, the optimal estimation of $\theta$ is determined using the maximum a posteriori probability rule.
-Hence, the distributed setting is reduced to finding the optimal decision rule of each encoder.
-The work of \cite{52470} addresses the counterpart of our setting (iii) in the case of hypothesis testing, although the results there cannot be extended to parametric estimation.
-When the parameter space $\Theta$ is finite, Tsitsiklist \cite{tsitsiklis1988decentralized} showed that when the cardinality of $\Theta$ is at most $M$ and the probability of error criterion is used, then no more than $M(M-1)/2$ different detection rules are necessary in order to attain probability of error decreasing exponentially with the optimal exponent.
-%That is, beyond $M(M-1)/2$ some decision rules can be repeated without losing optimality.
-Furthermore, in a version of this problem for the adaptive setting \cite{5751320}, it was shown that, with specific two-stage feedback, there is no gain in feedback compared to the fully distributed setting.
-Our results imply that the ARE in the distributed setting with threshold detection rules is strictly larger than that in the adaptive setting for almost all points in $\Theta$, suggesting that the case where the cardinality of $\Theta$ is finite is different from the case where $\Theta$ is an open set.\par
-%
-As we explain in detail in Section~ \ref{sec:preliminary}, the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}, leads to lower bounds on the MSE in setting (iii).
-For the case of a Gaussian distribution, this lower bound bounds the ARE to be at most $3/4$.
-Thus, while this bound on the ARE provides no new information compared to the upper bound of $2/\pi$ we derive for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimum even under the one bit per sample constraint.
- \par
-% 
-Finally, we note that minimax estimation under limited communication with an arbitrary number of bits per node was considered in 
-\cite{zhang2013information, duchi2014optimality}.
-The specialization of the results in \cite{zhang2013information, duchi2014optimality} to our settings (ii) and (iii) leads to looser lower bounds then the ones we derive in this paper.
-Looser bounds can also be obtained from works considering general inference and distributed estimation problems under data compression constraint \cite{DBLP:journals/corr/abs-1802-08417, zhang1988estimation, han2018distributed, xu2017information, Barnes2018}.
-In particular, the subsequent work of \cite{Barnes2018} uses an approach similar to ours to derive lower bound on the error in various parametric estimation problems from quantized measurements.
-\\
-
-The remainder of this paper is organized as follows.
-In Section~\ref{sec:problem} we describe the problem and useful notation.
-In Section~\ref{sec:preliminary} we provide two simple bounds on the efficiency and MSE.
-Our main results for the adaptive and distributed cases are given in Sections~\ref{sec:sequential} and \ref{sec:distributed}, respectively.
-In Section~\ref{sec:conclusions} we provide concluding remarks.
+% -*- Mode: latex -*- %
 
@@
 \[
-\sqrt{a_n}\left(\hat{\theta}_n - \theta\right) \overset{D}{\longrightarrow} \mathcal N(0, \sigma^2).
+\sqrt{a_n}\left({\theta}_n - \theta\right) \overset{d}{\longrightarrow} \Ncal(0, \sigma^2).
 \]
-Then the ARE of $\hat{\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
+Then the ARE of ${\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
 \[
-\ARE(\hat{\theta}_n) \triangleq
+\ARE({\theta}_n) \triangleq
 \lim_{n\rightarrow \infty} \frac{a_n}{n}. 
@@
 \[
-a_n \mathbb E \left(\hat{\theta}_n - \theta \right)^2 = V + o(1),
+a_n \mathbb E \left({\theta}_n - \theta \right)^2 = V + o(1),
 \]
-with $o(1)\to 0$ as $n\to \infty$, then the ARE of $\hat{\theta}_n$ is finite and equals $\sigma^2/V$. \\
+with $o(1)\to 0$ as $n\to \infty$, then the ARE of ${\theta}_n$ is finite and equals $\sigma^2/V$. \par
 
@@
 Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions).
-Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.
-\\
+Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.\par
 
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -3, xmax=3, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.9,
-samples=10, 
-xlabel= $x$,
-xtick={-2,-1,0,1,2},
-xticklabels={-2,-1,0,1,2},
-ytick={0,0.3989423,0.6366198},
-yticklabels={0,$\frac{1}{\sqrt{2 \pi}}$,$2/\pi$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\eta(x)$};
-\addplot[domain = -5:5, samples = 50, color = red, solid, smooth]  {exp(-x^2/2) / sqrt(2*3.14159)};
-\addlegendentry{$\phi(x)$};
-\addplot[domain = -5:5, samples = 50, color = black, solid, dashed]  {4*exp(-x^2) / (2*3.14159)};
-\addlegendentry{$4\phi^2(x)$};
+%% \begin{figure}
+%% \begin{center}
+%% \begin{tikzpicture}[scale = 0.6]
+%% \begin{axis}[
+%% width=8cm, height=6cm,
+%% xmin = -3, xmax=3, 
+%% restrict y to domain = 0:100,
+%% ymin = 0,
+%% ymax = 0.9,
+%% samples=10, 
+%% xlabel= $x$,
+%% xtick={-2,-1,0,1,2},
+%% xticklabels={-2,-1,0,1,2},
+%% ytick={0,0.3989423,0.6366198},
+%% yticklabels={0,$\frac{1}{\sqrt{2 \pi}}$,$2/\pi$},
+%% line width=1.0pt,
+%% mark size=1.5pt,
+%% ymajorgrids,
+%% xmajorgrids,
+%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+%% ]
+%% \addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {./Figs/eta.csv};
+%% \addlegendentry{$\eta(x)$};
+%% \addplot[domain = -5:5, samples = 50, color = red, solid, smooth]  {exp(-x^2/2) / sqrt(2*3.14159)};
+%% \addlegendentry{$\phi(x)$};
+%% \addplot[domain = -5:5, samples = 50, color = black, solid, dashed]  {4*exp(-x^2) / (2*3.14159)};
+%% \addlegendentry{$4\phi^2(x)$};
 
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -4, xmax=4, 
-restrict y to domain = -10:0,
-ymin = -10,
-samples=10, 
-xlabel= $x$,
-xtick={-3,-2,-1,0,1,2,3},
-xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,-0.45158,-0.919},
-yticklabels={0,,},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {./Figs/eta.csv};
-\addlegendentry{$\log \eta(x)$};
-\addplot[domain = -5:5, samples = 30, color = red, solid, smooth]  {-(x)^2/2 -0.9189};
-\addlegendentry{$\log \phi(x)$};
-\end{axis}
-\end{tikzpicture}
-\caption{
-The function $\eta(x) = f^2(x) / F(x)F(-x)$ for $f(x) = \phi(x)$ the standard normal density.
-\label{fig:eta}
-}
-\end{center}
-\end{figure}
-
-\section{Consisten Estimation and Existing Bounds \label{sec:preliminary}}
-%On a first impression, it may not be clear whether consistent estimation of the mean is even possible in the adaptive and centralized settings.
-On the other hand, it may seem as if estimation in these cases is trivial as in the centralized setting (i).
-%
-We next settle such skepticism by deriving lower and upper bounds to the relative efficiency under setting (iii).
-
-In this section, we derive lower and upper bounds on the relative efficiency under setting (iii) using known results. These bounds establish the following facts:
-\begin{itemize}
-\item[I.] A consistent estimator with an asymptotically normal distribution always exists in setting (iii), and hence in setting (ii). 
-\item[II.] For the normal distribution, the ARE in setting (iii) is at most $3/4$. Namely, under setting (iii), all estimators are strictly inferior compared to the sample mean. 
-\end{itemize}
-
-\subsection{Consistent Estimation}
-Fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
-\[
-B_i = \mathbf 1_{X_i>\theta_0}, 
-\]
-where $\mathbf 1_A$ is the indicator of the event $A$. We have
-\[
-p_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
-\]
-so that 
-\begin{equation}
-\label{eq:estimator_naive}
-\hat{\theta}_n = \theta_0 + F^{-1}\left( p_n \right)
-\end{equation}
-is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set.
-Furthermore, the variance of $p_n$ is $F(\theta-\theta_0)F(\theta_0-\theta)$, and hence the delta method implies that $\hat{\theta}_n$ is asymptotically normal with variance
-\begin{equation} 
-\frac{1}{
-\eta(\theta-\theta_0)} = \frac{F(\theta-\theta_0)F(\theta_0-\theta)}{f^2(\theta-\theta_0)}. 
-\end{equation}
-In particular, the ARE of $\hat{\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
-In other words, for a prescribed accuracy, $\hat{\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
-\par
-%
-%
-Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of $\hat{\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
-This ARE is attained only when $\theta_0 = \theta$, although $\theta$ is unknown apriori.
-Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of $\hat{\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
-As an example, when $f(x)$ is a normal density, the ARE of $\hat{\theta}_n$ is $\approx 0.07$ when $\theta_0$ is $2.33$ standard deviations from $\theta$.
-Therefore, the estimator $\hat{\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
-\par
-It is suggested that lower variance can be obtained by an estimator of the form \eqref{eq:estimator_naive} if, after observing a batch of the single bit messages, one can update the threshold value $\theta_0$.
-Such a scheme falls within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
-\\
-% variance equals to $1/\eta(0)n + o(1)$.
-We also show in Section~\ref{sec:sequential} that no estimator can attain variance that is asymptotically smaller than $1/\eta(0)n$, so that the ARE of any estimator in settings (ii) and (iii) is at least $\eta(0) \sigma^2$.
-
-\subsection{Multiterminal Source Coding \label{sec:ceo}}
-The CEO setting considers the estimation of a sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_i$ is available at $n$ terminals.
-At each terminal $i$, an encoder observes the $k$ noisy samples
-\[
-X_{i,j} = \theta_j + Z_{i,j},\qquad j=1,\ldots,k, \qquad i = 1,\ldots,n,
-\]
-and transmits $R_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates $\hat{\theta}_1,\ldots,\hat{\theta}_k$ with the goal of minimizing the average MSE:
-\[
-D_{CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - \hat{\theta}_j \right)^2 \right]. 
-\]
-Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $R_1=\ldots=R_n = 1$.
-It follows that, assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
-%
-Consequently, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the minimal MSE in the CEO setting as $k \to \infty$.
-Note that the difference between the CEO setting and ours lays in the privilege of each of the encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realizations, rather than a single realization using a single bit in ours.
- \par
-When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k\to \infty$ were fully characterized in \cite{prabhakaran2004rate}.
-Furthermore, the work of \cite{chen2004upper} provided an expression for MSE attained in the CEO setting under Gaussian priors.
-Adapting to our setting, this expression provides the following proposition:
-\begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$. Then any estimator $\hat{\theta}_n$ of $\theta$ in the distributed setting satisfies
-\begin{equation} \label{eq:ceo_bound}
- n\mathbb E \left( \theta - \theta_n \right)^2 \geq \frac{4\sigma^2}{3} + O(n^{-1}),
-\end{equation}
-where the expectation is with respect to $\theta$ and $X^n$.
-\end{prop}
-
-\begin{proof}
-See Appendix. 
-\end{proof}
-
-From the formulation of the CEO problem, it follows that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is attributed to the ability to perform coding over blocks.
-Namely, each encoder in the CEO setting may encode an arbitrary number of $k$ independent realizations of $\theta$ using $k$ bits, versus only one realization with one bit in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product probability space that distinguishes between the CEO problem with one bit per encoder on average and the mean estimation problem from one-bit measurements in the distributed setting.
-
-\section{Adaptive Estimation \label{sec:sequential}}
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $\eta(0)\sigma^2$, which is the ARE of the median of the sample $X_1,\ldots,X_n$.
-We also provide a particular adaptive estimation scheme that attains this maximal efficiency.
-%Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $B_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages.
-%Numerical simulations for the case of $f(x)$ the normal density function shows that the ARE of the estimator described by this scheme is $\eta(0)\sigma^2$.
-
-\subsection{Limited efficiency in the adaptive setting}
-Our first result asserts that the ARE of any adaptive encoding and estimation scheme is bounded from above by $\eta(0)\sigma^2$. %This result follows from the following theorem:
-\begin{thm}[maximal relative effeciency] \label{thm:adpative_lower_bound}
-Let $\hat{\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Figure~\ref{fig:setup}-(ii). Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-n\mathbb E\left[ (\theta-\hat{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0},
-\]
-where 
-\[
-I_0 = \mathbb E \left( \frac{d}{d\theta} \log \pi (\theta) \right)^2
-\]
-is the Fisher information with respect to a location model in $\theta$. 
-\end{thm}
-
-\subsubsection*{Sketch of Proof}
-The main idea in the proof is to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
-Once this bound is achieved, the result follows by using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are in the Appendix.\\
-
-Theorem~\ref{thm:adpative_lower_bound} implies that any estimator $\hat{\theta}_n$ from any adaptive encoding scheme satisfies
-\[
-n\mathbb E\left[ (\theta-\theta_n)^2 \right] \leq  \frac{1}{4f^2(0)}+O(n^{-1}),
-\]
-and 
-\[
-\ARE(\hat{\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
-\]
-
-Next, we present an adaptive encoding and estimation scheme that attains the maximal ARE of $\eta(0)\sigma^2$.
-
-\subsection{Asymptotically optimal estimator}
-Let $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ be a strictly positive sequence. Consider the following estimator $\hat{\theta}_n$ for $\theta$:  
-\begin{equation}
-\label{eq:sgd_alg}
-\theta_n = \theta_{n-1} +  \gamma_n B_n, \quad n = 1,2,\ldots,
-\end{equation}
-where 
-\begin{equation}
-B_n = B_n (X_n,\theta_{n-1}) =\sgn (X_n - \theta_{n-1}).
-\end{equation}
-Define the $n$th step estimation as
-\begin{equation} \label{eq:sgd_est}
-\hat{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
-\end{equation}
-
-We have the following results:
-\begin{thm} \label{thm:sgd}
-Consider the sequence $\left\{\hat{\theta}_n,\, n\in \mathbb N \right\}$ defined by \eqref{eq:sgd_est}. 
-\begin{enumerate}
-\item[(i)] Assume that $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ satisfies
-\begin{equation} \label{eq:conditions1}
-\begin{cases}
-\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
-\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
-\mathrm{for~some~}0< \lambda \leq 1
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Then
-\[
-\sqrt{n} \left( \hat{\theta}_n - \theta \right) \overset{d}{\rightarrow} \mathcal N \left(0,  1/\eta(0) \right).
-\]
-\item[(ii)] Assume that in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n,\, n\in \mathbb N \right\}$ satisfies
-\begin{equation} \label{eq:conditions2}
-\begin{cases}
-\gamma_n = o(n^{-2/3}), &  \\
-\sum_{n=1}^\infty \gamma_n = \infty.  & \\
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ with $2/3<\beta<1$). Then
-\[
-\lim_{n\rightarrow \infty} n\mathbb E \left[ \left(\theta-\hat{\theta}_n \right)^2 \right] = \frac{1}{\eta(0)}. 
-\]
-\end{enumerate}
-\end{thm}
-
-\subsubsection*{Proof}
-The asymptotic behavior of \eqref{eq:sgd_est} follows from \cite[Thm. 4]{polyak1992acceleration} and \cite[Thm. 2]{polyak1990new}. The details are in the Appendix. \\
-
-Theorem~\ref{thm:sgd} implies that the estimator $\hat{\theta}_n$, defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}, attains the maximal ARE as established by Theorem~\ref{thm:adpative_lower_bound}.
-The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$.
-Consequently, the procedure above is known as averaged stochastic gradient descent for minimizing $x \to |x|$ given the data $X_1,\ldots,X_n$.
-The minimal value of this optimization is the sample median, and Theorem~\ref{thm:sgd} provides conditions for the sequence of gradient steps so that the algorithm converges to this minimum.
- \par
-%Note that $\theta_0$ is not explicitly defined in equation \eqref{eq:sgd_est}.
-A reasonable initialization for $\theta_0$ is $\theta_0 = \mathbb E [\theta]$, although Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
-Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$.
-\\
-In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $B_n$ depends on its private sample as well as the current gradient descent estimate $\theta_{n-1}$.
-In this sense, each encoder in this algorithm interacts with previous one by using the current estimate.
-%
-As we explain next, 
-it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ with only one round of interactions among the encoders.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {Enc};  
-\draw[->,line width = 2pt] (source) -- (enc1);
-
-% \node[below of = source, node distance = 1cm] (source2) {$X_2$};
-%\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};  
-%\draw[->,line width = 2pt] (source2) -- (enc2);
-
-\node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {Enc};
-
-\draw[->,line width = 2pt] (source3) -- (enc3);
-
-\node[below of = source, node distance = 0.5cm] {$\vdots$};
-
-\node[int1, right of = enc3, node distance = 2.1cm ] (est) {Est 1};
-
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
-
-%\draw[->,line width = 2pt] (enc2) -| node[above, xshift = -1cm] (mes2) {$B_2$} (est);
-
-\draw[->,line width = 2pt] (enc3) -- node[above, xshift = 0cm]  {$B_{n_1}$} (est);
-
-\node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
-\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {Enc$(\hat{\theta}_1)$};  
-\draw[->,line width = 2pt] (sourceB) -- (enc1B);
-
-\node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
-\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {Enc$(\hat{\theta}_1)$};  
-\draw[->,line width = 2pt] (source3B) -- (enc3B); 
-\node[below of = sourceB, node distance = 0.4cm] {$\vdots$};
-
-\node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {Est 2};
-
-\draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.8cm] {$B_{n_1+1}$} (estB);
-\draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);
-
-\draw[->,line width = 0.5pt] (est.east) node[above, xshift  =0.5cm] {$\hat{\theta}_{n_1}$} -| (enc1B.north);
-
-\draw[->,line width = 0.5pt] (enc1B) -- (enc3B);
-
-%\draw[->,line width = 1pt] (enc1B)  -- node[right] {$\hat{\theta}_{n_1}$} (enc3B);
-
-\draw[->,line width = 2pt] (estB) -- +(0.8,0) node[right] {$\hat{\theta}_n$};
-\end{tikzpicture}
-\end{center}
-\caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
-\label{fig:one_round}
-}
-\end{figure}
-
-\subsection{Optimality using a Single Interaction}
-In Section~\ref{sec:preliminary} we considered an estimator that is based on messages of the form 
-\[
-B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
-\]
-and showed that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
-%
-We now show that a similar encoding leads to an asymptotically normal estimator with the minimal variance $1/\eta(0)$, provided we allow at least once to update the threshold value $\theta_0$. 
-%
-In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
-We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate $\hat{\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use $\hat{\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$.
-Figure~\ref{fig:one_round} illustrates a diagram of this procedure.
-%
-The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
-\begin{thm}
-For $i=1,\ldots,n$ set
-\[
-B_i = \begin{cases}
- \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
- \mathbf 1_{X_i \geq \hat{\theta}_{n_1} }& i={n_1+1,\ldots,n},
-\end{cases}
-\]
-where $n = n_1+ n_2$ and 
-\[
-\hat{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
-\frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
- \right).
-\] 
-Let 
-\[
-\hat{\theta}_{n_2}  = \hat{\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
-\]
-and assume that $n_1(n) \rightarrow \infty$ and $n_1(n)/n \rightarrow 0$. Then:
-\begin{align*}
- \sqrt{n} \left( \hat{\theta}_{n_2} - \theta  \right)^2  \overset{D}{\longrightarrow}  \mathcal N\left( 0, 1/\eta(0) \right).
-\end{align*}
-\end{thm}
-%
-%
-\begin{proof}
-For $t\in \mathbb R$, set
-\[
-p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
-\]
-From the central limit theorem
-\begin{align*}
-& \sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)  = \sqrt{\frac{n}{n_2}} \sqrt{n_2} \left(  p_{n_2}(t) - F(\theta - t) \right) \\
-& \overset{D}{\rightarrow} \mathcal N\left( 0, V(t) \right),
-\end{align*}
-where
-\[
-V(t) \triangleq F(\theta - t) F \left( t - \theta\right). 
-\]
-Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ we obtain
-\begin{align*}
-& \sqrt{n} \left( t + F^{-1}(\hat{p}_{n_2}(t)) - \theta \right) \\
-&= \sqrt{n} \left( g(\hat{p}_{n_2}(t)) - g \left(F(\theta-t) \right)  \right) \\
-& \overset{D}{\to} \mathcal N\left(0, 
-1/\eta(\theta-t) \right).
-\end{align*}
-%where this convergence is uniform in $t$ since all moments of $F^{-1}(\hat{p}_{n_2})$ exists. 
-By the law of large numbers we also have
-\[
-p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
-\]
-so that $\hat{\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity, and thus 
-\[
-\eta( \hat{\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
-\]
-By Slutsky's theorem we get
-\begin{align*}
-& \sqrt{n}\left(\hat{\theta}_{n_2} - \theta\right) \\
-& = \sqrt{n} \left( \hat{\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}(\hat{\theta}_{n_1})) - \theta \right)  \\
-& \overset{D}{\to} \mathcal N\left( 0, 
-1/\eta(0) \right). 
-\end{align*}
-\end{proof}
-%
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=10cm, height=6cm,
-xmin = 0, xmax=800, 
-restrict y to domain = 0:3,
-ymin = 0,
-ymax = 3.4,
-samples=10, 
-xlabel= $n$,
-ylabel = {$n\mathbb E \left[\left(\theta - \hat{\theta}_n \right)^2 \right]$},
-%xtick={-3,-2,-1,0,1,2,3},
-%xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,1,1.57},
-yticklabels={0,1,$\pi/2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-
-\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{asymptotically optimal};
-
-%\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
-
-\addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{single interaction};
-
-\end{axis}
-\end{tikzpicture}
-%\begin{tikzpicture}
-%\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
-%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left(\hat{\theta}_n - \theta \right)^2$};
-%\node[scale = 0.7] at (0,-2.4) {$n$};
-%\end{tikzpicture}
-\caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.
-In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$.
-The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage.
-\label{fig:adaptive_error}  }
-\end{center}
-\end{figure}
-
-\section{Distributed Estimation \label{sec:distributed}}
-We now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii).
-In this setting each one-bit message $B_i$ is only a function of its private sample $X_i$, and hence $B_i$ characterized by its \emph{detection region}, defined as
-\[
-A_i = \left\{ x \in \mathbb R \,:\, B_i(x) = 1 \right\}.
-\]
-Consequently, $B_i$ is of the form
-\[
-B_i = \begin{cases} 1 & X_i \in A_i, \\
--1 & X_i \notin A_i,
-\end{cases} \quad i\in \mathbb N,
-\]
-where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\\
-
-As a first step, we provide conditions under which the messages $B_1,B_2,\ldots$ define a local asymptotic normal family.
-
-\begin{thm} \label{thm:LAN1}
-For $n \in \mathbb N$ and $A_n \subset \mathbb R$,  define
-\begin{equation}
-\label{eq:precision_general}
-L_n(A_1,\ldots,A_n;\theta) \triangleq \frac{1}{n} \sum_{i=1}^n \frac{ \left(\frac{d}{d \theta} \Prob(X_i \in A_i) \right)^2 }{ \Prob(X_i \in A_i)\left(1- \Prob(X_i \in A_i) \right) }. 
-\end{equation}
-Consider the following conditions:
-\begin{itemize}
-\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is a log-concave, differentiable and symmetric density function such that $\eta(x)$ is unimodal.
-\item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
-\item[(iii)] The limit 
-\begin{equation}
-\label{eq:LAN_lim}
-\kappa(\theta) \triangleq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
-\end{equation}
-exists. 
-\end{itemize}
-For $i=1,\ldots,n$ set
-\[
-B_n = \begin{cases} 1 & X_n \in A_n, \\
--1 & X_n \notin A_n. 
-\end{cases} 
-\]
-For any $\theta$, $f(x)$ and a sequence of sets $A_1,A_2,\ldots$ such that (i)-(iii) hold, and any $h\in \mathbb R$, we have
-\begin{align*}
-& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (B_1,\ldots,B_n) }{
-\mathbb P_{\theta} (B_1,\ldots,B_n)} \\
-& \overset{D}{\longrightarrow} \mathcal N\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
-\end{align*} 
-\end{thm}
-Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}. 
-%
-Among these conditions, (iii) is arguably the strongest and hardest to verify.
-As we show in Section~\ref{subsec:threshold} below, this condition is satisfied, for example, when $A_1, \ldots,A_n$ are half lines whose starting points are drawn independently from some probability measure on $\mathbb R$.
-Similar ideas imply that condition (iii) holds whenever we choose the intervals consisting each $A_i$ according to some pre-specified distribution.
-\par
-%
-An important conclusion of  Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models (e.g. \cite{van2000asymptotic}):
-\begin{cor} \label{cor:LA_minimax}
-Let $\hat{\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
-Then for any bounded, symmetric, and quasi-convex function $L$,
-\begin{align*}
-& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\hat{\theta}_{n} - \tau) \right) \right]
-\\
-& \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
-\end{align*}
-where $Z \sim \mathcal N(0,1)$. In particular, for $L(x) = x^2$, 
-\begin{align*}
-\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( \hat{\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
-\end{align*}
-\end{cor}
-%
-Corollary~\ref{cor:LA_minimax} says that when the messages define a LAN model, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model at $\theta$.
-This fact poses the upper bound of $\kappa(\theta)\sigma^2$ for the ARE of estimators in such models.
-\\
-
-Next, we show that under LAN no estimator can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly for all $\theta \in \Theta$.
-
-\subsection{Non-existence of a Uniformly Optimal Strategy}
-We now show that under LAN models, the optimal minimal risk $1/\eta(0)$ can only be attained at a finite number of points within $\Theta$.
-This fact implies in particular that, unlike in the adaptive setting, no distributed estimation scheme has ARE of $\eta(0)\sigma^2$ for all $\theta \in \Theta$.
-
-\begin{thm} \label{thm:non_existence}
-Under conditions (i)-(iii) in Theorem~\ref{thm:LAN1}, assume that each $A_i$ is a union of at most $K$ intervals.
-The number of points $\theta \in \Theta$ satisfying $\kappa(\theta) = \eta(0)$ is at most $2K$.
-\end{thm}
-
-\begin{proof}
-See Appendix. 
-\end{proof}
-
-We next consider the case where each detection region is a half-open interval, i.e., the $i$th message is obtained by comparing $X_i$ against a single threshold.
-As we explain next, the existence of a density for the sequence of thresholds is enough to establish local asymptotic normality and leads to a closed form expression for the precision parameter and the ARE.
-
-%In the adaptive setting, it follows from Theorem~\ref{thm:sgd} that messages of this kind with appropriately chosen thresholds lead to an estimator with the optimal ARE of $\eta(0)sigma^2$.
-However, Theorem~\ref{thm:non_existence} implies that such ARE can only be attained for a negligible subset of the parameter space.
-As we shall see next, messages obtained via a comparison against a sequence of thresholds cannot attain the optimal efficiency one more than a single point of $\Theta$.
-
-\subsection{Threshold Detection \label{subsec:threshold}}
-Assume now that each $B_i$ is of the form
-\begin{equation}
-\label{eq:threshold_message}
-B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
--1 & X_i > t_i,
-\end{cases}  
-\end{equation}
-where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder.
-In other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and $\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$.
-It follows that
-\begin{equation}
-L_n(A_1,\ldots,A_n;\theta) = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
-\label{eq:Ln_threshold}
-\end{equation}
-A natural condition for the existence of the limit \eqref{eq:Ln_threshold} as $n\to \infty$ is that the empirical distribution of the threshold values converges to a probability measure.
-Specifically, for an interval $I \subset \mathbb R$ define
-\[
-\lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
-\]
-Theorem~\ref{thm:LAN1} implies:
-\begin{cor} \label{cor:LAN_thresh}
-Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$.
-Then $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a LAN family with precision parameter
-\[
-\kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
-\]
-\end{cor}
-The condition that $\lambda_n$ converges to a probability measure is satisfies, for example, whenever the $t_1,\ldots,t_n$s are drawn independently from a probability distribution $\lambda(dt)$ on $\mathbb R$.
-\par
-Due to local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by 
-$\hat{\theta}^{ML}_n$, is local asymptotic minimax in the sense that 
-\[
-\sqrt{n} \left( \hat{\theta}^{ML}_n - \theta \right) \overset{D}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
-\]
-It follows that when the density of the threshold values converges to a probability measure, the ARE of the ML estimator is $\kappa(\theta)\sigma^2$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-We note that $\hat{\theta}^{ML}_n$ is given by the root of
-\begin{equation}
-\label{eq:ML}
-\sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) },  
-\end{equation}
-which is the derivative of the log-likelihood function.
-This root is unique since the log-likelihood function is concave.
-Furthermore, for any $n \in \mathbb R$, we have that $\hat{\theta}^{ML}_n  \in [t_{(1)}, t_{(n)}]$ where $t_{(i)}$ denotes the $i$th element of $\{t_1,t_2\ldots\}$.
-Therefore, if $\{t_1,t_2\ldots\}$ is bounded (for example $\{t_1,t_2\ldots\} \subset \Theta$), then
-\[
-\lim_{n\to \infty} n\left(\hat{\theta}^{ML}_n - \theta \right)  = 1/\kappa(\theta), 
-\] 
-so that the ML estimator attains the local asymptotic MSE of Corollary~\ref{cor:LA_minimax}. \par
-%
-Since $\eta(x)$ attains its maximum at the origin, we conclude that
-\[
-\kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
-\]
-This upper bound on $\kappa(\theta)$ implies that the ARE of any distributed estimator based on a sequence of threshold detectors does not exceed $\eta(0)\sigma^2$, a fact that agrees with the lower bound under adaptive estimation derived in Theorem~\ref{thm:adpative_lower_bound}.
-%
-This upper bound on $\kappa(\theta)$ is attained only when $\lambda$ is the mass distribution at $\theta$.
-Since $\theta$ is apriori unknown, we conclude that estimation in the distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting.
-In other words, the ability to choose the threshold values in an adaptive manner based on previous messages strictly improves relative efficiency compared to a non-adaptive threshold selection.
-\\
-
-%We conclude that when the density of the threshold values converges to a probability measure, the ARE of the ML is $\kappa(\theta)$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-
-%
-We conclude this section by considering the density of the threshold values that maximizes the ARE $\kappa(\theta)$ under the worst choice of $\theta \in \Theta$.
-
-\subsection{Minimax Threshold Density}
-The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta = [-T,T]$ is given as the solution to the following optimization problem:
-\begin{align}
-\label{eq:var_cvx_minimax}
-\begin{split}
-\mathrm{maximize} \quad &  \inf_{\theta \in [-T,T]} \int \eta(t-\theta) \lambda(dt)
-\\ 
-\mathrm{subject~to} 
-\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
-\end{split}
-\end{align}
-The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program.
-We denote by $\kappa^\star(T)$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum.
-%
-%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
-%\begin{align}
-%\label{eq:cvx_minimax}
-%\begin{split}
-%\mathrm{maximize} \quad &  K \\ 
-%\mathrm{subject~to} 
-%\quad &  K \leq \mathbf H\lambda \\
-%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
-%\end{split}
-%\end{align}
-%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
-%\begin{rem}
-%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$.
-Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points.
-Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using
-%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
-%\end{rem}
-
-Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$.
-The minimal asymptotic risk $\kappa^\star(\theta)$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $T$.
-Also illustrated in these Figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
-\begin{align}
-& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
- \\
-& = 
-\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
-= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
-\end{align}
-From Corollary~\ref{cor:LAN_thresh}, we conclude that the ARE under a uniform distribution is $\kappa_\unif \sigma^2$. \\
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-title = {$\sigma/T = 1/2$},
-ytick={0,0.1,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.6,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/T = 1/5$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.5},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.5},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.3,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma / T = 1/10$},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.2},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.2},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.15,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma / T = 1/20$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:minimax_support}
-Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \mathcal N(\theta,\sigma^2)$ and $\theta \in \Theta = [-T,T]$.
-%
-The continuous curve (red) represents the reciprocal of the asymptotic risk for at a fixed $\theta \in \Theta$ under the optimal density, so the minimax risk is the inverse of its minimal value.
-The dashed curve (green) is the reciprocal of the asymptotic risk for a fixed $\theta$ under a uniform distribution of threshold values over $\Theta$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
-}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmax=2.5, 
-xmode = log,
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=1, 
-xlabel= {$\sigma/T$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,0.637,1},
-yticklabels={0,$2/\pi$,1},
-ylabel = {$\ARE$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{optimal threshold density};
-
-\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{uniform threshold desnity};
-\end{axis}
-\end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \mathcal N(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
-The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
-}.
-\end{center}
-\end{figure}
-
-%We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
-Next, we prove that with any set of messages obtained via a distributed strategy, there exists at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
-
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-title = {$\sigma/\sigma_{\theta} = 1$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 2$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma/\sigma_{\theta} = 3$},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 4$},
-xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:opt_density}
-Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=b^2/3$ is the variance of the prior.
-}
-\end{center}
-\end{figure}
-
- We consider now the problem of minimizing the asymptotic Bayes risk $
-R_{\pi,\lambda} \triangleq \mathbb E  K^{-1}(\theta)$ over all probability measures $\lambda(dt)$ with support in $\mathbb R$. This optimization problem can be written as follows:
-\begin{align}
-\label{eq:cvx_average}
-\begin{split}
-\mathrm{minimize} \quad & R_{\pi,\lambda} =  \int \frac{\pi(d\theta)}{ \int \eta \left( t-\theta\right) \lambda(dt)}. \\ 
-\mathrm{subject~to} \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) =1. 
-\end{split}
-\end{align}
-We denote by $R^\star_{\pi}$ the minimal value of the objective function in \eqref{eq:cvx_average}.
-Since the function $x \rightarrow 1/x$ is convex for positive values, \eqref{eq:cvx_average} defines a convex optimization problem in $\lambda$ whose solution depends on the prior $\pi$.
-The solution to this problem is approximated by considering $\lambda$ and $\pi$ over a discrete set.
-On Figure~\ref{fig:opt_density} we illustrate the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distributon ($P_X = \mathcal N(\theta, \sigma^2)$) and the prior on $\theta$ is uniform over $\Theta = [-b,b]$.
-Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
-\par
-\begin{figure}
-\begin{center}
-
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = 0, xmax=2, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 10,
-samples=1, 
-xlabel= {$\sigma/\sigma_\theta$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,1.5708,5},
-yticklabels={0,$\pi/2$,5},
-ylabel = {$R_{\pi}^\star/\sigma^2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-\addplot[color = black, dashed] {3.14159 / 2};
-\end{axis}
-\end{tikzpicture}
-\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \mathcal N(\theta, \sigma^2)$under an optimal threshold distribution $\lambda^\star$ for $\pi$ the uniform distribution over $\Theta = [-0.5,0.5]$.
-%
-%versus $\sigma/\sigma_\theta = 2\sqrt{3}\sigma$.
-The distribution $\lambda^\star$ is the minimizer of \eqref{eq:cvx_average}.
-It is illustrated for various cases in Fig.~\ref{fig:opt_density}.
-The dashed curve represents the upper bound \eqref{eq:upper_bound}.
-\label{fig:dist_bound_uniform}  }
-\end{center}
-\end{figure}
-
-As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \mathcal N(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution.
-In this case, the ML estimator reduces to the estimator $\hat{\theta}_n$ of \eqref{eq:estimator_naive}.
-As the following proposition shows, the Bayes risk for this choice of $\lambda$ is maximal, and thus provides an upper bound on the Bayes risk under any $\lambda$.
- \eqref{eq:cvx_average}. 
-\begin{prop}\label{prop:upper_bound}
-For any prior $\pi(d\theta)$ and $\theta_0$ in the support of $\eta(x)$ we have
-\begin{equation} 
-\label{eq:upper_bound}
-R_\pi^\star  \leq 
- \int \frac{\pi(d\theta)}{\eta \left( \theta_0 - \theta \right)},
-\end{equation}
-Furthermore, assuming that $\theta_0 = \mathbb E \theta$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
-\begin{equation}
-\label{eq:bound_Taylor}
-R^\star_\pi \leq \frac{1}{4 f^2(0)} + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right) \sigma_\theta^2 + O(\sigma_\theta^3).
-\end{equation}
-\end{prop}
-\begin{proof}
-The function $x \rightarrow 1/x$ is convex for positive values, hence Jensen's inequality implies
-\[
-\left( \int \eta \left( t-\theta\right) \lambda(dt) \right)^{-1}  \leq \int  \frac{ \lambda(dt)}{ \eta \left( t-\theta\right)  }. 
-\]
-Therefore, the expected value of $\kappa^{-1}(\theta)$ satisfies
-\begin{align}
-\mathbb E  \frac{1}{\kappa(\theta)}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
-\end{align}
-The bound \eqref{eq:upper_bound} is obtained by taking $\lambda$ to be a mass distribution at any $\theta_0$ in the support of $\eta(x)$.
-Finally, \eqref{eq:bound_Taylor} is obtained by expanding $1/\eta(x)$ to a third order Taylor series around zero
-%\[
-%1/\eta(x) = \frac{1}{4f^2(0)}  + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right)  x^2 + O(x^3),
-%\]
-and taking its expectation with respect to $\pi$ at $x=\theta_0-\theta$. 
-\end{proof}
-We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so taking $\theta_0 = \mathbb E \theta$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
-The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$.
-The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $\kappa^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.
-
-\begin{example} \label{ex:bound}
-In the normal case $P_X = \mathcal N(\theta, \sigma^2)$, the bound in \eqref{eq:bound_Taylor} implies 
-\[
-\frac{R^\star_\pi}{\sigma^2}  \leq \frac{\pi}{2} + \left( \frac{\pi}{2} -1 \right) \left( \frac{ \sigma_\theta}{\sigma} \right)^2 + O \left(  \frac{\sigma_\theta} { \sigma} \right)^3. 
-\]
-It follows that the ARE approaches its maximal value of $2/\pi$ whenever $\sigma_\theta/\sigma$ is small.
-The exact value of \eqref{eq:upper_bound} in this case, as well as the Bayes ARE with the optimal threshold density $\lambda^\star$ for a uniform $\pi$, are illustrated in Fig.~\ref{fig:dist_bound_uniform}.
-%i.e., each encoder simply reports "$1$" or "$-1$" whenever $X_i$ is larger or smaller than $\theta_0$, respectively.
-Intuitively, an accurate estimation of $\theta$ in this case is possible only if a sufficient mix of ''$1$''s and ''$-1$''s is obtained from the sample.
-When $\sigma_\theta^2$ is high compared to $\simga^2$, one of the events $"1"$ or "$-1"$ becomes too rare to
-\end{example}
-
-\section{Conclusions \label{sec:conclusions}}
-We considered the MSE risk in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
-%
-In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency (ARE) larger than that of the median of the samples.
-We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median.
-%We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
-\par
-In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and ARE. 
-%
-We conclude that under such conditions, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in the distributed setting.
-%
-We further considered the special case of messages obtained by comparing against a prescribed sequence of thresholds.
-We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.
- \\
-
-%\section*{ACKNOWLEDGMENT}
-%This research is supported in parts by...
-%Tsachy Weissman, Stefano Rini, Robert Gray.
-
-\onecolumn
-
-\appendices
-
-\section{Proofs \label{app:proofs}}
-
-\subsection{Proof of Proposition~\ref{prop:ceo_lower_bound}}
-
-First, we note that when $f(x) = \mathcal N(0,\sigma^2)$ and $\pi(\theta) = \mathcal N(0,\sigma_\theta^2)$, our distributed setting reduces to the Gaussian CEO problem with $R_1=\ldots = R_n =1$ and $k=1$.
-Therefore, any MSE attained in our distributed setting is also attained by the CEO and thus the optimal CEO strategy (with arbitrary $k$) provides a lower bound to the MSE in our setting.
-\\
-
-Consider the minimal distortion $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
-from \cite[Eq. 10]{chen2004upper}:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-For the special case of $R_\Sigma = n$ and $L=n$, we get
-\begin{equation} \label{eq:ceo_optimal_sumrate2}
-n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, this $D^\star$ provides a lower bound to the CEO distortion with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
-\[
-D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO distortion while enforcing the condition $R_1=\ldots = R_n = 1$.
-Indeed, an upper bound for the CEO distortion under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
-\[
-D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
-\]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.
-
-\begin{lem} \label{lem:bound_intervals}
-Let $f(x)$ be a log-concave, symmetric, and differentiable density such that $\eta(x)$ is strongly unimodal. For any $x_1 > \ldots > x_n \in \mathbb R$, 
-\begin{equation}
-\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-\leq \max_i \eta(x_i). \label{eq:lem_bound_intervals}
-\end{equation}
-In particular, if $|x_i|>\epsilon > 0$ for all $i=1,\ldots,n$, then 
-\[
-\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-\leq \eta(\epsilon) < 0. 
-\]
-\end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals}} 
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-so 
-\[
-\eta(x) =  \frac{  \left(\delta_1(x) \right)^2}{\Delta_1(x)
-(1-\Delta_1(x))}
-= \frac{  \left( f (x) \right)^2}{ F(x)\left(1-F(x)\right)^2}. 
-\]
-We use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:lem_bound_intervals} is bounded from above by $\max_i \eta(x_i)$. The case $n=1$ is trivial. Assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^2} 
-{\Delta_n \left(1- \Delta_n \right) } \leq \max_i \eta(x_i)
-\label{eq:lem_bound_intervals_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  2 \log \delta_N -  \log \Delta_N -  \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(-1)^{k+1} f(x_k)}{1-\Delta_N },
-\]
-and we conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-%
-Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable. We have 
-\[
-\frac{f'(x)}{f(x)} = c'(x), \quad x\in \mathbb R,
-\]
-which is anti-symmetric, non-negative for $x<0$,  non-positive for $x>0$, and non-increasing since $c(x)$ is concave.
-Therefore, if $c'(x_i) = c'(x_{i+1})$ for some $i =1,\ldots,N-1$, then either (1) $x_i = x_{i+1}$ or (2) $c'(x)$ is the zero function.
-Since (2) violates the assumption that $f(x)$ is a density function, we conclude that $c'(x)$ is an injection.
-%
-As a result, \eqref{eq:gradient_zero} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_proof} equals $\eta(x_1) = \max_i \eta(x_i)$ hence the statement holds.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$, or  $x_i, x_{i+1}$ for some $i$.
-It is left to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Under case (1) we have
-\begin{align*}
-\lim_{x_N \to -\infty} \frac{  \delta_N^2} 
-{\Delta_N \left(1- \Delta_N \right) }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^2} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)} ,
-\end{align*}
-which is smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis. Under case (2) we have
-\begin{align*}
-&  \lim_{x_1 \to \infty}
-\frac{ \delta_N} 
-{\Delta_N\left(1- \Delta_N \right) } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right) \left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right) }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^2 } 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right) },
-\end{align*}
-where $x'_{m} = x_{m+1}$. The last expression is also smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis.  \QEDA \\
-
-\subsection*{Proof of Theorem~\ref{thm:adpative_lower_bound}}
-
-We first prove the following lemma:
-\begin{lem} \label{lem:fisher_bound}
-Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that $\eta(x)$ is unimodal. For a Borel measurable $A$ set, 
-\[
-M(X) = \begin{cases} 1,& X \in A, \\
--1, & X \notin A.
-\end{cases}
-\]
-Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $\eta(0)$.
-\end{lem}
-
-\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
-When $f(x)$ is the normal density function, this lemma follows from \cite[Thm.
-3]{Barnes2018}.
-The proof below is based on a different techique than in \cite{Barnes2018}, and is valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}.
-\\
-
-The Fisher information of $M$ with respect to $\theta$ is given by
-\begin{align}
-I_\theta & =  \mathbb E \left[ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta \right] \nonumber \\
-& = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
-& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\
-& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\ 
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
-\end{align}
-where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$.
-Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
-\[
-\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
-\]
-which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$.
-It is therefore enough to proceed in the proof assuming that $A$ is of the form
-\[
-A = \cup_{j=1}^k (a_j,b_j),
-\]
-with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
-\begin{align*}
-\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
-& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
-\end{align*}
-so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
-\begin{align}
-& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
-{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
-& \times \frac {1} 
-{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
-\label{eq:lemma_J}
-\end{align}
-It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $4f^2(0)$.  \QEDA \\
-
-We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
-\begin{equation}
-\label{eq:general_messages}
-B_i = \begin{cases}
-X_i \in A_i & 1, \\
-X_i \notin A_i & -1,
-\end{cases} 
-\end{equation}
-where $A_i \subset \mathbb R$ is a Borel measurable set. 
-%Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
-Consider the conditional distribution $P({B^n|\theta})$ of $B^n$ given $\theta$. We have 
-\begin{align}
-P\left( B^n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
-\end{align}
-where $P\left(B_i =1 | \theta, B^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B^n$ with respect to $\theta$ is given by 
-\begin{align}
-I_\theta(B^n) = \sum_{i=1}^n I_\theta (B_i|B^{i-1}),
-\label{eq:fisher_information}
-\end{align}
-where $I_\theta (B_i|B^{i-1})$ is the Fisher information of the distribution of $B_i$ given $B^{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B^{i-1}) \leq 4f^2(0)$.
-The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
-\begin{align*}
-\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(B^n) + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
-& \geq \frac{1}{ 4f^2(0) n + I_0}.
-\end{align*}
-
-\QEDA
-
-\subsection*{Proof of Theorem~\ref{thm:sgd}}
-The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.
-Specifically, (i) in Theorem~\ref{thm:sgd} follows from the following simplified version of \cite[Thm.
-4]{polyak1992acceleration}:
-\begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
-Let 
-\[
-X_i = \theta + Z_i,\quad i=1,\ldots,n,
-\]
-where the $Z_i$s are i.i.d. with zero means and finite variances. Define
-\begin{align*}
-\theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
-\hat{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
-\end{align*}
-where in addition, assume the following: 
-\begin{enumerate}
-\item[(i)] There exits $K_1$ such that $\left| \varphi(x) \right| \leq K_1(1+|x|)$ for all $x\in \mathbb R$.
-\item[(ii)] The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions \eqref{eq:conditions1}.
-\item[(iii)] The function $\psi(x) \triangleq \mathbb E \varphi(x+Z_1)$ is differentiable at zero with $\psi'(0)>0$, and satisfies $\psi(0)=0$ and $x\psi(x) >0$ for all $x\neq 0$.
-Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
-\begin{equation}
-\label{eq:Polyak_Juditsky_cond3}
-\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
-\end{equation}
-\item[(iv)] The function 
-$\chi(x) \triangleq \mathbb E \varphi^2(x+Z_1)$ is continuous at zero. 
-\end{enumerate}
-Then $\hat{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}(\hat{\theta}_n - \theta)$ converges in distribution to $\mathcal N(0,V)$, where
-\[
-V = \frac{ \chi(0)} {\psi'^2(0)}. 
-\]
-\end{thm}
-
-Using the notation above, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have that $\chi(x) = \mathbb E \sgn^2(x+Z_1) = 1$, so $\chi(0) = 1$. In addition,
-\begin{align*}
-\psi(x) & = \mathbb E \sgn(x+ Z_1) = \int_{-\infty}^\infty \sgn(x+z) f(z) dz \\
-& = \int_{-x}^\infty f(z) dz -\int_{-\infty}^{-x} f(z) dz. 
-\end{align*}
-Using the symmetry of $f(x)$ around zero, it follows that $\psi'(x) = 2f(x)$ and thus $\psi'(0) = 2f(0)$.
-It is now easy to verify that the rest of the conditions in Theorem~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$.
-Since
-\[
-\frac{\chi(0)}{\psi'^2(0)} = \frac{1}{4 f^2(0)},
-\]
-Theorem~\ref{thm:sgd}-(i) follows from Theorem~\ref{thm:polyak_juditsky}.  \\
-
-In order to prove part (ii) of Theorem~\ref{thm:sgd} we use the following result from \cite{polyak1990new}:
-\begin{thm}{ \cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
-Let
-\begin{align} \label{eq:polyak_new_measurements}
-\begin{cases}
-U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = g'(U_{n-1})+Z_n \\
-\bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
-\end{cases}
-\end{align}
-Assume that the function $g(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative.
-In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \mathbb R$.
-Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution for which the Fisher information exits.
-Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{thm:polyak_juditsky}-(iii) and satisfies the conditions there.
-Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$,
-and there exits $K_3$ such that 
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] \leq K_3(1+|x|^4). 
-\]
-Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions  \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
-\[
-V_n \triangleq \mathbb E \left[ \left(\bar{U}_n-x^\star \right)^2 \right] = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
-\]
-\end{thm}
-
-We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = -\sgn(-x)$, $Z_n = \theta-X_n$ and $U_n = \theta_n$. From \eqref{eq:polyak_new_measurements} we have
-\begin{align*} 
-\theta_n & = \theta_{n-1} + \gamma_n \sgn(\theta-\theta_{n-1} - Z_n )  \\
-& = \theta_{n-1} + \gamma_n \sgn(X_n-\theta_{n-1} ),
-\end{align*}
-so the estimator $\hat{\theta}_n$ defined by $\hat{\theta}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
-\[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] = 1 \leq K_3(1+|x|^4)
-\]
-for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
-the conditions in Theorem~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
-In particular, $\psi'(0) = (2f(0))^{-2}$.
-Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$.
-Theorem~\ref{thm:polyak_new} implies
-\[
-n V_n = \mathbb E \left[ \left(\hat{\theta}_n-\theta \right)^2 \right]  = \frac{1}{4 f^2(0)} + o(1).
-\]
-\QEDA
-
-\subsection*{Proof of Theorem~\ref{thm:LAN1}}
-The log probability mass distribution of $B^n=(B_1,\ldots,B_n)$ is given by
-\begin{align*}
-& \log \Prob_\theta(b^n) = \sum_{i=1}^n \left( \frac{b_i+1}{2} \log  \Prob(X_i\in A_i) + 
-\frac{1-b_i}{2} \log \Prob(X_i\in A_i) \right), \quad b^n \in \{-1,1\}^n. 
-\end{align*}
-Consequently, 
-\begin{align}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) } = \sum_{i=1}^n    \frac{b_i+1}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} + 
-\sum_{i=1}^n  \frac{1-b_i}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}. 
-\label{eq:LAN_proof1}
-\end{align}
-For each $i=1,\ldots,n$, write 
-\[
-A_i = \bigcup_{k=1}^{K_i} \left(t_{i,k},t_{i,k+1} \right),
-\]
-where $t_{i,1}<\ldots<t_{i,K_i}$ and, with a slight abuse of notation, $t_{i,1}$ and $t_{i,K_i}$ may also be $-\infty$ or $+\infty$, respectively. Thus
-\[
-\Prob_{\theta}(X_i \in A_i) = \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta).
-\]
-In particular, since $f$ is differentible, $\Prob_{\theta}(X_i \in A_i)$ is twice differentiable, and we may write
-\begin{align*}
-\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)  = \Prob_{\theta} (X_i \in A_i) + \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \frac{h}{\sqrt{n}} + o(h), 
-\end{align*}
-and thus
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} = \log \left(1 + \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} + o(h) \right) \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2 + o(h^2).
-\end{align*}
-Similarly, we have
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 + o(h^2).
-\end{align*}
-From \eqref{eq:LAN_proof1} we obtain
-\begin{align*}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
-\left( 
-\frac{b_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-b_i}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}   \right) \\
- & - \frac{h^2}{2n} 
- \sum_{i=1}^n 
-\left( 
- \frac{b_i+1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-b_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 \right) + o(h^2) \\
-\end{align*}
-%
-Noting that 
-\[
-\frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} = \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)},
-\]
-the proof is completed by proving the following two claims:
-\begin{itemize}
-\item[I.] 
-For $i=1,\ldots,n$ denote 
-\[
-U_i = \frac{B_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-B_i}{2}  \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}. 
-\]
-Then 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0, \kappa(\theta) \right). 
-\]
-\item[II.]
-For $i=1,\ldots,n$ denote 
-\[
-V_i =  \frac{B_i-1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-B_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2.
-\]
-Then 
-\[
-\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} \kappa(\theta). 
-\]
-\end{itemize}
-\subsubsection*{Proof of Claim I}
-First note that 
-\begin{align*}
-\mathbb E  [U_i] & = 
- \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=1)   + 
- \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=-1)  = 0. 
-\end{align*}
-In addition,
-\begin{align*}
-& \mathbb E U_i^2 = 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2  \Prob (B_i=1)   + 
-\left( \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2 \Prob (B_i=-1) \\
-& =
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)} +  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)} \\
- & =  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left(1-\Prob_{\theta}(X_i \in A_i) \right)} 
-\end{align*}
-Therefore
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 = L_n(A_1,\ldots,A_n) \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ such that the limit above exists.
-We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition for his version of the central limit time: for any $\delta>0$ we have that
-\begin{align*}
-& \mathbb E \left| U_i \right|^{2+\delta} =
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} 
-\end{align*}
-and
-\begin{equation}
-\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} } { \left( \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta} = 
-\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
-\label{eq:Lyaponov}
-\end{equation}
-Next, we claim that there exits $\delta>0$ and $K>0$, that are independent of $n$, such that
-\begin{align}
-\frac{1}{n} \sum_{i=1}^n \mathbb E  |U_i|^{2+\delta}  < M \label{eq:Lyaponov_num}
-\end{align} 
-for all $n$ large enough. To see this, note that
-\begin{align*}
-& \mathbb E |U_i|^{2+\delta} = 
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}  \\
-  &  = \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} } 
-  \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \\
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}, 
-\end{align*}
-where the last transition is because 
-\[
- \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \leq 1. 
-\]
-We now use the fact that each $A_i$ is a finite union of interval and consider the following lemma, proof of which is given in the appendix:
-\begin{lem} \label{lem:bound_intervals_delta}
-Let $f(x)$ be a log-concave, symmetric, and differentiable PDF such that $\eta(x)$ is unimodal.  There exists $\delta>0$ such that for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, 
-\begin{equation}
-\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^{2+\delta} }
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} } 
-\leq  2^\delta f^{2+\delta}(0). 
-\label{eq:lem_bound_intervals_delta}
-\end{equation}
-\end{lem}
-
-Lemma~\ref{lem:bound_intervals_delta} implies 
-\begin{align*}
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} = \frac{\left| \sum_{k=1}^{K_i} (-1)^k f(x_{i,k}-\theta) \right|^{2+\delta} }
-  { \left( \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta} \left( 1 - \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta}} \\
-  & \leq 2^\delta f^{2+\delta}(0). 
-\end{align*}
-In particular, we conclude that 
-\[
-\frac{1}{n} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} \leq 2^\delta f^{2+\delta}(0), 
-\]
-and thus for any $\delta>0$ the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we conclude that 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{D}{\rightarrow} \mathcal N\left(0,\kappa(\theta) \right). 
-\]
-
-\subsubsection*{Proof of Claim II} 
-We have:
-\begin{align*}
-\mathbb E V_i  & = 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)}  
-+ 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)}  \\
- & = 
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left( 1-\Prob_{\theta}(X_i \in A_i) \right)}  
-\end{align*}
- We conclude that:
-\begin{equation} \label{eq:LAN_limit_cond}
-\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =   L_n(A_1,\ldots,A_n)  \to \kappa(\theta)
-\end{equation}
-Since the $V_i$s are independent of each other, Kolmogorov's law of large numbers implies
-%(e.g. \cite[Theorem 10.2.3]{sen1994large}) 
-\[
-\frac{1}{n} \sum_{i=1}^n  V_i \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ for which the limit \eqref{eq:LAN_limit_cond} exists.
-
-\QEDA
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals_delta}} 
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-and 
-\[
-\eta_\delta(x) \triangleq  \frac{  \left(\delta_1(x) \right)^{2+\delta}}{  \left(\Delta_1(x)  \right)^{1+\delta}
-(1-\Delta_1(x))^{1+\delta}}
-= \frac{  \left( f (x) \right)^{2+\delta}}{ \left(F(x) \right)^{1+\delta}(1-F(x))^{1+\delta}}. 
-\]
-The proof is by induction on $n$.
-For the case $n=1$ the LHS of \eqref{eq:lem_bound_intervals_delta} equals $\eta_\delta(x)$.
-Note that $\eta_\delta(0) = 2^\delta f^{2+\delta}(0)$, so it is enough to prove that $\eta_\delta(0)$ attains it maximum at $x=0$.
-We have $\eta_\delta(x) = \eta^{1+\delta}(x)/f^\delta(x)$, and thus
-\[
-\log \eta_\delta'(x) = (1+\delta) \frac{\eta'(x)}{\eta(x)} - \delta \frac{f'(x)}{f(x)}. 
-\]
-By Assumption~\ref{assump:failure_rate} both terms above are negative for $x>0$, so that $\log \eta_\delta'(x) \leq 0$ if and only if
-\begin{equation} \label{eq:delta_proof_cond}
-(1+\delta) \left| \frac{\eta'(x)}{\eta(x)} \right| \geq \delta \left| \frac{f'(x)}{f(x)} \right|, \qquad x>0.
-\end{equation}
-Also by Assumption~\ref{assump:failure_rate}, for $x>0$ we have
-\[
-0 > (\log \eta(x))' = \frac{h'(x)}{h(x)}-\frac{h'(-x)}{h(-x)},
-\]
-so that \eqref{eq:delta_proof_cond} is satisfies for $\delta>0$ small enough.
-
-Next, assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^{2+\delta}} 
-{\left(\Delta_n \right)^{1+\delta}\left(1- \Delta_n \right)^{1+\delta} } \leq \eta_\delta(0) = 2^\delta f^{2+\delta}(0) . 
-\label{eq:lem_bound_intervals_delta_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%If $x_{i+1} = x_i$ for some $i=1,\ldots,N-1$, then then the indices $i$ and $i+1$ may  be removed from all sums in \eqref{eq:lem_bound_intervals}, what brings us to the case $n = N-2$.
-Therefore, we may assume that $x_1 < \ldots < x_n$.
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  (2+\delta) \log \delta_N - (1+\delta) \log \Delta_N - (1+\delta) \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{(2+\delta) (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(1+\delta)(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(1+\delta)(-1)^{k+1} f(x_k)}{1-\Delta_N }.
-\]
-We conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero_delta}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N(1+\delta)}{2+\delta} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-From the same reason as in the proof of Lemma~\ref{lem:bound_intervals}, \eqref{eq:gradient_zero_delta} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_delta_proof} equals $\eta_\delta(x_1)$ which was shown to be smaller than $\eta_\delta(\epsilon)$.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_delta_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$,  $x_i, x_{i+1} = -\epsilon$ for some $i$, or $x_i, x_{i+1} = \epsilon$ for some $i$.
-It is therefore enough to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Assume first $x_N \rightarrow -\infty$. Then 
-\begin{align*}
-\frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)^{1+\delta} } ,
-\end{align*}
-which is smaller than $\eta_\delta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
-\begin{align*}
-& \frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right)^{1+\delta} }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^{2+\delta}} 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)^{1+\delta}\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right)^{1+\delta} },
-\end{align*}
-where $x'_{m} = x_{m+1}$ for $m=1,\ldots, N-1$. The last expression is smaller than $\eta_{\delta}(0)$ by the induction hypothesis.  \QEDA \\
-
-\subsection*{Proof of Theorem~\ref{thm:non_existence}}
-
-Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta) = \eta(0)$. 
-%
-Since $B_1,B_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, for $\theta \in \Xi$ if and only if
-\begin{equation}
-\label{eq:non_existence_proof}
-\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0). 
-\end{equation}
-By assumption, we have $B_i^{-1} = A_i$ where $A_i$ can be expressed as
-\[
-A_i = \cup_{i=1}^K (a_{i,k},b_{i,k}), 
-\]
-where $a_{i,1} \leq b_{i,1} \leq \ldots \leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values $-\infty$ and $\infty$, respectively. Denote
-\[
-\mathcal B_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\}.
-\]
-For any $\theta$ and $\epsilon>0$, denote 
-\[
-S_n(\theta, \epsilon) \triangleq \left\{ i\leq n \,:\, (\theta-\epsilon,\theta+\epsilon) \cap \mathcal B_i \neq \emptyset \right\}
-\]
-In words, $S_n$ contains all integers smaller than $n$ in which an $\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals consisting $A_i$. 
-%
-We now claim that 
-if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. Indeed, for such $\theta$ we have
-\begin{align}
-& L_n(A_1,\ldots,A_n; \theta) \nonumber \\
-& = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
-\frac{ \left(\sum_{k=1}^{K}  f(\theta - b_{i,k})- f(\theta - a_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& 
-+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(b_{i,k}-\theta) - f(a_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
-& \overset{(a)}{\leq}
-\frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
- \label{eq:non_existence_proof1}
-\end{align}
-where $(a)$ follows from Lemma~\ref{lem:bound_intervals} and the fact that for $i \in S_n(\theta, \epsilon)$, 
-\[
-\max\left\{ \max_k \eta(b_{i,k}-\theta) , \max_k \eta(a_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
-\]
-Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, \eqref{eq:non_existence_proof1}, and thus $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.
-\par
-For $k\in \mathbb N$, assume by contradiction that there exists $N \geq 2K + 1$ distinct elements
-$\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$ consists of at most $K$ intervals, we have that 
-\begin{equation}
-\label{eq:few_optimality_points_proof}
-\card (\cup_{i=1}^n \mathcal B_i) \leq 2 n K. 
-\end{equation}
-Fix $\epsilon>0$ such that 
-\[
-\epsilon < \frac{1}{2}\min_{i\neq j} |\theta_i - \theta_j|. 
-\]
-Since for each $\theta \in \Theta$ we have $S_n(\theta, \epsilon) \to 1$, there exists $n$ large enough such that 
-\[
-\card \left(S_n(\theta_i, \epsilon) \right) \geq n \left(1-\frac{1}{2N} \right)
-\]
-for all $i=1,\ldots,N$.
-However, $S_n(\theta_1,\epsilon), \ldots S_n(\theta_N,\epsilon)$ are disjoint, so the cardinallity of their union is at least $n\left(1-\frac{1}{2N} \right)N$ which is grater than $2nK + n/2$ in contradiction to \eqref{eq:few_optimality_points_proof}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEfull,onebit}
-
-\end{document}
+%% \end{axis}
+%% \end{tikzpicture}
+%% %
+%% \begin{tikzpicture}[scale = 0.6]
+%% \begin{axis}[
+%% width=8cm, height=6cm,
+%% xmin = -4, xmax=4, 
+%% restrict y to domain = -10:0,
+%% ymin = -10,
+%% samples=10, 
+%% xlabel= $x$,
+%% xtick={-3,-2,-1,0,1,2,3},
+%% xticklabels={-3,-2,-1,0,1,2,3},
+%% ytick={0,-0.45158,-0.919},
+%% yticklabels={0,,},
+%% line width=1.0pt,
+%% mark size=1.5pt,
+%% ymajorgrids,
+%% xmajorgrids,
+%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+%% ]
+%% \addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {./Figs/eta.csv};
+%% \addlegendentry{$\log \eta(x)$};
+%% \addplot[domain = -5:5, samples = 30, color = red, solid, smooth]  {-(x)^2/2 -0.9189};
+%% \addlegendentry{$\log \phi(x)$};
+%% \end{axis}
+%% \end{tikzpicture}
+%% \caption{
+%% The function $\eta(x) = f^2(x) / F(x)F(-x)$ for $f(x) = \phi(x)$ the standard normal density.
+%% \label{fig:eta}
+%% }
+%% \end{center}
+%% \end{figure}

### 2019-09-23 introduction.tex
Rewriting intro

@@
 
-\subsection*{Related Works}
+\subsection*{Related Work}
 
-When the variance $\sigma^2$ is negligible compared the to desired accuracy,
-the task of finding $\theta$ using one-bit queries in the adaptive setting
-(ii) is solved by a bisection style method over the parameter
-space. Therefore, the general case of non-zero variance is reminiscent of
-the noisy binary search problem with a possibly infinite number of
-unreliable tests \cite{cicalese2002least,
-  Karp:2007:NBS:1283383.1283478}. However, since we assume a continuous
-parameter space, a more closely related problem is that of one-bit
-analog-to-digital conversion of a constant input corrupted by Gaussian
-noise. Using an SDM, Wong and Gray \cite{53738} showed that the output of
-the modulator converges to the true constant input almost surely, so that an
-SDM provides a consistent estimator for setting (ii). The rate of this
-convergence, however, was not analyzed and cannot be derived from the
-results of \cite{53738}. In particular, our results for setting (ii) imply
-that the asymptotic rate of convergence of the MSE in SDM to a constant
-input under an additive white Gaussian noise is at most $\sigma^2\pi/2$ over
-the number of feedback iterations. Baraniuk et. al
-\cite{baraniuk2017exponential} also considered adaptive one-bit measurements
-in the context of analog-to-digital conversion, although without noise at
-the input. By establishing the lower bound of $\sigma^2\pi/2n$ on the MSE,
-we show that the main results of \cite{baraniuk2017exponential}, an
-exponential MSE decaying rate, does not hold in the noisy setting. Stated
-otherwise, the MSE in the setting of \cite{baraniuk2017exponential} may
-decay exponentially up to the noise level, after which it decays at most as
-$\sigma^2\pi/2n$. \par
-%
-One-bit measurements in the distributed setting (iii) was considered in \cite{904560,4244748, 6882252, chen2010performance, 5184907}, but without optimizing the encoders and their detection rules.
-Consequently, the performance derived in these works are not optimal.
- % analyzed the estimation from distributed quantized measurements when the same detection rule is applied by all encoders.
-However, the error criterion considered in these works is the Fisher information rather than the MSE risk or ARE criterion.
-\par
-%Once the decision rule of each encoder is fixed, the optimal estimation of $\theta$ is determined using the maximum a posteriori probability rule.
-Hence, the distributed setting is reduced to finding the optimal decision rule of each encoder.
-The work of \cite{52470} addresses the counterpart of our setting (iii) in the case of hypothesis testing, although the results there cannot be extended to parametric estimation.
-When the parameter space $\Theta$ is finite, Tsitsiklist \cite{tsitsiklis1988decentralized} showed that when the cardinality of $\Theta$ is at most $M$ and the probability of error criterion is used, then no more than $M(M-1)/2$ different detection rules are necessary in order to attain probability of error decreasing exponentially with the optimal exponent.
-%That is, beyond $M(M-1)/2$ some decision rules can be repeated without losing optimality.
-Furthermore, in a version of this problem for the adaptive setting \cite{5751320}, it was shown that, with specific two-stage feedback, there is no gain in feedback compared to the fully distributed setting.
+The many challenges of estimation under communication constraints have given
+rise to a large literature investigating different aspects of constrained
+estimation. While our setting---in which we observe a single bit per signal
+$X_i$---is restrictive, it inspires substantial work.  Perhaps the most
+related is that of Wong and Gray~\cite{53738}, who study one-bit
+analog-to-digital conversion of a constant input corrupted by Gaussian noise
+using a Sigma-Delta Modulator (SDM). They show almost sure convergence, but
+provide no rate (and no rates follow from their analysis); in contrast, we
+provide an optimal procedure and matching lower bound achieving risk
+$\frac{\pi}{2} \sigma^2$ in the limit~\eqref{eq:ARE_def} when $X_i \simiid
+\normal(\theta, \sigma^2)$. A growing literature on one-bit measurements in
+high-dimensional problems \cite{baraniuk2017exponential, DavenportPlVaWo15,
+  PlanVe13} shows how to reconstruct sparse signals, where Baraniuk et
+al.~\cite{baraniuk2017exponential} show that in noiseless settings,
+exponential decay in MSE is possible; our results make precise the penalty
+for noise under one-bit sensing, showing that the error can decay (under
+Gaussian noise) at best as $\frac{\pi}{2} \frac{\sigma^2}{n}$.
+
+In fully distributed settings (iii), the challenges are different, and there
+is also a substantial literature with one-bit (quantized)
+measurements~\cite{904560,4244748, 6882252, chen2010performance, 5184907}.
+We complement these results by providing precise lower bounds and optimality
+results; previous performance bounds are suboptimal.  Work on the remote
+multiterminal source coding problem, or CEO problem~\cite{berger1996ceo,
+  viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}, provides
+lower bounds on the MSE in setting~(iii); because of the somewhat distinct
+setting, these bounds are looser than ours (which have optimal constants).
+In settings more similar to our statistical estimation scenario---such as
+estimation of parameters in a multi-dimensional linear model---a line of
+work provides lower bounds on statistical
+estimation~\cite{zhang2013information, duchi2014optimality, GargMaNg14,
+  BravermanGaMaNgWo16, DBLP:journals/corr/abs-1802-08417,
+  zhang1988estimation, han2018distributed, xu2017information}. These results
+are finite sample and apply more broadly than ours, but as a consequence,
+they have unusable constants, while our stylized model allows precise
+identification of exact constants.  Work subsequent to the initial draft of
+this paper~\cite{Barnes2018} uses an approach similar to ours---bounding
+quantized Fisher information---to derive lower bounds on the error in
+parametric estimation problems from quantized measurements in non-adaptive
+settings.
+
+Testing (and discrete estimation) problems also enjoy a robust literature,
+though as a consequence of our results to come, the results for testing,
+i.e., when the parameter space $\Theta$ is finite, are quite different from
+those for estimation, as it is possible to construct optimal decision
+(testing) rules in a completely distributed fashion. In this context, Longo
+et al.~\cite{52470} propose procedures for distributed testing based on
+optimizing a Bhattacharyya distance.
+Tsitsiklis~\cite{tsitsiklis1988decentralized} shows that when the
+cardinality of $\Theta$ is at most $M$ and the probability of error
+criterion is used, then no more than $M(M-1)/2$ different detection rules
+are necessary in order to attain probability of error with optimal exponent.
+Moreover, in a distributed setting, feedback is unnecessary for optimal
+testing/detection~\cite{5751320}, in strong distinction to the estimation
+case we consider.
+
+%% , it was shown that, with specific two-stage feedback, there is no gain in feedback compared to the fully distributed setting.
 Our results imply that the ARE in the distributed setting with threshold detection rules is strictly larger than that in the adaptive setting for almost all points in $\Theta$, suggesting that the case where the cardinality of $\Theta$ is finite is different from the case where $\Theta$ is an open set.\par
-%
-As we explain in detail in Section~ \ref{sec:preliminary}, the remote multiterminal source coding problem, also known as the CEO problem \cite{berger1996ceo, viswanathan1997quadratic, oohama1998rate, prabhakaran2004rate}, leads to lower bounds on the MSE in setting (iii).
-For the case of a Gaussian distribution, this lower bound bounds the ARE to be at most $3/4$.
-Thus, while this bound on the ARE provides no new information compared to the upper bound of $2/\pi$ we derive for setting (ii), it shows that the distributed nature of the problem is not a limiting factor in achieving MSE close to optimum even under the one bit per sample constraint.
- \par
-% 
-Finally, we note that minimax estimation under limited communication with an arbitrary number of bits per node was considered in 
-\cite{zhang2013information, duchi2014optimality}.
-The specialization of the results in \cite{zhang2013information, duchi2014optimality} to our settings (ii) and (iii) leads to looser lower bounds then the ones we derive in this paper.
-Looser bounds can also be obtained from works considering general inference and distributed estimation problems under data compression constraint \cite{DBLP:journals/corr/abs-1802-08417, zhang1988estimation, han2018distributed, xu2017information, Barnes2018}.
-In particular, the subsequent work of \cite{Barnes2018} uses an approach similar to ours to derive lower bound on the error in various parametric estimation problems from quantized measurements.
-\par
+
+%% As we explain in detail in Section~ \ref{sec:preliminary}, the remote
+%% multiterminal source coding problem, also known as the CEO problem
+%% \cite{}, leads to lower bounds on the MSE in setting
+%% (iii). For the case of a Gaussian distribution, this lower bound bounds the
+%% ARE to be at most $3/4$. Thus, while this bound on the ARE provides no new
+%% information compared to the upper bound of $2/\pi$ we derive for setting
+%% (ii), it shows that the distributed nature of the problem is not a limiting
+%% factor in achieving MSE close to optimum even under the one bit per sample
+%% constraint. 
+%% %
+
+%% Finally, we note that minimax estimation under limited communication with an
+%% arbitrary number of bits per node was considered in
+%% \cite{zhang2013information, duchi2014optimality}. The specialization of the
+%% results in \cite{zhang2013information, duchi2014optimality} to our settings
+%% (ii) and (iii) leads to looser lower bounds then the ones we derive in this
+%% paper. Looser bounds can also be obtained from works considering general
+%% inference and distributed estimation problems under data compression
+%% constraint \cite{DBLP:journals/corr/abs-1802-08417, zhang1988estimation,
+%%   han2018distributed, xu2017information, Barnes2018}. In particular, the
+%% subsequent work of \cite{Barnes2018} uses an approach similar to ours to
+%% derive lower bound on the error in various parametric estimation problems
+%% from quantized measurements. \par
 

### 2019-09-23 problem-formulation.tex
Working on problem setting

@@
 
-\section{Problem Formulation \label{sec:problem}}
+\section{Problem Formulation and Notation}
+\label{sec:problem}
 
-Let $f(x)$ be a symmetric and log-concave density function with a finite second moment $\sigma^2$.
-For $\theta \in \Theta$, denote by $P_X$ the probability distribution with density $f\left( x-\theta \right)$.
-Therefore, $P_X$ is an absolutely continuous log-concave distribution with mean $\theta$ and variance $\sigma^2$.
-Symmetry and log-concavity of $f(x)$ imply that $P_X$ is strongly unimodal (has a unique local maxima) with its mode at $x =\theta$ \cite{ibragimov1956composition}.
-We further assume that the \emph{parameter space} $\Theta$ is a closed interval of the real line.
-\par
-In some situations it is useful to assume that $\theta$ is drawn once from the prior distribution $\pi$ on $\Theta$.
-In this case we assume that $\pi$ is an absolutely continuous distribution, and denote its density by $\pi(\theta)$, i.e., $\pi(d\theta) = \pi(\theta)d\theta$.
-\par
-The random variables $X_1,\ldots,X_n$ represent $n$ independent samples from $P_X$. 
-We are interested in estimating $\theta$ from a set of $n$ binary messages $B_1,\ldots,B_n$, obtained from $X_1,\ldots,X_n$ under three possible scenarios illustrated in Figure~\ref{fig:setup}: 
-\begin{itemize}
-\item[(i)~~] Centralized $B_i(X_1,\ldots,X_n)$, $i=1,\ldots,n$.
-\item[(ii)~] Adaptive $B_i(X_i,B_1,\ldots,B_{i-1})$, $i=2,\ldots,n$.
-\item[(iii)] Distributed $B_i(X_i)$, $i=1,\ldots,n$.
-\end{itemize}
+Let $f : \R \to \R_+$ be a symmetric and log-concave probability density,
+which necessarily has finite second moment $\sigma^2$, and let $\Theta
+\subset \R$ be closed and convex.  For $\theta \in \R$, let $P_\theta$ be
+the probability distribution with density $f(x-\theta)$, so that $\theta$
+indexes the location family $\{P_\theta\}_{\theta \in \Theta}$.  The
+log-concavity and symmetry $f(x)$ imply that $P_\theta$ has a unique mean
+and median at $\theta$~\cite{ibragimov1956composition}.
+We observe a sample $X_1, \ldots, X_n \simiid P_\theta$, where $\theta$
+is unknown, and wish to estimate $\theta$ given only binary
+messages $B_1, \ldots, B_n \in \{0, 1\}$ about each $X_i$.
+We study this under three distinct computational scenarios, which
+we illustrate in Figure~\ref{fig:setup}:
+\begin{enumerate}[(i)]
+\item \label{item:centralized} Centralized, where $B_i =
+  B_i(X_1,\ldots,X_n)$, $i=1,\ldots,n$.
+\item \label{item:adaptive} Adaptive, where $B_i =
+  B_i(X_i,B_1,\ldots,B_{i-1})$, $i=2,\ldots,n$.
+\item \label{item:distributed}
+  Distributed, where $B_i = B_i(X_i)$, $i=1,\ldots,n$.
+\end{enumerate}
+\noindent
+We also consider a hybrid of the fully distributed setting (where the bits
+$B_i$ are independent) and the adaptive setting (where each bit $B_i$ may
+depend on the previous bits) to a \emph{one-step} adaptive setting, where
+the quantization scheme may be modified to depend on one fixed function of
+the previous information.
+\begin{enumerate}[(i')]
+\setcounter{enumi}{1}
+\item One-step adaptive, where for some function $g$ and
+  a (fixed) $t$, if $i \le t$ then
+  $B_i = B_i(X_i)$ while if $i > t$, then
+  $B_i = B_i(X_i, g(B_1, \ldots, B_t))$.
+\end{enumerate}
 
-The performance of an estimator ${\theta}_n \triangleq {\theta}_n(B^n)$ in any of these cases is measured according to the quadratic risk:
+We measure the performance of an estimator $\theta_n \defeq
+\theta_n(B_1^n)$ by one of a few notions. In the simplest case,
+we assume a prior $\pi$ on $\theta$ (which may be a point
+mass) and consider the quadratic risk
 \begin{equation}
   \label{eq:error_def}
-R_n \triangleq \mathbb E\left({\theta}_n - \theta \right)^2,
+  R_n = R_n(\pi) \defeq \int \E_\theta\left({\theta}_n - \theta \right)^2
+  d\pi(\theta),
 \end{equation}
-where the expectation is taken with respect to the distribution of $X_1,\ldots,X_n$ and, whenever available, a prior distribution $\pi(\theta)$ over $\Theta$.  
-%It is well known that minmax estimation error 
-%\begin{equation}
-%R_n = \min \sup_{\theta \in \Theta}  \mathbb E\left[ \left({\theta}_n - \theta \right)^2 | \theta \right],
-%\end{equation}
-%can be obtained from $R_n$ by assuming a particular least favorable prior distribution on the parameter space $\Theta$ \cite{casella1981}. 
-%
-The main problems we consider in this paper are the minimal value of \eqref{eq:error_def}, as a function of $n$ and $f(x)$, under different choices of the encoding functions in cases (i), (ii), and (iii).
-\par
+where the expectation is taken with respect to the distribution of
+$X_1,\ldots,X_n \simiid P_\theta$.  The main problems we consider in this
+paper are the minimal value of the risk~\eqref{eq:error_def} as a function
+of the sample size $n$ and the density $f$, under different choices of the
+encoding functions in
+cases~\eqref{item:centralized}--\eqref{item:distributed}.
+The quadratic risk~\eqref{eq:error_def} may be infinite in some cases;
+we defer discussion of this case to later sections, as it is technically
+demanding and detracts from the presentation here.
 
-We give particular attention to the ARE of estimators with respect to an asymptotically normal efficient estimator that is not subject to the bit constraint.
-Specifically, let $\{a_n,\,n\in \mathbb N\}$ be a sequence such that
+Now, let $\sigma_f^2 \defeq \E[\frac{f'(X)^2}{f(X)^2}]$ be the Fisher
+information for the location in the family $\{P_\theta\}$, which is finite
+when $f$ is log-concave and symmetric. We give particular attention to the
+asymptotic relative efficiency (ARE) of estimators with respect to
+asymptotically normal efficient estimators achieving the information
+bound~\cite{VanDerVaart98}. In this case,
+if $\{m(n), n \in \N\}$ is a sequence such that
+\begin{equation*}
+  \sqrt{m(n)} (\theta_n - \theta) \cd \normal(0, \sigma_f^2),
+\end{equation*}
+then the ARE of the estimator is~\cite[Def.~6.6.6]{LehmannCa98}
+\begin{equation*}
+  \ARE({\theta}_n) \defeq
+  \liminf_{n\rightarrow \infty} \frac{m(n)}{n}.
+\end{equation*}
+In the special case where there exists $V \in \mathbb R$ such that
 \[
-\sqrt{a_n}\left({\theta}_n - \theta\right) \overset{d}{\longrightarrow} \Ncal(0, \sigma^2).
+m(n) R_n =
+m(n) \mathbb E_\theta\left({\theta}_n - \theta \right)^2 = V + o(1),
 \]
-Then the ARE of ${\theta}_n$ with respect to an unconstrained efficient estimator for $\theta$ is defined as \cite[Def. 6.6.6]{lehmann2006theory}
-\[
-\ARE({\theta}_n) \triangleq
-\lim_{n\rightarrow \infty} \frac{a_n}{n}. 
-\]
-Note that in the special case where there exists $V \in \mathbb R$ such that
-\[
-a_n \mathbb E \left({\theta}_n - \theta \right)^2 = V + o(1),
-\]
-with $o(1)\to 0$ as $n\to \infty$, then the ARE of ${\theta}_n$ is finite and equals $\sigma^2/V$. \par
+the ARE of ${\theta}_n$ is $\sigma_f^2/V$, so that $\theta_n$ requires a
+sample $V / \sigma_f^2$-times larger than that of an efficient estimator for
+comparable accuracy to the (information) efficient estimator.
+
+%%% JCD: I AM HERE BUT STILL GOING THROUGH THINGS %%%
 

### 2019-09-24 problem-formulation.tex
Minor

@@
 In the special case where there exists $V \in \mathbb R$ such that
-\[
+\begin{equation*}
 m(n) R_n =
 m(n) \mathbb E_\theta\left({\theta}_n - \theta \right)^2 = V + o(1),
-\]
+\end{equation*}
 the ARE of ${\theta}_n$ is $\sigma_f^2/V$, so that $\theta_n$ requires a
@@
 where 
-\[
+\begin{equation*}
 h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
-\]
+\end{equation*}
 is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function since $f(x)$ is log-concave \cite{bagnoli2005log}. 
@@
 Under this assumption we have, 
-\[
+\begin{equation*}
 4f^2(x) \leq \eta(x) \leq \eta(0),
-\] 
+\end{equation*} 
 %

### 2019-09-26 appendices.tex
Fixed proof of (previously) Lemma 15 and made changes in structure regarding this lemma. Now one lemma (Lemma 12) is used in three different results.

@@
 
-\subsection{Proof of Lemma~\ref{lem:bound_intervals_delta} \label{proof:lem:bound_intervals_delta}}
-
-%\begin{lem} \label{lem:bound_intervals}
-%Let $f(x)$ be a log-concave, symmetric, and differentiable density such that $\eta(x)$ is strongly unimodal. For any $x_1 > \ldots > x_n \in \mathbb R$, 
-%\begin{equation}
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \max_i \eta(x_i). \label{eq:lem_bound_intervals}
-%\end{equation}
-%In particular, if $|x_i|>\epsilon > 0$ for all $i=1,\ldots,n$, then 
-%\[
-%\frac{ \left(  \sum_{k=1}^n (-1)^{k+1} f(x_k) \right)^2} 
-%{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)\left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-%\leq \eta(\epsilon) < 0. 
-%\]
-%\end{lem}
-
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-so 
-\[
-\eta(x) =  \frac{  \left(\delta_1(x) \right)^2}{\Delta_1(x)
-(1-\Delta_1(x))}
-= \frac{  \left( f (x) \right)^2}{ F(x)\left(1-F(x)\right)^2}. 
-\]
-We use induction on $n \in \mathbb N$ to show that the LHS of \eqref{eq:lem_bound_intervals_delta} is bounded from above by $\max_i \eta(x_i)$. The case $n=1$ is trivial. Assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^2} 
-{\Delta_n \left(1- \Delta_n \right) } \leq \max_i \eta(x_i)
-\label{eq:lem_bound_intervals_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  2 \log \delta_N -  \log \Delta_N -  \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{2 (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(-1)^{k+1} f(x_k)}{1-\Delta_N },
-\]
-and we conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-%
-Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable. We have 
-\[
-\frac{f'(x)}{f(x)} = c'(x), \quad x\in \mathbb R,
-\]
-which is anti-symmetric, non-negative for $x<0$,  non-positive for $x>0$, and non-increasing since $c(x)$ is concave.
-Therefore, if $c'(x_i) = c'(x_{i+1})$ for some $i =1,\ldots,N-1$, then either (1) $x_i = x_{i+1}$ or (2) $c'(x)$ is the zero function.
-Since (2) violates the assumption that $f(x)$ is a density function, we conclude that $c'(x)$ is an injection.
-%
-As a result, \eqref{eq:gradient_zero} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_proof} equals $\eta(x_1) = \max_i \eta(x_i)$ hence the statement holds.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$, or  $x_i, x_{i+1}$ for some $i$.
-It is left to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Under case (1) we have
-\begin{align*}
-\lim_{x_N \to -\infty} \frac{  \delta_N^2} 
-{\Delta_N \left(1- \Delta_N \right) }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^2} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)} ,
-\end{align*}
-which is smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis. Under case (2) we have
-\begin{align*}
-&  \lim_{x_1 \to \infty}
-\frac{ \delta_N} 
-{\Delta_N\left(1- \Delta_N \right) } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right) \left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right) }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^2 } 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right) },
-\end{align*}
-where $x'_{m} = x_{m+1}$. The last expression is also smaller than $\max_i \eta_i(x_i)$ by the induction hypothesis.  \QEDA \\
-
 \subsection{Proof of Theorem~\ref{thm:adpative_lower_bound}
@@
 }
-
-We first prove the following lemma:
+Consider the following two Lemmas:
+\begin{lem} \label{lem:bound_intervals}
+Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$ and $\delta>0$,
+\begin{equation}
+\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^2 }
+{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
+\leq  4f^2(0). 
+\label{eq:lem_bound_intervals}
+\end{equation}
+\end{lem}
 \begin{lem} \label{lem:fisher_bound}
-Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that $\eta(x)$ is unimodal. For a Borel measurable $A$ set, 
+Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that Assumption~1 holds. For a Borel measurable $A$ set, 
 \[
@@
 
+Lemma~\ref{lem:bound_intervals} is obtained as the special case $\delta = 0$ of lemma \ref{lem:bound_intervals_delta}. 
+We now prove Lemma~\ref{lem:fisher_bound}.
 \subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
@@
 \begin{align}
-I_\theta & =  \mathbb E \left[ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta \right] \nonumber \\
+I_\theta & =  \ex{ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta } \nonumber \\
 & = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
@@
 \end{align}
-It follows from Lemma~\ref{lem:bound_intervals_delta} that for any $\theta \in \mathbb R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than $4f^2(0)$.  \QEDA \\
+It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in \R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than 
+\[
+\max_{t \in \{a_j,b_j, j=1,\ldots,k\} } 4f^2(t) \leq 4 f^2(0), 
+\]
+where the last transition is due to Assumption~1. 
+\QEDA \\
 
@@
 \end{equation}
-where $A_i \subset \mathbb R$ is a Borel measurable set. 
+where $A_i \subset \R$ is a Borel measurable set. 
 %Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
@@
 \begin{align*}
-\mathbb E \left( \theta_n - \theta \right)^2 &  \geq \frac{1}{ \mathbb E I_\theta(B^n) + I_0} \\
+\ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ \ex{ I_\theta(B^n)} + I_0} \\
 & = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
@@
 \end{align*}
+\QEDA
+
+\subsection{Isoperimetric Lemma
+\label{sec:bound_intervals_delta} }
+The following lemma is used in the proof Theorems~\ref{thm:adpative_lower_bound}, \ref{thm:LAN1}, and \ref{thm:non_existence}.
+
+\begin{lem} \label{lem:bound_intervals_delta}
+Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$ and $\delta>0$,
+\begin{equation}
+\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
+{\left( \sum_{i=1}^n (-1)^{i+1} F(x_i) \right) \left(1- \sum_{k=1}^n (-1)^{i+1} F(x_i) \right) } 
+\leq  \max_{i} \eta_\delta(x_i),
+\label{eq:lem_bound_intervals_delta}
+\end{equation}
+where 
+\[
+\eta_\delta(x) \triangleq \frac{  \left( f(x) \right)^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}}. 
+\]
+\end{lem}
+
+\subsubsection*{
+Proof of Lemma~\ref{lem:bound_intervals_delta}}
+Denote 
+\[
+\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
+\]
+\[
+\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k). 
+\]
+Note that 
+\[
+\eta_\delta(x) =  \frac{  \left(\delta_1(x) \right)^{2+\delta}}{ (\Delta_1(x))^{1+\delta}
+(1-\Delta_1(x))^{1+\delta}}. 
+\]
+Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable, with a non-increasing derivative $c'(x)$.
+We first prove the lemma under the assumption that
+\[
+c'(x) \triangleq \frac{f'(x)}{f(x)}, 
+\]
+is an injection, or, equivalently, that $c(x)$ is strictly decreasing for all $x\in \R$. \par
+We use induction on $n \in \N$ to show that the LHS of \eqref{eq:lem_bound_intervals_delta} is bounded from above by $\max_i \eta_\delta(x_i)$. The case $n=1$ is trivial. Assume that 
+\begin{equation}
+\frac{ \left( \delta_n \right)^{2+\delta}} 
+{\left(\Delta_n\left(1- \Delta_n \right) \right)^{1+\delta} } \leq \max_i \eta_{\delta}(x_i)
+\label{eq:lem_bound_intervals_proof}
+\end{equation}
+for all integers up to $n = N-1$ and consider the case $n = N$. 
+%
+The maximal value of the LHS of \eqref{eq:lem_bound_intervals_proof} is attained for the same $(x_1,\ldots,x_N) \in \R^N$ that attains the maximal value of 
+\begin{align*}
+& g(x_1,\ldots, x_N) \triangleq  (2+\delta) \log \delta_N - (1+\delta) \log \Delta_N - (1+\delta) \log \left(1 - \Delta_N  \right),
+\end{align*}
+The partial derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
+\[
+\frac{\partial  g}{\partial x_k} = \frac{(2+\delta) (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(1+\delta) (-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(1+\delta)(-1)^{k+1} f(x_k)}{1-\Delta_N },
+\]
+and we conclude that the gradient of $g$ vanishes if and only if
+\begin{equation}
+\label{eq:gradient_zero}
+c'(x_k) = \frac{f'(x_k)}{f(x_k)} = \frac{1+\delta}{2+\delta} \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
+\end{equation}
+%
+Since we assumed that $c'(x)$ is an injection, \eqref{eq:gradient_zero} is satisfied if and only if $x_1 = \ldots = x_N$.
+For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_proof} equals $\eta(x_1) = \max_i \eta(x_i)$ hence the statement holds.
+For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
+Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_proof} is not attained at the line $x_1=\ldots=x_N)$.
+We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_proof} is maximized at the borders.
+That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
+As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_proof} is zero and thus this case reduces to the case $n= N-2$.
+A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$, or  $x_i, x_{i+1}$ for some $i$.
+It is left to consider the cases:
+\begin{itemize}
+\item[(1)]  $x_N \to -\infty$.
+\item[(2)] $x_1 \to \infty$.
+\end{itemize}
+Under case (1) we have
+Assume first $x_N \rightarrow -\infty$. Then 
+\begin{align*}
+\frac{ \left( \delta_N \right)^{2+\delta}} 
+{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  }
+ = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
+{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)^{1+\delta} } ,
+\end{align*}
+which is smaller than $\eta_\delta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
+\begin{align*}
+& \frac{ \left( \delta_N \right)^{2+\delta}} 
+{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  } \\
+=
+& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
+{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right)^{1+\delta} }  \\
+& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^{2+\delta}} 
+{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)^{1+\delta}\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right)^{1+\delta} },
+\end{align*}
+where $x'_{m} = x_{m+1}$ for $m=1,\ldots, N-1$. The last expression is also smaller than $\max_i \eta_\delta (x_i)$ by the induction hypothesis.  \par
+It is left to consider the case where $c'(x)$ is not necessarily strictly decreasing.
+We approximate $c(x)$ using another concave symmetric function whose derivative is always negative except at the origin.
+For $\alpha>0$ consider the function  $f_\alpha(x) = \kappa(\alpha) e^{\sgn(c(x))|c(x)|^{1+\alpha}}$, where $\kappa(\alpha)$ is chosen such that $f_\alpha(x)$ is a probability density function.
+Then $c_\alpha(x)$ is concave, symmetric, and differentiable with
+\[
+c_\alpha'(x) \triangleq \frac{f'_\alpha(x)}{f_\alpha(x)} = (1+\alpha)|c(x)|^{\alpha} c'(x). 
+\]
+Now $c_\alpha'(x)$ is non-increasing since it is the derivative of a concave function.
+It can be verified that it is non-constant on any interval (because $c(x)$ is non-constant and $c'(x)$ is non-increasing), and hence an injection.
+It follows from the first part of the proof that, for any $\alpha>0$,
+\begin{align}
+\label{eq:proof:lem:bound_intervals}
+\frac{(\delta_{n,\alpha})^2}{\Delta_{n,\alpha}(1-\Delta_{n,\alpha})} \leq \max_i \eta_{\alpha}(x_i),
+\end{align}
+where 
+\[
+\delta_{n,\alpha} \triangleq  \sum_{k=1}^{n} (-1)^{k+1} f_{\alpha}(x_k),
+\]
+\[
+\Delta_{n,\alpha} \triangleq \sum_{k=1}^n (-1)^{k+1} F_{\alpha}(x_k), 
+\]
+and 
+\[
+\eta_{\delta,\alpha}(x) \triangleq \frac{(f_\alpha(x))^{2+\delta}}{\left(F_{\alpha}(x)(1-F(x)) \right)^{1+\delta}}. 
+\]
+The proof is completed by noting that 
+\begin{align*}
+\lim_{\alpha \to 0} \frac{(\delta_{n,\alpha})^{2+\delta} }{ \left(\Delta_{n,\alpha}(1-\Delta_{n,\alpha})\right)^{1+\delta}}  = \frac{(\delta_{n})^{2+\delta }}{\left(\Delta_{n}(1-\Delta_{n}) \right)^{1+\delta}},
+\end{align*}
+and, since the maximum is over a finite set,
+\begin{align*}
+\lim_{\alpha \to 0}  \max_i \eta_{\delta,\alpha}(x_i)  = \max_i\eta_\delta(x_i).
+\end{align*}
+
+%Our goal is to construct an approximation to $f(x)$ using a log-concave, symmetric, and differentiable function $\hat{f}(x)$ such that $\hat{f}'(x)/\hat{f}(x)$ is strictly decreasing.
+We achieve such an approximation by modifying $f(x)$ over intervals over which $c'(x)$ is a constant.
+Assume first $c'(x)$ is only a constant over an interval $(a_1,b_1)\subset \R$ containing $x_1>0$ and on the mirror image of this interval around $x=0$.
+Over this interval, $f(x)$ is necessarily of the form $f(x) = e^{-c_1|x| + d_1}$ for some $c_1\geq 0$ and $d_1$.
+% and For $\alpha>0$, consider
+%\[
+%F_1(x,\alpha) \triangleq  F(a_1) + \frac{1}{c_1} e^{-c_1 (|x|^{1+\alpha} +d_1}, \quad x \in (a_1,b_1),
+%\]
+%and 
+%\[
+%f_1(x,\alpha) \triangleq  F_1'(x,\alpha) =  -\sgn(x)(1+\alpha)|x|^\alpha e^{-c_1 |x|^{1+\alpha} + d_1}, \quad x \in (a_1,b_1).
+%\]
 
@@
 \begin{enumerate}
-\item[(i)] There exits $K_1$ such that $\left| \varphi(x) \right| \leq K_1(1+|x|)$ for all $x\in \mathbb R$.
+\item[(i)] There exits $K_1$ such that $\left| \varphi(x) \right| \leq K_1(1+|x|)$ for all $x\in \R$.
 \item[(ii)] The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions \eqref{eq:conditions1}.
@@
 
-Using the notation above, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have that $\chi(x) = \mathbb E \sgn^2(x+Z_1) = 1$, so $\chi(0) = 1$. In addition,
+Using the notation above, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have that $\chi(x) = \ex{ \sgn^2(x+Z_1) }= 1$, so $\chi(0) = 1$. In addition,
 \begin{align*}
@@
 \subsubsection*{Proof of (ii)}
-We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\mathbb R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates.
+We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates.
 Then
@@
 under $\Prob_{\theta,n}$.
-Under the assumption that $f(x)$ is continuously differentiable with a finite location Fisher information, the model $\{Z_n+ \theta\}_{n \in \mathbb N}$ is differentiable in quadratic mean \cite[Exm.
+Under the assumption that $f(x)$ is continuously differentiable with a finite location Fisher information, the model $\{Z_n+ \theta\}_{n \in \N}$ is differentiable in quadratic mean \cite[Exm.
 7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
@@
 \[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)} \right)^2 f(x) dx,
+I_\theta = \int_{\R} \left( \frac{f'(x)}{f(x)} \right)^2 f(x) dx,
 \]
@@
 \[
-\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-h}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
+\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-h}{\psi'(0)} \int_{\R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
 \]
@@
 \end{thm}
-We now use this theorem to show regularity of $\bar{\theta}_n$. We have, 
+We now use this theorem to establish the regularity of $\bar{\theta}_n$. We have, 
 \begin{align*}
@@
 \[
-\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = -2f(0) = -\psi'(0). 
+\int_{\R} \varphi(x) f'(x) dx = \int_{\R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = -2f(0) = -\psi'(0). 
 \]
@@
 Assume that the function $g(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative.
-In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \mathbb R$.
+In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \R$.
 Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution with a density for which the Fisher information exits.
@@
 Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$.
-Theorem~\ref{thm:polyak_new} implies that for any $\theta \in \mathbb R$,
+Theorem~\ref{thm:polyak_new} implies that for any $\theta \in \R$,
 \[
@@
 \]
-For $a>0$ and $n \in \mathbb N$, define the event
+For $a>0$ and $n \in \N$, define the event
 \[
@@
 & \ex{ G_n J_n} = \frac{1}{\psi'(0)}\frac{1}{n} \sum_{i=1}^n \ex{ \varphi(Z_i) \frac{f'(Z_i)}{f(Z_i)} }  \\
-& = \frac{1}{ \psi'(0)} \ex{ \varphi(Z_1) \frac{f'(Z_1)}{f(Z_1)}} =  \frac{1}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx , 
+& = \frac{1}{ \psi'(0)} \ex{ \varphi(Z_1) \frac{f'(Z_1)}{f(Z_1)}} =  \frac{1}{ \psi'(0)} \int_{\R} \varphi(x) f'(x) dx , 
 \end{align*}
@@
 \left(\sqrt{n} \bar{\Delta}_n, \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} \right) \overset{d}{\to} \Ncal \left( \left(0,-\frac{h^2}{2} I_\theta \right),  \begin{pmatrix}
-\frac{\chi(0)}{\psi'^2(0)} & \frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx \\
-\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx & h^2 I_\theta 
+\frac{\chi(0)}{\psi'^2(0)} & \frac{-h}{ \psi'(0)} \int_{\R} \varphi(x) f'(x) dx \\
+\frac{-h}{ \psi'(0)} \int_{\R} \varphi(x) f'(x) dx & h^2 I_\theta 
 \end{pmatrix}  \right)
@@
 \[
-\sqrt{n}\bar{\Delta}_n \overset{d}{\to} \Ncal\left(\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx,  \frac{\chi(0)}{\psi'^2(0)} \right).
+\sqrt{n}\bar{\Delta}_n \overset{d}{\to} \Ncal\left(\frac{-h}{ \psi'(0)} \int_{\R} \varphi(x) f'(x) dx,  \frac{\chi(0)}{\psi'^2(0)} \right).
 \]
@@
 \begin{align*}
-\mathbb E  [U_i] & = 
+\ex{U_i} & = 
  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=1)   + 
@@
 \begin{align*}
-& \mathbb E U_i^2 = 
+& \ex{ U_i^2} = 
 \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2  \Prob (B_i=1)   + 
@@
 \[
-\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2 = L_n(A_1,\ldots,A_n) \overset{a.s.}{\longrightarrow} \kappa(\theta)
+\frac{1}{n} \sum_{i=1}^n \ex{ U_i^2} = L_n(A_1,\ldots,A_n) \overset{a.s.}{\longrightarrow} \kappa(\theta)
 \]
@@
 \begin{align*}
-& \mathbb E \left| U_i \right|^{2+\delta} =
+& \ex{ \left| U_i \right|^{2+\delta} }=
  \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
@@
 \begin{align}
-\frac{1}{n} \sum_{i=1}^n \mathbb E  |U_i|^{2+\delta}  < M \label{eq:Lyaponov_num}
+\frac{1}{n} \sum_{i=1}^n \ex{ |U_i|^{2+\delta}}  < M \label{eq:Lyaponov_num}
 \end{align} 
@@
 \begin{align*}
-& \mathbb E |U_i|^{2+\delta} = 
+& \ex{ |U_i|^{2+\delta} }= 
  \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
@@
 \]
-We now use the fact that each $A_i$ is a finite union of interval and consider the following lemma, proof of which is given in Appendix~\ref{proof:lem:bound_intervals_delta}.
-\begin{lem} \label{lem:bound_intervals_delta}
-Let $f(x)$ be a log-concave, symmetric, and differentiable PDF such that $\eta(x)$ is unimodal.  There exists $\delta>0$ such that for any $x_1 \geq \ldots \geq x_n \in \mathbb R$, 
-\begin{equation}
-\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^{2+\delta} }
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right)^{1+\delta} } 
-\leq  2^\delta f^{2+\delta}(0). 
-\label{eq:lem_bound_intervals_delta}
-\end{equation}
-\end{lem}
-
+We now use the fact that each $A_i$ is a finite union of intervals.
+Under the assumption that there exists $\delta>0$ such that $\eta^{1+\delta}(x)/f^\delta(x)$ has a unique maximum at the origin, we get
+\[
+\eta^{1+\delta}(x)/f^\delta(x) = \frac{(f(x))^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}} \leq 4^{1+\delta} (f(0))^{2+\delta}. 
+\]
 Lemma~\ref{lem:bound_intervals_delta} implies
@@
   { \left( \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta} \left( 1 - \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta}} \\
-  & \leq 2^\delta f^{2+\delta}(0). 
+  & \leq 4^{1+\delta}(f(0))^{2+\delta}.
 \end{align*}
-In particular, we conclude that 
+It follows that
 \[
-\frac{1}{n} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} \leq 2^\delta f^{2+\delta}(0), 
+\frac{1}{n} \sum_{i=1}^n \ex{ |U_i|^{2+\delta}} \leq 4^{1+\delta}(f(0))^{2+\delta}, 
 \]
-and thus for any $\delta>0$ the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we conclude that 
+and thus the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we conclude that 
 \[
@@
 \begin{align*}
-\mathbb E V_i  & = 
+\ex{ V_i}  & = 
  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)}  
@@
 \begin{equation} \label{eq:LAN_limit_cond}
-\frac{1}{n} \sum_{i=1}^n \mathbb E V_i =   L_n(A_1,\ldots,A_n)  \to \kappa(\theta)
+\frac{1}{n} \sum_{i=1}^n \ex{ V_i} =   L_n(A_1,\ldots,A_n)  \to \kappa(\theta)
 \end{equation}
@@
 for any $\theta \in \Theta$ for which the limit \eqref{eq:LAN_limit_cond} exists.
-
 \QEDA
-
-\subsubsection*{Proof of Lemma~\ref{lem:bound_intervals_delta}} 
-Denote 
-\[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k),
-\]
-and 
-\[
-\eta_\delta(x) \triangleq  \frac{  \left(\delta_1(x) \right)^{2+\delta}}{  \left(\Delta_1(x)  \right)^{1+\delta}
-(1-\Delta_1(x))^{1+\delta}}
-= \frac{  \left( f (x) \right)^{2+\delta}}{ \left(F(x) \right)^{1+\delta}(1-F(x))^{1+\delta}}. 
-\]
-The proof is by induction on $n$.
-For the case $n=1$ the LHS of \eqref{eq:lem_bound_intervals_delta} equals $\eta_\delta(x)$.
-Note that $\eta_\delta(0) = 2^\delta f^{2+\delta}(0)$, so it is enough to prove that $\eta_\delta(0)$ attains it maximum at $x=0$.
-We have $\eta_\delta(x) = \eta^{1+\delta}(x)/f^\delta(x)$, and thus
-\[
-\log \eta_\delta'(x) = (1+\delta) \frac{\eta'(x)}{\eta(x)} - \delta \frac{f'(x)}{f(x)}. 
-\]
-By Assumption~\ref{assump:failure_rate} both terms above are negative for $x>0$, so that $\log \eta_\delta'(x) \leq 0$ if and only if
-\begin{equation} \label{eq:delta_proof_cond}
-(1+\delta) \left| \frac{\eta'(x)}{\eta(x)} \right| \geq \delta \left| \frac{f'(x)}{f(x)} \right|, \qquad x>0.
-\end{equation}
-Also by Assumption~\ref{assump:failure_rate}, for $x>0$ we have
-\[
-0 > (\log \eta(x))' = \frac{h'(x)}{h(x)}-\frac{h'(-x)}{h(-x)},
-\]
-so that \eqref{eq:delta_proof_cond} is satisfies for $\delta>0$ small enough.
-
-Next, assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^{2+\delta}} 
-{\left(\Delta_n \right)^{1+\delta}\left(1- \Delta_n \right)^{1+\delta} } \leq \eta_\delta(0) = 2^\delta f^{2+\delta}(0) . 
-\label{eq:lem_bound_intervals_delta_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
-%If $x_{i+1} = x_i$ for some $i=1,\ldots,N-1$, then then the indices $i$ and $i+1$ may  be removed from all sums in \eqref{eq:lem_bound_intervals}, what brings us to the case $n = N-2$.
-Therefore, we may assume that $x_1 < \ldots < x_n$.
-%
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is attained for the same $(x_1,\ldots,x_N) \in \mathbb R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  (2+\delta) \log \delta_N - (1+\delta) \log \Delta_N - (1+\delta) \log \left(1 - \Delta_N  \right),
-\end{align*}
- The derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{(2+\delta) (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(1+\delta)(-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(1+\delta)(-1)^{k+1} f(x_k)}{1-\Delta_N }.
-\]
-We conclude that the gradient of $g$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero_delta}
-\frac{f'(x_k)}{f(x_k)} = \frac{\delta_N(1+\delta)}{2+\delta} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
-\end{equation}
-From the same reason as in the proof of Lemma~\ref{lem:bound_intervals_delta}, \eqref{eq:gradient_zero_delta} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_delta_proof} equals $\eta_\delta(x_1)$ which was shown to be smaller than $\eta_\delta(\epsilon)$.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_delta_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_delta_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$,  $x_i, x_{i+1} = -\epsilon$ for some $i$, or $x_i, x_{i+1} = \epsilon$ for some $i$.
-It is therefore enough to consider the cases:
-\begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
-\end{itemize}
-Assume first $x_N \rightarrow -\infty$. Then 
-\begin{align*}
-\frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)^{1+\delta} } ,
-\end{align*}
-which is smaller than $\eta_\delta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
-\begin{align*}
-& \frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right)^{1+\delta} }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^{2+\delta}} 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)^{1+\delta}\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right)^{1+\delta} },
-\end{align*}
-where $x'_{m} = x_{m+1}$ for $m=1,\ldots, N-1$. The last expression is smaller than $\eta_{\delta}(0)$ by the induction hypothesis.  \QEDA \\
 
@@
 \end{align}
-where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} and the fact that for $i \in S_n(\theta, \epsilon)$, 
+where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} with $\delta =0$, and the fact that for $i \in S_n(\theta, \epsilon)$, 
 \[
@@
 \]
-Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, \eqref{eq:non_existence_proof1}, and thus $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.
+Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, we get that \eqref{eq:non_existence_proof1}, hence $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.
 \par
-For $k\in \mathbb N$, assume by contradiction that there exists $N \geq 2K + 1$ distinct elements
+For $k\in \N$, assume by contradiction that there exists $N \geq 2K + 1$ distinct elements
 $\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$ consists of at most $K$ intervals, we have that 

### 2019-09-26 distributed-estimation.tex
Fixed proof of (previously) Lemma 15 and made changes in structure regarding this lemma. Now one lemma (Lemma 12) is used in three different results.

@@
 \begin{itemize}
-\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is a log-concave, differentiable and symmetric density function such that $\eta(x)$ is unimodal.
+\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is log-concave, differentiable, symmetric,  and  there exists $\delta>0$ such that $\eta^{1+\delta}(x)/f^\delta(x)$ has a unique maximum at the origin.
 \item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
@@
 \end{equation}
-Furthermore, assuming that $\theta_0 = \mathbb E \theta$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
+Furthermore, assuming that $\theta_0 = \ex{\theta}$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
 \begin{equation}

### 2019-09-30 appendices.tex
Trying to understand proofs

@@
 \section{}
+
+\subsection{Fast convergence of uniform estimators under bit constraints}
+\label{sec:uniform-weirdos}
+
+Here we consider the uniform distribution as our location family,
+demonstrating that in the adaptive setting~\eqref{item:adaptive} or even the
+one-step adaptive setting~(\ref{item:one-step-adaptive}'), constrained
+estimators can attain rates faster than the $1 / \sqrt{n}$ rates regular
+estimands allow.  Indeed, define $c(x) = -\log 2$ for $x \in [-1, 1]$ and
+$c(x) = -\infty$ for $x \not \in [-1, 1]$. Then $f(x) = e^{-c(x)}$ is
+log-concave and symmetric, and we may consider the location family with
+densities $f(x - \theta)$. For notational simplicity, we assume we have
+a sample of size $2n$. We provide a proof sketch that
+there is a one-step adaptive estimator $\theta_n$ such that
+\begin{equation}
+  \label{eqn:uniforms-are-easy}
+  \sup_{|\theta| \le \log n}
+  P_\theta\left(|\theta_n - \theta| \ge \frac{8 \log n}{n^{3/4}}\right)
+  \le \frac{2}{n^2}.
+\end{equation}
+for all large $n$,
+and so (by the Borel-Cantelli lemmas), for any $\theta \in \R$ we have
+$P_\theta(|\theta_n - \theta| \le \sqrt{2 \log n} / n^{3/4} ~
+\mbox{eventually}) = 1$. This is of course faster than the $1/\sqrt{n}$
+rates we prove throughout.
+
+To prove inequality~\eqref{eqn:uniforms-are-easy}, we proceed in two steps,
+both quite similar.
+First, we define an initial estimator $\theta\init_n$.
+Let $\epsilon > 0$, which we will determine presently, though we will
+take $n \epsilon \to \infty$ as $n \to \infty$, so that we may assume
+w.l.o.g.\ that $\theta \in [-n\epsilon/2, n \epsilon/2]$. Take the interval
+$[-n\epsilon, n\epsilon]$, and construct
+$m$ thresholds at intervals of size $2 n \epsilon / m$; let
+the $j$th such threshold be
+\begin{equation*}
+  t_j \defeq -n \epsilon + \frac{2 n (j-1) \epsilon}{m}
+\end{equation*}
+Then we ``assign'' observations to each pair of thresholds, so that
+threshold $j$ corresponds to observations $I_j \defeq \{\frac{n (j - 1)}{m}
++ 1, \ldots, \frac{n j}{m}\}$, of which there are $n/m$.  For each index $i
+\in I_j$, we set
+\begin{equation*}
+  B_i = \begin{cases}
+    1 & \mbox{if~} X_i \ge t_j \\
+    0 & \mbox{otherwise}.
+  \end{cases}
+\end{equation*}
+Then we simply set $\theta_n\init$ to be the maximal threshold for which
+$B_i = 0$ for all observations $X_i$ corresponding to that threshold.
+
+Let us now consider the probability that $\theta_n\init$ is substantially
+wrong. For notational simplicity, let $U_i = (1 + X_i - \theta) / 2$, so that
+the $U_i$ are uniform on $[0, 1]$.
+First, note that we always have $\theta_n\init \ge \theta
+- \frac{2 n \epsilon}{m}$, because no observations will be below
+the appropriate threshold. Let $j\opt$ be the smallest index $j$
+for which $\theta \le t_{j\opt}$, and consider
+the index sets $I_{j\opt}$, $I_{j\opt + 1}$, and so on.
+The event $\theta\init_n \ge t_{j\opt} + \frac{2 n \epsilon}{m}$ may
+occur only if for each of the $n/m$ observations in the set
+$I_{j\opt + 1}$, we have $U_i \ge \frac{n \epsilon}{m}$. Thus,
+\begin{equation*}
+  P_\theta\left(\theta_n\init \ge t_{j\opt} + \frac{2 n \epsilon}{m}
+  \right)
+  \le \left(1 - \frac{n \epsilon}{m}\right)^\frac{n}{m}
+  \le \exp\left(-\frac{n^2\epsilon}{m^2}\right).
+\end{equation*}
+Setting the number of bins $m = \sqrt{n}$,
+the resolution $\epsilon = 2 \log n / n$, we obtain
+$P_\theta(\theta_n\init \ge t_{j\opt} + 4 \log n / \sqrt{n})
+\le n^{-2}$. Thus we have
+\begin{equation}
+  \label{eqn:quality-of-initial-estimate}
+  \sup_{|\theta| \le \log n} P_\theta\left(|\theta_n\init - \theta| \ge
+  \frac{8 \log n}{\sqrt{n}}\right) \le \frac{1}{n^2}.
+\end{equation}
+
+The second stage estimator follows roughly the same strategy, except that
+the resolution of the bins is tighter. In particular, let us assume that
+$|\theta_n\init - \theta| \le \frac{8 \log n}{\sqrt{n}}$, which happens
+eventually by inequality~\eqref{eqn:quality-of-initial-estimate}.  (We will
+assume this tacitly for the remainder of the argument.)  Consider the
+interval $\Theta_n \defeq \theta_n\init + [-\frac{16 \log n}{\sqrt{n}},
+  \frac{16 \log n}{\sqrt{n}}]$ centered at $\theta_n\init$; we know that the
+interval includes $[\theta - \frac{8 \log n}{\sqrt{n}}, \theta + \frac{8
+    \log n}{\sqrt{n}}]$. Without loss of generality we assume $\theta_n\init
+= 0$.  Following precisely the same discretization strategy as that for
+$\theta_n\init$, we divide $\Theta_n$ into $m$ equal intervals, with
+thresholds $t_j = -\frac{16 \log n}{\sqrt{n}} + \frac{32 (j - 1) \log n}{m
+  \sqrt{n}}$; let $\epsilon_n = \frac{32 \log n}{m \sqrt{n}}$ be the width of
+these intervals.  Then following exactly the same reasoning as above, we
+assign indices $I_j = \{\frac{n(j - 1)}{m} + 1, \ldots, \frac{n j}{m}\}$ and
+for $i \in I_j$, set $B_i = 1$ if $X_i \ge t_j$. We define $\theta_n$ to be
+the maximal threshold $t_j$ for which $B_i = 0$ for all observations $X_i
+\in I_j$. Then following precisely the reasoning above, we have (on the
+event that $|\theta_n\init - \theta| \le \frac{8 \log n}{\sqrt{n}}$)
+\begin{equation*}
+  P_\theta(|\theta_n - \theta|
+  \ge 2 \epsilon_n)
+  \le (1 - \epsilon_n)^\frac{n}{m}
+  \le \exp\left(-\frac{n \epsilon_n}{m}\right)
+  = \exp\left(-\frac{32 \sqrt{n} \log n}{m^2}\right).
+\end{equation*}
+Set $m = 4 n^{1/4}$ to obtain the claimed
+result~\eqref{eqn:uniforms-are-easy}.
 

### 2019-09-30 preliminaries.tex
Trying to understand proofs

@@
 \section{Consistent Estimation and Off-the-shelf Bounds \label{sec:preliminary}}
-%
-In this section we adapt known results to derive lower and upper bounds on the relative efficiency under setting (iii). These bounds establish the following facts:
-\begin{itemize}
-\item[I.] A consistent estimator with an asymptotically normal distribution always exists in setting (iii), and hence in setting (ii). 
-\item[II.] For the normal distribution, the ARE in setting (iii) is at most $3/4$. Namely, under setting (iii), all estimators are strictly inferior compared to the sample mean. 
-\end{itemize}
+
+We begin our technical treatment by deriving a few
+bounds on the efficiency of estimators in
+setting~\eqref{item:distributed}. These bounds establish the
+following facts:
+\begin{enumerate}[1.]
+\item A consistent estimator with an asymptotically normal distribution
+  always exists in setting~\eqref{item:distributed}, and hence in the
+  adaptive settings~\eqref{item:adaptive} and
+  (\ref{item:one-step-adaptive}').
+\item For the normal distribution, the asymptotic relative
+  efficiency~\eqref{eqn:are-def} in the distributed
+  setting~\eqref{item:distributed} is at most $3/4$. No estimator can be as
+  efficient as the sample mean.
+\end{enumerate}
 
 \subsection{Consistent Estimation}
-Fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
+The simplest estimator is simply to invert a quantile. Indeed,
+fix $\theta_0 \in \mathbb R$ and define the $i$th message by 
 \[
@@
 \end{equation}
-is a consistent estimator for $\theta$ in the distributed setting of Figure~\ref{fig:setup}-(iii), where we note that $F(x)$ is invertible over the support of $f(x)$ which is a connected set due to log-concavity.
-Furthermore, the variance of $P_n$ is $F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)$, and hence the delta method implies that ${\theta}_n$ is asymptotically normal with variance
-\begin{equation} 
+is a consistent estimator for $\theta$ in the distributed setting of
+Figure~\ref{fig:setup}-(iii), where we note that $F$ is invertible over the
+support of $f$. As the variance of $P_n$ is
+$F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)$, a delta method
+calculation~\cite[Ch.~23]{VanDerVaart98} implies that ${\theta}_n$ is
+asymptotically normal with variance
+\begin{equation*}
   \frac{F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}{f^2(\theta-\theta_0)} = \frac{1}{
 \eta(\theta-\theta_0)}.
-\end{equation}
-In particular, the ARE of ${\theta}_n$ equals $\eta(\theta - \theta_0)\sigma^2$.
-In other words, for a prescribed accuracy, ${\theta}_n$ of  \eqref{eq:estimator_naive} estimates $\theta$ with sample size that is $\eta(\theta- \theta_0)  \sigma^2$ times the samples size required for the sample mean.
-\par
-%
-%
-Assumption~\ref{assump:failure_rate} implies that for  all $n$ large enough the ARE of ${\theta}_n$ of \eqref{eq:estimator_naive} is never greater than $\eta(0)$, which is the ARE of the sample median.
-This ARE is attained only when $\theta_0 = \theta$, whereas $\theta$ is apriori unknown.
-Since $\eta(x)$ vanishes as $|x|\rightarrow \infty$, the ARE of ${\theta}_n$ may be very small when $\theta$ is away from $\theta_0$.
-As an example, when $f(x)$ is a normal density, the ARE of ${\theta}_n$ is less than $\approx 0.14$ when $\theta_0$ is $2$ standard deviations from $\theta$.
-Therefore, the estimator ${\theta}_n$ has little practical value unless the radius of $\Theta$ is small compared to the standard deviation.
-\par
-It is suggested that we can attain lower variance in estimation by updating the threshold value $\theta_0$ in \eqref{eq:estimator_naive} after observing one or a batch of the single bit messages.
-Schemes with such adaptation fall within the adaptive setting of Figure~\ref{fig:setup}-(ii) which we consider in Section~\ref{sec:sequential}.
-\par
+\end{equation*}
+In the Gaussian case where the $X_i \simiid \normal(\theta, \sigma^2)$, the
+ARE of ${\theta}_n$ is $\eta(\theta - \theta_0)\sigma^2$.
 
-\subsection{Multiterminal Source Coding \label{sec:ceo}}
-The CEO setting considers the estimation of a sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_i$ is available at $n$ terminals.
-At each terminal $i$, an encoder observes the $k$ noisy samples
+Assumption~\ref{assump:failure_rate} implies that the optimal asymptotic
+variance for an estimator of the form~\eqref{eq:estimator_naive} is $1 /
+\eta(0)$, the asymptotic of the sample median. Unfortunately, as $\theta$ is
+(by definition) \emph{a priori} unknown and $\eta(x)$ monotonically
+decreases in $|x|$, this naive estimator $\theta_n$ may be very inefficient
+when $\theta$ is far from the initial guess $\theta_0$. As an example, when
+$f$ is a the normal density, the ARE of ${\theta}_n$ is less than $0.15$
+when $|\theta_0 - \theta| \ge 2\sigma$, and more broadly, $\ARE(\theta_n)$
+asymptotes to $|\theta_0| \exp(-\theta_0^2 / 2) / \sqrt{2\pi}$ as $|\theta_0
+- \theta|$ gets large.  Yet that $\theta_0 = \theta$ minimizes this
+asymptotic variance, and $\eta$ is continuous, is suggestive: if we can use
+a suitably good initial estimate $\theta_n\init$ for $\theta$, it is
+possible that a one-step adaptive estimator
+(recall~(\ref{item:one-step-adaptive}')) may be asymptotically strong, as we
+see in Section~\ref{sec:sequential}.
+
+\subsection{Multiterminal Source Coding}
+\label{sec:ceo}
+
+A related problem is the CEO problem, which considers the estimation of a
+sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_i$
+is available at $n$ terminals. At each terminal $i$, an encoder observes the
+$k$ noisy samples
 \[
@@
 \]
-and transmits $r_i k$ bits to a central estimator  \cite{berger1996ceo}. The central estimator produces an estimates ${\theta}_1,\ldots,{\theta}_k$ with the goal of minimizing the quadratic risk:
+and transmits $r_i k$ bits to a central estimator~\cite{berger1996ceo}. The
+central estimator produces an estimates ${\theta}_1,\ldots,{\theta}_k$ with
+the goal of minimizing the quadratic risk:
 \[
@@
 %
-Consequently, a lower bound on the MSE in estimating $\theta$ in the distributed encoding setting is given by the minimal MSE in the CEO setting as $k \to \infty$.
-Note that the difference between the CEO setting and ours lays in the privilege of each of the encoders to describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realizations, rather than a single realization using a single bit in ours.
- \par
-When the prior on $\theta$ and the noise corrupting it at each location are Gaussian, the optimal encoding scheme and its asymptotic risk as $k$ goes to infinity were fully characterized in \cite{prabhakaran2004rate}.
-Furthermore, the work of \cite{chen2004upper} provided an expression for quadratic risk attained in the CEO setting under Gaussian priors.
-Adapting to our setting, this expression provides the following proposition:
+Consequently, a lower bound on the MSE in estimating $\theta$ in the
+distributed encoding setting is given by the minimal MSE in the CEO setting
+as $k \to \infty$. Note that the difference between the CEO setting and ours
+lays in the privilege of each of the encoders to describe $k$ realizations
+of $\theta$ using $k$ bits with MSE averaged over these realizations, rather
+than a single realization using a single bit in ours.
+
+When the prior on $\theta$ and the noise corrupting it at each location are
+Gaussian, Prabhakaran et al.~\cite{prabhakaran2004rate} characterize the
+optimal encoding and its asymptotic risk as $k \to \infty$.  Chen et
+al.~\cite{chen2004upper} also provide an expression for the quadratic risk
+in the CEO setting under Gaussian priors. Adapting to our setting, this
+expression provides the following proposition:
 \begin{prop} \label{prop:ceo_lower_bound}
-Assume that $\Theta = \mathbb R$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is arbitrary.
-Then any estimator ${\theta}_n$ of $\theta$ in the distributed setting satisfies
+  Assume that $\Theta = \mathbb R$ and $\pi(\theta) =
+  \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is
+  arbitrary. Then any estimator ${\theta}_n$ of $\theta$ in the distributed
+  setting satisfies
   \begin{equation} \label{eq:ceo_bound}
@@
 \end{prop}
+\noindent
+See Appendix~\ref{app:proof:prop_ceo_lower_bound} for a proof.
 
-\begin{proof}
-See Appendix~\ref{app:proof:prop_ceo_lower_bound}.
-\end{proof}
-
-From the formulation of the CEO problem, it follows that the difference between the MSE lower bound \eqref{eq:ceo_bound} and the actual MSE in the distributed setting (case (iii)) is attributed to the ability to perform coding over blocks.
-Namely, each encoder in the CEO setting may encode an arbitrary number of $k$ independent realizations of $\theta$ using $k$ bits, versus only one realization with one bit in ours.
-In other words, it is the ability to exploit the geometry of a high-dimensional product probability space that distinguishes between the CEO problem with one bit per encoder on average and the mean estimation problem from one-bit measurements in the distributed setting.
+As we shall see, this bound is loose: the difference between the MSE lower
+bound~\eqref{eq:ceo_bound} and the actual MSE in the distributed setting
+(case~\eqref{item:distributed}) occurs because in the CEO setting, each
+encoder may encode an arbitrary number of $k$ independent realizations of
+$\theta$ using $k$ bits; in our situation, $k = 1$. That blocking allows
+more efficient encoding and exploiting the high-dimensional geometry of the
+product probability space in the CEO problem is perhaps unsurprising, and
+our goal in the sequel will be to characterize the performance degradation
+one bit encoding engenders.

### 2019-09-30 problem-formulation.tex
Trying to understand proofs

@@
 \setcounter{enumi}{1}
-\item One-step adaptive, where for some function $g$ and
+\item \label{item:one-step-adaptive}
+  One-step adaptive, where for some function $g$ and
   a (fixed) $t$, if $i \le t$ then
@@
 then the ARE of the estimator is~\cite[Def.~6.6.6]{LehmannCa98}
-\begin{equation*}
+\begin{equation}
+  \label{eqn:are-def}
   \ARE({\theta}_n) \defeq
   \liminf_{n\rightarrow \infty} \frac{m(n)}{n}.
-\end{equation*}
+\end{equation}
 In the special case where there exists $V \in \mathbb R$ such that
@@
 
-%%% JCD: I AM HERE BUT STILL GOING THROUGH THINGS %%%
+\subsection*{Notation and basic assumptions}
 
-In addition to the notation above, we also denote by $F(x)$ the cumulative distribution function of $X_i$, and define
-\begin{equation} \label{eq:eta_def}
-\eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))} =  \frac{f(x)f(-x)}{F(x)F(-x)}, 
-\end{equation}
-where the last equality is due to symmetry of $f(x)$. We note that 
-\begin{equation}
-\label{eq:eta_h}
-\eta(x) = h(x)h(-x) = f(x) \left( h(x) + h(-x) \right), 
-\end{equation}
-where 
+To describe our results and make them formal, we require some additional
+notation and one main assumption, which restricts the class of distributions
+we consider.  We use the typical notation that
+$F(x) = \int_{-\infty}^x f(t) dt$ is the cumulative distribution function
+of the $X_i$, and we let
 \begin{equation*}
@@
 \end{equation*}
-is the \emph{hazard} function (a.k.a. \emph{failure rate} or \emph{force of mortality}), which is a monotone increasing function since $f(x)$ is log-concave \cite{bagnoli2005log}. 
+be the \emph{hazard} function (or the \emph{failure rate} or \emph{force of
+  mortality}), which is monotone increasing as $f$ is
+log-concave~\cite{bagnoli2005log}. Given the centrality of the median
+to our efficiency bounds, it is unsurprising that the quantity
+\begin{equation}
+  \label{eq:eta_def}
+  \eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))}
+  \stackrel{(\star)}{=} \frac{f(x)f(-x)}{F(x)F(-x)}
+\end{equation}
+appears throughout our development. (Here equality~$(\star)$ is immediate by
+the symmetry of $f$.)  For $p \in (0, 1)$ and $x = F^{-1}(p)$,
+\begin{equation}
+  \label{eqn:variance-quantiles}
+  \frac{1}{\eta(x)} =
+  \frac{1}{\eta(F^{-1}(p))}
+  = \frac{p (1 - p)}{f(F^{-1}(p))^2}
+\end{equation}
+is of course the familiar asymptotic variance of the $p$th quantile of the
+sample $X_1^n$ (cf.~\cite{VanDerVaart98}, Ch.~21).
+
+For $f$ the normal density, it classical results~\cite{Samford1953,
+  hammersley1950estimating} show that that $\eta(x)$ is a strictly
+decreasing function of $|x|$, as we illustrate in Fig.~\ref{fig:eta}.
 %
-For $f(x)$ the normal density, it is shown in \cite{Samford1953} and \cite{hammersley1950estimating} that $\eta(x)$ is a strictly decreasing function of $|x|$, as illustrated in Fig.~\ref{fig:eta}. 
-%
-In this paper we only consider the normal distribution and other log-concave symmetric distributions for which this property of $\eta(x)$ holds. Specifically, we require the following:
-\begin{assump} \label{assump:failure_rate}
- $\eta(x)$ has a unique maximum (at the origin) and is a non-increasing function of $|x|$. 
-\end{assump}
-%That is, Assumption~\ref{assump:failure_rate} says that $\eta'(x) < 0 $ for all $x>0$. 
-Under this assumption we have, 
+We consider symmetric log-concave symmetric distributions sharing this
+property.  Specifically, we require the following.
+\begin{assumption} \label{assump:failure_rate}
+  The origin $x = 0$ uniquely maximizes $\eta(x)$, and $\eta(x)$ is
+  non-increasing in $|x|$.
+\end{assumption}
+Under this assumption,
 \begin{equation*}
-4f^2(x) \leq \eta(x) \leq \eta(0),
+  4 f^2(x) \leq \eta(x) \leq \eta(0),
 \end{equation*} 
 %
-where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median.
-Combined with log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that $\eta(x)$ vanishes as $|x|\rightarrow \infty$.
-\par
+where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median
+(Eq.~\eqref{eqn:variance-quantiles} at $p = 1/2$).  Combined with
+log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that
+$\eta(x)$ vanishes as $|x|\rightarrow \infty$.  Several distributions
+satisfy Assumption~\ref{assump:failure_rate}, including the generalized
+normal distributions with a shape parameter between $1$ and $2$ (including
+the normal and Laplace distributions). Symmetric log-concave distributions
+that failing Assumption~\ref{assump:failure_rate} include the uniform
+distribution and the generalized normal distribution with shape parameter
+greater than $2$. (See Appendix~\ref{sec:uniform-weirdos} for
+a brief discussion on the uniform distribution, which illustrates
+why some restriction of the class of distributions is necessary to
+develop our results; in brief, even one-step adaptive estimators
+with a single bit can achieve rates faster than the paramateric
+$\sqrt{n}$ convergence for location estimation in the uniform distribution.)
+
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}[scale = 0.6]
+\begin{axis}[
+width=8cm, height=6cm,
+xmin = -3, xmax=3, 
+restrict y to domain = 0:100,
+ymin = 0,
+ymax = 0.9,
+samples=10, 
+xlabel= $x$,
+xtick={-2,-1,0,1,2},
+xticklabels={-2,-1,0,1,2},
+ytick={0,0.3989423,0.6366198},
+yticklabels={0,$\frac{1}{\sqrt{2 \pi}}$,$2/\pi$},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+\addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {./Figs/eta.csv};
+\addlegendentry{$\eta(x)$};
+\addplot[domain = -5:5, samples = 50, color = red, solid, smooth]  {exp(-x^2/2) / sqrt(2*3.14159)};
+\addlegendentry{$\phi(x)$};
+\addplot[domain = -5:5, samples = 50, color = black, solid, dashed]  {4*exp(-x^2) / (2*3.14159)};
+\addlegendentry{$4\phi^2(x)$};
+
+\end{axis}
+\end{tikzpicture}
 %
-Assumption~\ref{assump:failure_rate} is satisfied, for example, by the generalized normal distributions with a shape parameter between $1$ and $2$ (including normal and Laplace distributions).
-Symmetric log-concave distributions that do not satisfy Assumption~\ref{assump:failure_rate} include the uniform distribution and the generalized normal distribution with shape parameter greater than $2$.\par
-
-%% \begin{figure}
-%% \begin{center}
-%% \begin{tikzpicture}[scale = 0.6]
-%% \begin{axis}[
-%% width=8cm, height=6cm,
-%% xmin = -3, xmax=3, 
-%% restrict y to domain = 0:100,
-%% ymin = 0,
-%% ymax = 0.9,
-%% samples=10, 
-%% xlabel= $x$,
-%% xtick={-2,-1,0,1,2},
-%% xticklabels={-2,-1,0,1,2},
-%% ytick={0,0.3989423,0.6366198},
-%% yticklabels={0,$\frac{1}{\sqrt{2 \pi}}$,$2/\pi$},
-%% line width=1.0pt,
-%% mark size=1.5pt,
-%% ymajorgrids,
-%% xmajorgrids,
-%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-%% ]
-%% \addplot[color = blue, solid, smooth] plot table [x = x, y = y, col sep=comma] {./Figs/eta.csv};
-%% \addlegendentry{$\eta(x)$};
-%% \addplot[domain = -5:5, samples = 50, color = red, solid, smooth]  {exp(-x^2/2) / sqrt(2*3.14159)};
-%% \addlegendentry{$\phi(x)$};
-%% \addplot[domain = -5:5, samples = 50, color = black, solid, dashed]  {4*exp(-x^2) / (2*3.14159)};
-%% \addlegendentry{$4\phi^2(x)$};
-
-%% \end{axis}
-%% \end{tikzpicture}
-%% %
-%% \begin{tikzpicture}[scale = 0.6]
-%% \begin{axis}[
-%% width=8cm, height=6cm,
-%% xmin = -4, xmax=4, 
-%% restrict y to domain = -10:0,
-%% ymin = -10,
-%% samples=10, 
-%% xlabel= $x$,
-%% xtick={-3,-2,-1,0,1,2,3},
-%% xticklabels={-3,-2,-1,0,1,2,3},
-%% ytick={0,-0.45158,-0.919},
-%% yticklabels={0,,},
-%% line width=1.0pt,
-%% mark size=1.5pt,
-%% ymajorgrids,
-%% xmajorgrids,
-%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-%% ]
-%% \addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {./Figs/eta.csv};
-%% \addlegendentry{$\log \eta(x)$};
-%% \addplot[domain = -5:5, samples = 30, color = red, solid, smooth]  {-(x)^2/2 -0.9189};
-%% \addlegendentry{$\log \phi(x)$};
-%% \end{axis}
-%% \end{tikzpicture}
-%% \caption{
-%% The function $\eta(x) = f^2(x) / F(x)F(-x)$ for $f(x) = \phi(x)$ the standard normal density.
-%% \label{fig:eta}
-%% }
-%% \end{center}
-%% \end{figure}
+\begin{tikzpicture}[scale = 0.6]
+\begin{axis}[
+width=8cm, height=6cm,
+xmin = -4, xmax=4, 
+restrict y to domain = -10:0,
+ymin = -10,
+samples=10, 
+xlabel= $x$,
+xtick={-3,-2,-1,0,1,2,3},
+xticklabels={-3,-2,-1,0,1,2,3},
+ytick={0,-0.45158,-0.919},
+yticklabels={0,,},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+\addplot[color = blue, solid, smooth] plot table [x = x, y = logy, col sep=comma] {./Figs/eta.csv};
+\addlegendentry{$\log \eta(x)$};
+\addplot[domain = -5:5, samples = 30, color = red, solid, smooth]  {-(x)^2/2 -0.9189};
+\addlegendentry{$\log \phi(x)$};
+\end{axis}
+\end{tikzpicture}
+\caption{
+The function $\eta(x) = f^2(x) / F(x)F(-x)$ for $f(x) = \phi(x)$ the standard normal density.
+\label{fig:eta}
+}
+\end{center}
+\end{figure}

### 2019-10-02 appendices.tex
Corrected proof of isoprimetric lemma

@@
 We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO MSE while enforcing the condition $R_1=\ldots = R_n = 1$.
-Indeed, an upper bound for the CEO MSE under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
+Indeed, an upper bound for the CEO MSE under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2019}, and leads to
 \[
@@
 \[
-M(X) = \begin{cases} 1,& X \in A, \\
+B(X) = \begin{cases} 1,& X \in A, \\
 -1, & X \notin A.
@@
 \]
-Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $\eta(0)$.
+Then the Fisher information of $B$ with respect to $\theta$ is bounded from above by $\eta(0)$.
 \end{lem}
@@
 where $A_i \subset \R$ is a Borel measurable set. 
-%Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
+%Indeed, any measurable function $(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
 Consider the conditional distribution $P({B^n|\theta})$ of $B^n$ given $\theta$. We have 
@@
 \begin{lem} \label{lem:bound_intervals_delta}
-Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$ and $\delta>0$,
+Let $f(x)$ be log-concave, symmetric, and differentiable density function. Let $\delta\geq 0$. Assume that the origin $x=0$ uniquely maximizes the function
+\[
+\eta_\delta(x) \triangleq  \eta^{1+\delta}(x)/f^\delta(x) = \frac{  \left( f(x) \right)^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}}
+\]
+and that $\eta_\delta(x)$ is non-increasing in $|x|$. For any $x_1 \ge \ldots \ge x_n \in \R^n$,
 \begin{equation}
 \frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
-{\left( \sum_{i=1}^n (-1)^{i+1} F(x_i) \right) \left(1- \sum_{k=1}^n (-1)^{i+1} F(x_i) \right) } 
-\leq  \max_{i} \eta_\delta(x_i),
+{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{k=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
+\leq  \max_{i} \eta_\delta(x_i).
 \label{eq:lem_bound_intervals_delta}
 \end{equation}
-where 
-\[
-\eta_\delta(x) \triangleq \frac{  \left( f(x) \right)^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}}. 
-\]
 \end{lem}
+In particular, 
+\[
+\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
+{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
+\leq \eta_\delta(0)
+\]
+since $\eta_\delta(x)$ attains its maximum at the origin.
 
@@
 \[
-\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),
-\]
-\[
-\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k). 
-\]
-Note that 
-\[
-\eta_\delta(x) =  \frac{  \left(\delta_1(x) \right)^{2+\delta}}{ (\Delta_1(x))^{1+\delta}
-(1-\Delta_1(x))^{1+\delta}}. 
-\]
-Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable, with a non-increasing derivative $c'(x)$.
-We first prove the lemma under the assumption that
-\[
-c'(x) \triangleq \frac{f'(x)}{f(x)}, 
-\]
-is an injection, or, equivalently, that $c(x)$ is strictly decreasing for all $x\in \R$. \par
-We use induction on $n \in \N$ to show that the LHS of \eqref{eq:lem_bound_intervals_delta} is bounded from above by $\max_i \eta_\delta(x_i)$. The case $n=1$ is trivial. Assume that 
-\begin{equation}
-\frac{ \left( \delta_n \right)^{2+\delta}} 
-{\left(\Delta_n\left(1- \Delta_n \right) \right)^{1+\delta} } \leq \max_i \eta_{\delta}(x_i)
-\label{eq:lem_bound_intervals_proof}
-\end{equation}
-for all integers up to $n = N-1$ and consider the case $n = N$. 
+\delta_n(x_1,\ldots,x_n) \triangleq \sum_{i=1}^{n} s_i f(x_i),
+\]
+\[
+ \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{i=1}^n s_i F(x_i), 
+\]
+where $s_i \triangleq (-1)^{i+1}$. Set
+\[
+\frac{ \left| \delta_n(x_1,\ldots,x_n) \right|^{2+\delta}} 
+{\left|\Delta_n(x_1,\ldots,x_n)  \left(1- \Delta_n(x_1,\ldots,x_n) \right) \right|^{1+\delta} }.
+\]
+We use induction on $n \in \N$ to show that 
+\begin{align}
+\label{eq:lemm:interval_bounds:to_show}
+\frac{ \left| \delta_n(x_1,\ldots,x_n) \right|^{2+\delta}} 
+{\left|\Delta_n(x_1,\ldots,x_n)\left(1- \Delta_n(x_1,\ldots,x_n) \right) \right|^{1+\delta} } \leq \max_{i}\eta_{\delta}(x_i).
+\end{align}
+ Since 
+\[
+\eta_\delta(x) =  \frac{  \left|\delta_1(x) \right|^{2+\delta}}{\left|\Delta_1(x)
+(1-\Delta_1(x)) \right|^{1+\delta}}, 
+\]
+The case $n=1$ is trivial.  
+%follows from the assumption that $\eta_\delta(x)$ is non-increasing in $|x|$. 
+Assume that \eqref{eq:lemm:interval_bounds:to_show} holds for all integers up to $n = N$ and for any $x_1 \ge \ldots \ge x_n$.
+Consider the case $n = N+1$.
+Let $i^*$ be the index such that $x_{i^*}$ has minimal absolute value among $x_1,\ldots,x_N$.
+The assumption on $\eta_\delta(x)$ implies that
+\[
+\eta_\delta(x_{i^*}) = \max_i \eta_\delta(x_i).
+\]
+Since the LHS of \eqref{eq:lem_bound_intervals_delta} is invariant to a sign flip of all $x_1,\ldots,x_{N+1}$, we may assume that $x_{i^*}$ is positive without loss of generality. 
+%For simplicity, we also assume that $s_{i^*} = 1$ and note that the case $s_{i^*} = -1$ is obtained using identical arguments. 
+Set $x^* = x_{i^*}$ and let $k=i^*-1$. In what follows, variables with subscript of non-positive index are ignored in summations and in lists of arguments to functions. Consider the function
+\begin{align*}
+& g(y_1,\ldots,y_N) \triangleq  \frac{\left| \delta_N(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N) )\right|^{2+\delta}}{
+\left|\Delta_N(y_1,\ldots,y_k,x_{i^*},y_{k+1}\ldots,y_N)  \right) \left(1 -\Delta_N(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N))  \right|^{1+\delta}
+} .
+\end{align*}
+The claim in the lemma is obtained by taking $y_i=x_{i'}$ where $i'$ is the $i$th element in $\{1,\ldots,N+1\}\setminus \{i^*\}$. It is therefore enough to prove that 
+\[
+\max_{(y_1,\ldots,y_N) \in A_N} g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*),
+\]
+where 
+\[
+A_N(x^*,k) \triangleq \left\{ (y_1,\ldots,y_N) \in \R^N\, : \, y_1 \ge y_k \ge x^* \ge -x^* \ge y_{k+1} \ldots \ge y_N
+\right\}.
+\]
 %
-The maximal value of the LHS of \eqref{eq:lem_bound_intervals_proof} is attained for the same $(x_1,\ldots,x_N) \in \R^N$ that attains the maximal value of 
-\begin{align*}
-& g(x_1,\ldots, x_N) \triangleq  (2+\delta) \log \delta_N - (1+\delta) \log \Delta_N - (1+\delta) \log \left(1 - \Delta_N  \right),
-\end{align*}
-The partial derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by
-\[
-\frac{\partial  g}{\partial x_k} = \frac{(2+\delta) (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(1+\delta) (-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(1+\delta)(-1)^{k+1} f(x_k)}{1-\Delta_N },
-\]
-and we conclude that the gradient of $g$ vanishes if and only if
+Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable with derivative 
+\[
+c'(x) \triangleq \frac{f'(x)}{f(x)} 
+\]
+that is non-increasing. We first prove the lemma under the assumption that $c'(x)$ is an injection, or, equivalently, that $c(x)$ is strictly decreasing for all $x\in \R$. \par
+%
+The maximal value of $g(y_1,\ldots,y_N)$ is attained for the same $(y_1,\ldots,y_N) \in A_{N+1}(x^*,k)$ that maximizes
+\begin{align*}
+ \log(g)(y_1,\ldots, y_N) =  (2+\delta) \log \left( \delta_N  \right)  - (1+\delta) \log \left( \Delta_N  \right) - (1+\delta) \log \left(1 - \Delta_N \right),
+\end{align*}
+where in the last display and henceforth we suppress the arguments $y_1,\ldots,y_k,x^*,y_{k+1},\ldots, y_N$ of the functions $\delta_N$ and $\Delta_N$.
+%
+The partial derivative of $\log(g)(y_1,\ldots,y_N)$ with respect to $y_i$ within the interior of $A_N(x^*,k)$ is given by
+\[
+\frac{\partial \log(g)}{\partial y_i} = \frac{(2+\delta) s_i f'(x_i)}{\delta_N } -\frac{(1+\delta) s_i f(x_i)}{\Delta_N  } + \frac{(1+\delta)s_i f(y_i)}{1-\Delta_N }.
+\]
+We conclude that the gradient of $\log(g)$ vanishes if and only if
 \begin{equation}
 \label{eq:gradient_zero}
-c'(x_k) = \frac{f'(x_k)}{f(x_k)} = \frac{1+\delta}{2+\delta} \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.
+c'(y_i) = \frac{f'(y_i)}{f(y_i)} = \frac{1+\delta}{2+\delta} \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N } \right),\quad i=1,\ldots,N.
 \end{equation}
 %
-Since we assumed that $c'(x)$ is an injection, \eqref{eq:gradient_zero} is satisfied if and only if $x_1 = \ldots = x_N$.
-For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_proof} equals $\eta(x_1) = \max_i \eta(x_i)$ hence the statement holds.
-For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero.
-Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_proof} is not attained at the line $x_1=\ldots=x_N)$.
-We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_proof} is maximized at the borders.
-That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$.
-As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_proof} is zero and thus this case reduces to the case $n= N-2$.
-A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$, or  $x_i, x_{i+1}$ for some $i$.
-It is left to consider the cases:
+Since we assumed that $c'(x)$ is an injection, \eqref{eq:gradient_zero} is satisfied if and only if $y_1 = \ldots = y_N$. In this case, 
+$g(y_1,\ldots,y_N) = \eta_\delta(x_{i^*})$  
+if $N$ is even, or
+\begin{align*}
+& g(y_1,\ldots,y_N) = \frac{\left| s_1f(y_1)+s_{N+1}f(x_{i^*})  \right|^{2+\delta}} { 
+\left|  s_1F(y_N) + s_{N+1}F(x_{i^*}) \right|^{1+ \delta} 
+\left| 1 - (s_1F(y_1) + s_{N+1}F(x_{i^*})) \right|^{1+ \delta} } 
+\end{align*} 
+if $N$ is odd and $y_1 < x^*$. Form the induction assumption, the last display is bounded from above by $\eta_\delta(x_{i^*})$. The case where $N$ is odd and $y_1 > x^*$ is similar. 
+%
+We now consider the possibility that the maximum of $g(y_1,\ldots,y_N)$ is attained at the boundaries of $A_N(x^*,k)$.
+For boundary points for which $y_i = y_{i+1}$ for some $i$, the contribution of $y_i$ and $y_{i+1}$ to $g(y_1,\ldots,y_N)$ is zero and the induction assumption for $n=N-1$ implies that
+\[
+g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*)
+\]
+at these points. The remaining boundary points of $A_N(x^*,k)$ are covered by the following cases:
 \begin{itemize}
-\item[(1)]  $x_N \to -\infty$.
-\item[(2)] $x_1 \to \infty$.
+\item[(1)]  $y_N \to -\infty$. 
+\item[(2)] $y_1 \to \infty$.
+\item[(3)] $y_k = x_{i^*}$.
+\item[(4)] $y_{k+1} = -x_{i^*}$. 
 \end{itemize}
-Under case (1) we have
-Assume first $x_N \rightarrow -\infty$. Then 
-\begin{align*}
-\frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  }
- = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)^{1+\delta} } ,
-\end{align*}
-which is smaller than $\eta_\delta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 
-\begin{align*}
-& \frac{ \left( \delta_N \right)^{2+\delta}} 
-{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  } \\
-=
-& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
-{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right)^{1+\delta} }  \\
-& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^{2+\delta}} 
-{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)^{1+\delta}\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right)^{1+\delta} },
-\end{align*}
-where $x'_{m} = x_{m+1}$ for $m=1,\ldots, N-1$. The last expression is also smaller than $\max_i \eta_\delta (x_i)$ by the induction hypothesis.  \par
-It is left to consider the case where $c'(x)$ is not necessarily strictly decreasing.
-We approximate $c(x)$ using another concave symmetric function whose derivative is always negative except at the origin.
+For case (1), 
+\begin{align*}
+g(y_1,\ldots,y_N) \to \frac{ \left| \sum_{i=1}^{k} s_i f(y_i) + s_{i^*} f(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i f(y_i) \right|^{2+\delta}} 
+{\left| \sum_{i=1}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i F(y_i) \right|^{1+\delta}\left|1- \left( \sum_{i=1}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i F(y_i) \right)  \right|^{1+\delta} },
+\end{align*}
+which is smaller than $\eta_\delta(x_{i^*})$ by the induction hypothesis. Similarly, under case (2),
+\begin{align*}
+& g(y_1,\ldots,y_N) \to 
+\frac{ \left| \sum_{i=2}^{k} s_i f(y_i) + s_{i^*} f(x_{i^*}) - \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
+{\left| 1+ \sum_{i=2}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta}\left|-\left( \sum_{i=2}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N} s_i F(y_i) \right)  \right|^{1+\delta} },
+ \\
+& = \frac{ \left| -\sum_{i=2}^{k} s_i f(y_i) - s_{i^*} f(x_{i^*}) + \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
+{ \left|1 - \left(-\sum_{i=2}^{k} s_i F(y_i) - s_{i^*} F(x_{i^*}) + \sum_{i=k+1}^{N} s_i F(y_i) \right) \right|^{1+\delta} 
+\left|-\sum_{i=2}^{k} s_i F(y_i) - s_{i^*} F(x_{i^*}) + \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta} }
+\end{align*}
+which is smaller than $\eta_{\delta}(x_{i^*})$ by the induction hypothesis.
+Under case (3), the terms in $\delta_N$ and $\Delta_N$ corresponding to $y_k$ and $x_{i^*}$ cancel each other.
+As a result,  $g(y_1,\ldots,y_N)$ reduces to an expression with $n=N-1$ variables hence this case is handled by the induction hypothesis.
+%
+Under case (4), set 
+\[
+d \triangleq s_k F(-x^*) + s_{i^*} F(x^*) = s_{i^*}\left(1-2F(-x^*) \right), 
+\]
+\[
+\sigma \triangleq \sum_{i=1}^{k-1} s_i f(y_i) - \sum_{i=k+1}^{N} s_i f(y_i). 
+\]
+and 
+\[
+\Sigma \triangleq \sum_{i=1}^{k-1} s_i F(y_i) - \sum_{i=k+1}^{N} s_i F(y_i). 
+\]
+We have
+\begin{align*}
+& g(y_1,\ldots,y_N) =\nonumber  \\ 
+& =
+\frac{ \left| \sum_{i=1}^{k-1} s_i f(y_i) - \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
+{\left| \sum_{i=1}^{k-1} s_i F(y_i) + d(x^*) - \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta} \left|1- \sum_{i=1}^{k-1} s_i F(y_i) - d(x^*) + \sum_{i=k+1}^{N} s_i F(y_i)   \right|^{1+\delta} }, \\
+& = \frac{ \left| \sigma \right|^{2+\delta}} 
+{\left| \Sigma+d \right|^{1+\delta} \left|1- \Sigma - d \right|^{1+\delta} }  =  
+\frac{ \left| \sigma \right|^{2+\delta}} 
+{\left| \Sigma \right|^{1+\delta} \left|1- \Sigma \right|^{1+\delta} }  \left| \frac{\Sigma(1-\Sigma) } { \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} \right|^{1+\delta}. 
+\end{align*}
+By the induction hypothesis,
+\[
+\frac{ \left| \sigma \right|^{2+\delta}} 
+{\left| \Sigma \right|^{1+\delta} \left|1- \Sigma \right|^{1+\delta} } \leq \eta_\delta(x^*), 
+\]
+hence it is left to show that 
+\[
+ \frac{\Sigma(1-\Sigma) } { \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} \leq 1.
+\]
+Note that whenever $d>0$, 
+\begin{align*}
+& \frac{ \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} {\Sigma(1-\Sigma)} \geq 1 \Leftrightarrow  1-2\Sigma \geq d, 
+\end{align*}
+while for $d<0$,
+\begin{align*}
+& \frac{ \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} {\Sigma(1-\Sigma)} \geq 1 \Leftrightarrow  1-2\Sigma \leq d. 
+\end{align*}
+Therefore, it is enough to show that $\Sigma \leq F(-x^*)$ if $s_{i^*}=1$ and 
+$\Sigma \geq F(-x^*)$ if $s_{i^*}=-1$. 
+%
+Indeed, if $s_{i^*}=1$, then $s_{k+1}=-1$ and monotonicity of $F(x)$ implies that 
+\[
+\Sigma + d \leq F(y_1) - F(y_k) + F(x^*) - F(-x^*) + F(y_{k+2}) - F(y_N), 
+\]
+and hence
+\[
+\Sigma \leq 1-F(x^*) = F(-x^*). 
+\]
+Similarly, if $s_{i^*}=-1$ then 
+\[
+1 - \Sigma \leq 1 -  F(-x^*).
+\]
+This conclude the proof in the case where $c'(x)$ is an injection. 
+\par  
+In the case where $c'(x)$ is not necessarily strictly decreasing, we approximate $c(x)$ using another concave symmetric function whose derivative is always negative except at the origin.
 For $\alpha>0$ consider the function  $f_\alpha(x) = \kappa(\alpha) e^{\sgn(c(x))|c(x)|^{1+\alpha}}$, where $\kappa(\alpha)$ is chosen such that $f_\alpha(x)$ is a probability density function.

### 2019-10-06 adaptive-estimation.tex
corrected Isoprimetric Lemma. Went through it with Vardan

@@
 %
-\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with a finite location Fisher information, namely
+\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with a finite Fisher information 
 \[
-I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)}  \right)^2 f(x) dx < \infty.
+\sigma_f^2 \triangleq \ex{\frac{f'(X)}{f(X)} } 
 \]
+for the location in the family $\{P_\theta\}$.
 %(or that $f(x-\theta)$ is differentiable in quadratic mean).  
@@
 \]
-and assume that $n_1(n) \rightarrow \infty$ and $n_1(n)/n \rightarrow 0$. Then:
+and assume that, as $n\to \infty$, $n_1(n) \rightarrow \infty$ and $n_2(n)/n \rightarrow 1$. Then:
 \begin{align*}
@@
 \begin{proof}
+By the law of large numbers,
+\[
+p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
+\]
+so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity. 
 For $t\in \mathbb R$, set
@@
 \]
-From the central limit theorem
+Since $n_2(n)/n \to 1$, the central limit theorem and Slutsky's theorem imply
 \begin{align*}
-& \sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)  = \sqrt{\frac{n}{n_2}} \sqrt{n_2} \left(  p_{n_2}(t) - F(\theta - t) \right) \\
-& \overset{d}{\rightarrow} \Ncal\left( 0, V(t) \right),
+\sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)   \overset{d}{\rightarrow} \sqrt{F(\theta - t) F \left( t - \theta\right)} Z,
 \end{align*}
-where
+where $Z \sim \Ncal(0,1)$. In addition, Slutsky's theorem imply
 \[
-V(t) \triangleq F(\theta - t) F \left( t - \theta\right). 
+\sqrt{F(\theta-\theta_{n_1}) F(\theta_{n_1} - \theta)} Z_1 \overset{d}{\rightarrow}  F(0) Z,  
 \]
-Applying the delta method to $p_{n_2}(t)$ with $g(x) = F^{-1}(x)$ implies
+hence 
+\[
+\sqrt{n} \left( p_{n_2}( \theta_{n_1}) - F( \theta - \theta_{n_1}) \right)  \overset{d}{\rightarrow} F(0) Z.
+\]
+Finally, we use the delta method with $g(x) = F^{-1}(x)$ to conclude
 \begin{align*}
-& \sqrt{n} \left( t + F^{-1}(\hat{p}_{n_2}(t)) - \theta \right) \\
-&= \sqrt{n} \left( g(\hat{p}_{n_2}(t)) - g \left(F(\theta-t) \right)  \right) \\
-& \overset{d}{\to} \Ncal\left(0, 
-1/\eta(\theta-t) \right).
+& \sqrt{n}\left( \theta_{n_2} - \theta \right) = \sqrt{n} \left( \theta_{n_1} + F^{-1}(p_{n_2}(\theta_{n_1})) - \theta \right) \\
+&= \sqrt{n} \left( g(p_{n_2}(\theta_{n_1})) - g \left(F(\theta-\theta_{n_1}) \right)  \right) \overset{d}{\to} \Ncal\left(0, 
+F^2(0)/ f^2(0) \right).
 \end{align*}
-%where this convergence is uniform in $t$ since all moments of $F^{-1}(\hat{p}_{n_2})$ exists. 
-On the other hand, by the law of large numbers,
-\[
-p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
-\]
-so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity and thus 
-\[
-\eta( {\theta}_{n_1}-\theta) \overset{a.s.}{\rightarrow} \eta(0). 
-\]
-Finally,
-\begin{align*}
-& \sqrt{n}\left({\theta}_{n_2} - \theta\right) \\
-& = \sqrt{n} \left( {\theta}_{n_1} + F^{-1}(\hat{p}_{n_2}({\theta}_{n_1})) - \theta \right)  \\
-& \overset{d}{\to} \Ncal\left( 0, 
-1/\eta(0) \right) 
-\end{align*}
-by Slutsky's theorem.
 \end{proof}

### 2019-10-06 appendices.tex
corrected Isoprimetric Lemma. Went through it with Vardan

@@
 
-\subsection{Proof of Proposition~\ref{prop:ceo_lower_bound}
-\label{app:proof:prop_ceo_lower_bound}}
-
-First, we note that when $f(x) = \Ncal(0,\sigma^2)$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$, our distributed setting reduces to the Gaussian CEO problem with $R_1=\ldots = R_n =1$ and $k=1$.
-Therefore, any MSE attained in our distributed setting is also attained by the CEO and thus the optimal CEO strategy (with arbitrary $k$) provides a lower bound to the MSE in our setting.
-\\
-
-Consider the minimal MSE $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
-from \cite[Eq. 10]{chen2004upper}:
+\subsection{Proof of Proposition~\ref{prop:CEO}
+\label{app:proof:CEO}}
+
+%
+Denote by $D^\star$ the optimal MSE in the Gaussian CEO with $L$ observers and under a total sum-rate $r = r_1 + \ldots +r_L$.
+An expression for $D^\star$ as a function of $r$ is give as \cite[Eq.
+10]{chen2004upper}:
 \begin{equation} \label{eq:ceo_optimal_sumrate}
-R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-For the special case of $R_\Sigma = n$ and $L=n$, we get
+r = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
+\end{equation}
+For the special case where $r = n$ and $L=n$, we have
 \begin{equation} \label{eq:ceo_optimal_sumrate2}
@@
 \end{equation}
-$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders.
-Therefore, this $D^\star$ provides a lower bound to the CEO MSE with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that
+Consider the distributed encoding setting (iii) in the case where $f(x) = \Ncal(0,\sigma^2)$ and the prior on $\Theta$ is $\pi = \Ncal(0,\sigma_\theta^2)$.
+The Gaussian CEO problem of \cite{viswanathan1997quadratic} with a unit bitrate $r_1=\ldots = r_n =1$ at each terminal and blocklength $k=1$ reduces to our distributed setting (iii).
+Since $D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describes the MSE in the CEO setting under an optimal allocation of the sum-rate $r = n$ among $n$ encoders, it provides a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
+By considering the limit $n\rightarrow \infty$ in \eqref{eq:ceo_optimal_sumrate2}, we see that
 \[
@@
 \]
-We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO MSE while enforcing the condition $R_1=\ldots = R_n = 1$.
-Indeed, an upper bound for the CEO MSE under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2019}, and leads to
-\[
-D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
-\]
-which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.
+This implies Proposition~\ref{prop:CEO}. 
+%We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the MSE in the CEO setting while enforcing the condition $r_1=\ldots = r_n = 1$.
+Indeed, an upper bound for the CEO MSE under the condition $r_1=\ldots = r_n = 1$ follows from \cite{KipnisRini2019}, and leads to
+%\[
+%D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
+%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
+%\]
+%which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.
 
@@
 \begin{lem} \label{lem:bound_intervals}
-Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$ and $\delta>0$,
+Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$,
 \begin{equation}
@@
 
-The Fisher information of $M$ with respect to $\theta$ is given by
-\begin{align}
-I_\theta & =  \ex{ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta } \nonumber \\
-& = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
-& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\
-& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\ 
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
+The Fisher information of $B$ with respect to $\theta$ is given by
+\begin{align}
+I_\theta & =  \ex{ \left( \frac{d}{d\theta} \log P\left( B | \theta \right) \right)^2 |\theta } \nonumber \\
+& = \frac{ \left(\frac{d}{d\theta} P(B=1|\theta) \right)^2}{P(B=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(B=-1|\theta) \right)^2} {P(B=-1| \theta)} \nonumber \\
+& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(B=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(B=-1| \theta) } \nonumber \\
+& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(B=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(B=-1| \theta) } \nonumber \\ 
+& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(B=1 | \theta) \left(1-P(B=1|\theta) \right)  }, \nonumber \\
 & = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
@@
 {\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
-\leq \eta_\delta(0)
-\]
-since $\eta_\delta(x)$ attains its maximum at the origin.
+\leq \eta_\delta(0) = 4^{1+\delta} f^{2+\delta}(0).
+\]
 
@@
 \]
-where $s_i \triangleq (-1)^{i+1}$. Set
-\[
-\frac{ \left| \delta_n(x_1,\ldots,x_n) \right|^{2+\delta}} 
-{\left|\Delta_n(x_1,\ldots,x_n)  \left(1- \Delta_n(x_1,\ldots,x_n) \right) \right|^{1+\delta} }.
-\]
-We use induction on $n \in \N$ to show that 
+where $s_i \triangleq (-1)^{i+1}$. We use induction on $n \in \N$ to show that 
 \begin{align}
@@
 %follows from the assumption that $\eta_\delta(x)$ is non-increasing in $|x|$. 
-Assume that \eqref{eq:lemm:interval_bounds:to_show} holds for all integers up to $n = N$ and for any $x_1 \ge \ldots \ge x_n$.
+Assume that \eqref{eq:lemm:interval_bounds:to_show} holds for all integers up to $n = N$ and for any $x_1 \ge \ldots \ge x_N$.
 Consider the case $n = N+1$.
@@
 Set $x^* = x_{i^*}$ and let $k=i^*-1$. In what follows, variables with subscript of non-positive index are ignored in summations and in lists of arguments to functions. Consider the function
-\begin{align*}
-& g(y_1,\ldots,y_N) \triangleq  \frac{\left| \delta_N(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N) )\right|^{2+\delta}}{
-\left|\Delta_N(y_1,\ldots,y_k,x_{i^*},y_{k+1}\ldots,y_N)  \right) \left(1 -\Delta_N(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N))  \right|^{1+\delta}
-} .
-\end{align*}
-The claim in the lemma is obtained by taking $y_i=x_{i'}$ where $i'$ is the $i$th element in $\{1,\ldots,N+1\}\setminus \{i^*\}$. It is therefore enough to prove that 
+\begin{align}
+& g(y_1,\ldots,y_N) \triangleq g(y_1,\ldots,y_N|x^*,k) \\
+&  \triangleq  \frac{\left| \delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N) )\right|^{2+\delta}}{
+\left|\Delta_{N+1}(y_1,\ldots,y_k,x_{i^*},y_{k+1}\ldots,y_N)  (1 -\Delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N)  \right|^{1+\delta}
+} \label{eq:g_def}.
+\end{align}
+The LHS of \eqref{eq:lemm:interval_bounds:to_show} is obtained by taking $y_i=x_{k_i}$ where $k_i$ is the $i$th element in $\{1,\ldots,N+1\}\setminus \{i^*\}$. It is therefore enough to prove that 
 \[
@@
 %
-The maximal value of $g(y_1,\ldots,y_N)$ is attained for the same $(y_1,\ldots,y_N) \in A_{N+1}(x^*,k)$ that maximizes
+The maximal value of $g(y_1,\ldots,y_N)$ is attained for the same $(y_1,\ldots,y_N) \in A_N(x^*,k)$ that maximizes
 \begin{align*}
@@
 %
-The partial derivative of $\log(g)(y_1,\ldots,y_N)$ with respect to $y_i$ within the interior of $A_N(x^*,k)$ is given by
+Within the interior of $A_N(x^*,k)$, all three expressions in \eqref{eq:g_def} within an absolute value are positive.
+It follows that partial derivative of $\log(g)(y_1,\ldots,y_N)$ with respect to $y_i$ within the interior of $A_N(x^*,k)$ is given by
 \[
@@
 $g(y_1,\ldots,y_N) = \eta_\delta(x_{i^*})$  
-if $N$ is even, or
-\begin{align*}
-& g(y_1,\ldots,y_N) = \frac{\left| s_1f(y_1)+s_{N+1}f(x_{i^*})  \right|^{2+\delta}} { 
-\left|  s_1F(y_N) + s_{N+1}F(x_{i^*}) \right|^{1+ \delta} 
-\left| 1 - (s_1F(y_1) + s_{N+1}F(x_{i^*})) \right|^{1+ \delta} } 
-\end{align*} 
-if $N$ is odd and $y_1 < x^*$. Form the induction assumption, the last display is bounded from above by $\eta_\delta(x_{i^*})$. The case where $N$ is odd and $y_1 > x^*$ is similar. 
+if $N$ is even. If $N$ is odd and $y_1 = \ldots = y_N > x^*$, then 
+\begin{align*}
+& g(y_1,\ldots,y_N) = \frac{\left| f(y_1)-f(x_{i^*})  \right|^{2+\delta}} { 
+\left|  F(y_1) - F(x_{i^*}) \right|^{1+ \delta} 
+\left| 1 - (F(y_1) -F(x_{i^*})) \right|^{1+ \delta} } 
+\end{align*} 
+which is bounded from from above by $\eta_\delta(x_{i^*})$ by the induction hypothesis. The case where $N$ is odd and $-x^* \leq y_1 = \ldots = y_N$ is similar. 
 %
 We now consider the possibility that the maximum of $g(y_1,\ldots,y_N)$ is attained at the boundaries of $A_N(x^*,k)$.
-For boundary points for which $y_i = y_{i+1}$ for some $i$, the contribution of $y_i$ and $y_{i+1}$ to $g(y_1,\ldots,y_N)$ is zero and the induction assumption for $n=N-1$ implies that
+At boundary points for which $y_i = y_{i+1}$ for some $i$, the contribution of $y_i$ and $y_{i+1}$ to $g(y_1,\ldots,y_N)$ is zero and the induction assumption for $n=N-1$ implies that
 \[
@@
 \]
-at these points. The remaining boundary points of $A_N(x^*,k)$ are covered by the following cases:
+The remaining boundary points of $A_N(x^*,k)$ are covered by the following cases:
 \begin{itemize}
@@
 %
-Under case (4), set 
+Finally, under case (4), set 
 \[
@@
 \]
-Note that whenever $d>0$, 
+Whenever $d>0$, 
 \begin{align*}
@@
 \par  
-In the case where $c'(x)$ is not necessarily strictly decreasing, we approximate $c(x)$ using another concave symmetric function whose derivative is always negative except at the origin.
+In the case where $c'(x)$ is not necessarily strictly decreasing, we approximate $c(x)$ using another concave symmetric function whose derivative is always negative except, perhaps, at the origin.
 For $\alpha>0$ consider the function  $f_\alpha(x) = \kappa(\alpha) e^{\sgn(c(x))|c(x)|^{1+\alpha}}$, where $\kappa(\alpha)$ is chosen such that $f_\alpha(x)$ is a probability density function.
@@
 Now $c_\alpha'(x)$ is non-increasing since it is the derivative of a concave function.
-It can be verified that it is non-constant on any interval (because $c(x)$ is non-constant and $c'(x)$ is non-increasing), and hence an injection.
+Furthermore, since $c(x)$ is non-constant on any interval and $c'(x)$ is non-increasing, $c_\alpha'(x)$ is non-constant on any interval hence an injection.
 It follows from the first part of the proof that, for any $\alpha>0$,
@@
 }
-The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.
+The estimation algorithm of \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.
+The proof of Theorem~\ref{thm:sgd} relies on various results from these works.
 
@@
 under $\Prob_{\theta,n}$.
-Under the assumption that $f(x)$ is continuously differentiable with a finite location Fisher information, the model $\{Z_n+ \theta\}_{n \in \N}$ is differentiable in quadratic mean \cite[Exm.
-7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
-\[
-\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
-\]
-where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$. 
- The random variable $L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)
-$ is bounded, and hence 
-\[
-\ex{ L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)} \to \ex{L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)}
-\]
-Any regular estimators in a LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}, hence in order to prove (ii) it is left to show that $\bar{\theta}_n$ is regular. For this purpose, 
-we use the following refinement of Theorem~\ref{thm:polyak_juditsky}, proof of which is given in Subsection~\ref{proof:thm:normal_expansion} below.
+In order to show \eqref{eq:sgd_part2} we use the following refinement of Theorem~\ref{thm:polyak_juditsky}, proof of which is given in Subsection~\ref{proof:thm:normal_expansion} below.
 %
@@
 where $o_{p,n}(1)$ converges in probability to $0$ as $n\to \infty$.
-\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite location Fisher information 
-\[
-I_\theta = \int_{\R} \left( \frac{f'(x)}{f(x)} \right)^2 f(x) dx,
-\]
-then for any converging sequence $h_n \to h$,
+\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite Fisher information for location $\sigma_f^2$, then for any converging sequence $h_n \to h$,
 \[
@@
 \end{thm}
-We now use this theorem to establish the regularity of $\bar{\theta}_n$. We have, 
+In our setting, we have
 \begin{align*}
@@
 \end{align*}
-hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
+and hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
 \[
@@
 \]
-Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}.
+Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}. \par
+
+Under the assumption that $f(x)$ is continuously differentiable with a finite Fisher information for location, the model $\{Z_n+ \theta\}_{n \in \N}$ is differentiable in quadratic mean \cite[Exm.
+7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
+\[
+\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
+\]
+where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$.
+The proof is concluded since any regular estimator in LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}.
 
@@
 \[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] \leq K_3(1+|x|^4). 
+\ex{  | \varphi(x+Z_1) |^4 } \leq K_3(1+|x|^4). 
 \]
@@
 \[
-V_n \triangleq \mathbb E \left[ \left(\bar{U}_n-x^\star \right)^2 \right] = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
+V_n \triangleq \ex{ \left(\bar{U}_n-x^\star \right)^2 } = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
 \]
@@
 \[
-\mathbb E \left[ | \varphi(x+Z_1) |^4 \right] = 1 \leq K_3(1+|x|^4)
+\ex{ | \varphi(x+Z_1) |^4 } = 1 \leq K_3(1+|x|^4)
 \]
@@
 \[
-V_n = \mathbb E \left[ \left({\theta}_n-\theta \right)^2 \right]  = \frac{1}{4n f^2(0)} + o(n^{-1}).
-\]
-
-{\color{red}
+V_n = \ex{ \left({\theta}_n-\theta \right)^2 } = \frac{1}{4n f^2(0)} + o(n^{-1}).
+\]
 
@@
 In order to prove this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$.
-The first expression on the RHS on \eqref{eq:Polyak_expansion} goes to zero in variance.
+The first expression on the RHS of \eqref{eq:Polyak_expansion} goes to zero in variance.
 In addition,
@@
 \end{align*}
-Plugging this bound in \eqref{eq:PJ_proof_3} and using Lemma~\ref{lem:PJ_converging_sum},we obtain 
+Plugging this bound in \eqref{eq:PJ_proof_3} and using Lemma~\ref{lem:PJ_converging_sum}, we obtain 
 \[
@@
 From \cite[Exm.
-7.8]{van2000asymptotic}, the location model $f(x-\theta)$ with continuously differentiable $f(x)$ is differentiable in quadratic mean with the score function $-f'(x-\theta)/f(x-\theta)$.
-This fact implies the following expansion \cite[Thm.
-7.2]{van2000asymptotic}:
+7.8]{van2000asymptotic}, the location model $f(x-\theta)$ with continuously differentiable $f(x)$ is differentiable in quadratic mean.
+% with the score function $-f'(x-\theta)/f(x-\theta)$.
+This fact implies the following expansion \cite[Thm. 7.2]{van2000asymptotic}:
 \begin{align}
@@
 \]
-
 \QEDA
-}
 
@@
 \]
-where $t_{i,1}<\ldots<t_{i,K_i}$ and, with a slight abuse of notation, $t_{i,1}$ and $t_{i,K_i}$ may also be $-\infty$ or $+\infty$, respectively. Thus
+where $t_{i,1}<\ldots<t_{i,K_i}$ and, with a slight abuse of notation, $t_{i,1}$ and $t_{i,K_i}$ may take the values $-\infty$ or $+\infty$, respectively. Thus
 \[
@@
 \begin{equation}
-\frac{\sum_{i=1}^n \mathbb E \left| U_i \right|^{2+\delta} } { \left( \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta} = 
-\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \mathbb E |U_i|^{2+\delta} }{ \left(\frac{1}{n} \sum_{i=1}^n \mathbb E U_i^2  \right)^\delta}. 
+\frac{\sum_{i=1}^n\ex{\left| U_i \right|^{2+\delta}} } { \left( \sum_{i=1}^n \ex{U_i^2}  \right)^\delta} = 
+\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \ex{ |U_i|^{2+\delta}} }{ \left(\frac{1}{n} \sum_{i=1}^n \ex{U_i^2 } \right)^\delta}. 
 \label{eq:Lyaponov}
@@
 \begin{align}
-\frac{1}{n} \sum_{i=1}^n \ex{ |U_i|^{2+\delta}}  < M \label{eq:Lyaponov_num}
+\frac{1}{n} \sum_{i=1}^n \ex{ |U_i|^{2+\delta}}  < K \label{eq:Lyaponov_num}
 \end{align} 
@@
 \]
-We now use the fact that each $A_i$ is a finite union of intervals.
-Under the assumption that there exists $\delta>0$ such that $\eta^{1+\delta}(x)/f^\delta(x)$ has a unique maximum at the origin, we get
+We now use the fact that each $A_i$ is a finite union of intervals. Under the assumption that there exists $\delta>0$ such that $\eta^{1+\delta}(x)/f^\delta(x)$ is maximized by the origin, we get
 \[

### 2019-10-06 conclusions.tex
corrected Isoprimetric Lemma. Went through it with Vardan

@@
 We further considered the special case of messages obtained by comparing against a prescribed sequence of thresholds.
-We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.
+We characterized the performance of the optimal estimator from such messages using the density of these thresholds and considered the threshold density that minimizes the minimax risk.

### 2019-10-06 distributed-estimation.tex
corrected Isoprimetric Lemma. Went through it with Vardan

@@
 
-As a first step, we provide conditions under which the messages $B_1,B_2,\ldots$ define a local asymptotic normal family.
+As a first step, the following theorem provides conditions under which the messages $B_1,B_2,\ldots$ define a local asymptotic normal family.
+The proof of this theorem is in Appendix~\ref{proof:thm:LAN1}.
 
@@
 \begin{itemize}
-\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is log-concave, differentiable, symmetric,  and  there exists $\delta>0$ such that $\eta^{1+\delta}(x)/f^\delta(x)$ has a unique maximum at the origin.
+\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is log-concave, differentiable, and symmetric.
+Furthermore, there exists $\delta>0$ such that the function $\eta^{1+\delta}(x)/f^\delta(x)$ is non-increasing in $|x|$ and is uniquely maximized by the $x=0$.
 \item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
@@
 \end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:LAN1}. 
-\end{proof}
-
 Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}.
-%
-Among these conditions, (iii) is arguably the strongest and hardest to verify.
+Condition (i) is satisfied, for example, by the normal distribution with $\delta\leq 2$.
+Condition (iii) is arguably the strongest and hardest to verify.
 As we show in Section~\ref{subsec:threshold} below, this condition is satisfied, for example, when $A_1, \ldots,A_n$ are half lines whose starting points are drawn independently from some probability measure on $\mathbb R$.
@@
 %
-Corollary~\ref{cor:LA_minimax} says that when the messages define a LAN model, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model at $\theta$.
-This fact poses the upper bound of $\kappa(\theta)\sigma^2$ for the ARE of estimators in such models.
-\par
-
-Next, we show that under LAN no estimator can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly for all $\theta \in \Theta$.
+Corollary~\ref{cor:LA_minimax} says that when the sequence of one-bit messages defines a LAN model with respect to $\theta$, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model.
+Consequently, the ARE  in such case is at most $\kappa(\theta)\sigma^2$.
+Furthermore, as we show next, no estimator in this setting can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly over $ \Theta$.
 
@@
 \begin{thm} \label{thm:non_existence}
-Under conditions (i)-(iii) in Theorem~\ref{thm:LAN1}, assume that each $A_i$ is a union of at most $K$ intervals.
+Under conditions (i)-(iii) in Theorem~\ref{thm:LAN1}, assume that each $A_i$ is the union of at most $K$ intervals.
 The number of points $\theta \in \Theta$ satisfying $\kappa(\theta) = \eta(0)$ is at most $2K$.
@@
 \end{cor}
-The condition that $\lambda_n$ converges to a probability measure is satisfies, for example, whenever the $t_1,\ldots,t_n$s are drawn independently from a probability distribution $\lambda(dt)$ on $\mathbb R$.
+The condition that $\lambda_n$ converges to a probability measure is satisfied, for example, whenever the $t_1,\ldots,t_n$s are drawn independently from a probability distribution $\lambda(dt)$ on $\mathbb R$.
 \par
@@
 \end{equation}
-which is the derivative of the log-likelihood function.
 This root is unique since the log-likelihood function is concave.
@@
 Since $\theta$ is apriori unknown, we conclude that estimation in the distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting.
-In other words, the ability to choose the threshold values in an adaptive manner based on previous messages strictly improves relative efficiency compared to a non-adaptive threshold selection.
+In other words, the ability to choose the threshold values in an adaptive manner based on previous messages necessarily improves relative efficiency compared to a non-adaptive threshold selection.
 \par
@@
 The minimal asymptotic risk $\kappa^\star(\theta)$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $T$.
-Also illustrated in these Figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
+Also illustrated in these figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
 \begin{align}
@@
 xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
+xticklabels={-$T$, 0, $T$},
 title = {$\sigma/\sigma_{\theta} = 1$},
@@
 xtick={-0.5,0,0.5},
-xticklabels={-$b$, 0, $b$},
+xticklabels={-$T$, 0, $T$},
 ytick={0,1},
@@
 title = {$\sigma/\sigma_{\theta} = 3$},
-xticklabels={-$b$, 0, $b$},
+xticklabels={-$T$, 0, $T$},
 ytick={0,1},
@@
 \caption{\label{fig:opt_density}
-Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=b^2/3$ is the variance of the prior.
+Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=T^2/3$ is the variance of the prior.
 }
@@
 
- We consider now the problem of minimizing the asymptotic Bayes risk $
-R_{\pi,\lambda} \triangleq \mathbb E  K^{-1}(\theta)$ over all probability measures $\lambda(dt)$ with support in $\mathbb R$. This optimization problem can be written as follows:
+When a prior $\pi$ on $\Theta$ is provided, one may be interested in the threshold density $\lambda$ minimizing the Bayes risk $R_n(\pi)$. The resulting minimization problem is 
 \begin{align}
@@
 \begin{split}
-\mathrm{minimize} \quad & R_{\pi,\lambda} =  \int \frac{\pi(d\theta)}{ \int \eta \left( t-\theta\right) \lambda(dt)}. \\ 
-\mathrm{subject~to} \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) =1. 
+\mathrm{minimize} \quad & R_{\pi} =  \int \frac{\pi(d\theta)}{ \int \eta \left( t-\theta\right) \lambda(dt)}. \\ 
+\mathrm{subject~to} \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) =1, 
 \end{split}
 \end{align}
-We denote by $R^\star_{\pi}$ the minimal value of the objective function in \eqref{eq:cvx_average}.
-Since the function $x \rightarrow 1/x$ is convex for positive values, \eqref{eq:cvx_average} defines a convex optimization problem in $\lambda$ whose solution depends on the prior $\pi$.
-The solution to this problem is approximated by considering $\lambda$ and $\pi$ over a discrete set.
-On Figure~\ref{fig:opt_density} we illustrate the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distributon ($P_X = \Ncal(\theta, \sigma^2)$) and the prior on $\theta$ is uniform over $\Theta = [-b,b]$.
-Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
-\par
+which is convex in $\lambda$ since $x \rightarrow 1/x$, $x>0$, is convex.
+Figure~\ref{fig:opt_density}  illustrates the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distribution and $\pi$ is the uniform over $\Theta = [-T,T]$.
+%Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
+
+\iffalse
 \begin{figure}
 \begin{center}
-
 \begin{tikzpicture}[scale = 1]
@@
 \end{example}
+\fi

### 2019-10-06 introduction.tex
Trying to understand proofs
corrected Isoprimetric Lemma. Went through it with Vardan

@@
 Let us provide an informal description of our results and setting. For an
-estimator $\theta_n$ with finite quadratic risk (mean squared error) $R_n =
+estimator $\theta_n$ with finite quadratic risk (mean squared error (MSE)) $R_n =
 \E_\theta[(\theta_n - \theta)^2]$, we study the limit
@@
 
-The remainder of this paper is organized as follows.
-In Section~\ref{sec:problem} we describe the problem and useful notation.
-In Section~\ref{sec:preliminary} we provide two simple bounds on the efficiency and MSE.
-Our main results for the adaptive and distributed cases are given in Sections~\ref{sec:sequential} and \ref{sec:distributed}, respectively.
-In Section~\ref{sec:conclusions} we provide concluding remarks.
+The remainder of this paper is organized as follows. In
+Section~\ref{sec:problem} we describe the problem, notation, and
+our basic assumptions. In
+Section~\ref{sec:preliminary} we provide two simple bounds on the efficiency
+and MSE. Our main results for the adaptive and distributed cases are given
+in Sections~\ref{sec:sequential} and \ref{sec:distributed}, respectively. In
+Section~\ref{sec:conclusions} we provide concluding remarks.

### 2019-10-06 preliminaries.tex
corrected Isoprimetric Lemma. Went through it with Vardan

@@
 expression provides the following proposition:
-\begin{prop} \label{prop:ceo_lower_bound}
+\begin{prop} \label{prop:CEO}
   Assume that $\Theta = \mathbb R$ and $\pi(\theta) =
@@
 \noindent
-See Appendix~\ref{app:proof:prop_ceo_lower_bound} for a proof.
+See Appendix~\ref{app:proof:CEO} for a proof.
 

### 2019-10-06 problem-formulation.tex
corrected Isoprimetric Lemma. Went through it with Vardan

@@
 \end{equation}
-is of course the familiar asymptotic variance of the $p$th quantile of the
-sample $X_1^n$ (cf.~\cite{VanDerVaart98}, Ch.~21).
+is of course the familiar asymptotic variance of the $p$th quantile of the sample $X_1,\ldots,X^n$ (cf.~\cite{VanDerVaart98}, Ch.~21).
 
-For $f$ the normal density, it classical results~\cite{Samford1953,
+For $f$ the normal density, classical results~\cite{Samford1953,
   hammersley1950estimating} show that that $\eta(x)$ is a strictly
@@
 %
-We consider symmetric log-concave symmetric distributions sharing this
+We consider log-concave symmetric distributions sharing this
 property.  Specifically, we require the following.

### 2019-10-07 appendices.tex
went through proof of Theorem 5

@@
 %Indeed, any measurable function $(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
-Consider the conditional distribution $P({B^n|\theta})$ of $B^n$ given $\theta$. We have 
-\begin{align}
-P\left( B^n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
-\end{align}
-where $P\left(B_i =1 | \theta, B^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B^n$ with respect to $\theta$ is given by 
-\begin{align}
-I_\theta(B^n) = \sum_{i=1}^n I_\theta (B_i|B^{i-1}),
+Consider the conditional distribution $P({B_1,\ldots,B_n|\theta})$ of $(B_1,\ldots,B_n)$ given $\theta$. We have 
+\begin{align}
+P\left( B_1,\ldots,B_n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B_1,\ldots,B_{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
+\end{align}
+where $P\left(B_i =1 | \theta, B_1,\ldots,B_{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B_1,\ldots,B_n$ with respect to $\theta$ is given by 
+\begin{align}
+I_\theta(B_1,\ldots,B_N) = \sum_{i=1}^n I_\theta (B_i|B_1,\ldots,B_{i-1}),
 \label{eq:fisher_information}
 \end{align}
-where $I_\theta (B_i|B^{i-1})$ is the Fisher information of the distribution of $B_i$ given $B^{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B^{i-1}) \leq 4f^2(0)$.
+where $I_\theta (B_i|B_{i-1},\ldots,B_1)$ is the Fisher information of the distribution of $B_i$ given $B_1,\ldots,B_{i-1}$.
+From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B_{i-1},\ldots,B_1) \leq 4f^2(0)$.
 The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
 \begin{align*}
-\ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ \ex{ I_\theta(B^n)} + I_0} \\
+\ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ \ex{ I_\theta(B_1,\ldots,B_n)} + I_0} \\
 & = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
@@
 \begin{lem} \label{lem:bound_intervals_delta}
-Let $f(x)$ be log-concave, symmetric, and differentiable density function. Let $\delta\geq 0$. Assume that the origin $x=0$ uniquely maximizes the function
+Let $f(x)$ be log-concave, symmetric, and differentiable density function. Let $\delta\geq 0$. Assume that the function
 \[
@@
 \]
-and that $\eta_\delta(x)$ is non-increasing in $|x|$. For any $x_1 \ge \ldots \ge x_n \in \R^n$,
+is non-increasing in $|x|$. For any $x_1 \ge \ldots \ge x_n \in \R^n$,
 \begin{equation}
@@
 }
-The log probability mass distribution of $B^n=(B_1,\ldots,B_n)$ is given by
-\begin{align*}
-& \log \Prob_\theta(b^n) = \sum_{i=1}^n \left( \frac{b_i+1}{2} \log  \Prob(X_i\in A_i) + 
-\frac{1-b_i}{2} \log \Prob(X_i\in A_i) \right), \quad b^n \in \{-1,1\}^n. 
+The log-probability mass distribution of $(B_1,\ldots,B_n)$ is given by
+\begin{align*}
+& \log \Prob_\theta(b_1,\ldots,b_n) = \sum_{i=1}^n \left( \frac{b_i+1}{2} \log  \Prob(X_i\in A_i) + 
+\frac{1-b_i}{2} \log \Prob(X_i\in A_i) \right), \quad b_i \in \{-1,1\}, \quad i=1,\ldots,n. 
 \end{align*}
@@
 \begin{align}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) } = \sum_{i=1}^n    \frac{b_i+1}{2} 
+& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b_1,\ldots,b_n)} { \Prob_\theta (b_1,\ldots,b_n) } = \sum_{i=1}^n    \frac{b_i+1}{2} 
 \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} + 
@@
 \[
-A_i = \bigcup_{k=1}^{K_i} \left(t_{i,k},t_{i,k+1} \right),
+A_i = \bigcup_{k=1}^{K_i} \left(t_{i,2k-1},t_{i,2k} \right),
 \]
@@
 \[
-\Prob_{\theta}(X_i \in A_i) = \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta).
-\]
-In particular, since $f$ is differentible, $\Prob_{\theta}(X_i \in A_i)$ is twice differentiable, and we may write
+\Prob_{\theta}(X_i \in A_i) = \sum_{k=1}^{K_i} (-1)^k F(t_{i,k}-\theta).
+\]
+In particular, since $f$ is differentible in $\theta$, $\Prob_{\theta}(X_i \in A_i)$ is twice differentiable, and we may write
 \begin{align*}
@@
 \begin{align*}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b^n)} { \Prob_\theta (b^n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
+& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b_1,\ldots,b_n)} { \Prob_\theta (b_1,\ldots,b_n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
 \left( 
@@
 \end{equation}
-Next, we claim that there exits $\delta>0$ and $K>0$, that are independent of $n$, such that
-\begin{align}
-\frac{1}{n} \sum_{i=1}^n \ex{ |U_i|^{2+\delta}}  < K \label{eq:Lyaponov_num}
+Next, we claim that there exits $\delta>0$ and $K(\delta)>0$, that are independent of $n$, such that
+\begin{align}
+\frac{1}{n} \sum_{i=1}^n \ex{ |U_i|^{2+\delta}}  < K(\delta) \label{eq:Lyaponov_num}
 \end{align} 
@@
   &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}, 
-\end{align*}
-where the last transition is because 
-\[
- \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}  \right) \leq 1. 
-\]
-We now use the fact that each $A_i$ is a finite union of intervals. Under the assumption that there exists $\delta>0$ such that $\eta^{1+\delta}(x)/f^\delta(x)$ is maximized by the origin, we get
-\[
-\eta^{1+\delta}(x)/f^\delta(x) = \frac{(f(x))^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}} \leq 4^{1+\delta} (f(0))^{2+\delta}. 
-\]
-Lemma~\ref{lem:bound_intervals_delta} implies
+  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}. 
+\end{align*}
+%where the last transition is because 
+%\[
+% \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}  \right) \leq 1. 
+%\]
+We now use the fact that each $A_i$ is a finite union of intervals.
+Under the assumption that there exists $\delta>0$ such that $\eta^{1+\delta}(x)/f^\delta(x)$ is uniquely maximized by the origin and is non-increasing in $|x|$, Lemma~\ref{lem:bound_intervals_delta} implies
 \begin{align*}
@@
 \]
-and thus the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we conclude that 
+and thus the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we obtain 
 \[
@@
 \[
-\mathcal B_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\}.
+C_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\}.
 \]
@@
 \[
-S_n(\theta, \epsilon) \triangleq \left\{ i\leq n \,:\, (\theta-\epsilon,\theta+\epsilon) \cap \mathcal B_i \neq \emptyset \right\}
+S_n(\theta, \epsilon) \triangleq \left\{ i\leq n \,:\, (\theta-\epsilon,\theta+\epsilon) \cap C_i \neq \emptyset \right\}
 \]

### 2019-10-07 distributed-estimation.tex
went through proof of Theorem 5

@@
 \begin{itemize}
-\item [(i)\,\,] The pdf $f(x)$ of $X_n-\theta$ is log-concave, differentiable, and symmetric.
-Furthermore, there exists $\delta>0$ such that the function $\eta^{1+\delta}(x)/f^\delta(x)$ is non-increasing in $|x|$ and is uniquely maximized by the $x=0$.
+\item [(i)\,\,] The probability density function $f(x)$ of $X_n-\theta$ is log-concave, differentiable, and symmetric.
+Furthermore, there exists $\delta>0$ such that the function $\eta^{1+\delta}(x)/f^\delta(x)$ is non-increasing in $|x|$.
 \item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
@@
 \subsection{Minimax Threshold Density}
-The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta = [-T,T]$ is given as the solution to the following optimization problem:
+The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta$ is given as the solution to the following optimization problem:
 \begin{align}
@@
 \begin{split}
-\mathrm{maximize} \quad &  \inf_{\theta \in [-T,T]} \int \eta(t-\theta) \lambda(dt)
+\mathrm{maximize} \quad &  \inf_{\theta \in \Theta} \int \eta(t-\theta) \lambda(dt)
 \\ 
@@
 The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program.
-We denote by $\kappa^\star(T)$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum.
+We denote by $\kappa^\star$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum.
+Theorem~\ref{thm:LAN1} and Corollary~\ref{cor:LAN_thresh} imply that for any $\theta \in \Theta$, the ARE of any local asymptotic minimax estimator (such as the ML estimator) from $\{B_i,\,i\in N\}$ of the form \eqref{eq:threshold_message} with $t_i \sim \lambda^\star$ i.i.d.
+is at least $\kappa^\star$.
 %
@@
 %\end{rem} 
-
-Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$.
-The minimal asymptotic risk $\kappa^\star(\theta)$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of the support size $T$.
+\par
+Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$ and $\Theta = [-T,T]$.
+The minimax asymptotic precision parameter $\kappa^\star$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of half the support size $T$.
 Also illustrated in these figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
@@
 \end{align}
-From Corollary~\ref{cor:LAN_thresh}, we conclude that the ARE under a uniform distribution is $\kappa_\unif \sigma^2$. \par
+Corollary~\ref{cor:LAN_thresh} implies that the ARE under threshold values uniformly distributed is $\kappa_\unif \sigma^2$. \par
 
@@
 \caption{\label{fig:minimax_support}
-Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in \Theta = [-T,T]$.
+Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in [-T,T]$.
 %
-The continuous curve (red) represents the reciprocal of the asymptotic risk for at a fixed $\theta \in \Theta$ under the optimal density, so the minimax risk is the inverse of its minimal value.
-The dashed curve (green) is the reciprocal of the asymptotic risk for a fixed $\theta$ under a uniform distribution of threshold values over $\Theta$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
+The continuous curve (red) represents the reciprocal of the asymptotic risk at a fixed $\theta \in [-T,T]$ under the optimal density, i.e., the minimax risk is the inverse of the minimal value of this curve.
+The dashed curve (green) is the reciprocal of the asymptotic risk at a fixed $\theta \in [-T,T]$ when the threshold values are uniformly distributed over $[-T,T]$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
 }
@@
 \begin{center}
+%
+\begin{tikzpicture}[scale = 0.55]
+\begin{axis}[
+width=8cm, height=6cm,
+xmin = -0.5, xmax=0.5, 
+restrict y to domain = 0:100,
+ymin = 0,
+ymax = 1,
+samples=10, 
+xlabel= {$dt$},
+title = {$\sigma/\sigma_{\theta} = 4$},
+xtick={-0.5,0,0.5},
+xticklabels={-$T$, 0, $T$},
+ytick={0,1},
+ylabel = {$\lambda(dt)$},
+yticklabels={0,1},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
+%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
+\end{axis}
+\end{tikzpicture}
+%
 \begin{tikzpicture}[scale = 0.55]
@@
 xtick={-0.5,0,0.5},
+title = {$\sigma/\sigma_{\theta} = 3$},
 xticklabels={-$T$, 0, $T$},
-title = {$\sigma/\sigma_{\theta} = 1$},
 ytick={0,1},
@@
 ]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
 %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
@@
 xtick={-0.5,0,0.5},
-title = {$\sigma/\sigma_{\theta} = 3$},
 xticklabels={-$T$, 0, $T$},
+title = {$\sigma/\sigma_{\theta} = 1$},
 ytick={0,1},
@@
 ]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
 %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
@@
 \end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 4$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
 \caption{\label{fig:opt_density}

### 2019-10-08 adaptive-estimation.tex
fixed (I think) the proof of Theorem 4

@@
 \[
-{\theta}_{n_2}  = {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
+{\theta}_{n_2}  \triangleq {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
 \]
@@
 \begin{proof}
-By the law of large numbers,
-\[
-p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
-\]
-so that ${\theta}_{n_1}$ converges almost surely to $\theta$ as $n$ goes to infinity. 
 For $t\in \mathbb R$, set
@@
 \]
-Since $n_2(n)/n \to 1$, the central limit theorem and Slutsky's theorem imply
+Since $n_2(n)/n \to 1$, if follows from the Berry Esseen theorem that there exists $C$, independent of $n$ and $t$, such that 
 \begin{align*}
-\sqrt{n} \left( p_{n_2}(t) - F( \theta - t) \right)   \overset{d}{\rightarrow} \sqrt{F(\theta - t) F \left( t - \theta\right)} Z,
+\sup_{t \in \R} \left| \sqrt{n} \frac{ p_{n_2}(t) - F( \theta - t)} {F(\theta - t) F \left( t - \theta\right) }  - \Phi(t) \right|  \leq C/\sqrt{n}. 
 \end{align*}
-where $Z \sim \Ncal(0,1)$. In addition, Slutsky's theorem imply
+where $Z \sim \Ncal(0,1)$. It follows that
+\begin{align}
+\label{eq:two_step_proof}
+ \sqrt{n} \frac{ p_{n_2}(Y_n) - F(0)} {F^2(0) }  \overset{d}{\rightarrow} \Ncal(0,1)
+\end{align}
+for any sequence of random variables $\{Y_n\}$ converging in probability to $\theta$. In particular, since
 \[
-\sqrt{F(\theta-\theta_{n_1}) F(\theta_{n_1} - \theta)} Z_1 \overset{d}{\rightarrow}  F(0) Z,  
+p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
 \]
-hence 
-\[
-\sqrt{n} \left( p_{n_2}( \theta_{n_1}) - F( \theta - \theta_{n_1}) \right)  \overset{d}{\rightarrow} F(0) Z.
-\]
-Finally, we use the delta method with $g(x) = F^{-1}(x)$ to conclude
+by the law of large numbers, \eqref{eq:two_step_proof} holds with $Y_n = \theta_{n_1}$. Finally, we use the delta method with $g(x) = F^{-1}(x)$ to conclude
 \begin{align*}

### 2019-11-13 preliminaries.tex
updated preliminaties.tex

@@
 \[
-B_i = \mathbf 1_{X_i>\theta_0}, 
+B_i = \mathbf 1_{X_i<\theta_0}, 
 \]
@@
 \[
-P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),  
+P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta_0 - \theta),  
 \]
@@
 \label{eq:estimator_naive}
-{\theta}_n = \theta_0 + F^{-1}\left( P_n \right)
+{\theta}_n = \theta_0 - F^{-1}\left( P_n \right)
 \end{equation}
@@
 support of $f$. As the variance of $P_n$ is
-$F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)$, a delta method
+$F(\theta_0-\theta)\left(1-F(\theta_0-\theta)\right)$, a delta method
 calculation~\cite[Ch.~23]{VanDerVaart98} implies that ${\theta}_n$ is
@@
 \begin{equation*}
-  \frac{F(\theta-\theta_0)\left(1-F(\theta-\theta_0)\right)}{f^2(\theta-\theta_0)} = \frac{1}{
-\eta(\theta-\theta_0)}.
+  \frac{F(\theta_0-\theta)\left(1-F(\theta_0-\theta)\right)}{f^2(\theta_0-\theta)} = \frac{1}{
+\eta(\theta_0-\theta)}.
 \end{equation*}
 In the Gaussian case where the $X_i \simiid \normal(\theta, \sigma^2)$, the
-ARE of ${\theta}_n$ is $\eta(\theta - \theta_0)\sigma^2$.
+ARE of ${\theta}_n$ is $\eta(\theta_0 - \theta)\sigma^2$.
 

### 2019-11-24 conclusions.tex
minor changes to Conclusions

--- 2019-09-23 conclusions.tex
@@
 \section{Conclusions \label{sec:conclusions}}
-We considered the MSE risk in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
+We considered the risk and efficiency in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution.
 %
-In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency (ARE) larger than that of the median of the samples.
+In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency larger than that of the median of the samples.
 We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median.
@@
 \par
-In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and ARE. 
+In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and efficiency relative to the mean. 
 %
-We conclude that under such conditions, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in the distributed setting.
+These condition implies that, in the distributed, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in this setting.
 %
-We further considered the special case of messages obtained by comparing against a prescribed sequence of thresholds.
-We characterized the performance of the optimal estimator from such messages using the density of these thresholds, and consider the threshold density that minimizes the minimax risk.
+We further considered the special case where the sequence of bits is obtained by comparing against a prescribed sequence of thresholds.
+We characterized the performance of the optimal estimator from such bit-sequence using the density of the thresholds and considered the density that minimizes the minimax risk.

### 2019-12-11 adaptive-estimation.tex
fixed proof of Theorem 4
Working on proof of SGD

@@
 \section{Adaptive Estimation \label{sec:sequential}}
-The first main results of this paper, as described in Theorem~\ref{thm:adpative_lower_bound} below, states that the ARE of any adaptive estimator cannot be larger than $\eta(0)\sigma^2$, which is the ARE of the median of the sample $X_1,\ldots,X_n$.
-We also provide a particular adaptive estimation scheme that attains this maximal efficiency.
+
+The first main result of this paper (Theorem~\ref{thm:adpative_lower_bound})
+gives that the asymptotic variance of any adaptive estimator must be at
+least $\eta(0)\sigma^2$, which is precisely the efficiency of the median of
+the sample $X_1,\ldots,X_n$. Conveniently, the stochastic (sub)gradient
+estimator for the median---which minimizes $\E[|X - \theta|]$---is a
+sequence of signs (single bits), so that we can exhibit an asymptotically
+optimal adaptive estimation scheme.
+
 %Finally, in Theorem~\ref{thm:opt_one_step}, we provide an adaptive estimation scheme that is one-step optimal in the sense that at each step $i$, the chosen message $B_i$  minimizes the MSE given $X_i$ and the previous $i-1$ messages.
@@
 
-\subsection{Limited efficiency in the adaptive setting}
-Our first result asserts that the ARE of any adaptive encoding and estimation scheme is bounded from above by $\eta(0)\sigma^2$. %This result follows from the following theorem:
-\begin{thm}[maximal relative effeciency] \label{thm:adpative_lower_bound}
-Let ${\theta}_n$ be any estimator of $\theta$ in the adaptive setting of Figure~\ref{fig:setup}-(ii). Assumes that $\pi(\theta)$ converges to zero at the endpoints of the interval $\Theta$. Then
-\[
-n\mathbb E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0},
-\]
-where 
-\[
-I_0 = \mathbb E \left( \frac{d}{d\theta} \log \pi (\theta) \right)^2
-\]
-is the Fisher information with respect to a location model in $\theta$. 
+We begin with our first theorem, whose proof we provide in
+Appendix~\ref{proof:thm:adpative_lower_bound}.
+\begin{thm}[Fundamental limits]\label{thm:adpative_lower_bound}
+  Let Assumption~\ref{assump:failure_rate} hold.
+  Let ${\theta}_n$ be any estimator of $\theta$ in the adaptive setting of
+  Figure~\ref{fig:setup}(ii). Assume that the prior
+  density $\pi(\cdot)$ on $\theta$ converges to zero
+  at the endpoints of the interval $\Theta$ and
+  define the prior Fisher information
+  $I_0 \defeq \E_\pi[(\pi'(\theta) / \pi(\theta))^2]$.
+  Then
+  \begin{equation*}
+    n \E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0}.
+  \end{equation*}
 \end{thm}
 
-\subsubsection*{Proof}
 %We first bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
@@
 The details are in
-See Appendix~\ref{proof:thm:adpative_lower_bound}.\par
 
-Theorem~\ref{thm:adpative_lower_bound} implies that any estimator ${\theta}_n$ from any adaptive encoding scheme satisfies
-\[
-n\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{1}{4f^2(0)}+O(n^{-1}),
-\]
-and 
-\[
-\ARE({\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
-\]
-It is possible to extend Theorem~\ref{thm:adpative_lower_bound} to any other loss functions using a more subtle version of the Van Tress inequality provided in \cite{efroimovich1980information}.
-See also \cite{DBLP:journals/corr/abs-1902-08582}.
-\par
-%
-Next, we provide an adaptive encoding and estimation scheme that attains the maximal ARE of $\eta(0)\sigma^2$.
+%% Theorem~\ref{thm:adpative_lower_bound} implies that any estimator ${\theta}_n$ from any adaptive encoding scheme satisfies
+%% \begin{equation*}
+%% n\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{1}{4f^2(0)}+O(n^{-1}),
+%% \end{equation*}
+%% and 
+%% \begin{equation*}
+%% \ARE({\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
+%% \end{equation*}
+It is possible to extend Theorem~\ref{thm:adpative_lower_bound} to any other
+loss functions using a more subtle version of the Van Trees
+inequality~\cite{efroimovich1980information}; see also
+\cite{DBLP:journals/corr/abs-1902-08582}.
+
+We now turn to asymptotically optimal estimators, first
+showing how a simple stochastic gradient scheme is asymptotically
+optimal (in the fully adaptive setting), after which we show that
+a one-round adaptive scheme can also achieve this optimal efficiency.
 
 \subsection{Asymptotically optimal estimator}
-Let $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ be a strictly positive sequence. Consider the following estimator ${\theta}_n$ for $\theta$:  
+
+The starting point for our first estimator is to note that the median of a
+distribution minimizes $\E[|X - \theta|]$ over $\theta \in \R$, and
+moreover, we have the familiar result (cf.~\cite{VanDerVaart98}, Ch.~21)
+that given a sample $X_1^n \simiid P$, if $\theta = \mbox{med}(P)$ and
+$P$ has density $f$ near $\theta$, then
+\begin{equation*}
+  \sqrt{n}(\mbox{med}(X_1^n) - \theta)
+  \cd \normal\left(0, \frac{1}{4 f(\theta)^2}\right),
+\end{equation*}
+which is precisely the variance lower bound in
+Theorem~\ref{thm:adpative_lower_bound}.  Thus, it it is natural consider a
+stochastic gradient procedure for minimizing $\E[|X - \theta|]$. To that end,
+let $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ be a strictly positive
+sequence of stepsizes,
+and define the sequence
 \begin{equation}
@@
 where 
-\begin{equation}
-B_n = B_n (X_n,\theta_{n-1}) =\sgn (X_n - \theta_{n-1}).
-\end{equation}
-Define the $n$th step estimation as
-\begin{equation} \label{eq:sgd_est}
-\bar{\theta}_n =  \frac{1}{n} \sum_{i=1}^n  \theta_i. 
-\end{equation}
+\begin{equation*}
+  B_n = \sgn (X_n - \theta_{n-1}).
+\end{equation*}
+We make one of two assumptions on the stepsizes $\gamma_n$, which
+are relatively standard: we always have $\gamma_n$ non-increasing, and
+\begin{subequations}
+  For some $0 < \lambda \le 1$,
+  \begin{align}
+    \label{eqn:lazy-gamma}
+    \frac{\gamma_n - \gamma_{n+1}}{\gamma_n^2}
+    \to 0, & ~~~
+    \sum_n \frac{\gamma_n^\frac{1 + \lambda}{2}}{\sqrt{n}} < \infty
+    ~~ \mbox{or} \\
+    \gamma_n = o(n^{-2/3}),
+    & ~~~
+    \sum_n \gamma_n = \infty.
+    \label{eqn:stringent-gamma}
+  \end{align}
+\end{subequations}
 
-We have the following results:
-\begin{thm} \label{thm:sgd}
-Consider the sequence $\left\{\bar{\theta}_n \right\}_{n\in \mathbb N}$ defined by \eqref{eq:sgd_est}. 
-\begin{enumerate}
-\item[(i)] Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions1}
-\begin{cases}
-\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
-\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
-\mathrm{for~some~}0< \lambda \leq 1
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Then
-\[
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left(0,\frac{1}{\eta(0)}\right).
-\]
+Then we can adapt the results of Polyak and Juditsky~\cite{PolyakJu92}
+on the asymptotic normality of averaged stochastic gradient estimators
+to establish the following theorem.
+\begin{thm}
+  \label{thm:sgd}
+  Define the average $\bar{\theta}_n \defeq \frac{1}{n}
+  \sum_{i = 1}^n \theta_i$. Assume
+  that in a neighborhood
+  of $\theta = \mbox{med}(P)$,
+  the distribution $P$ has a Lipschitz continuous density $f$.
+  Then
+  \begin{enumerate}[(i)]
+  \item \label{item:normal-sgd}
+    Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
+    condition~\eqref{eqn:lazy-gamma}.
+    Then
+    \begin{equation*}
+      \sqrt{n}\left( \bar{\theta}_n - \theta\right)
+      \cd \normal\left(0,\frac{1}{4 f(\theta)^2}\right).
+    \end{equation*}
     %
     %
-\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with a finite Fisher information 
-\[
+  \item
+    Assume in addition that $f(x)$ is continuously differentiable with a
+    finite Fisher information
+    \begin{equation*}
       \sigma_f^2 \triangleq \ex{\frac{f'(X)}{f(X)} } 
-\]
+    \end{equation*}
     for the location in the family $\{P_\theta\}$.
@@
     %
-\item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
-\begin{equation} \label{eq:conditions2}
-\begin{cases}
-\gamma_n = o(n^{-2/3}), &  \\
-\sum_{n=1}^\infty \gamma_n = \infty.  & \\
-\end{cases}
-\end{equation}
-(e.g., $\gamma_n = n^{-\beta}$ with $\beta \in (2/3,1)$). Then
-\[
- \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{n\eta(0)} + o(n^{-1}). 
-\]
+  \item Assume the stepsizes $\gamma_n$ satisfy both
+    conditions~\eqref{eqn:lazy-gamma} and~\eqref{eqn:stringent-gamma}.
+    Then
+    \begin{equation*}
+      \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{4 n f(\theta)^2} + o(n^{-1}). 
+    \end{equation*}
   \end{enumerate}
@@
 
-\subsubsection*{Proof}
-See Appendix~\ref{proof:thm:sgd}. \par
+\noindent
+We provide the proof in Appendix~\ref{proof:sgd}.
+
+As an immediate corollary to Theorem~\ref{thm:sgd}, we obtain the following
+asymptotic optimality results of the averaged stochastic gradient
+sequence.
+%% \begin{corollary}
+
+\textbf{FILL THIS IN}
+
+%% \end{corollary}
 
@@
 In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
-\[
+\begin{equation*}
 B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
-\]
+\end{equation*}
 and deduced that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
@@
 For $i=1,\ldots,n$ set
-\[
+\begin{equation*}
 B_i = \begin{cases}
@@
 \end{cases}
-\]
+\end{equation*}
 where $n = n_1+ n_2$ and 
-\[
+\begin{equation*}
 {\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
@@
  \right).
-\] 
+\end{equation*} 
 Let 
-\[
+\begin{equation*}
 {\theta}_{n_2}  \triangleq {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
-\]
+\end{equation*}
 and assume that, as $n\to \infty$, $n_1(n) \rightarrow \infty$ and $n_2(n)/n \rightarrow 1$. Then:
@@
 For $t\in \mathbb R$, set
-\[
+\begin{equation*}
 p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
-\]
+\end{equation*}
 Since $n_2(n)/n \to 1$, if follows from the Berry Esseen theorem that there exists $C$, independent of $n$ and $t$, such that 
@@
 for any sequence of random variables $\{Y_n\}$ converging in probability to $\theta$. In particular, since
-\[
-p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0),
-\]
-by the law of large numbers, \eqref{eq:two_step_proof} holds with $Y_n = \theta_{n_1}$. Finally, we use the delta method with $g(x) = F^{-1}(x)$ to conclude
+\begin{equation*}
+p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0)
+\end{equation*}
+by the law of large numbers, \eqref{eq:two_step_proof} holds for $Y_n = \theta_{n_1}$. Finally, we use the delta method with $g(x) = F^{-1}(x)$ to conclude
 \begin{align*}

### 2019-12-11 appendices.tex
Working on proof of SGD

@@
 
-\subsection{Proof of Theorem~\ref{thm:sgd}
-\label{proof:thm:sgd}
-}
-The estimation algorithm of \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.
-The proof of Theorem~\ref{thm:sgd} relies on various results from these works.
-
-\subsubsection*{Proof of (i)}
-%Specifically, (i) in Theorem~\ref{thm:sgd} 
-Consider the following simplified version of \cite[Thm. 4]{polyak1992acceleration}:
-\begin{thm}{\cite[Thm. 4]{polyak1992acceleration}} \label{thm:polyak_juditsky}
-Let 
-\[
-X_i = \theta + Z_i,\quad i=1,\ldots,n,
-\]
-where the $Z_i$s are i.i.d. with zero means and finite variances. Define
-\begin{align}
-\begin{split}
-\theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
-\bar{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
-\end{split}
-\label{eq:Polyak_Juditsky_alg}
-\end{align}
-where in addition, assume the following: 
-\begin{enumerate}
-\item[(i)] There exits $K_1$ such that $\left| \varphi(x) \right| \leq K_1(1+|x|)$ for all $x\in \R$.
-\item[(ii)] The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies conditions \eqref{eq:conditions1}.
-\item[(iii)] The function $\psi(x) \triangleq \ex{ \varphi(x+Z_1)}$ is differentiable at zero with $\psi'(0)>0$, and satisfies $\psi(0)=0$ and $x\psi(x) >0$ for all $x\neq 0$.
-Moreover, assume that there exists $K_2$ and $0<\lambda \leq 1$ such that
-\begin{equation}
-\label{eq:Polyak_Juditsky_cond3}
-\left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
-\end{equation}
-\item[(iv)] The function 
-$\chi(x) \triangleq \ex{\varphi^2(x+Z_1)}$ is continuous at zero. 
-\end{enumerate}
-Then $\bar{\theta}_n \rightarrow \theta$ almost surely and $ \sqrt{n}({\theta}_n - \theta)$ converges in distribution to $\Ncal(0,V)$, where
-\[
-V = \frac{ \chi(0)} {\psi'^2(0)}. 
-\]
-\end{thm}
-
-Using the notation above, we set $\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$. We have that $\chi(x) = \ex{ \sgn^2(x+Z_1) }= 1$, so $\chi(0) = 1$. In addition,
-\begin{align*}
-\psi(x) & = \ex{ \sgn(x+ Z_1) }= \int_{-\infty}^\infty \sgn(x+z) f(z) dz \\
-& = \int_{-x}^\infty f(z) dz -\int_{-\infty}^{-x} f(z) dz. 
-\end{align*}
-Using the symmetry of $f(x)$ around zero, it follows that $\psi'(x) = 2f(x)$ and thus $\psi'(0) = 2f(0)$.
-It is now easy to verify that the rest of the conditions in Theorem~\ref{thm:polyak_juditsky} are fulfilled for any $\lambda > 0$.
-Since
-\[
-\frac{\chi(0)}{\psi'^2(0)} = \frac{1}{4 f^2(0)} = \frac{1}{\eta(0)},
-\]
-it follows from Theorem~\ref{thm:polyak_juditsky} that
-\[
-\sqrt{n}\left({\theta}_n-\theta \right) \overset{d}{\to} \Ncal \left(0, 1/ \eta(0)\right). 
-\]
-
-\subsubsection*{Proof of (ii)}
-We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates.
-Then
-\begin{align}
-\label{eq:sgd_part2}
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
-\end{align}
-under $\Prob_{\theta,n}$.
-In order to show \eqref{eq:sgd_part2} we use the following refinement of Theorem~\ref{thm:polyak_juditsky}, proof of which is given in Subsection~\ref{proof:thm:normal_expansion} below.
-%
-\begin{thm} \label{thm:normal_expansion}
-Set $\Delta_i = \theta_i - \theta$ and
-$\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \Delta_i$. Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{thm:polyak_juditsky}, there exists $K_1$ and $\lambda>0$ such that
-\begin{equation}
-\ex{\left| \varphi(Z_1) - \varphi(x+Z_1)  \right|} \leq K_1 |x|^{1+\lambda}
-\label{eq:PJ_additional_cond}. 
-\end{equation}
-Then:
-\begin{itemize}
-\item[(i)] \begin{equation}
-\sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1). \label{eq:normal_expansion_lem}
-\end{equation}
-where $o_{p,n}(1)$ converges in probability to $0$ as $n\to \infty$.
-\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite Fisher information for location $\sigma_f^2$, then for any converging sequence $h_n \to h$,
-\[
-\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-h}{\psi'(0)} \int_{\R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
-\]
-under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h_n/\sqrt{n}}$ with density $\prod_{i=1}^n f(x_i-h_n/\sqrt{n})$.
-\end{itemize}
-\end{thm}
-In our setting, we have
-\begin{align*}
-& %\varphi(Z_1) - \varphi(x+Z_1) = 
-\sgn(Z_1) - \sgn(x + Z_1) \\
-& = \begin{cases}
-2 & Z_1 > 0,\, x+Z_1<0, \\
--2 & Z_1 <0, \, x+Z_1>0, \\
-0 & \text{otherwise}.
-\end{cases}
-\end{align*}
-It follows that
-\begin{align*}
-\ex{ \left| \varphi(Z_1) - \varphi(x+Z_1) \right| }  \leq \Prob\left( |Z_1| < x  \right) \leq f(0) |x|, 
-\end{align*}
-and hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
-\[
-\int_{\R} \varphi(x) f'(x) dx = \int_{\R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = -2f(0) = -\psi'(0). 
-\]
-Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}. \par
-
-Under the assumption that $f(x)$ is continuously differentiable with a finite Fisher information for location, the model $\{Z_n+ \theta\}_{n \in \N}$ is differentiable in quadratic mean \cite[Exm.
-7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
-\[
-\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
-\]
-where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$.
-The proof is concluded since any regular estimator in LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}.
-
-\subsubsection*{Proof of (iii)}
-%In order to prove part (ii) of Theorem~\ref{thm:sgd} 
-Consider the following result from \cite{polyak1990new}:
-\begin{thm}{\cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
-Let
-\begin{align} \label{eq:polyak_new_measurements}
-\begin{cases}
-U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = g'(U_{n-1})+Z_n \\
-\bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
-\end{cases}
-\end{align}
-Assume that the function $g(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative.
-In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \R$.
-Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution with a density for which the Fisher information exits.
-Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{thm:polyak_juditsky}-(iii) and satisfy the conditions there.
-Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$,
-and there exits $K_3$ such that 
-\[
-\ex{  | \varphi(x+Z_1) |^4 } \leq K_3(1+|x|^4). 
-\]
-Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
-\[
-V_n \triangleq \ex{ \left(\bar{U}_n-x^\star \right)^2 } = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
-\]
-\end{thm}
-
-We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$. From \eqref{eq:polyak_new_measurements} we have
-\begin{align*} 
-U_n & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
-& = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
-\end{align*}
-so the estimator $\bar{U}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
-\[
-\ex{ | \varphi(x+Z_1) |^4 } = 1 \leq K_3(1+|x|^4)
-\]
-for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
-the conditions in Theorem~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
-In particular, $\psi'(0) = (2f(0))^{-2}$.
-Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$.
-Theorem~\ref{thm:polyak_new} implies that for any $\theta \in \R$,
-\[
-V_n = \ex{ \left({\theta}_n-\theta \right)^2 } = \frac{1}{4n f^2(0)} + o(n^{-1}).
-\]
-
 \subsection{Proof of Theorem~\ref{thm:normal_expansion}

### 2019-12-11 problem-formulation.tex
Working on proof of SGD

@@
 property.  Specifically, we require the following.
-\begin{assumption} \label{assump:failure_rate}
-  The origin $x = 0$ uniquely maximizes $\eta(x)$, and $\eta(x)$ is
-  non-increasing in $|x|$.
+\begin{assumption}
+  \label{assump:failure_rate}
+  The density $f$ is log-concave and symmetric.  Additionally, the origin $x
+  = 0$ uniquely maximizes $\eta(x)$, and $\eta(x)$ is non-increasing in
+  $|x|$.
 \end{assumption}
@@
 the normal and Laplace distributions). Symmetric log-concave distributions
-that failing Assumption~\ref{assump:failure_rate} include the uniform
+failing Assumption~\ref{assump:failure_rate} include the uniform
 distribution and the generalized normal distribution with shape parameter
-greater than $2$. (See Appendix~\ref{sec:uniform-weirdos} for
-a brief discussion on the uniform distribution, which illustrates
-why some restriction of the class of distributions is necessary to
-develop our results; in brief, even one-step adaptive estimators
-with a single bit can achieve rates faster than the paramateric
-$\sqrt{n}$ convergence for location estimation in the uniform distribution.)
+greater than $2$. Some restriction on the class of distributions is
+necessary to develop our results; indeed, in
+Appendix~\ref{sec:uniform-weirdos} we provide a brief discussion on the
+uniform distribution, where a one-step adaptive estimator with single bit
+observations can achieve convergence rates faster than the familiar
+$\sqrt{n}$ paramateric rate.
 

### 2019-12-11 proof-sgd.tex
Working on proof of SGD

\subsection{Proof of Theorem~\ref{thm:sgd}}
\label{proof:sgd}

The estimation algorithm~\eqref{eq:sgd_alg} is a special
case of the stochastic gradient procedures in the papers
\cite{PolyakJu92, polyak1990new}.
We rely on several of their results. Throughout this proof,
we assume without loss of generality that the median
$\theta = \mbox{med}(P) = 0$.

\subsubsection*{Proof of (i)}

Consider the following simplified version of
\cite[Thm. 4]{polyak1992acceleration}:
\begin{corollary}{\cite[Thms. 3 \& 4]{PolyakJu92}}
  \label{corollary:polyak-juditsky}
  Let $\varphi : \R \to \R$ and $Z_i$ be i.i.d.\ random
  variables, and
  \[
  X_i = \theta + Z_i.
  \]
  Define
  \begin{align}
    \begin{split}
      \theta_i & = \theta_{i-1} + \gamma_i \varphi(X_i - \theta_{i-1}), \\
      \bar{\theta}_n & = \frac{1}{n} \sum_{i=0}^{n-1} \theta_i, 
    \end{split}
    \label{eq:Polyak_Juditsky_alg}
  \end{align}
  where in addition,
  \begin{enumerate}[(i)]
  \item There exists $K_1$ such that $\left| \varphi(x) \right| \leq
    K_1(1+|x|)$ for all $x\in \R$.
  \item The sequence $\left\{ \gamma_i \right\}_{i=1}^\infty$ satisfies
    condition~\eqref{eqn:lazy-gamma}.
  \item The function $\psi(x) \triangleq \ex{ \varphi(x+Z_1)}$
    satisfies $\psi(0) = 0$ and
    $x\psi(x) > 0$ for $x\neq 0$.  Moreover, $\psi$ is differentiable
    at 0 with $\psi'(0) > 0$ and there exists
    $K_2$ and $0 < \lambda \leq 1$ such that
    \begin{equation}
      \label{eq:Polyak_Juditsky_cond3}
      \left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
    \end{equation}
  \item The function 
    $\chi(x) \triangleq \ex{\varphi^2(x+Z_1)}$ is continuous at zero. 
  \end{enumerate}
  Then $\bar{\theta}_n \cas \theta$ and $ \sqrt{n}({\theta}_n - \theta)
  \cd \normal(0,V)$ for
  $V = \frac{ \chi(0)} {\psi'(0)^2}$.
\end{corollary}

Using the notation in Corollary~\ref{corollary:polyak-juditsky}, we set
$\varphi(x) = \sgn(x)$ and $Z_i = X_i - \theta$, where $\theta =
\mbox{med}(P)$. Without loss of generality and for notational convenience,
we assume for the remainder of this derivation that $\theta = 0$.
As a consequence, we have $\mbox{med}(Z) = 0$,
and $\chi(x) = \ex{ \sgn^2(x+Z_1) }= 1$, so
$\chi(0) = 1$. In addition,
\begin{align*}
  \psi(x) & = \ex{ \sgn(x+ Z_1) } =
  P(Z \ge -x) - P(Z < -x) = 1 - 2 P(Z \le -x).
  %%   \int_{-\infty}^\infty \sgn(x+z) f(z) dz \\
  %% & = \int_{-x}^\infty f(z) dz -\int_{-\infty}^{-x} f(z) dz. 
\end{align*}
Using that $P$ has a density $f$ near its median, it follows that $\psi'(x)
= 2f(-x)$ and thus $\psi'(0) = 2f(0) > 0$.  We may now verify that the
conditions in Corollary~\ref{corollary:polyak-juditsky} hold for $\lambda =
1$. Condition~(i) is obvious, and the convexity of $|\cdot|$ gives most of
condition~(iii) excepting inequality~\eqref{eq:Polyak_Juditsky_cond3}. For
that, note that as $f$ is Lipschitz near 0 with constant $\lip_0(f)$, we
have for small $x$ that
\begin{equation*}
  \psi(x) = 2 \int_0^x f(-t) dt
  = 2 \int_0^x \left[f(0) \pm \lip_0(f) t \right] dt
  = 2 f(0) x \pm \frac{\lip_0(f)}{2} x^2
  = \psi'(0) x \pm \frac{\lip_0(f)}{2} x^2,
\end{equation*}
so that condition~(iii) holds.
As evidently $\chi(0) / \psi'(0)^2 = \frac{1}{4 f(0)^2}$,
Corollary~\ref{corollary:polyak-juditsky} gives
Theorem~\ref{thm:sgd}\eqref{item:normal-sgd}.

\subsubsection*{Proof of (ii)}
We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates. Then 
\begin{align}
\label{eq:sgd_part2}
\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
\end{align}
under $\Prob_{\theta,n}$. In order to show \eqref{eq:sgd_part2} we use the following refinement of Theorem~\ref{corollary:polyak-juditsky}, proof of which is given in Subsection~\ref{proof:thm:normal_expansion} below.
%
\begin{thm} \label{thm:normal_expansion}
Set $\Delta_i = \theta_i - \theta$ and
$\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \Delta_i$. Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{corollary:polyak-juditsky}, there exists $K_1$ and $\lambda>0$ such that
\begin{equation}
\ex{\left| \varphi(Z_1) - \varphi(x+Z_1)  \right|} \leq K_1 |x|^{1+\lambda}
\label{eq:PJ_additional_cond}. 
\end{equation}
Then:
\begin{itemize}
\item[(i)] \begin{equation}
\sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1). \label{eq:normal_expansion_lem}
\end{equation}
where $o_{p,n}(1)$ converges in probability to $0$ as $n\to \infty$.
\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite Fisher information for location $\sigma_f^2$, then for any converging sequence $h_n \to h$,
\[
\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-h}{\psi'(0)} \int_{\R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
\]
under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h_n/\sqrt{n}}$ with density $\prod_{i=1}^n f(x_i-h_n/\sqrt{n})$.
\end{itemize}
\end{thm}
In our setting, we have
\begin{align*}
& %\varphi(Z_1) - \varphi(x+Z_1) = 
\sgn(Z_1) - \sgn(x + Z_1) \\
& = \begin{cases}
2 & Z_1 > 0,\, x+Z_1<0, \\
-2 & Z_1 <0, \, x+Z_1>0, \\
0 & \text{otherwise}.
\end{cases}
\end{align*}
It follows that
\begin{align*}
\ex{ \left| \varphi(Z_1) - \varphi(x+Z_1) \right| }  \leq \Prob\left( |Z_1| < x  \right) \leq f(0) |x|, 
\end{align*}
and hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
\[
\int_{\R} \varphi(x) f'(x) dx = \int_{\R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = -2f(0) = -\psi'(0). 
\]
Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}. \par

Under the assumption that $f(x)$ is continuously differentiable with a finite Fisher information for location, the model $\{Z_n+ \theta\}_{n \in \N}$ is differentiable in quadratic mean \cite[Exm. 7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
\[
\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
\]
where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$. The proof is concluded since any regular estimator in LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}.

\subsubsection*{Proof of (iii)}
%In order to prove part (ii) of Theorem~\ref{thm:sgd} 
Consider the following result from \cite{polyak1990new}:
\begin{thm}{\cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
Let
\begin{align} \label{eq:polyak_new_measurements}
\begin{cases}
U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = g'(U_{n-1})+Z_n \\
\bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
\end{cases}
\end{align}
Assume that the function $g(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative. In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \R$. Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution with a density for which the Fisher information exits. Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{corollary:polyak-juditsky}-(iii) and satisfy the conditions there. Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$, 
and there exits $K_3$ such that 
\[
\ex{  | \varphi(x+Z_1) |^4 } \leq K_3(1+|x|^4). 
\]
Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
\[
V_n \triangleq \ex{ \left(\bar{U}_n-x^\star \right)^2 } = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
\]
\end{thm}

We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$. From \eqref{eq:polyak_new_measurements} we have
\begin{align*} 
U_n & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
& = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
\end{align*}
so the estimator $\bar{U}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
\[
\ex{ | \varphi(x+Z_1) |^4 } = 1 \leq K_3(1+|x|^4)
\]
for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
the conditions in Theorem~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof. In particular, $\psi'(0) = (2f(0))^{-2}$. Since $f(x)$ satisfies the conditions above with $x^\star = \theta$ and $g''(x) = 1$. Theorem~\ref{thm:polyak_new} implies that for any $\theta \in \R$, 
\[
V_n = \ex{ \left({\theta}_n-\theta \right)^2 } = \frac{1}{4n f^2(0)} + o(n^{-1}).
\]

### 2019-12-12 adaptive-estimation.tex
Working on the regularity stupidity

@@
     %
-  \item
+  \item \label{item:sgd-regular}
     Assume in addition that $f(x)$ is continuously differentiable with a
@@
 
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=2cm,auto]
-  \node at (0,0) (source) {$X_1$} ;
-  \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
-\draw[->,line width = 2pt] (source) -- (enc1);
+%% \begin{figure}
+%% \begin{center}
+%% \begin{tikzpicture}[node distance=2cm,auto]
+%%   \node at (0,0) (source) {$X_1$} ;
+%%   \node[int1, right of = source, node distance = 1.2cm] (enc1) {$\enc$};  
+%% \draw[->,line width = 2pt] (source) -- (enc1);
 
-% \node[below of = source, node distance = 1cm] (source2) {$X_2$};
-%\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};  
-%\draw[->,line width = 2pt] (source2) -- (enc2);
+%% % \node[below of = source, node distance = 1cm] (source2) {$X_2$};
+%% %\node[int1, right of = source2, node distance = 1.2cm] (enc2) {Enc};  
+%% %\draw[->,line width = 2pt] (source2) -- (enc2);
 
-\node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
-\node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};
+%% \node[below of = source, node distance = 1.7cm] (source3) {$X_{n_1}$};
+%% \node[int1, right of = source3, node distance = 1.2cm] (enc3) {$\enc$};
 
-\draw[->,line width = 2pt] (source3) -- (enc3);
+%% \draw[->,line width = 2pt] (source3) -- (enc3);
 
-\node[below of = source, node distance = 0.5cm] {$\vdots$};
+%% \node[below of = source, node distance = 0.5cm] {$\vdots$};
 
-\node[int1, right of = enc3, node distance = 2.1cm ] (est) {$\est_1$};
+%% \node[int1, right of = enc3, node distance = 2.1cm ] (est) {$\est_1$};
 
-\draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
+%% \draw[->,line width = 2pt] (enc1) -| node[above, xshift = -1cm] (mes1) {$B_1$} (est);
 
-%\draw[->,line width = 2pt] (enc2) -| node[above, xshift = -1cm] (mes2) {$B_2$} (est);
+%% %\draw[->,line width = 2pt] (enc2) -| node[above, xshift = -1cm] (mes2) {$B_2$} (est);
 
-\draw[->,line width = 2pt] (enc3) -- node[above, xshift = 0cm]  {$B_{n_1}$} (est);
+%% \draw[->,line width = 2pt] (enc3) -- node[above, xshift = 0cm]  {$B_{n_1}$} (est);
 
-\node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
-\node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {$\enc$};  
-\draw[->,line width = 2pt] (sourceB) -- (enc1B);
+%% \node[below right = 0.75 and 1.5 of source3] (sourceB) {$X_{n_1 +1}$} ;
+%% \node[int1, right of = sourceB, node distance = 1.7cm] (enc1B) {$\enc$};  
+%% \draw[->,line width = 2pt] (sourceB) -- (enc1B);
 
-\node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
-\node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {$\enc$};  
-\draw[->,line width = 2pt] (source3B) -- (enc3B); 
-\node[below of = sourceB, node distance = 0.4cm] {$\vdots$};
+%% \node[below of = sourceB, node distance = 1.7cm] (source3B) {$X_n$};
+%% \node[int1, right of = source3B, node distance = 1.7cm] (enc3B) {$\enc$};  
+%% \draw[->,line width = 2pt] (source3B) -- (enc3B); 
+%% \node[below of = sourceB, node distance = 0.4cm] {$\vdots$};
 
-\node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {$\est_2$};
+%% \node[int1, right of = enc3B, node distance = 2.1cm ] (estB) {$\est_2$};
 
-\draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.5cm] {$B_{n_1+1}$} (estB);
-\draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);
+%% \draw[->,line width = 2pt] (enc1B) -| node[above, xshift = -0.5cm] {$B_{n_1+1}$} (estB);
+%% \draw[->,line width = 2pt] (enc3B) -- node[above] {$B_n$} (estB);
 
-\draw[->,line width = 1pt] (est.east) node[above, xshift  =0.5cm] {${\theta}_{n_1}$} -| (enc1B.north);
+%% \draw[->,line width = 1pt] (est.east) node[above, xshift  =0.5cm] {${\theta}_{n_1}$} -| (enc1B.north);
 
-%\draw[->,line width = 1pt] (enc1B) -- (enc3B);
+%% %\draw[->,line width = 1pt] (enc1B) -- (enc3B);
 
-\draw[->,line width = 0.5pt] (est.east) -| +(1.3,-0.5) -- +(1.3,-2.5) -| (enc3B.north);
+%% \draw[->,line width = 0.5pt] (est.east) -| +(1.3,-0.5) -- +(1.3,-2.5) -| (enc3B.north);
 
-%\draw[->,line width = 1pt] (enc1B)  -- node[right] {${\theta}_{n_1}$} (enc3B);
+%% %\draw[->,line width = 1pt] (enc1B)  -- node[right] {${\theta}_{n_1}$} (enc3B);
 
-\draw[->,line width = 0.5pt] (estB) -- +(0.8,0) node[right] {${\theta}_n$};
-\node[below of = enc1B, node distance = 0.5cm] {$\vdots$};
+%% \draw[->,line width = 0.5pt] (estB) -- +(0.8,0) node[right] {${\theta}_n$};
+%% \node[below of = enc1B, node distance = 0.5cm] {$\vdots$};
 
-\end{tikzpicture}
-\end{center}
-\caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
-\label{fig:one_round}
-}
-\end{figure}
+%% \end{tikzpicture}
+%% \end{center}
+%% \caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
+%% \label{fig:one_round}
+%% }
+%% \end{figure}
 
@@
 
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=10cm, height=6cm,
-xmin = 0, xmax=800, 
-restrict y to domain = 0:3,
-ymin = 0,
-ymax = 3.4,
-samples=10, 
-xlabel= $n$,
-ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
-%xtick={-3,-2,-1,0,1,2,3},
-%xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,1,1.57},
-yticklabels={0,1,$\pi/2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
+%% \begin{figure}
+%% \begin{center}
+%% \begin{tikzpicture}[scale = 0.6]
+%% \begin{axis}[
+%% width=10cm, height=6cm,
+%% xmin = 0, xmax=800, 
+%% restrict y to domain = 0:3,
+%% ymin = 0,
+%% ymax = 3.4,
+%% samples=10, 
+%% xlabel= $n$,
+%% ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
+%% %xtick={-3,-2,-1,0,1,2,3},
+%% %xticklabels={-3,-2,-1,0,1,2,3},
+%% ytick={0,1,1.57},
+%% yticklabels={0,1,$\pi/2$},
+%% line width=1.0pt,
+%% mark size=1.5pt,
+%% ymajorgrids,
+%% xmajorgrids,
+%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+%% ]
 
-\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{asymptotically optimal};
+%% \addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
+%% \addlegendentry{asymptotically optimal};
 
-%\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
+%% %\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
 
-\addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{single interaction};
+%% \addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
+%% \addlegendentry{single interaction};
 
-\end{axis}
-\end{tikzpicture}
-%\begin{tikzpicture}
-%\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
-%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left({\theta}_n - \theta \right)^2$};
-%\node[scale = 0.7] at (0,-2.4) {$n$};
-%\end{tikzpicture}
-\caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.
+%% \end{axis}
+%% \end{tikzpicture}
+%% %\begin{tikzpicture}
+%% %\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
+%% %\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left({\theta}_n - \theta \right)^2$};
+%% %\node[scale = 0.7] at (0,-2.4) {$n$};
+%% %\end{tikzpicture}
+%% \caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.
 In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$.
 The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage.
-\label{fig:adaptive_error}  }
-\end{center}
-\end{figure}
+%% \label{fig:adaptive_error}  }
+%% \end{center}
+%% \end{figure}

### 2019-12-12 appendices.tex
Working on the regularity stupidity

@@
 
-\subsection{Proof of Theorem~\ref{thm:normal_expansion}
-\label{proof:thm:normal_expansion}
-}
-\subsubsection*{Proof of (i)}
-The proof of part (i) of Theorem~\ref{thm:normal_expansion} requires the following two additional results from \cite{polyak1992acceleration}:
-\begin{lem}{\cite[Lem. 2]{polyak1992acceleration}}
-\label{lem:Polyak_expansion}
-Consider the process $\{\Delta_i^1 \}_{i=0}^\infty$ defined by
-\[
-\Delta^1_i = \Delta^1_{i-1} - \gamma_i (A \Delta_{i-1}+ \xi_i),\quad i=1,2\ldots.
-\]
-Assume that $A>0$ and condition (ii) of Theorem~\ref{thm:polyak_juditsky} holds. Then 
-\begin{equation}
-\label{eq:Polyak_expansion}
-\sqrt{n} \bar{\Delta}_n^1 = \frac{1}{\sqrt{n}}\sum_{i=0}^{n-1} \Delta_i^1 = \frac{\alpha_n \Delta_0^1}{\sqrt{n} \gamma_0}  + \frac{1}{\sqrt{n} A} \sum_{i=1}^{n-1} \xi_i + \frac{1}{\sqrt{n}}\sum_{i=1}^{n-1} w_i^n \xi_i,
-\end{equation}
-where $\alpha_n$ and $w_i^n$ are real numbers such that $|\alpha_n| \leq K$ and $|w_i^n|\leq K$ for some $K< \infty$, and 
-\[
-\lim_{n\to \infty} \frac{1}{n} \sum_{i=1}^{n-1} |w_i^n| = 0. 
-\]
-\end{lem}
-
-\begin{lem} \label{lem:PJ_converging_sum}
-Under the conditions of Theorem~\ref{thm:polyak_juditsky},
-\[
-\sum_{i=1}^\infty \frac{|\Delta_{i}|^{1+\lambda}}{\sqrt{i}} < \infty 
-\]
-almost surely. 
-\end{lem}
-Lemma~\ref{lem:PJ_converging_sum} follows from the proof of Theorem 2 in \cite{polyak1992acceleration}.
-
-We separate the proof of part (i) into two steps.
-\subsubsection*{Step I}
-The expansion \eqref{eq:normal_expansion_lem} holds for the process  $\{\bar{\Delta}^1_i\}_{i=1}^\infty$ defined as follows:
-\begin{align} \label{eq:Polyak_expansion_lem1_alg}
-& \Delta_i^1  = \Delta_{i-1}^1 - \gamma_i \psi'(0) \Delta_{i-1}^1 - \gamma_i \varphi(Z_i), \qquad
- \delta_0^1 = \Delta_0\\
-& \bar{\Delta}^1_i = \frac{1}{n}\sum_{i=0}^{n-1} \Delta^1_i.
-\end{align}
-
-In order to prove this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$.
-The first expression on the RHS of \eqref{eq:Polyak_expansion} goes to zero in variance.
-In addition,
-\begin{align*}
-& \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }  = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
-& = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0. 
-\end{align*}
-We obtain
-\begin{equation}
-\sqrt{n} \bar{\Delta}^1_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1), \label{eq:Polyak_expansion_aux_process}
-\end{equation}
-
-\subsubsection*{Step II} $\bar{\Delta}_n$ and $\bar{\Delta}^1_n$ are asymptotically equivalent. \\
-
-From \eqref{eq:Polyak_Juditsky_alg} and \eqref{eq:Polyak_expansion_lem1_alg}, the difference $\delta_i = \Delta_i - \Delta_i^1$ satisfies the recursion
-\[
-\delta_i = \delta_{i-1} - \gamma_i \psi'(0) \delta_{i-1} + \gamma_i \left( \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i) \right),
-\]
-where $\delta_0 = 0$. Use Lemma~\ref{lem:Polyak_expansion} with $\xi_i =  \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i)$ to obtain
-\begin{align}
-& \sqrt{n}\bar{\delta}_n = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \xi_i  \\
-& = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \label{eq:PJ_proof1} \\
-& + 
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi(\Delta_{i-1})  + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i)
-\right) \label{eq:PJ_proof2}
-\end{align}
-For the term \eqref{eq:PJ_proof1} and using \eqref{eq:Polyak_Juditsky_cond3}, there exists $K_1$ and $K_2$ such that 
-\begin{align*}
-& \eqref{eq:PJ_proof1}
-\leq K_1 \sum_{i=1}^\infty \frac{1}{\sqrt{i}} \left| \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \right| \\
-& \leq K_2 \sum_{i=1}^\infty \frac{ |\Delta_i|^{1+\lambda}}{\sqrt{i}}. 
-\end{align*}
-
-Lemma~\ref{lem:PJ_converging_sum} shows that 
-\begin{align}
-\sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}}  < \infty \label{eq:PJ_converging_sum},
-\end{align}
-hence the Kronecker lemma implies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \to 0.
-\]
-For the term \eqref{eq:PJ_proof2}, set 
-\[
-\epsilon_i \triangleq \psi(\Delta_{i-1}) + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i).
-\]
-For $a>0$ and $n \in \N$, define the event
-\[
-A_{n,a} \triangleq \left\{ \sum_{i=1}^{n-1} \frac{|\epsilon_i|}{\sqrt{i}}  \geq a  \right\}. 
-\]
-By Markov's inequality, we have
-\begin{align}
-\ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } \leq \frac{1}{a} \sum_{i=1}^{n-1} \frac{ \ex{|\epsilon_i| \Delta_{i-1} \mid }}{\sqrt{i}}. \label{eq:PJ_proof_3}
-\end{align}
-Using \eqref{eq:Polyak_Juditsky_cond3} and \eqref{eq:PJ_additional_cond}, there exists $K'$ and $\lambda'>0$ such that
-\begin{align*}
-& \ex{ |\epsilon_i| | \Delta_{i-1}}  \leq |\psi(\Delta_{i-1})| + \left| \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i) \right|  \\
-& \leq K' |\Delta_{i-1}|^{1+\lambda}. 
-\end{align*}
-Plugging this bound in \eqref{eq:PJ_proof_3} and using Lemma~\ref{lem:PJ_converging_sum}, we obtain 
-\[
-\Prob(A_{n,a}) = \ex{ \ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } } \leq  \frac{K''}{a}
-\]
-for some constant $K''$. It follows that for any $\epsilon$, we may choose $a$ large enough such that 
-\[
-\sup_{n} \Prob(A_{n,a}) < \epsilon.
-\]
-This implies that for any $\epsilon>0$,
-\[
-\Prob \left( \sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty \right) \geq 1-\epsilon,
-\]
-and hence 
-\[
-\sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty
-\]
-almost surely. The Kronecker lemma now implies 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left|\epsilon_i\right| \to 0,
-\]
-hence the term \eqref{eq:PJ_proof2} satisfies
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right) \epsilon_i \leq \frac{K'''}{\sqrt{n}} \sum_{i=1}^{n-1} |\epsilon_i| \to 0. 
-\]
-This conclude the proof of part (i).
-
-\subsubsection*{Part (ii)}
-Use \eqref{eq:normal_expansion_lem} to write
-\[
-\sqrt{n} \bar{\Delta}_n = G_n + o_{p,n}(1),
-\]
-where
-\[
-G_n \triangleq -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n} \varphi(Z_i). 
-\]
-From \cite[Exm.
-7.8]{van2000asymptotic}, the location model $f(x-\theta)$ with continuously differentiable $f(x)$ is differentiable in quadratic mean.
-% with the score function $-f'(x-\theta)/f(x-\theta)$.
-This fact implies the following expansion \cite[Thm. 7.2]{van2000asymptotic}:
-\begin{align}
-\label{eq:PJ_LAN}
-& \log \frac{\Prob^n_{h_n/\sqrt{n}}}{\Prob^n_0} (Z_1,\ldots,Z_n) =  \log \prod_{i=1}^{n} \frac{f(Z_i-h_n/\sqrt{n})}  {f(X_i-\theta)} = h J_n - \frac{1}{2}h^2 I_{\theta} + o_{p,n}(1),
-\end{align}
-for any converging sequence $h_n \to h$, 
-where 
-\[
-J_n \triangleq -\frac{1}{\sqrt{n}} \sum_{i=1}^n \frac{f'(Z_i)}{f(Z_i)} .
-\]
-We have
-\begin{align*}
-& \ex{ G_n J_n} = \frac{1}{\psi'(0)}\frac{1}{n} \sum_{i=1}^n \ex{ \varphi(Z_i) \frac{f'(Z_i)}{f(Z_i)} }  \\
-& = \frac{1}{ \psi'(0)} \ex{ \varphi(Z_1) \frac{f'(Z_1)}{f(Z_1)}} =  \frac{1}{ \psi'(0)} \int_{\R} \varphi(x) f'(x) dx , 
-\end{align*}
-Since both $\sqrt{n}G_n$ and $\sqrt{n}J_n$ are the sum of $n$ i.i.d. random variables with zero mean and finite variance, we obtain, from the central limit theorem and Slutsky's theorem, that
-\[
-\left(\sqrt{n} \bar{\Delta}_n, \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} \right) \overset{d}{\to} \Ncal \left( \left(0,-\frac{h^2}{2} I_\theta \right),  \begin{pmatrix}
-\frac{\chi(0)}{\psi'^2(0)} & \frac{-h}{ \psi'(0)} \int_{\R} \varphi(x) f'(x) dx \\
-\frac{-h}{ \psi'(0)} \int_{\R} \varphi(x) f'(x) dx & h^2 I_\theta 
-\end{pmatrix}  \right)
-\]
-Le Cam's third lemma \cite[Exm. 6.7]{van2000asymptotic} implies that under $\Prob^n_{h/\sqrt{n}}$, 
-\[
-\sqrt{n}\bar{\Delta}_n \overset{d}{\to} \Ncal\left(\frac{-h}{ \psi'(0)} \int_{\R} \varphi(x) f'(x) dx,  \frac{\chi(0)}{\psi'^2(0)} \right).
-\]
-\QEDA
-
 \subsection{Proof of Theorem~\ref{thm:LAN1}

### 2019-12-12 proof-sgd.tex
Working on the regularity stupidity

@@
-\subsection{Proof of Theorem~\ref{thm:sgd}}
+\section{Proof of Theorem~\ref{thm:sgd}}
 \label{proof:sgd}
+
+\providecommand{\score}{\dot{\ell}}
 
@@
 
-\subsubsection*{Proof of (i)}
+\subsection{Proof of Theorem~\ref{thm:sgd}\eqref{item:normal-sgd}}
 
@@
   variables, and
-  \[
+  \begin{equation*}
   X_i = \theta + Z_i.
-  \]
+  \end{equation*}
   Define
@@
     condition~\eqref{eqn:lazy-gamma}.
-  \item The function $\psi(x) \triangleq \ex{ \varphi(x+Z_1)}$
+  \item \label{item:zero-gradient}
+    The function $\psi(x) \triangleq \ex{ \varphi(x+Z_1)}$
     satisfies $\psi(0) = 0$ and
@@
     \begin{equation}
-      \label{eq:Polyak_Juditsky_cond3}
+      \label{eqn:local-hessian-psi}
         \left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
@@
 1$. Condition~(i) is obvious, and the convexity of $|\cdot|$ gives most of
-condition~(iii) excepting inequality~\eqref{eq:Polyak_Juditsky_cond3}. For
+condition~(iii) excepting inequality~\eqref{eqn:local-hessian-psi}. For
 that, note that as $f$ is Lipschitz near 0 with constant $\lip_0(f)$, we
@@
 
-\subsubsection*{Proof of (ii)}
-We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates.
+\subsection{Proof of Theorem~\ref{thm:sgd}\eqref{item:sgd-regular}}
+
+This proof requires somewhat more techinicality than the first part of the
+theorem, including a brief detour into local asymptotic normality theory,
+regular estimators, and quadratic-mean
+differentiability~\cite[cf.]{VanDerVaart98}.
+We begin by recalling some of these concepts.
+\begin{definition}
+  A sequence of estimators $T_n$ for a parameter $\theta$ in the parametric
+  family $\{P_\theta\}_{\theta \in \Theta}$ is \emph{regular at $\theta$} if
+  there exists a distribution $Q$ such that for all bounded sequence
+  $h_n$,
+  \begin{equation*}
+    \sqrt{n}(T_n - (\theta + h_n / \sqrt{n}))
+    \mathop{\cd}_{P_{\theta + h_n/\sqrt{n}}}
+    Q.
+  \end{equation*}
+\end{definition}
+\begin{definition}
+  Let $\{P_\theta\}_{\theta \in \Theta}$ have densities $p_\theta$
+  with respect to a base measure $\mu$. The family
+  is \emph{quadratic mean differentiable} (QMD) at
+  $\theta$ with score $\score_\theta$ if
+  \begin{equation}
+    \label{eqn:qmd}
+    \int \left(\sqrt{p_{\theta + h}} - \sqrt{p_\theta}
+    - \half h^\top \score_\theta\sqrt{p_\theta} \right)^2 d\mu
+    = o(\norm{h}^2)
+  \end{equation}
+  as $h \to 0$.
+\end{definition}
+\begin{definition}
+  A family of distributions $\{P_\theta\}_{\theta \in \Theta}$ is
+  \emph{locally asymptotically normal with information matrix $I_\theta$} at
+  $\theta$ if there exists a sequence of random vectors $Z_n$ such that for
+  all $h_n \to h$,
+  \begin{equation*}
+    \sum_{i = 1}^n \log \frac{dP_{\theta + h_n/\sqrt{n}}}{dP_\theta}
+    (X_1, \ldots, X_n)
+    = h^\top Z_n - \half h^\top I_\theta h + o_P(1)
+  \end{equation*}
+  where $Z_n \cd \normal(0, I_\theta)$ under $P_\theta$, where
+  $X_i \simiid P_\theta$.
+\end{definition}
+
+These three definitions are linked in our case by a few important results.
+First~\cite[Theorem 7.2]{VanDerVaart98},
+if $P_\theta$ is QMD at $\theta$, then
+it is locally asymptotically normal with
+$Z_n = \frac{1}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(X_i)$ and information
+matrix $I_\theta = \E_\theta[\score_\theta \score_\theta^\top]$. Moreover,
+in any locally asymptotically normal family at $\theta$,
+if $T_n$ is a regular estimator at $\theta$ with limiting distribution $Q$,
+then for any bounded, symmetric, quasi-convex loss $L$ and $c < \infty$,
+\begin{equation*}
+  \limsup_n \sup_{\norm{h} \le c}
+  \E_{P_{\theta + h/\sqrt{n}}}
+  \left[L(\sqrt{n}(T_n - \theta - h / \sqrt{n}))\right]
+  = \E[L(W)] ~~ \mbox{for~}W \sim Q
+\end{equation*}
+(see Beran~\cite{beran1995role}, Eq.~(4.2)).
+
+Thus, we show three results: first, that $\bar{\theta}_n$ is regular,
+second, that the family $P_\theta$ is QMD, and finally, combining the two
+results.
+
+We first show that the estimator $\bar{\theta}_n$ is regular in the
+following sense: For $\theta \in \Theta$, a sequence $h_n \to h \in \R$ and
+$n$ large enough that $\theta + h_n /\sqrt{n} \in \Theta$, let
+$P_{\theta,n}$ be a product probability measure on $\R^n$ distributed
+i.i.d.\ with density
+$f(x - \theta - h_n/\sqrt{n})$. Then
+\begin{align}
+  \label{eqn:sgd-median-regular}
+  \sqrt{n}\left( \bar{\theta}_n - \theta\right)
+  \mathop{\cd}_{\Prob_{\theta,n}}
+  \normal\left( h,\frac{1}{4 f(\theta)^2}\right),
+\end{align}
+under $\Prob_{\theta,n}$. To show the convergence~\eqref{eqn:sgd-median-regular} we
+use the following refinement of Corollary~\ref{corollary:polyak-juditsky},
+whose proof we defer to Section~\ref{proof:normal-expansion}.
+%
+\begin{corollary}
+  \label{corollary:normal-expansion}
+  Set $\Delta_i = \theta_i - \theta$ and $\bar{\Delta}_i = \frac{1}{n}
+  \sum_{i=1}^n \Delta_i$. Let the conditions of
+  Corollary~\ref{corollary:polyak-juditsky} hold, and additionally
+  assume the local smoothness condition that there exist
+  $0 < \lambda \le 1$ and $K < \infty$ such that
+  \begin{equation}
+    \label{eqn:additional-local-smooth}
+    \E[|\varphi(x + Z) - \varphi(Z)|^2]
+    \le K (|x|^\lambda + x^2).
+  \end{equation}
   Then
-\begin{align}
-\label{eq:sgd_part2}
-\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
-\end{align}
-under $\Prob_{\theta,n}$.
-In order to show \eqref{eq:sgd_part2} we use the following refinement of Theorem~\ref{corollary:polyak-juditsky}, proof of which is given in Subsection~\ref{proof:thm:normal_expansion} below.
-%
-\begin{thm} \label{thm:normal_expansion}
-Set $\Delta_i = \theta_i - \theta$ and
-$\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \Delta_i$. Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{corollary:polyak-juditsky}, there exists $K_1$ and $\lambda>0$ such that
+  \begin{enumerate}[(i)]
+  \item \label{item:regularity}
+    The sequence $\Delta_i$ is regular, that is,
     \begin{equation}
-\ex{\left| \varphi(Z_1) - \varphi(x+Z_1)  \right|} \leq K_1 |x|^{1+\lambda}
-\label{eq:PJ_additional_cond}. 
+      \sqrt{n} \bar{\Delta}_n
+      = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)
+      + o_{P,n}(1).
+      \label{eq:normal_expansion_lem}
     \end{equation}
-Then:
-\begin{itemize}
-\item[(i)] \begin{equation}
-\sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1). \label{eq:normal_expansion_lem}
-\end{equation}
-where $o_{p,n}(1)$ converges in probability to $0$ as $n\to \infty$.
-\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite Fisher information for location $\sigma_f^2$, then for any converging sequence $h_n \to h$,
-\[
-\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-h}{\psi'(0)} \int_{\R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
-\]
-under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h_n/\sqrt{n}}$ with density $\prod_{i=1}^n f(x_i-h_n/\sqrt{n})$.
-\end{itemize}
-\end{thm}
-In our setting, we have
+  \item \label{item:apply-le-cam} Let $Z_i$ as in
+    Corollary~\ref{corollary:polyak-juditsky} have absolutely continuous
+    density $p$ with median $0$, define $\score_h(z) = \frac{p'(z - h)}{p(z
+      - h)}$, and assume that $I_h \defeq \E_\theta[\score_h(Z)^2]$ is
+    continuous in $h$ near 0.  Then for any converging sequence $h_n \to h$,
+    \begin{equation*}
+      \sqrt{n} \bar{\Delta}_n
+      \mathop{\cd}_{P_{\theta + h_n/\sqrt{n}}^n}
+      \normal\left( \frac{-h}{\psi'(0)} \E_p[\varphi(Z) \score_0(Z)]
+      , \frac{\chi(0)}{\psi'^2(0)} \right).
+    \end{equation*}
+  \end{enumerate}
+\end{corollary}
+
+We now verify that the setting of Theorem~\ref{thm:sgd} satisfies the
+conditions of Corollary~\ref{corollary:polyak-juditsky}. First,
+we have the obvious fact that
+\begin{equation*}
+  |\sgn(z) - \sgn(x + z)|
+  \le 2 \cdot \indic{|x| \ge |z|}.
+\end{equation*}
+Recalling our w.l.o.g.\ assumption that $\theta = \mbox{med}(X) = 0$,
+for $\varphi(z) = \sgn(z)$, and $Z = X - \theta = X$ we have
 \begin{align*}
-& %\varphi(Z_1) - \varphi(x+Z_1) = 
-\sgn(Z_1) - \sgn(x + Z_1) \\
-& = \begin{cases}
-2 & Z_1 > 0,\, x+Z_1<0, \\
--2 & Z_1 <0, \, x+Z_1>0, \\
-0 & \text{otherwise}.
-\end{cases}
+  \ex{ \left| \varphi(Z) - \varphi(x + Z) \right| }
+  \leq 2 \Prob\left( |Z_1| \le |x|  \right)
+  \le 2 f(0) |x| + \lip(f) x^2
 \end{align*}
-It follows that
-\begin{align*}
-\ex{ \left| \varphi(Z_1) - \varphi(x+Z_1) \right| }  \leq \Prob\left( |Z_1| < x  \right) \leq f(0) |x|, 
-\end{align*}
-and hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
-\[
-\int_{\R} \varphi(x) f'(x) dx = \int_{\R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = -2f(0) = -\psi'(0). 
-\]
-Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}. \par
+for $x$ near 0, where $\lip(f)$ is the Lipschitz constant of $f$ near
+its median. For large $x$ we always have
+$\E[|\varphi(Z) - \varphi(x + Z)|] \le 2$, so that
+condition~\eqref{eqn:additional-local-smooth} holds.
+In addition, we have
+\begin{equation*}
+  \int_{\R} \varphi(x) f'(x ) dx
+  = \int_{\R} \sgn(x) f'(x ) dx =
+  \int_0^\infty f'(x ) dx
+  - \int_{-\infty}^0 f'(x )
+  = -2 f(0) = -\psi'(0).
+\end{equation*}
+Corollary~\ref{corollary:normal-expansion}
+now implies the convergence \eqref{eqn:sgd-median-regular}.
+
+With the convergence~\eqref{eqn:sgd-median-regular},
+the limiting efficiency estimate~\eqref{eq:attaining_LAM} is straightforward.
+Indeed, the limiting distribution~\eqref{eqn:sgd-median-regular}
+guarantees that $\bar{\theta}_n$ is a regular estimator,
 
@@
 7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
-\[
+\begin{equation*}
 \log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
-\]
+\end{equation*}
 where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$.
@@
 \end{align}
-Assume that the function $g(x)$ is twice differentiable with a strictly positive and uniformly bounded second derivative.
-In particular, $g(x)$ is convex with a unique minimizer $x^\star \in \R$.
-Moreover, assume that the noises $Z_n$ are uncorrelated and identically distributed with a distribution with a density for which the Fisher information exits.
-Let $\psi(x)$ and $\chi(x)$ be defined as in Theorem~\ref{corollary:polyak-juditsky}-(iii) and satisfy the conditions there.
-Assume in addition that $\chi(0)>0$, condition \eqref{eq:Polyak_Juditsky_cond3} with $\lambda = 1$,
-and there exits $K_3$ such that 
-\[
+Assume that the function $g(x)$ is twice differentiable with a strictly
+positive and uniformly bounded second derivative. In particular, $g(x)$ is
+convex with a unique minimizer $x^\star \in \R$. Moreover, assume that the
+noises $Z_n$ are uncorrelated and identically distributed with a
+distribution with a density for which the Fisher information exits. Let
+$\psi(x)$ and $\chi(x)$ be defined as in
+Theorem~\ref{corollary:polyak-juditsky}-(iii) and satisfy the conditions
+there. Assume in addition that $\chi(0)>0$, condition
+\eqref{eqn:local-hessian-psi} with $\lambda = 1$, and there exits $K_3$ such
+that
+\begin{equation*}
 \ex{  | \varphi(x+Z_1) |^4 } \leq K_3(1+|x|^4). 
-\]
+\end{equation*}
 Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
-\[
+\begin{equation*}
 V_n \triangleq \ex{ \left(\bar{U}_n-x^\star \right)^2 } = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
-\]
+\end{equation*}
 \end{thm}
@@
 so the estimator $\bar{U}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
-\[
+\begin{equation*}
 \ex{ | \varphi(x+Z_1) |^4 } = 1 \leq K_3(1+|x|^4)
-\]
+\end{equation*}
 for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
@@
 Theorem~\ref{thm:polyak_new} implies that for any $\theta \in \R$,
-\[
+\begin{equation*}
 V_n = \ex{ \left({\theta}_n-\theta \right)^2 } = \frac{1}{4n f^2(0)} + o(n^{-1}).
-\]
+\end{equation*}
+
+\subsection{Proof of Corollary~\ref{corollary:normal-expansion}}
+\label{proof:normal-expansion}
+
+\subsubsection*{Proof of
+  Corollary~\ref{corollary:normal-expansion}\eqref{item:regularity}}
+
+The proof of part~\eqref{item:regularity} requires two additional lemmas of
+Polyak and Juditsky~\cite{PolyakJu92}.
+\begin{lem}[\cite{PolyakJu92}, Lemma 2]
+  \label{lemma:polyak-expansion}
+  Define the process $\Delta_i^1 = \Delta_{i-1}^i
+  - \gamma_i (A \Delta_{i-1} + \xi_i)$ for $i = 1, 2, \ldots$.
+  Assume that $A>0$ and the stepsizes $\gamma_i$ satisfy
+  condition~\eqref{eqn:lazy-gamma}. Then
+  for $\bar{\Delta}_n^1 = \frac{1}{n} \sum_{i = 1}^n \Delta_i^1$, we have
+  \begin{equation}
+    \label{eqn:polyak-expansion}
+    \sqrt{n} \bar{\Delta}_n^1
+    % = \frac{1}{\sqrt{n}}\sum_{i=0}^{n-1} \Delta_i^1
+    = \frac{\alpha_n \Delta_0^1}{\sqrt{n} \gamma_0}
+    + \frac{1}{\sqrt{n} A} \sum_{i=1}^{n-1} \xi_i
+    + \frac{1}{\sqrt{n}}\sum_{i=1}^{n-1} w_i^n \xi_i,
+  \end{equation}
+  where $\alpha_n$ and $w_i^n$ are real numbers such that $|\alpha_n| \leq
+  K$ and $|w_i^n|\leq K$ for some $K< \infty$, and $\lim_{n\to \infty}
+  \frac{1}{n} \sum_{i=1}^{n-1} |w_i^n| = 0$.
+\end{lem}
+
+\begin{lem}[\cite{PolyakJu92}]
+  \label{lemma:converging-power-sum}
+  Under the conditions of Corollary~\ref{corollary:normal-expansion},
+  with probability 1,
+  \begin{equation*}
+  \sum_{i=1}^\infty \frac{|\Delta_{i}|^{1+\lambda}}{\sqrt{i}} < \infty.
+  \end{equation*}
+\end{lem}
+\noindent
+Lemma~\ref{lemma:converging-power-sum} follows from the proof of Theorem 2
+in \cite[page 851]{polyak1992acceleration}.
+
+We separate the proof of part~\eqref{item:regularity} into two lemmas, which
+mirror the proofs of Polyak and Juditsky~\cite{PolyakJu92}; together they
+immediately give the result.
+
+\begin{lemma}
+  The expansion~\eqref{eq:normal_expansion_lem} holds for the process
+  $\bar{\Delta}^1_n$ defined by the iteration
+  \begin{align}
+    \label{eqn:polyak-expansion_lem1_alg}
+    & \Delta_i^1  = \Delta_{i-1}^1 - \gamma_i \psi'(0) \Delta_{i-1}^1 - \gamma_i \varphi(Z_i), \qquad
+    \Delta_0^1 = \Delta_0\\
+    & \bar{\Delta}^1_n = \frac{1}{n}\sum_{i=0}^{n-1} \Delta^1_i.
+    \nonumber
+  \end{align}
+\end{lemma}
+\begin{proof}
+  To prove this claim, use Lemma~\ref{lemma:polyak-expansion} with $A =
+  \psi'(0)$ and $\xi_i = -\varphi(Z_i)$, which by
+  condition~\eqref{item:zero-gradient} in
+  Corollary~\ref{corollary:polyak-juditsky} gives that
+  $\E[\xi_i] = 0$ and that the $\xi_i$ are independent.
+  The first term $\alpha_n \Delta_0^1 / \gamma_0 \sqrt{n} \to 0$
+  in Eq.~\eqref{eqn:polyak-expansion}. In addition,
+  by independence and that the $\xi_i$ are mean-zero, we have
+  \begin{align*}
+    \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }
+    & = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
+    & = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0
+  \end{align*}
+  by Lemma~\ref{lemma:polyak-expansion}.
+  Thus, the expansion~\eqref{eqn:polyak-expansion} in
+  Lemma~\ref{lemma:polyak-expansion} gives
+  \begin{equation*}
+    \sqrt{n} \bar{\Delta}^1_n
+    = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)}
+    \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{P,n}(1)
+  \end{equation*}
+  as desired.
+\end{proof}
+
+We then have the following asymptotic equivalence.
+\begin{lemma}
+  The sequences $\bar{\Delta}_n$ and $\bar{\Delta}^1_n$ are asymptotically
+  equivalent, meaning that
+  $\sqrt{n} (\bar{\Delta}_n - \bar{\Delta}_n^1) \cp 0$.
+\end{lemma}
+\begin{proof}
+  From the recursions~\eqref{eq:Polyak_Juditsky_alg} and
+  \eqref{eqn:polyak-expansion_lem1_alg}, the difference $\delta_i = \Delta_i
+  - \Delta_i^1$ satisfies
+  \begin{equation*}
+  \delta_i = \delta_{i-1} - \gamma_i \psi'(0) \delta_{i-1} + \gamma_i \left( \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i) \right),
+  \end{equation*}
+  where $\delta_0 = 0$. Applying Lemma~\ref{lemma:polyak-expansion} with the
+  choices $\xi_i = \psi'(0) \Delta_{i-1} + \varphi(Z_i) -
+  \varphi(\Delta_{i-1} + Z_i)$ yields
+  \begin{align}
+    \sqrt{n}\bar{\delta}_n
+    & = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1}
+    \left( \frac{1}{\psi'(0)} + w_i^n \right)  \xi_i  \nonumber \\
+    & = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1}
+    \left( \frac{1}{\psi'(0)} + w_i^n \right)
+    \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right)
+    \label{eq:PJ_proof1} \\
+    & \qquad ~ + 
+    \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}
+    + w_i^n \right)
+    \left( \psi(\Delta_{i-1})  + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i)
+    \right) \label{eq:PJ_proof2}
+  \end{align}
+  For the term \eqref{eq:PJ_proof1},
+  the assumption~\eqref{eqn:local-hessian-psi} that
+  $|\psi(x) - \psi'(0) x| = O(x^{1 + \lambda})$
+  and that $\sup_{i,n} |w_i^n| < \infty$ by Lemma~\ref{lemma:polyak-expansion}
+  give that there exists $K < \infty$ such that
+  $|\psi'(0)^{-1} + w_i^n| |\psi'(0) \Delta_{i-1} - \psi(\Delta_{i-1})|
+  \le K |\Delta_i|^{1 + \lambda}$.
+  Lemma~\ref{lemma:converging-power-sum} gives that
+  $\sum_{i = 1}^n
+  \frac{1}{\sqrt{i}} |\Delta_i|^{1 + \lambda} < \infty$,
+  and so the Kronecker lemma gives that
+  \begin{equation*}
+    \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \cas 0.
+  \end{equation*}
+
+  The term \eqref{eq:PJ_proof2} is somewhat more challenging to control.
+  We define
+  \begin{equation*}
+    \epsilon_i \triangleq \psi(\Delta_{i-1}) + \varphi(Z_i)
+    - \varphi(\Delta_{i-1}+Z_i),
+  \end{equation*}
+  and let
+  $\mc{F}_i = \sigma(Z_1, \ldots, Z_i)$ be the $\sigma$-field of the randomness
+  through time $i$. We use a square integrable martingale convergence
+  theorem~\cite[Exercise~5.3.35]{Dembo16}. Noting that
+  $\Delta_i \in \mc{F}_i$, we have
+  \begin{align}
+    \E[\epsilon_i^2 \mid \mc{F}_{i-1}]
+    & = \E[(\psi(\Delta_{i-1}) + \varphi(Z_i)
+      - \varphi(\Delta_{i-1} + Z_i))^2 \mid \mc{F}_{i-1}]
+    \nonumber \\
+    & \le 2 \psi(\Delta_{i-1})^2
+    + 2 \E[(\varphi(\Delta_{i-1} + Z_i) - \varphi(Z_i))^2 \mid \mc{F}_{i-1}]
+    \nonumber \\
+    & \le
+    K \left[|\Delta_{i-1}|^{1 + \lambda}
+      + |\Delta_{i-1}|^\lambda
+      + \Delta_{i-1}^2 \right],
+    \label{eqn:bound-psi-error-expectations}
+  \end{align}
+  where inequality~\eqref{eqn:bound-psi-error-expectations} follows by the
+  conditions~\eqref{eqn:local-hessian-psi}
+  and~\eqref{eqn:additional-local-smooth}, and $\E[\varepsilon_i \mid
+    \mc{F}_{i-1}] = 0$ for all $i$ by definition of $\psi(x) = \E[\varphi(x
+    + Z)]$ and that $\psi(0) = 0$.  We now control the expectations of these
+  quantities. For $R < \infty$, define the stopping time $\tau_R \defeq \inf
+  \{i : |\Delta_i| > R\}$, which satisfies $\{\tau_R \le i\} \in \mc{F}_i$
+  for each $i$.  Then using~\cite[Eq.~(A14)]{PolyakJu92}, we have
+  \begin{equation*}
+    \E[\Delta_i^2 \indic{\tau_R > i}] \le K \gamma_i,
+  \end{equation*}
+  and so inequality~\eqref{eqn:bound-psi-error-expectations} gives that
+  \begin{equation*}
+    \E\bigg[\sum_{i = 1}^\infty \frac{1}{i}
+      |\varepsilon_i|^2 \indic{\tau_R > i} \bigg]
+    \le K \sum_{i = 1}^\infty \frac{\gamma_i^\lambda}{i}
+    < \infty
+    ~~ \mbox{so} ~~
+    \sum_{i = 1}^\infty \frac{1}{i}
+    \varepsilon_i^2 \indic{\tau_R > i} < \infty
+    ~ \mbox{a.s.}
+  \end{equation*}
+  by Condition~\eqref{eqn:lazy-gamma}.
+  As with probability 1 there exists some (random) $R < \infty$ such that
+  $\tau_R = \infty$, we obtain that 
+  \begin{equation*}
+    \sum_{i = 1}^\infty \frac{1}{i}
+    \varepsilon_i^2  < \infty
+    ~ \mbox{a.s.}
+  \end{equation*}
+  Applying the square integrable martingale convergence
+  theorem of \cite[Ex.~5.3.35]{Dembo16}, we have
+  \begin{equation*}
+    \frac{1}{\sqrt{n}} \sum_{i = 1}^n
+    \left(\frac{1}{\psi'(0)} + w_i^n\right) \epsilon_i \cas 0,
+  \end{equation*}
+  so that both equations~\eqref{eq:PJ_proof1} and~\eqref{eq:PJ_proof2}
+  converge almost surely to 0.
+\end{proof}
+
+\subsubsection*{Proof of
+  Corollary~\ref{corollary:normal-expansion}\eqref{item:apply-le-cam}}
+
+This is essentially an immediate consequence of Le Cam's third
+lemma~\cite[Example 6.7]{VanDerVaart98}.
+We recall~\cite[Thm.~7.2]{VanDerVaart98} that if
+a family $\{P_\theta\}_{\theta \in \Theta}$ is quadratic mean differentiable
+at $\theta$ with score $\score_\theta$, then for any sequence
+$h_n \to h$, if $Z_i \simiid P_\theta$ then
+\begin{equation}
+  \label{eqn:lan-from-qmd}
+  \log \frac{dP_{\theta + h/\sqrt{n}}^n}{dP_\theta} (Z_1, \ldots, Z_n)
+  = \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(Z_i)
+  - \half h^2 I_\theta
+  + o_{P_\theta,n}(1)
+\end{equation}
+where $I_\theta = \E_{P_\theta}[\score_\theta^2]$ is the Fisher information,
+which necessarily exists.
+
+We thus show that under the conditions we have assumed,
+we have quadratic mean differentiability.
+\begin{lemma}[Extension of \cite{VanDerVaart98}, Lemma 7.6]
+  \label{lemma:qmd}
+  Let $p_\theta$ be a density with respect to $\mu$,
+  and assume that $\theta \mapsto s_\theta(x) \defeq \sqrt{p_\theta(x)}$
+  is absolutely continuous for all $x$. Let
+  $\dot{p}_\theta(x) = \nabla_\theta p_\theta(x)$ (when it exists),
+  and assume that
+  \begin{equation*}
+    \mu(\{x : \dot{p}_\theta(x) ~ \mbox{fails~to~exist}\}) = 0.
+  \end{equation*}
+  Assume that $I_\theta \defeq \E_{P_\theta}[\dot{p}_\theta
+    \dot{p}_\theta^\top / p_\theta^2]$ is continuous at $\theta_0$. Then
+  $P_\theta$ is QMD~\eqref{eqn:qmd} at $\theta = \theta_0$ with
+  $\score_\theta = \dot{p}_\theta / p_\theta$.
+\end{lemma}
+
+Deferring the proof of Lemma~\ref{lemma:qmd} temporarily,
+we note that the regularity result~\eqref{eq:normal_expansion_lem}
+gives
+\begin{equation*}
+  \sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}}
+  \sum_{i = 1}^n  \frac{\varphi(Z_i)}{\psi'(0)} + o_{P,n}(1).
+\end{equation*}
+The conditions in
+Corollary~\ref{corollary:normal-expansion}\eqref{item:apply-le-cam} imply
+that the Fisher information $I_h =
+\E_h[\score_h(Z)^2]$ exists and is continuous for
+$\score_h(z) = \frac{p'(z - h)}{f(z - h)}$,
+and the asymptotic expansion~\eqref{eqn:lan-from-qmd}
+with the preceding display give the joint convergence
+\begin{equation*}
+  \left(\sqrt{n} \bar{\Delta}_n, \log \frac{P^n_{h_n/\sqrt{n}}}{P^n_0}(Z_1^n)
+  \right)
+  \cd \normal \left( \left(0,-\frac{h^2}{2} I_0 \right),
+  \begin{pmatrix}
+    \frac{\chi(0)}{\psi'(0)^2} & \frac{-h}{ \psi'(0)}
+    \E_p[\varphi(Z) \score_0(Z)] \\
+    \frac{-h}{ \psi'(0)} \E_p[\varphi(Z) \score_0(Z)]
+    & h^2 I_0
+  \end{pmatrix}  \right).
+\end{equation*}
+Le Cam's third lemma \cite[Exm. 6.7]{VanDerVaart98} then implies the
+convergence
+\begin{equation*}
+  \sqrt{n}\bar{\Delta}_n
+  \mathop{\cd}_{P_{h_n/\sqrt{n}}^n}
+  \Ncal\left(\frac{-h}{ \psi'(0)} \E_f[\varphi(Z) \score(Z)],
+  \frac{\chi(0)}{\psi'(0)^2} \right)
+\end{equation*}
+under the alternatives $P_{h_n/\sqrt{n}}$, which gives
+Corollary~\ref{corollary:normal-expansion}\eqref{item:apply-le-cam}.
+
+All that remains is to return to our proof of Lemma~\ref{lemma:qmd}:
+
+\subsubsection*{Proof of Lemma~\ref{lemma:qmd}}
+
+The proof is essentially completely parallel to that of \cite[Lemma
+  7.6]{VanDerVaart98}. Define $\dot{s}_\theta = \half
+\frac{\dot{p}_\theta}{p_\theta} \sqrt{p_\theta}$, which exists $\mu$-almost
+surely, so that $\int \dot{s}_\theta \dot{s}_\theta^\top d\mu$ is
+well-defined (though it may be infinite). By Lebesgue's integration theorem,
+we have
+\begin{equation*}
+  s_{\theta + h}(x) - s_\theta(x) = \int_0^1 h^\top \dot{s}_{\theta + t h}(x) dt,
+\end{equation*}
+and so Jensen's inequality (or Cauchy-Schwarz) we have
+\begin{equation*}
+  (s_{\theta + h}(x) - s_\theta(x))^2
+  \le \int_0^1 h^\top \dot{s}_{\theta + t h}(x)
+  \dot{s}_{\theta + t h}(x) ^\top h dt.
+\end{equation*}
+Thus for any $h_t$ we have
+\begin{align*}
+  \int \left(\frac{s_{\theta + t h_t}(x) - s_\theta(x)}{t}\right)^2
+  d\mu(x)
+  & \le \int \int_0^1 (h_t^\top \dot{s}_{\theta + u t h_t})^2 du
+  d\mu \\
+  & = \int_0^1 h_t^\top \int
+  \dot{s}_{\theta + u t h_t}\dot{s}_{\theta + u t h_t}^\top
+  d\mu(x) h_t  du
+  = \frac{1}{4} h_t^\top \left(\int_0^1 I_{\theta + u t h_t} du\right) h_t.
+\end{align*}
+By continuity, as $h_t \to h$ and $t \to 0$ the assumed continuity
+of $\theta \mapsto I_\theta$ gives that the final display converges
+to $h^\top I_\theta h$.
+
+Now, we note that
+\begin{equation*}
+  \lim_{t \downarrow 0}
+  \left(\frac{s_{\theta + t h_t}(x) - s_\theta(x)}{t}
+  - h^\top \dot{s}_\theta(x)\right)^2 = 0
+\end{equation*}
+for all $x$ excepting a $\mu$-null set, and the
+variant dominated convergence theorem in
+\cite[Prop.~2.29]{VanDerVaart98} implies that
+\begin{equation*}
+  \lim_{t \to 0}
+  \frac{1}{t^2}
+  \int \left(s_{\theta + t h_t}(x) - s_\theta(x)
+  - t h^\top \dot{s}_\theta(x)\right)^2 d\mu(x)
+  = \lim_{t \to 0}
+  \int \left(\frac{s_{\theta + t h_t}(x) - s_\theta(x)}{t}
+  - h^\top \dot{s}_\theta(x)\right)^2 d\mu(x)
+  = 0,
+\end{equation*}
+completing the proof.

### 2019-12-12 proof-sgd.tex
Working on the proof of the bloody sgd theorem

@@
 \begin{definition}
+  \label{definition:regular-estimator}
   A sequence of estimators $T_n$ for a parameter $\theta$ in the parametric
@@
 \begin{definition}
+  \label{definition:qmd}
   Let $\{P_\theta\}_{\theta \in \Theta}$ have densities $p_\theta$
@@
 \begin{definition}
+  \label{definition:lan}
   A family of distributions $\{P_\theta\}_{\theta \in \Theta}$ is
-  \emph{locally asymptotically normal with information matrix $I_\theta$} at
+  \emph{locally asymptotically normal with information matrix $I_\theta$} (LAN)
+  at
   $\theta$ if there exists a sequence of random vectors $Z_n$ such that for
@@
 These three definitions are linked in our case by a few important results.
-First~\cite[Theorem 7.2]{VanDerVaart98},
-if $P_\theta$ is QMD at $\theta$, then
-it is locally asymptotically normal with
-$Z_n = \frac{1}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(X_i)$ and information
-matrix $I_\theta = \E_\theta[\score_\theta \score_\theta^\top]$. Moreover,
-in any locally asymptotically normal family at $\theta$,
-if $T_n$ is a regular estimator at $\theta$ with limiting distribution $Q$,
-then for any bounded, symmetric, quasi-convex loss $L$ and $c < \infty$,
+First~\cite[Theorem 7.2]{VanDerVaart98}, if $\{P_\theta\}$ is QMD
+(Def.~\ref{definition:qmd}) at the point $\theta$, then it is locally
+asymptotically normal with $Z_n = \frac{1}{\sqrt{n}} \sum_{i = 1}^n
+\score_\theta(X_i)$ and information matrix $I_\theta =
+\E_\theta[\score_\theta \score_\theta^\top]$. Moreover, in any family
+$\{P_\theta\}$ that is LAN (Def.~\ref{definition:lan}) at $\theta$, if $T_n$
+is a regular estimator (Def.~\ref{definition:regular-estimator}) at $\theta$
+with limiting distribution $Q$, then for any bounded, symmetric,
+quasi-convex loss $L$ and $c < \infty$,
 \begin{equation*}
@@
 (see Beran~\cite{beran1995role}, Eq.~(4.2)).
+%
+Thus, we show two results: first, that
+that the family $\{P_\theta\}$ of distributions
+defined by the shifted densities $\{f(\cdot - \theta)\}_{\theta \in \R}$
+is quadratic-mean-differentiable at any $\theta$,
+and second, that $\bar{\theta}_n$ is regular and
+asymptotically normal.
+The combination evidently gives the theorem.
 
-Thus, we show three results: first, that $\bar{\theta}_n$ is regular,
-second, that the family $P_\theta$ is QMD, and finally, combining the two
-results.
+First, we have the following lemma, somewhat more general than we need, but
+whose proof we provide in Sec.~\ref{sec:proof-qmd}.
+\begin{lemma}[Extension of \cite{VanDerVaart98}, Lemma 7.6]
+  \label{lemma:qmd}
+  Let $p_\theta$ be a density with respect to $\mu$,
+  and assume that $\theta \mapsto s_\theta(x) \defeq \sqrt{p_\theta(x)}$
+  is absolutely continuous for all $x$. Let
+  $\dot{p}_\theta(x) = \nabla_\theta p_\theta(x)$ (when it exists),
+  and assume that
+  \begin{equation*}
+    \mu(\{x : \dot{p}_\theta(x) ~ \mbox{fails~to~exist}\}) = 0.
+  \end{equation*}
+  Assume that $I_\theta \defeq \E_{P_\theta}[\dot{p}_\theta
+    \dot{p}_\theta^\top / p_\theta^2]$ is continuous at $\theta_0$. Then
+  $P_\theta$ is QMD (Definition~\ref{definition:qmd}) at $\theta = \theta_0$
+  with $\score_\theta = \dot{p}_\theta / p_\theta$.
+\end{lemma}
 
@@
 lemma~\cite[Example 6.7]{VanDerVaart98}.
-We recall~\cite[Thm.~7.2]{VanDerVaart98} that if
+Recall~\cite[Thm.~7.2]{VanDerVaart98} that if
 a family $\{P_\theta\}_{\theta \in \Theta}$ is quadratic mean differentiable
-at $\theta$ with score $\score_\theta$, then for any sequence
-$h_n \to h$, if $Z_i \simiid P_\theta$ then
-\begin{equation}
-  \label{eqn:lan-from-qmd}
-  \log \frac{dP_{\theta + h/\sqrt{n}}^n}{dP_\theta} (Z_1, \ldots, Z_n)
-  = \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(Z_i)
-  - \half h^2 I_\theta
-  + o_{P_\theta,n}(1)
-\end{equation}
-where $I_\theta = \E_{P_\theta}[\score_\theta^2]$ is the Fisher information,
-which necessarily exists.
+at $\theta$ with score $\score_\theta$, then
+it is LAN at $\theta$ (Definition~\ref{definition:lan})
+with information matrix $I_\theta = \E[\score_\theta \score_\theta^\top]$.
 
-We thus show that under the conditions we have assumed,
-we have quadratic mean differentiability.
-\begin{lemma}[Extension of \cite{VanDerVaart98}, Lemma 7.6]
-  \label{lemma:qmd}
-  Let $p_\theta$ be a density with respect to $\mu$,
-  and assume that $\theta \mapsto s_\theta(x) \defeq \sqrt{p_\theta(x)}$
-  is absolutely continuous for all $x$. Let
-  $\dot{p}_\theta(x) = \nabla_\theta p_\theta(x)$ (when it exists),
-  and assume that
-  \begin{equation*}
-    \mu(\{x : \dot{p}_\theta(x) ~ \mbox{fails~to~exist}\}) = 0.
-  \end{equation*}
-  Assume that $I_\theta \defeq \E_{P_\theta}[\dot{p}_\theta
-    \dot{p}_\theta^\top / p_\theta^2]$ is continuous at $\theta_0$. Then
-  $P_\theta$ is QMD~\eqref{eqn:qmd} at $\theta = \theta_0$ with
-  $\score_\theta = \dot{p}_\theta / p_\theta$.
-\end{lemma}
+%% then for any sequence
+%% $h_n \to h$, if $Z_i \simiid P_\theta$ then
+%% \begin{equation}
+%%   \label{eqn:lan-from-qmd}
+%%   \log \frac{dP_{\theta + h/\sqrt{n}}^n}{dP_\theta} (Z_1, \ldots, Z_n)
+%%   = \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(Z_i)
+%%   - \half h^2 I_\theta
+%%   + o_{P_\theta,n}(1)
+%% \end{equation}
+%% where $I_\theta = \E_{P_\theta}[\score_\theta^2]$ is the Fisher information,
+%% which necessarily exists.
 
-Deferring the proof of Lemma~\ref{lemma:qmd} temporarily,
-we note that the regularity result~\eqref{eq:normal_expansion_lem}
-gives
+%% We thus show that under the conditions we have assumed,
+%% we have quadratic mean differentiability.
+
+%% Deferring the proof of Lemma~\ref{lemma:qmd} temporarily,
+
+The regularity result~\eqref{eq:normal_expansion_lem} gives
 \begin{equation*}
@@
 
-\subsubsection*{Proof of Lemma~\ref{lemma:qmd}}
+\subsection{Proof of Lemma~\ref{lemma:qmd}}
+\label{sec:proof-qmd}
 

### 2019-12-12 adaptive-estimation.tex
Finishing part (ii) of SGD theorem convergence

@@
 that given a sample $X_1^n \simiid P$, if $\theta = \mbox{med}(P)$ and
-$P$ has density $f$ near $\theta$, then
+$P$ has continuous density $f(\cdot - \theta)$ near $\theta$, then
 \begin{equation*}
   \sqrt{n}(\mbox{med}(X_1^n) - \theta)
-  \cd \normal\left(0, \frac{1}{4 f(\theta)^2}\right),
+  \cd \normal\left(0, \frac{1}{4 f(0)^2}\right),
 \end{equation*}
@@
   \item \label{item:sgd-regular}
-    Assume in addition that $f(x)$ is continuously differentiable with a
-    finite Fisher information
-    \begin{equation*}
-      \sigma_f^2 \triangleq \ex{\frac{f'(X)}{f(X)} } 
-    \end{equation*}
-    for the location in the family $\{P_\theta\}$.
     %(or that $f(x-\theta)$ is differentiable in quadratic mean).  
-    Then for any bounded, symmetric, and quasi-convex function $L$, 
+    For any bounded, symmetric, and quasi-convex function $L$, 
     \begin{align} 
-      & \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
+      & \sup_{c < \infty} \limsup_{n \to \infty}
+      \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}
+      \E_\tau \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
       \\
-      & \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
+      & \qquad \qquad \qquad \qquad = \mathbb E \left[L(W/ 2 f(0)) \right],
+        \label{eq:attaining_LAM}
     \end{align}
-    where $Z \sim \Ncal(0,1)$. 
+    where $W \sim \normal(0,1)$. 
     %
     %
-  \item Assume the stepsizes $\gamma_n$ satisfy both
+  \item \label{item:sgd-ms-convergence}
+    Assume the stepsizes $\gamma_n$ satisfy both
     conditions~\eqref{eqn:lazy-gamma} and~\eqref{eqn:stringent-gamma}.

### 2019-12-12 proof-sgd.tex
Finishing part (ii) of SGD theorem convergence

@@
 differentiability~\cite[cf.]{VanDerVaart98}.
-We begin by recalling some of these concepts.
+We assume without loss of generality that the median of the density
+$f$ is 0, so that if $P_\theta$ has density $f(\cdot - \theta)$, the
+median of $P_\theta$ is $\theta$.
+We begin by recalling the statistical concepts we require.
 \begin{definition}
@@
 quasi-convex loss $L$ and $c < \infty$,
-\begin{equation*}
+\begin{equation}
+  \label{eqn:limit-law-regular}
   \limsup_n \sup_{\norm{h} \le c}
@@
   = \E[L(W)] ~~ \mbox{for~}W \sim Q
-\end{equation*}
+\end{equation}
 (see Beran~\cite{beran1995role}, Eq.~(4.2)).
@@
 
-First, we have the following lemma, somewhat more general than we need, but
-whose proof we provide in Sec.~\ref{sec:proof-qmd}.
+For quadratic mean differentiability, we have the following lemma, somewhat
+more general than we need; we defer proof to Sec.~\ref{sec:proof-qmd}.
 \begin{lemma}[Extension of \cite{VanDerVaart98}, Lemma 7.6]
@@
 
-We first show that the estimator $\bar{\theta}_n$ is regular in the
-following sense: For $\theta \in \Theta$, a sequence $h_n \to h \in \R$ and
-$n$ large enough that $\theta + h_n /\sqrt{n} \in \Theta$, let
-$P_{\theta,n}$ be a product probability measure on $\R^n$ distributed
-i.i.d.\ with density
-$f(x - \theta - h_n/\sqrt{n})$. Then
+By the assumption in Theorem~\ref{thm:sgd} that the density $f$
+is Lipschitz continuous, we see that the location family
+$\{P_\theta\}_{\theta \in \R}$ defined by $dP_\theta(x) = f(x - \theta)$
+satisfies the conditions of Lemma~\ref{lemma:qmd}.
+
+It remains to show that the average $\bar{\theta}_n$ is regular:
+\begin{lemma}
+  \label{lemma:sgd-median-regular}
+  Let $h_n \to h \in \R$, and define $P_n = P_{\theta + h_n / \sqrt{n}}^n$.
+  Then $\bar{\theta}_n$ is regular with
   \begin{align}
@@
     \sqrt{n}\left( \bar{\theta}_n - \theta\right)
-  \mathop{\cd}_{\Prob_{\theta,n}}
-  \normal\left( h,\frac{1}{4 f(\theta)^2}\right),
+    \mathop{\cd}_{P_n}
+    \normal\left( h,\frac{1}{4 f(0)^2}\right).
   \end{align}
-under $\Prob_{\theta,n}$. To show the convergence~\eqref{eqn:sgd-median-regular} we
-use the following refinement of Corollary~\ref{corollary:polyak-juditsky},
-whose proof we defer to Section~\ref{proof:normal-expansion}.
+\end{lemma}
+\begin{proof}
+  To show the convergence~\eqref{eqn:sgd-median-regular} we use the
+  following refinement of Corollary~\ref{corollary:polyak-juditsky}, which
+  provides a generalized convergence result for iteratively defined
+  $\theta_n$, and whose
+  proof we defer to Section~\ref{proof:normal-expansion}.
   %
@@
     \label{corollary:normal-expansion}
-  Set $\Delta_i = \theta_i - \theta$ and $\bar{\Delta}_i = \frac{1}{n}
-  \sum_{i=1}^n \Delta_i$. Let the conditions of
-  Corollary~\ref{corollary:polyak-juditsky} hold, and additionally
-  assume the local smoothness condition that there exist
-  $0 < \lambda \le 1$ and $K < \infty$ such that
+    Let the conditions of Corollary~\ref{corollary:polyak-juditsky} hold,
+    meaning that $\theta_i = \theta_{i-1} + \gamma_i \varphi(X_i -
+    \theta_{i-1})$ for $X_i = \theta + Z_i$, where $Z_i$ are i.i.d.\ with
+    $\E[\varphi(Z)] = 0$. Additionally assume the local smoothness
+    condition that there exist $0 < \lambda \le 1$ and $K < \infty$ such
+    that
     \begin{equation}
@@
     \end{equation}
-  Then
+    Set $\Delta_i = \theta_i - \theta$ and $\bar{\Delta}_i = \frac{1}{n}
+    \sum_{i=1}^n \Delta_i$. Then
     \begin{enumerate}[(i)]
@@
         \mathop{\cd}_{P_{\theta + h_n/\sqrt{n}}^n}
-      \normal\left( \frac{-h}{\psi'(0)} \E_p[\varphi(Z) \score_0(Z)]
-      , \frac{\chi(0)}{\psi'^2(0)} \right).
+        \normal\left( \frac{-h}{\psi'(0)} \E_p[\varphi(Z) \score_0(Z)],
+        \frac{\chi(0)}{\psi'^2(0)} \right).
       \end{equation*}
@@
 
-We now verify that the setting of Theorem~\ref{thm:sgd} satisfies the
-conditions of Corollary~\ref{corollary:polyak-juditsky}. First,
-we have the obvious fact that
+  We now verify that the setting of Theorem~\ref{thm:sgd}
+  (and Lemma~\ref{lemma:sgd-median-regular}) satisfies the
+  conditions of Corollary~\ref{corollary:polyak-juditsky}. First, we have
+  the obvious fact that
   \begin{equation*}
@@
   \end{equation*}
-Recalling our w.l.o.g.\ assumption that $\theta = \mbox{med}(X) = 0$,
-for $\varphi(z) = \sgn(z)$, and $Z = X - \theta = X$ we have
+  Recalling that the density $f$ is Lipschitz with median 0,
+  for $\varphi(z) = \sgn(z)$, and $Z = X - \theta$ distributed with
+  density $f$, we have
   \begin{align*}
@@
     \leq 2 \Prob\left( |Z_1| \le |x|  \right)
-  \le 2 f(0) |x| + \lip(f) x^2
+    = 2 \int_{-|x|}^{|x|} f(t) dt
+    = 4 f(0)|x| \pm 2 \int_{-|x|}^{|x|}
+    \lip(f) t dt
+    = 4 f(0) |x| + 2 \lip(f) x^2
   \end{align*}
-for $x$ near 0, where $\lip(f)$ is the Lipschitz constant of $f$ near
-its median. For large $x$ we always have
+  where $\lip(f)$ is the Lipschitz constant of $f$.
+  For large $x$ we always have
   $\E[|\varphi(Z) - \varphi(x + Z)|] \le 2$, so that
@@
   now implies the convergence \eqref{eqn:sgd-median-regular}.
+\end{proof}
 
-With the convergence~\eqref{eqn:sgd-median-regular},
-the limiting efficiency estimate~\eqref{eq:attaining_LAM} is straightforward.
-Indeed, the limiting distribution~\eqref{eqn:sgd-median-regular}
-guarantees that $\bar{\theta}_n$ is a regular estimator,
+Combining Lemmas~\ref{lemma:qmd} and~\ref{lemma:sgd-median-regular}
+with the limit~\eqref{eqn:limit-law-regular} gives
+Theorem~\ref{thm:sgd}\eqref{item:sgd-regular}.
 
-Under the assumption that $f(x)$ is continuously differentiable with a finite Fisher information for location, the model $\{Z_n+ \theta\}_{n \in \N}$ is differentiable in quadratic mean \cite[Exm.
-7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
-\begin{equation*}
-\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
-\end{equation*}
-where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$.
-The proof is concluded since any regular estimator in LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}.
+\subsubsection*{Proof of Theorem~\ref{thm:sgd}\eqref{item:sgd-ms-convergence}}
 
-\subsubsection*{Proof of (iii)}
-%In order to prove part (ii) of Theorem~\ref{thm:sgd} 
-Consider the following result from \cite{polyak1990new}:
-\begin{thm}{\cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
+We begin with the following result from \cite{polyak1990new}:
+\begin{corollary}[\cite{polyak1990new}, Theorem 2]
+  \label{corollary:polyak-mse}
   Let
@@
   \end{equation*}
-\end{thm}
+\end{corollary}
 
@@
 \E_h[\score_h(Z)^2]$ exists and is continuous for
-$\score_h(z) = \frac{p'(z - h)}{f(z - h)}$,
+$\score_h(z) = \frac{p'(z - h)}{p(z - h)}$,
 and the asymptotic expansion~\eqref{eqn:lan-from-qmd}
@@
   \mathop{\cd}_{P_{h_n/\sqrt{n}}^n}
-  \Ncal\left(\frac{-h}{ \psi'(0)} \E_f[\varphi(Z) \score(Z)],
+  \Ncal\left(\frac{-h}{ \psi'(0)} \E_p[\varphi(Z) \score(Z)],
   \frac{\chi(0)}{\psi'(0)^2} \right)
@@
 Corollary~\ref{corollary:normal-expansion}\eqref{item:apply-le-cam}.
-
-All that remains is to return to our proof of Lemma~\ref{lemma:qmd}:
 

### 2019-12-13 adaptive-estimation.tex
Working on rewriting proof of theorem 2

--- 2019-12-11 adaptive-estimation.tex
@@
   \begin{equation*}
-    n \E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0}.
+    \E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0}.
   \end{equation*}
@@
       \sqrt{n}\left( \bar{\theta}_n - \theta\right)
-      \cd \normal\left(0,\frac{1}{4 f(\theta)^2}\right).
+      \cd \normal\left(0,\frac{1}{4 f(0)^2}\right).
     \end{equation*}
@@
     %
-  \item
-    Assume in addition that $f(x)$ is continuously differentiable with a
-    finite Fisher information
+  \item \label{item:sgd-regular}
+    %(or that $f(x-\theta)$ is differentiable in quadratic mean).  
+    Let $\{P_\theta\}_{\theta \in \R}$ be the family of distributions
+    with density $f(\cdot - \theta)$, where $f$ has median 0.
+    Let $h_n \to h \in \R$, and define the distributions
+    $P_n = P_{\theta + h_n/\sqrt{n}}^n$. Then
     \begin{equation*}
-      \sigma_f^2 \triangleq \ex{\frac{f'(X)}{f(X)} } 
+      \sqrt{n}\left(\bar{\theta}_n - \theta - h_n / \sqrt{n}\right)
+      \mathop{\cd}_{P_n}
+      \normal\left(0, \frac{1}{4 f(0)^2}\right),
     \end{equation*}
-    for the location in the family $\{P_\theta\}$.
-    %(or that $f(x-\theta)$ is differentiable in quadratic mean).  
-    Then for any bounded, symmetric, and quasi-convex function $L$, 
+    and for any bounded, symmetric, and quasi-convex function $L$,
     \begin{align} 
-      & \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
+      & \sup_{c < \infty} \limsup_{n \to \infty}
+      \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}
+      \E_\tau \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
       \\
-      & \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
+      & \qquad \qquad \qquad \qquad = \mathbb E \left[L(W/ 2 f(0)) \right],
+        \label{eq:attaining_LAM}
     \end{align}
-    where $Z \sim \Ncal(0,1)$. 
+    where $W \sim \normal(0,1)$. 
     %
     %
-  \item Assume the stepsizes $\gamma_n$ satisfy both
-    conditions~\eqref{eqn:lazy-gamma} and~\eqref{eqn:stringent-gamma}.
-    Then
+  \item \label{item:sgd-ms-convergence} Assume the stepsizes $\gamma_n$
+    satisfy both conditions~\eqref{eqn:lazy-gamma}
+    and~\eqref{eqn:stringent-gamma}. Let
+    $\pi$ be a distribution on $\R$.
     \begin{equation*}
-      \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{4 n f(\theta)^2} + o(n^{-1}). 
+      \int \E\Big[( \bar{\theta}_n - \theta )^2\Big] d\pi(\theta)
+      = \frac{1}{4 n f(0)^2} + o(n^{-1}). 
     \end{equation*}
@@
 \noindent
-We provide the proof in Appendix~\ref{proof:sgd}.
+We provide the proofs of the items in Appendices~\ref{sec:proof-normal-sgd},
+\ref{sec:proof-sgd-regular}, \ref{sec:proof-sgd-ms-convergence},
+respectively.
 
@@
 sequence.
-%% \begin{corollary}
-
-\textbf{FILL THIS IN}
-
-%% \end{corollary}
+\begin{corollary}
+  Let the conditions of Theorem~\ref{thm:adpative_lower_bound} hold
+  and $\theta_n$ be defined by the iteration~\eqref{eq:sgd_alg}.
+  Let $\{P_\theta\}_{\theta \in \R}$ be the family of distributions
+  with densities $f(\cdot - \theta)$.
+  \begin{enumerate}[(i)]
+  \item Define the shorthand $P_n = P_{\theta + h_n/\sqrt{n}}^n$.
+    If the stepsizes satisfy condition~\eqref{eqn:lazy-gamma}, then
+    \begin{equation*}
+      \sqrt{n}(\bar{\theta}_n - \theta - h_n / \sqrt{n})
+      \mathop{\cd}_{P_n} \normal\left(0, \frac{1}{\eta(0)}\right).
+    \end{equation*}
+  \item If in addition the stepsizes satisfy
+    condition~\eqref{eqn:stringent-gamma}, then for any
+    prior $\pi$ on $\R$, we have
+    \begin{equation*}
+      \int \E\left[(\bar{\theta}_n - \theta)^2\right] d\pi(\theta)
+      = \frac{1}{4 n f(0)^2} + o(n^{-1}).
+    \end{equation*}
+  \end{enumerate}
+\end{corollary}
+\noindent
 
@@
 \begin{figure}
+  %%%%% COMMENTED TIKZ PICTURE %%%%%
 \begin{center}
-\begin{tikzpicture}[scale = 0.6]
-\begin{axis}[
-width=10cm, height=6cm,
-xmin = 0, xmax=800, 
-restrict y to domain = 0:3,
-ymin = 0,
-ymax = 3.4,
-samples=10, 
-xlabel= $n$,
-ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
-%xtick={-3,-2,-1,0,1,2,3},
-%xticklabels={-3,-2,-1,0,1,2,3},
-ytick={0,1,1.57},
-yticklabels={0,1,$\pi/2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
+%% \begin{tikzpicture}[scale = 0.6]
+%% \begin{axis}[
+%% width=10cm, height=6cm,
+%% xmin = 0, xmax=800, 
+%% restrict y to domain = 0:3,
+%% ymin = 0,
+%% ymax = 3.4,
+%% samples=10, 
+%% xlabel= $n$,
+%% ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
+%% %xtick={-3,-2,-1,0,1,2,3},
+%% %xticklabels={-3,-2,-1,0,1,2,3},
+%% ytick={0,1,1.57},
+%% yticklabels={0,1,$\pi/2$},
+%% line width=1.0pt,
+%% mark size=1.5pt,
+%% ymajorgrids,
+%% xmajorgrids,
+%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+%% ]
 
-\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{asymptotically optimal};
+%% \addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
+%% \addlegendentry{asymptotically optimal};
 
-%\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
+%% %\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
 
-\addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{single interaction};
+%% \addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
+%% \addlegendentry{single interaction};
 
-\end{axis}
-\end{tikzpicture}
-%\begin{tikzpicture}
-%\node at (0,0) {\includegraphics[scale=0.4]{one_bit_adpative}};
-%\node[rotate = 90, scale = 0.7] at (-3.8,0) {$n \mathbb E \left({\theta}_n - \theta \right)^2$};
-%\node[scale = 0.7] at (0,-2.4) {$n$};
-%\end{tikzpicture}
+%% \end{axis}
+%% \end{tikzpicture}
 \caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.

### 2019-12-13 appendices.tex
Working on rewriting proof of theorem 2

@@
 % -*- Mode: latex -*- %
-
-\section{}
-
-\subsection{Fast convergence of uniform estimators under bit constraints}
-\label{sec:uniform-weirdos}
-
-Here we consider the uniform distribution as our location family,
-demonstrating that in the adaptive setting~\eqref{item:adaptive} or even the
-one-step adaptive setting~(\ref{item:one-step-adaptive}'), constrained
-estimators can attain rates faster than the $1 / \sqrt{n}$ rates regular
-estimands allow. Indeed, define $c(x) = -\log 2$ for $x \in [-1, 1]$ and
-$c(x) = -\infty$ for $x \not \in [-1, 1]$. Then $f(x) = e^{-c(x)}$ is
-log-concave and symmetric, and we may consider the location family with
-densities $f(x - \theta)$. For notational simplicity, we assume we have
-a sample of size $2n$. We provide a proof sketch that
-there is a one-step adaptive estimator $\theta_n$ such that
-\begin{equation}
-  \label{eqn:uniforms-are-easy}
-  \sup_{|\theta| \le \log n}
-  P_\theta\left(|\theta_n - \theta| \ge \frac{8 \log n}{n^{3/4}}\right)
-  \le \frac{2}{n^2}.
-\end{equation}
-for all large $n$,
-and so (by the Borel-Cantelli lemmas), for any $\theta \in \R$ we have
-$P_\theta(|\theta_n - \theta| \le \sqrt{2 \log n} / n^{3/4} ~
-\mbox{eventually}) = 1$. This is of course faster than the $1/\sqrt{n}$
-rates we prove throughout.
-
-To prove inequality~\eqref{eqn:uniforms-are-easy}, we proceed in two steps,
-both quite similar.
-First, we define an initial estimator $\theta\init_n$.
-Let $\epsilon > 0$, which we will determine presently, though we will
-take $n \epsilon \to \infty$ as $n \to \infty$, so that we may assume
-w.l.o.g.\ that $\theta \in [-n\epsilon/2, n \epsilon/2]$. Take the interval
-$[-n\epsilon, n\epsilon]$, and construct
-$m$ thresholds at intervals of size $2 n \epsilon / m$; let
-the $j$th such threshold be
-\begin{equation*}
-  t_j \defeq -n \epsilon + \frac{2 n (j-1) \epsilon}{m}
-\end{equation*}
-Then we ``assign'' observations to each pair of thresholds, so that
-threshold $j$ corresponds to observations $I_j \defeq \{\frac{n (j - 1)}{m}
-+ 1, \ldots, \frac{n j}{m}\}$, of which there are $n/m$.  For each index $i
-\in I_j$, we set
-\begin{equation*}
-  B_i = \begin{cases}
-    1 & \mbox{if~} X_i \ge t_j \\
-    0 & \mbox{otherwise}.
-  \end{cases}
-\end{equation*}
-Then we simply set $\theta_n\init$ to be the maximal threshold for which
-$B_i = 0$ for all observations $X_i$ corresponding to that threshold.
-
-Let us now consider the probability that $\theta_n\init$ is substantially
-wrong. For notational simplicity, let $U_i = (1 + X_i - \theta) / 2$, so that
-the $U_i$ are uniform on $[0, 1]$.
-First, note that we always have $\theta_n\init \ge \theta
-- \frac{2 n \epsilon}{m}$, because no observations will be below
-the appropriate threshold. Let $j\opt$ be the smallest index $j$
-for which $\theta \le t_{j\opt}$, and consider
-the index sets $I_{j\opt}$, $I_{j\opt + 1}$, and so on.
-The event $\theta\init_n \ge t_{j\opt} + \frac{2 n \epsilon}{m}$ may
-occur only if for each of the $n/m$ observations in the set
-$I_{j\opt + 1}$, we have $U_i \ge \frac{n \epsilon}{m}$. Thus,
-\begin{equation*}
-  P_\theta\left(\theta_n\init \ge t_{j\opt} + \frac{2 n \epsilon}{m}
-  \right)
-  \le \left(1 - \frac{n \epsilon}{m}\right)^\frac{n}{m}
-  \le \exp\left(-\frac{n^2\epsilon}{m^2}\right).
-\end{equation*}
-Setting the number of bins $m = \sqrt{n}$,
-the resolution $\epsilon = 2 \log n / n$, we obtain
-$P_\theta(\theta_n\init \ge t_{j\opt} + 4 \log n / \sqrt{n})
-\le n^{-2}$. Thus we have
-\begin{equation}
-  \label{eqn:quality-of-initial-estimate}
-  \sup_{|\theta| \le \log n} P_\theta\left(|\theta_n\init - \theta| \ge
-  \frac{8 \log n}{\sqrt{n}}\right) \le \frac{1}{n^2}.
-\end{equation}
-
-The second stage estimator follows roughly the same strategy, except that
-the resolution of the bins is tighter. In particular, let us assume that
-$|\theta_n\init - \theta| \le \frac{8 \log n}{\sqrt{n}}$, which happens
-eventually by inequality~\eqref{eqn:quality-of-initial-estimate}.  (We will
-assume this tacitly for the remainder of the argument.)  Consider the
-interval $\Theta_n \defeq \theta_n\init + [-\frac{16 \log n}{\sqrt{n}},
-  \frac{16 \log n}{\sqrt{n}}]$ centered at $\theta_n\init$; we know that the
-interval includes $[\theta - \frac{8 \log n}{\sqrt{n}}, \theta + \frac{8
-    \log n}{\sqrt{n}}]$. Without loss of generality we assume $\theta_n\init
-= 0$.  Following precisely the same discretization strategy as that for
-$\theta_n\init$, we divide $\Theta_n$ into $m$ equal intervals, with
-thresholds $t_j = -\frac{16 \log n}{\sqrt{n}} + \frac{32 (j - 1) \log n}{m
-  \sqrt{n}}$; let $\epsilon_n = \frac{32 \log n}{m \sqrt{n}}$ be the width of
-these intervals.  Then following exactly the same reasoning as above, we
-assign indices $I_j = \{\frac{n(j - 1)}{m} + 1, \ldots, \frac{n j}{m}\}$ and
-for $i \in I_j$, set $B_i = 1$ if $X_i \ge t_j$. We define $\theta_n$ to be
-the maximal threshold $t_j$ for which $B_i = 0$ for all observations $X_i
-\in I_j$. Then following precisely the reasoning above, we have (on the
-event that $|\theta_n\init - \theta| \le \frac{8 \log n}{\sqrt{n}}$)
-\begin{equation*}
-  P_\theta(|\theta_n - \theta|
-  \ge 2 \epsilon_n)
-  \le (1 - \epsilon_n)^\frac{n}{m}
-  \le \exp\left(-\frac{n \epsilon_n}{m}\right)
-  = \exp\left(-\frac{32 \sqrt{n} \log n}{m^2}\right).
-\end{equation*}
-Set $m = 4 n^{1/4}$ to obtain the claimed
-result~\eqref{eqn:uniforms-are-easy}.
-
-\subsection{Proof of Proposition~\ref{prop:CEO}
-\label{app:proof:CEO}}
-
-%
-Denote by $D^\star$ the optimal MSE in the Gaussian CEO with $L$ observers and under a total sum-rate $r = r_1 + \ldots +r_L$.
-An expression for $D^\star$ as a function of $r$ is give as \cite[Eq.
-10]{chen2004upper}:
-\begin{equation} \label{eq:ceo_optimal_sumrate}
-r = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
-\end{equation}
-For the special case where $r = n$ and $L=n$, we have
-\begin{equation} \label{eq:ceo_optimal_sumrate2}
-n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
-\end{equation}
-Consider the distributed encoding setting (iii) in the case where $f(x) = \Ncal(0,\sigma^2)$ and the prior on $\Theta$ is $\pi = \Ncal(0,\sigma_\theta^2)$.
-The Gaussian CEO problem of \cite{viswanathan1997quadratic} with a unit bitrate $r_1=\ldots = r_n =1$ at each terminal and blocklength $k=1$ reduces to our distributed setting (iii).
-Since $D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describes the MSE in the CEO setting under an optimal allocation of the sum-rate $r = n$ among $n$ encoders, it provides a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering the limit $n\rightarrow \infty$ in \eqref{eq:ceo_optimal_sumrate2}, we see that
-\[
-D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
-\]
-This implies Proposition~\ref{prop:CEO}. 
-%We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the MSE in the CEO setting while enforcing the condition $r_1=\ldots = r_n = 1$.
-Indeed, an upper bound for the CEO MSE under the condition $r_1=\ldots = r_n = 1$ follows from \cite{KipnisRini2019}, and leads to
-%\[
-%D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
-%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
-%\]
-%which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.
-
-\subsection{Proof of Theorem~\ref{thm:adpative_lower_bound}
-\label{proof:thm:adpative_lower_bound}
-}
-Consider the following two Lemmas:
-\begin{lem} \label{lem:bound_intervals}
-Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$,
-\begin{equation}
-\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^2 }
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-\leq  4f^2(0). 
-\label{eq:lem_bound_intervals}
-\end{equation}
-\end{lem}
-\begin{lem} \label{lem:fisher_bound}
-Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that Assumption~1 holds. For a Borel measurable $A$ set, 
-\[
-B(X) = \begin{cases} 1,& X \in A, \\
--1, & X \notin A.
-\end{cases}
-\]
-Then the Fisher information of $B$ with respect to $\theta$ is bounded from above by $\eta(0)$.
-\end{lem}
-
-Lemma~\ref{lem:bound_intervals} is obtained as the special case $\delta = 0$ of lemma \ref{lem:bound_intervals_delta}. 
-We now prove Lemma~\ref{lem:fisher_bound}.
-\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
-When $f(x)$ is the normal density function, this lemma follows from \cite[Thm.
-3]{Barnes2018}.
-The proof below is based on a different techique than in \cite{Barnes2018}, and is valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}.
-\\
-
-The Fisher information of $B$ with respect to $\theta$ is given by
-\begin{align}
-I_\theta & =  \ex{ \left( \frac{d}{d\theta} \log P\left( B | \theta \right) \right)^2 |\theta } \nonumber \\
-& = \frac{ \left(\frac{d}{d\theta} P(B=1|\theta) \right)^2}{P(B=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(B=-1|\theta) \right)^2} {P(B=-1| \theta)} \nonumber \\
-& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(B=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(B=-1| \theta) } \nonumber \\
-& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(B=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(B=-1| \theta) } \nonumber \\ 
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(B=1 | \theta) \left(1-P(B=1|\theta) \right)  }, \nonumber \\
-& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
-\end{align}
-where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$.
-Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
-\[
-\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
-\]
-which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$.
-It is therefore enough to proceed in the proof assuming that $A$ is of the form
-\[
-A = \cup_{j=1}^k (a_j,b_j),
-\]
-with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
-\begin{align*}
-\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
-& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
-\end{align*}
-so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
-\begin{align}
-& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
-{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
-& \times \frac {1} 
-{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
-\label{eq:lemma_J}
-\end{align}
-It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in \R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than 
-\[
-\max_{t \in \{a_j,b_j, j=1,\ldots,k\} } 4f^2(t) \leq 4 f^2(0), 
-\]
-where the last transition is due to Assumption~1. 
-\QEDA \\
-
-We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
-\begin{equation}
-\label{eq:general_messages}
-B_i = \begin{cases}
-X_i \in A_i & 1, \\
-X_i \notin A_i & -1,
-\end{cases} 
-\end{equation}
-where $A_i \subset \R$ is a Borel measurable set. 
-%Indeed, any measurable function $(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
-Consider the conditional distribution $P({B_1,\ldots,B_n|\theta})$ of $(B_1,\ldots,B_n)$ given $\theta$. We have 
-\begin{align}
-P\left( B_1,\ldots,B_n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B_1,\ldots,B_{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
-\end{align}
-where $P\left(B_i =1 | \theta, B_1,\ldots,B_{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B_1,\ldots,B_n$ with respect to $\theta$ is given by 
-\begin{align}
-I_\theta(B_1,\ldots,B_N) = \sum_{i=1}^n I_\theta (B_i|B_1,\ldots,B_{i-1}),
-\label{eq:fisher_information}
-\end{align}
-where $I_\theta (B_i|B_{i-1},\ldots,B_1)$ is the Fisher information of the distribution of $B_i$ given $B_1,\ldots,B_{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B_{i-1},\ldots,B_1) \leq 4f^2(0)$.
-The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
-\begin{align*}
-\ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ \ex{ I_\theta(B_1,\ldots,B_n)} + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
-& \geq \frac{1}{ 4f^2(0) n + I_0}.
-\end{align*}
-\QEDA
-
-\subsection{Isoperimetric Lemma
-\label{sec:bound_intervals_delta} }
-The following lemma is used in the proof Theorems~\ref{thm:adpative_lower_bound}, \ref{thm:LAN1}, and \ref{thm:non_existence}.
-
-\begin{lem} \label{lem:bound_intervals_delta}
-Let $f(x)$ be log-concave, symmetric, and differentiable density function. Let $\delta\geq 0$. Assume that the function
-\[
-\eta_\delta(x) \triangleq  \eta^{1+\delta}(x)/f^\delta(x) = \frac{  \left( f(x) \right)^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}}
-\]
-is non-increasing in $|x|$. For any $x_1 \ge \ldots \ge x_n \in \R^n$,
-\begin{equation}
-\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
-{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{k=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
-\leq  \max_{i} \eta_\delta(x_i).
-\label{eq:lem_bound_intervals_delta}
-\end{equation}
-\end{lem}
-In particular, 
-\[
-\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
-{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
-\leq \eta_\delta(0) = 4^{1+\delta} f^{2+\delta}(0).
-\]
-
-\subsubsection*{
-Proof of Lemma~\ref{lem:bound_intervals_delta}}
-Denote 
-\[
-\delta_n(x_1,\ldots,x_n) \triangleq \sum_{i=1}^{n} s_i f(x_i),
-\]
-\[
- \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{i=1}^n s_i F(x_i), 
-\]
-where $s_i \triangleq (-1)^{i+1}$. We use induction on $n \in \N$ to show that 
-\begin{align}
-\label{eq:lemm:interval_bounds:to_show}
-\frac{ \left| \delta_n(x_1,\ldots,x_n) \right|^{2+\delta}} 
-{\left|\Delta_n(x_1,\ldots,x_n)\left(1- \Delta_n(x_1,\ldots,x_n) \right) \right|^{1+\delta} } \leq \max_{i}\eta_{\delta}(x_i).
-\end{align}
- Since 
-\[
-\eta_\delta(x) =  \frac{  \left|\delta_1(x) \right|^{2+\delta}}{\left|\Delta_1(x)
-(1-\Delta_1(x)) \right|^{1+\delta}}, 
-\]
-The case $n=1$ is trivial.  
-%follows from the assumption that $\eta_\delta(x)$ is non-increasing in $|x|$. 
-Assume that \eqref{eq:lemm:interval_bounds:to_show} holds for all integers up to $n = N$ and for any $x_1 \ge \ldots \ge x_N$.
-Consider the case $n = N+1$.
-Let $i^*$ be the index such that $x_{i^*}$ has minimal absolute value among $x_1,\ldots,x_N$.
-The assumption on $\eta_\delta(x)$ implies that
-\[
-\eta_\delta(x_{i^*}) = \max_i \eta_\delta(x_i).
-\]
-Since the LHS of \eqref{eq:lem_bound_intervals_delta} is invariant to a sign flip of all $x_1,\ldots,x_{N+1}$, we may assume that $x_{i^*}$ is positive without loss of generality. 
-%For simplicity, we also assume that $s_{i^*} = 1$ and note that the case $s_{i^*} = -1$ is obtained using identical arguments. 
-Set $x^* = x_{i^*}$ and let $k=i^*-1$. In what follows, variables with subscript of non-positive index are ignored in summations and in lists of arguments to functions. Consider the function
-\begin{align}
-& g(y_1,\ldots,y_N) \triangleq g(y_1,\ldots,y_N|x^*,k) \\
-&  \triangleq  \frac{\left| \delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N) )\right|^{2+\delta}}{
-\left|\Delta_{N+1}(y_1,\ldots,y_k,x_{i^*},y_{k+1}\ldots,y_N)  (1 -\Delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N)  \right|^{1+\delta}
-} \label{eq:g_def}.
-\end{align}
-The LHS of \eqref{eq:lemm:interval_bounds:to_show} is obtained by taking $y_i=x_{k_i}$ where $k_i$ is the $i$th element in $\{1,\ldots,N+1\}\setminus \{i^*\}$. It is therefore enough to prove that 
-\[
-\max_{(y_1,\ldots,y_N) \in A_N} g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*),
-\]
-where 
-\[
-A_N(x^*,k) \triangleq \left\{ (y_1,\ldots,y_N) \in \R^N\, : \, y_1 \ge y_k \ge x^* \ge -x^* \ge y_{k+1} \ldots \ge y_N
-\right\}.
-\]
-%
-Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable with derivative 
-\[
-c'(x) \triangleq \frac{f'(x)}{f(x)} 
-\]
-that is non-increasing. We first prove the lemma under the assumption that $c'(x)$ is an injection, or, equivalently, that $c(x)$ is strictly decreasing for all $x\in \R$. \par
-%
-The maximal value of $g(y_1,\ldots,y_N)$ is attained for the same $(y_1,\ldots,y_N) \in A_N(x^*,k)$ that maximizes
-\begin{align*}
- \log(g)(y_1,\ldots, y_N) =  (2+\delta) \log \left( \delta_N  \right)  - (1+\delta) \log \left( \Delta_N  \right) - (1+\delta) \log \left(1 - \Delta_N \right),
-\end{align*}
-where in the last display and henceforth we suppress the arguments $y_1,\ldots,y_k,x^*,y_{k+1},\ldots, y_N$ of the functions $\delta_N$ and $\Delta_N$.
-%
-Within the interior of $A_N(x^*,k)$, all three expressions in \eqref{eq:g_def} within an absolute value are positive.
-It follows that partial derivative of $\log(g)(y_1,\ldots,y_N)$ with respect to $y_i$ within the interior of $A_N(x^*,k)$ is given by
-\[
-\frac{\partial \log(g)}{\partial y_i} = \frac{(2+\delta) s_i f'(x_i)}{\delta_N } -\frac{(1+\delta) s_i f(x_i)}{\Delta_N  } + \frac{(1+\delta)s_i f(y_i)}{1-\Delta_N }.
-\]
-We conclude that the gradient of $\log(g)$ vanishes if and only if
-\begin{equation}
-\label{eq:gradient_zero}
-c'(y_i) = \frac{f'(y_i)}{f(y_i)} = \frac{1+\delta}{2+\delta} \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N } \right),\quad i=1,\ldots,N.
-\end{equation}
-%
-Since we assumed that $c'(x)$ is an injection, \eqref{eq:gradient_zero} is satisfied if and only if $y_1 = \ldots = y_N$. In this case, 
-$g(y_1,\ldots,y_N) = \eta_\delta(x_{i^*})$  
-if $N$ is even. If $N$ is odd and $y_1 = \ldots = y_N > x^*$, then 
-\begin{align*}
-& g(y_1,\ldots,y_N) = \frac{\left| f(y_1)-f(x_{i^*})  \right|^{2+\delta}} { 
-\left|  F(y_1) - F(x_{i^*}) \right|^{1+ \delta} 
-\left| 1 - (F(y_1) -F(x_{i^*})) \right|^{1+ \delta} } 
-\end{align*} 
-which is bounded from from above by $\eta_\delta(x_{i^*})$ by the induction hypothesis. The case where $N$ is odd and $-x^* \leq y_1 = \ldots = y_N$ is similar. 
-%
-We now consider the possibility that the maximum of $g(y_1,\ldots,y_N)$ is attained at the boundaries of $A_N(x^*,k)$.
-At boundary points for which $y_i = y_{i+1}$ for some $i$, the contribution of $y_i$ and $y_{i+1}$ to $g(y_1,\ldots,y_N)$ is zero and the induction assumption for $n=N-1$ implies that
-\[
-g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*)
-\]
-The remaining boundary points of $A_N(x^*,k)$ are covered by the following cases:
-\begin{itemize}
-\item[(1)]  $y_N \to -\infty$. 
-\item[(2)] $y_1 \to \infty$.
-\item[(3)] $y_k = x_{i^*}$.
-\item[(4)] $y_{k+1} = -x_{i^*}$. 
-\end{itemize}
-For case (1), 
-\begin{align*}
-g(y_1,\ldots,y_N) \to \frac{ \left| \sum_{i=1}^{k} s_i f(y_i) + s_{i^*} f(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i f(y_i) \right|^{2+\delta}} 
-{\left| \sum_{i=1}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i F(y_i) \right|^{1+\delta}\left|1- \left( \sum_{i=1}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i F(y_i) \right)  \right|^{1+\delta} },
-\end{align*}
-which is smaller than $\eta_\delta(x_{i^*})$ by the induction hypothesis. Similarly, under case (2),
-\begin{align*}
-& g(y_1,\ldots,y_N) \to 
-\frac{ \left| \sum_{i=2}^{k} s_i f(y_i) + s_{i^*} f(x_{i^*}) - \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
-{\left| 1+ \sum_{i=2}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta}\left|-\left( \sum_{i=2}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N} s_i F(y_i) \right)  \right|^{1+\delta} },
- \\
-& = \frac{ \left| -\sum_{i=2}^{k} s_i f(y_i) - s_{i^*} f(x_{i^*}) + \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
-{ \left|1 - \left(-\sum_{i=2}^{k} s_i F(y_i) - s_{i^*} F(x_{i^*}) + \sum_{i=k+1}^{N} s_i F(y_i) \right) \right|^{1+\delta} 
-\left|-\sum_{i=2}^{k} s_i F(y_i) - s_{i^*} F(x_{i^*}) + \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta} }
-\end{align*}
-which is smaller than $\eta_{\delta}(x_{i^*})$ by the induction hypothesis.
-Under case (3), the terms in $\delta_N$ and $\Delta_N$ corresponding to $y_k$ and $x_{i^*}$ cancel each other.
-As a result,  $g(y_1,\ldots,y_N)$ reduces to an expression with $n=N-1$ variables hence this case is handled by the induction hypothesis.
-%
-Finally, under case (4), set 
-\[
-d \triangleq s_k F(-x^*) + s_{i^*} F(x^*) = s_{i^*}\left(1-2F(-x^*) \right), 
-\]
-\[
-\sigma \triangleq \sum_{i=1}^{k-1} s_i f(y_i) - \sum_{i=k+1}^{N} s_i f(y_i). 
-\]
-and 
-\[
-\Sigma \triangleq \sum_{i=1}^{k-1} s_i F(y_i) - \sum_{i=k+1}^{N} s_i F(y_i). 
-\]
-We have
-\begin{align*}
-& g(y_1,\ldots,y_N) =\nonumber  \\ 
-& =
-\frac{ \left| \sum_{i=1}^{k-1} s_i f(y_i) - \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
-{\left| \sum_{i=1}^{k-1} s_i F(y_i) + d(x^*) - \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta} \left|1- \sum_{i=1}^{k-1} s_i F(y_i) - d(x^*) + \sum_{i=k+1}^{N} s_i F(y_i)   \right|^{1+\delta} }, \\
-& = \frac{ \left| \sigma \right|^{2+\delta}} 
-{\left| \Sigma+d \right|^{1+\delta} \left|1- \Sigma - d \right|^{1+\delta} }  =  
-\frac{ \left| \sigma \right|^{2+\delta}} 
-{\left| \Sigma \right|^{1+\delta} \left|1- \Sigma \right|^{1+\delta} }  \left| \frac{\Sigma(1-\Sigma) } { \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} \right|^{1+\delta}. 
-\end{align*}
-By the induction hypothesis,
-\[
-\frac{ \left| \sigma \right|^{2+\delta}} 
-{\left| \Sigma \right|^{1+\delta} \left|1- \Sigma \right|^{1+\delta} } \leq \eta_\delta(x^*), 
-\]
-hence it is left to show that 
-\[
- \frac{\Sigma(1-\Sigma) } { \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} \leq 1.
-\]
-Whenever $d>0$, 
-\begin{align*}
-& \frac{ \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} {\Sigma(1-\Sigma)} \geq 1 \Leftrightarrow  1-2\Sigma \geq d, 
-\end{align*}
-while for $d<0$,
-\begin{align*}
-& \frac{ \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} {\Sigma(1-\Sigma)} \geq 1 \Leftrightarrow  1-2\Sigma \leq d. 
-\end{align*}
-Therefore, it is enough to show that $\Sigma \leq F(-x^*)$ if $s_{i^*}=1$ and 
-$\Sigma \geq F(-x^*)$ if $s_{i^*}=-1$. 
-%
-Indeed, if $s_{i^*}=1$, then $s_{k+1}=-1$ and monotonicity of $F(x)$ implies that 
-\[
-\Sigma + d \leq F(y_1) - F(y_k) + F(x^*) - F(-x^*) + F(y_{k+2}) - F(y_N), 
-\]
-and hence
-\[
-\Sigma \leq 1-F(x^*) = F(-x^*). 
-\]
-Similarly, if $s_{i^*}=-1$ then 
-\[
-1 - \Sigma \leq 1 -  F(-x^*).
-\]
-This conclude the proof in the case where $c'(x)$ is an injection. 
-\par  
-In the case where $c'(x)$ is not necessarily strictly decreasing, we approximate $c(x)$ using another concave symmetric function whose derivative is always negative except, perhaps, at the origin.
-For $\alpha>0$ consider the function  $f_\alpha(x) = \kappa(\alpha) e^{\sgn(c(x))|c(x)|^{1+\alpha}}$, where $\kappa(\alpha)$ is chosen such that $f_\alpha(x)$ is a probability density function.
-Then $c_\alpha(x)$ is concave, symmetric, and differentiable with
-\[
-c_\alpha'(x) \triangleq \frac{f'_\alpha(x)}{f_\alpha(x)} = (1+\alpha)|c(x)|^{\alpha} c'(x). 
-\]
-Now $c_\alpha'(x)$ is non-increasing since it is the derivative of a concave function.
-Furthermore, since $c(x)$ is non-constant on any interval and $c'(x)$ is non-increasing, $c_\alpha'(x)$ is non-constant on any interval hence an injection.
-It follows from the first part of the proof that, for any $\alpha>0$,
-\begin{align}
-\label{eq:proof:lem:bound_intervals}
-\frac{(\delta_{n,\alpha})^2}{\Delta_{n,\alpha}(1-\Delta_{n,\alpha})} \leq \max_i \eta_{\alpha}(x_i),
-\end{align}
-where 
-\[
-\delta_{n,\alpha} \triangleq  \sum_{k=1}^{n} (-1)^{k+1} f_{\alpha}(x_k),
-\]
-\[
-\Delta_{n,\alpha} \triangleq \sum_{k=1}^n (-1)^{k+1} F_{\alpha}(x_k), 
-\]
-and 
-\[
-\eta_{\delta,\alpha}(x) \triangleq \frac{(f_\alpha(x))^{2+\delta}}{\left(F_{\alpha}(x)(1-F(x)) \right)^{1+\delta}}. 
-\]
-The proof is completed by noting that 
-\begin{align*}
-\lim_{\alpha \to 0} \frac{(\delta_{n,\alpha})^{2+\delta} }{ \left(\Delta_{n,\alpha}(1-\Delta_{n,\alpha})\right)^{1+\delta}}  = \frac{(\delta_{n})^{2+\delta }}{\left(\Delta_{n}(1-\Delta_{n}) \right)^{1+\delta}},
-\end{align*}
-and, since the maximum is over a finite set,
-\begin{align*}
-\lim_{\alpha \to 0}  \max_i \eta_{\delta,\alpha}(x_i)  = \max_i\eta_\delta(x_i).
-\end{align*}
-
-%Our goal is to construct an approximation to $f(x)$ using a log-concave, symmetric, and differentiable function $\hat{f}(x)$ such that $\hat{f}'(x)/\hat{f}(x)$ is strictly decreasing.
-We achieve such an approximation by modifying $f(x)$ over intervals over which $c'(x)$ is a constant.
-Assume first $c'(x)$ is only a constant over an interval $(a_1,b_1)\subset \R$ containing $x_1>0$ and on the mirror image of this interval around $x=0$.
-Over this interval, $f(x)$ is necessarily of the form $f(x) = e^{-c_1|x| + d_1}$ for some $c_1\geq 0$ and $d_1$.
-% and For $\alpha>0$, consider
-%\[
-%F_1(x,\alpha) \triangleq  F(a_1) + \frac{1}{c_1} e^{-c_1 (|x|^{1+\alpha} +d_1}, \quad x \in (a_1,b_1),
-%\]
-%and 
-%\[
-%f_1(x,\alpha) \triangleq  F_1'(x,\alpha) =  -\sgn(x)(1+\alpha)|x|^\alpha e^{-c_1 |x|^{1+\alpha} + d_1}, \quad x \in (a_1,b_1).
-%\]
-
-\QEDA
 

### 2019-12-13 distributed-estimation.tex
Working on rewriting proof of theorem 2

@@
 \begin{figure}
+  %%%%% COMMENTED TIKZ PICTURE %%%%%
   \begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-title = {$\sigma/T = 1/2$},
-ytick={0,0.1,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
+%% \begin{tikzpicture}[scale = 0.55]
+%% \begin{axis}[
+%% width=8cm, height=6cm,
+%% xmin = -0.5, xmax=0.5, 
+%% restrict y to domain = 0:100,
+%% ymin = 0,
+%% ymax = 1,
+%% samples=10, 
+%% xlabel= {$dt$},
+%% xtick={-0.5,0,0.5},
+%% xticklabels={-$T$, 0, $T$},
+%% title = {$\sigma/T = 1/2$},
+%% ytick={0,0.1,1},
+%% %ylabel = {$\lambda(dt)$},
+%% yticklabels={0,0.1,1},
+%% line width=1.0pt,
+%% mark size=1.5pt,
+%% ymajorgrids,
+%% xmajorgrids,
+%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+%% ]
+%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
 
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
+%% \addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
 
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
+%% \addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
 
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.6,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/T = 1/5$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.5},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.5},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
+%% \end{axis}
+%% \end{tikzpicture}
+%% %
+%% \begin{tikzpicture}[scale = 0.55]
+%% \begin{axis}[
+%% width=8cm, height=6cm,
+%% xmin = -0.5, xmax=0.5, 
+%% restrict y to domain = 0:100,
+%% ymin = 0,
+%% ymax = 0.6,
+%% samples=10, 
+%% xlabel= {$dt$},
+%% title = {$\sigma/T = 1/5$},
+%% xtick={-0.5,0,0.5},
+%% xticklabels={-$T$, 0, $T$},
+%% ytick={0,0.5},
+%% ylabel = {$\lambda(dt)$},
+%% yticklabels={0,0.5},
+%% line width=1.0pt,
+%% mark size=1.5pt,
+%% ymajorgrids,
+%% xmajorgrids,
+%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+%% ]
+%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
 
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
+%% \addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
 
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
+%% \addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
 
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.3,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma / T = 1/10$},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.2},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.2},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
+%% \end{axis}
+%% \end{tikzpicture}
+%% %
+%% \begin{tikzpicture}[scale = 0.55]
+%% \begin{axis}[
+%% width=8cm, height=6cm,
+%% xmin = -0.5, xmax=0.5, 
+%% restrict y to domain = 0:100,
+%% ymin = 0,
+%% ymax = 0.3,
+%% samples=10, 
+%% xlabel= {$dt$},
+%% xtick={-0.5,0,0.5},
+%% title = {$\sigma / T = 1/10$},
+%% xticklabels={-$T$, 0, $T$},
+%% ytick={0,0.2},
+%% %ylabel = {$\lambda(dt)$},
+%% yticklabels={0,0.2},
+%% line width=1.0pt,
+%% mark size=1.5pt,
+%% ymajorgrids,
+%% xmajorgrids,
+%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+%% ]
+%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
 
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
+%% \addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
 
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
+%% \addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
 
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.15,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma / T = 1/20$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
+%% \end{axis}
+%% \end{tikzpicture}
+%% %
+%% \begin{tikzpicture}[scale = 0.55]
+%% \begin{axis}[
+%% width=8cm, height=6cm,
+%% xmin = -0.5, xmax=0.5, 
+%% restrict y to domain = 0:100,
+%% ymin = 0,
+%% ymax = 0.15,
+%% samples=10, 
+%% xlabel= {$dt$},
+%% title = {$\sigma / T = 1/20$},
+%% xtick={-0.5,0,0.5},
+%% xticklabels={-$T$, 0, $T$},
+%% ytick={0,0.1},
+%% ylabel = {$\lambda(dt)$},
+%% yticklabels={0,0.1},
+%% line width=1.0pt,
+%% mark size=1.5pt,
+%% ymajorgrids,
+%% xmajorgrids,
+%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+%% ]
+%% \addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
 
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
+%% \addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
 
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
+%% \addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
 
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
+%% %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
+%% \end{axis}
+%% \end{tikzpicture}
 
@@
 \begin{figure}
+  %%%%% COMMENTED TIKZ PICTURE %%%%%
   \begin{center}

### 2019-12-13 proof-adaptive-optimality.tex
Working on rewriting proof of theorem 2

\section{Proof of Theorem~\ref{thm:adpative_lower_bound}
\label{proof:thm:adpative_lower_bound}
}
Consider the following two Lemmas:
\begin{lem} \label{lem:bound_intervals}
Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$,
\begin{equation}
\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^2 }
{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
\leq  4f^2(0). 
\label{eq:lem_bound_intervals}
\end{equation}
\end{lem}
\begin{lem} \label{lem:fisher_bound}
Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that Assumption~1 holds. For a Borel measurable $A$ set, 
\[
B(X) = \begin{cases} 1,& X \in A, \\
-1, & X \notin A.
\end{cases}
\]
Then the Fisher information of $B$ with respect to $\theta$ is bounded from above by $\eta(0)$.
\end{lem}

Lemma~\ref{lem:bound_intervals} is obtained as the special case $\delta = 0$ of lemma \ref{lem:bound_intervals_delta}. 
We now prove Lemma~\ref{lem:fisher_bound}.
\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
When $f(x)$ is the normal density function, this lemma follows from \cite[Thm. 3]{Barnes2018}. The proof below is based on a different techique than in \cite{Barnes2018}, and is valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}. \\

The Fisher information of $B$ with respect to $\theta$ is given by
\begin{align}
I_\theta & =  \ex{ \left( \frac{d}{d\theta} \log P\left( B | \theta \right) \right)^2 |\theta } \nonumber \\
& = \frac{ \left(\frac{d}{d\theta} P(B=1|\theta) \right)^2}{P(B=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(B=-1|\theta) \right)^2} {P(B=-1| \theta)} \nonumber \\
& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(B=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(B=-1| \theta) } \nonumber \\ 
& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(B=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(B=-1| \theta) } \nonumber \\ 
& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(B=1 | \theta) \left(1-P(B=1|\theta) \right)  }, \nonumber \\
& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
\end{align}
where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$. Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that 
\[
\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
\]
which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$. It is therefore enough to proceed in the proof assuming that $A$ is of the form
\[
A = \cup_{j=1}^k (a_j,b_j),
\]
with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
\begin{align*}
\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
\end{align*}
so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
\begin{align}
& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
& \times \frac {1} 
{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
\label{eq:lemma_J}
\end{align}
It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in \R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than 
\[
\max_{t \in \{a_j,b_j, j=1,\ldots,k\} } 4f^2(t) \leq 4 f^2(0), 
\]
where the last transition is due to Assumption~1. 
\QEDA \\

We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}. In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
\begin{equation}
\label{eq:general_messages}
B_i = \begin{cases}
X_i \in A_i & 1, \\
X_i \notin A_i & -1,
\end{cases} 
\end{equation}
where $A_i \subset \R$ is a Borel measurable set. 
%Indeed, any measurable function $(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
Consider the conditional distribution $P({B_1,\ldots,B_n|\theta})$ of $(B_1,\ldots,B_n)$ given $\theta$. We have 
\begin{align}
P\left( B_1,\ldots,B_n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B_1,\ldots,B_{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
\end{align}
where $P\left(B_i =1 | \theta, B_1,\ldots,B_{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B_1,\ldots,B_n$ with respect to $\theta$ is given by 
\begin{align}
I_\theta(B_1,\ldots,B_N) = \sum_{i=1}^n I_\theta (B_i|B_1,\ldots,B_{i-1}),
\label{eq:fisher_information}
\end{align}
where $I_\theta (B_i|B_{i-1},\ldots,B_1)$ is the Fisher information of the distribution of $B_i$ given $B_1,\ldots,B_{i-1}$. From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B_{i-1},\ldots,B_1) \leq 4f^2(0)$. The Van Trees inequality \cite{van2004detection, gill1995applications} now implies 
\begin{align*}
\ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ \ex{ I_\theta(B_1,\ldots,B_n)} + I_0} \\
& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
& \geq \frac{1}{ 4f^2(0) n + I_0}.
\end{align*}
\QEDA

\subsection{Isoperimetric Lemma
\label{sec:bound_intervals_delta} }
The following lemma is used in the proof Theorems~\ref{thm:adpative_lower_bound}, \ref{thm:LAN1}, and \ref{thm:non_existence}.

\begin{lem} \label{lem:bound_intervals_delta}
Let $f(x)$ be log-concave, symmetric, and differentiable density function. Let $\delta\geq 0$. Assume that the function
\[
\eta_\delta(x) \triangleq  \eta^{1+\delta}(x)/f^\delta(x) = \frac{  \left( f(x) \right)^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}}
\]
is non-increasing in $|x|$. For any $x_1 \ge \ldots \ge x_n \in \R^n$,
\begin{equation}
\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{k=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
\leq  \max_{i} \eta_\delta(x_i).
\label{eq:lem_bound_intervals_delta}
\end{equation}
\end{lem}
In particular, 
\[
\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
\leq \eta_\delta(0) = 4^{1+\delta} f^{2+\delta}(0).
\]

\subsubsection*{
Proof of Lemma~\ref{lem:bound_intervals_delta}}
Denote 
\[
\delta_n(x_1,\ldots,x_n) \triangleq \sum_{i=1}^{n} s_i f(x_i),
\]
\[
 \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{i=1}^n s_i F(x_i), 
\]
where $s_i \triangleq (-1)^{i+1}$. We use induction on $n \in \N$ to show that 
\begin{align}
\label{eq:lemm:interval_bounds:to_show}
\frac{ \left| \delta_n(x_1,\ldots,x_n) \right|^{2+\delta}} 
{\left|\Delta_n(x_1,\ldots,x_n)\left(1- \Delta_n(x_1,\ldots,x_n) \right) \right|^{1+\delta} } \leq \max_{i}\eta_{\delta}(x_i).
\end{align}
 Since 
\[
\eta_\delta(x) =  \frac{  \left|\delta_1(x) \right|^{2+\delta}}{\left|\Delta_1(x)
(1-\Delta_1(x)) \right|^{1+\delta}}, 
\]
The case $n=1$ is trivial.  
%follows from the assumption that $\eta_\delta(x)$ is non-increasing in $|x|$. 
Assume that \eqref{eq:lemm:interval_bounds:to_show} holds for all integers up to $n = N$ and for any $x_1 \ge \ldots \ge x_N$. Consider the case $n = N+1$. Let $i^*$ be the index such that $x_{i^*}$ has minimal absolute value among $x_1,\ldots,x_N$. The assumption on $\eta_\delta(x)$ implies that
\[
\eta_\delta(x_{i^*}) = \max_i \eta_\delta(x_i).
\]
Since the LHS of \eqref{eq:lem_bound_intervals_delta} is invariant to a sign flip of all $x_1,\ldots,x_{N+1}$, we may assume that $x_{i^*}$ is positive without loss of generality. 
%For simplicity, we also assume that $s_{i^*} = 1$ and note that the case $s_{i^*} = -1$ is obtained using identical arguments. 
Set $x^* = x_{i^*}$ and let $k=i^*-1$. In what follows, variables with subscript of non-positive index are ignored in summations and in lists of arguments to functions. Consider the function
\begin{align}
& g(y_1,\ldots,y_N) \triangleq g(y_1,\ldots,y_N|x^*,k) \\
&  \triangleq  \frac{\left| \delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N) )\right|^{2+\delta}}{
\left|\Delta_{N+1}(y_1,\ldots,y_k,x_{i^*},y_{k+1}\ldots,y_N)  (1 -\Delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N)  \right|^{1+\delta}
} \label{eq:g_def}.
\end{align}
The LHS of \eqref{eq:lemm:interval_bounds:to_show} is obtained by taking $y_i=x_{k_i}$ where $k_i$ is the $i$th element in $\{1,\ldots,N+1\}\setminus \{i^*\}$. It is therefore enough to prove that 
\[
\max_{(y_1,\ldots,y_N) \in A_N} g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*),
\]
where 
\[
A_N(x^*,k) \triangleq \left\{ (y_1,\ldots,y_N) \in \R^N\, : \, y_1 \ge y_k \ge x^* \ge -x^* \ge y_{k+1} \ldots \ge y_N
\right\}.
\]
%
Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable with derivative 
\[
c'(x) \triangleq \frac{f'(x)}{f(x)} 
\]
that is non-increasing. We first prove the lemma under the assumption that $c'(x)$ is an injection, or, equivalently, that $c(x)$ is strictly decreasing for all $x\in \R$. \par
%
The maximal value of $g(y_1,\ldots,y_N)$ is attained for the same $(y_1,\ldots,y_N) \in A_N(x^*,k)$ that maximizes
\begin{align*}
 \log(g)(y_1,\ldots, y_N) =  (2+\delta) \log \left( \delta_N  \right)  - (1+\delta) \log \left( \Delta_N  \right) - (1+\delta) \log \left(1 - \Delta_N \right),
\end{align*}
where in the last display and henceforth we suppress the arguments $y_1,\ldots,y_k,x^*,y_{k+1},\ldots, y_N$ of the functions $\delta_N$ and $\Delta_N$.
%
Within the interior of $A_N(x^*,k)$, all three expressions in \eqref{eq:g_def} within an absolute value are positive. It follows that partial derivative of $\log(g)(y_1,\ldots,y_N)$ with respect to $y_i$ within the interior of $A_N(x^*,k)$ is given by
\[
\frac{\partial \log(g)}{\partial y_i} = \frac{(2+\delta) s_i f'(x_i)}{\delta_N } -\frac{(1+\delta) s_i f(x_i)}{\Delta_N  } + \frac{(1+\delta)s_i f(y_i)}{1-\Delta_N }.
\]
We conclude that the gradient of $\log(g)$ vanishes if and only if
\begin{equation}
\label{eq:gradient_zero}
c'(y_i) = \frac{f'(y_i)}{f(y_i)} = \frac{1+\delta}{2+\delta} \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N } \right),\quad i=1,\ldots,N.
\end{equation}
%
Since we assumed that $c'(x)$ is an injection, \eqref{eq:gradient_zero} is satisfied if and only if $y_1 = \ldots = y_N$. In this case, 
$g(y_1,\ldots,y_N) = \eta_\delta(x_{i^*})$  
if $N$ is even. If $N$ is odd and $y_1 = \ldots = y_N > x^*$, then 
\begin{align*}
& g(y_1,\ldots,y_N) = \frac{\left| f(y_1)-f(x_{i^*})  \right|^{2+\delta}} { 
\left|  F(y_1) - F(x_{i^*}) \right|^{1+ \delta} 
\left| 1 - (F(y_1) -F(x_{i^*})) \right|^{1+ \delta} } 
\end{align*} 
which is bounded from from above by $\eta_\delta(x_{i^*})$ by the induction hypothesis. The case where $N$ is odd and $-x^* \leq y_1 = \ldots = y_N$ is similar. 
%
We now consider the possibility that the maximum of $g(y_1,\ldots,y_N)$ is attained at the boundaries of $A_N(x^*,k)$. At boundary points for which $y_i = y_{i+1}$ for some $i$, the contribution of $y_i$ and $y_{i+1}$ to $g(y_1,\ldots,y_N)$ is zero and the induction assumption for $n=N-1$ implies that 
\[
g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*)
\]
The remaining boundary points of $A_N(x^*,k)$ are covered by the following cases:
\begin{itemize}
\item[(1)]  $y_N \to -\infty$. 
\item[(2)] $y_1 \to \infty$.
\item[(3)] $y_k = x_{i^*}$.
\item[(4)] $y_{k+1} = -x_{i^*}$. 
\end{itemize}
For case (1), 
\begin{align*}
g(y_1,\ldots,y_N) \to \frac{ \left| \sum_{i=1}^{k} s_i f(y_i) + s_{i^*} f(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i f(y_i) \right|^{2+\delta}} 
{\left| \sum_{i=1}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i F(y_i) \right|^{1+\delta}\left|1- \left( \sum_{i=1}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i F(y_i) \right)  \right|^{1+\delta} },
\end{align*}
which is smaller than $\eta_\delta(x_{i^*})$ by the induction hypothesis. Similarly, under case (2),
\begin{align*}
& g(y_1,\ldots,y_N) \to 
\frac{ \left| \sum_{i=2}^{k} s_i f(y_i) + s_{i^*} f(x_{i^*}) - \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
{\left| 1+ \sum_{i=2}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta}\left|-\left( \sum_{i=2}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N} s_i F(y_i) \right)  \right|^{1+\delta} },
 \\
& = \frac{ \left| -\sum_{i=2}^{k} s_i f(y_i) - s_{i^*} f(x_{i^*}) + \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
{ \left|1 - \left(-\sum_{i=2}^{k} s_i F(y_i) - s_{i^*} F(x_{i^*}) + \sum_{i=k+1}^{N} s_i F(y_i) \right) \right|^{1+\delta} 
\left|-\sum_{i=2}^{k} s_i F(y_i) - s_{i^*} F(x_{i^*}) + \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta} }
\end{align*}
which is smaller than $\eta_{\delta}(x_{i^*})$ by the induction hypothesis. Under case (3), the terms in $\delta_N$ and $\Delta_N$ corresponding to $y_k$ and $x_{i^*}$ cancel each other. As a result,  $g(y_1,\ldots,y_N)$ reduces to an expression with $n=N-1$ variables hence this case is handled by the induction hypothesis. 
%
Finally, under case (4), set 
\[
d \triangleq s_k F(-x^*) + s_{i^*} F(x^*) = s_{i^*}\left(1-2F(-x^*) \right), 
\]
\[
\sigma \triangleq \sum_{i=1}^{k-1} s_i f(y_i) - \sum_{i=k+1}^{N} s_i f(y_i). 
\]
and 
\[
\Sigma \triangleq \sum_{i=1}^{k-1} s_i F(y_i) - \sum_{i=k+1}^{N} s_i F(y_i). 
\]
We have
\begin{align*}
& g(y_1,\ldots,y_N) =\nonumber  \\ 
& =
\frac{ \left| \sum_{i=1}^{k-1} s_i f(y_i) - \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
{\left| \sum_{i=1}^{k-1} s_i F(y_i) + d(x^*) - \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta} \left|1- \sum_{i=1}^{k-1} s_i F(y_i) - d(x^*) + \sum_{i=k+1}^{N} s_i F(y_i)   \right|^{1+\delta} }, \\
& = \frac{ \left| \sigma \right|^{2+\delta}} 
{\left| \Sigma+d \right|^{1+\delta} \left|1- \Sigma - d \right|^{1+\delta} }  =  
\frac{ \left| \sigma \right|^{2+\delta}} 
{\left| \Sigma \right|^{1+\delta} \left|1- \Sigma \right|^{1+\delta} }  \left| \frac{\Sigma(1-\Sigma) } { \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} \right|^{1+\delta}. 
\end{align*}
By the induction hypothesis,
\[
\frac{ \left| \sigma \right|^{2+\delta}} 
{\left| \Sigma \right|^{1+\delta} \left|1- \Sigma \right|^{1+\delta} } \leq \eta_\delta(x^*), 
\]
hence it is left to show that 
\[
 \frac{\Sigma(1-\Sigma) } { \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} \leq 1.
\]
Whenever $d>0$, 
\begin{align*}
& \frac{ \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} {\Sigma(1-\Sigma)} \geq 1 \Leftrightarrow  1-2\Sigma \geq d, 
\end{align*}
while for $d<0$,
\begin{align*}
& \frac{ \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} {\Sigma(1-\Sigma)} \geq 1 \Leftrightarrow  1-2\Sigma \leq d. 
\end{align*}
Therefore, it is enough to show that $\Sigma \leq F(-x^*)$ if $s_{i^*}=1$ and 
$\Sigma \geq F(-x^*)$ if $s_{i^*}=-1$. 
%
Indeed, if $s_{i^*}=1$, then $s_{k+1}=-1$ and monotonicity of $F(x)$ implies that 
\[
\Sigma + d \leq F(y_1) - F(y_k) + F(x^*) - F(-x^*) + F(y_{k+2}) - F(y_N), 
\]
and hence
\[
\Sigma \leq 1-F(x^*) = F(-x^*). 
\]
Similarly, if $s_{i^*}=-1$ then 
\[
1 - \Sigma \leq 1 -  F(-x^*).
\]
This conclude the proof in the case where $c'(x)$ is an injection. 
\par  
In the case where $c'(x)$ is not necessarily strictly decreasing, we approximate $c(x)$ using another concave symmetric function whose derivative is always negative except, perhaps, at the origin. For $\alpha>0$ consider the function  $f_\alpha(x) = \kappa(\alpha) e^{\sgn(c(x))|c(x)|^{1+\alpha}}$, where $\kappa(\alpha)$ is chosen such that $f_\alpha(x)$ is a probability density function. Then $c_\alpha(x)$ is concave, symmetric, and differentiable with
\[
c_\alpha'(x) \triangleq \frac{f'_\alpha(x)}{f_\alpha(x)} = (1+\alpha)|c(x)|^{\alpha} c'(x). 
\]
Now $c_\alpha'(x)$ is non-increasing since it is the derivative of a concave function. Furthermore, since $c(x)$ is non-constant on any interval and $c'(x)$ is non-increasing, $c_\alpha'(x)$ is non-constant on any interval hence an injection. It follows from the first part of the proof that, for any $\alpha>0$,
\begin{align}
\label{eq:proof:lem:bound_intervals}
\frac{(\delta_{n,\alpha})^2}{\Delta_{n,\alpha}(1-\Delta_{n,\alpha})} \leq \max_i \eta_{\alpha}(x_i),
\end{align}
where 
\[
\delta_{n,\alpha} \triangleq  \sum_{k=1}^{n} (-1)^{k+1} f_{\alpha}(x_k),
\]
\[
\Delta_{n,\alpha} \triangleq \sum_{k=1}^n (-1)^{k+1} F_{\alpha}(x_k), 
\]
and 
\[
\eta_{\delta,\alpha}(x) \triangleq \frac{(f_\alpha(x))^{2+\delta}}{\left(F_{\alpha}(x)(1-F(x)) \right)^{1+\delta}}. 
\]
The proof is completed by noting that 
\begin{align*}
\lim_{\alpha \to 0} \frac{(\delta_{n,\alpha})^{2+\delta} }{ \left(\Delta_{n,\alpha}(1-\Delta_{n,\alpha})\right)^{1+\delta}}  = \frac{(\delta_{n})^{2+\delta }}{\left(\Delta_{n}(1-\Delta_{n}) \right)^{1+\delta}},  
\end{align*}
and, since the maximum is over a finite set,
\begin{align*}
\lim_{\alpha \to 0}  \max_i \eta_{\delta,\alpha}(x_i)  = \max_i\eta_\delta(x_i).
\end{align*}

%Our goal is to construct an approximation to $f(x)$ using a log-concave, symmetric, and differentiable function $\hat{f}(x)$ such that $\hat{f}'(x)/\hat{f}(x)$ is strictly decreasing. We achieve such an approximation by modifying $f(x)$ over intervals over which $c'(x)$ is a constant. Assume first $c'(x)$ is only a constant over an interval $(a_1,b_1)\subset \R$ containing $x_1>0$ and on the mirror image of this interval around $x=0$. Over this interval, $f(x)$ is necessarily of the form $f(x) = e^{-c_1|x| + d_1}$ for some $c_1\geq 0$ and $d_1$. % and For $\alpha>0$, consider
%\[
%F_1(x,\alpha) \triangleq  F(a_1) + \frac{1}{c_1} e^{-c_1 (|x|^{1+\alpha} +d_1}, \quad x \in (a_1,b_1),
%\]
%and 
%\[
%f_1(x,\alpha) \triangleq  F_1'(x,\alpha) =  -\sgn(x)(1+\alpha)|x|^\alpha e^{-c_1 |x|^{1+\alpha} + d_1}, \quad x \in (a_1,b_1).
%\]

\QEDA

### 2019-12-13 proof-sgd.tex
Working on rewriting proof of theorem 2

@@
 \subsection{Proof of Theorem~\ref{thm:sgd}\eqref{item:normal-sgd}}
+\label{sec:proof-normal-sgd}
 
@@
 \subsection{Proof of Theorem~\ref{thm:sgd}\eqref{item:sgd-regular}}
+\label{sec:proof-sgd-regular}
 
-This proof requires somewhat more techinicality than the first part of the
+This proof requires somewhat more technicality than the first part of the
 theorem, including a brief detour into local asymptotic normality theory,
@@
     \label{eqn:sgd-median-regular}
-    \sqrt{n}\left( \bar{\theta}_n - \theta\right)
+    \sqrt{n}\left( \bar{\theta}_n - \theta - h_n / \sqrt{n}\right)
     \mathop{\cd}_{P_n}
@@
 
-\subsubsection*{Proof of Theorem~\ref{thm:sgd}\eqref{item:sgd-ms-convergence}}
+\subsection{Proof of Theorem~\ref{thm:sgd}\eqref{item:sgd-ms-convergence}}
+\label{sec:proof-sgd-ms-convergence}
 
@@
   \label{corollary:polyak-mse}
-  Let
+  Define the iteration
   \begin{align} \label{eq:polyak_new_measurements}
@@
   \end{align}
-  Assume that the function $g(x)$ is twice differentiable with a strictly
-  positive and uniformly bounded second derivative. In particular, $g(x)$ is
-  convex with a unique minimizer $x^\star \in \R$. Moreover, assume that the
-  noises $Z_n$ are uncorrelated and identically distributed with a
-  distribution with a density for which the Fisher information exits. Let
-  $\psi(x)$ and $\chi(x)$ be defined as in
-  Theorem~\ref{corollary:polyak-juditsky}-(iii) and satisfy the conditions
-  there. Assume in addition that $\chi(0)>0$, condition
-  \eqref{eqn:local-hessian-psi} with $\lambda = 1$, and there exits $K_3$ such
-  that
+  Assume that the function $g$ is $\mc{C}^2$, strictly convex, has Lipschitz
+  derivative, and is minimized by $x^\star$. Moreover, assume that the
+  noises $Z_n$ are i.i.d.\ with density $p$ and
+  that the Fisher information $\E[(p'(Z))^2 / p(Z)^2]$ exists and is finite.
+  Let $\psi(x)$ and $\chi(x)$ be defined as in
+  Corollary~\ref{corollary:polyak-juditsky} and satisfy the conditions in
+  the corollary. Assume in addition that $\chi(0)>0$, condition
+  \eqref{eqn:local-hessian-psi} with $\lambda = 1$, and there exits $K_3$
+  such that
   \begin{equation*}
@@
   \end{equation*}
-  Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
+  Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions
+  \eqref{eqn:lazy-gamma} and \eqref{eqn:stringent-gamma}. Then
   \begin{equation*}
-    V_n \triangleq \ex{ \left(\bar{U}_n-x^\star \right)^2 } = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
+    V_n \defeq
+    \E\Big[(\bar{U}_n-x^\star )^2\Big] = n^{-1}\frac{\chi(0)} {
+      (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
   \end{equation*}
@@
 
-We now use Theorem~\ref{thm:polyak_new} with $g(x) = 0.5(x-\theta)^2$, $\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$. From \eqref{eq:polyak_new_measurements} we have
+We apply Corollary~\ref{corollary:polyak-mse} with $g(x) = 0.5(x-\theta)^2$,
+$\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$.
+The update~\eqref{eq:polyak_new_measurements} gives
 \begin{align*} 
-U_n & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
+  U_n %% & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
   & = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
 \end{align*}
-so the estimator $\bar{U}_n$ equals to the one defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg}. Note that
-\begin{equation*}
-\ex{ | \varphi(x+Z_1) |^4 } = 1 \leq K_3(1+|x|^4)
-\end{equation*}
-for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
-the conditions in Theorem~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
+so the estimator $\bar{U}_n$ is identical to the stochastic gradient
+estimator~\eqref{eq:sgd_est}. We have $\E[\varphi(x + Z)^4] = 1$ and by
+assumption the Fisher information $\E[(f'(Z))^2 / f(Z)^2]$ exists, and the
+functions $\psi$ and $\chi$ have the desired conditions of
+Corollary~\ref{corollary:polyak-juditsky} (as we verify in
+Section~\ref{sec:proof-normal-sgd}). Finally, the function $\theta \mapsto
+\E_{P_\theta}[(\bar{\theta}_n - \theta)^2]$ is continuous in $\theta$, so
+that for $x^\star = \theta$ and $g'' \equiv 1$, we may apply
+Corollary~\ref{corollary:polyak-mse} and a finite approximation to the prior
+measure $\pi$ to obtain
+Theorem~\ref{thm:sgd}\eqref{item:sgd-ms-convergence}.
+
+%% \begin{equation*}
+%% \ex{ | \varphi(x+Z_1) |^4 } = 1 \leq K_3(1+|x|^4)
+%% \end{equation*}
+%% for any $K_3\geq 1$, the Fisher information of $Z_1$ is $\sigma^2$, $\chi(x) = 1 > 0$, and that 
+%% the conditions in Theorem~\ref{thm:polyak_new} on $\psi(x)$ and $\chi(x)$ were verified to hold in the first part of the proof.
 In particular, $\psi'(0) = (2f(0))^{-2}$.
@@
 Theorem~\ref{thm:polyak_new} implies that for any $\theta \in \R$,
-\begin{equation*}
-V_n = \ex{ \left({\theta}_n-\theta \right)^2 } = \frac{1}{4n f^2(0)} + o(n^{-1}).
-\end{equation*}
+%% \begin{equation*}
+%% V_n = \ex{ \left({\theta}_n-\theta \right)^2 } = \frac{1}{4n f^2(0)} + o(n^{-1}).
+%% \end{equation*}
 

### 2019-12-13 uniform-are-weirdos.tex
Working on rewriting proof of theorem 2

% -*- Mode: latex -*- %

\section{Fast convergence of uniform estimators under bit constraints}
\label{sec:uniform-weirdos}

Here we consider the uniform distribution as our location family,
demonstrating that in the adaptive setting~\eqref{item:adaptive} or even the
one-step adaptive setting~(\ref{item:one-step-adaptive}'), constrained
estimators can attain rates faster than the $1 / \sqrt{n}$ rates regular
estimands allow. Indeed, define $c(x) = -\log 2$ for $x \in [-1, 1]$ and
$c(x) = -\infty$ for $x \not \in [-1, 1]$. Then $f(x) = e^{-c(x)}$ is
log-concave and symmetric, and we may consider the location family with
densities $f(x - \theta)$. For notational simplicity, we assume we have
a sample of size $2n$. We provide a proof sketch that
there is a one-step adaptive estimator $\theta_n$ such that
\begin{equation}
  \label{eqn:uniforms-are-easy}
  \sup_{|\theta| \le \log n}
  P_\theta\left(|\theta_n - \theta| \ge \frac{8 \log n}{n^{3/4}}\right)
  \le \frac{2}{n^2}.
\end{equation}
for all large $n$,
and so (by the Borel-Cantelli lemmas), for any $\theta \in \R$ we have
$P_\theta(|\theta_n - \theta| \le \sqrt{2 \log n} / n^{3/4} ~
\mbox{eventually}) = 1$. This is of course faster than the $1/\sqrt{n}$
rates we prove throughout.

To prove inequality~\eqref{eqn:uniforms-are-easy}, we proceed in two steps,
both quite similar.
First, we define an initial estimator $\theta\init_n$.
Let $\epsilon > 0$, which we will determine presently, though we will
take $n \epsilon \to \infty$ as $n \to \infty$, so that we may assume
w.l.o.g.\ that $\theta \in [-n\epsilon/2, n \epsilon/2]$. Take the interval
$[-n\epsilon, n\epsilon]$, and construct
$m$ thresholds at intervals of size $2 n \epsilon / m$; let
the $j$th such threshold be
\begin{equation*}
  t_j \defeq -n \epsilon + \frac{2 n (j-1) \epsilon}{m}
\end{equation*}
Then we ``assign'' observations to each pair of thresholds, so that
threshold $j$ corresponds to observations $I_j \defeq \{\frac{n (j - 1)}{m}
+ 1, \ldots, \frac{n j}{m}\}$, of which there are $n/m$.  For each index $i
\in I_j$, we set
\begin{equation*}
  B_i = \begin{cases}
    1 & \mbox{if~} X_i \ge t_j \\
    0 & \mbox{otherwise}.
  \end{cases}
\end{equation*}
Then we simply set $\theta_n\init$ to be the maximal threshold for which
$B_i = 0$ for all observations $X_i$ corresponding to that threshold.

Let us now consider the probability that $\theta_n\init$ is substantially
wrong. For notational simplicity, let $U_i = (1 + X_i - \theta) / 2$, so that
the $U_i$ are uniform on $[0, 1]$.
First, note that we always have $\theta_n\init \ge \theta
- \frac{2 n \epsilon}{m}$, because no observations will be below
the appropriate threshold. Let $j\opt$ be the smallest index $j$
for which $\theta \le t_{j\opt}$, and consider
the index sets $I_{j\opt}$, $I_{j\opt + 1}$, and so on.
The event $\theta\init_n \ge t_{j\opt} + \frac{2 n \epsilon}{m}$ may
occur only if for each of the $n/m$ observations in the set
$I_{j\opt + 1}$, we have $U_i \ge \frac{n \epsilon}{m}$. Thus,
\begin{equation*}
  P_\theta\left(\theta_n\init \ge t_{j\opt} + \frac{2 n \epsilon}{m}
  \right)
  \le \left(1 - \frac{n \epsilon}{m}\right)^\frac{n}{m}
  \le \exp\left(-\frac{n^2\epsilon}{m^2}\right).
\end{equation*}
Setting the number of bins $m = \sqrt{n}$,
the resolution $\epsilon = 2 \log n / n$, we obtain
$P_\theta(\theta_n\init \ge t_{j\opt} + 4 \log n / \sqrt{n})
\le n^{-2}$. Thus we have
\begin{equation}
  \label{eqn:quality-of-initial-estimate}
  \sup_{|\theta| \le \log n} P_\theta\left(|\theta_n\init - \theta| \ge
  \frac{8 \log n}{\sqrt{n}}\right) \le \frac{1}{n^2}.
\end{equation}

The second stage estimator follows roughly the same strategy, except that
the resolution of the bins is tighter. In particular, let us assume that
$|\theta_n\init - \theta| \le \frac{8 \log n}{\sqrt{n}}$, which happens
eventually by inequality~\eqref{eqn:quality-of-initial-estimate}.  (We will
assume this tacitly for the remainder of the argument.)  Consider the
interval $\Theta_n \defeq \theta_n\init + [-\frac{16 \log n}{\sqrt{n}},
  \frac{16 \log n}{\sqrt{n}}]$ centered at $\theta_n\init$; we know that the
interval includes $[\theta - \frac{8 \log n}{\sqrt{n}}, \theta + \frac{8
    \log n}{\sqrt{n}}]$. Without loss of generality we assume $\theta_n\init
= 0$.  Following precisely the same discretization strategy as that for
$\theta_n\init$, we divide $\Theta_n$ into $m$ equal intervals, with
thresholds $t_j = -\frac{16 \log n}{\sqrt{n}} + \frac{32 (j - 1) \log n}{m
  \sqrt{n}}$; let $\epsilon_n = \frac{32 \log n}{m \sqrt{n}}$ be the width of
these intervals.  Then following exactly the same reasoning as above, we
assign indices $I_j = \{\frac{n(j - 1)}{m} + 1, \ldots, \frac{n j}{m}\}$ and
for $i \in I_j$, set $B_i = 1$ if $X_i \ge t_j$. We define $\theta_n$ to be
the maximal threshold $t_j$ for which $B_i = 0$ for all observations $X_i
\in I_j$. Then following precisely the reasoning above, we have (on the
event that $|\theta_n\init - \theta| \le \frac{8 \log n}{\sqrt{n}}$)
\begin{equation*}
  P_\theta(|\theta_n - \theta|
  \ge 2 \epsilon_n)
  \le (1 - \epsilon_n)^\frac{n}{m}
  \le \exp\left(-\frac{n \epsilon_n}{m}\right)
  = \exp\left(-\frac{32 \sqrt{n} \log n}{m^2}\right).
\end{equation*}
Set $m = 4 n^{1/4}$ to obtain the claimed
result~\eqref{eqn:uniforms-are-easy}.

\subsection{Proof of Proposition~\ref{prop:CEO}
\label{app:proof:CEO}}

%
Denote by $D^\star$ the optimal MSE in the Gaussian CEO with $L$ observers and under a total sum-rate $r = r_1 + \ldots +r_L$. An expression for $D^\star$ as a function of $r$ is give as \cite[Eq. 10]{chen2004upper}:
\begin{equation} \label{eq:ceo_optimal_sumrate}
r = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
\end{equation}
For the special case where $r = n$ and $L=n$, we have
\begin{equation} \label{eq:ceo_optimal_sumrate2}
n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
\end{equation}
Consider the distributed encoding setting (iii) in the case where $f(x) = \Ncal(0,\sigma^2)$ and the prior on $\Theta$ is $\pi = \Ncal(0,\sigma_\theta^2)$. The Gaussian CEO problem of \cite{viswanathan1997quadratic} with a unit bitrate $r_1=\ldots = r_n =1$ at each terminal and blocklength $k=1$ reduces to our distributed setting (iii). Since $D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describes the MSE in the CEO setting under an optimal allocation of the sum-rate $r = n$ among $n$ encoders, it provides a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting. By considering the limit $n\rightarrow \infty$ in \eqref{eq:ceo_optimal_sumrate2}, we see that 
\[
D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
\]
This implies Proposition~\ref{prop:CEO}. 
%We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the MSE in the CEO setting while enforcing the condition $r_1=\ldots = r_n = 1$. Indeed, an upper bound for the CEO MSE under the condition $r_1=\ldots = r_n = 1$ follows from \cite{KipnisRini2019}, and leads to
%\[
%D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
%\]
%which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.

### 2019-12-13 adaptive-estimation.tex
Giving the one step estimator proof

@@
 asymptotic optimality results of the averaged stochastic gradient
-sequence.
+sequence. Specifically, the average of the stochastic gradient
+iterates~\eqref{eq:sgd_alg}
+is locally asymptotically minimax, and they achieve the lower
+bound of Theorem~\ref{thm:adpative_lower_bound}.
+
 \begin{corollary}
@@
   \item If in addition the stepsizes satisfy
-    condition~\eqref{eqn:stringent-gamma}, then for any
-    prior $\pi$ on $\R$, we have
-    \begin{equation*}
-      \int \E\left[(\bar{\theta}_n - \theta)^2\right] d\pi(\theta)
-      = \frac{1}{4 n f(0)^2} + o(n^{-1}).
-    \end{equation*}
+    condition~\eqref{eqn:stringent-gamma}, then they
+    achieve the lower bound of Theorem~\ref{thm:adpative_lower_bound} for any
+    prior $\pi$ on $\R$.
   \end{enumerate}
 \end{corollary}
-\noindent
 
-Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the maximal ARE, as established by Theorem~\ref{thm:adpative_lower_bound}.
+%% Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the maximal ARE, as established by Theorem~\ref{thm:adpative_lower_bound}.
 %Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$.
-%
-The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$.
+%% %
+%% The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$.
 Consequently, the procedure above is known as averaged stochastic gradient descent for minimizing $x \to |x|$ given the data $X_1,\ldots,X_n$.
@@
 Part (iii) provides an additional condition under which $\bar{\theta}$ also converges in its second moment.
- \par
-%Note that $\theta_0$ is not explicitly defined in equation \eqref{eq:sgd_est}.
-A reasonable initialization for $\theta_0$ is $\theta_0 = \mathbb E [\theta]$, although Theorem~\ref{thm:sgd} implies that the asymptotic behavior of the estimator is indifferent to this initialization.
-Thus, the optimal efficiency is attained regardless of the prior distribution on $\theta$ or the radius of the parameter space $\Theta$.
-\\
-In the encoding and estimating procedure \eqref{eq:sgd_alg} and \eqref{eq:sgd_est}, each one-bit message $B_n$ depends on its private sample as well as the current gradient descent estimate $\theta_{n-1}$.
-In this sense, each encoder in this algorithm interacts with previous one by using the current estimate.
-%
-As we explain next, 
-it is possible to obtain the optimal efficiency of $\eta(0)\sigma^2$ with only one round of interactions among the encoders.
 
@@
 \subsection{Maximal Efficiency using One Round of Threshold Adaptation}
-In Section~\ref{sec:preliminary} we considered an estimator that is based on binary messages of the form 
+
+In the encoding and estimating procedure \eqref{eq:sgd_alg}, each one-bit
+message $B_n$ depends on its private sample as well as the current gradient
+descent estimate $\theta_{n-1}$. In this sense, each encoder in this
+algorithm interacts with previous one by using the current estimate.  This
+amount of adaptivity is unnecessary: as we now consider, a similar encoding
+yields an asymptotically normal estimator attaining the lower variance bound
+$1/\eta(0)$, provided we allow \emph{one} adaptive update to the threshold
+value $\theta_0$ based on previously observed bits.
+%
+In this procedure we separate the sample into the disjoint sets
+$X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.  We
+first use the estimator \eqref{eq:estimator_naive} to obtain an estimate
+${\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use
+${\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1},
+\ldots, B_n$. Figure~\ref{fig:one_round} illustrates a diagram of this
+procedure.
+
+More formally, we consider the following estimation scheme. Given
+$n_1 \in \{1, \ldots, n\}$,
+set the individual bits
 \begin{equation*}
-B_i = \mathbf 1_{X_i > \theta_0},\qquad i=1,\ldots,n,
-\end{equation*}
-and deduced that it is asymptotically normal with variance $1/\eta(\theta-\theta_0)$.
-%
-We now show that a similar encoding leads to an asymptotically normal estimator attaining the lower variance bound $1/\eta(0)$, provided we allow to  update the threshold value $\theta_0$ based on previously observed bits at least once.
-%
-In this procedure we separate the sample into two disjoint sets: $X_1,\ldots,X_{n_1}$ and $X_{n_1+1},\ldots,X_n$ for some $n_1 < n$.
-We first use the estimator \eqref{eq:estimator_naive} to obtain an estimate ${\theta}_{n_1}$ based on $B_1,\ldots,B_{n_1}$, and then use ${\theta}_{n_1}$ as the new threshold value to obtain messages $B_{n_1+1}, \ldots, B_n$.
-Figure~\ref{fig:one_round} illustrates a diagram of this procedure.
-%
-The specific encoding and estimation scheme, as well as its asymptotic performance, are given by the following theorem:
-\begin{thm}
-For $i=1,\ldots,n$ set
-\begin{equation*}
-B_i = \begin{cases}
- \mathbf 1_{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
- \mathbf 1_{X_i \geq {\theta}_{n_1} }& i={n_1+1,\ldots,n},
+  B_i =
+  \begin{cases}
+    \indic{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
+    \indic{X_i \geq T_n}& i={n_1+1,\ldots,n},
   \end{cases}
 \end{equation*}
-where $n = n_1+ n_2$ and 
+where
 \begin{equation*}
-{\theta}_{n_1} \triangleq \theta_0 + F^{-1}\left(
+  T_n \defeq \theta_0 + F^{-1}\left(
   \frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
- \right).
+  \right)
+  ~~ \mbox{and} ~~
+  \theta_n \defeq
+  \theta_{n_1} + F^{-1} \left(\frac{1}{n - n_1}
+  \sum_{i = n_1}^n B_i \right).
 \end{equation*} 
-Let 
-\begin{equation*}
-{\theta}_{n_2}  \triangleq {\theta}_{n_1} +  F^{-1} \left( \frac{1}{n_2} \sum_{i=n_1+1}^{n_2} B_i \right)
-\end{equation*}
-and assume that, as $n\to \infty$, $n_1(n) \rightarrow \infty$ and $n_2(n)/n \rightarrow 1$. Then:
+Then
+\begin{thm}
+  Assume that as $n\to \infty$, $n_1(n) \rightarrow \infty$ and $n_1 / n \to
+  0$. Then
   \begin{align*}
- \sqrt{n} \left( {\theta}_{n_2} - \theta  \right) \overset{d}{\longrightarrow}  \Ncal\left( 0, 1/\eta(0) \right).
+    \sqrt{n} \left( {\theta}_n - \theta  \right)
+    \cd  \normal\left( 0, 1/\eta(0) \right).
   \end{align*}
@@
 \begin{proof}
-For $t\in \mathbb R$, set
+  We abuse notation and instead of assuming we receive $n$ observations, assume
+  we receive the $n + n_1$ observations $X_{-n_1}, \ldots, X_{-1}$ and
+  $X_1, \ldots, X_n$, defining $T_n = \theta_0 + F^{-1}(\frac{1}{n_1}
+  \sum_{i = -n_1}^{-1} B_i)$ and
+  $B_i = \indic{X_i \ge T_n}$ for $i \ge 1$.
+  By continuity, we have $T_n \cas \theta$ as $n_1 \to \infty$.
+  Let
+  $E_n = \E[B_i \mid T_n] = P(X_i \ge T_n)$,
+  so that $V_n \defeq \var(B_i \mid T_n) = E_n(1 - E_n)$. Define also the random
+  variable
   \begin{equation*}
-p_{n_2}(t) \triangleq \frac{1}{n_2} \sum_{i=n_1+1}^{n} \mathbf 1_{X_i \geq t}. 
+    Y_n \defeq \frac{1}{\sqrt{n}} \sum_{i = 1}^n \frac{B_i - E_i}{
+      \sqrt{E_n (1 - E_n)}},
   \end{equation*}
-Since $n_2(n)/n \to 1$, if follows from the Berry Esseen theorem that there exists $C$, independent of $n$ and $t$, such that 
-\begin{align*}
-\sup_{t \in \R} \left| \sqrt{n} \frac{ p_{n_2}(t) - F( \theta - t)} {F(\theta - t) F \left( t - \theta\right) }  - \Phi(t) \right|  \leq C/\sqrt{n}. 
-\end{align*}
-where $Z \sim \Ncal(0,1)$. It follows that
-\begin{align}
-\label{eq:two_step_proof}
- \sqrt{n} \frac{ p_{n_2}(Y_n) - F(0)} {F^2(0) }  \overset{d}{\rightarrow} \Ncal(0,1)
-\end{align}
-for any sequence of random variables $\{Y_n\}$ converging in probability to $\theta$. In particular, since
+  and let $F_n(\cdot \mid T_n)$ be its cumulative distribution function.
+  Then because
   \begin{equation*}
-p_{n_1} \triangleq \frac{1}{n_1} \sum_{i=1}^{n_1} B_i \overset{a.s.}{\rightarrow} F(\theta - \theta_0)
+    \E\left[|B_i - E_n|^3 \mid T_n\right] \le V_n = E_n(1 - E_n)
+    ~~ \mbox{we have} ~~
+    \E\left[\frac{|B_i - E_n|^3}{(E_n(1 - E_n))^{3/2}} \mid T_n\right]
+    \le \frac{1}{\sqrt{V_n}}.
   \end{equation*}
-by the law of large numbers, \eqref{eq:two_step_proof} holds for $Y_n = \theta_{n_1}$. Finally, we use the delta method with $g(x) = F^{-1}(x)$ to conclude
-\begin{align*}
-& \sqrt{n}\left( \theta_{n_2} - \theta \right) = \sqrt{n} \left( \theta_{n_1} + F^{-1}(p_{n_2}(\theta_{n_1})) - \theta \right) \\
-&= \sqrt{n} \left( g(p_{n_2}(\theta_{n_1})) - g \left(F(\theta-\theta_{n_1}) \right)  \right) \overset{d}{\to} \Ncal\left(0, 
-F^2(0)/ f^2(0) \right).
-\end{align*}
+  Then the Berry-Esseen theorem implies that there exists a constant
+  $C \le 1$ such that
+  \begin{equation*}
+    \sup_t \left|F_n(t \mid T_n) - \Phi(t) \right|
+    \le \frac{C}{\sqrt{V_n} \sqrt{n}} \wedge 2,
+  \end{equation*}
+  where $\Phi$ is the standard Gaussian CDF.
+  As $V_n \cas \frac{1}{4}$ by definition of the median,
+  we have
+  that (with probability 1)
+  \begin{equation*}
+    \sup_t \left|F_n(t \mid T_n) - \Phi(t)\right| \le \frac{C}{\sqrt{n}}
+    ~~ \mbox{eventually}.
+  \end{equation*}
+  By dominated convergence and Jensen's inequality we thus obtain
+  \begin{equation*}
+    \sup_t \left|\mathbb{P}(Y_n - \theta \le t) - \Phi(t)\right|
+    \le \E\left[
+      \sup_t \left|F_n(t \mid T_n) - \Phi(t)\right| \right]
+    \to 0,
+  \end{equation*}
+  which gives the result when combined with Slutsky's lemmas.
 \end{proof}

### 2019-12-13 adaptive-estimation.tex
Fixed up the most recent broken proof

@@
   \begin{cases}
-    \indic{X_i \geq \theta_0} & i = 1,\ldots,n_1, \\
-    \indic{X_i \geq T_n}& i={n_1+1,\ldots,n},
+    \indic{X_i \le \theta_0} & i = 1,\ldots,n_1, \\
+    \indic{X_i \le T_n}& i={n_1+1,\ldots,n},
   \end{cases}
@@
 \begin{equation*}
-  T_n \defeq \theta_0 + F^{-1}\left(
+  T_n \defeq \theta_0 - F^{-1}\left(
   \frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
@@
   \theta_n \defeq
-  \theta_{n_1} + F^{-1} \left(\frac{1}{n - n_1}
+  T_n - F^{-1} \left(\frac{1}{n - n_1}
   \sum_{i = n_1}^n B_i \right).
 \end{equation*} 
-Then
+The intuition here is that the estimator $\theta_n$ is a one-step
+correction (cf.~\cite[Thm.~6.4.3]{LehmannCa98}) of the initial estimator
+$T_n$, which approximately estimates
+$\theta_0 - F^{-1}(\theta_0 - \theta) = \theta$. We then have the
+following convergence result.
 \begin{thm}
-  Assume that as $n\to \infty$, $n_1(n) \rightarrow \infty$ and $n_1 / n \to
+  Assume that $X_i = Z_i + \theta$, where $Z_i$ are i.i.d.\
+  with density $f$ and CDF $F$ and $\mbox{med}(Z_i) = 0$. Assume that
+  $f$ is continuous at 0, and that as $n \to \infty$,
+  $n_1(n) \rightarrow \infty$ and $n_1 / n \to
   0$. Then
@@
     \sqrt{n} \left( {\theta}_n - \theta  \right)
-    \cd  \normal\left( 0, 1/\eta(0) \right).
+    \cd  \normal\left( 0, \frac{1}{4 f(0)^2}\right).
   \end{align*}
 \end{thm}
-%
+\noindent
+That is, under Assumption~\ref{assump:failure_rate}, the method is
+asymptotically optimal.
 %
@@
   we receive the $n + n_1$ observations $X_{-n_1}, \ldots, X_{-1}$ and
-  $X_1, \ldots, X_n$, defining $T_n = \theta_0 + F^{-1}(\frac{1}{n_1}
+  $X_1, \ldots, X_n$, defining $T_n = \theta_0 - F^{-1}(\frac{1}{n_1}
   \sum_{i = -n_1}^{-1} B_i)$ and
-  $B_i = \indic{X_i \ge T_n}$ for $i \ge 1$.
-  By continuity, we have $T_n \cas \theta$ as $n_1 \to \infty$.
-  Let
-  $E_n = \E[B_i \mid T_n] = P(X_i \ge T_n)$,
-  so that $V_n \defeq \var(B_i \mid T_n) = E_n(1 - E_n)$. Define also the random
+  $B_i = \indic{X_i \le T_n}$ for $i \ge 1$.
+  Letting $X_i = Z_i + \theta$ for $Z_i$ i.i.d.\ with fixed density
+  $f = F'$, we have
+  $B_i \cas F(\theta_0 - \theta)$, so that
+  $\frac{1}{n_1} \sum_{i = -n_1}^{-1} B_i \cas F(\theta - \theta_0)$ and
+  by the continuous
+  mapping theorem we have $T_n \cas \theta$ as $n_1 \to \infty$.
+
+  Now let
+  $E_n = \E[B_i \mid T_n] = P(X_i \le T_n)$,
+  so that $\var(B_i \mid T_n) = E_n(1 - E_n)$. Define also the random
   variable
   \begin{equation*}
-    Y_n \defeq \frac{1}{\sqrt{n}} \sum_{i = 1}^n \frac{B_i - E_i}{
-      \sqrt{E_n (1 - E_n)}},
+    Y_n \defeq \sqrt{n}
+    \frac{1}{\sqrt{E_n (1 - E_n)}}
+    \bigg[\frac{1}{n}\sum_{i = 1}^n B_i - E_n\bigg],
   \end{equation*}
@@
   \begin{equation*}
-    \E\left[|B_i - E_n|^3 \mid T_n\right] \le V_n = E_n(1 - E_n)
+    \E\left[|B_i - E_n|^3 \mid T_n\right] \le E_n(1 - E_n)
     ~~ \mbox{we have} ~~
     \E\left[\frac{|B_i - E_n|^3}{(E_n(1 - E_n))^{3/2}} \mid T_n\right]
-    \le \frac{1}{\sqrt{V_n}}.
+    \le \frac{1}{\sqrt{E_n(1 - E_n)}},
   \end{equation*}
-  Then the Berry-Esseen theorem implies that there exists a constant
+  the Berry-Esseen theorem implies that there exists a constant
   $C \le 1$ such that
@@
     \sup_t \left|F_n(t \mid T_n) - \Phi(t) \right|
-    \le \frac{C}{\sqrt{V_n} \sqrt{n}} \wedge 2,
+    \le \frac{C}{\sqrt{E_n (1 - E_n)} \sqrt{n}} \wedge 2,
   \end{equation*}
   where $\Phi$ is the standard Gaussian CDF.
-  As $V_n \cas \frac{1}{4}$ by definition of the median,
+  As $E_n (1 - E_n) \cas \frac{1}{4}$ by definition of the median,
   we have
@@
   \begin{equation*}
-    \sup_t \left|\mathbb{P}(Y_n - \theta \le t) - \Phi(t)\right|
+    \sup_t \left|\mathbb{P}(Y_n \le t) - \Phi(t)\right|
     \le \E\left[
@@
   \end{equation*}
-  which gives the result when combined with Slutsky's lemmas.
+  which gives that $Y_n \cd \normal(0, 1)$.
+
+  Now,
+  Slutsky's lemmas imply
+  \begin{equation}
+    \sqrt{n}
+    \cdot \frac{2}{n} \sum_{i = 1}^n (B_i - E_n)
+    =
+    (1 + o_P(1)) \frac{1}{\sqrt{n E_n(1 - E_n)}}
+    \sum_{i = 1}^n \left(B_i - E_n\right)
+    \cd \normal(0, 1).
+    \label{eqn:apply-slutsky}
+  \end{equation}
+  For shorthand we write $P_n B = \frac{1}{n} \sum_{i = 1}^n B_i$,
+  and using that $E_n = \E[B_i \mid T_n] = F(T_n - \theta)$, we may thus
+  use the delta method to write
+  \begin{align*}
+    \sqrt{n}(\theta_n - \theta)
+    & = \sqrt{n}\left(T_n - F^{-1}\left(P_n B\right)
+    - \theta \right) \\
+    & = \sqrt{n} \left(T_n - F^{-1}\left(F(T_n - \theta)
+    + P_n B - F(T_n - \theta)\right) - \theta \right) \\
+    & = \sqrt{n} \left(T_n - (T_n - \theta )
+    + (F^{-1})'(T_n - \theta + o_P(1))\cdot \left(
+    P_n B - E_n\right) \right) \\
+    & = \sqrt{n} (F^{-1})'(0) (P_n B - E_n)
+    + o_P(1)
+    \cd \normal\left(0, \frac{1}{4 f(0)^2}\right),
+  \end{align*}
+  where we have used the limiting distribution~\eqref{eqn:apply-slutsky}.
 \end{proof}

### 2019-12-14 adaptive-estimation.tex
Starting to work on distributed part

@@
 \begin{center}
-%% \begin{tikzpicture}[scale = 0.6]
-%% \begin{axis}[
-%% width=10cm, height=6cm,
-%% xmin = 0, xmax=800, 
-%% restrict y to domain = 0:3,
-%% ymin = 0,
-%% ymax = 3.4,
-%% samples=10, 
-%% xlabel= $n$,
-%% ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
-%% %xtick={-3,-2,-1,0,1,2,3},
-%% %xticklabels={-3,-2,-1,0,1,2,3},
-%% ytick={0,1,1.57},
-%% yticklabels={0,1,$\pi/2$},
-%% line width=1.0pt,
-%% mark size=1.5pt,
-%% ymajorgrids,
-%% xmajorgrids,
-%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-%% ]
+\begin{tikzpicture}[scale = 0.6]
+\begin{axis}[
+width=10cm, height=6cm,
+xmin = 0, xmax=800, 
+restrict y to domain = 0:3,
+ymin = 0,
+ymax = 3.4,
+samples=10, 
+xlabel= $n$,
+ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
+%xtick={-3,-2,-1,0,1,2,3},
+%xticklabels={-3,-2,-1,0,1,2,3},
+ytick={0,1,1.57},
+yticklabels={0,1,$\pi/2$},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
 
-%% \addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-%% \addlegendentry{asymptotically optimal};
+\addplot[color = blue, solid, smooth] plot table [x = itr, y = SGD, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
+\addlegendentry{asymptotically optimal};
 
-%% %\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
+%\addplot[color = red, solid, smooth] plot table [x = itr, y = Bayes, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};\addlegendentry{one step optimal};
 
-%% \addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-%% \addlegendentry{single interaction};
+\addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
+\addlegendentry{single interaction};
 
-%% \end{axis}
-%% \end{tikzpicture}
+\end{axis}
+\end{tikzpicture}
 \caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density.

### 2019-12-14 distributed-estimation.tex
Starting to work on distributed part

@@
   \begin{center}
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmax=2.5, 
-xmode = log,
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=1, 
-xlabel= {$\sigma/T$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,0.637,1},
-yticklabels={0,$2/\pi$,1},
-ylabel = {$\ARE$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{optimal threshold density};
+%% \begin{tikzpicture}[scale = 1]
+%% \begin{axis}[
+%% width=8cm, height=6cm,
+%% xmax=2.5, 
+%% xmode = log,
+%% restrict y to domain = 0:100,
+%% ymin = 0,
+%% ymax = 1,
+%% samples=1, 
+%% xlabel= {$\sigma/T$},
+%% %xtick={-0.5,0,0.5},
+%% %xticklabels={-$$, 0, $b$},
+%% ytick={0,0.637,1},
+%% yticklabels={0,$2/\pi$,1},
+%% ylabel = {$\ARE$},
+%% line width=1.0pt,
+%% mark size=1.5pt,
+%% ymajorgrids,
+%% xmajorgrids,
+%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+%% ]
+%% \addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
+%% \addlegendentry{optimal threshold density};
 
-\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{uniform threshold desnity};
-\end{axis}
-\end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \Ncal(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
+%% \addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
+%% \addlegendentry{uniform threshold desnity};
+%% \end{axis}
+%% \end{tikzpicture}
+%% \caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \Ncal(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
 The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
 }.
-\end{center}
-\end{figure}
+%% \end{center}
+%% \end{figure}
 
-%We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
+%% %We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
 Next, we prove that with any set of messages obtained via a distributed strategy, there exists at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
 
-\begin{figure}
-\begin{center}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 4$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma/\sigma_{\theta} = 3$},
-xticklabels={-$T$, 0, $T$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/\sigma_{\theta} = 2$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-title = {$\sigma/\sigma_{\theta} = 1$},
-ytick={0,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
+%% \begin{figure}
+%% \begin{center}
+%% %
+%% \begin{tikzpicture}[scale = 0.55]
+%% \begin{axis}[
+%% width=8cm, height=6cm,
+%% xmin = -0.5, xmax=0.5, 
+%% restrict y to domain = 0:100,
+%% ymin = 0,
+%% ymax = 1,
+%% samples=10, 
+%% xlabel= {$dt$},
+%% title = {$\sigma/\sigma_{\theta} = 4$},
+%% xtick={-0.5,0,0.5},
+%% xticklabels={-$T$, 0, $T$},
+%% ytick={0,1},
+%% ylabel = {$\lambda(dt)$},
+%% yticklabels={0,1},
+%% line width=1.0pt,
+%% mark size=1.5pt,
+%% ymajorgrids,
+%% xmajorgrids,
+%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+%% ]
+%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
+%% %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
+%% \end{axis}
+%% \end{tikzpicture}
+%% %
+%% \begin{tikzpicture}[scale = 0.55]
+%% \begin{axis}[
+%% width=8cm, height=6cm,
+%% xmin = -0.5, xmax=0.5, 
+%% restrict y to domain = 0:100,
+%% ymin = 0,
+%% ymax = 1,
+%% samples=10, 
+%% xlabel= {$dt$},
+%% xtick={-0.5,0,0.5},
+%% title = {$\sigma/\sigma_{\theta} = 3$},
+%% xticklabels={-$T$, 0, $T$},
+%% ytick={0,1},
+%% %ylabel = {$\lambda(dt)$},
+%% yticklabels={0,1},
+%% line width=1.0pt,
+%% mark size=1.5pt,
+%% ymajorgrids,
+%% xmajorgrids,
+%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+%% ]
+%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
+%% %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
+%% \end{axis}
+%% \end{tikzpicture}
+%% %
+%% \begin{tikzpicture}[scale = 0.55]
+%% \begin{axis}[
+%% width=8cm, height=6cm,
+%% xmin = -0.5, xmax=0.5, 
+%% restrict y to domain = 0:100,
+%% ymin = 0,
+%% ymax = 1,
+%% samples=10, 
+%% xlabel= {$dt$},
+%% title = {$\sigma/\sigma_{\theta} = 2$},
+%% xtick={-0.5,0,0.5},
+%% xticklabels={-$T$, 0, $T$},
+%% ytick={0,1},
+%% ylabel = {$\lambda(dt)$},
+%% yticklabels={0,1},
+%% line width=1.0pt,
+%% mark size=1.5pt,
+%% ymajorgrids,
+%% xmajorgrids,
+%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+%% ]
+%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
+%% %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
+%% \end{axis}
+%% \end{tikzpicture}
+%% %
+%% \begin{tikzpicture}[scale = 0.55]
+%% \begin{axis}[
+%% width=8cm, height=6cm,
+%% xmin = -0.5, xmax=0.5, 
+%% restrict y to domain = 0:100,
+%% ymin = 0,
+%% ymax = 1,
+%% samples=10, 
+%% xlabel= {$dt$},
+%% xtick={-0.5,0,0.5},
+%% xticklabels={-$T$, 0, $T$},
+%% title = {$\sigma/\sigma_{\theta} = 1$},
+%% ytick={0,1},
+%% %ylabel = {$\lambda(dt)$},
+%% yticklabels={0,1},
+%% line width=1.0pt,
+%% mark size=1.5pt,
+%% ymajorgrids,
+%% xmajorgrids,
+%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+%% ]
+%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
+%% %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
+%% \end{axis}
+%% \end{tikzpicture}
 \caption{\label{fig:opt_density}
@@
 %Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
-
-\iffalse
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[scale = 1]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = 0, xmax=2, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 10,
-samples=1, 
-xlabel= {$\sigma/\sigma_\theta$},
-%xtick={-0.5,0,0.5},
-%xticklabels={-$$, 0, $b$},
-ytick={0,1.5708,5},
-yticklabels={0,$\pi/2$,5},
-ylabel = {$R_{\pi}^\star/\sigma^2$},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = red, smooth] plot table [x = x, y = Runif, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\addplot[color = red, smooth, dashed, line width = 0.5pt] plot table [x = x, y = Rbound, col sep=comma] {./Figs/unif_Bayes_Risk.csv};
-\addplot[color = black, dashed] {3.14159 / 2};
-\end{axis}
-\end{tikzpicture}
-\caption{Asymptotic Bayes risk $R_{\pi}^\star$ in estimating the mean of a normal distribution ($P_X = \Ncal(\theta, \sigma^2)$ under an optimal threshold distribution $\lambda^\star$, when the prior $\pi$ is the uniform distribution over $\Theta = [-0.5,0.5]$.
-%
-%versus $\sigma/\sigma_\theta = 2\sqrt{3}\sigma$.
-The distribution $\lambda^\star$ is the minimizer of \eqref{eq:cvx_average}.
-It is illustrated for various cases in Fig.~\ref{fig:opt_density}.
-The dashed curve represents the upper bound \eqref{eq:upper_bound}.
-\label{fig:dist_bound_uniform}  }
-\end{center}
-\end{figure}
-
-As can be seen in Fig.~\ref{fig:opt_density} for the case $P_X = \Ncal(\theta ,\sigma^2)$ and a uniform $\pi$, when the radius of $\Theta$ is small compared to $\sigma$, the optimal distribution $\lambda^\star$ is a mass distribution.
-In this case, the ML estimator reduces to the estimator ${\theta}_n$ of \eqref{eq:estimator_naive}.
-As the following proposition shows, the Bayes risk for this choice of $\lambda$ is maximal, and thus provides an upper bound on the Bayes risk under any $\lambda$.
- \eqref{eq:cvx_average}. 
-\begin{prop}\label{prop:upper_bound}
-For any prior $\pi(d\theta)$ and $\theta_0$ in the support of $\eta(x)$ we have
-\begin{equation} 
-\label{eq:upper_bound}
-R_\pi^\star  \leq 
- \int \frac{\pi(d\theta)}{\eta \left( \theta_0 - \theta \right)},
-\end{equation}
-Furthermore, assuming that $\theta_0 = \ex{\theta}$ and that $\pi$ has a finite third moment $\sigma_\theta^3$, we have: 
-\begin{equation}
-\label{eq:bound_Taylor}
-R^\star_\pi \leq \frac{1}{4 f^2(0)} + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right) \sigma_\theta^2 + O(\sigma_\theta^3).
-\end{equation}
-\end{prop}
-\begin{proof}
-The function $x \rightarrow 1/x$ is convex for positive values, hence Jensen's inequality implies
-\[
-\left( \int \eta \left( t-\theta\right) \lambda(dt) \right)^{-1}  \leq \int  \frac{ \lambda(dt)}{ \eta \left( t-\theta\right)  }. 
-\]
-Therefore, the expected value of $\kappa^{-1}(\theta)$ satisfies
-\begin{align}
-\ex{  \frac{1}{\kappa(\theta)}}  \leq \int \int \frac{\pi(d\theta) \lambda(dt) }{\eta \left( t - \theta \right)}. \label{eq:upper_bound_proof}
-\end{align}
-The bound \eqref{eq:upper_bound} is obtained by taking $\lambda$ to be a mass distribution at any $\theta_0$ in the support of $\eta(x)$.
-Finally, \eqref{eq:bound_Taylor} is obtained by expanding $1/\eta(x)$ to a third order Taylor series around zero
-%\[
-%1/\eta(x) = \frac{1}{4f^2(0)}  + \left(\frac{1}{4 f^2(0)} \frac{-f''(0)}{f(0)} -1 \right)  x^2 + O(x^3),
-%\]
-and taking its expectation with respect to $\pi$ at $x=\theta_0-\theta$. 
-\end{proof}
-We note that the function $1/\eta(x)$ is quasi-convex and symmetric around zero, so the choice $\theta_0 = \ex{ \theta}$ minimizes the RHS of \eqref{eq:upper_bound} among all $\theta_0$ in the support of $\eta(x)$.\par
-The bound \eqref{eq:upper_bound} is not trivial as long as the integral in the RHS of \eqref{eq:upper_bound} is finite, i.e., whenever the tail of $\pi(\theta)$ vanishes fast enough compared to $\eta(x)$.
-The expansion \eqref{eq:bound_Taylor} implies that this bound becomes tight whenever the support of the optimal distribution is a mass distribution at $\mathbb E \theta$, in which case the expected value of $\kappa^{-1}(\theta)$ approaches $1/\eta(0) = 1/4f^2(0)$.
-
-\begin{example} \label{ex:bound}
-In the normal case $P_X = \Ncal(\theta, \sigma^2)$, the bound in \eqref{eq:bound_Taylor} implies 
-\[
-\frac{R^\star_\pi}{\sigma^2}  \leq \frac{\pi}{2} + \left( \frac{\pi}{2} -1 \right) \left( \frac{ \sigma_\theta}{\sigma} \right)^2 + O \left(  \frac{\sigma_\theta} { \sigma} \right)^3. 
-\]
-It follows that the ARE approaches its maximal value of $2/\pi$ whenever $\sigma_\theta/\sigma$ is small.
-The exact value of \eqref{eq:upper_bound} in this case, as well as the Bayes ARE with the optimal threshold density $\lambda^\star$ for a uniform $\pi$, are illustrated in Fig.~\ref{fig:dist_bound_uniform}.
-%i.e., each encoder simply reports "$1$" or "$-1$" whenever $X_i$ is larger or smaller than $\theta_0$, respectively.
-Intuitively, an accurate estimation of $\theta$ in this case is possible only if a sufficient mix of ''$1$''s and ''$-1$''s is obtained from the sample.
-When $\sigma_\theta^2$ is high compared to $\simga^2$, one of the events $"1"$ or "$-1"$ becomes too rare to
-\end{example}
-\fi

### 2019-12-15 distributed-estimation.tex
Rewrote entire proof of local asymptotic normality

@@
 \section{Distributed Estimation \label{sec:distributed}}
-In this section, we now consider the distributed encoding setting in Figure~\ref{fig:setup}-(iii) where  each one-bit message $B_i$ is only a function of its private sample $X_i$.
-In this case, the $i$th encoder is fully characterized its \emph{detection region}, defined as
-\[
-A_i = \left\{ x \in \mathbb R \,:\, B_i(x) = 1 \right\}.
-\]
-Consequently, $B_i$ is of the form
-\[
-B_i = \begin{cases} 1 & X_i \in A_i, \\
--1 & X_i \notin A_i,
-\end{cases} \quad i\in \mathbb N,
-\]
-where the detection region $A_i$ is a Borel set that is independent of $X_1,\ldots,X_n$.\par
 
-As a first step, the following theorem provides conditions under which the messages $B_1,B_2,\ldots$ define a local asymptotic normal family.
-The proof of this theorem is in Appendix~\ref{proof:thm:LAN1}.
+We now consider the distributed encoding setting in
+Figure~\ref{fig:setup}-(iii) where each one-bit message $B_i$ is a
+function only of its private sample $X_i$. In this case, the $i$th encoder is
+of the form $B_i = \indic{X_i \in A_i}$, where the detection region
+$A_i$ is a Borel set independent of $X_1, X_2, \ldots$.
 
-\begin{thm} \label{thm:LAN1}
-For $n \in \mathbb N$ and $A_n \subset \mathbb R$,  define
+We begin by making a few restrictions on the collections of the sets $A_i$,
+which we believe not unreasonable, but which allow us to develop fundamental
+limits for estimation.  We require a bit of notation to define the
+assumptions. As we work with a location family based on a density $f$
+with associated probability distribution $P$ on variables $Z$,
+we define
+\begin{equation*}
+  P_\theta(A) \defeq P(Z - \theta \in A)
+\end{equation*}
+for $Z$ with density $f$. Whenever $A$ is a collection
+of disjoint intervals $A = \cup_i \{[t_i^-, t_i^+]\}$, we may define
+\begin{equation*}
+  \dPtheta(A) \defeq \frac{\partial}{\partial \theta} P_\theta(A)
+  = \sum_i \left(f(t_i^- - \theta) - f(t_i^+ - \theta)\right),
+\end{equation*}
+and similarly we define the score
+function $\score_\theta(A) \defeq \dPtheta(A) / P_\theta(A)$.
+For $B = \indic{X \in A}$, we abuse notation and also write
+$\score_\theta(B) = \score_\theta(A)$ and similarly for $\dPtheta$.
+With this, we may define the variance of the
+scores $\score_\theta(B_i)$ under $P_\theta$ via
 \begin{equation}
   \label{eq:precision_general}
-L_n(A_1,\ldots,A_n;\theta) \triangleq \frac{1}{n} \sum_{i=1}^n \frac{ \left(\frac{d}{d \theta} \Prob(X_i \in A_i) \right)^2 }{ \Prob(X_i \in A_i)\left(1- \Prob(X_i \in A_i) \right) }. 
+  L_n(A_1,\ldots,A_n;\theta) \defeq
+  \frac{1}{n} \sum_{i=1}^n \frac{ \dPtheta(A_i)^2}{
+    P_\theta(A_i) (1 - P_\theta(A_i))}.
 \end{equation}
-Consider the following conditions:
-\begin{itemize}
-\item [(i)\,\,] The probability density function $f(x)$ of $X_n-\theta$ is log-concave, differentiable, and symmetric.
-Furthermore, there exists $\delta>0$ such that the function $\eta^{1+\delta}(x)/f^\delta(x)$ is non-increasing in $|x|$.
-\item[(ii)\,] $A_n$ is a finite union of disjoint intervals.
-\item[(iii)] The limit 
+We then make the following assumption.
+\begin{assumption}
+  \label{assumption:detection-regions}
+  The density and detection regions satisfy
+  \begin{enumerate}[(i)]
+  \item \label{item:density-nice}
+    The density function $f$ of $X_n - \theta$ is Lipschitz continuous.
+  \item \label{item:finite-intervals}
+    Each set $A_n$ is a finite union of at most $K < \infty$ intervals
+    (which may include $\pm \infty$), and
+    $0 < \inf_n P_\theta(A_n) \le \sup_n P_\theta(A_n) < 1$.
+  \item \label{item:limit-variance}
+    The limit
     \begin{equation}
-\label{eq:LAN_lim}
-\kappa(\theta) \triangleq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
+      \label{eqn:LAN-limit}
+      \kappa(\theta) \defeq \lim_{n\to \infty} L_n(A_1,\ldots,A_n; \theta)
     \end{equation}
-exists. 
-\end{itemize}
-For $i=1,\ldots,n$ set
-\[
-B_n = \begin{cases} 1 & X_n \in A_n, \\
--1 & X_n \notin A_n. 
-\end{cases} 
-\]
-For any $\theta$, $f(x)$ and a sequence of sets $A_1,A_2,\ldots$ such that (i)-(iii) hold, and any $h\in \mathbb R$, we have
-\begin{align*}
-& \log  \frac{ \mathbb P_{\theta+h/\sqrt{n}} (B_1,\ldots,B_n) }{
-\mathbb P_{\theta} (B_1,\ldots,B_n)} \\
-& \overset{d}{\longrightarrow} \Ncal\left(-\frac{1}{2} h^2 \kappa(\theta), h^2 \kappa(\theta) \right).
-\end{align*} 
-\end{thm}
-Theorem~\ref{thm:LAN1} provides conditions under which $B_1,\ldots,B_n$ defines a LAN family with a precision parameter given by the limit in \eqref{eq:LAN_lim}.
-Condition (i) is satisfied, for example, by the normal distribution with $\delta\leq 2$.
-Condition (iii) is arguably the strongest and hardest to verify.
-As we show in Section~\ref{subsec:threshold} below, this condition is satisfied, for example, when $A_1, \ldots,A_n$ are half lines whose starting points are drawn independently from some probability measure on $\mathbb R$.
-Similar ideas imply that condition (iii) holds whenever we choose the intervals consisting each $A_i$ according to some pre-specified distribution.
-\par
-%
-An important conclusion of Theorem~\ref{thm:LAN1} follows from the local asymptotic minimax property of estimators in LAN models \cite{van2000asymptotic}):
-\begin{cor} \label{cor:LA_minimax}
-Let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from $B_1,\ldots,B_n$ with detection regions $A_1,\ldots,A_n$ such that conditions (i)-(iii) of Theorem~\ref{thm:LAN1} hold.
-Then for any symmetric and quasi-convex function $L$,
+    exists and is finite.
+  \end{enumerate}
+\end{assumption}
+
+Under this assumption, we have the following theorem, which provides
+a local asymptotic minimax lower bound on the efficiency of
+\emph{any} non-adaptive estimator.
+\begin{theorem}
+  \label{theorem:non-adaptive-minimax}
+  Let Assumption~\ref{assumption:detection-regions} hold, and
+  let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from
+  observations $B_i = \indic{X_i \in A_i}$.
+  Then for any
+  symmetric and quasi-convex function $L$,
   \begin{align*}
@@
 \end{align*}
-where $Z \sim \Ncal(0,1)$. In particular, for $L(x) = x^2$,
-\begin{align*}
-\liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  n \mathbb E  \left( {\theta}_{n} - \tau \right)^2 \geq 1/\kappa(\theta).
-\end{align*}
-\end{cor}
-%
-Corollary~\ref{cor:LA_minimax} says that when the sequence of one-bit messages defines a LAN model with respect to $\theta$, no estimator can attain MSE smaller than $1/\kappa(\theta)n + O(1/n)$ where $\kappa(\theta)$ is the precision parameter of the model.
-Consequently, the ARE  in such case is at most $\kappa(\theta)\sigma^2$.
-Furthermore, as we show next, no estimator in this setting can attain the optimal ARE of $\eta(0)\sigma^2$ uniformly over $ \Theta$.
+  where $Z \sim \normal(0,1)$.
+\end{theorem}
+
+Theorem~\ref{theorem:non-adaptive-minimax} shows that the limiting variance
+term $\kappa(\theta)$ provides strong lower bounds on the efficiency of any
+non-adaptive estimator, and moreover, that these bounds necessarily depend
+on $\theta$. This suggests that attaining any type of good (uniform)
+efficiency with non-adaptive estimators will be challenging.  As a
+particular consequence, for the squared error $L(x) = x^2$, for any $\delta
+> 0$ and $\theta$, there exists a $c < \infty$ such that $\sup_{|\tau -
+  \theta| \le c / \sqrt{n}} \E_\tau[(\theta_n - \tau)^2] \ge \frac{(1 -
+  \delta)}{n \kappa(\theta)} + o(1/n)$.
+We next turn to the uniformity limitations of non-adaptive strategies.
 
 \subsection{Non-existence of a Uniformly Optimal Strategy}
-We now show that under LAN models, the optimal minimal risk $1/\eta(0)$ can only be attained at a finite number of points within $\Theta$.
-This fact implies in particular that, unlike in the adaptive setting, no distributed estimation scheme has ARE of $\eta(0)\sigma^2$ for all $\theta \in \Theta$.
+
+We now show that under LAN models, the optimal minimal risk $1/\eta(0)$ can
+only be attained at a finite number of points within $\Theta$. This fact
+implies in particular that, unlike in the adaptive setting, no distributed
+estimation scheme has ARE of $\eta(0)\sigma^2$ for all $\theta \in \Theta$.
 

### 2019-12-15 proof-adaptive-optimality.tex
Rewrote entire proof of local asymptotic normality

@@
-\section{Proof of Theorem~\ref{thm:adpative_lower_bound}
+\section{Proof of Theorem~\ref{thm:adpative_lower_bound}}
 \label{proof:thm:adpative_lower_bound}
-}
-Consider the following two Lemmas:
+
+We begin with two technical lemmas.
 \begin{lem} \label{lem:bound_intervals}
-Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$,
+  Let $f$ be a log-concave and symmetric density function
+  for which Assumption~\ref{assump:failure_rate} holds. For any $x_1 \geq
+  \ldots \geq x_n \in \R$,
   \begin{equation}
-\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^2 }
-{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
-\leq  4f^2(0). 
+    \frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^2 }{
+      \left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
+    \leq  4f(0)^2.
     \label{eq:lem_bound_intervals}
@@
 \begin{lem} \label{lem:fisher_bound}
-Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that Assumption~1 holds. For a Borel measurable $A$ set, 
-\[
-B(X) = \begin{cases} 1,& X \in A, \\
--1, & X \notin A.
+  Let $X$ be a random variable with a symmetric, log-concave, and
+  continuously differentiable density function $f(x)$ such that Assumption~1
+  holds. For a Borel measurable set $A$, define
+  \begin{equation*}
+    B(x) \defeq \begin{cases} 1
+      & \mbox{if} ~x \in A, \\
+      -1 & \mbox{if}~ x \notin A.
     \end{cases}
-\]
-Then the Fisher information of $B$ with respect to $\theta$ is bounded from above by $\eta(0)$.
+  \end{equation*}
+  Then the Fisher information of $B$ with respect to $\theta$ is bounded
+  from above by $\eta(0)$.
 \end{lem}
 
-Lemma~\ref{lem:bound_intervals} is obtained as the special case $\delta = 0$ of lemma \ref{lem:bound_intervals_delta}. 
-We now prove Lemma~\ref{lem:fisher_bound}.
-\subsubsection*{Proof of Lemma~\ref{lem:fisher_bound}}
-When $f(x)$ is the normal density function, this lemma follows from \cite[Thm.
-3]{Barnes2018}.
-The proof below is based on a different techique than in \cite{Barnes2018}, and is valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}.
-\\
+Lemma~\ref{lem:bound_intervals} is the special case $\delta = 0$ of
+Lemma~\ref{lem:bound_intervals_delta} to come in
+Section~\ref{sec:bound_intervals_delta}.  We now prove
+Lemma~\ref{lem:fisher_bound}.
+
+\begin{proof-of-lemma}[\ref{lem:fisher_bound}]  
+  When $f$ is the normal density function, this lemma follows from
+  \cite[Thm.~3]{Barnes2018}. The proof below is based on a different techique
+  than in \cite{Barnes2018}, and is valid for any log-concave symmetric
+  density satisfying Assumption~\ref{assump:failure_rate}. \\
 
@@
   \end{align}
-where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$.
-Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
-\[
+  where differentiation under the integral sign in $(a)$ is possible since
+  $f$ is log-concave and so a.e.\ differentiable
+  (cf.~\cite{Bertsekas73}),
+  with a.e.\ derivative $f'(x)$. Regularity of
+  the Lebesgue measure implies that for any $\epsilon>0$, there exists a
+  finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
+  \begin{equation*}
     \int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
-\]
-which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$.
-It is therefore enough to proceed in the proof assuming that $A$ is of the form
-\[
+  \end{equation*}
+  which implies that for any $\epsilon' > 0$, the set $A$ in
+  \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of
+  disjoint intervals without increasing $I_\theta$ by more than
+  $\epsilon'$. It is therefore enough to proceed in the proof assuming that
+  $A$ is of the form
+  \begin{equation*}
     A = \cup_{j=1}^k (a_j,b_j),
-\]
+  \end{equation*}
   with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
@@
   \end{align*}
-so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
-\begin{align}
-& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
+  so we may rewrite Eq.~\eqref{eq:lem_fisher_bound_proof1} as
+  \begin{align*}
+    I_\theta & =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
     { \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
@@
     {1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
-\label{eq:lemma_J}
-\end{align}
-It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in \R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than 
-\[
-\max_{t \in \{a_j,b_j, j=1,\ldots,k\} } 4f^2(t) \leq 4 f^2(0), 
-\]
-where the last transition is due to Assumption~1. 
-\QEDA \\
+  \end{align*}
+  It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in
+  \R$ and any choice of the intervals' endpoints,
+  \begin{equation*}
+    I_\theta \le
+    \max_{t \in \{a_j,b_j, j=1,\ldots,k\} } 4f(t)^2 \leq 4 f(0)^2, 
+  \end{equation*}
+  where the last transition is by Assumption~\ref{assump:failure_rate}. 
+\end{proof-of-lemma}
 
 We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
-In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
-\begin{equation}
-\label{eq:general_messages}
-B_i = \begin{cases}
-X_i \in A_i & 1, \\
-X_i \notin A_i & -1,
-\end{cases} 
-\end{equation}
-where $A_i \subset \R$ is a Borel measurable set. 
-%Indeed, any measurable function $(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
-Consider the conditional distribution $P({B_1,\ldots,B_n|\theta})$ of $(B_1,\ldots,B_n)$ given $\theta$. We have 
-\begin{align}
-P\left( B_1,\ldots,B_n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B_1,\ldots,B_{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
-\end{align}
-where $P\left(B_i =1 | \theta, B_1,\ldots,B_{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B_1,\ldots,B_n$ with respect to $\theta$ is given by 
+To bound the Fisher information of any set of $n$ one-bit
+messages with respect to $\theta$,
+%% we first note that without loss of
+%% each message $B_i$ can is of the form
+%% \begin{equation}
+%% B_i = \begin{cases}
+%% X_i \in A_i & 1, \\
+%% X_i \notin A_i & -1,
+%% \end{cases} 
+%% \end{equation}
+%% where $A_i \subset \R$ is a Borel measurable set. 
+%% %Indeed, any measurable function $(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
+we consider the conditional distribution $P({B_1,\ldots,B_n|\theta})$ of
+$(B_1,\ldots,B_n)$ given $\theta$. We have
+\begin{align*}
+  P\left( B_1,\ldots,B_n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B_1,\ldots,B_{i-1} \right),
+  %% \label{eq:adpt_lower_bound_proof:1}
+\end{align*}
+where $P\left(B_i =1 | \theta, B_1,\ldots,B_{i-1} \right) = \mathbb P\left(
+X_i \in A_i\right)$, when $B_i = \indic{X_i \in A_i}$ by independence,
+so that the Fisher information of $B_1,\ldots,B_n$ with
+respect to $\theta$ is
 \begin{align}
@@
 \end{align}
-where $I_\theta (B_i|B_{i-1},\ldots,B_1)$ is the Fisher information of the distribution of $B_i$ given $B_1,\ldots,B_{i-1}$.
-From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B_{i-1},\ldots,B_1) \leq 4f^2(0)$.
-The Van Trees inequality \cite{van2004detection, gill1995applications} now implies
+where $I_\theta (B_i|B_{i-1},\ldots,B_1)$ is the Fisher information of the
+distribution of $B_i$ given $B_1,\ldots,B_{i-1}$.
+Lemma~\ref{lem:fisher_bound} implies that $I_\theta
+(B_i|B_{i-1},\ldots,B_1) \leq 4f(0)^2$. The Van Trees inequality
+\cite{van2004detection, gill1995applications} now implies
 \begin{align*}
@@
 & = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
-& \geq \frac{1}{ 4f^2(0) n + I_0}.
+& \geq \frac{1}{ 4f^2(0) n + I_0}
 \end{align*}
-\QEDA
+as desired.
 
-\subsection{Isoperimetric Lemma
-\label{sec:bound_intervals_delta} }
-The following lemma is used in the proof Theorems~\ref{thm:adpative_lower_bound}, \ref{thm:LAN1}, and \ref{thm:non_existence}.
+\subsection{An Isoperimetric Lemma}
+\label{sec:bound_intervals_delta}
 
-\begin{lem} \label{lem:bound_intervals_delta}
-Let $f(x)$ be log-concave, symmetric, and differentiable density function. Let $\delta\geq 0$. Assume that the function
-\[
-\eta_\delta(x) \triangleq  \eta^{1+\delta}(x)/f^\delta(x) = \frac{  \left( f(x) \right)^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}}
-\]
-is non-increasing in $|x|$. For any $x_1 \ge \ldots \ge x_n \in \R^n$,
+The following lemma is essential to the the proofs
+of Theorems~\ref{thm:adpative_lower_bound}, \ref{thm:LAN1}, and
+\ref{thm:non_existence}.
+
+\begin{lem}
+  \label{lem:bound_intervals_delta}
+  Let $f$ be a log-concave and symmetric density
+  function. Let $\delta\geq 0$. Assume that the function
+  \begin{equation*}
+    \eta_\delta(x) \triangleq  \eta^{1+\delta}(x)/f^\delta(x)
+    = \frac{  \left( f(x) \right)^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}}
+  \end{equation*}
+  is non-increasing in $|x|$. Then for any $x_1 \ge \ldots \ge x_n \in \R^n$,
   \begin{equation}
-\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
-{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{k=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
-\leq  \max_{i} \eta_\delta(x_i).
+    \frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} } {\left|
+      \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{k=1}^n
+      (-1)^{i+1} F(x_i) \right|^{1+\delta} } \leq \max_{i} \eta_\delta(x_i).
     \label{eq:lem_bound_intervals_delta}
@@
 In particular, 
-\[
+\begin{equation*}
 \frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
@@
 \leq \eta_\delta(0) = 4^{1+\delta} f^{2+\delta}(0).
-\]
+\end{equation*}
 
-\subsubsection*{
-Proof of Lemma~\ref{lem:bound_intervals_delta}}
+\begin{proof-of-lemma}[\ref{lem:bound_intervals_delta}]
   Denote 
-\[
+  \begin{equation*}
     \delta_n(x_1,\ldots,x_n) \triangleq \sum_{i=1}^{n} s_i f(x_i),
-\]
-\[
+  \end{equation*}
+  \begin{equation*}
     \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{i=1}^n s_i F(x_i), 
-\]
+  \end{equation*}
   where $s_i \triangleq (-1)^{i+1}$. We use induction on $n \in \N$ to show that 
@@
   Since 
-\[
+  \begin{equation*}
     \eta_\delta(x) =  \frac{  \left|\delta_1(x) \right|^{2+\delta}}{\left|\Delta_1(x)
       (1-\Delta_1(x)) \right|^{1+\delta}}, 
-\]
+  \end{equation*}
   The case $n=1$ is trivial.  
@@
 The assumption on $\eta_\delta(x)$ implies that
-\[
+  \begin{equation*}
     \eta_\delta(x_{i^*}) = \max_i \eta_\delta(x_i).
-\]
+  \end{equation*}
   Since the LHS of \eqref{eq:lem_bound_intervals_delta} is invariant to a sign flip of all $x_1,\ldots,x_{N+1}$, we may assume that $x_{i^*}$ is positive without loss of generality. 
@@
   The LHS of \eqref{eq:lemm:interval_bounds:to_show} is obtained by taking $y_i=x_{k_i}$ where $k_i$ is the $i$th element in $\{1,\ldots,N+1\}\setminus \{i^*\}$. It is therefore enough to prove that 
-\[
+  \begin{equation*}
     \max_{(y_1,\ldots,y_N) \in A_N} g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*),
-\]
+  \end{equation*}
   where 
-\[
+  \begin{equation*}
     A_N(x^*,k) \triangleq \left\{ (y_1,\ldots,y_N) \in \R^N\, : \, y_1 \ge y_k \ge x^* \ge -x^* \ge y_{k+1} \ldots \ge y_N
     \right\}.
-\]
+  \end{equation*}
   %
-Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable with derivative 
-\[
+  Since $f(x)$ is log-concave and symmetric, we may write $f(x) = e^{c(x)}$
+  where $c(x)$ is concave, symmetric, and superdifferentiable on the interior
+  of its domain with
+  supergradient set $\partial c(x) = \{v \in \R \mid c(y) \le c(x) + v (y - x) ~
+  \mbox{for~all}~ y\}$; $c$ is also
+  differentiable a.e.\ with derivative
+  \begin{equation*}
     c'(x) \triangleq \frac{f'(x)}{f(x)}
-\]
-that is non-increasing. We first prove the lemma under the assumption that $c'(x)$ is an injection, or, equivalently, that $c(x)$ is strictly decreasing for all $x\in \R$. \par
-%
-The maximal value of $g(y_1,\ldots,y_N)$ is attained for the same $(y_1,\ldots,y_N) \in A_N(x^*,k)$ that maximizes
+  \end{equation*}
+  (when it exists), and we otherwise simply treat $f'(x) / f(x) = c'(x) \in
+  \partial c(x)$ as an arbitrary element of the superdifferential.  The
+  supergradient sets $\partial c(x)$ are increasing, in that $v_0 \in
+  \partial c(x_0)$ and $v_1 \in \partial c(x_1)$ implies that $(v_1 - v_0)
+  (x_1 - x_0) \le 0$.  We first prove the lemma under the assumption that
+  $c$ is strictly concave, or, equivalently, that $v_i \in \partial c(x_i)$
+  implies that $(v_1 - v_0)(x_1 - x_0) < 0$ whenever $x_1 \neq x_0$; that
+  is, $c'$ is strictly decreasing.
+
+  The maximal value of $g(y_1,\ldots,y_N)$ is attained for the same
+  $(y_1,\ldots,y_N) \in A_N(x^*,k)$ that maximizes
   \begin{align*}
@@
   \end{align*}
-where in the last display and henceforth we suppress the arguments $y_1,\ldots,y_k,x^*,y_{k+1},\ldots, y_N$ of the functions $\delta_N$ and $\Delta_N$.
+  where in the last display and henceforth we suppress the arguments
+  $y_1,\ldots,y_k,x^*,y_{k+1},\ldots, y_N$ of the functions $\delta_N$ and
+  $\Delta_N$. (We may take the compactification of $\R$ as $[-\infty, \infty]$.)
   %
-Within the interior of $A_N(x^*,k)$, all three expressions in \eqref{eq:g_def} within an absolute value are positive.
-It follows that partial derivative of $\log(g)(y_1,\ldots,y_N)$ with respect to $y_i$ within the interior of $A_N(x^*,k)$ is given by
-\[
-\frac{\partial \log(g)}{\partial y_i} = \frac{(2+\delta) s_i f'(x_i)}{\delta_N } -\frac{(1+\delta) s_i f(x_i)}{\Delta_N  } + \frac{(1+\delta)s_i f(y_i)}{1-\Delta_N }.
-\]
+  Within the interior of $A_N(x^*,k)$, all three expressions in
+  \eqref{eq:g_def} within an absolute value are positive. It follows that
+  partial derivative of $\log(g)(y_1,\ldots,y_N)$ with respect to $y_i$ within
+  the interior of $A_N(x^*,k)$ is
+  \begin{equation*}
+    \frac{\partial \log(g)}{\partial y_i} = \frac{(2+\delta) s_i
+      f'(x_i)}{\delta_N } -\frac{(1+\delta) s_i f(x_i)}{\Delta_N } +
+    \frac{(1+\delta)s_i f(y_i)}{1-\Delta_N }.
+  \end{equation*}
   We conclude that the gradient of $\log(g)$ vanishes if and only if
@@
   %
-Since we assumed that $c'(x)$ is an injection, \eqref{eq:gradient_zero} is satisfied if and only if $y_1 = \ldots = y_N$. In this case, 
-$g(y_1,\ldots,y_N) = \eta_\delta(x_{i^*})$  
-if $N$ is even. If $N$ is odd and $y_1 = \ldots = y_N > x^*$, then 
+  Since we assumed that $\partial c(x)$ is injective,
+  equality~\eqref{eq:gradient_zero} holds if and only if $y_1 = \ldots
+  = y_N$. In this case, $g(y_1,\ldots,y_N) = \eta_\delta(x_{i^*})$ if $N$ is
+  even. If $N$ is odd and $y_1 = \ldots = y_N > x^*$, then
   \begin{align*}
@@
 At boundary points for which $y_i = y_{i+1}$ for some $i$, the contribution of $y_i$ and $y_{i+1}$ to $g(y_1,\ldots,y_N)$ is zero and the induction assumption for $n=N-1$ implies that
-\[
+  \begin{equation*}
     g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*)
-\]
+  \end{equation*}
   The remaining boundary points of $A_N(x^*,k)$ are covered by the following cases:
@@
   Finally, under case (4), set 
-\[
+  \begin{equation*}
     d \triangleq s_k F(-x^*) + s_{i^*} F(x^*) = s_{i^*}\left(1-2F(-x^*) \right), 
-\]
-\[
+  \end{equation*}
+  \begin{equation*}
     \sigma \triangleq \sum_{i=1}^{k-1} s_i f(y_i) - \sum_{i=k+1}^{N} s_i f(y_i). 
-\]
+  \end{equation*}
   and 
-\[
+  \begin{equation*}
     \Sigma \triangleq \sum_{i=1}^{k-1} s_i F(y_i) - \sum_{i=k+1}^{N} s_i F(y_i). 
-\]
+  \end{equation*}
   We have
@@
   By the induction hypothesis,
-\[
+  \begin{equation*}
     \frac{ \left| \sigma \right|^{2+\delta}} 
          {\left| \Sigma \right|^{1+\delta} \left|1- \Sigma \right|^{1+\delta} } \leq \eta_\delta(x^*), 
-\]
+  \end{equation*}
   hence it is left to show that 
-\[
+  \begin{equation*}
     \frac{\Sigma(1-\Sigma) } { \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} \leq 1.
-\]
+  \end{equation*}
   Whenever $d>0$, 
@@
   Indeed, if $s_{i^*}=1$, then $s_{k+1}=-1$ and monotonicity of $F(x)$ implies that 
-\[
+  \begin{equation*}
     \Sigma + d \leq F(y_1) - F(y_k) + F(x^*) - F(-x^*) + F(y_{k+2}) - F(y_N), 
-\]
+  \end{equation*}
   and hence
-\[
+  \begin{equation*}
     \Sigma \leq 1-F(x^*) = F(-x^*). 
-\]
+  \end{equation*}
   Similarly, if $s_{i^*}=-1$ then 
-\[
+  \begin{equation*}
     1 - \Sigma \leq 1 -  F(-x^*).
-\]
+  \end{equation*}
   This conclude the proof in the case where $c'(x)$ is an injection.
-\par  
-In the case where $c'(x)$ is not necessarily strictly decreasing, we approximate $c(x)$ using another concave symmetric function whose derivative is always negative except, perhaps, at the origin.
-For $\alpha>0$ consider the function  $f_\alpha(x) = \kappa(\alpha) e^{\sgn(c(x))|c(x)|^{1+\alpha}}$, where $\kappa(\alpha)$ is chosen such that $f_\alpha(x)$ is a probability density function.
-Then $c_\alpha(x)$ is concave, symmetric, and differentiable with
-\[
+
+  In the case where $c(x)$ is not strictly concave, so that $c'$ does not
+  strictly decrease, we approximate $c$ using another concave symmetric
+  function with decreasing derivative. We assume w.l.o.g.\ that $c(0) = 0$
+  maximizes $c$.  For $\alpha>0$ consider the function $f_\alpha(x) =
+  \kappa(\alpha) e^{-|c(x)|^{1+\alpha}}$, where $\kappa(\alpha)$ normalizes
+  $f_\alpha$.  Then $c_\alpha(x)$ is concave, symmetric, and
+  a.e.\ differentiable with
+  \begin{equation*}
     c_\alpha'(x) \triangleq \frac{f'_\alpha(x)}{f_\alpha(x)} = (1+\alpha)|c(x)|^{\alpha} c'(x). 
-\]
-Now $c_\alpha'(x)$ is non-increasing since it is the derivative of a concave function.
-Furthermore, since $c(x)$ is non-constant on any interval and $c'(x)$ is non-increasing, $c_\alpha'(x)$ is non-constant on any interval hence an injection.
-It follows from the first part of the proof that, for any $\alpha>0$,
+  \end{equation*}
+  Now $c_\alpha'(x)$ is non-increasing since it is the derivative of a concave
+  function. Furthermore, since $c(x)$ is non-constant on any interval and
+  $c'(x)$ is non-increasing, $c_\alpha'(x)$ is non-constant on any interval
+  hence an injection. It follows from the first part of the proof that, for
+  any $\alpha>0$,
   \begin{align}
@@
   where 
-\[
+  \begin{equation*}
     \delta_{n,\alpha} \triangleq  \sum_{k=1}^{n} (-1)^{k+1} f_{\alpha}(x_k),
-\]
-\[
+  \end{equation*}
+  \begin{equation*}
     \Delta_{n,\alpha} \triangleq \sum_{k=1}^n (-1)^{k+1} F_{\alpha}(x_k), 
-\]
+  \end{equation*}
   and 
-\[
+  \begin{equation*}
     \eta_{\delta,\alpha}(x) \triangleq \frac{(f_\alpha(x))^{2+\delta}}{\left(F_{\alpha}(x)(1-F(x)) \right)^{1+\delta}}. 
-\]
+  \end{equation*}
   The proof is completed by noting that 
@@
 % and For $\alpha>0$, consider
-%\[
+  %\begin{equation*}
   %F_1(x,\alpha) \triangleq  F(a_1) + \frac{1}{c_1} e^{-c_1 (|x|^{1+\alpha} +d_1}, \quad x \in (a_1,b_1),
-%\]
+  %\end{equation*}
   %and 
-%\[
+  %\begin{equation*}
   %f_1(x,\alpha) \triangleq  F_1'(x,\alpha) =  -\sgn(x)(1+\alpha)|x|^\alpha e^{-c_1 |x|^{1+\alpha} + d_1}, \quad x \in (a_1,b_1).
-%\]
+  %\end{equation*}
 
-\QEDA
+\end{proof-of-lemma}

### 2019-12-15 proof-lan-distributed.tex
Rewrote entire proof of local asymptotic normality

% -*- Mode: latex -*- %

\section{Proof of Theorem~\ref{theorem:non-adaptive-minimax}}

We follow a similar outline to the optimality results we establish
in the proof of Theorem~\ref{thm:sgd}\eqref{item:sgd-regular} in
Sec.~\ref{sec:proof-sgd-regular}.
Roughly, we establish that the family $P_\theta$ of distributions
on the bits $B_i$ is locally asymptotically normal
(Definition~\ref{definition:lan}) via a quadratic
mean differentiability argument. After this, the result
follows by standard local asymptotic minimax theory.

\begin{lemma}
  \label{lemma:lan-bits}
  Let Assumption~\ref{assumption:detection-regions}\eqref{item:density-nice}
  and~\eqref{item:finite-intervals} hold, and let
  $B_i = \indic{X_i \in A_i}$.
  Let $h_n \to h \in \R$. Then for any $\theta \in \mbox{int}\Theta$,
  \begin{equation*}
    \sum_{i = 1}^n \log \frac{P_{\theta + h_n/\sqrt{n}}(B_i)}{
      P_\theta(B_i)}
    = \frac{h}{\sqrt{n}}
    \sum_{i = 1}^n \score_\theta(B_i)
    - \frac{h}{4n} \sum_{i = 1}^n \var(\score_\theta(B_i))
    - \frac{h}{4n} \sum_{i = 1}^n \score_\theta(B_i)^2
    + o_P(1).
  \end{equation*}
  If additionally
  Assumption~\ref{assumption:detection-regions}\eqref{item:limit-variance}
  holds, then
  \begin{equation*}
    \sum_{i = 1}^n \log \frac{P_{\theta + h_n/\sqrt{n}}(B_i)}{
      P_\theta(B_i)}
    = \frac{h}{\sqrt{n}}
    \sum_{i = 1}^n \score_\theta(B_i)
    - \frac{h^2}{2} \kappa(\theta) + o_P(1).
  \end{equation*}
\end{lemma}
\noindent
The proof of Lemma~\ref{lemma:lan-bits} is quite technical,
so we defer it to Section~\ref{sec:proof-lan-bits}.

With this lemma, it is not too challenging to demonstrate the local
asymptotic normality (Definition~\ref{definition:lan}) of the family
$\{P_\theta\}$. Indeed, the assumption that $f$ is Lipschitz guarantees that
$f(z) \le \sqrt{\lip(f)}$ for all $z$, and thus we obtain that
$|\dPtheta(A_n)| \le K \sqrt{\lip(f)}$ for all $n$, whence $\sup_n
\max\{|\score_\theta(A_n)|, |\score_\theta(A_n^c)|\} \le C < \infty$ for
some $C$. Thus, the strong law of large numbers
gives that
$\frac{1}{n} \sum_{i = 1}^n \score_\theta(B_i)
\cas 0$ as $\E_\theta[\score_\theta(B_i)] = 0$, and Lyapunov's central
limit theorem applies to give
\begin{equation*}
  \frac{1}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
  \cd \normal\left(0, \kappa(\theta)\right)
\end{equation*}
under
Assumption~\ref{assumption:detection-regions}\eqref{item:limit-variance},
so that the family $\{P_\theta\}$ is locally asymptotically normal
(Def.~\ref{definition:lan}).

We now recall the familiar H\'{a}jek-Le-Cam local asymptotic minimax
result~\cite[Thm.~8.11]{VanDerVaart98}: if the family
$\{P_\theta\}$ is LAN with precision $\kappa(\theta)$, then
\begin{equation*}
  \liminf_{c \to \infty} \liminf_n \sup_{\norm{\tau - \theta} \le
    c / \sqrt{n}} \E_\tau\left[L(\sqrt{n}(\theta_n - \tau))\right]
  \ge \E[L(Z / \sqrt{\kappa(\theta)})]
\end{equation*}
for any symmetric quasi-convex loss $L$, where $Z \sim normal(0, 1)$.
This immediately gives Theorem~\ref{theorem:non-adaptive-minimax}.

\subsection{Proof of Lemma~\ref{lemma:lan-bits}}
\label{sec:proof-lan-bits}

Our proof follows that of \cite[Thm.~7.2]{VanDerVaart98} closely.
The first step is to note that
if $\lip(f)$ denotes the Lipschitz constant of $f$, then for any
$h \in \R$ and $A = \cup_{i = 1}^K \{[t_i^-, t_i^+]\}$, we have
\begin{equation}
  \label{eqn:expansion-dPtheta}
  P_{\theta + h}(A) = P_\theta(A) + \dPtheta(A)
  \pm \frac{K \cdot \lip(f)}{2}  h^2.
\end{equation}
Indeed, for any interval $[t_0, t_1]$ we immediately have
\begin{align*}
  P_{\theta + h}([t_0, t_1])
  & = \int_{t_0}^{t_1} f(z - \theta - h) dz
  = \int_{t_0}^{t_1} \left(f(z - \theta)
  + \int_0^h f'(z - \theta - v) dv\right) dz \\
  & = P_\theta([t_0, t_1])
  + \int_0^h \int_{t_0}^{t_1} f'(z - \theta - v) dz dv \\
  & = P_\theta([t_0, t_1])
  + \int_0^h \left[f(t_1 - \theta - v) - f(t_0 - \theta - v)\right] dv \\
  & = P_\theta([t_0, t_1])
  + \left(f(t_1 - \theta) - f(t_0 - \theta)\right) h
  \pm \int_0^h \lip(f) |v| dv \\
  & = P_\theta([t_0, t_1]) + \dPtheta([t_0, t_1])
  \pm \frac{\lip(f)}{2} h^2,
\end{align*}
giving the result~\eqref{eqn:expansion-dPtheta}.

Now we demonstrate a type of uniform quadratic mean differentiability
(Definition~\ref{definition:qmd}) for such sets
$A$. First, note that by a Taylor approximation and concavity
of $\sqrt{\cdot}$, we have
\begin{equation*}
  \sqrt{a} + \frac{b}{2 \sqrt{a}} -
  \frac{b^2}{4\sqrt{a}}
  \le \sqrt{a + b} \le \sqrt{a}
  + \frac{b}{2 \sqrt{a}}
\end{equation*}
for any $a > 0$ and $|b| \le 3a/4$. Consequently,
recalling that $\score_\theta(A) = \dPtheta(A) / P_\theta(A)$,
for any $h \in \R$ the expansion~\eqref{eqn:expansion-dPtheta} yields
\begin{equation*}
  \left(\sqrt{P_{\theta + h}(A)} -
  \sqrt{P_\theta(A)} - \half h \score_\theta(A) \sqrt{P_\theta(A)}
  \right)^2
  \le
  \left(
  \frac{K \lip(f)}{2 \sqrt{P_\theta(A)}} h^2
  + \frac{(|\dPtheta(A) h| + h^2 \lip(f))^2}{P_\theta(A)^{3/2}}
  \right)^2.
\end{equation*}
Now, note that for any Lipschitz-continuous $f$, that
$1 = \int f(z) dz$ and $f \ge 0$ yield that
$f(z) \le \sqrt{\lip(f)}$ for all $z \in \R$. Thus, under
Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals},
there exists a finite constant $C < \infty$ such that
\begin{subequations}
  \label{eqn:h-fourth}
  \begin{align}
    \nonumber \left(\sqrt{P_{\theta + h}(A)} -
    \sqrt{P_\theta(A)} - \half
    h \score_\theta(A) \sqrt{P_\theta(A)}\right)^2
    & \le
    \left(\frac{h^2 k \cdot \lip(f)}{2 \sqrt{P_\theta(A)}}
    + \frac{(|\dPtheta(A) h| + k h^2 \lip(f))^2}{
      P_\theta(A)^{3/2}}\right)^2 \\
    & \le \frac{C}{P_\theta(A)} \left[k^2 \lip^2(f)
      + \score_\theta(A)^2
      + \frac{k^4 h^4 \lip^4(f)}{P_\theta(A)^2}
      \right] \cdot h^4
  \end{align}
  where $C < \infty$ is a numerical constant, valid whenever $|\dPtheta(A) h|
  \le P_\theta(A) / 4$ and $k h^2 \lip^4(f) \le P_\theta(A) / 4$,
  and similarly, we have
  \begin{equation}
    \left(\sqrt{P_{\theta + h}(A^c)} -
    \sqrt{P_\theta(A^c)} - \half
    h \score_\theta(A^c) \sqrt{P_\theta(A^c)}\right)^2
    \le \frac{C}{P_\theta(A^c)}
    \left[k^2 \lip^2(f)
      + \score_\theta(A^c)^2
      + \frac{k^4 h^4 \lip^4(f)}{P_\theta(A^c)^2}
      \right] \cdot h^4.
  \end{equation}
\end{subequations}
That is, the family $\{P_\theta\}$ with bit observations $B_n$ satisfies a
uniform type of quadratic-mean differentiability
(Def.~\ref{definition:qmd}).

Now, for shorthand, define $P_n = P_{\theta + h_n / \sqrt{n}}$ and $P =
P_\theta$, and let $p_n, p$ be shorthand for the p.m.f.s of the two
distributions.  For the sets $A_i$ we recall that $B_i = \indic{X_i \in
  A_i}$.  The random variables
\begin{equation*}
  W_{n,i} \defeq 2 \left(\sqrt{\frac{p_n}{p}}(B_i) - 1\right)
\end{equation*}
are with $P$-probability 1 well-defined, and by the
inequalities~\eqref{eqn:h-fourth}, we have
that
\begin{align*}
  \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
  & \le 
  C \frac{k^2 \lip^2(f) + \score_\theta(A_i)^2
  + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
  \cdot \frac{h_n^4}{n^2}
  + C \frac{k^4 \lip^4(f)}{
    P_\theta(A_i)^3 P_\theta(A_i^c)^3}
  \frac{h_n^8}{n^4} \\
  & \le 
  C \frac{k^2 \lip^2(f) + \score_\theta(A_i)^2
  + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
  \cdot \frac{h^4}{n^2}
  + C \frac{k^4 \lip^4(f)}{
    P_\theta(A_i)^3 P_\theta(A_i^c)^3}
  \frac{h^8}{n^4}
\end{align*}
whenever
\begin{equation*}
  \frac{h}{\sqrt{n}} \max\{\score_\theta(A_i),
  \score_\theta(A_i^c)\}
  \le \frac{1}{4}
  ~~ \mbox{and} ~~
  \frac{h^2}{n} \lip^2(f)
  \le \frac{\min\{P_\theta(A_i), P_\theta(A_i^c)\}}{4}
\end{equation*}
In particular, using the uniform boundedness of $0 < P_\theta(A_i) < 1$,
we see that unifomly in $i, n$ we have
\begin{equation*}
  \var\left(W_{n,i} - \frac{h}{\sqrt{n}} \score_\theta(B_i)\right)
  = O\left(\frac{h^4}{n^2}\right)
  + O(1) \E[\score_\theta(B_i)^2]
  \frac{(h_n - h)^2}{n},
\end{equation*}
while $\E[\score_\theta(B_i)] = 0$. Additionally, defining $\mu_i$ to be the
induced counting measure on $B_i = \indic{X_i \in A_i}$,
\begin{align*}
  \sum_{i = 1}^n \E[W_{n,i}]
  & = 2\sum_{i = 1}^n
  \left(\int \sqrt{p_n(b)} \sqrt{p(b)} d\mu_i(b) - 1 \right)
  = -\sum_{i = 1}^n \int \left(\sqrt{p_n(b)} - \sqrt{p(b)}\right)^2
  d\mu_i(b) \\
  & = -\frac{h_n^2}{4 n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
  - \sum_{i = 1}^n \int \left(\sqrt{p_n(b)} - \sqrt{p(b)}
  - \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}\right)^2 d\mu_i(b) \\
  & \qquad \qquad ~
  - \sum_{i = 1}^n \int \left(\sqrt{p_n(b)} - \sqrt{p(b)}
  - \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}\right)
  \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}d\mu_i(b) \\
  & = -\frac{h^2}{4n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
  - O(h^4 / n) - O(h^2 / n^{1/2})
\end{align*}
uniformly in $h$.
Therefore, we obtain
\begin{equation*}
  \sum_{i = 1}^n W_{n,i}
  = \sum_{i = 1}^n \left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
  + \frac{h_n}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
  = -\frac{h^2}{4n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
  + \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
  + o_P(1),
\end{equation*}
where we have used that $h_n \to h$.

Now, we write the log-likelihood ratio. We have
\begin{align*}
  \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
  & = 2 \sum_{i = 1}^n \log\left(1 + \half W_{n,i}\right) \\
  & = \sum_{i = 1}^n W_{n,i}
  - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2
  + \half \sum_{i = 1}^n W_{n,i}^2 R(W_{n,i})
\end{align*}
where the remainder $|R(W_{n,i})| \le |W_{n,i}|$ for $|W_{n,i}| \le 1$.
In particular, using the Taylor approximation to $\sqrt{\cdot}$ and
that $\inf_i P_\theta(A_i) > 0$, we have
$\max_i W_{n,i} \cas 0$, so that
\begin{equation}
  \label{eqn:almost-at-the-end}
  \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
  = \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
  - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2 + o_P(1).
\end{equation}

It remains to compute $\E[W_{n,i}^2]$. Using the
expansions~\eqref{eqn:h-fourth}, we have for any $B = \indic{X \in A}$,
%% \begin{align*}
%%   \E\left[
%%     \left(\sqrt{\frac{P_{\theta + h}(B)}{P_\theta(B)}}
%%     - 1\right)^2
%%     \right]
%%   & = (\sqrt{P_{\theta + h}(A)} - \sqrt{P_\theta(A)})^2
%%   + (\sqrt{P_{\theta + h}(A^c)} - \sqrt{P_\theta(A^c)})^2 \\
%%   & = (h \dPtheta(A) / \sqrt{P_\theta(A)}
%%   + O(h^2)) + (h \dPtheta(A^c) / \sqrt{P_\theta(A^c)} + O(h^2))^2 \\
%%   & = h^2 P_\theta(A) \score_\theta(A)^2
%%   + h^2 P_\theta(A^c) \score_\theta(A^c)^2
%%   + O(h^3)
%%   = h^2 \var(\score_\theta(B))
%%   + O(h^3)
%% \end{align*}
%% uniformly in $h$,
%% and
\begin{align*}
  \left(\sqrt{\frac{P_{\theta + h}(B)}{P_\theta(B)}}
  - 1\right)^2
  & = \left(\sqrt{1 + h \score_\theta(B) + O(h^2)} - 1\right)^2
  % = \left(h \score_\theta(B) / 2 + O(h^2)\right)^2
  = h^2 \score_\theta(B)^2 / 4 + O(h^3)
\end{align*}
uniformly in $h$ near 0, as the probabilities $P_\theta(A)$ are bounded from
0 and 1. Thus
\begin{equation*}
  \sum_{i = 1}^n W_{n,i}^2
  = \frac{h_n^2}{n} \sum_{i = 1}^n \score_\theta(B_i)^2
  + O(h_n^2 / \sqrt{n}),
\end{equation*}
giving Lemma~\ref{lemma:lan-bits}.

### 2019-12-15 proof-no-distributed.tex
Rewrote entire proof of local asymptotic normality

--- 2019-12-13 appendices.tex
@@
 
-\subsection{Proof of Theorem~\ref{thm:LAN1}
-\label{proof:thm:LAN1}
-}
-The log-probability mass distribution of $(B_1,\ldots,B_n)$ is given by
-\begin{align*}
-& \log \Prob_\theta(b_1,\ldots,b_n) = \sum_{i=1}^n \left( \frac{b_i+1}{2} \log  \Prob(X_i\in A_i) + 
-\frac{1-b_i}{2} \log \Prob(X_i\in A_i) \right), \quad b_i \in \{-1,1\}, \quad i=1,\ldots,n. 
-\end{align*}
-Consequently, 
-\begin{align}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b_1,\ldots,b_n)} { \Prob_\theta (b_1,\ldots,b_n) } = \sum_{i=1}^n    \frac{b_i+1}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} + 
-\sum_{i=1}^n  \frac{1-b_i}{2} 
-\log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}. 
-\label{eq:LAN_proof1}
-\end{align}
-For each $i=1,\ldots,n$, write 
-\[
-A_i = \bigcup_{k=1}^{K_i} \left(t_{i,2k-1},t_{i,2k} \right),
-\]
-where $t_{i,1}<\ldots<t_{i,K_i}$ and, with a slight abuse of notation, $t_{i,1}$ and $t_{i,K_i}$ may take the values $-\infty$ or $+\infty$, respectively. Thus
-\[
-\Prob_{\theta}(X_i \in A_i) = \sum_{k=1}^{K_i} (-1)^k F(t_{i,k}-\theta).
-\]
-In particular, since $f$ is differentible in $\theta$, $\Prob_{\theta}(X_i \in A_i)$ is twice differentiable, and we may write
-\begin{align*}
-\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)  = \Prob_{\theta} (X_i \in A_i) + \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \frac{h}{\sqrt{n}} + o(h), 
-\end{align*}
-and thus
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)} = \log \left(1 + \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} + o(h) \right) \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2 + o(h^2).
-\end{align*}
-Similarly, we have
-\begin{align*}
-& \log \frac{\Prob_{\theta+\frac{h}{\sqrt{n}}}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} \\
-& = \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \frac{h}{\sqrt{n}} - \frac{h}{2n} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 + o(h^2).
-\end{align*}
-From \eqref{eq:LAN_proof1} we obtain
-\begin{align*}
-& \log \frac{ \Prob_{\theta + \frac{h}{\sqrt{n}}}(b_1,\ldots,b_n)} { \Prob_\theta (b_1,\ldots,b_n) }   = \frac{h}{\sqrt{n}} \sum_{i=1}^n  
-\left( 
-\frac{b_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-b_i}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}   \right) \\
- & - \frac{h^2}{2n} 
- \sum_{i=1}^n 
-\left( 
- \frac{b_i+1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-b_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)}  \right)^2 \right) + o(h^2) \\
-\end{align*}
-%
-Noting that 
-\[
-\frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \notin A_i)}{\Prob_{\theta}(X_i \notin A_i)} = \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)},
-\]
-the proof is completed by proving the following two claims:
-\begin{itemize}
-\item[I.] 
-For $i=1,\ldots,n$ denote 
-\[
-U_i = \frac{B_i+1}{2}  \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  + 
- \frac{1-B_i}{2}  \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}. 
-\]
-Then 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0, \kappa(\theta) \right). 
-\]
-\item[II.]
-For $i=1,\ldots,n$ denote 
-\[
-V_i =  \frac{B_i-1}{2} 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2
-+ 
- \frac{1-B_i}{2} \left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2.
-\]
-Then 
-\[
-\frac{1}{n} \sum_{i=1}^n V_i \overset{a.s.}{\rightarrow} \kappa(\theta). 
-\]
-\end{itemize}
-\subsubsection*{Proof of Claim I}
-First note that 
-\begin{align*}
-\ex{U_i} & = 
- \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=1)   + 
- \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}   \Prob (B_i=-1)  = 0. 
-\end{align*}
-In addition,
-\begin{align*}
-& \ex{ U_i^2} = 
-\left( \frac{\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{\Prob_{\theta}(X_i \in A_i)}  \right)^2  \Prob (B_i=1)   + 
-\left( \frac{-\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i)}{1-\Prob_{\theta}(X_i \in A_i)}  \right)^2 \Prob (B_i=-1) \\
-& =
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)} +  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)} \\
- & =  
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left(1-\Prob_{\theta}(X_i \in A_i) \right)} 
-\end{align*}
-Therefore
-\[
-\frac{1}{n} \sum_{i=1}^n \ex{ U_i^2} = L_n(A_1,\ldots,A_n) \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ such that the limit above exists.
-We now verify that the sequence $\{ U_i,\,i=1,2,\ldots \}$ satisfies Lyaponov's condition for his version of the central limit time: for any $\delta>0$ we have that
-\begin{align*}
-& \ex{ \left| U_i \right|^{2+\delta} }=
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} 
-\end{align*}
-and
-\begin{equation}
-\frac{\sum_{i=1}^n\ex{\left| U_i \right|^{2+\delta}} } { \left( \sum_{i=1}^n \ex{U_i^2}  \right)^\delta} = 
-\frac{ \frac{1}{n^{1+\delta}} \sum_{i=1}^n \ex{ |U_i|^{2+\delta}} }{ \left(\frac{1}{n} \sum_{i=1}^n \ex{U_i^2 } \right)^\delta}. 
-\label{eq:Lyaponov}
-\end{equation}
-Next, we claim that there exits $\delta>0$ and $K(\delta)>0$, that are independent of $n$, such that
-\begin{align}
-\frac{1}{n} \sum_{i=1}^n \ex{ |U_i|^{2+\delta}}  < K(\delta) \label{eq:Lyaponov_num}
-\end{align} 
-for all $n$ large enough. To see this, note that
-\begin{align*}
-& \ex{ |U_i|^{2+\delta} }= 
- \frac{ \left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(\Prob_{\theta}(X_i \in A_i))^{1+\delta}} +  
-  \frac{ \left|\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta}} {(1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}  \\
-  &  = \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} } 
-  \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}   \right) \\
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}}. 
-\end{align*}
-%where the last transition is because 
-%\[
-% \left( (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta} + (\Prob_{\theta}(X_i \in A_i))^{1+\delta}  \right) \leq 1. 
-%\]
-We now use the fact that each $A_i$ is a finite union of intervals.
-Under the assumption that there exists $\delta>0$ such that $\eta^{1+\delta}(x)/f^\delta(x)$ is uniquely maximized by the origin and is non-increasing in $|x|$, Lemma~\ref{lem:bound_intervals_delta} implies
-\begin{align*}
-  &  \leq \frac{\left| \frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right|^{2+\delta} }
-  { (\Prob_{\theta}(X_i \in A_i))^{1+\delta} (1-\Prob_{\theta}(X_i \in A_i))^{1+\delta}} = \frac{\left| \sum_{k=1}^{K_i} (-1)^k f(x_{i,k}-\theta) \right|^{2+\delta} }
-  { \left( \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta} \left( 1 - \sum_{k=1}^{K_i} (-1)^k F(x_{i,k}-\theta) \right)^{1+\delta}} \\
-  & \leq 4^{1+\delta}(f(0))^{2+\delta}.
-\end{align*}
-It follows that
-\[
-\frac{1}{n} \sum_{i=1}^n \ex{ |U_i|^{2+\delta}} \leq 4^{1+\delta}(f(0))^{2+\delta}, 
-\]
-and thus the numerator of \eqref{eq:Lyaponov}, as well as the entire expression, goes to zero. From Lyaponov's central limit theorem we obtain 
-\[
-\frac{1}{\sqrt{n}} \sum_{i=1}^n U_i \overset{d}{\rightarrow} \Ncal\left(0,\kappa(\theta) \right). 
-\]
-
-\subsubsection*{Proof of Claim II} 
-We have:
-\begin{align*}
-\ex{ V_i}  & = 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i)}  
-+ 
- \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{1-\Prob_{\theta}(X_i \in A_i)}  \\
- & = 
-  \frac{ \left(\frac{d}{d\theta} \Prob_{\theta}(X_i \in A_i) \right)^2}{\Prob_{\theta}(X_i \in A_i) \left( 1-\Prob_{\theta}(X_i \in A_i) \right)}  
-\end{align*}
- We conclude that:
-\begin{equation} \label{eq:LAN_limit_cond}
-\frac{1}{n} \sum_{i=1}^n \ex{ V_i} =   L_n(A_1,\ldots,A_n)  \to \kappa(\theta)
-\end{equation}
-Since the $V_i$s are independent of each other, Kolmogorov's law of large numbers implies
-%(e.g. \cite[Theorem 10.2.3]{sen1994large}) 
-\[
-\frac{1}{n} \sum_{i=1}^n  V_i \overset{a.s.}{\longrightarrow} \kappa(\theta)
-\]
-for any $\theta \in \Theta$ for which the limit \eqref{eq:LAN_limit_cond} exists.
-\QEDA
-
-\subsection{Proof of Theorem~\ref{thm:non_existence}
+\section{Proof of Theorem~\ref{thm:non_existence}}
 \label{proof:thm:non_existence}
-}
 

### 2019-12-17 distributed-estimation.tex
Proving distributed results

@@
   \begin{enumerate}[(i)]
-  \item \label{item:density-nice}
+  \item \label{item:lipschitz-density}
     The density function $f$ of $X_n - \theta$ is Lipschitz continuous.
   \item \label{item:finite-intervals}
-    Each set $A_n$ is a finite union of at most $K < \infty$ intervals
-    (which may include $\pm \infty$), and
-    $0 < \inf_n P_\theta(A_n) \le \sup_n P_\theta(A_n) < 1$.
+    Each set $A_n$ is the finite union of $k_n$ disjoint intervals
+    (which may include $\pm \infty$), where
+    \begin{equation*}
+      \frac{1}{n} \cdot \max_{i \le n} \frac{k_i^3}{P_\theta(A_i)^4
+        (1 - P_\theta(A_i))^4} \to 0.
+    \end{equation*}
+    %% Each set $A_n$ is a finite union of at most $K < \infty$ intervals
+    %% (which may include $\pm \infty$), and
+    %% $0 < \inf_n P_\theta(A_n) \le \sup_n P_\theta(A_n) < 1$.
   \item \label{item:limit-variance}
@@
   observations $B_i = \indic{X_i \in A_i}$.
-  Then for any
+  Then for $Z \sim \normal(0, 1)$ and any
   symmetric and quasi-convex function $L$,
   \begin{align*}
-    & \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right]
-    \\
-    & \qquad \qquad \qquad \qquad \geq \mathbb E \left[ L (Z/\sqrt{\kappa(\theta)}) \right],
+    & \liminf_{c \to \infty} \liminf_{n \to \infty}
+    \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}
+    \E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right] \\
+    & \qquad \qquad \qquad \qquad \geq
+    \E\left[ L (Z/\sqrt{\kappa(\theta)}) \right].
   \end{align*}
-  where $Z \sim \normal(0,1)$.
 \end{theorem}

### 2019-12-17 proof-lan-distributed.tex
Proving distributed results

@@
 
+We begin with an argument on the smoothness properties of the densities,
+which is important for our Taylor expansions to come.
+\begin{lemma}
+  \label{lemma:derivative-bounds}
+  Let
+  Assumption~\ref{assumption:detection-regions}\eqref{item:lipschitz-density}
+  and \eqref{item:finite-intervals} hold. Then for any $A = \cup_{i = 1}^k
+  \{[a_i, b_i]\}$ and $h \in \R$,
+  \begin{equation*}
+    P_{\theta + h}(A) = P_\theta(A) + \dPtheta(A) h \pm
+    k \cdot \lip(f) h^2,
+  \end{equation*}
+  where
+  \begin{equation}
+    \dPtheta(A) = \sum_{i = 1}^k f(a_i - \theta) - f(b_i - \theta).
+    \label{eqn:expansion-dPtheta}
+  \end{equation}
+  Additionally, we have the bounds
+  \begin{equation}
+    \label{eqn:bound-density-diffs}
+    |f(b) - f(a)| \le 2 \sqrt{\lip(f) P([a, b])}
+    ~~ \mbox{and} ~~
+    |\dPtheta(A)| \le 2 \sqrt{k \lip(f)}.
+  \end{equation}
+\end{lemma}
+\noindent
+See Section~\ref{sec:proof-derivative-bounds} for a proof.
+
+The second lemma provides the local asymptotic normality we require.
 \begin{lemma}
   \label{lemma:lan-bits}
-  Let Assumption~\ref{assumption:detection-regions}\eqref{item:density-nice}
-  and~\eqref{item:finite-intervals} hold, and let
-  $B_i = \indic{X_i \in A_i}$.
-  Let $h_n \to h \in \R$. Then for any $\theta \in \mbox{int}\Theta$,
+  Let
+  Assumption~\ref{assumption:detection-regions}\eqref{item:lipschitz-density}
+  and~\eqref{item:finite-intervals} hold, and let $B_i = \indic{X_i \in
+    A_i}$.  Let $h_n \to h \in \R$. Then for any $\theta \in
+  \mbox{int}\Theta$,
   \begin{equation*}
@@
     \sum_{i = 1}^n \score_\theta(B_i)
-    - \frac{h}{4n} \sum_{i = 1}^n \var(\score_\theta(B_i))
-    - \frac{h}{4n} \sum_{i = 1}^n \score_\theta(B_i)^2
+    - \frac{h^2}{4n} \sum_{i = 1}^n \var(\score_\theta(B_i))
+    - \frac{h^2}{4n} \sum_{i = 1}^n \score_\theta(B_i)^2
     + o_P(1).
@@
 asymptotic normality (Definition~\ref{definition:lan}) of the family
-$\{P_\theta\}$. Indeed, the assumption that $f$ is Lipschitz guarantees that
-$f(z) \le \sqrt{\lip(f)}$ for all $z$, and thus we obtain that
-$|\dPtheta(A_n)| \le K \sqrt{\lip(f)}$ for all $n$, whence $\sup_n
-\max\{|\score_\theta(A_n)|, |\score_\theta(A_n^c)|\} \le C < \infty$ for
-some $C$. Thus, the strong law of large numbers
-gives that
-$\frac{1}{n} \sum_{i = 1}^n \score_\theta(B_i)
-\cas 0$ as $\E_\theta[\score_\theta(B_i)] = 0$, and Lyapunov's central
-limit theorem applies to give
+$\{P_\theta\}$. Indeed, Lemma~\ref{lemma:derivative-bounds} guarantees that
+$|\dPtheta(A_n)| \le 2\sqrt{k_n \lip(f)}$ for all $n$, so that
+$\E_\theta[|\score_\theta(B_i)|^3] \le C \frac{k_i^{3/2}
+  \lip(f)^{3/2}}{P_\theta(A_i)^2 (1 - P_\theta(A_i))^2}$, while
+Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals}
+guarantees that
+$\frac{1}{n^3} \sum_{i = 1}^n \E_\theta[|\score_\theta(B_i)|^3]
+\to 0$. Because $\E[\score_\theta(B_i)] = 0$,
+the Lyapunov central limit theorem
+applies to give
 \begin{equation*}
@@
 \end{equation*}
-for any symmetric quasi-convex loss $L$, where $Z \sim normal(0, 1)$.
+for any symmetric quasi-convex loss $L$, where $Z \sim \normal(0, 1)$.
 This immediately gives Theorem~\ref{theorem:non-adaptive-minimax}.
@@
 
-Our proof follows that of \cite[Thm.~7.2]{VanDerVaart98} closely.
-The first step is to note that
-if $\lip(f)$ denotes the Lipschitz constant of $f$, then for any
-$h \in \R$ and $A = \cup_{i = 1}^K \{[t_i^-, t_i^+]\}$, we have
-\begin{equation}
-  \label{eqn:expansion-dPtheta}
-  P_{\theta + h}(A) = P_\theta(A) + \dPtheta(A)
-  \pm \frac{K \cdot \lip(f)}{2}  h^2.
-\end{equation}
-Indeed, for any interval $[t_0, t_1]$ we immediately have
-\begin{align*}
-  P_{\theta + h}([t_0, t_1])
-  & = \int_{t_0}^{t_1} f(z - \theta - h) dz
-  = \int_{t_0}^{t_1} \left(f(z - \theta)
-  + \int_0^h f'(z - \theta - v) dv\right) dz \\
-  & = P_\theta([t_0, t_1])
-  + \int_0^h \int_{t_0}^{t_1} f'(z - \theta - v) dz dv \\
-  & = P_\theta([t_0, t_1])
-  + \int_0^h \left[f(t_1 - \theta - v) - f(t_0 - \theta - v)\right] dv \\
-  & = P_\theta([t_0, t_1])
-  + \left(f(t_1 - \theta) - f(t_0 - \theta)\right) h
-  \pm \int_0^h \lip(f) |v| dv \\
-  & = P_\theta([t_0, t_1]) + \dPtheta([t_0, t_1])
-  \pm \frac{\lip(f)}{2} h^2,
-\end{align*}
-giving the result~\eqref{eqn:expansion-dPtheta}.
-
-Now we demonstrate a type of uniform quadratic mean differentiability
-(Definition~\ref{definition:qmd}) for such sets
-$A$. First, note that by a Taylor approximation and concavity
-of $\sqrt{\cdot}$, we have
+Our proof follows that of \cite[Thm.~7.2]{VanDerVaart98} closely.  We first
+demonstrate a type of uniform quadratic mean differentiability
+(Definition~\ref{definition:qmd}) for sets $A$ that are finite unions of
+intervals. By a Taylor approximation and concavity of
+$\sqrt{\cdot}$, we have
 \begin{equation*}
@@
 recalling that $\score_\theta(A) = \dPtheta(A) / P_\theta(A)$,
-for any $h \in \R$ the expansion~\eqref{eqn:expansion-dPtheta} yields
+for any $h \in \R$ and $A = \cup_{i = 1}^k \{[t_i^-, t_i^+]\}$ the
+union of $k$ intervals, the expansion~\eqref{eqn:expansion-dPtheta} yields
 \begin{equation*}
@@
   \left(
-  \frac{K \lip(f)}{2 \sqrt{P_\theta(A)}} h^2
+  \frac{k \lip(f)}{2 \sqrt{P_\theta(A)}} h^2
   + \frac{(|\dPtheta(A) h| + h^2 \lip(f))^2}{P_\theta(A)^{3/2}}
-  \right)^2.
+  \right)^2,
 \end{equation*}
-Now, note that for any Lipschitz-continuous $f$, that
-$1 = \int f(z) dz$ and $f \ge 0$ yield that
-$f(z) \le \sqrt{\lip(f)}$ for all $z \in \R$. Thus, under
+valid for $h$ such that
+$|\dPtheta(A) h| \le P_\theta(A) / 4$ and
+$k h^2 \lip^2(f) \le P_\theta(A) / 4$.
+Thus, under
 Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals},
-there exists a finite constant $C < \infty$ such that
+there exists a numerical constant $C < \infty$ such that
 \begin{subequations}
@@
       + \frac{k^4 h^4 \lip^4(f)}{P_\theta(A)^2}
-      \right] \cdot h^4
+      \right] \cdot h^4,
   \end{align}
-  where $C < \infty$ is a numerical constant, valid whenever $|\dPtheta(A) h|
-  \le P_\theta(A) / 4$ and $k h^2 \lip^4(f) \le P_\theta(A) / 4$,
+  valid whenever $|\dPtheta(A) h|
+  \le P_\theta(A) / 4$ and $k h^2 \lip^2(f) \le P_\theta(A) / 4$,
   and similarly, we have
@@
 
-Now, for shorthand, define $P_n = P_{\theta + h_n / \sqrt{n}}$ and $P =
+For shorthand, define $P_n = P_{\theta + h_n / \sqrt{n}}$ and $P =
 P_\theta$, and let $p_n, p$ be shorthand for the p.m.f.s of the two
@@
 that
-\begin{align*}
-  \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
-  & \le 
-  C \frac{k^2 \lip^2(f) + \score_\theta(A_i)^2
+\begin{align}
+  \lefteqn{\var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
+    \le 
+    C \frac{k_i^2 \lip^2(f) + \score_\theta(A_i)^2
       + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
@@
       P_\theta(A_i)^3 P_\theta(A_i^c)^3}
-  \frac{h_n^8}{n^4} \\
-  & \le 
-  C \frac{k^2 \lip^2(f) + \score_\theta(A_i)^2
+    \frac{h_n^8}{n^4}} \nonumber \\
+  & \qquad\qquad\qquad\qquad\qquad \le 
+  C \frac{k_i^2 \lip^2(f) + \score_\theta(A_i)^2
   + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
@@
   \frac{h^8}{n^4}
-\end{align*}
+  \label{eqn:var-wni-expansion}
+\end{align}
 whenever
@@
   ~~ \mbox{and} ~~
-  \frac{h^2}{n} \lip^2(f)
+  \frac{k_i h^2}{n} \lip^2(f)
   \le \frac{\min\{P_\theta(A_i), P_\theta(A_i^c)\}}{4}
 \end{equation*}
-In particular, using the uniform boundedness of $0 < P_\theta(A_i) < 1$,
-we see that unifomly in $i, n$ we have
+Now, we use
+Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals},
+coupled with Lemma~\ref{lemma:derivative-bounds} to show that the summed
+variances converge to zero.  Indeed, Lemma~\ref{lemma:derivative-bounds} and
+inequality~\eqref{eqn:var-wni-expansion} give that
 \begin{equation*}
-  \var\left(W_{n,i} - \frac{h}{\sqrt{n}} \score_\theta(B_i)\right)
-  = O\left(\frac{h^4}{n^2}\right)
-  + O(1) \E[\score_\theta(B_i)^2]
-  \frac{(h_n - h)^2}{n},
+  \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
+  \le C \cdot
+  \left[\frac{k_i^2}{P_\theta(A_i) P_\theta(A_i^c)}
+    \frac{1}{n}
+    + \frac{k_i}{P_\theta(A_i) P_\theta(A_i^c)}
+    \frac{1}{n}
+    + \frac{k_i^4}{P_\theta(A_i)^3 P_\theta(A_i^c)^3}
+    \frac{1}{n^3}\right] \frac{1}{n},
 \end{equation*}
-while $\E[\score_\theta(B_i)] = 0$. Additionally, defining $\mu_i$ to be the
+where $C < \infty$ depends only on $\lip(f)$ and $h$ (both of which are
+uniformly bounded) whenever
+\begin{equation*}
+  \frac{k_i}{P_\theta(A_i) P_\theta(A_i^c)} \frac{1}{n} \le
+  \frac{1}{C}.
+\end{equation*}
+Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals}
+thus implies that $\E[\score_\theta(B_i)] = 0$ and
+\begin{equation}
+  \label{eqn:summed-variances-to-zero}
+  \var\left(\sum_{i = 1}^n W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
+  \right)
+  = \sum_{i = 1}^n \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
+  \right)
+  \to 0.
+\end{equation}
+
+We now control the expectation of the $W_{n,i}$. Defining $\mu_i$ to be the
 induced counting measure on $B_i = \indic{X_i \in A_i}$,
@@
   \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}d\mu_i(b) \\
-  & = -\frac{h^2}{4n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
-  - O(h^4 / n) - O(h^2 / n^{1/2})
+  & = -\bigg(\frac{h^2}{4n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]\bigg)
+  - o(1)
 \end{align*}
-uniformly in $h$.
+uniformly in $h$, with a derivation completely paralleling that above.
 Therefore, we obtain
@@
 where the remainder $|R(W_{n,i})| \le |W_{n,i}|$ for $|W_{n,i}| \le 1$.
-In particular, using the Taylor approximation to $\sqrt{\cdot}$ and
-that $\inf_i P_\theta(A_i) > 0$, we have
-$\max_i W_{n,i} \cas 0$, so that
+Using the Taylor expansions of $\sqrt{\cdot}$ and
+Lemma~\ref{lemma:derivative-bounds}, we have
+\begin{align}
+  \nonumber
+  \half W_{n,i}
+  & = \half \score_\theta(B_i)
+  \frac{h_n}{\sqrt{n}}
+  \pm \left|\frac{h_n^2}{n} \frac{k_i \lip(f)}{p(B_i)}
+  + \frac{h_n^2}{n} \score_\theta(B_i)^2
+  + \frac{ h_n^4}{n^2} \frac{k_i^2 \lip(f)^2}{p(B_i)^2}\right| \\
+  & \in \pm
+  C \left|\frac{\sqrt{k_i}}{\sqrt{n} p(B_i)}
+  + \frac{k_i}{n p(B_i)}
+  + \frac{\sqrt{k_i}}{p(B_i)^2 n}
+  + \frac{k_i^2}{p(B_i)^2 n^2}
+  \right| \to 0,
+  \label{eqn:max-wni-zero}
+\end{align}
+where $C < \infty$ depends only on $\lip(f)$ and $h_n$ and so is
+uniformly bounded;
+the limit follows from
+and Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals}.
+Consequently $\max_i W_{n,i} \to 0$, so that
 \begin{equation}
@@
   = \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
+  - \frac{1}{4} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
   - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2 + o_P(1).
@@
 
-It remains to compute $\E[W_{n,i}^2]$. Using the
-expansions~\eqref{eqn:h-fourth}, we have for any $B = \indic{X \in A}$,
-%% \begin{align*}
-%%   \E\left[
-%%     \left(\sqrt{\frac{P_{\theta + h}(B)}{P_\theta(B)}}
-%%     - 1\right)^2
-%%     \right]
-%%   & = (\sqrt{P_{\theta + h}(A)} - \sqrt{P_\theta(A)})^2
-%%   + (\sqrt{P_{\theta + h}(A^c)} - \sqrt{P_\theta(A^c)})^2 \\
-%%   & = (h \dPtheta(A) / \sqrt{P_\theta(A)}
-%%   + O(h^2)) + (h \dPtheta(A^c) / \sqrt{P_\theta(A^c)} + O(h^2))^2 \\
-%%   & = h^2 P_\theta(A) \score_\theta(A)^2
-%%   + h^2 P_\theta(A^c) \score_\theta(A^c)^2
-%%   + O(h^3)
-%%   = h^2 \var(\score_\theta(B))
-%%   + O(h^3)
-%% \end{align*}
-%% uniformly in $h$,
-%% and
+It remains to compute $\E[W_{n,i}^2]$. Using the bounds
+that $|\score_\theta(B_i)| \le C \sqrt{k_i} / p(B_i)$ from
+Lemma~\ref{lemma:derivative-bounds},
+the
+expansion~\eqref{eqn:max-wni-zero}
+yields
 \begin{align*}
-  \left(\sqrt{\frac{P_{\theta + h}(B)}{P_\theta(B)}}
-  - 1\right)^2
-  & = \left(\sqrt{1 + h \score_\theta(B) + O(h^2)} - 1\right)^2
-  % = \left(h \score_\theta(B) / 2 + O(h^2)\right)^2
-  = h^2 \score_\theta(B)^2 / 4 + O(h^3)
+  \lefteqn{\left|\E\left[W_{n,i}^2 - \frac{h_n^2}{2n} \score_\theta(B_i)^2\right]
+    \right|} \\
+  &
+  \le \frac{C}{n} \left[
+    \frac{k_i^{3/2}}{p(A_i)(1 - p(A_i)) \sqrt{n}}
+    + \frac{k_i^{3/2}}{p(A_i)^2 (1 - p(A_i))^2 \sqrt{n}}
+    + \frac{k_i^2}{p(A_i)(1 - p(A_i))} \frac{1}{n^{3/2}}
+    \right] \\
+  & \qquad ~ +
+  \frac{C}{n}
+  \left[\frac{k_i^2}{p(A_i)(1 - p(A_i))} \frac{1}{n}
+    + \frac{k_i}{p(A_i)^3(1 - p(A_i))^3} \frac{1}{n}
+    + \frac{k_i^4}{p(A_i)^3 (1 - p(A_i))^3} \frac{1}{n^3} \right],
 \end{align*}
-uniformly in $h$ near 0, as the probabilities $P_\theta(A)$ are bounded from
-0 and 1. Thus
+where $C$ depends only on $h$ and $\lip(f)$.
+Thus
 \begin{equation*}
@@
   = \frac{h_n^2}{n} \sum_{i = 1}^n \score_\theta(B_i)^2
-  + O(h_n^2 / \sqrt{n}),
+  + o(1),
 \end{equation*}
-giving Lemma~\ref{lemma:lan-bits}.
+giving the theorem.
+
+%% Returning to the expansion~\eqref{eqn:almost-at-the-end}, we thus obtain
+%% %% \begin{equation*}
+%% %%   \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
+%% %%   = \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
+%% %%   - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2 + o_P(1).
+
+%% %% \begin{equation*}
+%% %%   W_{n,i}
+%% %%   = \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
+%% %%   \pm \frac{h_n^2 k \lip(f)}{n p(B_i)}
+%% %%   \pm \frac{1}{2}
+%% %% \end{equation*}
+
+%% \begin{equation*}
+%%   g(b) = h \score_\theta(b),
+%% \end{equation*}
+
+%% Under the assumption that $0 < \inf_i P_{\theta}(A_i) \le \sup_i P_{\theta}(A_i)
+%% < 1$, the random
+
+\subsection{Proof of Lemma~\ref{lemma:derivative-bounds}}
+\label{sec:proof-derivative-bounds}
+
+To see the first claim of the lemma, we consider the simpler special case
+that $A = [a, b]$. Then as $f$ is Lipschitz (and hence absolutely
+continuous and a.e.\ differentiable with $\linf{f'} \le \lip(f)$),
+we have
+\begin{align*}
+  P_{\theta + h}(A)
+  - P_\theta(A)
+  & = \int_a^b (f(z - \theta - h) - f(z - \theta)) dz \\
+  & = -\int_a^b \int_0^h f'(z - \theta - u) du dz \\
+  & = -\int_0^h \int_a^b f'(z - \theta - u) dz du \\
+  & = \int_0^h f(a - \theta - u) - f(b - \theta - u) du \\
+  & = \int_0^h (f(a - \theta) - f(b - \theta)) du
+  \pm 2 \int_0^h \lip(f) u du \\
+  & = \left[f(a - \theta) - f(b - \theta)\right] h \pm \lip(f) h^2.
+\end{align*}
+This gives the first two claims of the lemma.
+
+For the second, we require a bit more work.
+Let $L = \lip(f)$ for shorthand. Let $a < b$.
+Then we always have
+\begin{equation}
+  \label{eqn:interval-length-thing}
+  P([a, b])
+  \ge \int_a^b f(z) dz
+  \ge \int_a^b \max\{f(b) - L (b - z), f(a) - L(z - a), 0\} dz.
+\end{equation}
+If $f(a) + f(b) \ge L (b - a)$, then the point $\hat{z} =
+\frac{a + b}{2} - \frac{f(b) - f(a)}{2L}$ satisfies both $f(b) - L(b -
+\hat{z}) \ge 0$ and $f(a) - L(\hat{z} - a) \ge 0$. The
+integral~\eqref{eqn:interval-length-thing} then becomes
+\begin{align*}
+  \lefteqn{\int_a^{\hat{z}}
+    (f(a) - L (z - a) dz)
+    + \int_{\hat{z}}^b
+    (f(b) - L (b - z)) dz} \\
+  & = \frac{f(a) + f(b)}{2}
+  \left(\frac{b - a}{2}\right)
+  - L \left(\frac{b - a}{2} \right)^2
+  + \frac{(f(b) - f(a))^2}{4L},
+\end{align*}
+and using the assumption that $\frac{f(a) + f(b)}{2} \ge L(b - a)$,
+we obtain
+\begin{align*}
+  \frac{(f(b) - f(a))^2}{4L}
+  & \le \frac{f(b) + f(b)}{2} \frac{b - a}{2}
+  - L \left(\frac{b - a}{2}\right)^2
+  + \frac{(f(b) - f(a))^2}{4L}
+  \le P([a, b]).
+\end{align*}
+That is, $|f(b) - f(a)| \le 2 \sqrt{\lip(f) P([a, b])}$.
+In the converse case that $f(a) + f(b) \le L(b - a)$, then
+the integral~\eqref{eqn:interval-length-thing} becomes
+\begin{align*}
+  P([a, b])
+  & \ge \int_a^{a + \frac{f(a)}{L}}
+  (f(a) - L (z - a)) dz
+  + \int_{b - \frac{f(b)}{L}}^b (f(b) - L (b - z)) dz \\
+  & = \frac{f(a)^2}{L}
+  - \frac{f(a)^2}{2L}
+  + \frac{f(b)^2}{L}
+  - \frac{f(b)^2}{2L},
+\end{align*}
+so that $\sqrt{f(a)^2 + f(b)^2} \le \sqrt{2 \lip(f) P([a, b])}$.  In sum,
+we have demonstrated that always the first
+bound~\eqref{eqn:bound-density-diffs} holds.
+To show the second inequality in expression~\eqref{eqn:bound-density-diffs},
+note that
+$\sum_i P([a_i, b_i]) \le 1$, and apply Cauchy-Schwarz.

### 2019-12-17 distributed-estimation.tex
Finished writing major proofs and fixing references. Still needs a once through

@@
 \end{theorem}
+\noindent
+See Appendix~\ref{sec:proof-non-adaptive-minimax} for a proof.
 
@@
   \delta)}{n \kappa(\theta)} + o(1/n)$.
-We next turn to the uniformity limitations of non-adaptive strategies.
 
-\subsection{Non-existence of a Uniformly Optimal Strategy}
-
-We now show that under LAN models, the optimal minimal risk $1/\eta(0)$ can
-only be attained at a finite number of points within $\Theta$. This fact
-implies in particular that, unlike in the adaptive setting, no distributed
-estimation scheme has ARE of $\eta(0)\sigma^2$ for all $\theta \in \Theta$.
+Yet Theorem~\ref{theorem:non-adaptive-minimax}
+limits non-adaptive strategies in stronger ways.
+%%
+%% \subsection{Non-existence of a Uniformly Optimal Strategy}
+%%
+Under the density models we have considered, with the additional
+Assumption~\ref{assump:failure_rate}, we can show stronger
+optimality results that adaptivity is essential for achieving
+optimal convergence guarantees.
+Recall the transformation~\eqref{eq:eta_def} of the
+hazard rate function, $\eta(x) = \frac{f^2(x)}{F(x)(1 - F(x))}$, which
+has unique maximum at $x = 0$ under Assumption~\ref{assump:failure_rate}.
+When each detection region $A_n$ consists of a bounded number
+of intervals, the next theorem
+shows that
+the optimal minimal risk $1/\eta(0)$ can
+only be attained at finitely many points within $\Theta$.
+In particular, distinct from the adaptive setting, no distributed
+estimation scheme can achieve asymptotic variance $\eta(0)$
+uniformly in $\theta \in \Theta$.
 
 \begin{thm} \label{thm:non_existence}
-Under conditions (i)-(iii) in Theorem~\ref{thm:LAN1}, assume that each $A_i$ is the union of at most $K$ intervals.
-The number of points $\theta \in \Theta$ satisfying $\kappa(\theta) = \eta(0)$ is at most $2K$.
+  Let Assumptions~\ref{assump:failure_rate}
+  and~\ref{assumption:detection-regions} hold.
+  Additionally, assume that $A_i$ is the union of at most $K$
+  intervals. The number of points $\theta \in \Theta$ satisfying
+  $\kappa(\theta) = \eta(0)$ is at most $2K$.
 \end{thm}
-
-\begin{proof}
-See Appendix~\ref{proof:thm:non_existence}.
-\end{proof}
-
-We next consider the case where each detection region is a half-open interval, i.e., the $i$th message is obtained by comparing $X_i$ against a single threshold.
-As we explain next, the existence of a density for the sequence of thresholds is enough to establish local asymptotic normality and leads to a closed form expression for the precision parameter and the ARE.
+\noindent
+See Appendix~\ref{proof:thm:non_existence} for a proof.
 
@@
 
-\subsection{Threshold Detection \label{subsec:threshold}}
+\subsection{Threshold Detection}
+\label{subsec:threshold}
+
+We now consider consider a restricted case where each detection region is a
+half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
+against a single threshold. Under adaptive signal acquisition,
+this is sufficient for asymptotic optimality;
+in non-adaptive settings, it is not sufficient, though we may characterize
+a few additional optimality results.
+%% As we explain next, the existence of a density
+%% for the sequence of thresholds is enough to establish local asymptotic
+%% normality and leads to a closed form expression for the precision parameter
+%% and the ARE.
 Assume now that each $B_i$ is of the form
@@
 \end{equation}
-where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder.
-In other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and $\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$.
-It follows that
+where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder. In
+other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and
+$\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
 \begin{equation}
-L_n(A_1,\ldots,A_n;\theta) = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
+  L_n(A_1,\ldots,A_n;\theta)
+  = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
   \label{eq:Ln_threshold}
 \end{equation}
-A natural condition for the existence of the limit \eqref{eq:Ln_threshold} as $n\to \infty$ is that the empirical distribution of the threshold values converges to a probability measure.
-Specifically, for an interval $I \subset \mathbb R$ define
-\[
+A natural condition for the existence of the limit \eqref{eq:Ln_threshold}
+as $n\to \infty$ is that the empirical distribution of the threshold values
+converges to a probability measure. Specifically, for an interval $I \subset
+\mathbb R$ define
+\begin{equation*}
   \lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
-\]
-Theorem~\ref{thm:LAN1} implies:
+\end{equation*}
+Then an investigation of the proof of
+Theorem~\ref{theorem:non-adaptive-minimax} in
+Section~\ref{sec:proof-non-adaptive-minimax}, specifically
+Sec.~\ref{sec:proof-lan-bits} and the bounds~\eqref{eqn:h-fourth}, show that
+as $\eta(t) \le \eta(0)$ for all $t \in \R$ under
+Assumption~\ref{assump:failure_rate}, the following corollary follows. (The
+corollary relies on local asymptotic normality~\cite[Ch.~7]{VanDerVaart98};
+see Appendix~\ref{sec:proof-sgd-regular} for some brief discussion of such
+conditions.)
 \begin{cor} \label{cor:LAN_thresh}
-Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$.
-Then $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a LAN family with precision parameter
-\[
+  Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that
+  $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on
+  $\mathbb R$. Then the conclusions of
+  Theorem~\ref{theorem:non-adaptive-minimax} apply with
+  %% $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a
+  %% LAN family with precision parameter
+  \begin{equation*}
     \kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
-\]
+  \end{equation*}
+  Moreover, the family of laws of $\{B_i = \sgn(X_i - t_i)\}_{i = 1}^n$
+  under $\{P_\theta\}_{\theta \in \Theta}$ is locally asymptotically normal
+  with information $\kappa(\theta)$.
 \end{cor}
-The condition that $\lambda_n$ converges to a probability measure is satisfied, for example, whenever the $t_1,\ldots,t_n$s are drawn independently from a probability distribution $\lambda(dt)$ on $\mathbb R$.
-\par
-Due to local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by 
+
+The condition that $\lambda_n$ converges to a probability measure is
+satisfied, for example, whenever the $t_1,\ldots,t_n$s are drawn
+independently from a probability distribution $\lambda(dt)$ on $\mathbb
+R$.
+
+The local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum
+likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by
 ${\theta}^{ML}_n$, is local asymptotic minimax in the sense that
-\[
-\sqrt{n} \left( {\theta}^{ML}_n - \theta \right) \overset{d}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
-\]
-It follows that when the density of the threshold values converges to a probability measure, the ARE of the ML estimator is $\kappa(\theta)\sigma^2$, and this ARE is maximal with respect to all local alternative estimators for $\theta$.
-We note that ${\theta}^{ML}_n$ is given by the root of
+\begin{equation*}
+  \sqrt{n} \left( {\theta}^{ML}_n - \theta \right)
+  \cd \normal\left(0, 1/\kappa(\theta) \right). 
+\end{equation*}
+It follows that when the density of the threshold values converges to a
+probability measure, the ML estimator has asymptotic variance $1 /
+\kappa(\theta)$, and this is minimal. We note that ${\theta}^{ML}_n$
+solves
 \begin{equation}
   \label{eq:ML}
-\sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) },  
+  0 = \sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) }.
 \end{equation}
-This root is unique since the log-likelihood function is concave.
-Furthermore, for any $n \in \mathbb R$, we have that ${\theta}^{ML}_n  \in [t_{(1)}, t_{(n)}]$ where $t_{(i)}$ denotes the $i$th element of $\{t_1,t_2\ldots\}$.
-Therefore, if $\{t_1,t_2\ldots\}$ is bounded (for example $\{t_1,t_2\ldots\} \subset \Theta$), then
-\[
+If the collection $\{t_1,t_2\ldots\}$ is bounded
+(for example $\{t_1,t_2\ldots\} \subset \Theta$), then
+\begin{equation*}
 \lim_{n\to \infty} n \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
-\] 
-so that the ML estimator attains the local asymptotic MSE of Corollary~\ref{cor:LA_minimax}. \par
-%
-Since $\eta(x)$ attains its maximum at the origin, we conclude that
-\[
+\end{equation*} 
+so that the ML estimator attains the local asymptotic MSE of
+Theorem~\ref{thm:adpative_lower_bound}.
+
+By Assumption~\ref{assump:failure_rate},
+$\eta(x)$ attains its maximum at the origin, so we conclude that
+\begin{equation*}
   \kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
-\]
-This upper bound on $\kappa(\theta)$ implies that the ARE of any distributed estimator based on a sequence of threshold detectors does not exceed $\eta(0)\sigma^2$, a fact that agrees with the lower bound under adaptive estimation derived in Theorem~\ref{thm:adpative_lower_bound}.
-%
-This upper bound on $\kappa(\theta)$ is attained only when $\lambda$ is the mass distribution at $\theta$.
-Since $\theta$ is apriori unknown, we conclude that estimation in the distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting.
-In other words, the ability to choose the threshold values in an adaptive manner based on previous messages necessarily improves relative efficiency compared to a non-adaptive threshold selection.
-\par
+\end{equation*}
+Moreover, this upper bound on $\kappa(\theta)$ is attained only when
+$\lambda$ is the point mass at $\theta$. Since $\theta$ is \emph{a priori}
+unknown, we conclude that estimation in the distributed setting using
+threshold detection is strictly suboptimal compared to the adaptive
+setting; the ability to choose the thresholds $t_i$
+adaptively conditional on previous messages is necessary for optimal
+efficiency.
 
@@
 
-%
-We conclude this section by considering the density of the threshold values that maximizes the ARE $\kappa(\theta)$ under the worst choice of $\theta \in \Theta$.
+\subsection{Minimax Threshold Density}
 
-\subsection{Minimax Threshold Density}
-The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta$ is given as the solution to the following optimization problem:
+We conclude this section by considering the density of the threshold values
+that maximizes the worst-case information $\inf_\theta \kappa(\theta)
+= \kappa_\lambda(\theta)$ where $\kappa_\lambda(\theta)
+= \int \eta(t - \theta) d\lambda(t)$.
+This distribution $\lambda$ solves the
+optimization problem
 \begin{align}
@@
 \end{align}
-The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program.
-We denote by $\kappa^\star$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum.
-Theorem~\ref{thm:LAN1} and Corollary~\ref{cor:LAN_thresh} imply that for any $\theta \in \Theta$, the ARE of any local asymptotic minimax estimator (such as the ML estimator) from $\{B_i,\,i\in N\}$ of the form \eqref{eq:threshold_message} with $t_i \sim \lambda^\star$ i.i.d.
-is at least $\kappa^\star$.
+The objective function~\eqref{eq:var_cvx_minimax} is concave in
+$\lambda(dt)$ and continuous in the weak topology over measures on $\Theta$,
+so that by discretizing, we can approximately solve this problem using
+convex optimization. We let $\kappa^\star$ denote the maximal value of
+problem~\eqref{eq:var_cvx_minimax} and $\lambda^\star(dt)$ be the density
+achieving the maximum. By drawing thresholds
+$t_i \simiid \lambda^\star$,
+Corollary~\ref{cor:LAN_thresh} guarantees that for any $\theta \in \Theta$, the
+maximum likelihood estimator
+using $\{B_i = \sgn(X_i - t_i)\}_{i \in \N}$ is at least $\kappa^\star$.
 %
@@
 %\end{rem}
-\par
-Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$ and $\Theta = [-T,T]$.
-The minimax asymptotic precision parameter $\kappa^\star$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of half the support size $T$.
-Also illustrated in these figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
+
+Figure~\ref{fig:minimax_support} illustrates an approximation to
+$\lambda^\star(dt)$ obtained by solving a discretized version of
+\eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density
+with variance $\sigma^2$ and $\Theta = [-T,T]$. The minimax asymptotic
+precision parameter $\kappa^\star$ obtained this way is illustrated in
+Fig.~\ref{fig:minimax_ARE} as a function of half the support size $T$. Also
+illustrated in these figures is $\kappa_{\unif}$, the precision
+parameter corresponding to threshold values uniformly distribution over
+$\Theta = [-T,T]$,
 \begin{align}
@@
 \end{align}
-Corollary~\ref{cor:LAN_thresh} implies that the ARE under threshold values uniformly distributed is $\kappa_\unif \sigma^2$. \par
 
@@
   \begin{center}
-%% \begin{tikzpicture}[scale = 0.55]
-%% \begin{axis}[
-%% width=8cm, height=6cm,
-%% xmin = -0.5, xmax=0.5, 
-%% restrict y to domain = 0:100,
-%% ymin = 0,
-%% ymax = 1,
-%% samples=10, 
-%% xlabel= {$dt$},
-%% xtick={-0.5,0,0.5},
-%% xticklabels={-$T$, 0, $T$},
-%% title = {$\sigma/T = 1/2$},
-%% ytick={0,0.1,1},
-%% %ylabel = {$\lambda(dt)$},
-%% yticklabels={0,0.1,1},
-%% line width=1.0pt,
-%% mark size=1.5pt,
-%% ymajorgrids,
-%% xmajorgrids,
-%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-%% ]
-%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
+\begin{tikzpicture}[scale = 0.55]
+\begin{axis}[
+width=8cm, height=6cm,
+xmin = -0.5, xmax=0.5, 
+restrict y to domain = 0:100,
+ymin = 0,
+ymax = 1,
+samples=10, 
+xlabel= {$dt$},
+xtick={-0.5,0,0.5},
+xticklabels={-$T$, 0, $T$},
+title = {$\sigma/T = 1/2$},
+ytick={0,0.1,1},
+%ylabel = {$\lambda(dt)$},
+yticklabels={0,0.1,1},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
 
-%% \addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
+\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
 
-%% \addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
+\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
 
-%% \end{axis}
-%% \end{tikzpicture}
-%% %
-%% \begin{tikzpicture}[scale = 0.55]
-%% \begin{axis}[
-%% width=8cm, height=6cm,
-%% xmin = -0.5, xmax=0.5, 
-%% restrict y to domain = 0:100,
-%% ymin = 0,
-%% ymax = 0.6,
-%% samples=10, 
-%% xlabel= {$dt$},
-%% title = {$\sigma/T = 1/5$},
-%% xtick={-0.5,0,0.5},
-%% xticklabels={-$T$, 0, $T$},
-%% ytick={0,0.5},
-%% ylabel = {$\lambda(dt)$},
-%% yticklabels={0,0.5},
-%% line width=1.0pt,
-%% mark size=1.5pt,
-%% ymajorgrids,
-%% xmajorgrids,
-%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-%% ]
-%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
+\end{axis}
+\end{tikzpicture}
+%
+\begin{tikzpicture}[scale = 0.55]
+\begin{axis}[
+width=8cm, height=6cm,
+xmin = -0.5, xmax=0.5, 
+restrict y to domain = 0:100,
+ymin = 0,
+ymax = 0.6,
+samples=10, 
+xlabel= {$dt$},
+title = {$\sigma/T = 1/5$},
+xtick={-0.5,0,0.5},
+xticklabels={-$T$, 0, $T$},
+ytick={0,0.5},
+ylabel = {$\lambda(dt)$},
+yticklabels={0,0.5},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
 
-%% \addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
+\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
 
-%% \addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
+\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
 
-%% \end{axis}
-%% \end{tikzpicture}
-%% %
-%% \begin{tikzpicture}[scale = 0.55]
-%% \begin{axis}[
-%% width=8cm, height=6cm,
-%% xmin = -0.5, xmax=0.5, 
-%% restrict y to domain = 0:100,
-%% ymin = 0,
-%% ymax = 0.3,
-%% samples=10, 
-%% xlabel= {$dt$},
-%% xtick={-0.5,0,0.5},
-%% title = {$\sigma / T = 1/10$},
-%% xticklabels={-$T$, 0, $T$},
-%% ytick={0,0.2},
-%% %ylabel = {$\lambda(dt)$},
-%% yticklabels={0,0.2},
-%% line width=1.0pt,
-%% mark size=1.5pt,
-%% ymajorgrids,
-%% xmajorgrids,
-%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-%% ]
-%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
+\end{axis}
+\end{tikzpicture}
+%
+\begin{tikzpicture}[scale = 0.55]
+\begin{axis}[
+width=8cm, height=6cm,
+xmin = -0.5, xmax=0.5, 
+restrict y to domain = 0:100,
+ymin = 0,
+ymax = 0.3,
+samples=10, 
+xlabel= {$dt$},
+xtick={-0.5,0,0.5},
+title = {$\sigma / T = 1/10$},
+xticklabels={-$T$, 0, $T$},
+ytick={0,0.2},
+%ylabel = {$\lambda(dt)$},
+yticklabels={0,0.2},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
 
-%% \addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
+\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
 
-%% \addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
+\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
 
-%% \end{axis}
-%% \end{tikzpicture}
-%% %
-%% \begin{tikzpicture}[scale = 0.55]
-%% \begin{axis}[
-%% width=8cm, height=6cm,
-%% xmin = -0.5, xmax=0.5, 
-%% restrict y to domain = 0:100,
-%% ymin = 0,
-%% ymax = 0.15,
-%% samples=10, 
-%% xlabel= {$dt$},
-%% title = {$\sigma / T = 1/20$},
-%% xtick={-0.5,0,0.5},
-%% xticklabels={-$T$, 0, $T$},
-%% ytick={0,0.1},
-%% ylabel = {$\lambda(dt)$},
-%% yticklabels={0,0.1},
-%% line width=1.0pt,
-%% mark size=1.5pt,
-%% ymajorgrids,
-%% xmajorgrids,
-%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-%% ]
-%% \addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
+\end{axis}
+\end{tikzpicture}
+%
+\begin{tikzpicture}[scale = 0.55]
+\begin{axis}[
+width=8cm, height=6cm,
+xmin = -0.5, xmax=0.5, 
+restrict y to domain = 0:100,
+ymin = 0,
+ymax = 0.15,
+samples=10, 
+xlabel= {$dt$},
+title = {$\sigma / T = 1/20$},
+xtick={-0.5,0,0.5},
+xticklabels={-$T$, 0, $T$},
+ytick={0,0.1},
+ylabel = {$\lambda(dt)$},
+yticklabels={0,0.1},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
 
-%% \addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
+\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
 
-%% \addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
+\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
 
-%% %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-%% \end{axis}
-%% \end{tikzpicture}
+%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
+\end{axis}
+\end{tikzpicture}
 
@@
   \begin{center}
-%% \begin{tikzpicture}[scale = 1]
-%% \begin{axis}[
-%% width=8cm, height=6cm,
-%% xmax=2.5, 
-%% xmode = log,
-%% restrict y to domain = 0:100,
-%% ymin = 0,
-%% ymax = 1,
-%% samples=1, 
-%% xlabel= {$\sigma/T$},
-%% %xtick={-0.5,0,0.5},
-%% %xticklabels={-$$, 0, $b$},
-%% ytick={0,0.637,1},
-%% yticklabels={0,$2/\pi$,1},
-%% ylabel = {$\ARE$},
-%% line width=1.0pt,
-%% mark size=1.5pt,
-%% ymajorgrids,
-%% xmajorgrids,
-%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-%% ]
-%% \addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-%% \addlegendentry{optimal threshold density};
+\begin{tikzpicture}[scale = 1]
+\begin{axis}[
+width=8cm, height=6cm,
+xmax=2.5, 
+xmode = log,
+restrict y to domain = 0:100,
+ymin = 0,
+ymax = 1,
+samples=1, 
+xlabel= {$\sigma/T$},
+%xtick={-0.5,0,0.5},
+%xticklabels={-$$, 0, $b$},
+ytick={0,0.637,1},
+yticklabels={0,$2/\pi$,1},
+ylabel = {$\ARE$},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
+\addlegendentry{optimal threshold density};
 
-%% \addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-%% \addlegendentry{uniform threshold desnity};
-%% \end{axis}
-%% \end{tikzpicture}
-%% \caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \Ncal(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
+\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
+\addlegendentry{uniform threshold desnity};
+\end{axis}
+\end{tikzpicture}
+\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \Ncal(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
 The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
 }.
-%% \end{center}
-%% \end{figure}
+\end{center}
+\end{figure}
 
-%% %We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
+%We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
 Next, we prove that with any set of messages obtained via a distributed strategy, there exists at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
 
-%% \begin{figure}
-%% \begin{center}
-%% %
-%% \begin{tikzpicture}[scale = 0.55]
-%% \begin{axis}[
-%% width=8cm, height=6cm,
-%% xmin = -0.5, xmax=0.5, 
-%% restrict y to domain = 0:100,
-%% ymin = 0,
-%% ymax = 1,
-%% samples=10, 
-%% xlabel= {$dt$},
-%% title = {$\sigma/\sigma_{\theta} = 4$},
-%% xtick={-0.5,0,0.5},
-%% xticklabels={-$T$, 0, $T$},
-%% ytick={0,1},
-%% ylabel = {$\lambda(dt)$},
-%% yticklabels={0,1},
-%% line width=1.0pt,
-%% mark size=1.5pt,
-%% ymajorgrids,
-%% xmajorgrids,
-%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-%% ]
-%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
-%% %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-%% \end{axis}
-%% \end{tikzpicture}
-%% %
-%% \begin{tikzpicture}[scale = 0.55]
-%% \begin{axis}[
-%% width=8cm, height=6cm,
-%% xmin = -0.5, xmax=0.5, 
-%% restrict y to domain = 0:100,
-%% ymin = 0,
-%% ymax = 1,
-%% samples=10, 
-%% xlabel= {$dt$},
-%% xtick={-0.5,0,0.5},
-%% title = {$\sigma/\sigma_{\theta} = 3$},
-%% xticklabels={-$T$, 0, $T$},
-%% ytick={0,1},
-%% %ylabel = {$\lambda(dt)$},
-%% yticklabels={0,1},
-%% line width=1.0pt,
-%% mark size=1.5pt,
-%% ymajorgrids,
-%% xmajorgrids,
-%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-%% ]
-%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
-%% %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-%% \end{axis}
-%% \end{tikzpicture}
-%% %
-%% \begin{tikzpicture}[scale = 0.55]
-%% \begin{axis}[
-%% width=8cm, height=6cm,
-%% xmin = -0.5, xmax=0.5, 
-%% restrict y to domain = 0:100,
-%% ymin = 0,
-%% ymax = 1,
-%% samples=10, 
-%% xlabel= {$dt$},
-%% title = {$\sigma/\sigma_{\theta} = 2$},
-%% xtick={-0.5,0,0.5},
-%% xticklabels={-$T$, 0, $T$},
-%% ytick={0,1},
-%% ylabel = {$\lambda(dt)$},
-%% yticklabels={0,1},
-%% line width=1.0pt,
-%% mark size=1.5pt,
-%% ymajorgrids,
-%% xmajorgrids,
-%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-%% ]
-%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
-%% %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-%% \end{axis}
-%% \end{tikzpicture}
-%% %
-%% \begin{tikzpicture}[scale = 0.55]
-%% \begin{axis}[
-%% width=8cm, height=6cm,
-%% xmin = -0.5, xmax=0.5, 
-%% restrict y to domain = 0:100,
-%% ymin = 0,
-%% ymax = 1,
-%% samples=10, 
-%% xlabel= {$dt$},
-%% xtick={-0.5,0,0.5},
-%% xticklabels={-$T$, 0, $T$},
-%% title = {$\sigma/\sigma_{\theta} = 1$},
-%% ytick={0,1},
-%% %ylabel = {$\lambda(dt)$},
-%% yticklabels={0,1},
-%% line width=1.0pt,
-%% mark size=1.5pt,
-%% ymajorgrids,
-%% xmajorgrids,
-%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-%% ]
-%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
-%% %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-%% \end{axis}
-%% \end{tikzpicture}
+\begin{figure}
+\begin{center}
+%
+\begin{tikzpicture}[scale = 0.55]
+\begin{axis}[
+width=8cm, height=6cm,
+xmin = -0.5, xmax=0.5, 
+restrict y to domain = 0:100,
+ymin = 0,
+ymax = 1,
+samples=10, 
+xlabel= {$dt$},
+title = {$\sigma/\sigma_{\theta} = 4$},
+xtick={-0.5,0,0.5},
+xticklabels={-$T$, 0, $T$},
+ytick={0,1},
+ylabel = {$\lambda(dt)$},
+yticklabels={0,1},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
+%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
+\end{axis}
+\end{tikzpicture}
+%
+\begin{tikzpicture}[scale = 0.55]
+\begin{axis}[
+width=8cm, height=6cm,
+xmin = -0.5, xmax=0.5, 
+restrict y to domain = 0:100,
+ymin = 0,
+ymax = 1,
+samples=10, 
+xlabel= {$dt$},
+xtick={-0.5,0,0.5},
+title = {$\sigma/\sigma_{\theta} = 3$},
+xticklabels={-$T$, 0, $T$},
+ytick={0,1},
+%ylabel = {$\lambda(dt)$},
+yticklabels={0,1},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
+%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
+\end{axis}
+\end{tikzpicture}
+%
+\begin{tikzpicture}[scale = 0.55]
+\begin{axis}[
+width=8cm, height=6cm,
+xmin = -0.5, xmax=0.5, 
+restrict y to domain = 0:100,
+ymin = 0,
+ymax = 1,
+samples=10, 
+xlabel= {$dt$},
+title = {$\sigma/\sigma_{\theta} = 2$},
+xtick={-0.5,0,0.5},
+xticklabels={-$T$, 0, $T$},
+ytick={0,1},
+ylabel = {$\lambda(dt)$},
+yticklabels={0,1},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
+%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
+\end{axis}
+\end{tikzpicture}
+%
+\begin{tikzpicture}[scale = 0.55]
+\begin{axis}[
+width=8cm, height=6cm,
+xmin = -0.5, xmax=0.5, 
+restrict y to domain = 0:100,
+ymin = 0,
+ymax = 1,
+samples=10, 
+xlabel= {$dt$},
+xtick={-0.5,0,0.5},
+xticklabels={-$T$, 0, $T$},
+title = {$\sigma/\sigma_{\theta} = 1$},
+ytick={0,1},
+%ylabel = {$\lambda(dt)$},
+yticklabels={0,1},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
+%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
+\end{axis}
+\end{tikzpicture}
 \caption{\label{fig:opt_density}

### 2019-12-17 proof-no-distributed.tex
Finished writing major proofs and fixing references. Still needs a once through

@@
 
-Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta) = \eta(0)$. 
+Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta)
+= \eta(0)$.
 %
-Since $B_1,B_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, $\theta$ is in $\Xi$ if and only if
-\begin{equation}
-\label{eq:non_existence_proof}
-\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0). 
-\end{equation}
-By assumption, we have $B_i^{-1} = A_i$ where $A_i$ can be expressed as
-\[
-A_i = \cup_{i=1}^K (a_{i,k},b_{i,k}), 
-\]
-where $a_{i,1} \leq b_{i,1} \leq \ldots \leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values $-\infty$ and $\infty$, respectively. Denote
-\[
-C_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\}.
-\]
-For any $\theta$ and $\epsilon>0$, denote 
-\[
-S_n(\theta, \epsilon) \triangleq \left\{ i\leq n \,:\, (\theta-\epsilon,\theta+\epsilon) \cap C_i \neq \emptyset \right\}
-\]
-In words, $S_n$ contains all integers smaller than $n$ in which an $\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals consisting $A_i$. 
+Since $B_1,B_2,\ldots$ satisfy the conditions in
+Theorem~\ref{theorem:non-adaptive-minimax}, $\theta$ is in $\Xi$ if and only
+if $\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0)$.  By
+assumption, we have $B_i = \indic{X_i \in A_i}$ where each $A_i =
+\cup_{i=1}^K \{[a_{i,k},b_{i,k}]\}$, where $a_{i,1} \leq b_{i,1} \leq \ldots
+\leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values
+$-\infty$ and $\infty$, respectively. Denote the endpoints
+\begin{equation*}
+  E_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\},
+\end{equation*}
+and for $\theta$ and $\epsilon>0$, define
+\begin{equation*}
+  S_n(\theta, \epsilon) \triangleq \left\{ i\leq n ~ \mbox{s.t.}~
+  (\theta-\epsilon,\theta+\epsilon) \cap E_i \neq \emptyset \right\}
+\end{equation*}
+In words, $S_n$ contains all integers smaller than $n$ in which an
+$\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals
+defining $A_i$.
 %
@@
 where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} with $\delta =0$, and the fact that for $i \in S_n(\theta, \epsilon)$, 
-\[
+\begin{equation*}
 \max\left\{ \max_k \eta(b_{i,k}-\theta) , \max_k \eta(a_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
-\]
+\end{equation*}
 Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, we get that \eqref{eq:non_existence_proof1}, hence $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.
-\par
-For $k\in \N$, assume by contradiction that there exists $N \geq 2K + 1$ distinct elements
-$\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$ consists of at most $K$ intervals, we have that 
+
+Assume for the sake of contradiction that there exists $N \geq 2K + 1$
+distinct elements $\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$
+consists of at most $K$ intervals, we have that
 \begin{equation}
@@
 Fix $\epsilon>0$ such that 
-\[
+\begin{equation*}
   \epsilon < \frac{1}{2}\min_{i\neq j} |\theta_i - \theta_j|. 
-\]
+\end{equation*}
 Since for each $\theta \in \Theta$ we have $S_n(\theta, \epsilon) \to 1$, there exists $n$ large enough such that 
-\[
-\card \left(S_n(\theta_i, \epsilon) \right) \geq n \left(1-\frac{1}{2N} \right)
-\]
-for all $i=1,\ldots,N$.
-However, $S_n(\theta_1,\epsilon), \ldots S_n(\theta_N,\epsilon)$ are disjoint, so the cardinallity of their union is at least $n\left(1-\frac{1}{2N} \right)N$ which is grater than $2nK + n/2$ in contradiction to \eqref{eq:few_optimality_points_proof}.
+\begin{equation*}
+  \card \left(S_n(\theta_i, \epsilon) \right)
+  \geq n \left(1-\frac{1}{2N} \right)
+\end{equation*}
+for all $i=1,\ldots,N$. However, $S_n(\theta_1,\epsilon), \ldots
+S_n(\theta_N,\epsilon)$ are disjoint, so the cardinality of their union is
+at least $n\left(1-\frac{1}{2N} \right)N > 2nK + n/2$, a contradiction to
+inequality~\eqref{eq:few_optimality_points_proof}.

### 2019-12-17 proof-sgd.tex
Rewrote entire proof of local asymptotic normality
Finished writing major proofs and fixing references. Still needs a once through

@@
 \label{proof:sgd}
-
-\providecommand{\score}{\dot{\ell}}
 
@@
 so the estimator $\bar{U}_n$ is identical to the stochastic gradient
-estimator~\eqref{eq:sgd_est}. We have $\E[\varphi(x + Z)^4] = 1$ and by
-assumption the Fisher information $\E[(f'(Z))^2 / f(Z)^2]$ exists, and the
-functions $\psi$ and $\chi$ have the desired conditions of
+estimator~\eqref{eq:sgd_alg} with $\bar{\theta}_n = \frac{1}{n} \sum_{i =
+  1}^n \theta_i$. We have $\E[\varphi(x + Z)^4] = 1$ and by assumption the
+Fisher information $\E[(f'(Z))^2 / f(Z)^2]$ exists, and the functions $\psi$
+and $\chi$ have the desired conditions of
 Corollary~\ref{corollary:polyak-juditsky} (as we verify in
@@
 $\score_h(z) = \frac{p'(z - h)}{p(z - h)}$,
-and the asymptotic expansion~\eqref{eqn:lan-from-qmd}
-with the preceding display give the joint convergence
+and the asymptotic expansion Definitions~\ref{definition:qmd}
+and~\ref{definition:lan} allow combines
+with the preceding display to give the joint convergence
 \begin{equation*}

### 2019-12-23 adaptive-estimation.tex
Finished writing major proofs and fixing references. Still needs a once through
corrected various typos

@@
 %% \end{equation*}
-It is possible to extend Theorem~\ref{thm:adpative_lower_bound} to any other
+It is possible to extend Theorem~\ref{thm:adpative_lower_bound} to other
 loss functions using a more subtle version of the Van Trees
@@
 moreover, we have the familiar result (cf.~\cite{VanDerVaart98}, Ch.~21)
-that given a sample $X_1^n \simiid P$, if $\theta = \mbox{med}(P)$ and
+that given a sample $X_1,\ldots,X_n \simiid P$, if $\theta = \mbox{med}(P)$ and
 $P$ has continuous density $f(\cdot - \theta)$ near $\theta$, then
@@
 which is precisely the variance lower bound in
-Theorem~\ref{thm:adpative_lower_bound}.  Thus, it it is natural consider a
+Theorem~\ref{thm:adpative_lower_bound}.  Thus, it is natural to consider a
 stochastic gradient procedure for minimizing $\E[|X - \theta|]$. To that end,
@@
     and~\eqref{eqn:stringent-gamma}. Let
-    $\pi$ be a distribution on $\R$.
+    $\pi$ be a distribution on $\R$. Then
     \begin{equation*}
-      \int \E\Big[( \bar{\theta}_n - \theta )^2\Big] d\pi(\theta)
+      \int \E\Big[( \bar{\theta}_n - \theta )^2\Big] \pi(d\theta)
       = \frac{1}{4 n f(0)^2} + o(n^{-1}). 
@@
 \end{corollary}
-
-%% Theorem~\ref{thm:sgd} implies that the estimator ${\theta}_n$ defined by \eqref{eq:sgd_est} and \eqref{eq:sgd_alg} attains the maximal ARE, as established by Theorem~\ref{thm:adpative_lower_bound}.
-%Furthermore, it is locally minimax in the sense that it attains the minimal MSE for all local alternatives of $\theta$.
-%% %
-%% The update step \eqref{eq:sgd_alg} can be seen as a gradient descent step for the function $x\to |x|$ at the point $x=X_n - \theta_{n-1}$.
-Consequently, the procedure above is known as averaged stochastic gradient descent for minimizing $x \to |x|$ given the data $X_1,\ldots,X_n$.
-The minimal value of this optimization is the sample median, and Theorem~\ref{thm:sgd} provides conditions for the sequence of gradient steps so that the algorithm converges to this minimum.
-In particular, parts (i) and (ii) of Theorem~\ref{thm:sgd} provides conditions under which $\bar{\theta}$ is asymptotically normal and local asymptotically minimax, in the sense that it attains the local asymptotic minimax bound \cite{van2000asymptotic}.
-Part (iii) provides an additional condition under which $\bar{\theta}$ also converges in its second moment.
 
@@
     \E\left[\frac{|B_i - E_n|^3}{(E_n(1 - E_n))^{3/2}} \mid T_n\right]
-    \le \frac{1}{\sqrt{E_n(1 - E_n)}},
+    \le \frac{1}{\sqrt{E_n(1 - E_n)}}.
   \end{equation*}
-  the Berry-Esseen theorem implies that there exists a constant
+ The Berry-Esseen theorem implies that there exists a constant
   $C \le 1$ such that

### 2019-12-23 conclusions.tex
corrected various typos

@@
 %
-These condition implies that, in the distributed, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in this setting.
+These condition implies that, in the distributed setting, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in this setting.
 %

### 2019-12-23 distributed-estimation.tex
corrected various typos

@@
 %
-The continuous curve (red) represents the reciprocal of the asymptotic risk at a fixed $\theta \in [-T,T]$ under the optimal density, i.e., the minimax risk is the inverse of the minimal value of this curve.
-The dashed curve (green) is the reciprocal of the asymptotic risk at a fixed $\theta \in [-T,T]$ when the threshold values are uniformly distributed over $[-T,T]$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
+The continuous curve (red) represents the reciprocal of the asymptotic risk for each $\theta \in [-T,T]$ under the optimal density, i.e., the minimax risk is the inverse of the minimal value of this curve.
+The dashed curve (green) is the reciprocal of the asymptotic risk for each $\theta \in [-T,T]$ when the threshold values are uniformly distributed over $[-T,T]$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
 }
@@
 which is convex in $\lambda$ since $x \rightarrow 1/x$, $x>0$, is convex.
-Figure~\ref{fig:opt_density}  illustrates the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distribution and $\pi$ is the uniform over $\Theta = [-T,T]$.
+Figure~\ref{fig:opt_density}  illustrates the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distribution and $\pi$ is the uniform distribution over $\Theta = [-T,T]$.
 %Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.

### 2019-12-23 preliminaries.tex
corrected various typos

@@
 \[
-R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - {\theta}_j \right)^2 \right]. 
+R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - {\theta} \right)^2 \right]. 
 \]
 Note that any distributed encoding scheme using one-bit per sample can be replicated $k$ times and thus leads to a legitimate encoding and estimation scheme for the CEO problem with $r_1=\ldots=r_n = 1$.
-It follows that, assuming that $\theta$ is drawn once from the prior $\pi(d\theta)$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
+It follows that, assuming that $\theta$ is drawn once from the prior $\pi$, our mean estimation problem from one-bit samples under distributed encoding corresponds to the CEO setting with $k=1$ realization of $\theta$ observed under noise at $n$ different locations, and communicated at each location using an encoder sending a single bit.
 %
@@
   \end{equation}
-  where the expectation is with respect to $\theta$ and $X^n$.
+  where the expectation is with respect to $\theta$ and $X_1,\ldots,X_n$.
 \end{prop}

### 2019-12-23 problem-formulation.tex
corrected various typos

@@
 For $f$ the normal density, classical results~\cite{Samford1953,
-  hammersley1950estimating} show that that $\eta(x)$ is a strictly
+  hammersley1950estimating} show that $\eta(x)$ is a strictly
 decreasing function of $|x|$, as we illustrate in Fig.~\ref{fig:eta}.

### 2019-12-23 proof-adaptive-optimality.tex
Finished writing major proofs and fixing references. Still needs a once through
corrected various typos

@@
 
-The following lemma is essential to the the proofs
-of Theorems~\ref{thm:adpative_lower_bound}, \ref{thm:LAN1}, and
+The following lemma is essential to the proofs
+of Theorems~\ref{thm:adpative_lower_bound} and
 \ref{thm:non_existence}.
@@
   \end{align*} 
-  which is bounded from from above by $\eta_\delta(x_{i^*})$ by the induction hypothesis. The case where $N$ is odd and $-x^* \leq y_1 = \ldots = y_N$ is similar. 
+  which is bounded from above by $\eta_\delta(x_{i^*})$ by the induction hypothesis. The case where $N$ is odd and $-x^* \leq y_1 = \ldots = y_N$ is similar. 
   %
@@
     \label{eq:proof:lem:bound_intervals}
-    \frac{(\delta_{n,\alpha})^2}{\Delta_{n,\alpha}(1-\Delta_{n,\alpha})} \leq \max_i \eta_{\alpha}(x_i),
+    \frac{(\delta_{n,\alpha})^{2+\delta}}{\left(\Delta_{n,\alpha}(1-\Delta_{n,\alpha})\right)^{1+\delta}} \leq \max_i \eta_{\delta,\alpha}(x_i),
   \end{align}

### 2019-12-23 proof-lan-distributed.tex
Finished writing major proofs and fixing references. Still needs a once through
corrected various typos

@@
 \section{Proof of Theorem~\ref{theorem:non-adaptive-minimax}}
+\label{sec:proof-non-adaptive-minimax}
 
@@
 This immediately gives Theorem~\ref{theorem:non-adaptive-minimax}.
+
+%% Returning to the expansion~\eqref{eqn:almost-at-the-end}, we thus obtain
+%% %% \begin{equation*}
+%% %%   \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
+%% %%   = \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
+%% %%   - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2 + o_P(1).
+
+%% %% \begin{equation*}
+%% %%   W_{n,i}
+%% %%   = \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
+%% %%   \pm \frac{h_n^2 k \lip(f)}{n p(B_i)}
+%% %%   \pm \frac{1}{2}
+%% %% \end{equation*}
+
+%% \begin{equation*}
+%%   g(b) = h \score_\theta(b),
+%% \end{equation*}
+
+%% Under the assumption that $0 < \inf_i P_{\theta}(A_i) \le \sup_i P_{\theta}(A_i)
+%% < 1$, the random
+
+\subsection{Proof of Lemma~\ref{lemma:derivative-bounds}}
+\label{sec:proof-derivative-bounds}
+
+To see the first claim of the lemma, we consider the simpler special case
+that $A = [a, b]$. Then as $f$ is Lipschitz (and hence absolutely
+continuous and a.e.\ differentiable with $\linf{f'} \le \lip(f)$),
+we have
+\begin{align*}
+  P_{\theta + h}(A)
+  - P_\theta(A)
+  & = \int_a^b (f(z - \theta - h) - f(z - \theta)) dz \\
+  & = -\int_a^b \int_0^h f'(z - \theta - u) du dz \\
+  & = -\int_0^h \int_a^b f'(z - \theta - u) dz du \\
+  & = \int_0^h f(a - \theta - u) - f(b - \theta - u) du \\
+  & = \int_0^h (f(a - \theta) - f(b - \theta)) du
+  \pm 2 \int_0^h \lip(f) u du \\
+  & = \left[f(a - \theta) - f(b - \theta)\right] h \pm \lip(f) h^2.
+\end{align*}
+This gives the first two claims of the lemma.
+
+For the second, we require a bit more work.
+Let $L = \lip(f)$ for shorthand. Let $a < b$.
+Then we always have
+\begin{equation}
+  \label{eqn:interval-length-thing}
+  P([a, b])
+  \ge \int_a^b f(z) dz
+  \ge \int_a^b \max\{f(b) - L (b - z), f(a) - L(z - a), 0\} dz.
+\end{equation}
+If $f(a) + f(b) \ge L (b - a)$, then the point $\hat{z} =
+\frac{a + b}{2} - \frac{f(b) - f(a)}{2L}$ satisfies both $f(b) - L(b -
+\hat{z}) \ge 0$ and $f(a) - L(\hat{z} - a) \ge 0$. The
+integral~\eqref{eqn:interval-length-thing} then becomes
+\begin{align*}
+  \lefteqn{\int_a^{\hat{z}}
+    (f(a) - L (z - a) dz)
+    + \int_{\hat{z}}^b
+    (f(b) - L (b - z)) dz} \\
+  & = \frac{f(a) + f(b)}{2}
+  \left(\frac{b - a}{2}\right)
+  - L \left(\frac{b - a}{2} \right)^2
+  + \frac{(f(b) - f(a))^2}{4L},
+\end{align*}
+and using the assumption that $\frac{f(a) + f(b)}{2} \ge L(b - a)$,
+we obtain
+\begin{align*}
+  \frac{(f(b) - f(a))^2}{4L}
+  & \le \frac{f(b) + f(b)}{2} \frac{b - a}{2}
+  - L \left(\frac{b - a}{2}\right)^2
+  + \frac{(f(b) - f(a))^2}{4L}
+  \le P([a, b]).
+\end{align*}
+That is, $|f(b) - f(a)| \le 2 \sqrt{\lip(f) P([a, b])}$.
+In the converse case that $f(a) + f(b) \le L(b - a)$, then
+the integral~\eqref{eqn:interval-length-thing} becomes
+\begin{align*}
+  P([a, b])
+  & \ge \int_a^{a + \frac{f(a)}{L}}
+  (f(a) - L (z - a)) dz
+  + \int_{b - \frac{f(b)}{L}}^b (f(b) - L (b - z)) dz \\
+  & = \frac{f(a)^2}{L}
+  - \frac{f(a)^2}{2L}
+  + \frac{f(b)^2}{L}
+  - \frac{f(b)^2}{2L},
+\end{align*}
+so that $\sqrt{f(a)^2 + f(b)^2} \le \sqrt{2 \lip(f) P([a, b])}$.  In sum,
+we have demonstrated that always the first
+bound~\eqref{eqn:bound-density-diffs} holds.
+To show the second inequality in expression~\eqref{eqn:bound-density-diffs},
+note that
+$\sum_i P([a_i, b_i]) \le 1$, and apply Cauchy-Schwarz.
 
@@
 uniformly bounded;
-the limit follows from
-and Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals}.
+the limit follows from Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals}.
 Consequently $\max_i W_{n,i} \to 0$, so that
@@
 \end{equation*}
-giving the theorem.
-
-%% Returning to the expansion~\eqref{eqn:almost-at-the-end}, we thus obtain
-%% %% \begin{equation*}
-%% %%   \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
-%% %%   = \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
-%% %%   - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2 + o_P(1).
-
-%% %% \begin{equation*}
-%% %%   W_{n,i}
-%% %%   = \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
-%% %%   \pm \frac{h_n^2 k \lip(f)}{n p(B_i)}
-%% %%   \pm \frac{1}{2}
-%% %% \end{equation*}
-
-%% \begin{equation*}
-%%   g(b) = h \score_\theta(b),
-%% \end{equation*}
-
-%% Under the assumption that $0 < \inf_i P_{\theta}(A_i) \le \sup_i P_{\theta}(A_i)
-%% < 1$, the random
-
-\subsection{Proof of Lemma~\ref{lemma:derivative-bounds}}
-\label{sec:proof-derivative-bounds}
-
-To see the first claim of the lemma, we consider the simpler special case
-that $A = [a, b]$. Then as $f$ is Lipschitz (and hence absolutely
-continuous and a.e.\ differentiable with $\linf{f'} \le \lip(f)$),
-we have
-\begin{align*}
-  P_{\theta + h}(A)
-  - P_\theta(A)
-  & = \int_a^b (f(z - \theta - h) - f(z - \theta)) dz \\
-  & = -\int_a^b \int_0^h f'(z - \theta - u) du dz \\
-  & = -\int_0^h \int_a^b f'(z - \theta - u) dz du \\
-  & = \int_0^h f(a - \theta - u) - f(b - \theta - u) du \\
-  & = \int_0^h (f(a - \theta) - f(b - \theta)) du
-  \pm 2 \int_0^h \lip(f) u du \\
-  & = \left[f(a - \theta) - f(b - \theta)\right] h \pm \lip(f) h^2.
-\end{align*}
-This gives the first two claims of the lemma.
-
-For the second, we require a bit more work.
-Let $L = \lip(f)$ for shorthand. Let $a < b$.
-Then we always have
-\begin{equation}
-  \label{eqn:interval-length-thing}
-  P([a, b])
-  \ge \int_a^b f(z) dz
-  \ge \int_a^b \max\{f(b) - L (b - z), f(a) - L(z - a), 0\} dz.
-\end{equation}
-If $f(a) + f(b) \ge L (b - a)$, then the point $\hat{z} =
-\frac{a + b}{2} - \frac{f(b) - f(a)}{2L}$ satisfies both $f(b) - L(b -
-\hat{z}) \ge 0$ and $f(a) - L(\hat{z} - a) \ge 0$. The
-integral~\eqref{eqn:interval-length-thing} then becomes
-\begin{align*}
-  \lefteqn{\int_a^{\hat{z}}
-    (f(a) - L (z - a) dz)
-    + \int_{\hat{z}}^b
-    (f(b) - L (b - z)) dz} \\
-  & = \frac{f(a) + f(b)}{2}
-  \left(\frac{b - a}{2}\right)
-  - L \left(\frac{b - a}{2} \right)^2
-  + \frac{(f(b) - f(a))^2}{4L},
-\end{align*}
-and using the assumption that $\frac{f(a) + f(b)}{2} \ge L(b - a)$,
-we obtain
-\begin{align*}
-  \frac{(f(b) - f(a))^2}{4L}
-  & \le \frac{f(b) + f(b)}{2} \frac{b - a}{2}
-  - L \left(\frac{b - a}{2}\right)^2
-  + \frac{(f(b) - f(a))^2}{4L}
-  \le P([a, b]).
-\end{align*}
-That is, $|f(b) - f(a)| \le 2 \sqrt{\lip(f) P([a, b])}$.
-In the converse case that $f(a) + f(b) \le L(b - a)$, then
-the integral~\eqref{eqn:interval-length-thing} becomes
-\begin{align*}
-  P([a, b])
-  & \ge \int_a^{a + \frac{f(a)}{L}}
-  (f(a) - L (z - a)) dz
-  + \int_{b - \frac{f(b)}{L}}^b (f(b) - L (b - z)) dz \\
-  & = \frac{f(a)^2}{L}
-  - \frac{f(a)^2}{2L}
-  + \frac{f(b)^2}{L}
-  - \frac{f(b)^2}{2L},
-\end{align*}
-so that $\sqrt{f(a)^2 + f(b)^2} \le \sqrt{2 \lip(f) P([a, b])}$.  In sum,
-we have demonstrated that always the first
-bound~\eqref{eqn:bound-density-diffs} holds.
-To show the second inequality in expression~\eqref{eqn:bound-density-diffs},
-note that
-$\sum_i P([a_i, b_i]) \le 1$, and apply Cauchy-Schwarz.
+giving Lemma~\ref{lemma:lan-bits}.

### 2019-12-23 proof-sgd.tex
corrected various typos

@@
   family $\{P_\theta\}_{\theta \in \Theta}$ is \emph{regular at $\theta$} if
-  there exists a distribution $Q$ such that for all bounded sequence
+  there exists a distribution $Q$ such that for any bounded sequence
   $h_n$,
@@
 and the asymptotic expansion Definitions~\ref{definition:qmd}
-and~\ref{definition:lan} allow combines
-with the preceding display to give the joint convergence
+and~\ref{definition:lan} combined
+with the preceding display, give the joint convergence
 \begin{equation*}

### 2019-12-23 distributed-estimation.tex
corrected various typos

@@
 
-Yet Theorem~\ref{theorem:non-adaptive-minimax}
+Yet, Theorem~\ref{theorem:non-adaptive-minimax}
 limits non-adaptive strategies in stronger ways.
@@
 When each detection region $A_n$ consists of a bounded number
-of intervals, the next theorem
-shows that
-the optimal minimal risk $1/\eta(0)$ can
+of intervals, the next theorem shows that
+the minimal risk $1/\eta(0)$ can
 only be attained at finitely many points within $\Theta$.
@@
 converges to a probability measure. Specifically, for an interval $I \subset
-\mathbb R$ define
+\mathbb R$, define
 \begin{equation*}
@@
   Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that
-  $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on
+  $\lambda_n$ converges (weakly) to a probability measure $\lambda$ on
   $\mathbb R$. Then the conclusions of

### 2019-12-23 preliminaries.tex
corrected various typos

@@
 A related problem is the CEO problem, which considers the estimation of a
-sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_i$
+sequence $\theta_1,\theta_2\ldots$, where a noisy version of each $\theta_j$
 is available at $n$ terminals. At each terminal $i$, an encoder observes the
@@
 and transmits $r_i k$ bits to a central estimator~\cite{berger1996ceo}. The
-central estimator produces an estimates ${\theta}_1,\ldots,{\theta}_k$ with
+central estimator produces estimates ${\hat{\theta}}_1,\ldots,{\hat{\theta}}_k$ with
 the goal of minimizing the quadratic risk:
 \[
-R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\theta_j - {\theta} \right)^2 \right]. 
+R_{\CEO} = \frac{1}{k} \sum_{j=1}^k \mathbb E \left[\left(\hat{\theta}_j - {\theta_j} \right)^2 \right]. 
 \]

### 2019-12-28 distributed-estimation.tex
update to distributed section

@@
 
-The local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum
+When the conclusions of Corollary~\ref{cor:LAN_thresh} hold, local asymptotic normality of $\{B_n\}_{n=1}^\infty$ implies that the maximum
 likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by
@@
 \end{equation*}
-It follows that when the density of the threshold values converges to a
-probability measure, the ML estimator has asymptotic variance $1 /
-\kappa(\theta)$, and this is minimal. We note that ${\theta}^{ML}_n$
-solves
+We note that ${\theta}^{ML}_n$ solves
 \begin{equation}
@@
 \end{equation*} 
-so that the ML estimator attains the local asymptotic MSE of
-Theorem~\ref{thm:adpative_lower_bound}.
+so that the ML estimator attains the local asymptotic MSE of Theorem~\ref{thm:adpative_lower_bound}.
 

### 2020-12-01 Figs/opt_thr_den.tex
Fixed typos. Updated Fig. "optimal density".  Rewrote Conclusions

\begin{tikzpicture}[scale = 0.8]
\begin{axis}[
width=6cm, height=5cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1.05,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
xticklabels={$-.5$, 0, $.5$},
title = {$\sigma = .5$},
ytick={0,0.636},
ylabel = {$\lambda(dt)$},
yticklabels={0,\scriptsize $\frac{2}{\pi}$,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};

\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};

\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.8]
\begin{axis}[
width=6cm, height=5cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 0.7,
samples=10, 
xlabel= {$dt$},
title = {$\sigma = .2$},
xtick={-0.5,0,0.5},
xticklabels={$-.5$, 0, $.5$},
ytick={0,0.636},
%ylabel = {$\lambda(dt)$},
yticklabels={0,\scriptsize $\frac{2}{\pi}$},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {Figs/minmax_lmd_b0.5_sig0.2.csv};

\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {Figs/minimax_th_b0.5_sig0.2.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {Figs/minimax_th_b0.5_sig0.2.csv};

\end{axis}
\end{tikzpicture}

\begin{tikzpicture}[scale = 0.8]
\begin{axis}[
width=6cm, height=5cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 0.7,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
title = {$\sigma = .1$},
xticklabels={$-.5$, 0, $.5$},
ytick={0,0.636},
ylabel = {$\lambda(dt)$},
yticklabels={0,\scriptsize $\frac{2}{\pi}$},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {Figs/minmax_lmd_b0.5_sig0.1.csv};

\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {Figs/minimax_th_b0.5_sig0.1.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {Figs/minimax_th_b0.5_sig0.1.csv};

\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = .8]
\begin{axis}[
width=6cm, height=5cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:10,
ymin = 0,
ymax = .7,
samples=10, 
xlabel= {$dt$},
title = {$\sigma = .05$},
xtick={-0.5,0,0.5},
xticklabels={$-.5$, 0, $.5$},
ytick={0,0.636},
%ylabel = {$\lambda(dt)$},
yticklabels={0,\scriptsize $\frac{2}{\pi}$},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {Figs/minmax_lmd_b0.5_sig0.05.csv};

\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {Figs/minimax_th_b0.5_sig0.05.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {Figs/minimax_th_b0.5_sig0.05.csv};

%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}

### 2020-12-01 adaptive-estimation.tex
missing \theta in proof of Thm. 5
Fixed typos. Updated Fig. "optimal density".  Rewrote Conclusions

@@
 \end{center}
-\caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
+\caption{Distributed encoding with one round of interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is utilized in obtaining another $n-n_1$ bits in a distributed manner.
 \label{fig:one_round}
@@
     + (F^{-1})'(T_n - \theta + o_P(1))\cdot \left(
-    P_n B - E_n\right) \right) \\
+    P_n B - E_n\right) - \theta \right) \\
     & = \sqrt{n} (F^{-1})'(0) (P_n B - E_n)
@@
 width=10cm, height=6cm,
-xmin = 0, xmax=800, 
+xmin = 200, xmax=800, 
 restrict y to domain = 0:3,
@@
 xlabel= $n$,
-ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
+ylabel = {$n\cdot\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
 %xtick={-3,-2,-1,0,1,2,3},
@@
 In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$.
-The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage.
+The one round threshold adaptation strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples before adapting the threshold.
 \label{fig:adaptive_error}  }

### 2020-12-01 conclusions.tex
Fixed typos. Updated Fig. "optimal density".  Rewrote Conclusions

--- 2019-11-24 conclusions.tex
@@
 %
-In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency larger than that of the median of the samples.
+In an adaptive encoding setting, we showed that, asymptotically, no estimator can be more efficient than the median of the samples.
 We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median.
-%We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
-\par
+Furtheremore, we showed that only one round of adapticity is required to attain the optimal efficiecny.
 In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and efficiency relative to the mean.
 %
-These condition implies that, in the distributed, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in this setting.
+Under local asymptotic normality, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in this setting.
 %
-We further considered the special case where the sequence of bits is obtained by comparing against a prescribed sequence of thresholds.
+We further considered the special case where the sequence of bits is obtained in a distributed manner by comparing against a prescribed sequence of thresholds.
 We characterized the performance of the optimal estimator from such bit-sequence using the density of the thresholds and considered the density that minimizes the minimax risk.
+\par
+Obvious extensions of our work include the derviation explicit bounds and optimal procedures when more than one-bit per sample is provided or when each sample is a vector.
+Another possible extension may consider estimation when single bits are sent between nodes of a directed graph.

### 2020-12-01 distributed-estimation.tex
Fixed typos. Updated Fig. "optimal density".  Rewrote Conclusions

@@
 
-We now consider consider a restricted case where each detection region is a
+We now consider a restricted case where each detection region is a
 half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
@@
   B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i<  t_i, \\
-    -1 & X_i > t_i,
+    -1 & X_i \geq t_i,
   \end{cases}  
@@
 The condition that $\lambda_n$ converges to a probability measure is
-satisfied, for example, whenever the $t_1,\ldots,t_n$s are drawn
+satisfied, for example, whenever $t_1,\ldots,t_n$ are drawn
 independently from a probability distribution $\lambda(dt)$ on $\mathbb
@@
 \begin{equation*}
-\lim_{n\to \infty} n \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
+\lim_{n\to \infty} n \cdot \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
 \end{equation*} 
@@
 maximum likelihood estimator
-using $\{B_i = \sgn(X_i - t_i)\}_{i \in \N}$ is at least $\kappa^\star$.
+using $\{B_i = \sgn(X_i - t_i)\}_{i \in \N}$ is at least $\kappa^\star$. \par
 %
-%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
-%\begin{align}
-%\label{eq:cvx_minimax}
-%\begin{split}
-%\mathrm{maximize} \quad &  K \\ 
-%\mathrm{subject~to} 
-%\quad &  K \leq \mathbf H\lambda \\
-%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
-%\end{split}
-%\end{align}
-%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
-%\begin{rem}
-%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$.
-Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points.
-Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using
-%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
-%\end{rem}
-
 Figure~\ref{fig:minimax_support} illustrates an approximation to
@@
 \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density
-with variance $\sigma^2$ and $\Theta = [-T,T]$. The minimax asymptotic
+with variance $\sigma^2$ and $\Theta = [-1/2,1/2]$. The minimax asymptotic
 precision parameter $\kappa^\star$ obtained this way is illustrated in
-Fig.~\ref{fig:minimax_ARE} as a function of half the support size $T$. Also
+Fig.~\ref{fig:minimax_ARE} as a function of $\sigma$. Also
 illustrated in these figures is $\kappa_{\unif}$, the precision
 parameter corresponding to threshold values uniformly distribution over
-$\Theta = [-T,T]$,
+$\Theta$,
 \begin{align}
@@
   \begin{center}
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 1,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-title = {$\sigma/T = 1/2$},
-ytick={0,0.1,1},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1,1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};
-
-\end{axis}
-\end{tikzpicture}
+\input{Figs/opt_thr_den.tex}
+\caption{\label{fig:minimax_support}
+Optimal threshold density. The threshold density $\lambda^\star(dt)$ (blue) that maximizes the asymptotic relative efficiency for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in [-T,T]$.
 %
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.6,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma/T = 1/5$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.5},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.5},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.3,
-samples=10, 
-xlabel= {$dt$},
-xtick={-0.5,0,0.5},
-title = {$\sigma / T = 1/10$},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.2},
-%ylabel = {$\lambda(dt)$},
-yticklabels={0,0.2},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};
-
-\end{axis}
-\end{tikzpicture}
-%
-\begin{tikzpicture}[scale = 0.55]
-\begin{axis}[
-width=8cm, height=6cm,
-xmin = -0.5, xmax=0.5, 
-restrict y to domain = 0:100,
-ymin = 0,
-ymax = 0.15,
-samples=10, 
-xlabel= {$dt$},
-title = {$\sigma / T = 1/20$},
-xtick={-0.5,0,0.5},
-xticklabels={-$T$, 0, $T$},
-ytick={0,0.1},
-ylabel = {$\lambda(dt)$},
-yticklabels={0,0.1},
-line width=1.0pt,
-mark size=1.5pt,
-ymajorgrids,
-xmajorgrids,
-legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
-]
-\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};
-
-\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};
-
-%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
-\end{axis}
-\end{tikzpicture}
-
-\caption{\label{fig:minimax_support}
-Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in [-T,T]$.
-%
-The continuous curve (red) represents the reciprocal of the asymptotic risk for each $\theta \in [-T,T]$ under the optimal density, i.e., the minimax risk is the inverse of the minimal value of this curve.
-The dashed curve (green) is the reciprocal of the asymptotic risk for each $\theta \in [-T,T]$ when the threshold values are uniformly distributed over $[-T,T]$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}.
+The continuous curve (red) is the ARE for each $\theta \in [-1/2,1/2]$ under the optimal density, hence the minimax ARE is the minimal value of this curve.
+The dashed curve (green) is the ARE when the threshold values are uniformly distributed over $[-1/2,1/2]$; its minimal value is $\kappa_{\unif}$ \eqref{eq:uniform_risk}.
 }
@@
 samples=1, 
-xlabel= {$\sigma/T$},
+xlabel= {$\sigma$},
 %xtick={-0.5,0,0.5},
@@
 yticklabels={0,$2/\pi$,1},
-ylabel = {$\ARE$},
+ylabel = {\scriptsize Relative Efficiency},
 line width=1.0pt,
@@
 \end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \Ncal(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$.
-The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}.
-}.
+\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma$ for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in \Theta = [-1/2,1/2]$.
+The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$ of \eqref{eq:uniform_risk}.}.
 \end{center}
@@
 
-%We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$.
-Next, we prove that with any set of messages obtained via a distributed strategy, there exists at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.
-
+%%% Optimal density under a prior %%%%
+\iffalse %%% This part have been removed $$$
 \begin{figure}
@@
 %Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk.
+\fi

### 2020-12-01 proof-sgd.tex
Fixed typos. Updated Fig. "optimal density".  Rewrote Conclusions

@@
 %
-Thus, we show two results: first, that
+Thus, we show two results: first,
 that the family $\{P_\theta\}$ of distributions
@@
     = 2 \int_{-|x|}^{|x|} f(t) dt
-    = 4 f(0)|x| \pm 2 \int_{-|x|}^{|x|}
+    = 4 f(0)|x| + 2 \int_{-|x|}^{|x|}
     \lip(f) t dt
@@
     \int_0^\infty f'(x ) dx
-    - \int_{-\infty}^0 f'(x )
+    - \int_{-\infty}^0 f'(x ) dx
     = -2 f(0) = -\psi'(0).

### 2020-12-04 proof-adaptive-optimality.tex
Fixed typos. Updated Fig. "optimal density".  Rewrote Conclusions
minor changes to proofs of Sec IV

@@
 \begin{proof-of-lemma}[\ref{lem:fisher_bound}]  
-  When $f$ is the normal density function, this lemma follows from
-  \cite[Thm.~3]{Barnes2018}. The proof below is based on a different techique
-  than in \cite{Barnes2018}, and is valid for any log-concave symmetric
-  density satisfying Assumption~\ref{assump:failure_rate}. \\
+  We first note that in the special case where $f$ is a normal density, Lemma~\ref{lem:fisher_bound} follows from \cite[Thm.~3]{Barnes2018}.
+The proof below, valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}, is based on a different techique than that of \cite{Barnes2018}.
+\\
 
-  The Fisher information of $B$ with respect to $\theta$ is given by
+  Write the Fisher information of $B$ with respect to $\theta$ as
   \begin{align}
@@
   where differentiation under the integral sign in $(a)$ is possible since
-  $f$ is log-concave and so a.e.\ differentiable
-  (cf.~\cite{Bertsekas73}),
-  with a.e.\ derivative $f'(x)$. Regularity of
+  $f$ is log-concave hence a.e.\ differentiable
+  (cf.~\cite{Bertsekas73}) with a.e.\ derivative $f'(x)$. Regularity of
   the Lebesgue measure implies that for any $\epsilon>0$, there exists a
@@
   \begin{equation*}
-    \int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
+    \int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon.
   \end{equation*}
-  which implies that for any $\epsilon' > 0$, the set $A$ in
+  It follows that for any $\epsilon' > 0$, the set $A$ in
   \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of
   disjoint intervals without increasing $I_\theta$ by more than
-  $\epsilon'$. It is therefore enough to proceed in the proof assuming that
+  $\epsilon'$. Consequently, we may proceed assuming that
   $A$ is of the form
@@
 To bound the Fisher information of any set of $n$ one-bit
-messages with respect to $\theta$,
-%% we first note that without loss of
-%% each message $B_i$ can is of the form
-%% \begin{equation}
-%% B_i = \begin{cases}
-%% X_i \in A_i & 1, \\
-%% X_i \notin A_i & -1,
-%% \end{cases} 
-%% \end{equation}
-%% where $A_i \subset \R$ is a Borel measurable set. 
-%% %Indeed, any measurable function $(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
-we consider the conditional distribution $P({B_1,\ldots,B_n|\theta})$ of
+messages with respect to $\theta$, we consider the conditional distribution $P({B_1,\ldots,B_n|\theta})$ of
 $(B_1,\ldots,B_n)$ given $\theta$. We have
@@
 
-\subsection{An Isoperimetric Lemma}
+\subsection{Isoperimetric Lemma}
 \label{sec:bound_intervals_delta}
@@
   $y_1,\ldots,y_k,x^*,y_{k+1},\ldots, y_N$ of the functions $\delta_N$ and
-  $\Delta_N$. (We may take the compactification of $\R$ as $[-\infty, \infty]$.)
+  $\Delta_N$. %(We may take the compactification of $\R$ as $[-\infty, \infty]$.)
   %

### 2020-12-09 conclusions.tex
removed last paragraph
fixed typos in the proof of Lemma 22

@@
 We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median.
-Furtheremore, we showed that only one round of adapticity is required to attain the optimal efficiecny.
+Furthermore, we showed that only one round of adaptivity is required to attain optimal efficiency.
 In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and efficiency relative to the mean.
@@
 We characterized the performance of the optimal estimator from such bit-sequence using the density of the thresholds and considered the density that minimizes the minimax risk.
-\par
-Obvious extensions of our work include the derviation explicit bounds and optimal procedures when more than one-bit per sample is provided or when each sample is a vector.
-Another possible extension may consider estimation when single bits are sent between nodes of a directed graph.
+%
+%\par
+%Obvious extensions of our work include deriving explicit bounds and optimal procedures when more than one-bit per sample is provided or when each sample is a vector.
+Another possible extension may consider the efficiency of estimation when single bits are sent between nodes of a directed graph.

### 2020-12-09 distributed-estimation.tex
fixed typos in the proof of Lemma 22

@@
 However, Theorem~\ref{thm:non_existence} implies that such ARE can only be attained for a negligible subset of the parameter space.
-As we shall see next, messages obtained via a comparison against a sequence of thresholds cannot attain the optimal efficiency one more than a single point of $\Theta$.
+As we shall see next, messages obtained via comparison against a sequence of thresholds cannot attain the optimal efficiency one more than a single point of $\Theta$.
 
@@
 half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
-against a single threshold. Under adaptive signal acquisition,
+against a single threshold. Under the adaptive signal acquisition,
 this is sufficient for asymptotic optimality;
@@
 %% for the sequence of thresholds is enough to establish local asymptotic
-%% normality and leads to a closed form expression for the precision parameter
+%% normality and leads to a closed-form expression for the precision parameter
 %% and the ARE.

### 2020-12-09 proof-lan-distributed.tex
removed Assumption A(ii) from Lemma 21
fixed typos in the proof of Lemma 22

@@
   Assumption~\ref{assumption:detection-regions}\eqref{item:lipschitz-density}
-  and \eqref{item:finite-intervals} hold. Then for any $A = \cup_{i = 1}^k
+%  and \eqref{item:finite-intervals} 
+ hold. Then for any $A = \cup_{i = 1}^k
   \{[a_i, b_i]\}$ and $h \in \R$,
   \begin{equation*}
-    P_{\theta + h}(A) = P_\theta(A) + \dPtheta(A) h \pm
+    \left|P_{\theta + h}(A) - P_\theta(A) - \dPtheta(A) h \right| \leq 
     k \cdot \lip(f) h^2,
@@
   + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
-  \cdot \frac{h^4}{n^2}
+  \cdot \frac{h_n^4}{n^2}
   + C \frac{k^4 \lip^4(f)}{
     P_\theta(A_i)^3 P_\theta(A_i^c)^3}
-  \frac{h^8}{n^4}
+  \frac{h_n^8}{n^4}
   \label{eqn:var-wni-expansion}
@@
   ~~ \mbox{and} ~~
-  \frac{k_i h^2}{n} \lip^2(f)
+  \frac{k_i h_n^2}{n} \lip^2(f)
   \le \frac{\min\{P_\theta(A_i), P_\theta(A_i^c)\}}{4}
@@
 \end{equation*}
-where $C < \infty$ depends only on $\lip(f)$ and $h$ (both of which are
+where $C < \infty$ depends only on $\lip(f)$ and $h_n$ (both of which are
 uniformly bounded) whenever
@@
   + \frac{ h_n^4}{n^2} \frac{k_i^2 \lip(f)^2}{p(B_i)^2}\right| \\
-  & \in \pm
+  & = \half \score_\theta(B_i)
+  \frac{h_n}{\sqrt{n}} +
   C \left|\frac{\sqrt{k_i}}{\sqrt{n} p(B_i)}
@@
   + \frac{k_i^2}{p(B_i)^2 n^2}
-  \right| \to 0,
+  \right|
   \label{eqn:max-wni-zero}
 \end{align}
-where $C < \infty$ depends only on $\lip(f)$ and $h_n$ and so is
-uniformly bounded;
-the limit follows from Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals}.
+where $|C| < \infty$ depends only on $\lip(f)$ and $h_n$ and so is
+uniformly bounded. From Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals} we get
+\[
+C \left|\frac{\sqrt{k_i}}{\sqrt{n} p(B_i)}
+  + \frac{k_i}{n p(B_i)}
+  + \frac{\sqrt{k_i}}{p(B_i)^2 n}
+  + \frac{k_i^2}{p(B_i)^2 n^2}
+  \right| \to 0. 
+\]
 Consequently $\max_i W_{n,i} \to 0$, so that
@@
   \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
-  = \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
+  = \frac{h_n}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
   - \frac{1}{4} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]

### 2020-12-20 proof-lan-distributed.tex
removed expressions with \pm

@@
   & = \int_0^h f(a - \theta - u) - f(b - \theta - u) du \\
-  & = \int_0^h (f(a - \theta) - f(b - \theta)) du
+  & \lesseqgtr \int_0^h (f(a - \theta) - f(b - \theta)) du
   \pm 2 \int_0^h \lip(f) u du \\
@@
   \nonumber
-  \half W_{n,i}
-  & = \half \score_\theta(B_i)
+  \left| \half W_{n,i} \right|
+  & \leq \half \left| \score_\theta(B_i) \right|
   \frac{h_n}{\sqrt{n}}
-  \pm \left|\frac{h_n^2}{n} \frac{k_i \lip(f)}{p(B_i)}
+  + \left|\frac{h_n^2}{n} \frac{k_i \lip(f)}{p(B_i)}
   + \frac{h_n^2}{n} \score_\theta(B_i)^2

### 2021-01-06 adaptive-estimation.tex
minor changes to proofs of Sec IV
fixed 1/2 typo and \pm in the proof of thm:sgd
ready for submission

@@
   \begin{equation*}
-    \E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{n}{ 4f^2(0) n + I_0}.
+    \E\left[ (\theta-{\theta}_n)^2 \right] \geq   \frac{1}{ 4f^2(0) n + I_0}.
   \end{equation*}
 \end{thm}
-
-%We first bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$.
-The result then follows using the van-Trees inequality which bounds from below the risk of any estimator of $\theta$ by the inverse of the expected value of the aforementioned Fisher information plus $I_0$.
-The details are in
-
-%% Theorem~\ref{thm:adpative_lower_bound} implies that any estimator ${\theta}_n$ from any adaptive encoding scheme satisfies
-%% \begin{equation*}
-%% n\mathbb E\left[ (\theta-\theta_n)^2 \right] \geq  \frac{1}{4f^2(0)}+O(n^{-1}),
-%% \end{equation*}
-%% and 
-%% \begin{equation*}
-%% \ARE({\theta}_n) \leq 4f^2(0)\sigma^2 = \eta(0)\sigma^2.
-%% \end{equation*}
-It is possible to extend Theorem~\ref{thm:adpative_lower_bound} to other
-loss functions using a more subtle version of the Van Trees
-inequality~\cite{efroimovich1980information}; see also
-\cite{DBLP:journals/corr/abs-1902-08582}.
+%Theorem~\ref{thm:adpative_lower_bound} can be extended to other loss functions using more general versions of the Van Trees inequality~\cite{efroimovich1980information}; see also \cite{DBLP:journals/corr/abs-1902-08582}.
 
@@
       \\
-      & \qquad \qquad \qquad \qquad = \mathbb E \left[L(W/ 2 f(0)) \right],
+      & \qquad \qquad \qquad \qquad = \mathbb E \left[L(Z/ 2 f(0)) \right],
         \label{eq:attaining_LAM}
     \end{align}
-    where $W \sim \normal(0,1)$. 
+    where $Z \sim \normal(0,1)$. 
     %
@@
 \noindent
-We provide the proofs of the items in Appendices~\ref{sec:proof-normal-sgd},
+We provide the proofs of items (i)-(iii) in Appendices~\ref{sec:proof-normal-sgd},
 \ref{sec:proof-sgd-regular}, \ref{sec:proof-sgd-ms-convergence},
@@
 \end{center}
-\caption{Distributed encoding with one round of interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is utilized in obtaining another $n-n_1$ bits in a distributed manner.
+\caption{Distributed encoding with one round of threshold adaptation.
+The estimation obtained from the first $n_1$ bits in a distributed manner is utilized in obtaining another $n-n_1$ bits in a distributed manner.
 \label{fig:one_round}
@@
 
+Figure \ref{fig:adaptive_error} illustrates the empirical risks 
+of the estimator \eqref{eq:sgd_alg} and an estimator obtained using one round of threshold adaptation under a series of Monte Carlo simulations when $f(x)$ is the standard normal desnity.
+
 \begin{figure}
@@
 \addplot[color = red, solid, smooth] plot table [x = itr, y = split, col sep=comma] {./SimRes/sim_res_nMonte5000.csv};
-\addlegendentry{single interaction};
+\addlegendentry{one adaptation};
 

### 2021-01-06 distributed-estimation.tex
ready for submission

@@
 \caption{\label{fig:minimax_support}
-Optimal threshold density. The threshold density $\lambda^\star(dt)$ (blue) that maximizes the asymptotic relative efficiency for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in [-T,T]$.
+Optimal threshold density.
+The threshold density $\lambda^\star(dt)$ (blue) that maximizes the asymptotic relative efficiency for $f(x)$ the normal desnity with variance $\sigma^2$ and $\Theta= [-1/2,1/2]$.
 %
@@
 \end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma$ for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in \Theta = [-1/2,1/2]$.
+\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma$ for $f(x)$ the standard normal density with variance $\sigma^2$ and $\Theta = [-1/2,1/2]$.
 The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$ of \eqref{eq:uniform_risk}.}.

### 2021-01-06 onebit_full.tex
Rewriting intro
Working on problem setting
Compiler
Fixed proof of (previously) Lemma 15 and made changes in structure regarding this lemma. Now one lemma (Lemma 12) is used in three different results.
Corrected proof of isoprimetric lemma
Working on proof of SGD
Working on rewriting proof of theorem 2
Giving the one step estimator proof
Starting to work on distributed part
Rewrote entire proof of local asymptotic normality
Finished writing major proofs and fixing references. Still needs a once through
added funding information
ready for submission

@@
 %% \documentclass[11pt]{article}
-\documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper
+\documentclass[letterpaper, 11pt, draftcls]{IEEEtran}      % Use this line for a4 paper
 
@@
     \IEEEauthorblockA{\IEEEauthorrefmark{2}Stanford University, Department of Electrical Engineering. }
+
+\thanks{This paper was presented in part at the 55th Annual Allerton Conference on Communication, Control, and Computing (Allerton) \cite{KipnisAllerton2017}.
 }
+}
+
+%% \renewenvironment{figure}{%
+%%   \ignorespaces
+%% }{}
 
@@
 
-%{\color{red}  See LASSO results in http://arxiv.org/abs/1506.02181v1}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%% \input{adaptive-estimation}
+\input{adaptive-estimation}
 
-%% \input{distributed-estimation}
+\input{distributed-estimation}
 
-%% \input{conclusions}
+\input{conclusions}
 
-%\section*{ACKNOWLEDGMENT}
-%This research is supported in parts by...
-%Tsachy Weissman, Stefano Rini, Robert Gray.
+\section*{Acknowledgments}
+%% \textbf{WRITE THIS SECTION}
+The work of A. Kipnis was supported in part by funding from the NSF under Grant No.~DMS-1418362 and DMS-1407813, and by a fellowship from the Koret Foundation.
 
@@
 
-\appendix
+\newpage
+% \appendix
 
-%% \input{appendices}
+\section*{Appendices}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{uniform-are-weirdos}
+\input{proof-adaptive-optimality}
+\input{proof-sgd}
+\input{proof-lan-distributed}
+\input{proof-no-distributed}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{IEEEtran}
-\bibliography{IEEEfull,onebit}
+\bibliography{IEEEfull,onebit,bib}
 

### 2021-01-06 proof-adaptive-optimality.tex
removed expressions with \pm
ready for submission

@@
   Let $X$ be a random variable with a symmetric, log-concave, and
-  continuously differentiable density function $f(x)$ such that Assumption~1
-  holds. For a Borel measurable set $A$, define
+  continuously differentiable density function $f(x)$ such that Assumption~1 holds. For a Borel measurable set $A$, define
   \begin{equation*}
@@
   \end{equation*}
-  Then the Fisher information of $B$ with respect to $\theta$ is bounded
-  from above by $\eta(0)$.
+  The Fisher information of $B$ with respect to $\theta$ is bounded from above by $\eta(0)$.
 \end{lem}
@@
 The proof below, valid for any log-concave symmetric density satisfying Assumption~\ref{assump:failure_rate}, is based on a different techique than that of \cite{Barnes2018}.
-\\
-
+\par
   Write the Fisher information of $B$ with respect to $\theta$ as
@@
   \end{align}
-  where differentiation under the integral sign in $(a)$ is possible since
-  $f$ is log-concave hence a.e.\ differentiable
-  (cf.~\cite{Bertsekas73}) with a.e.\ derivative $f'(x)$. Regularity of
-  the Lebesgue measure implies that for any $\epsilon>0$, there exists a
-  finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
+  where differentiation under the integral sign in $(a)$ is justified since $f$ is log-concave hence a.e.\ differentiable
+  (cf.~\cite{Bertsekas73}) with a.e.\ derivative $f'(x)$. By regularity of the Lebesgue, for any $\epsilon>0$ there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that
   \begin{equation*}
@@
   It follows that for any $\epsilon' > 0$, the set $A$ in
-  \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of
-  disjoint intervals without increasing $I_\theta$ by more than
+  \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than
   $\epsilon'$. Consequently, we may proceed assuming that
@@
   \begin{equation*}
-    A = \cup_{j=1}^k (a_j,b_j),
+    A = \cup_{j=1}^k (t^+_j,t^-_j),
   \end{equation*}
-  with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
+  with $\infty \leq t^-_1 \leq \ldots t^-_k$, $t^+_1 \leq t^+_k \leq \infty$ and $t^-_j \leq t^+_j$ for $j=1,\ldots,k$. Under this assumption, 
   \begin{align*}
-    \mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
-    & = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
+    P_{\theta}(B_n=1) & = \sum_{j=1}^k \left( F \left(t^+_j-\theta\right) -  F \left(t^-_j-\theta\right)  \right),
   \end{align*}
@@
   \begin{align*}
-    I_\theta & =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
-    { \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
+    I_\theta & = \frac { \left( \sum_{j=1}^{k} \left[ f \left(t^+_j-\theta \right) - f \left( t^-_j-\theta \right) \right] \right)^2 } 
+    { \left( \sum_{j=1}^k \left[ F \left( t^+_j-\theta \right) - F \left( t^-_j-\theta \right) \right] \right) }  \nonumber \\
     & \times \frac {1} 
-    {1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
+    {1- \left( \sum_{j=1}^k \left[ F \left(  t^+_j-\theta \right) - F \left( t^-_j-\theta \right) \right] \right) } 
   \end{align*}
-  It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in
-  \R$ and any choice of the intervals' endpoints,
+  It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in \R$ and any choice of the intervals' endpoints,
   \begin{equation*}
     I_\theta \le
-    \max_{t \in \{a_j,b_j, j=1,\ldots,k\} } 4f(t)^2 \leq 4 f(0)^2, 
+    \max_{t \in \{t^\pm_1,\ldots,t^\pm_k\} } 4f(t)^2 \leq 4 f(0)^2. 
   \end{equation*}
-  where the last transition is by Assumption~\ref{assump:failure_rate}. 
 \end{proof-of-lemma}
 
-We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}.
-To bound the Fisher information of any set of $n$ one-bit
-messages with respect to $\theta$, we consider the conditional distribution $P({B_1,\ldots,B_n|\theta})$ of
-$(B_1,\ldots,B_n)$ given $\theta$. We have
+We now prove Theorem~\ref{thm:adpative_lower_bound}. Write the Fisher information of $B_1,\ldots,B_n$ with respect to $\theta$ as 
 \begin{align*}
-  P\left( B_1,\ldots,B_n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B_1,\ldots,B_{i-1} \right),
-  %% \label{eq:adpt_lower_bound_proof:1}
+I_\theta(B_1,\ldots,B_n) = \sum_{i=1}^n I_\theta (B_i|B_1,\ldots,B_{i-1}),
 \end{align*}
-where $P\left(B_i =1 | \theta, B_1,\ldots,B_{i-1} \right) = \mathbb P\left(
-X_i \in A_i\right)$, when $B_i = \indic{X_i \in A_i}$ by independence,
-so that the Fisher information of $B_1,\ldots,B_n$ with
-respect to $\theta$ is
+where $I_\theta (B_i|B_{i-1},\ldots,B_1)$ is the Fisher information of the distribution of $B_i$ given $B_1,\ldots,B_{i-1}$.
+By the definition of the adaptive setting, $P_{\theta}(B_i|B_1,\ldots,B_{i-1}) = P_{\theta}(X_i \in A_i)$ for some Borel measurable $A_i$.
+Consequently, Lemma~\ref{lem:fisher_bound} applies, leading to the bound
+\[
+ I_\theta (B_i|B_{i-1},\ldots,B_1) \leq 4f(0)^2,
+\]
+We conclude
 \begin{align}
-I_\theta(B_1,\ldots,B_N) = \sum_{i=1}^n I_\theta (B_i|B_1,\ldots,B_{i-1}),
-\label{eq:fisher_information}
+I_\theta(B_1,\ldots,B_n) = 4f(0)^2 n
+\label{eq:fisher_information}.
 \end{align}
-where $I_\theta (B_i|B_{i-1},\ldots,B_1)$ is the Fisher information of the
-distribution of $B_i$ given $B_1,\ldots,B_{i-1}$.
-Lemma~\ref{lem:fisher_bound} implies that $I_\theta
-(B_i|B_{i-1},\ldots,B_1) \leq 4f(0)^2$. The Van Trees inequality
-\cite{van2004detection, gill1995applications} now implies
+The Van Trees inequality in the version of 
+\cite{gill1995applications} holds under the regularity conditions on $\pi(\cdot)$, which implies
+\begin{align*}
+\ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ \E_{\pi} \left[ I_\theta(B_1,\ldots,B_n)\right] + I_0}.
+\end{align*}
+Combining the last display with \eqref{eq:fisher_information}, we get
+\begin{align*}
+\ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ 4f(0)^2 n + I_0}.
+\end{align*}
+
+\cite{van2004detection} and \eqref{eq:fisher_information} imply
 \begin{align*}
 \ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ \ex{ I_\theta(B_1,\ldots,B_n)} + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
-& \geq \frac{1}{ 4f^2(0) n + I_0}
+& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B_1,\ldots,B_{i-1}) + I_0} \\
+& \geq \frac{1}{ 4f^2(0) n + I_0}.
 \end{align*}
-as desired.
 
@@
   %For simplicity, we also assume that $s_{i^*} = 1$ and note that the case $s_{i^*} = -1$ is obtained using identical arguments. 
-  Set $x^* = x_{i^*}$ and let $k=i^*-1$. In what follows, variables with subscript of non-positive index are ignored in summations and in lists of arguments to functions. Consider the function
+  Set $x^* = x_{i^*}$ and let $k=i^*-1$. Consider the function
   \begin{align}
@@
   \begin{equation*}
-    \max_{(y_1,\ldots,y_N) \in A_N} g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*),
+    \max_{(y_1,\ldots,y_N) \in A_N(x^*,k) } g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*),
   \end{equation*}
@@
   \begin{equation*}
-    g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*)
+    g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*).
   \end{equation*}
@@
   \begin{itemize}
-  \item[(1)]  $y_N \to -\infty$. 
-  \item[(2)] $y_1 \to \infty$.
-  \item[(3)] $y_k = x_{i^*}$.
-  \item[(4)] $y_{k+1} = -x_{i^*}$. 
+  \item[(i)]  $y_N = -\infty$. 
+  \item[(ii)] $y_1 = \infty$.
+  \item[(iii)] $y_k = x_{i^*}$.
+  \item[(iv)] $y_{k+1} = -x_{i^*}$. 
   \end{itemize}
-  For case (1), 
+  For case (i), 
   \begin{align*}
@@
   \end{align*}
-  which is smaller than $\eta_\delta(x_{i^*})$ by the induction hypothesis. Similarly, under case (2),
+  which is smaller than $\eta_\delta(x_{i^*})$ by the induction hypothesis. Similarly, under case (ii),
   \begin{align*}
@@
   which is smaller than $\eta_{\delta}(x_{i^*})$ by the induction hypothesis.
-Under case (3), the terms in $\delta_N$ and $\Delta_N$ corresponding to $y_k$ and $x_{i^*}$ cancel each other.
-As a result,  $g(y_1,\ldots,y_N)$ reduces to an expression with $n=N-1$ variables hence this case is handled by the induction hypothesis.
+Under case (iii), the terms in $\delta_N$ and $\Delta_N$ corresponding to $y_k$ and $x_{i^*}$ cancel each other.
+As a result,  $g(y_1,\ldots,y_N)$ reduces to an expression with $N-2$ variables hence this case is handled by the induction hypothesis.
   %
-  Finally, under case (4), set 
+  Finally, under case (iv), set 
   \begin{equation*}

### 2021-09-08 abstract.tex
fixed all minor comments from R1

@@
   We consider the problem of estimating the mean of a symmetric log-concave
-  distribution under constraint that only a single bit per sample
+  distribution under the constraint that only a single bit per sample
   from this distribution is available to the estimator. We study the mean
   squared error as a function of the
-  sample size (and hence number of bits).
+  sample size (and hence the number of bits).
   We consider three settings: first, a centralized setting, where

### 2021-09-08 adaptive-estimation.tex
fixed all minor comments from R1

@@
     and~\eqref{eqn:stringent-gamma}. Let
-    $\pi$ be a distribution on $\R$. Then
-    \begin{equation*}
+    $\pi$ be a distribution on $\R$ \newtext{with a finite second moment}. Then
+    \begin{align}
       \int \E\Big[( \bar{\theta}_n - \theta )^2\Big] \pi(d\theta)
       = \frac{1}{4 n f(0)^2} + o(n^{-1}). 
-    \end{equation*}
+      \label{eq:adaptive_3}
+    \end{align}
   \end{enumerate}
@@
   $f = F'$, we have
-  $B_i \cas F(\theta_0 - \theta)$, so that
+  $\ex{B_i} \cas F(\theta_0 - \theta)$, so that
   $\frac{1}{n_1} \sum_{i = -n_1}^{-1} B_i \cas F(\theta - \theta_0)$ and

### 2021-09-08 distributed-estimation.tex
fixed all minor comments from R1

@@
 \end{equation*}
-for $Z$ with density $f$. Whenever $A$ is a collection
-of disjoint intervals $A = \cup_i \{[t_i^-, t_i^+]\}$, we may define
+for $Z$ with density $f$. Whenever $A$ is a collection of disjoint intervals $A = \cup_i [t_i^-, t_i^+]$, we may define
 \begin{equation*}
@@
   \item \label{item:finite-intervals}
-    Each set $A_n$ is the finite union of $k_n$ disjoint intervals
+    Each set $A_i$ is the finite union of $k_i$ disjoint intervals
     (which may include $\pm \infty$), where
@@
 \end{equation*} 
-so that the ML estimator attains the local asymptotic MSE of Theorem~\ref{thm:adpative_lower_bound}.
+so that the ML estimator attains the local asymptotic MSE of Theorem~\ref{theorem:non-adaptive-minimax}.
 
@@
 
-We conclude this section by considering the density of the threshold values
+We conclude this section by considering the \newtext{distribution} of the threshold values
 that maximizes the worst-case information $\inf_\theta \kappa(\theta)
@@
 = \int \eta(t - \theta) d\lambda(t)$.
-This distribution $\lambda$ solves the
+The \newtext{optimal distribution $\lambda^\star$} solves the
 optimization problem

### 2021-09-08 proof-adaptive-optimality.tex
fixed all minor comments from R1

@@
   Let $X$ be a random variable with a symmetric, log-concave, and
-  continuously differentiable density function $f(x)$ such that Assumption~1 holds. For a Borel measurable set $A$, define
+  continuously differentiable density function $f(x)$ such that Assumption~\ref{assump:failure_rate} holds. For a Borel measurable set $A$, define
   \begin{equation*}
@@
   \end{equation*}
-  with $\infty \leq t^-_1 \leq \ldots t^-_k$, $t^+_1 \leq t^+_k \leq \infty$ and $t^-_j \leq t^+_j$ for $j=1,\ldots,k$. Under this assumption, 
+  with $\infty \leq t^-_1 \leq \ldots \leq t^-_k$, $t^+_1 \leq \ldots \leq t^+_k \leq \infty$ and $t^-_j \leq t^+_j$ for $j=1,\ldots,k$. Under this assumption, 
   \begin{align*}
@@
 \begin{align}
-I_\theta(B_1,\ldots,B_n) = 4f(0)^2 n
+I_\theta(B_1,\ldots,B_n) \leq 4f(0)^2 n
 \label{eq:fisher_information}.
@@
 
-\cite{van2004detection} and \eqref{eq:fisher_information} imply
-\begin{align*}
-\ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ \ex{ I_\theta(B_1,\ldots,B_n)} + I_0} \\
-& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B_1,\ldots,B_{i-1}) + I_0} \\
-& \geq \frac{1}{ 4f^2(0) n + I_0}.
-\end{align*}
+%\cite{van2004detection} and \eqref{eq:fisher_information} imply
+%\begin{align*}
+%\ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ \ex{ I_\theta(B_1,\ldots,B_n)} + I_0} \\
+%& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B_1,\ldots,B_{i-1}) + I_0} \\
+%& \geq \frac{1}{ 4f^2(0) n + I_0}.
+%\end{align*}
 
@@
     &  \triangleq  \frac{\left| \delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N) )\right|^{2+\delta}}{
-      \left|\Delta_{N+1}(y_1,\ldots,y_k,x_{i^*},y_{k+1}\ldots,y_N)  (1 -\Delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N)  \right|^{1+\delta}
+      \left|\Delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N)  (1 -\Delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N)  \right|^{1+\delta}
     } \label{eq:g_def}.
@@
   \begin{equation*}
-    A_N(x^*,k) \triangleq \left\{ (y_1,\ldots,y_N) \in \R^N\, : \, y_1 \ge y_k \ge x^* \ge -x^* \ge y_{k+1} \ldots \ge y_N
+    A_N(x^*,k) \triangleq \left\{ (y_1,\ldots,y_N) \in \R^N\, : \, y_1 \ge \ldots \ge y_k \ge x^* \ge -x^* \ge y_{k+1} \ldots \ge y_N
     \right\}.

### 2021-09-08 proof-no-distributed.tex
ready for submission
fixed all minor comments from R1

@@
 if $\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0)$. By
-assumption, we have $B_i = \indic{X_i \in A_i}$ where each $A_i =
-\cup_{i=1}^K \{[a_{i,k},b_{i,k}]\}$, where $a_{i,1} \leq b_{i,1} \leq \ldots
-\leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values
-$-\infty$ and $\infty$, respectively. Denote the endpoints
+assumption, we have $B_i = \indic{X_i \in A_i}$, $A_i =
+\cup_{k=1}^K (t^-_{i,k},t^+_{i,k})$, where $t^-_{i,1} \leq t^+_{i,1} \leq \ldots
+\leq t^-_{i,K} \leq t^+_{i,K}$, and $t^-_{i,1}$ and $t^+_{i,K}$ may take the values
+$-\infty$ and $\infty$, respectively. Denote the set of endpoints
 \begin{equation*}
-  E_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\},
+  E_i = \bigcup_{k=1}^{K}\{t^-_{i,k},t^+_{i,k}\},
 \end{equation*}
@@
 & = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
-\frac{ \left(\sum_{k=1}^{K}  f(\theta - b_{i,k})- f(\theta - a_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
+\frac{ \left(\sum_{k=1}^{K}  f(\theta - t^+_{i,k})- f(\theta - t^-_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)\right)} \nonumber \\
 & 
-+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(b_{i,k}-\theta) - f(a_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
++ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(t^+_{i,k}-\theta) - f(t^-_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)\right)} \nonumber \\
 & \overset{(a)}{\leq}
@@
 \begin{equation*}
-\max\left\{ \max_k \eta(b_{i,k}-\theta) , \max_k \eta(a_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
+\max\left\{ \max_k \eta(t^+_{i,k}-\theta) , \max_k \eta(t^-_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
 \end{equation*}
@@
   \label{eq:few_optimality_points_proof}
-  \card (\cup_{i=1}^n \mathcal B_i) \leq 2 n K. 
+  \card \left(\bigcup_{i=1}^n  A_i \right) \leq 2 n K. 
 \end{equation}
@@
 \end{equation*}
-Since for each $\theta \in \Theta$ we have $S_n(\theta, \epsilon) \to 1$, there exists $n$ large enough such that 
+Since for each $\theta \in \Theta$ we have $\card \left(S_n(\theta, \epsilon) \right) \to 1$, there exists $n$ large enough such that 
 \begin{equation*}

### 2021-09-08 proof-sgd.tex
fixed 1/2 typo and \pm in the proof of thm:sgd
removed expressions with \pm
fixed all minor comments from R1

@@
   \label{corollary:polyak-juditsky}
-  Let $\varphi : \R \to \R$ and $Z_i$ be i.i.d.\ random
+  Let $\varphi : \R \to \R$ and $\{Z_i\}$ be i.i.d.\ random
   variables, and
@@
   \item \label{item:zero-gradient}
-    The function $\psi(x) \triangleq \ex{ \varphi(x+Z_1)}$
+    The function $\psi(x) \defeq \ex{ \varphi(x+Z_1)}$
     satisfies $\psi(0) = 0$ and
@@
       \label{eqn:local-hessian-psi}
-        \left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}.
+        \left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}
     \end{equation}
+    \newtext{for all $|x|<r$ for some $r>0$ small enough. }
   \item The function 
-    $\chi(x) \triangleq \ex{\varphi^2(x+Z_1)}$ is continuous at zero. 
+    $\chi(x) \defeq \ex{\varphi^2(x+Z_1)}$ is continuous at zero. 
   \end{enumerate}
@@
 have for small $x$ that
+% AK: Here I changed \pm to \leq and \geq
 \begin{equation*}
   \psi(x) = 2 \int_0^x f(-t) dt
-  = 2 \int_0^x \left[f(0) \pm \lip_0(f) t \right] dt
-  = 2 f(0) x \pm \frac{\lip_0(f)}{2} x^2
-  = \psi'(0) x \pm \frac{\lip_0(f)}{2} x^2,
+  \leq 2 \int_0^x \left[f(0) + \lip_0(f) t \right] dt
+  = 2 f(0) x + \lip_0(f) x^2
+  = \psi'(0) x + \lip_0(f) x^2,
+\end{equation*}
+\begin{equation*}
+  \psi(x) = 2 \int_0^x f(-t) dt
+  \geq 2 \int_0^x \left[f(0) - \lip_0(f) t \right] dt
+  = 2 f(0) x - \lip_0(f) x^2
+  = \psi'(0) x - \lip_0(f) x^2,
 \end{equation*}
@@
   at
-  $\theta$ if there exists a sequence of random vectors $Z_n$ such that for
+  $\theta$ if there exists a sequence of random vectors $\{Z_n\}$ such that for
   all $h_n \to h$,
@@
     \sum_{i = 1}^n \log \frac{dP_{\theta + h_n/\sqrt{n}}}{dP_\theta}
-    (X_1, \ldots, X_n)
+    \newtext{(X_i)}
     = h^\top Z_n - \half h^\top I_\theta h + o_P(1)
@@
 By the assumption in Theorem~\ref{thm:sgd} that the density $f$
-is Lipschitz continuous, we see that the location family
+is Lipschitz continuous, \newtext{$\sqrt{f}$ is Lipschitz continuous hence absolutely continuous}. We see that the location family
 $\{P_\theta\}_{\theta \in \R}$ defined by $dP_\theta(x) = f(x - \theta)$
@@
 
-It remains to show that the average $\bar{\theta}_n$ is regular:
+It remains to show that the average $\bar{\theta}_n$ is regular \newtext{at $\theta$ with the limiting distribution $\Ncal(0,(4f(0)^2)^{-1})$}:
 \begin{lemma}
@@
   Let $h_n \to h \in \R$, and define $P_n = P_{\theta + h_n / \sqrt{n}}^n$.
-  Then $\bar{\theta}_n$ is regular with
+  Then 
   \begin{align}
     \label{eqn:sgd-median-regular}
-    \sqrt{n}\left( \bar{\theta}_n - \theta - h_n / \sqrt{n}\right)
+    \newtext{
+    \sqrt{n}\left( \bar{\theta}_n - \theta \right)
     \mathop{\cd}_{P_n}
     \normal\left( h,\frac{1}{4 f(0)^2}\right).
+    }
   \end{align}
@@
     meaning that $\theta_i = \theta_{i-1} + \gamma_i \varphi(X_i -
-    \theta_{i-1})$ for $X_i = \theta + Z_i$, where $Z_i$ are i.i.d.\ with
+    \theta_{i-1})$ for $X_i = \theta + Z_i$, where $\{Z_i\}$ are i.i.d.\ with
     $\E[\varphi(Z)] = 0$. Additionally assume the local smoothness
@@
       \label{eqn:additional-local-smooth}
-      \E[|\varphi(x + Z) - \varphi(Z)|^2]
+      \E[|\varphi(x + Z_1) - \varphi(Z)|^2]
       \le K (|x|^\lambda + x^2).
     \end{equation}
-    Set $\Delta_i = \theta_i - \theta$ and $\bar{\Delta}_i = \frac{1}{n}
+    Set $\Delta_i \defeq \theta_i - \theta$ and $\bar{\Delta}_n \defeq \frac{1}{n}
     \sum_{i=1}^n \Delta_i$. Then
@@
     \item \label{item:regularity}
-      The sequence $\Delta_i$ is regular, that is,
+      The sequence $\{\Delta_i\}$ is regular, that is,
       \begin{equation}
@@
       \end{equation}
-    \item \label{item:apply-le-cam} Let $Z_i$ as in
+    \item \label{item:apply-le-cam} Let $\{Z_i\}$ as in
       Corollary~\ref{corollary:polyak-juditsky} have absolutely continuous
       density $p$ with median $0$, define $\score_h(z) = \frac{p'(z - h)}{p(z
-        - h)}$, and assume that $I_h \defeq \E_\theta[\score_h(Z)^2]$ is
+        - h)}$, and assume that $I_h \defeq \E_p[\score_h(Z_1)^2]$ is
       continuous in $h$ near 0.  Then for any converging sequence $h_n \to h$,
@@
         \mathop{\cd}_{P_{\theta + h_n/\sqrt{n}}^n}
-        \normal\left( \frac{-h}{\psi'(0)} \E_p[\varphi(Z) \score_0(Z)],
+        \normal\left( \frac{-h}{\psi'(0)} \E_p[\varphi(Z_1) \score_0(Z_1)],
         \frac{\chi(0)}{\psi'^2(0)} \right).
@@
     = 2 \int_{-|x|}^{|x|} f(t) dt
-    = 4 f(0)|x| + 2 \int_{-|x|}^{|x|}
+    \le 4 f(0)|x| + 2 \int_{-|x|}^{|x|}
     \lip(f) t dt
@@
   where $\lip(f)$ is the Lipschitz constant of $f$.
-  For large $x$ we always have
-  $\E[|\varphi(Z) - \varphi(x + Z)|] \le 2$, so that
-  condition~\eqref{eqn:additional-local-smooth} holds.
+\newtext{It follows that condition~\eqref{eqn:additional-local-smooth} holds.}  
+   %For large $x$ we always have  $\E[|\varphi(Z) - \varphi(x + Z)|] \le 2$, so that condition~\eqref{eqn:additional-local-smooth} holds.
   In addition, we have
-  \begin{equation*}
+  \begin{align*}
+\newtext{ \E_p[\varphi(Z_1) \score_0(Z_1)] } & = 
     \int_{\R} \varphi(x) f'(x ) dx
-    = \int_{\R} \sgn(x) f'(x ) dx =
+    = \int_{\R} \sgn(x) f'(x ) dx\\
+     &  =
     \int_0^\infty f'(x ) dx
@@
     = -2 f(0) = -\psi'(0).
-  \end{equation*}
+  \end{align*}
   Corollary~\ref{corollary:normal-expansion}
@@
   derivative, and is minimized by $x^\star$. Moreover, assume that the
-  noises $Z_n$ are i.i.d.\ with density $p$ and
-  that the Fisher information $\E[(p'(Z))^2 / p(Z)^2]$ exists and is finite.
+  noises $\{Z_n\}$ are i.i.d.\ with density $p$ and
+  that the Fisher information $\E[(p'(Z_1))^2 / p(Z_1)^2]$ exists and is finite.
   Let $\psi(x)$ and $\chi(x)$ be defined as in
@@
 
-We apply Corollary~\ref{corollary:polyak-mse} with $g(x) = 0.5(x-\theta)^2$,
+\newtext{Fix $\theta \in \R$}. Apply Corollary~\ref{corollary:polyak-mse} with $g(x) = 0.5(x-\theta)^2$,
 $\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$.
@@
 \E_{P_\theta}[(\bar{\theta}_n - \theta)^2]$ is continuous in $\theta$, so
-that for $x^\star = \theta$ and $g'' \equiv 1$, we may apply
-Corollary~\ref{corollary:polyak-mse} and a finite approximation to the prior
-measure $\pi$ to obtain
-Theorem~\ref{thm:sgd}\eqref{item:sgd-ms-convergence}.
+that for $x^\star = \theta$ and $g'' \defeq 1$, \newtext{we may apply
+Corollary~\ref{corollary:polyak-mse} to obtain}
+\begin{align*}
+\ex{(\bar{\theta}_n - \theta)^2} = \frac{1}{4nf(0)^2} + o(n^{-1}).
+\end{align*}
+\newtext{
+From here, existence of the second moment of $\pi$ implies \eqref{eq:thm:sgd_3}. }
+%Theorem~\ref{thm:sgd}\eqref{item:sgd-ms-convergence}.}
+
+%and a finite approximation to the prior measure $\pi$ to obtain
 
@@
   \label{lemma:polyak-expansion}
-  Define the process $\Delta_i^1 = \Delta_{i-1}^i
-  - \gamma_i (A \Delta_{i-1} + \xi_i)$ for $i = 1, 2, \ldots$.
+  Define the process $\Delta_i^1 = \Delta_{i-1}^1
+  - \gamma_i (A \Delta_{i-1}^1 + \xi_i)$ for $i = 1, 2, \ldots$.
   Assume that $A>0$ and the stepsizes $\gamma_i$ satisfy
@@
   \begin{equation*}
-    \epsilon_i \triangleq \psi(\Delta_{i-1}) + \varphi(Z_i)
+    \epsilon_i \defeq \psi(\Delta_{i-1}) + \varphi(Z_i)
     - \varphi(\Delta_{i-1}+Z_i),
@@
   by Condition~\eqref{eqn:lazy-gamma}.
-  As with probability 1 there exists some (random) $R < \infty$ such that
-  $\tau_R = \infty$, we obtain that 
+\newtext{As Lemma~\ref{lemma:converging-power-sum} implies in particular that $\{\Delta_i\}$ is a.s.
+bounded, with probability 1 there exists some (random) $R < \infty$ such that $\tau_R = \infty$.} We obtain that
   \begin{equation*}
@@
     \varepsilon_i^2  < \infty
-    ~ \mbox{a.s.}
+    ~ \mbox{a.s.}.
   \end{equation*}
@@
 that the Fisher information $I_h =
-\E_h[\score_h(Z)^2]$ exists and is continuous for
+\E_h[\score_h(Z_1)^2]$ exists and is continuous for
 $\score_h(z) = \frac{p'(z - h)}{p(z - h)}$,
@@
 \begin{equation*}
-  \left(\sqrt{n} \bar{\Delta}_n, \log \frac{P^n_{h_n/\sqrt{n}}}{P^n_0}(Z_1^n)
+  \left(\sqrt{n} \bar{\Delta}_n, \sum_{i=1}^n \log \frac{P_{h_n/\sqrt{n}}}{P_0}(Z_i)
   \right)
@@
     \frac{\chi(0)}{\psi'(0)^2} & \frac{-h}{ \psi'(0)}
-    \E_p[\varphi(Z) \score_0(Z)] \\
-    \frac{-h}{ \psi'(0)} \E_p[\varphi(Z) \score_0(Z)]
+    \E_p[\varphi(Z_1) \score_0(Z_1)] \\
+    \frac{-h}{ \psi'(0)} \E_p[\varphi(Z_1) \score_0(Z_1)]
     & h^2 I_0
@@
 \end{equation*}
-under the alternatives $P_{h_n/\sqrt{n}}$, which gives
+under the alternatives $P^n_{h_n/\sqrt{n}}$, which gives
 Corollary~\ref{corollary:normal-expansion}\eqref{item:apply-le-cam}.
@@
 \end{equation*}
-and so Jensen's inequality (or Cauchy-Schwarz) we have
+and so By Jensen's inequality (or Cauchy-Schwartz) we have
 \begin{equation*}
@@
 for all $x$ excepting a $\mu$-null set, and the
-variant dominated convergence theorem in
+variant of the dominated convergence theorem in
 \cite[Prop.~2.29]{VanDerVaart98} implies that

### 2021-09-08 uniform-are-weirdos.tex
fixed all minor comments from R1

@@
 and so (by the Borel-Cantelli lemmas), for any $\theta \in \R$ we have
-$P_\theta(|\theta_n - \theta| \le \sqrt{2 \log n} / n^{3/4} ~
+$P_\theta(|\theta_n - \theta| \le \sqrt{\newtext{8} \log n} / n^{3/4} ~
 \mbox{eventually}) = 1$. This is of course faster than the $1/\sqrt{n}$

### 2021-09-29 adaptive-estimation.tex
fixed all comments after first revision, sending to John

@@
 
-Then we can adapt the results of Polyak and Juditsky~\cite{PolyakJu92}
+Then we can adapt the results of Polyak and Juditsky~\cite{polyak1992acceleration}
 on the asymptotic normality of averaged stochastic gradient estimators

### 2021-09-29 conclusions.tex
fixed all comments after first revision, sending to John

@@
 %\par
-%Obvious extensions of our work include deriving explicit bounds and optimal procedures when more than one-bit per sample is provided or when each sample is a vector.
-Another possible extension may consider the efficiency of estimation when single bits are sent between nodes of a directed graph.
+
+\newtext{
+Natural extensions of the setting of this work are situations when the communication bit-budget $b$ is larger than one and when each sample is a $d$-dimensional vector.
+Fundamental bounds for this general case follows from several recent works (e.g.
+\cite{zhang2013information,shamir2014fundamental,braverman2016communication,han2018geometric,barnes2020lower}), which imply that in the adaptive and distributed cases the MSE scales in the regular parametric rate of $1/n$ when $b$ and $d$ are held fixed in the sample size $n$.
+Nevertheless, the coefficient of the $1/n$ term corresponding to the ARE is still unknown; deriving the ARE for general $b$ and $d$ is left as a future challenge.}

### 2021-09-29 distributed-estimation.tex
fixed all comments after first revision, sending to John

@@
 
+\subsection{Optimal Efficiency}
 We begin by making a few restrictions on the collections of the sets $A_i$,
@@
 = \kappa_\lambda(\theta)$ where $\kappa_\lambda(\theta)
-= \int \eta(t - \theta) d\lambda(t)$.
+= \int \eta(t - \theta) \lambda(dt)$.
 The \newtext{optimal distribution $\lambda^\star$} solves the
@@
 \caption{\label{fig:minimax_support}
-Optimal threshold density.
+Optimal threshold density under distributed encoding.
 The threshold density $\lambda^\star(dt)$ (blue) that maximizes the asymptotic relative efficiency for $f(x)$ the normal desnity with variance $\sigma^2$ and $\Theta= [-1/2,1/2]$.
@@
 \end{tikzpicture}
-\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma$ for $f(x)$ the standard normal density with variance $\sigma^2$ and $\Theta = [-1/2,1/2]$.
-The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$ of \eqref{eq:uniform_risk}.}.
+\caption{\label{fig:minimax_ARE} 
+Minimax relative efficiency under distributed encoding.
+ARE versus $\sigma$ for $f(x)$ the standard normal density with variance $\sigma^2$ and $\Theta = [-1/2,1/2]$.
+The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$ of \eqref{eq:uniform_risk}.
+\newtext{
+The line $\pi/2$ is the optimal relative efficiency, attained under adaptive encoding for any $\sigma$ uniformly over the parameter space.}}
 \end{center}

### 2021-09-29 proof-lan-distributed.tex
fixed all minor comments from R1
fixed all comments after first revision, sending to John

@@
   \label{lemma:derivative-bounds}
-  Let
-  Assumption~\ref{assumption:detection-regions}\eqref{item:lipschitz-density}
-%  and \eqref{item:finite-intervals} 
- hold. Then for any $A = \cup_{i = 1}^k
-  \{[a_i, b_i]\}$ and $h \in \R$,
-  \begin{equation*}
+  Let Assumption~\ref{assumption:detection-regions}\eqref{item:lipschitz-density} hold. Then for any $A = \cup_{i = 1}^k
+  [a_i, b_i]$ and $h \in \R$,
+  \begin{align}
     \left|P_{\theta + h}(A) - P_\theta(A) - \dPtheta(A) h \right| \leq 
     k \cdot \lip(f) h^2,
-  \end{equation*}
+    \label{eqn:expansion-dPtheta}
+  \end{align}
   where
-  \begin{equation}
+  \begin{align*}
     \dPtheta(A) = \sum_{i = 1}^k f(a_i - \theta) - f(b_i - \theta).
-    \label{eqn:expansion-dPtheta}
-  \end{equation}
+  \end{align*}
   Additionally, we have the bounds
-  \begin{equation}
+  \begin{align}
     \label{eqn:bound-density-diffs}
@@
     |\dPtheta(A)| \le 2 \sqrt{k \lip(f)}.
-  \end{equation}
+  \end{align}
 \end{lemma}
@@
 \end{align*}
-so that $\sqrt{f(a)^2 + f(b)^2} \le \sqrt{2 \lip(f) P([a, b])}$.  In sum,
-we have demonstrated that always the first
+so that 
+\begin{align*}
+\newtext{\frac{f(a) + f(b)}{\sqrt{2}} \le} \sqrt{f(a)^2 + f(b)^2} \le \sqrt{2 \lip(f) P([a, b])},
+\end{align*}
+\newtext{where the left inequality follows from concavity of $\sqrt{\cdot}$.} In sum, we have demonstrated that always the first
 bound~\eqref{eqn:bound-density-diffs} holds.
@@
   \sqrt{a} + \frac{b}{2 \sqrt{a}} -
-  \frac{b^2}{4\sqrt{a}}
+  \frac{b^2}{4a^{\newtext{3/2}}}
   \le \sqrt{a + b} \le \sqrt{a}
@@
 recalling that $\score_\theta(A) = \dPtheta(A) / P_\theta(A)$,
-for any $h \in \R$ and $A = \cup_{i = 1}^k \{[t_i^-, t_i^+]\}$ the
+for any $h \in \R$ and $A = \cup_{i = 1}^k [t_i^-, t_i^+]$ the
 union of $k$ intervals, the expansion~\eqref{eqn:expansion-dPtheta} yields

### 2021-09-29 proof-sgd.tex
fixed all comments after first revision, sending to John

@@
 case of the stochastic gradient procedures in the papers
-\cite{PolyakJu92, polyak1990new}.
+\cite{polyak1992acceleration, polyak1990new}.
 We rely on several of their results. Throughout this proof,
@@
 \cite[Thm. 4]{polyak1992acceleration}:
-\begin{corollary}{\cite[Thms. 3 \& 4]{PolyakJu92}}
+\begin{corollary}{\cite[Thms. 3 \& 4]{polyak1992acceleration}}
   \label{corollary:polyak-juditsky}
-  Let $\varphi : \R \to \R$ and $\{Z_i\}$ be i.i.d.\ random
+  Let $\varphi : \R \to \R$ and $\{Z_i\}$ be i.i.d.\ \newtext{zero-mean} random
   variables, and
@@
     at 0 with $\psi'(0) > 0$ and there exists
-    $K_2$ and $0 < \lambda \leq 1$ such that
+    $K_2$, $0 < \lambda \leq 1$, \newtext{and $r>0$}, such that
     \begin{equation}
@@
     \end{equation}
-    \newtext{for all $|x|<r$ for some $r>0$ small enough. }
+    \newtext{for all $|x|<r$. }
   \item The function 
@@
 By the assumption in Theorem~\ref{thm:sgd} that the density $f$
-is Lipschitz continuous, \newtext{$\sqrt{f}$ is Lipschitz continuous hence absolutely continuous}. We see that the location family
+is Lipschitz continuous, \newtext{$f$ is absolutely continuous hence 
+$\sqrt{f}$ is absolutely continuous}. We see that the location family
 $\{P_\theta\}_{\theta \in \R}$ defined by $dP_\theta(x) = f(x - \theta)$
@@
   \label{lemma:sgd-median-regular}
-  Let $h_n \to h \in \R$, and define $P_n = P_{\theta + h_n / \sqrt{n}}^n$.
+  Let $h_n \to h \in \R$, and define $P_{n,h} = P_{\theta + h_n / \sqrt{n}}^n$.
   Then 
@@
     \sqrt{n}\left( \bar{\theta}_n - \theta \right)
-    \mathop{\cd}_{P_n}
+    \mathop{\cd}_{P_{n,h}}
     \normal\left( h,\frac{1}{4 f(0)^2}\right).
@@
 \newtext{
-From here, existence of the second moment of $\pi$ implies \eqref{eq:thm:sgd_3}. }
+From here, existence of the second moment of $\pi$ implies \eqref{eq:adaptive_3}.}
 %Theorem~\ref{thm:sgd}\eqref{item:sgd-ms-convergence}.}
@@
 The proof of part~\eqref{item:regularity} requires two additional lemmas of
-Polyak and Juditsky~\cite{PolyakJu92}.
-\begin{lem}[\cite{PolyakJu92}, Lemma 2]
+Polyak and Juditsky~\cite{polyak1992acceleration}.
+\begin{lem}[\cite{polyak1992acceleration}, Lemma 2]
   \label{lemma:polyak-expansion}
@@
 
-\begin{lem}[\cite{PolyakJu92}]
+\begin{lem}[\cite{polyak1992acceleration}]
   \label{lemma:converging-power-sum}
@@
 We separate the proof of part~\eqref{item:regularity} into two lemmas, which
-mirror the proofs of Polyak and Juditsky~\cite{PolyakJu92}; together they
+mirror the proofs of Polyak and Juditsky~\cite{polyak1992acceleration}; together they
 immediately give the result.
@@
     + Z)]$ and that $\psi(0) = 0$.  We now control the expectations of these
-  quantities. For $R < \infty$, define the stopping time $\tau_R \defeq \inf
+  quantities. 
+  \newtext{
+  As in the proof of Theorems~2 and~4 in \cite{polyak1992acceleration}, the Robbins-Siegmund Theorem \cite{robbins1971convergence} applies to the increment of $|\Delta_t|^2$ implies that for every 
+  $\epsilon>0$ there exists some $R>0$ such that
+  \begin{align}
+  \label{eq:sup_delta}
+  \Prob\left(\sup_i |\Delta_i| \le R \right) \ge 1-\epsilon.
+  \end{align} 
+  Define the the stopping time $\tau_R \defeq \inf
   \{i : |\Delta_i| > R\}$, which satisfies $\{\tau_R \le i\} \in \mc{F}_i$
-  for each $i$.  Then using~\cite[Eq.~(A14)]{PolyakJu92}, we have
+  for each $i$. 
+  }
+  Then using~\cite[Eq.~(A14)]{polyak1992acceleration}, we have
   \begin{equation*}
@@
   \end{equation*}
-  by Condition~\eqref{eqn:lazy-gamma}.
-\newtext{As Lemma~\ref{lemma:converging-power-sum} implies in particular that $\{\Delta_i\}$ is a.s.
+  by Condition~\eqref{eqn:lazy-gamma}. Since
+  \begin{align*}
+\left\{ \sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}} < \infty \subset \left\{ \sup_i |\Delta_i| \leq R \right\} \cap \left\{ \sum_{i=0}^\infty  \right\}
+ \right\},
+  \end{align*}
+  \newtext{it follows from \eqref{eq:sup_delta} and by the arbitrary choice of $\epsilon$ that}
+  %\newtext{As it follows from \cite[Eq.~(A11)]{polyak1992acceleration} that $\Prob\left( \sup |\Delta_t| < \infty  \right)=1$}, we obtain
+  %\newtext{As Lemma~\ref{lemma:converging-power-sum} implies in particular that $\{\Delta_i\}$ is a.s.
 bounded, with probability 1 there exists some (random) $R < \infty$ such that $\tau_R = \infty$.} We obtain that

### 2021-09-29 uniform-are-weirdos.tex
fixed all comments after first revision, sending to John

--- 2019-12-13 uniform-are-weirdos.tex
@@
   \sup_{|\theta| \le \log n}
-  P_\theta\left(|\theta_n - \theta| \ge \frac{8 \log n}{n^{3/4}}\right)
+  P_\theta\left(|\theta_n - \theta| \ge \frac{\newtext{16} \log n}{n^{3/4}}\right)
   \le \frac{2}{n^2}.
@@
 and so (by the Borel-Cantelli lemmas), for any $\theta \in \R$ we have
-$P_\theta(|\theta_n - \theta| \le \sqrt{2 \log n} / n^{3/4} ~
+$P_\theta(|\theta_n - \theta| \le \newtext{16 \log n} / n^{3/4} ~
 \mbox{eventually}) = 1$. This is of course faster than the $1/\sqrt{n}$
@@
 \end{equation*}
-Then we simply set $\theta_n\init$ to be the maximal threshold for which
+Then we simply set $\theta_n\init$ to be the \newtext{minimal} threshold for which
 $B_i = 0$ for all observations $X_i$ corresponding to that threshold.
@@
 - \frac{2 n \epsilon}{m}$, because no observations will be below
-the appropriate threshold. Let $j\opt$ be the smallest index $j$
-for which $\theta \le t_{j\opt}$, and consider
+the appropriate threshold. Let $j\opt$ be the \newtext{largest} index $j$
+for which $\theta \newtext{\ge} t_{j\opt}$, and consider
 the index sets $I_{j\opt}$, $I_{j\opt + 1}$, and so on.
@@
 $I_{j\opt + 1}$, we have $U_i \ge \frac{n \epsilon}{m}$. Thus,
-\begin{equation*}
+\begin{align*}
+  P_\theta\left(\theta_n\init \ge \theta + \frac{2 n \epsilon}{m}
+  \right) \le
   P_\theta\left(\theta_n\init \ge t_{j\opt} + \frac{2 n \epsilon}{m}
@@
   \le \exp\left(-\frac{n^2\epsilon}{m^2}\right).
-\end{equation*}
+\end{align*}
 Setting the number of bins $m = \sqrt{n}$,
@@
 \le n^{-2}$. Thus we have
-\begin{equation}
+\begin{align}
   \label{eqn:quality-of-initial-estimate}
@@
   \frac{8 \log n}{\sqrt{n}}\right) \le \frac{1}{n^2}.
-\end{equation}
+\end{align}
 
@@
 for $i \in I_j$, set $B_i = 1$ if $X_i \ge t_j$. We define $\theta_n$ to be
-the maximal threshold $t_j$ for which $B_i = 0$ for all observations $X_i
+the \newtext{minimal} threshold $t_j$ for which $B_i = 0$ for all observations $X_i
 \in I_j$. Then following precisely the reasoning above, we have (on the

### 2021-09-30 response.tex
Commented on O(1/n) in Prop. 1

\documentclass[journal, 12pt]{article}
\usepackage{fullpage}
\onecolumn
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage[cmex10]{amsmath}
\usepackage[font=itshape]{quoting}
\usepackage{url}

\usepackage{macros}

\newcommand{\redit}[1]{\textcolor{red}{#1}}
\newcommand{\bitem}{\begin{itemize}}
\newcommand{\eitem}{\end{itemize}}

\newenvironment{response}
{\color{blue}   
\vspace{2ex}
}

\newenvironment{review}
    {
%    \it
    \vspace{2ex}
    }

\title{Response to review IT-21-0014: Mean estimation from one-bit measurements
}

\author{Alon Kipnis and John Duchi}

\date{\today}

\begin{document}

\maketitle

\begin{response}
%Dear Associate Editor Tyagi,\\

We thank the Associate Editor (AE) and the referees for their thoughtful and thorough review, which we have found very helpful and prompted quite a few improvements. \\

Below we provide a detailed response to the reviewers' comments. The original comments of the reviewers are in {\color{black}black} while our response is in {\color{blue}blue}. In the manuscript, we also indicate in blue significant changes from the previous version. \\

\end{response}

\subsection*{Summary of the Review by AE Tyagi}
The first reviewer has asked further clarification about the proofs. I, too, think that more details about the proof are needed. The second reviewer has raised questions concerning extensions to more general settings, perhaps requiring further elaboration on the limitation of the approach. Since both reviewers have requested revision, I think it is important that the authors address their concerns in a rebuttal and provide the required details.

\begin{response}
Thank you for handling the paper and for obtaining two excellent reviews. We addressed all reviewers' comments as explained below, with particular attention to the proofs and the extension to more general settings. 
\end{response}

\subsection*{Response to comments by Reviewer 1}
\begin{review}
(1) My main concern is with Theorem 3(ii) -- if I understand correctly, the proof given does not quite prove the statement. In particular, the statement says that the limiting distribution is normal with mean 0, whereas the proof (Lemma 14) says that it is normal with mean h. If the mean indeed depends on h, then the estimator is not regular (Definition 1) and so the statement about the estimator attaining local asymptotic minimaxity in Theorem 3(ii) becomes dubious.
\end{review}

\begin{response}
We greatly appreciate the reviewer's overall through work and in particular for bringing the issue with the proof of Theorem 3 to our attention. As it turns out, one of the equations in the proof was incorrect because it indicated a location shift by $h$ in both sides of the equation instead of only in one side as per the definition of a regular estimator. As it turns out, an easy fix to this issue in our case is obtained by changing Lemma 14 to the following from.
\setcounter{thm}{13}
\begin{lemma} 
  Let $h_n \to h \in \R$, and define $P_{n,h} = P_{\theta + h_n / \sqrt{n}}^n$.
  Then 
  \begin{align}
    \sqrt{n}\left( \bar{\theta}_n - \theta \right)
    \mathop{\cd}_{P_{n,h}}
    \normal\left( h,\frac{1}{4 f(0)^2}\right).
  \end{align}
\end{lemma}
%The new notation is in accordance with \cite[Ch. 7]{van2000asymptotic}. 
\end{response}

\begin{review}
(2) I think there are problems with the example in Appendix VII that demonstrates fast convergence in the case of uniform distribution. The initial estimate $\theta^{init}$ is set to be the maximal threshold for which $B_i$ = 0 for all observations corresponding to that threshold. But the way $B_i$ is defined, wouldn't this maximal threshold always be the very last threshold in the interval $[-n \epsilon, n \epsilon]$? If, instead, we interchange the roles of $0$ and $1$ in the defining $B_i$, then we might be on to something. But then, what confuses me is the statement: ``we always have $\theta^{init} \geq \theta - (2n\epsilon)/m$''; which is not true (since $\theta$ is the median of the distribution, and not the left-end point). Ok, this can be salvaged by saying that $\theta^{init}$ is estimate of the left-end point (i.e. $\theta - 1$). But then again, the confusion arises in the next line: ``The event $\theta^{init} \geq t_j* + (2n\epsilon)/m$ may occur only if for each of the $n/m$ observations in the set $I_{j^\star+1}...$''. Why ``only if''? It may well be that we observe both $0$ and $1$ for observations in $I_{j^\star+1}$ and observe only $0$'s in $I_{j^\star+2}$; this would also make the event ``$\theta^{init} \geq t_j^\star + (2n\epsilon)/m$'' happen.
\end{review}

\begin{response}
We thank Reviewer 1 for pointing on the problems with this example. As it turns out, the original example were missing the important ingredient of comparing our communication-limited estimator to the maximum of the samples within a bin. We have carefully went through this example and revised to add the missing part and resolve all other issues.  
\end{response}

\begin{review}
\begin{enumerate}
\item  Section III A, page 8: Extra braces in the indicator function in the definition of $B_i$ and the line after that.
\begin{response}
Fixed. 
\end{response}

\item Section III B, page 9, equation (7): Why is it $O(1/n)$? In the proof (Appendix VII A), $D*$ has $o(1/n)$; so after multiplication by $n$, we get $o(1)$. Could you clarify what $o(1/n)$ is hiding that makes it $O(1/n)$ in (7) instead of merely $o(1)$?
\begin{response}
Thank you for this comment. It made us realized that there was a mistake in the proof and we should replace $o(1/n)$ with $O(n^{-2})$. The $O(n^{-2})$ term is the remainder in the first order taylor expansion of $D^\star$ in $1/n$. 
\end{response}

\item Section IV B, page 13, line 3: It says $B_i$ a.s. converges to $F(\theta_0 - \theta)$. Shouldn't it say $E[B_i] = F(\theta_0 - \theta)$?
\begin{response} It should. We fixed this issue. 
\end{response}

\item Section IV B, page 14, line just above title of section V: Should be "density" and not "desnity".
\begin{response} Fixed.
\end{response}

\item Section V, page 14, line below the definition of $P_{\theta}(A)$: Extra braces around $[t_i^-,t_i^+]$ not required.
\begin{response} We agree. We removed the extra braces.
\end{response}

\item Section V, page 15, Assumption A2(ii): The subscript in $A_n$ and $k_n$ should be "$i$" and not "$n$".
\begin{response} Fixed.
\end{response}

\item Section V A, page 17, line 3: In "...ML estimator attains the local asymptotic MSE of Theorem 2", it should be "Theorem 6" instead of "Theorem 2".
\begin{response} Fixed.
\end{response}

\item Section V B, page 17, second line in the subsection: In "...density of the threshold values that maximizes the worst-case information $\inf_\theta \kappa(\theta) = \kappa_\lambda(\theta)$...", it seems to say that "$\inf_\theta \kappa(\theta) = \kappa_\lambda(\theta)$", whereas I think what the authors mean is "$\kappa(\theta) = \kappa_\lambda(\theta)$". Better phrasing required.
\end{enumerate}

\begin{response}
We thank the reviewer for bringing it to our attention that the here notation is unclear. We rewritten the relevant part as follows. 
\begin{quote}
    We conclude this section by considering the \newtext{distribution} of the threshold values
that maximizes the worst-case information $\inf_\theta \kappa(\theta)
= \kappa_\lambda(\theta)$ where $\kappa_\lambda(\theta)
= \int \eta(t - \theta) \lambda(dt)$.
The \newtext{optimal distribution $\lambda^\star$} solves the
optimization problem
\begin{align*}
  \begin{split}
    \mathrm{maximize} \quad &  \inf_{\theta \in \Theta} \int \eta(t-\theta) \lambda(dt)
    \\ 
    \mathrm{subject~to} 
    \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
  \end{split}
\end{align*}
\end{quote}
\end{response}

\begin{enumerate}
    \item Appendix VII, page 20, line after equation (19): Instead of $\sqrt{2 \log n}$, should it be $(8 \log n)$?
\begin{response}
Yes. Thank you for catching this. 
\end{response}

\item Appendix VIII, page 22, second line of Lemma 10: Should say "Assumption A1" instead of "Assumption 1".
\begin{response}
Fixed.  
\end{response}

\item Appendix VIII, page 23, proof of Lemma 10, line after equation defining A: It says "$t_1^+ \leq t_k^+ \leq \infty$", which is technically true, but it might be better to insert ellipsis and write "$t_1^+ \leq ... \leq t_k^+ \leq \infty$".

\begin{response}
We agree and fixed this according to the Reviewer's suggestion. 
\end{response}

\item Appendix VIII, page 23, equation (25): Should be inequality "$\leq$" instead of "$=$".
\begin{response}
Fixed. 
\end{response}

\item Appendix VIII, page 24: Line 1 and the corresponding block of equation seem superfluous. I think the whole thing ought to be removed.

\begin{response}
We agree. We removed this part.
\end{response}

\item Appendix VIII A, page 25, equation (29): First term in the denominator should have $x*$ and not $x*_i$.

\begin{response}
Fixed. 
\end{response}

\item Appendix VIII A, page 25, definition of $A_N(x*,k)$: Insert ellipsis and write "$y_1 \geq ... \geq y_k$" instead of just "$y_1 \geq y_k$".
\begin{response}
Fixed. 
\end{response}

\item Appendix IX A, page 28, Corollary 12: Does it not require $Z_i$ to be a mean 0 random variable? Reference [48] has that assumption, but Corollary 12 does not mention it.

\begin{response}
We thank the reviewer for pointing on this issue. We added the assumption that the $\{Z_i\}$ are zero-mean. 
\end{response}

\item Appendix IX A, page 29, Corollary 12: In condition (iii), it seems equation (33) needs to hold only in a small neighborhood of 0, but it doesn't mention that.

\begin{response}
The reviewer is correct here. We changed Condition (iii) in Corollary 12 as follows.

\begin{quote}
    The function $\psi(x) \defeq \ex{ \varphi(x+Z_1)}$
    satisfies $\psi(0) = 0$ and
    $x\psi(x) > 0$ for $x\neq 0$. Moreover, $\psi$ is differentiable
    at 0 with $\psi'(0) > 0$ and there exists
    $K_2$, $0 < \lambda \leq 1$, \newtext{and $r>0$}, such that
    \begin{equation}
      \label{eqn:local-hessian-psi}
        \left| \psi(x) - \psi'(0)x \right|\leq K_2 |x|^{1+\lambda}
    \end{equation}
    \newtext{for all $|x|<r$. }
\end{quote}
\end{response}

\item Appendix IX A, page 29, Corollary 12, line after condition (iv): It says "...for b n V = ...". What is "b n" here?

\begin{response}
``b n" was redundant here. We removed it. 
\end{response}

\item Appendix IX B, page 30, Definition 3: In the LHS of the equation, the summation is over "i", but there is no "i" in the summand. I think it should be "$(X_i)$" instead of "$(X_1,...,X_n)$".
\begin{response}
We agree and have fixed this issue.
\end{response}

\item Appendix IX B, page 30, after Lemma 13: When stating that the location family satisfies conditions of Lemma 12, it might be useful to state that square root of a Lipschitz function is absolutely continuous (I think?).

\begin{response}
We thank the reviewer for this suggestion. We changed the statement as follows:
\begin{quote}
    By the assumption in Theorem~3 that the density $f$
is Lipschitz continuous,  \newtext{$f$ is absolutely continuous hence 
$\sqrt{f}$ is absolutely continuous}.
\end{quote}
\end{response}

\item Appendix IX B, page 31, line after equation (37): the quantity "delta-bar" should have subscript "n" instead of "i".
\begin{response}
Fixed.
\end{response}

\item Appendix IX B, page 31, Corollary 15, condition (ii): In the definition of the Fisher information $I_h$, the expectation should have subscript "h" instead of "theta".
\begin{response}
Fixed.
\end{response}

\item Appendix IX C, page 32, last line of Appendix IX C: Could you clarify what you mean by "a finite approximation to the prior measure $\pi$"?

\begin{response}
We revised this part in a way that we no longer rely on a finite approximation to the prior measure $\pi$. Instead, prove the result for a fixed $\theta$ and rely on an additional requirement saying that the second moment of $\pi$ exists.
\end{response}

\item Appendix IX D, page 32, first line of Lemma 17: For the quantity "delta" the superscript on the LHS is "1" (which is correct), but on the RHS, the first term has superscript "i" (should be "1") and the second term has no superscript (should have superscript "1").
\begin{response}
We fixed this issue by changing the two terms on the RHS to match the LHS. 
\end{response}

\item Appendix IX D, page 34, proof of Lemma 20: It says "As with probability 1 there exists some (random) R...". Why "(random)"?

\begin{response}
This comment made us realized that this part of the proof was somewhat unclear. We revised this part so that we do not use a random $R$. The revised part is as follows. 
\begin{quote}
\newtext{
\setcounter{equation}{45}
  As in the proof of Theorems~2 and~4 in \cite{polyak1992acceleration}, the Robbins-Siegmund Theorem applies to the increment of $|\Delta_t|^2$ implies that for every 
  $\epsilon>0$ there exists some $R>0$ such that
  \begin{align}
  \label{eq:sup_delta}
  \Prob\left(\sup_i |\Delta_i| \le R \right) \ge 1-\epsilon.
  \end{align} 
  Define the the stopping time $\tau_R \defeq \inf
  \{i : |\Delta_i| > R\}$, which satisfies $\{\tau_R \le i\} \in \mc{F}_i$
  for each $i$. 
  }
  Then using~\cite[Eq.~(A14)]{polyak1992acceleration}, we have
  \begin{equation*}
    \E[\Delta_i^2 \indic{\tau_R > i}] \le K \gamma_i,
  \end{equation*}
  and so inequality~(45) gives that
  \begin{equation*}
    \E\bigg[\sum_{i = 1}^\infty \frac{1}{i}
      |\varepsilon_i|^2 \indic{\tau_R > i} \bigg]
    \le K \sum_{i = 1}^\infty \frac{\gamma_i^\lambda}{i}
    < \infty
    ~~ \mbox{so} ~~
    \sum_{i = 1}^\infty \frac{1}{i}
    \varepsilon_i^2 \indic{\tau_R > i} < \infty
    ~ \mbox{a.s.}
  \end{equation*}
  \newtext{it follows from \eqref{eq:sup_delta} and by the arbitrary choice of $\epsilon$ that}
  \begin{equation*}
    \sum_{i = 1}^\infty \frac{1}{i}
    \varepsilon_i^2  < \infty
    ~ \mbox{a.s.}.
  \end{equation*}
\end{quote}
\end{response}

\item Appendix IX E, page 35: Insert "by" in the statement "and so Jensen's inequality...".
\begin{response}
Done. 
\end{response}

\item Appendix IX E, page 36, line 1: Insert "of" in the statement "...the variant dominated convergence theorem...".
\begin{response}
Done. 
\end{response}

\item Appendix X, page 36, first line of Lemma 21: Remove extra braces in the definition of A (i.e., it should just be "$[a_i,b_i]$", instead of "$\{[a_i,b_i]\}$".
\begin{response}
Done. 
\end{response}

\item Appendix X B, page 38: In the first equation,  the lower bound on $\sqrt{a+b}$ seems wrong. E.g., for $a = 1/4, b = 1/8$, the LHS is bigger than $\sqrt{a+b}$.

\begin{response}
Thank you for catching this! The power of $a$ in the denominator of the third term on the LHS
should be $3/2$ rather than $1/2$. The correct inequality is:
\begin{quote}
\begin{align*}
  \sqrt{a} + \frac{b}{2 \sqrt{a}} -
  \frac{b^2}{4a^{\newtext{3/2}}}
  \le \sqrt{a + b} \le \sqrt{a}
  + \frac{b}{2 \sqrt{a}}
\end{align*}
for any $a > 0$ and $|b| \le 3a/4$.
\end{quote}
We verified that the proof is now correct. 
\end{response}

\item Appendix XI, page 41, line 1: In the definition of $A_i$, the union should be over the index "k" (and not "i").
\begin{response}
Fixed.
\end{response}

\item Appendix XI, page 41, line 1: There should be a "$\leq$" sign (instead of a comma) between $t_{i,K}^-$ and $t_{i,K}^+$.
\begin{response}
Fixed.
\end{response}

\item Appendix XI, page 41, 4th line from the end: It should be "$\theta \in \Xi$" (instead of "$\theta \in \Theta$").
\begin{response}
Fixed.
\end{response}

\item Appendix XI, page 41, 4th line from the end: It should be "card$(S_n(\theta,\epsilon)) \to n$" (instead of "$S_n(\theta,\epsilon) \to 1$").
\begin{response}
Fixed.
\end{response}

\item References, page 44: [48] and [53] are exactly the same reference.
\end{enumerate}

\begin{response}
We removed one of the references.
\end{response}

\end{review}

\subsection*{Response to comments by Reviewer 2}
%My main comments are below.
\begin{itemize}
    \item For the lower bound on non-adaptive estimators, is it possible to characterize the worst-case gap between the efficiency of a non- adaptive estimator and the best rate for an adaptive estimator (possibly in terms of the diameter of the parameter space or variance of the density)? This will give a more quantitative view of the separation between adaptive and non-adaptive estimators.

    \begin{response}
    We thank the Reviewer for raising this interesting point. We should first clarify that our results in the distributed encoding setting provides the asymptotic relative efficiency only when the estimator is based on thresholds detectors, in which case this efficiency depends on the density of the thresholds. 
    Under this setting, it appears to us that Fig. 6 provides a characterization of the efficiency gap similarly to the one proposed by the reviewer, at least in the special case in which the samples are normally distributed and the threshold density is either uniform or obtained as the solution of the optimization problem (17).

    The Reviewer's comment made us realize that we initially did not explain well that our results in Section V-C yields the exact efficiency gap under distributed threshold encoding. To improve this point, we added the following sentence to the caption of Fig. 6. 
    \begin{quote}
The line $\pi/2$ is the optimal relative efficiency, attained under adaptive encoding for any $\sigma$ uniformly over the parameter space.
    \end{quote}

    \end{response}
\item The setting of one-dimensional distribution and one-bit messages is a bit limited. How does the technique of the paper generalize to higher dimensions or higher communication budget (more bits from each user)? The result will be stronger if more general results can be provided.

\begin{response}
We agree that the extension of the setting of the paper to higher dimensions is an excellent point for discussion and probably for a future work. We thank the reviewer for proposing it.

Arguably, there are several ways to generalize our setting to higher dimension and higher communication budgets. Many of these generalizations falls under the settings discussed in 
\cite{zhang2013information,shamir2014fundamental,braverman2016communication,han2018geometric,barnes2020lower}, although these references do not yield the asymptotic relative efficiency (ARE) but only characterization of the way the error scales in the communication bit-budget and the dimension. It is still unclear whether we can extend our methods to derive the ARE for any dimension and bit budget, but anyway such extension is not straightforward. Consequently, we decided to leave this extension as a future work. 
%characterizing the way the error scales with the number of bits and the dimension and not on the exact asymptotic efficiency. 
%
%Indeed, it seems challenging to derive the exact efficiency in higher dimensions and communication bit budgets. To illustrates a possible source for this challenge, consider a known symmetric base distribution $F$ over $\reals^k$ and the problem of estimating the shift $\theta \in \reals^k$ of a sequence of samples from the shifted $F$ with $b$ bits per round of communication. The following estimation and quantization scheme is proposed to outperform a naive tenderized scheme: construct a $b$-bit optimal vector quantizer matching to $F$. Namely, dissect $\reals^k$ into $b$ regions in a way that the MSE obtained between a sample from $F$ and the center of mass of $F$ over the region where the sample falls is minimal across all possible dissections. The Lloyd algorithms provides an iterative method of approximating such optimal quantizer. The estimation-encoding scheme is as follows: Given an estimate $\theta_{i-1}$, and an expected error $\sigma_{i-1}$, and a new observation $X_i \in \reals^k$, send the index of the region in $\reals^k$ where $X_i/\sigma_{i-1}$ falls. The estimation $\theta_i$ is the center of mass of this region. This method is expected to...
Consequently, we added the following paragraph to the Conclusions: 
\begin{quote}
    Natural extensions of the setting of this work are situations when the communication bit-budget $b$ is larger than one and when each sample is a $d$-dimensional vector. Fundamental bounds for this general case follows from several recent works (e.g. \cite{zhang2013information,shamir2014fundamental,braverman2016communication,han2018geometric,barnes2020lower}), which imply that in the adaptive and distributed cases the MSE scales in the regular parametric rate of $1/n$ when $b$ and $d$ are held fixed in the sample size $n$. Nevertheless, the coefficient of the $1/n$ term corresponding to the ARE is still unknown; deriving the ARE for general $b$ and $d$ is left as a future challenge.
\end{quote}

\end{response}

\item First line of page 4: asyptotic --> asymptotic.

\begin{response}
Thank you. We have fixed this typo. 
\end{response}
\item Beginning of Section III.A: The indicator function is not properly displayed.

\begin{response}
Thank you. We resolved this issue. 
\end{response}
\end{itemize}

\iffalse
\subsection*{Draft}

\begin{response}
We thank the Reviewer for raising this excellent point for discussion...

We thank the Reviewer for this question.

Thanks for your query, which gives us a chance to clarify our views of the situation.

We agree that the optimality of the phase diagram of Higher Criticism we derive in our paper is an excellent point for discussion and wish to thank the reviewer for bringing it.

it appears that the Reviewer proposes a very interesting non-parametric test for homogeneity.

We are grateful for the Reviewer for pointing on this vagueness in our setting and the connection between our setting and the multinomial setting. The Reviewer is correct that

We thank the Reviewer for bringing it to our attention that this point requires clarification. 
We thank the reviewer for raising this interesting point regarding an information theoretic lower bound. 
%
This is an excellent question.

We apologize for our delay in publishing this proof.

Thank you for this comment.

We agree with the Reviewer that it is interesting in principle to consider simulations of other distributions aside from the uniform baseline. 
\end{response}
\fi

\bibliographystyle{plain}
\bibliography{onebit}

\end{document}

### 2021-09-30 conclusions.tex
Commented on O(1/n) in Prop. 1

@@
 Natural extensions of the setting of this work are situations when the communication bit-budget $b$ is larger than one and when each sample is a $d$-dimensional vector.
-Fundamental bounds for this general case follows from several recent works (e.g.
+Rough bounds in this general case follow from several recent works (e.g.
 \cite{zhang2013information,shamir2014fundamental,braverman2016communication,han2018geometric,barnes2020lower}), which imply that in the adaptive and distributed cases the MSE scales in the regular parametric rate of $1/n$ when $b$ and $d$ are held fixed in the sample size $n$.
-Nevertheless, the coefficient of the $1/n$ term corresponding to the ARE is still unknown; deriving the ARE for general $b$ and $d$ is left as a future challenge.}
+Nevertheless, the coefficients of the $1/n$ term corresponding to the ARE are in general unknown; deriving the ARE for general $b$ and $d$ is left as a future challenge.}

### 2021-09-30 proof-adaptive-optimality.tex
Commented on O(1/n) in Prop. 1

@@
   equality~\eqref{eq:gradient_zero} holds if and only if $y_1 = \ldots
-  = y_N$. In this case, $g(y_1,\ldots,y_N) = \eta_\delta(x_{i^*})$ if $N$ is
+  = y_N$. In this case, $g(y_1,\ldots,y_N) = \eta_\delta(x^*)$ if $N$ is
   even. If $N$ is odd and $y_1 = \ldots = y_N > x^*$, then
   \begin{align*}
-    & g(y_1,\ldots,y_N) = \frac{\left| f(y_1)-f(x_{i^*})  \right|^{2+\delta}} { 
-      \left|  F(y_1) - F(x_{i^*}) \right|^{1+ \delta} 
-      \left| 1 - (F(y_1) -F(x_{i^*})) \right|^{1+ \delta} } 
+    & g(y_1,\ldots,y_N) = \frac{\left| f(y_1)-f(x^*)  \right|^{2+\delta}} { 
+      \left|  F(y_1) - F(x^*) \right|^{1+ \delta} 
+      \left| 1 - (F(y_1) -F(x^*)) \right|^{1+ \delta} } 
   \end{align*} 
-  which is bounded from above by $\eta_\delta(x_{i^*})$ by the induction hypothesis. The case where $N$ is odd and $-x^* \leq y_1 = \ldots = y_N$ is similar. 
+  which is bounded from above by $\eta_\delta(x^*)$ by the induction hypothesis. The case where $N$ is odd and $-x^* \leq y_1 = \ldots = y_N$ is similar. 
   %
@@
   \item[(ii)] $y_1 = \infty$.
-  \item[(iii)] $y_k = x_{i^*}$.
-  \item[(iv)] $y_{k+1} = -x_{i^*}$. 
+  \item[(iii)] $y_k = x^*$.
+  \item[(iv)] $y_{k+1} = -x^*$. 
   \end{itemize}
@@
   \begin{align*}
-    g(y_1,\ldots,y_N) \to \frac{ \left| \sum_{i=1}^{k} s_i f(y_i) + s_{i^*} f(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i f(y_i) \right|^{2+\delta}} 
-    {\left| \sum_{i=1}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i F(y_i) \right|^{1+\delta}\left|1- \left( \sum_{i=1}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i F(y_i) \right)  \right|^{1+\delta} },
+    g(y_1,\ldots,y_N) \to \frac{ \left| \sum_{i=1}^{k} s_i f(y_i) + s_{i^*} f(x^*) - \sum_{i=k+1}^{N-1} s_i f(y_i) \right|^{2+\delta}} 
+    {\left| \sum_{i=1}^{k} s_i F(y_i) + s_{i^*} F(x^*) - \sum_{i=k+1}^{N-1} s_i F(y_i) \right|^{1+\delta}\left|1- \left( \sum_{i=1}^{k} s_i F(y_i) + s_{i^*} F(x^*) - \sum_{i=k+1}^{N-1} s_i F(y_i) \right)  \right|^{1+\delta} },
   \end{align*}
-  which is smaller than $\eta_\delta(x_{i^*})$ by the induction hypothesis. Similarly, under case (ii),
+  which is smaller than $\eta_\delta(x^*)$ by the induction hypothesis. Similarly, under case (ii),
   \begin{align*}
     & g(y_1,\ldots,y_N) \to 
-    \frac{ \left| \sum_{i=2}^{k} s_i f(y_i) + s_{i^*} f(x_{i^*}) - \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
-         {\left| 1+ \sum_{i=2}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta}\left|-\left( \sum_{i=2}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N} s_i F(y_i) \right)  \right|^{1+\delta} },
+    \frac{ \left| \sum_{i=2}^{k} s_i f(y_i) + s_{i^*} f(x^*) - \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
+         {\left| 1+ \sum_{i=2}^{k} s_i F(y_i) + s_{i^*} F(x^*) - \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta}\left|-\left( \sum_{i=2}^{k} s_i F(y_i) + s_{i^*} F(x^*) - \sum_{i=k+1}^{N} s_i F(y_i) \right)  \right|^{1+\delta} },
          \\
-         & = \frac{ \left| -\sum_{i=2}^{k} s_i f(y_i) - s_{i^*} f(x_{i^*}) + \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
-           { \left|1 - \left(-\sum_{i=2}^{k} s_i F(y_i) - s_{i^*} F(x_{i^*}) + \sum_{i=k+1}^{N} s_i F(y_i) \right) \right|^{1+\delta} 
-             \left|-\sum_{i=2}^{k} s_i F(y_i) - s_{i^*} F(x_{i^*}) + \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta} }
+         & = \frac{ \left| -\sum_{i=2}^{k} s_i f(y_i) - s_{i^*} f(x^*) + \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
+           { \left|1 - \left(-\sum_{i=2}^{k} s_i F(y_i) - s_{i^*} F(x^*) + \sum_{i=k+1}^{N} s_i F(y_i) \right) \right|^{1+\delta} 
+             \left|-\sum_{i=2}^{k} s_i F(y_i) - s_{i^*} F(x^*) + \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta} }
   \end{align*}
-  which is smaller than $\eta_{\delta}(x_{i^*})$ by the induction hypothesis.
-Under case (iii), the terms in $\delta_N$ and $\Delta_N$ corresponding to $y_k$ and $x_{i^*}$ cancel each other.
+  which is smaller than $\eta_{\delta}(x^*)$ by the induction hypothesis.
+Under case (iii), the terms in $\delta_N$ and $\Delta_N$ corresponding to $y_k$ and $x^*$ cancel each other.
 As a result,  $g(y_1,\ldots,y_N)$ reduces to an expression with $N-2$ variables hence this case is handled by the induction hypothesis.

### 2021-09-30 uniform-are-weirdos.tex
Commented on O(1/n) in Prop. 1

@@
   B_i = \begin{cases}
-    1 & \mbox{if~} X_i \ge t_j \\
+    1 & \mbox{if~} X_i \newtext{- 1} \ge t_j \\
     0 & \mbox{otherwise}.
@@
 \end{equation*}
-Then we simply set $\theta_n\init$ to be the \newtext{minimal} threshold for which
-$B_i = 0$ for all observations $X_i$ corresponding to that threshold.
+Then we simply set $\theta\init_n$ to be the \newtext{minimal} threshold for which
+$B_i = 0$ for all observations $X_i$ corresponding to that threshold. \newtext{Denote by $j^*$ the index of the threshold corresponding to $\theta\init_n$.}
 
-Let us now consider the probability that $\theta_n\init$ is substantially
-wrong. For notational simplicity, let $U_i = (1 + X_i - \theta) / 2$, so that
-the $U_i$ are uniform on $[0, 1]$.
-First, note that we always have $\theta_n\init \ge \theta
-- \frac{2 n \epsilon}{m}$, because no observations will be below
-the appropriate threshold. Let $j\opt$ be the \newtext{largest} index $j$
-for which $\theta \newtext{\ge} t_{j\opt}$, and consider
-the index sets $I_{j\opt}$, $I_{j\opt + 1}$, and so on.
-The event $\theta\init_n \ge t_{j\opt} + \frac{2 n \epsilon}{m}$ may
-occur only if for each of the $n/m$ observations in the set
-$I_{j\opt + 1}$, we have $U_i \ge \frac{n \epsilon}{m}$. Thus,
+\newtext{Let us now consider the probability that $\theta_n\init$ is substantially wrong.
+Set $\theta_M \equiv \max_{i \in I_j^*} X_i - 1$.
+Note that we always have $\theta\init_n \ge \theta_M$ because no observations will be above
+$t_j^*+1$, and that $\theta\init_n \le \theta_M + 2n\epsilon/m$. 
+ In addition, 
 \begin{align*}
-  P_\theta\left(\theta_n\init \ge \theta + \frac{2 n \epsilon}{m}
-  \right) \le
-  P_\theta\left(\theta_n\init \ge t_{j\opt} + \frac{2 n \epsilon}{m}
-  \right)
-  \le \left(1 - \frac{n \epsilon}{m}\right)^\frac{n}{m}
-  \le \exp\left(-\frac{n^2\epsilon}{m^2}\right).
+P_\theta\left( \left| \theta_M - \theta \right| \ge \frac{2n\epsilon}{m} \right) = \left(1 - \frac{2 n \epsilon}{m} \right)^{n/m}.
 \end{align*}
-Setting the number of bins $m = \sqrt{n}$,
-the resolution $\epsilon = 2 \log n / n$, we obtain
-$P_\theta(\theta_n\init \ge t_{j\opt} + 4 \log n / \sqrt{n})
-\le n^{-2}$. Thus we have
+Putting it all together using the triangle inequality, we have
+\begin{align*}
+  P_\theta\left( \left| \theta\init_n - \theta \right| \ge \frac{4n\epsilon}{m} \right) \le \left(1 - \frac{2 n \epsilon}{m} \right)^{n/m} \le e^{-2 \frac{n^2}{m^2} \epsilon}
+  .
+\end{align*}
+%For notational simplicity, let $U_i = (1 + X_i - \theta) / 2$, so that the $U_i$ are uniform on $[0, 1]$.
+First, note that we always have $\theta_n\init \ge \theta - \frac{2 n \epsilon}{m}$, because no observations will be below
+% the appropriate threshold. Let $j\opt$ be the \newtext{largest} index $j$
+% for which $\theta \newtext{\ge} t_{j\opt}$, and consider
+%the index sets $I_{j\opt}$, $I_{j\opt + 1}$, and so on.
+%The event $\theta\init_n \ge t_{j\opt} + \frac{2 n \epsilon}{m}$ may
+%occur only if for each of the $n/m$ observations in the set
+%$I_{j\opt + 1}$, we have $U_i \ge \frac{n \epsilon}{m}$. Thus,
+%\begin{align*}
+%  P_\theta\left(\theta_n\init \ge \theta + \frac{2 n \epsilon}{m}
+%  \right) \le
+%  P_\theta\left(\theta_n\init \ge t_{j\opt} + \frac{2 n \epsilon}{m}
+%  \right)
+%  \le \left(1 - \frac{n \epsilon}{m}\right)^\frac{n}{m}
+%  \le \exp\left(-\frac{n^2\epsilon}{m^2}\right).
+%\end{align*}
+Therefore, setting the number of bins $m = \sqrt{n}$ and
+the resolution $\epsilon = 2 \log n / n$, 
 \begin{align}
@@
   \sup_{|\theta| \le \log n} P_\theta\left(|\theta_n\init - \theta| \ge
-  \frac{8 \log n}{\sqrt{n}}\right) \le \frac{1}{n^2}.
+  \frac{8 \log n}{\sqrt{n}}\right) \le \frac{1}{n^4}.
 \end{align}
+}
+%$P_\theta(\theta_n\init \ge t_{j\opt} + 4 \log n / \sqrt{n})
+%\le n^{-2}$. Thus we have
+%\begin{align}
+%  \label{eqn:quality-of-initial-estimate}
+%  \sup_{|\theta| \le \log n} P_\theta\left(|\theta_n\init - \theta| \ge
+%  \frac{8 \log n}{\sqrt{n}}\right) \le \frac{1}{n^2}.
+%\end{align}
 
@@
 assign indices $I_j = \{\frac{n(j - 1)}{m} + 1, \ldots, \frac{n j}{m}\}$ and
-for $i \in I_j$, set $B_i = 1$ if $X_i \ge t_j$. We define $\theta_n$ to be
+for $i \in I_j$, set $B_i = 1$ if $X_i \newtext{- 1} \ge t_j$. We define $\theta_n$ to be
 the \newtext{minimal} threshold $t_j$ for which $B_i = 0$ for all observations $X_i
@@
 \[
-D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
+D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + O(n^{-2}) =  \frac{4\sigma^2}{3n} + O(n^{-2}). 
 \]

### 2021-10-01 response.tex
finished response
add detailed expansion in CEO proof

@@
 Could you clarify what $o(1/n)$ is hiding that makes it $O(1/n)$ in (7) instead of merely $o(1)$?
+
 \begin{response}
 Thank you for this comment.
-It made us realized that there was a mistake in the proof and we should replace $o(1/n)$ with $O(n^{-2})$.
-The $O(n^{-2})$ term is the remainder in the first order taylor expansion of $D^\star$ in $1/n$.
+It made us realized that there was a mistake in the proof and we should have replaced the $o(1/n)$ term with $O(n^{-2})$.
+We now provide a more detailed derivation of the expansion of $D^\star$ as $n\to \infty$ that provides the second order term.
 \end{response}

### 2021-10-01 uniform-are-weirdos.tex
add detailed expansion in CEO proof

@@
 Since $D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describes the MSE in the CEO setting under an optimal allocation of the sum-rate $r = n$ among $n$ encoders, it provides a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
-By considering the limit $n\rightarrow \infty$ in \eqref{eq:ceo_optimal_sumrate2}, we see that
-\[
-D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + O(n^{-2}) =  \frac{4\sigma^2}{3n} + O(n^{-2}). 
-\]
+\newtext{By noting that $1/D^\star$ grows no faster than a polynomial in $n$ \cite{viswanathan1997quadratic}, we rely on the expansion
+\begin{align*}
+\left(\frac{\sigma_{\theta}^2}{D^\star}\right)^{1/n} 
+= 1 + \frac{\log \left(\frac{\sigma_{\theta}^2}{D^\star}\right)}{n}+\frac{\log^2\left(\frac{\sigma_{\theta}^2}{D^\star}\right)}{2 n^2}+O\left(n^{-3}\right),
+\end{align*}
+to obtain that, in limit $n\rightarrow \infty$, \eqref{eq:ceo_optimal_sumrate2} behaves as 
+\begin{align*}
+D^\star = %\frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + O(n^{-2}) =  \frac{4\sigma^2}{3n} + O(n^{-2}). 
+\frac{4 \sigma^2}{3 n}
++ \frac{16 \sigma^2}{9 n^2 \sigma_{\theta}^2 }-\frac{4 \sigma^2 \log \left(\frac{\sigma_{\theta}^2}{D^\star}\right)}{9 n^2}
++O(n^{-3}).
+\end{align*}
+}
 This implies Proposition~\ref{prop:CEO}. 

### 2021-10-25 response.tex
finished response and revision

@@
 As it turns out, one of the equations in the proof was incorrect because it indicated a location shift by $h$ in both sides of the equation instead of only in one side as per the definition of a regular estimator.
-As it turns out, an easy fix to this issue in our case is obtained by changing Lemma 14 to the following from.
+We fixed this issue by changing Lemma 14 to the following from.
 \setcounter{thm}{13}
@@
 \begin{response}
-We thank Reviewer 1 for pointing on the problems with this example.
-As it turns out, the original example were missing the important ingredient of comparing our communication-limited estimator to the maximum of the samples within a bin.
+We thank Reviewer 1 for pointing on the problems with this example which indeed was missing a key ingredient: a comparison between our communication-limited estimator to the maximum of the samples within a bin.
 We have carefully went through this example and revised to add the missing part and resolve all other issues.
+
+We refer the reviewer to the revised manuscript for reviewing these changes; we highlighted in blue the parts that went through significant changes.
+
 \end{response}
@@
 Thank you for this comment.
-It made us realized that there was a mistake in the proof and we should have replaced the $o(1/n)$ term with $O(n^{-2})$.
+It made us realized that there was a mistake in the proof of Proposition~1: we should have replaced the $o(1/n)$ term with $O(n^{-2})$.
 We now provide a more detailed derivation of the expansion of $D^\star$ as $n\to \infty$ that provides the second order term.
+The relevant part is as follows.
+
+\begin{quote}
+Denote by $D^\star$ the optimal MSE in the Gaussian CEO with $L$ observers and under a total sum-rate $r = r_1 + \ldots +r_L$.
+An expression for $D^\star$ as a function of $r$ is give as \cite[Eq.
+10]{chen2004upper}:
+\begin{equation} \label{eq:ceo_optimal_sumrate}
+r = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
+\end{equation}
+For the special case where $r = n$ and $L=n$, we have
+\begin{equation} \label{eq:ceo_optimal_sumrate2}
+n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
+\end{equation}
+Consider the distributed encoding setting (iii) in the case where $f(x) = \Ncal(0,\sigma^2)$ and the prior on $\Theta$ is $\pi = \Ncal(0,\sigma_\theta^2)$.
+The Gaussian CEO problem of \cite{viswanathan1997quadratic} with a unit bitrate $r_1=\ldots = r_n =1$ at each terminal and blocklength $k=1$ reduces to our distributed setting (iii).
+Since $D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describes the MSE in the CEO setting under an optimal allocation of the sum-rate $r = n$ among $n$ encoders, it provides a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.
+
+By noting that $1/D^\star$ grows no faster than a polynomial in $n$ \cite{viswanathan1997quadratic}, we rely on the expansion
+\begin{align*}
+\left(\frac{\sigma_{\theta}^2}{D^\star}\right)^{1/n} 
+= 1 + \frac{\log \left(\frac{\sigma_{\theta}^2}{D^\star}\right)}{n}+\frac{\log^2\left(\frac{\sigma_{\theta}^2}{D^\star}\right)}{2 n^2}+O\left(n^{-3}\right),
+\end{align*}
+to obtain that, in limit $n\rightarrow \infty$, \eqref{eq:ceo_optimal_sumrate2} behaves as 
+\begin{align*}
+D^\star = 
+\frac{4 \sigma^2}{3 n}
++ \frac{16 \sigma^2}{9 n^2 \sigma_{\theta}^2 }-\frac{4 \sigma^2 \log \left(\frac{\sigma_{\theta}^2}{D^\star}\right)}{9 n^2}
++O(n^{-3}).
+\end{align*}
+\end{quote}
 \end{response}
@@
 \item Section IV B, page 13, line 3: It says $B_i$ a.s. converges to $F(\theta_0 - \theta)$. Shouldn't it say $E[B_i] = F(\theta_0 - \theta)$?
-\begin{response} It should. We fixed this issue. 
+\begin{response} Thank you. It should say $E[B_i] = F(\theta_0 - \theta)$. We fixed this issue. 
 \end{response}
@@
 \begin{response}
-We thank the reviewer for bringing it to our attention that the here notation is unclear. We rewritten the relevant part as follows. 
+We thank the reviewer for bringing it to our attention that the notation here is unclear. We rewritten the relevant part as follows. 
 \begin{quote}
@@
 \begin{response}
-We agree and fixed this according to the Reviewer's suggestion. 
+We agree. We have fixed this isssue according to the Reviewer's suggestion. 
 \end{response}
@@
 \begin{response}
-We revised this part in a way that we no longer rely on a finite approximation to the prior measure $\pi$.
-Instead, prove the result for a fixed $\theta$ and rely on an additional requirement saying that the second moment of $\pi$ exists.
+We added the assumption that $\pi$ has a finite second moment and revised this part accordingly without 
+using a finite approximation to the prior measure $\pi$. 
 \end{response}
@@
     The Reviewer's comment made us realize that we initially did not explain well that our results in Section V-C yields the exact efficiency gap under distributed threshold encoding.
-To improve this point, we added the following sentence to the caption of Fig.
-6.
+To improve this point, we revised Figure 6 as follows.
     \begin{quote}
-The line $\pi/2$ is the optimal relative efficiency, attained under adaptive encoding for any $\sigma$ uniformly over the parameter space.
+\begin{figure}[h!]
+  %%%%% COMMENTED TIKZ PICTURE %%%%%
+  \begin{center}
+\begin{tikzpicture}[scale = 1]
+\begin{axis}[
+width=8cm, height=6cm,
+xmin=.03,
+xmax=2.5, 
+xmode = log,
+restrict y to domain = 0:100,
+ymin = 0,
+ymax = 1,
+samples=1, 
+xlabel= {$\sigma$},
+%xtick={-0.5,0,0.5},
+%xticklabels={-$$, 0, $b$},
+ytick={0,0.637,1},
+yticklabels={0,$\frac{2}{\pi}$,1},
+ylabel = {\scriptsize Relative Efficiency},
+line width=1.0pt,
+mark size=1.5pt,
+ymajorgrids,
+xmajorgrids,
+legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
+]
+\addplot[color = red, smooth,
+line width=1.0pt,
+%mark size=1.5pt,mark=x,
+] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
+\addlegendentry{\scriptsize optimal threshold density};
+
+\addplot[color = black!35!green, dashed, line width=1.0pt,
+        %mark size=1.5pt, mark=^
+        ]
+ plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
+\addlegendentry{\scriptsize uniform threshold desnity};
+
+\addplot[color = black, smooth, dotted, line width = 1pt] 
+coordinates {
+            (0.03, .637) (10, .637)
+            };
+\addlegendentry{\scriptsize attained in the adaptive case};
+%\draw[->] (axis cs:0.1,.5) -- node[below, align=center] {\scriptsize ARE attained in \\ \scriptsize the adaptive case} (axis cs:0.1, .63);
+\end{axis}
+\end{tikzpicture}
+
+\setcounter{figure}{5}
+\caption{
+\newtext{
+Minimax relative efficiency under distributed encoding.
+ARE versus $\sigma$ for $f(x)$ the standard normal density with variance $\sigma^2$ and parameter space $\Theta = [-1/2,1/2]$.
+The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$ of (19).
+The line $\pi/2$ is attained under adaptive encoding uniformly over the parameter space for any $\sigma$.}}
+\end{center}
+\end{figure}
+
 \end{quote}
@@
 \cite{zhang2013information,shamir2014fundamental,braverman2016communication,han2018geometric,barnes2020lower}, although these references do not yield the asymptotic relative efficiency (ARE) but only characterization of the way the error scales in the communication bit-budget and the dimension.
-It is still unclear whether we can extend our methods to derive the ARE for any dimension and bit budget, but anyway such extension is not straightforward.
-Consequently, we decided to leave this extension as a future work.
+It is still unclear whether we can extend our methods to derive the ARE for any dimension and bit budget, but anyway such extension is not straightforward so we decided to leave this extension as a future work.
 %characterizing the way the error scales with the number of bits and the dimension and not on the exact asymptotic efficiency. 
@@
 \begin{quote}
-    Natural extensions of the setting of this work are situations when the communication bit-budget $b$ is larger than one and when each sample is a $d$-dimensional vector.
-Fundamental bounds for this general case follows from several recent works (e.g.
-\cite{zhang2013information,shamir2014fundamental,braverman2016communication,han2018geometric,barnes2020lower}), which imply that in the adaptive and distributed cases the MSE scales in the regular parametric rate of $1/n$ when $b$ and $d$ are held fixed in the sample size $n$.
-Nevertheless, the coefficient of the $1/n$ term corresponding to the ARE is still unknown; deriving the ARE for general $b$ and $d$ is left as a future challenge.
+    Natural extensions of the setting of this work include situations when the communication bit-budget $b$ is larger than one and when each sample is a $d$-dimensional vector.
+Rough lower bounds on the MSE for this general case follows from several recent works (e.g.
+\cite{zhang2013information,shamir2014fundamental,braverman2016communication,han2018geometric,barnes2020lower}), that in particular imply that in some cases the MSE scales in the regular parametric rate of $1/n$ when $b$ and $d$ are held fixed in the sample size $n$.
+Nevertheless, the coefficient of the leading scaling term corresponding to the ARE is still unknown; deriving the ARE for general $b$ and $d$ is left as a future challenge.
 \end{quote}
@@
 
-\item First line of page 4: asyptotic --> asymptotic.
+\item First line of page 4: asyptotic $\to$ asymptotic.
 

### 2021-10-25 conclusions.tex
finished response and revision

--- 2020-12-09 conclusions.tex
@@
 %\par
-%Obvious extensions of our work include deriving explicit bounds and optimal procedures when more than one-bit per sample is provided or when each sample is a vector.
-Another possible extension may consider the efficiency of estimation when single bits are sent between nodes of a directed graph.
+
+\newtext{
+Natural extensions of this work include situations when the communication bit-budget $b$ is larger than one and when each sample is a $d$-dimensional vector.
+Rough lower bounds on the MSE for this general case follows from several recent works (e.g.
+\cite{zhang2013information,shamir2014fundamental,braverman2016communication,han2018geometric,barnes2020lower}), that in particular imply that in some cases the MSE scales in the regular parametric rate of $1/n$ when $b$ and $d$ are held fixed in the sample size $n$.
+Nevertheless, the coefficient of the leading $1/n$ term corresponding to the ARE, which we characterized here in the case $b=1$and $d=1$, is still unknown in the general case.}

### 2021-10-25 distributed-estimation.tex
finished response and revision

@@
 Theorem~\ref{theorem:non-adaptive-minimax} shows that the limiting variance
-term $\kappa(\theta)$ provides strong lower bounds on the efficiency of any
-non-adaptive estimator, and moreover, that these bounds necessarily depend
-on $\theta$. This suggests that attaining any type of good (uniform)
-efficiency with non-adaptive estimators will be challenging.  As a
+term $\kappa(\theta)$ provides a strong lower bound on the efficiency of any
+non-adaptive estimator, and moreover, that this bound necessarily depends
+on $\theta$. As a
 particular consequence, for the squared error $L(x) = x^2$, for any $\delta
@@
   \theta| \le c / \sqrt{n}} \E_\tau[(\theta_n - \tau)^2] \ge \frac{(1 -
-  \delta)}{n \kappa(\theta)} + o(1/n)$.
+  \delta)}{n \kappa(\theta)} + o(1/n)$. Consequently, attaining any type of good (uniform)
+efficiency with non-adaptive estimators will be challenging.
 
@@
 half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
-against a single threshold. Under the adaptive signal acquisition,
+against a single threshold. Under the adaptive signal acquisition setting,
 this is sufficient for asymptotic optimality;
@@
 $\lambda$ is the point mass at $\theta$. Since $\theta$ is \emph{a priori}
-unknown, we conclude that estimation in the distributed setting using
+unknown, estimation in the distributed setting using
 threshold detection is strictly suboptimal compared to the adaptive
@@
 width=8cm, height=6cm,
+xmin=.03,
 xmax=2.5, 
@@
 ytick={0,0.637,1},
-yticklabels={0,$2/\pi$,1},
+yticklabels={0,$\frac{2}{\pi}$,1},
 ylabel = {\scriptsize Relative Efficiency},
@@
 ]
-\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{optimal threshold density};
+\addplot[color = red, smooth,
+line width=1.0pt,
+%mark size=1.5pt,mark=x,
+] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
+\addlegendentry{\scriptsize optimal threshold density};
 
-\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{uniform threshold desnity};
+\addplot[color = black!35!green, dashed, line width=1.0pt,
+        %mark size=1.5pt, mark=^
+        ]
+ plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
+\addlegendentry{\scriptsize uniform threshold desnity};
+
+\addplot[color = black, smooth, dotted, line width = 1pt] 
+coordinates {
+            (0.03, .637) (10, .637)
+            };
+\addlegendentry{\scriptsize attained in the adaptive case};
+%\draw[->] (axis cs:0.1,.5) -- node[below, align=center] {\scriptsize ARE attained in \\ \scriptsize the adaptive case} (axis cs:0.1, .63);
 \end{axis}
@@
 Minimax relative efficiency under distributed encoding.
-ARE versus $\sigma$ for $f(x)$ the standard normal density with variance $\sigma^2$ and $\Theta = [-1/2,1/2]$.
+ARE versus $\sigma$ for $f(x)$ the standard normal density with variance $\sigma^2$ and parameter space $\Theta = [-1/2,1/2]$.
 The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$ of \eqref{eq:uniform_risk}.
 \newtext{
-The line $\pi/2$ is the optimal relative efficiency, attained under adaptive encoding for any $\sigma$ uniformly over the parameter space.}}
+The line $\pi/2$ is attained under adaptive encoding uniformly over the parameter space for any $\sigma$.}}
 \end{center}

### 2022-04-20 adaptive-estimation.tex
addressed specific commets in R2

@@
 where
-\begin{equation*}
-  T_n \defeq \theta_0 - F^{-1}\left(
+\begin{align*}
+  T_n & \defeq \theta_0 - F^{-1}\left(
   \frac{1}{n_1} \sum_{i=1}^{n_1} B_i 
-  \right)
-  ~~ \mbox{and} ~~
-  \theta_n \defeq
+  \right)\\
+  \theta_n & \defeq
   T_n - F^{-1} \left(\frac{1}{n - n_1}
   \sum_{i = n_1}^n B_i \right).
-\end{equation*} 
+\end{align*} 
 The intuition here is that the estimator $\theta_n$ is a one-step
@@
 $T_n$, which approximately estimates
-$\theta_0 - F^{-1}(\theta_0 - \theta) = \theta$. We then have the
+$\theta_0 - F^{-1}\left(F(\theta_0 - \theta)\right) = \theta$. We then have the
 following convergence result.
@@
   \begin{equation*}
-    \E\left[|B_i - E_n|^3 \mid T_n\right] \le E_n(1 - E_n)
-    ~~ \mbox{we have} ~~
+    \E\left[|B_i - E_n|^3 \mid T_n\right] \le E_n(1 - E_n),
+    \end{equation*}
+      we have 
+\begin{equation*}
     \E\left[\frac{|B_i - E_n|^3}{(E_n(1 - E_n))^{3/2}} \mid T_n\right]
@@
   \end{equation*}
-  which gives that $Y_n \cd \normal(0, 1)$.
-
-  Now,
-  Slutsky's lemmas imply
-  \begin{equation}
-    \sqrt{n}
+  which gives that $Y_n \cd \normal(0, 1)$. Now, Slutsky's lemmas imply
+  \begin{align}
+    &\sqrt{n}
     \cdot \frac{2}{n} \sum_{i = 1}^n (B_i - E_n)
-    =
-    (1 + o_P(1)) \frac{1}{\sqrt{n E_n(1 - E_n)}}
+    \\
+    & \qquad  =
+ \frac{1 + o_P(1)}{\sqrt{n E_n(1 - E_n)}}
     \sum_{i = 1}^n \left(B_i - E_n\right)
@@
     \label{eqn:apply-slutsky}
-  \end{equation}
-  For shorthand we write $P_n B = \frac{1}{n} \sum_{i = 1}^n B_i$,
-  and using that $E_n = \E[B_i \mid T_n] = F(T_n - \theta)$, we may thus
-  use the delta method to write
+  \end{align}
+  where $o_P(1)$ denotes sequence of random variables converging to zero in probability as $n$ goes to infinity.
+With $\bar{B}_n \defeq \frac{1}{n} \sum_{i = 1}^n B_i$ and using that $E_n = \E[B_i \mid T_n] = F(T_n - \theta)$, we may use the delta method to write
   \begin{align*}
-    \sqrt{n}(\theta_n - \theta)
-    & = \sqrt{n}\left(T_n - F^{-1}\left(P_n B\right)
+    & \sqrt{n}(\theta_n - \theta)
+     = \sqrt{n}\left(T_n - F^{-1}\left( \bar{B}_n \right)
     - \theta \right) \\
-    & = \sqrt{n} \left(T_n - F^{-1}\left(F(T_n - \theta)
-    + P_n B - F(T_n - \theta)\right) - \theta \right) \\
-    & = \sqrt{n} \left(T_n - (T_n - \theta )
-    + (F^{-1})'(T_n - \theta + o_P(1))\cdot \left(
-    P_n B - E_n\right) - \theta \right) \\
-    & = \sqrt{n} (F^{-1})'(0) (P_n B - E_n)
-    + o_P(1)
-    \cd \normal\left(0, \frac{1}{4 f(0)^2}\right),
+    &\quad  = \sqrt{n} \left[T_n - F^{-1}\left(F(T_n - \theta)
+    + \bar{B}_n - F(T_n - \theta)\right) - \theta \right] \\
+    & \quad = \sqrt{n} \left[ T_n - (T_n - \theta ) \right. \\
+    &  \left. +  (F^{-1})' \left(T_n - \theta + o_P(1) \right)  
+    \cdot \left(\bar{B}_n - E_n\right) - \theta \right] \\
+    & \quad = \sqrt{n} (F^{-1})'(0) ( \bar{B}_n - E_n)
+    + o_P(1) \\
+    & \quad \cd \normal\left(0, \frac{1}{4 f(0)^2}\right),
   \end{align*}

### 2022-04-20 ak-bio.tex
addressed specific commets in R2

Alon Kipnis is a Senior Lecturer at the Efi Arazi School of Computer Science at Reichman University. Preivously, he was a postdoctoral research scholar and a lecturer at the Department of Statistics at Stanford University, advised by David Donoho. He completed the Ph.D. in electrical engineering from Stanford University in 2017. Dr. Kipnis is the recipient of numerous fellowships and awards, including the Koret foundation postdoctoral fellowship, Stanford's electrical engineering department fellowship, and a prize from the Wolf Foundation. His research is in the areas of mathematical statistics and information theory.

### 2022-04-20 conclusions.tex
addressed specific commets in R2

--- 2021-09-30 conclusions.tex
@@
 
-\newtext{
-Natural extensions of the setting of this work are situations when the communication bit-budget $b$ is larger than one and when each sample is a $d$-dimensional vector.
-Rough bounds in this general case follow from several recent works (e.g.
-\cite{zhang2013information,shamir2014fundamental,braverman2016communication,han2018geometric,barnes2020lower}), which imply that in the adaptive and distributed cases the MSE scales in the regular parametric rate of $1/n$ when $b$ and $d$ are held fixed in the sample size $n$.
-Nevertheless, the coefficients of the $1/n$ term corresponding to the ARE are in general unknown; deriving the ARE for general $b$ and $d$ is left as a future challenge.}
+Natural extensions of this work include situations when the communication bit-budget $b$ is larger than one and when each sample is a $d$-dimensional vector.
+Bounds on rate of convergence of the MSE in this general case follow from several recent works (e.g.
+\cite{zhang2013information,shamir2014fundamental,
+braverman2016communication,han2018geometric,
+barnes2020lower,cai2020distributed}), that in particular imply that in some cases the MSE decreases in the regular parametric rate of $1/n$ when $b$ and $d$ are held fixed in the sample size $n$.
+Nevertheless, the coefficient of the leading $1/n$ term corresponding to the ARE, which we characterized here in the case $b=1$ and $d=1$, is still unknown in the general case.

### 2022-04-20 distributed-estimation.tex
addressed specific commets in R2

@@
 $\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
-\begin{equation}
+\begin{align}
   L_n(A_1,\ldots,A_n;\theta)
-  = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
+  & = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) } \\
+  & = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
   \label{eq:Ln_threshold}
-\end{equation}
+\end{align}
 A natural condition for the existence of the limit \eqref{eq:Ln_threshold}
@@
 Optimal threshold density under distributed encoding.
-The threshold density $\lambda^\star(dt)$ (blue) that maximizes the asymptotic relative efficiency for $f(x)$ the normal desnity with variance $\sigma^2$ and $\Theta= [-1/2,1/2]$.
+The threshold density $\lambda^\star(dt)$ (blue) that maximizes the asymptotic relative efficiency for $f(x)$ the normal density with variance $\sigma^2$ and $\Theta= [-1/2,1/2]$.
 %
@@
  plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
-\addlegendentry{\scriptsize uniform threshold desnity};
+\addlegendentry{\scriptsize uniform threshold density};
 

### 2022-04-20 onebit_full.tex
addressed specific commets in R2

@@
 %% \documentclass[11pt]{article}
-\documentclass[letterpaper, 11pt, draftcls]{IEEEtran}      % Use this line for a4 paper
+\documentclass[letterpaper, 11pt]{IEEEtran}      % Use this line for a4 paper
 
@@
 
-\onecolumn
-
 \usepackage{macros}
@@
     \IEEEauthorblockN{
-Alon Kipnis\IEEEauthorrefmark{1} and   
-    John C. Duchi\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}  \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}Stanford University, Department of Statistics \\}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Stanford University, Department of Electrical Engineering. }
+Alon Kipnis and   
+    John C. Duchi }
 
-\thanks{This paper was presented in part at the 55th Annual Allerton Conference on Communication, Control, and Computing (Allerton) \cite{KipnisAllerton2017}.
+\thanks{
+Alon Kipnis is with the School of Computer Science at Reichman University, Herzliya, Israel (kipnisal@stanford.edu).} 
+\thanks{J. Duchi is with the Department of Statistics and Department of Electrical Engineering at Stanford University, Stanford, CA, 94035 (jduchi@stanford.edu).}
+\thanks{Copyright (c) 2017 IEEE.
+Personal use of this material is permitted.
+However, permission to use this material for any other purposes must be obtained from the IEEE by sending a request to pubs-permissions@ieee.org.}
+\thanks{This paper was presented in part at the 55th Annual Allerton Conference on Communication, Control, and Computing (Allerton) \cite{KipnisAllerton2017}. }
+\thanks{
+The work of A. Kipnis was supported in part by funding from the NSF under Grant No.~DMS-1418362 and DMS-1407813, and by a fellowship from the Koret Foundation.}
 }
-}
-
-%% \renewenvironment{figure}{%
-%%   \ignorespaces
-%% }{}
 
@@
 
-\section*{Acknowledgments}
-%% \textbf{WRITE THIS SECTION}
-The work of A. Kipnis was supported in part by funding from the NSF under Grant No.~DMS-1418362 and DMS-1407813, and by a fellowship from the Koret Foundation.
-
 \onecolumn

### 2022-04-20 preliminaries.tex
ready for submission
fixed all minor comments from R1
addressed specific commets in R2

@@
 \[
-B_i = \mathbf 1_{X_i<\theta_0}, 
+B_i = \indic{X_i<\theta_0}, 
 \]
-where $\mathbf 1_A$ is the indicator of the event $A$. We have
+where $\indic{A}$ is the indicator of the event $A$. We have
 \[
-P_n \triangleq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta_0 - \theta),  
+\bar{B}_n \defeq\frac{1}{n} \sum_{i=1}^n B_i \overset{a.s.}{\rightarrow} F(\theta_0 - \theta),  
 \]
@@
 \label{eq:estimator_naive}
-{\theta}_n = \theta_0 - F^{-1}\left( P_n \right)
+{\theta}_n = \theta_0 - F^{-1}\left( \bar{B}_n \right)
 \end{equation}
@@
 Figure~\ref{fig:setup}-(iii), where we note that $F$ is invertible over the
-support of $f$. As the variance of $P_n$ is
+support of $f$. As the variance of $\bar{B}_n$ is
 $F(\theta_0-\theta)\left(1-F(\theta_0-\theta)\right)$, a delta method
@@
   \begin{equation} \label{eq:ceo_bound}
-    n \ex{\left( \theta - \theta_n \right)^2} \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
+    n \cdot \ex{\left( \theta - \theta_n \right)^2} \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
   \end{equation}

### 2022-04-20 proof-sgd.tex
addressed specific commets in R2

@@
     \theta_{i-1})$ for $X_i = \theta + Z_i$, where $\{Z_i\}$ are i.i.d.\ with
-    $\E[\varphi(Z)] = 0$. Additionally assume the local smoothness
+   $\E[Z_1]=0$ and  $\E[\varphi(Z_1)] = 0$. Additionally assume the local smoothness
     condition that there exist $0 < \lambda \le 1$ and $K < \infty$ such
@@
       \label{eqn:additional-local-smooth}
-      \E[|\varphi(x + Z_1) - \varphi(Z)|^2]
+      \E[|\varphi(x + Z_1) - \varphi(Z_1)|^2]
       \le K (|x|^\lambda + x^2).
@@
   (and Lemma~\ref{lemma:sgd-median-regular}) satisfies the
-  conditions of Corollary~\ref{corollary:polyak-juditsky}. First, we have
+  conditions of Corollary~\ref{corollary:normal-expansion}. First, we have
   the obvious fact that
@@
     + Z)]$ and that $\psi(0) = 0$.  We now control the expectations of these
-  quantities. 
-  \newtext{
-  As in the proof of Theorems~2 and~4 in \cite{polyak1992acceleration}, the Robbins-Siegmund Theorem \cite{robbins1971convergence} applies to the increment of $|\Delta_t|^2$ implies that for every 
-  $\epsilon>0$ there exists some $R>0$ such that
-  \begin{align}
-  \label{eq:sup_delta}
-  \Prob\left(\sup_i |\Delta_i| \le R \right) \ge 1-\epsilon.
-  \end{align} 
-  Define the the stopping time $\tau_R \defeq \inf
+  quantities. For $R<\infty$, define the the stopping time $\tau_R \defeq \inf
   \{i : |\Delta_i| > R\}$, which satisfies $\{\tau_R \le i\} \in \mc{F}_i$
-  for each $i$. 
-  }
-  Then using~\cite[Eq.~(A14)]{polyak1992acceleration}, we have
+  for each $i$. Then using~\cite[Eq.~(A13-A14)]{polyak1992acceleration}, we have
   \begin{equation*}
@@
     \E\bigg[\sum_{i = 1}^\infty \frac{1}{i}
-      |\varepsilon_i|^2 \indic{\tau_R > i} \bigg]
+      |\varepsilon_i|^2 \indic{\tau_R > n} \bigg]
     \le K \sum_{i = 1}^\infty \frac{\gamma_i^\lambda}{i}
@@
     \sum_{i = 1}^\infty \frac{1}{i}
-    \varepsilon_i^2 \indic{\tau_R > i} < \infty
+    \epsilon_i^2 \indic{\tau_R > n} < \infty
     ~ \mbox{a.s.}
   \end{equation*}
-  by Condition~\eqref{eqn:lazy-gamma}. Since
-  \begin{align*}
-\left\{ \sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}} < \infty \subset \left\{ \sup_i |\Delta_i| \leq R \right\} \cap \left\{ \sum_{i=0}^\infty  \right\}
- \right\},
-  \end{align*}
-  \newtext{it follows from \eqref{eq:sup_delta} and by the arbitrary choice of $\epsilon$ that}
+by Condition~\eqref{eqn:lazy-gamma}. 
+%  
+%  Since
+%  \begin{align*}
+%\left\{ \sup_i |\Delta_i| \leq R \right\} \cap \left\{ \sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda} \indic{\tau_T > n} }{\sqrt{i}} < \infty  \right\}  
+%\subset \left\{ \sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}} < \infty  \right\}
+%  \end{align*}
+%it follows from \eqref{eq:sup_delta} and by the arbitrary choice of $\epsilon$ that
   %\newtext{As it follows from \cite[Eq.~(A11)]{polyak1992acceleration} that $\Prob\left( \sup |\Delta_t| < \infty  \right)=1$}, we obtain
-  %\newtext{As Lemma~\ref{lemma:converging-power-sum} implies in particular that $\{\Delta_i\}$ is a.s.
-bounded, with probability 1 there exists some (random) $R < \infty$ such that $\tau_R = \infty$.} We obtain that
+%As Lemma~\ref{lemma:converging-power-sum} implies in particular that $\{\Delta_i\}$ is a.s. bounded, 
+ As in the proof of Theorems~2 and~4 in \cite{polyak1992acceleration}, the Robbins-Siegmund Theorem \cite{robbins1971convergence} applied to the increment of $|\Delta_t|^2$ implies that for every 
+  $\epsilon>0$ there exists some $R'>0$ such that
+  \begin{align}
+  \label{eq:sup_delta}
+  \Prob\left(\sup_i |\Delta_i| \le R' \right) \ge 1-\epsilon.
+  \end{align} 
+Consequently, there exists some $R'' < \infty$ such that $\tau_{R''} = \infty$. 
+We obtain that 
  \begin{equation*}
@@
     \varepsilon_i^2  < \infty
-    ~ \mbox{a.s.}.
+    ~~ \mbox{a.s.}.
   \end{equation*}

### 2022-04-20 introduction.tex
addressed specific commets in R2

@@
 $n$ bits. As the accuracy in describing the empirical mean decreases
-exponentially in $n$, the quantization error is negligible compared
-to the statistical error in mean estimation~\cite{720540}. That is,
+exponentially in the number of bits, the quantization error is negligible compared
+to the statistical error in mean estimation~\cite{720540, cai2020distributed}. That is,
 centralized encoding induces no asymptotic efficiency loss.

### 2022-04-20 onebit_full.tex
addressed specific commets in R2

@@
     \IEEEauthorblockN{
-Alon Kipnis and   
-    John C. Duchi }
+Alon~Kipnis and   
+    John~C.~Duchi}
 
 \thanks{
-Alon Kipnis is with the School of Computer Science at Reichman University, Herzliya, Israel (kipnisal@stanford.edu).} 
-\thanks{J. Duchi is with the Department of Statistics and Department of Electrical Engineering at Stanford University, Stanford, CA, 94035 (jduchi@stanford.edu).}
+Alon Kipnis is with the School of Computer Science at Reichman University, Herzliya, Israel (alon.kipnis@idc.ac.il).} 
+\thanks{J. Duchi is with the Department of Statistics and the Department of Electrical Engineering at Stanford University, Stanford, CA, 94035 (jduchi@stanford.edu).}
 \thanks{Copyright (c) 2017 IEEE.
@@
 
+\begin{IEEEbiographynophoto}{Alon Kipnis}
+\input{ak-bio}
+\end{IEEEbiographynophoto}
+
+\begin{IEEEbiographynophoto}{Alon Kipnis}
+\input{jd-bio}
+\end{IEEEbiographynophoto}
+
 \end{document}

### 2022-04-27 ak-bio.tex
addressed specific commets in R2
updated bios

@@
-Alon Kipnis is a Senior Lecturer at the Efi Arazi School of Computer Science at Reichman University.
-Preivously, he was a postdoctoral research scholar and a lecturer at the Department of Statistics at Stanford University, advised by David Donoho.
-He completed the Ph.D.
+Alon Kipnis is a Senior Lecturer (Assistant Professor) at the School of Computer Science at Reichman University.
+Previously, he was a postdoctoral research scholar at the Department of Statistics at Stanford University, advised by David Donoho.
+He completed his Ph.D.
 in electrical engineering from Stanford University in 2017.
+His research is in the areas of mathematical statistics and information theory.
+He is particularly interested in ambitious machine learning and data science applications of his theoretical work.
+
 Dr.

### 2022-04-27 jd-bio.tex
updated bios

John Duchi is an associate professor of Statistics and Electrical Engineering and (by courtesy) Computer Science at Stanford University. His work spans statistical learning, optimization, information theory, and computation, with a few driving goals. (1) To discover statistical learning procedures that optimally trade between real-world resources---computation, communication, privacy provided to study participants---while maintaining statistical efficiency. (2) To build efficient large-scale optimization methods that address the spectrum of optimization, machine learning, and data analysis problems we face, allowing us to move beyond bespoke solutions to methods that robustly work. (3) To develop tools to assess and guarantee the validity of---and confidence we should have in---machine-learned systems.

He has won several awards and fellowships. His paper awards include the SIAM SIGEST award for "an outstanding paper of general interest" and best papers at the Neural Information Processing Systems conference, the International Conference on Machine Learning, and an INFORMS Applied Probability Society Best Student Paper Award (as advisor). He has also received the Society for Industrial and Applied Mathematics (SIAM) Early Career Prize in Optimization, an Office of Naval Research (ONR) Young Investigator Award, an NSF CAREER award, a Sloan Fellowship in Mathematics, the Okawa Foundation Award, the Association for Computing Machinery (ACM) Doctoral Dissertation Award (honorable mention), and U.C. Berkeley's C.V. Ramamoorthy Distinguished Research Award.

### 2022-04-27 problem-formulation.tex
ready for submission
addressed specific commets in R2
updated bios

@@
 We measure the performance of an estimator $\theta_n \defeq
-\theta_n(B_1^n)$ by one of a few notions. In the simplest case,
+\theta_n(B_1,\ldots,B_n)$ by one of a few notions. In the simplest case,
 we assume a prior $\pi$ on $\theta$ (which may be a point
@@
 \end{equation}
-appears throughout our development. (Here equality~$(\star)$ is immediate by
-the symmetry of $f$.)  For $p \in (0, 1)$ and $x = F^{-1}(p)$,
+appears throughout our development (equality~$(\star)$ is immediate by
+the symmetry of $f$). For $p \in (0, 1)$ and $x = F^{-1}(p)$,
 \begin{equation}
@@
 \end{equation}
-is of course the familiar asymptotic variance of the $p$th quantile of the sample $X_1,\ldots,X^n$ (cf.~\cite{VanDerVaart98}, Ch.~21).
+is of course the familiar asymptotic variance of the $p$th quantile of the sample $X_1,\ldots,X_n$ (cf.~\cite{VanDerVaart98}, Ch.~21).
 

### 2022-05-02 distributed-estimation.tex
example for A2-(ii)

@@
     \end{equation*}
-    %% Each set $A_n$ is a finite union of at most $K < \infty$ intervals
-    %% (which may include $\pm \infty$), and
-    %% $0 < \inf_n P_\theta(A_n) \le \sup_n P_\theta(A_n) < 1$.
   \item \label{item:limit-variance}
@@
 \end{assumption}
+Roughly speaking, \eqref{item:finite-intervals} above holds whenever the intervals consisting each $A_i$ are appropriately seperated.
+For example, it applies when each set $A_i$ is a half-bounded interval $(t_i,\infty)$ with $\min\{P_\theta((t_i,\infty)), P_\theta((-\infty,t_i])\} = \omega(1/n)$ as we dicscuss in more detail below.
+More generally, suppose that $A_i = \cup_{j=1}^{k_i}[t_{i,j}^-, t_{i,j}^+]$ and let
+\begin{align*}
+c_n^+ & =  \min_{i \le n} \min_{j \leq k_i}  F(t^+_{i,j} - \theta) - F(t^-_{i,j}- \theta) \\
+c_n^- & = \min_{i \le n} \min_{j \leq k_i}  F(t^-_{i,j+1}- \theta)  - F(t^+_{i,j}- \theta),
+\end{align*}
+with $t^-_{i,k_i+1} = \infty$. Then Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals} holds whenever $\max_{i \le n} k_i^3 (c_n^- c_n^+)^4 = o(n)$.
 
-Under this assumption, we have the following theorem, which provides
+Under Assumption~\ref{assumption:detection-regions}, we have the following theorem, which provides
 a local asymptotic minimax lower bound on the efficiency of

### 2022-05-02 distributed-estimation.tex
example for A2-(ii)

@@
 \end{assumption}
-Roughly speaking, \eqref{item:finite-intervals} above holds whenever the intervals consisting each $A_i$ are appropriately seperated.
+Roughly speaking, \eqref{item:finite-intervals} above holds whenever the intervals consisting each $A_i$ are appropriately seperated and their number is relatively small.
 For example, it applies when each set $A_i$ is a half-bounded interval $(t_i,\infty)$ with $\min\{P_\theta((t_i,\infty)), P_\theta((-\infty,t_i])\} = \omega(1/n)$ as we dicscuss in more detail below.
-More generally, suppose that $A_i = \cup_{j=1}^{k_i}[t_{i,j}^-, t_{i,j}^+]$ and let
-\begin{align*}
-c_n^+ & =  \min_{i \le n} \min_{j \leq k_i}  F(t^+_{i,j} - \theta) - F(t^-_{i,j}- \theta) \\
-c_n^- & = \min_{i \le n} \min_{j \leq k_i}  F(t^-_{i,j+1}- \theta)  - F(t^+_{i,j}- \theta),
-\end{align*}
-with $t^-_{i,k_i+1} = \infty$. Then Assumption~\ref{assumption:detection-regions}\eqref{item:finite-intervals} holds whenever $\max_{i \le n} k_i^3 (c_n^- c_n^+)^4 = o(n)$.
+More generally, let $\Delta_i$ the minimal distance between any two interval endpoints in $A_i$.
+Then,
+if $A_i = \cup_{j=1}^{k_i}[t_{i,j}^-, t_{i,j}^+]$, we have that 
+$P_\theta(A_i) \ge \Delta_i \sum_{j=1}^{k_i} F(t_{i,j}^-)$ and $1-P_\theta(A_i) \ge \Delta_i \sum_{j=1}^{k_i} F(t_{i,j}^+)$.
+Therefore, As long as $\sum_{j=1}^{k_i} F(t_{i,j}^-)$ and $\sum_{j=1}^{k_i} F(t_{i,j}^+)$ are bounded away from zero, \ref{assumption:detection-regions}\eqref{item:finite-intervals} holds whenever $ \max_{i \le n} k_i^3 \Delta_i^{-4} = o(n)$.
 

### 2022-05-02 distributed-estimation.tex
example for A2-(ii)

@@
 $P_\theta(A_i) \ge \Delta_i \sum_{j=1}^{k_i} F(t_{i,j}^-)$ and $1-P_\theta(A_i) \ge \Delta_i \sum_{j=1}^{k_i} F(t_{i,j}^+)$.
-Therefore, As long as $\sum_{j=1}^{k_i} F(t_{i,j}^-)$ and $\sum_{j=1}^{k_i} F(t_{i,j}^+)$ are bounded away from zero, \ref{assumption:detection-regions}\eqref{item:finite-intervals} holds whenever $ \max_{i \le n} k_i^3 \Delta_i^{-4} = o(n)$.
+Therefore, \ref{assumption:detection-regions}\eqref{item:finite-intervals} holds whenever $ \max_{i \le n} k_i^3 \Delta_i^{-4} = o(n)$ as long as $\sum_{j=1}^{k_i} F(t_{i,j}^-)$ and $\sum_{j=1}^{k_i} F(t_{i,j}^+)$ are bounded away from zero.
 

### 2022-05-04 distributed-estimation.tex
arranged appendix in two-columns

@@
 $P_\theta(A_i) \ge \Delta_i \sum_{j=1}^{k_i} F(t_{i,j}^-)$ and $1-P_\theta(A_i) \ge \Delta_i \sum_{j=1}^{k_i} F(t_{i,j}^+)$.
-Therefore, \ref{assumption:detection-regions}\eqref{item:finite-intervals} holds whenever $ \max_{i \le n} k_i^3 \Delta_i^{-4} = o(n)$ as long as $\sum_{j=1}^{k_i} F(t_{i,j}^-)$ and $\sum_{j=1}^{k_i} F(t_{i,j}^+)$ are bounded away from zero.
+Therefore, \ref{assumption:detection-regions}\eqref{item:finite-intervals} holds whenever $ \max_{i \le n} k_i^3 \Delta_i^{-4} = o(n)$ as long as $\sum_{j=1}^{k_i} F(t_{i,j}^-)$ and $\sum_{j=1}^{k_i} F(t_{i,j}^+)$ are bounded away of zero.
 

### 2022-05-04 proof-lan-distributed.tex
arranged appendix in two-columns

@@
   \begin{align}
-    \label{eqn:bound-density-diffs}
-    |f(b) - f(a)| \le 2 \sqrt{\lip(f) P([a, b])}
+    & \label{eqn:bound-density-diffs}
+    |f(b) - f(a)| \le 2 \sqrt{\lip(f) P([a, b])} \\
+    & 
     ~~ \mbox{and} ~~
-    |\dPtheta(A)| \le 2 \sqrt{k \lip(f)}.
+    |\dPtheta(A)| \le 2 \sqrt{k \lip(f)}. \nonumber
   \end{align}
@@
   \mbox{int}\Theta$,
-  \begin{equation*}
-    \sum_{i = 1}^n \log \frac{P_{\theta + h_n/\sqrt{n}}(B_i)}{
-      P_\theta(B_i)}
-    = \frac{h}{\sqrt{n}}
-    \sum_{i = 1}^n \score_\theta(B_i)
-    - \frac{h^2}{4n} \sum_{i = 1}^n \var(\score_\theta(B_i))
-    - \frac{h^2}{4n} \sum_{i = 1}^n \score_\theta(B_i)^2
+  \begin{align*}
+    & \sum_{i = 1}^n \log \frac{P_{\theta + h_n/\sqrt{n}}(B_i)}{
+      P_\theta(B_i)} \\
+    & \qquad = \frac{h}{\sqrt{n}}
+    \sum_{i = 1}^n \score_\theta(B_i) - \frac{h^2}{4n} \sum_{i = 1}^n \var(\score_\theta(B_i)) \\
+    & \qquad \qquad - \frac{h^2}{4n} \sum_{i = 1}^n \score_\theta(B_i)^2
     + o_P(1).
-  \end{equation*}
+  \end{align*}
   If additionally
@@
 $\{P_\theta\}$ is LAN with precision $\kappa(\theta)$, then
-\begin{equation*}
-  \liminf_{c \to \infty} \liminf_n \sup_{\norm{\tau - \theta} \le
-    c / \sqrt{n}} \E_\tau\left[L(\sqrt{n}(\theta_n - \tau))\right]
-  \ge \E[L(Z / \sqrt{\kappa(\theta)})]
-\end{equation*}
+\begin{align*}
+  \liminf_{c \to \infty} & \liminf_n \sup_{\norm{\tau - \theta} \le
+    c / \sqrt{n}} \E_\tau\left[L(\sqrt{n}(\theta_n - \tau))\right] \\
+  & \qquad  \ge \E[L(Z / \sqrt{\kappa(\theta)})]
+\end{align*}
 for any symmetric quasi-convex loss $L$, where $Z \sim \normal(0, 1)$.
@@
 \begin{align*}
-  P_{\theta + h}(A)
+  & P_{\theta + h}(A)
   - P_\theta(A)
-  & = \int_a^b (f(z - \theta - h) - f(z - \theta)) dz \\
-  & = -\int_a^b \int_0^h f'(z - \theta - u) du dz \\
-  & = -\int_0^h \int_a^b f'(z - \theta - u) dz du \\
-  & = \int_0^h f(a - \theta - u) - f(b - \theta - u) du \\
-  & \lesseqgtr \int_0^h (f(a - \theta) - f(b - \theta)) du
+   = \int_a^b (f(z - \theta - h) - f(z - \theta)) dz \\
+  & \qquad = -\int_a^b \int_0^h f'(z - \theta - u) du dz \\
+  & \qquad = -\int_0^h \int_a^b f'(z - \theta - u) dz du \\
+  & \qquad = \int_0^h f(a - \theta - u) - f(b - \theta - u) du \\
+  & \qquad \lesseqgtr \int_0^h (f(a - \theta) - f(b - \theta)) du
   \pm 2 \int_0^h \lip(f) u du \\
-  & = \left[f(a - \theta) - f(b - \theta)\right] h \pm \lip(f) h^2.
+  & \qquad = \left[f(a - \theta) - f(b - \theta)\right] h \pm \lip(f) h^2.
 \end{align*}
@@
 Then we always have
-\begin{equation}
+\begin{align}
   \label{eqn:interval-length-thing}
-  P([a, b])
-  \ge \int_a^b f(z) dz
-  \ge \int_a^b \max\{f(b) - L (b - z), f(a) - L(z - a), 0\} dz.
-\end{equation}
+  & P([a, b]) \ge \int_a^b f(z) dz \\
+  & \quad \ge \int_a^b \max\{f(b) - L (b - z), f(a) - L(z - a), 0\} dz. \nonumber
+\end{align}
 If $f(a) + f(b) \ge L (b - a)$, then the point $\hat{z} =
@@
     (f(b) - L (b - z)) dz} \\
-  & = \frac{f(a) + f(b)}{2}
+  & = \medmath{\frac{f(a) + f(b)}{2}
   \left(\frac{b - a}{2}\right)
   - L \left(\frac{b - a}{2} \right)^2
-  + \frac{(f(b) - f(a))^2}{4L},
+  + \frac{(f(b) - f(a))^2}{4L}},
 \end{align*}
@@
   \frac{(f(b) - f(a))^2}{4L}
-  & \le \frac{f(b) + f(b)}{2} \frac{b - a}{2}
-  - L \left(\frac{b - a}{2}\right)^2
-  + \frac{(f(b) - f(a))^2}{4L}
-  \le P([a, b]).
+  & \le \frac{f(b) + f(b)}{2} \frac{b - a}{2} \\
+  & \qquad - L \left(\frac{b - a}{2}\right)^2
+  + \frac{(f(b) - f(a))^2}{4L} \\
+  & \le P([a, b]).
 \end{align*}
@@
   & \ge \int_a^{a + \frac{f(a)}{L}}
-  (f(a) - L (z - a)) dz
-  + \int_{b - \frac{f(b)}{L}}^b (f(b) - L (b - z)) dz \\
+  (f(a) - L (z - a)) dz \\
+  & \qquad + \int_{b - \frac{f(b)}{L}}^b (f(b) - L (b - z)) dz \\
   & = \frac{f(a)^2}{L}
@@
 union of $k$ intervals, the expansion~\eqref{eqn:expansion-dPtheta} yields
-\begin{equation*}
-  \left(\sqrt{P_{\theta + h}(A)} -
+\begin{align*}
+  & \left(\sqrt{P_{\theta + h}(A)} -
   \sqrt{P_\theta(A)} - \half h \score_\theta(A) \sqrt{P_\theta(A)}
-  \right)^2
-  \le
+  \right)^2 \\
+  & \quad \le
   \left(
@@
   \right)^2,
-\end{equation*}
+\end{align*}
 valid for $h$ such that
@@
   \begin{align}
-    \nonumber \left(\sqrt{P_{\theta + h}(A)} -
+    & \nonumber \left(\sqrt{P_{\theta + h}(A)} -
     \sqrt{P_\theta(A)} - \half
-    h \score_\theta(A) \sqrt{P_\theta(A)}\right)^2
-    & \le
+    h \score_\theta(A) \sqrt{P_\theta(A)}\right)^2 \\
+    & \nonumber \quad \le
     \left(\frac{h^2 k \cdot \lip(f)}{2 \sqrt{P_\theta(A)}}
@@
       P_\theta(A)^{3/2}}\right)^2 \\
-    & \le \frac{C}{P_\theta(A)} \left[k^2 \lip^2(f)
+    & \quad \le \frac{C}{P_\theta(A)} \left[k^2 \lip^2(f)
       + \score_\theta(A)^2
@@
   and similarly, we have
-  \begin{equation}
-    \left(\sqrt{P_{\theta + h}(A^c)} -
+  \begin{align}
+    & \left(\sqrt{P_{\theta + h}(A^c)} -
     \sqrt{P_\theta(A^c)} - \half
-    h \score_\theta(A^c) \sqrt{P_\theta(A^c)}\right)^2
-    \le \frac{C}{P_\theta(A^c)}
+    h \score_\theta(A^c) \sqrt{P_\theta(A^c)}\right)^2 \nonumber \\
+    & ~~ \le \frac{C}{P_\theta(A^c)}
     \left[k^2 \lip^2(f)
@@
       \right] \cdot h^4. 
-  \end{equation}
+  \end{align}
 \end{subequations}
@@
 \begin{align}
-  \lefteqn{\var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
-    \le 
+\label{eqn:var-wni-expansion}
+  & \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right) \\
+    & \quad \le C \frac{k_i^2 \lip^2(f) + \score_\theta(A_i)^2
+      + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
+    \cdot \frac{h_n^4}{n^2} \nonumber \\
+    & \qquad + C \frac{k^4 \lip^4(f)}{
+      P_\theta(A_i)^3 P_\theta(A_i^c)^3}
+    \frac{h_n^8}{n^4} \nonumber \\
+  & \quad \le 
   C \frac{k_i^2 \lip^2(f) + \score_\theta(A_i)^2
   + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
-    \cdot \frac{h_n^4}{n^2}
-    + C \frac{k^4 \lip^4(f)}{
-      P_\theta(A_i)^3 P_\theta(A_i^c)^3}
-    \frac{h_n^8}{n^4}} \nonumber \\
-  & \qquad\qquad\qquad\qquad\qquad \le 
-  C \frac{k_i^2 \lip^2(f) + \score_\theta(A_i)^2
-  + \score_\theta(A_i^c)^2}{P_\theta(A_i) P_\theta(A_i^c)}
-  \cdot \frac{h_n^4}{n^2}
-  + C \frac{k^4 \lip^4(f)}{
+  \cdot \frac{h_n^4}{n^2} \\
+  & \qquad + C \frac{k^4 \lip^4(f)}{
     P_\theta(A_i)^3 P_\theta(A_i^c)^3}
   \frac{h_n^8}{n^4}
-  \label{eqn:var-wni-expansion}
 \end{align}
 whenever
-\begin{equation*}
-  \frac{h}{\sqrt{n}} \max\{\score_\theta(A_i),
+\begin{align*}
+  & \frac{h}{\sqrt{n}} \max\{\score_\theta(A_i),
   \score_\theta(A_i^c)\}
-  \le \frac{1}{4}
-  ~~ \mbox{and} ~~
+  \le \frac{1}{4} \\
+  & ~~ \mbox{and} ~~
   \frac{k_i h_n^2}{n} \lip^2(f)
   \le \frac{\min\{P_\theta(A_i), P_\theta(A_i^c)\}}{4}
-\end{equation*}
+\end{align*}
 Now, we use
@@
 inequality~\eqref{eqn:var-wni-expansion} give that
-\begin{equation*}
-  \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
+\begin{align*}
+  & \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
    \le C \cdot
   \left[\frac{k_i^2}{P_\theta(A_i) P_\theta(A_i^c)}
-    \frac{1}{n}
-    + \frac{k_i}{P_\theta(A_i) P_\theta(A_i^c)}
+    \frac{1}{n} \right. \\
+    & \left. \qquad + \frac{k_i}{P_\theta(A_i) P_\theta(A_i^c)}
     \frac{1}{n}
@@
     \frac{1}{n^3}\right] \frac{1}{n},
-\end{equation*}
+\end{align*}
 where $C < \infty$ depends only on $\lip(f)$ and $h_n$ (both of which are
@@
 thus implies that $\E[\score_\theta(B_i)] = 0$ and
-\begin{equation}
-  \label{eqn:summed-variances-to-zero}
-  \var\left(\sum_{i = 1}^n W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
+\begin{align}
+  & \var\left(\sum_{i = 1}^n W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
+  \right) \nonumber \\
+  & \qquad = \sum_{i = 1}^n \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
   \right)
-  = \sum_{i = 1}^n \var\left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)
-  \right)
-  \to 0.
-\end{equation}
+  \to 0. \label{eqn:summed-variances-to-zero}
+\end{align}
 
@@
 \begin{align*}
-  \sum_{i = 1}^n \E[W_{n,i}]
-  & = 2\sum_{i = 1}^n
-  \left(\int \sqrt{p_n(b)} \sqrt{p(b)} d\mu_i(b) - 1 \right)
-  = -\sum_{i = 1}^n \int \left(\sqrt{p_n(b)} - \sqrt{p(b)}\right)^2
+  & \sum_{i = 1}^n \E[W_{n,i}]
+  = 2\sum_{i = 1}^n
+  \left(\int \sqrt{p_n(b)} \sqrt{p(b)} d\mu_i(b) - 1 \right) \\
+  & \quad = -\sum_{i = 1}^n \int \left(\sqrt{p_n(b)} - \sqrt{p(b)}\right)^2
   d\mu_i(b) \\
-  & = -\frac{h_n^2}{4 n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
+  & \quad = -\frac{h_n^2}{4 n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2] \\
+  & \qquad 
   - \sum_{i = 1}^n \int \left(\sqrt{p_n(b)} - \sqrt{p(b)}
   - \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}\right)^2 d\mu_i(b) \\
-  & \qquad \qquad ~
+  & \qquad \medmath{
   - \sum_{i = 1}^n \int \left(\sqrt{p_n(b)} - \sqrt{p(b)}
   - \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}\right)
-  \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}d\mu_i(b) \\
+  \frac{h_n}{\sqrt{n}} \score_\theta(b) \sqrt{p(b)}d\mu_i(b)} \\
   & = -\bigg(\frac{h^2}{4n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]\bigg)
@@
 Therefore, we obtain
-\begin{equation*}
-  \sum_{i = 1}^n W_{n,i}
-  = \sum_{i = 1}^n \left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
-  + \frac{h_n}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
-  = -\frac{h^2}{4n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
+\begin{align*}
+   \sum_{i = 1}^n W_{n,i} & = \sum_{i = 1}^n \left(W_{n,i} - \frac{h_n}{\sqrt{n}} \score_\theta(B_i)\right)
+  + \frac{h_n}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i) \\
+  & = -\frac{h^2}{4n} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
   + \frac{h}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
   + o_P(1),
-\end{equation*}
+\end{align*}
 where we have used that $h_n \to h$.
@@
 \begin{align*}
-  \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
-  & = 2 \sum_{i = 1}^n \log\left(1 + \half W_{n,i}\right) \\
-  & = \sum_{i = 1}^n W_{n,i}
+  & \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
+  = 2 \sum_{i = 1}^n \log\left(1 + \half W_{n,i}\right) \\
+  & \qquad  = \sum_{i = 1}^n W_{n,i}
   - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2
@@
 \begin{align}
-  \nonumber
-  \left| \half W_{n,i} \right|
-  & \leq \half \left| \score_\theta(B_i) \right|
-  \frac{h_n}{\sqrt{n}}
-  + \left|\frac{h_n^2}{n} \frac{k_i \lip(f)}{p(B_i)}
+  &\left| \half W_{n,i} \right|
+   \leq \half \left| \score_\theta(B_i) \right|
+  \frac{h_n}{\sqrt{n}} \nonumber \\
+  & \qquad + \left|\frac{h_n^2}{n} \frac{k_i \lip(f)}{p(B_i)}
   + \frac{h_n^2}{n} \score_\theta(B_i)^2
-  + \frac{ h_n^4}{n^2} \frac{k_i^2 \lip(f)^2}{p(B_i)^2}\right| \\
-  & = \half \score_\theta(B_i)
-  \frac{h_n}{\sqrt{n}} +
+  + \frac{ h_n^4}{n^2} \frac{k_i^2 \lip(f)^2}{p(B_i)^2}\right| \nonumber \\
+  & \quad = \half \score_\theta(B_i)
+  \frac{h_n}{\sqrt{n}} \nonumber \\
+  & \qquad + 
   C \left|\frac{\sqrt{k_i}}{\sqrt{n} p(B_i)}
@@
 Consequently $\max_i W_{n,i} \to 0$, so that
-\begin{equation}
+\begin{align}
   \label{eqn:almost-at-the-end}
   \sum_{i = 1}^n \log \frac{p_n(B_i)}{p(B_i)}
-  = \frac{h_n}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
-  - \frac{1}{4} \sum_{i = 1}^n \E[\score_\theta(B_i)^2]
-  - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2 + o_P(1).
-\end{equation}
+  & = \frac{h_n}{\sqrt{n}} \sum_{i = 1}^n \score_\theta(B_i)
+  - \frac{1}{4} \sum_{i = 1}^n \E[\score_\theta(B_i)^2] \\
+  & \qquad - \frac{1}{4} \sum_{i = 1}^n W_{n,i}^2 + o_P(1). \nonumber
+\end{align}
 
@@
 that $|\score_\theta(B_i)| \le C \sqrt{k_i} / p(B_i)$ from
-Lemma~\ref{lemma:derivative-bounds},
-the
-expansion~\eqref{eqn:max-wni-zero}
-yields
+Lemma~\ref{lemma:derivative-bounds}, the 
+expansion~\eqref{eqn:max-wni-zero} yields
 \begin{align*}
@@
     \frac{k_i^{3/2}}{p(A_i)(1 - p(A_i)) \sqrt{n}}
-    + \frac{k_i^{3/2}}{p(A_i)^2 (1 - p(A_i))^2 \sqrt{n}}
-    + \frac{k_i^2}{p(A_i)(1 - p(A_i))} \frac{1}{n^{3/2}}
+    + \frac{k_i^{3/2}}{p(A_i)^2 (1 - p(A_i))^2 \sqrt{n}} \right. \\
+    & \left. ~~ \qquad + \frac{k_i^2}{p(A_i)(1 - p(A_i))} \frac{1}{n^{3/2}}
     \right] \\
-  & \qquad ~ +
+  & \quad \quad +
   \frac{C}{n}
   \left[\frac{k_i^2}{p(A_i)(1 - p(A_i))} \frac{1}{n}
-    + \frac{k_i}{p(A_i)^3(1 - p(A_i))^3} \frac{1}{n}
+    + \frac{k_i}{p(A_i)^3(1 - p(A_i))^3} \frac{1}{n} \right. \\
+    & \left. ~~ \qquad 
     + \frac{k_i^4}{p(A_i)^3 (1 - p(A_i))^3} \frac{1}{n^3} \right],

### 2022-05-04 proof-no-distributed.tex
arranged appendix in two-columns

@@
 We now claim that 
-if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. Indeed, for such $\theta$ we have
+if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. 
+Indeed, for such $\theta$ we have
 \begin{align}
@@
 & = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
-\frac{ \left(\sum_{k=1}^{K}  f(\theta - t^+_{i,k})- f(\theta - t^-_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)\right)} \nonumber \\
+\frac{ \left(\sum_{k=1}^{K}  f(\theta - t^+_{i,k})- f(\theta - t^-_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)} \nonumber \\
+& \qquad \times \frac{1} {\left(1-\sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)\right)} \nonumber \\
 & 
-+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(t^+_{i,k}-\theta) - f(t^-_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)\right)} \nonumber \\
-& \overset{(a)}{\leq}
++ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(t^+_{i,k}-\theta) - f(t^-_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)} \nonumber \\
+& \qquad \times \frac{1} {\left(1-\sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)\right)} \nonumber \\
+& \le
 \frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
@@
 \end{align}
-where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} with $\delta =0$, and the fact that for $i \in S_n(\theta, \epsilon)$, 
+where the last transition follows from Lemma~\ref{lem:bound_intervals_delta} with $\delta =0$ and the fact that for $i \in S_n(\theta, \epsilon)$, 
 \begin{equation*}

### 2022-05-04 proof-sgd.tex
arranged appendix in two-columns

@@
   \label{corollary:polyak-juditsky}
-  Let $\varphi : \R \to \R$ and $\{Z_i\}$ be i.i.d.\ \newtext{zero-mean} random
+  Let $\varphi : \R \to \R$ and $\{Z_i\}$ be i.i.d.\ zero-mean random
   variables, and
@@
 condition~(iii) excepting inequality~\eqref{eqn:local-hessian-psi}. For
-that, note that as $f$ is Lipschitz near 0 with constant $\lip_0(f)$, we
+that, note that as $f$ is Lipschitz near $0$ with constant $\lip_0(f)$, we 
 have for small $x$ that
-% AK: Here I changed \pm to \leq and \geq
-\begin{equation*}
-  \psi(x) = 2 \int_0^x f(-t) dt
-  \leq 2 \int_0^x \left[f(0) + \lip_0(f) t \right] dt
-  = 2 f(0) x + \lip_0(f) x^2
-  = \psi'(0) x + \lip_0(f) x^2,
-\end{equation*}
-\begin{equation*}
-  \psi(x) = 2 \int_0^x f(-t) dt
+\begin{align*}
+  \psi(x) & = 2 \int_0^x f(-t) dt
+  \leq 2 \int_0^x \left[f(0) + \lip_0(f) t \right] dt \\
+  & = 2 f(0) x + \lip_0(f) x^2 = \psi'(0) x + \lip_0(f) x^2,
+\end{align*}
+\begin{align*}
+  \psi(x) & = 2 \int_0^x f(-t) dt
   \geq 2 \int_0^x \left[f(0) - \lip_0(f) t \right] dt
-  = 2 f(0) x - \lip_0(f) x^2
-  = \psi'(0) x - \lip_0(f) x^2,
-\end{equation*}
+  \\
+  & = 2 f(0) x - \lip_0(f) x^2 = \psi'(0) x - \lip_0(f) x^2,
+\end{align*}
 so that condition~(iii) holds.
@@
 quasi-convex loss $L$ and $c < \infty$,
-\begin{equation}
-  \label{eqn:limit-law-regular}
+\begin{align}
   \limsup_n \sup_{\norm{h} \le c}
-  \E_{P_{\theta + h/\sqrt{n}}}
-  \left[L(\sqrt{n}(T_n - \theta - h / \sqrt{n}))\right]
-  = \E[L(W)] ~~ \mbox{for~}W \sim Q
-\end{equation}
+  & \E_{P_{\theta + h/\sqrt{n}}}
+  \left[L(\sqrt{n}(T_n - \theta - h / \sqrt{n}))\right] \nonumber \\
+  & = \E[L(W)] ~~ \mbox{for~}W \sim Q \label{eqn:limit-law-regular}
+\end{align}
 (see Beran~\cite{beran1995role}, Eq.~(4.2)).
@@
   \begin{align*}
-    \ex{ \left| \varphi(Z) - \varphi(x + Z) \right| }
-    \leq 2 \Prob\left( |Z_1| \le |x|  \right)
-    = 2 \int_{-|x|}^{|x|} f(t) dt
+    & \ex{ \left| \varphi(Z) - \varphi(x + Z) \right| }
+    \leq 2 \Prob\left( |Z_1| \le |x|  \right) \\
+    & \quad = 2 \int_{-|x|}^{|x|} f(t) dt
     \le 4 f(0)|x| + 2 \int_{-|x|}^{|x|}
-    \lip(f) t dt
-    = 4 f(0) |x| + 2 \lip(f) x^2
+    \lip(f) t dt \\
+     & \quad = 4 f(0) |x| + 2 \lip(f) x^2
   \end{align*}
@@
   \begin{align*}
-\newtext{ \E_p[\varphi(Z_1) \score_0(Z_1)] } & = 
+& \newtext{ \E_p[\varphi(Z_1) \score_0(Z_1)] } = 
     \int_{\R} \varphi(x) f'(x ) dx
     = \int_{\R} \sgn(x) f'(x ) dx\\
-     &  =
+     & \quad  =
     \int_0^\infty f'(x ) dx
@@
   \begin{align}
+    & \Delta_i^1  = \Delta_{i-1}^1 - \gamma_i \psi'(0) \Delta_{i-1}^1 - \gamma_i \varphi(Z_i), \qquad
+    \Delta_0^1 = \Delta_0 \nonumber\\
+    & \bar{\Delta}^1_n = \frac{1}{n}\sum_{i=0}^{n-1} \Delta^1_i.
     \label{eqn:polyak-expansion_lem1_alg}
-    & \Delta_i^1  = \Delta_{i-1}^1 - \gamma_i \psi'(0) \Delta_{i-1}^1 - \gamma_i \varphi(Z_i), \qquad
-    \Delta_0^1 = \Delta_0\\
-    & \bar{\Delta}^1_n = \frac{1}{n}\sum_{i=0}^{n-1} \Delta^1_i.
-    \nonumber
   \end{align}
@@
   \begin{align*}
-    \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }
-    & = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
-    & = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0
+    & \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 } \\
+     & \quad = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
+    & \quad = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0
   \end{align*}
@@
   - \Delta_i^1$ satisfies
-  \begin{equation*}
-  \delta_i = \delta_{i-1} - \gamma_i \psi'(0) \delta_{i-1} + \gamma_i \left( \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i) \right),
-  \end{equation*}
+  \begin{align*}
+  & \delta_i = \delta_{i-1} - \gamma_i \psi'(0) \delta_{i-1}  \\
+  & \qquad + \gamma_i \left( \psi'(0) \Delta_{i-1}  + \varphi(Z_i) - \varphi(\Delta_{i-1} + Z_i) \right),
+  \end{align*}
   where $\delta_0 = 0$. Applying Lemma~\ref{lemma:polyak-expansion} with the
@@
   \begin{align}
-    \sqrt{n}\bar{\delta}_n
-    & = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1}
+    & \sqrt{n}\bar{\delta}_n
+    = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1}
     \left( \frac{1}{\psi'(0)} + w_i^n \right)  \xi_i  \nonumber \\
-    & = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1}
+    & \quad = \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1}
     \left( \frac{1}{\psi'(0)} + w_i^n \right)
@@
     \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}
-    + w_i^n \right)
+    + w_i^n \right) \label{eq:PJ_proof2} \\
+    & \qquad \qquad \times 
     \left( \psi(\Delta_{i-1})  + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i)
-    \right) \label{eq:PJ_proof2}
+    \right) \nonumber 
   \end{align}
@@
   \begin{align}
-    \E[\epsilon_i^2 \mid \mc{F}_{i-1}]
-    & = \E[(\psi(\Delta_{i-1}) + \varphi(Z_i)
+    & \E[\epsilon_i^2 \mid \mc{F}_{i-1}] \nonumber \\
+    & \quad = \E[(\psi(\Delta_{i-1}) + \varphi(Z_i)
       - \varphi(\Delta_{i-1} + Z_i))^2 \mid \mc{F}_{i-1}]
     \nonumber \\
-    & \le 2 \psi(\Delta_{i-1})^2
+    & \quad  \le 2 \psi(\Delta_{i-1})^2
     + 2 \E[(\varphi(\Delta_{i-1} + Z_i) - \varphi(Z_i))^2 \mid \mc{F}_{i-1}]
     \nonumber \\
-    & \le
+    & \quad \le
     K \left[|\Delta_{i-1}|^{1 + \lambda}
@@
   and so inequality~\eqref{eqn:bound-psi-error-expectations} gives that
-  \begin{equation*}
-    \E\bigg[\sum_{i = 1}^\infty \frac{1}{i}
+  \begin{align*}
+    & \E\bigg[\sum_{i = 1}^\infty \frac{1}{i}
       |\varepsilon_i|^2 \indic{\tau_R > n} \bigg]
     \le K \sum_{i = 1}^\infty \frac{\gamma_i^\lambda}{i}
-    < \infty
+    < \infty \\
+    & 
     ~~ \mbox{so} ~~
@@
     ~ \mbox{a.s.}
-  \end{equation*}
+  \end{align*}
 by Condition~\eqref{eqn:lazy-gamma}. 
@@
 with the preceding display, give the joint convergence
-\begin{equation*}
-  \left(\sqrt{n} \bar{\Delta}_n, \sum_{i=1}^n \log \frac{P_{h_n/\sqrt{n}}}{P_0}(Z_i)
-  \right)
-  \cd \normal \left( \left(0,-\frac{h^2}{2} I_0 \right),
-  \begin{pmatrix}
+\begin{align*}
+  & \left(\sqrt{n} \bar{\Delta}_n, \sum_{i=1}^n \log \frac{P_{h_n/\sqrt{n}}}{P_0}(Z_i)
+  \right) \cd \normal \left(\mu, \Sigma \right), \\
+\end{align*}  
+where
+\begin{align*}
+  \mu & = \left(0,-\frac{h^2}{2} I_0 \right), ~~~\mbox{and} \\
+  \Sigma & = \begin{pmatrix}
     \frac{\chi(0)}{\psi'(0)^2} & \frac{-h}{ \psi'(0)}
@@
     & h^2 I_0
-  \end{pmatrix}  \right).
-\end{equation*}
+  \end{pmatrix}.
+\end{align*}
 Le Cam's third lemma \cite[Exm. 6.7]{VanDerVaart98} then implies the
@@
 \end{equation*}
-Thus for any $h_t$ we have
+Thus, for any $h_t$ we have
 \begin{align*}
-  \int \left(\frac{s_{\theta + t h_t}(x) - s_\theta(x)}{t}\right)^2
-  d\mu(x)
-  & \le \int \int_0^1 (h_t^\top \dot{s}_{\theta + u t h_t})^2 du
+  & \int \left(\frac{s_{\theta + t h_t}(x) - s_\theta(x)}{t}\right)^2
+  d\mu(x) \\
+  & \qquad \le \int \int_0^1 (h_t^\top \dot{s}_{\theta + u t h_t})^2 du
   d\mu \\
-  & = \int_0^1 h_t^\top \int
+  & \qquad  = \int_0^1 h_t^\top \int
   \dot{s}_{\theta + u t h_t}\dot{s}_{\theta + u t h_t}^\top
-  d\mu(x) h_t  du
-  = \frac{1}{4} h_t^\top \left(\int_0^1 I_{\theta + u t h_t} du\right) h_t.
+  d\mu(x) h_t  du \\
+  & \qquad = \frac{1}{4} h_t^\top \left(\int_0^1 I_{\theta + u t h_t} du\right) h_t.
 \end{align*}
@@
 \cite[Prop.~2.29]{VanDerVaart98} implies that
-\begin{equation*}
-  \lim_{t \to 0}
+\begin{align*}
+  & \lim_{t \to 0} 
   \frac{1}{t^2}
   \int \left(s_{\theta + t h_t}(x) - s_\theta(x)
-  - t h^\top \dot{s}_\theta(x)\right)^2 d\mu(x)
-  = \lim_{t \to 0}
+  - t h^\top \dot{s}_\theta(x)\right)^2 d\mu(x) \\
+  & ~~ = \lim_{t \to 0}
   \int \left(\frac{s_{\theta + t h_t}(x) - s_\theta(x)}{t}
@@
   = 0,
-\end{equation*}
+\end{align*}
 completing the proof.

### 2022-05-04 uniform-are-weirdos.tex
finished response and revision
arranged appendix in two-columns

@@
 Therefore, setting the number of bins $m = \sqrt{n}$ and
-the resolution $\epsilon = 2 \log n / n$, 
+the resolution $\epsilon = \log n / n$, 
 \begin{align}
@@
   \sup_{|\theta| \le \log n} P_\theta\left(|\theta_n\init - \theta| \ge
-  \frac{8 \log n}{\sqrt{n}}\right) \le \frac{1}{n^4}.
+  \frac{4 \log n}{\sqrt{n}}\right) \le \frac{1}{n^2}.
 \end{align}
@@
 event that $|\theta_n\init - \theta| \le \frac{8 \log n}{\sqrt{n}}$)
-\begin{equation*}
-  P_\theta(|\theta_n - \theta|
+\begin{align*}
+  & P_\theta(|\theta_n - \theta|
   \ge 2 \epsilon_n)
   \le (1 - \epsilon_n)^\frac{n}{m}
-  \le \exp\left(-\frac{n \epsilon_n}{m}\right)
-  = \exp\left(-\frac{32 \sqrt{n} \log n}{m^2}\right).
-\end{equation*}
+  \le \exp\left(-\frac{n \epsilon_n}{m}\right) \\
+  & \quad = \exp\left(-\frac{32 \sqrt{n} \log n}{m^2}\right).
+\end{align*}
 Set $m = 4 n^{1/4}$ to obtain the claimed

### 2022-05-09 ak-bio.tex
arranged appendix in two-columns
update bio

@@
-Alon Kipnis is a Senior Lecturer (Assistant Professor) at the School of Computer Science at Reichman University.
+is a Senior Lecturer (Assistant Professor) at the School of Computer Science at Reichman University.
 Previously, he was a postdoctoral research scholar at the Department of Statistics at Stanford University, advised by David Donoho.
@@
 His research is in the areas of mathematical statistics and information theory.
-He is particularly interested in ambitious machine learning and data science applications of his theoretical work.
-
-Dr.
-Kipnis is the recipient of numerous fellowships and awards, including the Koret foundation postdoctoral fellowship, Stanford's electrical engineering department fellowship, and a prize from the Wolf Foundation.
-His research is in the areas of mathematical statistics and information theory.
